### 2018-10-24 awipev-CO2.Rmd
first commit

---
title: "Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project" 
author: "Jean-Pierre Gattuso and Samir Alliouane"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::html_document:
    theme: paper
    number_sections: false

---
![ ](../fb_server/shinyroot/AWIPEV-CO2/www/AWIPEV-Logo.jpg){width=250px}
```{r set-up, echo=FALSE, warning=FALSE, message=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
library(robfilter)
library(seacarb)
library(gridExtra)
library(reshape2)
library(lubridate)
library(lmtest)
library(grid)
library(viridis)
library(dygraphs)
require("knitr")
library("lmodel2")
library(captioner)
library(xts)
library(seismicRoll)
library(scales)
knitr::opts_chunk$set(echo = TRUE)

fig_nums <- captioner()
table_nums <- captioner(prefix = "Table")

######## function to make regression plot with model I equation in title
ggreg <- function (fit, point_size=2) {
  ggplot(fit$model, aes_string(x = names(fit$model)[2],
                               y = names(fit$model)[1])) +
    geom_point(size = point_size, col = "blue") +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste(title, "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       "; Intercept =",signif(fit$coef[[1]],5 ),
                       "; Slope =",signif(fit$coef[[2]], 5),
                       "; P =",signif(summary(fit)$coef[2,4], 5))) +
    theme(plot.title = element_text(size=7))
}

#################### which.closest function
which.closest <- function(x, table, ...) {
  round(approx(x=table, y=1:length(table), xout=x, ...)$y)
}

#################### Regression function
# function regression plot with model II equation (MA) in title
## Dans labs ajout de la variable title pour mettre title avant chaque graphe
ggreg2 <- function (fit, x, y, point.size=5) { # x and y are the names of the variables
  fit_data <- data.frame(fit$x, fit$y)
  colnames(fit_data) = c(x, y)
reg <- fit$regression.results[2,] #one selects MA only
intercept <- reg$Intercept
slope <- reg$Slope
  ggplot(data = fit_data, aes_string(x = x, y = y)) + 
  geom_point(size = point.size, col = "blue") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "; P =", signif(fit$P.param, 3))) +
    theme(plot.title = element_text(size=7))
}

#################### Mytheme
Mytheme <- function(size_labs = 7, face_font="plain") {
  theme_bw() +
  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face=face_font, size=size_labs),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face=face_font, size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_line(size = 0.25, color="black", linetype="dashed"),
        aspect.ratio = 1 / 2,
        plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")
  )
}

ggplotRegression <- function(fit){

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se= FALSE) +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}
```

```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
d <- read.table("../fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv", header = T, dec = ".", as.is = T, sep = ";", fill = TRUE) 
d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
d$measure_date <- dmy(d$measure_date, tz="UTC")

# Add the flag location: some samples have been collected at the peer. Notes them here.
# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
 # And keep data with flag 0 for FB location
d <- d%>%
  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00", 1,0)
  )
d <- d%>%
  dplyr::filter(location_flag== 0)

# Keep only flag = 2 for at/ct analysis 
# Keep only flag = 2 for pH durafet and seaFET.
d <- d%>%
  dplyr::mutate(ct= replace(ct, qflag_ct != 2, NA),
                at= replace(at, qflag_at != 2, NA),
                pH_s_seafet= replace(pH_s_seafet, qflag_pH_s_seafet != 2, NA),
                pH_s_durafet= replace(pH_s_durafet, qflag_pH_s_durafet != 2, NA))

# Mercury chloride correction (Dickson et al. 2007, SOP3a)
# AT
d$at <- d$at * 1.0002
#CT
d$ct <- d$ct * 1.0002

# Fill "at/ct" to all line with same day.
at_ct_mean <- d %>% 
  group_by(datetime)%>%
  dplyr::summarize(at_mean = mean(at, na.rm = T),
                   ct_mean = mean(ct, na.rm = T),
                   at_sd = sd(at, na.rm = T), 
                   ct_sd = sd(ct, na.rm = T)
                   )

d <- left_join(d, at_ct_mean, by='datetime')
# Fill the gaps in at_mean with interpolation
TAinterp <-approx(d$datetime, d$at_mean, xout=d$datetime, method="linear", rule=2)
names(TAinterp) <- c("datetime", "at_mean_interp")
TAinterp <- as.data.frame(TAinterp)
d$at_mean_interp <- TAinterp$at_mean_interp

CTinterp <-approx(d$datetime, d$ct_mean, xout=d$datetime, method="linear", rule=2)
names(CTinterp) <- c("datetime", "ct_mean_interp")
CTinterp <- as.data.frame(CTinterp)
d$ct_mean_interp <- CTinterp$ct_mean_interp

# Conversion of spectro pH to a same T°
pH_seafet <- d %>%
  dplyr::filter(!is.na(pH_s_seafet))
pH_seafet <- pH_seafet %>%
  dplyr::mutate(pH_s_seafet_temp_field = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_field, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$salinity_field,Pt=0,Sit=0))

pH_durafet <- d %>%
  dplyr::filter(!is.na(pH_s_durafet))
pH_durafet <- pH_durafet %>%
  dplyr::mutate(pH_s_durafet_temp_field = pHinsi(pH=pH_durafet$pH_s_durafet,ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_field, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$salinity_field,Pt=0,Sit=0))

# create separate seafet/durafet df to join to initial "d" df
pH_seafet_mean <- pH_seafet%>%
  dplyr::select(datetime,pH_s_seafet_temp_field)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_seafet_temp_field = mean(pH_s_seafet_temp_field, na.rm = T))
pH_durafet_mean <- pH_durafet%>%
  dplyr::select(datetime,pH_s_durafet_temp_field)%>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(pH_s_durafet_temp_field = mean(pH_s_durafet_temp_field, na.rm = T))

#  make means in "d" to have same format and call it "discrete"
discrete <- d %>% 
  dplyr::group_by(datetime) %>% 
  dplyr::summarize(sal = mean(salinity_field, na.rm = T),
            temp = mean(temp_field, na.rm = T),
            at_mean_interp = mean(at_mean_interp, na.rm = T),
            at = mean(at, na.rm = T),
            qflag_at = mean(qflag_at, na.rm = T),
            ct_mean_interp = mean(ct_mean_interp, na.rm = T),
            ct = mean(ct, na.rm = T),
            qflag_ct = mean(qflag_ct, na.rm = T)
            )
# join discrete + seafet/durafet
discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
discrete <- left_join(discrete, pH_durafet_mean, by='datetime')

##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******

# discrete_steffen <- discrete[c(21:72),1:4]
# write.table( discrete_steffen,"../fb_data/DiscreteTA_for_steffen.txt", sep= ",", dec=".", row.names = FALSE)

carb <- carb(15, discrete$at*1e-6, discrete$ct*1e-6,S=discrete$sal, T=discrete$temp, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
discrete$phcalc<- carb$pH
discrete$pco2calc<- carb$pCO2
```

```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
# xx <- read_tsv("../fb_server/ny-alesund/data/old/All_sensors_731101_2016-08-20.txt", skip=16, col_names=TRUE)
load(file = "../fb_server/shinyroot/AWIPEV-CO2/nydata_hour_shiny.Rdata")
#load(file = "../fb_server/shinyroot/AWIPEV-CO2/nydata_shiny.Rdata") #d
# load = d_hour
d_hour <- d_hour %>%
  dplyr::select(-date) %>%
  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT, NA), # beginning of data series for AT
         AT = ifelse(AT == "NaN", NA, AT), #3 columns are character
         pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
         PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
         ) %>%
  dplyr::rename(at_contros=AT, ph_at_contros=pH_AT, pco2_contros=PCO2_corr_contros_filtered, zero_contros=PCO2_Corr_Zero2, 
         sal_fb=Salinity_filtered, temp_fb=Temperature_filtered, pH_durafet=HW_pH1_filtered, temp_insitu=Temp_SBE38_filtered)
```

```{r Combine discrete and continous data, echo=FALSE}
d_all <- d_hour #d_all will be the merger
d_all<- d_all%>%
  dplyr::mutate(month = month(month(datetime)))
# at
closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
discrete$closest_datetime <- d_all$datetime[closest]
# if the closest value is more than 30 min away, then we do not take it
discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
# remove the drop_na() because of seafet/durafet line with na
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, at, qflag_at) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# ct
# closest <- which.closest(discrete$datetime, d$datetime) # closest date and time
# discrete$closest_datetime <- d$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, ct, qflag_ct) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# pH calculated
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, phcalc) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# seaFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_seafet_temp_field) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltINT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltINT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")
# #voltEXT
# discrete2merge <- discrete %>%
#   #drop_na() %>%
#   dplyr::select(closest_datetime, voltEXT) %>%
#   rename(datetime=closest_datetime)
# d_all <- full_join(d_all, discrete2merge, by="datetime")

# duraFET pH 
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pH_s_durafet_temp_field) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

# pCO2
# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
# discrete$closest_datetime <- d_all$datetime[closest]
# # if the closest value is more than 30 min away, then we do not take it
# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
discrete2merge <- discrete %>%
  #drop_na() %>%
  dplyr::select(closest_datetime, pco2calc) %>%
  rename(datetime=closest_datetime)
d_all <- full_join(d_all, discrete2merge, by="datetime")

save(file="../fb_data/d_all.Rdata", d_all)

## bind the voltages and deployment ##

# Duplicate datetime in closest_datetime to do the left_join
d_all$closest_datetime <- d_all$datetime
discrete <- left_join(discrete, d_all%>%dplyr::select(c(closest_datetime, voltEXT, voltINT)), by="closest_datetime")
```

<style type="text/css">

body{ /* Normal  */
      font-size: 18px;
  }
h3{ /* Header 3 */
  font-size: 22px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
h4{ /* Header 4 */
  font-size: 18px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
h5{ /* Header 5 */
  font-size: 16px;
  <!-- font-family: "Times New Roman", Times, serif; -->
  color: DarkBlue;
}
</style>

#{.tabset .tabset-fade .tabset-pills}

##Infos

###**Introduction**
<div style="text-align: justify">  
The AWIPEV-CO2 project aims at starting the first time series for the carbonate chemistry in the Arctic Ocean as part of the AWIPEV Underwater Observatory. It comprises two components: (1) continuous real-time measurements and (2) discrete measurements. The rationale is that discrete measurements are absolutely needed to calibrate and validate the sensors.

###**AWIPEV Underwater Observatory**
<div style="text-align: justify">  
The AWIPEV Underwater Observatory has been deployed at Ny-Alesund (Spitsbergen, 78°55'18N, 11°56'31E) in June 2012. It is part of the German Project COSYNA (Coastal Observation Systems of the Northern- and Arctic Seas), which aims at increasing the availability of continuous real-time data from remote but climatically-sensitive ecosystems. The AWIPEV underwater observatory comprises a fully remote controlled FerryBox system fed with seawater pumped in front of the old peer at 12 m depth. Temperature, salinity, pressure, turbidity, oxygen, chl-*a* fluorescence are measured. Furthermore, an additional remote controlled underwater sensor unit able to profile from 12 m to the surface at any frequency carries additional sensors for salinity, pressure, turbidity, oxygen chl-*a* fluorescence and PAR. The system also comprises an ADCP for continuous measurements of currents and waves. Besides these standard sensors, the underwater unit is equipped with a webcam and stereo-optical device to remotely assess fish and jellyfish populations. The AWIPEV observatory is specifically designed for polar experimental work under extreme conditions including ice coverage and the inaccessibility for about 7 months during polar winter. During this time, the system is remotely controlled and maintained from Germany. All data sampled by the sensors are continuously sent to a central server system at Helgoland Island where the data are stored and processed. The processed data are open access and available at http://codm.hzg.de/codm.

<div style="text-align:center" markdown="1">
  <img  src="../fb_figures/Photos/Outside/Container.png" width="200" height="200">
  <img  src="../fb_figures/Photos/Outside/Intake.png" width="200" height="200">
  <img  src="../fb_figures/Photos/FerryBox/2018-04-17_Ferrybox2.jpg" width="200" height="200">

</div>

###**Continuous and semi-continuous measurements**
<div style="text-align: justify">  
The Arctic version of the Contros-Kongsberg HydroC CO~2~ FT (Carbon Dioxyde partial pressure Flow Through surface water sensor) has been installed in July 2015. Molecules of dissolved CO~2~ diffuse through a thin composite membrane into the internal gas circuit leading to a detector chamber, where the partial pressure of CO~2~ is determined by means of infra-red absorption spectrometry. Concentration-dependent IR light is converted into the output signal from calibration coefficients stored in firmware and data from additional sensors within the gas circuit. The measuring range is 200-1000 uatm, resolution is < 1 uatm and accuracy is +- 1% reading. The sensor is the first instrument in the measuring loop; data are logged every minute. This instrument requires yearly factory calibration; two sensors ara available to allow a continuous time series.

Since February 2016, total alkalinity (AT) is measured every 90 min with a Contros-Kongsberg HydroFIA TA (Total Alkalinity analyser flow through system). Fifty ml of seawater is filtered (0.2 um) using a Contros-Kongsberg cross-flow filter and then acidified using dilute hydrochloric acid (0.1 N). CO~2~ is then flushed out (open-cell titration) and the final pH measured by means of an indicator dye (bromocresol green) and visible absorption spectrometry. Together with salinity and temperature at the time of measurement, the pH reading is used to calculate AT. According to the manufacturer, the measuring range is 400 umol/kg dynamic range, resolution 0.1 umol/kg, accuracy 25 umol/kg (+- 1%) and precision 5 umol/kg (+- 0.2%).

In August 2017, a seaFET Ocean pH sensor (Sea-Bird Scientific) has been added to the UWO. This new sensor continuously measures pH at 11 m using an ISFET (Ion Sensitive Field Effect Transistor). According to the manufacturer, the measuring range is between 6.5 and 9 pH units, initial accuracy is 0.02 pH units and precision is 0.004 pH units. Operating salinity and temperature range are 20 to 40 PSU and 0 to 50°C respectively.

In August 2017, a Durafet III pH electrode connected to a UDA2128 Analyser (Honeywell) was also implemented to the Ferrybox flow-through system. This electrode continuously measures pH, in the Ferrybox, through an ISFET. According to the manufacturer, the measuring range is between 0 and 14 pH units.

##Key plots
```{r whole time series, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
#SAL
sal_fb_xts <- dplyr::select(d_all, datetime, sal_fb)%>%
  dplyr::filter(sal_fb >28)
sal_fb_xts <- as.xts(sal_fb_xts, order.by = sal_fb_xts$datetime)
dygraph(sal_fb_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
      dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "S") %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)
# TEMP Ferrybox SBE45
temp_fb_xts <- dplyr::select(d_all, datetime, temp_fb)
temp_fb_xts <- as.xts(temp_fb_xts, order.by = temp_fb_xts$datetime)
dygraph(temp_fb_xts, group = "awipev", main="Temperature (in Ferrybox)", ylab="Temperature") %>%
      dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "T") %>%
      dyAxis("y", valueRange = c(-2.5, 9.5)) %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)
# TEMP insitu SBE38
temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu)
temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ)", ylab="Temperature") %>%
      dySeries("temp_insitu", color = "blue", strokeWidth = 0, label = "T") %>%
      dyAxis("y", valueRange = c(-2.5, 9.5)) %>%
      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
      dyRangeSelector(height = 30)
# PCO2 
#+ Ajout de la pCO2 corrigé par le script contros (dans R server ny-alesund_cc.R)
pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_contros, PCO2_Corr_filtered)
pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
    dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 2) %>%
    dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30)
# DURAFET 
durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field)
durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30) 
# SEAFET 
seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30)

# to create periods according to TA deployments
TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00", "2018-01-07 00:00:00", "2018-07-31 00:00:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))

at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at)
at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
  #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
  dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[6], to = TAevents[7], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(2100, 2550)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30)

f <- as.data.frame(table(d_all$at))
sum(f$Freq)
# Number of outliers removed in the dataset
# numberOutliers <- length(which((dat_ATnoNA$outliers > 0)))
```

##Total alkalinity

Since we bought the AT analyser (February 2016), numerous problems happened due to a leak of the degassing unit in each analyser and sudden step changes. Last analyser repaired by Contros was installed back in the FB on 2018-07-31. This was the 3rd analyser on site.

We identify four periods (see plot at the end of this page with dark and ligth grey):

- from the set-up of the instrument on **2016-02-23** to **2017-02-09** during which we try to correct for the drift
- from **2017-02-09** to **2017-03-10** during which no drift correction is made, just an offset is applied to correct for the sudden shift in the data
- from the set-up of a new instrument on **2018-01-08** to **2018-06-20**, during which another correction using the discrete samples will be performed. In this period and before to stop it, continuous leakages in the degasing unit happened.
- from the set-up of a repaired unit on **2018-07-31** to **the present days**. Here, the instrument took wrong salinity to perform AT measurements. The cause is not clear yet but Steffen sent to Samir a protocol on 2018-08-24 to correct those data with right salinity. Also, after this issue, since 2018-08-20, bad data were still measured. Steffen diagnosed a "bubble issue" in the indicator tubbings.Steps will be sent to Marine to solve this issue.

###**Filtration of AT data: outliers removing**

Outliers are present because of the cleaning operations made on the FerryBox everydays at 12:00am and 12:00pm. We first removed the outliers using a filter and decided, after a Skype conference with Steffen on September 2016, to:

  - Remove existing filters ( > 2350 µmol/kg).
  - Filter using salinity flag.
  - Filter using pH flag.
  - Not to filter on temperature flag.
  - Apply a 3 data points median filter (no longer used; see despike function in "oce" package)

We decided to use "despike" function as data filter. This filter is done in "ny-alesund_cc.R". Length of runing median is: k = 121 days and the indicator (n times the sd between x and the reference) to consider a data from an outlier is: n = 0.5.

###**Correction of AT data**

Calibration was initially performed twice a year since the analyser was supposed to be stable. Calibration was performed using the internal "calibration mode" against a CRM from A.Dickson (Batch #145, 2016-02-24) right after the instrument was installed and a second time on 2016-09-16. This approch is not longer used since September 2016 (Skype with Contros).

Since this date, the analyser is calibrated by measuring a CRM with the "measurement mode" in order to measure the offset of the instrument. Additionally, discrete seawater are sampled weekly and TA is analysed by SNAPO-CO2.

  - Two methods to correct the drift are available:
    - based on CRMs 
    - based on AT measurement of discrete samples ("references").

####**CRM measurements**

The calibration of the sensor is made against a CRM standard from A. Dickson. We run a standard on the analyser as a regular measurement (measurement mode). Result sof calibrations are shown on the following plot.Dashed lines represent the theoritical value of AT (CRM) and hard lines represent CRM measured AT by the instrument.

```{r CRM measurements, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%",fig.show='hold', fig.align="center"}
calib_analyser <-  read.table("../fb_data/Calibration/TA_#1215/measure_CRM_TA.txt", header = T, dec = ".", as.is = T, sep = ",", fill = TRUE)

# To make the mean 
# Keep dates as Character to plot without date gaps.
calib_analyser3 <- calib_analyser %>%
  dplyr::filter(analyser == "TA3") 
meanTA3 <- calib_analyser3 %>% 
  group_by(day) %>% 
  summarise (meanTA = mean(TA))

melt_calib <- melt(calib_analyser, id.vars=c("analyser", "TA_theo", "datetime", "CRM"), measure.vars=c("TA"))
calib_p <- ggplot()+ 
          geom_point(data= melt_calib, aes(x=datetime, y=value, color=factor(CRM), shape= factor(analyser)) , size=3) +
          scale_color_manual(values=c("blue","red"))+
         # set dashed lines for theoritical CRM
          geom_segment(aes(x=1,xend=20,y=2226.16,yend=2226.16), linetype="dashed", color="blue")+
          annotate("text", x = 11, y = 2228, label = "Batch #145 = 2226.16", color="blue")+
          geom_segment(aes(x=20,xend=23,y=2213.59,yend=2213.59), linetype="dashed", color="red")+
          annotate("text", x = 15.5, y = 2213.59, label = "Batch #159 = 2213.59", color="red")+
        # set hard lines for measured CRM
          geom_segment(aes(x=1,xend=5,y=2254,yend=2254), color="blue") +
          annotate("text", x = 3, y = 2249, label = "2254", color="blue")+
          geom_segment(aes(x=6,xend=10,y=2251.6,yend=2251.6), color="blue") +
          annotate("text", x = 8, y = 2247, label = "2251.6", color="blue")+
          geom_segment(aes(x=11,xend=15,y=2190.4,yend=2190.4), color="blue")+
          annotate("text", x = 14, y = 2195, label = "2190.4", color="blue")+
          geom_segment(aes(x=16,xend=20,y=2203.5,yend=2203.5), color="blue")+
          annotate("text", x = 18, y = 2200, label = "2203.5", color="blue")+
          geom_segment(aes(x=21,xend=23,y=2224.20,yend=2224.20), color="red")+
          annotate("text", x = 22, y = 2230, label = "2224.2", color="red") +
  theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1))+ 
  labs(title= "",y=expression(paste("Total alkalinity (µmoles.",kg^-1,")")), x="Date", color= "CRM",shape= "Deployed instrument")

ggsave("../fb_figures/TA_Analyser/Calibration/TA_calibration_CRM.png", calib_p, units="cm")
print(calib_p)
```

####**Discrete samples ("references")**

On 2018-04-19, Steffen sent his answer concerning the drift correction during the period February 2016 to March 2017. Within this one year period, the analyser was running, except the first week of May 2016. Discrete samples were collected and 3 CRMs were measured which was deemed not enough (see below). He suggested to base the correction on the AT of discrete ("reference") samples.

> "I chose the discrete reference samples due to the fact that those cover the entire working range including time, salinity and also provide a broader data basis for this kind of correction. Also, when looking at the uncertainty below, I fear that the three CRM measurements over 5 month are not sufficient enough for such a drift determination."

A linear regression was performed based on the difference between the measured (analyzer) and discrete samples. Discrete samples were matched with the AT measured by the analyser. If there is no measurement coincident with a discrete sample, a linear interpolation was made between the two data surrounding the discrete sample data. The differences between the measured (analyzer) and analysed ("reference") data was plotted as a function of time.

This approach was performed:

  - on the same period than in Steffen email's (**First period**, 2016-02-23 to 2017-02-09)
  - and during the **third period**, with the new analyzer (2018-01-07 to 2018-06-20)

##### **First period**

```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
#Interpolation of continuous sensor data to match a maximum of reference data.
TAinterp_all <-approx(d_all$datetime, d_all$AT_filtered, xout=d_all$datetime, method="linear", rule=2)
names(TAinterp_all) <- c("datetime", "AT_filtered_interp")
TAinterp_all <- as.data.frame(TAinterp_all)
d_all$AT_filtered_interp <- TAinterp_all$AT_filtered_interp

# create a column with difference between sensor and ref
d_all <- d_all%>%
  dplyr::mutate(diff_ta =  at-AT_filtered_interp )
# create colum with instrument number
d_all <- d_all %>% 
  dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
                            ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
                            ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-07-31 00:00:00", "TA3", 
                            ifelse(datetime >= "2018-07-31 00:00:00" , "TA4", "TA0")))))

#remove outliers
calib_ta_first <- d_all%>%
  dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta,TA_period)%>%
  dplyr::filter(TA_period =="TA1" & !is.na(at))
  #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
# & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))

# Parameters of regression
fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime)
at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6)
at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2)
at_intercept1 <- round(fit$coefficients[[1]], digits= 2)
```

The slope is: `r at_slope_TA1` x 3600 x 24 x 365.24 = `r at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red.

```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# Plot of regression
p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + 
    geom_point() + geom_smooth(method='lm', se=FALSE)+ 
    geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
  geom_hline(yintercept = 0, linetype="dashed" )+
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     "Slope =",signif(fit$coef[[2]], 5),
                     "P =",signif(summary(fit)$coef[2,4], 5))) + 
  ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
print(p)
ggsave("../fb_figures/TA_Analyser/Calibration/Diff_ref_TA_first_period.png", p, units="cm")
```

#####**Third period**

```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"}

#remove outliers and remove period without TA measurements 
calib_ta_third <- d_all%>%
  dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
  dplyr::filter(TA_period == "TA3" & !is.na(at))

# Parameters of regression
fit <- lm( data=calib_ta_third, diff_ta ~ datetime)
at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8)
at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2)
at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici.
```

The slope is in days: `r at_slope_TA3` x 3600 x 24 x 365.24 = `r at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.

```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
# Plot of regression
p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
    geom_point() + geom_smooth(method='lm', se=FALSE)+ 
    #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
   geom_hline(yintercept = 0, linetype="dashed" )+
  geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
  #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
  scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
print(p)
ggsave("../fb_figures/TA_Analyser/Calibration/Diff_ref_TA_third_period.png", p, units="cm")
```

#####**Second period**

```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}

#remove outliers and remove period without TA measurements 
calib_ta_second <- d_all%>%
  dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
  dplyr::filter(TA_period == "TA2" & !is.na(at))

mean_offset <- mean(calib_ta_second$diff_ta)

```
For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r mean_offset` µmoles.kg~-1~) was added to TA value as an offset.

#### **Final TA corrected data (Regression)**

The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition.
It is clear that these corrected data (in green) cannot be used for periods 1 to 3. The jury is still out for period 4. The issue of salinity must be clarified before an assessment can be made.

```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
# Correction for the 3 periods is apply
d_all <- d_all%>%
  dplyr::mutate(datetime_reg = as.numeric(datetime), 
                at_intercept = ifelse(TA_period == "TA1", at_intercept1, 
                               ifelse(TA_period == "TA3", at_intercept3, NA)),
                at_slope = ifelse(TA_period == "TA1", at_slope_TA1, 
                           ifelse(TA_period == "TA3", at_slope_TA3, NA))
                )

d_all <- d_all%>%
 dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT_filtered + (d_all$datetime_reg * d_all$at_slope + at_intercept)),
                                        ifelse(TA_period == "TA2", (AT_filtered + mean_offset),
                                        ifelse(TA_period == "TA3", (AT_filtered + (datetime_reg * at_slope)+ at_intercept), NA))))

at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at,TA_reg_corrected)
at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
  dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[6], to = TAevents[7], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(1600, 2450)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30)

```

###**Discrete total alkalinity (reference) vs salinity relationship**

In the previous part, missing TA were interpolated with a linear model. This does not reflect the natural variability of TA. For this reason, missing TA is now calculated from salinity data by making a relationship between the same reference TA samples as in the previous part and salinity data.

```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
d_all_at_discrete <- d_all %>% #  To remove an outlier in red 
  dplyr::select(datetime, month,closest_datetime, at, sal_fb)%>%
  dplyr::filter( !is.na(at) & !is.na(sal_fb) & sal_fb >30)

  #at != "2307.05" & sal_fb > 28, !is.na(at))

# d_all_Out <- d_all %>% #  To keep an outlier in red 
#   filter(at == "2307.05")

#fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal_fb)
fit <- lm(data = d_all_at_discrete, at ~ sal_fb)
slope_s_at <- fit$coefficients[[2]]
intercept_s_at <- fit$coefficients[[1]]
# at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()

at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
  geom_text( aes(color=factor(month))) +
  scale_color_discrete(guide="none")+
    labs(x="Salinity", y="Discrete TA", color = "Months") +  
    theme(plot.title = element_text(size=7))  +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste("Discrete TA vs Salinity", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       "; Intercept =",signif(fit$coef[[1]],5 ),
                       "; Slope =",signif(fit$coef[[2]], 5),
                       "; P =",signif(summary(fit)$coef[2,4], 5))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + theme_bw()

ggsave("../fb_figures/Discrete_TA_salinity_AWIPEV.png", at_s, width=15, height =10, units="cm")

# Salinity is a predictor of AT -> using the regression defined above
d_all$at_calc <- slope_s_at * d_all$sal_fb + intercept_s_at
```
The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r round(summary(fit)$r.squared, digits=2)`. Need to compare with other relationships from the literature.

```{r plot Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%", fig.align="center"}
# PLOT
print(at_s)
```

#### **Final TA re-calculated data (Salinity relationship)**
```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
  dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[6], to = TAevents[7], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(2100, 2450)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30)

# Property plots : x= at (discretes data), y = at_contros/at_contros_rep/at_calibrated/at_calibrated_rep
```

## *p*CO~2~
The HydroC CO~2~ FT sensor (S/N: CO2FT-0215-001) was bought from Contros (Germany) in February 2015. It was deployed in the FerryBox with other sensors since July 2015, the 20th. A spare sensor (S/N: CO2FT-0515-001) was also bought in March 2015 and carried to Ny-Alesund to replace the first one in case of calibration or problem. Both sensors were set on a cycle according to informations given by Contros in March 2015 (c.kirbach@contros.eu):

30 min warm up --> (3 min Zeroing + 15 min Flushing + 702 minutes Measuring) --> (3 + 15 + 702)...

  - **Warm-up**: running without sending data. Done once, after the sensor is turned on. Time can vary depending on T water and power supply.
  - **Flushing**: running normally. Phase of equilibration that depends on the sensor configuration and the environment conditions. Warmer the water is and larger the flow is in front of the membrane, faster will be the response time and shorter will be the flush time. Recovery data of the sensor signal from the zeroing interval happen in this time. During this step the flush flag is set to “1” for simplifier extraction of the flush values.
  - **Measuring**: running normally and all other flags are on “0”. Sensor is fully equilibrated and T is stable.

During those steps (except zeroing) the sensor runs normally. Equilibration between the gas inside the sensor and the dissolved gas in ambient water takes place. Gas is led to NDIR unit while T control is running.

### **Corrected Contros vs calculated *p*CO~2~ data**
```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  PCO2_corr_contros ~ pco2calc , nperm = 99)

pco2calc_pCO2_contros_text <-  ggplot(d_all,aes(x=pco2calc, y= PCO2_corr_contros, label = month))+
   geom_text(aes(color = factor(month)))+
  scale_color_discrete(guide="none")+
  geom_line(aes(x = PCO2_corr_contros, y = PCO2_corr_contros), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()

```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(pco2calc_pCO2_contros_text)
ggsave("../fb_figures/pco2calc_pCO2_contros.png", pco2calc_pCO2_contros_text, width=5, height=5, units="cm")
```

### **Final *p*CO~2~ data**

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_contros, PCO2_Corr_filtered)
pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
    dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 2) %>%
    dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
    #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30)
    ```

## pH seaFET

pH is measured continuously by an autonomous seaFET pH sensor. Because of issue, measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17. pH calibration is based on monthly discrete samples that are analysed with spectrophotometric method in Villefranche by Samir Alliouane. When it is not possible to sample at the vicinity of the sensor for practice reasons (in winter), sampling is done in the harbour and is not taken in consideration for calibration for spatial reasons. Calibration was done following the methods and code described in Bresnahan et al. (2014) and adapted to use in R (seacarb package). Deployment periods are difined 15 days before and after the pH spectro sample and are in shading colors on the plot. Within this deployment period, calibration is made with E0 calculation (first plot) and final corrected pH is calculated (second plot).

###**seaFET calibration constante E0**

Plots of E0int25 and E0ext25 returned by the function "pHCalib" for each period of deployement are shown below.

```{r seaFET calibration sf_calib, echo=FALSE, message= FALSE, warning=FALSE, out.width= "60%"}

# deployment period between 2 spectro measurements.
sfPeriod <- d_all%>%
  dplyr::select(datetime, pH_s_seafet_temp_field)%>%
  dplyr::filter(!is.na(pH_s_seafet_temp_field))

sfPeriod <-  sfPeriod %>%
  dplyr::arrange(datetime) %>%
  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600 *24)))%>%
  dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])

#put interval in a list with the start date of seaFET measurements
sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
 #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")

#sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
# set deployment period between 2 spectro measurements.
# add here the new periods sfinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
                                ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
                                ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
                                ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
                                ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
                                       ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07, NA ))))))))

# Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04 (1) and removed from 2018-01-08 to 2018-02-02 (2)
# 1
d_all$phINT_filtered <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phINT_filtered < 8.04, NA, d_all$phINT_filtered) 
d_all$phEXT_filtered <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phEXT_filtered < 8.04, NA, d_all$phEXT_filtered) 
d_all$voltINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltINT < -0.9439, NA, d_all$voltINT) 
d_all$voltEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
# 2
d_all$voltINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltINT)
d_all$voltEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltEXT)
d_all$phINT_filtered <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phINT_filtered)
d_all$phEXT_filtered <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phEXT_filtered)

# # 5th period, pH spectro from 2018-04-16 07:00:00 must fit one  voltINT to calculate E0
# we put the mean of 4 previous days because voltINT was not present.
mean_voltINT_4d <- d_all%>%
  dplyr::filter(datetime >= "2018-04-11" & datetime <= "2018-04-14")%>%
  dplyr::summarise( mean(voltINT, na.rm = TRUE))
mean_voltINT_4d <- as.numeric(mean_voltINT_4d)
d_all$voltINT <- ifelse(d_all$datetime == "2018-04-16 07:00:00" , mean_voltINT_4d, d_all$voltINT)

mean_voltEXT_4d <- d_all%>%
  dplyr::filter(datetime >= "2018-04-11" & datetime <= "2018-04-14")%>%
  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
mean_voltEXT_4d <- as.numeric(mean_voltEXT_4d)
d_all$voltEXT <- ifelse(d_all$datetime == "2018-04-16 07:00:00" , mean_voltEXT_4d, d_all$voltEXT)

# put also a salinity value because FB was off
sal_to_replace <- d_all%>%
  dplyr::filter(datetime >= "2018-04-16 00:00:00" & datetime <= "2018-04-16 23:59:59")%>%
  dplyr::summarise( mean(sal_fb, na.rm = TRUE))
sal_to_replace <- as.numeric(sal_to_replace)
d_all$sal_fb <- ifelse(d_all$datetime == "2018-04-16 07:00:00" , sal_to_replace, d_all$sal_fb)
#interpolation of salinity during the FB off maintenance
sal_fbinterp <-approx(d_all$datetime, d_all$sal_fb, xout=d_all$datetime, method="linear", rule=2)
names(sal_fbinterp) <- c("datetime", "sal_fb_interp")
sal_fbinterp <- as.data.frame(sal_fbinterp)
d_all$sal_fb_interp <- sal_fbinterp$sal_fb_interp

d_all$sal_fb <- ifelse(d_all$datetime > "2018-03-09 00:00:00" & d_all$datetime < "2018-04-16 16:00:00", d_all$sal_fb_interp, d_all$sal_fb)

temp_to_replace <- d_all%>%
  dplyr::filter(datetime >= "2018-04-16 00:00:00" & datetime <= "2018-04-16 23:59:59")%>%
  dplyr::summarise( mean(temp_fb, na.rm = TRUE))
temp_to_replace <- as.numeric(temp_to_replace)
d_all$temp_fb <- ifelse(d_all$datetime == "2018-04-16 07:00:00" , temp_to_replace, d_all$temp_fb)

# put also a temp insi value because FB was off FOR PERIOD ONE 2017-08-24
temp_to_replace <- d_all%>%
  dplyr::filter(datetime == "2017-08-24 12:00:00")%>%
  dplyr::summarise( mean(temp_insitu, na.rm = TRUE))
temp_to_replace <- as.numeric(temp_to_replace)
d_all$temp_insitu <- ifelse(d_all$datetime == "2017-08-24 13:00:00" , temp_to_replace, d_all$temp_insitu)

test <- d_all%>%
  dplyr::filter(datetime=="2017-08-24 13:00:00")
####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_field,
                          calT = d_all$temp_insitu, calSal = d_all$sal_fb )
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

# make the mean of E0 by period of deployement
calib_spectro <- group_by(calib_spectro, deployment_sf) %>%
  summarise(E0int25 = mean(E0int25, na.rm = T),
            E0ext25 = mean(E0ext25, na.rm = T) 
            )
names(calib_spectro) <- c("deployment_sf", "E0int25_sf", "E0ext25_sf")
# add E0 mean to seaFET data per deployment
d_all <-left_join(d_all, calib_spectro,by="deployment_sf" )

#### plot
kk <- melt(calib_spectro, id.vars="deployment_sf")
p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable),size=2) +
  facet_grid(variable~., scales="free_y") + theme_bw() +
  scale_colour_discrete(guide="none")
print(p_calib)
```

###**seaFET pHT calibrated**
pH is measured continuously by an autonomous seaFET pH sensor. Final calibrated seaFET pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
Calibration was done following the methods and code described in Bresnahan *et al.* (2014) using seaFET voltage and spectro measurements.
During the fifth period, seaFET cannot be calibrated because seaFET was not working during the time of reference (pH spectro) sampling (2018-04-16). To solve this calibration, we decided to fit the spectro measurement with a pH mean of 4 previous days.

We also defined a period of malfunction from **2017-12-14** to **2018-02-02**. in the first part of this period, until 2018-01-08, we decided to filter outliers.  In the second part, until the end of the period, data must be removed.

```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE}
####
## calculation of the calibrated pH ##
##       new sf_calc function       ##
####
seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf, 
                        E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu, calSal = d_all$sal_fb_interp)

# bind new calibrated pH data to the seafet data set.
names(seafet_calib) <- c("pHint_tot_sf", "pHext_tot_sf")
d_all <- cbind(d_all, seafet_calib )

# pH seaFET Final
seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field,pHint_tot_sf)
#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
  dyRangeSelector(height = 30)

# Offset between seafet pH and spec pH 
sfoffset <- left_join(sfPeriod[,c(1,2)], d_all%>%dplyr::select(datetime, pHint_tot_sf), by="datetime")
dat <- mutate(sfoffset, diff_pH_sf = pH_s_seafet_temp_field - pHint_tot_sf)
average_offset <- mean(abs(dat$diff_pH_sf), na.rm=TRUE)

plot_offset <- ggplot(data = filter(dat, !is.na(diff_pH_sf))) +
  geom_hline(yintercept=mean(dat$diff_pH_sf, na.rm = TRUE), size=0.3, linetype="dashed", col="red") +
  geom_hline(yintercept=0, size=0.3) +
  geom_point(aes(x = datetime, y = diff_pH_sf), size = 1, colour = "#51C56AFF") +
  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
  scale_x_datetime(date_breaks="month", date_minor_breaks="1 week", labels=date_format("%b %Y")) +
  Mytheme() + theme(panel.grid.major.x = element_blank())

print(plot_offset)

```

## pH durafet

pH is measured continuously by an autonomous durafet pH sensor. Final calibrated durafet pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey). Calibration was done appliying an offset of pH between measured and spectro data per periods.

###**durafet calibration**

```{r durafet calibration, echo=FALSE, message= FALSE, warning=FALSE}
# deployment period between 2 spectro measurements.
durPeriod <- d_all%>%
  dplyr::select(datetime, pH_s_durafet_temp_field)%>%
  dplyr::filter(!is.na(pH_s_durafet_temp_field))

durPeriod <-  durPeriod %>%
  dplyr::arrange(datetime) %>%
  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(durPeriod)])/2* 3600 *24)))%>%
  dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])

#put interval in a list with the start date of seaFET measurements
durinterv <- c( as_datetime("2017-08-24 13:00:00"), durPeriod[,4])

# set deployment period between 2 spectro measurements.
# add here the new periods durinterv[..]
d_all <- d_all %>%
  dplyr::mutate(deployment_dur = ifelse(datetime >= durinterv[1] & datetime <= durinterv[2], 01, 
                                ifelse(datetime >= durinterv[2] & datetime <= durinterv[3], 02, 
                                ifelse(datetime >= durinterv[3] & datetime <= durinterv[4], 03, 
                                ifelse(datetime >= durinterv[4] & datetime <= durinterv[5], 04,
                                ifelse(datetime >= durinterv[5] & datetime <= durinterv[6], 05,
                                ifelse(datetime >= durinterv[6] & datetime <= durinterv[7], 06,
                                ifelse(datetime >= durinterv[7] & datetime <= durinterv[8], 08, NA ))))))))

# Offset between durafet pH and spec pH 
duroffset <- left_join(durPeriod[,c(1,2)], d_all[,c(1,18)], by="datetime")
dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_field - pH_durafet)
average_offset_dur <- round(mean(dat_dur$diff_pH_dur, na.rm=TRUE), digits = 2)
sd_offset_dur <- round(sd(abs(dat_dur$diff_pH_dur), na.rm=TRUE), digits = 2)
n_offset_dur <- length(!is.na(dat_dur$diff_pH_dur))

plot_offset_dur <- ggplot(data = filter(dat_dur, !is.na(diff_pH_dur))) +
  geom_hline(yintercept=mean(dat_dur$diff_pH_dur, na.rm = TRUE), size=0.3, col="red") +
  annotate("text", x = dat_dur$datetime[3], y = -0.16, label = "offset mean", color="red")+
  geom_hline(yintercept=0, size=0.3) +
  geom_point(aes(x = datetime, y = diff_pH_dur), size = 1, colour = "#51C56AFF") +
  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
  scale_x_datetime(date_breaks="month", date_minor_breaks="1 week", labels=date_format("%b %Y")) +
  Mytheme() + theme(panel.grid.major.x = element_blank())

# create offset per period + add this offset per period.
d_all <- d_all%>%
 dplyr::mutate(offset_durafet = ifelse(deployment_dur == 1, dat_dur$diff_pH_dur[1],
                                ifelse(deployment_dur == 2, dat_dur$diff_pH_dur[2],
                                ifelse(deployment_dur == 3, dat_dur$diff_pH_dur[3],
                                ifelse(deployment_dur == 4, dat_dur$diff_pH_dur[4],
                                ifelse(deployment_dur == 5, dat_dur$diff_pH_dur[5],
                                ifelse(deployment_dur == 6, dat_dur$diff_pH_dur[6], 0)))))),
              pH_durafet_corrected = pH_durafet + offset_durafet
              )
# DURAFET 
durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected)
durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
 dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyShading(from =  durinterv[1], to= durinterv[2], color = "#CCCCCC") %>%
    dyShading(from = durinterv[2], to= durinterv[3], color = "#E0E0E0") %>%
    dyShading(from = durinterv[3], to= durinterv[4], color = "#CCCCCC") %>%
    dyShading(from = durinterv[4], to= durinterv[5], color = "#E0E0E0") %>%
    dyShading(from = durinterv[5], to= durinterv[6], color = "#CCCCCC") %>%
    dyShading(from = durinterv[6], to= durinterv[7], color = "#E0E0E0") %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30)

print(plot_offset_dur)
```
The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).

## pHs 
Comparaison is done here with **corrected pHs** (**seaFET**, **durafet** and **calculated** (from AT/CT)) and normalized at 4°C with a total alkalinity of 2273 µmoles.kg-1 (mean data). 
For information, mean temperatures in Ferrybox and *in situ* are repectively 3.5°C and 2.5°C.

###**seaFET / durafet pHs**

```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
# remove sf biofouling period
pH_sf <- d_all %>%
  dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pHint_tot_sf)%>%
  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu), !is.na(temp_fb)) %>%
  dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu, Pinsi=11, S=pH_sf$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

pH_dur <- d_all %>%
  dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pH_durafet_corrected)%>%
  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_insitu))
pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_insitu, Pinsi=11, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

# join pH sf norm + pH dur norm
d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime,pHint_tot_sf_norm4 ), by="datetime")
d_all <- left_join(d_all, pH_dur%>%dplyr::select(datetime,pH_durafet_norm4 ), by="datetime")

fit <- lmodel2(data = d_all,  pHint_tot_sf_norm4 ~ pH_durafet_norm4 , nperm = 99)

pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pHint_tot_sf_norm4, label = month))+
  geom_text( aes(color=factor(month))) + 
 # scale_color_viridis_d(option = "C", guide="none")+
  geom_line(aes(x = pHint_tot_sf_norm4, y = pHint_tot_sf_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH seaFET vs pH durafet, normalized 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 , xlim=c(7.8,8.35), ylim=c(7.8,8.35))+ scale_colour_discrete(guide="none") +
  labs( x="pH durafet, 4°C", y="pH seaFET, 4°C ", color = "Months")  +theme_bw()

print(pdur_sf_norm_text)

durafet_sf_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pHint_tot_sf_norm4)
durafet_sf_contros_xts <- as.xts(durafet_sf_contros_xts, order.by = d_all$datetime)
dygraph(durafet_sf_contros_xts, group = "awipev", main="pH durafet vs pH seaFET at 4°C", ylab="pHT") %>%
    dySeries("pH_durafet_norm4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color =  "red", strokeWidth = 0, pointSize = 2 ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30) 
```

###**calculated / durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal,temp, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

# join pH calc norm + pH dur/sf norm in d_all
d_all <- left_join(d_all, pH_calc[, c(1,6)], by="datetime")

# DURAFET vs CALC
pdur_calc_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pH_calc_norm4, label = month))+
  geom_text( aes(color=factor(month))) + 
  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH calculated vs pH durafet, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
   coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2)) + scale_color_discrete(guide="none")+
  labs(x="pH durafet, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
pdur_calc_norm_text

durafet_calc_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pH_calc_norm4)
durafet_calc_contros_xts <- as.xts(durafet_calc_contros_xts, order.by = d_all$datetime)
dygraph(durafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH durafet, normalized at 4°C", ylab="pHT") %>%
    dySeries("pH_durafet_norm4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_calc_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30)
```

###**calculated / seaFET pHs**
```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
# SEAFET vs CALC
psf_calc_norm_text <-  ggplot(d_all,aes(x=pHint_tot_sf_norm4, y= pH_calc_norm4, label = month))+
  geom_text( aes(color=factor(month))) + 
  scale_color_discrete(guide = "none")+
  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste("pH calculated vs pH seaFET, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
  labs(x="pH seaFET, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
psf_calc_norm_text

seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_norm4, pH_calc_norm4)
seafet_calc_contros_xts <- as.xts(seafet_calc_contros_xts, order.by = d_all$datetime)
dygraph(seafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH seaFET, normalized at 4°C", ylab="pHT") %>%
    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_calc_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30)
```

## SNAPO-CO2
We found that some analysed discrete seawater replicates for AT/CT, performed by SNAPO in Paris sometimes show a large difference between duplicates.
Arbitrary, we decided to take in consideration replicates with a standard deviation smaller than 10 µmoles.kg-1. In the other case (greater than 10 µmoles.kg-1), the closest replicate from the general trend will be kept with qflag_at/qflag_ct of 2 (correct analysis) and the farthest one will be rejected with a flag of 1.
There are exceptions when it is difficult to decide which of the replicates need to be eliminated.

For TA, dupicates's flags that have been changed to 1 are:

- 2015-11-18
- 2016-07-28
- 2016-09-29
- 2016-11-17
- 2016-11-23
- 2016-12-29
- 2017-01-19
- 2017-05-04
- 2018-04-26
- 2018-05-04
- 2018-05-16
- 2018-05-25
- 2018-06-22
- 2018-06-30
- 2018-07-27

For CT, dupicates's flags that have been changed to 1 are:

- 2015-08-06
- 2015-08-13
- 2016-05-12
- 2016-05-16
- 2016-06-16
- 2016-07-28
- 2016-09-08
- 2016-10-27
- 2016-11-17
- 2017-01-19
- 2017-03-02
- 2017-04-27
- 2017-09-17
- 2018-04-26
- 2018-05-04
- 2018-05-12
- 2018-05-25
- 2018-06-30

```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
# use the df at_ct for mean and sd
# creat a new df to calculate the diff between replicate
 diff <- d %>%
    group_by(datetime) %>%
   dplyr::select(datetime, at, ct)%>%   
   dplyr::mutate(at_diff = abs(at - lag(at)),
                 ct_diff = abs(ct - lag(ct)))

pdelta_at_snapo <-ggplot() +
    geom_point(data=diff, aes(x= datetime, y= at_diff)) +
    geom_hline(yintercept= 3, size= 0.6, col="red", linetype="dashed") +
    geom_hline(yintercept= -3, size= 0.6, col="red", linetype="dashed") +
    #annotate("text", x = dat_dur$datetime[3], y = -0.16, label = "offset mean", color="red")+
    labs(title= "AT", x="Time", y="Delta between TA replicates")+
    Mytheme()
pdelta_ct_snapo <-ggplot() +
    geom_point(data=diff, aes(x= datetime, y= ct_diff)) +
    geom_hline(yintercept= 3, size= 0.6, col="red", linetype="dashed") +
    geom_hline(yintercept= -3, size= 0.6, col="red", linetype="dashed") +
    #annotate("text", x = dat_dur$datetime[3], y = -0.16, label = "offset mean", color="red")+
    labs(title= "CT",x="Time", y="Delta between CT replicates")+
    Mytheme()

# DYGRAPH
at_diff_xts <- dplyr::select(diff, datetime, at_diff, at)
at_diff_xts <- as.xts(at_diff_xts, order.by = diff$datetime)
pdelta_at_snapo_dygraph <- dygraph(at_diff_xts, group = "awipev", main="Discrete AT (SNAPO) measurements", ylab="AT") %>%
    dySeries("at_diff", label = "AT delta", color ="red", strokeWidth=0, pointSize=4) %>%
    dySeries("at", label = "AT duplicates", color =  "blue", strokeWidth = 0, pointSize = 2, axis = "y2" ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
    dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=2) %>%
    dyRangeSelector(height = 30)

ct_diff_xts <- dplyr::select(diff, datetime, ct_diff, ct)
ct_diff_xts <- as.xts(ct_diff_xts, order.by = diff$datetime)
pdelta_ct_snapo_dygraph <- dygraph(ct_diff_xts, group = "awipev", main="Discrete CT (SNAPO) measurements", ylab="CT") %>%
    dySeries("ct_diff", label = "CT delta", color ="red", strokeWidth=0, pointSize=4) %>%
    dySeries("ct", label = "CT duplicates", color =  "blue", strokeWidth = 0, pointSize = 2, axis = "y2" ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
    dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=2) %>%
    dyRangeSelector(height = 30)

pdelta_at_snapo
pdelta_at_snapo_dygraph
pdelta_ct_snapo
pdelta_ct_snapo_dygraph
ggsave("../fb_figures/SNAPO/delta_at_awipev_snapo.png", pdelta_at_snapo, units="cm")
ggsave("../fb_figures/SNAPO/delta_ct_awipev_snapo.png", pdelta_ct_snapo, units="cm")
```

##Maintenance
<div style="text-align: justify"> 
- **2018-10-15**: FB is stopped after a seawater leakage. 
- **2018-10-10**: FB is stopped after a seawater leakage. 
- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again. First data were received (high: 2450 and low: 2150) but salinity issue since this time. Uwe/Philipp try to find if this comes from comunication issue with the FB.
- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen.
- **2018-04-17**: seaFET #1005 was changed on the REMOS and seaFET #007 (from Villefranche) was installed. Continuous mode with external power supply was set and internal pack of baterries was removed. Old seaFET will be brought back to France with Samir.
- **2018-04-16**: *p*CO~2~ analyser switching by Uwe and Samir. S/N CO2FT-0515-001 is now installed. Old *p*CO~2~ sensor will be brought back to France with Samir.
- **2018-04-14**: Ferrybox is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.  
- **2018-03-09**: #007 seaFET currently in USA will be sent by seabird to NYA. #1005 seaFET currently in NYA will be sent to USA for update, following all external issues, for free.
- **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet tubings) in Svalbard, maybe due to a power failure over night in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
- **2018-02-02**: Based on Darrell's advices (SeaBird), Philipp implemented the seaFET as: 1h periodic sampling with the following commands: perdival 1h, navg 5, brstsize 1, opermode periodic. 
- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
- **2017-12-29**: "SVL_20171218_010426.dat" from seaFet data was deleted because of bug with its size (0 octect). pH filter was added to "ny_alesund_cc" file for seaFet data (<7.5 and <8.5).
- **2017-10-30**: (13:00 UTC) Durafet holder was changed by Benoit and the new one (made by Uwe) more larger (all the durafet's body is plunge in the seawater) was installed.
- **2017-08-24**: One durafet was installed in the Ferrybox and seaFET #1005 on the REMOS into the field.
- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
- **2017-05-24**: FerryBox was shut down due to many connexion issues...see Philipp's email 24/05/2017 18:17.
- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
- **2017-03-20**: Philipp arrived in NYA to solve the problem.
- **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's email on 2017-03-11 10:40). No more data for all parameters.
- **2017-02-10**: TA cleaning salt crusts.
- **2017-02-09**: TA calibration with CRM at 12:20.
- **2017-02-07**: pCO2 analyser switching by Uwe. S/N CO2FT-0215-001 is now installed.
- **2017-01-31**: Beginning of the 14-days maintenance by Philipp and Uwe. Gaps in data could be present during this period.
- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19 
- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode). Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
 - **2016-09-24**: No data because of maintenance until the 28th. Except for TA wich has data available for this period.
 - **2016-09-20**: Test in the Ferrybox with the seawater. Seawater was "sucked" (not pumped) from 7:40 to 10:00 by a vaccum system in order to test it. This system was installed if the pumps 1 and 2 broke during winter. This is a "plan C". This system is not automatic and we will be informed about its power up in case of emergency. As long as the water is not pumped with this system, we have to monitor the data because changements in gas partial pressure can occur.
 - **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
 - **2016-09-13**: Changement of the *p*CO~2~ S/N CO2FT-0515-001 membrane (Uwe from 4H-Jena).
 - **2016-09-12**: No data because of maintenance until the 18th.
 - **2016-09-10**: No data because of maintenance until the 11th.
 - **2016-07-20**: Cross filter was cleanned by Obs. eng. with 10-15 min tape water flush.
 - **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
 - **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
 - **2016-05-09**: data are back.
 - **2016-05-04**: No data for all parameters because of electricity issues. 
 - **2016-05-01**: No data for TA.
 - **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).
 - **2016-04-23**: FerryBox was shut down by AWI team for maintenance.
 - **2016-02-28**: *p*CO~2~ analyser (S/N CO2FT-0215-001) was sent to calibration and the second *p*CO~2~ analyser (S/N: CO2FT-0515-001) have been installed.
 - **2016-02-23**: FerryBox was switched on by AWI team after maintenance.
 - **2015-12-20**: FerryBox was shut down because of pump issues. Waiting for the maintenance in February.
 - **2015-11-27**: The ferrybox was down from Nov. 18th until today Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader AWIPEV 2015-11-27 12:57). Tubes frozen.
 - **2015-10-13**: we put back the spike.pCO2 to 600 because data in October reached more than 350 µAtm. We let this like that and we are going to deal with it manually later if needed.
 - **2015-09-28**: we put the spike.pCO2 (detection of peaks: threshold) at 350 to remove anomalies on the 12 and 15 September. We have to monitor data. If data reach this value, then problem.

<div style="text-align:center" markdown="1">
<img  src="../fb_figures/Photos/Salt/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200">
<img  src="../fb_figures/Photos/Salt/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200">
</div>

##Script + data
<div style="text-align: justify">  
Here is reported all important modifications made on *ny-alesund_cc.*. This script is accessible via http://efoce-shiny.obs-vlfr.fr:8787/auth-sign-in.

###**pH seaFET**
- **2018-08-30**: voltINT + phINT were filtered from 2017-12-14 to 2018-01-08 and bad data were removed from 2018-01-08 to 2018-02-02. pH spectro from 2018-04-16 07:00:00 was fitted with a mean of 4 days of voltINT in order to make the calibration for this 5th period.
- **2018-07-30**: Flag location (location_flag) is added in the script to localize seaFET/durafet discrete samples: flag 1 = at the harbor (not takken in consideration) and flag 0 = in the FB for durafet or on site for seaFET (takken in consideration as "normal" sampling"). See seaFET part.

###***p*CO~2~**
- **2018-08-29**: Calibration parameters from #0215-001 were added to "./data/Calibration_pCO2/Data_Processing_sheet_pCO2.csv".
- **2018-04-20**: For *p*CO~2~ Calibration the previous period (N° 4) was added to the script "ny-alesund_cc" line 466.

###**SNAPO**
- **2018-08-30**: flag of 1 AT duplicate (2205) from 2017-08-31 was put to 3 (dosage douteux).

###**Files - server**
- **2018-04-19**: Since "Ferrybox" is on again, the adding to solve the files issues are making not data into d_hour for this period (2018-09-03 to 2018-14-04). This adding was put in comments now. In seaFET data reading, S/N have been changed from 1005 to 0007.
- **2018-03-21**: Files issues. FerryBox instruments are down because of freezing but UWO instrument as seaFET and SBE38 are OK. Removing of one 0 octet file from seaFET20180317_1404 and put back seaFET files from 20180309 to 20180312 in seaFET folder. They were in SBE38 folder...Weird. Additionnal script lines were added in order to deal with the issue of "in situ" created date whereas "Ferrybox" created data ware not. Since "in situ" parameters are running (d df) and not "in ferrybox" parameters (z df), the new datetime lines are not taking in consideration with the left_join function we have to add them during Ferrybox shutdown.
- **2018-03-09**: Script issue solved with first negative values encountred in SBE38 files. We find a regex solution to take "space + space or negative value" in consideration.
- **2017-11-07**: Wrong seaFET files (wrong datetime starting on the 5th September) from 24 to 26 October were fixed. File "SVL_20171024_030426_to_20171026_110425_SeaFet-1005.txt" were created in SeaFet_archive.

<!-- ```{r Graph pour proposal, echo=FALSE, message= FALSE, warning=FALSE} -->

<!-- p_sal <- ggplot() + -->
<!--          geom_point(data=d_all%>%filter(sal_fb >28),aes(x=datetime, y=sal_fb),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Salinity", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_temp_fb <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=temp_fb),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Temperature (in Ferrybox)", x="Time")+ ylim(c(-2.5, 9.5)) + -->
<!--         theme_bw() -->
<!--  p_pco2 <- ggplot() + -->
<!--          geom_point(data=d_all%>%filter(pco2_contros < 450),aes(x=datetime, y=pco2_contros),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Corrected pCO2", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_ta_raw <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=sal_fb),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Salinity", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_sf <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=pHint_tot_sf),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Corrected seaFET pH", x="Time")+ -->
<!--         theme_bw() -->
<!--  p_df <- ggplot() + -->
<!--          geom_point(data=d_all,aes(x=datetime, y=pH_durafet_),size=1, color="blue") + -->
<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
<!--          labs(y = "Corrected seaFET pH", x="Time")+ -->
<!--         theme_bw() -->
<!-- ggsave("../fb_figures/Plots_proposal/p_sal.png", p_sal,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_temp_fb.png", p_temp_fb,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_pco2.png", p_pco2,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_sf.png", p_sf,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_df.png", p_df,width = 15, height = 5 ,units="cm") -->
<!-- ggsave("../fb_figures/Plots_proposal/p_ta.png", p_ta,width = 15, height = 5 ,units="cm") -->

<!--  # DURAFET  -->
<!-- durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field) -->
<!-- durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime) -->
<!-- dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>% -->
<!--     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>% -->
<!--     dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
<!--     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>% -->
<!--     dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>%  -->
<!--     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>% -->
<!--     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
<!--     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>% -->
<!--     dyRangeSelector(height = 30)  -->
<!-- # SEAFET  -->
<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field) -->
<!-- seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime) -->
<!-- dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>% -->
<!--   dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>% -->
<!--   dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
<!--   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>% -->
<!--   dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%  -->
<!--   dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>% -->
<!--     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
<!--     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>% -->
<!--     dyRangeSelector(height = 30)  -->

<!-- ``` -->

### 2018-10-24 awipev-CO2.Rmd
add path
test_jp
ajout path

@@
 
+#define who is the user and define path
+if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
+if (Sys.getenv("LOGNAME") == "samir") path = "../pCloud\\ Sync/exp153_carbonates_point_B/"
+
 ######## function to make regression plot with model I equation in title
@@
 ```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
-d <- read.table("../fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv", header = T, dec = ".", as.is = T, sep = ";", fill = TRUE) 
+d <- read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
 d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")

### 2018-10-24 awipev-CO2.Rmd
changement 2e read.table

@@
 if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
-if (Sys.getenv("LOGNAME") == "samir") path = "../pCloud\\ Sync/exp153_carbonates_point_B/"
+if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"
 
@@
 ```{r CRM measurements, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%",fig.show='hold', fig.align="center"}
-calib_analyser <-  read.table("../fb_data/Calibration/TA_#1215/measure_CRM_TA.txt", header = T, dec = ".", as.is = T, sep = ",", fill = TRUE)
+calib_analyser <-  read.table(paste0(path, "fb_data/Calibration/TA_#1215/measure_CRM_TA.txt"), header = T, dec = ".", as.is = T, sep = ",", fill = TRUE)
 

### 2018-10-24 awipev-CO2.Rmd
changement des paths pour les readtable/loads/ggsave/save

@@
 # xx <- read_tsv("../fb_server/ny-alesund/data/old/All_sensors_731101_2016-08-20.txt", skip=16, col_names=TRUE)
-load(file = "../fb_server/shinyroot/AWIPEV-CO2/nydata_hour_shiny.Rdata")
+load(file = paste0(path, "fb_server/shinyroot/AWIPEV-CO2/nydata_hour_shiny.Rdata"))
 #load(file = "../fb_server/shinyroot/AWIPEV-CO2/nydata_shiny.Rdata") #d
@@
 
-save(file="../fb_data/d_all.Rdata", d_all)
+save(file= paste0(path, "fb_data/d_all.Rdata"), d_all)
 
@@
 
-ggsave("../fb_figures/TA_Analyser/Calibration/TA_calibration_CRM.png", calib_p, units="cm")
+ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/TA_calibration_CRM.png"), calib_p, units="cm")
 print(calib_p)
@@
 print(p)
-ggsave("../fb_figures/TA_Analyser/Calibration/Diff_ref_TA_first_period.png", p, units="cm")
+ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/Diff_ref_TA_first_period.png"), p, units="cm")
 ```
@@
 print(p)
-ggsave("../fb_figures/TA_Analyser/Calibration/Diff_ref_TA_third_period.png", p, units="cm")
+ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/Diff_ref_TA_third_period.png"), p, units="cm")
 ```
@@
 
-ggsave("../fb_figures/Discrete_TA_salinity_AWIPEV.png", at_s, width=15, height =10, units="cm")
+ggsave(paste0(path, "fb_figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =10, units="cm")
 
@@
 print(pco2calc_pCO2_contros_text)
-ggsave("../fb_figures/pco2calc_pCO2_contros.png", pco2calc_pCO2_contros_text, width=5, height=5, units="cm")
+ggsave(paste0(path, "fb_figures/pco2calc_pCO2_contros.png"), pco2calc_pCO2_contros_text, width=5, height=5, units="cm")
 ```
@@
 pdelta_ct_snapo_dygraph
-ggsave("../fb_figures/SNAPO/delta_at_awipev_snapo.png", pdelta_at_snapo, units="cm")
-ggsave("../fb_figures/SNAPO/delta_ct_awipev_snapo.png", pdelta_ct_snapo, units="cm")
+ggsave(paste0(path, "fb_figures/SNAPO/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
+ggsave(paste0(path, "fb_figures/SNAPO/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
 ```

### 2018-10-24 awipev-CO2.Rmd
Added www/logo

@@
 ---
-![ ](../fb_server/shinyroot/AWIPEV-CO2/www/AWIPEV-Logo.jpg){width=250px}
+![ ](www/AWIPEV-Logo.jpg){width=250px}
+
 ```{r set-up, echo=FALSE, warning=FALSE, message=FALSE}

### 2018-10-24 awipev-CO2.Rmd
ajout des paths pour les photos + dossier Images

@@
 ---
-![ ](www/AWIPEV-Logo.jpg){width=250px}
+![ ](Images/AWIPEV-Logo.jpg){width=250px}
 
@@
 <div style="text-align:center" markdown="1">
-  <img  src="../fb_figures/Photos/Outside/Container.png" width="200" height="200">
-  <img  src="../fb_figures/Photos/Outside/Intake.png" width="200" height="200">
-  <img  src="../fb_figures/Photos/FerryBox/2018-04-17_Ferrybox2.jpg" width="200" height="200">
-
+  <img  src="./Images/Outside/Container.png" width="200" height="200">
+  <img  src="./Images/Outside/Intake.png" width="200" height="200">
+  <img  src="./Images/FerryBox/2018-04-17_Ferrybox2.jpg" width="200" height="200">
 </div>
@@
 <div style="text-align:center" markdown="1">
-<img  src="../fb_figures/Photos/Salt/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200">
-<img  src="../fb_figures/Photos/Salt/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200">
+<img  src="./Images/Salt/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200">
+<img  src="./Images/Salt/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200">
 </div>

### 2018-10-24 awipev-CO2.Rmd
ajout des paths pour les photos + dossier Images

@@
 <div style="text-align:center" markdown="1">
-  <img  src="./Images/Outside/Container.png" width="200" height="200">
-  <img  src="./Images/Outside/Intake.png" width="200" height="200">
-  <img  src="./Images/FerryBox/2018-04-17_Ferrybox2.jpg" width="200" height="200">
+  <img  src="./Images/Container.png" width="200" height="200">
+  <img  src="./Images/Intake.png" width="200" height="200">
+  <img  src="./Images/2018-04-17_Ferrybox2.jpg" width="200" height="200">
 </div>
@@
 <div style="text-align:center" markdown="1">
-<img  src="./Images/Salt/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200">
-<img  src="./Images/Salt/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200">
+<img  src="./Images/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200">
+<img  src="./Images/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200">
 </div>

### 2018-11-28 awipev-CO2.Rmd
Maintenance part updated

@@
 
-```{r set-up, echo=FALSE, warning=FALSE, message=FALSE}
+```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
 Sys.setlocale("LC_ALL", "en_US.UTF-8")
@@
 <div style="text-align: justify">
-- **2018-10-15**: FB is stopped after a seawater leakage. 
+
+###**REMOS**
+- **2018-11-24**: REMOS stopped because of an iceberg. At the moment we dont know if instruments are still there/broken.
+
+###**FerryBox**
+- **2018-10-12**: FB is working again. 
 - **2018-10-10**: FB is stopped after a seawater leakage. 
-- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again.
-First data were received (high: 2450 and low: 2150) but salinity issue since this time.
-Uwe/Philipp try to find if this comes from comunication issue with the FB.
-- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen.
-- **2018-04-17**: seaFET #1005 was changed on the REMOS and seaFET #007 (from Villefranche) was installed.
-Continuous mode with external power supply was set and internal pack of baterries was removed.
-Old seaFET will be brought back to France with Samir.
-- **2018-04-16**: *p*CO~2~ analyser switching by Uwe and Samir. S/N CO2FT-0515-001 is now installed. Old *p*CO~2~ sensor will be brought back to France with Samir.
-- **2018-04-14**: Ferrybox is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.  
-- **2018-03-09**: #007 seaFET currently in USA will be sent by seabird to NYA. #1005 seaFET currently in NYA will be sent to USA for update, following all external issues, for free.
+- **2018-10-08**: FB is working again. 
+- **2018-10-05**: FB is stopped after a seawater leakage. 
+- **2018-09-12**: FB is stopped. Problems inland could be the reason. The same day Marine make it working again.
+- **2018-04-14**: FB is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.
 - **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet tubings) in Svalbard, maybe due to a power failure over night in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
-- **2018-02-02**: Based on Darrell's advices (SeaBird), Philipp implemented the seaFET as: 1h periodic sampling with the following commands: perdival 1h, navg 5, brstsize 1, opermode periodic. 
-- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
-- **2017-12-29**: "SVL_20171218_010426.dat" from seaFet data was deleted because of bug with its size (0 octect). pH filter was added to "ny_alesund_cc" file for seaFet data (<7.5 and <8.5).
-- **2017-10-30**: (13:00 UTC) Durafet holder was changed by Benoit and the new one (made by Uwe) more larger (all the durafet's body is plunge in the seawater) was installed.
-- **2017-08-24**: One durafet was installed in the Ferrybox and seaFET #1005 on the REMOS into the field.
-- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
 - **2017-05-24**: FerryBox was shut down due to many connexion issues...see Philipp's email 24/05/2017 18:17.
-- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
-- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
-- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
-- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
-- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
 - **2017-03-20**: Philipp arrived in NYA to solve the problem.
 - **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's email on 2017-03-11 10:40). No more data for all parameters.
-- **2017-02-10**: TA cleaning salt crusts.
-- **2017-02-09**: TA calibration with CRM at 12:20.
-- **2017-02-07**: pCO2 analyser switching by Uwe. S/N CO2FT-0215-001 is now installed.
-- **2017-01-31**: Beginning of the 14-days maintenance by Philipp and Uwe. Gaps in data could be present during this period.
-- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
-- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19 
-- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode).
-Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
+- **2017-01-31**: Beginning of the 14-days FB maintenance by Philipp and Uwe. Gaps in data could be present during this period.
+- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19.
 - **2016-09-24**: No data because of maintenance until the 28th. Except for TA wich has data available for this period.
@@
 As long as the water is not pumped with this system, we have to monitor the data because changements in gas partial pressure can occur.
- - **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
- - **2016-09-13**: Changement of the *p*CO~2~ S/N CO2FT-0515-001 membrane (Uwe from 4H-Jena).
 - **2016-09-12**: No data because of maintenance until the 18th.
 - **2016-09-10**: No data because of maintenance until the 11th.
- - **2016-07-20**: Cross filter was cleanned by Obs. eng. with 10-15 min tape water flush.
- - **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
- - **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
 - **2016-05-09**: data are back.
 - **2016-05-04**: No data for all parameters because of electricity issues. 
- - **2016-05-01**: No data for TA.
- - **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).
 - **2016-04-23**: FerryBox was shut down by AWI team for maintenance.
- - **2016-02-28**: *p*CO~2~ analyser (S/N CO2FT-0215-001) was sent to calibration and the second *p*CO~2~ analyser (S/N: CO2FT-0515-001) have been installed.
 - **2016-02-23**: FerryBox was switched on by AWI team after maintenance.
@@
 - **2015-11-27**: The ferrybox was down from Nov. 18th until today Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader AWIPEV 2015-11-27 12:57). Tubes frozen.
- - **2015-10-13**: we put back the spike.pCO2 to 600 because data in October reached more than 350 µAtm. We let this like that and we are going to deal with it manually later if needed.
- - **2015-09-28**: we put the spike.pCO2 (detection of peaks: threshold) at 350 to remove anomalies on the 12 and 15 September. We have to monitor data. If data reach this value, then problem.
+
+###**TA analyser**
+- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
+- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
+- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again.
+First data were received (high: 2450 and low: 2150) but salinity issue since this time.
+Uwe/Philipp try to find if this comes from comunication issue with the FB.
+- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
+- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
+- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
+- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
+- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
+- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
+- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
+- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
+- **2017-02-10**: TA cleaning salt crusts.
+- **2017-02-09**: TA calibration with CRM at 12:20.
+- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
+- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode).
+Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
+- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
+- **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
+- **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
+- **2016-05-01**: No data for TA.
+- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).
+
+###**pH seaFET**
+- **2018-04-17**: seaFET #1005 was changed on the REMOS and seaFET #007 (from Villefranche) was installed.
+Continuous mode with external power supply was set and internal pack of baterries was removed.
+Old seaFET will be brought back to France with Samir.
+- **2018-03-09**: #007 seaFET currently in USA will be sent by seabird to NYA. #1005 seaFET currently in NYA will be sent to USA for update, following all external issues, for free.
+- **2017-08-24**: seaFET #1005 was installed on the REMOS into the field.
+
+###**Cross-Flow filter**
+- **2018-11-01**: The filter clogged a lot of time even after acid cycles. It was not replaced since its initial installation with the TA analyser. We think to replace it soon.
+- **2016-07-20**: Cross filter was cleanned by Obs. eng. with 10-15 min tape water flush.
+
+###**durafet**
+- **2017-10-30**: (13:00 UTC) Durafet holder was changed by Benoit and the new one (made by Uwe) more larger (all the durafet's body is plunge in the seawater) was installed.
+- **2017-08-24**: durafet was installed.
+
+###***p*CO~2~**
+- **2018-10-31**: *p*CO~2~ analyser (S/N: CO2FT-0215-001) have been installed and *p*CO~2~ analyser (S/N: CO2FT-0515-001) was brought back to France and waiting 2019 fundings to bring it for calibration.
+- **2018-04-16**: *p*CO~2~ analyser switching by Uwe and Samir. S/N CO2FT-0515-001 is now installed. Old *p*CO~2~ sensor will be brought back to France with Samir.
+- **2017-02-07**: pCO2 analyser switching by Uwe. S/N CO2FT-0215-001 is now installed.
+- **2016-09-13**: Changement of the *p*CO~2~ S/N CO2FT-0515-001 membrane (Uwe from 4H-Jena).
+- **2016-02-28**: *p*CO~2~ analyser (S/N CO2FT-0215-001) was sent to calibration and the second *p*CO~2~ analyser (S/N: CO2FT-0515-001) have been installed.
 
@@
 Here is reported all important modifications made on *ny-alesund_cc.*. This script is accessible via http://efoce-shiny.obs-vlfr.fr:8787/auth-sign-in.
+
+###**FerryBox**
+- **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.
 
@@
 See seaFET part.
+- **2018-02-02**: Based on Darrell's advices (SeaBird), Philipp implemented the seaFET as: 1h periodic sampling with the following commands: perdival 1h, navg 5, brstsize 1, opermode periodic. 
+- **2017-12-29**: "SVL_20171218_010426.dat" from seaFet data was deleted because of bug with its size (0 octect). pH filter was added to "ny_alesund_cc" file for seaFet data (<7.5 and <8.5).
 
@@
 - **2018-04-20**: For *p*CO~2~ Calibration the previous period (N° 4) was added to the script "ny-alesund_cc" line 466.
+- **2015-10-13**: we put back the spike.pCO2 to 600 because data in October reached more than 350 µAtm. We let this like that and we are going to deal with it manually later if needed.
+- **2015-09-28**: we put the spike.pCO2 (detection of peaks: threshold) at 350 to remove anomalies on the 12 and 15 September. We have to monitor data. If data reach this value, then problem.
 

### 2018-11-28 awipev-CO2.Rmd
dates and marks added on plots

@@
     dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
+    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
     #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
 # to create periods according to TA deployments
-TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00", "2018-01-07 00:00:00", "2018-07-31 00:00:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
+TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00", 
+              "2018-01-07 00:00:00", "2018-07-31 00:00:00","2018-10-30 18:00:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
 
@@
   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "bottom", color="red") %>%
+  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "bottom", color="red") %>%
   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
@@
   dyShading(from = TAevents[6], to = TAevents[7], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[7], to = TAevents[8], color = "#EDEDED") %>%
   dyAxis("y",valueRange = c(2100, 2550)) %>%
@@
 Also, after this issue, since 2018-08-20, bad data were still measured.
-Steffen diagnosed a "bubble issue" in the indicator tubbings.Steps will be sent to Marine to solve this issue.
+Steffen diagnosed a "bubble issue" in the indicator tubbings.
+Steps will be sent to Marine to solve this issue.
+After this, it was not a bubble.
+We decided to switch off the instrument to save reagents and wait until the comming of Steffen in NYA with a new instrument.
+- new instrument was installed with Steffen on **2018-11-31**.
+This new instrument has a complete new designed membrane which will solve the problem.
+Steffen also developped a TA webInterface to communicate remotly with the analyser.
 
@@
   dyShading(from = TAevents[6], to = TAevents[7], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[7], to = TAevents[8], color = "#EDEDED") %>%
   dyAxis("y",valueRange = c(1600, 2450)) %>%
@@
   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "bottom", color="red") %>%
+    dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "bottom", color="red") %>%
   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
@@
   dyShading(from = TAevents[6], to = TAevents[7], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[7], to = TAevents[8], color = "#EDEDED") %>%
   dyAxis("y",valueRange = c(2100, 2450)) %>%
@@
 - **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
+- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer).
+Samir received password and access from the AWI in order to communicate from France with the TA.
 - **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.

### 2018-11-28 awipev-CO2.Rmd
last text update

@@
 TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00", 
-              "2018-01-07 00:00:00", "2018-07-31 00:00:00","2018-10-30 18:00:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
+              "2018-01-07 00:00:00", "2018-06-20 00:00:00",  "2018-07-31 00:00:00","2018-10-30 18:00:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
 
@@
   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "top") %>%
   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-  dyShading(from = TAevents[6], to = TAevents[7], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[7], to = TAevents[8], color = "#EDEDED") %>%
+  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[8], to = TAevents[9], color = "#EDEDED") %>%
   dyAxis("y",valueRange = c(2100, 2550)) %>%
@@
 In this period and before to stop it, continuous leakages in the degasing unit happened.
-- from the set-up of a repaired unit on **2018-07-31** to **the present days**.
+- from the set-up of a repaired unit on **2018-07-31** to **2018-10-31**.
 Here, the instrument took wrong salinity to perform AT measurements.
@@
 We decided to switch off the instrument to save reagents and wait until the comming of Steffen in NYA with a new instrument.
-- new instrument was installed with Steffen on **2018-11-31**.
+
+A new instrument was installed with Steffen on **2018-10-31**.
 This new instrument has a complete new designed membrane which will solve the problem.
-Steffen also developped a TA webInterface to communicate remotly with the analyser.
+Steffen also developped a TA web interface to communicate remotly with the analyser.
+Samir has all the passwords and ID to connect.
 
@@
   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-  dyShading(from = TAevents[6], to = TAevents[7], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[7], to = TAevents[8], color = "#EDEDED") %>%
+  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[8], to = TAevents[9], color = "#EDEDED") %>%
   dyAxis("y",valueRange = c(1600, 2450)) %>%
@@
   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-  dyShading(from = TAevents[6], to = TAevents[7], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[7], to = TAevents[8], color = "#EDEDED") %>%
+  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[8], to = TAevents[9], color = "#EDEDED") %>%
   dyAxis("y",valueRange = c(2100, 2450)) %>%

### 2018-11-30 awipev-CO2.Rmd
hashtag

@@
     dyRangeSelector(height = 30) 
-
+##
 # to create periods according to TA deployments

### 2018-11-30 awipev-CO2.Rmd
add plot notes

@@
       dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-      dyRangeSelector(height = 30)
+      dyRangeSelector(height = 30, dateWindow= NULL)
 # TEMP Ferrybox SBE45
@@
       dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-      dyRangeSelector(height = 30)
+      dyRangeSelector(height = 30, dateWindow= NULL)
 # TEMP insitu SBE38
@@
       dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-      dyRangeSelector(height = 30)
+      dyRangeSelector(height = 30, dateWindow= NULL)
 # PCO2 
@@
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
-    dyRangeSelector(height = 30)
+    dyRangeSelector(height = 30, dateWindow= NULL)
 # DURAFET 
@@
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30) 
+    dyRangeSelector(height = 30, dateWindow= NULL) 
 # SEAFET 
@@
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30) 
+    dyRangeSelector(height = 30, dateWindow= NULL) 
 ##
@@
   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-    dyRangeSelector(height = 30)
+    dyRangeSelector(height = 30, dateWindow= NULL)
 
@@
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
-    dyRangeSelector(height = 30)
+    dyRangeSelector(height = 30, dateWindow= NULL)
     ```
@@
   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-  dyRangeSelector(height = 30)
+  dyRangeSelector(height = 30, dateWindow= NULL)
 
@@
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30)
+    dyRangeSelector(height = 30, dateWindow= NULL)
 
@@
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30) 
+    dyRangeSelector(height = 30, dateWindow= NULL) 
 ```
@@
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30)
+    dyRangeSelector(height = 30, dateWindow= NULL)
 ```
@@
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=2) %>%
-    dyRangeSelector(height = 30)
+    dyRangeSelector(height = 30, dateWindow= NULL)
 

### 2018-12-28 awipev-CO2.Rmd
text maintenance TA
pH seaFET discrete data + shading period dygraph added

@@
                                 ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
-                                       ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07, NA ))))))))
+                                ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
+                                ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
+                                ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
+                                ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 09, NA )))))))))))
 
@@
   dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
+   dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
   scale_x_datetime(date_breaks="month", date_minor_breaks="1 week", labels=date_format("%b %Y")) +
-  Mytheme() + theme(panel.grid.major.x = element_blank())
+  Mytheme() + theme(panel.grid.major.x = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1))
 
@@
 ###**TA analyser**
+- **2018-12-28**: HCL and BCG cartridges were changed by Marine.
 - **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.

### 2018-12-28 awipev-CO2.Rmd
pH durafet discrete data + shading period dygraph added

@@
 
-#put interval in a list with the start date of seaFET measurements
+#put interval in a list with the start date of durafet measurements
 durinterv <- c( as_datetime("2017-08-24 13:00:00"), durPeriod[,4])
@@
                                 ifelse(datetime >= durinterv[6] & datetime <= durinterv[7], 06,
-                                ifelse(datetime >= durinterv[7] & datetime <= durinterv[8], 08, NA ))))))))
+                                ifelse(datetime >= durinterv[7] & datetime <= durinterv[8], 07,
+                                ifelse(datetime >= durinterv[8] & datetime <= durinterv[9], 08,
+                                ifelse(datetime >= durinterv[9] & datetime <= durinterv[10], 09,
+                                ifelse(datetime >= durinterv[10] & datetime <= durinterv[11], 10, NA )))))))))))
 
@@
   geom_hline(yintercept=mean(dat_dur$diff_pH_dur, na.rm = TRUE), size=0.3, col="red") +
-  annotate("text", x = dat_dur$datetime[3], y = -0.16, label = "offset mean", color="red")+
+  annotate("text", x = dat_dur$datetime[3], y =-0.16, label = "offset mean", color="red")+
   geom_hline(yintercept=0, size=0.3) +
@@
                                 ifelse(deployment_dur == 5, dat_dur$diff_pH_dur[5],
-                                ifelse(deployment_dur == 6, dat_dur$diff_pH_dur[6], 0)))))),
+                                ifelse(deployment_dur == 6, dat_dur$diff_pH_dur[6],
+                                ifelse(deployment_dur == 7, dat_dur$diff_pH_dur[7],
+                                ifelse(deployment_dur == 8, dat_dur$diff_pH_dur[8],
+                                ifelse(deployment_dur == 9, dat_dur$diff_pH_dur[9],
+                                ifelse(deployment_dur == 10, dat_dur$diff_pH_dur[10], 0)))))))))),
               pH_durafet_corrected = pH_durafet + offset_durafet
@@
     dyShading(from = durinterv[6], to= durinterv[7], color = "#E0E0E0") %>%
+   dyShading(from = durinterv[7], to= durinterv[8], color = "#CCCCCC") %>%
+   dyShading(from = durinterv[8], to= durinterv[9], color = "#E0E0E0") %>%
+   dyShading(from = durinterv[9], to= durinterv[10], color = "#CCCCCC") %>%
+   dyShading(from = durinterv[10], to= durinterv[11], color = "#E0E0E0") %>%
     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%

### 2019-01-04 awipev-CO2.Rmd

@@
 ```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
+#
 Sys.setlocale("LC_ALL", "en_US.UTF-8")

### 2019-01-29 awipev-CO2.Rmd
maintenance part updated with calibration date

@@
 ###**TA analyser**
+- **2019-01-26**: Philipp did the TA caibration: T0 with CRM 145.Beginning of a 3-months period. Flow filter was also lifted up and the saewater flow was rised up.
+- **2019-01-16**: Bad data since this date. 
 - **2018-12-28**: HCL and BCG cartridges were changed by Marine.
@@
 ###**Cross-Flow filter**
+- **2019-01-26**: The filter was lifted up in order to fix the flow problem. 
 - **2018-11-01**: The filter clogged a lot of time even after acid cycles. It was not replaced since its initial installation with the TA analyser. We think to replace it soon.

### 2019-01-29 awipev-CO2.Rmd
minor language editing

@@
 We found that some analysed discrete seawater replicates for AT/CT, performed by SNAPO in Paris sometimes show a large difference between duplicates.
-Arbitrary, we decided to take in consideration replicates with a standard deviation smaller than 10 µmoles.kg-1.
+Arbitrarily, we decided to take in consideration replicates with a standard deviation smaller than 10 µmoles.kg-1.
 In the other case (greater than 10 µmoles.kg-1), the closest replicate from the general trend will be kept with qflag_at/qflag_ct of 2 (correct analysis) and the farthest one will be rejected with a flag of 1.
@@
 
-For TA, dupicates's flags that have been changed to 1 are:
+For TA, dulpicates's flags that have been changed to 1 are:
 
@@
 
-For CT, dupicates's flags that have been changed to 1 are:
+For CT, duplicates's flags that have been changed to 1 are:
 
@@
 ggsave(paste0(path, "fb_figures/SNAPO/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
+```
+
+```{r Klara Wolf}
+
 ```
@@
 ###**TA analyser**
-- **2019-01-26**: Philipp did the TA caibration: T0 with CRM 145.Beginning of a 3-months period. Flow filter was also lifted up and the saewater flow was rised up.
+- **2019-01-26**: Philipp did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. Flow filter was also lifted up and the seawater flow has therefore increased.
 - **2019-01-16**: Bad data since this date. 

### 2019-01-29 awipev-CO2.Rmd
extract data for K. Wolf and minor editing

@@
 
+The instrument is usually calibrated against CRM standards after deployment, CRMs are run after 3 months as samples (measurement mode, not calibration mode), an then immediately calibrated again.
+This procedure is repeated every 3 months.
+
 ###**Filtration of AT data: outliers removing**
@@
     - based on AT measurement of discrete samples ("references").
+
+####**Calibration**
+
+- 2019-01-29 14:10: calibration started by Philipp Fisher using CRM XXX (XXXXX umol/kg). The three previous measurements were X1, X2, X3 and the three subsequent measurements were Y1, Y2, Y3.
 
@@
 ## pHs 
-Comparaison is done here with **corrected pHs** (**seaFET**, **durafet** and **calculated** (from AT/CT)) and normalized at 4°C with a total alkalinity of 2273 µmoles.kg-1 (mean data). 
+Comparaison is done here with **corrected pHs** (**seaFET**, **durafet** and **calculated** (from AT/CT)) and normalized at 4°C with a total alkalinity of 2273 µmoles kg-1 (mean data).
 For information, mean temperatures in Ferrybox and *in situ* are repectively 3.5°C and 2.5°C.
@@
 
-```{r Klara Wolf}
-
-```
+<!-- ```{r Klara Wolf} -->
+<!-- wolf <- d_all %>% -->
+<!--   dplyr::select(datetime, PCO2_Corr_filtered, phcalc, pH_calc_norm4) %>% -->
+<!--   dplyr::filter(datetime >= "2016-03-01" & datetime <= "2016-09-30") -->
+<!-- write_csv(path = "wolf.csv", wolf, col_names = TRUE) -->
+<!-- ``` -->
 

### 2019-01-30 awipev-CO2.Rmd
TA periods updated

@@
     dyRangeSelector(height = 30, dateWindow= NULL) 
-##
+# TA
 # to create periods according to TA deployments
 TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00", 
-              "2018-01-07 00:00:00", "2018-06-20 00:00:00",  "2018-07-31 00:00:00","2018-10-30 18:00:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
+              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00", "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
 
@@
   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "bottom", color="red") %>%
+  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
@@
   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "top") %>%
+  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[8], to = TAevents[9], color = "#EDEDED") %>%
-  dyAxis("y",valueRange = c(2100, 2550)) %>%
+  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
+  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
+  dyAxis("y",valueRange = c(2000, 2550)) %>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
 
-```{r CRM measurements, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%",fig.show='hold', fig.align="center"}
+```{r CRM measurements, echo=FALSE, warning=FALSE, message=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
 calib_analyser <-  read.table(paste0(path, "fb_data/Calibration/TA_#1215/measure_CRM_TA.txt"), header = T, dec = ".", as.is = T, sep = ",", fill = TRUE)
@@
                             ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
-                            ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-07-31 00:00:00", "TA3", 
-                            ifelse(datetime >= "2018-07-31 00:00:00" , "TA4", "TA0")))))
+                            ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3", 
+                            ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4", 
+                            ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
+                            ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))
 
@@
   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[8], to = TAevents[9], color = "#EDEDED") %>%
+  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
+  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
   dyAxis("y",valueRange = c(1600, 2450)) %>%
@@
   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[8], to = TAevents[9], color = "#EDEDED") %>%
-  dyAxis("y",valueRange = c(2100, 2450)) %>%
+  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
+  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
+  dyAxis("y",valueRange = c(2000, 2450)) %>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
 ###**FerryBox**
+- **2019-01-17**: FB is stopped until 19th January 
+- **2019-01-11**: FB is stopped until 12th Decmeber. 
+- **2018-12-28**: FB is stopped until 31st Decmeber. 
 - **2018-10-12**: FB is working again. 

### 2019-01-30 awipev-CO2.Rmd

@@
 
-- 2019-01-29 14:10: calibration started by Philipp Fisher using CRM XXX (XXXXX umol/kg). The three previous measurements were X1, X2, X3 and the three subsequent measurements were Y1, Y2, Y3.
+- **2019-01-29 14:10**: Calibration started by Philipp Fisher using CRM 145 (2226.16 umol/kg, 33.572).
+The three previous measurements were 2314.5, 233.8, 2313.7 (analyser stable) and the six subsequent measurements were 2211.8, 2277.5, 2305.4, 2316.6, 2317.9.
+Error was done with CRM salinity (Analyser was not unplugged from the FB).
+Steffen's response:
+> Hence, the serial connection should be cut off or the FB module feeding the analyzer with salinity data should be stopped during calibration.
+The calibration can be recalculated afterwards in the data post-processing.
+However, I see that the calibration resulted in very similar pH values 3.540 (September calibration) and 3.543 (January calibration) with very similar correction factors 1.2371 and 1.2365.
+Also the TA values are very similar to the baseline measurements from before at approx.
+2316 µM.
+So for now, it should be fine.
 

### 2019-02-03 awipev-CO2.Rmd

@@
 # xx <- read_tsv("../fb_server/ny-alesund/data/old/All_sensors_731101_2016-08-20.txt", skip=16, col_names=TRUE)
-load(file = paste0(path, "fb_server/shinyroot/AWIPEV-CO2/nydata_hour_shiny.Rdata"))
+load(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/processed/nydata_hour.Rdata"))
+#load(file = paste0(path, "fb_server/shinyroot/AWIPEV-CO2/nydata_hour_shiny.Rdata"))
 #load(file = "../fb_server/shinyroot/AWIPEV-CO2/nydata_shiny.Rdata") #d
@@
 ## SNAPO-CO2
+Since November 2018, informations on weekly Ferrybox and monthly durafet/seaFET samplings are collected in a online document that can be consulted at anytime:
+
+[weekly and monthly samplings](https://docs.google.com/spreadsheets/d/1bNh9q4bkNoh2ra78XC451EmGb9Q8kMf4ByBnKngeHOg/edit?usp=sharing)
+
 We found that some analysed discrete seawater replicates for AT/CT, performed by SNAPO in Paris sometimes show a large difference between duplicates.
@@
 <div style="text-align: justify">  
-Here is reported all important modifications made on *ny-alesund_cc.*. This script is accessible via http://efoce-shiny.obs-vlfr.fr:8787/auth-sign-in.
+Here is reported all important modifications made on *ny-alesund_cc.*.
+All documents concerning maintenance, tasks to do, calibration... are accessible by the AWIPEV staff on this link with special access:
+
+[wiki document](https://spaces.awi.de/confluence/login.action?os_destination=%2Fpages%2Fviewpage.action%3FspaceKey%3DMOS%26title%3DWater%2Bsampling&permissionViolation=true)
 

### 2019-02-04 presentation/awipev-CO2_pres_2019-02-19.Rmd
first version of presentation

---
title: "AWIPEV-CO2"
subtitle: "First time-series of carbonate chemistry in the Arctic"
author: "Jean-Pierre Gattuso"
date: '`r format(Sys.Date(), "%d %B %Y")`'
#output: slidy_presentation
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
    self_contained: FALSE
    seal: FALSE
---

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
#was in r-setup chunk of test presentation
#knitr::opts_chunk$set(echo = FALSE)
#options(htmltools.dir.version = FALSE)

Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
library(robfilter)
library(seacarb)
library(gridExtra)
library(reshape2)
library(lubridate)
library(lmtest)
library(grid)
library(viridis)
library(dygraphs)
require("knitr")
library("lmodel2")
library(captioner)
library(xts)
library(seismicRoll)
library(scales)
library(widgetframe)

knitr::opts_chunk$set(echo = TRUE)

fig_nums <- captioner()
table_nums <- captioner(prefix = "Table")

#define who is the user and define path
if (Sys.getenv("LOGNAME") == "gattuso") path = "../../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"

######## function to make regression plot with model I equation in title
ggreg <- function (fit, point_size=2) {
  ggplot(fit$model, aes_string(x = names(fit$model)[2],
                               y = names(fit$model)[1])) +
    geom_point(size = point_size, col = "blue") +
    stat_smooth(method = "lm", col = "black") +
    labs(title = paste(title, "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                       "; Intercept =",signif(fit$coef[[1]],5 ),
                       "; Slope =",signif(fit$coef[[2]], 5),
                       "; P =",signif(summary(fit)$coef[2,4], 5))) +
    theme(plot.title = element_text(size=7))
}

#################### which.closest function
which.closest <- function(x, table, ...) {
  round(approx(x=table, y=1:length(table), xout=x, ...)$y)
}

#################### Regression function
# function regression plot with model II equation (MA) in title
## Dans labs ajout de la variable title pour mettre title avant chaque graphe
ggreg2 <- function (fit, x, y, point.size=5) { # x and y are the names of the variables
  fit_data <- data.frame(fit$x, fit$y)
  colnames(fit_data) = c(x, y)
reg <- fit$regression.results[2,] #one selects MA only
intercept <- reg$Intercept
slope <- reg$Slope
  ggplot(data = fit_data, aes_string(x = x, y = y)) + 
  geom_point(size = point.size, col = "blue") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),
              colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(intercept, 3),
                     "; Slope =", signif(slope, 3),
                     "; P =", signif(fit$P.param, 3))) +
    theme(plot.title = element_text(size=7))
}

#################### Mytheme
Mytheme <- function(size_labs = 7, face_font="plain") {
  theme_bw() +
  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face=face_font, size=size_labs),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face=face_font, size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_line(size = 0.25, color="black", linetype="dashed"),
        aspect.ratio = 1 / 2,
        plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")
  )
}

ggplotRegression <- function(fit){

require(ggplot2)

ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
  geom_point() +
  stat_smooth(method = "lm", col = "red", se= FALSE) +
  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
                     "Intercept =",signif(fit$coef[[1]],5 ),
                     " Slope =",signif(fit$coef[[2]], 5),
                     " P =",signif(summary(fit)$coef[2,4], 5)))
}
```

class: center, middle, title-slide

# AWIPEV-CO2: First time-series of carbonate chemistry in the Arctic

### Jean-Pierre Gattuso (1,2), Samir Alliouane (1) & Philipp Fischer (3)
(1) CNRS and Sorbonne University
(2) Iddri
(3) AWI

18 February 2019

![ ](images/AWIPEV-Logo.jpg)

---
# What is ocean acidification?

.pull-left[
- CO2 is an acid gas (it produces acid when combined with water)
- Each of us adds 4 kg CO2 per day to the ocean (increasing acidity, reducing pH)
- The Arctic It will become corrosive for aragonite: 50% in 2050, 100% in 2100
- Critical to document the changes but no time-series until recently
]
.pull-right[
![ ](images/steinacher.png)
]

---
# History and instruments

- Water pumped from 12 m water depth at Ny-Ålesund
- **Since July 2015**: Two pCO2 sensors rotating every year (in FerryBox, 1 min) 
- **Since February 2016**: Total alkalinity analyser (in FerryBox, 90 min) but lots of technical issues
- For calibration and quality insurance: weekly discrete samples for high-precision measurements of dissolved inorganic carbon and total alkalinity
- **Since August 2017**: pH measurements
  - Continuous measurements in fjord water (seaFET)
  - DURAFET pH sensor in the FerryBox
  - Discrete pH samples once a month for calibration
- Regular maintenance twice a year

---
# Data available in near real-time: https://awipev-co2.obs-vlfr.fr

![ ](images/web_page_small.png)

---
```{r whole time series, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
load(file= paste0(path, "fb_data/d_all.Rdata"))
```

```{r pCO2, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
# PCO2
#+ Ajout de la pCO2 corrigé par le script contros (dans R server ny-alesund_cc.R)
pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_contros, PCO2_Corr_filtered)
pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
pco2_dyg <- dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
    dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 2) %>%
    dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>%
    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
    #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
frameWidget(pco2_dyg)
```
---

```{r seafet, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
# SEAFET
seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field)
seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
seafet_dyg <- dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
frameWidget(seafet_dyg)
```

---

```{r at, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
# TA
# to create periods according to TA deployments
TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00", "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))

at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at)
at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
at_dyg <- dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
  #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
  dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
  dyAxis("y",valueRange = c(2000, 2550)) %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
  dyOptions( strokeWidth= 0) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)

frameWidget(at_dyg)

```
```{r others not used, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
#SAL
# sal_fb_xts <- dplyr::select(d_all, datetime, sal_fb)%>%
#   dplyr::filter(sal_fb >28)
# sal_fb_xts <- as.xts(sal_fb_xts, order.by = sal_fb_xts$datetime)
# sal_dyg <- dygraph(sal_fb_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
#       dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "S") %>%
#       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
#       dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
#       dyRangeSelector(height = 30, dateWindow= NULL)
# frameWidget(sal_dyg)

# # TEMP Ferrybox SBE45
# temp_fb_xts <- dplyr::select(d_all, datetime, temp_fb)
# temp_fb_xts <- as.xts(temp_fb_xts, order.by = temp_fb_xts$datetime)
# dygraph(temp_fb_xts, group = "awipev", main="Temperature (in Ferrybox)", ylab="Temperature") %>%
#       dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "T") %>%
#       dyAxis("y", valueRange = c(-2.5, 9.5)) %>%
#       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#       dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
#       dyRangeSelector(height = 30, dateWindow= NULL)
# # TEMP insitu SBE38
# temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu)
# temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
# dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ)", ylab="Temperature") %>%
#       dySeries("temp_insitu", color = "blue", strokeWidth = 0, label = "T") %>%
#       dyAxis("y", valueRange = c(-2.5, 9.5)) %>%
#       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#       dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
#       dyRangeSelector(height = 30, dateWindow= NULL)

# # DURAFET 
# durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field)
# durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
# dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
#     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
#     dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
#     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
#     dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
#     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
#     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
#     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
#     dyRangeSelector(height = 30, dateWindow= NULL) 
```
---
## Relationship between discrete AT and salinity

![ ](images/Discrete_TA_salinity_AWIPEV.png)

---

# Difficulties with logistics
```{r}

```

- Bullet 1
- Bullet 2
- Bullet 3

### 2019-02-04 presentation/xaringan.Rmd
first version of presentation

---
title: "Presentation Ninja"
subtitle: "⚔<br/>with xaringan"
author: "Yihui Xie"
date: "2016/12/12 (updated: `r Sys.Date()`)"
output:
  xaringan::moon_reader:
    lib_dir: libs
    nature:
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
.pull-left[
```{r}
# plot code here
```
]

.pull-right[
Plot output here!
]
---

```{r setup, include=FALSE}
options(htmltools.dir.version = FALSE)
```

background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)

???

Image credit: [Wikimedia Commons](https://commons.wikimedia.org/wiki/File:Sharingan_triple.svg)

---
class: center, middle

# xaringan

### /ʃæ.'riŋ.ɡæn/

---
class: inverse, center, middle

# Get Started

---

# Hello World

Install the **xaringan** package from [Github](https://github.com/yihui/xaringan):

```{r eval=FALSE, tidy=FALSE}
devtools::install_github("yihui/xaringan")
```

--

You are recommended to use the [RStudio IDE](https://www.rstudio.com/products/rstudio/), but you do not have to.

- Create a new R Markdown document from the menu `File -> New File -> R Markdown -> From Template -> Ninja Presentation`;<sup>1</sup>

--

- Click the `Knit` button to compile it;

--

- or use the [RStudio Addin](https://rstudio.github.io/rstudioaddins/)<sup>2</sup> "Infinite Moon Reader" to live preview the slides (every time you update and save the Rmd document, the slides will be automatically reloaded in RStudio Viewer.

.footnote[
[1] 中文用户请看[这份教程](http://slides.yihui.name/xaringan/zh-CN.html)

[2] See [#2](https://github.com/yihui/xaringan/issues/2) if you do not see the template or addin in RStudio.
]

---
background-image: url(`r xaringan:::karl`)
background-position: 50% 50%
class: center, bottom, inverse

# You only live once!

---

# Hello Ninja

As a presentation ninja, you certainly should not be satisfied by the "Hello World" example. You need to understand more about two things:

1. The [remark.js](https://remarkjs.com) library;

1. The **xaringan** package;

Basically **xaringan** injected the chakra of R Markdown (minus Pandoc) into **remark.js**. The slides are rendered by remark.js in the web browser, and the Markdown source needed by remark.js is generated from R Markdown (**knitr**).

---

# remark.js

You can see an introduction of remark.js from [its homepage](https://remarkjs.com). You should read the [remark.js Wiki](https://github.com/gnab/remark/wiki) at least once to know how to

- create a new slide (Markdown syntax<sup>*</sup> and slide properties);

- format a slide (e.g. text alignment);

- configure the slideshow;

- and use the presentation (keyboard shortcuts).

It is important to be familiar with remark.js before you can understand the options in **xaringan**.

.footnote[[*] It is different with Pandoc's Markdown! It is limited but should be enough for presentation purposes. Come on... You do not need a slide for the Table of Contents! Well, the Markdown support in remark.js [may be improved](https://github.com/gnab/remark/issues/142) in the future.]

---
background-image: url(`r xaringan:::karl`)
background-size: cover
class: center, bottom, inverse

# I was so happy to have discovered remark.js!

---
class: inverse, middle, center

# Using xaringan

---

# xaringan

Provides an R Markdown output format `xaringan::moon_reader` as a wrapper for remark.js, and you can use it in the YAML metadata, e.g.

```yaml
---
title: "A Cool Presentation"
output:
  xaringan::moon_reader:
    yolo: true
    nature:
      autoplay: 30000
---
```

See the help page `?xaringan::moon_reader` for all possible options that you can use.

---

# remark.js vs xaringan

Some differences between using remark.js (left) and using **xaringan** (right):

.pull-left[
1. Start with a boilerplate HTML file;

1. Plain Markdown;

1. Write JavaScript to autoplay slides;

1. Manually configure MathJax;

1. Highlight code with `*`;

1. Edit Markdown source and refresh browser to see updated slides;
]

.pull-right[
1. Start with an R Markdown document;

1. R Markdown (can embed R/other code chunks);

1. Provide an option `autoplay`;

1. MathJax just works;<sup>*</sup>

1. Highlight code with `{{}}`;

1. The RStudio addin "Infinite Moon Reader" automatically refreshes slides on changes;
]

.footnote[[*] Not really. See next page.]

---

# Math Expressions

You can write LaTeX math expressions inside a pair of dollar signs, e.g. &#36;\alpha+\beta$ renders $\alpha+\beta$. You can use the display style with double dollar signs:

```
$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$
```

$$\bar{X}=\frac{1}{n}\sum_{i=1}^nX_i$$

Limitations:

1. The source code of a LaTeX math expression must be in one line, unless it is inside a pair of double dollar signs, in which case the starting `$$` must appear in the very beginning of a line, followed immediately by a non-space character, and the ending `$$` must be at the end of a line, led by a non-space character;

1. There should not be spaces after the opening `$` or before the closing `$`.

1. Math does not work on the title slide (see [#61](https://github.com/yihui/xaringan/issues/61) for a workaround).

---

# R Code

```{r comment='#'}
# a boring regression
fit = lm(dist ~ 1 + speed, data = cars)
coef(summary(fit))
dojutsu = c('地爆天星', '天照', '加具土命', '神威', '須佐能乎', '無限月読')
grep('天', dojutsu, value = TRUE)
```

---

# R Plots

```{r cars, fig.height=4, dev='svg'}
par(mar = c(4, 4, 1, .1))
plot(cars, pch = 19, col = 'darkgray', las = 1)
abline(fit, lwd = 2)
```

---

# Tables

If you want to generate a table, make sure it is in the HTML format (instead of Markdown or other formats), e.g.,

```{r}
knitr::kable(head(iris), format = 'html')
```

---

# HTML Widgets

I have not thoroughly tested HTML widgets against **xaringan**. Some may work well, and some may not. It is a little tricky.

Similarly, the Shiny mode (`runtime: shiny`) does not work. I might get these issues fixed in the future, but these are not of high priority to me. I never turn my presentation into a Shiny app. When I need to demonstrate more complicated examples, I just launch them separately. It is convenient to share slides with other people when they are plain HTML/JS applications.

See the next page for two HTML widgets.

---

```{r out.width='100%', fig.height=6, eval=require('leaflet')}
library(leaflet)
leaflet() %>% addTiles() %>% setView(-93.65, 42.0285, zoom = 17)
```

---

```{r eval=require('DT'), tidy=FALSE}
DT::datatable(
  head(iris, 10),
  fillContainer = FALSE, options = list(pageLength = 8)
)
```

---

# Some Tips

- When you use the "Infinite Moon Reader" addin in RStudio, your R session will be blocked by default. You can click the red button on the right of the console to stop serving the slides, or use the _daemonized_ mode so that it does not block your R session. To do the latter, you can set the option

    ```r
    options(servr.daemon = TRUE)
    ```

    in your current R session, or in `~/.Rprofile` so that it is applied to all future R sessions. I do the latter by myself.

    To know more about the web server, see the [**servr**](https://github.com/yihui/servr) package.

--

- Do not forget to try the `yolo` option of `xaringan::moon_reader`.

    ```yaml
    output:
      xaringan::moon_reader:
        yolo: true
    ```

---

# Some Tips

- Slides can be automatically played if you set the `autoplay` option under `nature`, e.g. go to the next slide every 30 seconds in a lightning talk:

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          autoplay: 30000
    ```

--

- A countdown timer can be added to every page of the slides using the `countdown` option under `nature`, e.g. if you want to spend one minute on every page when you give the talk, you can set:

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          countdown: 60000
    ```

    Then you will see a timer counting down from `01:00`, to `00:59`, `00:58`, ... When the time is out, the timer will continue but the time turns red.

---

# Some Tips

- The title slide is created automatically by **xaringan**, but it is just another remark.js slide added before your other slides.

    The title slide is set to `class: center, middle, inverse, title-slide` by default. You can change the classes applied to the title slide with the `titleSlideClass` option of `nature` (`title-slide` is always applied).

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          titleSlideClass: [top, left, inverse]
    ```

--

- If you'd like to create your own title slide, disable **xaringan**'s title slide with the `seal = FALSE` option of `moon_reader`.

    ```yaml
    output:
      xaringan::moon_reader:
        seal: false
    ```

---

# Some Tips

- There are several ways to build incremental slides. See [this presentation](https://slides.yihui.name/xaringan/incremental.html) for examples.

- The option `highlightLines: true` of `nature` will highlight code lines that start with `*`, or are wrapped in `{{ }}`, or have trailing comments `#<<`;

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          highlightLines: true
    ```

    See examples on the next page.

---

# Some Tips

.pull-left[
An example using a leading `*`:

    ```r
    if (TRUE) {
    ** message("Very important!")
    }
    ```
Output:
```r
if (TRUE) {
* message("Very important!")
}
```

This is invalid R code, so it is a plain fenced code block that is not executed.
]

.pull-right[
An example using `{{}}`:

    `r ''````{r tidy=FALSE}
    if (TRUE) {
    *{{ message("Very important!") }}
    }
    ```
Output:
```{r tidy=FALSE}
if (TRUE) {
{{ message("Very important!") }}
}
```

It is valid R code so you can run it. Note that `{{}}` can wrap an R expression of multiple lines.
]

---

# Some Tips

An example of using the trailing comment `#<<` to highlight lines:

````markdown
`r ''````{r tidy=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```
````

Output:

```{r tidy=FALSE, eval=FALSE}
library(ggplot2)
ggplot(mtcars) + 
  aes(mpg, disp) + 
  geom_point() +   #<<
  geom_smooth()    #<<
```

---

# Some Tips

When you enable line-highlighting, you can also use the chunk option `highlight.output` to highlight specific lines of the text output from a code chunk. For example, `highlight.output = TRUE` means highlighting all lines, and `highlight.output = c(1, 3)` means highlighting the first and third line.

````md
`r ''````{r, highlight.output=c(1, 3)}
head(iris)
```
````

```{r, highlight.output=c(1, 3), echo=FALSE}
head(iris)
```

Question: what does `highlight.output = c(TRUE, FALSE)` mean? (Hint: think about R's recycling of vectors)

---

# Some Tips

- To make slides work offline, you need to download a copy of remark.js in advance, because **xaringan** uses the online version by default (see the help page `?xaringan::moon_reader`).

- You can use `xaringan::summon_remark()` to download the latest or a specified version of remark.js. By default, it is downloaded to `libs/remark-latest.min.js`.

- Then change the `chakra` option in YAML to point to this file, e.g.

    ```yaml
    output:
      xaringan::moon_reader:
        chakra: libs/remark-latest.min.js
    ```

- If you used Google fonts in slides (the default theme uses _Yanone Kaffeesatz_, _Droid Serif_, and _Source Code Pro_), they won't work offline unless you download or install them locally. The Heroku app [google-webfonts-helper](https://google-webfonts-helper.herokuapp.com/fonts) can help you download fonts and generate the necessary CSS.

---

# Macros

- remark.js [allows users to define custom macros](https://github.com/yihui/xaringan/issues/80) (JS functions) that can be applied to Markdown text using the syntax `![:macroName arg1, arg2, ...]` or `![:macroName arg1, arg2, ...](this)`. For example, before remark.js initializes the slides, you can define a macro named `scale`:

    ```js
    remark.macros.scale = function (percentage) {
      var url = this;
      return '<img src="' + url + '" style="width: ' + percentage + '" />';
    };
    ```

    Then the Markdown text

    ```markdown
    ![:scale 50%](image.jpg)
    ```

    will be translated to

    ```html
    <img src="image.jpg" style="width: 50%" />
    ```

---

# Macros (continued)

- To insert macros in **xaringan** slides, you can use the option `beforeInit` under the option `nature`, e.g.,

    ```yaml
    output:
      xaringan::moon_reader:
        nature:
          beforeInit: "macros.js"
    ```

    You save your remark.js macros in the file `macros.js`.

- The `beforeInit` option can be used to insert arbitrary JS code before `remark.create()`. Inserting macros is just one of its possible applications.

---

# CSS

Among all options in `xaringan::moon_reader`, the most challenging but perhaps also the most rewarding one is `css`, because it allows you to customize the appearance of your slides using any CSS rules or hacks you know.

You can see the default CSS file [here](https://github.com/yihui/xaringan/blob/master/inst/rmarkdown/templates/xaringan/resources/default.css). You can completely replace it with your own CSS files, or define new rules to override the default. See the help page `?xaringan::moon_reader` for more information.

---

# CSS

For example, suppose you want to change the font for code from the default "Source Code Pro" to "Ubuntu Mono". You can create a CSS file named, say, `ubuntu-mono.css`:

```css
@import url(https://fonts.googleapis.com/css?family=Ubuntu+Mono:400,700,400italic);

.remark-code, .remark-inline-code { font-family: 'Ubuntu Mono'; }
```

Then set the `css` option in the YAML metadata:

```yaml
output:
  xaringan::moon_reader:
    css: ["default", "ubuntu-mono.css"]
```

Here I assume `ubuntu-mono.css` is under the same directory as your Rmd.

See [yihui/xaringan#83](https://github.com/yihui/xaringan/issues/83) for an example of using the [Fira Code](https://github.com/tonsky/FiraCode) font, which supports ligatures in program code.

---

# Themes

Don't want to learn CSS? Okay, you can use some user-contributed themes. A theme typically consists of two CSS files `foo.css` and `foo-fonts.css`, where `foo` is the theme name. Below are some existing themes:

```{r}
names(xaringan:::list_css())
```

---

# Themes

To use a theme, you can specify the `css` option as an array of CSS filenames (without the `.css` extensions), e.g.,

```yaml
output:
  xaringan::moon_reader:
    css: [default, metropolis, metropolis-fonts]
```

If you want to contribute a theme to **xaringan**, please read [this blog post](https://yihui.name/en/2017/10/xaringan-themes).

---
class: inverse, middle, center
background-image: url(https://upload.wikimedia.org/wikipedia/commons/3/39/Naruto_Shiki_Fujin.svg)
background-size: contain

# Naruto

---
background-image: url(https://upload.wikimedia.org/wikipedia/commons/b/be/Sharingan_triple.svg)
background-size: 100px
background-position: 90% 8%

# Sharingan

The R package name **xaringan** was derived<sup>1</sup> from **Sharingan**, a dōjutsu in the Japanese anime _Naruto_ with two abilities:

- the "Eye of Insight"

- the "Eye of Hypnotism"

I think a presentation is basically a way to communicate insights to the audience, and a great presentation may even "hypnotize" the audience.<sup>2,3</sup>

.footnote[
[1] In Chinese, the pronounciation of _X_ is _Sh_ /ʃ/ (as in _shrimp_). Now you should have a better idea of how to pronounce my last name _Xie_.

[2] By comparison, bad presentations only put the audience to sleep.

[3] Personally I find that setting background images for slides is a killer feature of remark.js. It is an effective way to bring visual impact into your presentations.
]

---

# Naruto terminology

The **xaringan** package borrowed a few terms from Naruto, such as

- [Sharingan](http://naruto.wikia.com/wiki/Sharingan) (写輪眼; the package name)

- The [moon reader](http://naruto.wikia.com/wiki/Moon_Reader) (月読; an attractive R Markdown output format)

- [Chakra](http://naruto.wikia.com/wiki/Chakra) (查克拉; the path to the remark.js library, which is the power to drive the presentation)

- [Nature transformation](http://naruto.wikia.com/wiki/Nature_Transformation) (性質変化; transform the chakra by setting different options)

- The [infinite moon reader](http://naruto.wikia.com/wiki/Infinite_Tsukuyomi) (無限月読; start a local web server to continuously serve your slides)

- The [summoning technique](http://naruto.wikia.com/wiki/Summoning_Technique) (download remark.js from the web)

You can click the links to know more about them if you want. The jutsu "Moon Reader" may seem a little evil, but that does not mean your slides are evil.

---

class: center

# Hand seals (印)

Press `h` or `?` to see the possible ninjutsu you can use in remark.js.

![](https://upload.wikimedia.org/wikipedia/commons/7/7e/Mudra-Naruto-KageBunshin.svg)

---

class: center, middle

# Thanks!

Slides created via the R package [**xaringan**](https://github.com/yihui/xaringan).

The chakra comes from [remark.js](https://remarkjs.com), [**knitr**](http://yihui.name/knitr), and [R Markdown](https://rmarkdown.rstudio.com).

### 2019-02-11 awipev-CO2.Rmd
path changed figures are now saved in figures folder in not synced rather than on pCloud

@@
 
-ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/TA_calibration_CRM.png"), calib_p, units="cm")
+ggsave("figures/TA_calibration_CRM.png", calib_p, units="cm")
 print(calib_p)
@@
 print(p)
-ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/Diff_ref_TA_first_period.png"), p, units="cm")
+ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
 ```
@@
 print(p)
-ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/Diff_ref_TA_third_period.png"), p, units="cm")
+ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
 ```
@@
 
-ggsave(paste0(path, "fb_figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =10, units="cm")
+ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =10, units="cm")
 
@@
 print(pco2calc_pCO2_contros_text)
-ggsave(paste0(path, "fb_figures/pco2calc_pCO2_contros.png"), pco2calc_pCO2_contros_text, width=5, height=5, units="cm")
+ggsave(paste0("figures/pco2calc_pCO2_contros.png"), pco2calc_pCO2_contros_text, width=5, height=5, units="cm")
 ```
@@
 pdelta_ct_snapo_dygraph
-ggsave(paste0(path, "fb_figures/SNAPO/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
-ggsave(paste0(path, "fb_figures/SNAPO/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
+ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
+ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
 ```

### 2019-02-11 presentation/awipev-CO2_pres.Rmd
path changed figures are now saved in figures folder in not synced rather than on pCloud

--- 2019-02-04 presentation/awipev-CO2_pres_2019-02-19.Rmd
@@
 }
+
+#define who is the user and define path
+if (Sys.getenv("LOGNAME") == "gattuso") path = "../../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
+if (Sys.getenv("LOGNAME") == "samir") path = "../../../pCloud\ Sync/exp168_awipev-CO2/"
+
 ```
@@
 
-![ ](images/Discrete_TA_salinity_AWIPEV.png)
+![ ](../figures/Discrete_TA_salinity_AWIPEV.png)
 

### 2019-02-11 awipev-CO2.Rmd
Adde chunk at the end to save d_all

@@
 ```
+```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
+# d_hour is the real data set that is read at the beginning of the script
+# d_all comprises additional columns calculated in this script
+# These additional variablrs are useful elsewhere (for example in "presentation")
+# Hence, here we save it for this use
+save(file= paste0(path, "fb_data/d_all.Rdata"), d_all)
+```
 

### 2019-02-11 presentation/awipev-CO2_pres.Rmd
Adde chunk at the end to save d_all

@@
 ![ ](../figures/Discrete_TA_salinity_AWIPEV.png)
+---
+#### **Final TA re-calculated data (Salinity relationship)**
+```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
+at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
+at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
+dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
+  dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
+  dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
+  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
+  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
+  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
+  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
+  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
+  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
+  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
+  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
+  dyAxis("y",valueRange = c(2000, 2450)) %>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions( strokeWidth= 0) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
+    dyRangeSelector(height = 30, dateWindow= NULL)
+```
 

### 2019-02-11 awipev-CO2.Rmd
Finalized complete draft of presentation Bremerhaven Feb. 2018

@@
 print(pco2calc_pCO2_contros_text)
-ggsave(paste0("figures/pco2calc_pCO2_contros.png"), pco2calc_pCO2_contros_text, width=5, height=5, units="cm")
+ggsave(paste0("figures/pco2calc_pCO2_contros.png"), pco2calc_pCO2_contros_text, units="cm")
 ```

### 2019-02-11 presentation/awipev-CO2_pres.Rmd
Finalized complete draft of presentation Bremerhaven Feb. 2018

--- 2019-02-11 presentation/awipev-CO2_pres.Rmd
@@
 ---
-# History and instruments
+# Instruments installed
 
@@
 ---
-# Data available in near real-time: https://awipev-co2.obs-vlfr.fr
+## Instruments in the FerryBox
+.pull-left[
+![ ](images/container.png)
+]
+.pull-right[
+![ ](images/ferrybox.jpg)
+]
 
-![ ](images/web_page_small.png)
+---
+## seaFET pH on the REMOS
+![ ](images/seafet.png)
+
+---
+## Near real-time: https://awipev-co2.obs-vlfr.fr
+![ ](images/web_page_cropped.png)
+<!-- .element height="50%" width="50%" -->
 
@@
 
+## pCO2
 ```{r pCO2, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
@@
 ```
----
-
-```{r seafet, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-# SEAFET
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field)
-seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-seafet_dyg <- dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-frameWidget(seafet_dyg)
-```
 
 ---
+## Measured vs calculated pCO2
 
+![ ](../figures/pco2calc_pCO2_contros.png)
+
+---
+## Total alkalinity
 ```{r at, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
@@
 at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
-at_dyg <- dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
+at_dyg <- dygraph(at_contros_cleaned_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
@@
     dyRangeSelector(height = 30, dateWindow= NULL)
+frameWidget(at_dyg)
+```
 
-frameWidget(at_dyg)
+---
+## Discrete total alkalinity vs salinity
 
+![ ](../figures/Discrete_TA_salinity_AWIPEV.png)
+---
+#### **Final TA re-calculated data**
+```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
+at_contros_calc_xts <- dplyr::select(d_all, datetime, at_calc, AT_filtered, at)
+at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
+at_contros_calc_dyg <- dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
+  dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
+  dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
+  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
+  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
+  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
+  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
+  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
+  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
+  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
+  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
+  dyAxis("y",valueRange = c(2000, 2450)) %>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions( strokeWidth= 0) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
+    dyRangeSelector(height = 30, dateWindow= NULL)
+frameWidget(at_contros_calc_dyg)
 ```
-```{r others not used, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-#SAL
-# sal_fb_xts <- dplyr::select(d_all, datetime, sal_fb)%>%
-#   dplyr::filter(sal_fb >28)
-# sal_fb_xts <- as.xts(sal_fb_xts, order.by = sal_fb_xts$datetime)
-# sal_dyg <- dygraph(sal_fb_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
-#       dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "S") %>%
-#       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
-#       dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-#       dyRangeSelector(height = 30, dateWindow= NULL)
-# frameWidget(sal_dyg)
 
-# # TEMP Ferrybox SBE45
-# temp_fb_xts <- dplyr::select(d_all, datetime, temp_fb)
-# temp_fb_xts <- as.xts(temp_fb_xts, order.by = temp_fb_xts$datetime)
-# dygraph(temp_fb_xts, group = "awipev", main="Temperature (in Ferrybox)", ylab="Temperature") %>%
-#       dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "T") %>%
-#       dyAxis("y", valueRange = c(-2.5, 9.5)) %>%
-#       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#       dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-#       dyRangeSelector(height = 30, dateWindow= NULL)
-# # TEMP insitu SBE38
-# temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu)
-# temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
-# dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ)", ylab="Temperature") %>%
-#       dySeries("temp_insitu", color = "blue", strokeWidth = 0, label = "T") %>%
-#       dyAxis("y", valueRange = c(-2.5, 9.5)) %>%
-#       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#       dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-#       dyRangeSelector(height = 30, dateWindow= NULL)
-
-# # DURAFET 
-# durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field)
-# durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
-# dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
-#     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-#     dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-#     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
-#     dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
-#     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-#     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-#     dyRangeSelector(height = 30, dateWindow= NULL) 
+---
+## seaFET pH (in situ)
+```{r seafet final, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
+seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered, pH_s_seafet_temp_field, pHint_tot_sf)
+seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+seafet_dy <- dygraph(seafet_contros_xts, group = "awipev", main="", ylab="pHT") %>%
+  #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
+  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
+  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
+  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
+  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
+  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
+  # dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
+  # dyShading(from = sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
+  # dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
+  # dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
+  # dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
+  # dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
+  # dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
+  # dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
+  # dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
+  #  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyRangeSelector(dateWindow = c("2017-08-01", substr(d_all$datetime[1], 1, 10)))
+  #dyRangeSelector(height = 30, dateWindow= NULL) 
+frameWidget(seafet_dy)
 ```
 ---
-## Relationship between discrete AT and salinity
+## Durafet pH (in FerryBox)
 
-![ ](../figures/Discrete_TA_salinity_AWIPEV.png)
+```{r durafet, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
+durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected)
+durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
+pH_durafet_dyg <- dygraph(durafet_contros_xts, group = "awipev", main="", ylab="pHT") %>%
+    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
+    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
+    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
+   #  # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
+   #  dyShading(from =  durinterv[1], to= durinterv[2], color = "#CCCCCC") %>%
+   #  dyShading(from = durinterv[2], to= durinterv[3], color = "#E0E0E0") %>%
+   #  dyShading(from = durinterv[3], to= durinterv[4], color = "#CCCCCC") %>%
+   #  dyShading(from = durinterv[4], to= durinterv[5], color = "#E0E0E0") %>%
+   #  dyShading(from = durinterv[5], to= durinterv[6], color = "#CCCCCC") %>%
+   #  dyShading(from = durinterv[6], to= durinterv[7], color = "#E0E0E0") %>%
+   # dyShading(from = durinterv[7], to= durinterv[8], color = "#CCCCCC") %>%
+   # dyShading(from = durinterv[8], to= durinterv[9], color = "#E0E0E0") %>%
+   # dyShading(from = durinterv[9], to= durinterv[10], color = "#CCCCCC") %>%
+   # dyShading(from = durinterv[10], to= durinterv[11], color = "#E0E0E0") %>%
+    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+    dyRangeSelector(dateWindow = c("2017-08-01", substr(d_all$datetime[1], 1, 10)))
+    #dyRangeSelector(height = 30, dateWindow= NULL) 
+frameWidget(pH_durafet_dyg)
+```
 
 ---
+## SeaFET pH vs DuraFET pH (normalized at 4°C)
 
-# Difficulties with logistics
-```{r}
-
+```{r comparing pH, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
+durafet_sf_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pHint_tot_sf_norm4)
+durafet_sf_contros_xts <- as.xts(durafet_sf_contros_xts, order.by = d_all$datetime)
+durafet_sf_contros_dyg <- dygraph(durafet_sf_contros_xts, group = "awipev", main="pH durafet vs pH seaFET at 4°C", ylab="pHT") %>%
+    dySeries("pH_durafet_norm4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color =  "red", strokeWidth = 0, pointSize = 2 ) %>%
+    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
+    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+    dyRangeSelector(dateWindow = c("2017-08-01", substr(d_all$datetime[1], 1, 10)))
+    #dyRangeSelector(height = 30, dateWindow= NULL) 
+frameWidget(durafet_sf_contros_dyg)
 ```
 
-- Bullet 1
-- Bullet 2
-- Bullet 3
+---
+## Logistics
+
+- **Assets**: 
+  - Excellent support from AWIPEV staff
+  - IPEV support secured for another 4-year period (2019-2022)
+- **Difficulties**:
+  - Challenging environment; divers needed to sort out issues
+  - Difficult and costly to gather a team and organize field trip at short notice
+  - Winter sampling essential (once a month this season, more frequently would be more desirable)
+  - Demanding for AWIPEV staff
+  - IPEV does not cover the cost of analyses required for calibration (ca. 1000 €)

### 2019-02-12 presentation/awipev-CO2_pres.Rmd
Completed conclusion slide

@@
 ---
-## Logistics
+## Conclusion
 
-- **Assets**: 
+- **First** high-frequency time series of the carbonate system in the Arctic 
+- **Positive aspects**: 
   - Excellent support from AWIPEV staff
   - IPEV support secured for another 4-year period (2019-2022)
-- **Difficulties**:
+- **Logistical difficulties**:
   - Challenging environment; divers needed to sort out issues

### 2019-02-12 presentation/awipev-CO2_pres.Rmd
Minor cosmetic changes

--- 2019-02-11 presentation/awipev-CO2_pres.Rmd
@@
 library(widgetframe)
+# # install http://phantomjs.org/download.html
+# library(webshot)
+# # remotes::install_github(c('rstudio/pagedown', 'yihui/xaringan'))
+# library(pagedown)
 
@@
 
-# AWIPEV-CO2: First time-series of carbonate chemistry in the Arctic
+# AWIPEV-CO<sub>2</sub>: First high-frequency time series of carbonate chemistry in the Arctic
 
 ### Jean-Pierre Gattuso (1,2), Samir Alliouane (1) & Philipp Fischer (3)
-(1) CNRS and Sorbonne University
-(2) Iddri
-(3) AWI
+(1) CNRS and Sorbonne University, (2) Iddri, (3) AWI
 
@@
 .pull-left[
-- CO2 is an acid gas (it produces acid when combined with water)
-- Each of us adds 4 kg CO2 per day to the ocean (increasing acidity, reducing pH)
-- The Arctic It will become corrosive for aragonite: 50% in 2050, 100% in 2100
-- Critical to document the changes but no time-series until recently
+- CO<sub>2</sub> is an acid gas (it produces a weak acid when combined with water)
+- Each of us adds 4 kg CO<sub>2</sub> per day to the ocean (increasing acidity, reducing pH)
+- Arctic surface water will become corrosive for aragonite: 50% in 2050, 100% in 2100
+- Critical to document the changes but no high frequency time-series
 ]
@@
 - Water pumped from 12 m water depth at Ny-Ålesund
-- **Since July 2015**: Two pCO2 sensors rotating every year (in FerryBox, 1 min) 
+- **Since July 2015**: Two pCO<sub>2</sub> sensors rotating every year (in FerryBox, 1 min) 
 - **Since February 2016**: Total alkalinity analyser (in FerryBox, 90 min) but lots of technical issues
@@
 
-## pCO2
+## pCO<sub>2</sub>
 ```{r pCO2, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
@@
 pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
-pco2_dyg <- dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
+pco2_dyg <- dygraph(pco2_contros_xts, group = "awipev", main="", ylab="") %>%
     dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 2) %>%
@@
 ---
-## Measured vs calculated pCO2
+## Measured vs calculated pCO<sub>2</sub>
 
@@
 at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
-at_dyg <- dygraph(at_contros_cleaned_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
+at_dyg <- dygraph(at_contros_cleaned_xts, group = "awipev", main="", ylab="") %>%
    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
@@
 ## Discrete total alkalinity vs salinity
+![ ](../figures/Discrete_TA_salinity_AWIPEV.png)
 
-![ ](../figures/Discrete_TA_salinity_AWIPEV.png)
 ---
@@
 at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
-at_contros_calc_dyg <- dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
+at_contros_calc_dyg <- dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="") %>%
   dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
@@
 ---
-## seaFET pH (in situ)
+## seaFET pH<sub>total scale</sub> (in situ)
 ```{r seafet final, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
@@
 seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-seafet_dy <- dygraph(seafet_contros_xts, group = "awipev", main="", ylab="pHT") %>%
+seafet_dy <- dygraph(seafet_contros_xts, group = "awipev", main="", ylab="") %>%
   #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
@@
 ---
-## Durafet pH (in FerryBox)
+## Durafet pH<sub>total scale</sub> (in FerryBox)
 
@@
 ---
-## SeaFET pH vs DuraFET pH (normalized at 4°C)
+## SeaFET pH<sub>T</sub> vs DuraFET pH<sub>T</sub> (both normalized at 4°C)
 
@@
 ---
-## Logistics
+## Conclusion
 
-- **Assets**: 
-  - Excellent support from AWIPEV staff
+- **First** high-frequency time series of the carbonate system in the Arctic 
+- **Positive aspects**: 
+  - Excellent support from AWIPEV staff but work overload
   - IPEV support secured for another 4-year period (2019-2022)
-- **Difficulties**:
+- **Logistical difficulties**:
   - Challenging environment; divers needed to sort out issues

### 2019-02-21 awipev-CO2.Rmd
added AT analysis since new instrument installed, Nov 2018

@@
 # function regression plot with model II equation (MA) in title
-## Dans labs ajout de la variable title pour mettre title avant chaque graphe
-ggreg2 <- function (fit, x, y, point.size=5) { # x and y are the names of the variables
+## Dans labs ajout de la variable TITRE pour mettre titre avant chaque graphe
+ggreg2 <- function (fit, xdata, ydata) { # x and y are the names of the variables
   fit_data <- data.frame(fit$x, fit$y)
-  colnames(fit_data) = c(x, y)
+  colnames(fit_data) = c(xdata, ydata)
 reg <- fit$regression.results[2,] #one selects MA only
@@
 slope <- reg$Slope
-  ggplot(data = fit_data, aes_string(x = x, y = y)) + 
-  geom_point(size = point.size, col = "blue") +
+  ggplot(data = fit_data, aes_string(x = xdata, y = ydata)) + 
+  geom_point(size = 3, col = "blue") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),
               colour = "blue")  + 
-  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
+  labs(title = paste(titre,"\n Adj R2 = ", signif(fit$rsquare, 3),
                      "; Intercept =", signif(intercept, 3),
                      "; Slope =", signif(slope, 3),
-                     "; P =", signif(fit$P.param, 3))) +
-    theme(plot.title = element_text(size=7))
+                     "; P =", signif(fit$P.param, 3)))
 }
+
+mytheme <- theme_bw() +
+  theme(axis.text.x=element_text(size=16, color="black"),
+        axis.title.x=element_text(face="bold", size=16),
+        axis.text.y=element_text(size=16, color="black"),
+        axis.title.y=element_text(face="bold", size=16),
+        plot.title = element_text(face="bold", size=14)
+)
 
@@
 calib_ta_second <- d_all%>%
-  dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
+  dplyr::select(datetime, closest_datetime, AT_filtered, AT_filtered_interp, at, diff_ta, TA_period)%>%
   dplyr::filter(TA_period == "TA2" & !is.na(at))
@@
     dyRangeSelector(height = 30, dateWindow= NULL)
-
-# Property plots : x= at (discretes data), y = at_contros/at_contros_rep/at_calibrated/at_calibrated_rep
+```
+
+There are a lot of outliers in the 4th period (since the new analyzer was set up in Nov. 2018). We use the desplike function to remove them.
+
+#### **TA since November 2018 (final installation)**
+```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
+# select subset of data and remove obvious outliers
+at_nov_2018 <- 
+  dplyr::select(d_all, datetime, at_calc, AT_filtered, at) %>%
+  filter(datetime > "2018-11-01", AT_filtered > 2250)
+#despike
+at_nov_2018 <- mutate(at_nov_2018, AT_filtered_despike = despike(AT_filtered, reference= "median", n=0.5, k=10, replace="NA"))
+#plot
+at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) +
+  geom_point(aes(y=AT_filtered, colour = "before")) +
+  geom_point(aes(y=AT_filtered_despike, colour = "after")) +
+  labs(x = "Time", y = "Total alkalinity", color = "despike") 
+print(at_datetime)
+
+at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_filtered_despike != "NA")
+titre <- "Contros AT vs Calculated AT"
+fit <- lmodel2(data = at_nov_2018_no_NA, AT_filtered_despike ~ at_calc, nperm = 99)
+ggreg2(fit, x = "at_calc", y = "AT_filtered_despike")
 ```

### 2019-02-26 awipev-CO2.Rmd
do not sync html file
maintenance updated

--- 2019-02-11 awipev-CO2.Rmd
@@
 
-ggsave("figures/TA_calibration_CRM.png", calib_p, units="cm")
+ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/TA_calibration_CRM.png"), calib_p, units="cm")
 print(calib_p)
@@
 print(p)
-ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
+ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/Diff_ref_TA_first_period.png"), p, units="cm")
 ```
@@
 print(p)
-ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
+ggsave(paste0(path, "fb_figures/TA_Analyser/Calibration/Diff_ref_TA_third_period.png"), p, units="cm")
 ```
@@
 
-ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =10, units="cm")
+ggsave(paste0(path, "fb_figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =10, units="cm")
 
@@
 print(pco2calc_pCO2_contros_text)
-ggsave(paste0("figures/pco2calc_pCO2_contros.png"), pco2calc_pCO2_contros_text, units="cm")
+ggsave(paste0(path, "fb_figures/pco2calc_pCO2_contros.png"), pco2calc_pCO2_contros_text, width=5, height=5, units="cm")
 ```
@@
 pdelta_ct_snapo_dygraph
-ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
-ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
-```
-```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
-# d_hour is the real data set that is read at the beginning of the script
-# d_all comprises additional columns calculated in this script
-# These additional variablrs are useful elsewhere (for example in "presentation")
-# Hence, here we save it for this use
-save(file= paste0(path, "fb_data/d_all.Rdata"), d_all)
+ggsave(paste0(path, "fb_figures/SNAPO/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
+ggsave(paste0(path, "fb_figures/SNAPO/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
 ```
@@
 ###**FerryBox**
+- **2019-02-26**: FB is stopped because of a "leakage" issue. 
 - **2019-01-17**: FB is stopped until 19th January 
@@
 ###**TA analyser**
+- **2019-02-15**: No data from 15th (14:08:21 UTC) to 19th February (14:58:46 UTC). files transfered but no data. No explanation.
 - **2019-01-26**: Philipp did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. Flow filter was also lifted up and the seawater flow has therefore increased.

### 2019-02-27 awipev-CO2.Rmd

--- 2019-02-21 awipev-CO2.Rmd
@@
 
-# deployment period between 2 spectro measurements.
+# deployment period between 2 spectro measurements
 sfPeriod <- d_all%>%
@@
 ###**FerryBox**
+- **2019-02-27**: FB is working again. 
+- **2019-02-26**: FB is stopped because of a "leakage" issue. 
 - **2019-01-17**: FB is stopped until 19th January 

### 2019-02-27 awipev-CO2.Rmd
TA

--- 2019-02-21 awipev-CO2.Rmd
@@
 
-##Key plots
+### **Data availability**
+TO DO: add here an horizontal bar plot showing the percent availability of the data
+
+## Whole time series
 ```{r whole time series, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}

### 2019-03-04 awipev-CO2.Rmd

--- 2019-02-27 awipev-CO2.Rmd
@@
 
+##Server
+
+- Serveur : awipev-co2 (193.50.85.104)
+- 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer).
+- Pour se connecter à awipev-co2.obs-vlfr.fr
+    - ssh awipev@awipev-co2.obs-vlfr.fr
+- Intervention sur le serveur :
+    - ssh awipev@awipev-co2.obs-vlfr.fr
+    - rebooting Ubuntu server: sudo shutdown -r now
+    - to check versions:
+        - dpkg -l | grep shiny
+        - dpkg -l | grep r-base
+    - To update Ubuntu, R and its packages:
+        - sudo su
+        - apt-get upgrade
+    - To restart shiny server: sudo systemctl restart shiny-server
+    - update shiny server: follow procedure detailed on the shiny web page Data processing
+- Every night at 01:00 (?) two data files ("all sensors" and AT) are sent by ftp to:
+    - awipev-co2.obs-vlfr.fr
+    - User name: nydata
+    - password:
+- Every hour a crontab action runs the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files added each day around 01:00 and cleans the data
+- Every night at 03:00 the web page is generated
+- Every night at 05:00 the files are copied to gattuso’s iMac crontab awipev@awipev-co2.obs-vlfr.fr si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync # m h dom mon dow command 00 */1 * * * cd ; R --vanilla < ny-alesund/R/ny-alesund_cc.R 00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/awipev-co2_web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/' 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/' 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/' Web page
+- La page web index.html est faite sur awipev@awipev-co2.obs-vlfr.fr
+- Création du répertoire web qui contient ce qu’il faut pour générer la page web:
+    - AWIPEV-Logo.jpg
+    - Discrete_sampling_AWIPEV.csv
+    - awipev-CO2_web.Rmd
+    - awipev-co2.sh (lancer par bash awipev-co2.sh)
+- Accessible https://awipev-co2.obs-vlfr.fr On utilise un shell script awipev-co2.sh: #!/bin/bash # script de lancement via crontab echo '---------deb awipev-co2.sh -----------' # On lance la fabrication du html cd web; R -e 'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html echo '---------fin awipev-co2.sh -----------'
+
 <!-- ```{r Graph pour proposal, echo=FALSE, message= FALSE, warning=FALSE} -->

### 2019-03-06 awipev-CO2.Rmd
update in script + data tab

--- 2019-02-27 awipev-CO2.Rmd
@@
 
+[UWO-Ferrybox variables from our sensors](https://docs.google.com/spreadsheets/d/1arKYfUjmg3YrgQ5g9LN_XFwUORyz7nqlKNWq3uYok3U/edit?ts=5c7e1d16#gid=393659093)
+
+[All UWO-Ferrybox data / NearRealTime (NRT) AWI database](https://dashboard.awi.de/data-xxl/overview.jsp)
+
+[Procedure to download NRT data](https://spaces.awi.de/confluence/display/MOS/NRT+data+download+procedures)
+
 ###**FerryBox**
@@
 pH spectro from 2018-04-16 07:00:00 was fitted with a mean of 4 days of voltINT in order to make the calibration for this 5th period.
-- **2018-07-30**: Flag location (location_flag) is added in the script to localize seaFET/durafet discrete samples: flag 1 = at the harbor (not takken in consideration) and flag 0 = in the FB for durafet or on site for seaFET (takken in consideration as "normal" sampling").
+- **2018-07-30**: Flag location (location_flag) is added in the script to localize seaFET/durafet discrete samples: flag 1 = at the harbor (not taken in consideration) and flag 0 = in the FB for durafet or on site for seaFET (takken in consideration as "normal" sampling").
 See seaFET part.
@@
 File "SVL_20171024_030426_to_20171026_110425_SeaFet-1005.txt" were created in SeaFet_archive.
+
+## Villefranche Server informations
+
+- Serveur : awipev-co2 (193.50.85.104)
+- 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer).
+- Pour se connecter à awipev-co2.obs-vlfr.fr
+    - ssh awipev@awipev-co2.obs-vlfr.fr
+- Intervention sur le serveur :
+    - ssh awipev@awipev-co2.obs-vlfr.fr
+    - rebooting Ubuntu server: sudo shutdown -r now
+    - to check versions:
+        - dpkg -l | grep shiny
+        - dpkg -l | grep r-base
+    - To update Ubuntu, R and its packages:
+        - sudo su
+        - apt-get upgrade
+    - To restart shiny server: sudo systemctl restart shiny-server
+    - update shiny server: follow procedure detailed on the shiny web page
+
+**Data processing**
+
+- Every night at 01:00 (?) two data files ("all sensors" and AT) are sent by ftp to:
+    - awipev-co2.obs-vlfr.fr
+    - User name: nydata
+    - password:
+- Every hour a crontab action runs the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files added each day around 01:00 and cleans the data
+- Every night at 03:00 the web page is generated
+- Every night at 05:00 the files are copied to gattuso’s iMac
+
+**crontab awipev@awipev-co2.obs-vlfr.fr**
+
+si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync # m h dom mon dow command 
+00 */1 * * * cd ; R --vanilla < ny-alesund/R/ny-alesund_cc.R 
+00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/awipev-co2_web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
+00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
+00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
+
+**Web page**
+
+- La page web index.html est faite sur awipev@awipev-co2.obs-vlfr.fr
+- Création du répertoire web qui contient ce qu’il faut pour générer la page web:
+    - AWIPEV-Logo.jpg
+    - Discrete_sampling_AWIPEV.csv
+    - awipev-CO2_web.Rmd
+    - awipev-co2.sh (lancer par bash awipev-co2.sh)
+- Accessible https://awipev-co2.obs-vlfr.fr
+
+**On utilise un shell script awipev-co2.sh:**
+
+ #!/bin/bash
+
+ # script de lancement via crontab echo '---------deb awipev-co2.sh -----------'
+
+ # On lance la fabrication du html cd web; R -e 'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html
+
+echo '---------fin awipev-co2.sh -----------'
 

### 2019-04-17 awipev-CO2.Rmd
test

@@
 ```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
-#
+# test
 Sys.setlocale("LC_ALL", "en_US.UTF-8")
@@
 
-si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync # m h dom mon dow command 
-00 */1 * * * cd ; R --vanilla < ny-alesund/R/ny-alesund_cc.R 
+<span style="color:red">**Warning:**</span> In the present HTML document double "-" appear with an espace between them (for display reasons).
+**Do not put the space when typing the code on a terminal wondow.**
+
+si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “- -delete” à la commande rsync # m h dom mon dow command 
+00 */1 * * * cd ; R - -vanilla < ny-alesund/R/ny-alesund_cc.R
+
 00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/awipev-co2_web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
+
 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
+
 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'

### 2019-04-17 awipev-CO2.Rmd
AT/CT serie from 07-2018 to 11-2018 updated with flags 1

@@
 - 2017-05-04
+- 2017-08-31
 - 2018-04-26
@@
 - 2018-07-27
+- 2018-07-20
+- 2018-08-03
+- 2018-08-10
+- 2018-08-31
+- 2018-09-07
+- 2018-09-14
+- 2018-09-21
+- 2018-09-28
+- 2018-10-05
+- 2018-10-12
+- 2018-10-19
+- 2018-10-26
+- 2018-11-02
+- 2018-11-09
+- 2018-11-16
+- 2018-11-23
 
@@
 - 2016-05-12
-- 2016-05-16
+- 2016-05-19
 - 2016-06-16
@@
 - 2017-04-27
-- 2017-09-17
+- 2017-09-14
 - 2018-04-26
@@
 - 2018-06-30
-
+- 2018-07-20
+- 2018-08-03
+- 2018-08-31
+- 2018-09-07
+- 2018-09-14
+- 2018-09-28
+- 2018-10-05
+- 2018-10-12
+- 2018-10-19
+- 2018-10-26
+- 2018-11-02
+- 2018-11-09
+- 2018-11-16
+- 2018-11-23
 ```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}

### 2019-04-29 awipev-CO2.Rmd
AT/CT serie from 07-2018 to 11-2018 updated with flags 1
add text to html
RDM updated with new seaFET/durafet measurements

--- 2019-04-17 awipev-CO2.Rmd
@@
                                 ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
-                                ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 09, NA )))))))))))
+                                ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
+                                       ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
+                                              ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
+                                                     ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,NA ))))))))))))))
 
@@
   dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
+
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
                                 ifelse(datetime >= durinterv[9] & datetime <= durinterv[10], 09,
-                                ifelse(datetime >= durinterv[10] & datetime <= durinterv[11], 10, NA )))))))))))
+                                ifelse(datetime >= durinterv[10] & datetime <= durinterv[11], 10, 
+                                ifelse(datetime >= durinterv[11] & datetime <= durinterv[12], 10,
+                                ifelse(datetime >= durinterv[12] & datetime <= durinterv[13], 10,NA )))))))))))))
 
@@
                                 ifelse(deployment_dur == 9, dat_dur$diff_pH_dur[9],
-                                ifelse(deployment_dur == 10, dat_dur$diff_pH_dur[10], 0)))))))))),
+                                ifelse(deployment_dur == 10, dat_dur$diff_pH_dur[10], 
+                               ifelse(deployment_dur == 11, dat_dur$diff_pH_dur[11],
+                                ifelse(deployment_dur == 12, dat_dur$diff_pH_dur[12],0)))))))))))),
               pH_durafet_corrected = pH_durafet + offset_durafet
@@
    dyShading(from = durinterv[10], to= durinterv[11], color = "#E0E0E0") %>%
+    dyShading(from = durinterv[11], to= durinterv[12], color = "#CCCCCC") %>%
+    dyShading(from = durinterv[12], to= durinterv[13], color = "#E0E0E0") %>%
+   dyShading(from = durinterv[13], to= durinterv[14], color = "#CCCCCC") %>%
     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
 - 2018-07-27
+- 2018-07-20
+- 2018-08-03
+- 2018-08-10
+- 2018-08-24
+- 2018-08-31
+- 2018-09-07
+- 2018-09-14
+- 2018-09-21
+- 2018-09-28
+- 2018-10-05
+- 2018-10-12
+- 2018-10-19
+- 2018-10-26
+- 2018-11-02
+- 2018-11-09
+- 2018-11-16
+- 2018-11-23
 
@@
 - 2018-06-30
+- 2018-07-20
+- 2018-08-03
+- 2018-08-31
+- 2018-09-07
+- 2018-09-14
+- 2018-09-28
+- 2018-10-05
+- 2018-10-12
+- 2018-10-19
+- 2018-10-26
+- 2018-11-02
+- 2018-11-09
+- 2018-11-16
+- 2018-11-23
 

### 2019-04-29 awipev-CO2.Rmd
RDM updated with new seaFET/durafet measurements 2/2

@@
                                 ifelse(datetime >= durinterv[10] & datetime <= durinterv[11], 10, 
-                                ifelse(datetime >= durinterv[11] & datetime <= durinterv[12], 10,
-                                ifelse(datetime >= durinterv[12] & datetime <= durinterv[13], 10,NA )))))))))))))
+                                ifelse(datetime >= durinterv[11] & datetime <= durinterv[12], 11,
+                                ifelse(datetime >= durinterv[12] & datetime <= durinterv[13], 12,
+                                        ifelse(datetime >= durinterv[13] & datetime <= durinterv[14], 13,NA ))))))))))))))
 
@@
                                ifelse(deployment_dur == 11, dat_dur$diff_pH_dur[11],
-                                ifelse(deployment_dur == 12, dat_dur$diff_pH_dur[12],0)))))))))))),
+                                ifelse(deployment_dur == 12, dat_dur$diff_pH_dur[12],
+                                       ifelse(deployment_dur == 13, dat_dur$diff_pH_dur[13],0))))))))))))),
               pH_durafet_corrected = pH_durafet + offset_durafet

### 2019-04-29 awipev-CO2.Rmd
seaFET period number 13 readjusted to take in consideration seaFET data corrected from 2019-01-29 to 2019-02-07

@@
 sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
+ #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
+sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
 

### 2019-04-30 awipev-CO2.Rmd
last update for durafet and the text

@@
       dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+    dyAxis("y",valueRange = c(30, 36)) %>%
       dyRangeSelector(height = 30, dateWindow= NULL)
@@
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+    dyAxis("y",valueRange = c(8, 8.6)) %>%
+
     dyRangeSelector(height = 30, dateWindow= NULL) 
@@
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+    dyAxis("y",valueRange = c(7.45, 8.6)) %>%
     dyRangeSelector(height = 30, dateWindow= NULL) 
@@
                                  ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
-                                                     ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,NA ))))))))))))))
+                                 ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
+                                ifelse(datetime >= sfinterv[14] , 14,NA )))))))))))))))
 
@@
   dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[14], to= Sys.Date(), color = "#E0E0E0") %>%
 
@@
 durinterv <- c( as_datetime("2017-08-24 13:00:00"), durPeriod[,4])
+ #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
+durinterv[13] <- ymd_hms("2019-01-17 23:00:00")
+ #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
+durinterv[14] <- ymd_hms("2019-01-19 00:00:00")
 
@@
                                 ifelse(datetime >= durinterv[12] & datetime <= durinterv[13], 12,
-                                        ifelse(datetime >= durinterv[13] & datetime <= durinterv[14], 13,NA ))))))))))))))
+                                ifelse(datetime >= durinterv[13] & datetime <= durinterv[14], 13,
+                                ifelse(datetime >= durinterv[14] & datetime <= durinterv[15], 14,
+                                ifelse(datetime >= durinterv[15], 14,NA ))))))))))))))))
 
@@
                                 ifelse(deployment_dur == 12, dat_dur$diff_pH_dur[12],
-                                       ifelse(deployment_dur == 13, dat_dur$diff_pH_dur[13],0))))))))))))),
+                                ifelse(deployment_dur == 13, dat_dur$diff_pH_dur[13],
+                                ifelse(deployment_dur == 14, dat_dur$diff_pH_dur[14],0)))))))))))))),
               pH_durafet_corrected = pH_durafet + offset_durafet
@@
     dyShading(from = durinterv[12], to= durinterv[13], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[13], to= durinterv[14], color = "#CCCCCC") %>%
+   dyShading(from = durinterv[14], to= Sys.Date(), color = "#CCCCCC") %>%
     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
 
-- 2015-11-18
-- 2016-07-28
-- 2016-09-29
-- 2016-11-17
-- 2016-11-23
-- 2016-12-29
-- 2017-01-19
-- 2017-05-04
-- 2017-08-31
-- 2018-04-26
-- 2018-05-04
-- 2018-05-16
-- 2018-05-25
-- 2018-06-22
-- 2018-06-30
-- 2018-07-27
-- 2018-07-20
-- 2018-08-03
-- 2018-08-10
-- 2018-08-24
-- 2018-08-31
-- 2018-09-07
-- 2018-09-14
-- 2018-09-21
-- 2018-09-28
-- 2018-10-05
-- 2018-10-12
-- 2018-10-19
-- 2018-10-26
-- 2018-11-02
-- 2018-11-09
-- 2018-11-16
-- 2018-11-23
+2015-11-18
+, 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29, 2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16, 2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03, 2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23.
 
@@
 
-- 2015-08-06
-- 2015-08-13
-- 2016-05-12
-- 2016-05-19
-- 2016-06-16
-- 2016-07-28
-- 2016-09-08
-- 2016-10-27
-- 2016-11-17
-- 2017-01-19
-- 2017-03-02
-- 2017-04-27
-- 2017-09-14
-- 2018-04-26
-- 2018-05-04
-- 2018-05-12
-- 2018-05-25
-- 2018-06-30
-- 2018-07-20
-- 2018-08-03
-- 2018-08-31
-- 2018-09-07
-- 2018-09-14
-- 2018-09-28
-- 2018-10-05
-- 2018-10-12
-- 2018-10-19
-- 2018-10-26
-- 2018-11-02
-- 2018-11-09
-- 2018-11-16
-- 2018-11-23
+2015-08-06, 2015-08-13, 2016-05-12, 2016-05-19, 2016-06-16, 2016-07-28, 2016-09-08, 2016-10-27, 2016-11-17, 2017-01-19, 2017-03-02, 2017-04-27, 2017-09-14, 2018-04-26, 2018-05-04, 2018-05-12, 2018-05-25, 2018-06-30, 2018-07-20, 2018-08-03, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23.
 

### 2019-04-30 awipev-CO2.Rmd

@@
 ###**FerryBox**
+- **2019-04-14**: FB is working again. 
+- **2019-04-13**: FB is stopped since 05:00am (the level switch stuck in the full position in the waste tank). 
 - **2019-02-27**: FB is working again. 
@@
 
+###**durafet**
+Reference spectro measurement from the 2019-01-18 11:00 do not match with a durafet raw data because Ferrybox was off.
+This reference point was not takken in consideration for calibration.
+The window of the previous and next calibration periods was extended.
+
 ###***p*CO~2~**
@@
 ###**SNAPO**
+- **2019-04-30**: Duplicate "Ferrybox" samples (SN0316 and SN264, 2019-02-22 14:05) were sent by mistake in Villefranche for pH measurements.
+Those results were put in the datafile as "durafet" samples as soon as they are comming from the Ferrybox tape seawater.
+We will ad a lack of DIC for this week.
+TA will be measured in Villefranche.
 - **2018-08-30**: flag of 1 AT duplicate (2205) from 2017-08-31 was put to 3 (dosage douteux).

### 2019-05-11 awipev-CO2.Rmd

@@
 # numberOutliers <- length(which((dat_ATnoNA$outliers > 0)))
+
+#plot for POSTER june 2019
+#plot of S/T
+poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 ), aes(x=datetime,y=temp_fb)) +
+  geom_point(col="blue", size=0.5 )+
+  labs(x = "Time", y="Temperature (°C)") +
+  scale_x_datetime(date_minor_breaks ="1 month")+
+  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+print(poster_temp)
+ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
+
+poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb)) +
+  geom_point(col="blue", size=0.5 )+
+  labs(x = "Time", y="Salinity (PSU)") +
+  scale_x_datetime(date_minor_breaks ="1 month")+
+  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+print(poster_sal)
+ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")
+
 ```
@@
     dyRangeSelector(height = 30, dateWindow= NULL)
+
+#plot for POSTER june 2019
+#plot of TA calculated from S + discrete
+p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
+  geom_point(col="blue", size=0.5 )+
+  geom_point(aes(y=at, fill= "Reference measured samples"), col="red") +
+  labs(x = "Time", y = "Calculated TA from salinity (µmoles/kg)") +
+  scale_x_datetime(date_minor_breaks ="1 month")+
+  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+print(p_at_sal)
+ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
+
 ```
@@
 ggreg2(fit, x = "at_calc", y = "AT_filtered_despike")
+
+#plot for POSTER june 2019
+#plot of TA VS calculated
+poster_at_atcal <- ggplot(data = at_nov_2018%>%dplyr::filter(at_calc > 2000), aes(x=at_calc,y=AT_filtered_despike,col="TA calculated from salinity") ) +
+  geom_point(col="blue", size=0.5 )+
+  labs(x = "Calculated TA", y = "Calculated TA from salinity (µmoles/kg)") +
+  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+print(poster_at_atcal)
+ggsave(paste0("figures/poster_at_atcal.png"), width= 30, height=10, poster_at_atcal, units="cm")
 ```
@@
     dyRangeSelector(height = 30, dateWindow= NULL)
+
+#plot for POSTER june 2019
+#plot of pCO2
+poster_pco2 <- ggplot( ) +
+  geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros,col="blue"), col="blue",size=0.5 ) +
+  geom_point(data=d_all, aes(x=datetime, y=pco2calc, fill="Calculated from AT/CT"), col="red" )+
+  labs(x = "Time", y = expression(~italic(p)~CO[2]~"(µatm)")) +
+  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+print(poster_pco2)
+ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
     ```
@@
 print(plot_offset)
+
+#plot for POSTER june 2019
+#plot of pH seafet
+poster_ph <- ggplot( ) +
+  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
+  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Reference measured samples"), col="red" )+
+  labs(x = "Time", y = expression(pH[T]~seaFET)) +
+  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+
+print(poster_ph)
+ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")
+
+# RANGE of pH
+d_all<- d_all%>%
+  dplyr::mutate(year = year(datetime))
+range <- tbl_df(
+  d_all %>%
+  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
+  summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
+)
+quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
+
+# Per month
+range_month <-
+  range %>%
+  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
+  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
+
+size_point <- 0.4 # size of data points
+plot_range_sf <-  
+  ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+print(plot_range_sf)
+ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
 
@@
 print(plot_offset_dur)
+
+#plot for POSTER june 2019
+#plot of pH durafet
+poster_dur <- ggplot( ) +
+  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
+  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Reference measured samples"), col="red" )+
+  labs(x = "Time", y = expression(pH[T]~durafet)) +
+  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+
+print(poster_dur)
+ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")
+
+# RANGE of pH
+range_dur <- tbl_df(
+  d_all %>%
+  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
+  summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
+)
+quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
+
+# Per month
+range_month <-
+  range_dur %>%
+  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
+  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
+
+size_point <- 0.4 # size of data points
+plot_range_dur <-  
+  ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+print(plot_range_dur)
+ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
 ```

### 2019-05-13 awipev-CO2.Rmd
adding script for plot poster2

@@
 
-#plot for POSTER june 2019
-#plot of S/T
-poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 ), aes(x=datetime,y=temp_fb)) +
-  geom_point(col="blue", size=0.5 )+
-  labs(x = "Time", y="Temperature (°C)") +
-  scale_x_datetime(date_minor_breaks ="1 month")+
-  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
-print(poster_temp)
-ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
-
-poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb)) +
-  geom_point(col="blue", size=0.5 )+
-  labs(x = "Time", y="Salinity (PSU)") +
-  scale_x_datetime(date_minor_breaks ="1 month")+
-  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
-print(poster_sal)
-ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")
+# #plot for POSTER june 2019
+# #plot of S/T
+# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
+#   geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
+#   labs(x = "Time", y="Temperature (°C)") +
+#   scale_x_datetime(date_minor_breaks ="1 month")+
+#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
+#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity (PSU)"))
+# print(poster_temp)
+# par(mar=c(5, 4, 4, 6) + 0.1)
+# 
+# png("poster_sal_temp.png", width= 900, height=600)
+# 
+# plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.lab = 3) +
+# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)  
+# 
+#     grid(lty=1)
+#   
+#    par(new = T)
+#  
+# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="", axes=FALSE,ylim=c(-2,9))+
+# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
+#    # axis.POSIXct(1, at=seq(as.Date("2015-09-01"), max =as.Date("2019-09-01"), by="year"), format="%Y") +
+# axis.POSIXct(1,d_all$datetime,format(d_all$datetime,"%Y-%m-%d %H:%M:%S",tz="UTC"), major.format = "%Y-%m",labels = format(d_all$datetime, "%Y-%m-d %H:%M:%S"), cex =3)
+# 
+# mtext("Time",side=1,col="black",line=0.5)  
+# legend("topleft", legend=c("Temperature (°C)", "Salinity (PSU)"),
+#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
+#   #grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
+#    #  lwd = "months")
+#      box()
+#      dev.off()
+#      
+#      
+# ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
+# 
+# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
+#   geom_point(col="blue", size=0.5 )+
+#   labs(x = "Time", y="Salinity (PSU)") +
+#   scale_x_datetime(date_minor_breaks ="1 month")+
+#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+# print(poster_sal)
+# ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")
 
@@
   geom_point(col="blue", size=0.5 )+
-  geom_point(aes(y=at, fill= "Reference measured samples"), col="red") +
-  labs(x = "Time", y = "Calculated TA from salinity (µmoles/kg)") +
+  geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
+  labs(title=  "Calculated TA from salinity (µmoles/kg)", x = "Time", y= "") +
   scale_x_datetime(date_minor_breaks ="1 month")+
-  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+  theme_bw() + theme(legend.position= c(0.7, 0.15), 
+                     legend.text=element_text(size=15),
+                     plot.title = element_text(vjust = 0.5,size = rel(1.5),margin = margin(t = 10, b = -20)),
+                     axis.text=element_text(size=15),
+                     legend.title=element_blank())
+
 print(p_at_sal)

### 2019-05-14 awipev-CO2.Rmd
updated scrptfor Poster

--- 2019-05-11 awipev-CO2.Rmd
@@
 
-#plot for POSTER june 2019
-#plot of S/T
-poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 ), aes(x=datetime,y=temp_fb)) +
-  geom_point(col="blue", size=0.5 )+
+# #plot for POSTER june 2019
+# #plot of S/T
+poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
+  geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
   labs(x = "Time", y="Temperature (°C)") +
   scale_x_datetime(date_minor_breaks ="1 month")+
-  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
+  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity (PSU)"))
 print(poster_temp)
-ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
-
-poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb)) +
-  geom_point(col="blue", size=0.5 )+
-  labs(x = "Time", y="Salinity (PSU)") +
-  scale_x_datetime(date_minor_breaks ="1 month")+
-  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
-print(poster_sal)
-ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")
+
+png("poster_sal_temp.png", width= 1100, height=600)
+par(mar=c(5, 4, 4, 6) + 0.1)
+
+plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
+axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
+
+    grid(lty=1)
+
+   par(new = T)
+
+plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
+axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
+mtext("Time",side=1,col="black",line=1.5, cex=1.8)
+legend("topleft", legend=c("Temperature (°C)", "Salinity (PSU)"),
+       col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
+  #grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
+   #  lwd = "months")
+     box()
+     dev.off()
+
+# ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
+# 
+# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
+#   geom_point(col="blue", size=0.5 )+
+#   labs(x = "Time", y="Salinity (PSU)") +
+#   scale_x_datetime(date_minor_breaks ="1 month")+
+#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+# print(poster_sal)
+# ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")
 
@@
     labs(x="Salinity", y="Discrete TA", color = "Months")  +
-    theme(plot.title = element_text(size=7))  +
     stat_smooth(method = "lm", col = "black") +
-    labs(title = paste("Discrete TA vs Salinity", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                       "; Intercept =",signif(fit$coef[[1]],5 ),
-                       "; Slope =",signif(fit$coef[[2]], 5),
-                       "; P =",signif(summary(fit)$coef[2,4], 5))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + theme_bw()
-
-ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =10, units="cm")
+    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
+                       ";\nSlope =",signif(fit$coef[[2]], 5),
+                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
+  theme_bw() + 
+  theme(aspect.ratio=1,
+        axis.text=element_text(size=15),
+        axis.title.y= element_text(size =15),
+        axis.title.x= element_text(size =15),
+        plot.margin = unit(c(0.5,1,1,1), "cm"),
+        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70))) 
+  print(at_s)
+
+ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")
 
@@
 
-#plot for POSTER june 2019
-#plot of TA calculated from S + discrete
-p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
-  geom_point(col="blue", size=0.5 )+
-  geom_point(aes(y=at, fill= "Reference measured samples"), col="red") +
-  labs(x = "Time", y = "Calculated TA from salinity (µmoles/kg)") +
-  scale_x_datetime(date_minor_breaks ="1 month")+
-  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
-print(p_at_sal)
-ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
+# #plot for POSTER june 2019
+# #plot of TA calculated from S + discrete
+# p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
+#   geom_point(col="blue", size=0.5 )+
+#   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
+#   labs(title=  "Calculated TA from salinity (µmoles/kg)", x = "Time", y= "") +
+#   scale_x_datetime(date_minor_breaks ="1 month")+
+#   theme_bw() + theme(legend.position= c(0.7, 0.15), 
+#                      legend.text=element_text(size=15),
+#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 10, b = -20)),
+#                      axis.text=element_text(size=15),
+#                      axis.title.x= element_text(size =15),
+#                      legend.title=element_blank())
+# 
+#   
+# print(p_at_sal)
+# ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
 
@@
 
-#plot for POSTER june 2019
-#plot of TA VS calculated
-poster_at_atcal <- ggplot(data = at_nov_2018%>%dplyr::filter(at_calc > 2000), aes(x=at_calc,y=AT_filtered_despike,col="TA calculated from salinity") ) +
-  geom_point(col="blue", size=0.5 )+
-  labs(x = "Calculated TA", y = "Calculated TA from salinity (µmoles/kg)") +
-  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
-print(poster_at_atcal)
-ggsave(paste0("figures/poster_at_atcal.png"), width= 30, height=10, poster_at_atcal, units="cm")
 ```
@@
   geom_point(data=d_all, aes(x=datetime, y=pco2calc, fill="Calculated from AT/CT"), col="red" )+
-  labs(x = "Time", y = expression(~italic(p)~CO[2]~"(µatm)")) +
-  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+  labs(x = "Time", y ="", title = expression(~italic(p)~CO[2]~"(µatm)")) +
+  theme_bw() + theme(legend.position= c(0.59, 0.1),
+                     legend.text=element_text(size=14),
+                     plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
+                     axis.text=element_text(size=15),
+                     plot.margin = unit(c(0.5,1,1,1), "cm"),
+                     axis.title.x= element_text(size =15),
+                     legend.title=element_blank())
 print(poster_pco2)
 ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
+
     ```
@@
 
-#plot for POSTER june 2019
-#plot of pH seafet
-poster_ph <- ggplot( ) +
-  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Reference measured samples"), col="red" )+
-  labs(x = "Time", y = expression(pH[T]~seaFET)) +
-  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
-
-print(poster_ph)
-ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")
-
-# RANGE of pH
-d_all<- d_all%>%
-  dplyr::mutate(year = year(datetime))
-range <- tbl_df(
-  d_all %>%
-  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
-  summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
-)
-quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
-
-# Per month
-range_month <-
-  range %>%
-  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
-  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
-
-size_point <- 0.4 # size of data points
-plot_range_sf <-  
-  ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
-  Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-print(plot_range_sf)
-ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
+# #plot for POSTER june 2019
+# #plot of pH seafet
+# poster_ph <- ggplot( ) +
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
+#   labs(x = "Time", y ="", title = expression(pH[T]~seaFET)) +
+#   theme_bw() + theme(legend.position= c(0.8, 0.1), 
+#                      legend.text=element_text(size=14),
+#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
+#                       axis.text=element_text(size=15),
+#                       plot.margin = unit(c(1,1,1,1), "cm"),
+#                       axis.title.x= element_text(size =15),
+#                       legend.title=element_blank())
+# 
+# print(poster_ph)
+# ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")
+# 
+# # RANGE of pH
+# d_all<- d_all%>%
+#   dplyr::mutate(year = year(datetime))
+# range <- tbl_df(
+#   d_all %>%
+#   group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
+#   summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
+# )
+# quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
+# 
+# # Per month
+# range_month <-
+#   range %>%
+#   group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
+#   summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
+# 
+# size_point <- 0.4 # size of data points
+# plot_range_sf <-  
+#   ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
+#   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+#   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+#   labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
+#   Mytheme() +
+#   theme(panel.grid.major.x = element_blank())
+# print(plot_range_sf)
+# ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
 
@@
 
-#plot for POSTER june 2019
-#plot of pH durafet
-poster_dur <- ggplot( ) +
-  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Reference measured samples"), col="red" )+
-  labs(x = "Time", y = expression(pH[T]~durafet)) +
-  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
-
-print(poster_dur)
-ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")
-
-# RANGE of pH
-range_dur <- tbl_df(
-  d_all %>%
-  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
-  summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
-)
-quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
-
-# Per month
-range_month <-
-  range_dur %>%
-  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
-  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
-
-size_point <- 0.4 # size of data points
-plot_range_dur <-  
-  ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
-  Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-print(plot_range_dur)
-ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
+# #plot for POSTER june 2019
+# #plot of pH durafet
+# poster_dur <- ggplot( ) +
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
+#   labs(x = "Time", y= "", title = expression(pH[T]~durafet)) +
+#   theme_bw() + theme(legend.position= c(0.7, 0.8), 
+#                      legend.text=element_text(size=14),
+#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
+#                       axis.text=element_text(size=15),
+#                       plot.margin = unit(c(1,1,1,1), "cm"),
+#                       axis.title.x= element_text(size =15),
+#                       legend.title=element_blank())
+# 
+# print(poster_dur)
+# ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")
+# 
+# # RANGE of pH
+# range_dur <- tbl_df(
+#   d_all %>%
+#   group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
+#   summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
+# )
+# quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
+# 
+# # Per month
+# range_month <-
+#   range_dur %>%
+#   group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
+#   summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
+# 
+# size_point <- 0.4 # size of data points
+# plot_range_dur <-  
+#   ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
+#   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+#   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+#   labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
+#   Mytheme() +
+#   theme(panel.grid.major.x = element_blank())
+# print(plot_range_dur)
+# ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
 ```

### 2019-05-15 awipev-CO2.Rmd
updated scrptfor Poster 2

@@
   ggplot(data = fit_data, aes_string(x = xdata, y = ydata)) + 
-  geom_point(size = 3, col = "blue") +
+  geom_point(size = 2, col = "blue") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),
@@
 # #plot of S/T
-poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
-  geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
-  labs(x = "Time", y="Temperature (°C)") +
-  scale_x_datetime(date_minor_breaks ="1 month")+
-  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
-  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity (PSU)"))
-print(poster_temp)
-
-png("poster_sal_temp.png", width= 1100, height=600)
-par(mar=c(5, 4, 4, 6) + 0.1)
-
-plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
-axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
-
-    grid(lty=1)
-
-   par(new = T)
-
-plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
-axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
-mtext("Time",side=1,col="black",line=1.5, cex=1.8)
-legend("topleft", legend=c("Temperature (°C)", "Salinity (PSU)"),
-       col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
-  #grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
-   #  lwd = "months")
-     box()
-     dev.off()
+# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
+#   geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
+#   labs(x = "Time", y="Temperature (°C)") +
+#   scale_x_datetime(date_minor_breaks ="1 month")+
+#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
+#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity (PSU)"))
+# print(poster_temp)
+# 
+# png("poster_sal_temp.png", width= 1100, height=600)
+# par(mar=c(5, 4, 4, 6) + 0.1)
+# 
+# plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
+# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
+# 
+#     grid(lty=1)
+# 
+#    par(new = T)
+# 
+# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
+# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
+# mtext("Time",side=1,col="black",line=1.5, cex=1.8)
+# legend("topleft", legend=c("Temperature (°C)", "Salinity (PSU)"),
+#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
+#   #grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
+#    #  lwd = "months")
+#      box()
+#      dev.off()
 
@@
         plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70))) 
-  print(at_s)
+  #print(at_s)
 

### 2019-05-24 awipev-CO2.Rmd
script for poster

@@
 #   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
-#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity (PSU)"))
+#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
 # print(poster_temp)
 # 
-# png("poster_sal_temp.png", width= 1100, height=600)
+# png("figures/poster_sal_temp.png", width= 1100, height=600)
 # par(mar=c(5, 4, 4, 6) + 0.1)
@@
 # axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
-# mtext("Time",side=1,col="black",line=1.5, cex=1.8)
-# legend("topleft", legend=c("Temperature (°C)", "Salinity (PSU)"),
+# mtext("",side=1,col="black",line=1.5, cex=1.8)
+# legend("topleft", legend=c("Temperature (°C)", "Salinity"),
 #        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
@@
   scale_color_discrete(guide="none")+
-    labs(x="Salinity", y="Discrete TA", color = "Months")  +
+    labs(x="Salinity", y="Discrete AT", color = "Months")  +
     stat_smooth(method = "lm", col = "black") +
@@
 #   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
-#   labs(title=  "Calculated TA from salinity (µmoles/kg)", x = "Time", y= "") +
-#   scale_x_datetime(date_minor_breaks ="1 month")+
-#   theme_bw() + theme(legend.position= c(0.7, 0.15), 
+#   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
+#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
+#   theme(legend.position= c(0.5, 0.93),
 #                      legend.text=element_text(size=15),
-#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 10, b = -20)),
+#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
 #                      axis.text=element_text(size=15),
@@
 #plot of pCO2
-poster_pco2 <- ggplot( ) +
-  geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros,col="blue"), col="blue",size=0.5 ) +
-  geom_point(data=d_all, aes(x=datetime, y=pco2calc, fill="Calculated from AT/CT"), col="red" )+
-  labs(x = "Time", y ="", title = expression(~italic(p)~CO[2]~"(µatm)")) +
-  theme_bw() + theme(legend.position= c(0.59, 0.1),
-                     legend.text=element_text(size=14),
-                     plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
-                     axis.text=element_text(size=15),
-                     plot.margin = unit(c(0.5,1,1,1), "cm"),
-                     axis.title.x= element_text(size =15),
-                     legend.title=element_blank())
-print(poster_pco2)
-ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
+
+#  add pCO2 atmospheric data from URL
+
+# noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
+# noaa <- noaa %>%
+#   dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
+#   unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
+#   unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
+#   unite("datetime", c("date", "time"), sep=" ")
+#  
+# noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
+# noaa <- noaa %>%
+#  dplyr::filter(datetime > "2015-07-01 00:00:00")
+# 
+# 
+# poster_pco2 <- ggplot( ) +
+#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros,col="blue"), col="blue",size=0.5 ) +
+#   geom_point(data=d_all, aes(x=datetime, y=pco2calc), col="red" )+
+#   geom_point() +geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value),size=0.5 ) +
+#   scale_color_manual("",values=c("red", "blue", "black"), labels=c("pH spectro", "seaFET EXT ", "seaFET EXT corrected"))+
+#   labs(x = "", y ="", title = expression(paste(italic(p),CO[2]," (µatm)"))) +
+#   theme_bw() + theme(legend.position= c(0.59, 0.1),
+#                      legend.text=element_text(size=14),
+#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
+#                      axis.text=element_text(size=15),
+#                      plot.margin = unit(c(0.5,1,1,1), "cm"),
+#                      axis.title.x= element_text(size =15),
+#                      legend.title=element_blank())
+# print(poster_pco2)
+# ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
 
@@
 #   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
-#   labs(x = "Time", y ="", title = expression(pH[T]~seaFET)) +
-#   theme_bw() + theme(legend.position= c(0.8, 0.1), 
+#   labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
+#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
+#   theme(legend.position= c(0.17, 0.8),
 #                      legend.text=element_text(size=14),
@@
 # ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")
-# 
+
 # # RANGE of pH
@@
 #   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
-#   labs(x = "Time", y= "", title = expression(pH[T]~durafet)) +
-#   theme_bw() + theme(legend.position= c(0.7, 0.8), 
+#   labs(x = "", y= "", title = expression(pH[T]~durafet)) +
+#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
+#    theme(legend.position= c(0.17, 0.8),
 #                      legend.text=element_text(size=14),
@@
 ###**FerryBox**
+- **2019-05-22**: FB is stopped because of several problems. Philipp and Marine are working on it.
+- **2019-05-21**: FB is unstable. 
 - **2019-04-14**: FB is working again. 

### 2019-05-27 awipev-CO2.Rmd
update pCO2 plot

@@
 
-# noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
-# noaa <- noaa %>%
-#   dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
-#   unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
-#   unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
-#   unite("datetime", c("date", "time"), sep=" ")
-#  
-# noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
-# noaa <- noaa %>%
-#  dplyr::filter(datetime > "2015-07-01 00:00:00")
-# 
-# 
-# poster_pco2 <- ggplot( ) +
-#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros,col="blue"), col="blue",size=0.5 ) +
-#   geom_point(data=d_all, aes(x=datetime, y=pco2calc), col="red" )+
-#   geom_point() +geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value),size=0.5 ) +
-#   scale_color_manual("",values=c("red", "blue", "black"), labels=c("pH spectro", "seaFET EXT ", "seaFET EXT corrected"))+
-#   labs(x = "", y ="", title = expression(paste(italic(p),CO[2]," (µatm)"))) +
-#   theme_bw() + theme(legend.position= c(0.59, 0.1),
-#                      legend.text=element_text(size=14),
-#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
-#                      axis.text=element_text(size=15),
-#                      plot.margin = unit(c(0.5,1,1,1), "cm"),
-#                      axis.title.x= element_text(size =15),
-#                      legend.title=element_blank())
-# print(poster_pco2)
+noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
+noaa <- noaa %>%
+  dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
+  unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
+  unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
+  unite("datetime", c("date", "time"), sep=" ")
+
+noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
+noaa <- noaa %>%
+ dplyr::filter(datetime > "2015-07-01 00:00:00")
+
+#create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
+lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
+           "Calculated from AT/CT",
+          expression(paste(italic(p),CO[2]," (ppm; NOAA)"))
+          )
+
+col <- c("blue","red","green")
+
+poster_pco2 <- ggplot( ) +
+  geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
+  geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
+  geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="green" ),size=0.5)+
+  scale_shape_discrete(labels=lab, guide="none")+
+  scale_colour_manual(labels=lab, values=col)+
+  labs(x = "", y ="", title = "") +
+  theme_bw() +
+  scale_x_datetime(minor_breaks  = "1 month ")+
+  theme(legend.position= c(0.18, 0.85),
+                     legend.text=element_text(size=14, colour="black"),
+                     #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
+                     axis.text=element_text(size=15),
+                     plot.margin = unit(c(0.5,1,1,1), "cm"),
+                     axis.title.x= element_text(size =15),
+                     legend.title=element_blank()
+                     ) 
+print(poster_pco2)
  # ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")

### 2019-05-29 awipev-CO2.Rmd
update pCO2 plot

--- 2019-05-24 awipev-CO2.Rmd
@@
 
-#plot for POSTER june 2019
-#plot of pCO2
-
-#  add pCO2 atmospheric data from URL
-
+# #plot for POSTER june 2019
+# #plot of pCO2
+# 
+# #  add pCO2 atmospheric data from URL
+# 
 # noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
@@
 # 
+# #create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
+# lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
+#           expression(paste(italic(p),CO[2]," (ppm; from NOAA)")),
+#            "Calculated from AT/CT"
+#           
+#           )
+# 
+# col <- c("blue","black","red")
 # 
 # poster_pco2 <- ggplot( ) +
-#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros,col="blue"), col="blue",size=0.5 ) +
-#   geom_point(data=d_all, aes(x=datetime, y=pco2calc), col="red" )+
-#   geom_point() +geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value),size=0.5 ) +
-#   scale_color_manual("",values=c("red", "blue", "black"), labels=c("pH spectro", "seaFET EXT ", "seaFET EXT corrected"))+
-#   labs(x = "", y ="", title = expression(paste(italic(p),CO[2]," (µatm)"))) +
-#   theme_bw() + theme(legend.position= c(0.59, 0.1),
-#                      legend.text=element_text(size=14),
-#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
+#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
+#   geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
+#   geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+
+#   scale_shape_discrete(labels=lab, guide="none")+
+#   scale_colour_manual(labels=lab, values=col)+
+#   labs(x = "", y ="", title = "") +
+#   theme_bw() +
+#   scale_x_datetime(minor_breaks  = "1 month ")+
+#   theme(legend.position="top",  #c(0.18, 0.85)
+#                      legend.text=element_text(size=14, colour="black"),
+#                      #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
 #                      axis.text=element_text(size=15),
@@
 #                      axis.title.x= element_text(size =15),
-#                      legend.title=element_blank())
+#                      legend.title=element_blank()
+#                      ) 
 # print(poster_pco2)

### 2019-06-04 awipev-CO2.Rmd
discrete samplings data updated
one comment deleted

@@
 ```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
-# test
 Sys.setlocale("LC_ALL", "en_US.UTF-8")
@@
 ###**FerryBox**
+- **2019-06-03**: Samir is on site alone. Different tests were made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the problem (low flow).
 - **2019-05-22**: FB is stopped because of several problems. Philipp and Marine are working on it.

### 2019-06-05 awipev-CO2.Rmd
fixed knitting issue

@@
 
-#{.tabset .tabset-fade .tabset-pills}
-
-##Infos
-
-###**Introduction**
+# {.tabset .tabset-fade .tabset-pills}
+
+## Infos
+
+### **Introduction**
 <div style="text-align: justify">  
@@
 
-###**AWIPEV Underwater Observatory**
+### **AWIPEV Underwater Observatory**
 <div style="text-align: justify">  
@@
 
-###**Continuous and semi-continuous measurements**
+### **Continuous and semi-continuous measurements**
 <div style="text-align: justify">  
@@
 
-##Total alkalinity
+## Total alkalinity
 
@@
 
-###**Filtration of AT data: outliers removing**
+### **Filtration of AT data: outliers removing**
 
@@
 
-###**Correction of AT data**
+### **Correction of AT data**
 
@@
 
-####**Calibration**
+#### **Calibration**
 
@@
 
-####**CRM measurements**
+#### **CRM measurements**
 
@@
 
-####**Discrete samples ("references")**
+#### **Discrete samples ("references")**
 
@@
 
-#####**Third period**
+##### **Third period**
 
@@
 
-#####**Second period**
+##### **Second period**
 
@@
 
-###**Discrete total alkalinity (reference) vs salinity relationship**
+### **Discrete total alkalinity (reference) vs salinity relationship**
 
@@
 
-###**seaFET calibration constante E0**
+### **seaFET calibration constante E0**
 
@@
 
-###**seaFET pHT calibrated**
+### **seaFET pHT calibrated**
 pH is measured continuously by an autonomous seaFET pH sensor.
@@
 
-###**durafet calibration**
+### **Durafet calibration**
 
@@
 
-###**seaFET / durafet pHs**
+### **seaFET / durafet pHs**
 
@@
 
-###**calculated / durafet pHs**
+### **Calculated vs Durafet pHs**
 ```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
@@
 
-###**calculated / seaFET pHs**
+### **Calculated / seaFET pHs**
 ```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
@@
 
-##Maintenance
+## Maintenance
 <div style="text-align: justify">
 
-###**REMOS**
+### **REMOS**
 - **2018-11-24**: REMOS stopped because of an iceberg. At the moment we dont know if instruments are still there/broken.
 
-###**FerryBox**
+### **FerryBox**
 - **2019-06-03**: Samir is on site alone. Different tests were made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the problem (low flow).
@@
 
-###**TA analyser**
+### **TA analyser**
 - **2019-02-15**: No data from 15th (14:08:21 UTC) to 19th February (14:58:46 UTC). files transfered but no data. No explanation.
@@
 
-###**pH seaFET**
+### **pH seaFET**
 - **2018-04-17**: seaFET #1005 was changed on the REMOS and seaFET #007 (from Villefranche) was installed.
@@
 
-###***p*CO~2~**
+### ***p*CO~2~**
 - **2018-10-31**: *p*CO~2~ analyser (S/N: CO2FT-0215-001) have been installed and *p*CO~2~ analyser (S/N: CO2FT-0515-001) was brought back to France and waiting 2019 fundings to bring it for calibration.
@@
 
-##Script + data
+## Script + data
 <div style="text-align: justify">  
@@
 
-###**pH seaFET**
+### **pH seaFET**
 - **2018-08-30**: voltINT + phINT were filtered from 2017-12-14 to 2018-01-08 and bad data were removed from 2018-01-08 to 2018-02-02.
@@
 
-###**durafet**
+### **Durafet**
 Reference spectro measurement from the 2019-01-18 11:00 do not match with a durafet raw data because Ferrybox was off.
@@
 
-###***p*CO~2~**
+### ***p*CO~2~**
 - **2018-08-29**: Calibration parameters from #0215-001 were added to "./data/Calibration_pCO2/Data_Processing_sheet_pCO2.csv".
@@
 
-###**SNAPO**
+### **SNAPO**
 - **2019-04-30**: Duplicate "Ferrybox" samples (SN0316 and SN264, 2019-02-22 14:05) were sent by mistake in Villefranche for pH measurements.
@@
 
-###**Files - server**
+### **Files - server**
 - **2018-04-19**: Since "Ferrybox" is on again, the adding to solve the files issues are making not data into d_hour for this period (2018-09-03 to 2018-14-04).
@@
 
-**Data processing**
+** Data processing**
 

### 2019-06-05 awipev-CO2.Rmd
SNAPO plots + maintenance updated

@@
    dplyr::select(datetime, at, ct)%>%   
-   dplyr::mutate(at_diff = abs(at - lag(at)),
-                 ct_diff = abs(ct - lag(ct)))
+   dplyr::mutate(at_diff = at - lag(at),
+                 ct_diff = ct - lag(ct))
 
@@
     geom_point(data=diff, aes(x= datetime, y= at_diff)) +
-    geom_hline(yintercept= 3, size= 0.6, col="red", linetype="dashed") +
-    geom_hline(yintercept= -3, size= 0.6, col="red", linetype="dashed") +
-    #annotate("text", x = dat_dur$datetime[3], y = -0.16, label = "offset mean", color="red")+
+    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
+    geom_hline(yintercept= -4, size= 0.6, col="red", linetype="dashed") +
+    annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
+    annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
 labs(title= "AT", x="Time", y="Delta between TA replicates")+
@@
     geom_point(data=diff, aes(x= datetime, y= ct_diff)) +
-    geom_hline(yintercept= 3, size= 0.6, col="red", linetype="dashed") +
-    geom_hline(yintercept= -3, size= 0.6, col="red", linetype="dashed") +
-    #annotate("text", x = dat_dur$datetime[3], y = -0.16, label = "offset mean", color="red")+
+    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
+    geom_hline(yintercept= -4, size= 0.6, col="red", linetype="dashed") +
+annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
+    annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
   labs(title= "CT",x="Time", y="Delta between CT replicates")+
@@
 ### **FerryBox**
+- **2019-06-05**: PRoblem in the relay 15 that controls the waste water pump was found. The spare part will be brought here next week (when Samir will leave...).
 - **2019-06-03**: Samir is on site alone. Different tests were made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the problem (low flow).

### 2019-06-07 awipev-CO2.Rmd

@@
 # DYGRAPH
+
+# to create periods according to SNAPCO analysis 
+snapcoevents <- c("2015-07-23 00:00:00", "2015-11-18 00:00:00", "2015-11-27 00:00:00", "2016-10-13 00:00:00", 
+              "2017-05-11 00:00:00", "2018-02-09 00:00:00", "2018-02-16 00:00:00", "2018-07-27 00:00:00", "2018-08-03 00:00:00", "2018-11-23 00:00:00", "2018-11-03 00:00:00", "2019-04-12 00:00:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
+
 at_diff_xts <- dplyr::select(diff, datetime, at_diff, at)
@@
     dySeries("at", label = "AT duplicates", color =  "blue", strokeWidth = 0, pointSize = 2, axis = "y2" ) %>%
+  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
+  dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#EDEDED") %>%
+  dyShading(from = snapcoevents[3], to = snapcoevents[4], color = "#C2C2C2") %>%
+  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#EDEDED") %>%
+  dyShading(from = snapcoevents[7], to = snapcoevents[8], color = "#C2C2C2") %>%
+  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#EDEDED") %>%
+  dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C2C2") %>%
   dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
@@
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
+   dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#EDEDED") %>%
+  dyShading(from = snapcoevents[3], to = snapcoevents[4], color = "#C2C2C2") %>%
+  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#EDEDED") %>%
+  dyShading(from = snapcoevents[7], to = snapcoevents[8], color = "#C2C2C2") %>%
+  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#EDEDED") %>%
+  dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C2C2") %>%
   dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%

### 2019-06-07 awipev-CO2.Rmd
plot updated

@@
 snapcoevents <- c("2015-07-23 00:00:00", "2015-11-18 00:00:00", "2015-11-27 00:00:00", "2016-10-13 00:00:00", 
-              "2017-05-11 00:00:00", "2018-02-09 00:00:00", "2018-02-16 00:00:00", "2018-07-27 00:00:00", "2018-08-03 00:00:00", "2018-11-23 00:00:00", "2018-11-03 00:00:00", "2019-04-12 00:00:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
+              "2017-05-11 00:00:00", "2018-02-09 00:00:00", "2018-02-16 00:00:00", "2018-07-27 00:00:00", "2018-08-03 00:00:00", "2018-11-23 00:00:00", "2018-11-30 00:00:00", "2019-04-12 00:00:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
 
@@
     dySeries("at", label = "AT duplicates", color =  "blue", strokeWidth = 0, pointSize = 2, axis = "y2" ) %>%
-  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
   dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C2C2") %>%
-  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
+  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5,valueRange = c(-25, 30)) %>%
     dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%

### 2019-06-18 awipev-CO2.Rmd
text updated

@@
 ##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
+##   *****Attention, I asked to the logisticians to log outside temp from 9 june 2019
 
@@
 
+p_ct_ts <- ggplot() +
+    geom_point(data=discrete, aes(x= datetime, y= ct)) +
+  labs(title= "",x="Time", y="CT (µmoles/kg)")+
+    Mytheme()
+p_at_ts <- ggplot() +
+    geom_point(data=discrete, aes(x= datetime, y= at)) +
+  labs(title= "",x="Time", y="AT (µmoles/kg)")+
+    Mytheme()
+
 # DYGRAPH
@@
 pdelta_at_snapo_dygraph
+p_at_ts
 pdelta_ct_snapo
 pdelta_ct_snapo_dygraph
+p_ct_ts
 ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")

### 2019-07-12 awipev-CO2.Rmd
Uncommented the poster sections

@@
 
-# #plot for POSTER june 2019
-# #plot of S/T
-# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
-#   geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
-#   labs(x = "Time", y="Temperature (°C)") +
-#   scale_x_datetime(date_minor_breaks ="1 month")+
-#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
-#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
-# print(poster_temp)
+#plot for POSTER june 2019
+#plot of S/T
+poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
+  geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
+  labs(x = "Time", y="Temperature (°C)") +
+  scale_x_datetime(date_minor_breaks ="1 month")+
+  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
+  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
+print(poster_temp)
 #
-# png("figures/poster_sal_temp.png", width= 1100, height=600)
-# par(mar=c(5, 4, 4, 6) + 0.1)
+png("figures/poster_sal_temp.png", width= 1100, height=600)
+par(mar=c(5, 4, 4, 6) + 0.1)
 #
-# plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
-# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
+plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
+axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
 #
-#     grid(lty=1)
+   grid(lty=1)
 #
-#    par(new = T)
+   par(new = T)
 #
-# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
-# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
-# mtext("",side=1,col="black",line=1.5, cex=1.8)
-# legend("topleft", legend=c("Temperature (°C)", "Salinity"),
-#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
-#   #grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
-#    #  lwd = "months")
-#      box()
-#      dev.off()
-
-# ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
+plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
+axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
+mtext("",side=1,col="black",line=1.5, cex=1.8)
+legend("topleft", legend=c("Temperature (°C)", "Salinity"),
+       col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
+  grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
+    lwd = "months")
+     box()
+     dev.off()
+
+ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
 #
-# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
-#   geom_point(col="blue", size=0.5 )+
-#   labs(x = "Time", y="Salinity (PSU)") +
-#   scale_x_datetime(date_minor_breaks ="1 month")+
-#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
-# print(poster_sal)
-# ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")
+poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
+  geom_point(col="blue", size=0.5 )+
+  labs(x = "Time", y="Salinity (PSU)") +
+  scale_x_datetime(date_minor_breaks ="1 month")+
+  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+print(poster_sal)
+ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")
 
@@
 
-# #plot for POSTER june 2019
-# #plot of TA calculated from S + discrete
-# p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
-#   geom_point(col="blue", size=0.5 )+
-#   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
-#   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
-#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-#   theme(legend.position= c(0.5, 0.93),
-#                      legend.text=element_text(size=15),
-#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
-#                      axis.text=element_text(size=15),
-#                      axis.title.x= element_text(size =15),
-#                      legend.title=element_blank())
-# 
-# 
-# print(p_at_sal)
-# ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
+#plot for POSTER june 2019
+#plot of TA calculated from S + discrete
+p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
+  geom_point(col="blue", size=0.5 )+
+  geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
+  labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
+  theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
+  theme(legend.position= c(0.5, 0.93),
+                     legend.text=element_text(size=15),
+                     plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
+                     axis.text=element_text(size=15),
+                     axis.title.x= element_text(size =15),
+                     legend.title=element_blank())
+
+print(p_at_sal)
+ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
 
@@
 
-# #plot for POSTER june 2019
-# #plot of pCO2
-# 
-# #  add pCO2 atmospheric data from URL
-# 
-# noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
-# noaa <- noaa %>%
-#   dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
-#   unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
-#   unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
-#   unite("datetime", c("date", "time"), sep=" ")
-# 
-# noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
-# noaa <- noaa %>%
-#  dplyr::filter(datetime > "2015-07-01 00:00:00")
-# 
-# #create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
-# lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
-#           expression(paste(italic(p),CO[2]," (ppm; from NOAA)")),
-#            "Calculated from AT/CT"
-#           
-#           )
-# 
-# col <- c("blue","black","red")
-# 
-# poster_pco2 <- ggplot( ) +
-#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
-#   geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
-#   geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+
-#   scale_shape_discrete(labels=lab, guide="none")+
-#   scale_colour_manual(labels=lab, values=col)+
-#   labs(x = "", y ="", title = "") +
-#   theme_bw() +
-#   scale_x_datetime(minor_breaks  = "1 month ")+
-#   theme(legend.position="top",  #c(0.18, 0.85)
-#                      legend.text=element_text(size=14, colour="black"),
-#                      #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
-#                      axis.text=element_text(size=15),
-#                      plot.margin = unit(c(0.5,1,1,1), "cm"),
-#                      axis.title.x= element_text(size =15),
-#                      legend.title=element_blank()
-#                      ) 
-# print(poster_pco2)
-#   ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
+#plot for POSTER june 2019
+#plot of pCO2
+
+#  add pCO2 atmospheric data from URL
+
+noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
+noaa <- noaa %>%
+  dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
+  unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
+  unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
+  unite("datetime", c("date", "time"), sep=" ")
+
+noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
+noaa <- noaa %>%
+ dplyr::filter(datetime > "2015-07-01 00:00:00")
+
+#create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
+lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
+          expression(paste(italic(p),CO[2]," (ppm; from NOAA)")),
+           "Calculated from AT/CT"
+
+          )
+
+col <- c("blue","black","red")
+
+poster_pco2 <- ggplot( ) +
+  geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
+  geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
+  geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+
+  scale_shape_discrete(labels=lab, guide="none")+
+  scale_colour_manual(labels=lab, values=col)+
+  labs(x = "", y ="", title = "") +
+  theme_bw() +
+  scale_x_datetime(minor_breaks  = "1 month ")+
+  theme(legend.position="top",  #c(0.18, 0.85)
+                     legend.text=element_text(size=14, colour="black"),
+                     #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
+                     axis.text=element_text(size=15),
+                     plot.margin = unit(c(0.5,1,1,1), "cm"),
+                     axis.title.x= element_text(size =15),
+                     legend.title=element_blank()
+                     )
+print(poster_pco2)
+  ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
 
@@
 
-# #plot for POSTER june 2019
-# #plot of pH seafet
-# poster_ph <- ggplot( ) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
-#   labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
-#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-#   theme(legend.position= c(0.17, 0.8),
-#                      legend.text=element_text(size=14),
-#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
-#                       axis.text=element_text(size=15),
-#                       plot.margin = unit(c(1,1,1,1), "cm"),
-#                       axis.title.x= element_text(size =15),
-#                       legend.title=element_blank())
-# 
-# print(poster_ph)
-# ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")
-
-# # RANGE of pH
-# d_all<- d_all%>%
-#   dplyr::mutate(year = year(datetime))
-# range <- tbl_df(
-#   d_all %>%
-#   group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
-#   summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
-# )
-# quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
-# 
-# # Per month
-# range_month <-
-#   range %>%
-#   group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
-#   summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
-# 
-# size_point <- 0.4 # size of data points
-# plot_range_sf <-  
-#   ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
-#   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-#   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-#   labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
-#   Mytheme() +
-#   theme(panel.grid.major.x = element_blank())
-# print(plot_range_sf)
-# ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
+#plot for POSTER june 2019
+#plot of pH seafet
+poster_ph <- ggplot() +
+  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
+  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
+  labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
+  theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
+  theme(legend.position= c(0.17, 0.8),
+                     legend.text=element_text(size=14),
+                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
+                      axis.text=element_text(size=15),
+                      plot.margin = unit(c(1,1,1,1), "cm"),
+                      axis.title.x= element_text(size =15),
+                      legend.title=element_blank())
+
+print(poster_ph)
+ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")
+
+#RANGE of pH
+d_all<- d_all%>%
+  dplyr::mutate(year = year(datetime))
+range <- tbl_df(
+  d_all %>%
+  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
+  summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
+)
+quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
+
+#Per month
+range_month <-
+  range %>%
+  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
+  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
+
+size_point <- 0.4 #size of data points
+plot_range_sf <-  
+  ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+print(plot_range_sf)
+ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
 
@@
 
-# #plot for POSTER june 2019
-# #plot of pH durafet
-#  poster_dur <- ggplot( ) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
-#   labs(x = "", y= "", title = expression(pH[T]~durafet)) +
-#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-#    theme(legend.position= c(0.17, 0.8),
-#                      legend.text=element_text(size=14),
-#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
-#                       axis.text=element_text(size=15),
-#                       plot.margin = unit(c(1,1,1,1), "cm"),
-#                       axis.title.x= element_text(size =15),
-#                       legend.title=element_blank())
-# 
-# print(poster_dur)
-# ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")
-# 
-# # RANGE of pH
-# range_dur <- tbl_df(
-#   d_all %>%
-#   group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
-#   summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
-# )
-# quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
-# 
-# # Per month
-# range_month <-
-#   range_dur %>%
-#   group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
-#   summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
-# 
-# size_point <- 0.4 # size of data points
-# plot_range_dur <-  
-#   ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
-#   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-#   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-#   labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
-#   Mytheme() +
-#   theme(panel.grid.major.x = element_blank())
-# print(plot_range_dur)
-# ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
+#plot for POSTER june 2019
+#plot of pH durafet
+ poster_dur <- ggplot( ) +
+  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
+  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
+  labs(x = "", y= "", title = expression(pH[T]~durafet)) +
+  theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
+   theme(legend.position= c(0.17, 0.8),
+                     legend.text=element_text(size=14),
+                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
+                      axis.text=element_text(size=15),
+                      plot.margin = unit(c(1,1,1,1), "cm"),
+                      axis.title.x= element_text(size =15),
+                      legend.title=element_blank())
+
+print(poster_dur)
+ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")
+
+# RANGE of pH
+range_dur <- tbl_df(
+  d_all %>%
+  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
+  summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
+)
+quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
+
+# Per month
+range_month <-
+  range_dur %>%
+  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
+  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
+
+size_point <- 0.4 # size of data points
+plot_range_dur <-
+  ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+print(plot_range_dur)
+ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
 ```

### 2019-07-18 awipev-CO2.Rmd
ph plots updated

@@
 
-#plot for POSTER june 2019
-#plot of pH seafet
-poster_ph <- ggplot() +
-  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
-  labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
-  theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-  theme(legend.position= c(0.17, 0.8),
-                     legend.text=element_text(size=14),
-                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
-                      axis.text=element_text(size=15),
-                      plot.margin = unit(c(1,1,1,1), "cm"),
-                      axis.title.x= element_text(size =15),
-                      legend.title=element_blank())
-
-print(poster_ph)
-ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")
+# #plot for POSTER june 2019
+# #plot of pH seafet
+# poster_ph <- ggplot() +
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
+#   labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
+#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
+#   theme(legend.position= c(0.17, 0.8),
+#                      legend.text=element_text(size=14),
+#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
+#                       axis.text=element_text(size=15),
+#                       plot.margin = unit(c(1,1,1,1), "cm"),
+#                       axis.title.x= element_text(size =15),
+#                       legend.title=element_blank())
+# 
+# print(poster_ph)
+# ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")
 
@@
 ```
+
 The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).
@@
 
-### **Calculated vs Durafet pHs**
+### **Calculated / Durafet pHs**
 ```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
@@
 # DURAFET vs CALC
+fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pH_durafet_norm4 , nperm = 99)
+
 pdur_calc_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pH_calc_norm4, label = month))+
@@
   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-   coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2)) + scale_color_discrete(guide="none")+
+   coord_fixed(ratio = 1 , xlim=c(8,8.22), ylim=c(8,8.22)) + 
+  scale_color_discrete(guide="none")+
   labs(x="pH durafet, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
@@
 # SEAFET vs CALC
+fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pHint_tot_sf_norm4 , nperm = 99)
+
 psf_calc_norm_text <-  ggplot(d_all,aes(x=pHint_tot_sf_norm4, y= pH_calc_norm4, label = month))+
@@
 ```
-
+### **Spectro / durafet**
+
+```{r pHs comparaison durafet spectro, echo=FALSE, message= FALSE, warning=FALSE}
+# Spectro / durafet
+fit <- lmodel2(data = d_all,  pH_s_durafet_temp_field ~ pH_durafet_corrected , nperm = 99)
+
+p_dura_spectro <-  ggplot(d_all,aes(x=pH_durafet_corrected, y= pH_s_durafet_temp_field, label = month))+
+  geom_text( aes(color=factor(month))) + 
+  scale_color_discrete(guide = "none")+
+  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
+  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+  labs(title = paste("pH spectro vs pH durafet","\n Adj R2 = ", signif(fit$rsquare, 3),
+                     "; Intercept =", signif(fit$regression.results[2,2], 3),
+                     "; Slope =", signif( fit$regression.results[2,3], 3),
+                     "; P =", signif(fit$P.param, 3))) +
+  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
+  labs(x="pH durafet", y="pH spectro, 4°C ", color = "Months") + theme_bw() 
+p_dura_spectro
+```
+
+### **Spectro / seaFET**
+
+```{r pHs comparaison sf spectro, echo=FALSE, message= FALSE, warning=FALSE}
+# Spectro / seafet
+fit <- lmodel2(data = d_all,  pH_s_seafet_temp_field ~ pHint_tot_sf , nperm = 99)
+
+p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_field, label = month))+
+  geom_text( aes(color=factor(month))) + 
+  scale_color_discrete(guide = "none")+
+  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
+  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+  labs(title = paste("pH spectro vs pH seaFET","\n Adj R2 = ", signif(fit$rsquare, 3),
+                     "; Intercept =", signif(fit$regression.results[2,2], 3),
+                     "; Slope =", signif( fit$regression.results[2,3], 3),
+                     "; P =", signif(fit$P.param, 3))) +
+  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
+  labs(x="pH seaFET", y="pH spectro, 4°C ", color = "Months") + theme_bw() 
+p_sf_spectro
+```
 ## SNAPO-CO2

### 2019-07-18 awipev-CO2.Rmd
ph plots updated

@@
 ```
+
 ### **Spectro / durafet**
@@
 ```
+
 ## SNAPO-CO2

### 2019-07-19 awipev-CO2.Rmd

@@
 
-#plot for POSTER june 2019
-#plot of S/T
-poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
-  geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
-  labs(x = "Time", y="Temperature (°C)") +
-  scale_x_datetime(date_minor_breaks ="1 month")+
-  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
-  scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
-print(poster_temp)
+# #plot for POSTER june 2019
+# #plot of S/T
+# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
+#   geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
+#   labs(x = "Time", y="Temperature (°C)") +
+#   scale_x_datetime(date_minor_breaks ="1 month")+
+#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
+#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
+# print(poster_temp)
+# #
+# png("figures/poster_sal_temp.png", width= 1100, height=600)
+# par(mar=c(5, 4, 4, 6) + 0.1)
+# #
+# plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
+# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
+# #
+#    grid(lty=1)
+# #
+#    par(new = T)
+# #
+# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
+# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
+# mtext("",side=1,col="black",line=1.5, cex=1.8)
+# legend("topleft", legend=c("Temperature (°C)", "Salinity"),
+#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
+#   grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
+#     lwd = "months")
+#      box()
+#      dev.off()
 # 
-png("figures/poster_sal_temp.png", width= 1100, height=600)
-par(mar=c(5, 4, 4, 6) + 0.1)
 # 
-plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
-axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
-#
-   grid(lty=1)
-#
-   par(new = T)
-#
-plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
-axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
-mtext("",side=1,col="black",line=1.5, cex=1.8)
-legend("topleft", legend=c("Temperature (°C)", "Salinity"),
-       col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
-  grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
-    lwd = "months")
-     box()
-     dev.off()
-
-ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
-#
-poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
-  geom_point(col="blue", size=0.5 )+
-  labs(x = "Time", y="Salinity (PSU)") +
-  scale_x_datetime(date_minor_breaks ="1 month")+
-  theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
-print(poster_sal)
-ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")
+# ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
+# #
+# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
+#   geom_point(col="blue", size=0.5 )+
+#   labs(x = "Time", y="Salinity (PSU)") +
+#   scale_x_datetime(date_minor_breaks ="1 month")+
+#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
+# print(poster_sal)
+# ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")
 
@@
 
-#plot for POSTER june 2019
-#plot of TA calculated from S + discrete
-p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
-  geom_point(col="blue", size=0.5 )+
-  geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
-  labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
-  theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-  theme(legend.position= c(0.5, 0.93),
-                     legend.text=element_text(size=15),
-                     plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
-                     axis.text=element_text(size=15),
-                     axis.title.x= element_text(size =15),
-                     legend.title=element_blank())
-
-print(p_at_sal)
-ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
+# #plot for POSTER june 2019
+# #plot of TA calculated from S + discrete
+# p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
+#   geom_point(col="blue", size=0.5 )+
+#   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
+#   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
+#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
+#   theme(legend.position= c(0.5, 0.93),
+#                      legend.text=element_text(size=15),
+#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
+#                      axis.text=element_text(size=15),
+#                      axis.title.x= element_text(size =15),
+#                      legend.title=element_blank())
+# 
+# 
+# print(p_at_sal)
+# ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
 
@@
 
-#plot for POSTER june 2019
-#plot of pCO2
-
-#  add pCO2 atmospheric data from URL
-
-noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
-noaa <- noaa %>%
-  dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
-  unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
-  unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
-  unite("datetime", c("date", "time"), sep=" ")
-
-noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
-noaa <- noaa %>%
- dplyr::filter(datetime > "2015-07-01 00:00:00")
-
-#create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
-lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
-          expression(paste(italic(p),CO[2]," (ppm; from NOAA)")),
-           "Calculated from AT/CT"
-
-          )
-
-col <- c("blue","black","red")
-
-poster_pco2 <- ggplot( ) +
-  geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
-  geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
-  geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+
-  scale_shape_discrete(labels=lab, guide="none")+
-  scale_colour_manual(labels=lab, values=col)+
-  labs(x = "", y ="", title = "") +
-  theme_bw() +
-  scale_x_datetime(minor_breaks  = "1 month ")+
-  theme(legend.position="top",  #c(0.18, 0.85)
-                     legend.text=element_text(size=14, colour="black"),
-                     #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
-                     axis.text=element_text(size=15),
-                     plot.margin = unit(c(0.5,1,1,1), "cm"),
-                     axis.title.x= element_text(size =15),
-                     legend.title=element_blank()
-                     )
-print(poster_pco2)
-  ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
+# #plot for POSTER june 2019
+# #plot of pCO2
+# 
+# #  add pCO2 atmospheric data from URL
+# 
+# noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
+# noaa <- noaa %>%
+#   dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
+#   unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
+#   unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
+#   unite("datetime", c("date", "time"), sep=" ")
+# 
+# noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
+# noaa <- noaa %>%
+#  dplyr::filter(datetime > "2015-07-01 00:00:00")
+# 
+# #create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
+# lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
+#           expression(paste(italic(p),CO[2]," (ppm; from NOAA)")),
+#            "Calculated from AT/CT"
+# 
+#           )
+# 
+# col <- c("blue","black","red")
+# 
+# poster_pco2 <- ggplot( ) +
+#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
+#   geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
+#   geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+
+#   scale_shape_discrete(labels=lab, guide="none")+
+#   scale_colour_manual(labels=lab, values=col)+
+#   labs(x = "", y ="", title = "") +
+#   theme_bw() +
+#   scale_x_datetime(minor_breaks  = "1 month ")+
+#   theme(legend.position="top",  #c(0.18, 0.85)
+#                      legend.text=element_text(size=14, colour="black"),
+#                      #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
+#                      axis.text=element_text(size=15),
+#                      plot.margin = unit(c(0.5,1,1,1), "cm"),
+#                      axis.title.x= element_text(size =15),
+#                      legend.title=element_blank()
+#                      )
+# print(poster_pco2)
+#   ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
 
@@
 
-#plot for POSTER june 2019
-#plot of pH durafet
- poster_dur <- ggplot( ) +
-  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-  geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
-  labs(x = "", y= "", title = expression(pH[T]~durafet)) +
-  theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-   theme(legend.position= c(0.17, 0.8),
-                     legend.text=element_text(size=14),
-                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
-                      axis.text=element_text(size=15),
-                      plot.margin = unit(c(1,1,1,1), "cm"),
-                      axis.title.x= element_text(size =15),
-                      legend.title=element_blank())
-
-print(poster_dur)
-ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")
+# #plot for POSTER june 2019
+# #plot of pH durafet
+#  poster_dur <- ggplot( ) +
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
+#   labs(x = "", y= "", title = expression(pH[T]~durafet)) +
+#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
+#    theme(legend.position= c(0.17, 0.8),
+#                      legend.text=element_text(size=14),
+#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
+#                       axis.text=element_text(size=15),
+#                       plot.margin = unit(c(1,1,1,1), "cm"),
+#                       axis.title.x= element_text(size =15),
+#                       legend.title=element_blank())
+# 
+# print(poster_dur)
+# ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")
 
@@
 ### **FerryBox**
-- **2019-06-05**: PRoblem in the relay 15 that controls the waste water pump was found. The spare part will be brought here next week (when Samir will leave...).
+- **2019-06-12**: Markus came to do maintenace. 
+- **2019-06-05**: Problem in the relay 15 that controls the waste water pump was found. The spare part will be brought here next week (when Samir will leave...).
 - **2019-06-03**: Samir is on site alone. Different tests were made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the problem (low flow).
@@
 ### **TA analyser**
+- **2019-07-12**: Steffen told us that calibration was not OK.
+To check it, he calculated the mediane of the pH/volume sample / volumeIndicatorfactor and compared them to January/October calibration.
+We wait for Steffen recommandations before to make another calibration.
+- **2019-06-07**: Samir did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. TA was stable before the calibration and calibration was OK.
 - **2019-02-15**: No data from 15th (14:08:21 UTC) to 19th February (14:58:46 UTC). files transfered but no data. No explanation.

### 2019-08-28 awipev-CO2.Rmd
Changed y scale for AT

@@
   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-  dyAxis("y",valueRange = c(1600, 2450)) %>%
+  dyAxis("y",valueRange = c(1600, 2550)) %>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%

### 2019-08-29 awipev-CO2.Rmd
plot parameters updates

@@
       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
-      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+    dyLegend(show = "follow")   %>%
     dyAxis("y",valueRange = c(30, 36)) %>%
@@
       dyAxis("y", valueRange = c(-2.5, 9.5)) %>%
+      dyLegend(show = "follow")   %>%
       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
       dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+      dyLegend(show = "follow")   %>%
       dyRangeSelector(height = 30, dateWindow= NULL)
@@
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
+    dyLegend(show = "follow")   %>%
     dyRangeSelector(height = 30, dateWindow= NULL)
@@
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyAxis("y",valueRange = c(8, 8.6)) %>%
-
+    dyAxis("y",valueRange = c(8, 8.8)) %>%
+    dyLegend(show = "follow")   %>%
     dyRangeSelector(height = 30, dateWindow= NULL) 
@@
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyAxis("y",valueRange = c(7.45, 8.6)) %>%
+    dyAxis("y",valueRange = c(7.45, 8.8)) %>%
+    dyLegend(show = "follow")   %>%
     dyRangeSelector(height = 30, dateWindow= NULL) 
@@
   dyOptions( strokeWidth= 0) %>%
+  dyLegend(show = "follow")   %>%
   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
@@
   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-  dyAxis("y",valueRange = c(1600, 2550)) %>%
+  dyAxis("y",valueRange = c(1600, 2650)) %>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
   dyOptions( strokeWidth= 0) %>%
+  dyLegend(show = "follow")   %>%
   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
@@
   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-  dyAxis("y",valueRange = c(2000, 2450)) %>%
+  dyAxis("y",valueRange = c(2000, 2650)) %>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
   dyOptions( strokeWidth= 0) %>%
+  dyLegend(show = "follow")   %>%
   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
@@
 at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) +
-  geom_point(aes(y=AT_filtered, colour = "before")) +
-  geom_point(aes(y=AT_filtered_despike, colour = "after")) +
+  geom_point(aes(y=AT_filtered, colour = "before"), size =3) +
+  geom_point(aes(y=AT_filtered_despike, colour = "after"), size = 2) +
   labs(x = "Time", y = "Total alkalinity", color = "despike") 
@@
     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+    dyLegend(show = "follow")   %>%
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
@@
                                  ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
-                                ifelse(datetime >= sfinterv[14] , 14,NA )))))))))))))))
+                                 ifelse(datetime >= sfinterv[14] & datetime <= sfinterv[15], 14,
+                                 ifelse(datetime >= sfinterv[15] & datetime <= sfinterv[16], 15,
+                                 ifelse(datetime >= sfinterv[16] & datetime <= sfinterv[17], 16,
+                                        ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
+                                ifelse(datetime >= sfinterv[18] , 18,NA )))))))))))))))))))
 
@@
 
-```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE}
+```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE, warning=FALSE}
 ####
@@
   dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[14], to= Sys.Date(), color = "#E0E0E0") %>%
-
+   dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
+   dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
+   dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
+     dyShading(from = sfinterv[17], to= sfinterv[18], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[18], to= Sys.Date(), color = "#CCCCCC") %>%
+  dyLegend(show = "follow")   %>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
                                 ifelse(datetime >= durinterv[14] & datetime <= durinterv[15], 14,
-                                ifelse(datetime >= durinterv[15], 14,NA ))))))))))))))))
+                                ifelse(datetime >= durinterv[15] & datetime <= durinterv[16], 15,
+                                ifelse(datetime >= durinterv[16] & datetime <= durinterv[17], 16,
+                                 ifelse(datetime >= durinterv[17] & datetime <= durinterv[18], 17,
+                                ifelse(datetime >= durinterv[18] & datetime <= durinterv[19], 18,
+
+                                ifelse(datetime >= durinterv[19], 18,NA ))))))))))))))))))))
 
@@
                                 ifelse(deployment_dur == 13, dat_dur$diff_pH_dur[13],
-                                ifelse(deployment_dur == 14, dat_dur$diff_pH_dur[14],0)))))))))))))),
+                                ifelse(deployment_dur == 14, dat_dur$diff_pH_dur[14],
+                                ifelse(deployment_dur == 15, dat_dur$diff_pH_dur[15],
+                                ifelse(deployment_dur == 16, dat_dur$diff_pH_dur[16],
+                                ifelse(deployment_dur == 17, dat_dur$diff_pH_dur[17],
+                                ifelse(deployment_dur == 18, dat_dur$diff_pH_dur[18],
+                                ifelse(deployment_dur == 19, dat_dur$diff_pH_dur[19],0))))))))))))))))))),
               pH_durafet_corrected = pH_durafet + offset_durafet
@@
     dyShading(from = durinterv[12], to= durinterv[13], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[14], to= Sys.Date(), color = "#CCCCCC") %>%
+   dyShading(from = durinterv[13], to= durinterv[14], color = "#CCCCCC") %>%
+   dyShading(from = durinterv[14], to= durinterv[15], color = "#E0E0E0") %>%
+   dyShading(from = durinterv[15], to= durinterv[16], color = "#CCCCCC") %>%
+   dyShading(from = durinterv[16], to= durinterv[17], color = "#E0E0E0") %>%
+   dyShading(from = durinterv[17], to= Sys.Date(), color = "#CCCCCC") %>%
+     dyLegend(show = "follow")   %>%
     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+       dyLegend(show = "follow")   %>%
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
@@
     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+       dyLegend(show = "follow")   %>%
 dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
@@
     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+       dyLegend(show = "follow")   %>%
     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=2) %>%
@@
     dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%
+       dyLegend(show = "follow")   %>%
     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
 
-###**Cross-Flow filter**
+### **Cross-Flow filter**
 - **2019-01-26**: The filter was lifted up in order to fix the flow problem. 
@@
 
-###**durafet**
+### **durafet**
 - **2017-10-30**: (13:00 UTC) Durafet holder was changed by Benoit and the new one (made by Uwe) more larger (all the durafet's body is plunge in the seawater) was installed.

### 2019-09-12 awipev-CO2.Rmd
maintenance text updated

@@
     dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
+      dyEvent(as.POSIXct("2019-09-03 15:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>%
+
     #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
+       dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="GMT"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
+
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
 ### **REMOS**
+- **2019-09-07**: REMOS back in the water.
+- **2019-09-02**: REMOS removed from the water for maintenance with Philipp and Samir.
 - **2018-11-24**: REMOS stopped because of an iceberg. At the moment we dont know if instruments are still there/broken.
@@
 ### **FerryBox**
+- **2019-09-01**: Some interruptions for the FB during 2 weeks of maintenance.
 - **2019-06-12**: Markus came to do maintenace. 
@@
 ### **pH seaFET**
+- **2019-09-02**: Out from the water for maintenance and cleaning only.
 - **2018-04-17**: seaFET #1005 was changed on the REMOS and seaFET #007 (from Villefranche) was installed.
@@
 ### **durafet**
+- **2019-09-05**: same durafet 
 - **2017-10-30**: (13:00 UTC) Durafet holder was changed by Benoit and the new one (made by Uwe) more larger (all the durafet's body is plunge in the seawater) was installed.
@@
 ### ***p*CO~2~**
+- **2019-09-03**: *p*CO~2~ analyser (S/N: CO2FT-0515-001) have been installed and *p*CO~2~ analyser (S/N: CO2FT-0215-001) was sent to Kiel for calibration.
 - **2018-10-31**: *p*CO~2~ analyser (S/N: CO2FT-0215-001) have been installed and *p*CO~2~ analyser (S/N: CO2FT-0515-001) was brought back to France and waiting 2019 fundings to bring it for calibration.

### 2019-09-13 awipev-CO2.Rmd

@@
                                  ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
-                                ifelse(datetime >= sfinterv[18] , 18,NA )))))))))))))))))))
+                                ifelse(datetime >= sfinterv[18] & datetime <= sfinterv[19], 18,
+                                ifelse(datetime >= sfinterv[19] & datetime <= sfinterv[20], 19,
+                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
+                                ifelse(datetime >= sfinterv[21] , 21,NA ))))))))))))))))))))))
 
@@
    dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
-     dyShading(from = sfinterv[17], to= sfinterv[18], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[18], to= Sys.Date(), color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[20], to= Sys.Date(), color = "#E0E0E0") %>%
   dyLegend(show = "follow")   %>%

### 2019-11-14 awipev-CO2.Rmd
server text updated

@@
         - To restart shiny server: sudo systemctl restart shiny-server
-    - update shiny server: follow procedure detailed on the shiny web page
+        - update shiny server: follow procedure detailed on the shiny web page Data processing
 
@@
       - password:
-- Every hour a crontab action runs the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files added each day around 01:00 and cleans the data
-- Every night at 03:00 the web page is generated
-- Every night at 05:00 the files are copied to gattuso’s iMac
 
@@
 
-si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “- -delete” à la commande rsync # m h dom mon dow command 
-00 */1 * * * cd ; R - -vanilla < ny-alesund/R/ny-alesund_cc.R
-
-00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/awipev-co2_web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
-
+si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync # m h dom mon dow command
+
+- (At 01:00, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
+00 01 * * * cd ; R --vanilla < ny-alesund/R/ny-alesund_cc.R
+
+- (At 03:00, web page is generated)
+00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1
+
+- (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud/Exp168)
 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
 
+- (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)
 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
@@
 
- # On lance la fabrication du html cd web; R -e 'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html
+ # On lance la fabrication du html cd web; R -e 
+    'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html
 

### 2019-11-14 awipev-CO2.Rmd
server text updated

@@
 - (At 01:00, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
+
 00 01 * * * cd ; R --vanilla < ny-alesund/R/ny-alesund_cc.R
@@
 - (At 03:00, web page is generated)
+
 00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1
@@
 - (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud/Exp168)
+
 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
@@
 - (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)
+
 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'

### 2019-11-15 awipev-CO2.Rmd
update of server information

@@
 ```{r CRM measurements, echo=FALSE, warning=FALSE, message=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-calib_analyser <-  read.table(paste0(path, "fb_data/Calibration/TA_#1215/measure_CRM_TA.txt"), header = T, dec = ".", as.is = T, sep = ",", fill = TRUE)
+calib_analyser <-  read.table(paste0(path, "fb_data/Calibration_TA/TA_#1215/measure_CRM_TA.txt"), header = T, dec = ".", as.is = T, sep = ",", fill = TRUE)
 
@@
 - Serveur : awipev-co2 (193.50.85.104)
-- 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer).
+- 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer mais n'est plus utilisé).
 - Pour se connecter à awipev-co2.obs-vlfr.fr
@@
 
-- Every night at 01:00 (?) two data files ("all sensors" and AT) are sent by ftp to:
-      - awipev-co2.obs-vlfr.fr
-      - User name: nydata
-      - password:
+We use the AWI database XXXXX
 
@@
 
-<span style="color:red">**Warning:**</span> In the present HTML document double "-" appear with an espace between them (for display reasons).
-**Do not put the space when typing the code on a terminal wondow.**
-
-si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync # m h dom mon dow command
+si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync
+
+Pattern des commandes :
+# m h dom mon dow command
 
@@
 
-00 01 * * * cd ; R --vanilla < ny-alesund/R/ny-alesund_cc.R
+00 01 * * * cd ; R \-\-vanilla < ny-alesund/R/ny-alesund_cc.R
 
@@
 
-- (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud/Exp168)
+- (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud ... Exp168)
 
@@
 
-- La page web index.html est faite sur awipev@awipev-co2.obs-vlfr.fr
+- La page web index.html est faite sur le serveur awipev/web grâce au script awipev-CO2_web.Rmd puis transférée et renommée dans awipev/awipev-CO2_web
 - Création du répertoire web qui contient ce qu’il faut pour générer la page web:
     - AWIPEV-Logo.jpg
-    - Discrete_sampling_AWIPEV.csv
+    - Discrete_sampling_AWIPEV.csurv
     - awipev-CO2_web.Rmd
@@
 echo '---------fin awipev-co2.sh -----------'
+
+![ ](Images/awipev_server_arborescence.jpg){width=65%}
 

### 2019-11-18 awipev-CO2.Rmd
script updated with new path and data from NRT database

@@
 ```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
-# xx <- read_tsv("../fb_server/ny-alesund/data/old/All_sensors_731101_2016-08-20.txt", skip=16, col_names=TRUE)
-load(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/processed/nydata_hour.Rdata"))
+load(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.Rdata"))
 #load(file = paste0(path, "fb_server/shinyroot/AWIPEV-CO2/nydata_hour_shiny.Rdata"))
@@
   dplyr::select(-date) %>%
-  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT, NA), # beginning of data series for AT
-         AT = ifelse(AT == "NaN", NA, AT), #3 columns are character
-         pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
-         PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
+  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
+         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
+         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
+         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
          ) %>%
-  dplyr::rename(at_contros=AT, ph_at_contros=pH_AT, pco2_contros=PCO2_corr_contros_filtered, zero_contros=PCO2_Corr_Zero2, 
-         sal_fb=Salinity_filtered, temp_fb=Temperature_filtered, pH_durafet=HW_pH1_filtered, temp_insitu=Temp_SBE38_filtered)
+  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=Salinity_filtered,temp_fb=Temperature_filtered)
 ```
@@
   dplyr::select(closest_datetime, at, qflag_at) %>%
+    dplyr::filter(!is.na(closest_datetime)) %>%
   rename(datetime=closest_datetime)
@@
   dplyr::select(closest_datetime, ct, qflag_ct) %>%
+  dplyr::filter(!is.na(closest_datetime)) %>%
   rename(datetime=closest_datetime)
@@
   dplyr::select(closest_datetime, phcalc) %>%
+  dplyr::filter(!is.na(closest_datetime)) %>%
   rename(datetime=closest_datetime)
@@
   dplyr::select(closest_datetime, pH_s_seafet_temp_field) %>%
+  dplyr::filter(!is.na(closest_datetime)) %>%
   rename(datetime=closest_datetime)
@@
   dplyr::select(closest_datetime, pH_s_durafet_temp_field) %>%
+  dplyr::filter(!is.na(closest_datetime)) %>%
   rename(datetime=closest_datetime)
@@
   dplyr::select(closest_datetime, pco2calc) %>%
+  dplyr::filter(!is.na(closest_datetime)) %>%
   rename(datetime=closest_datetime)
@@
     dyLegend(show = "follow")   %>%
-    dyAxis("y",valueRange = c(30, 36)) %>%
+    dyAxis("y",valueRange = c(30, 37)) %>%
       dyRangeSelector(height = 30, dateWindow= NULL)
@@
       dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "T") %>%
-      dyAxis("y", valueRange = c(-2.5, 9.5)) %>%
+      dyAxis("y", valueRange = c(-2.5, 10)) %>%
       dyLegend(show = "follow")   %>%
@@
       dySeries("temp_insitu", color = "blue", strokeWidth = 0, label = "T") %>%
-      dyAxis("y", valueRange = c(-2.5, 9.5)) %>%
+      dyAxis("y", valueRange = c(-2.8, 10)) %>%
       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-  dyAxis("y",valueRange = c(2000, 2550)) %>%
+  dyAxis("y",valueRange = c(2000, 2650)) %>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
 f <- as.data.frame(table(d_all$at))
-sum(f$Freq)
+#sum(f$Freq)
 # Number of outliers removed in the dataset
@@
 ```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
-#Interpolation of continuous sensor data to match a maximum of reference data.
-TAinterp_all <-approx(d_all$datetime, d_all$AT_filtered, xout=d_all$datetime, method="linear", rule=2)
-names(TAinterp_all) <- c("datetime", "AT_filtered_interp")
-TAinterp_all <- as.data.frame(TAinterp_all)
-d_all$AT_filtered_interp <- TAinterp_all$AT_filtered_interp
-
-# create a column with difference between sensor and ref
-d_all <- d_all%>%
-  dplyr::mutate(diff_ta =  at-AT_filtered_interp )
-# create colum with instrument number
-d_all <- d_all %>% 
-  dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
-                            ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
-                            ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3", 
-                            ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4", 
-                            ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
-                            ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))
-
-#remove outliers
-calib_ta_first <- d_all%>%
-  dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta,TA_period)%>%
-  dplyr::filter(TA_period =="TA1" & !is.na(at))
-  #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
-# & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))
-
-# Parameters of regression
-fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime)
-at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6)
-at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2)
-at_intercept1 <- round(fit$coefficients[[1]], digits= 2)
-```
-
-The slope is: `r at_slope_TA1` x 3600 x 24 x 365.24 = `r at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red.
+# #Interpolation of continuous sensor data to match a maximum of reference data.
+# TAinterp_all <-approx(d_all$datetime, d_all$AT_filtered, xout=d_all$datetime, method="linear", rule=2)
+# names(TAinterp_all) <- c("datetime", "AT_filtered_interp")
+# TAinterp_all <- as.data.frame(TAinterp_all)
+# d_all$AT_filtered_interp <- TAinterp_all$AT_filtered_interp
+# 
+# # create a column with difference between sensor and ref
+# d_all <- d_all%>%
+#   dplyr::mutate(diff_ta =  at-AT_filtered_interp )
+# # create colum with instrument number
+# d_all <- d_all %>% 
+#   dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
+#                             ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
+#                             ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3", 
+#                             ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4", 
+#                             ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
+#                             ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))
+# 
+# #remove outliers
+# calib_ta_first <- d_all%>%
+#   dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta,TA_period)%>%
+#   dplyr::filter(TA_period =="TA1" & !is.na(at))
+#   #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
+# # & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))
+# 
+# # Parameters of regression
+# fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime)
+# at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6)
+# at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2)
+# at_intercept1 <- round(fit$coefficients[[1]], digits= 2)
+```
+
+<!--The slope is: `r at_slope_TA1` x 3600 x 24 x 365.24 = `r at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red.
+-->
 
 ```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
-# Plot of regression
-p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + 
-    geom_point() + geom_smooth(method='lm', se=FALSE)+ 
-    geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
-  geom_hline(yintercept = 0, linetype="dashed" )+
-  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                     "Intercept =",signif(fit$coef[[1]],5 ),
-                     "Slope =",signif(fit$coef[[2]], 5),
-                     "P =",signif(summary(fit)$coef[2,4], 5))) + 
-  ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
-print(p)
-ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
+# # Plot of regression
+# p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + 
+#     geom_point() + geom_smooth(method='lm', se=FALSE)+ 
+#     geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
+#   geom_hline(yintercept = 0, linetype="dashed" )+
+#   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+#                      "Intercept =",signif(fit$coef[[1]],5 ),
+#                      "Slope =",signif(fit$coef[[2]], 5),
+#                      "P =",signif(summary(fit)$coef[2,4], 5))) + 
+#   ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
+# print(p)
+# ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
 ```
@@
 
-#remove outliers and remove period without TA measurements 
-calib_ta_third <- d_all%>%
-  dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
-  dplyr::filter(TA_period == "TA3" & !is.na(at))
-
-# Parameters of regression
-fit <- lm( data=calib_ta_third, diff_ta ~ datetime)
-at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8)
-at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2)
-at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici.
-```
-
-The slope is in days: `r at_slope_TA3` x 3600 x 24 x 365.24 = `r at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.
+# #remove outliers and remove period without TA measurements 
+# calib_ta_third <- d_all%>%
+#   dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
+#   dplyr::filter(TA_period == "TA3" & !is.na(at))
+# 
+# # Parameters of regression
+# fit <- lm( data=calib_ta_third, diff_ta ~ datetime)
+# at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8)
+# at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2)
+# at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici.
+```
+
+<!--The slope is in days: `r at_slope_TA3` x 3600 x 24 x 365.24 = `r at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.
+-->
 
 ```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
-# Plot of regression
-p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
-    geom_point() + geom_smooth(method='lm', se=FALSE)+ 
-    #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
-   geom_hline(yintercept = 0, linetype="dashed" )+
-  geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
-  #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
-  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                     "Intercept =",signif(fit$coef[[1]],5 ),
-                     " Slope =",signif(fit$coef[[2]], 5),
-                     " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
-  scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
-print(p)
-ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
-```
+# # Plot of regression
+# p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
+#     geom_point() + geom_smooth(method='lm', se=FALSE)+ 
+#     #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
+#    geom_hline(yintercept = 0, linetype="dashed" )+
+#   geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
+#   #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
+#   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+#                      "Intercept =",signif(fit$coef[[1]],5 ),
+#                      " Slope =",signif(fit$coef[[2]], 5),
+#                      " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
+#   scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
+# print(p)
+# ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
+# ```
 
@@
 
-#remove outliers and remove period without TA measurements 
-calib_ta_second <- d_all%>%
-  dplyr::select(datetime, closest_datetime, AT_filtered, AT_filtered_interp, at, diff_ta, TA_period)%>%
-  dplyr::filter(TA_period == "TA2" & !is.na(at))
-
-mean_offset <- mean(calib_ta_second$diff_ta)
-
-```
-For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
+# #remove outliers and remove period without TA measurements 
+# calib_ta_second <- d_all%>%
+#   dplyr::select(datetime, closest_datetime, AT_filtered, AT_filtered_interp, at, diff_ta, TA_period)%>%
+#   dplyr::filter(TA_period == "TA2" & !is.na(at))
+# 
+# mean_offset <- mean(calib_ta_second$diff_ta)
+
+```
+<!--For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
+-->
 
@@
 ```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
-# Correction for the 3 periods is apply
-d_all <- d_all%>%
-  dplyr::mutate(datetime_reg = as.numeric(datetime), 
-                at_intercept = ifelse(TA_period == "TA1", at_intercept1, 
-                               ifelse(TA_period == "TA3", at_intercept3, NA)),
-                at_slope = ifelse(TA_period == "TA1", at_slope_TA1, 
-                           ifelse(TA_period == "TA3", at_slope_TA3, NA))
-                )
-
-d_all <- d_all%>%
- dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT_filtered + (d_all$datetime_reg * d_all$at_slope + at_intercept)),
-                                        ifelse(TA_period == "TA2", (AT_filtered + mean_offset),
-                                        ifelse(TA_period == "TA3", (AT_filtered + (datetime_reg * at_slope)+ at_intercept), NA))))
-
-at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at,TA_reg_corrected)
-at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
-dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
-   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
-  dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
-  dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
-  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
-  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
-  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
-  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
-  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-  dyAxis("y",valueRange = c(1600, 2650)) %>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions( strokeWidth= 0) %>%
-  dyLegend(show = "follow")   %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
+# # Correction for the 3 periods is apply
+# d_all <- d_all%>%
+#   dplyr::mutate(datetime_reg = as.numeric(datetime), 
+#                 at_intercept = ifelse(TA_period == "TA1", at_intercept1, 
+#                                ifelse(TA_period == "TA3", at_intercept3, NA)),
+#                 at_slope = ifelse(TA_period == "TA1", at_slope_TA1, 
+#                            ifelse(TA_period == "TA3", at_slope_TA3, NA))
+#                 )
+#                 
+# d_all <- d_all%>%
+#  dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT_filtered + (d_all$datetime_reg * d_all$at_slope + at_intercept)),
+#                                         ifelse(TA_period == "TA2", (AT_filtered + mean_offset),
+#                                         ifelse(TA_period == "TA3", (AT_filtered + (datetime_reg * at_slope)+ at_intercept), NA))))
+# 
+# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at,TA_reg_corrected)
+# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
+# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
+#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
+#   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
+#   dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
+#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
+#   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
+#   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
+#   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+#   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
+#   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+#   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+#   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+#   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+#   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
+#   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
+#   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
+#   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
+#   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
+#   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
+#   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
+#   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
+#   dyAxis("y",valueRange = c(1600, 2650)) %>%
+#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+#   dyOptions( strokeWidth= 0) %>%
+#   dyLegend(show = "follow")   %>%
+#   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
+#     dyRangeSelector(height = 30, dateWindow= NULL)
 
@@
 ```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
-d_all_at_discrete <- d_all %>% #  To remove an outlier in red 
-  dplyr::select(datetime, month,closest_datetime, at, sal_fb)%>%
-  dplyr::filter( !is.na(at) & !is.na(sal_fb) & sal_fb >30)
-
-  #at != "2307.05" & sal_fb > 28, !is.na(at))
-
-# d_all_Out <- d_all %>% #  To keep an outlier in red 
-#   filter(at == "2307.05")
-
-#fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal_fb)
-fit <- lm(data = d_all_at_discrete, at ~ sal_fb)
-slope_s_at <- fit$coefficients[[2]]
-intercept_s_at <- fit$coefficients[[1]]
-# at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()
-
-at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
-  geom_text( aes(color=factor(month))) +
-  scale_color_discrete(guide="none")+
-    labs(x="Salinity", y="Discrete AT", color = "Months")  +
-    stat_smooth(method = "lm", col = "black") +
-    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
-                       ";\nSlope =",signif(fit$coef[[2]], 5),
-                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
-  theme_bw() + 
-  theme(aspect.ratio=1,
-        axis.text=element_text(size=15),
-        axis.title.y= element_text(size =15),
-        axis.title.x= element_text(size =15),
-        plot.margin = unit(c(0.5,1,1,1), "cm"),
-        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70))) 
-  #print(at_s)
-
-ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")
-
-# Salinity is a predictor of AT -> using the regression defined above
-d_all$at_calc <- slope_s_at * d_all$sal_fb + intercept_s_at
-```
-The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r round(summary(fit)$r.squared, digits=2)`.
+# d_all_at_discrete <- d_all %>% #  To remove an outlier in red 
+#   dplyr::select(datetime, month,closest_datetime, at, sal_fb)%>%
+#   dplyr::filter( !is.na(at) & !is.na(sal_fb) & sal_fb >30)
+#   
+#   #at != "2307.05" & sal_fb > 28, !is.na(at))
+# 
+# # d_all_Out <- d_all %>% #  To keep an outlier in red 
+# #   filter(at == "2307.05")
+# 
+# #fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal_fb)
+# fit <- lm(data = d_all_at_discrete, at ~ sal_fb)
+# slope_s_at <- fit$coefficients[[2]]
+# intercept_s_at <- fit$coefficients[[1]]
+# # at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()
+#  
+# at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
+#   geom_text( aes(color=factor(month))) +
+#   scale_color_discrete(guide="none")+
+#     labs(x="Salinity", y="Discrete AT", color = "Months")  +
+#     stat_smooth(method = "lm", col = "black") +
+#     labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+#                        ";\nIntercept =",signif(fit$coef[[1]],5 ),
+#                        ";\nSlope =",signif(fit$coef[[2]], 5),
+#                        ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
+#   theme_bw() + 
+#   theme(aspect.ratio=1,
+#         axis.text=element_text(size=15),
+#         axis.title.y= element_text(size =15),
+#         axis.title.x= element_text(size =15),
+#         plot.margin = unit(c(0.5,1,1,1), "cm"),
+#         plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70))) 
+#   #print(at_s)
+# 
+# ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")
+# 
+# # Salinity is a predictor of AT -> using the regression defined above
+# d_all$at_calc <- slope_s_at * d_all$sal_fb + intercept_s_at
+```
+<!--The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r round(summary(fit)$r.squared, digits=2)`.
 Need to compare with other relationships from the literature.
-
+-->
 ```{r plot Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%", fig.align="center"}
-# PLOT
-print(at_s)
+# # PLOT
+# print(at_s)
 ```
@@
 ```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
-at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
-at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
-dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
-  dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
-  dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
-  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
-  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
-  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
-  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
-  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-  dyAxis("y",valueRange = c(2000, 2650)) %>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions( strokeWidth= 0) %>%
-  dyLegend(show = "follow")   %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-# #plot for POSTER june 2019
-# #plot of TA calculated from S + discrete
-# p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
-#   geom_point(col="blue", size=0.5 )+
-#   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
-#   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
-#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-#   theme(legend.position= c(0.5, 0.93),
-#                      legend.text=element_text(size=15),
-#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
-#                      axis.text=element_text(size=15),
-#                      axis.title.x= element_text(size =15),
-#                      legend.title=element_blank())
-# 
-# 
-# print(p_at_sal)
-# ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
+# at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
+# at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
+# dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
+#   dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
+#   dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
+#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
+#   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
+#   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
+#   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+#   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
+#   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+#   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+#   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+#   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+#   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
+#   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
+#   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
+#   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
+#   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
+#   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
+#   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
+#   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
+#   dyAxis("y",valueRange = c(2000, 2650)) %>%
+#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+#   dyOptions( strokeWidth= 0) %>%
+#   dyLegend(show = "follow")   %>%
+#   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
+#     dyRangeSelector(height = 30, dateWindow= NULL)
+# 
+# # #plot for POSTER june 2019
+# # #plot of TA calculated from S + discrete
+# # p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
+# #   geom_point(col="blue", size=0.5 )+
+# #   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
+# #   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
+# #   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
+# #   theme(legend.position= c(0.5, 0.93),
+# #                      legend.text=element_text(size=15),
+# #                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
+# #                      axis.text=element_text(size=15),
+# #                      axis.title.x= element_text(size =15),
+# #                      legend.title=element_blank())
+# # 
+# # 
+# # print(p_at_sal)
+# # ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
 
@@
 ```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
-# select subset of data and remove obvious outliers
-at_nov_2018 <- 
-  dplyr::select(d_all, datetime, at_calc, AT_filtered, at) %>%
-  filter(datetime > "2018-11-01", AT_filtered > 2250)
-#despike
-at_nov_2018 <- mutate(at_nov_2018, AT_filtered_despike = despike(AT_filtered, reference= "median", n=0.5, k=10, replace="NA"))
-#plot
-at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) +
-  geom_point(aes(y=AT_filtered, colour = "before"), size =3) +
-  geom_point(aes(y=AT_filtered_despike, colour = "after"), size = 2) +
-  labs(x = "Time", y = "Total alkalinity", color = "despike") 
-print(at_datetime)
-
-at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_filtered_despike != "NA")
-titre <- "Contros AT vs Calculated AT"
-fit <- lmodel2(data = at_nov_2018_no_NA, AT_filtered_despike ~ at_calc, nperm = 99)
-ggreg2(fit, x = "at_calc", y = "AT_filtered_despike")
+# # select subset of data and remove obvious outliers
+# at_nov_2018 <- 
+#   dplyr::select(d_all, datetime, at_calc, AT_filtered, at) %>%
+#   filter(datetime > "2018-11-01", AT_filtered > 2250)
+# #despike
+# at_nov_2018 <- mutate(at_nov_2018, AT_filtered_despike = despike(AT_filtered, reference= "median", n=0.5, k=10, replace="NA"))
+# #plot
+# at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) +
+#   geom_point(aes(y=AT_filtered, colour = "before"), size =3) +
+#   geom_point(aes(y=AT_filtered_despike, colour = "after"), size = 2) +
+#   labs(x = "Time", y = "Total alkalinity", color = "despike") 
+# print(at_datetime)
+# 
+# at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_filtered_despike != "NA")
+# titre <- "Contros AT vs Calculated AT"
+# fit <- lmodel2(data = at_nov_2018_no_NA, AT_filtered_despike ~ at_calc, nperm = 99)
+# ggreg2(fit, x = "at_calc", y = "AT_filtered_despike")
 
@@
 
-Pattern des commandes :
-# m h dom mon dow command
+Pattern des commandes : # m h dom mon dow command
 

### 2019-11-18 awipev-CO2.Rmd
script updated with new path and data from NRT database

@@
 dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
-    dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 2) %>%
     dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
+      dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
     dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
@@
     dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
+    dyEvent(as.POSIXct("2019-09-03 15:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
     #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
 <!--The slope is in days: `r at_slope_TA3` x 3600 x 24 x 365.24 = `r at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.
--->
 
@@
 # # Plot of regression
-# p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
-#     geom_point() + geom_smooth(method='lm', se=FALSE)+ 
-#     #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
-#    geom_hline(yintercept = 0, linetype="dashed" )+
-#   geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
-#   #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
-#   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-#                      "Intercept =",signif(fit$coef[[1]],5 ),
-#                      " Slope =",signif(fit$coef[[2]], 5),
-#                      " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
-#   scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
-# print(p)
-# ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
-# ```
+ p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
+     geom_point() + geom_smooth(method='lm', se=FALSE)+ 
+     #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
+    geom_hline(yintercept = 0, linetype="dashed" )+
+   geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
+   #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
+   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                      "Intercept =",signif(fit$coef[[1]],5 ),
+                      " Slope =",signif(fit$coef[[2]], 5),
+                      " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
+   scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
+ print(p)
+ ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
+```
 
@@
 ```
-<!--For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
+For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
 -->
-
+<!--
 #### **Final TA corrected data (Regression)**
@@
 ```
-<!--The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r round(summary(fit)$r.squared, digits=2)`.
+The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r round(summary(fit)$r.squared, digits=2)`.
 Need to compare with other relationships from the literature.
@@
 title <- "Contros vs calculated pCO2"
-fit <- lmodel2(data = d_all,  PCO2_corr_contros ~ pco2calc , nperm = 99)
-
-pco2calc_pCO2_contros_text <-  ggplot(d_all,aes(x=pco2calc, y= PCO2_corr_contros, label = month))+
+fit <- lmodel2(data = d_all,  pco2_contros ~ pco2calc , nperm = 99)
+
+pco2calc_pCO2_contros_text <-  ggplot(d_all,aes(x=pco2calc, y= pco2_contros, label = month))+
    geom_text(aes(color = factor(month)))+
   scale_color_discrete(guide="none")+
-  geom_line(aes(x = PCO2_corr_contros, y = PCO2_corr_contros), linetype = "dashed") +
+  geom_line(aes(x = pco2_contros, y = pco2_contros), linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
@@
 dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
-    dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 2) %>%
   dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
+    dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
     dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
@@
 ####
-seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf, 
-                        E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu, calSal = d_all$sal_fb_interp)
+seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu, calSal = d_all$sal_fb_interp)
 
@@
 # Offset between durafet pH and spec pH 
-duroffset <- left_join(durPeriod[,c(1,2)], d_all[,c(1,18)], by="datetime")
+duroffset <- left_join(durPeriod%>%dplyr::select(datetime,pH_s_durafet_temp_field), d_all%>%dplyr::select(datetime,pH_durafet ), by="datetime")
 dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_field - pH_durafet)
@@
   dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pHint_tot_sf)%>%
-  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu), !is.na(temp_fb)) %>%
+  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal_fb)) %>%
   dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
@@
   dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pH_durafet_corrected)%>%
-  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_insitu))
+  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal_fb))
 pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_insitu, Pinsi=11, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
@@
 # join pH calc norm + pH dur/sf norm in d_all
-d_all <- left_join(d_all, pH_calc[, c(1,6)], by="datetime")
+d_all <- left_join(d_all, pH_calc%>%dplyr::select(datetime,pH_calc_norm4), by="datetime")
 
@@
 ### **TA analyser**
+- **2019-11-15**: TA calibration done by Gwendall is OK but the sensore seems to have problem since 2019-10-16.
+Video conference is scheduled with Steffen on 2019-11-19.
+Maybe sample supply is defective.
 - **2019-07-12**: Steffen told us that calibration was not OK.
@@
 
+[AWI NRT database](https://dashboard.awi.de/data-xxl/overview.jsp)
+
 ###**FerryBox**
@@
 ### ***p*CO~2~**
+- **2019-11-18**: Calibration parameters from #0215-001 were added to "server.../data/NRT_data/Data_Processing_sheet_pCO2.csv" (new path).
 - **2018-08-29**: Calibration parameters from #0215-001 were added to "./data/Calibration_pCO2/Data_Processing_sheet_pCO2.csv".
@@
 ### **Files - server**
+- **2019-11-15**: Script including the new data downloading from the NRT AWI database is running (ny-alesund_cc.R).
+From this date, data are donwloaded from AWI NRT dtabase.
+We are waiting some setting from Philipp to have the entire dataset.
+Only 2018-2019 are available for the moment.
+New path was created in the server and pCloud/exp168 with "NRT_data" file.
+Please see the picture bellow.
 - **2018-04-19**: Since "Ferrybox" is on again, the adding to solve the files issues are making not data into d_hour for this period (2018-09-03 to 2018-14-04).

### 2019-11-20 awipev-CO2.Rmd

@@
 
-<!--The slope is: `r at_slope_TA1` x 3600 x 24 x 365.24 = `r at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red.
--->
-
-```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
+<!-- The slope is: `r #at_slope_TA1` x 3600 x 24 x 365.24 = `r #at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red. -->
+
+#```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
 # # Plot of regression
@@
 # ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
-```
+#```
 
@@
 
-```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"}
+#```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"}
 
@@
 # at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici.
-```
-
-<!--The slope is in days: `r at_slope_TA3` x 3600 x 24 x 365.24 = `r at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.
-
-```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
-# # Plot of regression
- p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
-     geom_point() + geom_smooth(method='lm', se=FALSE)+ 
-     #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
-    geom_hline(yintercept = 0, linetype="dashed" )+
-   geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
-   #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
-   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                      "Intercept =",signif(fit$coef[[1]],5 ),
-                      " Slope =",signif(fit$coef[[2]], 5),
-                      " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
-   scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
- print(p)
- ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
-```
+#```
+
+<!--The slope is in days: `r #at_slope_TA3` x 3600 x 24 x 365.24 = `r #at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.
+-->
+
+# ```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
+# # # Plot of regression
+#  p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
+#      geom_point() + geom_smooth(method='lm', se=FALSE)+ 
+#      #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
+#     geom_hline(yintercept = 0, linetype="dashed" )+
+#    geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
+#    #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
+#    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+#                       "Intercept =",signif(fit$coef[[1]],5 ),
+#                       " Slope =",signif(fit$coef[[2]], 5),
+#                       " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
+#    scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
+#  print(p)
+#  ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
+# ```
 
@@
 
-```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
+# ```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
 
@@
 
-```
-For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
+# ```
+
+<!--For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r #mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
 -->
-<!--
+
 #### **Final TA corrected data (Regression)**
 
-The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition.
+<!--The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition.
 It is clear that these corrected data (in green) cannot be used for periods 1 to 3. The jury is still out for period 4. The issue of salinity must be clarified before an assessment can be made. 
-
-```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
+-->
+
+#```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
 # # Correction for the 3 periods is apply
@@
 
-```
+#```
 
@@
 
-In the previous part, missing TA were interpolated with a linear model.
+<!--In the previous part, missing TA were interpolated with a linear model.
 This does not reflect the natural variability of TA.
 For this reason, missing TA is now calculated from salinity data by making a relationship between the same reference TA samples as in the previous part and salinity data.
+-->
 
 ```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
-# d_all_at_discrete <- d_all %>% #  To remove an outlier in red 
-#   dplyr::select(datetime, month,closest_datetime, at, sal_fb)%>%
-#   dplyr::filter( !is.na(at) & !is.na(sal_fb) & sal_fb >30)
-#   
-#   #at != "2307.05" & sal_fb > 28, !is.na(at))
-# 
-# # d_all_Out <- d_all %>% #  To keep an outlier in red 
-# #   filter(at == "2307.05")
-# 
-# #fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal_fb)
-# fit <- lm(data = d_all_at_discrete, at ~ sal_fb)
-# slope_s_at <- fit$coefficients[[2]]
-# intercept_s_at <- fit$coefficients[[1]]
-# # at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()
-#  
-# at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
-#   geom_text( aes(color=factor(month))) +
-#   scale_color_discrete(guide="none")+
-#     labs(x="Salinity", y="Discrete AT", color = "Months")  +
-#     stat_smooth(method = "lm", col = "black") +
-#     labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-#                        ";\nIntercept =",signif(fit$coef[[1]],5 ),
-#                        ";\nSlope =",signif(fit$coef[[2]], 5),
-#                        ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
-#   theme_bw() + 
-#   theme(aspect.ratio=1,
-#         axis.text=element_text(size=15),
-#         axis.title.y= element_text(size =15),
-#         axis.title.x= element_text(size =15),
-#         plot.margin = unit(c(0.5,1,1,1), "cm"),
-#         plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70))) 
-#   #print(at_s)
-# 
-# ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")
-# 
-# # Salinity is a predictor of AT -> using the regression defined above
-# d_all$at_calc <- slope_s_at * d_all$sal_fb + intercept_s_at
-```
-The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r round(summary(fit)$r.squared, digits=2)`.
+d_all_at_discrete <- d_all %>% #  To remove an outlier in red
+  dplyr::select(datetime, month,closest_datetime, at, sal_fb)%>%
+  dplyr::filter( !is.na(at) & !is.na(sal_fb) & sal_fb >30)
+
+  #at != "2307.05" & sal_fb > 28, !is.na(at))
+
+# d_all_Out <- d_all %>% #  To keep an outlier in red
+#   filter(at == "2307.05")
+
+#fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal_fb)
+fit <- lm(data = d_all_at_discrete, at ~ sal_fb)
+slope_s_at <- fit$coefficients[[2]]
+intercept_s_at <- fit$coefficients[[1]]
+# at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()
+
+at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
+  geom_text( aes(color=factor(month))) +
+  scale_color_discrete(guide="none")+
+    labs(x="Salinity", y="Discrete AT", color = "Months")  +
+    stat_smooth(method = "lm", col = "black") +
+    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
+                       ";\nSlope =",signif(fit$coef[[2]], 5),
+                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
+  theme_bw() +
+  theme(aspect.ratio=1,
+        axis.text=element_text(size=15),
+        axis.title.y= element_text(size =15),
+        axis.title.x= element_text(size =15),
+        plot.margin = unit(c(0.5,1,1,1), "cm"),
+        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70)))
+  #print(at_s)
+
+ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")
+
+# Salinity is a predictor of AT -> using the regression defined above
+d_all$at_calc <- slope_s_at * d_all$sal_fb + intercept_s_at
+```
+
+<!--
+The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r #round(summary(fit)$r.squared, digits=2)`.
 Need to compare with other relationships from the literature.
 -->
+
 ```{r plot Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%", fig.align="center"}
-# # PLOT
-# print(at_s)
+ # PLOT
+ print(at_s)
 ```
@@
 #### **Final TA re-calculated data (Salinity relationship)**
+
 ```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
-# at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
-# at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
-# dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
-#   dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
-#   dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
-#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
-#   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
-#   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
-#   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-#   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
-#   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-#   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-#   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-#   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-#   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
-#   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-#   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
-#   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
-#   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-#   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-#   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
-#   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-#   dyAxis("y",valueRange = c(2000, 2650)) %>%
-#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#   dyOptions( strokeWidth= 0) %>%
-#   dyLegend(show = "follow")   %>%
-#   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-#     dyRangeSelector(height = 30, dateWindow= NULL)
+at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
+at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
+dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
+  dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
+  dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
+  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
+  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
+  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
+  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
+  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
+  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
+  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
+  dyAxis("y",valueRange = c(2000, 2650)) %>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions( strokeWidth= 0) %>%
+  dyLegend(show = "follow")   %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
+    dyRangeSelector(height = 30, dateWindow= NULL)
+
+# #plot for POSTER june 2019
+# #plot of TA calculated from S + discrete
+# p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
+#   geom_point(col="blue", size=0.5 )+
+#   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
+#   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
+#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
+#   theme(legend.position= c(0.5, 0.93),
+#                      legend.text=element_text(size=15),
+#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
+#                      axis.text=element_text(size=15),
+#                      axis.title.x= element_text(size =15),
+#                      legend.title=element_blank())
 #
-# # #plot for POSTER june 2019
-# # #plot of TA calculated from S + discrete
-# # p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
-# #   geom_point(col="blue", size=0.5 )+
-# #   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
-# #   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
-# #   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-# #   theme(legend.position= c(0.5, 0.93),
-# #                      legend.text=element_text(size=15),
-# #                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
-# #                      axis.text=element_text(size=15),
-# #                      axis.title.x= element_text(size =15),
-# #                      legend.title=element_blank())
-# # 
-# # 
-# # print(p_at_sal)
-# # ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
+#
+# print(p_at_sal)
+# ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
 
@@
 ```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
-# # select subset of data and remove obvious outliers
-# at_nov_2018 <- 
-#   dplyr::select(d_all, datetime, at_calc, AT_filtered, at) %>%
-#   filter(datetime > "2018-11-01", AT_filtered > 2250)
-# #despike
-# at_nov_2018 <- mutate(at_nov_2018, AT_filtered_despike = despike(AT_filtered, reference= "median", n=0.5, k=10, replace="NA"))
-# #plot
-# at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) +
-#   geom_point(aes(y=AT_filtered, colour = "before"), size =3) +
-#   geom_point(aes(y=AT_filtered_despike, colour = "after"), size = 2) +
-#   labs(x = "Time", y = "Total alkalinity", color = "despike") 
-# print(at_datetime)
-# 
-# at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_filtered_despike != "NA")
-# titre <- "Contros AT vs Calculated AT"
-# fit <- lmodel2(data = at_nov_2018_no_NA, AT_filtered_despike ~ at_calc, nperm = 99)
-# ggreg2(fit, x = "at_calc", y = "AT_filtered_despike")
+ # select subset of data and remove obvious outliers
+ at_nov_2018 <-
+  dplyr::select(d_all, datetime, at_calc, AT_filtered, at) %>%
+  filter(datetime > "2018-11-01", AT_filtered > 2250)
+#despike
+at_nov_2018 <- mutate(at_nov_2018, AT_filtered_despike = despike(AT_filtered, reference= "median", n=0.5, k=10, replace="NA"))
+#plot
+at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) +
+  geom_point(aes(y=AT_filtered, colour = "before"), size =3) +
+  geom_point(aes(y=AT_filtered_despike, colour = "after"), size = 2) +
+  labs(x = "Time", y = "Total alkalinity", color = "despike")
+print(at_datetime)
+
+at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_filtered_despike != "NA")
+titre <- "Contros AT vs Calculated AT"
+fit <- lmodel2(data = at_nov_2018_no_NA, AT_filtered_despike ~ at_calc, nperm = 99)
+ggreg2(fit, x = "at_calc", y = "AT_filtered_despike")
 
@@
   dplyr::select(datetime, sal,temp, phcalc, at)%>%
-  dplyr::filter(!is.na(phcalc), !is.na(temp))
+  dplyr::filter(!is.na(phcalc), !is.na(temp), !is.na(sal))
 pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
@@
 # DURAFET vs CALC
-fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pH_durafet_norm4 , nperm = 99)
-
-pdur_calc_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pH_calc_norm4, label = month))+
-  geom_text( aes(color=factor(month))) + 
-  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("pH calculated vs pH durafet, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-   coord_fixed(ratio = 1 , xlim=c(8,8.22), ylim=c(8,8.22)) + 
-  scale_color_discrete(guide="none")+
-  labs(x="pH durafet, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
-pdur_calc_norm_text
+# fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pH_durafet_norm4 , nperm = 99)
+# 
+# pdur_calc_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pH_calc_norm4, label = month))+
+#   geom_text( aes(color=factor(month))) + 
+#   geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
+#   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+#   labs(title = paste("pH calculated vs pH durafet, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
+#                      "; Intercept =", signif(fit$regression.results[2,2], 3),
+#                      "; Slope =", signif( fit$regression.results[2,3], 3),
+#                      "; P =", signif(fit$P.param, 3))) +
+#   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+#    coord_fixed(ratio = 1 , xlim=c(8,8.22), ylim=c(8,8.22)) + 
+#   scale_color_discrete(guide="none")+
+#   labs(x="pH durafet, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
+# pdur_calc_norm_text
 

### 2019-11-20 TA_filter_despike.R
script updated and tests done

@@ -1,0 +1,58 @@
+# Script to experiment despike() on TA data because of spike for acid wash around midnight
+
+if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_AWIPEV-CO2/fb_awipev-co2_server/"
+
+load(file = paste0(path,"ny-alesund/data/NRT_data/all_nydata_hour.Rdata"))
+d_hour <- d_hour %>%
+  dplyr::select(datetime, AT_filtered)
+
+# despike
+d_hour <- d_hour %>%
+  dplyr::mutate(AT_filtered2= despike(d_hour$AT_filtered, reference= "median", n=0.3, k=217, replace="NA"))%>%
+#dplyr::mutate(AT_filtered2= despike(d_hour$AT_filtered, reference= "median", n=0.3, k=217, replace="NA"))
+dplyr::mutate(AT_filtered3= despike(d_hour$AT_filtered2, reference= "median", n=0.3, k=217, replace="NA"))
+
+# plot
+at_fb_xts <- dplyr::select(d_hour, datetime,AT_filtered,AT_filtered2,AT_filtered3)
+at_fb_xts <- as.xts(at_fb_xts, order.by = at_fb_xts$datetime)
+dygraph(at_fb_xts, ylab="at") %>%
+  dySeries("AT_filtered", color = "blue", strokeWidth = 0, label = "raw") %>%
+  dySeries("AT_filtered2", color = "red", strokeWidth = 0, label = "filt") %>%
+  dySeries("AT_filtered3", color = "green", strokeWidth = 0, label = "filt3") %>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.2,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+  dyRangeSelector(height = 30)
+
+tmp <- NULL
+df <- expand.grid(n = seq(0.1, 1, by = 0.1), k =as.integer(seq(25, 221, by = 4)))
+df$N <- NULL
+for (i in 1:nrow(df)) {
+  tmp <- despike(d_hour$AT_filtered, reference= "median", n=df$n[i], k=df$k[i], replace="NA")
+  df$N[i] <- length(tmp[!is.na(tmp)])
+  df$V[i] <- sd(tmp, na.rm = TRUE)
+  }
+summary(df)
[…]

### 2019-11-20 TA_filter_despike.Rmd
script updated and tests done

---
title: "TA_filter_despike"
author: "samir"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::html_document:
    theme: paper
    number_sections: false

---

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
Sys.setlocale("LC_ALL", "en_US.UTF-8")
Sys.setenv(TZ='UTC') # on utilise UTC
rm(list = ls())
library(tidyverse)
library(robfilter)
library(seacarb)
library(gridExtra)
library(reshape2)
library(lubridate)
library(lmtest)
library(grid)
library(viridis)
library(dygraphs)
require("knitr")
library("lmodel2")
library(captioner)
library(xts)
library(seismicRoll)
library(scales)

if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"
```

## Introduction

In this document, we try to deal with "cleaning TA dataset" because of high variability.
Variability of the dataset is partly due to the measurement of the seawater + acid during washing periode (noon and midnight).
We only deal with 2018-2019 TA data.

```{r prepare data, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
load(file = paste0(path,"ny-alesund/data/NRT_data/all_nydata_hour.Rdata"))
d_hour <- d_hour %>%
  dplyr::select(datetime, AT_filtered)

```

## Dataset

Here the TA dataset already cleaned by despike() at the end of the ny-alesund_cc.R script. If we zoom in November 2019 we can see the drop in data around midnight each day, due to acid washing cycle.

```{r plot data, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

# plot
at_fb_xts <- dplyr::select(d_hour, datetime,AT_filtered)
at_fb_xts <- as.xts(at_fb_xts, order.by = at_fb_xts$datetime)
dygraph(at_fb_xts, ylab="at") %>%
  dySeries("AT_filtered", color = "blue", strokeWidth = 0, label = "raw") %>%
  #dySeries("AT_filtered2", color = "red", strokeWidth = 0, label = "filt") %>%
  #dySeries("AT_filtered3", color = "green", strokeWidth = 0, label = "filt3") %>%
  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.2,hideOnMouseOut = TRUE) %>%
  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
  dyRangeSelector(height = 30)

```

## Despike() parameters setting
The idea was to find best parameters (n and k) in despike() in order to keep largest data (N = number of points) with a smallest standard deviation (V).

  - Create a dataframe with all posibilities for parameters n and k comprised between 0.1 - 1 for n and 25 - 221 for k.
```{r despike parameters, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}

tmp <- NULL
#create a dataframe with all posibilities for parameters n and k comprised between 0.1 - 1 for n and 25 - 221 for k.
df <- expand.grid(n = seq(0.1, 1, length.out =0.1 ), k =as.integer(seq(25, 221, by = 4)))
df$N <- NULL
for (i in 1:
     nrow(df)) {
  tmp <- despike(d_hour$AT_filtered, reference= "median", n=df$n[i], k=df$k[i], replace="NA")
  df$N[i] <- length(tmp[!is.na(tmp)])
  df$V[i] <- sd(tmp, na.rm = TRUE)
  }
summary(df)
#We want to keep data with highest N AND smallest Variance
df$percentN <- (df$N/max(df$N))*100
acceptable <- df%>%
  mutate(N = ifelse(percentN > 70 & V <80, N, NA),
         k = ifelse(percentN > 70 & V <80, k, NA))%>%
  filter(!is.na(k))

ggplot(data=df, aes(x = k, y = n)) +
  geom_point(aes(colour = N))

ggplot(data=df, aes(x = k, y = n)) +
  geom_point(aes(colour = V)) 
  ```

### 2019-11-25 TA_filter_despike.Rmd

@@
 ---
-title: "TA_filter_despike"
+title: "TA data filtration: despike()"
 author: "samir"
@@
 ---
+<style type="text/css">
 
+body{ /* Normal  */
+      font-size: 18px;
+
+}
+</style>
 ```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
@@
 library(scales)
+library(knitr)
 
@@
 ```{r prepare data, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
-load(file = paste0(path,"ny-alesund/data/NRT_data/all_nydata_hour.Rdata"))
+load(file = paste0(path,"fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.Rdata"))
 d_hour <- d_hour %>%
@@
 
-```{r plot data, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
+```{r plot data, echo=FALSE, warning=FALSE, message=FALSE}
 
@@
   dyRangeSelector(height = 30)
-
 ```
 
-## Despike() parameters setting
+## Despike() parameters settings
 The idea was to find best parameters (n and k) in despike() in order to keep largest data (N = number of points) with a smallest standard deviation (V).
@@
   - Create a dataframe with all posibilities for parameters n and k comprised between 0.1 - 1 for n and 25 - 221 for k.
-```{r despike parameters, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
+
+  Final dataframe is created, compiling best n and K parameters: lowest standard deviation (V) and highest number of point (N).
+
+Number of point > 80% and sd < 80 were choosen here.
+
+## Despike() parameters results
+
+```{r despike parameters, echo=FALSE, warning=FALSE, message=FALSE}
 
@@
 df$N <- NULL
+# create a tmp vector with different n, k parameters when i is different. i corresponds to the different lines of df and thus has different combinaisons of n,k.
 for (i in 1:
@@
   tmp <- despike(d_hour$AT_filtered, reference= "median", n=df$n[i], k=df$k[i], replace="NA")
+  #create a new N column with the number of data. 
   df$N[i] <- length(tmp[!is.na(tmp)])
+  #create a new V column with the standard deviation of each despike measurement.
   df$V[i] <- sd(tmp, na.rm = TRUE)
@@
 summary(df)
-#We want to keep data with highest N AND smallest Variance
+
+#We want to keep data with highest N and smallest V
+# We transform N in percentage for easy understanding.
 df$percentN <- (df$N/max(df$N))*100
+
+#final dataframe is created with bes despike() parameters for our arbitrary choice
 acceptable <- df%>%
@@
   filter(!is.na(k))
+kable(acceptable)
 
@@
 ```
+
+Best n and k were found for 0.2 > n < 0.3 and 109 >= K <= 221
+```{r final plot, echo=FALSE, warning=FALSE, message=FALSE}
+# final plot
+at_fb_xts <- dplyr::select(d_hour, datetime,AT_filtered)
+at_fb_xts <- as.xts(at_fb_xts, order.by = at_fb_xts$datetime)
+dygraph(at_fb_xts, ylab="at") %>%
+  dySeries("AT_filtered", color = "blue", strokeWidth = 0, label = "raw") %>%
+  #dySeries("AT_filtered2", color = "red", strokeWidth = 0, label = "filt") %>%
+  #dySeries("AT_filtered3", color = "green", strokeWidth = 0, label = "filt3") %>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.2,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+  dyRangeSelector(height = 30)
+```

### 2019-11-25 awipev-CO2.Rmd

@@
                    )
-
+#at_ct_mean <- at_ct_mean%>%filter(!is.na(at_mean))
+#write.table(file= paste0(path, "fb_data/at_ct_mean.txt"), at_ct_mean)
 d <- left_join(d, at_ct_mean, by='datetime')

### 2019-11-26 TA_filter_despike.Rmd
script update with final results for TA_filter_despike

@@
 
-Here the TA dataset already cleaned by despike() at the end of the ny-alesund_cc.R script. If we zoom in November 2019 we can see the drop in data around midnight each day, due to acid washing cycle.
+TA dataset (blue) already cleaned by despike() with n = 0.5 and k = 121, at the end of the ny-alesund_cc.R script.
+If we zoom in November 2019 we can see lot of drops in data around midnight each day, due to acid washing cycle.
 
@@
 ## Despike() parameters settings
-The idea was to find best parameters (n and k) in despike() in order to keep largest data (N = number of points) with a smallest standard deviation (V).
+The idea was to find better parameters (n and k) in despike() in order to keep largest data (N = number of points) with a smallest standard deviation (V).
 
-  - Create a dataframe with all posibilities for parameters n and k comprised between 0.1 - 1 for n and 25 - 221 for k.
+  - Create a dataframe with all posibilities for parameters n and k comprised between 0.1 - 1 for n and between 25 - 221 for k.
 
@@
 
-Number of point > 80% and sd < 80 were choosen here.
-
 ## Despike() parameters results
 
+Summary of dataframe with all posibilities + N and V plots:
+
 ```{r despike parameters, echo=FALSE, warning=FALSE, message=FALSE}
-
 tmp <- NULL
 #create a dataframe with all posibilities for parameters n and k comprised between 0.1 - 1 for n and 25 - 221 for k.
-df <- expand.grid(n = seq(0.1, 1, length.out =0.1 ), k =as.integer(seq(25, 221, by = 4)))
+df <- expand.grid(n = seq(0.1, 1, by =0.1 ), k =as.integer(seq(25, 221, by = 4)))
 df$N <- NULL
@@
 
+ggplot(data=df, aes(x = k, y = n)) +
+  geom_point(aes(colour = N))
+
+ggplot(data=df, aes(x = k, y = n)) +
+  geom_point(aes(colour = V)) 
+```
+
+Here, best dataframe compiling best n and k resulting of Number of point (N) > 80% and sd (V) < 80:
+- 0.2 > n < 0.3 
+- 109 > k < 221
+
+```{r best despike parameters, echo=FALSE, warning=FALSE, message=FALSE}
 #We want to keep data with highest N and smallest V
@@
 
-ggplot(data=df, aes(x = k, y = n)) +
-  geom_point(aes(colour = N))
-
-ggplot(data=df, aes(x = k, y = n)) +
-  geom_point(aes(colour = V)) 
+# despike
+d_hour <- d_hour %>%
+  dplyr::mutate(AT_filtered2= despike(d_hour$AT_filtered, reference= "median", n=0.3, k=217, replace="NA"))
+d_hour <- d_hour %>%
+  dplyr::mutate(AT_filtered3= despike(d_hour$AT_filtered2, reference= "median", n=0.3, k=217, replace="NA"))
+#dplyr::mutate(AT_filtered2= despike(d_hour$AT_filtered, reference= "median", n=0.3, k=217, replace="NA"))
 ```
 
-Best n and k were found for 0.2 > n < 0.3 and 109 >= K <= 221
+In the following plot, n = 0.3 and k = 217 were kept as 2nd time despike() parameters (red dots). A third despike() run (green dots) was discarded because of the large lack of data.
+
 ```{r final plot, echo=FALSE, warning=FALSE, message=FALSE}
 # final plot
-at_fb_xts <- dplyr::select(d_hour, datetime,AT_filtered)
+at_fb_xts <- dplyr::select(d_hour, datetime,AT_filtered,AT_filtered2, AT_filtered3)
 at_fb_xts <- as.xts(at_fb_xts, order.by = at_fb_xts$datetime)
@@
   dySeries("AT_filtered", color = "blue", strokeWidth = 0, label = "raw") %>%
-  #dySeries("AT_filtered2", color = "red", strokeWidth = 0, label = "filt") %>%
-  #dySeries("AT_filtered3", color = "green", strokeWidth = 0, label = "filt3") %>%
+  dySeries("AT_filtered2", color = "red", strokeWidth = 0, label = "filt") %>%
+  dySeries("AT_filtered3", color = "green", strokeWidth = 0, label = "filt3") %>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.2,hideOnMouseOut = TRUE) %>%

### 2019-11-26 awipev-CO2.Rmd
script update text

@@
 
-###**FerryBox**
+[Missing data to add to the NRT database](https://docs.google.com/spreadsheets/d/1Cbc4hWyclnBsNsOH_3QDA3AGZfwF4I1HuadfBe1BVjI/edit?usp=sharing)
+
+[Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736)
+
+### **FerryBox**
 - **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.

### 2020-01-17 awipev-CO2.Rmd
some script updates in discrete ATCT part

@@
 d <- read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
-d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
+#d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
+d$datetime <- dmy_hm(d$sampling_date, tz="UTC")
 d$measure_date <- dmy(d$measure_date, tz="UTC")
@@
 d <- d%>%
-  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00", 1,0)
+  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00"|datetime == "2019-05-31 11:45:00", 1,0)
   )

### 2020-01-18 awipev-CO2.Rmd

@@
   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
+  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
-  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
@@
 ```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
-# #Interpolation of continuous sensor data to match a maximum of reference data.
-# TAinterp_all <-approx(d_all$datetime, d_all$AT_filtered, xout=d_all$datetime, method="linear", rule=2)
-# names(TAinterp_all) <- c("datetime", "AT_filtered_interp")
-# TAinterp_all <- as.data.frame(TAinterp_all)
-# d_all$AT_filtered_interp <- TAinterp_all$AT_filtered_interp
-# 
-# # create a column with difference between sensor and ref
-# d_all <- d_all%>%
-#   dplyr::mutate(diff_ta =  at-AT_filtered_interp )
-# # create colum with instrument number
-# d_all <- d_all %>% 
-#   dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
-#                             ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
-#                             ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3", 
-#                             ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4", 
-#                             ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
-#                             ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))
-# 
-# #remove outliers
-# calib_ta_first <- d_all%>%
-#   dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta,TA_period)%>%
-#   dplyr::filter(TA_period =="TA1" & !is.na(at))
-#   #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
-# # & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))
-# 
-# # Parameters of regression
-# fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime)
-# at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6)
-# at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2)
-# at_intercept1 <- round(fit$coefficients[[1]], digits= 2)
-```
-
-<!-- The slope is: `r #at_slope_TA1` x 3600 x 24 x 365.24 = `r #at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red. -->
-
-#```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
+#Interpolation of continuous sensor data to match a maximum of reference data.
+TAinterp_all <-approx(d_all$datetime, d_all$AT_filtered, xout=d_all$datetime, method="linear", rule=2)
+names(TAinterp_all) <- c("datetime", "AT_filtered_interp")
+TAinterp_all <- as.data.frame(TAinterp_all)
+d_all$AT_filtered_interp <- TAinterp_all$AT_filtered_interp
+
+# create a column with difference between sensor and ref
+d_all <- d_all%>%
+  dplyr::mutate(diff_ta =  at-AT_filtered_interp )
+# create colum with instrument number
+d_all <- d_all %>%
+  dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
+                            ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
+                            ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3",
+                            ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4",
+                            ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
+                            ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))
+
+#remove outliers
+calib_ta_first <- d_all%>%
+  dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta,TA_period)%>%
+  dplyr::filter(TA_period =="TA1" & !is.na(at))
+  #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
+# & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))
+
+# Parameters of regression
+fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime)
+at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6)
+at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2)
+at_intercept1 <- round(fit$coefficients[[1]], digits= 2)
+```
+
+The slope is: `r #at_slope_TA1` x 3600 x 24 x 365.24 = `r #at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red.
+
+```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
+ # Plot of regression
+ p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) +
+     geom_point() + geom_smooth(method='lm', se=FALSE)+
+     geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
+   geom_hline(yintercept = 0, linetype="dashed" )+
+   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                      "Intercept =",signif(fit$coef[[1]],5 ),
+                      "Slope =",signif(fit$coef[[2]], 5),
+                      "P =",signif(summary(fit)$coef[2,4], 5))) +
+   ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
+ print(p)
+ ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
+```
+
+##### **Third period**
+
+```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"}
+
+ #remove outliers and remove period without TA measurements
+ calib_ta_third <- d_all%>%
+   dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
+   dplyr::filter(TA_period == "TA3" & !is.na(at))
+
+ # Parameters of regression
+ fit <- lm( data=calib_ta_third, diff_ta ~ datetime)
+ at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8)
+ at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2)
+ at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici.
+```
+
+The slope is in days: `r #at_slope_TA3` x 3600 x 24 x 365.24 = `r #at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.
+
+```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
 # # Plot of regression
-# p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + 
-#     geom_point() + geom_smooth(method='lm', se=FALSE)+ 
-#     geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
-#   geom_hline(yintercept = 0, linetype="dashed" )+
-#   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-#                      "Intercept =",signif(fit$coef[[1]],5 ),
-#                      "Slope =",signif(fit$coef[[2]], 5),
-#                      "P =",signif(summary(fit)$coef[2,4], 5))) + 
-#   ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
-# print(p)
-# ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
-#```
-
-##### **Third period**
-
-#```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"}
-
-# #remove outliers and remove period without TA measurements 
-# calib_ta_third <- d_all%>%
-#   dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
-#   dplyr::filter(TA_period == "TA3" & !is.na(at))
-# 
-# # Parameters of regression
-# fit <- lm( data=calib_ta_third, diff_ta ~ datetime)
-# at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8)
-# at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2)
-# at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici.
-#```
-
-<!--The slope is in days: `r #at_slope_TA3` x 3600 x 24 x 365.24 = `r #at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.
--->
-
-# ```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
-# # # Plot of regression
-#  p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ 
-#      geom_point() + geom_smooth(method='lm', se=FALSE)+ 
-#      #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
-#     geom_hline(yintercept = 0, linetype="dashed" )+
-#    geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
-#    #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
-#    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-#                       "Intercept =",signif(fit$coef[[1]],5 ),
-#                       " Slope =",signif(fit$coef[[2]], 5),
-#                       " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + 
-#    scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
-#  print(p)
-#  ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
-# ```
+ p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+
+     geom_point() + geom_smooth(method='lm', se=FALSE)+
+     #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
+    geom_hline(yintercept = 0, linetype="dashed" )+
+   geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
+   #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
+   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                      "Intercept =",signif(fit$coef[[1]],5 ),
+                      " Slope =",signif(fit$coef[[2]], 5),
+                      " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") +
+   scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
+ print(p)
+ ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
+```
 
@@
 
-# ```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
-
-# #remove outliers and remove period without TA measurements 
-# calib_ta_second <- d_all%>%
-#   dplyr::select(datetime, closest_datetime, AT_filtered, AT_filtered_interp, at, diff_ta, TA_period)%>%
-#   dplyr::filter(TA_period == "TA2" & !is.na(at))
-# 
-# mean_offset <- mean(calib_ta_second$diff_ta)
-
-# ```
-
-<!--For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r #mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
--->
+```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
+
+#remove outliers and remove period without TA measurements
+calib_ta_second <- d_all%>%
+  dplyr::select(datetime, closest_datetime, AT_filtered, AT_filtered_interp, at, diff_ta, TA_period)%>%
+  dplyr::filter(TA_period == "TA2" & !is.na(at))
+
+mean_offset <- mean(calib_ta_second$diff_ta)
+
+```
+
+For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r #mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
 
@@
 
-<!--The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition.
+The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition.
 It is clear that these corrected data (in green) cannot be used for periods 1 to 3. The jury is still out for period 4. The issue of salinity must be clarified before an assessment can be made.
--->
-
-#```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
-# # Correction for the 3 periods is apply
-# d_all <- d_all%>%
-#   dplyr::mutate(datetime_reg = as.numeric(datetime), 
-#                 at_intercept = ifelse(TA_period == "TA1", at_intercept1, 
-#                                ifelse(TA_period == "TA3", at_intercept3, NA)),
-#                 at_slope = ifelse(TA_period == "TA1", at_slope_TA1, 
-#                            ifelse(TA_period == "TA3", at_slope_TA3, NA))
-#                 )
-#                 
-# d_all <- d_all%>%
-#  dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT_filtered + (d_all$datetime_reg * d_all$at_slope + at_intercept)),
-#                                         ifelse(TA_period == "TA2", (AT_filtered + mean_offset),
-#                                         ifelse(TA_period == "TA3", (AT_filtered + (datetime_reg * at_slope)+ at_intercept), NA))))
-# 
-# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at,TA_reg_corrected)
-# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
-# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
-#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
-#   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
-#   dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
-#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
-#   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
-#   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
-#   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-#   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
-#   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-#   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-#   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-#   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-#   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
-#   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-#   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
-#   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
-#   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-#   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-#   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
-#   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-#   dyAxis("y",valueRange = c(1600, 2650)) %>%
-#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#   dyOptions( strokeWidth= 0) %>%
-#   dyLegend(show = "follow")   %>%
-#   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-#     dyRangeSelector(height = 30, dateWindow= NULL)
-
-#```
+
+```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
+# Correction for the 3 periods is apply
+d_all <- d_all%>%
+  dplyr::mutate(datetime_reg = as.numeric(datetime),
+                at_intercept = ifelse(TA_period == "TA1", at_intercept1,
+                               ifelse(TA_period == "TA3", at_intercept3, NA)),
+                at_slope = ifelse(TA_period == "TA1", at_slope_TA1,
+                           ifelse(TA_period == "TA3", at_slope_TA3, NA))
+                )
+
+d_all <- d_all%>%
+ dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT_filtered + (d_all$datetime_reg * d_all$at_slope + at_intercept)),
+                                        ifelse(TA_period == "TA2", (AT_filtered + mean_offset),
+                                        ifelse(TA_period == "TA3", (AT_filtered + (datetime_reg * at_slope)+ at_intercept), NA))))
+
+at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at,TA_reg_corrected)
+at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
+dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
+   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
+  dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
+  dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
+  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
+  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
+  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
+  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
+  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
+  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
+  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
+  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
+  dyAxis("y",valueRange = c(1600, 2650)) %>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions( strokeWidth= 0) %>%
+  dyLegend(show = "follow")   %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
+    dyRangeSelector(height = 30, dateWindow= NULL)
+
+```
 
@@
 
-<!--In the previous part, missing TA were interpolated with a linear model.
+In the previous part, missing TA were interpolated with a linear model.
 This does not reflect the natural variability of TA.
 For this reason, missing TA is now calculated from salinity data by making a relationship between the same reference TA samples as in the previous part and salinity data.
--->
 
@@
 
-<!--
 The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r #round(summary(fit)$r.squared, digits=2)`.
 Need to compare with other relationships from the literature.
--->
 
@@
   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
+    coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
   labs(x="pH durafet", y="pH spectro, 4°C ", color = "Months") + theme_bw() 

### 2020-01-20 awipev-CO2.Rmd
update SNAPO graph

@@
    dplyr::select(datetime, at, ct)%>%   
-   dplyr::mutate(at_diff = at - lag(at),
-                 ct_diff = ct - lag(ct))
+   dplyr::mutate(at_diff = abs(at - lag(at)),
+                 ct_diff = abs(ct - lag(ct)))
 
@@
     geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
-    geom_hline(yintercept= -4, size= 0.6, col="red", linetype="dashed") +
     annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
@@
     geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
-    geom_hline(yintercept= -4, size= 0.6, col="red", linetype="dashed") +
 annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
@@
 snapcoevents <- c("2015-07-23 00:00:00", "2015-11-18 00:00:00", "2015-11-27 00:00:00", "2016-10-13 00:00:00", 
-              "2017-05-11 00:00:00", "2018-02-09 00:00:00", "2018-02-16 00:00:00", "2018-07-27 00:00:00", "2018-08-03 00:00:00", "2018-11-23 00:00:00", "2018-11-30 00:00:00", "2019-04-12 00:00:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
+              "2017-05-11 00:00:00", "2018-02-09 00:00:00", "2018-02-16 00:00:00", "2018-07-27 00:00:00", "2018-08-03 00:00:00", "2018-11-23 00:00:00", "2018-11-30 00:00:00", "2019-04-12 00:00:00","2019-08-31 23:59:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
 

### 2020-01-20 awipev-CO2.Rmd
update SNAPO graph2

@@
   dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C2C2") %>%
-  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5,valueRange = c(-25, 30)) %>%
+  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
     dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%

### 2020-01-24 awipev-CO2.Rmd
MAintenance updated with frozen samples details

@@
 ### **FerryBox**
+- **2020-01-24**: heater issues in the contenair (power shutdown maybe) caused some samples to freeze. See part "SNAPO" for details on samples.
 - **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.
@@
 ### **Durafet**
-Reference spectro measurement from the 2019-01-18 11:00 do not match with a durafet raw data because Ferrybox was off.
+- Reference spectro measurement from the 2019-01-18 11:00 do not match with a durafet raw data because Ferrybox was off.
 This reference point was not takken in consideration for calibration.
@@
 ### **SNAPO**
+- **2020-01-23**: Freezed and lost samples because of heater issue in the container: 15/11/2019 (durafet x1), 03/12/2019 (FB x2), 11/12/2019 (FB x2), 13/12/2019 (FB x2), 20/12/2019 (FB x2), 03/01/2020 (FB x2).
+Following samples could have been frozen, not sure: 06/09/2019 (FB x2), 13/09/2019 (seaFET x1), 13/09/2019 (FB x2), 20/09/2019 (FB x1), 27/09/2019(FB x2), 04/10/2019 (FB x2), 11/10/2019 (FB x1), 11/10/2019  (durafet x1), 25/10/2019 (FB x2), 01/11/2019 (FB x1), 15/11/2019 (FB x1).
+
+- **2020-01-15**: Results from 2019-04-19 to 2019-08-31 (sent in September 2019) were received.
+FB duplicates from 2019-08-09 were analysed as Durafet because of wrong box.
+One sample from 2019-06-07 (durafet) was analysed by Paris because of wrong box.
 - **2019-04-30**: Duplicate "Ferrybox" samples (SN0316 and SN264, 2019-02-22 14:05) were sent by mistake in Villefranche for pH measurements.
 Those results were put in the datafile as "durafet" samples as soon as they are comming from the Ferrybox tape seawater.
-We will ad a lack of DIC for this week.
+We will add a lack of DIC for this week.
 TA will be measured in Villefranche.

### 2020-01-24 awipev-CO2.Rmd

@@
 ### **FerryBox**
+- **2020-01-24**: heater issues in the contenair (power shutdown maybe) caused some samples to freeze. See part "SNAPO" for details on samples.
 - **2019-09-01**: Some interruptions for the FB during 2 weeks of maintenance.
@@
 ### **FerryBox**
-- **2020-01-24**: heater issues in the contenair (power shutdown maybe) caused some samples to freeze. See part "SNAPO" for details on samples.
 - **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.

### 2020-02-20 awipev-CO2.Rmd
new pH spectro from sf and dur updated in the dicrete_sample file + update of the sf calibration part

@@
   dplyr::arrange(datetime) %>%
-  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600 *24)))%>%
+  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
   dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
@@
                                 ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
-                                ifelse(datetime >= sfinterv[21] , 21,NA ))))))))))))))))))))))
+                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[22], 21,
+                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[23], 22,
+                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[24], 23,
+                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[25], 24,
+                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[26], 25,
+                                ifelse(datetime >= sfinterv[26] , 26,NA )))))))))))))))))))))))))))
 
@@
 
-# # 5th period, pH spectro from 2018-04-16 07:00:00 must fit one  voltINT to calculate E0
-# we put the mean of 4 previous days because voltINT was not present.
+# # 5th period, with pH spectro at 2018-04-16 07:00:00 must fit one voltINT to calculate E0
+# we put the mean of 4 following days because voltINT was not present.
 mean_voltINT_4d <- d_all%>%
-  dplyr::filter(datetime >= "2018-04-11" & datetime <= "2018-04-14")%>%
+  dplyr::filter(datetime >= "2018-04-25" & datetime <= "2018-04-29")%>%
   dplyr::summarise( mean(voltINT, na.rm = TRUE))
 mean_voltINT_4d <- as.numeric(mean_voltINT_4d)
-d_all$voltINT <- ifelse(d_all$datetime == "2018-04-16 07:00:00" , mean_voltINT_4d, d_all$voltINT)
+d_all <- d_all%>%
+  dplyr::mutate(voltINT = ifelse(datetime == "2018-04-16 07:00:00" , mean_voltINT_4d, voltINT))
 
 mean_voltEXT_4d <- d_all%>%
-  dplyr::filter(datetime >= "2018-04-11" & datetime <= "2018-04-14")%>%
+  dplyr::filter(datetime >= "2018-04-25" & datetime <= "2018-04-29")%>%
   dplyr::summarise( mean(voltEXT, na.rm = TRUE))
@@
 
+# put also a temp value because FB was off
 temp_to_replace <- d_all%>%
@@
 
-# put also a temp insi value because FB was off FOR PERIOD ONE 2017-08-24
+# put also a temp insi value because FB was off FOR PERIOD 1 : 2017-08-24
 temp_to_replace <- d_all%>%
-  dplyr::filter(datetime == "2017-08-24 12:00:00")%>%
-  dplyr::summarise( mean(temp_insitu, na.rm = TRUE))
+  dplyr::filter(datetime >= "2017-08-24 12:00:00" & datetime <= "2017-08-24 23:00:00")%>%
+  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
 temp_to_replace <- as.numeric(temp_to_replace)
-d_all$temp_insitu <- ifelse(d_all$datetime == "2017-08-24 13:00:00" , temp_to_replace, d_all$temp_insitu)
+d_all$temp_insitu <- ifelse(d_all$datetime == "2017-08-24 14:00:00" , temp_to_replace, d_all$temp_insitu)
 
 test <- d_all%>%
-  dplyr::filter(datetime=="2017-08-24 13:00:00")
+  dplyr::filter(datetime=="2017-08-24 14:00:00")
+
 ####
@@
   #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
+  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
     dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
     dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+
   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
@@
   dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[20], to= Sys.Date(), color = "#E0E0E0") %>%
-  dyLegend(show = "follow")   %>%
+   dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
+   dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[22], to= sfinterv[23], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[23], to= sfinterv[24], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[24], to= sfinterv[25], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[25], to= Sys.Date(), color = "#CCCCCC") %>%
+  dyLegend(show = "auto")   %>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
   dyRangeSelector(height = 30, dateWindow= NULL)
+
+#@@@@@ test plot #@@@@@ #@@@@@ #@@@@@ 
+# seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu)
+# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
+# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+#   dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
+#     dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
+#     dySeries("phINT_filtered", label = "Raw pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+# 
+#   dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#   dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#     dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#   dyLegend(show = "auto")   %>%
+#   dyAxis( "y",valueRange = c(-1, 2))%>%
+#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+#   dyRangeSelector(height = 30, dateWindow= NULL) 
+#@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
 
@@
   dplyr::arrange(datetime) %>%
-  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(durPeriod)])/2* 3600 *24)))%>%
+  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(durPeriod)])/2* 3600 )))%>%
   dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])

### 2020-02-21 awipev-CO2.Rmd
seafet calibration text updated

@@
 When it is not possible to sample at the vicinity of the sensor for practice reasons (in winter), sampling is done in the harbour and is not taken in consideration for calibration for spatial reasons.
+
 Calibration was done following the methods and code described in Bresnahan et al.
 (2014) and adapted to use in R (seacarb package).
-Deployment periods are difined 15 days before and after the pH spectro sample and are in shading colors on the plot.
+Deployment periods are difined so that one spectrophotometric measurement is in the middle of a defined period of calibration (shaded colors in the plot).
+
 Within this deployment period, calibration is made with E0 calculation (first plot) and final corrected pH is calculated (second plot).
+To allow calibration, one spectrophotometric pH measurement must match: seaFET voltage, in situ temperature (SBE38) and salinity.
+When one of these parameters is missing for any reasons (Ferrybox maintenance, breakdown...), the gap is filled with a mean of the 4 previous or next hours when available.
+If the pH spectrophotometric measurement is too far from the available values, the calibration is not performed (environemental variability reasons).
+The SBE38 insitu temperature and seaFET temperature are very similar (slope = 0.997, r2 = 0.948).
+These two temperatures were used interchangeably if one is missing.
+
+Missing data which could be estimated on : 2017-08-24, 2017-09-28, 2019-09-13 x 2.
+Missing data which could not be estimated on : 2018-04-16 , 2018-12-14, 2019-01-18.
 
@@
 
-# deployment period between 2 spectro measurements
+# We decided to calibrate pH data within each pH spectro measurement.
+# Thus, each pH spectro is taken as one calibration periode. 
+# We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
 sfPeriod <- d_all%>%
@@
                                 ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
-                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[22], 21,
-                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[23], 22,
-                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[24], 23,
-                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[25], 24,
-                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[26], 25,
+                                ifelse(datetime >= sfinterv[21] & datetime <= sfinterv[22], 21,
+                                ifelse(datetime >= sfinterv[22] & datetime <= sfinterv[23], 22,
+                                ifelse(datetime >= sfinterv[23] & datetime <= sfinterv[24], 23,
+                                ifelse(datetime >= sfinterv[24] & datetime <= sfinterv[25], 24,
+                                ifelse(datetime >= sfinterv[25] & datetime <= sfinterv[26], 25,
                                 ifelse(datetime >= sfinterv[26] , 26,NA )))))))))))))))))))))))))))
 
+# To make sf calibration against pH spectro, we need: sal - T insi - voltINT/EXT . If we missed one of these parameters, calibration will not run
+# Here we try to fill the gap when it is possible: make a mean with 4 previous/next hours available in the time serie. 
+# If the pH spectro is too far from a needed value, we decided to skip it for the calibration.
+# we highlighted 7 pH spectro that dont match one of these parameters : 2017-08-24 14:00:00 - 2017-09-28 13:00:00 - 2018-04-16 07:00:00 - 2018-12-14 09:00:00 - 2019-01-18 09:00:00 - 2019-09-13 08:00:00 - 2019-09-13 13:00:00
 # Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04 (1) and removed from 2018-01-08 to 2018-02-02 (2)
@@
 names(calib_spectro) <- c("deployment_sf", "E0int25_sf", "E0ext25_sf")
+
 # add E0 mean to seaFET data per deployment
@@
 #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@ 
-# seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu)
-# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
-# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-#   dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-#     dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
-#     dySeries("phINT_filtered", label = "Raw pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-# 
-#   dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#     dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dyLegend(show = "auto")   %>%
-#   dyAxis( "y",valueRange = c(-1, 2))%>%
-#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-#   dyRangeSelector(height = 30, dateWindow= NULL) 
+seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb)
+#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
+seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+  dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("phINT_filtered", label = "Raw pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
+
+  dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+    dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dyLegend(show = "auto")   %>%
+  dyAxis( "y",valueRange = c(-1, 2))%>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyRangeSelector(height = 30, dateWindow= NULL)
 #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
@@
 
+### **T in situ / T seaFET**
+```{r Temp comparaison, echo=FALSE, message= FALSE, warning=FALSE}
+fit <- lmodel2(data = d_all,  T_seaF ~ temp_insitu , nperm = 99)
+
+pTseaf_Tinsi<-  ggplot(d_all,aes(x=temp_insitu, y= T_seaF, label = month))+
+  geom_text( aes(color=factor(month))) + 
+ # scale_color_viridis_d(option = "C", guide="none")+
+  geom_line(aes(x = T_seaF, y = T_seaF), linetype = "dashed") +
+  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+  labs(title = paste("T seaF vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
+                     "; Intercept =", signif(fit$regression.results[2,2], 3),
+                     "; Slope =", signif( fit$regression.results[2,3], 3),
+                     "; P =", signif(fit$P.param, 3))) +
+  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
+  labs( x="T insi", y="T seaF ", color = "Months")  +theme_bw()
+
+print(pTseaf_Tinsi)
+```
+
 ### **seaFET / durafet pHs**
@@
 fit <- lmodel2(data = d_all,  pHint_tot_sf_norm4 ~ pH_durafet_norm4 , nperm = 99)
-
 pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pHint_tot_sf_norm4, label = month))+

### 2020-02-21 awipev-CO2.Rmd
temperature insitu + seafet calibration OK

@@
 
+## Temperatures
+Several temperature sensors are on site, 1 inside the Ferrybox and 2 outside:
+
+- 1 SBE45 inside the Ferrybox (temp_fb)
+- 1 seaFET T°C inside the seaFET at 11 meters depth (T_seaF)
+- 1 SBE38 at 11 meters depth (temp_insitu)
+
+Comparative approch allowed by following plots:
+
+### **T seaFET / T in situ **
+```{r Temp comparaison, echo=FALSE, message= FALSE, warning=FALSE}
+# seaF outliers (T - volt int - volt ext) to remove from 2017-12-10 to 2017-12-14
+d_all <- d_all %>%
+  dplyr::mutate(T_seaF = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, T_seaF),
+                voltINT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltINT), 
+                voltEXT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltEXT))
+
+fit <- lmodel2(data = d_all,  T_seaF ~ temp_insitu , nperm = 99)
+
+pTseaf_Tinsi<-  ggplot(d_all,aes(x=temp_insitu, y= T_seaF, label = month))+
+  geom_text( aes(color=factor(month))) + 
+ # scale_color_viridis_d(option = "C", guide="none")+
+  geom_line(aes(x = T_seaF, y = T_seaF), linetype = "dashed") +
+  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+  labs(title = paste("T seaF vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
+                     "; Intercept =", signif(fit$regression.results[2,2], 3),
+                     "; Slope =", signif( fit$regression.results[2,3], 3),
+                     "; P =", signif(fit$P.param, 3))) +
+  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
+  labs( x="T insi", y="T seaF ", color = "Months")  +theme_bw()
+print(pTseaf_Tinsi)
+
+d_all$diff_T_seaF_insitu <- d_all$T_seaF - d_all$temp_insitu
+mean_diff_T_seaF_insitu <- round(mean(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)
+sd_diff_T_seaF_insitu <- round(sd(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)
+
+```
+
+The mean difference between T seaFET and in situ is: `r mean_diff_T_seaF_insitu` ± `r sd_diff_T_seaF_insitu°C.
+
+### **T Ferrybox / T in situ **
+```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
+# Remove temp_fb outliers 
+d_all <- d_all %>%
+  dplyr::mutate(temp_fb = ifelse(datetime >= "2017-03-22 08:00:00" & datetime <= "2017-03-23 16:00:00", NA, temp_fb),
+                temp_fb = ifelse(temp_fb >15, NA, temp_fb))
+
+fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu , nperm = 99)
+
+pTfb_Tinsi<-  ggplot(d_all,aes(x=temp_insitu, y= temp_fb, label = month))+
+  geom_text( aes(color=factor(month))) + 
+ # scale_color_viridis_d(option = "C", guide="none")+
+  geom_line(aes(x = temp_fb, y = temp_fb), linetype = "dashed") +
+  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+  labs(title = paste("T FB vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
+                     "; Intercept =", signif(fit$regression.results[2,2], 3),
+                     "; Slope =", signif( fit$regression.results[2,3], 3),
+                     "; P =", signif(fit$P.param, 3))) +
+  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
+  labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
+print(pTfb_Tinsi)
+
+d_all$diff_T_fb_insitu <- d_all$T_seaF - d_all$temp_insitu
+mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
+sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
+```
+
+The mean difference between T seaFET and in situ is: `r mean_diff_T_fb_insitu` ± `r sd_diff_T_fb_insitu`°C.
+
 ## Total alkalinity
@@
 If the pH spectrophotometric measurement is too far from the available values, the calibration is not performed (environemental variability reasons).
-The SBE38 insitu temperature and seaFET temperature are very similar (slope = 0.997, r2 = 0.948).
+The SBE38 insitu temperature and seaFET temperature are very similar (slope = 0.992, r2 = 0.96, see tab "Temperatures").
 These two temperatures were used interchangeably if one is missing.
@@
   dplyr::filter(!is.na(pH_s_seafet_temp_field))
+# Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
+sfPeriod <- sfPeriod%>%
+dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
 
@@
 sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
- #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
- #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
+#  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
+# sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
+#  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
+# sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
 
@@
 
-# # 5th period, with pH spectro at 2018-04-16 07:00:00 must fit one voltINT to calculate E0
-# we put the mean of 4 following days because voltINT was not present.
-mean_voltINT_4d <- d_all%>%
-  dplyr::filter(datetime >= "2018-04-25" & datetime <= "2018-04-29")%>%
+# period 1, mean of 4 next hours for volt int + T seaF
+mean_voltINT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
   dplyr::summarise( mean(voltINT, na.rm = TRUE))
-mean_voltINT_4d <- as.numeric(mean_voltINT_4d)
+mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
 d_all <- d_all%>%
-  dplyr::mutate(voltINT = ifelse(datetime == "2018-04-16 07:00:00" , mean_voltINT_4d, voltINT))
-
-mean_voltEXT_4d <- d_all%>%
-  dplyr::filter(datetime >= "2018-04-25" & datetime <= "2018-04-29")%>%
+  dplyr::mutate(voltINT = ifelse(datetime == "2017-08-24 14:00:00" , mean_voltINT_4h, voltINT))
+
+mean_voltEXT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
   dplyr::summarise( mean(voltEXT, na.rm = TRUE))
-mean_voltEXT_4d <- as.numeric(mean_voltEXT_4d)
-d_all$voltEXT <- ifelse(d_all$datetime == "2018-04-16 07:00:00" , mean_voltEXT_4d, d_all$voltEXT)
-
-# put also a salinity value because FB was off
-sal_to_replace <- d_all%>%
-  dplyr::filter(datetime >= "2018-04-16 00:00:00" & datetime <= "2018-04-16 23:59:59")%>%
-  dplyr::summarise( mean(sal_fb, na.rm = TRUE))
-sal_to_replace <- as.numeric(sal_to_replace)
-d_all$sal_fb <- ifelse(d_all$datetime == "2018-04-16 07:00:00" , sal_to_replace, d_all$sal_fb)
+mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
+d_all <- d_all%>%
+  dplyr::mutate(voltEXT = ifelse(datetime == "2017-08-24 14:00:00" , mean_voltEXT_4h, voltEXT))
+
+mean_TseaF_4h <- d_all%>%
+  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
+  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
+mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
+d_all <- d_all%>%
+  dplyr::mutate(temp_insitu = ifelse(datetime == "2017-08-24 14:00:00" , mean_TseaF_4h, temp_insitu))
+
+# period 2, mean of 4 next hours for volt int + T seaF
+mean_voltINT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
+  dplyr::summarise( mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+d_all <- d_all%>%
+  dplyr::mutate(voltINT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltINT_4h, voltINT))
+
+mean_voltEXT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
+  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
+mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
+d_all <- d_all%>%
+  dplyr::mutate(voltEXT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltEXT_4h, voltEXT))
+
+# period 20, mean of 4 previous hours for volt int + T seaF
+mean_voltINT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
+  dplyr::summarise( mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+d_all <- d_all%>%
+  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltINT_4h, voltINT))
+
+mean_voltEXT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
+  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
+mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
+d_all <- d_all%>%
+  dplyr::mutate(voltEXT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltEXT_4h, voltEXT))
+
+# period 21, mean of 4 previous hours for volt int + T seaF
+mean_voltINT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
+  dplyr::summarise( mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+d_all <- d_all%>%
+  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltINT_4h, voltINT))
+
+mean_voltEXT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
+  dplyr::summarise( mean(voltINT, na.rm = TRUE))
+mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
+d_all <- d_all%>%
+  dplyr::mutate(voltEXT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltEXT_4h, voltEXT))
+
+mean_TseaF_4h <- d_all%>%
+  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
+  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
+mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
+d_all <- d_all%>%
+  dplyr::mutate(temp_insitu = ifelse(datetime == "2019-09-13 13:00:00" , mean_TseaF_4h, temp_insitu))
+
 #interpolation of salinity during the FB off maintenance
@@
 
-# put also a temp value because FB was off
-temp_to_replace <- d_all%>%
-  dplyr::filter(datetime >= "2018-04-16 00:00:00" & datetime <= "2018-04-16 23:59:59")%>%
-  dplyr::summarise( mean(temp_fb, na.rm = TRUE))
-temp_to_replace <- as.numeric(temp_to_replace)
-d_all$temp_fb <- ifelse(d_all$datetime == "2018-04-16 07:00:00" , temp_to_replace, d_all$temp_fb)
-
-# put also a temp insi value because FB was off FOR PERIOD 1 : 2017-08-24
-temp_to_replace <- d_all%>%
-  dplyr::filter(datetime >= "2017-08-24 12:00:00" & datetime <= "2017-08-24 23:00:00")%>%
-  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
-temp_to_replace <- as.numeric(temp_to_replace)
-d_all$temp_insitu <- ifelse(d_all$datetime == "2017-08-24 14:00:00" , temp_to_replace, d_all$temp_insitu)
-
-test <- d_all%>%
-  dplyr::filter(datetime=="2017-08-24 14:00:00")
+# test <- d_all%>%
+#   dplyr::filter(datetime=="2017-08-24 14:00:00")
 
@@
 
-#@@@@@ test plot #@@@@@ #@@@@@ #@@@@@ 
-seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb)
-#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
-seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-  dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
-    dySeries("phINT_filtered", label = "Raw pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
-
-  dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
-    dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dyLegend(show = "auto")   %>%
-  dyAxis( "y",valueRange = c(-1, 2))%>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-  dyRangeSelector(height = 30, dateWindow= NULL)
-#@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
+# #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@ 
+# seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb,pHint_tot_sf)
+# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
+# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+#   dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
+#     dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
+#     dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#   dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
+# 
+#   dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#   dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#     dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#   dyLegend(show = "auto")   %>%
+#   dyAxis( "y2",valueRange = c(-3, 36))%>%
+#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+#   dyRangeSelector(height = 30, dateWindow= NULL)
+# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
 
@@
 sfoffset <- left_join(sfPeriod[,c(1,2)], d_all%>%dplyr::select(datetime, pHint_tot_sf), by="datetime")
-dat <- mutate(sfoffset, diff_pH_sf = pH_s_seafet_temp_field - pHint_tot_sf)
+dat <- mutate(sfoffset, diff_pH_sf = round((pH_s_seafet_temp_field - pHint_tot_sf),digits  = 4))
 average_offset <- mean(abs(dat$diff_pH_sf), na.rm=TRUE)
@@
 For information, mean temperatures in Ferrybox and *in situ* are repectively 3.5°C and 2.5°C.
-
-### **T in situ / T seaFET**
-```{r Temp comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-fit <- lmodel2(data = d_all,  T_seaF ~ temp_insitu , nperm = 99)
-
-pTseaf_Tinsi<-  ggplot(d_all,aes(x=temp_insitu, y= T_seaF, label = month))+
-  geom_text( aes(color=factor(month))) + 
- # scale_color_viridis_d(option = "C", guide="none")+
-  geom_line(aes(x = T_seaF, y = T_seaF), linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("T seaF vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
-  labs( x="T insi", y="T seaF ", color = "Months")  +theme_bw()
-
-print(pTseaf_Tinsi)
-```
 

### 2020-02-21 awipev-CO2.Rmd
temperature insitu + seafet calibration OK2

@@
    dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[22], to= sfinterv[23], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[23], to= sfinterv[24], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[24], to= sfinterv[25], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[25], to= Sys.Date(), color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[22], to= Sys.Date(), color = "#CCCCCC") %>%
   dyLegend(show = "auto")   %>%

### 2020-02-24 awipev-CO2.Rmd
seafet calibration period 1 updated

@@
 
-The mean difference between T seaFET and in situ is: `r mean_diff_T_seaF_insitu` ± `r sd_diff_T_seaF_insitu°C.
+The mean difference between T seaFET and in situ is: `r mean_diff_T_seaF_insitu` ± `r sd_diff_T_seaF_insitu°C`.
 
@@
                                 ifelse(datetime >= sfinterv[21] & datetime <= sfinterv[22], 21,
-                                ifelse(datetime >= sfinterv[22] & datetime <= sfinterv[23], 22,
-                                ifelse(datetime >= sfinterv[23] & datetime <= sfinterv[24], 23,
-                                ifelse(datetime >= sfinterv[24] & datetime <= sfinterv[25], 24,
-                                ifelse(datetime >= sfinterv[25] & datetime <= sfinterv[26], 25,
-                                ifelse(datetime >= sfinterv[26] , 26,NA )))))))))))))))))))))))))))
+                                #ifelse(datetime >= sfinterv[22] & datetime <= sfinterv[23], 22,
+                                #ifelse(datetime >= sfinterv[23] & datetime <= sfinterv[24], 23,
+                                #ifelse(datetime >= sfinterv[24] & datetime <= sfinterv[25], 24,
+                                #ifelse(datetime >= sfinterv[25] & datetime <= sfinterv[26], 25,
+                                ifelse(datetime >= sfinterv[22] , 22,NA )))))))))))))))))))))))
 
@@
 d_all <- d_all%>%
-  dplyr::mutate(voltINT = ifelse(datetime == "2017-08-24 14:00:00" , mean_voltINT_4h, voltINT))
+  dplyr::mutate(voltINT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltINT_4h, voltINT))
 
@@
 d_all <- d_all%>%
-  dplyr::mutate(voltEXT = ifelse(datetime == "2017-08-24 14:00:00" , mean_voltEXT_4h, voltEXT))
+  dplyr::mutate(voltEXT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltEXT_4h, voltEXT))
 
@@
 d_all <- d_all%>%
-  dplyr::mutate(temp_insitu = ifelse(datetime == "2017-08-24 14:00:00" , mean_TseaF_4h, temp_insitu))
+  dplyr::mutate(temp_insitu = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_insitu))
 
@@
    dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[22], to= Sys.Date(), color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[22], to= Sys.Date(), color = "#E0E0E0") %>%
   dyLegend(show = "auto")   %>%
@@
 # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@ 
-# seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb,pHint_tot_sf)
-# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
-# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-#   dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-#     dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
-#     dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
-# 
-#   dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#     dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dyLegend(show = "auto")   %>%
-#   dyAxis( "y2",valueRange = c(-3, 36))%>%
-#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-#   dyRangeSelector(height = 30, dateWindow= NULL)
+seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb,pHint_tot_sf)
+#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
+seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+  dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
+
+  dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+    dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dyLegend(show = "auto")   %>%
+  dyAxis( "y2",valueRange = c(-3, 36))%>%
+  dyAxis( "y",valueRange = c(-2, 2))%>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyRangeSelector(height = 30, dateWindow= NULL)
 # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@

### 2020-02-24 awipev-CO2.Rmd
seafet calibration period 5 updated

@@
 
-The mean difference between T seaFET and in situ is: `r mean_diff_T_seaF_insitu` ± `r sd_diff_T_seaF_insitu°C`.
+The mean difference between T seaFET and in situ is: `r mean_diff_T_seaF_insitu` ± `r sd_diff_T_seaF_insitu`°C.
 
@@
 sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
+#Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
+# This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
+sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
 #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00

### 2020-02-24 awipev-CO2.Rmd
durafet calibration part updated

@@
 # we highlighted 7 pH spectro that dont match one of these parameters : 2017-08-24 14:00:00 - 2017-09-28 13:00:00 - 2018-04-16 07:00:00 - 2018-12-14 09:00:00 - 2019-01-18 09:00:00 - 2019-09-13 08:00:00 - 2019-09-13 13:00:00
-# Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04 (1) and removed from 2018-01-08 to 2018-02-02 (2)
-# 1
+# (1) Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04,
+# (2) removed from 2018-01-08 to 2018-02-02
+# (3) outliers removed
+# (1)
 d_all$phINT_filtered <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phINT_filtered < 8.04, NA, d_all$phINT_filtered) 
@@
 d_all$voltEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
-# 2
+# (2)
 d_all$voltINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltINT)
@@
 d_all$phEXT_filtered <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phEXT_filtered)
+# (3)
+d_all$voltINT <- ifelse(d_all$datetime == "2017-11-02 21:00:00" | d_all$datetime == "2018-04-18 14:00:00", NA, d_all$voltINT)
 
@@
 
-# #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@ 
-seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb,pHint_tot_sf)
-#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
-seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-  dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
-    dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
-
-  dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
-    dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dyLegend(show = "auto")   %>%
-  dyAxis( "y2",valueRange = c(-3, 36))%>%
-  dyAxis( "y",valueRange = c(-2, 2))%>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-  dyRangeSelector(height = 30, dateWindow= NULL)
-# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
+# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@ 
+# seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb,pHint_tot_sf)
+# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
+# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+#   dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
+#     dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
+#     dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#   dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
+# 
+#   dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#   dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#     dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#   dyLegend(show = "auto")   %>%
+#   dyAxis( "y2",valueRange = c(-3, 36))%>%
+#   dyAxis( "y",valueRange = c(-2, 2))%>%
+#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+#   dyRangeSelector(height = 30, dateWindow= NULL)
+# # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
 
@@
   d_all %>%
-  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
+  group_by(date=as.Date(datetime), 
+           month=month(datetime, label=TRUE), 
+           year=year(datetime)) %>%
   summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
@@
 durinterv[14] <- ymd_hms("2019-01-19 00:00:00")
+
+# Remove outliers from 2018-07-10 00:00 to 05:00
+d_all$pH_durafet_corrected <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$pH_durafet_corrected)
+d_all$pH_durafet <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$pH_durafet)
 
@@
                                 ifelse(datetime >= durinterv[18] & datetime <= durinterv[19], 18,
-
-                                ifelse(datetime >= durinterv[19], 18,NA ))))))))))))))))))))
+                                ifelse(datetime >= durinterv[19] & datetime <= durinterv[20], 19,
+                                 ifelse(datetime >= durinterv[20] & datetime <= durinterv[21], 20,
+                                ifelse(datetime >= durinterv[21] & datetime <= durinterv[22], 21,
+                                 ifelse(datetime >= durinterv[22] & datetime <= durinterv[23], 22,
+                                ifelse(datetime >= durinterv[23] & datetime <= durinterv[24], 23,
+                                ifelse(datetime >= durinterv[24] & datetime <= durinterv[25], 24,
+                                 ifelse(datetime >= durinterv[25] & datetime <= durinterv[26], 25,
+                                ifelse(datetime >= durinterv[26], 26,NA )))))))))))))))))))))))))))
 
@@
                                 ifelse(deployment_dur == 18, dat_dur$diff_pH_dur[18],
-                                ifelse(deployment_dur == 19, dat_dur$diff_pH_dur[19],0))))))))))))))))))),
+                                ifelse(deployment_dur == 19, dat_dur$diff_pH_dur[19],
+                                ifelse(deployment_dur == 20, dat_dur$diff_pH_dur[20],
+                                ifelse(deployment_dur == 21, dat_dur$diff_pH_dur[21],
+                                ifelse(deployment_dur == 22, dat_dur$diff_pH_dur[22],
+                                ifelse(deployment_dur == 23, dat_dur$diff_pH_dur[23],
+                                ifelse(deployment_dur == 24, dat_dur$diff_pH_dur[24],
+                                ifelse(deployment_dur == 25, dat_dur$diff_pH_dur[25],0))))))))))))))))))))))))),
               pH_durafet_corrected = pH_durafet + offset_durafet
@@
     dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="GMT"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
-
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
    dyShading(from = durinterv[16], to= durinterv[17], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[17], to= Sys.Date(), color = "#CCCCCC") %>%
+   dyShading(from = durinterv[17], to= durinterv[18], color = "#CCCCCC") %>%
+   dyShading(from = durinterv[18], to= durinterv[19], color = "#E0E0E0") %>%
+    dyShading(from = durinterv[19], to= durinterv[20], color = "#CCCCCC") %>%
+    dyShading(from = durinterv[20], to= durinterv[21], color = "#E0E0E0") %>%
+   dyShading(from = durinterv[21], to= durinterv[22], color = "#CCCCCC") %>%
+   dyShading(from = durinterv[22], to= durinterv[23], color = "#E0E0E0") %>%
+   dyShading(from = durinterv[23], to= durinterv[24], color = "#CCCCCC") %>%
+   dyShading(from = durinterv[24], to= durinterv[25], color = "#E0E0E0") %>%
+  dyShading(from = durinterv[25], to= durinterv[26], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[26], to= Sys.Date(), color = "#E0E0E0") %>%
      dyLegend(show = "follow")   %>%
@@
 The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).
+
+## Range per months
+
+```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
+range_month <-
+  d_all %>%
+  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
+  #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
+  summarize(Tinsi_max = max(temp_insitu, na.rm=TRUE),
+            Tinsi_min = min(temp_insitu, na.rm=TRUE),
+            Tfrbx_max = max(temp_fb, na.rm=TRUE),
+            Tfrbx_min = min(temp_fb, na.rm=TRUE),
+            pH_sf_max = max(pHint_tot_sf, na.rm=TRUE),
+            pH_sf_min = min(pHint_tot_sf, na.rm=TRUE),
+            pH_dur_max = max(pH_durafet_corrected, na.rm=TRUE),
+            pH_dur_min = min(pH_durafet_corrected, na.rm=TRUE))
+kable(range_month)
+```
 

### 2020-02-24 awipev-CO2.Rmd
durafet calibration part updated2

@@
 
-# Remove outliers from 2018-07-10 00:00 to 05:00
-d_all$pH_durafet_corrected <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$pH_durafet_corrected)
-d_all$pH_durafet <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$pH_durafet)
-
 # set deployment period between 2 spectro measurements.
@@
               )
+
+# Remove outliers from 2018-07-10 00:00 to 05:00
+d_all$pH_durafet_corrected <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$pH_durafet_corrected)
+d_all$pH_durafet <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$pH_durafet)
+
 # DURAFET 

### 2020-02-24 awipev-CO2.Rmd
durafet calibration part updated2

@@
 # pH seaFET Final
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field,pHint_tot_sf)
+# add spectro points that are not taking into consideration
+d_all <- d_all%>%
+  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", pH_s_seafet_temp_field, NA ))
+
+seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field,pHint_tot_sf, pH_s_sf_no_calb)
 #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
     dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pH_s_seafet_temp_field", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
 
@@
 durinterv <- c( as_datetime("2017-08-24 13:00:00"), durPeriod[,4])
+ #Change period sfinterv[2]. Because durafet measurementwas not working on period 1. No match between spectro and sensor. Durafet spectro 1 not taking into consideration.
+durinterv[2] <- ymd_hms("2017-08-24 13:00:00")
+ #Change period sfinterv[06]. Because durafet was not responding good after 2018-03-08 23:00:00.
+durinterv[6] <- ymd_hms("2018-03-08 23:00:00")
+ #Change period sfinterv[13]. Because durafet was off just after 2018-12-28.
+durinterv[13] <- ymd_hms("2019-12-28 17:00:00")
  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-durinterv[13] <- ymd_hms("2019-01-17 23:00:00")
- #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-durinterv[14] <- ymd_hms("2019-01-19 00:00:00")
+#durinterv[14] <- ymd_hms("2019-01-19 00:00:00")
 
@@
 # DURAFET 
-durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected)
+# add spectro points that are not taking into consideration
+d_all <- d_all%>%
+  dplyr::mutate( pH_s_dur_no_calb = ifelse(datetime == "2017-08-24 13:00:00", pH_s_durafet_temp_field, NA ))
+
+durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected, pH_s_dur_no_calb)
 durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
@@
     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("pH_s_durafet_temp_field", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+       dySeries("pH_s_dur_no_calb", label = "pH spectro no calibration", color ="black", pointShape = "triangle",strokeWidth=0, pointSize=6) %>%
        dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
-    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
     dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
@@
 
+# #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
+durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected)
+durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
+ dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
+    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
+    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
+    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
+    dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="GMT"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
+  dyLegend(show = "auto")   %>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyRangeSelector(height = 30, dateWindow= NULL)
+# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
+
 # #plot for POSTER june 2019
@@
   #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
-  summarize(Tinsi_max = max(temp_insitu, na.rm=TRUE),
-            Tinsi_min = min(temp_insitu, na.rm=TRUE),
-            Tfrbx_max = max(temp_fb, na.rm=TRUE),
-            Tfrbx_min = min(temp_fb, na.rm=TRUE),
-            pH_sf_max = max(pHint_tot_sf, na.rm=TRUE),
-            pH_sf_min = min(pHint_tot_sf, na.rm=TRUE),
-            pH_dur_max = max(pH_durafet_corrected, na.rm=TRUE),
-            pH_dur_min = min(pH_durafet_corrected, na.rm=TRUE))
+  summarize(Tinsi_max =round( max(temp_insitu, na.rm=TRUE), digits = 2),
+            Tinsi_min = round(min(temp_insitu, na.rm=TRUE), digits = 2),
+            sal_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
+            sal_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
+            pH_sf_max = round(max(pHint_tot_sf, na.rm=TRUE), digits = 4),
+            pH_sf_min = round(min(pHint_tot_sf, na.rm=TRUE), digits = 4))
 kable(range_month)

### 2020-02-24 awipev-CO2.Rmd

@@
     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_durafet_temp_field", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pH_s_durafet_temp_field", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
        dySeries("pH_s_dur_no_calb", label = "pH spectro no calibration", color ="black", pointShape = "triangle",strokeWidth=0, pointSize=6) %>%
@@
 print(plot_offset_dur)
-
-# #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected)
-durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
- dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
-    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
-    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="GMT"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
-  dyLegend(show = "auto")   %>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-  dyRangeSelector(height = 30, dateWindow= NULL)
-# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
 

### 2020-02-28 sal_temp.Rmd
New Rmd for salinity and temperature

---
title: "Salinity and temperature at Ny-Ålesund" 
author: "Jean-Pierre Gattuso and Samir Alliouane"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  rmarkdown::html_document:
    theme: paper
    number_sections: false

---
![ ](Images/AWIPEV-Logo.jpg){width=250px}
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}

####define who is the user and define path
rm(list = ls())

if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_AWIPEV-CO2/fb_awipev-co2_server/ny-alesund/data/NRT_data/"

####Set environmental variables####
Sys.setenv(TZ="UTC")
if (!require("data.table")) install.packages("data.table")
##Provide in this section the parameters to be downloaded
#*********************************
#Use the following aggregation parameters
agg_time = "MINUTE" #SECOND, MINUTE, HOUR, DAY, MONTH, YEAR
#Calculate the following statistical values. 
agg_fun_1 = "MEAN" #MEDIAN
agg_fun_2 = "STDDEV"
agg_fun_3 = "N"
#*********************************

#### Download data ####
# Choose end date or take the date of today
# end_date <- ymd_hms("2017-12-31 23:59:59")
end_date <- ymd_hms(paste0(Sys.Date(), " 00:00:00 UTC"))
enddate <- format(end_date,"%Y-%m-%dT%H:%M:%S")

# Choose start date
start_date <- ymd_hms("2015-07-23 00:00:00")
startdate <- format(start_date, "%Y-%m-%dT%H:%M:%S")

# if enddate - startdate < 1 d one skips everything until the end of this script
if (end_date-start_date <= days(1)) {
  stop()
  }

if(agg_time=="MINUTE"){
  aggregate_string=paste0("&aggregate=",agg_time)
} else {
  aggregate_string=paste0("&aggregate=",agg_time,"&aggregateFunctions=",agg_fun_1,"&aggregateFunctions=",agg_fun_2,"&aggregateFunctions=",agg_fun_3)
}

code <- paste0("https://dashboard.awi.de/data-xxl/rest/data?beginDate=",startdate,"&endDate=",enddate,"&format=text/tab-separated-values",aggregate_string,
               "&sensors=station:svluwobs:fb_731101:sbe45_awi_0403:salinity",
               "&sensors=station:svluwobs:svluw2:sbe38_awi_0657:temperature")

data <- data.table::fread(code, encoding = "UTF-8", showProgress    = TRUE)
colnames(data) <- c("datetime", "Salinity", "Temperature" )
data$datetime <- ymd_hms(data$datetime)
```

### 2020-03-06 awipev-CO2.Rmd
seaFET's deployment periods changed

@@
 
+We decided to change the calculation of E0.
+Before E0 was calculated for each pH spectro measurements.
+Now, EO is calculated making a mean of several E0 that come from one deployment period (sensor in the water for several months).
+
 ### **seaFET calibration constante E0**
@@
 
-# We decided to calibrate pH data within each pH spectro measurement.
-# Thus, each pH spectro is taken as one calibration periode. 
-# We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
-sfPeriod <- d_all%>%
-  dplyr::select(datetime, pH_s_seafet_temp_field)%>%
-  dplyr::filter(!is.na(pH_s_seafet_temp_field))
-# Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
-sfPeriod <- sfPeriod%>%
-dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
-
-sfPeriod <-  sfPeriod %>%
-  dplyr::arrange(datetime) %>%
-  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
-  dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
-
-#put interval in a list with the start date of seaFET measurements
-sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
-#Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
-# This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
-sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
-#  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-# sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
-#  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-# sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
-
-#sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
-# set deployment period between 2 spectro measurements.
+# # We decided to calibrate pH data within each pH spectro measurement.
+# # Thus, each pH spectro is taken as one calibration periode. 
+# # We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
+# sfPeriod <- d_all%>%
+#   dplyr::select(datetime, pH_s_seafet_temp_field)%>%
+#   dplyr::filter(!is.na(pH_s_seafet_temp_field))
+# # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
+# sfPeriod <- sfPeriod%>%
+# dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
+# 
+# sfPeriod <-  sfPeriod %>%
+#   dplyr::arrange(datetime) %>%
+#   dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
+#   dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
+# 
+# #put interval in a list with the start date of seaFET measurements
+# sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
+# #Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
+# # This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
+# sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
+# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
+# # sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
+# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
+# # sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
+# 
+# #sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
+# # set deployment period between 2 spectro measurements.
+
+# # add here the new periods sfinterv[..]
+# d_all <- d_all %>%
+#   dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
+#                                 ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
+#                                 ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
+#                                 ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
+#                                 ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
+#                                 ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
+#                                 ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
+#                                 ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
+#                                 ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
+#                                 ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
+#                                 ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
+#                                  ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
+#                                  ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
+#                                  ifelse(datetime >= sfinterv[14] & datetime <= sfinterv[15], 14,
+#                                  ifelse(datetime >= sfinterv[15] & datetime <= sfinterv[16], 15,
+#                                  ifelse(datetime >= sfinterv[16] & datetime <= sfinterv[17], 16,
+#                                  ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
+#                                 ifelse(datetime >= sfinterv[18] & datetime <= sfinterv[19], 18,
+#                                 ifelse(datetime >= sfinterv[19] & datetime <= sfinterv[20], 19,
+#                                 ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
+#                                 ifelse(datetime >= sfinterv[21] & datetime <= sfinterv[22], 21,
+#                                 #ifelse(datetime >= sfinterv[22] & datetime <= sfinterv[23], 22,
+#                                 #ifelse(datetime >= sfinterv[23] & datetime <= sfinterv[24], 23,
+#                                 #ifelse(datetime >= sfinterv[24] & datetime <= sfinterv[25], 24,
+#                                 #ifelse(datetime >= sfinterv[25] & datetime <= sfinterv[26], 25,
+#                                 ifelse(datetime >= sfinterv[22] , 22,NA )))))))))))))))))))))))
+
+# set deployment period when seaFET is in/out of water
+sfinterv <- c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00")
+
 # add here the new periods sfinterv[..]
@@
                                 ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02,
-                                ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
-                                ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
-                                ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
-                                ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
-                                ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
-                                ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
-                                ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
-                                ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
-                                ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
-                                 ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
-                                 ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
-                                 ifelse(datetime >= sfinterv[14] & datetime <= sfinterv[15], 14,
-                                 ifelse(datetime >= sfinterv[15] & datetime <= sfinterv[16], 15,
-                                 ifelse(datetime >= sfinterv[16] & datetime <= sfinterv[17], 16,
-                                 ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
-                                ifelse(datetime >= sfinterv[18] & datetime <= sfinterv[19], 18,
-                                ifelse(datetime >= sfinterv[19] & datetime <= sfinterv[20], 19,
-                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
-                                ifelse(datetime >= sfinterv[21] & datetime <= sfinterv[22], 21,
-                                #ifelse(datetime >= sfinterv[22] & datetime <= sfinterv[23], 22,
-                                #ifelse(datetime >= sfinterv[23] & datetime <= sfinterv[24], 23,
-                                #ifelse(datetime >= sfinterv[24] & datetime <= sfinterv[25], 24,
-                                #ifelse(datetime >= sfinterv[25] & datetime <= sfinterv[26], 25,
-                                ifelse(datetime >= sfinterv[22] , 22,NA )))))))))))))))))))))))
+                                ifelse(datetime >= sfinterv[3] , 03,NA ))))
 
@@
 
-# period 2, mean of 4 next hours for volt int + T seaF
+# period 1 also, mean of 4 next hours for volt int + T seaF
 mean_voltINT_4h <- d_all%>%
@@
 
-# period 20, mean of 4 previous hours for volt int + T seaF
+# period 03, mean of 4 previous hours for volt int + T seaF
 mean_voltINT_4h <- d_all%>%
@@
 
-# period 21, mean of 4 previous hours for volt int + T seaF
+# period 03 also, mean of 4 previous hours for volt int + T seaF
 mean_voltINT_4h <- d_all%>%
@@
   dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
+    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
+
   dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
@@
 
-# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@ 
-# seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb,pHint_tot_sf)
-# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
-# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-#   dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-#     dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
-#     dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
-# 
-#   dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#     dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dyLegend(show = "auto")   %>%
-#   dyAxis( "y2",valueRange = c(-3, 36))%>%
-#   dyAxis( "y",valueRange = c(-2, 2))%>%
-#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-#   dyRangeSelector(height = 30, dateWindow= NULL)
-# # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
+# #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
+seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb)
+#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
+seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+  dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
+    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
+
+  dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+    dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
+    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
+  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
+  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
+    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
+  dyLegend(show = "auto")   %>%
+  dyAxis( "y2",valueRange = c(-3, 36))%>%
+  dyAxis( "y",valueRange = c(-2, 2))%>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyRangeSelector(height = 30, dateWindow= NULL)
+# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
 

### 2020-03-08 sal_temp.Rmd
sal_temp but not working yet

@@
 ![ ](Images/AWIPEV-Logo.jpg){width=250px}
-```{r setup, include=FALSE}
+```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
+Sys.setlocale("LC_ALL", "en_US.UTF-8")
+Sys.setenv(TZ='UTC') # on utilise UTC
+rm(list = ls())
+library(tidyverse)
+library(robfilter)
+library(seacarb)
+library(gridExtra)
+library(reshape2)
+library(lubridate)
+library(lmtest)
+library(grid)
+library(viridis)
+library(dygraphs)
+require("knitr")
+library("lmodel2")
+library(captioner)
+library(xts)
+library(seismicRoll)
+library(scales)
+if (!require("data.table")) install.packages("data.table")
 knitr::opts_chunk$set(echo = TRUE)
+
+fig_nums <- captioner()
+table_nums <- captioner(prefix = "Table")
+
+#define who is the user and define path
+if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
+if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"
+
+######## function to make regression plot with model I equation in title
+ggreg <- function (fit, point_size=2) {
+  ggplot(fit$model, aes_string(x = names(fit$model)[2],
+                               y = names(fit$model)[1])) +
+    geom_point(size = point_size, col = "blue") +
+    stat_smooth(method = "lm", col = "black") +
+    labs(title = paste(title, "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                       "; Intercept =",signif(fit$coef[[1]],5 ),
+                       "; Slope =",signif(fit$coef[[2]], 5),
+                       "; P =",signif(summary(fit)$coef[2,4], 5))) +
+    theme(plot.title = element_text(size=7))
+}
+
+#################### which.closest function
+which.closest <- function(x, table, ...) {
+  round(approx(x=table, y=1:length(table), xout=x, ...)$y)
+}
+
+#################### Regression function
+# function regression plot with model II equation (MA) in title
+## Dans labs ajout de la variable TITRE pour mettre titre avant chaque graphe
+ggreg2 <- function (fit, xdata, ydata) { # x and y are the names of the variables
+  fit_data <- data.frame(fit$x, fit$y)
+  colnames(fit_data) = c(xdata, ydata)
+reg <- fit$regression.results[2,] #one selects MA only
+intercept <- reg$Intercept
+slope <- reg$Slope
+  ggplot(data = fit_data, aes_string(x = xdata, y = ydata)) + 
+  geom_point(size = 2, col = "blue") +
+  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),
+              colour = "blue")  + 
+  labs(title = paste(titre,"\n Adj R2 = ", signif(fit$rsquare, 3),
+                     "; Intercept =", signif(intercept, 3),
+                     "; Slope =", signif(slope, 3),
+                     "; P =", signif(fit$P.param, 3)))
+}
+
+mytheme <- theme_bw() +
+  theme(axis.text.x=element_text(size=16, color="black"),
+        axis.title.x=element_text(face="bold", size=16),
+        axis.text.y=element_text(size=16, color="black"),
+        axis.title.y=element_text(face="bold", size=16),
+        plot.title = element_text(face="bold", size=14)
+)
+
+#################### Mytheme
+Mytheme <- function(size_labs = 7, face_font="plain") {
+  theme_bw() +
+  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
+        axis.title.x = element_text(face=face_font, size=size_labs),
+        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
+        axis.title.y = element_text(face=face_font, size=size_labs),
+        axis.ticks.x = element_line(size=0.1),
+        axis.ticks.y = element_line(size=0.1),
+        axis.ticks.length = unit(1.1, "mm"),
+        panel.grid.major = element_line(size = 0.25, color="black", linetype="dashed"),
+        aspect.ratio = 1 / 2,
+        plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")
+  )
+}
+
+ggplotRegression <- function(fit){
+  require(ggplot2)
+  ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
+  geom_point() +
+  stat_smooth(method = "lm", col = "red", se= FALSE) +
+  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                     "Intercept =",signif(fit$coef[[1]],5 ),
+                     " Slope =",signif(fit$coef[[2]], 5),
+                     " P =",signif(summary(fit)$coef[2,4], 5)))
+}
 ```
+
 ```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
 
-####define who is the user and define path
-rm(list = ls())
-
-if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_AWIPEV-CO2/fb_awipev-co2_server/ny-alesund/data/NRT_data/"
-
-####Set environmental variables####
-Sys.setenv(TZ="UTC")
-if (!require("data.table")) install.packages("data.table")
 ##Provide in this section the parameters to be downloaded
@@
 #Use the following aggregation parameters
-agg_time = "MINUTE" #SECOND, MINUTE, HOUR, DAY, MONTH, YEAR
+agg_time = "HOUR" #SECOND, MINUTE, HOUR, DAY, MONTH, YEAR
 #Calculate the following statistical values. 
@@
 # Choose end date or take the date of today
-# end_date <- ymd_hms("2017-12-31 23:59:59")
-end_date <- ymd_hms(paste0(Sys.Date(), " 00:00:00 UTC"))
+ end_date <- ymd_hms("2019-12-31 23:59:59")
+#end_date <- ymd_hms(paste0(Sys.Date(), " 00:00:00 UTC"))
 enddate <- format(end_date,"%Y-%m-%dT%H:%M:%S")
@@
 # Choose start date
-start_date <- ymd_hms("2015-07-23 00:00:00")
+start_date <- ymd_hms("2012-01-01 00:00:00")
 startdate <- format(start_date, "%Y-%m-%dT%H:%M:%S")
@@
 
-if(agg_time=="MINUTE"){
+if(agg_time=="HOUR"){
   aggregate_string=paste0("&aggregate=",agg_time)
@@
 data <- data.table::fread(code, encoding = "UTF-8", showProgress    = TRUE)
-colnames(data) <- c("datetime", "Salinity", "Temperature" )
-data$datetime <- ymd_hms(data$datetime)
+data <- tibble(data) %>%
+  dplyr::rename(datetime = data$datetime,
+                sal = $sal)
+colnames(data) <- c("datetime", "sal", "temp" )
+#data$datetime <- ymd_hms(data$datetime)
 ```
+
+```{r average, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
+data <- data %>%
+  dplyr::mutate(hour = hour(data$datetime),
+                date = 
+                )
+
+data_hour <- data %>%
+  dplyr::group_by( date, hour) %>%
+  dplyr::summarise(Salinity_filtered = mean(Salinity_filtered, na.rm = TRUE),
+                   Temperature_filtered = mean(Temperature_filtered, na.rm = TRUE),
+                   Temp_SBE38_filtered= mean(Temp_SBE38_filtered, na.rm = TRUE),
+                   PCO2_Corr_filtered = mean(PCO2_Corr_filtered, na.rm = TRUE),
+                   PeriodDeplpCO2 = mean(PeriodDeplpCO2, na.rm = TRUE),
+                   PCO2_corr_contros_filtered= mean(PCO2_corr_contros_filtered, na.rm = TRUE),
+                   AT_filtered= mean(AT_filtered, na.rm = TRUE),
+                   HW_pH1_filtered= mean(HW_pH1_filtered, na.rm = TRUE),
+                   HW_Temperature1_filtered= mean(HW_Temperature1_filtered, na.rm = TRUE),
+                   T_seaF= mean(T_seaF, na.rm = TRUE),
+                   phINT_filtered= mean(phINT_filtered, na.rm = TRUE),
+                   phEXT_filtered= mean(phEXT_filtered, na.rm = TRUE),
+                   voltINT= mean(voltINT, na.rm = TRUE),
+                   voltEXT= mean(voltEXT, na.rm = TRUE),
+                   pco2_inst= mean(pco2_inst, na.rm = TRUE),
+                   ta_inst= mean(ta_inst, na.rm = TRUE),
+                   seafet_inst= mean(seafet_inst, na.rm = TRUE) ) %>%
+  dplyr::mutate(datetime = ymd_h(paste(date, hour, sep=" ", tz = "UTC"))) %>%
+  dplyr::ungroup() %>% # this is to be able to perform the following changes
+  dplyr::select(datetime, everything()) %>%
+  dplyr::select(-c( hour)) %>% # not needed in the shiny display
+  dplyr::arrange(desc(datetime))
+
+```
+
+```{r whole time series, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
+
+#SAL
+sal_xts <- dplyr::select(data, datetime, sal)
+  #dplyr::filter(sal_fb >28)
+sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
+dygraph(sal_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
+      dySeries("sal", color = "blue", strokeWidth = 0, label = "S") %>%
+      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
+      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+    dyLegend(show = "follow")   %>%
+    dyAxis("y",valueRange = c(30, 37)) %>%
+      dyRangeSelector(height = 30, dateWindow= NULL)
+
+# temp
+temp_xts <- dplyr::select(data, datetime, temp)
+temp_xts <- as.xts(temp_xts, order.by = temp_xts$datetime)
+dygraph(temp_xts, group = "awipev", main="Temperature", ylab="Temperature") %>%
+      dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "T") %>%
+      dyAxis("y", valueRange = c(-2.5, 10)) %>%
+      dyLegend(show = "follow")   %>%
+      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+      dyRangeSelector(height = 30, dateWindow= NULL)
+```

### 2020-03-09 awipev-CO2.Rmd

@@
 
+```{r TA 2nd cleaning , echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
+
+```
+
 ##### **First period**
@@
 ### **Corrected Contros vs calculated *p*CO~2~ data**
+
+```{r pCO2 2nd cleaning, echo=FALSE, warning=FALSE, message=FALSE}
+
+```
+
 ```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
@@
 
+### **seaFET data cleaning**
+
+```{r seaFET 2nd cleaning, echo=FALSE, message= FALSE, warning=FALSE, out.width= "60%"}
+
+```                
 ### **seaFET calibration constante E0**

### 2020-03-10 awipev-CO2.Rmd
rds rather than Rdata

--- 2020-02-24 awipev-CO2.Rmd
@@
 ```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
-load(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.Rdata"))
-#load(file = paste0(path, "fb_server/shinyroot/AWIPEV-CO2/nydata_hour_shiny.Rdata"))
-#load(file = "../fb_server/shinyroot/AWIPEV-CO2/nydata_shiny.Rdata") #d
+d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
 # load = d_hour
@@
 
-save(file= paste0(path, "fb_data/d_all.Rdata"), d_all)
+save(file= paste0(path, "fb_data/d_all.rds"), d_all)
 
@@
 
+```{r water masses, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
+# One tries to identify water masses coming from the Atlantic or freshwater
+
+```
 ## Temperatures
@@
 # Hence, here we save it for this use
-save(file= paste0(path, "fb_data/d_all.Rdata"), d_all)
+save(file= paste0(path, "fb_data/d_all.rds"), d_all)
 ```

### 2020-03-11 paper.Rmd
added paper.Rmd

--- 2020-03-10 awipev-CO2.Rmd
@@
 ---
-title: "Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project" 
-author: "Jean-Pierre Gattuso and Samir Alliouane"
+title: "Paper on the carbonate chemistry at Ny-Ålesund" 
+author: "Jean-Pierre Gattuso, Samir Alliouane and Philipp Fischer"
 date: '`r format(Sys.Date(), "%d %B %Y")`'
@@
 ---
-![ ](Images/AWIPEV-Logo.jpg){width=250px}
 
@@
 library(tidyverse)
-library(robfilter)
+#library(robfilter)
 library(seacarb)
 library(gridExtra)
-library(reshape2)
+#library(reshape2)
 library(lubridate)
-library(lmtest)
-library(grid)
+#library(lmtest)
+#library(grid)
 library(viridis)
-library(dygraphs)
+#library(dygraphs)
 require("knitr")
 library("lmodel2")
-library(captioner)
-library(xts)
-library(seismicRoll)
-library(scales)
+#library(captioner)
+#library(xts)
+#library(seismicRoll)
+#library(scales)
 knitr::opts_chunk$set(echo = TRUE)
 
-fig_nums <- captioner()
-table_nums <- captioner(prefix = "Table")
+#fig_nums <- captioner()
+#table_nums <- captioner(prefix = "Table")
 
@@
 ggplotRegression <- function(fit){
-
-require(ggplot2)
-
 ggplot(fit$model, aes_string(x = names(fit$model)[2], y = names(fit$model)[1])) + 
@@
   stat_smooth(method = "lm", col = "red", se= FALSE) +
-  labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                     "Intercept =",signif(fit$coef[[1]],5 ),
-                     " Slope =",signif(fit$coef[[2]], 5),
-                     " P =",signif(summary(fit)$coef[2,4], 5)))
+  labs(title = paste("Adj R2 = ", signif(summary(fit)$adj.r.squared, 5),
+                     "Intercept =", signif(fit$coef[[1]],5 ),
+                     " Slope =", signif(fit$coef[[2]], 5),
+                     " P =", signif(summary(fit)$coef[2,4], 5)))
 }

### 2020-03-11 awipev-CO2.Rmd
part on offset seaFET discarded for the moment

@@
 
-# #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb)
-#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
-seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-  dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
-    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
-
-  dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
-    dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
-    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
-  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
-  dyLegend(show = "auto")   %>%
-  dyAxis( "y2",valueRange = c(-3, 36))%>%
-  dyAxis( "y",valueRange = c(-2, 2))%>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-  dyRangeSelector(height = 30, dateWindow= NULL)
-# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
-
-# Offset between seafet pH and spec pH 
-sfoffset <- left_join(sfPeriod[,c(1,2)], d_all%>%dplyr::select(datetime, pHint_tot_sf), by="datetime")
-dat <- mutate(sfoffset, diff_pH_sf = round((pH_s_seafet_temp_field - pHint_tot_sf),digits  = 4))
-average_offset <- mean(abs(dat$diff_pH_sf), na.rm=TRUE)
-
-plot_offset <- ggplot(data = filter(dat, !is.na(diff_pH_sf))) +
-  geom_hline(yintercept=mean(dat$diff_pH_sf, na.rm = TRUE), size=0.3, linetype="dashed", col="red") +
-  geom_hline(yintercept=0, size=0.3) +
-  geom_point(aes(x = datetime, y = diff_pH_sf), size = 1, colour = "#51C56AFF") +
-  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
-  scale_x_datetime(date_breaks="month", date_minor_breaks="1 week", labels=date_format("%b %Y")) +
-  Mytheme() + theme(panel.grid.major.x = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1))
-
-print(plot_offset)
+# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
+# seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb)
+# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
+# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+#   dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
+#     dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
+#     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#   dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
+# 
+#   dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#   dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#     dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
+#   dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
+#   dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
+#     dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
+#   dyLegend(show = "auto")   %>%
+#   dyAxis( "y2",valueRange = c(-3, 36))%>%
+#   dyAxis( "y",valueRange = c(-2, 2))%>%
+#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+#   dyRangeSelector(height = 30, dateWindow= NULL)
+# # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
+
+# # Offset between seafet pH and spec pH 
+# sfoffset <- left_join(sfPeriod[,c(1,2)], d_all%>%dplyr::select(datetime, pHint_tot_sf), by="datetime")
+# dat <- mutate(sfoffset, diff_pH_sf = round((pH_s_seafet_temp_field - pHint_tot_sf),digits  = 4))
+# average_offset <- mean(abs(dat$diff_pH_sf), na.rm=TRUE)
+# 
+# plot_offset <- ggplot(data = filter(dat, !is.na(diff_pH_sf))) +
+#   geom_hline(yintercept=mean(dat$diff_pH_sf, na.rm = TRUE), size=0.3, linetype="dashed", col="red") +
+#   geom_hline(yintercept=0, size=0.3) +
+#   geom_point(aes(x = datetime, y = diff_pH_sf), size = 1, colour = "#51C56AFF") +
+#   labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
+#   scale_x_datetime(date_breaks="month", date_minor_breaks="1 week", labels=date_format("%b %Y")) +
+#   Mytheme() + theme(panel.grid.major.x = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1)) 
+# 
+# print(plot_offset)
 

### 2020-03-11 paper.Rmd
more figures in paper.Rmd

@@
 #library(seismicRoll)
-#library(scales)
+library(scales)
 knitr::opts_chunk$set(echo = TRUE)
@@
         panel.grid.major = element_line(size = 0.25, color="black", linetype="dashed"),
-        aspect.ratio = 1 / 2,
+        #aspect.ratio = 1 / 2,
         plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")
@@
 
-```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
-d <- read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
-#d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
-d$datetime <- dmy_hm(d$sampling_date, tz="UTC")
-d$measure_date <- dmy(d$measure_date, tz="UTC")
-
-# Add the flag location: some samples have been collected at the peer. Notes them here.
-# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
- # And keep data with flag 0 for FB location
-d <- d%>%
-  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00"|datetime == "2019-05-31 11:45:00", 1,0)
-  )
-d <- d%>%
-  dplyr::filter(location_flag== 0)
-
-# Keep only flag = 2 for at/ct analysis 
-# Keep only flag = 2 for pH durafet and seaFET.
-d <- d%>%
-  dplyr::mutate(ct= replace(ct, qflag_ct != 2, NA),
-                at= replace(at, qflag_at != 2, NA),
-                pH_s_seafet= replace(pH_s_seafet, qflag_pH_s_seafet != 2, NA),
-                pH_s_durafet= replace(pH_s_durafet, qflag_pH_s_durafet != 2, NA))
-
-# Mercury chloride correction (Dickson et al. 2007, SOP3a)
-# AT
-d$at <- d$at * 1.0002
-#CT
-d$ct <- d$ct * 1.0002
-
-# Fill "at/ct" to all line with same day.
-at_ct_mean <- d %>% 
-  group_by(datetime)%>%
-  dplyr::summarize(at_mean = mean(at, na.rm = T),
-                   ct_mean = mean(ct, na.rm = T),
-                   at_sd = sd(at, na.rm = T), 
-                   ct_sd = sd(ct, na.rm = T)
-                   )
-#at_ct_mean <- at_ct_mean%>%filter(!is.na(at_mean))
-#write.table(file= paste0(path, "fb_data/at_ct_mean.txt"), at_ct_mean)
-d <- left_join(d, at_ct_mean, by='datetime')
-# Fill the gaps in at_mean with interpolation
-TAinterp <-approx(d$datetime, d$at_mean, xout=d$datetime, method="linear", rule=2)
-names(TAinterp) <- c("datetime", "at_mean_interp")
-TAinterp <- as.data.frame(TAinterp)
-d$at_mean_interp <- TAinterp$at_mean_interp
-
-CTinterp <-approx(d$datetime, d$ct_mean, xout=d$datetime, method="linear", rule=2)
-names(CTinterp) <- c("datetime", "ct_mean_interp")
-CTinterp <- as.data.frame(CTinterp)
-d$ct_mean_interp <- CTinterp$ct_mean_interp
-
-# Conversion of spectro pH to a same T°
-pH_seafet <- d %>%
-  dplyr::filter(!is.na(pH_s_seafet))
-pH_seafet <- pH_seafet %>%
-  dplyr::mutate(pH_s_seafet_temp_field = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_field, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$salinity_field,Pt=0,Sit=0))
-
-pH_durafet <- d %>%
-  dplyr::filter(!is.na(pH_s_durafet))
-pH_durafet <- pH_durafet %>%
-  dplyr::mutate(pH_s_durafet_temp_field = pHinsi(pH=pH_durafet$pH_s_durafet,ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_field, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$salinity_field,Pt=0,Sit=0))
-
-# create separate seafet/durafet df to join to initial "d" df
-pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(datetime,pH_s_seafet_temp_field)%>% 
-  dplyr::group_by(datetime) %>% 
-  dplyr::summarize(pH_s_seafet_temp_field = mean(pH_s_seafet_temp_field, na.rm = T))
-pH_durafet_mean <- pH_durafet%>%
-  dplyr::select(datetime,pH_s_durafet_temp_field)%>% 
-  dplyr::group_by(datetime) %>% 
-  dplyr::summarize(pH_s_durafet_temp_field = mean(pH_s_durafet_temp_field, na.rm = T))
-
-#  make means in "d" to have same format and call it "discrete"
-discrete <- d %>% 
-  dplyr::group_by(datetime) %>% 
-  dplyr::summarize(sal = mean(salinity_field, na.rm = T),
-            temp = mean(temp_field, na.rm = T),
-            at_mean_interp = mean(at_mean_interp, na.rm = T),
-            at = mean(at, na.rm = T),
-            qflag_at = mean(qflag_at, na.rm = T),
-            ct_mean_interp = mean(ct_mean_interp, na.rm = T),
-            ct = mean(ct, na.rm = T),
-            qflag_ct = mean(qflag_ct, na.rm = T)
-            )
-# join discrete + seafet/durafet
-discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
-discrete <- left_join(discrete, pH_durafet_mean, by='datetime')
-
-##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
-##   *****Attention, I asked to the logisticians to log outside temp from 9 june 2019
-
-# discrete_steffen <- discrete[c(21:72),1:4]
-# write.table( discrete_steffen,"../fb_data/DiscreteTA_for_steffen.txt", sep= ",", dec=".", row.names = FALSE)
-
-carb <- carb(15, discrete$at*1e-6, discrete$ct*1e-6,S=discrete$sal, T=discrete$temp, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
-discrete$phcalc<- carb$pH
-discrete$pco2calc<- carb$pCO2
+```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
+d_all <- as_tibble(
+  readRDS(file = paste0(path, "fb_data/d_all.rds"))
+) %>%
+  filter(sal_fb > 28) # remove salinity data lower than 28
 ```
 
-```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
-d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
-# load = d_hour
-d_hour <- d_hour %>%
-  dplyr::select(-date) %>%
-  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
-         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
-         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
-         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
-         ) %>%
-  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=Salinity_filtered,temp_fb=Temperature_filtered)
+## Whole time series
+```{r whole time series, fig.width=10, fig.height=15, echo=FALSE, message= FALSE}
+size_point <- 1 # size of data points
+
+#SAL SBE45
+ts_sal <- d_all %>%
+  ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
+  labs(title="Salinity FerryBox? SBE45",x="", y="Salinity") +
+  #coord_fixed() +
+  Mytheme(size_labs = 8)
+
+# TEMP in situ SBE38
+ts_temp <- d_all %>%
+  ggplot(aes(x = datetime, y = temp_insitu), na.rm=TRUE) +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
+  labs(title="Temperature SBE38",x="", y="In situ temperature (°C)") +
+  #coord_fixed() +
+  Mytheme(size_labs = 8)
+
+# PCO2 
+ts_pCO2 <- d_all %>%
+  ggplot() +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(aes(x = datetime, y = pco2_contros), 
+             colour="black", na.rm=TRUE, size=size_point) + 
+  geom_point(aes(x = datetime, y = pco2calc), colour="blue", na.rm=TRUE, size=size_point) + 
+  labs(title="CO2 partial pressure",x="", y="pCO2 (uatm)") +
+  #coord_fixed() +
+  Mytheme(size_labs = 8)
+
+# SEAFET pH
+ts_pH <- d_all %>%
+  ggplot(aes(x = datetime, y = pHint_tot_sf), na.rm=TRUE) +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
+  labs(title="In situ pH",x="", y="pCO2 (uatm)") +
+  #coord_fixed() +
+  Mytheme(size_labs = 8)
+
+# TA
+ts_at <- d_all %>%
+  ggplot(aes(x = datetime, y = at_calc), na.rm=TRUE) +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
+  labs(title="Total alkalinity calculated from salinity", x="", y="AT (umol/kg)") +
+  #coord_fixed() +
+  Mytheme(size_labs = 8)
+
+g <- cowplot::plot_grid(ts_sal, ts_temp, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
+print(g)
 ```
 
-```{r Combine discrete and continous data, echo=FALSE}
-d_all <- d_hour #d_all will be the merger
-d_all<- d_all%>%
-  dplyr::mutate(month = month(month(datetime)))
-# at
-closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
-discrete$closest_datetime <- d_all$datetime[closest]
-# if the closest value is more than 30 min away, then we do not take it
-discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
-# remove the drop_na() because of seafet/durafet line with na
-discrete2merge <- discrete %>%
-  #drop_na() %>%
-  dplyr::select(closest_datetime, at, qflag_at) %>%
-    dplyr::filter(!is.na(closest_datetime)) %>%
-  rename(datetime=closest_datetime)
-d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-# ct
-# closest <- which.closest(discrete$datetime, d$datetime) # closest date and time
-# discrete$closest_datetime <- d$datetime[closest]
-# # if the closest value is more than 30 min away, then we do not take it
-# discrete$closest_datetime[abs(discrete$datetime - d$datetime[closest]) > 30*60] <- NA
-discrete2merge <- discrete %>%
-  #drop_na() %>%
-  dplyr::select(closest_datetime, ct, qflag_ct) %>%
-  dplyr::filter(!is.na(closest_datetime)) %>%
-  rename(datetime=closest_datetime)
-d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-# pH calculated
-# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
-# discrete$closest_datetime <- d_all$datetime[closest]
-# # if the closest value is more than 30 min away, then we do not take it
-# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
-discrete2merge <- discrete %>%
-  #drop_na() %>%
-  dplyr::select(closest_datetime, phcalc) %>%
-  dplyr::filter(!is.na(closest_datetime)) %>%
-  rename(datetime=closest_datetime)
-d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-# seaFET pH 
-# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
-# discrete$closest_datetime <- d_all$datetime[closest]
-# # if the closest value is more than 30 min away, then we do not take it
-# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
-discrete2merge <- discrete %>%
-  #drop_na() %>%
-  dplyr::select(closest_datetime, pH_s_seafet_temp_field) %>%
-  dplyr::filter(!is.na(closest_datetime)) %>%
-  rename(datetime=closest_datetime)
-d_all <- full_join(d_all, discrete2merge, by="datetime")
-# #voltINT
-# discrete2merge <- discrete %>%
-#   #drop_na() %>%
-#   dplyr::select(closest_datetime, voltINT) %>%
-#   rename(datetime=closest_datetime)
-# d_all <- full_join(d_all, discrete2merge, by="datetime")
-# #voltEXT
-# discrete2merge <- discrete %>%
-#   #drop_na() %>%
-#   dplyr::select(closest_datetime, voltEXT) %>%
-#   rename(datetime=closest_datetime)
-# d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-# duraFET pH 
-# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
-# discrete$closest_datetime <- d_all$datetime[closest]
-# # if the closest value is more than 30 min away, then we do not take it
-# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
-discrete2merge <- discrete %>%
-  #drop_na() %>%
-  dplyr::select(closest_datetime, pH_s_durafet_temp_field) %>%
-  dplyr::filter(!is.na(closest_datetime)) %>%
-  rename(datetime=closest_datetime)
-d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-# pCO2
-# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
-# discrete$closest_datetime <- d_all$datetime[closest]
-# # if the closest value is more than 30 min away, then we do not take it
-# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
-discrete2merge <- discrete %>%
-  #drop_na() %>%
-  dplyr::select(closest_datetime, pco2calc) %>%
-  dplyr::filter(!is.na(closest_datetime)) %>%
-  rename(datetime=closest_datetime)
-d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-save(file= paste0(path, "fb_data/d_all.rds"), d_all)
-
-## bind the voltages and deployment ##
-
-# Duplicate datetime in closest_datetime to do the left_join
-d_all$closest_datetime <- d_all$datetime
-discrete <- left_join(discrete, d_all%>%dplyr::select(c(closest_datetime, voltEXT, voltINT)), by="closest_datetime")
-```
-
-<style type="text/css">
-
-body{ /* Normal  */
-      font-size: 18px;
-  }
-h3{ /* Header 3 */
-  font-size: 22px;
-  <!-- font-family: "Times New Roman", Times, serif; -->
-  color: DarkBlue;
-}
-h4{ /* Header 4 */
-  font-size: 18px;
-  <!-- font-family: "Times New Roman", Times, serif; -->
-  color: DarkBlue;
-}
-h5{ /* Header 5 */
-  font-size: 16px;
-  <!-- font-family: "Times New Roman", Times, serif; -->
-  color: DarkBlue;
-}
-</style>
-
-# {.tabset .tabset-fade .tabset-pills}
-
-## Infos
-
-### **Introduction**
-<div style="text-align: justify">  
-The AWIPEV-CO2 project aims at starting the first time series for the carbonate chemistry in the Arctic Ocean as part of the AWIPEV Underwater Observatory.
-It comprises two components: (1) continuous real-time measurements and (2) discrete measurements.
-The rationale is that discrete measurements are absolutely needed to calibrate and validate the sensors.
-
-### **AWIPEV Underwater Observatory**
-<div style="text-align: justify">  
-The AWIPEV Underwater Observatory has been deployed at Ny-Alesund (Spitsbergen, 78°55'18N, 11°56'31E) in June 2012.
-It is part of the German Project COSYNA (Coastal Observation Systems of the Northern- and Arctic Seas), which aims at increasing the availability of continuous real-time data from remote but climatically-sensitive ecosystems.
-The AWIPEV underwater observatory comprises a fully remote controlled FerryBox system fed with seawater pumped in front of the old peer at 12 m depth.
-Temperature, salinity, pressure, turbidity, oxygen, chl-*a* fluorescence are measured.
-Furthermore, an additional remote controlled underwater sensor unit able to profile from 12 m to the surface at any frequency carries additional sensors for salinity, pressure, turbidity, oxygen chl-*a* fluorescence and PAR.
-The system also comprises an ADCP for continuous measurements of currents and waves.
-Besides these standard sensors, the underwater unit is equipped with a webcam and stereo-optical device to remotely assess fish and jellyfish populations.
-The AWIPEV observatory is specifically designed for polar experimental work under extreme conditions including ice coverage and the inaccessibility for about 7 months during polar winter.
-During this time, the system is remotely controlled and maintained from Germany.
-All data sampled by the sensors are continuously sent to a central server system at Helgoland Island where the data are stored and processed.
-The processed data are open access and available at http://codm.hzg.de/codm.
-
-<div style="text-align:center" markdown="1">
-  <img  src="./Images/Container.png" width="200" height="200">
-  <img  src="./Images/Intake.png" width="200" height="200">
-  <img  src="./Images/2018-04-17_Ferrybox2.jpg" width="200" height="200">
-</div>
-
-### **Continuous and semi-continuous measurements**
-<div style="text-align: justify">  
-The Arctic version of the Contros-Kongsberg HydroC CO~2~ FT (Carbon Dioxyde partial pressure Flow Through surface water sensor) has been installed in July 2015.
-Molecules of dissolved CO~2~ diffuse through a thin composite membrane into the internal gas circuit leading to a detector chamber, where the partial pressure of CO~2~ is determined by means of infra-red absorption spectrometry.
-Concentration-dependent IR light is converted into the output signal from calibration coefficients stored in firmware and data from additional sensors within the gas circuit.
-The measuring range is 200-1000 uatm, resolution is < 1 uatm and accuracy is +- 1% reading.
-The sensor is the first instrument in the measuring loop; data are logged every minute.
-This instrument requires yearly factory calibration; two sensors ara available to allow a continuous time series.
-
-Since February 2016, total alkalinity (AT) is measured every 90 min with a Contros-Kongsberg HydroFIA TA (Total Alkalinity analyser flow through system).
-Fifty ml of seawater is filtered (0.2 um) using a Contros-Kongsberg cross-flow filter and then acidified using dilute hydrochloric acid (0.1 N).
-CO~2~ is then flushed out (open-cell titration) and the final pH measured by means of an indicator dye (bromocresol green) and visible absorption spectrometry.
-Together with salinity and temperature at the time of measurement, the pH reading is used to calculate AT.
-According to the manufacturer, the measuring range is 400 umol/kg dynamic range, resolution 0.1 umol/kg, accuracy 25 umol/kg (+- 1%) and precision 5 umol/kg (+- 0.2%).
-
-In August 2017, a seaFET Ocean pH sensor (Sea-Bird Scientific) has been added to the UWO.
-This new sensor continuously measures pH at 11 m using an ISFET (Ion Sensitive Field Effect Transistor).
-According to the manufacturer, the measuring range is between 6.5 and 9 pH units, initial accuracy is 0.02 pH units and precision is 0.004 pH units.
-Operating salinity and temperature range are 20 to 40 PSU and 0 to 50°C respectively.
-
-In August 2017, a Durafet III pH electrode connected to a UDA2128 Analyser (Honeywell) was also implemented to the Ferrybox flow-through system.
-This electrode continuously measures pH, in the Ferrybox, through an ISFET.
-According to the manufacturer, the measuring range is between 0 and 14 pH units.
-
-### **Data availability**
-TO DO: add here an horizontal bar plot showing the percent availability of the data
-
-## Whole time series
-```{r whole time series, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-#SAL
-sal_fb_xts <- dplyr::select(d_all, datetime, sal_fb)%>%
-  dplyr::filter(sal_fb >28)
-sal_fb_xts <- as.xts(sal_fb_xts, order.by = sal_fb_xts$datetime)
-dygraph(sal_fb_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
-      dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "S") %>%
-      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
-      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-    dyLegend(show = "follow")   %>%
-    dyAxis("y",valueRange = c(30, 37)) %>%
-      dyRangeSelector(height = 30, dateWindow= NULL)
-# TEMP Ferrybox SBE45
-temp_fb_xts <- dplyr::select(d_all, datetime, temp_fb)
-temp_fb_xts <- as.xts(temp_fb_xts, order.by = temp_fb_xts$datetime)
-dygraph(temp_fb_xts, group = "awipev", main="Temperature (in Ferrybox)", ylab="Temperature") %>%
-      dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "T") %>%
-      dyAxis("y", valueRange = c(-2.5, 10)) %>%
-      dyLegend(show = "follow")   %>%
-      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-      dyRangeSelector(height = 30, dateWindow= NULL)
-# TEMP insitu SBE38
-temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu)
-temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
-dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ)", ylab="Temperature") %>%
-      dySeries("temp_insitu", color = "blue", strokeWidth = 0, label = "T") %>%
-      dyAxis("y", valueRange = c(-2.8, 10)) %>%
-      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-      dyLegend(show = "follow")   %>%
-      dyRangeSelector(height = 30, dateWindow= NULL)
-# PCO2 
-#+ Ajout de la pCO2 corrigé par le script contros (dans R server ny-alesund_cc.R)
-pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_contros, PCO2_Corr_filtered)
-pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
-dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
-    dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
-      dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
-    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
-    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2019-09-03 15:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
-    #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
-    dyLegend(show = "follow")   %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-# DURAFET 
-durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field)
-durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
-dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
-    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyAxis("y",valueRange = c(8, 8.8)) %>%
-    dyLegend(show = "follow")   %>%
-    dyRangeSelector(height = 30, dateWindow= NULL) 
-# SEAFET 
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field)
-seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
-  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyAxis("y",valueRange = c(7.45, 8.8)) %>%
-    dyLegend(show = "follow")   %>%
-    dyRangeSelector(height = 30, dateWindow= NULL) 
-# TA
-# to create periods according to TA deployments
-TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00", 
-              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00", "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
-
-at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at)
-at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
-dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
-   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
-  #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
-  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
-  dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
-  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
-  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
-  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
-  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-  dyAxis("y",valueRange = c(2000, 2650)) %>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions( strokeWidth= 0) %>%
-  dyLegend(show = "follow")   %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-f <- as.data.frame(table(d_all$at))
-#sum(f$Freq)  
-# Number of outliers removed in the dataset
-# numberOutliers <- length(which((dat_ATnoNA$outliers > 0)))
-
-# #plot for POSTER june 2019
-# #plot of S/T
-# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
-#   geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
-#   labs(x = "Time", y="Temperature (°C)") +
-#   scale_x_datetime(date_minor_breaks ="1 month")+
-#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
-#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
-# print(poster_temp)
-# #
-# png("figures/poster_sal_temp.png", width= 1100, height=600)
-# par(mar=c(5, 4, 4, 6) + 0.1)
-# #
-# plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
-# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
-# #
-#    grid(lty=1)
-# #
-#    par(new = T)
-# #
-# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
-# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
-# mtext("",side=1,col="black",line=1.5, cex=1.8)
-# legend("topleft", legend=c("Temperature (°C)", "Salinity"),
-#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
-#   grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
-#     lwd = "months")
-#      box()
-#      dev.off()
-# 
-# 
-# ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
-# #
-# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
-#   geom_point(col="blue", size=0.5 )+
-#   labs(x = "Time", y="Salinity (PSU)") +
-#   scale_x_datetime(date_minor_breaks ="1 month")+
-#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
-# print(poster_sal)
-# ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")
+```{r water masses, fig.width=15, fig.height=15, echo=FALSE, message= FALSE}
+# One tries to identify water masses coming from the Atlantic or freshwater
+temp_sal <- d_all %>%
+  ggplot(aes(x = sal_fb, y = temp_insitu), na.rm=TRUE) +
+  #scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
+  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
+  labs(title="Temperature vs salinity SBE45",x="Salinity", y="Temp. (°C)") +
+  coord_fixed() +
+  Mytheme(size_labs = 8) #+
+  #theme(axis.text.x=element_blank())
+#  +annotation_custom(grob_A)
+print(temp_sal)
 
 ```
-
-```{r water masses, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-# One tries to identify water masses coming from the Atlantic or freshwater
-
-```
-## Temperatures
-Several temperature sensors are on site, 1 inside the Ferrybox and 2 outside:
-
-- 1 SBE45 inside the Ferrybox (temp_fb)
-- 1 seaFET T°C inside the seaFET at 11 meters depth (T_seaF)
-- 1 SBE38 at 11 meters depth (temp_insitu)
-
-Comparative approch allowed by following plots:
-
-### **T seaFET / T in situ **
-```{r Temp comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-# seaF outliers (T - volt int - volt ext) to remove from 2017-12-10 to 2017-12-14
-d_all <- d_all %>%
-  dplyr::mutate(T_seaF = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, T_seaF),
-                voltINT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltINT), 
-                voltEXT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltEXT))
-
-fit <- lmodel2(data = d_all,  T_seaF ~ temp_insitu , nperm = 99)
-
-pTseaf_Tinsi<-  ggplot(d_all,aes(x=temp_insitu, y= T_seaF, label = month))+
-  geom_text( aes(color=factor(month))) + 
- # scale_color_viridis_d(option = "C", guide="none")+
-  geom_line(aes(x = T_seaF, y = T_seaF), linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("T seaF vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
-  labs( x="T insi", y="T seaF ", color = "Months")  +theme_bw()
-print(pTseaf_Tinsi)
-
-d_all$diff_T_seaF_insitu <- d_all$T_seaF - d_all$temp_insitu
-mean_diff_T_seaF_insitu <- round(mean(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)
-sd_diff_T_seaF_insitu <- round(sd(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)
-
-```
-
-The mean difference between T seaFET and in situ is: `r mean_diff_T_seaF_insitu` ± `r sd_diff_T_seaF_insitu`°C.
-
-### **T Ferrybox / T in situ **
-```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-# Remove temp_fb outliers 
-d_all <- d_all %>%
-  dplyr::mutate(temp_fb = ifelse(datetime >= "2017-03-22 08:00:00" & datetime <= "2017-03-23 16:00:00", NA, temp_fb),
-                temp_fb = ifelse(temp_fb >15, NA, temp_fb))
-
-fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu , nperm = 99)
-
-pTfb_Tinsi<-  ggplot(d_all,aes(x=temp_insitu, y= temp_fb, label = month))+
-  geom_text( aes(color=factor(month))) + 
- # scale_color_viridis_d(option = "C", guide="none")+
-  geom_line(aes(x = temp_fb, y = temp_fb), linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("T FB vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
-  labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
-print(pTfb_Tinsi)
-
-d_all$diff_T_fb_insitu <- d_all$T_seaF - d_all$temp_insitu
-mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
-sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
-```
-
-The mean difference between T seaFET and in situ is: `r mean_diff_T_fb_insitu` ± `r sd_diff_T_fb_insitu`°C.
-
-## Total alkalinity
-
-Since we bought the AT analyser (February 2016), numerous problems happened due to a leak of the degassing unit in each analyser and sudden step changes.
-Last analyser repaired by Contros was installed back in the FB on 2018-07-31.
-This was the 3rd analyser on site.
-
-We identify four periods (see plot at the end of this page with dark and ligth grey):
-
-- from the set-up of the instrument on **2016-02-23** to **2017-02-09** during which we try to correct for the drift
-- from **2017-02-09** to **2017-03-10** during which no drift correction is made, just an offset is applied to correct for the sudden shift in the data
-- from the set-up of a new instrument on **2018-01-08** to **2018-06-20**, during which another correction using the discrete samples will be performed.
-In this period and before to stop it, continuous leakages in the degasing unit happened.
-- from the set-up of a repaired unit on **2018-07-31** to **2018-10-31**.
-Here, the instrument took wrong salinity to perform AT measurements.
-The cause is not clear yet but Steffen sent to Samir a protocol on 2018-08-24 to correct those data with right salinity.
-Also, after this issue, since 2018-08-20, bad data were still measured.
-Steffen diagnosed a "bubble issue" in the indicator tubbings.
-Steps will be sent to Marine to solve this issue.
-After this, it was not a bubble.
-We decided to switch off the instrument to save reagents and wait until the comming of Steffen in NYA with a new instrument.
-
-A new instrument was installed with Steffen on **2018-10-31**.
-This new instrument has a complete new designed membrane which will solve the problem.
-Steffen also developped a TA web interface to communicate remotly with the analyser.
-Samir has all the passwords and ID to connect.
-
-The instrument is usually calibrated against CRM standards after deployment, CRMs are run after 3 months as samples (measurement mode, not calibration mode), an then immediately calibrated again.
-This procedure is repeated every 3 months.
-
-### **Filtration of AT data: outliers removing**
-
-Outliers are present because of the cleaning operations made on the FerryBox everydays at 12:00am and 12:00pm.
-We first removed the outliers using a filter and decided, after a Skype conference with Steffen on September 2016, to:
-
-  - Remove existing filters ( > 2350 µmol/kg).
-  - Filter using salinity flag.
-  - Filter using pH flag.
-  - Not to filter on temperature flag.
-  - Apply a 3 data points median filter (no longer used; see despike function in "oce" package)
-
-We decided to use "despike" function as data filter.
-This filter is done in "ny-alesund_cc.R".
-Length of runing median is: k = 121 days and the indicator (n times the sd between x and the reference) to consider a data from an outlier is: n = 0.5.
-
-### **Correction of AT data**
-
-Calibration was initially performed twice a year since the analyser was supposed to be stable.
-Calibration was performed using the internal "calibration mode" against a CRM from A.Dickson (Batch #145, 2016-02-24) right after the instrument was installed and a second time on 2016-09-16.
-This approch is not longer used since September 2016 (Skype with Contros).
-
-Since this date, the analyser is calibrated by measuring a CRM with the "measurement mode" in order to measure the offset of the instrument.
-Additionally, discrete seawater are sampled weekly and TA is analysed by SNAPO-CO2.
-
-  - Two methods to correct the drift are available:
-    - based on CRMs 
-    - based on AT measurement of discrete samples ("references").
-
-#### **Calibration**
-
-- **2019-01-29 14:10**: Calibration started by Philipp Fisher using CRM 145 (2226.16 umol/kg, 33.572).
-The three previous measurements were 2314.5, 233.8, 2313.7 (analyser stable) and the six subsequent measurements were 2211.8, 2277.5, 2305.4, 2316.6, 2317.9.
-Error was done with CRM salinity (Analyser was not unplugged from the FB).
-Steffen's response:
-> Hence, the serial connection should be cut off or the FB module feeding the analyzer with salinity data should be stopped during calibration.
-The calibration can be recalculated afterwards in the data post-processing.
-However, I see that the calibration resulted in very similar pH values 3.540 (September calibration) and 3.543 (January calibration) with very similar correction factors 1.2371 and 1.2365.
-Also the TA values are very similar to the baseline measurements from before at approx.
-2316 µM.
-So for now, it should be fine.
-
-#### **CRM measurements**
-
-The calibration of the sensor is made against a CRM standard from A.
-Dickson.
-We run a standard on the analyser as a regular measurement (measurement mode).
-Result sof calibrations are shown on the following plot.Dashed lines represent the theoritical value of AT (CRM) and hard lines represent CRM measured AT by the instrument.
-
-```{r CRM measurements, echo=FALSE, warning=FALSE, message=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-calib_analyser <-  read.table(paste0(path, "fb_data/Calibration_TA/TA_#1215/measure_CRM_TA.txt"), header = T, dec = ".", as.is = T, sep = ",", fill = TRUE)
-
-# To make the mean 
-# Keep dates as Character to plot without date gaps.
-calib_analyser3 <- calib_analyser %>%
-  dplyr::filter(analyser == "TA3") 
-meanTA3 <- calib_analyser3 %>% 
-  group_by(day) %>% 
-  summarise (meanTA = mean(TA))
-
-melt_calib <- melt(calib_analyser, id.vars=c("analyser", "TA_theo", "datetime", "CRM"), measure.vars=c("TA"))
-calib_p <- ggplot()+ 
-          geom_point(data= melt_calib, aes(x=datetime, y=value, color=factor(CRM), shape= factor(analyser)) , size=3) +
-          scale_color_manual(values=c("blue","red"))+
-         # set dashed lines for theoritical CRM
-          geom_segment(aes(x=1,xend=20,y=2226.16,yend=2226.16), linetype="dashed", color="blue")+
-          annotate("text", x = 11, y = 2228, label = "Batch #145 = 2226.16", color="blue")+
-          geom_segment(aes(x=20,xend=23,y=2213.59,yend=2213.59), linetype="dashed", color="red")+
-          annotate("text", x = 15.5, y = 2213.59, label = "Batch #159 = 2213.59", color="red")+
-        # set hard lines for measured CRM
-          geom_segment(aes(x=1,xend=5,y=2254,yend=2254), color="blue") +
-          annotate("text", x = 3, y = 2249, label = "2254", color="blue")+
-          geom_segment(aes(x=6,xend=10,y=2251.6,yend=2251.6), color="blue") +
-          annotate("text", x = 8, y = 2247, label = "2251.6", color="blue")+
-          geom_segment(aes(x=11,xend=15,y=2190.4,yend=2190.4), color="blue")+
-          annotate("text", x = 14, y = 2195, label = "2190.4", color="blue")+
-          geom_segment(aes(x=16,xend=20,y=2203.5,yend=2203.5), color="blue")+
-          annotate("text", x = 18, y = 2200, label = "2203.5", color="blue")+
-          geom_segment(aes(x=21,xend=23,y=2224.20,yend=2224.20), color="red")+
-          annotate("text", x = 22, y = 2230, label = "2224.2", color="red") +
-  theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1))+ 
-  labs(title= "",y=expression(paste("Total alkalinity (µmoles.",kg^-1,")")), x="Date", color= "CRM",shape= "Deployed instrument")
-
-ggsave("figures/TA_calibration_CRM.png", calib_p, units="cm")
-print(calib_p)
-```
-
-#### **Discrete samples ("references")**
-
-On 2018-04-19, Steffen sent his answer concerning the drift correction during the period February 2016 to March 2017.
-Within this one year period, the analyser was running, except the first week of May 2016.
-Discrete samples were collected and 3 CRMs were measured which was deemed not enough (see below).
-He suggested to base the correction on the AT of discrete ("reference") samples.
-
-> "I chose the discrete reference samples due to the fact that those cover the entire working range including time, salinity and also provide a broader data basis for this kind of correction.
-Also, when looking at the uncertainty below, I fear that the three CRM measurements over 5 month are not sufficient enough for such a drift determination."
-
-A linear regression was performed based on the difference between the measured (analyzer) and discrete samples.
-Discrete samples were matched with the AT measured by the analyser.
-If there is no measurement coincident with a discrete sample, a linear interpolation was made between the two data surrounding the discrete sample data.
-The differences between the measured (analyzer) and analysed ("reference") data was plotted as a function of time.
-
-This approach was performed:
-
-  - on the same period than in Steffen email's (**First period**, 2016-02-23 to 2017-02-09)
-  - and during the **third period**, with the new analyzer (2018-01-07 to 2018-06-20)
-
-##### **First period**
-
-```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
-#Interpolation of continuous sensor data to match a maximum of reference data.
-TAinterp_all <-approx(d_all$datetime, d_all$AT_filtered, xout=d_all$datetime, method="linear", rule=2)
-names(TAinterp_all) <- c("datetime", "AT_filtered_interp")
-TAinterp_all <- as.data.frame(TAinterp_all)
-d_all$AT_filtered_interp <- TAinterp_all$AT_filtered_interp
-
-# create a column with difference between sensor and ref
-d_all <- d_all%>%
-  dplyr::mutate(diff_ta =  at-AT_filtered_interp )
-# create colum with instrument number
-d_all <- d_all %>%
-  dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
-                            ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
-                            ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3",
-                            ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4",
-                            ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
-                            ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))
-
-#remove outliers
-calib_ta_first <- d_all%>%
-  dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta,TA_period)%>%
-  dplyr::filter(TA_period =="TA1" & !is.na(at))
-  #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
-# & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))
-
-# Parameters of regression
-fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime)
-at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6)
-at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2)
-at_intercept1 <- round(fit$coefficients[[1]], digits= 2)
-```
-
-The slope is: `r #at_slope_TA1` x 3600 x 24 x 365.24 = `r #at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red.
-
-```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
- # Plot of regression
- p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) +
-     geom_point() + geom_smooth(method='lm', se=FALSE)+
-     geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
-   geom_hline(yintercept = 0, linetype="dashed" )+
-   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                      "Intercept =",signif(fit$coef[[1]],5 ),
-                      "Slope =",signif(fit$coef[[2]], 5),
-                      "P =",signif(summary(fit)$coef[2,4], 5))) +
-   ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
- print(p)
- ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
-```
-
-##### **Third period**
-
-```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"}
-
- #remove outliers and remove period without TA measurements
- calib_ta_third <- d_all%>%
-   dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
-   dplyr::filter(TA_period == "TA3" & !is.na(at))
-
- # Parameters of regression
- fit <- lm( data=calib_ta_third, diff_ta ~ datetime)
- at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8)
- at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2)
- at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici.
-```
-
-The slope is in days: `r #at_slope_TA3` x 3600 x 24 x 365.24 = `r #at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.
-
-```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
-# # Plot of regression
- p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+
-     geom_point() + geom_smooth(method='lm', se=FALSE)+
-     #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
-    geom_hline(yintercept = 0, linetype="dashed" )+
-   geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
-   #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
-   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                      "Intercept =",signif(fit$coef[[1]],5 ),
-                      " Slope =",signif(fit$coef[[2]], 5),
-                      " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") +
-   scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
- print(p)
- ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
-```
-
-##### **Second period**
-
-```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
-
-#remove outliers and remove period without TA measurements
-calib_ta_second <- d_all%>%
-  dplyr::select(datetime, closest_datetime, AT_filtered, AT_filtered_interp, at, diff_ta, TA_period)%>%
-  dplyr::filter(TA_period == "TA2" & !is.na(at))
-
-mean_offset <- mean(calib_ta_second$diff_ta)
-
-```
-
-For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r #mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
-
-#### **Final TA corrected data (Regression)**
-
-The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition.
-It is clear that these corrected data (in green) cannot be used for periods 1 to 3. The jury is still out for period 4. The issue of salinity must be clarified before an assessment can be made.
-
-```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
-# Correction for the 3 periods is apply
-d_all <- d_all%>%
-  dplyr::mutate(datetime_reg = as.numeric(datetime),
-                at_intercept = ifelse(TA_period == "TA1", at_intercept1,
-                               ifelse(TA_period == "TA3", at_intercept3, NA)),
-                at_slope = ifelse(TA_period == "TA1", at_slope_TA1,
-                           ifelse(TA_period == "TA3", at_slope_TA3, NA))
-                )
-
-d_all <- d_all%>%
- dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT_filtered + (d_all$datetime_reg * d_all$at_slope + at_intercept)),
-                                        ifelse(TA_period == "TA2", (AT_filtered + mean_offset),
-                                        ifelse(TA_period == "TA3", (AT_filtered + (datetime_reg * at_slope)+ at_intercept), NA))))
-
-at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at,TA_reg_corrected)
-at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
-dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
-   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
-  dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
-  dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
-  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
-  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
-  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
-  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
-  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-  dyAxis("y",valueRange = c(1600, 2650)) %>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions( strokeWidth= 0) %>%
-  dyLegend(show = "follow")   %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-```
-
-### **Discrete total alkalinity (reference) vs salinity relationship**
-
-In the previous part, missing TA were interpolated with a linear model.
-This does not reflect the natural variability of TA.
-For this reason, missing TA is now calculated from salinity data by making a relationship between the same reference TA samples as in the previous part and salinity data.
-
-```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
-d_all_at_discrete <- d_all %>% #  To remove an outlier in red
-  dplyr::select(datetime, month,closest_datetime, at, sal_fb)%>%
-  dplyr::filter( !is.na(at) & !is.na(sal_fb) & sal_fb >30)
-
-  #at != "2307.05" & sal_fb > 28, !is.na(at))
-
-# d_all_Out <- d_all %>% #  To keep an outlier in red
-#   filter(at == "2307.05")
-
-#fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal_fb)
-fit <- lm(data = d_all_at_discrete, at ~ sal_fb)
-slope_s_at <- fit$coefficients[[2]]
-intercept_s_at <- fit$coefficients[[1]]
-# at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()
-
-at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
-  geom_text( aes(color=factor(month))) +
-  scale_color_discrete(guide="none")+
-    labs(x="Salinity", y="Discrete AT", color = "Months")  +
-    stat_smooth(method = "lm", col = "black") +
-    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
-                       ";\nSlope =",signif(fit$coef[[2]], 5),
-                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
-  theme_bw() +
-  theme(aspect.ratio=1,
-        axis.text=element_text(size=15),
-        axis.title.y= element_text(size =15),
-        axis.title.x= element_text(size =15),
-        plot.margin = unit(c(0.5,1,1,1), "cm"),
-        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70)))
-  #print(at_s)
-
-ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")
-
-# Salinity is a predictor of AT -> using the regression defined above
-d_all$at_calc <- slope_s_at * d_all$sal_fb + intercept_s_at
-```
-
-The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r #round(summary(fit)$r.squared, digits=2)`.
-Need to compare with other relationships from the literature.
-
-```{r plot Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%", fig.align="center"}
- # PLOT
- print(at_s)
-```
-
-#### **Final TA re-calculated data (Salinity relationship)**
-
-```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
-at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
-at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
-dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
-  dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
-  dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
-  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
-  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
-  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
-  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
-  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-  dyAxis("y",valueRange = c(2000, 2650)) %>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions( strokeWidth= 0) %>%
-  dyLegend(show = "follow")   %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-# #plot for POSTER june 2019
-# #plot of TA calculated from S + discrete
-# p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
-#   geom_point(col="blue", size=0.5 )+
-#   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
-#   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
-#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-#   theme(legend.position= c(0.5, 0.93),
-#                      legend.text=element_text(size=15),
-#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
-#                      axis.text=element_text(size=15),
-#                      axis.title.x= element_text(size =15),
-#                      legend.title=element_blank())
-#
-#
-# print(p_at_sal)
-# ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
-
-```
-
-There are a lot of outliers in the 4th period (since the new analyzer was set up in Nov. 2018). We use the desplike function to remove them.
-
-#### **TA since November 2018 (final installation)**
-```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
- # select subset of data and remove obvious outliers
- at_nov_2018 <-
-  dplyr::select(d_all, datetime, at_calc, AT_filtered, at) %>%
-  filter(datetime > "2018-11-01", AT_filtered > 2250)
-#despike
-at_nov_2018 <- mutate(at_nov_2018, AT_filtered_despike = despike(AT_filtered, reference= "median", n=0.5, k=10, replace="NA"))
-#plot
-at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) +
-  geom_point(aes(y=AT_filtered, colour = "before"), size =3) +
-  geom_point(aes(y=AT_filtered_despike, colour = "after"), size = 2) +
-  labs(x = "Time", y = "Total alkalinity", color = "despike")
-print(at_datetime)
-
-at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_filtered_despike != "NA")
-titre <- "Contros AT vs Calculated AT"
-fit <- lmodel2(data = at_nov_2018_no_NA, AT_filtered_despike ~ at_calc, nperm = 99)
-ggreg2(fit, x = "at_calc", y = "AT_filtered_despike")
-
-```
-
-## *p*CO~2~
-The HydroC CO~2~ FT sensor (S/N: CO2FT-0215-001) was bought from Contros (Germany) in February 2015.
-It was deployed in the FerryBox with other sensors since July 2015, the 20th.
-A spare sensor (S/N: CO2FT-0515-001) was also bought in March 2015 and carried to Ny-Alesund to replace the first one in case of calibration or problem.
-Both sensors were set on a cycle according to informations given by Contros in March 2015 (c.kirbach@contros.eu):
-
-30 min warm up --> (3 min Zeroing + 15 min Flushing + 702 minutes Measuring) --> (3 + 15 + 702)...
-
-  - **Warm-up**: running without sending data. Done once, after the sensor is turned on. Time can vary depending on T water and power supply.
-  - **Flushing**: running normally.
-Phase of equilibration that depends on the sensor configuration and the environment conditions.
-Warmer the water is and larger the flow is in front of the membrane, faster will be the response time and shorter will be the flush time.
-Recovery data of the sensor signal from the zeroing interval happen in this time.
-During this step the flush flag is set to “1” for simplifier extraction of the flush values.
-  - **Measuring**: running normally and all other flags are on “0”. Sensor is fully equilibrated and T is stable.
-
-During those steps (except zeroing) the sensor runs normally.
-Equilibration between the gas inside the sensor and the dissolved gas in ambient water takes place.
-Gas is led to NDIR unit while T control is running.
-
-### **Corrected Contros vs calculated *p*CO~2~ data**
-```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
-title <- "Contros vs calculated pCO2"
-fit <- lmodel2(data = d_all,  pco2_contros ~ pco2calc , nperm = 99)
-
-pco2calc_pCO2_contros_text <-  ggplot(d_all,aes(x=pco2calc, y= pco2_contros, label = month))+
-   geom_text(aes(color = factor(month)))+
-  scale_color_discrete(guide="none")+
-  geom_line(aes(x = pco2_contros, y = pco2_contros), linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
-  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()
-
-```
-The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
-```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-print(pco2calc_pCO2_contros_text)
-ggsave(paste0("figures/pco2calc_pCO2_contros.png"), pco2calc_pCO2_contros_text, units="cm")
-```
-
-### **Final *p*CO~2~ data**
-
-```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_contros, PCO2_Corr_filtered)
-pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
-dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
-  dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
-    dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
-    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
-    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2019-09-03 15:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>%
-
-    #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyLegend(show = "follow")   %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-# #plot for POSTER june 2019
-# #plot of pCO2
-# 
-# #  add pCO2 atmospheric data from URL
-# 
-# noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
-# noaa <- noaa %>%
-#   dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
-#   unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
-#   unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
-#   unite("datetime", c("date", "time"), sep=" ")
-# 
-# noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
-# noaa <- noaa %>%
-#  dplyr::filter(datetime > "2015-07-01 00:00:00")
-# 
-# #create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
-# lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
-#           expression(paste(italic(p),CO[2]," (ppm; from NOAA)")),
-#            "Calculated from AT/CT"
-# 
-#           )
-# 
-# col <- c("blue","black","red")
-# 
-# poster_pco2 <- ggplot( ) +
-#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
-#   geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
-#   geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+
-#   scale_shape_discrete(labels=lab, guide="none")+
-#   scale_colour_manual(labels=lab, values=col)+
-#   labs(x = "", y ="", title = "") +
-#   theme_bw() +
-#   scale_x_datetime(minor_breaks  = "1 month ")+
-#   theme(legend.position="top",  #c(0.18, 0.85)
-#                      legend.text=element_text(size=14, colour="black"),
-#                      #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
-#                      axis.text=element_text(size=15),
-#                      plot.margin = unit(c(0.5,1,1,1), "cm"),
-#                      axis.title.x= element_text(size =15),
-#                      legend.title=element_blank()
-#                      )
-# print(poster_pco2)
-#   ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
-
-    ```
-
-## pH seaFET
-
-pH is measured continuously by an autonomous seaFET pH sensor.
-Because of issue, measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17.
-pH calibration is based on monthly discrete samples that are analysed with spectrophotometric method in Villefranche by Samir Alliouane.
-When it is not possible to sample at the vicinity of the sensor for practice reasons (in winter), sampling is done in the harbour and is not taken in consideration for calibration for spatial reasons.
-
-Calibration was done following the methods and code described in Bresnahan et al.
-(2014) and adapted to use in R (seacarb package).
-Deployment periods are difined so that one spectrophotometric measurement is in the middle of a defined period of calibration (shaded colors in the plot).
-
-Within this deployment period, calibration is made with E0 calculation (first plot) and final corrected pH is calculated (second plot).
-To allow calibration, one spectrophotometric pH measurement must match: seaFET voltage, in situ temperature (SBE38) and salinity.
-When one of these parameters is missing for any reasons (Ferrybox maintenance, breakdown...), the gap is filled with a mean of the 4 previous or next hours when available.
-If the pH spectrophotometric measurement is too far from the available values, the calibration is not performed (environemental variability reasons).
-The SBE38 insitu temperature and seaFET temperature are very similar (slope = 0.992, r2 = 0.96, see tab "Temperatures").
-These two temperatures were used interchangeably if one is missing.
-
-Missing data which could be estimated on : 2017-08-24, 2017-09-28, 2019-09-13 x 2.
-Missing data which could not be estimated on : 2018-04-16 , 2018-12-14, 2019-01-18.
-
-### **seaFET calibration constante E0**
-
-Plots of E0int25 and E0ext25 returned by the function "pHCalib" for each period of deployement are shown below.
-
-```{r seaFET calibration sf_calib, echo=FALSE, message= FALSE, warning=FALSE, out.width= "60%"}
-
-# We decided to calibrate pH data within each pH spectro measurement.
-# Thus, each pH spectro is taken as one calibration periode. 
-# We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
-sfPeriod <- d_all%>%
-  dplyr::select(datetime, pH_s_seafet_temp_field)%>%
-  dplyr::filter(!is.na(pH_s_seafet_temp_field))
-# Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
-sfPeriod <- sfPeriod%>%
-dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
-
-sfPeriod <-  sfPeriod %>%
-  dplyr::arrange(datetime) %>%
-  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
-  dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
-
-#put interval in a list with the start date of seaFET measurements
-sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
-#Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
-# This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
-sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
-#  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-# sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
-#  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-# sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
-
-#sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
-# set deployment period between 2 spectro measurements.
-# add here the new periods sfinterv[..]
-d_all <- d_all %>%
-  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
-                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
-                                ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
-                                ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
-                                ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
-                                ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
-                                ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
-                                ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
-                                ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
-                                ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
-                                ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
-                                 ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
-                                 ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
-                                 ifelse(datetime >= sfinterv[14] & datetime <= sfinterv[15], 14,
-                                 ifelse(datetime >= sfinterv[15] & datetime <= sfinterv[16], 15,
-                                 ifelse(datetime >= sfinterv[16] & datetime <= sfinterv[17], 16,
-                                 ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
-                                ifelse(datetime >= sfinterv[18] & datetime <= sfinterv[19], 18,
-                                ifelse(datetime >= sfinterv[19] & datetime <= sfinterv[20], 19,
-                                ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
-                                ifelse(datetime >= sfinterv[21] & datetime <= sfinterv[22], 21,
-                                #ifelse(datetime >= sfinterv[22] & datetime <= sfinterv[23], 22,
-                                #ifelse(datetime >= sfinterv[23] & datetime <= sfinterv[24], 23,
-                                #ifelse(datetime >= sfinterv[24] & datetime <= sfinterv[25], 24,
-                                #ifelse(datetime >= sfinterv[25] & datetime <= sfinterv[26], 25,
-                                ifelse(datetime >= sfinterv[22] , 22,NA )))))))))))))))))))))))
-
-# To make sf calibration against pH spectro, we need: sal - T insi - voltINT/EXT . If we missed one of these parameters, calibration will not run
-# Here we try to fill the gap when it is possible: make a mean with 4 previous/next hours available in the time serie. 
-# If the pH spectro is too far from a needed value, we decided to skip it for the calibration.
-# we highlighted 7 pH spectro that dont match one of these parameters : 2017-08-24 14:00:00 - 2017-09-28 13:00:00 - 2018-04-16 07:00:00 - 2018-12-14 09:00:00 - 2019-01-18 09:00:00 - 2019-09-13 08:00:00 - 2019-09-13 13:00:00
-# (1) Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04,
-# (2) removed from 2018-01-08 to 2018-02-02
-# (3) outliers removed
-# (1)
-d_all$phINT_filtered <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phINT_filtered < 8.04, NA, d_all$phINT_filtered) 
-d_all$phEXT_filtered <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phEXT_filtered < 8.04, NA, d_all$phEXT_filtered) 
-d_all$voltINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltINT < -0.9439, NA, d_all$voltINT) 
-d_all$voltEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
-# (2)
-d_all$voltINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltINT)
-d_all$voltEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltEXT)
-d_all$phINT_filtered <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phINT_filtered)
-d_all$phEXT_filtered <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phEXT_filtered)
-# (3)
-d_all$voltINT <- ifelse(d_all$datetime == "2017-11-02 21:00:00" | d_all$datetime == "2018-04-18 14:00:00", NA, d_all$voltINT)
-
-# period 1, mean of 4 next hours for volt int + T seaF
-mean_voltINT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
-  dplyr::summarise( mean(voltINT, na.rm = TRUE))
-mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltINT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltINT_4h, voltINT))
-
-mean_voltEXT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
-  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
-mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltEXT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltEXT_4h, voltEXT))
-
-mean_TseaF_4h <- d_all%>%
-  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
-  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
-mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
-d_all <- d_all%>%
-  dplyr::mutate(temp_insitu = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_insitu))
-
-# period 2, mean of 4 next hours for volt int + T seaF
-mean_voltINT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
-  dplyr::summarise( mean(voltINT, na.rm = TRUE))
-mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltINT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltINT_4h, voltINT))
-
-mean_voltEXT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
-  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
-mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltEXT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltEXT_4h, voltEXT))
-
-# period 20, mean of 4 previous hours for volt int + T seaF
-mean_voltINT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
-  dplyr::summarise( mean(voltINT, na.rm = TRUE))
-mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltINT_4h, voltINT))
-
-mean_voltEXT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
-  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
-mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltEXT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltEXT_4h, voltEXT))
-
-# period 21, mean of 4 previous hours for volt int + T seaF
-mean_voltINT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
-  dplyr::summarise( mean(voltINT, na.rm = TRUE))
-mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltINT_4h, voltINT))
-
-mean_voltEXT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
-  dplyr::summarise( mean(voltINT, na.rm = TRUE))
-mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltEXT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltEXT_4h, voltEXT))
-
-mean_TseaF_4h <- d_all%>%
-  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
-  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
-mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
-d_all <- d_all%>%
-  dplyr::mutate(temp_insitu = ifelse(datetime == "2019-09-13 13:00:00" , mean_TseaF_4h, temp_insitu))
-
-#interpolation of salinity during the FB off maintenance
-sal_fbinterp <-approx(d_all$datetime, d_all$sal_fb, xout=d_all$datetime, method="linear", rule=2)
-names(sal_fbinterp) <- c("datetime", "sal_fb_interp")
-sal_fbinterp <- as.data.frame(sal_fbinterp)
-d_all$sal_fb_interp <- sal_fbinterp$sal_fb_interp
-
-d_all$sal_fb <- ifelse(d_all$datetime > "2018-03-09 00:00:00" & d_all$datetime < "2018-04-16 16:00:00", d_all$sal_fb_interp, d_all$sal_fb)
-
-# test <- d_all%>%
-#   dplyr::filter(datetime=="2017-08-24 14:00:00")
-
-####
-## calculation of E0INT25/E0EXT25 ##
-##     new sf_calib function      ##
-####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_field,
-                          calT = d_all$temp_insitu, calSal = d_all$sal_fb )
-# put number of deployment 
-calib_spectro$deployment_sf <- d_all$deployment_sf
-
-# make the mean of E0 by period of deployement
-calib_spectro <- group_by(calib_spectro, deployment_sf) %>%
-  summarise(E0int25 = mean(E0int25, na.rm = T),
-            E0ext25 = mean(E0ext25, na.rm = T) 
-            )
-names(calib_spectro) <- c("deployment_sf", "E0int25_sf", "E0ext25_sf")
-
-# add E0 mean to seaFET data per deployment
-d_all <-left_join(d_all, calib_spectro,by="deployment_sf" )
-
-#### plot
-kk <- melt(calib_spectro, id.vars="deployment_sf")
-p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable),size=2) +
-  facet_grid(variable~., scales="free_y") + theme_bw() +
-  scale_colour_discrete(guide="none")
-print(p_calib)
-```
-
-### **seaFET pHT calibrated**
-pH is measured continuously by an autonomous seaFET pH sensor.
-Final calibrated seaFET pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
-Calibration was done following the methods and code described in Bresnahan *et al.* (2014) using seaFET voltage and spectro measurements.
-During the fifth period, seaFET cannot be calibrated because seaFET was not working during the time of reference (pH spectro) sampling (2018-04-16).
-To solve this calibration, we decided to fit the spectro measurement with a pH mean of 4 previous days.
-
-We also defined a period of malfunction from **2017-12-14** to **2018-02-02**.
-in the first part of this period, until 2018-01-08, we decided to filter outliers.
-In the second part, until the end of the period, data must be removed.
-
-```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE, warning=FALSE}
-####
-## calculation of the calibrated pH ##
-##       new sf_calc function       ##
-####
-seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu, calSal = d_all$sal_fb_interp)
-
-# bind new calibrated pH data to the seafet data set.
-names(seafet_calib) <- c("pHint_tot_sf", "pHext_tot_sf")
-d_all <- cbind(d_all, seafet_calib )
-
-# pH seaFET Final
-# add spectro points that are not taking into consideration
-d_all <- d_all%>%
-  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", pH_s_seafet_temp_field, NA ))
-
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field,pHint_tot_sf, pH_s_sf_no_calb)
-#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
-seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-  #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
-    dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_seafet_temp_field", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-    dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
-
-  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
-  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
-  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
-   dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
-   dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
-   dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
-   dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
-   dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[22], to= Sys.Date(), color = "#E0E0E0") %>%
-  dyLegend(show = "auto")   %>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-  dyRangeSelector(height = 30, dateWindow= NULL)
-
-# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@ 
-# seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb,pHint_tot_sf)
-# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
-# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-#   dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-#     dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
-#     dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
-# 
-#   dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#     dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dyLegend(show = "auto")   %>%
-#   dyAxis( "y2",valueRange = c(-3, 36))%>%
-#   dyAxis( "y",valueRange = c(-2, 2))%>%
-#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-#   dyRangeSelector(height = 30, dateWindow= NULL)
-# # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
-
-# Offset between seafet pH and spec pH 
-sfoffset <- left_join(sfPeriod[,c(1,2)], d_all%>%dplyr::select(datetime, pHint_tot_sf), by="datetime")
-dat <- mutate(sfoffset, diff_pH_sf = round((pH_s_seafet_temp_field - pHint_tot_sf),digits  = 4))
-average_offset <- mean(abs(dat$diff_pH_sf), na.rm=TRUE)
-
-plot_offset <- ggplot(data = filter(dat, !is.na(diff_pH_sf))) +
-  geom_hline(yintercept=mean(dat$diff_pH_sf, na.rm = TRUE), size=0.3, linetype="dashed", col="red") +
-  geom_hline(yintercept=0, size=0.3) +
-  geom_point(aes(x = datetime, y = diff_pH_sf), size = 1, colour = "#51C56AFF") +
-  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
-  scale_x_datetime(date_breaks="month", date_minor_breaks="1 week", labels=date_format("%b %Y")) +
-  Mytheme() + theme(panel.grid.major.x = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1))
-
-print(plot_offset)
-
-# #plot for POSTER june 2019
-# #plot of pH seafet
-# poster_ph <- ggplot() +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
-#   labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
-#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-#   theme(legend.position= c(0.17, 0.8),
-#                      legend.text=element_text(size=14),
-#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
-#                       axis.text=element_text(size=15),
-#                       plot.margin = unit(c(1,1,1,1), "cm"),
-#                       axis.title.x= element_text(size =15),
-#                       legend.title=element_blank())
-# 
-# print(poster_ph)
-# ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")
-
-#RANGE of pH
-d_all<- d_all%>%
-  dplyr::mutate(year = year(datetime))
-range <- tbl_df(
-  d_all %>%
-  group_by(date=as.Date(datetime), 
-           month=month(datetime, label=TRUE), 
-           year=year(datetime)) %>%
-  summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
-)
-quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
-
-#Per month
-range_month <-
-  range %>%
-  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
-  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
-
-size_point <- 0.4 #size of data points
-plot_range_sf <-  
-  ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
-  Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-print(plot_range_sf)
-ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
-
-```
-
-## pH durafet
-
-pH is measured continuously by an autonomous durafet pH sensor.
-Final calibrated durafet pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
-Calibration was done appliying an offset of pH between measured and spectro data per periods.
-
-### **Durafet calibration**
-
-```{r durafet calibration, echo=FALSE, message= FALSE, warning=FALSE}
-# deployment period between 2 spectro measurements.
-durPeriod <- d_all%>%
-  dplyr::select(datetime, pH_s_durafet_temp_field)%>%
-  dplyr::filter(!is.na(pH_s_durafet_temp_field))
-
-durPeriod <-  durPeriod %>%
-  dplyr::arrange(datetime) %>%
-  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(durPeriod)])/2* 3600 )))%>%
-  dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])
-
-#put interval in a list with the start date of durafet measurements
-durinterv <- c( as_datetime("2017-08-24 13:00:00"), durPeriod[,4])
- #Change period sfinterv[2]. Because durafet measurementwas not working on period 1. No match between spectro and sensor. Durafet spectro 1 not taking into consideration.
-durinterv[2] <- ymd_hms("2017-08-24 13:00:00")
- #Change period sfinterv[06]. Because durafet was not responding good after 2018-03-08 23:00:00.
-durinterv[6] <- ymd_hms("2018-03-08 23:00:00")
- #Change period sfinterv[13]. Because durafet was off just after 2018-12-28.
-durinterv[13] <- ymd_hms("2019-12-28 17:00:00")
- #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-#durinterv[14] <- ymd_hms("2019-01-19 00:00:00")
-
-# set deployment period between 2 spectro measurements.
-# add here the new periods durinterv[..]
-d_all <- d_all %>%
-  dplyr::mutate(deployment_dur = ifelse(datetime >= durinterv[1] & datetime <= durinterv[2], 01, 
-                                ifelse(datetime >= durinterv[2] & datetime <= durinterv[3], 02, 
-                                ifelse(datetime >= durinterv[3] & datetime <= durinterv[4], 03, 
-                                ifelse(datetime >= durinterv[4] & datetime <= durinterv[5], 04,
-                                ifelse(datetime >= durinterv[5] & datetime <= durinterv[6], 05,
-                                ifelse(datetime >= durinterv[6] & datetime <= durinterv[7], 06,
-                                ifelse(datetime >= durinterv[7] & datetime <= durinterv[8], 07,
-                                ifelse(datetime >= durinterv[8] & datetime <= durinterv[9], 08,
-                                ifelse(datetime >= durinterv[9] & datetime <= durinterv[10], 09,
-                                ifelse(datetime >= durinterv[10] & datetime <= durinterv[11], 10, 
-                                ifelse(datetime >= durinterv[11] & datetime <= durinterv[12], 11,
-                                ifelse(datetime >= durinterv[12] & datetime <= durinterv[13], 12,
-                                ifelse(datetime >= durinterv[13] & datetime <= durinterv[14], 13,
-                                ifelse(datetime >= durinterv[14] & datetime <= durinterv[15], 14,
-                                ifelse(datetime >= durinterv[15] & datetime <= durinterv[16], 15,
-                                ifelse(datetime >= durinterv[16] & datetime <= durinterv[17], 16,
-                                 ifelse(datetime >= durinterv[17] & datetime <= durinterv[18], 17,
-                                ifelse(datetime >= durinterv[18] & datetime <= durinterv[19], 18,
-                                ifelse(datetime >= durinterv[19] & datetime <= durinterv[20], 19,
-                                 ifelse(datetime >= durinterv[20] & datetime <= durinterv[21], 20,
-                                ifelse(datetime >= durinterv[21] & datetime <= durinterv[22], 21,
-                                 ifelse(datetime >= durinterv[22] & datetime <= durinterv[23], 22,
-                                ifelse(datetime >= durinterv[23] & datetime <= durinterv[24], 23,
-                                ifelse(datetime >= durinterv[24] & datetime <= durinterv[25], 24,
-                                 ifelse(datetime >= durinterv[25] & datetime <= durinterv[26], 25,
-                                ifelse(datetime >= durinterv[26], 26,NA )))))))))))))))))))))))))))
-
-# Offset between durafet pH and spec pH 
-duroffset <- left_join(durPeriod%>%dplyr::select(datetime,pH_s_durafet_temp_field), d_all%>%dplyr::select(datetime,pH_durafet ), by="datetime")
-dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_field - pH_durafet)
-average_offset_dur <- round(mean(dat_dur$diff_pH_dur, na.rm=TRUE), digits = 2)
-sd_offset_dur <- round(sd(abs(dat_dur$diff_pH_dur), na.rm=TRUE), digits = 2)
-n_offset_dur <- length(!is.na(dat_dur$diff_pH_dur))
-
-plot_offset_dur <- ggplot(data = filter(dat_dur, !is.na(diff_pH_dur))) +
-  geom_hline(yintercept=mean(dat_dur$diff_pH_dur, na.rm = TRUE), size=0.3, col="red") +
-  annotate("text", x = dat_dur$datetime[3], y =-0.16, label = "offset mean", color="red")+
-  geom_hline(yintercept=0, size=0.3) +
-  geom_point(aes(x = datetime, y = diff_pH_dur), size = 1, colour = "#51C56AFF") +
-  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
-  scale_x_datetime(date_breaks="month", date_minor_breaks="1 week", labels=date_format("%b %Y")) +
-  Mytheme() + theme(panel.grid.major.x = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1))
-
-# create offset per period + add this offset per period.
-d_all <- d_all%>%
- dplyr::mutate(offset_durafet = ifelse(deployment_dur == 1, dat_dur$diff_pH_dur[1],
-                                ifelse(deployment_dur == 2, dat_dur$diff_pH_dur[2],
-                                ifelse(deployment_dur == 3, dat_dur$diff_pH_dur[3],
-                                ifelse(deployment_dur == 4, dat_dur$diff_pH_dur[4],
-                                ifelse(deployment_dur == 5, dat_dur$diff_pH_dur[5],
-                                ifelse(deployment_dur == 6, dat_dur$diff_pH_dur[6],
-                                ifelse(deployment_dur == 7, dat_dur$diff_pH_dur[7],
-                                ifelse(deployment_dur == 8, dat_dur$diff_pH_dur[8],
-                                ifelse(deployment_dur == 9, dat_dur$diff_pH_dur[9],
-                                ifelse(deployment_dur == 10, dat_dur$diff_pH_dur[10], 
-                                ifelse(deployment_dur == 11, dat_dur$diff_pH_dur[11],
-                                ifelse(deployment_dur == 12, dat_dur$diff_pH_dur[12],
-                                ifelse(deployment_dur == 13, dat_dur$diff_pH_dur[13],
-                                ifelse(deployment_dur == 14, dat_dur$diff_pH_dur[14],
-                                ifelse(deployment_dur == 15, dat_dur$diff_pH_dur[15],
-                                ifelse(deployment_dur == 16, dat_dur$diff_pH_dur[16],
-                                ifelse(deployment_dur == 17, dat_dur$diff_pH_dur[17],
-                                ifelse(deployment_dur == 18, dat_dur$diff_pH_dur[18],
-                                ifelse(deployment_dur == 19, dat_dur$diff_pH_dur[19],
-                                ifelse(deployment_dur == 20, dat_dur$diff_pH_dur[20],
-                                ifelse(deployment_dur == 21, dat_dur$diff_pH_dur[21],
-                                ifelse(deployment_dur == 22, dat_dur$diff_pH_dur[22],
-                                ifelse(deployment_dur == 23, dat_dur$diff_pH_dur[23],
-                                ifelse(deployment_dur == 24, dat_dur$diff_pH_dur[24],
-                                ifelse(deployment_dur == 25, dat_dur$diff_pH_dur[25],0))))))))))))))))))))))))),
-              pH_durafet_corrected = pH_durafet + offset_durafet
-              )
-
-# Remove outliers from 2018-07-10 00:00 to 05:00
-d_all$pH_durafet_corrected <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$pH_durafet_corrected)
-d_all$pH_durafet <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$pH_durafet)
-
-# DURAFET 
-# add spectro points that are not taking into consideration
-d_all <- d_all%>%
-  dplyr::mutate( pH_s_dur_no_calb = ifelse(datetime == "2017-08-24 13:00:00", pH_s_durafet_temp_field, NA ))
-
-durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected, pH_s_dur_no_calb)
-durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
- dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
-    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_durafet_temp_field", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
-       dySeries("pH_s_dur_no_calb", label = "pH spectro no calibration", color ="black", pointShape = "triangle",strokeWidth=0, pointSize=6) %>%
-       dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
-    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="GMT"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyShading(from =  durinterv[1], to= durinterv[2], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[2], to= durinterv[3], color = "#E0E0E0") %>%
-    dyShading(from = durinterv[3], to= durinterv[4], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[4], to= durinterv[5], color = "#E0E0E0") %>%
-    dyShading(from = durinterv[5], to= durinterv[6], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[6], to= durinterv[7], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[7], to= durinterv[8], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[8], to= durinterv[9], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[9], to= durinterv[10], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[10], to= durinterv[11], color = "#E0E0E0") %>%
-    dyShading(from = durinterv[11], to= durinterv[12], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[12], to= durinterv[13], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[13], to= durinterv[14], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[14], to= durinterv[15], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[15], to= durinterv[16], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[16], to= durinterv[17], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[17], to= durinterv[18], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[18], to= durinterv[19], color = "#E0E0E0") %>%
-    dyShading(from = durinterv[19], to= durinterv[20], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[20], to= durinterv[21], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[21], to= durinterv[22], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[22], to= durinterv[23], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[23], to= durinterv[24], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[24], to= durinterv[25], color = "#E0E0E0") %>%
-  dyShading(from = durinterv[25], to= durinterv[26], color = "#CCCCCC") %>%
-  dyShading(from = durinterv[26], to= Sys.Date(), color = "#E0E0E0") %>%
-     dyLegend(show = "follow")   %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-print(plot_offset_dur)
-
-# #plot for POSTER june 2019
-# #plot of pH durafet
-#  poster_dur <- ggplot( ) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
-#   labs(x = "", y= "", title = expression(pH[T]~durafet)) +
-#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-#    theme(legend.position= c(0.17, 0.8),
-#                      legend.text=element_text(size=14),
-#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
-#                       axis.text=element_text(size=15),
-#                       plot.margin = unit(c(1,1,1,1), "cm"),
-#                       axis.title.x= element_text(size =15),
-#                       legend.title=element_blank())
-# 
-# print(poster_dur)
-# ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")
-
-# RANGE of pH
-range_dur <- tbl_df(
-  d_all %>%
-  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
-  summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
-)
-quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
-
-# Per month
-range_month <-
-  range_dur %>%
-  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
-  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
-
-size_point <- 0.4 # size of data points
-plot_range_dur <-
-  ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
-  Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-print(plot_range_dur)
-ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
-```
-
-The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).
-
-## Range per months
-
-```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
-range_month <-
-  d_all %>%
-  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
-  #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
-  summarize(Tinsi_max =round( max(temp_insitu, na.rm=TRUE), digits = 2),
-            Tinsi_min = round(min(temp_insitu, na.rm=TRUE), digits = 2),
-            sal_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
-            sal_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
-            pH_sf_max = round(max(pHint_tot_sf, na.rm=TRUE), digits = 4),
-            pH_sf_min = round(min(pHint_tot_sf, na.rm=TRUE), digits = 4))
-kable(range_month)
-```
-
-## pHs 
-Comparaison is done here with **corrected pHs** (**seaFET**, **durafet** and **calculated** (from AT/CT)) and normalized at 4°C with a total alkalinity of 2273 µmoles kg-1 (mean data).
-For information, mean temperatures in Ferrybox and *in situ* are repectively 3.5°C and 2.5°C.
-
-### **seaFET / durafet pHs**
-
-```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-# remove sf biofouling period
-pH_sf <- d_all %>%
-  dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pHint_tot_sf)%>%
-  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal_fb)) %>%
-  dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
-pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu, Pinsi=11, S=pH_sf$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
-
-pH_dur <- d_all %>%
-  dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pH_durafet_corrected)%>%
-  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal_fb))
-pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_insitu, Pinsi=11, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
-
-# join pH sf norm + pH dur norm
-d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime,pHint_tot_sf_norm4 ), by="datetime")
-d_all <- left_join(d_all, pH_dur%>%dplyr::select(datetime,pH_durafet_norm4 ), by="datetime")
-
-fit <- lmodel2(data = d_all,  pHint_tot_sf_norm4 ~ pH_durafet_norm4 , nperm = 99)
-pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pHint_tot_sf_norm4, label = month))+
-  geom_text( aes(color=factor(month))) + 
- # scale_color_viridis_d(option = "C", guide="none")+
-  geom_line(aes(x = pHint_tot_sf_norm4, y = pHint_tot_sf_norm4), linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("pH seaFET vs pH durafet, normalized 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 , xlim=c(7.8,8.35), ylim=c(7.8,8.35))+ scale_colour_discrete(guide="none") +
-  labs( x="pH durafet, 4°C", y="pH seaFET, 4°C ", color = "Months")  +theme_bw()
-
-print(pdur_sf_norm_text)
-
-durafet_sf_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pHint_tot_sf_norm4)
-durafet_sf_contros_xts <- as.xts(durafet_sf_contros_xts, order.by = d_all$datetime)
-dygraph(durafet_sf_contros_xts, group = "awipev", main="pH durafet vs pH seaFET at 4°C", ylab="pHT") %>%
-    dySeries("pH_durafet_norm4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color =  "red", strokeWidth = 0, pointSize = 2 ) %>%
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-       dyLegend(show = "follow")   %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL) 
-```
-
-### **Calculated / Durafet pHs**
-```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
-# Normalize phcalc from AT/CT to 4°c
-pH_calc <- discrete %>%
-  dplyr::select(datetime, sal,temp, phcalc, at)%>%
-  dplyr::filter(!is.na(phcalc), !is.na(temp), !is.na(sal))
-pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
-
-# join pH calc norm + pH dur/sf norm in d_all
-d_all <- left_join(d_all, pH_calc%>%dplyr::select(datetime,pH_calc_norm4), by="datetime")
-
-# DURAFET vs CALC
-# fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pH_durafet_norm4 , nperm = 99)
-# 
-# pdur_calc_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pH_calc_norm4, label = month))+
-#   geom_text( aes(color=factor(month))) + 
-#   geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
-#   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-#   labs(title = paste("pH calculated vs pH durafet, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
-#                      "; Intercept =", signif(fit$regression.results[2,2], 3),
-#                      "; Slope =", signif( fit$regression.results[2,3], 3),
-#                      "; P =", signif(fit$P.param, 3))) +
-#   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-#    coord_fixed(ratio = 1 , xlim=c(8,8.22), ylim=c(8,8.22)) + 
-#   scale_color_discrete(guide="none")+
-#   labs(x="pH durafet, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
-# pdur_calc_norm_text
-
-durafet_calc_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pH_calc_norm4)
-durafet_calc_contros_xts <- as.xts(durafet_calc_contros_xts, order.by = d_all$datetime)
-dygraph(durafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH durafet, normalized at 4°C", ylab="pHT") %>%
-    dySeries("pH_durafet_norm4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_calc_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-       dyLegend(show = "follow")   %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-```
-
-### **Calculated / seaFET pHs**
-```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
-# SEAFET vs CALC
-fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pHint_tot_sf_norm4 , nperm = 99)
-
-psf_calc_norm_text <-  ggplot(d_all,aes(x=pHint_tot_sf_norm4, y= pH_calc_norm4, label = month))+
-  geom_text( aes(color=factor(month))) + 
-  scale_color_discrete(guide = "none")+
-  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("pH calculated vs pH seaFET, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
-  labs(x="pH seaFET, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
-psf_calc_norm_text
-
-seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_norm4, pH_calc_norm4)
-seafet_calc_contros_xts <- as.xts(seafet_calc_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH seaFET, normalized at 4°C", ylab="pHT") %>%
-    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_calc_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-       dyLegend(show = "follow")   %>%
-dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-```
-
-### **Spectro / durafet**
-
-```{r pHs comparaison durafet spectro, echo=FALSE, message= FALSE, warning=FALSE}
-# Spectro / durafet
-fit <- lmodel2(data = d_all,  pH_s_durafet_temp_field ~ pH_durafet_corrected , nperm = 99)
-
-p_dura_spectro <-  ggplot(d_all,aes(x=pH_durafet_corrected, y= pH_s_durafet_temp_field, label = month))+
-  geom_text( aes(color=factor(month))) + 
-  scale_color_discrete(guide = "none")+
-  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("pH spectro vs pH durafet","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-    coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
-  labs(x="pH durafet", y="pH spectro, 4°C ", color = "Months") + theme_bw() 
-p_dura_spectro
-```
-
-### **Spectro / seaFET**
-
-```{r pHs comparaison sf spectro, echo=FALSE, message= FALSE, warning=FALSE}
-# Spectro / seafet
-fit <- lmodel2(data = d_all,  pH_s_seafet_temp_field ~ pHint_tot_sf , nperm = 99)
-
-p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_field, label = month))+
-  geom_text( aes(color=factor(month))) + 
-  scale_color_discrete(guide = "none")+
-  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("pH spectro vs pH seaFET","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
-  labs(x="pH seaFET", y="pH spectro, 4°C ", color = "Months") + theme_bw() 
-p_sf_spectro
-```
-
-## SNAPO-CO2
-Since November 2018, informations on weekly Ferrybox and monthly durafet/seaFET samplings are collected in a online document that can be consulted at anytime:
-
-[weekly and monthly samplings](https://docs.google.com/spreadsheets/d/1bNh9q4bkNoh2ra78XC451EmGb9Q8kMf4ByBnKngeHOg/edit?usp=sharing)
-
-We found that some analysed discrete seawater replicates for AT/CT, performed by SNAPO in Paris sometimes show a large difference between duplicates.
-Arbitrarily, we decided to take in consideration replicates with a standard deviation smaller than 10 µmoles.kg-1.
-In the other case (greater than 10 µmoles.kg-1), the closest replicate from the general trend will be kept with qflag_at/qflag_ct of 2 (correct analysis) and the farthest one will be rejected with a flag of 1.
-There are exceptions when it is difficult to decide which of the replicates need to be eliminated.
-
-For TA, dulpicates's flags that have been changed to 1 are:
-
-2015-11-18
-, 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29, 2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16, 2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03, 2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23.
-
-For CT, duplicates's flags that have been changed to 1 are:
-
-2015-08-06, 2015-08-13, 2016-05-12, 2016-05-19, 2016-06-16, 2016-07-28, 2016-09-08, 2016-10-27, 2016-11-17, 2017-01-19, 2017-03-02, 2017-04-27, 2017-09-14, 2018-04-26, 2018-05-04, 2018-05-12, 2018-05-25, 2018-06-30, 2018-07-20, 2018-08-03, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23.
-
-```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
-# use the df at_ct for mean and sd
-# creat a new df to calculate the diff between replicate
- diff <- d %>%
-    group_by(datetime) %>%
-   dplyr::select(datetime, at, ct)%>%   
-   dplyr::mutate(at_diff = abs(at - lag(at)),
-                 ct_diff = abs(ct - lag(ct)))
-
-pdelta_at_snapo <-ggplot() +
-    geom_point(data=diff, aes(x= datetime, y= at_diff)) +
-    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
-    annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
-    annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
-labs(title= "AT", x="Time", y="Delta between TA replicates")+
-    Mytheme()
-pdelta_ct_snapo <-ggplot() +
-    geom_point(data=diff, aes(x= datetime, y= ct_diff)) +
-    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
-annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
-    annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
-  labs(title= "CT",x="Time", y="Delta between CT replicates")+
-    Mytheme()
-
-p_ct_ts <- ggplot() +
-    geom_point(data=discrete, aes(x= datetime, y= ct)) +
-  labs(title= "",x="Time", y="CT (µmoles/kg)")+
-    Mytheme()
-p_at_ts <- ggplot() +
-    geom_point(data=discrete, aes(x= datetime, y= at)) +
-  labs(title= "",x="Time", y="AT (µmoles/kg)")+
-    Mytheme()
-
-# DYGRAPH
-
-# to create periods according to SNAPCO analysis 
-snapcoevents <- c("2015-07-23 00:00:00", "2015-11-18 00:00:00", "2015-11-27 00:00:00", "2016-10-13 00:00:00", 
-              "2017-05-11 00:00:00", "2018-02-09 00:00:00", "2018-02-16 00:00:00", "2018-07-27 00:00:00", "2018-08-03 00:00:00", "2018-11-23 00:00:00", "2018-11-30 00:00:00", "2019-04-12 00:00:00","2019-08-31 23:59:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
-
-at_diff_xts <- dplyr::select(diff, datetime, at_diff, at)
-at_diff_xts <- as.xts(at_diff_xts, order.by = diff$datetime)
-pdelta_at_snapo_dygraph <- dygraph(at_diff_xts, group = "awipev", main="Discrete AT (SNAPO) measurements", ylab="AT") %>%
-    dySeries("at_diff", label = "AT delta", color ="red", strokeWidth=0, pointSize=4) %>%
-    dySeries("at", label = "AT duplicates", color =  "blue", strokeWidth = 0, pointSize = 2, axis = "y2" ) %>%
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-  dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#EDEDED") %>%
-  dyShading(from = snapcoevents[3], to = snapcoevents[4], color = "#C2C2C2") %>%
-  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#EDEDED") %>%
-  dyShading(from = snapcoevents[7], to = snapcoevents[8], color = "#C2C2C2") %>%
-  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#EDEDED") %>%
-  dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C2C2") %>%
-  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
-    dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-       dyLegend(show = "follow")   %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=2) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-ct_diff_xts <- dplyr::select(diff, datetime, ct_diff, ct)
-ct_diff_xts <- as.xts(ct_diff_xts, order.by = diff$datetime)
-pdelta_ct_snapo_dygraph <- dygraph(ct_diff_xts, group = "awipev", main="Discrete CT (SNAPO) measurements", ylab="CT") %>%
-    dySeries("ct_diff", label = "CT delta", color ="red", strokeWidth=0, pointSize=4) %>%
-    dySeries("ct", label = "CT duplicates", color =  "blue", strokeWidth = 0, pointSize = 2, axis = "y2" ) %>%
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-   dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#EDEDED") %>%
-  dyShading(from = snapcoevents[3], to = snapcoevents[4], color = "#C2C2C2") %>%
-  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#EDEDED") %>%
-  dyShading(from = snapcoevents[7], to = snapcoevents[8], color = "#C2C2C2") %>%
-  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#EDEDED") %>%
-  dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C2C2") %>%
-  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
-    dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%
-       dyLegend(show = "follow")   %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=2) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-pdelta_at_snapo
-pdelta_at_snapo_dygraph
-p_at_ts
-pdelta_ct_snapo
-pdelta_ct_snapo_dygraph
-p_ct_ts
-ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
-ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
-```
-```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
-# d_hour is the real data set that is read at the beginning of the script
-# d_all comprises additional columns calculated in this script
-# These additional variablrs are useful elsewhere (for example in "presentation")
-# Hence, here we save it for this use
-save(file= paste0(path, "fb_data/d_all.rds"), d_all)
-```
-
-<!-- ```{r Klara Wolf} -->
-<!-- wolf <- d_all %>% -->
-<!--   dplyr::select(datetime, PCO2_Corr_filtered, phcalc, pH_calc_norm4) %>% -->
-<!--   dplyr::filter(datetime >= "2016-03-01" & datetime <= "2016-09-30") -->
-<!-- write_csv(path = "wolf.csv", wolf, col_names = TRUE) -->
-<!-- ``` -->
-
-## Maintenance
-<div style="text-align: justify">
-
-### **REMOS**
-- **2019-09-07**: REMOS back in the water.
-- **2019-09-02**: REMOS removed from the water for maintenance with Philipp and Samir.
-- **2018-11-24**: REMOS stopped because of an iceberg. At the moment we dont know if instruments are still there/broken.
-
-### **FerryBox**
-- **2020-01-24**: heater issues in the contenair (power shutdown maybe) caused some samples to freeze. See part "SNAPO" for details on samples.
-- **2019-09-01**: Some interruptions for the FB during 2 weeks of maintenance.
-- **2019-06-12**: Markus came to do maintenace. 
-- **2019-06-05**: Problem in the relay 15 that controls the waste water pump was found. The spare part will be brought here next week (when Samir will leave...).
-- **2019-06-03**: Samir is on site alone. Different tests were made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the problem (low flow).
-- **2019-05-22**: FB is stopped because of several problems. Philipp and Marine are working on it.
-- **2019-05-21**: FB is unstable. 
-- **2019-04-14**: FB is working again. 
-- **2019-04-13**: FB is stopped since 05:00am (the level switch stuck in the full position in the waste tank). 
-- **2019-02-27**: FB is working again. 
-- **2019-02-26**: FB is stopped because of a "leakage" issue. 
-- **2019-01-17**: FB is stopped until 19th January 
-- **2019-01-11**: FB is stopped until 12th Decmeber. 
-- **2018-12-28**: FB is stopped until 31st Decmeber. 
-- **2018-10-12**: FB is working again. 
-- **2018-10-10**: FB is stopped after a seawater leakage. 
-- **2018-10-08**: FB is working again. 
-- **2018-10-05**: FB is stopped after a seawater leakage. 
-- **2018-09-12**: FB is stopped. Problems inland could be the reason. The same day Marine make it working again.
-- **2018-04-14**: FB is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.
-- **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet tubings) in Svalbard, maybe due to a power failure over night in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
-- **2017-05-24**: FerryBox was shut down due to many connexion issues...see Philipp's email 24/05/2017 18:17.
-- **2017-03-20**: Philipp arrived in NYA to solve the problem.
-- **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's email on 2017-03-11 10:40). No more data for all parameters.
-- **2017-01-31**: Beginning of the 14-days FB maintenance by Philipp and Uwe. Gaps in data could be present during this period.
-- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19.
-- **2016-09-24**: No data because of maintenance until the 28th. Except for TA wich has data available for this period.
-- **2016-09-20**: Test in the Ferrybox with the seawater.
-Seawater was "sucked" (not pumped) from 7:40 to 10:00 by a vaccum system in order to test it.
-This system was installed if the pumps 1 and 2 broke during winter.
-This is a "plan C".
-This system is not automatic and we will be informed about its power up in case of emergency.
-As long as the water is not pumped with this system, we have to monitor the data because changements in gas partial pressure can occur.
-- **2016-09-12**: No data because of maintenance until the 18th.
-- **2016-09-10**: No data because of maintenance until the 11th.
-- **2016-05-09**: data are back.
-- **2016-05-04**: No data for all parameters because of electricity issues. 
-- **2016-04-23**: FerryBox was shut down by AWI team for maintenance.
-- **2016-02-23**: FerryBox was switched on by AWI team after maintenance.
-- **2015-12-20**: FerryBox was shut down because of pump issues. Waiting for the maintenance in February.
-- **2015-11-27**: The ferrybox was down from Nov. 18th until today Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader AWIPEV 2015-11-27 12:57). Tubes frozen.
-
-### **TA analyser**
-- **2019-11-15**: TA calibration done by Gwendall is OK but the sensore seems to have problem since 2019-10-16.
-Video conference is scheduled with Steffen on 2019-11-19.
-Maybe sample supply is defective.
-- **2019-07-12**: Steffen told us that calibration was not OK.
-To check it, he calculated the mediane of the pH/volume sample / volumeIndicatorfactor and compared them to January/October calibration.
-We wait for Steffen recommandations before to make another calibration.
-- **2019-06-07**: Samir did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. TA was stable before the calibration and calibration was OK.
-- **2019-02-15**: No data from 15th (14:08:21 UTC) to 19th February (14:58:46 UTC). files transfered but no data. No explanation.
-- **2019-01-26**: Philipp did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. Flow filter was also lifted up and the seawater flow has therefore increased.
-- **2019-01-16**: Bad data since this date. 
-- **2018-12-28**: HCL and BCG cartridges were changed by Marine.
-- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
-- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer).
-Samir received password and access from the AWI in order to communicate from France with the TA.
-- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
-- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again.
-First data were received (high: 2450 and low: 2150) but salinity issue since this time.
-Uwe/Philipp try to find if this comes from comunication issue with the FB.
-- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
-- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
-- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
-- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
-- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
-- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
-- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
-- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
-- **2017-02-10**: TA cleaning salt crusts.
-- **2017-02-09**: TA calibration with CRM at 12:20.
-- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
-- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode).
-Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
-- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
-- **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
-- **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
-- **2016-05-01**: No data for TA.
-- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).
-
-### **pH seaFET**
-- **2019-09-02**: Out from the water for maintenance and cleaning only.
-- **2018-04-17**: seaFET #1005 was changed on the REMOS and seaFET #007 (from Villefranche) was installed.
-Continuous mode with external power supply was set and internal pack of baterries was removed.
-Old seaFET will be brought back to France with Samir.
-- **2018-03-09**: #007 seaFET currently in USA will be sent by seabird to NYA. #1005 seaFET currently in NYA will be sent to USA for update, following all external issues, for free.
-- **2017-08-24**: seaFET #1005 was installed on the REMOS into the field.
-
-### **Cross-Flow filter**
-- **2019-01-26**: The filter was lifted up in order to fix the flow problem. 
-- **2018-11-01**: The filter clogged a lot of time even after acid cycles. It was not replaced since its initial installation with the TA analyser. We think to replace it soon.
-- **2016-07-20**: Cross filter was cleanned by Obs. eng. with 10-15 min tape water flush.
-
-### **durafet**
-- **2019-09-05**: same durafet 
-- **2017-10-30**: (13:00 UTC) Durafet holder was changed by Benoit and the new one (made by Uwe) more larger (all the durafet's body is plunge in the seawater) was installed.
-- **2017-08-24**: durafet was installed.
-
-### ***p*CO~2~**
-- **2019-09-03**: *p*CO~2~ analyser (S/N: CO2FT-0515-001) have been installed and *p*CO~2~ analyser (S/N: CO2FT-0215-001) was sent to Kiel for calibration.
-- **2018-10-31**: *p*CO~2~ analyser (S/N: CO2FT-0215-001) have been installed and *p*CO~2~ analyser (S/N: CO2FT-0515-001) was brought back to France and waiting 2019 fundings to bring it for calibration.
-- **2018-04-16**: *p*CO~2~ analyser switching by Uwe and Samir. S/N CO2FT-0515-001 is now installed. Old *p*CO~2~ sensor will be brought back to France with Samir.
-- **2017-02-07**: pCO2 analyser switching by Uwe. S/N CO2FT-0215-001 is now installed.
-- **2016-09-13**: Changement of the *p*CO~2~ S/N CO2FT-0515-001 membrane (Uwe from 4H-Jena).
-- **2016-02-28**: *p*CO~2~ analyser (S/N CO2FT-0215-001) was sent to calibration and the second *p*CO~2~ analyser (S/N: CO2FT-0515-001) have been installed.
-
-<div style="text-align:center" markdown="1">
-<img  src="./Images/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200">
-<img  src="./Images/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200">
-</div>
-
-## Script + data
-<div style="text-align: justify">  
-Here is reported all important modifications made on *ny-alesund_cc.*.
-All documents concerning maintenance, tasks to do, calibration... are accessible by the AWIPEV staff on this link with special access:
-
-[wiki document](https://spaces.awi.de/confluence/login.action?os_destination=%2Fpages%2Fviewpage.action%3FspaceKey%3DMOS%26title%3DWater%2Bsampling&permissionViolation=true)
-
-[UWO-Ferrybox variables from our sensors](https://docs.google.com/spreadsheets/d/1arKYfUjmg3YrgQ5g9LN_XFwUORyz7nqlKNWq3uYok3U/edit?ts=5c7e1d16#gid=393659093)
-
-[All UWO-Ferrybox data / NearRealTime (NRT) AWI database](https://dashboard.awi.de/data-xxl/overview.jsp)
-
-[Procedure to download NRT data](https://spaces.awi.de/confluence/display/MOS/NRT+data+download+procedures)
-
-[AWI NRT database](https://dashboard.awi.de/data-xxl/overview.jsp)
-
-[Missing data to add to the NRT database](https://docs.google.com/spreadsheets/d/1Cbc4hWyclnBsNsOH_3QDA3AGZfwF4I1HuadfBe1BVjI/edit?usp=sharing)
-
-[Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736)
-
-### **FerryBox**
-- **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.
-
-### **pH seaFET**
-- **2018-08-30**: voltINT + phINT were filtered from 2017-12-14 to 2018-01-08 and bad data were removed from 2018-01-08 to 2018-02-02.
-pH spectro from 2018-04-16 07:00:00 was fitted with a mean of 4 days of voltINT in order to make the calibration for this 5th period.
-- **2018-07-30**: Flag location (location_flag) is added in the script to localize seaFET/durafet discrete samples: flag 1 = at the harbor (not taken in consideration) and flag 0 = in the FB for durafet or on site for seaFET (takken in consideration as "normal" sampling").
-See seaFET part.
-- **2018-02-02**: Based on Darrell's advices (SeaBird), Philipp implemented the seaFET as: 1h periodic sampling with the following commands: perdival 1h, navg 5, brstsize 1, opermode periodic. 
-- **2017-12-29**: "SVL_20171218_010426.dat" from seaFet data was deleted because of bug with its size (0 octect). pH filter was added to "ny_alesund_cc" file for seaFet data (<7.5 and <8.5).
-
-### **Durafet**
-- Reference spectro measurement from the 2019-01-18 11:00 do not match with a durafet raw data because Ferrybox was off.
-This reference point was not takken in consideration for calibration.
-The window of the previous and next calibration periods was extended.
-
-### ***p*CO~2~**
-- **2019-11-18**: Calibration parameters from #0215-001 were added to "server.../data/NRT_data/Data_Processing_sheet_pCO2.csv" (new path).
-- **2018-08-29**: Calibration parameters from #0215-001 were added to "./data/Calibration_pCO2/Data_Processing_sheet_pCO2.csv".
-- **2018-04-20**: For *p*CO~2~ Calibration the previous period (N° 4) was added to the script "ny-alesund_cc" line 466.
-- **2015-10-13**: we put back the spike.pCO2 to 600 because data in October reached more than 350 µAtm. We let this like that and we are going to deal with it manually later if needed.
-- **2015-09-28**: we put the spike.pCO2 (detection of peaks: threshold) at 350 to remove anomalies on the 12 and 15 September. We have to monitor data. If data reach this value, then problem.
-
-### **SNAPO**
-- **2020-01-23**: Freezed and lost samples because of heater issue in the container: 15/11/2019 (durafet x1), 03/12/2019 (FB x2), 11/12/2019 (FB x2), 13/12/2019 (FB x2), 20/12/2019 (FB x2), 03/01/2020 (FB x2).
-Following samples could have been frozen, not sure: 06/09/2019 (FB x2), 13/09/2019 (seaFET x1), 13/09/2019 (FB x2), 20/09/2019 (FB x1), 27/09/2019(FB x2), 04/10/2019 (FB x2), 11/10/2019 (FB x1), 11/10/2019  (durafet x1), 25/10/2019 (FB x2), 01/11/2019 (FB x1), 15/11/2019 (FB x1).
-
-- **2020-01-15**: Results from 2019-04-19 to 2019-08-31 (sent in September 2019) were received.
-FB duplicates from 2019-08-09 were analysed as Durafet because of wrong box.
-One sample from 2019-06-07 (durafet) was analysed by Paris because of wrong box.
-- **2019-04-30**: Duplicate "Ferrybox" samples (SN0316 and SN264, 2019-02-22 14:05) were sent by mistake in Villefranche for pH measurements.
-Those results were put in the datafile as "durafet" samples as soon as they are comming from the Ferrybox tape seawater.
-We will add a lack of DIC for this week.
-TA will be measured in Villefranche.
-- **2018-08-30**: flag of 1 AT duplicate (2205) from 2017-08-31 was put to 3 (dosage douteux).
-
-### **Files - server**
-- **2019-11-15**: Script including the new data downloading from the NRT AWI database is running (ny-alesund_cc.R).
-From this date, data are donwloaded from AWI NRT dtabase.
-We are waiting some setting from Philipp to have the entire dataset.
-Only 2018-2019 are available for the moment.
-New path was created in the server and pCloud/exp168 with "NRT_data" file.
-Please see the picture bellow.
-- **2018-04-19**: Since "Ferrybox" is on again, the adding to solve the files issues are making not data into d_hour for this period (2018-09-03 to 2018-14-04).
-This adding was put in comments now.
-In seaFET data reading, S/N have been changed from 1005 to 0007.
-- **2018-03-21**: Files issues.
-FerryBox instruments are down because of freezing but UWO instrument as seaFET and SBE38 are OK.
-Removing of one 0 octet file from seaFET20180317_1404 and put back seaFET files from 20180309 to 20180312 in seaFET folder.
-They were in SBE38 folder...Weird.
-Additionnal script lines were added in order to deal with the issue of "in situ" created date whereas "Ferrybox" created data ware not.
-Since "in situ" parameters are running (d df) and not "in ferrybox" parameters (z df), the new datetime lines are not taking in consideration with the left_join function we have to add them during Ferrybox shutdown.
-- **2018-03-09**: Script issue solved with first negative values encountred in SBE38 files. We find a regex solution to take "space + space or negative value" in consideration.
-- **2017-11-07**: Wrong seaFET files (wrong datetime starting on the 5th September) from 24 to 26 October were fixed.
-File "SVL_20171024_030426_to_20171026_110425_SeaFet-1005.txt" were created in SeaFet_archive.
-
-## Villefranche Server informations
-
-- Serveur : awipev-co2 (193.50.85.104)
-- 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer mais n'est plus utilisé).
-- Pour se connecter à awipev-co2.obs-vlfr.fr
-        - ssh awipev@awipev-co2.obs-vlfr.fr
-- Intervention sur le serveur :
-        - ssh awipev@awipev-co2.obs-vlfr.fr
-        - rebooting Ubuntu server: sudo shutdown -r now
-        - to check versions:
-            - dpkg -l | grep shiny
-            - dpkg -l | grep r-base
-        - To update Ubuntu, R and its packages:
-            - sudo su
-            - apt-get upgrade
-        - To restart shiny server: sudo systemctl restart shiny-server
-        - update shiny server: follow procedure detailed on the shiny web page Data processing
-
-** Data processing**
-
-We use the AWI database XXXXX
-
-**crontab awipev@awipev-co2.obs-vlfr.fr**
-
-si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync
-
-Pattern des commandes : # m h dom mon dow command
-
-- (At 01:00, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
-
-00 01 * * * cd ; R \-\-vanilla < ny-alesund/R/ny-alesund_cc.R
-
-- (At 03:00, web page is generated)
-
-00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1
-
-- (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud ... Exp168)
-
-00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
-
-- (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)
-
-00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
-
-**Web page**
-
-- La page web index.html est faite sur le serveur awipev/web grâce au script awipev-CO2_web.Rmd puis transférée et renommée dans awipev/awipev-CO2_web
-- Création du répertoire web qui contient ce qu’il faut pour générer la page web:
-    - AWIPEV-Logo.jpg
-    - Discrete_sampling_AWIPEV.csurv
-    - awipev-CO2_web.Rmd
-    - awipev-co2.sh (lancer par bash awipev-co2.sh)
-- Accessible https://awipev-co2.obs-vlfr.fr
-
-**On utilise un shell script awipev-co2.sh:**
-
- #!/bin/bash
-
- # script de lancement via crontab echo '---------deb awipev-co2.sh -----------'
-
- # On lance la fabrication du html cd web; R -e 
-    'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html
-
-echo '---------fin awipev-co2.sh -----------'
-
-![ ](Images/awipev_server_arborescence.jpg){width=65%}
-
-<!-- ```{r Graph pour proposal, echo=FALSE, message= FALSE, warning=FALSE} -->
-
-<!-- p_sal <- ggplot() + -->
-<!--          geom_point(data=d_all%>%filter(sal_fb >28),aes(x=datetime, y=sal_fb),size=1, color="blue") + -->
-<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
-<!--          labs(y = "Salinity", x="Time")+ -->
-<!--         theme_bw() -->
-<!--  p_temp_fb <- ggplot() + -->
-<!--          geom_point(data=d_all,aes(x=datetime, y=temp_fb),size=1, color="blue") + -->
-<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
-<!--          labs(y = "Temperature (in Ferrybox)", x="Time")+ ylim(c(-2.5, 9.5)) + -->
-<!--         theme_bw() -->
-<!--  p_pco2 <- ggplot() + -->
-<!--          geom_point(data=d_all%>%filter(pco2_contros < 450),aes(x=datetime, y=pco2_contros),size=1, color="blue") + -->
-<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
-<!--          labs(y = "Corrected pCO2", x="Time")+ -->
-<!--         theme_bw() -->
-<!--  p_ta_raw <- ggplot() + -->
-<!--          geom_point(data=d_all,aes(x=datetime, y=sal_fb),size=1, color="blue") + -->
-<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
-<!--          labs(y = "Salinity", x="Time")+ -->
-<!--         theme_bw() -->
-<!--  p_sf <- ggplot() + -->
-<!--          geom_point(data=d_all,aes(x=datetime, y=pHint_tot_sf),size=1, color="blue") + -->
-<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
-<!--          labs(y = "Corrected seaFET pH", x="Time")+ -->
-<!--         theme_bw() -->
-<!--  p_df <- ggplot() + -->
-<!--          geom_point(data=d_all,aes(x=datetime, y=pH_durafet_),size=1, color="blue") + -->
-<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
-<!--          labs(y = "Corrected seaFET pH", x="Time")+ -->
-<!--         theme_bw() -->
-<!-- ggsave("../fb_figures/Plots_proposal/p_sal.png", p_sal,width = 15, height = 5 ,units="cm") -->
-<!-- ggsave("../fb_figures/Plots_proposal/p_temp_fb.png", p_temp_fb,width = 15, height = 5 ,units="cm") -->
-<!-- ggsave("../fb_figures/Plots_proposal/p_pco2.png", p_pco2,width = 15, height = 5 ,units="cm") -->
-<!-- ggsave("../fb_figures/Plots_proposal/p_sf.png", p_sf,width = 15, height = 5 ,units="cm") -->
-<!-- ggsave("../fb_figures/Plots_proposal/p_df.png", p_df,width = 15, height = 5 ,units="cm") -->
-<!-- ggsave("../fb_figures/Plots_proposal/p_ta.png", p_ta,width = 15, height = 5 ,units="cm") -->
-
-<!--  # DURAFET  -->
-<!-- durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field) -->
-<!-- durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime) -->
-<!-- dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>% -->
-<!--     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>% -->
-<!--     dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
-<!--     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>% -->
-<!--     dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>%  -->
-<!--     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>% -->
-<!--     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
-<!--     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>% -->
-<!--     dyRangeSelector(height = 30)  -->
-<!-- # SEAFET  -->
-<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field) -->
-<!-- seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime) -->
-<!-- dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>% -->
-<!--   dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>% -->
-<!--   dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
-<!--   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%  -->
-<!--   dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>% -->
-<!--     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
-<!--     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>% -->
-<!--     dyRangeSelector(height = 30)  -->
-
-<!-- ``` -->

### 2020-03-11 awipev-CO2.Rmd

@@
 # # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-# seafet_contros_xts <- dplyr::select(d_all, datetime, voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb)
-# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
-# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-#   dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
+seafet_contros_xts <- dplyr::select(d_all, datetime, at, ct)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb)
+#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
+seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+  #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
    # dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
-#     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dySeries("temp_fb", label = "temp_fb", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
-# 
-#   dySeries("sal_fb", label = "sal_fb", color ="pink",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dySeries("ct", label = "ct", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+dySeries("at", label = "at", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  #dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
    # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
  #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-#   dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
-#   dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
+  #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
+  #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
    # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
-#   dyLegend(show = "auto")   %>%
-#   dyAxis( "y2",valueRange = c(-3, 36))%>%
-#   dyAxis( "y",valueRange = c(-2, 2))%>%
-#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-#   dyRangeSelector(height = 30, dateWindow= NULL)
-# # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
+  dyLegend(show = "auto")   %>%
+  #dyAxis( "y2",valueRange = c(-3, 36))%>%
+  #dyAxis( "y",valueRange = c(-2, 2))%>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyRangeSelector(height = 30, dateWindow= NULL)
+# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
 
@@
 2015-11-18
-, 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29, 2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16, 2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03, 2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23.
+, 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29, 2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16, 2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03, 2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-08-23.
 
@@
 
-2015-08-06, 2015-08-13, 2016-05-12, 2016-05-19, 2016-06-16, 2016-07-28, 2016-09-08, 2016-10-27, 2016-11-17, 2017-01-19, 2017-03-02, 2017-04-27, 2017-09-14, 2018-04-26, 2018-05-04, 2018-05-12, 2018-05-25, 2018-06-30, 2018-07-20, 2018-08-03, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23.
+2015-08-06, 2015-08-13, 2016-05-12, 2016-05-19, 2016-06-16, 2016-07-28, 2016-09-08, 2016-10-27, 2016-11-17, 2017-01-19, 2017-03-02, 2017-04-27, 2017-09-14, 2018-04-26, 2018-05-04, 2018-05-12, 2018-05-25, 2018-06-30, 2018-07-20, 2018-08-03, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-05-03, 2019-05-10, 2019-08-23.
 
@@
 # Hence, here we save it for this use
-save(file= paste0(path, "fb_data/d_all.rds"), d_all)
+saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
 ```
@@
 ### ***p*CO~2~**
+- **2020-03-11**: Post calibration parameters for period 4 (2018-04-16 to 2018-10-31) were not taken in consideration because they lead to wrong correction.
 - **2019-11-18**: Calibration parameters from #0215-001 were added to "server.../data/NRT_data/Data_Processing_sheet_pCO2.csv" (new path).

### 2020-03-12 paper.Rmd
added one plotly plot

@@
     number_sections: false
-
+fig_width: 12 
+fig_height: 8     
 ---
@@
 library(gridExtra)
-#library(reshape2)
 library(lubridate)
@@
 library(scales)
+library(plotly)
+library(htmlwidgets)
 knitr::opts_chunk$set(echo = TRUE)
+#knitr::opts_knit$set(root.dir = normalizePath("/Users/gattuso/not_synced_git/AWIPEV-CO2-git"))
+
+#knitr::opts_chunk$set(fig.width=12, fig.height=8)
 
@@
 
-#define who is the user and define path
-if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
-if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"
+#define who is the user and define paths
+if (Sys.getenv("LOGNAME") == "gattuso") path_data = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
+if (Sys.getenv("LOGNAME") == "gattuso") path_fig = "/Users/gattuso/pCloud\ Sync/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/figures/"
+if (Sys.getenv("LOGNAME") == "samir") path_data = "../../pCloud\ Sync/exp168_awipev-CO2/"
 
@@
         panel.grid.major = element_line(size = 0.25, color="black", linetype="dashed"),
-        #aspect.ratio = 1 / 2,
+        #aspect.ratio = 1 / 3,
         plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm")
@@
 d_all <- as_tibble(
-  readRDS(file = paste0(path, "fb_data/d_all.rds"))
+  #readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
+  readRDS(file = paste0(path_data, "fb_data/d_all_copy.rds"))
 ) %>%
@@
 ## Whole time series
-```{r whole time series, fig.width=10, fig.height=15, echo=FALSE, message= FALSE}
+```{r whole time series, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
 size_point <- 1 # size of data points
@@
   Mytheme(size_labs = 8)
+ts_sal_py <- ggplotly(ts_sal,dynamicTicks = TRUE)
+filename.html <- paste0(path_fig, "ts_sal_py.html")
+saveWidget(ts_sal_py, filename.html, selfcontained = T, libdir = "lib")
 
@@
 temp_sal <- d_all %>%
-  ggplot(aes(x = sal_fb, y = temp_insitu), na.rm=TRUE) +
-  #scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
+  ggplot(aes(x = sal_fb, y = temp_insitu, col = month), na.rm=TRUE) +
   geom_point(colour="black", na.rm=TRUE, size=size_point) + 
@@
 
+den <- seacarb::rho(S = d_all$sal_fb , T = d_all$temp_insitu, P = 1)
+d_all <- d_all %>%
+  dplyr::mutate(den = den)
+ts_den <- d_all %>%
+  ggplot(aes(x = datetime, y = den), na.rm=TRUE) +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
+  labs(title="Density",x="Time", y="Density") +
+  #coord_fixed() +
+  Mytheme(size_labs = 8)
+print(ts_den)
 ```

### 2020-03-12 paper.Rmd
refined water masses chunk

@@
 
-```{r water masses, fig.width=15, fig.height=15, echo=FALSE, message= FALSE}
+```{r water masses, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
 # One tries to identify water masses coming from the Atlantic or freshwater
 temp_sal <- d_all %>%
-  ggplot(aes(x = sal_fb, y = temp_insitu, col = month), na.rm=TRUE) +
-  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
+  #dplyr::mutate(month=factor(month)) %>%
+  ggplot(aes(x = sal_fb, y = temp_insitu), na.rm=TRUE) +
+  geom_point(aes(colour=factor(month)), na.rm=TRUE, size=size_point) + 
   labs(title="Temperature vs salinity SBE45",x="Salinity", y="Temp. (°C)") +
+  facet_wrap(~ year) +
+  stat_smooth(method=lm, na.rm=TRUE, show.legend=TRUE, se=FALSE, aes(fill=factor(month), colour=factor(month))) +
   coord_fixed() +
-  Mytheme(size_labs = 8) #+
-  #theme(axis.text.x=element_blank())
-#  +annotation_custom(grob_A)
+  Mytheme(size_labs = 8) 
+  #scale_color_viridis(name="Month", discrete=FALSE, option="plasma")
 print(temp_sal)

### 2020-03-12 awipev-CO2.Rmd
rename variable T and S at the begining

@@
          ) %>%
-  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=Salinity_filtered,temp_fb=Temperature_filtered)
+  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=sal_fb_filtered, sal_insi=sal_insi_filtered, sal=sal_filtered, temp_fb=Temperature_filtered)
 ```

### 2020-03-13 awipev-CO2.Rmd
last updates with salinity name variable in awipev-co2.rmd

--- 2020-03-11 awipev-CO2.Rmd
@@
          ) %>%
-  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=Salinity_filtered,temp_fb=Temperature_filtered)
+  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=sal_fb_filtered, sal_insitu=sal_insitu_filtered, sal=sal_filtered, temp_fb=temp_fb_filtered)
 ```
@@
 #SAL
-sal_fb_xts <- dplyr::select(d_all, datetime, sal_fb)%>%
-  dplyr::filter(sal_fb >28)
-sal_fb_xts <- as.xts(sal_fb_xts, order.by = sal_fb_xts$datetime)
-dygraph(sal_fb_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
-      dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "S") %>%
+sal_xts <- dplyr::select(d_all, datetime, sal)%>%
+  dplyr::filter(sal >28)
+sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
+dygraph(sal_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
+      dySeries("sal", color = "blue", strokeWidth = 0, label = "S") %>%
       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
 # #plot of S/T
-# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal_fb>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
-#   geom_point(aes(x=datetime,y=sal_fb/5),col="red", size=0.5 )+
+# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
+#   geom_point(aes(x=datetime,y=sal/5),col="red", size=0.5 )+
 #   labs(x = "Time", y="Temperature (°C)") +
@@
 # #
-# plot(sal_fb ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
+# plot(sal ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
 # axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
@@
 # #
-# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal_fb>30 ), aes(x=datetime,y=sal_fb), colour="sal_fb") +
+# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal>30 ), aes(x=datetime,y=sal), colour="sal") +
 #   geom_point(col="blue", size=0.5 )+
@@
 d_all_at_discrete <- d_all %>% #  To remove an outlier in red
-  dplyr::select(datetime, month,closest_datetime, at, sal_fb)%>%
-  dplyr::filter( !is.na(at) & !is.na(sal_fb) & sal_fb >30)
-
-  #at != "2307.05" & sal_fb > 28, !is.na(at))
+  dplyr::select(datetime, month,closest_datetime, at, sal)%>%
+  dplyr::filter( !is.na(at) & !is.na(sal) & sal >30)
+
+  #at != "2307.05" & sal > 28, !is.na(at))
 
@@
 
-#fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal_fb)
-fit <- lm(data = d_all_at_discrete, at ~ sal_fb)
+#fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal)
+fit <- lm(data = d_all_at_discrete, at ~ sal)
 slope_s_at <- fit$coefficients[[2]]
@@
 
-at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
+at_s <- ggplot(d_all_at_discrete,aes(x=sal, y= at, label = month))+
   geom_text( aes(color=factor(month))) +
@@
 # Salinity is a predictor of AT -> using the regression defined above
-d_all$at_calc <- slope_s_at * d_all$sal_fb + intercept_s_at
+d_all$at_calc <- slope_s_at * d_all$sal + intercept_s_at
 ```
@@
 #interpolation of salinity during the FB off maintenance
-sal_fbinterp <-approx(d_all$datetime, d_all$sal_fb, xout=d_all$datetime, method="linear", rule=2)
-names(sal_fbinterp) <- c("datetime", "sal_fb_interp")
-sal_fbinterp <- as.data.frame(sal_fbinterp)
-d_all$sal_fb_interp <- sal_fbinterp$sal_fb_interp
-
-d_all$sal_fb <- ifelse(d_all$datetime > "2018-03-09 00:00:00" & d_all$datetime < "2018-04-16 16:00:00", d_all$sal_fb_interp, d_all$sal_fb)
+salinterp <-approx(d_all$datetime, d_all$sal, xout=d_all$datetime, method="linear", rule=2)
+names(salinterp) <- c("datetime", "sal_interp")
+salinterp <- as.data.frame(salinterp)
+d_all$sal_interp <- salinterp$sal_interp
+
+d_all$sal <- ifelse(d_all$datetime > "2018-03-09 00:00:00" & d_all$datetime < "2018-04-16 16:00:00", d_all$sal_interp, d_all$sal)
 
@@
 calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_field,
-                          calT = d_all$temp_insitu, calSal = d_all$sal_fb )
+                          calT = d_all$temp_insitu, calSal = d_all$sal )
 # put number of deployment 
@@
 ####
-seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu, calSal = d_all$sal_fb_interp)
+seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu, calSal = d_all$sal_interp)
 
@@
 # # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-seafet_contros_xts <- dplyr::select(d_all, datetime, at, ct)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal_fb)
+seafet_contros_xts <- dplyr::select(d_all, datetime, at, ct)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal)
 #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
             Tinsi_min = round(min(temp_insitu, na.rm=TRUE), digits = 2),
-            sal_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
-            sal_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
+            sal_max = round(max(sal, na.rm=TRUE), digits = 2),
+            sal_min = round(min(sal, na.rm=TRUE), digits = 2),
             pH_sf_max = round(max(pHint_tot_sf, na.rm=TRUE), digits = 4),
@@
 pH_sf <- d_all %>%
-  dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pHint_tot_sf)%>%
-  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal_fb)) %>%
+  dplyr::select(datetime, sal,temp_fb,temp_insitu, pHint_tot_sf)%>%
+  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal)) %>%
   dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
-pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu, Pinsi=11, S=pH_sf$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu, Pinsi=11, S=pH_sf$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
 pH_dur <- d_all %>%
-  dplyr::select(datetime, sal_fb,temp_fb,temp_insitu, pH_durafet_corrected)%>%
-  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal_fb))
-pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_insitu, Pinsi=11, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+  dplyr::select(datetime, sal,temp_fb,temp_insitu, pH_durafet_corrected)%>%
+  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal))
+pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_insitu, Pinsi=11, S=pH_dur$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
@@
 <!-- p_sal <- ggplot() + -->
-<!--          geom_point(data=d_all%>%filter(sal_fb >28),aes(x=datetime, y=sal_fb),size=1, color="blue") + -->
+<!--          geom_point(data=d_all%>%filter(sal >28),aes(x=datetime, y=sal),size=1, color="blue") + -->
 <!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
@@
 <!--  p_ta_raw <- ggplot() + -->
-<!--          geom_point(data=d_all,aes(x=datetime, y=sal_fb),size=1, color="blue") + -->
+<!--          geom_point(data=d_all,aes(x=datetime, y=sal),size=1, color="blue") + -->
 <!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->

### 2020-03-13 paper.Rmd
refined water masses chunk

--- 2020-03-12 paper.Rmd
@@
 d_all <- as_tibble(
-  #readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
-  readRDS(file = paste0(path_data, "fb_data/d_all_copy.rds"))
+  readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
+  #readRDS(file = paste0(path_data, "fb_data/d_all_copy.rds"))
 ) %>%
@@
 
-```{r water masses, fig.width=15, fig.height=15, echo=FALSE, message= FALSE}
+#Temperature vs salinity
+We explore the use of a TS diagram to investigate changes in water sources. Now need to calculate slopes and r2, and see whether some months have a consistently different behaviour.
+
+```{r temperature vs salinity, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
 # One tries to identify water masses coming from the Atlantic or freshwater
-temp_sal <- d_all %>%
-  ggplot(aes(x = sal_fb, y = temp_insitu, col = month), na.rm=TRUE) +
-  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
-  labs(title="Temperature vs salinity SBE45",x="Salinity", y="Temp. (°C)") +
+den <- rho(S = s, T = t, P = 1)
+s <- c(seq(30.4, 35.3, by=0.1)) # pCO2
+t <- seq(-2, 8, by=0.1) #temperature throughout the year
+grid <- as_tibble(expand.grid(s, t)) %>%
+  rename(s=Var1, t=Var2) %>%
+  mutate(z=rho(S = s, T = t, P = 1))
+
+tmp <- ggplot(data = z, 
+              aes(x=s, y=s, z = z), na.rm = TRUE) +
+  geom_contour()
+
+d <- d_all %>%
+  dplyr::filter(year < 2020) %>%
+  dplyr::mutate(month=month(datetime, label = TRUE, abbr = TRUE)) # abbreviated months rather than digital months
+  #ggplot(aes(x = sal_fb, y = temp_insitu), na.rm=TRUE) +
+temp_sal <-  ggplot() +
+  geom_point(data = d, aes(x = sal_fb, y = temp_insitu, fill=month), na.rm=TRUE,
+             size=size_point) + 
+  labs(title="Temperature vs salinity SBE45", x="Salinity", y="Temp. (°C)") +
+  facet_wrap(~ year, ncol = 5) +
+  stat_smooth(data = d, aes(x = sal_fb, y = temp_insitu, color=month),
+              method=lm, na.rm=TRUE, show.legend=TRUE, se=FALSE) +
+  geom_contour(data = d, aes(x = s, y = t, z = z)) +
   coord_fixed() +
-  Mytheme(size_labs = 8) #+
-  #theme(axis.text.x=element_blank())
-#  +annotation_custom(grob_A)
+  Mytheme(size_labs = 14) +
+  #scale_color_viridis(name="Month", discrete=TRUE, option="plasma")
 print(temp_sal)
+```
 
-den <- seacarb::rho(S = d_all$sal_fb , T = d_all$temp_insitu, P = 1)
+```{r density, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
 d_all <- d_all %>%
@@
   #coord_fixed() +
-  Mytheme(size_labs = 8)
+  Mytheme(size_labs = 14)
 print(ts_den)

### 2020-03-13 awipev-CO2.Rmd

@@
 ```
+
+## Salinities
+Several salinity sensors are on site, 1 inside the Ferrybox and 1 outside. Note that several CTD have been replace in situ. The sal_insitu variable combine all these CTD salinity measurements:
+
+- 1 SBE45 inside the Ferrybox (sal_fb)
+- 1 CTD at 11 meters depth (sal_insitu)
+
+Comparative approch allowed by following plots:
+
+### **Sal FB / Sal *in situ* **
+```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE}
+
+d_all <- d_all%>%
+  dplyr::mutate( sal = ifelse(sal <28, NA, sal) ,
+                 sal_fb = ifelse(sal_fb <28, NA, sal_fb),
+                 sal_insitu = ifelse(sal_insitu <28, NA, sal_insitu))
+
+fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu , nperm = 99)
+
+p_sal_fb_sal_insitu<-  ggplot(d_all,aes(x=sal_insitu, y= sal_fb, label = month))+
+  geom_text( aes(color=factor(month))) + 
+ # scale_color_viridis_d(option = "C", guide="none")+
+  geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
+  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+  labs(title = paste("Sal in situ vs Sal FB","\n Adj R2 = ", signif(fit$rsquare, 3),
+                     "; Intercept =", signif(fit$regression.results[2,2], 3),
+                     "; Slope =", signif( fit$regression.results[2,3], 3),
+                     "; P =", signif(fit$P.param, 3))) +
+  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
+  labs( x="Salinity insitu", y="Salinity FB ", color = "Months")  +theme_bw()
+print(p_sal_fb_sal_insitu)
+
+d_all$diff_sal_fb_insitu <- d_all$sal_insitu - d_all$sal_fb
+mean_diff_sal_fb_insitu <- round(mean(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)
+sd_diff_sal_fb_insitu <- round(sd(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)
+
+```
+
+The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu` ± `r sd_diff_sal_fb_insitu`°C.
+
 ## Temperatures
@@
 # # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-seafet_contros_xts <- dplyr::select(d_all, datetime, at, ct)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal)
+seafet_contros_xts <- dplyr::select(d_all, datetime, sal_fb, sal_insitu, sal)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal)
 #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dySeries("ct", label = "ct", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-dySeries("at", label = "at", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  #dySeries("temp_insitu", label = "temp_insitu", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dySeries("sal_insitu", label = "sal_insitu", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
    # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
@@
 ### **FerryBox**
+
+- **2020-03-13**: Salinity was filtered above 28 in d_all.rds file.
 - **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.

### 2020-03-16 awipev-CO2.Rmd

@@
                  sal_insitu = ifelse(sal_insitu <28, NA, sal_insitu))
+  d_all <- d_all%>%
+  dplyr::mutate( sal = ifelse(datetime > "2019-12-26 00:00:00", NA, sal),
+                 sal_insitu = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu))
 

### 2020-03-17 awipev-CO2.Rmd
sal_fb takken in consideration

@@
 
-```
-
-The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu` ± `r sd_diff_sal_fb_insitu`°C.
+# PLOT
+seafet_contros_xts <- dplyr::select(d_all, datetime, sal_fb, sal_insitu, sal)
+seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+  dySeries("sal_insitu", label = "sal_insitu", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
+dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dyLegend(show = "auto")   %>%
+  #dyAxis( "y2",valueRange = c(-3, 36))%>%
+  #dyAxis( "y",valueRange = c(-2, 2))%>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyRangeSelector(height = 30, dateWindow= NULL)
+
+#Plot for philipp
+sal_15 <- ggplot(data= d_all%>%dplyr::filter(datetime > "2015-10-01 00:00:00" & datetime < "2015-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
+geom_point(aes(y=sal_fb,col="FB") , size=2) +
+geom_point(aes(y=sal_insitu, col="in situ"))  +
+labs(title=  "salinity 2015", x = "Time", y= "")
+
+sal_19 <-ggplot(data= d_all%>%dplyr::filter(datetime > "2019-10-01 00:00:00" & datetime < "2019-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
+geom_point(aes(y=sal_fb,col="FB") , size=2) +
+geom_point(aes(y=sal_insitu, col="in situ"))  +
+labs(title=  "salinity 2019", x = "Time", y= "")
+
+ggsave("figures/sal_2019.png", sal_19, units="cm")
+ggsave("figures/sal_2015.png", sal_15, units="cm")
+ggsave("figures/sal_property.png", p_sal_fb_sal_insitu, units="cm")
+
+```
+
+The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu` ± `r sd_diff_sal_fb_insitu` PSU.
 

### 2020-03-19 paper.Rmd
temp sal analyses

--- 2020-03-12 paper.Rmd
@@
 library(htmlwidgets)
+library(tsibble)
+if (!require("directlabels")) install.packages("directlabels")
+library("directlabels")
 knitr::opts_chunk$set(echo = TRUE)
@@
 ```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
-d_all <- as_tibble(
-  #readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
-  readRDS(file = paste0(path_data, "fb_data/d_all_copy.rds"))
-) %>%
-  filter(sal_fb > 28) # remove salinity data lower than 28
+d_all <- as_tibble(readRDS(file = paste0(path_data, "fb_data/d_all_copy.rds"))) %>% 
+  dplyr::filter(sal_fb > 28) %>% # remove salinity data lower than 28
+  dplyr::mutate(year_month = format(datetime, '%Y-%m'))
 ```
@@
 
-```{r water masses, fig.width=15, fig.height=15, echo=FALSE, message= FALSE}
+#Temperature vs salinity
+We explore the use of a TS diagram to investigate changes in water sources. Now need to calculate slopes and r2, and see whether some months have a consistently different behaviour.
+
+```{r temperature vs salinity plots, fig.width=8, fig.height=8, echo=FALSE, message= FALSE}
 # One tries to identify water masses coming from the Atlantic or freshwater
-temp_sal <- d_all %>%
-  ggplot(aes(x = sal_fb, y = temp_insitu, col = month), na.rm=TRUE) +
-  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
-  labs(title="Temperature vs salinity SBE45",x="Salinity", y="Temp. (°C)") +
+s <- c(seq(30.4, 35.3, length.out = 100)) # pCO2
+t <- seq(-2, 8, length.out = 100) #temperature throughout the year
+grid <- as_tibble(expand.grid(s=s, t=t))
+grid$z <- rho(S = grid$s, T = grid$t, P = 1)
+
+d <- d_all %>%
+  dplyr::filter(year < 2020) %>%
+  dplyr::mutate(month=month(datetime, label = TRUE, abbr = TRUE)) # abbreviated months rather than digital months
+  #ggplot(aes(x = sal_fb, y = temp_insitu), na.rm=TRUE) +
+temp_sal <-  ggplot() +
+  geom_point(data = d, aes(x = sal_fb, y = temp_insitu, fill=month), na.rm=TRUE,
+             size=size_point, show.legend=FALSE) + 
+  labs(title="Temperature vs salinity, blue lines show density", x="Salinity", y="Temp. (°C)") +
+  facet_wrap(~ year, ncol = 3) +
+  stat_smooth(data = d, aes(x = sal_fb, y = temp_insitu, color=month),
+              method=lm, na.rm=TRUE, se=FALSE) +
+  scale_color_viridis(name="Month", discrete=TRUE, option="plasma") +
+  geom_contour(data = grid, aes(x = s, y = t, z = z), 
+               stat = "contour", binwidth=1, show.legend=FALSE) +
+  #stat_contour(aes(colour=..level..), breaks=seq(1025, 1028, by=1)) +
   coord_fixed() +
-  Mytheme(size_labs = 8) #+
-  #theme(axis.text.x=element_blank())
-#  +annotation_custom(grob_A)
-print(temp_sal)
+  Mytheme(size_labs = 10)
+ggsave(temp_sal,filename = paste0(path_fig, "temp_sal.png"), width = 20, height = 20 ,units="cm")
+temp_sal_py <- ggplotly(temp_sal,dynamicTicks = TRUE)
+filename.html <- paste0(path_fig, "temp_sal_py.html")
+saveWidget(temp_sal_py, filename.html, selfcontained = T, libdir = "lib")
+```
 
-den <- seacarb::rho(S = d_all$sal_fb , T = d_all$temp_insitu, P = 1)
-d_all <- d_all %>%
-  dplyr::mutate(den = den)
-ts_den <- d_all %>%
-  ggplot(aes(x = datetime, y = den), na.rm=TRUE) +
-  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
-  labs(title="Density",x="Time", y="Density") +
-  #coord_fixed() +
-  Mytheme(size_labs = 8)
-print(ts_den)
+```{r temperature vs salinity regressions, fig.width=8, fig.height=8, echo=FALSE, message= FALSE}
+# AT as a function of salinity for every year
+j <- 0
+reg <- data.frame()
+for (i in 1:length(unique(d$year_month))) { #one loops through all years
+  j <- j + 1
+  ym <- unique(d$year_month)[i]
+  d_reg <- filter(d, year_month==ym)
+  if (length(!is.na(d_reg$temp_fb)) > 2) { #there is no temp_insitu in 2016-08, hence skip. Not needed if one uses temp_fb
+  lms <- summary(lm(data=d_reg, sal_fb ~ temp_fb))
+  # calculate probability of fstatistic because it cannot be extracted from lms above
+  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
+  # slope returned by lm is per second
+  prob <- pf(lms$fstatistic[1],lms$fstatistic[2],lms$fstatistic[3],lower.tail=FALSE)
+  reg <- rbind(reg, as.numeric(c(lms$coefficients[2,1], lms$coefficients[2,2], 
+                                 lms$coefficients[2,4], lms$coefficients[1,1], lms$coefficients[1,2],
+                                 lms$coefficients[1,4], lms$fstatistic[1], lms$fstatistic[3], lms$r.squared, prob)))
+  }
+}
+names(reg) <- c("Slope", "SE Slope", "P Slope","Intercept","SE int.","P int.", "F", "df",
+                "R2","P value")
+row.names(reg) <- as.character(unique(d$year_month))
+#transform in latex table and save
+tab_reg_temp_sal <- reg
+tmp_reg_temp_sal <- reg %>% # to enable plotting below
+  dplyr::mutate(date = as.Date(paste0(row.names(reg), "-01")),
+                month = month(date, label=TRUE, abbr = TRUE))
+#plot
+fig_reg_temp_sal <- tmp_reg_temp_sal %>%
+  ggplot() +
+  geom_point(aes(x=date, y=Slope, color=month), size=5) +
+  scale_color_viridis(name="Month", discrete = TRUE) +
+  Mytheme(size_labs = 14)
+fig_reg_temp_sal
 ```
+kable(tab_fig_dyf_surf_date_AT)
+print(dyf_surf_salinity_AT)
+
+```{r density, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+# d_all <- d_all %>%
+#   dplyr::mutate(den = den)
+# ts_den <- d_all %>%
+#   ggplot(aes(x = datetime, y = den), na.rm=TRUE) +
+#   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+#   geom_point(colour="black", na.rm=TRUE, size=size_point) + 
+#   labs(title="Density",x="Time", y="Density") +
+#   #coord_fixed() +
+#   Mytheme(size_labs = 14)
+# print(ts_den)
+```
+
+```{r pangaea data, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+data_2015 <- pg_data(doi="10.1594/PANGAEA.896771", overwrite = TRUE)
+data_2016 <- pg_data(doi="10.1594/PANGAEA.896770", overwrite = TRUE)
+data_2017 <- pg_data(doi="10.1594/PANGAEA.896170", overwrite = TRUE)
+data_2018 <- pg_data(doi="10.1594/PANGAEA.897349", overwrite = TRUE)
+tmp <- rbind(data_2015[[1]]$data, data_2016[[1]]$data, data_2017[[1]]$data, data_2018[[1]]$data)
+tmp <- tmp[, c(1,8)] # select date time and salinity
+tmp$`Date/Time` <- as.POSIXct(strptime(tmp$`Date/Time`, "%Y-%m-%dT%H:%M", tz = "UTC"))
+
+all_data <- tmp %>%
+  dplyr::filter(!are_duplicated(tmp)) %>%
+  dplyr::rename(datetime = `Date/Time`,
+                sal = `Sal ([PSU])`) %>%
+  as_tsibble(key = NULL, index = datetime) %>%
+  fill_gaps()
+
+all_data %>%
+  ggplot() +
+  geom_point(aes(x=datetime, y=sal), na.rm = TRUE)
+```

### 2020-03-19 paper.Rmd
finalized temp and salinity

@@
 library("directlabels")
+if (!require("pangaear")) install.packages("pangaear")
+library("pangaear")
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-# TEMP in situ SBE38
+# TEMP ferrybox
 ts_temp <- d_all %>%
-  ggplot(aes(x = datetime, y = temp_insitu), na.rm=TRUE) +
+  ggplot(aes(x = datetime, y = temp_fb), na.rm=TRUE) +
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
   geom_point(colour="black", na.rm=TRUE, size=size_point) + 
-  labs(title="Temperature SBE38",x="", y="In situ temperature (°C)") +
+  labs(title="Temperature FerryBox",x="", y="In situ temperature (°C)") +
   #coord_fixed() +
@@
 #Temperature vs salinity
-We explore the use of a TS diagram to investigate changes in water sources. Now need to calculate slopes and r2, and see whether some months have a consistently different behaviour.
+We explore the use of a TS diagram to investigate changes in water sources.
+Monthly slopes of the T vs S plots are calculated.
+It seems that slopes are mostly not significant in winter and that they can be both positive and negative in summer.
 
@@
 temp_sal <-  ggplot() +
-  geom_point(data = d, aes(x = sal_fb, y = temp_insitu, fill=month), na.rm=TRUE,
+  geom_point(data = d, aes(x = sal_fb, y = temp_fb, fill=month), na.rm=TRUE,
              size=size_point, show.legend=FALSE) + 
-  labs(title="Temperature vs salinity, blue lines show density", x="Salinity", y="Temp. (°C)") +
+  labs(title="Temperature vs salinity, both in FerryBox, blue lines show density", x="Salinity", y="Temp. (°C)") +
   facet_wrap(~ year, ncol = 3) +
-  stat_smooth(data = d, aes(x = sal_fb, y = temp_insitu, color=month),
+  stat_smooth(data = d, aes(x = sal_fb, y = temp_fb, color=month),
               method=lm, na.rm=TRUE, se=FALSE) +
@@
   geom_contour(data = grid, aes(x = s, y = t, z = z), 
-               stat = "contour", binwidth=1, show.legend=FALSE) +
-  #stat_contour(aes(colour=..level..), breaks=seq(1025, 1028, by=1)) +
+               stat = "contour", binwidth=1, show.legend=FALSE, na.rm=TRUE) +
+  scale_x_continuous(limits = c(30.4, 35.3), expand = c(0,0) ) +
+  scale_y_continuous(limits = c(-2,8.5), expand = c(0,0) ) +
   coord_fixed() +
+  annotate("text", label="Fresh and cold", x=31.5, y=-1.5) +
+  annotate("text", label="Salty and warm", x=34.5, y=8.1) +
   Mytheme(size_labs = 10)
@@
 ```
+print(temp_sal)
 
-```{r temperature vs salinity regressions, fig.width=8, fig.height=8, echo=FALSE, message= FALSE}
+```{r temperature vs salinity regressions, fig.width=6, fig.height=6, echo=FALSE, message= FALSE}
 # AT as a function of salinity for every year
@@
 }
-names(reg) <- c("Slope", "SE Slope", "P Slope","Intercept","SE int.","P int.", "F", "df",
-                "R2","P value")
+names(reg) <- c("Slope", "SE_Slope", "P Slope","Intercept","SE int.","P int.", "F", "df",
+                "R2","P_value")
 row.names(reg) <- as.character(unique(d$year_month))
@@
 fig_reg_temp_sal <- tmp_reg_temp_sal %>%
+  dplyr::filter(P_value < .05) %>% #eliminate when correlation not significant
   ggplot() +
-  geom_point(aes(x=date, y=Slope, color=month), size=5) +
-  scale_color_viridis(name="Month", discrete = TRUE) +
-  Mytheme(size_labs = 14)
+  labs(title = "Slope ± 2 x SE", subtitle = "3 months with correlation coefficient not significant were eliminated") +
+  geom_point(aes(x=date, y=Slope, color=month, size=P_value)) +
+  scale_color_viridis(discrete = TRUE) +
+  #scale_fill_continuous(name="P value slope") +
+  geom_hline(yintercept = 0) + 
+  scale_size_continuous(range = c(3,7)) +
+  geom_errorbar(aes(x=date, ymin=Slope-2*SE_Slope, ymax=Slope+2*SE_Slope), width=.2) +
+  Mytheme(size_labs = 14) +
+  guides(colour = guide_legend("Month", override.aes = list(size=4)), size = guide_legend("P value slope"))
 fig_reg_temp_sal
 ```
-kable(tab_fig_dyf_surf_date_AT)
-print(dyf_surf_salinity_AT)
+kable(tab_reg_temp_sal)
+print(fig_reg_temp_sal)
 

### 2020-03-19 paper.Rmd
prettier html

@@
     number_sections: false
+theme: cerulean
 fig_width: 12 
@@
 ---
+
+<style type="text/css">
+
+body{ /* Normal  */
+      font-size: 16px;
+  }
+td {  /* Table  */
+  font-size: 8px;
+}
+h1.title {
+  font-size: 38px;
+  color: DarkRed;
+}
+h1 { /* Header 1 */
+  font-size: 28px;
+  color: DarkBlue;
+}
+h2 { /* Header 2 */
+    font-size: 22px;
+  color: DarkBlue;
+}
+h3 { /* Header 3 */
+  font-size: 18px;
+  font-family: "Times New Roman", Times, serif;
+  color: DarkBlue;
+}
+code.r{ /* Code block */
+    font-size: 12px;
+}
+pre { /* Code block - determines code spacing between lines */
+    font-size: 14px;
+}
+</style>
 
@@
 
-#Temperature vs salinity
+## Temperature vs salinity
 We explore the use of a TS diagram to investigate changes in water sources.
@@
 It seems that slopes are mostly not significant in winter and that they can be both positive and negative in summer.
+
+**To do when the situation of the in situ CTDs will be clarified**: compare salinity values from the Ferrybox and in situ.
 
@@
   Mytheme(size_labs = 10)
+print(temp_sal)
 ggsave(temp_sal,filename = paste0(path_fig, "temp_sal.png"), width = 20, height = 20 ,units="cm")
@@
 ```
-print(temp_sal)
 
@@
   guides(colour = guide_legend("Month", override.aes = list(size=4)), size = guide_legend("P value slope"))
-fig_reg_temp_sal
-```
 kable(tab_reg_temp_sal)
 print(fig_reg_temp_sal)
+```
 
@@
 
-```{r pangaea data, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+```{r pangaea data, fig.width=9, fig.height=6, echo=FALSE, message= FALSE}
 data_2015 <- pg_data(doi="10.1594/PANGAEA.896771", overwrite = TRUE)
@@
 tmp <- rbind(data_2015[[1]]$data, data_2016[[1]]$data, data_2017[[1]]$data, data_2018[[1]]$data)
-tmp <- tmp[, c(1,8)] # select date time and salinity
+tmp <- tmp[, c(1, 8, 11)] # select date time and salinity
 tmp$`Date/Time` <- as.POSIXct(strptime(tmp$`Date/Time`, "%Y-%m-%dT%H:%M", tz = "UTC"))
 
-all_data <- tmp %>%
+pg_ts <- tmp %>% #Pangaea time series
   dplyr::filter(!are_duplicated(tmp)) %>%
   dplyr::rename(datetime = `Date/Time`,
-                sal = `Sal ([PSU])`) %>%
+                sal = `Sal ([PSU])`,
+                temp = `Temp [°C]`) %>%
   as_tsibble(key = NULL, index = datetime) %>%
@@
 
-all_data %>%
+fig_sal_pangaea <- pg_ts %>%
   ggplot() +
-  geom_point(aes(x=datetime, y=sal), na.rm = TRUE)
+  geom_point(aes(x=datetime, y=sal), na.rm = TRUE) +
+  labs(title="Salinity recovered from Pangaea") +
+  Mytheme(size_labs = 14)
+print(fig_sal_pangaea)
+
+fig_temp_pangaea <- pg_ts %>%
+  ggplot() +
+  geom_point(aes(x=datetime, y=temp), na.rm = TRUE) +
+  labs(title="Temperature recovered from Pangaea") +
+  Mytheme(size_labs = 14)
+print(fig_temp_pangaea)
 ```
+
+## Total alkalinity
+It is proposed not to use the data from the Contros instrument. It is too unfeliable and difficult to calibrate. We use instead the relationship between salinity and the discrete measurements of AT.

### 2020-03-21 awipev-CO2.Rmd
variable modification ; sal temp

@@
          ) %>%
-  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=sal_fb_filtered, sal_insitu=sal_insitu_filtered, sal=sal_filtered, temp_fb=temp_fb_filtered)
+  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu_11m=temp_insitu_11m_filtered, sal_fb=sal_fb_filtered, sal_insitu_ctds=sal_insitu_ctds_filtered, temp_fb=temp_fb_filtered)
 ```
@@
 ### **Sal FB / Sal *in situ* **
-```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE}
+```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+########### Binding sal_fb INTO sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
+d_all <- d_all %>%
+  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu))
 
@@
 
-#Plot for philipp
-sal_15 <- ggplot(data= d_all%>%dplyr::filter(datetime > "2015-10-01 00:00:00" & datetime < "2015-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
-geom_point(aes(y=sal_fb,col="FB") , size=2) +
-geom_point(aes(y=sal_insitu, col="in situ"))  +
-labs(title=  "salinity 2015", x = "Time", y= "")
-
-sal_19 <-ggplot(data= d_all%>%dplyr::filter(datetime > "2019-10-01 00:00:00" & datetime < "2019-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
-geom_point(aes(y=sal_fb,col="FB") , size=2) +
-geom_point(aes(y=sal_insitu, col="in situ"))  +
-labs(title=  "salinity 2019", x = "Time", y= "")
-
-ggsave("figures/sal_2019.png", sal_19, units="cm")
-ggsave("figures/sal_2015.png", sal_15, units="cm")
-ggsave("figures/sal_property.png", p_sal_fb_sal_insitu, units="cm")
+# #Plot for philipp
+# sal_15 <- ggplot(data= d_all%>%dplyr::filter(datetime > "2015-10-01 00:00:00" & datetime < "2015-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
+# geom_point(aes(y=sal_fb,col="FB") , size=2) +
+# geom_point(aes(y=sal_insitu, col="in situ"))  +
+# labs(title=  "salinity 2015", x = "Time", y= "")
+# 
+# sal_19 <-ggplot(data= d_all%>%dplyr::filter(datetime > "2019-10-01 00:00:00" & datetime < "2019-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
+# geom_point(aes(y=sal_fb,col="FB") , size=2) +
+# geom_point(aes(y=sal_insitu, col="in situ"))  +
+# labs(title=  "salinity 2019", x = "Time", y= "")
+# 
+# ggsave("figures/sal_2019.png", sal_19, units="cm")
+# ggsave("figures/sal_2015.png", sal_15, units="cm")
+# ggsave("figures/sal_property.png", p_sal_fb_sal_insitu, units="cm")
 
@@
 # # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-seafet_contros_xts <- dplyr::select(d_all, datetime, sal_fb, sal_insitu, sal)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal)
+seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal)
 #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dySeries("sal_insitu", label = "sal_insitu", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dySeries("temp_insitu", label = "temp_insitu", color ="red", strokeWidth=0, pointSize=2) %>%
+dySeries("temp_fb", label = "temp_fb", color ="blue", strokeWidth=0, pointSize=2) %>%
+ # dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
    # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
@@
   #dyAxis( "y2",valueRange = c(-3, 36))%>%
-  #dyAxis( "y",valueRange = c(-2, 2))%>%
+  dyAxis( "y",valueRange = c(-3, 9))%>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%

### 2020-03-23 awipev-CO2.Rmd
sal_mix and temp_mix modifications done

--- 2020-03-16 awipev-CO2.Rmd
@@
 pH_seafet <- pH_seafet %>%
-  dplyr::mutate(pH_s_seafet_temp_field = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_field, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$salinity_field,Pt=0,Sit=0))
+  dplyr::mutate(pH_s_seafet_temp_insitu = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_field, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$salinity_field,Pt=0,Sit=0))
 
@@
 pH_durafet <- pH_durafet %>%
-  dplyr::mutate(pH_s_durafet_temp_field = pHinsi(pH=pH_durafet$pH_s_durafet,ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_field, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$salinity_field,Pt=0,Sit=0))
+  dplyr::mutate(pH_s_durafet_temp_insitu = pHinsi(pH=pH_durafet$pH_s_durafet,ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_field, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$salinity_field,Pt=0,Sit=0))
 
@@
 pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(datetime,pH_s_seafet_temp_field)%>% 
+  dplyr::select(datetime,pH_s_seafet_temp_insitu)%>% 
   dplyr::group_by(datetime) %>% 
-  dplyr::summarize(pH_s_seafet_temp_field = mean(pH_s_seafet_temp_field, na.rm = T))
+  dplyr::summarize(pH_s_seafet_temp_insitu = mean(pH_s_seafet_temp_insitu, na.rm = T))
 pH_durafet_mean <- pH_durafet%>%
-  dplyr::select(datetime,pH_s_durafet_temp_field)%>% 
+  dplyr::select(datetime,pH_s_durafet_temp_insitu)%>% 
   dplyr::group_by(datetime) %>% 
-  dplyr::summarize(pH_s_durafet_temp_field = mean(pH_s_durafet_temp_field, na.rm = T))
+  dplyr::summarize(pH_s_durafet_temp_insitu = mean(pH_s_durafet_temp_insitu, na.rm = T))
 
@@
          ) %>%
-  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=sal_fb_filtered, sal_insitu=sal_insitu_filtered, sal=sal_filtered, temp_fb=temp_fb_filtered)
+  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered)
 ```
@@
   #drop_na() %>%
-  dplyr::select(closest_datetime, pH_s_seafet_temp_field) %>%
+  dplyr::select(closest_datetime, pH_s_seafet_temp_insitu) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
   #drop_na() %>%
-  dplyr::select(closest_datetime, pH_s_durafet_temp_field) %>%
+  dplyr::select(closest_datetime, pH_s_durafet_temp_insitu) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 
+```{r Sal filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
+#### filter salinities above 28
+d_all <- d_all%>%
+  dplyr::mutate( sal_fb = ifelse(sal_fb <28, NA, sal_fb),
+                 sal_insitu_ctd = ifelse(sal_insitu_ctd <28, NA, sal_insitu_ctd))
+ d_all <- d_all%>%
+  dplyr::mutate(sal_insitu_ctd = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu_ctd))
+
+########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
+d_all <- d_all %>%
+  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, 
+                               ifelse (pressure_insitu_ctd_filtered >=8 ,sal_insitu_ctd, NA )))
+### remove sal_mix datat that seem to be to high compared to sal_fb
+  d_all <- d_all%>%
+  dplyr::mutate(sal_mix = ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-13 18:00:00" , NA, 
+                          ifelse(datetime > "2018-05-21 19:00:00" & datetime < "2018-05-24 17:00:00" , NA,
+                          ifelse(datetime > "2018-05-28 06:00:00" & datetime < "2018-06-03 13:00:00" , NA,
+                          ifelse(datetime > "2018-06-16 06:00:00" & datetime < "2018-06-21 05:00:00" , NA,
+                          ifelse(datetime > "2019-12-02 08:00:00" & datetime < "2019-12-03 08:00:00" , NA,
+                          ifelse(datetime > "2019-12-09 07:00:00" & datetime < "2019-12-09 10:00:00" , NA, 
+                          ifelse(datetime > "2019-12-09 15:00:00" & datetime < "2019-12-09 18:00:00" , NA,
+                          ifelse(datetime > "2019-12-10 14:00:00" & datetime < "2019-12-10 18:00:00", NA, sal_mix)))))))))
+
+```
+
+```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
+###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
+d_all <- d_all %>%
+  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, 
+                               ifelse (pressure_insitu_ctd_filtered >=8 ,temp_insitu_ctd, NA )))
+```
+
 ## Whole time series
 ```{r whole time series, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-#SAL
-sal_xts <- dplyr::select(d_all, datetime, sal)%>%
-  dplyr::filter(sal >28)
+#SAL MIX
+sal_xts <- dplyr::select(d_all, datetime, sal_mix)
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
 dygraph(sal_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
-      dySeries("sal", color = "blue", strokeWidth = 0, label = "S") %>%
+      dySeries("sal_mix", color = "blue", strokeWidth = 0, label = "S") %>%
       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
 # TEMP insitu SBE38
-temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu)
+temp_insitu_xts <- dplyr::select(d_all, datetime, temp_mix)
 temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
-dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ)", ylab="Temperature") %>%
-      dySeries("temp_insitu", color = "blue", strokeWidth = 0, label = "T") %>%
+dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ 11 m)", ylab="Temperature") %>%
+      dySeries("temp_mix", color = "blue", strokeWidth = 0, label = "T") %>%
       dyAxis("y", valueRange = c(-2.8, 10)) %>%
@@
 # DURAFET 
-durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field)
+durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_insitu)
 durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
@@
     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pH_s_durafet_temp_insitu", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
@@
 # SEAFET 
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field)
+seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_insitu)
 seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
@@
   dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+  dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
@@
 
-```{r water masses, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-# One tries to identify water masses coming from the Atlantic or freshwater
-
-```
-
 ## Salinities
-Several salinity sensors are on site, 1 inside the Ferrybox and 1 outside. Note that several CTD have been replace in situ. The sal_insitu variable combine all these CTD salinity measurements:
+Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically.
+Salinity from FB is taken in consideration.
+If data gaps are encountered, they are filled with bottom salinty data from ctd (> 8 m).
+New column "sal_mix" is created.
 
 - 1 SBE45 inside the Ferrybox (sal_fb)
-- 1 CTD at 11 meters depth (sal_insitu)
+- 5 CTD > 8 meters depth (sal_insitu_ctd)
 
@@
 
-### **Sal FB / Sal *in situ* **
-```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-
-d_all <- d_all%>%
-  dplyr::mutate( sal = ifelse(sal <28, NA, sal) ,
-                 sal_fb = ifelse(sal_fb <28, NA, sal_fb),
-                 sal_insitu = ifelse(sal_insitu <28, NA, sal_insitu))
-  d_all <- d_all%>%
-  dplyr::mutate( sal = ifelse(datetime > "2019-12-26 00:00:00", NA, sal),
-                 sal_insitu = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu))
-
-fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu , nperm = 99)
-
-p_sal_fb_sal_insitu<-  ggplot(d_all,aes(x=sal_insitu, y= sal_fb, label = month))+
+### **Sal FB / Sal CTD > 8 m **
+
+Property-property salinity plot using:
+
+fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)
+
+```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)
+
+p_sal_fb_sal_insitu<-  ggplot(d_all,aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
 
-```
-
-The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu` ± `r sd_diff_sal_fb_insitu`°C.
+# # PLOT
+# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_insitu_11m, temp_insitu_ctd, pressure_insitu_ctd_filtered, temp_mix, sal_mix)
+# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+# dySeries("temp_insitu_11m", label = "temp_insitu_11m", color ="red",axis= "y2", strokeWidth=0, pointSize=4) %>%
+# dySeries("temp_insitu_ctd", label = "temp_insitu_ctd", color ="blue",axis= "y2", strokeWidth=0, pointSize=3) %>%
+# dySeries("temp_mix", label = "temp_mix", color ="green",axis= "y2", strokeWidth=0, pointSize=2) %>%
+# dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
+# dySeries("pressure_insitu_ctd_filtered", label = "pressure_insitu_ctd_filtered", color ="black", strokeWidth=0, pointSize=2) %>%
+#   dyLegend(show = "onmouseover")   %>%
+#   #dyAxis( "y2",valueRange = c(-3, 36))%>%
+#   dyAxis( "y2",valueRange = c(-3, 36))%>%
+#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+#   dyRangeSelector(height = 30, dateWindow= NULL)
+
+# #Plot for philipp
+# sal_15 <- ggplot(data= d_all%>%dplyr::filter(datetime > "2015-10-01 00:00:00" & datetime < "2015-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
+# geom_point(aes(y=sal_fb,col="FB") , size=2) +
+# geom_point(aes(y=sal_insitu, col="in situ"))  +
+# labs(title=  "salinity 2015", x = "Time", y= "")
+# 
+# sal_19 <-ggplot(data= d_all%>%dplyr::filter(datetime > "2019-10-01 00:00:00" & datetime < "2019-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
+# geom_point(aes(y=sal_fb,col="FB") , size=2) +
+# geom_point(aes(y=sal_insitu, col="in situ"))  +
+# labs(title=  "salinity 2019", x = "Time", y= "")
+# 
+# ggsave("figures/sal_2019.png", sal_19, units="cm")
+# ggsave("figures/sal_2015.png", sal_15, units="cm")
+# ggsave("figures/sal_property.png", p_sal_fb_sal_insitu, units="cm")
+
+```
+
+The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu` ± `r sd_diff_sal_fb_insitu` PSU.
 
 ## Temperatures
-Several temperature sensors are on site, 1 inside the Ferrybox and 2 outside:
+Several temperature sensors are on site, 1 inside the Ferrybox (SBE45), 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically and 1 fixed at 11 m depth (sbe38). 
+Temperature in situ at 11 m depth is taken in consideration.
+If data gaps are encountered, they are filled with bottom temperature data from ctd (> 8 m).
+New column "temp_mix" is created.
+For the moment, no gaps are encountered and temp_mix = temp_insitu_11m.
 
 - 1 SBE45 inside the Ferrybox (temp_fb)
-- 1 seaFET T°C inside the seaFET at 11 meters depth (T_seaF)
-- 1 SBE38 at 11 meters depth (temp_insitu)
+- 5 CTD > 8 meters depth (sal_insitu_ctd)
+- 5 fixed at 11 meters depth (sal_insitu_11m)
 
@@
 
-### **T seaFET / T in situ **
+### **T seaFET / T mix **
+
+Property-property temperature plot using:
+
+fit <- lmodel2(data = d_all,  T_seaF ~ temp_mix , nperm = 99)
+
 ```{r Temp comparaison, echo=FALSE, message= FALSE, warning=FALSE}
@@
 
-fit <- lmodel2(data = d_all,  T_seaF ~ temp_insitu , nperm = 99)
-
-pTseaf_Tinsi<-  ggplot(d_all,aes(x=temp_insitu, y= T_seaF, label = month))+
+fit <- lmodel2(data = d_all,  T_seaF ~ temp_mix , nperm = 99)
+
+pTseaf_Tinsi<-  ggplot(d_all,aes(x=temp_mix, y= T_seaF, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
 
-d_all$diff_T_seaF_insitu <- d_all$T_seaF - d_all$temp_insitu
+d_all$diff_T_seaF_insitu <- d_all$T_seaF - d_all$temp_mix
 mean_diff_T_seaF_insitu <- round(mean(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)
@@
 
-### **T Ferrybox / T in situ **
+### **T Ferrybox / T mix **
+
+Property-property temperature plot using:
+
+fit <- lmodel2(data = d_all,  temp_fb ~ temp_mix , nperm = 99)
+
 ```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
@@
 
-fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu , nperm = 99)
-
-pTfb_Tinsi<-  ggplot(d_all,aes(x=temp_insitu, y= temp_fb, label = month))+
+fit <- lmodel2(data = d_all,  temp_fb ~ temp_mix , nperm = 99)
+
+pTfb_Tinsi<-  ggplot(d_all,aes(x=temp_mix, y= temp_fb, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
 
-d_all$diff_T_fb_insitu <- d_all$T_seaF - d_all$temp_insitu
+d_all$diff_T_fb_insitu <- d_all$T_seaF - d_all$temp_mix
 mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
@@
 The mean difference between T seaFET and in situ is: `r mean_diff_T_fb_insitu` ± `r sd_diff_T_fb_insitu`°C.
+
+### **T 11 m / T CTD > 8 m **
+
+Property-property temperature plot using:
+
+fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)
+
+```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
+
+fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)
+
+p<-  ggplot(d_all,aes(x=temp_insitu_ctd, y= temp_insitu_11m, label = month))+
+  geom_text( aes(color=factor(month))) + 
+ # scale_color_viridis_d(option = "C", guide="none")+
+  geom_line(aes(x = temp_insitu_11m, y = temp_insitu_11m), linetype = "dashed") +
+  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+  labs(title = paste("T FB vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
+                     "; Intercept =", signif(fit$regression.results[2,2], 3),
+                     "; Slope =", signif( fit$regression.results[2,3], 3),
+                     "; P =", signif(fit$P.param, 3))) +
+  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
+  labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
+print(p)
+
+d_all$diff_T_fb_insitu <- d_all$T_seaF - d_all$temp_insitu_ctd
+mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
+sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
+```
 
@@
   - and during the **third period**, with the new analyzer (2018-01-07 to 2018-06-20)
-
-```{r TA 2nd cleaning , echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
-
-```
 
@@
 d_all_at_discrete <- d_all %>% #  To remove an outlier in red
-  dplyr::select(datetime, month,closest_datetime, at, sal)%>%
-  dplyr::filter( !is.na(at) & !is.na(sal) & sal >30)
+  dplyr::select(datetime, month,closest_datetime, at, sal_mix) #%>%
+ # dplyr::filter( !is.na(at) & !is.na(sal) & sal >30)
 
@@
 #fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal)
-fit <- lm(data = d_all_at_discrete, at ~ sal)
+fit <- lm(data = d_all_at_discrete, at ~ sal_mix)
 slope_s_at <- fit$coefficients[[2]]
@@
 
-at_s <- ggplot(d_all_at_discrete,aes(x=sal, y= at, label = month))+
+at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at, label = month))+
   geom_text( aes(color=factor(month))) +
@@
 # Salinity is a predictor of AT -> using the regression defined above
-d_all$at_calc <- slope_s_at * d_all$sal + intercept_s_at
+d_all$at_calc <- slope_s_at * d_all$sal_mix + intercept_s_at
 ```
@@
 # sfPeriod <- d_all%>%
-#   dplyr::select(datetime, pH_s_seafet_temp_field)%>%
-#   dplyr::filter(!is.na(pH_s_seafet_temp_field))
+#   dplyr::select(datetime, pH_s_seafet_temp_insitu)%>%
+#   dplyr::filter(!is.na(pH_s_seafet_temp_insitu))
 # # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
@@
 ####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_field,
+calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_insitu,
                           calT = d_all$temp_insitu, calSal = d_all$sal )
@@
 d_all <- d_all%>%
-  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", pH_s_seafet_temp_field, NA ))
-
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field,pHint_tot_sf, pH_s_sf_no_calb)
+  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", pH_s_seafet_temp_insitu, NA ))
+
+seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_insitu,pHint_tot_sf, pH_s_sf_no_calb)
 #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
     dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_seafet_temp_field", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pH_s_seafet_temp_insitu", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
     dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
@@
 # # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-seafet_contros_xts <- dplyr::select(d_all, datetime, sal_fb, sal_insitu, sal)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal)
+seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_insitu, T_seaF, temp_fb, temp_insitu, sal)
 #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
   #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-   # dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
+   # dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dySeries("sal_insitu", label = "sal_insitu", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dySeries("temp_insitu", label = "temp_insitu", color ="red", strokeWidth=0, pointSize=2) %>%
+dySeries("temp_fb", label = "temp_fb", color ="blue", strokeWidth=0, pointSize=2) %>%
+ # dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
    # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
@@
 # sfoffset <- left_join(sfPeriod[,c(1,2)], d_all%>%dplyr::select(datetime, pHint_tot_sf), by="datetime")
-# dat <- mutate(sfoffset, diff_pH_sf = round((pH_s_seafet_temp_field - pHint_tot_sf),digits  = 4))
+# dat <- mutate(sfoffset, diff_pH_sf = round((pH_s_seafet_temp_insitu - pHint_tot_sf),digits  = 4))
 # average_offset <- mean(abs(dat$diff_pH_sf), na.rm=TRUE)
@@
 #   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_insitu, fill="Discrete measurements"), col="red" )+
 #   labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
@@
 durPeriod <- d_all%>%
-  dplyr::select(datetime, pH_s_durafet_temp_field)%>%
-  dplyr::filter(!is.na(pH_s_durafet_temp_field))
+  dplyr::select(datetime, pH_s_durafet_temp_insitu)%>%
+  dplyr::filter(!is.na(pH_s_durafet_temp_insitu))
 
@@
 # Offset between durafet pH and spec pH 
-duroffset <- left_join(durPeriod%>%dplyr::select(datetime,pH_s_durafet_temp_field), d_all%>%dplyr::select(datetime,pH_durafet ), by="datetime")
-dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_field - pH_durafet)
+duroffset <- left_join(durPeriod%>%dplyr::select(datetime,pH_s_durafet_temp_insitu), d_all%>%dplyr::select(datetime,pH_durafet ), by="datetime")
+dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_insitu - pH_durafet)
 average_offset_dur <- round(mean(dat_dur$diff_pH_dur, na.rm=TRUE), digits = 2)
@@
 d_all <- d_all%>%
-  dplyr::mutate( pH_s_dur_no_calb = ifelse(datetime == "2017-08-24 13:00:00", pH_s_durafet_temp_field, NA ))
-
-durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected, pH_s_dur_no_calb)
+  dplyr::mutate( pH_s_dur_no_calb = ifelse(datetime == "2017-08-24 13:00:00", pH_s_durafet_temp_insitu, NA ))
+
+durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_insitu,pH_durafet_corrected, pH_s_dur_no_calb)
 durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
@@
     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_durafet_temp_field", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
+    dySeries("pH_s_durafet_temp_insitu", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
        dySeries("pH_s_dur_no_calb", label = "pH spectro no calibration", color ="black", pointShape = "triangle",strokeWidth=0, pointSize=6) %>%
@@
 #   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_insitu, fill="Discrete measurements"), col="red" )+
 #   labs(x = "", y= "", title = expression(pH[T]~durafet)) +
@@
 # Spectro / durafet
-fit <- lmodel2(data = d_all,  pH_s_durafet_temp_field ~ pH_durafet_corrected , nperm = 99)
-
-p_dura_spectro <-  ggplot(d_all,aes(x=pH_durafet_corrected, y= pH_s_durafet_temp_field, label = month))+
+fit <- lmodel2(data = d_all,  pH_s_durafet_temp_insitu ~ pH_durafet_corrected , nperm = 99)
+
+p_dura_spectro <-  ggplot(d_all,aes(x=pH_durafet_corrected, y= pH_s_durafet_temp_insitu, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
 # Spectro / seafet
-fit <- lmodel2(data = d_all,  pH_s_seafet_temp_field ~ pHint_tot_sf , nperm = 99)
-
-p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_field, label = month))+
+fit <- lmodel2(data = d_all,  pH_s_seafet_temp_insitu ~ pHint_tot_sf , nperm = 99)
+
+p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_insitu, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
 <!--  # DURAFET  -->
-<!-- durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field) -->
+<!-- durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_insitu) -->
 <!-- durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime) -->
@@
 <!--     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>% -->
-<!--     dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
+<!--     dySeries("pH_s_durafet_temp_insitu", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
 <!--     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>% -->
@@
 <!-- # SEAFET  -->
-<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field) -->
+<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_insitu) -->
 <!-- seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime) -->
@@
 <!--   dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>% -->
-<!--   dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
+<!--   dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
 <!--   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>% -->

### 2020-03-23 awipev-CO2.Rmd
sal_mix and temp_mix modifications done2

@@
 
-```{r pCO2 2nd cleaning, echo=FALSE, warning=FALSE, message=FALSE}
-
-```
-
 ```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
@@
 
-### **seaFET data cleaning**
-
-```{r seaFET 2nd cleaning, echo=FALSE, message= FALSE, warning=FALSE, out.width= "60%"}
-
-```                
 ### **seaFET calibration constante E0**
@@
 #interpolation of salinity during the FB off maintenance
-salinterp <-approx(d_all$datetime, d_all$sal, xout=d_all$datetime, method="linear", rule=2)
+salinterp <-approx(d_all$datetime, d_all$sal_mix, xout=d_all$datetime, method="linear", rule=2)
 names(salinterp) <- c("datetime", "sal_interp")
 salinterp <- as.data.frame(salinterp)
-d_all$sal_interp <- salinterp$sal_interp
-
-d_all$sal <- ifelse(d_all$datetime > "2018-03-09 00:00:00" & d_all$datetime < "2018-04-16 16:00:00", d_all$sal_interp, d_all$sal)
+d_all$sal_mix_interp <- salinterp$sal_mix_interp
+
+d_all$sal_mix_interp <- ifelse(d_all$datetime > "2018-03-09 00:00:00" & d_all$datetime < "2018-04-16 16:00:00", d_all$sal_mix_interp, d_all$sal_mix)
 
@@
 calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_insitu,
-                          calT = d_all$temp_insitu, calSal = d_all$sal )
+                          calT = d_all$temp_mix, calSal = d_all$sal_mix )
 # put number of deployment 
@@
 ####
-seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu, calSal = d_all$sal_interp)
+seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_mix, calSal = d_all$sal_mix_interp)
 
@@
 # # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_insitu, T_seaF, temp_fb, temp_insitu, sal)
-#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
-seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-  #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-   # dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
-    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-  dySeries("temp_insitu", label = "temp_insitu", color ="red", strokeWidth=0, pointSize=2) %>%
-dySeries("temp_fb", label = "temp_fb", color ="blue", strokeWidth=0, pointSize=2) %>%
- # dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
-   # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
- #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-  #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
-  #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-   # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
-  dyLegend(show = "auto")   %>%
-  #dyAxis( "y2",valueRange = c(-3, 36))%>%
-  dyAxis( "y",valueRange = c(-3, 9))%>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-  dyRangeSelector(height = 30, dateWindow= NULL)
-# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
+# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_insitu, T_seaF, temp_fb, temp_insitu, sal)
+# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
+# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+#   #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
+#    # dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
+#     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#   dySeries("temp_insitu", label = "temp_insitu", color ="red", strokeWidth=0, pointSize=2) %>%
+# dySeries("temp_fb", label = "temp_fb", color ="blue", strokeWidth=0, pointSize=2) %>%
+#  # dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#    # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#  #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
+#   #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
+#   #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
+#    # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
+#   dyLegend(show = "auto")   %>%
+#   #dyAxis( "y2",valueRange = c(-3, 36))%>%
+#   dyAxis( "y",valueRange = c(-3, 9))%>%
+#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+#   dyRangeSelector(height = 30, dateWindow= NULL)
+# # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
 
@@
   #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
-  summarize(Tinsi_max =round( max(temp_insitu, na.rm=TRUE), digits = 2),
-            Tinsi_min = round(min(temp_insitu, na.rm=TRUE), digits = 2),
-            sal_max = round(max(sal, na.rm=TRUE), digits = 2),
-            sal_min = round(min(sal, na.rm=TRUE), digits = 2),
+  summarize(Tinsi_max =round( max(temp_mix, na.rm=TRUE), digits = 2),
+            Tinsi_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
+            sal_max = round(max(sal_mix, na.rm=TRUE), digits = 2),
+            sal_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
             pH_sf_max = round(max(pHint_tot_sf, na.rm=TRUE), digits = 4),
@@
 pH_sf <- d_all %>%
-  dplyr::select(datetime, sal,temp_fb,temp_insitu, pHint_tot_sf)%>%
-  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal)) %>%
+  dplyr::select(datetime, sal_mix,temp_fb,temp_mix, pHint_tot_sf)%>%
+  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_mix), !is.na(temp_fb), !is.na(sal_mix)) %>%
   dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
-pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu, Pinsi=11, S=pH_sf$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_mix, Pinsi=11, S=pH_sf$sal_mix, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
 pH_dur <- d_all %>%
-  dplyr::select(datetime, sal,temp_fb,temp_insitu, pH_durafet_corrected)%>%
-  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal))
-pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_insitu, Pinsi=11, S=pH_dur$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+  dplyr::select(datetime, sal_mix,temp_fb,temp_mix, pH_durafet_corrected)%>%
+  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_mix), !is.na(temp_fb), !is.na(sal_mix))
+pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_mix, Pinsi=11, S=pH_dur$sal_mix, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
@@
 pH_calc <- discrete %>%
-  dplyr::select(datetime, sal,temp, phcalc, at)%>%
-  dplyr::filter(!is.na(phcalc), !is.na(temp), !is.na(sal))
-pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+  dplyr::select(datetime, sal_mix,temp, phcalc, at)%>%
+  dplyr::filter(!is.na(phcalc), !is.na(temp), !is.na(sal_mix))
+pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal_mix, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 

### 2020-03-23 awipev-CO2.Rmd
sal_mix and temp_mix modifications done3

@@
 
-d_all$diff_sal_fb_insitu <- d_all$sal_insitu - d_all$sal_fb
+d_all$diff_sal_fb_insitu <- d_all$sal_insitu_ctd - d_all$sal_fb
 mean_diff_sal_fb_insitu <- round(mean(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)
@@
 
-```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
+```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
 
@@
 d_all <- d_all%>%
-  dplyr::mutate(temp_insitu = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_insitu))
+  dplyr::mutate(temp_mix = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_mix))
 
@@
 d_all <- d_all%>%
-  dplyr::mutate(temp_insitu = ifelse(datetime == "2019-09-13 13:00:00" , mean_TseaF_4h, temp_insitu))
+  dplyr::mutate(temp_mix = ifelse(datetime == "2019-09-13 13:00:00" , mean_TseaF_4h, temp_mix))
 
@@
 salinterp <-approx(d_all$datetime, d_all$sal_mix, xout=d_all$datetime, method="linear", rule=2)
-names(salinterp) <- c("datetime", "sal_interp")
+names(salinterp) <- c("datetime", "sal_mix_interp")
 salinterp <- as.data.frame(salinterp)
@@
 
-d_all$sal_mix_interp <- ifelse(d_all$datetime > "2018-03-09 00:00:00" & d_all$datetime < "2018-04-16 16:00:00", d_all$sal_mix_interp, d_all$sal_mix)
+d_all <- d_all %>%
+  dplyr::mutate(sal_mix_interp =  ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-16 16:00:00", sal_mix_interp, sal_mix))
 
@@
 pH_calc <- discrete %>%
-  dplyr::select(datetime, sal_mix,temp, phcalc, at)%>%
-  dplyr::filter(!is.na(phcalc), !is.na(temp), !is.na(sal_mix))
-pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal_mix, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+  dplyr::select(datetime, sal,temp, phcalc, at)%>%
+  dplyr::filter(!is.na(phcalc), !is.na(temp), !is.na(sal))
+pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 

### 2020-03-24 awipev-CO2.Rmd
modif on seafet graph with depth group

@@
 library(scales)
+library(plotly)
+library(htmlwidgets)
 knitr::opts_chunk$set(echo = TRUE)
@@
          ) %>%
-  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered)
+  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered, temp_sf=T_seaF)
 ```
@@
 TO DO: add here an horizontal bar plot showing the percent availability of the data
+
+```{r Depth filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
+#Make groups
+
+d_all <- d_all%>%
+  dplyr::mutate(depth = ifelse(pressure_insitu_ctd_filtered <=2, "1 m", 
+                        ifelse(pressure_insitu_ctd_filtered >2 & pressure_insitu_ctd_filtered <=4, "3 m", 
+                        ifelse(pressure_insitu_ctd_filtered >4 & pressure_insitu_ctd_filtered <=6, "5 m",
+                        ifelse(pressure_insitu_ctd_filtered >6 & pressure_insitu_ctd_filtered <=8, "7 m",
+                        ifelse(pressure_insitu_ctd_filtered >8, "9 m",NA))))))
+```
 
@@
 
-p_sal_fb_sal_insitu<-  ggplot(d_all,aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
+# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,sal_fb,sal_insitu_ctd)
+# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
+# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
+#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
+#   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
+#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
+#   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) 
+#
+
+p_sal_fb_sal_insitu<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
   geom_text( aes(color=factor(month))) + 
  # scale_color_viridis_d(option = "C", guide="none")+
-  geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
+  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
+  geom_abline(slope=1, intercept=0, linetype = "dashed")+
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("Sal in situ vs Sal FB","\n Adj R2 = ", signif(fit$rsquare, 3),
+  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
+  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
                      "; Intercept =", signif(fit$regression.results[2,2], 3),
@@
                      "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
-  labs( x="Salinity insitu", y="Salinity FB ", color = "Months")  +theme_bw()
+  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
+  coord_fixed(ratio = 1 )+
+   scale_colour_discrete(guide="none") +
+  labs( x="Salinity CTD > 8 m", y="Salinity FB ", color = "Months") +theme_bw()
 print(p_sal_fb_sal_insitu)
@@
 - 1 SBE45 inside the Ferrybox (temp_fb)
-- 5 CTD > 8 meters depth (sal_insitu_ctd)
-- 5 fixed at 11 meters depth (sal_insitu_11m)
+- 5 CTD > 8 meters depth (temp_insitu_ctd)
+- 1 fixed at 11 meters depth (temp_insitu_11m)
 
@@
 
-### **T seaFET / T mix **
+### **T Ferrybox / T insitu 11 m **
 
@@
 
-fit <- lmodel2(data = d_all,  T_seaF ~ temp_mix , nperm = 99)
-
-```{r Temp comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-# seaF outliers (T - volt int - volt ext) to remove from 2017-12-10 to 2017-12-14
-d_all <- d_all %>%
-  dplyr::mutate(T_seaF = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, T_seaF),
-                voltINT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltINT), 
-                voltEXT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltEXT))
-
-fit <- lmodel2(data = d_all,  T_seaF ~ temp_mix , nperm = 99)
-
-pTseaf_Tinsi<-  ggplot(d_all,aes(x=temp_mix, y= T_seaF, label = month))+
-  geom_text( aes(color=factor(month))) + 
- # scale_color_viridis_d(option = "C", guide="none")+
-  geom_line(aes(x = T_seaF, y = T_seaF), linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("T seaF vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
-  labs( x="T insi", y="T seaF ", color = "Months")  +theme_bw()
-print(pTseaf_Tinsi)
-
-d_all$diff_T_seaF_insitu <- d_all$T_seaF - d_all$temp_mix
-mean_diff_T_seaF_insitu <- round(mean(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)
-sd_diff_T_seaF_insitu <- round(sd(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)
-
-```
-
-The mean difference between T seaFET and in situ is: `r mean_diff_T_seaF_insitu` ± `r sd_diff_T_seaF_insitu`°C.
-
-### **T Ferrybox / T mix **
-
-Property-property temperature plot using:
-
-fit <- lmodel2(data = d_all,  temp_fb ~ temp_mix , nperm = 99)
+fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)
 
@@
 
-fit <- lmodel2(data = d_all,  temp_fb ~ temp_mix , nperm = 99)
-
-pTfb_Tinsi<-  ggplot(d_all,aes(x=temp_mix, y= temp_fb, label = month))+
+fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)
+
+p<-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
   labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
-print(pTfb_Tinsi)
-
-d_all$diff_T_fb_insitu <- d_all$T_seaF - d_all$temp_mix
+print(p)
+
+d_all$diff_T_fb_insitu <- d_all$temp_sf - d_all$temp_insitu_11m
 mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
@@
 
-d_all$diff_T_fb_insitu <- d_all$T_seaF - d_all$temp_insitu_ctd
+d_all$diff_T_fb_insitu <- d_all$temp_sf - d_all$temp_insitu_ctd
 mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
@@
 Because of issue, measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17.
-pH calibration is based on monthly discrete samples that are analysed with spectrophotometric method in Villefranche by Samir Alliouane.
+*Note that pH sensor is mounted on a profiling structure.
+Here, only seaFET data recorded with a depth > 8 m are taken in consideration.* pH calibration is based on monthly discrete samples that are analysed with spectrophotometric method in Villefranche by Samir Alliouane.
 When it is not possible to sample at the vicinity of the sensor for practice reasons (in winter), sampling is done in the harbour and is not taken in consideration for calibration for spatial reasons.
@@
   dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
-  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
+  dplyr::summarise( mean(temp_sf, na.rm = TRUE))
 mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
@@
   dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
-  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
+  dplyr::summarise( mean(temp_sf, na.rm = TRUE))
 mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
@@
 
+d_all <-  d_all%>%
+  dplyr::mutate(voltINT_sup8m = ifelse(pressure_insitu_ctd_filtered >=8,voltINT, NA),
+                voltEXT_sup8m = ifelse(pressure_insitu_ctd_filtered >=8,voltEXT, NA), 
+                pH_s_seafet_temp_insitu_sup8m = ifelse(pressure_insitu_ctd_filtered >=8,pH_s_seafet_temp_insitu, NA) )
 ####
@@
 ####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_insitu,
+calib_spectro <- sf_calib(calEint = d_all$voltINT_sup8m, calEext = d_all$voltEXT_sup8m, calpH = d_all$pH_s_seafet_temp_insitu_sup8m,
                           calT = d_all$temp_mix, calSal = d_all$sal_mix )
@@
 ####
-seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_mix, calSal = d_all$sal_mix_interp)
+seafet_calib <- sf_calc(calEint = d_all$voltINT_sup8m, calEext = d_all$voltEXT_sup8m, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_mix, calSal = d_all$sal_mix_interp)
 
@@
 
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_insitu,pHint_tot_sf, pH_s_sf_no_calb)
+seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_insitu,pHint_tot_sf, pH_s_sf_no_calb, pressure_insitu_ctd_filtered)
 #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
 dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-  #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
+  dySeries("pressure_insitu_ctd_filtered", axis="y2",label = "Depth", color ="pink", strokeWidth=0, pointSize=2) %>%
   dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
@@
   dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
-   dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
-   dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
-   dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
-   dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
-   dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[22], to= Sys.Date(), color = "#E0E0E0") %>%
+  # dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
+  # dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
+  # dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
+  # dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
+  # dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
+  # dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
+  # dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
+  # dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
+  # dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
+  # dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
+  # dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
+  #  dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
+  #  dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
+  #  dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
+  # dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
+  # dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
+  # dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
+  #  dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
+  #  dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
   dyLegend(show = "auto")   %>%
@@
 
+p <- ggplot(d_all%>%filter(datetime >= ("2017-07-30")),aes(x=datetime, y= phINT_filtered, label = depth))+
+  geom_line( aes(color=factor(depth)))
+
+p_py <- ggplotly(p,dynamicTicks = TRUE)
+filename.html <- paste0("/figures/p_py.html")
+saveWidget(p_py, filename.html, selfcontained = T, libdir = "lib")
+
+getwd()
+
+seafet_depth_xts <- dplyr::select(d_all, datetime, phINT_filtered, depth)
+seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
+dygraph(seafet_depth_xts, group = "depth", main="pH seaFET RAW (in situ)", ylab="pHT") %>%
+  dySeries("phINT_filtered", axis="y2",label = "pH RAW", color ="green", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%
+  #dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
+  #dyGroup(depth, drawPoints = TRUE, color = "green")%>%
+  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
+  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
+  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
+    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
+  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
+  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
+  dyLegend(show = "auto")   %>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyRangeSelector(height = 30, dateWindow= NULL)
+
 # # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_insitu, T_seaF, temp_fb, temp_insitu, sal)
+# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_insitu, temp_sf, temp_fb, temp_insitu, sal)
 # #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
 #  # dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#    # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#    # dySeries("temp_sf", label = "temp_sf", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
 #  #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
@@
   scale_color_discrete(guide = "none")+
-  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
+ geom_abline(slope=1, intercept =0, linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
@@
   scale_color_discrete(guide = "none")+
-  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
+  geom_abline(slope=1, intercept =0, linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +

### 2020-03-26 paper.Rmd
2020-03-25

@@
 td {  /* Table  */
-  font-size: 8px;
+  font-size: 14px;
 }
@@
 library(tidyverse)
-#library(robfilter)
 library(seacarb)
@@
 library(lubridate)
-#library(lmtest)
-#library(grid)
 library(viridis)
-#library(dygraphs)
 require("knitr")
+library(kableExtra)
 library("lmodel2")
-#library(captioner)
-#library(xts)
-#library(seismicRoll)
 library(scales)
@@
 library("directlabels")
-if (!require("pangaear")) install.packages("pangaear")
+if (!require("pangaear")) install.packages("pangaea\r")
 library("pangaear")
@@
 if (Sys.getenv("LOGNAME") == "samir") path_data = "../../pCloud\ Sync/exp168_awipev-CO2/"
+
+######## function to calculate 3 quantiles
+qq <- function (data, digits) { 
+  as.numeric(formatC(quantile(x = data, probs = c(0.025, 0.50, 0.975), na.rm = TRUE),
+                     format = "f", digits = digits))
+}
 
@@
 ```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
-d_all <- as_tibble(readRDS(file = paste0(path_data, "fb_data/d_all_copy.rds"))) %>% 
+d_all <- as_tibble(readRDS(file = paste0(path_data, "fb_data/d_all.rds"))) %>% 
   dplyr::filter(sal_fb > 28) %>% # remove salinity data lower than 28
@@
 ## Whole time series
+
+**To do**: Filter pH values at more than 8 m depth.
+
 ```{r whole time series, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
-size_point <- 1 # size of data points
+size_point <- 2 # size of data points
+alpha <- 1 #transparency
 
@@
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
+  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
   labs(title="Salinity FerryBox? SBE45",x="", y="Salinity") +
-  #coord_fixed() +
   Mytheme(size_labs = 8)
@@
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
+  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
   labs(title="Temperature FerryBox",x="", y="In situ temperature (°C)") +
-  #coord_fixed() +
   Mytheme(size_labs = 8)
@@
   geom_point(aes(x = datetime, y = pco2_contros), 
-             colour="black", na.rm=TRUE, size=size_point) + 
-  geom_point(aes(x = datetime, y = pco2calc), colour="blue", na.rm=TRUE, size=size_point) + 
-  labs(title="CO2 partial pressure",x="", y="pCO2 (uatm)") +
-  #coord_fixed() +
+             colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(aes(x = datetime, y = pco2calc), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  labs(title="Mesured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
   Mytheme(size_labs = 8)
@@
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
-  labs(title="In situ pH",x="", y="pCO2 (uatm)") +
-  #coord_fixed() +
+  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  labs(title="In situ pH",x="", y=expression(paste(pH[T]))) +
   Mytheme(size_labs = 8)
@@
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(colour="black", na.rm=TRUE, size=size_point) + 
-  labs(title="Total alkalinity calculated from salinity", x="", y="AT (umol/kg)") +
-  #coord_fixed() +
+  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(aes(x = datetime, y = at), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  labs(title="Total alkalinity calculated from salinity (blue) and discrete measurements (red)", x="", y="AT (umol/kg)") +
   Mytheme(size_labs = 8)
@@
 print(g)
+```
+
+Monthly distribution of seawater carbonate chemistry using a combination of a violin plot showing the relative frequency of the observations (shaded blue area) and a box plot showing the median, ﬁrst, and third quartiles, as well as outliers (blue).
+
+```{r whole time series monthly box plots and stats, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+size_point <- 0.5 # size of data points
+alpha <- 1 #transparency
+ts_sal_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(y = "Salinity", x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+
+ts_temp_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = temp_fb)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
+               outlier.size = 0.3, na.rm=TRUE) +
+  labs(y = "Temperature", x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+
+ts_pCO2_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_contros)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
+               outlier.size = 0.3, na.rm=TRUE) +
+  labs(y = expression(paste(pCO[2])), x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+
+ts_pH_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pHint_tot_sf)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
+               outlier.size = 0.3, na.rm=TRUE) +
+  labs(y = expression(paste(pH[T])), x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+
+ts_at_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = at_calc)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
+               outlier.size = 0.3, na.rm=TRUE) +
+  labs(y = "Total alkalinity", x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+
+g <- cowplot::plot_grid(ts_sal_bp, ts_temp_bp, ts_pCO2_bp, ts_pH_bp, ts_at_bp, align='v', ncol=1)
+print(g)
+
+Salinity <- qq(d_all$sal_fb, digits=1)
+Temperature <- qq(d_all$temp_fb, digits=1)
+pCO2 <- qq(d_all$pco2_contros, digits=1)
+pH <- qq(d_all$pHint_tot_sf, digits=3)
+AT <- qq(d_all$at_calc, digits=1)
+tab_quartiles <- as_tibble(rbind(Salinity, Temperature, pCO2, pH, AT)) %>%
+  rename("2.5%"=V1, "50%"=V2, "97.5%"=V3) %>%
+  mutate(Variable=c("Salinity", "Temperature", "pCO2", "pH", "AT")) %>%
+  dplyr::select(Variable, everything())
+kable(tab_quartiles, caption = "Key quantiles") %>%
+  kable_styling(full_width=FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
 ```
@@
 **To do when the situation of the in situ CTDs will be clarified**: compare salinity values from the Ferrybox and in situ.
+
+**To do**: add discrete pH values on plot.
 
@@
 
-```{r temperature vs salinity regressions, fig.width=6, fig.height=6, echo=FALSE, message= FALSE}
+```{r temperature vs salinity regressions, echo=FALSE, message= FALSE, out.width="50%"}
 # AT as a function of salinity for every year
@@
 ```{r pangaea data, fig.width=9, fig.height=6, echo=FALSE, message= FALSE}
-data_2015 <- pg_data(doi="10.1594/PANGAEA.896771", overwrite = TRUE)
-data_2016 <- pg_data(doi="10.1594/PANGAEA.896770", overwrite = TRUE)
-data_2017 <- pg_data(doi="10.1594/PANGAEA.896170", overwrite = TRUE)
-data_2018 <- pg_data(doi="10.1594/PANGAEA.897349", overwrite = TRUE)
-tmp <- rbind(data_2015[[1]]$data, data_2016[[1]]$data, data_2017[[1]]$data, data_2018[[1]]$data)
-tmp <- tmp[, c(1, 8, 11)] # select date time and salinity
-tmp$`Date/Time` <- as.POSIXct(strptime(tmp$`Date/Time`, "%Y-%m-%dT%H:%M", tz = "UTC"))
-
-pg_ts <- tmp %>% #Pangaea time series
-  dplyr::filter(!are_duplicated(tmp)) %>%
-  dplyr::rename(datetime = `Date/Time`,
-                sal = `Sal ([PSU])`,
-                temp = `Temp [°C]`) %>%
-  as_tsibble(key = NULL, index = datetime) %>%
-  fill_gaps()
-
-fig_sal_pangaea <- pg_ts %>%
-  ggplot() +
-  geom_point(aes(x=datetime, y=sal), na.rm = TRUE) +
-  labs(title="Salinity recovered from Pangaea") +
-  Mytheme(size_labs = 14)
-print(fig_sal_pangaea)
-
-fig_temp_pangaea <- pg_ts %>%
-  ggplot() +
-  geom_point(aes(x=datetime, y=temp), na.rm = TRUE) +
-  labs(title="Temperature recovered from Pangaea") +
-  Mytheme(size_labs = 14)
-print(fig_temp_pangaea)
+# data_2015 <- pg_data(doi="10.1594/PANGAEA.896771", overwrite = TRUE)
+# data_2016 <- pg_data(doi="10.1594/PANGAEA.896770", overwrite = TRUE)
+# data_2017 <- pg_data(doi="10.1594/PANGAEA.896170", overwrite = TRUE)
+# data_2018 <- pg_data(doi="10.1594/PANGAEA.897349", overwrite = TRUE)
+# tmp <- rbind(data_2015[[1]]$data, data_2016[[1]]$data, data_2017[[1]]$data, data_2018[[1]]$data)
+# tmp <- tmp[, c(1, 8, 11)] # select date time and salinity
+# tmp$`Date/Time` <- as.POSIXct(strptime(tmp$`Date/Time`, "%Y-%m-%dT%H:%M", tz = "UTC"))
+# 
+# pg_ts <- tmp %>% #Pangaea time series
+#   dplyr::filter(!are_duplicated(tmp)) %>%
+#   dplyr::rename(datetime = `Date/Time`,
+#                 sal = `Sal ([PSU])`,
+#                 temp = `Temp [°C]`) %>%
+#   as_tsibble(key = NULL, index = datetime) %>%
+#   fill_gaps()
+# 
+# fig_sal_pangaea <- pg_ts %>%
+#   ggplot() +
+#   geom_point(aes(x=datetime, y=sal), na.rm = TRUE) +
+#   labs(title="Salinity recovered from Pangaea") +
+#   Mytheme(size_labs = 14)
+# print(fig_sal_pangaea)
+# 
+# fig_temp_pangaea <- pg_ts %>%
+#   ggplot() +
+#   geom_point(aes(x=datetime, y=temp), na.rm = TRUE) +
+#   labs(title="Temperature recovered from Pangaea") +
+#   Mytheme(size_labs = 14)
+# print(fig_temp_pangaea)
 ```
@@
 ## Total alkalinity
-It is proposed not to use the data from the Contros instrument. It is too unfeliable and difficult to calibrate. We use instead the relationship between salinity and the discrete measurements of AT.
+It is proposed not to use the data from the Contros instrument. It is too unreliable and difficult to calibrate. We use instead the relationship between salinity and the discrete measurements of AT.
+
+```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
+d_all_at_discrete <- d_all %>% #  To remove an outlier in red
+  dplyr::select(datetime, month, closest_datetime, at, sal_fb)%>%
+  dplyr::filter( !is.na(at) & !is.na(sal_fb) & sal_fb >30)
+
+#fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal)
+fit <- lm(data = d_all_at_discrete, at ~ sal_fb)
+slope_s_at <- fit$coefficients[[2]]
+intercept_s_at <- fit$coefficients[[1]]
+# at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()
+
+at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb, y= at, label = month))+
+#  geom_text( aes(color=factor(month))) +
+  geom_point(color = "blue") +
+#  scale_color_discrete(guide="none")+
+    labs(x="Salinity FerryBox", y="Discrete AT")  +
+    stat_smooth(method = "lm", col = "black") +
+    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
+                       ";\nSlope =",signif(fit$coef[[2]], 5),
+                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
+  theme_bw() +
+  theme(aspect.ratio=1,
+        axis.text=element_text(size=15),
+        axis.title.y= element_text(size =15),
+        axis.title.x= element_text(size =15),
+        plot.margin = unit(c(0.5,1,1,1), "cm"),
+        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70)))
+print(at_s)
+
+#ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")
+
+# Salinity is a predictor of AT -> using the regression defined above
+d_all$at_calc <- slope_s_at * d_all$sal_fb + intercept_s_at
+```
+
+The relationship between titrated total alkalinity and salinity is very good with an r2 of `r round(summary(fit)$r.squared, digits=2)`. Need to compare with other relationships from the literature.
+
+## Consistency: pCO2
+
+```{r pCO2, echo=FALSE, warning=FALSE, message=FALSE}
+title <- "Contros vs calculated pCO2"
+fit <- lmodel2(data = d_all,  pco2_contros ~ pco2calc , nperm = 99)
+
+pco2calc_pCO2contros <-  ggplot(d_all, aes(x=pco2calc, y= pco2_contros))+
+  geom_point(colour="blue", alpha = alpha)+
+  geom_abline(aes(intercept = 0, slope = 1), linetype = "dashed") +
+  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3), "\n",
+                     "Intercept =", signif(fit$regression.results[2,2], 3),
+                     "; Slope =", signif( fit$regression.results[2,3], 3),
+                     "; P =", signif(fit$P.param, 3))) +
+  theme(aspect.ratio=1, plot.title = element_text(size=7)) + 
+  coord_fixed(ratio = 1, xlim=c(200,460) , ylim=c(200,460))+
+  labs(x="Calculated pCO2", y="Measured pCO2") + theme_bw()  
+print(pco2calc_pCO2contros)
+ggsave(paste0("figures/pco2calc_pCO2contros.png"), pco2calc_pCO2contros, units="cm")
+
+# average uncertainty calculated pCO2 assuming uncertainties of 4 umol/kg for AT and CT
+e_pCO2 <- seacarb::errors(flag=15, 
+                var1=1e-6*mean(d_all$at, na.rm=TRUE), var2=1e-6*mean(d_all$ct, na.rm=TRUE),
+                S=mean(d_all$sal_fb, na.rm=TRUE), T=mean(d_all$temp_fb, na.rm=TRUE), P=0, Pt=0,
+                Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74", 
+                evar1=4e-6, evar2 = 4e-6)$pCO2
+```
+
+The relationship between the measured and calculated *p*CO~2~ is not very good.
+r2 (`r round(fit$rsquare, digits=2)`).
+Note that the accuracy of the pCO2 sensor is about 3 uatm (1% of reading) whereas it is `r round(e_pCO2, digits=1)` uatm.
+The later is estimated as described by Orr et al.
+(2019) assuming an uncertainty of 4 umol/kg for both AT and CT.

### 2020-03-26 awipev-CO2.Rmd
sal_fb + temp_fb added to discrete df to convert spectro durafet

@@
 
+```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
+d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
+# load = d_hour
+d_hour <- d_hour %>%
+  dplyr::select(-date) %>%
+  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
+         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
+         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
+         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
+         ) %>%
+  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered, temp_durafet = HW_Temperature1_filtered, temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered, temp_sf=T_seaF)
+
+d_all <- d_hour #d_all will be the merger
+d_all<- d_all%>%
+  dplyr::mutate(month = month(month(datetime)))
+
+```
+
 ```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
@@
 
+# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_hour TO d, to use pHinsi
+# use the closest time to add them
+closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
+d$closest_datetime <- d_all$datetime[closest]
+# if the closest value is more than 30 min away, then we do not take it
+d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
+# create closest_datetime in d_all (copy of datetime)
+d_all$closest_datetime <- d_all$datetime
+d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, sal_insitu_ctd, temp_insitu_ctd)), by="closest_datetime")
+
 # Conversion of spectro pH to a same T°
 pH_seafet <- d %>%
-  dplyr::filter(!is.na(pH_s_seafet))
+  dplyr::filter(!is.na(pH_s_seafet)& !is.na(sal_insitu_ctd) )
 pH_seafet <- pH_seafet %>%
-  dplyr::mutate(pH_s_seafet_temp_insitu = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_field, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$salinity_field,Pt=0,Sit=0))
+  dplyr::mutate(pH_s_seafet_temp_ctd = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_insitu_ctd, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_insitu_ctd,Pt=0,Sit=0))
 
@@
 pH_durafet <- pH_durafet %>%
-  dplyr::mutate(pH_s_durafet_temp_insitu = pHinsi(pH=pH_durafet$pH_s_durafet,ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_field, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$salinity_field,Pt=0,Sit=0))
+  dplyr::mutate(pH_s_durafet_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb,Pt=0,Sit=0))
 
@@
 pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(datetime,pH_s_seafet_temp_insitu)%>% 
+  dplyr::select(datetime,pH_s_seafet_temp_ctd)%>% 
   dplyr::group_by(datetime) %>% 
-  dplyr::summarize(pH_s_seafet_temp_insitu = mean(pH_s_seafet_temp_insitu, na.rm = T))
+  dplyr::summarize(pH_s_seafet_temp_ctd = mean(pH_s_seafet_temp_ctd, na.rm = T))
 pH_durafet_mean <- pH_durafet%>%
-  dplyr::select(datetime,pH_s_durafet_temp_insitu)%>% 
+  dplyr::select(datetime,pH_s_durafet_temp_fb)%>% 
   dplyr::group_by(datetime) %>% 
-  dplyr::summarize(pH_s_durafet_temp_insitu = mean(pH_s_durafet_temp_insitu, na.rm = T))
+  dplyr::summarize(pH_s_durafet_temp_fb = mean(pH_s_durafet_temp_fb, na.rm = T))
 
@@
   dplyr::group_by(datetime) %>% 
-  dplyr::summarize(sal = mean(salinity_field, na.rm = T),
-            temp = mean(temp_field, na.rm = T),
+  dplyr::summarize(sal_fb = mean(sal_fb, na.rm = T),
+                   temp_fb = mean(temp_fb, na.rm = T),
                    at_mean_interp = mean(at_mean_interp, na.rm = T),
@@
 ##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
-##   *****Attention, I asked to the logisticians to log outside temp from 9 june 2019
+##   *****Attention, I asked to the logisticians to log insitu temp from 9 june 2019
 
@@
 
-carb <- carb(15, discrete$at*1e-6, discrete$ct*1e-6,S=discrete$sal, T=discrete$temp, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
-discrete$phcalc<- carb$pH
-discrete$pco2calc<- carb$pCO2
-```
-
-```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
-d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
-# load = d_hour
-d_hour <- d_hour %>%
-  dplyr::select(-date) %>%
-  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
-         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
-         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
-         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
-         ) %>%
-  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered, temp_sf=T_seaF)
+discrete_no_na <- discrete %>%
+  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
+discrete_is_na <- discrete %>%
+  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
+
+carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6,S=discrete_no_na$sal_fb, T=discrete_no_na$temp_fb, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
+
+discrete_no_na$phcalc<- carb$pH
+discrete_no_na$pco2calc<- carb$pCO2
+
+#create new variable in "discrete_is_na" to bind "discrete_no_na"
+discrete_is_na$phcalc<- NA
+discrete_is_na$pco2calc<- NA
+discrete <- rbind(discrete_no_na, discrete_is_na)
+discrete%>%dplyr::arrange(datetime)
 ```
@@
 ```{r Combine discrete and continous data, echo=FALSE}
-d_all <- d_hour #d_all will be the merger
-d_all<- d_all%>%
-  dplyr::mutate(month = month(month(datetime)))
+
 # at
@@
   #drop_na() %>%
-  dplyr::select(closest_datetime, pH_s_seafet_temp_insitu) %>%
+  dplyr::select(closest_datetime, pH_s_seafet_temp_ctd) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
   #drop_na() %>%
-  dplyr::select(closest_datetime, pH_s_durafet_temp_insitu) %>%
+  dplyr::select(closest_datetime, pH_s_durafet_temp_fb) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 #SAL MIX
-sal_xts <- dplyr::select(d_all, datetime, sal_mix)
+sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd)
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
-dygraph(sal_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
-      dySeries("sal_mix", color = "blue", strokeWidth = 0, label = "S") %>%
+dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD)", ylab="Salinity") %>%
+      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "S") %>%
       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
 # TEMP insitu SBE38
-temp_insitu_xts <- dplyr::select(d_all, datetime, temp_mix)
+temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_11m)
 temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
 dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ 11 m)", ylab="Temperature") %>%
-      dySeries("temp_mix", color = "blue", strokeWidth = 0, label = "T") %>%
+      dySeries("temp_insitu_11m", color = "blue", strokeWidth = 0, label = "T") %>%
       dyAxis("y", valueRange = c(-2.8, 10)) %>%
@@
 # DURAFET 
-durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_insitu)
+durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_fb)
 durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
@@
     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_durafet_temp_insitu", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pH_s_durafet_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
@@
 # SEAFET 
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_insitu)
+seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_ctd)
 seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ T CTD)", ylab="pHT") %>%
   dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-  dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+  dySeries("pH_s_seafet_temp_ctd", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
@@
 #   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2)
-#
-
-p_sal_fb_sal_insitu<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
-  geom_text( aes(color=factor(month))) + 
+
+# date format into charactere
+d_all$datetime_chr <- as.character(d_all$datetime)
+
+p_sal_fb_ctd<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
+  geom_point( aes(color=factor(datetime_chr))) + 
  # scale_color_viridis_d(option = "C", guide="none")+
@@
   labs( x="Salinity CTD > 8 m", y="Salinity FB ", color = "Months") +theme_bw()
-print(p_sal_fb_sal_insitu)
+
+print(p_sal_fb_ctd)
 
@@
 
+### Plotly
+# p_p_sal_fb_ctd <- ggplotly(p_sal_fb_ctd,dynamicTicks = TRUE)
+# filename.html <- paste0("p_p_sal_fb_ctd.html")
+# saveWidget(p_p_sal_fb_ctd, filename.html, selfcontained = T, libdir = "lib")
+
 # # PLOT
-# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_insitu_11m, temp_insitu_ctd, pressure_insitu_ctd_filtered, temp_mix, sal_mix)
-# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-# dySeries("temp_insitu_11m", label = "temp_insitu_11m", color ="red",axis= "y2", strokeWidth=0, pointSize=4) %>%
-# dySeries("temp_insitu_ctd", label = "temp_insitu_ctd", color ="blue",axis= "y2", strokeWidth=0, pointSize=3) %>%
-# dySeries("temp_mix", label = "temp_mix", color ="green",axis= "y2", strokeWidth=0, pointSize=2) %>%
-# dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
-# dySeries("pressure_insitu_ctd_filtered", label = "pressure_insitu_ctd_filtered", color ="black", strokeWidth=0, pointSize=2) %>%
-#   dyLegend(show = "onmouseover")   %>%
-#   #dyAxis( "y2",valueRange = c(-3, 36))%>%
-#   dyAxis( "y2",valueRange = c(-3, 36))%>%
-#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-#   dyRangeSelector(height = 30, dateWindow= NULL)
+seafet_contros_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb, sal_mix)
+seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+dygraph(seafet_contros_xts, group = "awipev", main="Salinities", ylab="PSU") %>%
+dySeries("sal_insitu_ctd", label = "sal_insitu_ctd", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=4) %>%
+dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#dySeries("pressure_insitu_ctd_filtered", label = "pressure_insitu_ctd_filtered", color ="black", strokeWidth=0, pointSize=2) %>%
+  dyLegend(show = "onmouseover")   %>%
+  #dyAxis( "y2",valueRange = c(-3, 36))%>%
+  dyAxis( "y2",valueRange = c(25, 36))%>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyRangeSelector(height = 30, dateWindow= NULL)
 
@@
 
-p<-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
-  geom_text( aes(color=factor(month))) + 
+p_temp_11_fb<-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
+  geom_text( aes(color=factor(datetime_chr))) + 
  # scale_color_viridis_d(option = "C", guide="none")+
-  geom_line(aes(x = temp_fb, y = temp_fb), linetype = "dashed") +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("T FB vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
+  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
                      "; Intercept =", signif(fit$regression.results[2,2], 3),
@@
   coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
-  labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
-print(p)
-
-d_all$diff_T_fb_insitu <- d_all$temp_sf - d_all$temp_insitu_11m
-mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
-sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
-```
-
-The mean difference between T seaFET and in situ is: `r mean_diff_T_fb_insitu` ± `r sd_diff_T_fb_insitu`°C.
+  labs( x="T 11 m", y="T FB ", color = "Months")  +theme_bw()
+print(p_temp_11_fb)
+
+d_all$diff_T_fb_11m <- d_all$temp_fb - d_all$temp_insitu_11m
+mean_diff_T_fb_11m <- round(mean(d_all$diff_T_fb_11m, na.rm = TRUE), digits = 2)
+sd_diff_T_fb_11m <- round(sd(d_all$diff_T_fb_11m, na.rm = TRUE), digits = 2)
+
+### Plotly
+# p_p_temp_11_fb <- ggplotly(p_temp_11_fb,dynamicTicks = TRUE)
+# filename.html <- paste0("p_p_temp_11_fb.html")
+# saveWidget(p_p_temp_11_fb, filename.html, selfcontained = T, libdir = "lib")
+
+```
+
+The mean difference between temperature Ferrybox and in situ at 11 m is: `r mean_diff_T_fb_11m` ± `r sd_diff_T_fb_11m`°C.
 
@@
  # scale_color_viridis_d(option = "C", guide="none")+
-  geom_line(aes(x = temp_insitu_11m, y = temp_insitu_11m), linetype = "dashed") +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("T FB vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
+  labs(title = paste("T CTD > 8 m vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
                      "; Intercept =", signif(fit$regression.results[2,2], 3),
@@
   coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
-  labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
+  labs( x="T CTD > 8 m", y="T 11 m ", color = "Months")  +theme_bw()
 print(p)
 
-d_all$diff_T_fb_insitu <- d_all$temp_sf - d_all$temp_insitu_ctd
-mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
-sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
-```
+d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd
+mean_diff_T_ctd_11m <- round(mean(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
+sd_diff_T_ctd_11m <- round(sd(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
+```
+
+The mean difference between temperature Ferrybox and in situ at 11 m is: `r mean_diff_T_ctd_11m` ± `r sd_diff_T_ctd_11m`°C.
 
@@
 # sfPeriod <- d_all%>%
-#   dplyr::select(datetime, pH_s_seafet_temp_insitu)%>%
-#   dplyr::filter(!is.na(pH_s_seafet_temp_insitu))
+#   dplyr::select(datetime, pH_s_seafet_temp_ctd)%>%
+#   dplyr::filter(!is.na(pH_s_seafet_temp_ctd))
 # # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
@@
 
-# test <- d_all%>%
-#   dplyr::filter(datetime=="2017-08-24 14:00:00")
-
-d_all <-  d_all%>%
-  dplyr::mutate(voltINT_sup8m = ifelse(pressure_insitu_ctd_filtered >=8,voltINT, NA),
-                voltEXT_sup8m = ifelse(pressure_insitu_ctd_filtered >=8,voltEXT, NA), 
-                pH_s_seafet_temp_insitu_sup8m = ifelse(pressure_insitu_ctd_filtered >=8,pH_s_seafet_temp_insitu, NA) )
 ####
@@
 ####
-calib_spectro <- sf_calib(calEint = d_all$voltINT_sup8m, calEext = d_all$voltEXT_sup8m, calpH = d_all$pH_s_seafet_temp_insitu_sup8m,
-                          calT = d_all$temp_mix, calSal = d_all$sal_mix )
+calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_ctd,
+                          calT = d_all$temp_insitu_ctd, calSal = d_all$sal_insitu_ctd )
 # put number of deployment 
@@
 ####
-seafet_calib <- sf_calc(calEint = d_all$voltINT_sup8m, calEext = d_all$voltEXT_sup8m, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_mix, calSal = d_all$sal_mix_interp)
+seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu_ctd, calSal = d_all$sal_insitu_ctd)
 
@@
 d_all <- d_all%>%
-  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", pH_s_seafet_temp_insitu, NA ))
-
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_insitu,pHint_tot_sf, pH_s_sf_no_calb, pressure_insitu_ctd_filtered)
+  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", pH_s_seafet_temp_ctd, NA ))
+
+seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered, pH_s_seafet_temp_ctd, pHint_tot_sf, pH_s_sf_no_calb, pressure_insitu_ctd_filtered, sal_insitu_ctd, temp_insitu_ctd)
 #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
 dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-  dySeries("pressure_insitu_ctd_filtered", axis="y2",label = "Depth", color ="pink", strokeWidth=0, pointSize=2) %>%
+dySeries("temp_insitu_ctd", axis="y",label = "T ctd", color ="grey", strokeWidth=0, pointSize=2) %>%
+dySeries("sal_insitu_ctd", axis="y",label = "sS ctd", color ="orange", strokeWidth=0, pointSize=2) %>%
+dySeries("pressure_insitu_ctd_filtered", axis="y2",label = "Pression", color ="pink", strokeWidth=0, pointSize=2) %>%
 dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
 dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_seafet_temp_insitu", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+dySeries("pH_s_seafet_temp_ctd", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
 dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
@@
 
-p <- ggplot(d_all%>%filter(datetime >= ("2017-07-30")),aes(x=datetime, y= phINT_filtered, label = depth))+
-  geom_line( aes(color=factor(depth)))
-
-p_py <- ggplotly(p,dynamicTicks = TRUE)
-filename.html <- paste0("/figures/p_py.html")
-saveWidget(p_py, filename.html, selfcontained = T, libdir = "lib")
-
-getwd()
-
-seafet_depth_xts <- dplyr::select(d_all, datetime, phINT_filtered, depth)
+# p <- ggplot(d_all%>%filter(datetime >= ("2017-07-30") & !is.na(depth) ),aes(x=datetime, y= phINT_filtered, label = depth))+
+#   geom_point( aes(color=factor(depth)), size=1, alpha=0.5, na.rm=TRUE)
+
+###Plotly
+# p_py <- ggplotly(p,dynamicTicks = TRUE)
+# filename.html <- paste0("p_py.html")
+# saveWidget(p_py, filename.html, selfcontained = T, libdir = "lib")
+
+seafet_depth_xts <- dplyr::select(d_all, datetime, phINT_filtered, pH_s_seafet_temp_ctd,pHint_tot_sf)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
 dygraph(seafet_depth_xts, group = "depth", main="pH seaFET RAW (in situ)", ylab="pHT") %>%
+  dySeries("pH_s_seafet_temp_ctd", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
   dySeries("phINT_filtered", axis="y2",label = "pH RAW", color ="green", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%
-  #dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
-  #dyGroup(depth, drawPoints = TRUE, color = "green")%>%
+  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
@@
 # # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_insitu, temp_sf, temp_fb, temp_insitu, sal)
+# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_ctd, temp_sf, temp_fb, temp_insitu, sal)
 # #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
 #   #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-#    # dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
+#    # dySeries("pH_s_seafet_temp_ctd", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
 #     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
@@
 # sfoffset <- left_join(sfPeriod[,c(1,2)], d_all%>%dplyr::select(datetime, pHint_tot_sf), by="datetime")
-# dat <- mutate(sfoffset, diff_pH_sf = round((pH_s_seafet_temp_insitu - pHint_tot_sf),digits  = 4))
+# dat <- mutate(sfoffset, diff_pH_sf = round((pH_s_seafet_temp_ctd - pHint_tot_sf),digits  = 4))
 # average_offset <- mean(abs(dat$diff_pH_sf), na.rm=TRUE)
@@
 #   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_insitu, fill="Discrete measurements"), col="red" )+
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_ctd, fill="Discrete measurements"), col="red" )+
 #   labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
@@
 durPeriod <- d_all%>%
-  dplyr::select(datetime, pH_s_durafet_temp_insitu)%>%
-  dplyr::filter(!is.na(pH_s_durafet_temp_insitu))
+  dplyr::select(datetime, pH_s_durafet_temp_fb)%>%
+  dplyr::filter(!is.na(pH_s_durafet_temp_fb))
 
@@
 # Offset between durafet pH and spec pH 
-duroffset <- left_join(durPeriod%>%dplyr::select(datetime,pH_s_durafet_temp_insitu), d_all%>%dplyr::select(datetime,pH_durafet ), by="datetime")
-dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_insitu - pH_durafet)
+duroffset <- left_join(durPeriod%>%dplyr::select(datetime,pH_s_durafet_temp_fb), d_all%>%dplyr::select(datetime,pH_durafet ), by="datetime")
+dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_fb - pH_durafet)
 average_offset_dur <- round(mean(dat_dur$diff_pH_dur, na.rm=TRUE), digits = 2)
@@
 d_all <- d_all%>%
-  dplyr::mutate( pH_s_dur_no_calb = ifelse(datetime == "2017-08-24 13:00:00", pH_s_durafet_temp_insitu, NA ))
-
-durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_insitu,pH_durafet_corrected, pH_s_dur_no_calb)
+  dplyr::mutate( pH_s_dur_no_calb = ifelse(datetime == "2017-08-24 13:00:00", pH_s_durafet_temp_fb, NA ))
+
+durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_fb,pH_durafet_corrected, pH_s_dur_no_calb)
 durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
@@
     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_durafet_temp_insitu", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
+    dySeries("pH_s_durafet_temp_fb", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
        dySeries("pH_s_dur_no_calb", label = "pH spectro no calibration", color ="black", pointShape = "triangle",strokeWidth=0, pointSize=6) %>%
@@
 #   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_insitu, fill="Discrete measurements"), col="red" )+
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_fb, fill="Discrete measurements"), col="red" )+
 #   labs(x = "", y= "", title = expression(pH[T]~durafet)) +
@@
   #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
-  summarize(Tinsi_max =round( max(temp_mix, na.rm=TRUE), digits = 2),
-            Tinsi_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
-            sal_max = round(max(sal_mix, na.rm=TRUE), digits = 2),
-            sal_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
+  summarize(temp_mix_max =round( max(temp_mix, na.rm=TRUE), digits = 2),
+            temp_mix_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
+            temp_ctd_max =round( max(temp_insitu_ctd, na.rm=TRUE), digits = 2),
+            temp_ctd_min = round(min(temp_insitu_ctd, na.rm=TRUE), digits = 2),
+            temp_11m_max =round( max(temp_insitu_11m, na.rm=TRUE), digits = 2),
+            temp_11m_min = round(min(temp_insitu_11m, na.rm=TRUE), digits = 2),
+            temp_fb_max = round(max(temp_fb, na.rm=TRUE), digits = 2),
+            temp_fb_min =round( min(temp_fb, na.rm=TRUE), digits = 2),
+            sal_mix_max = round(max(sal_mix, na.rm=TRUE), digits = 2),
+            sal_mix_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
+            sal_ctd_max = round(max(sal_insitu_ctd, na.rm=TRUE), digits = 2),
+            sal_ctd_min = round(min(sal_insitu_ctd, na.rm=TRUE), digits = 2),
+            sal_fb_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
+            sal_fb_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
             pH_sf_max = round(max(pHint_tot_sf, na.rm=TRUE), digits = 4),
             pH_sf_min = round(min(pHint_tot_sf, na.rm=TRUE), digits = 4))
-kable(range_month)
+kable(range_month, caption ="")
 ```
@@
 pH_sf <- d_all %>%
-  dplyr::select(datetime, sal_mix,temp_fb,temp_mix, pHint_tot_sf)%>%
-  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_mix), !is.na(temp_fb), !is.na(sal_mix)) %>%
+  dplyr::select(datetime, sal_insitu_ctd,temp_insitu_ctd, pHint_tot_sf)%>%
+  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd), !is.na(sal_insitu_ctd)) %>%
   dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
-pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_mix, Pinsi=11, S=pH_sf$sal_mix, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd, Pinsi=11/10, S=pH_sf$sal_insitu_ctd, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
 pH_dur <- d_all %>%
-  dplyr::select(datetime, sal_mix,temp_fb,temp_mix, pH_durafet_corrected)%>%
-  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_mix), !is.na(temp_fb), !is.na(sal_mix))
-pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_mix, Pinsi=11, S=pH_dur$sal_mix, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+  dplyr::select(datetime, sal_fb,temp_fb, pH_durafet_corrected)%>%
+  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_fb), !is.na(sal_fb))
+pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
@@
 pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pHint_tot_sf_norm4, label = month))+
-  geom_text( aes(color=factor(month))) + 
+  geom_point( aes(color=factor(depth)), size =1, alpha=0.5) + 
+  facet_wrap( ~ factor(depth), ncol = 3) +
+  stat_smooth(data = d_all, aes(x = pH_durafet_norm4, y = pHint_tot_sf_norm4, color=depth),
+              method=lm, na.rm=TRUE, se=FALSE) +
  # scale_color_viridis_d(option = "C", guide="none")+
-  geom_line(aes(x = pHint_tot_sf_norm4, y = pHint_tot_sf_norm4), linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("pH seaFET vs pH durafet, normalized 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
+  #geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+  #labs(title = paste("pH seaFET vs pH durafet, normalized 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
+   #                  "; Intercept =", signif(fit$regression.results[2,2], 3),
+    #                 "; Slope =", signif( fit$regression.results[2,3], 3),
+    #                 "; P =", signif(fit$P.param, 3))) +
   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 , xlim=c(7.8,8.35), ylim=c(7.8,8.35))+ scale_colour_discrete(guide="none") +
-  labs( x="pH durafet, 4°C", y="pH seaFET, 4°C ", color = "Months")  +theme_bw()
+  coord_fixed(ratio = 1 , xlim=c(7.8,8.35), ylim=c(7.8,8.35))+ #scale_colour_discrete(guide="none") +
+  labs( x="pH durafet, 4°C", y="pH seaFET, 4°C ", color = "Depth ")  +theme_bw()
 
@@
 pH_calc <- discrete %>%
-  dplyr::select(datetime, sal,temp, phcalc, at)%>%
-  dplyr::filter(!is.na(phcalc), !is.na(temp), !is.na(sal))
-pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+  dplyr::select(datetime, sal_fb,temp_fb, phcalc, at)%>%
+  dplyr::filter(!is.na(phcalc), !is.na(temp_fb), !is.na(sal_fb))
+pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
@@
 # Spectro / durafet
-fit <- lmodel2(data = d_all,  pH_s_durafet_temp_insitu ~ pH_durafet_corrected , nperm = 99)
-
-p_dura_spectro <-  ggplot(d_all,aes(x=pH_durafet_corrected, y= pH_s_durafet_temp_insitu, label = month))+
+fit <- lmodel2(data = d_all,  pH_s_durafet_temp_fb ~ pH_durafet_corrected , nperm = 99)
+
+p_dura_spectro <-  ggplot(d_all,aes(x=pH_durafet_corrected, y= pH_s_durafet_temp_fb, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
 # Spectro / seafet
-fit <- lmodel2(data = d_all,  pH_s_seafet_temp_insitu ~ pHint_tot_sf , nperm = 99)
-
-p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_insitu, label = month))+
+fit <- lmodel2(data = d_all,  pH_s_seafet_temp_ctd ~ pHint_tot_sf , nperm = 99)
+
+p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_ctd, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
 <!--  # DURAFET  -->
-<!-- durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_insitu) -->
+<!-- durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_fb) -->
 <!-- durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime) -->
@@
 <!--     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>% -->
-<!--     dySeries("pH_s_durafet_temp_insitu", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
+<!--     dySeries("pH_s_durafet_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
 <!--     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>% -->
@@
 <!-- # SEAFET  -->
-<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_insitu) -->
+<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_ctd) -->
 <!-- seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime) -->
@@
 <!--   dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>% -->
-<!--   dySeries("pH_s_seafet_temp_insitu", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
+<!--   dySeries("pH_s_seafet_temp_ctd", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
 <!--   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>% -->

### 2020-03-26 awipev-CO2.Rmd
minor text corrections

@@
 discrete <- rbind(discrete_no_na, discrete_is_na)
-discrete%>%dplyr::arrange(datetime)
+discrete <-discrete%>%dplyr::arrange(datetime)
 ```
@@
 
-# # PLOT
-seafet_contros_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb, sal_mix)
-seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_contros_xts, group = "awipev", main="Salinities", ylab="PSU") %>%
-dySeries("sal_insitu_ctd", label = "sal_insitu_ctd", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=4) %>%
-dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#dySeries("pressure_insitu_ctd_filtered", label = "pressure_insitu_ctd_filtered", color ="black", strokeWidth=0, pointSize=2) %>%
-  dyLegend(show = "onmouseover")   %>%
-  #dyAxis( "y2",valueRange = c(-3, 36))%>%
-  dyAxis( "y2",valueRange = c(25, 36))%>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-  dyRangeSelector(height = 30, dateWindow= NULL)
-
 # #Plot for philipp
@@
 
+```
+
+```{r Sal plot, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+seafet_contros_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb, sal_mix)
+seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+dygraph(seafet_contros_xts, group = "awipev", main="Salinities", ylab="PSU") %>%
+dySeries("sal_insitu_ctd", label = "sal_insitu_ctd", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=4) %>%
+dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
+#dySeries("pressure_insitu_ctd_filtered", label = "pressure_insitu_ctd_filtered", color ="black", strokeWidth=0, pointSize=2) %>%
+  dyLegend(show = "onmouseover")   %>%
+  #dyAxis( "y2",valueRange = c(-3, 36))%>%
+  dyAxis( "y2",valueRange = c(25, 36))%>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyRangeSelector(height = 30, dateWindow= NULL)
 ```
@@
   dySeries("pH_s_seafet_temp_ctd", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-  dySeries("phINT_filtered", axis="y2",label = "pH RAW", color ="green", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%
-  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
+  dySeries("phINT_filtered", axis="y2",label = "pH RAW", color ="blue", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%
+  dySeries("pHint_tot_sf", axis="y2", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%

### 2020-03-27 paper.Rmd
revised tem_sal figs and regressions

@@
 ```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
+#R --quiet -e 'install.packages("plotly", type="binary", repos="http://cran.us.r-project.org")'
 Sys.setlocale("LC_ALL", "en_US.UTF-8")
@@
 
-```{r temperature vs salinity plots, fig.width=8, fig.height=8, echo=FALSE, message= FALSE}
+```{r temperature vs salinity plots, echo=FALSE, message= FALSE, warning=FALSE, out.width="100%"}
 # One tries to identify water masses coming from the Atlantic or freshwater
@@
   labs(title="Temperature vs salinity, both in FerryBox, blue lines show density", x="Salinity", y="Temp. (°C)") +
-  facet_wrap(~ year, ncol = 3) +
+  facet_grid(year ~ month) +
   stat_smooth(data = d, aes(x = sal_fb, y = temp_fb, color=month),
-              method=lm, na.rm=TRUE, se=FALSE) +
-  scale_color_viridis(name="Month", discrete=TRUE, option="plasma") +
+              method=lm, na.rm=TRUE, se=FALSE, show.legend=FALSE) +
+  #scale_color_viridis(name="Month", discrete=TRUE, option="plasma") +
   geom_contour(data = grid, aes(x = s, y = t, z = z), 
@@
   coord_fixed() +
-  annotate("text", label="Fresh and cold", x=31.5, y=-1.5) +
-  annotate("text", label="Salty and warm", x=34.5, y=8.1) +
+  #annotate("text", label="Fresh and cold", x=31.5, y=-1.5) +
+  #annotate("text", label="Salty and warm", x=34.5, y=8.1) +
   Mytheme(size_labs = 10)
@@
 
-```{r temperature vs salinity regressions, echo=FALSE, message= FALSE, out.width="50%"}
+```{r temperature vs salinity regressions, echo=FALSE, message= FALSE, warning=FALSE, out.width="50%"}
 # AT as a function of salinity for every year
@@
                 month = month(date, label=TRUE, abbr = TRUE))
+tab_reg_temp_sal <- tab_reg_temp_sal[sort(rownames(tab_reg_temp_sal)),] # order chronologically
+
 #plot
@@
   guides(colour = guide_legend("Month", override.aes = list(size=4)), size = guide_legend("P value slope"))
-kable(tab_reg_temp_sal)
+kable(tab_reg_temp_sal, caption = "Regression lines", digits = c(3,3,5,1,3,3,1,0,2,5)) %>%
+    kable_styling(full_width=FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
 print(fig_reg_temp_sal)

### 2020-03-28 awipev-CO2.Rmd

@@
 dygraph(seafet_depth_xts, group = "depth", main="pH seaFET RAW (in situ)", ylab="pHT") %>%
-  dySeries("pH_s_seafet_temp_ctd", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+  dySeries("pH_s_seafet_temp_ctd", axis="y2", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
   dySeries("phINT_filtered", axis="y2",label = "pH RAW", color ="blue", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%

### 2020-04-16 awipev-CO2 copy.Rmd
beleated update

--- 2020-03-26 awipev-CO2.Rmd
@@
 library(scales)
-library(plotly)
-library(htmlwidgets)
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
-d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
-# load = d_hour
-d_hour <- d_hour %>%
-  dplyr::select(-date) %>%
-  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
-         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
-         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
-         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
-         ) %>%
-  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered, temp_durafet = HW_Temperature1_filtered, temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered, temp_sf=T_seaF)
-
-d_all <- d_hour #d_all will be the merger
-d_all<- d_all%>%
-  dplyr::mutate(month = month(month(datetime)))
-
-```
-
 ```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
@@
 
-# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_hour TO d, to use pHinsi
-# use the closest time to add them
-closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
-d$closest_datetime <- d_all$datetime[closest]
-# if the closest value is more than 30 min away, then we do not take it
-d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
-# create closest_datetime in d_all (copy of datetime)
-d_all$closest_datetime <- d_all$datetime
-d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, sal_insitu_ctd, temp_insitu_ctd)), by="closest_datetime")
-
 # Conversion of spectro pH to a same T°
 pH_seafet <- d %>%
-  dplyr::filter(!is.na(pH_s_seafet)& !is.na(sal_insitu_ctd) )
+  dplyr::filter(!is.na(pH_s_seafet))
 pH_seafet <- pH_seafet %>%
-  dplyr::mutate(pH_s_seafet_temp_ctd = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_insitu_ctd, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_insitu_ctd,Pt=0,Sit=0))
+  dplyr::mutate(pH_s_seafet_temp_field = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_field, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$salinity_field,Pt=0,Sit=0))
 
@@
 pH_durafet <- pH_durafet %>%
-  dplyr::mutate(pH_s_durafet_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb,Pt=0,Sit=0))
+  dplyr::mutate(pH_s_durafet_temp_field = pHinsi(pH=pH_durafet$pH_s_durafet,ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_field, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$salinity_field,Pt=0,Sit=0))
 
@@
 pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(datetime,pH_s_seafet_temp_ctd)%>% 
+  dplyr::select(datetime,pH_s_seafet_temp_field)%>% 
   dplyr::group_by(datetime) %>% 
-  dplyr::summarize(pH_s_seafet_temp_ctd = mean(pH_s_seafet_temp_ctd, na.rm = T))
+  dplyr::summarize(pH_s_seafet_temp_field = mean(pH_s_seafet_temp_field, na.rm = T))
 pH_durafet_mean <- pH_durafet%>%
-  dplyr::select(datetime,pH_s_durafet_temp_fb)%>% 
+  dplyr::select(datetime,pH_s_durafet_temp_field)%>% 
   dplyr::group_by(datetime) %>% 
-  dplyr::summarize(pH_s_durafet_temp_fb = mean(pH_s_durafet_temp_fb, na.rm = T))
+  dplyr::summarize(pH_s_durafet_temp_field = mean(pH_s_durafet_temp_field, na.rm = T))
 
@@
   dplyr::group_by(datetime) %>% 
-  dplyr::summarize(sal_fb = mean(sal_fb, na.rm = T),
-                   temp_fb = mean(temp_fb, na.rm = T),
+  dplyr::summarize(sal = mean(salinity_field, na.rm = T),
+            temp = mean(temp_field, na.rm = T),
             at_mean_interp = mean(at_mean_interp, na.rm = T),
@@
 ##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
-##   *****Attention, I asked to the logisticians to log insitu temp from 9 june 2019
+##   *****Attention, I asked to the logisticians to log outside temp from 9 june 2019
 
@@
 
-discrete_no_na <- discrete %>%
-  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
-discrete_is_na <- discrete %>%
-  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
-
-carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6,S=discrete_no_na$sal_fb, T=discrete_no_na$temp_fb, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
-
-discrete_no_na$phcalc<- carb$pH
-discrete_no_na$pco2calc<- carb$pCO2
-
-#create new variable in "discrete_is_na" to bind "discrete_no_na"
-discrete_is_na$phcalc<- NA
-discrete_is_na$pco2calc<- NA
-discrete <- rbind(discrete_no_na, discrete_is_na)
-discrete%>%dplyr::arrange(datetime)
+carb <- carb(15, discrete$at*1e-6, discrete$ct*1e-6,S=discrete$sal, T=discrete$temp, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
+discrete$phcalc<- carb$pH
+discrete$pco2calc<- carb$pCO2
+```
+
+```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
+d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
+# load = d_hour
+d_hour <- d_hour %>%
+  dplyr::select(-date) %>%
+  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
+         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
+         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
+         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
+         ) %>%
+  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered,temp_insitu=Temp_SBE38_filtered, sal_fb=sal_fb_filtered, sal_insitu=sal_insitu_filtered, sal=sal_filtered, temp_fb=temp_fb_filtered)
 ```
@@
 ```{r Combine discrete and continous data, echo=FALSE}
-
+d_all <- d_hour #d_all will be the merger
+d_all<- d_all%>%
+  dplyr::mutate(month = month(month(datetime)))
 # at
@@
   #drop_na() %>%
-  dplyr::select(closest_datetime, pH_s_seafet_temp_ctd) %>%
+  dplyr::select(closest_datetime, pH_s_seafet_temp_field) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
   #drop_na() %>%
-  dplyr::select(closest_datetime, pH_s_durafet_temp_fb) %>%
+  dplyr::select(closest_datetime, pH_s_durafet_temp_field) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 
-```{r Depth filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-#Make groups
-
-d_all <- d_all%>%
-  dplyr::mutate(depth = ifelse(pressure_insitu_ctd_filtered <=2, "1 m", 
-                        ifelse(pressure_insitu_ctd_filtered >2 & pressure_insitu_ctd_filtered <=4, "3 m", 
-                        ifelse(pressure_insitu_ctd_filtered >4 & pressure_insitu_ctd_filtered <=6, "5 m",
-                        ifelse(pressure_insitu_ctd_filtered >6 & pressure_insitu_ctd_filtered <=8, "7 m",
-                        ifelse(pressure_insitu_ctd_filtered >8, "9 m",NA))))))
-```
-
-```{r Sal filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-#### filter salinities above 28
-d_all <- d_all%>%
-  dplyr::mutate( sal_fb = ifelse(sal_fb <28, NA, sal_fb),
-                 sal_insitu_ctd = ifelse(sal_insitu_ctd <28, NA, sal_insitu_ctd))
- d_all <- d_all%>%
-  dplyr::mutate(sal_insitu_ctd = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu_ctd))
-
-########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
-d_all <- d_all %>%
-  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, 
-                               ifelse (pressure_insitu_ctd_filtered >=8 ,sal_insitu_ctd, NA )))
-### remove sal_mix datat that seem to be to high compared to sal_fb
-  d_all <- d_all%>%
-  dplyr::mutate(sal_mix = ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-13 18:00:00" , NA, 
-                          ifelse(datetime > "2018-05-21 19:00:00" & datetime < "2018-05-24 17:00:00" , NA,
-                          ifelse(datetime > "2018-05-28 06:00:00" & datetime < "2018-06-03 13:00:00" , NA,
-                          ifelse(datetime > "2018-06-16 06:00:00" & datetime < "2018-06-21 05:00:00" , NA,
-                          ifelse(datetime > "2019-12-02 08:00:00" & datetime < "2019-12-03 08:00:00" , NA,
-                          ifelse(datetime > "2019-12-09 07:00:00" & datetime < "2019-12-09 10:00:00" , NA, 
-                          ifelse(datetime > "2019-12-09 15:00:00" & datetime < "2019-12-09 18:00:00" , NA,
-                          ifelse(datetime > "2019-12-10 14:00:00" & datetime < "2019-12-10 18:00:00", NA, sal_mix)))))))))
-
-```
-
-```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
-d_all <- d_all %>%
-  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, 
-                               ifelse (pressure_insitu_ctd_filtered >=8 ,temp_insitu_ctd, NA )))
-```
-
 ## Whole time series
 ```{r whole time series, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-#SAL MIX
-sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd)
+#SAL
+sal_xts <- dplyr::select(d_all, datetime, sal)%>%
+  dplyr::filter(sal >28)
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
-dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD)", ylab="Salinity") %>%
-      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "S") %>%
+dygraph(sal_xts, group = "awipev", main="Salinity", ylab="Salinity") %>%
+      dySeries("sal", color = "blue", strokeWidth = 0, label = "S") %>%
       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
 # TEMP insitu SBE38
-temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_11m)
+temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu)
 temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
-dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ 11 m)", ylab="Temperature") %>%
-      dySeries("temp_insitu_11m", color = "blue", strokeWidth = 0, label = "T") %>%
+dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ)", ylab="Temperature") %>%
+      dySeries("temp_insitu", color = "blue", strokeWidth = 0, label = "T") %>%
       dyAxis("y", valueRange = c(-2.8, 10)) %>%
@@
 # DURAFET 
-durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_fb)
+durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field)
 durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
@@
     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_durafet_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
@@
 # SEAFET 
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_ctd)
+seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field)
 seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ T CTD)", ylab="pHT") %>%
+dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
   dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-  dySeries("pH_s_seafet_temp_ctd", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+  dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
@@
 
+```{r water masses, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
+# One tries to identify water masses coming from the Atlantic or freshwater
+
+```
+
 ## Salinities
-Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically.
-Salinity from FB is taken in consideration.
-If data gaps are encountered, they are filled with bottom salinty data from ctd (> 8 m).
-New column "sal_mix" is created.
+Several salinity sensors are on site, 1 inside the Ferrybox and 1 outside. Note that several CTD have been replace in situ. The sal_insitu variable combine all these CTD salinity measurements:
 
 - 1 SBE45 inside the Ferrybox (sal_fb)
-- 5 CTD > 8 meters depth (sal_insitu_ctd)
+- 1 CTD at 11 meters depth (sal_insitu)
 
@@
 
-### **Sal FB / Sal CTD > 8 m **
-
-Property-property salinity plot using:
-
-fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)
-
+### **Sal FB / Sal *in situ* **
 ```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)
-
-# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,sal_fb,sal_insitu_ctd)
-# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
-# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
-#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
-#   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
-#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
-#   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2)
-
-# date format into charactere
-d_all$datetime_chr <- as.character(d_all$datetime)
-
-p_sal_fb_ctd<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
-  geom_point( aes(color=factor(datetime_chr))) + 
+
+d_all <- d_all%>%
+  dplyr::mutate( sal = ifelse(sal <28, NA, sal) ,
+                 sal_fb = ifelse(sal_fb <28, NA, sal_fb),
+                 sal_insitu = ifelse(sal_insitu <28, NA, sal_insitu))
+  d_all <- d_all%>%
+  dplyr::mutate( sal = ifelse(datetime > "2019-12-26 00:00:00", NA, sal),
+                 sal_insitu = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu))
+
+fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu , nperm = 99)
+
+p_sal_fb_sal_insitu<-  ggplot(d_all,aes(x=sal_insitu, y= sal_fb, label = month))+
+  geom_text( aes(color=factor(month))) + 
  # scale_color_viridis_d(option = "C", guide="none")+
-  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
-  geom_abline(slope=1, intercept=0, linetype = "dashed")+
+  geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
-  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
+  labs(title = paste("Sal in situ vs Sal FB","\n Adj R2 = ", signif(fit$rsquare, 3),
                      "; Intercept =", signif(fit$regression.results[2,2], 3),
@@
                      "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
-  coord_fixed(ratio = 1 )+
-   scale_colour_discrete(guide="none") +
-  labs( x="Salinity CTD > 8 m", y="Salinity FB ", color = "Months") +theme_bw()
-
-print(p_sal_fb_ctd)
-
-d_all$diff_sal_fb_insitu <- d_all$sal_insitu_ctd - d_all$sal_fb
+  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
+  labs( x="Salinity insitu", y="Salinity FB ", color = "Months")  +theme_bw()
+print(p_sal_fb_sal_insitu)
+
+d_all$diff_sal_fb_insitu <- d_all$sal_insitu - d_all$sal_fb
 mean_diff_sal_fb_insitu <- round(mean(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)
@@
 
-### Plotly
-# p_p_sal_fb_ctd <- ggplotly(p_sal_fb_ctd,dynamicTicks = TRUE)
-# filename.html <- paste0("p_p_sal_fb_ctd.html")
-# saveWidget(p_p_sal_fb_ctd, filename.html, selfcontained = T, libdir = "lib")
-
-# # PLOT
-seafet_contros_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb, sal_mix)
+# PLOT
+seafet_contros_xts <- dplyr::select(d_all, datetime, sal_fb, sal_insitu, sal)
 seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_contros_xts, group = "awipev", main="Salinities", ylab="PSU") %>%
-dySeries("sal_insitu_ctd", label = "sal_insitu_ctd", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=4) %>%
-dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#dySeries("pressure_insitu_ctd_filtered", label = "pressure_insitu_ctd_filtered", color ="black", strokeWidth=0, pointSize=2) %>%
-  dyLegend(show = "onmouseover")   %>%
+dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+  dySeries("sal_insitu", label = "sal_insitu", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
+dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dyLegend(show = "auto")   %>%
   #dyAxis( "y2",valueRange = c(-3, 36))%>%
-  dyAxis( "y2",valueRange = c(25, 36))%>%
+  #dyAxis( "y",valueRange = c(-2, 2))%>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
   dyRangeSelector(height = 30, dateWindow= NULL)
@@
 ## Temperatures
-Several temperature sensors are on site, 1 inside the Ferrybox (SBE45), 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically and 1 fixed at 11 m depth (sbe38). 
-Temperature in situ at 11 m depth is taken in consideration.
-If data gaps are encountered, they are filled with bottom temperature data from ctd (> 8 m).
-New column "temp_mix" is created.
-For the moment, no gaps are encountered and temp_mix = temp_insitu_11m.
+Several temperature sensors are on site, 1 inside the Ferrybox and 2 outside:
 
 - 1 SBE45 inside the Ferrybox (temp_fb)
-- 5 CTD > 8 meters depth (temp_insitu_ctd)
-- 1 fixed at 11 meters depth (temp_insitu_11m)
+- 1 seaFET T°C inside the seaFET at 11 meters depth (T_seaF)
+- 1 SBE38 at 11 meters depth (temp_insitu)
 
@@
 
-### **T Ferrybox / T insitu 11 m **
-
-Property-property temperature plot using:
-
-fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)
-
+### **T seaFET / T in situ **
+```{r Temp comparaison, echo=FALSE, message= FALSE, warning=FALSE}
+# seaF outliers (T - volt int - volt ext) to remove from 2017-12-10 to 2017-12-14
+d_all <- d_all %>%
+  dplyr::mutate(T_seaF = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, T_seaF),
+                voltINT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltINT), 
+                voltEXT = ifelse(datetime >= "2017-12-10 11:00:00" & datetime <= "2017-12-14 12:00:00", NA, voltEXT))
+
+fit <- lmodel2(data = d_all,  T_seaF ~ temp_insitu , nperm = 99)
+
+pTseaf_Tinsi<-  ggplot(d_all,aes(x=temp_insitu, y= T_seaF, label = month))+
+  geom_text( aes(color=factor(month))) + 
+ # scale_color_viridis_d(option = "C", guide="none")+
+  geom_line(aes(x = T_seaF, y = T_seaF), linetype = "dashed") +
+  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+  labs(title = paste("T seaF vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
+                     "; Intercept =", signif(fit$regression.results[2,2], 3),
+                     "; Slope =", signif( fit$regression.results[2,3], 3),
+                     "; P =", signif(fit$P.param, 3))) +
+  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
+  labs( x="T insi", y="T seaF ", color = "Months")  +theme_bw()
+print(pTseaf_Tinsi)
+
+d_all$diff_T_seaF_insitu <- d_all$T_seaF - d_all$temp_insitu
+mean_diff_T_seaF_insitu <- round(mean(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)
+sd_diff_T_seaF_insitu <- round(sd(d_all$diff_T_seaF_insitu, na.rm = TRUE), digits = 2)
+
+```
+
+The mean difference between T seaFET and in situ is: `r mean_diff_T_seaF_insitu` ± `r sd_diff_T_seaF_insitu`°C.
+
+### **T Ferrybox / T in situ **
 ```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
@@
 
-fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)
-
-p_temp_11_fb<-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
-  geom_text( aes(color=factor(datetime_chr))) + 
+fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu , nperm = 99)
+
+pTfb_Tinsi<-  ggplot(d_all,aes(x=temp_insitu, y= temp_fb, label = month))+
+  geom_text( aes(color=factor(month))) + 
  # scale_color_viridis_d(option = "C", guide="none")+
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
+  geom_line(aes(x = temp_fb, y = temp_fb), linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
+  labs(title = paste("T FB vs T insi","\n Adj R2 = ", signif(fit$rsquare, 3),
                      "; Intercept =", signif(fit$regression.results[2,2], 3),
@@
   coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
-  labs( x="T 11 m", y="T FB ", color = "Months")  +theme_bw()
-print(p_temp_11_fb)
-
-d_all$diff_T_fb_11m <- d_all$temp_fb - d_all$temp_insitu_11m
-mean_diff_T_fb_11m <- round(mean(d_all$diff_T_fb_11m, na.rm = TRUE), digits = 2)
-sd_diff_T_fb_11m <- round(sd(d_all$diff_T_fb_11m, na.rm = TRUE), digits = 2)
-
-### Plotly
-# p_p_temp_11_fb <- ggplotly(p_temp_11_fb,dynamicTicks = TRUE)
-# filename.html <- paste0("p_p_temp_11_fb.html")
-# saveWidget(p_p_temp_11_fb, filename.html, selfcontained = T, libdir = "lib")
-
-```
-
-The mean difference between temperature Ferrybox and in situ at 11 m is: `r mean_diff_T_fb_11m` ± `r sd_diff_T_fb_11m`°C.
-
-### **T 11 m / T CTD > 8 m **
-
-Property-property temperature plot using:
-
-fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)
-
-```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-
-fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)
-
-p<-  ggplot(d_all,aes(x=temp_insitu_ctd, y= temp_insitu_11m, label = month))+
-  geom_text( aes(color=factor(month))) + 
- # scale_color_viridis_d(option = "C", guide="none")+
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("T CTD > 8 m vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
-  labs( x="T CTD > 8 m", y="T 11 m ", color = "Months")  +theme_bw()
-print(p)
-
-d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd
-mean_diff_T_ctd_11m <- round(mean(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
-sd_diff_T_ctd_11m <- round(sd(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
-```
-
-The mean difference between temperature Ferrybox and in situ at 11 m is: `r mean_diff_T_ctd_11m` ± `r sd_diff_T_ctd_11m`°C.
+  labs( x="T insi", y="T FB ", color = "Months")  +theme_bw()
+print(pTfb_Tinsi)
+
+d_all$diff_T_fb_insitu <- d_all$T_seaF - d_all$temp_insitu
+mean_diff_T_fb_insitu <- round(mean(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
+sd_diff_T_fb_insitu <- round(sd(d_all$diff_T_fb_insitu, na.rm = TRUE), digits = 2)
+```
+
+The mean difference between T seaFET and in situ is: `r mean_diff_T_fb_insitu` ± `r sd_diff_T_fb_insitu`°C.
 
@@
   - and during the **third period**, with the new analyzer (2018-01-07 to 2018-06-20)
+
+```{r TA 2nd cleaning , echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
+
+```
 
@@
 d_all_at_discrete <- d_all %>% #  To remove an outlier in red
-  dplyr::select(datetime, month,closest_datetime, at, sal_mix) #%>%
- # dplyr::filter( !is.na(at) & !is.na(sal) & sal >30)
+  dplyr::select(datetime, month,closest_datetime, at, sal)%>%
+  dplyr::filter( !is.na(at) & !is.na(sal) & sal >30)
 
@@
 #fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal)
-fit <- lm(data = d_all_at_discrete, at ~ sal_mix)
+fit <- lm(data = d_all_at_discrete, at ~ sal)
 slope_s_at <- fit$coefficients[[2]]
@@
 
-at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at, label = month))+
+at_s <- ggplot(d_all_at_discrete,aes(x=sal, y= at, label = month))+
   geom_text( aes(color=factor(month))) +
@@
 # Salinity is a predictor of AT -> using the regression defined above
-d_all$at_calc <- slope_s_at * d_all$sal_mix + intercept_s_at
+d_all$at_calc <- slope_s_at * d_all$sal + intercept_s_at
 ```
@@
 ### **Corrected Contros vs calculated *p*CO~2~ data**
+
+```{r pCO2 2nd cleaning, echo=FALSE, warning=FALSE, message=FALSE}
+
+```
 
@@
 Because of issue, measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17.
-*Note that pH sensor is mounted on a profiling structure.
-Here, only seaFET data recorded with a depth > 8 m are taken in consideration.* pH calibration is based on monthly discrete samples that are analysed with spectrophotometric method in Villefranche by Samir Alliouane.
+pH calibration is based on monthly discrete samples that are analysed with spectrophotometric method in Villefranche by Samir Alliouane.
 When it is not possible to sample at the vicinity of the sensor for practice reasons (in winter), sampling is done in the harbour and is not taken in consideration for calibration for spatial reasons.
@@
 # sfPeriod <- d_all%>%
-#   dplyr::select(datetime, pH_s_seafet_temp_ctd)%>%
-#   dplyr::filter(!is.na(pH_s_seafet_temp_ctd))
+#   dplyr::select(datetime, pH_s_seafet_temp_field)%>%
+#   dplyr::filter(!is.na(pH_s_seafet_temp_field))
 # # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
@@
   dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
-  dplyr::summarise( mean(temp_sf, na.rm = TRUE))
+  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
 mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
 d_all <- d_all%>%
-  dplyr::mutate(temp_mix = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_mix))
+  dplyr::mutate(temp_insitu = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_insitu))
 
@@
   dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
-  dplyr::summarise( mean(temp_sf, na.rm = TRUE))
+  dplyr::summarise( mean(T_seaF, na.rm = TRUE))
 mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
 d_all <- d_all%>%
-  dplyr::mutate(temp_mix = ifelse(datetime == "2019-09-13 13:00:00" , mean_TseaF_4h, temp_mix))
+  dplyr::mutate(temp_insitu = ifelse(datetime == "2019-09-13 13:00:00" , mean_TseaF_4h, temp_insitu))
 
 #interpolation of salinity during the FB off maintenance
-salinterp <-approx(d_all$datetime, d_all$sal_mix, xout=d_all$datetime, method="linear", rule=2)
-names(salinterp) <- c("datetime", "sal_mix_interp")
+salinterp <-approx(d_all$datetime, d_all$sal, xout=d_all$datetime, method="linear", rule=2)
+names(salinterp) <- c("datetime", "sal_interp")
 salinterp <- as.data.frame(salinterp)
-d_all$sal_mix_interp <- salinterp$sal_mix_interp
-
-d_all <- d_all %>%
-  dplyr::mutate(sal_mix_interp =  ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-16 16:00:00", sal_mix_interp, sal_mix))
+d_all$sal_interp <- salinterp$sal_interp
+
+d_all$sal <- ifelse(d_all$datetime > "2018-03-09 00:00:00" & d_all$datetime < "2018-04-16 16:00:00", d_all$sal_interp, d_all$sal)
+
+# test <- d_all%>%
+#   dplyr::filter(datetime=="2017-08-24 14:00:00")
 
@@
 ####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_ctd,
-                          calT = d_all$temp_insitu_ctd, calSal = d_all$sal_insitu_ctd )
+calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_field,
+                          calT = d_all$temp_insitu, calSal = d_all$sal )
 # put number of deployment 
@@
 ####
-seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu_ctd, calSal = d_all$sal_insitu_ctd)
+seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu, calSal = d_all$sal_interp)
 
@@
 d_all <- d_all%>%
-  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", pH_s_seafet_temp_ctd, NA ))
-
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered, pH_s_seafet_temp_ctd, pHint_tot_sf, pH_s_sf_no_calb, pressure_insitu_ctd_filtered, sal_insitu_ctd, temp_insitu_ctd)
+  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", pH_s_seafet_temp_field, NA ))
+
+seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field,pHint_tot_sf, pH_s_sf_no_calb)
 #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
 dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-dySeries("temp_insitu_ctd", axis="y",label = "T ctd", color ="grey", strokeWidth=0, pointSize=2) %>%
-dySeries("sal_insitu_ctd", axis="y",label = "sS ctd", color ="orange", strokeWidth=0, pointSize=2) %>%
-dySeries("pressure_insitu_ctd_filtered", axis="y2",label = "Pression", color ="pink", strokeWidth=0, pointSize=2) %>%
+  #dySeries("voltINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
   dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
     dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-dySeries("pH_s_seafet_temp_ctd", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pH_s_seafet_temp_field", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
     dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
@@
   dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
-  # dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
-  # dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
-  # dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
-  # dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
-  # dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
-  #  dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
-  #  dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
-  #  dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
-  # dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
-  #  dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
-  #  dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
+   dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
+   dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
+   dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
+   dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
+   dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
+  dyShading(from = sfinterv[22], to= Sys.Date(), color = "#E0E0E0") %>%
   dyLegend(show = "auto")   %>%
@@
 
-# p <- ggplot(d_all%>%filter(datetime >= ("2017-07-30") & !is.na(depth) ),aes(x=datetime, y= phINT_filtered, label = depth))+
-#   geom_point( aes(color=factor(depth)), size=1, alpha=0.5, na.rm=TRUE)
-
-###Plotly
-# p_py <- ggplotly(p,dynamicTicks = TRUE)
-# filename.html <- paste0("p_py.html")
-# saveWidget(p_py, filename.html, selfcontained = T, libdir = "lib")
-
-seafet_depth_xts <- dplyr::select(d_all, datetime, phINT_filtered, pH_s_seafet_temp_ctd,pHint_tot_sf)
-seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
-dygraph(seafet_depth_xts, group = "depth", main="pH seaFET RAW (in situ)", ylab="pHT") %>%
-  dySeries("pH_s_seafet_temp_ctd", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-  dySeries("phINT_filtered", axis="y2",label = "pH RAW", color ="green", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%
-  dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
-  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
-  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
-  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
-  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
+# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
+seafet_contros_xts <- dplyr::select(d_all, datetime, sal_fb, sal_insitu, sal)#voltINT, phINT_filtered,pH_s_seafet_temp_field, T_seaF, temp_fb, temp_insitu, sal)
+#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
+seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
+  #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
+   # dySeries("pH_s_seafet_temp_field", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
+    #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dySeries("sal_insitu", label = "sal_insitu", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
+dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=2) %>%
+  dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
+   # dySeries("T_seaF", label = "T_seaF", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
+ #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
+  #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
+  #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
+   # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
   dyLegend(show = "auto")   %>%
+  #dyAxis( "y2",valueRange = c(-3, 36))%>%
+  #dyAxis( "y",valueRange = c(-2, 2))%>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
   dyRangeSelector(height = 30, dateWindow= NULL)
-
-# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_ctd, temp_sf, temp_fb, temp_insitu, sal)
-# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
-# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-#   #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-#    # dySeries("pH_s_seafet_temp_ctd", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
-#     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dySeries("temp_insitu", label = "temp_insitu", color ="red", strokeWidth=0, pointSize=2) %>%
-# dySeries("temp_fb", label = "temp_fb", color ="blue", strokeWidth=0, pointSize=2) %>%
-#  # dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#    # dySeries("temp_sf", label = "temp_sf", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#  #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-#   #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
-#   #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-#    # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
-#   dyLegend(show = "auto")   %>%
-#   #dyAxis( "y2",valueRange = c(-3, 36))%>%
-#   dyAxis( "y",valueRange = c(-3, 9))%>%
-#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-#   dyRangeSelector(height = 30, dateWindow= NULL)
-# # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
+# #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
 
@@
 # sfoffset <- left_join(sfPeriod[,c(1,2)], d_all%>%dplyr::select(datetime, pHint_tot_sf), by="datetime")
-# dat <- mutate(sfoffset, diff_pH_sf = round((pH_s_seafet_temp_ctd - pHint_tot_sf),digits  = 4))
+# dat <- mutate(sfoffset, diff_pH_sf = round((pH_s_seafet_temp_field - pHint_tot_sf),digits  = 4))
 # average_offset <- mean(abs(dat$diff_pH_sf), na.rm=TRUE)
@@
 #   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_ctd, fill="Discrete measurements"), col="red" )+
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_field, fill="Discrete measurements"), col="red" )+
 #   labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
@@
 durPeriod <- d_all%>%
-  dplyr::select(datetime, pH_s_durafet_temp_fb)%>%
-  dplyr::filter(!is.na(pH_s_durafet_temp_fb))
+  dplyr::select(datetime, pH_s_durafet_temp_field)%>%
+  dplyr::filter(!is.na(pH_s_durafet_temp_field))
 
@@
 # Offset between durafet pH and spec pH 
-duroffset <- left_join(durPeriod%>%dplyr::select(datetime,pH_s_durafet_temp_fb), d_all%>%dplyr::select(datetime,pH_durafet ), by="datetime")
-dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_fb - pH_durafet)
+duroffset <- left_join(durPeriod%>%dplyr::select(datetime,pH_s_durafet_temp_field), d_all%>%dplyr::select(datetime,pH_durafet ), by="datetime")
+dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_field - pH_durafet)
 average_offset_dur <- round(mean(dat_dur$diff_pH_dur, na.rm=TRUE), digits = 2)
@@
 d_all <- d_all%>%
-  dplyr::mutate( pH_s_dur_no_calb = ifelse(datetime == "2017-08-24 13:00:00", pH_s_durafet_temp_fb, NA ))
-
-durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_fb,pH_durafet_corrected, pH_s_dur_no_calb)
+  dplyr::mutate( pH_s_dur_no_calb = ifelse(datetime == "2017-08-24 13:00:00", pH_s_durafet_temp_field, NA ))
+
+durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field,pH_durafet_corrected, pH_s_dur_no_calb)
 durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
@@
     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_durafet_temp_fb", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
+    dySeries("pH_s_durafet_temp_field", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
        dySeries("pH_s_dur_no_calb", label = "pH spectro no calibration", color ="black", pointShape = "triangle",strokeWidth=0, pointSize=6) %>%
@@
 #   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_fb, fill="Discrete measurements"), col="red" )+
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_field, fill="Discrete measurements"), col="red" )+
 #   labs(x = "", y= "", title = expression(pH[T]~durafet)) +
@@
   #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
-  summarize(temp_mix_max =round( max(temp_mix, na.rm=TRUE), digits = 2),
-            temp_mix_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
-            temp_ctd_max =round( max(temp_insitu_ctd, na.rm=TRUE), digits = 2),
-            temp_ctd_min = round(min(temp_insitu_ctd, na.rm=TRUE), digits = 2),
-            temp_11m_max =round( max(temp_insitu_11m, na.rm=TRUE), digits = 2),
-            temp_11m_min = round(min(temp_insitu_11m, na.rm=TRUE), digits = 2),
-            temp_fb_max = round(max(temp_fb, na.rm=TRUE), digits = 2),
-            temp_fb_min =round( min(temp_fb, na.rm=TRUE), digits = 2),
-            sal_mix_max = round(max(sal_mix, na.rm=TRUE), digits = 2),
-            sal_mix_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
-            sal_ctd_max = round(max(sal_insitu_ctd, na.rm=TRUE), digits = 2),
-            sal_ctd_min = round(min(sal_insitu_ctd, na.rm=TRUE), digits = 2),
-            sal_fb_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
-            sal_fb_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
+  summarize(Tinsi_max =round( max(temp_insitu, na.rm=TRUE), digits = 2),
+            Tinsi_min = round(min(temp_insitu, na.rm=TRUE), digits = 2),
+            sal_max = round(max(sal, na.rm=TRUE), digits = 2),
+            sal_min = round(min(sal, na.rm=TRUE), digits = 2),
             pH_sf_max = round(max(pHint_tot_sf, na.rm=TRUE), digits = 4),
             pH_sf_min = round(min(pHint_tot_sf, na.rm=TRUE), digits = 4))
-kable(range_month, caption ="")
+kable(range_month)
 ```
@@
 pH_sf <- d_all %>%
-  dplyr::select(datetime, sal_insitu_ctd,temp_insitu_ctd, pHint_tot_sf)%>%
-  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd), !is.na(sal_insitu_ctd)) %>%
+  dplyr::select(datetime, sal,temp_fb,temp_insitu, pHint_tot_sf)%>%
+  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal)) %>%
   dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
-pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd, Pinsi=11/10, S=pH_sf$sal_insitu_ctd, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu, Pinsi=11, S=pH_sf$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
 pH_dur <- d_all %>%
-  dplyr::select(datetime, sal_fb,temp_fb, pH_durafet_corrected)%>%
-  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_fb), !is.na(sal_fb))
-pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+  dplyr::select(datetime, sal,temp_fb,temp_insitu, pH_durafet_corrected)%>%
+  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_insitu), !is.na(temp_fb), !is.na(sal))
+pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_insitu, Pinsi=11, S=pH_dur$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
@@
 pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pHint_tot_sf_norm4, label = month))+
-  geom_point( aes(color=factor(depth)), size =1, alpha=0.5) + 
-  facet_wrap( ~ factor(depth), ncol = 3) +
-  stat_smooth(data = d_all, aes(x = pH_durafet_norm4, y = pHint_tot_sf_norm4, color=depth),
-              method=lm, na.rm=TRUE, se=FALSE) +
+  geom_text( aes(color=factor(month))) + 
  # scale_color_viridis_d(option = "C", guide="none")+
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  #geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  #labs(title = paste("pH seaFET vs pH durafet, normalized 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
-   #                  "; Intercept =", signif(fit$regression.results[2,2], 3),
-    #                 "; Slope =", signif( fit$regression.results[2,3], 3),
-    #                 "; P =", signif(fit$P.param, 3))) +
+  geom_line(aes(x = pHint_tot_sf_norm4, y = pHint_tot_sf_norm4), linetype = "dashed") +
+  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+  labs(title = paste("pH seaFET vs pH durafet, normalized 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
+                     "; Intercept =", signif(fit$regression.results[2,2], 3),
+                     "; Slope =", signif( fit$regression.results[2,3], 3),
+                     "; P =", signif(fit$P.param, 3))) +
   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 , xlim=c(7.8,8.35), ylim=c(7.8,8.35))+ #scale_colour_discrete(guide="none") +
-  labs( x="pH durafet, 4°C", y="pH seaFET, 4°C ", color = "Depth ")  +theme_bw()
+  coord_fixed(ratio = 1 , xlim=c(7.8,8.35), ylim=c(7.8,8.35))+ scale_colour_discrete(guide="none") +
+  labs( x="pH durafet, 4°C", y="pH seaFET, 4°C ", color = "Months")  +theme_bw()
 
@@
 pH_calc <- discrete %>%
-  dplyr::select(datetime, sal_fb,temp_fb, phcalc, at)%>%
-  dplyr::filter(!is.na(phcalc), !is.na(temp_fb), !is.na(sal_fb))
-pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+  dplyr::select(datetime, sal,temp, phcalc, at)%>%
+  dplyr::filter(!is.na(phcalc), !is.na(temp), !is.na(sal))
+pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp, Pinsi=11, S=pH_calc$sal, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
@@
   scale_color_discrete(guide = "none")+
- geom_abline(slope=1, intercept =0, linetype = "dashed") +
+  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
@@
 # Spectro / durafet
-fit <- lmodel2(data = d_all,  pH_s_durafet_temp_fb ~ pH_durafet_corrected , nperm = 99)
-
-p_dura_spectro <-  ggplot(d_all,aes(x=pH_durafet_corrected, y= pH_s_durafet_temp_fb, label = month))+
+fit <- lmodel2(data = d_all,  pH_s_durafet_temp_field ~ pH_durafet_corrected , nperm = 99)
+
+p_dura_spectro <-  ggplot(d_all,aes(x=pH_durafet_corrected, y= pH_s_durafet_temp_field, label = month))+
   geom_text( aes(color=factor(month))) + 
   scale_color_discrete(guide = "none")+
-  geom_abline(slope=1, intercept =0, linetype = "dashed") +
+  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
@@
 # Spectro / seafet
-fit <- lmodel2(data = d_all,  pH_s_seafet_temp_ctd ~ pHint_tot_sf , nperm = 99)
-
-p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_ctd, label = month))+
+fit <- lmodel2(data = d_all,  pH_s_seafet_temp_field ~ pHint_tot_sf , nperm = 99)
+
+p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_field, label = month))+
   geom_text( aes(color=factor(month))) + 
   scale_color_discrete(guide = "none")+
- geom_abline(slope=1, intercept =0, linetype = "dashed") +
+  geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
@@
 <!--  # DURAFET  -->
-<!-- durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_fb) -->
+<!-- durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_field) -->
 <!-- durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime) -->
@@
 <!--     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>% -->
-<!--     dySeries("pH_s_durafet_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
+<!--     dySeries("pH_s_durafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
 <!--     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>% -->
@@
 <!-- # SEAFET  -->
-<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_ctd) -->
+<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_field) -->
 <!-- seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime) -->
@@
 <!--   dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>% -->
-<!--   dySeries("pH_s_seafet_temp_ctd", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
+<!--   dySeries("pH_s_seafet_temp_field", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
 <!--   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>% -->

### 2020-04-16 paper.Rmd
beleated update

@@
 ```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
-d_all <- as_tibble(readRDS(file = paste0(path_data, "fb_data/d_all.rds"))) %>% 
-  dplyr::filter(sal_fb > 28) %>% # remove salinity data lower than 28
-  dplyr::mutate(year_month = format(datetime, '%Y-%m'))
+d_all <- as_tibble(readRDS(file = paste0(path_data, "fb_data/d_all.rds"))) 
+d <- d_all %>% 
+  #dplyr::select
+  #dplyr::filter(sal_fb > 28) %>% # remove salinity data lower than 28
+  dplyr::mutate(year_month = format(datetime, '%Y-%m')) %>%
+  dplyr::arrange(datetime) %>%
+  dplyr::mutate(depth = as.numeric(str_remove(depth, pattern= " m"))) #depth is a string
 ```
@@
 ## Whole time series
-
-**To do**: Filter pH values at more than 8 m depth.
 
@@
 
-#SAL SBE45
+d_ts <- d %>%
+  dplyr::mutate(pH_s_seafet_temp_ctd = ifelse(depth >= 8, pH_s_seafet_temp_ctd, NA)) %>% # keep only seafet data below 8 m depth
+  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air_filtered, PCO2_Corr_filtered, pH_s_seafet_temp_ctd, at_calc, at) #%>%
+  #tidyr::pivot_longer(-datetime, values_to = "value")
+
+#sal_fb
 ts_sal <- d_all %>%
@@
   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-  labs(title="Salinity FerryBox? SBE45",x="", y="Salinity") +
+  labs(title="Salinity FerryBox",x="", y="Salinity") +
   Mytheme(size_labs = 8)
@@
 
-# TEMP ferrybox
+# temp_insitu_11m
 ts_temp <- d_all %>%
-  ggplot(aes(x = datetime, y = temp_fb), na.rm=TRUE) +
+  ggplot(aes(x = datetime, y = temp_insitu_11m), na.rm=TRUE) +
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-  labs(title="Temperature FerryBox",x="", y="In situ temperature (°C)") +
+  labs(title="In situ temperature 11 m",x="", y="Temperature (°C)") +
+  Mytheme(size_labs = 8)
+
+# PAR
+ts_par_air <- d_all %>%
+  ggplot(aes(x = datetime, y = par_air_filtered), na.rm=TRUE) +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  labs(title="Atmospheric PAR",x="", y="PAR (umol m-2 s-1)") +
   Mytheme(size_labs = 8)
@@
 ts_pH <- d_all %>%
-  ggplot(aes(x = datetime, y = pHint_tot_sf), na.rm=TRUE) +
+  ggplot(aes(x = datetime, y = pH_s_seafet_temp_ctd), na.rm=TRUE) +
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-  labs(title="In situ pH",x="", y=expression(paste(pH[T]))) +
+  labs(title="In situ pH (> 8 m)",x="", y=expression(paste(pH[T]))) +
   Mytheme(size_labs = 8)
 
-# TA
+# AT
 ts_at <- d_all %>%
@@
 
-g <- cowplot::plot_grid(ts_sal, ts_temp, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
+g <- cowplot::plot_grid(ts_sal, ts_temp, ts_par_air, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
 print(g)

### 2020-04-20 paper.Rmd
?

@@
   dplyr::filter(year < 2020) %>%
+  dplyr::mutate(year_month = format(datetime, '%Y-%m')) %>%
   dplyr::mutate(month=month(datetime, label = TRUE, abbr = TRUE)) # abbreviated months rather than digital months
@@
   ym <- unique(d$year_month)[i]
-  d_reg <- filter(d, year_month==ym)
-  if (length(!is.na(d_reg$temp_fb)) > 2) { #there is no temp_insitu in 2016-08, hence skip. Not needed if one uses temp_fb
+  d_reg <- d %>%
+    dplyr::select(year_month, sal_fb, temp_fb) %>%
+    filter(year_month==ym, complete.cases(.))
+  if (nrow(d_reg) > 2) { # There are months (2017-07) with no temp_fb nor sal_fb
   lms <- summary(lm(data=d_reg, sal_fb ~ temp_fb))
@@
                                  lms$coefficients[1,4], lms$fstatistic[1], lms$fstatistic[3], lms$r.squared, prob)))
+  } else {
+  reg <- rbind(reg, rep(NA, 9)) # if no sal and temp data fill with NA
   }

### 2020-04-20 paper.Rmd
now a tsibble

@@
 ```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
-d_all <- as_tibble(readRDS(file = paste0(path_data, "fb_data/d_all.rds"))) 
+d_all <- as_tsibble(readRDS(file = paste0(path_data, "fb_data/d_all.rds")), index = datetime) 
 d <- d_all %>% 

### 2020-04-22 awipev-CO2.Rmd
all variables updated

--- 2020-03-26 awipev-CO2.Rmd
@@
 ```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
-d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
+d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour_copy.rds"))
 # load = d_hour
@@
   dplyr::select(-date) %>%
-  dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
-         AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
-         #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
-         #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
-         ) %>%
-  dplyr::rename(at_contros=AT,pco2_contros=PCO2_corr_contros_filtered,pH_durafet=HW_pH1_filtered, temp_durafet = HW_Temperature1_filtered, temp_insitu_11m=temp_insitu_11m_filtered, sal_fb = sal_fb_filtered, sal_insitu_ctd = sal_insitu_ctd_filtered, temp_fb = temp_fb_filtered, temp_insitu_ctd = temp_insitu_ctd_filtered, temp_sf=T_seaF)
-
+  # dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
+  #        AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
+  #        #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
+  #        #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
+  #        ) %>%
+  # variables passed through despike with "-filtered" have been renamed without sufix.
+  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, temp_sf = T_seaF, ph_dur = ph_dur_filtered)
 d_all <- d_hour #d_all will be the merger
@@
 
+```
+
+```{r Depth filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
+#Make groups
+
+d_all <- d_all%>%
+  dplyr::mutate(depth = ifelse(pressure_insitu_ctd <=2, "1 m", 
+                        ifelse(pressure_insitu_ctd >2 & pressure_insitu_ctd <=4, "3 m", 
+                        ifelse(pressure_insitu_ctd >4 & pressure_insitu_ctd <=6, "5 m",
+                        ifelse(pressure_insitu_ctd >6 & pressure_insitu_ctd <=8, "7 m",
+                        ifelse(pressure_insitu_ctd >8, "9 m",NA))))))
+```
+
+```{r Sal filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
+#### filter salinities above 28
+d_all <- d_all%>%
+  dplyr::mutate( sal_fb = ifelse(sal_fb <28, NA, sal_fb),
+                 sal_insitu_ctd = ifelse(sal_insitu_ctd <28, NA, sal_insitu_ctd))
+ d_all <- d_all%>%
+  dplyr::mutate(sal_insitu_ctd = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu_ctd))
+
+########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
+d_all <- d_all %>%
+  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, 
+                               ifelse (pressure_insitu_ctd >=8 ,sal_insitu_ctd, NA )))
+### remove sal_mix data that seem to be to high compared to sal_fb
+  d_all <- d_all%>%
+  dplyr::mutate(sal_mix = ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-13 18:00:00" , NA, 
+                          ifelse(datetime > "2018-05-21 19:00:00" & datetime < "2018-05-24 17:00:00" , NA,
+                          ifelse(datetime > "2018-05-29 15:00:00" & datetime < "2018-06-03 13:00:00" , NA,
+                          ifelse(datetime > "2018-06-16 06:00:00" & datetime < "2018-06-21 05:00:00" , NA,
+                          ifelse(datetime > "2019-12-02 08:00:00" & datetime < "2019-12-03 08:00:00" , NA,
+                          ifelse(datetime > "2019-12-09 07:00:00" & datetime < "2019-12-09 10:00:00" , NA, 
+                          ifelse(datetime > "2019-12-09 15:00:00" & datetime < "2019-12-09 18:00:00" , NA,
+                          ifelse(datetime > "2019-12-10 14:00:00" & datetime < "2019-12-10 18:00:00", NA, sal_mix)))))))))
+
+```
+
+```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
+###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
+d_all <- d_all %>%
+  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, 
+                               ifelse (pressure_insitu_ctd >=8 ,temp_insitu_ctd, NA )))
 ```
@@
 
-# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_hour TO d, to use pHinsi
+# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
 # use the closest time to add them
@@
 d_all$closest_datetime <- d_all$datetime
-d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, sal_insitu_ctd, temp_insitu_ctd)), by="closest_datetime")
-
-# Conversion of spectro pH to a same T°
+d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, sal_insitu_ctd, temp_mix, temp_insitu_ctd, temp_insitu_11m, sal_mix )), by="closest_datetime")
+
+# Conversion of spectro pH to insitu mix T°
 pH_seafet <- d %>%
@@
 pH_seafet <- pH_seafet %>%
-  dplyr::mutate(pH_s_seafet_temp_ctd = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_insitu_ctd, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_insitu_ctd,Pt=0,Sit=0))
+  dplyr::mutate(pH_s_seafet_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_mix, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))
 
@@
 pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(datetime,pH_s_seafet_temp_ctd)%>% 
+  dplyr::select(datetime,pH_s_seafet_temp_mix)%>% 
   dplyr::group_by(datetime) %>% 
-  dplyr::summarize(pH_s_seafet_temp_ctd = mean(pH_s_seafet_temp_ctd, na.rm = T))
+  dplyr::summarize(pH_s_seafet_temp_mix = mean(pH_s_seafet_temp_mix, na.rm = T))
 pH_durafet_mean <- pH_durafet%>%
@@
   #drop_na() %>%
-  dplyr::select(closest_datetime, pH_s_seafet_temp_ctd) %>%
+  dplyr::select(closest_datetime, pH_s_seafet_temp_mix) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 
-```{r Depth filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-#Make groups
-
-d_all <- d_all%>%
-  dplyr::mutate(depth = ifelse(pressure_insitu_ctd_filtered <=2, "1 m", 
-                        ifelse(pressure_insitu_ctd_filtered >2 & pressure_insitu_ctd_filtered <=4, "3 m", 
-                        ifelse(pressure_insitu_ctd_filtered >4 & pressure_insitu_ctd_filtered <=6, "5 m",
-                        ifelse(pressure_insitu_ctd_filtered >6 & pressure_insitu_ctd_filtered <=8, "7 m",
-                        ifelse(pressure_insitu_ctd_filtered >8, "9 m",NA))))))
-```
-
-```{r Sal filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-#### filter salinities above 28
-d_all <- d_all%>%
-  dplyr::mutate( sal_fb = ifelse(sal_fb <28, NA, sal_fb),
-                 sal_insitu_ctd = ifelse(sal_insitu_ctd <28, NA, sal_insitu_ctd))
- d_all <- d_all%>%
-  dplyr::mutate(sal_insitu_ctd = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu_ctd))
-
-########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
-d_all <- d_all %>%
-  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, 
-                               ifelse (pressure_insitu_ctd_filtered >=8 ,sal_insitu_ctd, NA )))
-### remove sal_mix datat that seem to be to high compared to sal_fb
-  d_all <- d_all%>%
-  dplyr::mutate(sal_mix = ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-13 18:00:00" , NA, 
-                          ifelse(datetime > "2018-05-21 19:00:00" & datetime < "2018-05-24 17:00:00" , NA,
-                          ifelse(datetime > "2018-05-28 06:00:00" & datetime < "2018-06-03 13:00:00" , NA,
-                          ifelse(datetime > "2018-06-16 06:00:00" & datetime < "2018-06-21 05:00:00" , NA,
-                          ifelse(datetime > "2019-12-02 08:00:00" & datetime < "2019-12-03 08:00:00" , NA,
-                          ifelse(datetime > "2019-12-09 07:00:00" & datetime < "2019-12-09 10:00:00" , NA, 
-                          ifelse(datetime > "2019-12-09 15:00:00" & datetime < "2019-12-09 18:00:00" , NA,
-                          ifelse(datetime > "2019-12-10 14:00:00" & datetime < "2019-12-10 18:00:00", NA, sal_mix)))))))))
-
-```
-
-```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
-d_all <- d_all %>%
-  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, 
-                               ifelse (pressure_insitu_ctd_filtered >=8 ,temp_insitu_ctd, NA )))
-```
-
 ## Whole time series
 ```{r whole time series, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-#SAL MIX
+#SAL CTD profile
+sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb)
+sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
+dygraph(sal_xts, group = "awipev", main="Salinities (in situ CTD, all depths + FB)", ylab="Salinity") %>%
+      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "CTD") %>%
+            dySeries("sal_fb", color = "black", strokeWidth = 1, label = "FB") %>%
+dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
+      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+    dyLegend(show = "follow")   %>%
+    dyAxis("y",valueRange = c(30, 37)) %>%
+      dyRangeSelector(height = 30, dateWindow= NULL)
+#SAL FB
 sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd)
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
-dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD)", ylab="Salinity") %>%
+dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
       dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "S") %>%
@@
       dyRangeSelector(height = 30, dateWindow= NULL)
+# TEMP insitu CTD
+temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd)
+temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
+dygraph(temp_insitu_xts, group = "awipev", main="Temperature (ctd all depths)", ylab="Temperature") %>%
+      dySeries("temp_insitu_ctd", color = "blue", strokeWidth = 0, label = "T") %>%
+      dyAxis("y", valueRange = c(-2.8, 10)) %>%
+      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+      dyLegend(show = "follow")   %>%
+      dyRangeSelector(height = 30, dateWindow= NULL)
 # PCO2 
 #+ Ajout de la pCO2 corrigé par le script contros (dans R server ny-alesund_cc.R)
-pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_contros, PCO2_Corr_filtered)
+pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_corr)
 pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
 dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
-    dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
-      dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
+    dySeries("pco2_corr", label="Corrected pCO2", color=  "blue",strokeWidth=0, pointSize=2) %>%
     dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
@@
 # DURAFET 
-durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_fb)
+durafet_contros_xts <- dplyr::select(d_all, datetime, ph_dur, pH_s_durafet_temp_fb)
 durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
 dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
-    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("ph_dur", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
     dySeries("pH_s_durafet_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
@@
 # SEAFET 
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_ctd)
+seafet_contros_xts <- dplyr::select(d_all, datetime, phINT,pH_s_seafet_temp_mix)
 seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
 dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ T CTD)", ylab="pHT") %>%
-  dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-  dySeries("pH_s_seafet_temp_ctd", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+  dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
+  dySeries("pH_s_seafet_temp_mix", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
@@
 
-at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at)
+at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at)
 at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
@@
   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
-  dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
+  dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
@@
 
-fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)
+fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)
 
 ```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)
+fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)
 
@@
 
-p_sal_fb_ctd<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
+p_sal_fb_ctd<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd >=8),aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
   geom_point( aes(color=factor(datetime_chr))) + 
@@
 dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#dySeries("pressure_insitu_ctd_filtered", label = "pressure_insitu_ctd_filtered", color ="black", strokeWidth=0, pointSize=2) %>%
+#dySeries("pressure_insitu_ctd", label = "pressure_insitu_ctd", color ="black", strokeWidth=0, pointSize=2) %>%
   dyLegend(show = "onmouseover")   %>%
   #dyAxis( "y2",valueRange = c(-3, 36))%>%
-  dyAxis( "y2",valueRange = c(25, 36))%>%
+  #dyAxis( "y2",valueRange = c(25, 36))%>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
 
-fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd_filtered >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)
+fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)
 
@@
 #Interpolation of continuous sensor data to match a maximum of reference data.
-TAinterp_all <-approx(d_all$datetime, d_all$AT_filtered, xout=d_all$datetime, method="linear", rule=2)
-names(TAinterp_all) <- c("datetime", "AT_filtered_interp")
+TAinterp_all <-approx(d_all$datetime, d_all$AT, xout=d_all$datetime, method="linear", rule=2)
+names(TAinterp_all) <- c("datetime", "AT_interp")
 TAinterp_all <- as.data.frame(TAinterp_all)
-d_all$AT_filtered_interp <- TAinterp_all$AT_filtered_interp
+d_all$AT_interp <- TAinterp_all$AT_interp
 
@@
 d_all <- d_all%>%
-  dplyr::mutate(diff_ta =  at-AT_filtered_interp )
+  dplyr::mutate(diff_ta =  at-AT_interp )
 # create colum with instrument number
@@
 calib_ta_first <- d_all%>%
-  dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta,TA_period)%>%
+  dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta,TA_period)%>%
   dplyr::filter(TA_period =="TA1" & !is.na(at))
@@
  calib_ta_third <- d_all%>%
-   dplyr::select(datetime, closest_datetime,AT_filtered, AT_filtered_interp, at,diff_ta, TA_period)%>%
+   dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta, TA_period)%>%
    dplyr::filter(TA_period == "TA3" & !is.na(at))
@@
 calib_ta_second <- d_all%>%
-  dplyr::select(datetime, closest_datetime, AT_filtered, AT_filtered_interp, at, diff_ta, TA_period)%>%
+  dplyr::select(datetime, closest_datetime, AT, AT_interp, at, diff_ta, TA_period)%>%
   dplyr::filter(TA_period == "TA2" & !is.na(at))
@@
 d_all <- d_all%>%
- dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT_filtered + (d_all$datetime_reg * d_all$at_slope + at_intercept)),
-                                        ifelse(TA_period == "TA2", (AT_filtered + mean_offset),
-                                        ifelse(TA_period == "TA3", (AT_filtered + (datetime_reg * at_slope)+ at_intercept), NA))))
-
-at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT_filtered,at,TA_reg_corrected)
+ dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT + (d_all$datetime_reg * d_all$at_slope + at_intercept)),
+                                        ifelse(TA_period == "TA2", (AT + mean_offset),
+                                        ifelse(TA_period == "TA3", (AT + (datetime_reg * at_slope)+ at_intercept), NA))))
+
+at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at,TA_reg_corrected)
 at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
@@
    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
-  dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
+  dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
   dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
@@
 ```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
-at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, AT_filtered, at)
+at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, at)
 at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
-dygraph(at_contros_calc_xts, group = "awipev", main="", ylab="Total alkalinity") %>%
-  dySeries("AT_filtered", label= "Raw filtered TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
-  dySeries("at_calc", label="TA calculated from Salinity",color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
-  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
+dygraph(at_contros_calc_xts, group = "awipev", main="TA + TA calc from sal_mix + TA reference", ylab="Total alkalinity") %>%
+  #dySeries("AT", label= "Raw TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
+  dySeries("at_calc", label="TA calc ",color = "blue", strokeWidth = 0, pointSize=2) %>%
+  dySeries("at", label="TA ref",color = "red", strokeWidth = 0, pointSize=4) %>%
   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
@@
  at_nov_2018 <-
-  dplyr::select(d_all, datetime, at_calc, AT_filtered, at) %>%
-  filter(datetime > "2018-11-01", AT_filtered > 2250)
+  dplyr::select(d_all, datetime, at_calc, AT, at) %>%
+  filter(datetime > "2018-11-01", AT > 2250)
 #despike
-at_nov_2018 <- mutate(at_nov_2018, AT_filtered_despike = despike(AT_filtered, reference= "median", n=0.5, k=10, replace="NA"))
+at_nov_2018 <- mutate(at_nov_2018, AT_despike = despike(AT, reference= "median", n=0.5, k=10, replace="NA"))
 #plot
 at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) +
-  geom_point(aes(y=AT_filtered, colour = "before"), size =3) +
-  geom_point(aes(y=AT_filtered_despike, colour = "after"), size = 2) +
+  geom_point(aes(y=AT, colour = "before"), size =3) +
+  geom_point(aes(y=AT_despike, colour = "after"), size = 2) +
   labs(x = "Time", y = "Total alkalinity", color = "despike")
@@
 
-at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_filtered_despike != "NA")
+at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_despike != "NA")
 titre <- "Contros AT vs Calculated AT"
-fit <- lmodel2(data = at_nov_2018_no_NA, AT_filtered_despike ~ at_calc, nperm = 99)
-ggreg2(fit, x = "at_calc", y = "AT_filtered_despike")
+ fit <- lmodel2(data = at_nov_2018_no_NA, AT_despike ~ at_calc, nperm = 99)
+ggreg2(fit, x = "at_calc", y = "AT_despike")
 
@@
 title <- "Contros vs calculated pCO2"
-fit <- lmodel2(data = d_all,  pco2_contros ~ pco2calc , nperm = 99)
-
-pco2calc_pCO2_contros_text <-  ggplot(d_all,aes(x=pco2calc, y= pco2_contros, label = month))+
+fit <- lmodel2(data = d_all,  pco2_corr ~ pco2calc , nperm = 99)
+
+pco2calc_pCO2_contros_text <-  ggplot(d_all,aes(x=pco2calc, y= pco2_corr, label = month))+
    geom_text(aes(color = factor(month)))+
   scale_color_discrete(guide="none")+
-  geom_line(aes(x = pco2_contros, y = pco2_contros), linetype = "dashed") +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
@@
 ```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_contros, PCO2_Corr_filtered)
+pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_corr)
 pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
-dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
-  dySeries("pco2_contros", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
-    dySeries("PCO2_Corr_filtered", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
+dygraph(pco2_contros_xts, group = "awipev", main="<i>p</i>CO<sub>2</sub>", ylab="<i>p</i>CO<sub>2</sub>") %>%
+  dySeries("pco2_corr", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
+    #dySeries("pco2_raw", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
     dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
@@
 # sfPeriod <- d_all%>%
-#   dplyr::select(datetime, pH_s_seafet_temp_ctd)%>%
-#   dplyr::filter(!is.na(pH_s_seafet_temp_ctd))
+#   dplyr::select(datetime, pH_s_seafet_temp_mix)%>%
+#   dplyr::filter(!is.na(pH_s_seafet_temp_mix))
 # # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
@@
 # (1)
-d_all$phINT_filtered <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phINT_filtered < 8.04, NA, d_all$phINT_filtered) 
-d_all$phEXT_filtered <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phEXT_filtered < 8.04, NA, d_all$phEXT_filtered) 
+d_all$phINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phINT < 8.04, NA, d_all$phINT) 
+d_all$phEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phEXT < 8.04, NA, d_all$phEXT) 
 d_all$voltINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltINT < -0.9439, NA, d_all$voltINT) 
@@
 d_all$voltEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltEXT)
-d_all$phINT_filtered <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phINT_filtered)
-d_all$phEXT_filtered <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phEXT_filtered)
+d_all$phINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phINT)
+d_all$phEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phEXT)
 # (3)
@@
 ####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_ctd,
+calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_mix,
                           calT = d_all$temp_insitu_ctd, calSal = d_all$sal_insitu_ctd )
@@
 d_all <- d_all%>%
-  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", pH_s_seafet_temp_ctd, NA ))
-
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered, pH_s_seafet_temp_ctd, pHint_tot_sf, pH_s_sf_no_calb, pressure_insitu_ctd_filtered, sal_insitu_ctd, temp_insitu_ctd)
+  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", pH_s_seafet_temp_mix, NA ))
+
+seafet_contros_xts <- dplyr::select(d_all, datetime, phINT, pH_s_seafet_temp_mix, pHint_tot_sf, pH_s_sf_no_calb, pressure_insitu_ctd, sal_insitu_ctd, temp_insitu_ctd)
 #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
 dySeries("temp_insitu_ctd", axis="y",label = "T ctd", color ="grey", strokeWidth=0, pointSize=2) %>%
-dySeries("sal_insitu_ctd", axis="y",label = "sS ctd", color ="orange", strokeWidth=0, pointSize=2) %>%
-dySeries("pressure_insitu_ctd_filtered", axis="y2",label = "Pression", color ="pink", strokeWidth=0, pointSize=2) %>%
+dySeries("sal_insitu_ctd", axis="y",label = "S ctd", color ="orange", strokeWidth=0, pointSize=2) %>%
+dySeries("pressure_insitu_ctd", axis="y2",label = "Pression", color ="pink", strokeWidth=0, pointSize=2) %>%
 dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
-dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-dySeries("pH_s_seafet_temp_ctd", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
+dySeries("pH_s_seafet_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
 dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
@@
 
-# p <- ggplot(d_all%>%filter(datetime >= ("2017-07-30") & !is.na(depth) ),aes(x=datetime, y= phINT_filtered, label = depth))+
+# p <- ggplot(d_all%>%filter(datetime >= ("2017-07-30") & !is.na(depth) ),aes(x=datetime, y= phINT, label = depth))+
 #   geom_point( aes(color=factor(depth)), size=1, alpha=0.5, na.rm=TRUE)
@@
 
-seafet_depth_xts <- dplyr::select(d_all, datetime, phINT_filtered, pH_s_seafet_temp_ctd,pHint_tot_sf)
+seafet_depth_xts <- dplyr::select(d_all, datetime, phINT, pH_s_seafet_temp_mix,pHint_tot_sf)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
 dygraph(seafet_depth_xts, group = "depth", main="pH seaFET RAW (in situ)", ylab="pHT") %>%
-  dySeries("pH_s_seafet_temp_ctd", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-  dySeries("phINT_filtered", axis="y2",label = "pH RAW", color ="blue", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%
+  dySeries("pH_s_seafet_temp_mix", axis="y2", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+  dySeries("phINT", axis="y2",label = "pH RAW", color ="blue", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%
   dySeries("pHint_tot_sf", axis="y2", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
@@
 # # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT_filtered,pH_s_seafet_temp_ctd, temp_sf, temp_fb, temp_insitu, sal)
+# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT,pH_s_seafet_temp_mix, temp_sf, temp_fb, temp_insitu, sal)
 # #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
 #   #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-#    # dySeries("pH_s_seafet_temp_ctd", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
+#    # dySeries("pH_s_seafet_temp_mix", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
 #     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
@@
 # sfoffset <- left_join(sfPeriod[,c(1,2)], d_all%>%dplyr::select(datetime, pHint_tot_sf), by="datetime")
-# dat <- mutate(sfoffset, diff_pH_sf = round((pH_s_seafet_temp_ctd - pHint_tot_sf),digits  = 4))
+# dat <- mutate(sfoffset, diff_pH_sf = round((pH_s_seafet_temp_mix - pHint_tot_sf),digits  = 4))
 # average_offset <- mean(abs(dat$diff_pH_sf), na.rm=TRUE)
@@
 #   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_ctd, fill="Discrete measurements"), col="red" )+
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_mix, fill="Discrete measurements"), col="red" )+
 #   labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
@@
 # Offset between durafet pH and spec pH 
-duroffset <- left_join(durPeriod%>%dplyr::select(datetime,pH_s_durafet_temp_fb), d_all%>%dplyr::select(datetime,pH_durafet ), by="datetime")
-dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_fb - pH_durafet)
+duroffset <- left_join(durPeriod%>%dplyr::select(datetime,pH_s_durafet_temp_fb), d_all%>%dplyr::select(datetime,ph_dur ), by="datetime")
+dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_fb - ph_dur)
 average_offset_dur <- round(mean(dat_dur$diff_pH_dur, na.rm=TRUE), digits = 2)
@@
                                 ifelse(deployment_dur == 25, dat_dur$diff_pH_dur[25],0))))))))))))))))))))))))),
-              pH_durafet_corrected = pH_durafet + offset_durafet
+              ph_dur_corr = ph_dur + offset_durafet
               )
@@
 # Remove outliers from 2018-07-10 00:00 to 05:00
-d_all$pH_durafet_corrected <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$pH_durafet_corrected)
-d_all$pH_durafet <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$pH_durafet)
+d_all$ph_dur_corr <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$ph_dur_corr)
+d_all$ph_dur <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$ph_dur)
 
@@
 
-durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_fb,pH_durafet_corrected, pH_s_dur_no_calb)
+durafet_contros_xts <- dplyr::select(d_all, datetime, ph_dur, pH_s_durafet_temp_fb,ph_dur_corr, pH_s_dur_no_calb)
 durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
  dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
-    dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("ph_dur", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
+       dySeries("pH_s_dur_no_calb", label = "pH spectro no calibration", color ="black", pointShape = "triangle",strokeWidth=0, pointSize=6) %>%
+       dySeries("ph_dur_corr", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
        dySeries("pH_s_durafet_temp_fb", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
-       dySeries("pH_s_dur_no_calb", label = "pH spectro no calibration", color ="black", pointShape = "triangle",strokeWidth=0, pointSize=6) %>%
-       dySeries("pH_durafet_corrected", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
     dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
@@
 #  poster_dur <- ggplot( ) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pH_durafet_corrected,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= ph_dur_corr,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
 #   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_fb, fill="Discrete measurements"), col="red" )+
@@
   group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
-  summarize(pH_range = max(pH_durafet_corrected) - min(pH_durafet_corrected))
+  summarize(pH_range = max(ph_dur_corr) - min(ph_dur_corr))
 )
@@
 pH_sf <- d_all %>%
-  dplyr::select(datetime, sal_insitu_ctd,temp_insitu_ctd, pHint_tot_sf)%>%
+  dplyr::select(datetime, sal_insitu_ctd, temp_insitu_ctd, pHint_tot_sf)%>%
   dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd), !is.na(sal_insitu_ctd)) %>%
@@
 pH_dur <- d_all %>%
-  dplyr::select(datetime, sal_fb,temp_fb, pH_durafet_corrected)%>%
-  dplyr::filter(!is.na(pH_durafet_corrected), !is.na(temp_fb), !is.na(sal_fb))
-pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$pH_durafet_corrected, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+  dplyr::select(datetime, sal_fb,temp_fb, ph_dur_corr)%>%
+  dplyr::filter(!is.na(ph_dur_corr), !is.na(temp_fb), !is.na(sal_fb))
+pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
@@
 # Spectro / durafet
-fit <- lmodel2(data = d_all,  pH_s_durafet_temp_fb ~ pH_durafet_corrected , nperm = 99)
-
-p_dura_spectro <-  ggplot(d_all,aes(x=pH_durafet_corrected, y= pH_s_durafet_temp_fb, label = month))+
+fit <- lmodel2(data = d_all,  pH_s_durafet_temp_fb ~ ph_dur_corr , nperm = 99)
+
+p_dura_spectro <-  ggplot(d_all,aes(x=ph_dur_corr, y= pH_s_durafet_temp_fb, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
 # Spectro / seafet
-fit <- lmodel2(data = d_all,  pH_s_seafet_temp_ctd ~ pHint_tot_sf , nperm = 99)
-
-p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_ctd, label = month))+
+fit <- lmodel2(data = d_all,  pH_s_seafet_temp_mix ~ pHint_tot_sf , nperm = 99)
+
+p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_mix, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
 
+A la main dans le terminal, cela donne :
+ssh awipev@awipev-co2.obs-vlfr.fr
+R --vanilla < web/awipev-CO2_web.Rmd
+
 ![ ](Images/awipev_server_arborescence.jpg){width=65%}
@@
 <!-- # SEAFET  -->
-<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT_filtered,pH_s_seafet_temp_ctd) -->
+<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT,pH_s_seafet_temp_mix) -->
 <!-- seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime) -->
 <!-- dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>% -->
-<!--   dySeries("phINT_filtered", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>% -->
-<!--   dySeries("pH_s_seafet_temp_ctd", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
+<!--   dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>% -->
+<!--   dySeries("pH_s_seafet_temp_mix", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
 <!--   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>% -->

### 2020-04-22 awipev-CO2.Rmd
comment all TA parts except salinity relatinship

@@
 ```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
-d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour_copy.rds"))
+d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
 # load = d_hour
@@
   # variables passed through despike with "-filtered" have been renamed without sufix.
-  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, temp_sf = T_seaF, ph_dur = ph_dur_filtered)
+  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, temp_sf = T_seaF)
 d_all <- d_hour #d_all will be the merger
@@
 pH_seafet <- d %>%
-  dplyr::filter(!is.na(pH_s_seafet)& !is.na(sal_insitu_ctd) )
+  dplyr::filter(!is.na(pH_s_seafet) & !is.na(sal_insitu_ctd) & !is.na(temp_mix) )
 pH_seafet <- pH_seafet %>%
@@
     dyRangeSelector(height = 30, dateWindow= NULL) 
-# TA
-# to create periods according to TA deployments
+# # TA
+# # to create periods according to TA deployments
 TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
@@
 
-at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at)
-at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
-dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
-   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
-  #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
-  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
-  dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
-  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
-  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
-  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
-  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-  dyAxis("y",valueRange = c(2000, 2650)) %>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions( strokeWidth= 0) %>%
-  dyLegend(show = "follow")   %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
+# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at)
+# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
+# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
+#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
+#   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
+#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
+#   dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
+#   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
+#   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
+#   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+#   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
+#   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+#   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+#   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+#   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
+#   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+#   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
+#   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
+#   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
+#   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
+#   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
+#   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
+#   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
+#   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
+#   dyAxis("y",valueRange = c(2000, 2650)) %>%
+#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+#   dyOptions( strokeWidth= 0) %>%
+#   dyLegend(show = "follow")   %>%
+#   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
+#     dyRangeSelector(height = 30, dateWindow= NULL) 
+#  
 f <- as.data.frame(table(d_all$at))
@@
 ```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
-#Interpolation of continuous sensor data to match a maximum of reference data.
-TAinterp_all <-approx(d_all$datetime, d_all$AT, xout=d_all$datetime, method="linear", rule=2)
-names(TAinterp_all) <- c("datetime", "AT_interp")
-TAinterp_all <- as.data.frame(TAinterp_all)
-d_all$AT_interp <- TAinterp_all$AT_interp
-
-# create a column with difference between sensor and ref
-d_all <- d_all%>%
-  dplyr::mutate(diff_ta =  at-AT_interp )
-# create colum with instrument number
-d_all <- d_all %>%
-  dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
-                            ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
-                            ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3",
-                            ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4",
-                            ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
-                            ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))
-
-#remove outliers
-calib_ta_first <- d_all%>%
-  dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta,TA_period)%>%
-  dplyr::filter(TA_period =="TA1" & !is.na(at))
-  #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
-# & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))
-
-# Parameters of regression
-fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime)
-at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6)
-at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2)
-at_intercept1 <- round(fit$coefficients[[1]], digits= 2)
-```
-
-The slope is: `r #at_slope_TA1` x 3600 x 24 x 365.24 = `r #at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red.
-
-```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
- # Plot of regression
- p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) +
-     geom_point() + geom_smooth(method='lm', se=FALSE)+
-     geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  +
-   geom_hline(yintercept = 0, linetype="dashed" )+
-   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                      "Intercept =",signif(fit$coef[[1]],5 ),
-                      "Slope =",signif(fit$coef[[2]], 5),
-                      "P =",signif(summary(fit)$coef[2,4], 5))) +
-   ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
- print(p)
- ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm")
-```
-
-##### **Third period**
-
-```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"}
-
- #remove outliers and remove period without TA measurements
- calib_ta_third <- d_all%>%
-   dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta, TA_period)%>%
-   dplyr::filter(TA_period == "TA3" & !is.na(at))
-
- # Parameters of regression
- fit <- lm( data=calib_ta_third, diff_ta ~ datetime)
- at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8)
- at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2)
- at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici.
-```
-
-The slope is in days: `r #at_slope_TA3` x 3600 x 24 x 365.24 = `r #at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers.
-
-```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
-# # Plot of regression
- p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+
-     geom_point() + geom_smooth(method='lm', se=FALSE)+
-     #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  +
-    geom_hline(yintercept = 0, linetype="dashed" )+
-   geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") +
-   #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+
-   labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                      "Intercept =",signif(fit$coef[[1]],5 ),
-                      " Slope =",signif(fit$coef[[2]], 5),
-                      " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") +
-   scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC")
- print(p)
- ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm")
-```
-
-##### **Second period**
-
-```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
-
-#remove outliers and remove period without TA measurements
-calib_ta_second <- d_all%>%
-  dplyr::select(datetime, closest_datetime, AT, AT_interp, at, diff_ta, TA_period)%>%
-  dplyr::filter(TA_period == "TA2" & !is.na(at))
-
-mean_offset <- mean(calib_ta_second$diff_ta)
-
-```
-
-For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r #mean_offset` µmoles.kg~-1~) was added to TA value as an offset.
-
-#### **Final TA corrected data (Regression)**
-
-The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition.
-It is clear that these corrected data (in green) cannot be used for periods 1 to 3. The jury is still out for period 4. The issue of salinity must be clarified before an assessment can be made.
-
-```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'}
-# Correction for the 3 periods is apply
-d_all <- d_all%>%
-  dplyr::mutate(datetime_reg = as.numeric(datetime),
-                at_intercept = ifelse(TA_period == "TA1", at_intercept1,
-                               ifelse(TA_period == "TA3", at_intercept3, NA)),
-                at_slope = ifelse(TA_period == "TA1", at_slope_TA1,
-                           ifelse(TA_period == "TA3", at_slope_TA3, NA))
-                )
-
-d_all <- d_all%>%
- dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT + (d_all$datetime_reg * d_all$at_slope + at_intercept)),
-                                        ifelse(TA_period == "TA2", (AT + mean_offset),
-                                        ifelse(TA_period == "TA3", (AT + (datetime_reg * at_slope)+ at_intercept), NA))))
-
-at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at,TA_reg_corrected)
-at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
-dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
-   #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
-  dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
-  dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>%
-  dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>%
-  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
-  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
-  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
-  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-  dyAxis("y",valueRange = c(1600, 2650)) %>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions( strokeWidth= 0) %>%
-  dyLegend(show = "follow")   %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-```
+# #Interpolation of continuous sensor data to match a maximum of reference data.
+# TAinterp_all <-approx(d_all$datetime, d_all$AT, xout=d_all$datetime, method="linear", rule=2)
+# names(TAinterp_all) <- c("datetime", "AT_interp")
+# TAinterp_all <- as.data.frame(TAinterp_all)
+# d_all$AT_interp <- TAinterp_all$AT_interp
+# 
+# # create a column with difference between sensor and ref
+# d_all <- d_all%>%
+#   dplyr::mutate(diff_ta =  at-AT_interp )
+# # create colum with instrument number
+# d_all <- d_all %>%
+#   dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
+#                             ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
+#                             ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3",
+#                             ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4",
+#                             ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
+#                             ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))
+# 
+# #remove outliers
+# calib_ta_first <- d_all%>%
+#   dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta,TA_period)%>%
+#   dplyr::filter(TA_period =="TA1" & !is.na(at))
+#   #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
+# # & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))
+# 
+# # Parameters of regression
+# fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime)
+# at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6)
+# at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2)
+# at_intercept1 <- round(fit$coefficients[[1]], digits= 2)
+```
+
+<!-- The slope is: `r #at_slope_TA1` x 3600 x 24 x 365.24 = `r #at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red. -->
+
+<!-- ```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"} -->
+<!--  # Plot of regression -->
+<!--  p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + -->
+<!--      geom_point() + geom_smooth(method='lm', se=FALSE)+ -->
+<!--      geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  + -->
+<!--    geom_hline(yintercept = 0, linetype="dashed" )+ -->
+<!--    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5), -->
+<!--                       "Intercept =",signif(fit$coef[[1]],5 ), -->
+<!--                       "Slope =",signif(fit$coef[[2]], 5), -->
+<!--                       "P =",signif(summary(fit)$coef[2,4], 5))) + -->
+<!--    ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC") -->
+<!--  print(p) -->
+<!--  ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm") -->
+<!-- ``` -->
+
+<!-- ##### **Third period** -->
+
+<!-- ```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"} -->
+
+<!--  #remove outliers and remove period without TA measurements -->
+<!--  calib_ta_third <- d_all%>% -->
+<!--    dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta, TA_period)%>% -->
+<!--    dplyr::filter(TA_period == "TA3" & !is.na(at)) -->
+
+<!--  # Parameters of regression -->
+<!--  fit <- lm( data=calib_ta_third, diff_ta ~ datetime) -->
+<!--  at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8) -->
+<!--  at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2) -->
+<!--  at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici. -->
+<!-- ``` -->
+
+<!-- The slope is in days: `r #at_slope_TA3` x 3600 x 24 x 365.24 = `r #at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers. -->
+
+<!-- ```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"} -->
+<!-- # # Plot of regression -->
+<!--  p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ -->
+<!--      geom_point() + geom_smooth(method='lm', se=FALSE)+ -->
+<!--      #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  + -->
+<!--     geom_hline(yintercept = 0, linetype="dashed" )+ -->
+<!--    geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") + -->
+<!--    #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+ -->
+<!--    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5), -->
+<!--                       "Intercept =",signif(fit$coef[[1]],5 ), -->
+<!--                       " Slope =",signif(fit$coef[[2]], 5), -->
+<!--                       " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + -->
+<!--    scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC") -->
+<!--  print(p) -->
+<!--  ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm") -->
+<!-- ``` -->
+
+<!-- ##### **Second period** -->
+
+<!-- ```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'} -->
+
+<!-- #remove outliers and remove period without TA measurements -->
+<!-- calib_ta_second <- d_all%>% -->
+<!--   dplyr::select(datetime, closest_datetime, AT, AT_interp, at, diff_ta, TA_period)%>% -->
+<!--   dplyr::filter(TA_period == "TA2" & !is.na(at)) -->
+
+<!-- mean_offset <- mean(calib_ta_second$diff_ta) -->
+
+<!-- ```  -->
+
+<!-- For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r #mean_offset` µmoles.kg~-1~) was added to TA value as an offset. -->
+
+<!-- #### **Final TA corrected data (Regression)** -->
+
+<!-- The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition. -->
+<!-- It is clear that these corrected data (in green) cannot be used for periods 1 to 3.
+The jury is still out for period 4.
+The issue of salinity must be clarified before an assessment can be made.
+-->
+
+<!-- ```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'} -->
+<!-- # Correction for the 3 periods is apply -->
+<!-- d_all <- d_all%>% -->
+<!--   dplyr::mutate(datetime_reg = as.numeric(datetime), -->
+<!--                 at_intercept = ifelse(TA_period == "TA1", at_intercept1, -->
+<!--                                ifelse(TA_period == "TA3", at_intercept3, NA)), -->
+<!--                 at_slope = ifelse(TA_period == "TA1", at_slope_TA1, -->
+<!--                            ifelse(TA_period == "TA3", at_slope_TA3, NA)) -->
+<!--                 ) -->
+
+<!-- d_all <- d_all%>% -->
+<!--  dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT + (d_all$datetime_reg * d_all$at_slope + at_intercept)), -->
+<!--                                         ifelse(TA_period == "TA2", (AT + mean_offset), -->
+<!--                                         ifelse(TA_period == "TA3", (AT + (datetime_reg * at_slope)+ at_intercept), NA)))) -->
+
+<!-- at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at,TA_reg_corrected) -->
+<!-- at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime) -->
+<!-- dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>% -->
+<!--    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>% -->
+<!--   dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>% -->
+<!--   dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>% -->
+<!--   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% -->
+<!--   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>% -->
+<!--   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
+<!--   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>% -->
+<!--   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
+<!--   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>% -->
+<!--   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>% -->
+<!--   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>% -->
+<!--   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>% -->
+<!--   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>% -->
+<!--   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>% -->
+<!--   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>% -->
+<!--   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>% -->
+<!--   dyAxis("y",valueRange = c(1600, 2650)) %>% -->
+<!--   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
+<!--   dyOptions( strokeWidth= 0) %>% -->
+<!--   dyLegend(show = "follow")   %>% -->
+<!--   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>% -->
+<!--     dyRangeSelector(height = 30, dateWindow= NULL) -->
+
+<!-- ``` -->
 
@@
 
-#### **TA since November 2018 (final installation)**
-```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
- # select subset of data and remove obvious outliers
- at_nov_2018 <-
-  dplyr::select(d_all, datetime, at_calc, AT, at) %>%
-  filter(datetime > "2018-11-01", AT > 2250)
-#despike
-at_nov_2018 <- mutate(at_nov_2018, AT_despike = despike(AT, reference= "median", n=0.5, k=10, replace="NA"))
-#plot
-at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) +
-  geom_point(aes(y=AT, colour = "before"), size =3) +
-  geom_point(aes(y=AT_despike, colour = "after"), size = 2) +
-  labs(x = "Time", y = "Total alkalinity", color = "despike")
-print(at_datetime)
-
-at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_despike != "NA")
-titre <- "Contros AT vs Calculated AT"
- fit <- lmodel2(data = at_nov_2018_no_NA, AT_despike ~ at_calc, nperm = 99)
-ggreg2(fit, x = "at_calc", y = "AT_despike")
-
-```
+<!-- #### **TA since November 2018 (final installation)** -->
+<!-- ```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'} -->
+<!--  # select subset of data and remove obvious outliers -->
+<!--  at_nov_2018 <- -->
+<!--   dplyr::select(d_all, datetime, at_calc, AT, at) %>% -->
+<!--   filter(datetime > "2018-11-01", AT > 2250) -->
+<!-- #despike -->
+<!-- at_nov_2018 <- mutate(at_nov_2018, AT_despike = despike(AT, reference= "median", n=0.5, k=10, replace="NA")) -->
+<!-- #plot -->
+<!-- at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) + -->
+<!--   geom_point(aes(y=AT, colour = "before"), size =3) + -->
+<!--   geom_point(aes(y=AT_despike, colour = "after"), size = 2) + -->
+<!--   labs(x = "Time", y = "Total alkalinity", color = "despike") -->
+<!-- print(at_datetime) -->
+
+<!-- at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_despike != "NA") -->
+<!-- titre <- "Contros AT vs Calculated AT" -->
+<!--  fit <- lmodel2(data = at_nov_2018_no_NA, AT_despike ~ at_calc, nperm = 99) -->
+<!-- ggreg2(fit, x = "at_calc", y = "AT_despike") -->
+
+<!-- ``` -->
 

### 2020-04-22 paper.Rmd
completedness

--- 2020-04-20 paper.Rmd
@@
 library("pangaear")
+if (!require("naniar")) install.packages("naniar")
+library("naniar")
+if (!require("visdat")) install.packages("visdat")
+library("visdat")
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-######## function to calculate 3 quantiles
+######## function to calculate min, max 3 quantiles
 qq <- function (data, digits) { 
-  as.numeric(formatC(quantile(x = data, probs = c(0.025, 0.50, 0.975), na.rm = TRUE),
+  as.numeric(formatC(quantile(x = data, probs = c(0, 0.025, 0.50, 0.975, 1), na.rm = TRUE),
                      format = "f", digits = digits))
@@
 ```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
-d_all <- as_tibble(readRDS(file = paste0(path_data, "fb_data/d_all.rds"))) 
+# d_all <- readRDS(file = paste0(path_data, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour_copy.rds"))
+# d <- d_all %>% 
+#   as_tsibble(index = datetime) %>% 
+#   dplyr::rename(depth = pressure_insitu_ctd) %>% 
+#   dplyr::mutate(year_month = format(datetime, '%Y-%m'))
+# count_gaps(d, .full = TRUE)
+
+d_all <- readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
 d <- d_all %>% 
@@
   #dplyr::filter(sal_fb > 28) %>% # remove salinity data lower than 28
-  dplyr::mutate(year_month = format(datetime, '%Y-%m')) %>%
+  as_tsibble(index = datetime) %>% 
   dplyr::arrange(datetime) %>%
-  dplyr::mutate(depth = as.numeric(str_remove(depth, pattern= " m"))) #depth is a string
+  dplyr::mutate(depth = as.numeric(str_remove(depth, pattern= " m"))) %>% #depth is a string
+  fill_gaps() %>%
+  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
+                quarter = quarter(datetime)) %>%
+  replace(., is.na(.), NA) # replace NaN by NA everywhere
+tmp <- d %>% 
+  as_tibble() %>% 
+  dplyr::select(pH_s_seafet_temp_ctd, par_air_filtered, pco2_contros, pH_s_seafet_temp_ctd, starts_with("sal_"),
+                starts_with("temp_"), at_calc, year_month, quarter)
+tmp visdat::vis_miss(tmp)
+gg_miss_var(tmp, facet = quarter)
 ```
+
+```{r calculate missing, echo=FALSE, warning=FALSE, message=FALSE}
+
+```
+# {.tabset .tabset-fade .tabset-pills}
 
@@
 
-## Temperature vs salinity
+## TvsS
 We explore the use of a TS diagram to investigate changes in water sources.
@@
 
+## Sensitivity
+We look at how sensitive pH are to errors in salinity (0.1 to 0.3) and temperature (-0.3 to 0.3).
+delta_pH is the unit difference between the starting value of pH (8 at S=34 and T=5) and the value with errors in S and T.
+pCO2 is measured and not sensitive, I think to errors in temperature.
+
+```{r sensitivity, echo=FALSE, warning=FALSE, message=FALSE}
+err <- as_tibble(
+  expand.grid(sal = 34+seq(0, 0.3, by = 0.1), 
+              temp = 5+round(seq(-0.3, 0.3, by = 0.1), digits=1))) %>%
+    dplyr::arrange(sal)
+err$pH <- pHinsi(pH=8,ALK=2.4e-3,Tinsi=err$temp,Tlab=5,Pinsi=1,S=err$sal,Pt=0,Sit=0)
+err$delta_pH <- round(8 - err$pH, digits = 3)
+knitr::kable(err, caption = "Errors in pH related to the uncertainty in salinity and temperature.") %>%
+  kable_styling(bootstrap_options = "striped", full_width = F)
+saveRDS(err, file=paste0(path_data, "error.rds"))
+```
 ## Consistency: pCO2

### 2020-04-22 awipev-CO2.Rmd
added section Traitement des variables

@@
 
+### Traitement des variables
+
+* temp_mix = temp 11m + temp ctd > 8m si trous.
+* sal_mix = sal FB + sal ctd > 8m si trous.
+* ph_s_sf_temp_mix: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
+* ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
+* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
+* pco2_calc: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
+* Relation at / sal_mix (sal FB + sal ctd > 8m si trous)
+* at_calc: calculé from sal_mix
+* E0int25_sf: calculé à partir du voltage interne + pH_s_seafet_temp_mix (temp 11m + temp ctd > 8m si trous) + temp CTD + sal CTD (calib seaFET fonction 1)
+* phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
+
 ### **FerryBox**

### 2020-04-22 awipev-CO2.Rmd
added section Traitement des variables

@@
 ```{r whole time series, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-#SAL CTD profile
+#SAL FB 
 sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb)
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
-dygraph(sal_xts, group = "awipev", main="Salinities (in situ CTD, all depths + FB)", ylab="Salinity") %>%
-      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "CTD") %>%
-            dySeries("sal_fb", color = "black", strokeWidth = 1, label = "FB") %>%
+dygraph(sal_xts, group = "awipev", main="Salinity FerryBox)", ylab="Salinity") %>%
+            dySeries("sal_fb", color = "blue", strokeWidth = 1, label = "sal_fb") %>%
+            dySeries("sal_fb", color = "black", strokeWidth = 1, label = "sal_fb") %>%
 dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
       dyRangeSelector(height = 30, dateWindow= NULL)
-#SAL FB
+#SAL CTD profile
 sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd)

### 2020-04-22 awipev-CO2.Rmd
variable names modification according to part : traitement des variables

--- 2020-04-22 awipev-CO2.Rmd
@@
 
+### creation of column sal_insitu_sup_8m 
+   d_all <- d_all%>%
+     dplyr::mutate(sal_insitu_sup_8m = ifelse(pressure_insitu_ctd >=8, sal_insitu_ctd, NA))
+
 ```
@@
 pH_seafet <- pH_seafet %>%
-  dplyr::mutate(pH_s_seafet_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_mix, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))
+  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_mix, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))
 
@@
 pH_durafet <- pH_durafet %>%
-  dplyr::mutate(pH_s_durafet_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb,Pt=0,Sit=0))
+  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb,Pt=0,Sit=0))
 
@@
 pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(datetime,pH_s_seafet_temp_mix)%>% 
+  dplyr::select(datetime,ph_s_sf_temp_mix)%>% 
   dplyr::group_by(datetime) %>% 
-  dplyr::summarize(pH_s_seafet_temp_mix = mean(pH_s_seafet_temp_mix, na.rm = T))
+  dplyr::summarize(ph_s_sf_temp_mix = mean(ph_s_sf_temp_mix, na.rm = T))
 pH_durafet_mean <- pH_durafet%>%
-  dplyr::select(datetime,pH_s_durafet_temp_fb)%>% 
+  dplyr::select(datetime,ph_s_dur_temp_fb)%>% 
   dplyr::group_by(datetime) %>% 
-  dplyr::summarize(pH_s_durafet_temp_fb = mean(pH_s_durafet_temp_fb, na.rm = T))
+  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = T))
 
@@
   #drop_na() %>%
-  dplyr::select(closest_datetime, pH_s_seafet_temp_mix) %>%
+  dplyr::select(closest_datetime, ph_s_sf_temp_mix) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
   #drop_na() %>%
-  dplyr::select(closest_datetime, pH_s_durafet_temp_fb) %>%
+  dplyr::select(closest_datetime, ph_s_dur_temp_fb) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
     dyRangeSelector(height = 30, dateWindow= NULL)
-# DURAFET 
-durafet_contros_xts <- dplyr::select(d_all, datetime, ph_dur, pH_s_durafet_temp_fb)
-durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
-dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
-    dySeries("ph_dur", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_s_durafet_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyAxis("y",valueRange = c(8, 8.8)) %>%
-    dyLegend(show = "follow")   %>%
-    dyRangeSelector(height = 30, dateWindow= NULL) 
-# SEAFET 
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT,pH_s_seafet_temp_mix)
-seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ T CTD)", ylab="pHT") %>%
-  dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-  dySeries("pH_s_seafet_temp_mix", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
-  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyAxis("y",valueRange = c(7.45, 8.8)) %>%
-    dyLegend(show = "follow")   %>%
-    dyRangeSelector(height = 30, dateWindow= NULL) 
+# # DURAFET 
+# durafet_contros_xts <- dplyr::select(d_all, datetime, ph_dur, ph_s_dur_temp_fb)
+# durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
+# dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
+#     dySeries("ph_dur", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
+#     dySeries("ph_s_dur_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+#     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
+#     dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
+#     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
+#     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+#     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+#     dyAxis("y",valueRange = c(8, 8.8)) %>%
+#     dyLegend(show = "follow")   %>%
+#     dyRangeSelector(height = 30, dateWindow= NULL) 
+# # SEAFET 
+# seafet_contros_xts <- dplyr::select(d_all, datetime, phINT,ph_s_sf_temp_mix)
+# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
+# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ T CTD)", ylab="pHT") %>%
+#   dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
+#   dySeries("ph_s_sf_temp_mix", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+#   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
+#   dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
+#   dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
+#     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+#     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+#     dyAxis("y",valueRange = c(7.45, 8.8)) %>%
+#     dyLegend(show = "follow")   %>%
+#     dyRangeSelector(height = 30, dateWindow= NULL) 
 # # TA
@@
 
-# date format into charactere
-d_all$datetime_chr <- as.character(d_all$datetime)
-
-p_sal_fb_ctd<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd >=8),aes(x=sal_insitu_ctd, y= sal_fb, label = month))+
-  geom_point( aes(color=factor(datetime_chr))) + 
+p_sal_fb_ctd<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd >=8),aes(x=sal_insitu_ctd, y= sal_fb))+
+  geom_point( aes(color=factor(month))) + 
  # scale_color_viridis_d(option = "C", guide="none")+
@@
   coord_fixed(ratio = 1 )+
-   scale_colour_discrete(guide="none") +
+ #  scale_colour_discrete(guide="none") +
   labs( x="Salinity CTD > 8 m", y="Salinity FB ", color = "Months") +theme_bw()
@@
 p_temp_11_fb<-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
-  geom_text( aes(color=factor(datetime_chr))) + 
+  geom_text( aes(color=factor(month))) + 
  # scale_color_viridis_d(option = "C", guide="none")+
@@
 This was the 3rd analyser on site.
-
-We identify four periods (see plot at the end of this page with dark and ligth grey):
-
-- from the set-up of the instrument on **2016-02-23** to **2017-02-09** during which we try to correct for the drift
-- from **2017-02-09** to **2017-03-10** during which no drift correction is made, just an offset is applied to correct for the sudden shift in the data
-- from the set-up of a new instrument on **2018-01-08** to **2018-06-20**, during which another correction using the discrete samples will be performed.
+Even with this instrument, data collection didn't show satisfaction.
+
+<!-- We identify four periods (see plot at the end of this page with dark and ligth grey): -->
+
+<!-- - from the set-up of the instrument on **2016-02-23** to **2017-02-09** during which we try to correct for the drift -->
+<!-- - from **2017-02-09** to **2017-03-10** during which no drift correction is made, just an offset is applied to correct for the sudden shift in the data -->
+<!-- - from the set-up of a new instrument on **2018-01-08** to **2018-06-20**, during which another correction using the discrete samples will be performed.
 In this period and before to stop it, continuous leakages in the degasing unit happened.
-- from the set-up of a repaired unit on **2018-07-31** to **2018-10-31**.
+-->
+<!-- - from the set-up of a repaired unit on **2018-07-31** to **2018-10-31**.
 Here, the instrument took wrong salinity to perform AT measurements.
@@
 We decided to switch off the instrument to save reagents and wait until the comming of Steffen in NYA with a new instrument.
-
-A new instrument was installed with Steffen on **2018-10-31**.
+-->
+
+<!-- A new instrument was installed with Steffen on **2018-10-31**.
 This new instrument has a complete new designed membrane which will solve the problem.
@@
 Samir has all the passwords and ID to connect.
-
-The instrument is usually calibrated against CRM standards after deployment, CRMs are run after 3 months as samples (measurement mode, not calibration mode), an then immediately calibrated again.
+-->
+
+<!-- The instrument is usually calibrated against CRM standards after deployment, CRMs are run after 3 months as samples (measurement mode, not calibration mode), an then immediately calibrated again.
 This procedure is repeated every 3 months.
-
-### **Filtration of AT data: outliers removing**
-
-Outliers are present because of the cleaning operations made on the FerryBox everydays at 12:00am and 12:00pm.
-We first removed the outliers using a filter and decided, after a Skype conference with Steffen on September 2016, to:
-
-  - Remove existing filters ( > 2350 µmol/kg).
-  - Filter using salinity flag.
-  - Filter using pH flag.
-  - Not to filter on temperature flag.
-  - Apply a 3 data points median filter (no longer used; see despike function in "oce" package)
-
-We decided to use "despike" function as data filter.
+-->
+
+<!-- ### **Filtration of AT data: outliers removing** -->
+
+<!-- Outliers are present because of the cleaning operations made on the FerryBox everydays at 12:00am and 12:00pm.
+We first removed the outliers using a filter and decided, after a Skype conference with Steffen on September 2016, to: -->
+
+<!--   - Remove existing filters ( > 2350 µmol/kg). -->
+<!--   - Filter using salinity flag. -->
+<!--   - Filter using pH flag. -->
+<!--   - Not to filter on temperature flag. -->
+<!--   - Apply a 3 data points median filter (no longer used; see despike function in "oce" package) -->
+
+<!-- We decided to use "despike" function as data filter.
 This filter is done in "ny-alesund_cc.R".
 Length of runing median is: k = 121 days and the indicator (n times the sd between x and the reference) to consider a data from an outlier is: n = 0.5.
-
-### **Correction of AT data**
-
-Calibration was initially performed twice a year since the analyser was supposed to be stable.
+-->
+
+<!-- ### **Correction of AT data** -->
+
+<!-- Calibration was initially performed twice a year since the analyser was supposed to be stable.
 Calibration was performed using the internal "calibration mode" against a CRM from A.Dickson (Batch #145, 2016-02-24) right after the instrument was installed and a second time on 2016-09-16.
 This approch is not longer used since September 2016 (Skype with Contros).
-
-Since this date, the analyser is calibrated by measuring a CRM with the "measurement mode" in order to measure the offset of the instrument.
+-->
+
+<!-- Since this date, the analyser is calibrated by measuring a CRM with the "measurement mode" in order to measure the offset of the instrument.
 Additionally, discrete seawater are sampled weekly and TA is analysed by SNAPO-CO2.
-
-  - Two methods to correct the drift are available:
-    - based on CRMs 
-    - based on AT measurement of discrete samples ("references").
-
-#### **Calibration**
-
-- **2019-01-29 14:10**: Calibration started by Philipp Fisher using CRM 145 (2226.16 umol/kg, 33.572).
+-->
+
+<!--   - Two methods to correct the drift are available: -->
+<!--     - based on CRMs  -->
+<!--     - based on AT measurement of discrete samples ("references"). -->
+
+<!-- #### **Calibration** -->
+
+<!-- - **2019-01-29 14:10**: Calibration started by Philipp Fisher using CRM 145 (2226.16 umol/kg, 33.572).
 The three previous measurements were 2314.5, 233.8, 2313.7 (analyser stable) and the six subsequent measurements were 2211.8, 2277.5, 2305.4, 2316.6, 2317.9.
 Error was done with CRM salinity (Analyser was not unplugged from the FB).
-Steffen's response:
-> Hence, the serial connection should be cut off or the FB module feeding the analyzer with salinity data should be stopped during calibration.
+-->
+<!-- Steffen's response: -->
+<!-- > Hence, the serial connection should be cut off or the FB module feeding the analyzer with salinity data should be stopped during calibration.
 The calibration can be recalculated afterwards in the data post-processing.
@@
 So for now, it should be fine.
-
-#### **CRM measurements**
-
-The calibration of the sensor is made against a CRM standard from A.
+-->
+
+<!-- #### **CRM measurements** -->
+
+<!-- The calibration of the sensor is made against a CRM standard from A.
 Dickson.
@@
 Result sof calibrations are shown on the following plot.Dashed lines represent the theoritical value of AT (CRM) and hard lines represent CRM measured AT by the instrument.
-
-```{r CRM measurements, echo=FALSE, warning=FALSE, message=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-calib_analyser <-  read.table(paste0(path, "fb_data/Calibration_TA/TA_#1215/measure_CRM_TA.txt"), header = T, dec = ".", as.is = T, sep = ",", fill = TRUE)
-
-# To make the mean 
-# Keep dates as Character to plot without date gaps.
-calib_analyser3 <- calib_analyser %>%
-  dplyr::filter(analyser == "TA3") 
-meanTA3 <- calib_analyser3 %>% 
-  group_by(day) %>% 
-  summarise (meanTA = mean(TA))
-
-melt_calib <- melt(calib_analyser, id.vars=c("analyser", "TA_theo", "datetime", "CRM"), measure.vars=c("TA"))
-calib_p <- ggplot()+ 
-          geom_point(data= melt_calib, aes(x=datetime, y=value, color=factor(CRM), shape= factor(analyser)) , size=3) +
-          scale_color_manual(values=c("blue","red"))+
-         # set dashed lines for theoritical CRM
-          geom_segment(aes(x=1,xend=20,y=2226.16,yend=2226.16), linetype="dashed", color="blue")+
-          annotate("text", x = 11, y = 2228, label = "Batch #145 = 2226.16", color="blue")+
-          geom_segment(aes(x=20,xend=23,y=2213.59,yend=2213.59), linetype="dashed", color="red")+
-          annotate("text", x = 15.5, y = 2213.59, label = "Batch #159 = 2213.59", color="red")+
-        # set hard lines for measured CRM
-          geom_segment(aes(x=1,xend=5,y=2254,yend=2254), color="blue") +
-          annotate("text", x = 3, y = 2249, label = "2254", color="blue")+
-          geom_segment(aes(x=6,xend=10,y=2251.6,yend=2251.6), color="blue") +
-          annotate("text", x = 8, y = 2247, label = "2251.6", color="blue")+
-          geom_segment(aes(x=11,xend=15,y=2190.4,yend=2190.4), color="blue")+
-          annotate("text", x = 14, y = 2195, label = "2190.4", color="blue")+
-          geom_segment(aes(x=16,xend=20,y=2203.5,yend=2203.5), color="blue")+
-          annotate("text", x = 18, y = 2200, label = "2203.5", color="blue")+
-          geom_segment(aes(x=21,xend=23,y=2224.20,yend=2224.20), color="red")+
-          annotate("text", x = 22, y = 2230, label = "2224.2", color="red") +
-  theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1))+ 
-  labs(title= "",y=expression(paste("Total alkalinity (µmoles.",kg^-1,")")), x="Date", color= "CRM",shape= "Deployed instrument")
-
-ggsave("figures/TA_calibration_CRM.png", calib_p, units="cm")
-print(calib_p)
-```
-
-#### **Discrete samples ("references")**
-
-On 2018-04-19, Steffen sent his answer concerning the drift correction during the period February 2016 to March 2017.
+-->
+
+<!-- ```{r CRM measurements, echo=FALSE, warning=FALSE, message=FALSE, out.width="80%",fig.show='hold', fig.align="center"} -->
+<!-- calib_analyser <-  read.table(paste0(path, "fb_data/Calibration_TA/TA_#1215/measure_CRM_TA.txt"), header = T, dec = ".", as.is = T, sep = ",", fill = TRUE) -->
+
+<!-- # To make the mean  -->
+<!-- # Keep dates as Character to plot without date gaps. -->
+<!-- calib_analyser3 <- calib_analyser %>% -->
+<!--   dplyr::filter(analyser == "TA3")  -->
+<!-- meanTA3 <- calib_analyser3 %>%  -->
+<!--   group_by(day) %>%  -->
+<!--   summarise (meanTA = mean(TA)) -->
+
+<!-- melt_calib <- melt(calib_analyser, id.vars=c("analyser", "TA_theo", "datetime", "CRM"), measure.vars=c("TA")) -->
+<!-- calib_p <- ggplot()+  -->
+<!--           geom_point(data= melt_calib, aes(x=datetime, y=value, color=factor(CRM), shape= factor(analyser)) , size=3) + -->
+<!--           scale_color_manual(values=c("blue","red"))+ -->
+<!--          # set dashed lines for theoritical CRM -->
+<!--           geom_segment(aes(x=1,xend=20,y=2226.16,yend=2226.16), linetype="dashed", color="blue")+ -->
+<!--           annotate("text", x = 11, y = 2228, label = "Batch #145 = 2226.16", color="blue")+ -->
+<!--           geom_segment(aes(x=20,xend=23,y=2213.59,yend=2213.59), linetype="dashed", color="red")+ -->
+<!--           annotate("text", x = 15.5, y = 2213.59, label = "Batch #159 = 2213.59", color="red")+ -->
+<!--         # set hard lines for measured CRM -->
+<!--           geom_segment(aes(x=1,xend=5,y=2254,yend=2254), color="blue") + -->
+<!--           annotate("text", x = 3, y = 2249, label = "2254", color="blue")+ -->
+<!--           geom_segment(aes(x=6,xend=10,y=2251.6,yend=2251.6), color="blue") + -->
+<!--           annotate("text", x = 8, y = 2247, label = "2251.6", color="blue")+ -->
+<!--           geom_segment(aes(x=11,xend=15,y=2190.4,yend=2190.4), color="blue")+ -->
+<!--           annotate("text", x = 14, y = 2195, label = "2190.4", color="blue")+ -->
+<!--           geom_segment(aes(x=16,xend=20,y=2203.5,yend=2203.5), color="blue")+ -->
+<!--           annotate("text", x = 18, y = 2200, label = "2203.5", color="blue")+ -->
+<!--           geom_segment(aes(x=21,xend=23,y=2224.20,yend=2224.20), color="red")+ -->
+<!--           annotate("text", x = 22, y = 2230, label = "2224.2", color="red") + -->
+<!--   theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1))+  -->
+<!--   labs(title= "",y=expression(paste("Total alkalinity (µmoles.",kg^-1,")")), x="Date", color= "CRM",shape= "Deployed instrument") -->
+
+<!-- ggsave("figures/TA_calibration_CRM.png", calib_p, units="cm") -->
+<!-- print(calib_p) -->
+<!-- ``` -->
+
+<!-- #### **Discrete samples ("references")**  -->
+
+<!-- On 2018-04-19, Steffen sent his answer concerning the drift correction during the period February 2016 to March 2017.
 Within this one year period, the analyser was running, except the first week of May 2016.
@@
 He suggested to base the correction on the AT of discrete ("reference") samples.
-
-> "I chose the discrete reference samples due to the fact that those cover the entire working range including time, salinity and also provide a broader data basis for this kind of correction.
-Also, when looking at the uncertainty below, I fear that the three CRM measurements over 5 month are not sufficient enough for such a drift determination."
-
-A linear regression was performed based on the difference between the measured (analyzer) and discrete samples.
+-->
+
+<!-- > "I chose the discrete reference samples due to the fact that those cover the entire working range including time, salinity and also provide a broader data basis for this kind of correction.
+Also, when looking at the uncertainty below, I fear that the three CRM measurements over 5 month are not sufficient enough for such a drift determination." -->
+
+<!-- A linear regression was performed based on the difference between the measured (analyzer) and discrete samples.
 Discrete samples were matched with the AT measured by the analyser.
@@
 The differences between the measured (analyzer) and analysed ("reference") data was plotted as a function of time.
-
-This approach was performed:
-
-  - on the same period than in Steffen email's (**First period**, 2016-02-23 to 2017-02-09)
-  - and during the **third period**, with the new analyzer (2018-01-07 to 2018-06-20)
-
-##### **First period**
-
-```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"}
-# #Interpolation of continuous sensor data to match a maximum of reference data.
-# TAinterp_all <-approx(d_all$datetime, d_all$AT, xout=d_all$datetime, method="linear", rule=2)
-# names(TAinterp_all) <- c("datetime", "AT_interp")
-# TAinterp_all <- as.data.frame(TAinterp_all)
-# d_all$AT_interp <- TAinterp_all$AT_interp
-# 
-# # create a column with difference between sensor and ref
-# d_all <- d_all%>%
-#   dplyr::mutate(diff_ta =  at-AT_interp )
-# # create colum with instrument number
-# d_all <- d_all %>%
-#   dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1",
-#                             ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2",
-#                             ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3",
-#                             ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4",
-#                             ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5",
-#                             ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0")))))))
-# 
-# #remove outliers
-# calib_ta_first <- d_all%>%
-#   dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta,TA_period)%>%
-#   dplyr::filter(TA_period =="TA1" & !is.na(at))
-#   #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 )
-# # & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at))
-# 
-# # Parameters of regression
-# fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime)
-# at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6)
-# at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2)
-# at_intercept1 <- round(fit$coefficients[[1]], digits= 2)
-```
+-->
+
+<!-- This approach was performed: -->
+
+<!--   - on the same period than in Steffen email's (**First period**, 2016-02-23 to 2017-02-09) -->
+<!--   - and during the **third period**, with the new analyzer (2018-01-07 to 2018-06-20) -->
+
+<!-- ##### **First period**  -->
+
+<!-- ```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"} -->
+<!-- #Interpolation of continuous sensor data to match a maximum of reference data. -->
+<!-- TAinterp_all <-approx(d_all$datetime, d_all$AT, xout=d_all$datetime, method="linear", rule=2) -->
+<!-- names(TAinterp_all) <- c("datetime", "AT_interp") -->
+<!-- TAinterp_all <- as.data.frame(TAinterp_all) -->
+<!-- d_all$AT_interp <- TAinterp_all$AT_interp -->
+
+<!-- # create a column with difference between sensor and ref -->
+<!-- d_all <- d_all%>% -->
+<!--   dplyr::mutate(diff_ta =  at-AT_interp ) -->
+<!-- # create colum with instrument number -->
+<!-- d_all <- d_all %>% -->
+<!--   dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1", -->
+<!--                             ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2", -->
+<!--                             ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3", -->
+<!--                             ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4", -->
+<!--                             ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5", -->
+<!--                             ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0"))))))) -->
+
+<!-- #remove outliers -->
+<!-- calib_ta_first <- d_all%>% -->
+<!--   dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta,TA_period)%>% -->
+<!--   dplyr::filter(TA_period =="TA1" & !is.na(at)) -->
+<!--   #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 ) -->
+<!-- # & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at)) -->
+
+<!-- # Parameters of regression -->
+<!-- fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime) -->
+<!-- at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6) -->
+<!-- at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2) -->
+<!-- at_intercept1 <- round(fit$coefficients[[1]], digits= 2) -->
+<!-- ``` -->
 
@@
 
-```{r Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%", fig.align="center"}
+```{r Discrete salinity vs TA, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="100%"}
 d_all_at_discrete <- d_all %>% #  To remove an outlier in red
@@
 
-```{r plot Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="60%", fig.align="center"}
+```{r plot Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
  # PLOT
@@
   #dySeries("AT", label= "Raw TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
-  dySeries("at_calc", label="TA calc ",color = "blue", strokeWidth = 0, pointSize=2) %>%
-  dySeries("at", label="TA ref",color = "red", strokeWidth = 0, pointSize=4) %>%
+  dySeries("at_calc", label="at_calc",color = "blue", strokeWidth = 0, pointSize=2) %>%
+  dySeries("at", label="at (ref)",color = "red", strokeWidth = 0, pointSize=4) %>%
   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
@@
   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-  dyAxis("y",valueRange = c(2000, 2650)) %>%
+  #dyAxis("y",valueRange = c(2000, 2650)) %>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
 # sfPeriod <- d_all%>%
-#   dplyr::select(datetime, pH_s_seafet_temp_mix)%>%
-#   dplyr::filter(!is.na(pH_s_seafet_temp_mix))
+#   dplyr::select(datetime, ph_s_sf_temp_mix)%>%
+#   dplyr::filter(!is.na(ph_s_sf_temp_mix))
 # # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
@@
 ####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$pH_s_seafet_temp_mix,
+calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix,
                           calT = d_all$temp_insitu_ctd, calSal = d_all$sal_insitu_ctd )
@@
 d_all <- d_all%>%
-  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", pH_s_seafet_temp_mix, NA ))
-
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT, pH_s_seafet_temp_mix, pHint_tot_sf, pH_s_sf_no_calb, pressure_insitu_ctd, sal_insitu_ctd, temp_insitu_ctd)
+  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", ph_s_sf_temp_mix, NA ))
+
+seafet_contros_xts <- dplyr::select(d_all, datetime, phINT, ph_s_sf_temp_mix, pHint_tot_sf, pH_s_sf_no_calb, pressure_insitu_ctd, sal_insitu_ctd, temp_insitu_ctd)
 #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
 dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-dySeries("pH_s_seafet_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+dySeries("ph_s_sf_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
 dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
@@
 
-seafet_depth_xts <- dplyr::select(d_all, datetime, phINT, pH_s_seafet_temp_mix,pHint_tot_sf)
+seafet_depth_xts <- dplyr::select(d_all, datetime, phINT, ph_s_sf_temp_mix,pHint_tot_sf)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
-dygraph(seafet_depth_xts, group = "depth", main="pH seaFET RAW (in situ)", ylab="pHT") %>%
-  dySeries("pH_s_seafet_temp_mix", axis="y2", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+dygraph(seafet_depth_xts, group = "depth", main="pH seaFET (ref + corrected + raw)", ylab="pHT") %>%
+  dySeries("ph_s_sf_temp_mix", axis="y2", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
   dySeries("phINT", axis="y2",label = "pH RAW", color ="blue", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%
@@
 # # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT,pH_s_seafet_temp_mix, temp_sf, temp_fb, temp_insitu, sal)
+# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT,ph_s_sf_temp_mix, temp_sf, temp_fb, temp_insitu, sal)
 # #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
@@
 #   #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-#    # dySeries("pH_s_seafet_temp_mix", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
+#    # dySeries("ph_s_sf_temp_mix", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
 #     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
@@
 # sfoffset <- left_join(sfPeriod[,c(1,2)], d_all%>%dplyr::select(datetime, pHint_tot_sf), by="datetime")
-# dat <- mutate(sfoffset, diff_pH_sf = round((pH_s_seafet_temp_mix - pHint_tot_sf),digits  = 4))
+# dat <- mutate(sfoffset, diff_pH_sf = round((ph_s_sf_temp_mix - pHint_tot_sf),digits  = 4))
 # average_offset <- mean(abs(dat$diff_pH_sf), na.rm=TRUE)
@@
 #   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_seafet_temp_mix, fill="Discrete measurements"), col="red" )+
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=ph_s_sf_temp_mix, fill="Discrete measurements"), col="red" )+
 #   labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
@@
 durPeriod <- d_all%>%
-  dplyr::select(datetime, pH_s_durafet_temp_fb)%>%
-  dplyr::filter(!is.na(pH_s_durafet_temp_fb))
+  dplyr::select(datetime, ph_s_dur_temp_fb)%>%
+  dplyr::filter(!is.na(ph_s_dur_temp_fb))
 
@@
 # Offset between durafet pH and spec pH 
-duroffset <- left_join(durPeriod%>%dplyr::select(datetime,pH_s_durafet_temp_fb), d_all%>%dplyr::select(datetime,ph_dur ), by="datetime")
-dat_dur <- mutate(duroffset, diff_pH_dur = pH_s_durafet_temp_fb - ph_dur)
+duroffset <- left_join(durPeriod%>%dplyr::select(datetime,ph_s_dur_temp_fb), d_all%>%dplyr::select(datetime,ph_dur ), by="datetime")
+dat_dur <- mutate(duroffset, diff_pH_dur = ph_s_dur_temp_fb - ph_dur)
 average_offset_dur <- round(mean(dat_dur$diff_pH_dur, na.rm=TRUE), digits = 2)
@@
 d_all <- d_all%>%
-  dplyr::mutate( pH_s_dur_no_calb = ifelse(datetime == "2017-08-24 13:00:00", pH_s_durafet_temp_fb, NA ))
-
-durafet_contros_xts <- dplyr::select(d_all, datetime, ph_dur, pH_s_durafet_temp_fb,ph_dur_corr, pH_s_dur_no_calb)
+  dplyr::mutate( pH_s_dur_no_calb = ifelse(datetime == "2017-08-24 13:00:00", ph_s_dur_temp_fb, NA ))
+
+durafet_contros_xts <- dplyr::select(d_all, datetime, ph_dur, ph_s_dur_temp_fb,ph_dur_corr, pH_s_dur_no_calb)
 durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
@@
        dySeries("ph_dur_corr", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
-       dySeries("pH_s_durafet_temp_fb", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
+       dySeries("ph_s_dur_temp_fb", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
     dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
@@
 #   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= ph_dur_corr,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=pH_s_durafet_temp_fb, fill="Discrete measurements"), col="red" )+
+#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=ph_s_dur_temp_fb, fill="Discrete measurements"), col="red" )+
 #   labs(x = "", y= "", title = expression(pH[T]~durafet)) +
@@
 # Spectro / durafet
-fit <- lmodel2(data = d_all,  pH_s_durafet_temp_fb ~ ph_dur_corr , nperm = 99)
-
-p_dura_spectro <-  ggplot(d_all,aes(x=ph_dur_corr, y= pH_s_durafet_temp_fb, label = month))+
+fit <- lmodel2(data = d_all,  ph_s_dur_temp_fb ~ ph_dur_corr , nperm = 99)
+
+p_dura_spectro <-  ggplot(d_all,aes(x=ph_dur_corr, y= ph_s_dur_temp_fb, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
 # Spectro / seafet
-fit <- lmodel2(data = d_all,  pH_s_seafet_temp_mix ~ pHint_tot_sf , nperm = 99)
-
-p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= pH_s_seafet_temp_mix, label = month))+
+fit <- lmodel2(data = d_all,  ph_s_sf_temp_mix ~ pHint_tot_sf , nperm = 99)
+
+p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= ph_s_sf_temp_mix, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
 
+### Traitement des variables
+
+* temp_mix = temp 11m + temp ctd > 8m si trous.
+* sal_mix = sal FB + sal ctd > 8m si trous.
+* ph_s_sf_temp_mix: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
+* ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
+* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
+* pco2_calc: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
+* Relation at / sal_mix (sal FB + sal ctd > 8m si trous)
+* at_calc: calculé from sal_mix
+* E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_mix (temp 11m + temp ctd > 8m si trous) + temp CTD + sal CTD (calib seaFET fonction 1)
+* phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
+
 ### **FerryBox**
@@
 <!--  # DURAFET  -->
-<!-- durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, pH_s_durafet_temp_fb) -->
+<!-- durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, ph_s_dur_temp_fb) -->
 <!-- durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime) -->
@@
 <!--     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>% -->
-<!--     dySeries("pH_s_durafet_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
+<!--     dySeries("ph_s_dur_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
 <!--     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>% -->
@@
 <!-- # SEAFET  -->
-<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT,pH_s_seafet_temp_mix) -->
+<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT,ph_s_sf_temp_mix) -->
 <!-- seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime) -->
@@
 <!--   dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>% -->
-<!--   dySeries("pH_s_seafet_temp_mix", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
+<!--   dySeries("ph_s_sf_temp_mix", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
 <!--   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>% -->

### 2020-04-22 awipev-CO2.Rmd
variable names modification according to part : traitement des variables 2

@@
 discrete_no_na$phcalc<- carb$pH
-discrete_no_na$pco2calc<- carb$pCO2
+discrete_no_na$pco2_calc<- carb$pCO2
 
@@
 discrete_is_na$phcalc<- NA
-discrete_is_na$pco2calc<- NA
+discrete_is_na$pco2_calc<- NA
 discrete <- rbind(discrete_no_na, discrete_is_na)
@@
   #drop_na() %>%
-  dplyr::select(closest_datetime, pco2calc) %>%
+  dplyr::select(closest_datetime, pco2_calc) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 #SAL FB 
-sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb)
+sal_xts <- dplyr::select(d_all, datetime, sal_fb)
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
@@
             dySeries("sal_fb", color = "blue", strokeWidth = 1, label = "sal_fb") %>%
-            dySeries("sal_fb", color = "black", strokeWidth = 1, label = "sal_fb") %>%
 dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
 dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
-      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "S") %>%
+      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "sal_insitu_ctd") %>%
       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
 dygraph(temp_fb_xts, group = "awipev", main="Temperature (in Ferrybox)", ylab="Temperature") %>%
-      dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "T") %>%
+      dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "temp_fb") %>%
       dyAxis("y", valueRange = c(-2.5, 10)) %>%
@@
 dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ 11 m)", ylab="Temperature") %>%
-      dySeries("temp_insitu_11m", color = "blue", strokeWidth = 0, label = "T") %>%
+      dySeries("temp_insitu_11m", color = "blue", strokeWidth = 0, label = "temp_insitu_11m") %>%
       dyAxis("y", valueRange = c(-2.8, 10)) %>%
@@
 dygraph(temp_insitu_xts, group = "awipev", main="Temperature (ctd all depths)", ylab="Temperature") %>%
-      dySeries("temp_insitu_ctd", color = "blue", strokeWidth = 0, label = "T") %>%
+      dySeries("temp_insitu_ctd", color = "blue", strokeWidth = 0, label = "temp_insitu_ctd") %>%
       dyAxis("y", valueRange = c(-2.8, 10)) %>%
@@
 #+ Ajout de la pCO2 corrigé par le script contros (dans R server ny-alesund_cc.R)
-pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_corr)
+pco2_contros_xts <- dplyr::select(d_all, datetime, pco2_calc, pco2_corr)
 pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
@@
     dySeries("pco2_corr", label="Corrected pCO2", color=  "blue",strokeWidth=0, pointSize=2) %>%
-    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pco2_calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
     dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
@@
 title <- "Contros vs calculated pCO2"
-fit <- lmodel2(data = d_all,  pco2_corr ~ pco2calc , nperm = 99)
-
-pco2calc_pCO2_contros_text <-  ggplot(d_all,aes(x=pco2calc, y= pco2_corr, label = month))+
+fit <- lmodel2(data = d_all,  pco2_corr ~ pco2_calc , nperm = 99)
+
+pco2_calc_pco2_corr_text <-  ggplot(d_all,aes(x=pco2_calc, y= pco2_corr, label = month))+
    geom_text(aes(color = factor(month)))+
@@
 ```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-print(pco2calc_pCO2_contros_text)
-ggsave(paste0("figures/pco2calc_pCO2_contros.png"), pco2calc_pCO2_contros_text, units="cm")
+print(pco2_calc_pco2_corr_text)
+ggsave(paste0("figures/pco2_calc_pco2_corr.png"), pco2_calc_pco2_corr_text, units="cm")
 ```
@@
 ```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-pco2_contros_xts <- dplyr::select(d_all, datetime, pco2calc, pco2_corr)
+pco2_contros_xts <- dplyr::select(d_all, datetime, pco2_calc, pco2_corr)
 pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
@@
     #dySeries("pco2_raw", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
-    dySeries("pco2calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pco2_calc", label="pco2_calc",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
     dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
@@
 #   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
-#   geom_point(data=d_all, aes(x=datetime, y=pco2calc, shape="lab" , color= "red"))+
+#   geom_point(data=d_all, aes(x=datetime, y=pco2_calc, shape="lab" , color= "red"))+
 #   geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+

### 2020-04-23 awipev-CO2.Rmd
variable names updates

@@
                                ifelse (pressure_insitu_ctd >=8 ,temp_insitu_ctd, NA )))
+
+# qf added 
+d_all <- d_all %>% 
+  dplyr::mutate(
+    temp_fb_qf = ifelse(
+      State_Zero >= 1 | State_Flush >= 1 |
+        pco2_raw < 100 | pco2_raw > 450 |
+        Time >= "00:00:00" & Time <= "01:30:00" |
+        Time >= "12:00:00" & Time <= "13:00:00" |
+        datetime == "2017-03-22 08:00:00" ,
+      4,
+      1
+    ),
+    pco2_raw = ifelse(pco2_raw_qf == 4 , NA, pco2_raw),
+    pco2_corr_qf = ifelse(
+      State_Zero >= 1 | State_Flush >= 1 |
+        pco2_corr < 100 | pco2_corr > 450 |
+        Time >= "00:00:00" & Time <= "01:30:00" |
+        Time >= "12:00:00" & Time <= "13:00:00" |
+        datetime >= "2017-03-10 08:00:00" &
+        datetime < "2017-03-21 20:00:00",
+      4,
+      1
+    ),
+    pco2_corr = ifelse(pco2_corr_qf == 4 , NA, pco2_corr)
+  )
 ```
@@
 dygraph(sal_xts, group = "awipev", main="Salinity FerryBox)", ylab="Salinity") %>%
-            dySeries("sal_fb", color = "blue", strokeWidth = 1, label = "sal_fb") %>%
+            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
 dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
 # pH seaFET Final
+# add despike with n=2 k = 5762 to the final ph corrected data
+d_all <- d_all %>%     
+   dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA"))
+
 # add spectro points that are not taking into consideration
 d_all <- d_all%>%
-  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 09:00:00" | datetime == "2019-01-18 09:00:00", ph_s_sf_temp_mix, NA ))
-
-seafet_contros_xts <- dplyr::select(d_all, datetime, phINT, ph_s_sf_temp_mix, pHint_tot_sf, pH_s_sf_no_calb, pressure_insitu_ctd, sal_insitu_ctd, temp_insitu_ctd)
-#seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
-seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-dySeries("temp_insitu_ctd", axis="y",label = "T ctd", color ="grey", strokeWidth=0, pointSize=2) %>%
-dySeries("sal_insitu_ctd", axis="y",label = "S ctd", color ="orange", strokeWidth=0, pointSize=2) %>%
-dySeries("pressure_insitu_ctd", axis="y2",label = "Pression", color ="pink", strokeWidth=0, pointSize=2) %>%
-dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
-dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-dySeries("ph_s_sf_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
-
-  dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
-  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
-
-  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
-  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[3], to= sfinterv[4], color = "#CCCCCC") %>%
-  # dyShading(from = sfinterv[4], to= sfinterv[5], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[5], to= sfinterv[6], color = "#CCCCCC") %>%
-  # dyShading(from = sfinterv[6], to= sfinterv[7], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[7], to= sfinterv[8], color = "#CCCCCC") %>%
-  # dyShading(from = sfinterv[8], to= sfinterv[9], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[9], to= sfinterv[10], color = "#CCCCCC") %>%
-  # dyShading(from = sfinterv[10], to= sfinterv[11], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[11], to= sfinterv[12], color = "#CCCCCC") %>%
-  # dyShading(from = sfinterv[12], to= sfinterv[13], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[13], to= sfinterv[14], color = "#CCCCCC") %>%
-  #  dyShading(from = sfinterv[14], to= sfinterv[15], color = "#E0E0E0") %>%
-  #  dyShading(from = sfinterv[15], to= sfinterv[16], color = "#CCCCCC") %>%
-  #  dyShading(from = sfinterv[16], to= sfinterv[17], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[17], to= sfinterv[18], color = "#CCCCCC") %>%
-  # dyShading(from = sfinterv[18], to= sfinterv[19], color = "#E0E0E0") %>%
-  # dyShading(from = sfinterv[19], to= sfinterv[20], color = "#CCCCCC") %>%
-  #  dyShading(from = sfinterv[20], to= sfinterv[21], color = "#E0E0E0") %>%
-  #  dyShading(from = sfinterv[21], to= sfinterv[22], color = "#CCCCCC") %>%
-  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
-  dyLegend(show = "auto")   %>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-  dyRangeSelector(height = 30, dateWindow= NULL)
+  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 10:00:00" | datetime == "2019-01-18 11:00:00", ph_s_sf_temp_mix, NA ))
 
@@
 
-seafet_depth_xts <- dplyr::select(d_all, datetime, phINT, ph_s_sf_temp_mix,pHint_tot_sf)
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_mix,pHint_tot_sf, pHint_tot_sf_filtered, pH_s_sf_no_calb)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
 dygraph(seafet_depth_xts, group = "depth", main="pH seaFET (ref + corrected + raw)", ylab="pHT") %>%
-  dySeries("ph_s_sf_temp_mix", axis="y2", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-  dySeries("phINT", axis="y2",label = "pH RAW", color ="blue", strokeWidth=0, pointSize=2,  stepPlot = TRUE) %>%
-  dySeries("pHint_tot_sf", axis="y2", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
+dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 3) %>%
+dySeries("pHint_tot_sf_filtered", label = "pHint_tot_sf_filtered", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 2) %>%
+dySeries("ph_s_sf_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+
+dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
+
   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
@@
   dyLegend(show = "auto")   %>%
+  dyAxis("y2",valueRange = c(-2, 2)) %>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%

### 2020-04-24 awipev-CO2.Rmd
remove chunk with group depths

@@
 
-```
-
-```{r Depth filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-#Make groups
-
-d_all <- d_all%>%
-  dplyr::mutate(depth = ifelse(pressure_insitu_ctd <=2, "1 m", 
-                        ifelse(pressure_insitu_ctd >2 & pressure_insitu_ctd <=4, "3 m", 
-                        ifelse(pressure_insitu_ctd >4 & pressure_insitu_ctd <=6, "5 m",
-                        ifelse(pressure_insitu_ctd >6 & pressure_insitu_ctd <=8, "7 m",
-                        ifelse(pressure_insitu_ctd >8, "9 m",NA))))))
 ```

### 2020-04-25 awipev-CO2.Rmd
lost of several data due to change with sal_insitu_ctd and temp_insitu_ctd with 1m/3m/5m/7m/9m

@@
   # variables passed through despike with "-filtered" have been renamed without sufix.
-  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, temp_sf = T_seaF)
+  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered, temp_sf = T_seaF)
 d_all <- d_hour #d_all will be the merger
@@
 ```{r Sal filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-#### filter salinities above 28
-d_all <- d_all%>%
-  dplyr::mutate( sal_fb = ifelse(sal_fb <28, NA, sal_fb),
-                 sal_insitu_ctd = ifelse(sal_insitu_ctd <28, NA, sal_insitu_ctd))
- d_all <- d_all%>%
-  dplyr::mutate(sal_insitu_ctd = ifelse(datetime > "2019-12-26 00:00:00", NA, sal_insitu_ctd))
 
@@
 d_all <- d_all %>%
-  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, 
-                               ifelse (pressure_insitu_ctd >=8 ,sal_insitu_ctd, NA )))
-### remove sal_mix data that seem to be to high compared to sal_fb
-  d_all <- d_all%>%
-  dplyr::mutate(sal_mix = ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-13 18:00:00" , NA, 
-                          ifelse(datetime > "2018-05-21 19:00:00" & datetime < "2018-05-24 17:00:00" , NA,
-                          ifelse(datetime > "2018-05-29 15:00:00" & datetime < "2018-06-03 13:00:00" , NA,
-                          ifelse(datetime > "2018-06-16 06:00:00" & datetime < "2018-06-21 05:00:00" , NA,
-                          ifelse(datetime > "2019-12-02 08:00:00" & datetime < "2019-12-03 08:00:00" , NA,
-                          ifelse(datetime > "2019-12-09 07:00:00" & datetime < "2019-12-09 10:00:00" , NA, 
-                          ifelse(datetime > "2019-12-09 15:00:00" & datetime < "2019-12-09 18:00:00" , NA,
-                          ifelse(datetime > "2019-12-10 14:00:00" & datetime < "2019-12-10 18:00:00", NA, sal_mix)))))))))
-
-### creation of column sal_insitu_sup_8m 
-   d_all <- d_all%>%
-     dplyr::mutate(sal_insitu_sup_8m = ifelse(pressure_insitu_ctd >=8, sal_insitu_ctd, NA))
+  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_9m))
+
+# ### remove sal_mix data that seem to be to high compared to sal_fb
+#   d_all <- d_all%>%
+#   dplyr::mutate(sal_mix = ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-13 18:00:00" , NA, 
+#                           ifelse(datetime > "2018-05-21 19:00:00" & datetime < "2018-05-24 17:00:00" , NA,
+#                           ifelse(datetime > "2018-05-29 15:00:00" & datetime < "2018-06-03 13:00:00" , NA,
+#                           ifelse(datetime > "2018-06-16 06:00:00" & datetime < "2018-06-21 05:00:00" , NA,
+#                           ifelse(datetime > "2019-12-02 08:00:00" & datetime < "2019-12-03 08:00:00" , NA,
+#                           ifelse(datetime > "2019-12-09 07:00:00" & datetime < "2019-12-09 10:00:00" , NA, 
+#                           ifelse(datetime > "2019-12-09 15:00:00" & datetime < "2019-12-09 18:00:00" , NA,
+#                           ifelse(datetime > "2019-12-10 14:00:00" & datetime < "2019-12-10 18:00:00", NA, sal_mix)))))))))
 
@@
 d_all <- d_all %>%
-  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, 
-                               ifelse (pressure_insitu_ctd >=8 ,temp_insitu_ctd, NA )))
-
-# qf added 
-d_all <- d_all %>% 
-  dplyr::mutate(
-    temp_fb_qf = ifelse(
-      State_Zero >= 1 | State_Flush >= 1 |
-        pco2_raw < 100 | pco2_raw > 450 |
-        Time >= "00:00:00" & Time <= "01:30:00" |
-        Time >= "12:00:00" & Time <= "13:00:00" |
-        datetime == "2017-03-22 08:00:00" ,
-      4,
-      1
-    ),
-    pco2_raw = ifelse(pco2_raw_qf == 4 , NA, pco2_raw),
-    pco2_corr_qf = ifelse(
-      State_Zero >= 1 | State_Flush >= 1 |
-        pco2_corr < 100 | pco2_corr > 450 |
-        Time >= "00:00:00" & Time <= "01:30:00" |
-        Time >= "12:00:00" & Time <= "13:00:00" |
-        datetime >= "2017-03-10 08:00:00" &
-        datetime < "2017-03-21 20:00:00",
-      4,
-      1
-    ),
-    pco2_corr = ifelse(pco2_corr_qf == 4 , NA, pco2_corr)
-  )
+  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_9m))
 ```
@@
 d_all$closest_datetime <- d_all$datetime
-d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, sal_insitu_ctd, temp_mix, temp_insitu_ctd, temp_insitu_11m, sal_mix )), by="closest_datetime")
+d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_mix, temp_insitu_11m, sal_mix )), by="closest_datetime")
 
@@
 pH_seafet <- d %>%
-  dplyr::filter(!is.na(pH_s_seafet) & !is.na(sal_insitu_ctd) & !is.na(temp_mix) )
+  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_mix) )
 pH_seafet <- pH_seafet %>%
@@
 #SAL CTD profile
-sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd)
+sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m)
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
 dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
-      dySeries("sal_insitu_ctd", color = "blue", strokeWidth = 0, label = "sal_insitu_ctd") %>%
+dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
+dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
+dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
+dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
+dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
 # TEMP insitu CTD
-temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd)
+temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m)
 temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
 dygraph(temp_insitu_xts, group = "awipev", main="Temperature (ctd all depths)", ylab="Temperature") %>%
-      dySeries("temp_insitu_ctd", color = "blue", strokeWidth = 0, label = "temp_insitu_ctd") %>%
+      dySeries("temp_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
+dySeries("temp_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
+dySeries("temp_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
+dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
+dySeries("temp_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
   dyAxis("y", valueRange = c(-2.8, 10)) %>%
@@
 
-### **Sal FB / Sal CTD > 8 m **
+### **Sal FB / Sal CTD 9 m **
 
@@
 
-fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)
+fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu_ctd_9m , nperm = 99)
 
 ```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  sal_fb ~ sal_insitu_ctd , nperm = 99)
+fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu_ctd_9m , nperm = 99)
 
@@
 
-p_sal_fb_ctd<-  ggplot(d_all%>%dplyr::filter(pressure_insitu_ctd >=8),aes(x=sal_insitu_ctd, y= sal_fb))+
+p_sal_fb_ctd<-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
   geom_point( aes(color=factor(month))) + 
@@
  #  scale_colour_discrete(guide="none") +
-  labs( x="Salinity CTD > 8 m", y="Salinity FB ", color = "Months") +theme_bw()
+  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") +theme_bw()
 
@@
 
-d_all$diff_sal_fb_insitu <- d_all$sal_insitu_ctd - d_all$sal_fb
-mean_diff_sal_fb_insitu <- round(mean(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)
-sd_diff_sal_fb_insitu <- round(sd(d_all$diff_sal_fb_insitu, na.rm = TRUE), digits = 2)
+d_all$diff_sal_fb_insitu_9m <- d_all$sal_insitu_ctd_9m - d_all$sal_fb
+mean_diff_sal_fb_insitu_9m <- round(mean(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
+sd_diff_sal_fb_insitu_9m <- round(sd(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
 
@@
 ```{r Sal plot, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-seafet_contros_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd, sal_fb, sal_mix)
-seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_contros_xts, group = "awipev", main="Salinities", ylab="PSU") %>%
-dySeries("sal_insitu_ctd", label = "sal_insitu_ctd", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-dySeries("sal_fb", label = "sal_fb", color ="blue",axis= "y2", strokeWidth=0, pointSize=4) %>%
-dySeries("sal_mix", label = "sal_mix", color ="orange",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#dySeries("pressure_insitu_ctd", label = "pressure_insitu_ctd", color ="black", strokeWidth=0, pointSize=2) %>%
-  dyLegend(show = "onmouseover")   %>%
-  #dyAxis( "y2",valueRange = c(-3, 36))%>%
-  #dyAxis( "y2",valueRange = c(25, 36))%>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+
+sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, sal_mix, sal_fb)
+sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
+dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
+dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
+dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
+dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
+dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
+dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
+  dySeries("sal_fb", color = "grey", strokeWidth = 0, label = "sal_fb") %>%
+
+dySeries("sal_mix", color = "black", strokeWidth = 0, label = "sal_mix") %>%
+
+      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
+      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+    dyLegend(show = "follow")   %>%
+    dyAxis("y",valueRange = c(30, 37)) %>%
       dyRangeSelector(height = 30, dateWindow= NULL)
@@
 
-The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu` ± `r sd_diff_sal_fb_insitu` PSU.
+The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu_9m` ± `r sd_diff_sal_fb_insitu_9m` PSU.
 
@@
 - 1 SBE45 inside the Ferrybox (temp_fb)
-- 5 CTD > 8 meters depth (temp_insitu_ctd)
+- 5 CTD profiling (temp_insitu_ctd_1m - 3m - 5m - 7m - 9m)
 - 1 fixed at 11 meters depth (temp_insitu_11m)
@@
 
-fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)
+fit <- lmodel2(data = d_all,  temp_insitu_11m ~ temp_insitu_ctd_9m , nperm = 99)
 
@@
 
-fit <- lmodel2(data = d_all%>%dplyr::filter(pressure_insitu_ctd >=8),  temp_insitu_11m ~ temp_insitu_ctd , nperm = 99)
-
-p<-  ggplot(d_all,aes(x=temp_insitu_ctd, y= temp_insitu_11m, label = month))+
+fit <- lmodel2(data = d_all,  temp_insitu_11m ~ temp_insitu_ctd_9m , nperm = 99)
+
+p<-  ggplot(d_all,aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("T CTD > 8 m vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
+  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
                      "; Intercept =", signif(fit$regression.results[2,2], 3),
@@
   coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
-  labs( x="T CTD > 8 m", y="T 11 m ", color = "Months")  +theme_bw()
+  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")  +theme_bw()
 print(p)
 
-d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd
+d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd_9m
 mean_diff_T_ctd_11m <- round(mean(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
@@
 calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix,
-                          calT = d_all$temp_insitu_ctd, calSal = d_all$sal_insitu_ctd )
+                          calT = d_all$temp_insitu_ctd_9m, calSal = d_all$sal_insitu_ctd_9m )
 # put number of deployment 
@@
 ####
-seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu_ctd, calSal = d_all$sal_insitu_ctd)
+seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu_ctd_9m, calSal = d_all$sal_insitu_ctd_9m)
 
@@
 
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_mix,pHint_tot_sf, pHint_tot_sf_filtered, pH_s_sf_no_calb)
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_mix,pHint_tot_sf, pH_s_sf_no_calb)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
@@
 dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 3) %>%
-dySeries("pHint_tot_sf_filtered", label = "pHint_tot_sf_filtered", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 2) %>%
 dySeries("ph_s_sf_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-
 dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
-
 dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
@@
             temp_mix_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
-            temp_ctd_max =round( max(temp_insitu_ctd, na.rm=TRUE), digits = 2),
-            temp_ctd_min = round(min(temp_insitu_ctd, na.rm=TRUE), digits = 2),
+            temp_ctd_1m_max =round( max(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
+            temp_ctd_1m_min = round(min(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
+            temp_ctd_3m_max =round( max(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
+            temp_ctd_3m_min = round(min(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
+            temp_ctd_5m_max =round( max(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
+            temp_ctd_5m_min = round(min(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
+            temp_ctd_7m_max =round( max(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
+            temp_ctd_7m_min = round(min(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
+            temp_ctd_9m_max =round( max(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
+            temp_ctd_9m_min = round(min(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
             temp_11m_max =round( max(temp_insitu_11m, na.rm=TRUE), digits = 2),
@@
             sal_mix_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
-            sal_ctd_max = round(max(sal_insitu_ctd, na.rm=TRUE), digits = 2),
-            sal_ctd_min = round(min(sal_insitu_ctd, na.rm=TRUE), digits = 2),
+            sal_ctd_1m_max =round( max(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
+            sal_ctd_1m_min = round(min(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
+            sal_ctd_3m_max =round( max(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
+            sal_ctd_3m_min = round(min(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
+            sal_ctd_5m_max =round( max(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
+            sal_ctd_5m_min = round(min(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
+            sal_ctd_7m_max =round( max(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
+            sal_ctd_7m_min = round(min(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
+            sal_ctd_9m_max =round( max(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
+            sal_ctd_9m_min = round(min(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
             sal_fb_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
@@
 pH_sf <- d_all %>%
-  dplyr::select(datetime, sal_insitu_ctd, temp_insitu_ctd, pHint_tot_sf)%>%
-  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd), !is.na(sal_insitu_ctd)) %>%
+  dplyr::select(datetime, sal_insitu_ctd_9m , temp_insitu_ctd_9m, pHint_tot_sf)%>%
+  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd_9m), !is.na(sal_insitu_ctd_9m)) %>%
   dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
-pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd, Pinsi=11/10, S=pH_sf$sal_insitu_ctd, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
@@
 pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pHint_tot_sf_norm4, label = month))+
-  geom_point( aes(color=factor(depth)), size =1, alpha=0.5) + 
-  facet_wrap( ~ factor(depth), ncol = 3) +
-  stat_smooth(data = d_all, aes(x = pH_durafet_norm4, y = pHint_tot_sf_norm4, color=depth),
-              method=lm, na.rm=TRUE, se=FALSE) +
+  geom_point( aes(color=factor(month)), size =1, alpha=0.5) + 
+  facet_wrap( ~ factor(month), ncol = 3) +
+  #stat_smooth(data = d_all, aes(x = pH_durafet_norm4, y = pHint_tot_sf_norm4, color=month),
+  #            method=lm, na.rm=TRUE, se=FALSE) +
  # scale_color_viridis_d(option = "C", guide="none")+
@@
   coord_fixed(ratio = 1 , xlim=c(7.8,8.35), ylim=c(7.8,8.35))+ #scale_colour_discrete(guide="none") +
-  labs( x="pH durafet, 4°C", y="pH seaFET, 4°C ", color = "Depth ")  +theme_bw()
+  labs( x="pH durafet, 4°C", y="pH seaFET, 4°C ", color = "Month ")  +theme_bw()
 
@@
 # SEAFET vs CALC
-fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pHint_tot_sf_norm4 , nperm = 99)
-
-psf_calc_norm_text <-  ggplot(d_all,aes(x=pHint_tot_sf_norm4, y= pH_calc_norm4, label = month))+
-  geom_text( aes(color=factor(month))) + 
-  scale_color_discrete(guide = "none")+
- geom_abline(slope=1, intercept =0, linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("pH calculated vs pH seaFET, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
-  labs(x="pH seaFET, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
-psf_calc_norm_text
+# fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pHint_tot_sf_norm4 , nperm = 99)
+# 
+# psf_calc_norm_text <-  ggplot(d_all,aes(x=pHint_tot_sf_norm4, y= pH_calc_norm4, label = month))+
+#   geom_text( aes(color=factor(month))) + 
+#   scale_color_discrete(guide = "none")+
+#  geom_abline(slope=1, intercept =0, linetype = "dashed") +
+#   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+#   labs(title = paste("pH calculated vs pH seaFET, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
+#                      "; Intercept =", signif(fit$regression.results[2,2], 3),
+#                      "; Slope =", signif( fit$regression.results[2,3], 3),
+#                      "; P =", signif(fit$P.param, 3))) +
+#   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+#     coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
+#   labs(x="pH seaFET, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
+# psf_calc_norm_text
 
@@
 # Spectro / seafet
-fit <- lmodel2(data = d_all,  ph_s_sf_temp_mix ~ pHint_tot_sf , nperm = 99)
-
-p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= ph_s_sf_temp_mix, label = month))+
-  geom_text( aes(color=factor(month))) + 
-  scale_color_discrete(guide = "none")+
- geom_abline(slope=1, intercept =0, linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("pH spectro vs pH seaFET","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-    coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
-  labs(x="pH seaFET", y="pH spectro, 4°C ", color = "Months") + theme_bw() 
-p_sf_spectro
+# fit <- lmodel2(data = d_all,  ph_s_sf_temp_mix ~ pHint_tot_sf , nperm = 99)
+# 
+# p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= ph_s_sf_temp_mix, label = month))+
+#   geom_text( aes(color=factor(month))) + 
+#   scale_color_discrete(guide = "none")+
+#  geom_abline(slope=1, intercept =0, linetype = "dashed") +
+#   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+#   labs(title = paste("pH spectro vs pH seaFET","\n Adj R2 = ", signif(fit$rsquare, 3),
+#                      "; Intercept =", signif(fit$regression.results[2,2], 3),
+#                      "; Slope =", signif( fit$regression.results[2,3], 3),
+#                      "; P =", signif(fit$P.param, 3))) +
+#   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+#     coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
+#   labs(x="pH seaFET", y="pH spectro, 4°C ", color = "Months") + theme_bw() 
+# p_sf_spectro
 ```
@@
 
-* temp_mix = temp 11m + temp ctd > 8m si trous.
-* sal_mix = sal FB + sal ctd > 8m si trous.
+* temp_mix = temp 11m + temp_insitu_ctd_9m si trous.
+* sal_mix = sal FB + sal_insitu_ctd_9m si trous.
 * ph_s_sf_temp_mix: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
@@
 * pco2_calc: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
-* Relation at / sal_mix (sal FB + sal ctd > 8m si trous)
+* Relation at / sal_mix 
 * at_calc: calculé from sal_mix
-* E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_mix (temp 11m + temp ctd > 8m si trous) + temp CTD + sal CTD (calib seaFET fonction 1)
+* E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_mix (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
 * phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)

### 2020-04-26 awipev-CO2.Rmd
fixed issues ph_dur

@@
 ```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
-d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour.rds"))
+d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
 # load = d_hour
@@
   # variables passed through despike with "-filtered" have been renamed without sufix.
-  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered, temp_sf = T_seaF)
+  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
 d_all <- d_hour #d_all will be the merger
@@
 
-### **seaFET calibration constante E0**
+### **seaFET calibration constant E0**
 
@@
 calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix,
-                          calT = d_all$temp_insitu_ctd_9m, calSal = d_all$sal_insitu_ctd_9m )
+                          calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd)
 # put number of deployment 
@@
 ####
-seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_insitu_ctd_9m, calSal = d_all$sal_insitu_ctd_9m)
+seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd)
 

### 2020-04-26 paper.Rmd
fixed issues ph_dur

@@
 
-d_all <- readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
+d_all <- readRDS(file = paste0(path_data, "fb_data/d_all_copy.rds"))
 d <- d_all %>% 
-  #dplyr::select
-  #dplyr::filter(sal_fb > 28) %>% # remove salinity data lower than 28
   as_tsibble(index = datetime) %>% 
   dplyr::arrange(datetime) %>%
-  dplyr::mutate(depth = as.numeric(str_remove(depth, pattern= " m"))) %>% #depth is a string
   fill_gaps() %>%
@@
   replace(., is.na(.), NA) # replace NaN by NA everywhere
+```
+
+```{r calculate missing, echo=FALSE, warning=FALSE, message=FALSE}
+
+var_list <- c("sal_fb", "temp_fb")
+n_na <- NULL
+for (i in 1:length(var)) {
+  na <- sum(!is.na([[i]]))
+  a
+}
+
+pc_na <- function(x=df) {
+  NAs <- as.tibble(map_df(x, function(x) sum(!is.na(x)))) %>% # number of NAs
+    dplyr::select(-datetime)
+  NAs <- as.data.frame(t(NAs))
+  n <- nrow(x) # total number of rows
+  pc_na <- n_na/n #fraction of NAs
+  NAs$pc <- pc_na$V1
+  return(NAs)
+}
 tmp <- d %>% 
@@
   dplyr::select(pH_s_seafet_temp_ctd, par_air_filtered, pco2_contros, pH_s_seafet_temp_ctd, starts_with("sal_"),
-                starts_with("temp_"), at_calc, year_month, quarter)
+                starts_with("temp_"), at_calc, year_month, quarter) %>%
+  summarize()
+
 tmp visdat::vis_miss(tmp)
 gg_miss_var(tmp, facet = quarter)
-```
-
-```{r calculate missing, echo=FALSE, warning=FALSE, message=FALSE}
 

### 2020-04-26 awipev-CO2.Rmd
AWIPEV-CO2 functional again but to be checked

@@
 pH_durafet <- d %>%
-  dplyr::filter(!is.na(pH_s_durafet))
+#  dplyr::filter(!is.na(pH_s_durafet))
+    dplyr::filter(!is.na(pH_s_durafet) & !is.na(sal_fb) & !is.na(temp_fb))
 pH_durafet <- pH_durafet %>%
-  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb,Pt=0,Sit=0))
+  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb, Pt=0, Sit=0))
 

### 2020-04-26 awipev-CO2.Rmd
added dygraph temperature profiles

@@
 
-Comparative approch allowed by following plots:
+### **Depth profile**
+
+```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+
+```
 
 ### **Sal FB / Sal CTD 9 m **
+
+```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
 
@@
 
-```{r Sal plot, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+```{r Sal plots, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
 
@@
 
+```{r temperature plots, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+
+temp_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m, temp_mix, temp_fb)
+temp_xts <- as.xts(temp_xts, order.by = temp_xts$datetime)
+dygraph(temp_xts, group = "awipev", main="Temperature profile (in situ CTD, all depths)", ylab="Temperature") %>%
+dySeries("temp_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
+dySeries("temp_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
+dySeries("temp_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
+dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
+dySeries("temp_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
+#dySeries("temp_fb", color = "grey", strokeWidth = 0, label = "temp_fb") %>%
+#dySeries("temp_mix", color = "black", strokeWidth = 0, label = "temp_mix") %>%
+      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
+      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+    dyLegend(show = "follow")   %>%
+    dyAxis("y",valueRange = c(-2, 10)) %>%
+      dyRangeSelector(height = 30, dateWindow= NULL)
+```
 ## Total alkalinity

### 2020-04-27 awipev-CO2.Rmd
daily diff in temp and sal between 1 and 9 m

--- 2020-04-26 awipev-CO2.Rmd
@@
 
-Comparative approch allowed by following plots:
+### **Depth profile**
+
+```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+df <- d_all %>% 
+  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
+  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
+  group_by(date) %>% 
+  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
+            mean9m = mean(sal_insitu_ctd_9m, na.rm = TRUE),
+            range = mean(sal_insitu_ctd_1m, na.rm = TRUE)-mean(sal_insitu_ctd_9m, na.rm = TRUE)) %>% 
+  ungroup()
+summary(df)
+```
+There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m).
+The salinity difference between 1 and 9 m ranges between `r min(df$range)` and `r max(df$range)` (mean: `r mean(df$range)`; `r median(df$range)`).
+The difference with depth is therefore significant.
 
@@
 
-Comparative approch allowed by following plots:
+### **Temperature profiles**
+```{r temperature profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+temp_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m)
+temp_xts <- as.xts(temp_xts, order.by = temp_xts$datetime)
+dygraph(temp_xts, group = "awipev", main="Temperature profile (in situ CTD, all depths)", ylab="Temperature") %>%
+dySeries("temp_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
+dySeries("temp_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
+dySeries("temp_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
+dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
+dySeries("temp_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
+#dySeries("temp_fb", color = "grey", strokeWidth = 0, label = "temp_fb") %>%
+#dySeries("temp_mix", color = "black", strokeWidth = 0, label = "temp_mix") %>%
+      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
+      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+    dyLegend(show = "follow")   %>%
+    dyAxis("y",valueRange = c(-2, 10)) %>%
+      dyRangeSelector(height = 30, dateWindow= NULL)
+
+df <- d_all %>% 
+  dplyr::select(datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m) %>%
+  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
+  group_by(date) %>% 
+  summarize(mean1m = mean(temp_insitu_ctd_1m, na.rm = TRUE),
+            mean9m = mean(temp_insitu_ctd_9m, na.rm = TRUE),
+            range = mean(temp_insitu_ctd_1m, na.rm = TRUE)-mean(temp_insitu_ctd_9m, na.rm = TRUE)) %>% 
+  ungroup()
+summary(df)
+```
+There are `r sum(!is.na(df$range))` days with temperature values at both 1 m (0-2 m) and 9 m (> 8 m).
+The temperature difference between 1 and 9 m ranges between `r min(df$range)`°C and `r max(df$range)`°C (mean: `r mean(df$range)`°C; `r median(df$range)`°C).
+The difference with depth is therefore significant.
 

### 2020-04-28 awipev-CO2.Rmd
Clean up

@@
 
+#################### Function RMSE root mean square error
+rmse <- function(error) { sqrt(mean(error^2)) }
+#rmse(fit$residuals)
+
 #################### Mytheme
@@
 
-# Add the flag location: some samples have been collected at the peer. Notes them here.
+# Add the flag location: some samples have been collected at the pier. Notes them here.
 # Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
@@
 d <- d%>%
-  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00"|datetime == "2019-05-31 11:45:00", 1,0)
+  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00"|datetime == "2019-05-31 11:45:00", 1, 0)
   )
@@
 
-# Mercury chloride correction (Dickson et al. 2007, SOP3a)
+# Mercuric chloride correction (Dickson et al. 2007, SOP3a)
 # AT
@@
 d_all$closest_datetime <- d_all$datetime
-d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_mix, temp_insitu_11m, sal_mix )), by="closest_datetime")
+d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_sf, temp_mix, temp_insitu_11m, sal_mix)), by="closest_datetime")
 
@@
 pH_seafet <- d %>%
-  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_mix) )
+  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_sf) )
 pH_seafet <- pH_seafet %>%
-  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_mix, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))
+  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_sf, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))
 
@@
 
-## Whole time series
-```{r whole time series, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-#SAL FB 
+## Salinities
+Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically.
+Salinity from FB is taken in consideration.
+If data gaps are encountered, they are filled with bottom salinty data from ctd (> 8 m).
+New column "sal_mix" is created.
+
+- 1 SBE45 inside the Ferrybox (sal_fb)
+- 5 CTD > 8 meters depth (sal_insitu_ctd)
+
+### **Depth profile**
+
+```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
 sal_xts <- dplyr::select(d_all, datetime, sal_fb)
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
-dygraph(sal_xts, group = "awipev", main="Salinity FerryBox)", ylab="Salinity") %>%
+dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
             dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
@@
       dyRangeSelector(height = 30, dateWindow= NULL)
+
+df <- d_all %>% 
+  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
+  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
+  group_by(date) %>% 
+  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
+            mean9m = mean(sal_insitu_ctd_9m, na.rm = TRUE),
+            range = mean(sal_insitu_ctd_1m, na.rm = TRUE)-mean(sal_insitu_ctd_9m, na.rm = TRUE)) %>% 
+  ungroup()
+```
+There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m).
+The salinity difference between 1 and 9 m ranges between `r min(df$range)` and `r max(df$range)` (mean: `r mean(df$range)`; `r median(df$range)`).
+The difference with depth is therefore significant.
+
+### **Sal FB / Sal CTD 9 m **
+
+Property-property salinity plot using:
+
+fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu_ctd_9m , nperm = 99)
+
+```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu_ctd_9m , nperm = 99)
+
+# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,sal_fb,sal_insitu_ctd)
+# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
+# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
+#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
+#   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
+#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
+#   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2)
+
+p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
+  geom_point( aes(color=factor(month))) + 
+ # scale_color_viridis_d(option = "C", guide="none")+
+  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
+  geom_abline(slope=1, intercept=0, linetype = "dashed")+
+  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
+  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
+                     "; Intercept =", signif(fit$regression.results[2,2], 3),
+                     "; Slope =", signif( fit$regression.results[2,3], 3),
+                     "; P =", signif(fit$P.param, 3))) +
+  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
+  coord_fixed(ratio = 1 )+
+ #  scale_colour_discrete(guide="none") +
+  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") +theme_bw()
+
+print(p) #p_sal_fb_ctd
+
+d_all$diff_sal_fb_insitu_9m <- d_all$sal_insitu_ctd_9m - d_all$sal_fb
+mean_diff_sal_fb_insitu_9m <- round(mean(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
+sd_diff_sal_fb_insitu_9m <- round(sd(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
+
+### Plotly
+# p_p_sal_fb_ctd <- ggplotly(p_sal_fb_ctd,dynamicTicks = TRUE)
+# filename.html <- paste0("p_p_sal_fb_ctd.html")
+# saveWidget(p_p_sal_fb_ctd, filename.html, selfcontained = T, libdir = "lib")
+
+# #Plot for philipp
+# sal_15 <- ggplot(data= d_all%>%dplyr::filter(datetime > "2015-10-01 00:00:00" & datetime < "2015-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
+# geom_point(aes(y=sal_fb,col="FB") , size=2) +
+# geom_point(aes(y=sal_insitu, col="in situ"))  +
+# labs(title=  "salinity 2015", x = "Time", y= "")
+# 
+# sal_19 <-ggplot(data= d_all%>%dplyr::filter(datetime > "2019-10-01 00:00:00" & datetime < "2019-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
+# geom_point(aes(y=sal_fb,col="FB") , size=2) +
+# geom_point(aes(y=sal_insitu, col="in situ"))  +
+# labs(title=  "salinity 2019", x = "Time", y= "")
+# 
+# ggsave("figures/sal_2019.png", sal_19, units="cm")
+# ggsave("figures/sal_2015.png", sal_15, units="cm")
+# ggsave("figures/sal_property.png", p_sal_fb_sal_insitu, units="cm")
+
+```
+
+```{r Sal plots, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+
+sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, sal_mix, sal_fb)
+sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
+dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
+dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
+dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
+dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
+dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
+dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
+  dySeries("sal_fb", color = "grey", strokeWidth = 0, label = "sal_fb") %>%
+
+dySeries("sal_mix", color = "black", strokeWidth = 0, label = "sal_mix") %>%
+
+      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
+      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+    dyLegend(show = "follow")   %>%
+    dyAxis("y",valueRange = c(30, 37)) %>%
+      dyRangeSelector(height = 30, dateWindow= NULL)
+```
+
+The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu_9m` ± `r sd_diff_sal_fb_insitu_9m` PSU.
+
+## Temperatures
+Several temperature sensors are on site, 1 inside the Ferrybox (SBE45), 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically and 1 fixed at 11 m depth (sbe38). 
+Temperature in situ at 11 m depth is taken in consideration.
+If data gaps are encountered, they are filled with bottom temperature data from ctd (> 8 m).
+New column "temp_mix" is created.
+For the moment, no gaps are encountered and temp_mix = temp_insitu_11m.
+
+- 1 SBE45 inside the Ferrybox (temp_fb)
+- 5 CTD profiling (temp_insitu_ctd_1m - 3m - 5m - 7m - 9m)
+- 1 fixed at 11 meters depth (temp_insitu_11m)
+
+```{r temperature time series, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
 # TEMP Ferrybox SBE45
@@
       dyRangeSelector(height = 30, dateWindow= NULL)
-# TEMP insitu CTD
-temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m)
-temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
-dygraph(temp_insitu_xts, group = "awipev", main="Temperature (ctd all depths)", ylab="Temperature") %>%
-      dySeries("temp_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
-dySeries("temp_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
-dySeries("temp_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
-dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
-dySeries("temp_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
-  dyAxis("y", valueRange = c(-2.8, 10)) %>%
-      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-      dyLegend(show = "follow")   %>%
-      dyRangeSelector(height = 30, dateWindow= NULL)
-# PCO2 
-#+ Ajout de la pCO2 corrigé par le script contros (dans R server ny-alesund_cc.R)
-pco2_contros_xts <- dplyr::select(d_all, datetime, pco2_calc, pco2_corr)
-pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
-dygraph(pco2_contros_xts, group = "awipev", main="pCO2", ylab="pCO2") %>%
-    dySeries("pco2_corr", label="Corrected pCO2", color=  "blue",strokeWidth=0, pointSize=2) %>%
-    dySeries("pco2_calc", label="calculated pCO2",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
-    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2019-09-03 15:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
-    #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
-    dyLegend(show = "follow")   %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-# # DURAFET 
-# durafet_contros_xts <- dplyr::select(d_all, datetime, ph_dur, ph_s_dur_temp_fb)
-# durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
-# dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
-#     dySeries("ph_dur", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-#     dySeries("ph_s_dur_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-#     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
-#     dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
-#     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-#     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-#     dyAxis("y",valueRange = c(8, 8.8)) %>%
-#     dyLegend(show = "follow")   %>%
-#     dyRangeSelector(height = 30, dateWindow= NULL) 
-# # SEAFET 
-# seafet_contros_xts <- dplyr::select(d_all, datetime, phINT,ph_s_sf_temp_mix)
-# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ T CTD)", ylab="pHT") %>%
-#   dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>%
-#   dySeries("ph_s_sf_temp_mix", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-#   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-#   dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
-#   dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-#     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-#     dyAxis("y",valueRange = c(7.45, 8.8)) %>%
-#     dyLegend(show = "follow")   %>%
-#     dyRangeSelector(height = 30, dateWindow= NULL) 
-# # TA
-# # to create periods according to TA deployments
-TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
-              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00", "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
-
-# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at)
-# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
-# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
-#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
-#   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
-#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
-#   dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>%
-#   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% 
-#   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
-#   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-#   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
-#   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-#   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-#   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-#   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% 
-#   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-#   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
-#   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-#   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
-#   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
-#   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-#   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-#   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
-#   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-#   dyAxis("y",valueRange = c(2000, 2650)) %>%
-#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#   dyOptions( strokeWidth= 0) %>%
-#   dyLegend(show = "follow")   %>%
-#   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-#     dyRangeSelector(height = 30, dateWindow= NULL) 
-#  
-f <- as.data.frame(table(d_all$at))
-#sum(f$Freq)  
-# Number of outliers removed in the dataset
-# numberOutliers <- length(which((dat_ATnoNA$outliers > 0)))
-
-# #plot for POSTER june 2019
-# #plot of S/T
-# poster_temp <- ggplot(data = d_all%>%dplyr::filter(temp_fb<10 &sal>30 )) + geom_point(aes(x=datetime,y=temp_fb),col="blue", size=0.5) +
-#   geom_point(aes(x=datetime,y=sal/5),col="red", size=0.5 )+
-#   labs(x = "Time", y="Temperature (°C)") +
-#   scale_x_datetime(date_minor_breaks ="1 month")+
-#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())+
-#   scale_y_continuous(sec.axis = sec_axis(~.*5, name = "Salinity"))
-# print(poster_temp)
-# #
-# png("figures/poster_sal_temp.png", width= 1100, height=600)
-# par(mar=c(5, 4, 4, 6) + 0.1)
-# #
-# plot(sal ~ datetime,d_all,pch=16, axes=T, ylim=c(30.5,36), cex=0.5, col="red", ylab="", xlab="", yaxt ="n", lty=1, cex.axis=1.8) +
-# axis(2, ylim=c(0,1),col="red",col.axis="red", las = 1,lty=1, cex.axis =1.8)
-# #
-#    grid(lty=1)
-# #
-#    par(new = T)
-# #
-# plot(as.Date(d_all$datetime,"%Y-%m-d %H:%M:%S", tz= "UTC"), d_all$temp_fb, col="blue", pch=16, cex=0.5, xlab="", ylab="",xaxt="n", axes=FALSE,ylim=c(-2,9))+
-# axis(side = 4, col="blue",col.axis="blue",las=1, cex.axis =1.8) +
-# mtext("",side=1,col="black",line=1.5, cex=1.8)
-# legend("topleft", legend=c("Temperature (°C)", "Salinity"),
-#        col = c("blue", "red"), pch  = c(16, 16),  box.lty=0 , cex = 2)
-#   grid(nx = 1, ny = NULL, col = "lightgray", lty = 1,
-#     lwd = "months")
-#      box()
-#      dev.off()
-# 
-# 
-# ggsave(paste0("figures/poster_temp.png"), width= 30, height=10, poster_temp, units="cm")
-# #
-# poster_sal <- ggplot(data = d_all%>%dplyr::filter(sal>30 ), aes(x=datetime,y=sal), colour="sal") +
-#   geom_point(col="blue", size=0.5 )+
-#   labs(x = "Time", y="Salinity (PSU)") +
-#   scale_x_datetime(date_minor_breaks ="1 month")+
-#   theme_bw() + theme(legend.position="bottom",legend.title = element_blank())
-# print(poster_sal)
-# ggsave(paste0("figures/poster_sal.png"), width= 30, height=10, poster_sal, units="cm")
-
-```
-
-## Salinities
-Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically.
-Salinity from FB is taken in consideration.
-If data gaps are encountered, they are filled with bottom salinty data from ctd (> 8 m).
-New column "sal_mix" is created.
-
-- 1 SBE45 inside the Ferrybox (sal_fb)
-- 5 CTD > 8 meters depth (sal_insitu_ctd)
-
-### **Depth profile**
-
-```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-df <- d_all %>% 
-  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
-  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
-  group_by(date) %>% 
-  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
-            mean9m = mean(sal_insitu_ctd_9m, na.rm = TRUE),
-            range = mean(sal_insitu_ctd_1m, na.rm = TRUE)-mean(sal_insitu_ctd_9m, na.rm = TRUE)) %>% 
-  ungroup()
-summary(df)
-```
-There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m).
-The salinity difference between 1 and 9 m ranges between `r min(df$range)` and `r max(df$range)` (mean: `r mean(df$range)`; `r median(df$range)`).
-The difference with depth is therefore significant.
-
-### **Sal FB / Sal CTD 9 m **
-
-Property-property salinity plot using:
-
-fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu_ctd_9m , nperm = 99)
-
-```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu_ctd_9m , nperm = 99)
-
-# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,sal_fb,sal_insitu_ctd)
-# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
-# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
-#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
-#   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
-#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
-#   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2)
-
-p_sal_fb_ctd<-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
-  geom_point( aes(color=factor(month))) + 
- # scale_color_viridis_d(option = "C", guide="none")+
-  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
-  geom_abline(slope=1, intercept=0, linetype = "dashed")+
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
-  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
-  coord_fixed(ratio = 1 )+
- #  scale_colour_discrete(guide="none") +
-  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") +theme_bw()
-
-print(p_sal_fb_ctd)
-
-d_all$diff_sal_fb_insitu_9m <- d_all$sal_insitu_ctd_9m - d_all$sal_fb
-mean_diff_sal_fb_insitu_9m <- round(mean(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
-sd_diff_sal_fb_insitu_9m <- round(sd(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
-
-### Plotly
-# p_p_sal_fb_ctd <- ggplotly(p_sal_fb_ctd,dynamicTicks = TRUE)
-# filename.html <- paste0("p_p_sal_fb_ctd.html")
-# saveWidget(p_p_sal_fb_ctd, filename.html, selfcontained = T, libdir = "lib")
-
-# #Plot for philipp
-# sal_15 <- ggplot(data= d_all%>%dplyr::filter(datetime > "2015-10-01 00:00:00" & datetime < "2015-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
-# geom_point(aes(y=sal_fb,col="FB") , size=2) +
-# geom_point(aes(y=sal_insitu, col="in situ"))  +
-# labs(title=  "salinity 2015", x = "Time", y= "")
-# 
-# sal_19 <-ggplot(data= d_all%>%dplyr::filter(datetime > "2019-10-01 00:00:00" & datetime < "2019-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
-# geom_point(aes(y=sal_fb,col="FB") , size=2) +
-# geom_point(aes(y=sal_insitu, col="in situ"))  +
-# labs(title=  "salinity 2019", x = "Time", y= "")
-# 
-# ggsave("figures/sal_2019.png", sal_19, units="cm")
-# ggsave("figures/sal_2015.png", sal_15, units="cm")
-# ggsave("figures/sal_property.png", p_sal_fb_sal_insitu, units="cm")
-
-```
-
-```{r Sal plots, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-
-sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, sal_mix, sal_fb)
-sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
-dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
-dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
-dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
-dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
-dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
-dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
-  dySeries("sal_fb", color = "grey", strokeWidth = 0, label = "sal_fb") %>%
-
-dySeries("sal_mix", color = "black", strokeWidth = 0, label = "sal_mix") %>%
-
-      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
-      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-    dyLegend(show = "follow")   %>%
-    dyAxis("y",valueRange = c(30, 37)) %>%
-      dyRangeSelector(height = 30, dateWindow= NULL)
-```
-
-The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu_9m` ± `r sd_diff_sal_fb_insitu_9m` PSU.
-
-## Temperatures
-Several temperature sensors are on site, 1 inside the Ferrybox (SBE45), 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically and 1 fixed at 11 m depth (sbe38). 
-Temperature in situ at 11 m depth is taken in consideration.
-If data gaps are encountered, they are filled with bottom temperature data from ctd (> 8 m).
-New column "temp_mix" is created.
-For the moment, no gaps are encountered and temp_mix = temp_insitu_11m.
-
-- 1 SBE45 inside the Ferrybox (temp_fb)
-- 5 CTD profiling (temp_insitu_ctd_1m - 3m - 5m - 7m - 9m)
-- 1 fixed at 11 meters depth (temp_insitu_11m)
+```
 
@@
 
-p_temp_11_fb<-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
+p <-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
   labs( x="T 11 m", y="T FB ", color = "Months")  +theme_bw()
-print(p_temp_11_fb)
+print(p) # p_temp_11_fb
 
@@
   #print(at_s)
-
-ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")
+#ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")
 
@@
 ```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
+TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
+              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00", "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
 at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, at)
@@
 
-# #plot for POSTER june 2019
-# #plot of TA calculated from S + discrete
-# p_at_sal <- ggplot(data = d_all%>%dplyr::filter(at_calc > 2000), aes(x=datetime,y=at_calc,col="TA calculated from salinity") ) +
-#   geom_point(col="blue", size=0.5 )+
-#   geom_point(aes(y=at, fill= "Discrete measurements"), col="red") +
-#   labs(title=  "Calculated from salinity (µmol/kg)", x = "", y= "") + ylim(2100,2350)+
-#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-#   theme(legend.position= c(0.5, 0.93),
-#                      legend.text=element_text(size=15),
-#                      plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin(t = 9, b = -25)),
-#                      axis.text=element_text(size=15),
-#                      axis.title.x= element_text(size =15),
-#                      legend.title=element_blank())
-#
-#
-# print(p_at_sal)
-# ggsave(paste0("figures/poster_at_sal.png"), width= 30, height=10, p_at_sal, units="cm")
-
 ```
@@
 
-pco2_calc_pco2_corr_text <-  ggplot(d_all,aes(x=pco2_calc, y= pco2_corr, label = month))+
+p <-  ggplot(d_all,aes(x=pco2_calc, y= pco2_corr, label = month))+
    geom_text(aes(color = factor(month)))+
@@
   labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()  
-
 ```
@@
 ```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-print(pco2_calc_pco2_corr_text)
-ggsave(paste0("figures/pco2_calc_pco2_corr.png"), pco2_calc_pco2_corr_text, units="cm")
+print(p) # pco2_calc_pco2_corr_text
+#ggsave(paste0("figures/pco2_calc_pco2_corr.png"), pco2_calc_pco2_corr_text, units="cm")
 ```
@@
 ```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-pco2_contros_xts <- dplyr::select(d_all, datetime, pco2_calc, pco2_corr)
-pco2_contros_xts <- as.xts(pco2_contros_xts, order.by = d_all$datetime)
-dygraph(pco2_contros_xts, group = "awipev", main="<i>p</i>CO<sub>2</sub>", ylab="<i>p</i>CO<sub>2</sub>") %>%
-  dySeries("pco2_corr", label="Corrected pCO2", color=  RColorBrewer::brewer.pal(3, "Dark2")[1],strokeWidth=0, pointSize=2) %>%
+pco2_contros_xts <-
+  dplyr::select(d_all, datetime, pco2_calc, pco2_corr)
+pco2_contros_xts <-
+  as.xts(pco2_contros_xts, order.by = d_all$datetime)
+dygraph(pco2_contros_xts,
+        group = "awipev",
+        main = "<i>p</i>CO<sub>2</sub>",
+        ylab = "<i>p</i>CO<sub>2</sub>") %>%
+  dySeries(
+    "pco2_corr",
+    label = "Corrected pCO2",
+    color =  RColorBrewer::brewer.pal(3, "Dark2")[1],
+    strokeWidth = 0,
+    pointSize = 2
+  ) %>%
   #dySeries("pco2_raw", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
-    dySeries("pco2_calc", label="pco2_calc",color = "red", strokeWidth = 0, pointSize = 4 ) %>%
-    dyEvent(as.POSIXct("2016-02-28 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2017-02-07 12:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2018-04-16 12:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2018-10-31 15:00:00", tz="GMT"), "CO2FT-0215-001 installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2019-09-03 15:00:00", tz="GMT"), "CO2FT-0515-001 installed", labelLoc = "bottom", color="red") %>%
-
-    #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dySeries(
+    "pco2_calc",
+    label = "pco2_calc",
+    color = "red",
+    strokeWidth = 0,
+    pointSize = 4
+  ) %>%
+  dyEvent(
+    as.POSIXct("2016-02-28 12:00:00", tz = "GMT"),
+    "CO2FT-0515-001 installed",
+    labelLoc = "bottom",
+    color = "red"
+  ) %>%
+  dyEvent(
+    as.POSIXct("2017-02-07 12:00:00", tz = "GMT"),
+    "CO2FT-0215-001 installed",
+    labelLoc = "bottom",
+    color = "red"
+  ) %>%
+  dyEvent(
+    as.POSIXct("2018-04-16 12:00:00", tz = "GMT"),
+    "CO2FT-0515-001 installed",
+    labelLoc = "bottom",
+    color = "red"
+  ) %>%
+  dyEvent(
+    as.POSIXct("2018-10-31 15:00:00", tz = "GMT"),
+    "CO2FT-0215-001 installed",
+    labelLoc = "bottom",
+    color = "red"
+  ) %>%
+  dyEvent(
+    as.POSIXct("2019-09-03 15:00:00", tz = "GMT"),
+    "CO2FT-0515-001 installed",
+    labelLoc = "bottom",
+    color = "red"
+  ) %>%
+  dyHighlight(
+    highlightCircleSize = 8,
+    highlightSeriesBackgroundAlpha = 0.5,
+    hideOnMouseOut = TRUE
+  ) %>%
   dyLegend(show = "follow")   %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-# #plot for POSTER june 2019
-# #plot of pCO2
-# 
-# #  add pCO2 atmospheric data from URL
-# 
-# noaa <- read.csv("pco2_noaa.txt", header=T, sep ="", dec=".", stringsAsFactors = FALSE)
-# noaa <- noaa %>%
-#   dplyr::select(sample_year, sample_month, sample_day, sample_hour, sample_minute, sample_seconds, analysis_value, analysis_uncertainty) %>%
-#   unite("date", c("sample_year", "sample_month", "sample_day"), sep="-")%>%
-#   unite("time", c("sample_hour", "sample_minute", "sample_seconds"), sep=":") %>%
-#   unite("datetime", c("date", "time"), sep=" ")
-# 
-# noaa$datetime <- ymd_hms(noaa$datetime, tz="UTC")
-# noaa <- noaa %>%
-#  dplyr::filter(datetime > "2015-07-01 00:00:00")
-# 
-# #create a lab expression for pCO2 NOAA data lebel. Include it with scale_shape_discrete(labels=lab)
-# lab <- c( expression(paste(italic(p),CO[2]," (µatm)")),
-#           expression(paste(italic(p),CO[2]," (ppm; from NOAA)")),
-#            "Calculated from AT/CT"
-# 
-#           )
-# 
-# col <- c("blue","black","red")
-# 
-# poster_pco2 <- ggplot( ) +
-#   geom_point(data=d_all%>%dplyr::filter(pco2_contros > 150 & pco2_contros < 410), aes(x=datetime, y= pco2_contros, shape ="lab", colour="blue"),size=0.5 ) +
-#   geom_point(data=d_all, aes(x=datetime, y=pco2_calc, shape="lab" , color= "red"))+
-#   geom_point() + geom_point(data=noaa%>%dplyr::filter(analysis_value > 150), aes(x=datetime, y= analysis_value, shape="lab", color ="col" ),size=0.5)+
-#   scale_shape_discrete(labels=lab, guide="none")+
-#   scale_colour_manual(labels=lab, values=col)+
-#   labs(x = "", y ="", title = "") +
-#   theme_bw() +
-#   scale_x_datetime(minor_breaks  = "1 month ")+
-#   theme(legend.position="top",  #c(0.18, 0.85)
-#                      legend.text=element_text(size=14, colour="black"),
-#                      #plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -30)),
-#                      axis.text=element_text(size=15),
-#                      plot.margin = unit(c(0.5,1,1,1), "cm"),
-#                      axis.title.x= element_text(size =15),
-#                      legend.title=element_blank()
-#                      )
-# print(poster_pco2)
-#   ggsave(paste0("figures/poster_pco2.png"), width= 30, height=10, poster_pco2, units="cm")
-
+  dyOptions(
+    drawGrid = TRUE,
+    drawPoints = TRUE,
+    pointSize = c(1, 8, 1),
+    useDataTimezone = TRUE
+  ) %>%
+  dyRangeSelector(height = 30, dateWindow = NULL)
 ```
@@
 calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix,
-                          calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd)
+                          calT = d_all$temp_sf, calSal = d_all$sal_mix_interp)
 # put number of deployment 
@@
 
-```{r seaFET pH calculation sf_calc, echo=FALSE,message= FALSE, warning=FALSE}
+```{r seaFET pH calculation sf_calc, echo=FALSE, message= FALSE, warning=FALSE}
 ####
@@
 ####
-seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd)
+seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_mix_interp)
 
@@
 d_all <- d_all%>%
-  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 10:00:00" | datetime == "2019-01-18 11:00:00", ph_s_sf_temp_mix, NA ))
-
-# p <- ggplot(d_all%>%filter(datetime >= ("2017-07-30") & !is.na(depth) ),aes(x=datetime, y= phINT, label = depth))+
-#   geom_point( aes(color=factor(depth)), size=1, alpha=0.5, na.rm=TRUE)
+  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 10:00:00" | datetime == "2019-01-18 11:00:00", ph_s_sf_temp_mix, NA))
+
+p <- ggplot(d_all, aes(x=datetime, y= pHint_tot_sf))+
+  geom_point(size=1, alpha=0.5, na.rm=TRUE)
 
@@
 
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_mix,pHint_tot_sf, pH_s_sf_no_calb)
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_mix, pHint_tot_sf, pH_s_sf_no_calb)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
@@
 size_point <- 0.4 #size of data points
-plot_range_sf <-  
+p <-  
   ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
@@
   theme(panel.grid.major.x = element_blank())
-print(plot_range_sf)
-ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
+print(p) # plot_range_sf
+#ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
 
@@
 size_point <- 0.4 # size of data points
-plot_range_dur <-
+p <-
   ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
@@
   theme(panel.grid.major.x = element_blank())
-print(plot_range_dur)
-ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
+print(p) # plot_range_dur
+#ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
 ```
@@
 
-### **Spectro / seaFET**
+<!-- ### **Spectro / seaFET** -->
 
@@
 p_ct_ts
-ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
-ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
+#ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
+#ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
 ```

### 2020-04-28 awipev-CO2.Rmd
fixed issues with ranges in S and Tprofile

@@
 There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m).
-The salinity difference between 1 and 9 m ranges between `r min(df$range)` and `r max(df$range)` (mean: `r mean(df$range)`; `r median(df$range)`).
+The salinity difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)` and `r max(df$range, na.rm=TRUE)` (mean: `r mean(df$range, na.rm=TRUE)`; `r median(df$range, na.rm=TRUE)`).
 The difference with depth is therefore significant.
@@
 There are `r sum(!is.na(df$range))` days with temperature values at both 1 m (0-2 m) and 9 m (> 8 m).
-The temperature difference between 1 and 9 m ranges between `r min(df$range)`°C and `r max(df$range)`°C (mean: `r mean(df$range)`°C; `r median(df$range)`°C).
+The temperature difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)`°C and `r max(df$range, na.rm=TRUE)`°C (mean: `r mean(df$range, na.rm=TRUE)`°C; `r median(df$range, na.rm=TRUE)`°C).
 The difference with depth is therefore significant.

### 2020-04-28 awipev-CO2.Rmd
removed duplicate salinity graph

@@
 sd_diff_sal_fb_insitu_9m <- round(sd(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
-
-### Plotly
-# p_p_sal_fb_ctd <- ggplotly(p_sal_fb_ctd,dynamicTicks = TRUE)
-# filename.html <- paste0("p_p_sal_fb_ctd.html")
-# saveWidget(p_p_sal_fb_ctd, filename.html, selfcontained = T, libdir = "lib")
-
-# #Plot for philipp
-# sal_15 <- ggplot(data= d_all%>%dplyr::filter(datetime > "2015-10-01 00:00:00" & datetime < "2015-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
-# geom_point(aes(y=sal_fb,col="FB") , size=2) +
-# geom_point(aes(y=sal_insitu, col="in situ"))  +
-# labs(title=  "salinity 2015", x = "Time", y= "")
-# 
-# sal_19 <-ggplot(data= d_all%>%dplyr::filter(datetime > "2019-10-01 00:00:00" & datetime < "2019-12-31 00:00:00"), aes(x=datetime,  colour = "salinity"))+ 
-# geom_point(aes(y=sal_fb,col="FB") , size=2) +
-# geom_point(aes(y=sal_insitu, col="in situ"))  +
-# labs(title=  "salinity 2019", x = "Time", y= "")
-# 
-# ggsave("figures/sal_2019.png", sal_19, units="cm")
-# ggsave("figures/sal_2015.png", sal_15, units="cm")
-# ggsave("figures/sal_property.png", p_sal_fb_sal_insitu, units="cm")
-
-```
-
-```{r Sal plots, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-
-sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, sal_mix, sal_fb)
-sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
-dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
-dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
-dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
-dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
-dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
-dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
-  dySeries("sal_fb", color = "grey", strokeWidth = 0, label = "sal_fb") %>%
-
-dySeries("sal_mix", color = "black", strokeWidth = 0, label = "sal_mix") %>%
-
-      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
-      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-    dyLegend(show = "follow")   %>%
-    dyAxis("y",valueRange = c(30, 37)) %>%
-      dyRangeSelector(height = 30, dateWindow= NULL)
 ```

### 2020-04-29 awipev-CO2.Rmd
Blabla

@@
 ```
-
+#blabla
 ```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}

### 2020-04-29 awipev-CO2.Rmd

@@
 ```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-###### Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix ####### 
+# Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix 
 d_all <- d_all %>%
@@
 d_all$closest_datetime <- d_all$datetime
-d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_sf, temp_mix, temp_insitu_11m, sal_mix)), by="closest_datetime")
+d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_mix, sal_mix, temp_insitu_ctd)), by="closest_datetime")
 
@@
 pH_seafet <- d %>%
-  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_sf) )
+  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd) )
 pH_seafet <- pH_seafet %>%
-  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_sf, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))
+  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_insitu_ctd, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))
 
@@
 
-# create separate seafet/durafet df to join to initial "d" df
+# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
 pH_seafet_mean <- pH_seafet%>%
@@
 at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
-dygraph(at_contros_calc_xts, group = "awipev", main="TA + TA calc from sal_mix + TA reference", ylab="Total alkalinity") %>%
+dygraph(at_contros_calc_xts, group = "awipev", main="TA, calculated from sal_mix (blue) and reference (red)", ylab="Total alkalinity") %>%
   #dySeries("AT", label= "Raw TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
@@
 
+pco2_contros_xts <-
+  dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_mix)
+pco2_contros_xts <-
+  as.xts(pco2_contros_xts, order.by = d_all$datetime)
+dygraph(pco2_contros_xts,
+        group = "awipev",
+        main = "<i>p</i>CO<sub>2</sub>",
+        ylab = "<i>p</i>CO<sub>2</sub>") %>%
+  dySeries(
+    axis = "y2",
+    "voltINT",
+    label = "voltINT",
+    color =  RColorBrewer::brewer.pal(5, "Dark2")[1],
+    strokeWidth = 0,
+    pointSize = 2
+  ) %>%
+  dySeries(axis="y2",
+    "voltEXT",
+    label = "voltEXT",
+    color =  RColorBrewer::brewer.pal(5, "Dark2")[2],
+    strokeWidth = 0,
+    pointSize = 2
+  ) %>%
+   dySeries(
+    "temp_insitu_ctd",
+    label = "temp_insitu_ctd",
+    color =  RColorBrewer::brewer.pal(5, "Dark2")[3],
+    strokeWidth = 0,
+    pointSize = 2
+  ) %>%
+   dySeries(
+    "sal_fb",
+    label = "sal_fb",
+    color =  RColorBrewer::brewer.pal(5, "Dark2")[4],
+    strokeWidth = 0,
+    pointSize = 2
+  ) %>%
+   dySeries(
+    "ph_s_sf_temp_mix",
+    label = "ph_s_sf_temp_mix",
+    color =  RColorBrewer::brewer.pal(5, "Dark2")[5],
+    strokeWidth = 0,
+    pointSize = 4
+  ) %>%
+  dyHighlight(
+    highlightCircleSize = 8,
+    highlightSeriesBackgroundAlpha = 0.5,
+    hideOnMouseOut = TRUE
+  ) %>%
+  dyLegend(show = "follow")   %>%
+  dyAxis("y2",valueRange = c(-2,2))%>%
+  dyOptions(
+    drawGrid = TRUE,
+    drawPoints = TRUE,
+    pointSize = c(1, 8, 1),
+    useDataTimezone = TRUE
+  ) %>%
+  dyRangeSelector(height = 30, dateWindow = NULL)
 # To make sf calibration against pH spectro, we need: sal - T insi - voltINT/EXT . If we missed one of these parameters, calibration will not run
@@
 
-# period 1, mean of 4 next hours for volt int + T seaF
+#periode 1, mean of 4 next hours for volt int + T seaF
 mean_voltINT_4h <- d_all%>%
@@
 
-# period 1 also, mean of 4 next hours for volt int + T seaF
+# Periode 2, mean of 4 next hours for volt int + T seaF
 mean_voltINT_4h <- d_all%>%
@@
 
-# period 03, mean of 4 previous hours for volt int + T seaF
+# period 03, mean of 4 previous hours for volt int + volt ext
 mean_voltINT_4h <- d_all%>%
@@
 
-# period 03 also, mean of 4 previous hours for volt int + T seaF
+# period 04 also, mean of 4 previous hours for volt int + volt ext + T seaF
 mean_voltINT_4h <- d_all%>%
@@
 ####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix,
-                          calT = d_all$temp_sf, calSal = d_all$sal_mix_interp)
+calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix, calT = d_all$temp_sf, calSal = d_all$sal_mix_interp)
 # put number of deployment 

### 2020-04-29 awipev-CO2.Rmd
added chunk availability of data

--- 2020-04-28 awipev-CO2.Rmd
@@
 TO DO: add here an horizontal bar plot showing the percent availability of the data
+
+```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+selected_nydata_minute <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_minute.rds")) %>%
+  dplyr::select(ends_with("_qf")) #%>%
+s1 <- summary(as.factor(selected_nydata_minute$pco2_corr_qf))*100/length(selected_nydata_minute$pco2_raw_qf)
+s2 <- summary(as.factor(selected_nydata_minute$sal_fb_qf))*100/length(selected_nydata_minute$sal_fb_qf)
+s3 <- summary(as.factor(selected_nydata_minute$sal_insitu_ctd_qf))*100/length(selected_nydata_minute$sal_insitu_ctd_qf)
+s4 <- summary(as.factor(selected_nydata_minute$temp_dur_qf))*100/length(selected_nydata_minute$temp_dur_qf)
+s5 <- summary(as.factor(selected_nydata_minute$temp_fb_qf))*100/length(selected_nydata_minute$temp_fb_qf)
+s6 <- summary(as.factor(selected_nydata_minute$temp_insitu_11m_qf))*100/length(selected_nydata_minute$temp_insitu_11m_qf)
+s7 <- summary(as.factor(selected_nydata_minute$phINT_qf))*100/length(selected_nydata_minute$phINT_qf)
+s8 <- summary(as.factor(selected_nydata_minute$phEXT_qf))*100/length(selected_nydata_minute$phEXT_qf)
+qflags <- tibble(pco2_corr = s1,
+                 sal_fb = s2,
+                 sal_insitu_ctd = s3,
+                 temp_dur = s4,
+                 temp_fb = s5,
+                 temp_insitu_11m = s6,
+                 phINT = s7,
+                 phEXT = s8)
+
+  summarise_all(percentcumsum)
+  dplyr::mutate_all(funs("percent"= cumsum(.)/100))
+p <-  ggplot(data = selected_nydata_minute) +
+  geom_bar(aes(x = as.factor(pco2_corr_qf)))
+p
+rm(selected_nydata_minute)
+```
 

### 2020-04-29 awipev-CO2.Rmd

--- 2020-04-29 awipev-CO2.Rmd
@@
 ```
-#blabla
+
 ```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}

### 2020-05-01 awipev-CO2.Rmd
Completed and reformatted info in tab 'Villefranche" server

@@
   dplyr::select(ends_with("_qf")) #%>%
-s1 <- summary(as.factor(selected_nydata_minute$pco2_corr_qf))*100/length(selected_nydata_minute$pco2_raw_qf)
-s2 <- summary(as.factor(selected_nydata_minute$sal_fb_qf))*100/length(selected_nydata_minute$sal_fb_qf)
-s3 <- summary(as.factor(selected_nydata_minute$sal_insitu_ctd_qf))*100/length(selected_nydata_minute$sal_insitu_ctd_qf)
-s4 <- summary(as.factor(selected_nydata_minute$temp_dur_qf))*100/length(selected_nydata_minute$temp_dur_qf)
-s5 <- summary(as.factor(selected_nydata_minute$temp_fb_qf))*100/length(selected_nydata_minute$temp_fb_qf)
-s6 <- summary(as.factor(selected_nydata_minute$temp_insitu_11m_qf))*100/length(selected_nydata_minute$temp_insitu_11m_qf)
-s7 <- summary(as.factor(selected_nydata_minute$phINT_qf))*100/length(selected_nydata_minute$phINT_qf)
-s8 <- summary(as.factor(selected_nydata_minute$phEXT_qf))*100/length(selected_nydata_minute$phEXT_qf)
-qflags <- tibble(pco2_corr = s1,
-                 sal_fb = s2,
-                 sal_insitu_ctd = s3,
-                 temp_dur = s4,
-                 temp_fb = s5,
-                 temp_insitu_11m = s6,
-                 phINT = s7,
-                 phEXT = s8)
-
-  summarise_all(percentcumsum)
-  dplyr::mutate_all(funs("percent"= cumsum(.)/100))
-p <-  ggplot(data = selected_nydata_minute) +
-  geom_bar(aes(x = as.factor(pco2_corr_qf)))
-p
-rm(selected_nydata_minute)
+# s1 <- summary(as.factor(selected_nydata_minute$pco2_corr_qf))*100/length(selected_nydata_minute$pco2_raw_qf)
+# s2 <- summary(as.factor(selected_nydata_minute$sal_fb_qf))*100/length(selected_nydata_minute$sal_fb_qf)
+# s3 <- summary(as.factor(selected_nydata_minute$sal_insitu_ctd_qf))*100/length(selected_nydata_minute$sal_insitu_ctd_qf)
+# s4 <- summary(as.factor(selected_nydata_minute$temp_dur_qf))*100/length(selected_nydata_minute$temp_dur_qf)
+# s5 <- summary(as.factor(selected_nydata_minute$temp_fb_qf))*100/length(selected_nydata_minute$temp_fb_qf)
+# s6 <- summary(as.factor(selected_nydata_minute$temp_insitu_11m_qf))*100/length(selected_nydata_minute$temp_insitu_11m_qf)
+# s7 <- summary(as.factor(selected_nydata_minute$phINT_qf))*100/length(selected_nydata_minute$phINT_qf)
+# s8 <- summary(as.factor(selected_nydata_minute$phEXT_qf))*100/length(selected_nydata_minute$phEXT_qf)
+# qflags <- tibble(pco2_corr = s1,
+#                  sal_fb = s2,
+#                  sal_insitu_ctd = s3,
+#                  temp_dur = s4,
+#                  temp_fb = s5,
+#                  temp_insitu_11m = s6,
+#                  phINT = s7,
+#                  phEXT = s8)
+#   
+#   summarise_all(percentcumsum)
+#   dplyr::mutate_all(funs("percent"= cumsum(.)/100))
+# p <-  ggplot(data = selected_nydata_minute) +
+#   geom_bar(aes(x = as.factor(pco2_corr_qf)))
+# p
+# rm(selected_nydata_minute)
 ```
@@
 
-- Serveur : awipev-co2 (193.50.85.104)
-- 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer mais n'est plus utilisé).
-- Pour se connecter à awipev-co2.obs-vlfr.fr
-        - ssh awipev@awipev-co2.obs-vlfr.fr
-- Intervention sur le serveur :
-        - ssh awipev@awipev-co2.obs-vlfr.fr
-        - rebooting Ubuntu server: sudo shutdown -r now
-        - to check versions:
+* Serveur : awipev-co2 (193.50.85.104)
+* 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer mais n'est plus utilisé).
+* Pour se connecter à awipev-co2.obs-vlfr.fr
+    + ssh awipev@awipev-co2.obs-vlfr.fr
+* Intervention sur le serveur :
+    + ssh awipev@awipev-co2.obs-vlfr.fr
+    + rebooting Ubuntu server: sudo shutdown -r now
+    + to check versions:
         - dpkg -l | grep shiny
         - dpkg -l | grep r-base
-        - To update Ubuntu, R and its packages:
+    + To update Ubuntu, R and its packages:
         - sudo su
         - apt-get upgrade
-        - To restart shiny server: sudo systemctl restart shiny-server
+    + To restart shiny server: sudo systemctl restart shiny-server
         - update shiny server: follow procedure detailed on the shiny web page Data processing
-
-** Data processing**
-
-We use the AWI database XXXXX
-
-**crontab awipev@awipev-co2.obs-vlfr.fr**
-
-si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync
-
+* To install R packages:
+    + ssh gattuso@o
+    + sudo R (then password)
+    + install.packages (tidyverse")
+
+### Data processing
+We use the AWI database [Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736)
+
+* **crontab awipev@awipev-co2.obs-vlfr.fr**
+Si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync.
 Pattern des commandes : # m h dom mon dow command
 
-- (At 01:00, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
-
-00 01 * * * cd ; R \-\-vanilla < ny-alesund/R/ny-alesund_cc.R
-
-- (At 03:00, web page is generated)
-
-00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1
-
-- (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud ... Exp168)
-
-00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
-
-- (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)
-
-00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
-
-**Web page**
-
-- La page web index.html est faite sur le serveur awipev/web grâce au script awipev-CO2_web.Rmd puis transférée et renommée dans awipev/awipev-CO2_web
-- Création du répertoire web qui contient ce qu’il faut pour générer la page web:
-    - AWIPEV-Logo.jpg
-    - Discrete_sampling_AWIPEV.csurv
-    - awipev-CO2_web.Rmd
-    - awipev-co2.sh (lancer par bash awipev-co2.sh)
-- Accessible https://awipev-co2.obs-vlfr.fr
-
-**On utilise un shell script awipev-co2.sh:**
-
+* (At 01:00, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
+    + 00 01 * * * cd ; R \-\-vanilla < ny-alesund/R/ny-alesund_cc.R 
+* (At 03:00, web page is generated)
+    + 00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1  
+* (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud ... Exp168)
+    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
+* (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)
+    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
+
+### Web page
+
+* La page web index.html est faite sur le serveur awipev/web grâce au script awipev-CO2_web.Rmd puis transférée et renommée dans awipev/awipev-CO2_web
+* Création du répertoire web qui contient ce qu’il faut pour générer la page web:
+    + AWIPEV-Logo.jpg
+    + Discrete_sampling_AWIPEV.csurv
+    + awipev-CO2_web.Rmd
+    + awipev-co2.sh (lancer par bash awipev-co2.sh)
+* Accessible https://awipev-co2.obs-vlfr.fr 
+* On utilise un shell script awipev-co2.sh:
     #!/bin/bash 
-
     # script de lancement via crontab echo '---------deb awipev-co2.sh -----------' 
-
     # On lance la fabrication du html cd web; R -e 
     'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html 
-
     echo '---------fin awipev-co2.sh -----------'
@@
 A la main dans le terminal, cela donne :
-ssh awipev@awipev-co2.obs-vlfr.fr
-R --vanilla < web/awipev-CO2_web.Rmd
+* ssh awipev@awipev-co2.obs-vlfr.fr
+* R --vanilla < web/awipev-CO2_web.Rmd
 

### 2020-05-01 awipev-CO2.Rmd
Save replaced by saveRDS

@@
 
-save(file= paste0(path, "fb_data/d_all.rds"), d_all)
+saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
 
@@
 # d_all comprises additional columns calculated in this script
-# These additional variablrs are useful elsewhere (for example in "presentation")
-# Hence, here we save it for this use
 saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
@@
 ### Data processing
-We use the AWI database [Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736)
-
-* **crontab awipev@awipev-co2.obs-vlfr.fr**
+
+#### Script ny-alesund_cc.R which runs on awipev@awipev-co2.obs-vlfr.fr
+* reads data from the AWI NRT database [Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736) 
+* calibrates pCO2 data
+* data cleaning:
+  + Argo Global Range Test.
+  + filter salinities above 28
+  + filter temperatures above 10
+  + filter seaFET Volt (outliers)
+  + filter seaFET pH (outliers)
+  + filter durafet (outliers)
+* Quality flags
+    + 1: good data
+    + 3: impossible date and time test
+    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
+    + 6: failing the manufacturer range test (not used)
+    + 7: failing the regional range test 
+    + 12: failing the spike test (NAs from despike)
+    + 13: failing the gradient test
+    + 15: the instrument was not deployed or operated
+    + 99: failing the final visual inspection of the data. 
+* Despike using oce::despike with n=2, k=5761
+* Files generated:
+    + previous_NRT_data.rds: all NRT data without alteration from the beginning (2015)
+    + all_nydata_minute.rds: all data after filtering and despike describe above (every minute)
+    + all_nydata_hour.rds: hourly means of all data after filtering and despike describe above (every minute)
+    + nydata_minute.rds: selected data after filtering and despike describe above (every minute). **Useful?**
+    + nydata_hour.rds: selected hourly means of all data after filtering and despike describe above (every minute).  This is for further data processing.
+
+#### Script awipev-co2.Rmd which runs locally
+* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
+* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
+* calibrate seafet pH
+* calibrate durafet pH
+
+**crontab awipev@awipev-co2.obs-vlfr.fr**
 Si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync.
@@
 * Accessible https://awipev-co2.obs-vlfr.fr 
-* On utilise un shell script awipev-co2.sh:
+* On utilise un shell script awipev-co2.sh :
+
     #!/bin/bash
+
     # script de lancement via crontab echo '---------deb awipev-co2.sh -----------'
+
     # On lance la fabrication du html cd web; R -e 
     'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html
+
     echo '---------fin awipev-co2.sh -----------'
@@
 A la main dans le terminal, cela donne :
+
 * ssh awipev@awipev-co2.obs-vlfr.fr

### 2020-05-01 awipev-CO2.Rmd
clean up

@@
 
-### Traitement des variables
-
-* temp_mix = temp 11m + temp_insitu_ctd_9m si trous.
-* sal_mix = sal FB + sal_insitu_ctd_9m si trous.
-* ph_s_sf_temp_mix: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
-* ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
-* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
-* pco2_calc: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
-* Relation at / sal_mix 
-* at_calc: calculé from sal_mix
-* E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_mix (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
-* phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
-
 ### **FerryBox**
-
 - **2020-03-13**: Salinity was filtered above 28 in d_all.rds file.
@@
 
-## Villefranche Server informations
-
-* Serveur : awipev-co2 (193.50.85.104)
-* 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer mais n'est plus utilisé).
-* Pour se connecter à awipev-co2.obs-vlfr.fr
-    + ssh awipev@awipev-co2.obs-vlfr.fr
-* Intervention sur le serveur :
-    + ssh awipev@awipev-co2.obs-vlfr.fr
-    + rebooting Ubuntu server: sudo shutdown -r now
-    + to check versions:
-        - dpkg -l | grep shiny
-        - dpkg -l | grep r-base
-    + To update Ubuntu, R and its packages:
-        - sudo su
-        - apt-get upgrade
-    + To restart shiny server: sudo systemctl restart shiny-server
-        - update shiny server: follow procedure detailed on the shiny web page Data processing
-* To install R packages:
-    + ssh gattuso@o
-    + sudo R (then password)
-    + install.packages (tidyverse")
-
-### Data processing
-
+## Data processing
 #### Script ny-alesund_cc.R which runs on awipev@awipev-co2.obs-vlfr.fr
@@
 #### Script awipev-co2.Rmd which runs locally
+* reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
 * sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
 * temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
+* pco2_calc: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
 * calibrate seafet pH
+    - ph_s_sf_temp_mix: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
+    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_mix (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
+    - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
+* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
 * calibrate durafet pH
+    - ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
+* Relation at / sal_mix 
+* at_calc: calculé from sal_mix
+* saves locally d_all.rds which comprises all variables plus those generated in the script
+
+### Villefranche Server informations
+
+* Serveur : awipev-co2 (193.50.85.104)
+* 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer mais n'est plus utilisé).
+* Pour se connecter à awipev-co2.obs-vlfr.fr
+    + ssh awipev@awipev-co2.obs-vlfr.fr
+* Intervention sur le serveur :
+    + ssh awipev@awipev-co2.obs-vlfr.fr
+    + rebooting Ubuntu server: sudo shutdown -r now
+    + to check versions:
+        - dpkg -l | grep shiny
+        - dpkg -l | grep r-base
+    + To update Ubuntu, R and its packages:
+        - sudo su
+        - apt-get upgrade
+    + To restart shiny server: sudo systemctl restart shiny-server
+        - update shiny server: follow procedure detailed on the shiny web page Data processing
+* To install R packages:
+    + ssh gattuso@o
+    + sudo R (then password)
+    + install.packages (tidyverse")
 
@@
 ![ ](Images/awipev_server_arborescence.jpg){width=65%}
-
-<!-- ```{r Graph pour proposal, echo=FALSE, message= FALSE, warning=FALSE} -->
-
-<!-- p_sal <- ggplot() + -->
-<!--          geom_point(data=d_all%>%filter(sal >28),aes(x=datetime, y=sal),size=1, color="blue") + -->
-<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
-<!--          labs(y = "Salinity", x="Time")+ -->
-<!--         theme_bw() -->
-<!--  p_temp_fb <- ggplot() + -->
-<!--          geom_point(data=d_all,aes(x=datetime, y=temp_fb),size=1, color="blue") + -->
-<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
-<!--          labs(y = "Temperature (in Ferrybox)", x="Time")+ ylim(c(-2.5, 9.5)) + -->
-<!--         theme_bw() -->
-<!--  p_pco2 <- ggplot() + -->
-<!--          geom_point(data=d_all%>%filter(pco2_contros < 450),aes(x=datetime, y=pco2_contros),size=1, color="blue") + -->
-<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
-<!--          labs(y = "Corrected pCO2", x="Time")+ -->
-<!--         theme_bw() -->
-<!--  p_ta_raw <- ggplot() + -->
-<!--          geom_point(data=d_all,aes(x=datetime, y=sal),size=1, color="blue") + -->
-<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
-<!--          labs(y = "Salinity", x="Time")+ -->
-<!--         theme_bw() -->
-<!--  p_sf <- ggplot() + -->
-<!--          geom_point(data=d_all,aes(x=datetime, y=pHint_tot_sf),size=1, color="blue") + -->
-<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
-<!--          labs(y = "Corrected seaFET pH", x="Time")+ -->
-<!--         theme_bw() -->
-<!--  p_df <- ggplot() + -->
-<!--          geom_point(data=d_all,aes(x=datetime, y=pH_durafet_),size=1, color="blue") + -->
-<!--          scale_x_datetime(breaks=date_breaks("3 months"), labels = date_format("%b%y") ) + -->
-<!--          labs(y = "Corrected seaFET pH", x="Time")+ -->
-<!--         theme_bw() -->
-<!-- ggsave("../fb_figures/Plots_proposal/p_sal.png", p_sal,width = 15, height = 5 ,units="cm") -->
-<!-- ggsave("../fb_figures/Plots_proposal/p_temp_fb.png", p_temp_fb,width = 15, height = 5 ,units="cm") -->
-<!-- ggsave("../fb_figures/Plots_proposal/p_pco2.png", p_pco2,width = 15, height = 5 ,units="cm") -->
-<!-- ggsave("../fb_figures/Plots_proposal/p_sf.png", p_sf,width = 15, height = 5 ,units="cm") -->
-<!-- ggsave("../fb_figures/Plots_proposal/p_df.png", p_df,width = 15, height = 5 ,units="cm") -->
-<!-- ggsave("../fb_figures/Plots_proposal/p_ta.png", p_ta,width = 15, height = 5 ,units="cm") -->
-
-<!--  # DURAFET  -->
-<!-- durafet_contros_xts <- dplyr::select(d_all, datetime, pH_durafet, ph_s_dur_temp_fb) -->
-<!-- durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime) -->
-<!-- dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>% -->
-<!--     dySeries("pH_durafet", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>% -->
-<!--     dySeries("ph_s_dur_temp_fb", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
-<!--     dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>% -->
-<!--     dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>%  -->
-<!--     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>% -->
-<!--     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
-<!--     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>% -->
-<!--     dyRangeSelector(height = 30)  -->
-<!-- # SEAFET  -->
-<!-- seafet_contros_xts <- dplyr::select(d_all, datetime, phINT,ph_s_sf_temp_mix) -->
-<!-- seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime) -->
-<!-- dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>% -->
-<!--   dySeries("phINT", label = "Raw data INT", color ="blue", strokeWidth=0, pointSize=2) %>% -->
-<!--   dySeries("ph_s_sf_temp_mix", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>% -->
-<!--   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%  -->
-<!--   dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>% -->
-<!--     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
-<!--     dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>% -->
-<!--     dyRangeSelector(height = 30)  -->
-
-<!-- ``` -->

### 2020-05-01 awipev-CO2.Rmd
formatting

@@
 
-## Data processing
+### Data processing
 #### Script ny-alesund_cc.R which runs on awipev@awipev-co2.obs-vlfr.fr
@@
 * To install R packages:
-    + ssh gattuso@o
+    + ssh gattuso@awipev-co2.obs-vlfr.fr
     + sudo R (then password)
@@
 **crontab awipev@awipev-co2.obs-vlfr.fr**
+
 Si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync.

### 2020-05-01 awipev-CO2.Rmd
Clean up

@@
 d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
-# load = d_hour
 d_hour <- d_hour %>%
   dplyr::select(-date) %>%
-  # dplyr::mutate(AT = ifelse(datetime > "2016-02-26 12:00:00", AT_filtered, NA), # beginning of data series for AT
-  #        AT_filtered = ifelse(AT_filtered == "NaN", NA, AT_filtered), #3 columns are character
-  #        #pH_AT = ifelse(pH_AT == "NaN", NA, pH_AT),
-  #        #PCO2_Corr_Zero2 = ifelse(PCO2_Corr_Zero2 %in% c("NaN", 66666), NA, PCO2_Corr_Zero2)
-  #        ) %>%
-  # variables passed through despike with "-filtered" have been renamed without sufix.
   dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
@@
   dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_9m))
-
-# ### remove sal_mix data that seem to be to high compared to sal_fb
-#   d_all <- d_all%>%
-#   dplyr::mutate(sal_mix = ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-13 18:00:00" , NA, 
-#                           ifelse(datetime > "2018-05-21 19:00:00" & datetime < "2018-05-24 17:00:00" , NA,
-#                           ifelse(datetime > "2018-05-29 15:00:00" & datetime < "2018-06-03 13:00:00" , NA,
-#                           ifelse(datetime > "2018-06-16 06:00:00" & datetime < "2018-06-21 05:00:00" , NA,
-#                           ifelse(datetime > "2019-12-02 08:00:00" & datetime < "2019-12-03 08:00:00" , NA,
-#                           ifelse(datetime > "2019-12-09 07:00:00" & datetime < "2019-12-09 10:00:00" , NA, 
-#                           ifelse(datetime > "2019-12-09 15:00:00" & datetime < "2019-12-09 18:00:00" , NA,
-#                           ifelse(datetime > "2019-12-10 14:00:00" & datetime < "2019-12-10 18:00:00", NA, sal_mix)))))))))
-
 ```
@@
                    )
-#at_ct_mean <- at_ct_mean%>%filter(!is.na(at_mean))
-#write.table(file= paste0(path, "fb_data/at_ct_mean.txt"), at_ct_mean)
 d <- left_join(d, at_ct_mean, by='datetime')
@@
 
-# discrete_steffen <- discrete[c(21:72),1:4]
-# write.table( discrete_steffen,"../fb_data/DiscreteTA_for_steffen.txt", sep= ",", dec=".", row.names = FALSE)
-
 discrete_no_na <- discrete %>%
@@
 discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
-# remove the drop_na() because of seafet/durafet line with na
 discrete2merge <- discrete %>%
-  #drop_na() %>%
   dplyr::select(closest_datetime, at, qflag_at) %>%
@@
 # ct
-# closest <- which.closest(discrete$datetime, d$datetime) # closest date and time
-# discrete$closest_datetime <- d$datetime[closest]
-# # if the closest value is more than 30 min away, then we do not take it
-# discrete$closest_datetime[abs(discrete$datetime - d$datetime[closest]) > 30*60] <- NA
 discrete2merge <- discrete %>%
@@
 # pH calculated
-# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
-# discrete$closest_datetime <- d_all$datetime[closest]
-# # if the closest value is more than 30 min away, then we do not take it
-# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
 discrete2merge <- discrete %>%
@@
 # seaFET pH 
-# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
-# discrete$closest_datetime <- d_all$datetime[closest]
-# # if the closest value is more than 30 min away, then we do not take it
-# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
 discrete2merge <- discrete %>%
-  #drop_na() %>%
   dplyr::select(closest_datetime, ph_s_sf_temp_mix) %>%
@@
 d_all <- full_join(d_all, discrete2merge, by="datetime")
-# #voltINT
-# discrete2merge <- discrete %>%
-#   #drop_na() %>%
-#   dplyr::select(closest_datetime, voltINT) %>%
-#   rename(datetime=closest_datetime)
-# d_all <- full_join(d_all, discrete2merge, by="datetime")
-# #voltEXT
-# discrete2merge <- discrete %>%
-#   #drop_na() %>%
-#   dplyr::select(closest_datetime, voltEXT) %>%
-#   rename(datetime=closest_datetime)
-# d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-# duraFET pH 
-# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
-# discrete$closest_datetime <- d_all$datetime[closest]
-# # if the closest value is more than 30 min away, then we do not take it
-# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
 discrete2merge <- discrete %>%
@@
 d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-# pCO2
-# closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
-# discrete$closest_datetime <- d_all$datetime[closest]
-# # if the closest value is more than 30 min away, then we do not take it
-# discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
 discrete2merge <- discrete %>%
@@
 fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu_ctd_9m , nperm = 99)
-
-# at_contros_cleaned_xts <- dplyr::select(d_all, datetime,sal_fb,sal_insitu_ctd)
-# at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime)
-# dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>%
-#    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>%
-#   #dySeries("AT_filtered2", color = RColorBrewer::brewer.pal(4, "Set2"), strokeWidth = 0, pointSize=2) %>%
-#   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% 
-#   dySeries("AT_filtered", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2)
-
 p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
   geom_point( aes(color=factor(month))) + 
- # scale_color_viridis_d(option = "C", guide="none")+
-  #geom_line(aes(x = sal_fb, y = sal_fb), linetype = "dashed") +
   geom_abline(slope=1, intercept=0, linetype = "dashed")+
@@
   coord_fixed(ratio = 1 )+
- #  scale_colour_discrete(guide="none") +
   labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") +theme_bw()
@@
 dySeries("temp_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
-#dySeries("temp_fb", color = "grey", strokeWidth = 0, label = "temp_fb") %>%
-#dySeries("temp_mix", color = "black", strokeWidth = 0, label = "temp_mix") %>%
 dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
 sd_diff_T_fb_11m <- round(sd(d_all$diff_T_fb_11m, na.rm = TRUE), digits = 2)
-
-### Plotly
-# p_p_temp_11_fb <- ggplotly(p_temp_11_fb,dynamicTicks = TRUE)
-# filename.html <- paste0("p_p_temp_11_fb.html")
-# saveWidget(p_p_temp_11_fb, filename.html, selfcontained = T, libdir = "lib")
-
 ```
@@
 d_all_at_discrete <- d_all %>% #  To remove an outlier in red
-  dplyr::select(datetime, month,closest_datetime, at, sal_mix) #%>%
- # dplyr::filter( !is.na(at) & !is.na(sal) & sal >30)
-
-  #at != "2307.05" & sal > 28, !is.na(at))
-
-# d_all_Out <- d_all %>% #  To keep an outlier in red
-#   filter(at == "2307.05")
-
-#fit <- lm(data = drop_na(d_all_at_discrete, at), at ~ sal)
+  dplyr::select(datetime, month,closest_datetime, at, sal_mix)
+
 fit <- lm(data = d_all_at_discrete, at ~ sal_mix)
@@
 intercept_s_at <- fit$coefficients[[1]]
-# at_s <- ggreg(fit)+ labs(x="Salinity", y="Discrete TA") + Mytheme()
-
 at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at, label = month))+
@@
         plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70)))
-  #print(at_s)
-#ggsave(paste0("figures/Discrete_TA_salinity_AWIPEV.png"), at_s, width=15, height =11, units="cm")
 
@@
 print(p) # pco2_calc_pco2_corr_text
-#ggsave(paste0("figures/pco2_calc_pco2_corr.png"), pco2_calc_pco2_corr_text, units="cm")
 ```
@@
   ) %>%
-  #dySeries("pco2_raw", label="Raw pCO2",color ="blue", strokeWidth = 0, pointSize = 1) %>%
   dySeries(
@@
 
-###Plotly
-# p_py <- ggplotly(p,dynamicTicks = TRUE)
-# filename.html <- paste0("p_py.html")
-# saveWidget(p_py, filename.html, selfcontained = T, libdir = "lib")
-
 seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_mix, pHint_tot_sf, pH_s_sf_no_calb)
@@
   dyRangeSelector(height = 30, dateWindow= NULL)
-
-# # #@@@@@ test plot #@@@@@ #@@@@@ #@@@@@
-# seafet_contros_xts <- dplyr::select(d_all, datetime, temp_fb, temp_insitu)#voltINT, phINT,ph_s_sf_temp_mix, temp_sf, temp_fb, temp_insitu, sal)
-# #seafet_contros_xts <- dplyr::select(d_all, datetime,voltINT)
-# seafet_contros_xts <- as.xts(seafet_contros_xts, order.by = d_all$datetime)
-# dygraph(seafet_contros_xts, group = "awipev", main="pH seaFET (in situ)", ylab="pHT") %>%
-#   #dySeries("voltINT", label = "voltINTINT", color ="blue", strokeWidth=0, pointSize=2) %>%
-#    # dySeries("ph_s_sf_temp_mix", label = "pH spectro", axis= "y2", color =  "green", strokeWidth = 0, pointSize = 4 ) %>%
-#     #dySeries("pHint_tot_sf", label = "corr pH INT", color ="red",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#   dySeries("temp_insitu", label = "temp_insitu", color ="red", strokeWidth=0, pointSize=2) %>%
-# dySeries("temp_fb", label = "temp_fb", color ="blue", strokeWidth=0, pointSize=2) %>%
-#  # dySeries("sal", label = "sal", color ="black",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#    # dySeries("temp_sf", label = "temp_sf", color ="grey",axis= "y2", strokeWidth=0, pointSize=2) %>%
-#  #   dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-#   #dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>%
-#   #dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-#    # dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
-#   dyLegend(show = "auto")   %>%
-#   #dyAxis( "y2",valueRange = c(-3, 36))%>%
-#   dyAxis( "y",valueRange = c(-3, 9))%>%
-#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-#   dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-#   dyRangeSelector(height = 30, dateWindow= NULL)
-# # #@@@@@ #@@@@@ #@@@@@ #@@@@@ #@@@@@
-
-# # Offset between seafet pH and spec pH 
-# sfoffset <- left_join(sfPeriod[,c(1,2)], d_all%>%dplyr::select(datetime, pHint_tot_sf), by="datetime")
-# dat <- mutate(sfoffset, diff_pH_sf = round((ph_s_sf_temp_mix - pHint_tot_sf),digits  = 4))
-# average_offset <- mean(abs(dat$diff_pH_sf), na.rm=TRUE)
-# 
-# plot_offset <- ggplot(data = filter(dat, !is.na(diff_pH_sf))) +
-#   geom_hline(yintercept=mean(dat$diff_pH_sf, na.rm = TRUE), size=0.3, linetype="dashed", col="red") +
-#   geom_hline(yintercept=0, size=0.3) +
-#   geom_point(aes(x = datetime, y = diff_pH_sf), size = 1, colour = "#51C56AFF") +
-#   labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
-#   scale_x_datetime(date_breaks="month", date_minor_breaks="1 week", labels=date_format("%b %Y")) +
-#   Mytheme() + theme(panel.grid.major.x = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1)) 
-# 
-# print(plot_offset)
-
-# #plot for POSTER june 2019
-# #plot of pH seafet
-# poster_ph <- ggplot() +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= pHint_tot_sf,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=ph_s_sf_temp_mix, fill="Discrete measurements"), col="red" )+
-#   labs(x = "", y ="", title = expression(pH[T]~seaFET)) +
-#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-#   theme(legend.position= c(0.17, 0.8),
-#                      legend.text=element_text(size=14),
-#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
-#                       axis.text=element_text(size=15),
-#                       plot.margin = unit(c(1,1,1,1), "cm"),
-#                       axis.title.x= element_text(size =15),
-#                       legend.title=element_blank())
-# 
-# print(poster_ph)
-# ggsave(paste0("figures/poster_ph.png"), width= 30, height=10, poster_ph, units="cm")
 
@@
 
-# #plot for POSTER june 2019
-# #plot of pH durafet
-#  poster_dur <- ggplot( ) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y= ph_dur_corr,col="blue"), col="blue",size=0.5 , rm.na=TRUE) +
-#   geom_point(data=d_all%>%dplyr::filter(datetime > "2017-07-30"  ), aes(x=datetime, y=ph_s_dur_temp_fb, fill="Discrete measurements"), col="red" )+
-#   labs(x = "", y= "", title = expression(pH[T]~durafet)) +
-#   theme_bw() + scale_x_datetime(minor_breaks  = "1 month ")+
-#    theme(legend.position= c(0.17, 0.8),
-#                      legend.text=element_text(size=14),
-#                       plot.title = element_text(hjust =0.1, vjust = 1,size = rel(1.5),margin = margin( b = -35)),
-#                       axis.text=element_text(size=15),
-#                       plot.margin = unit(c(1,1,1,1), "cm"),
-#                       axis.title.x= element_text(size =15),
-#                       legend.title=element_blank())
-# 
-# print(poster_dur)
-# ggsave(paste0("figures/poster_dur.png"), width= 30, height=10, poster_dur, units="cm")
-
 # RANGE of pH
@@
 print(p) # plot_range_dur
-#ggsave(paste0("figures/plot_range_dur.png"), width= 30, height=10, plot_range_dur, units="cm")
 ```
@@
   facet_wrap( ~ factor(month), ncol = 3) +
-  #stat_smooth(data = d_all, aes(x = pH_durafet_norm4, y = pHint_tot_sf_norm4, color=month),
-  #            method=lm, na.rm=TRUE, se=FALSE) +
- # scale_color_viridis_d(option = "C", guide="none")+
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  #geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  #labs(title = paste("pH seaFET vs pH durafet, normalized 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
-   #                  "; Intercept =", signif(fit$regression.results[2,2], 3),
-    #                 "; Slope =", signif( fit$regression.results[2,3], 3),
-    #                 "; P =", signif(fit$P.param, 3))) +
   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
@@
 
-# DURAFET vs CALC
-# fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pH_durafet_norm4 , nperm = 99)
-# 
-# pdur_calc_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pH_calc_norm4, label = month))+
-#   geom_text( aes(color=factor(month))) + 
-#   geom_line(aes(x = pH_calc_norm4, y = pH_calc_norm4), linetype = "dashed") +
-#   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-#   labs(title = paste("pH calculated vs pH durafet, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
-#                      "; Intercept =", signif(fit$regression.results[2,2], 3),
-#                      "; Slope =", signif( fit$regression.results[2,3], 3),
-#                      "; P =", signif(fit$P.param, 3))) +
-#   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-#    coord_fixed(ratio = 1 , xlim=c(8,8.22), ylim=c(8,8.22)) + 
-#   scale_color_discrete(guide="none")+
-#   labs(x="pH durafet, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
-# pdur_calc_norm_text
-
 durafet_calc_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pH_calc_norm4)
@@
 ```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
-# SEAFET vs CALC
-# fit <- lmodel2(data = d_all,  pH_calc_norm4 ~ pHint_tot_sf_norm4 , nperm = 99)
-# 
-# psf_calc_norm_text <-  ggplot(d_all,aes(x=pHint_tot_sf_norm4, y= pH_calc_norm4, label = month))+
-#   geom_text( aes(color=factor(month))) + 
-#   scale_color_discrete(guide = "none")+
-#  geom_abline(slope=1, intercept =0, linetype = "dashed") +
-#   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-#   labs(title = paste("pH calculated vs pH seaFET, normalized at 4°C","\n Adj R2 = ", signif(fit$rsquare, 3),
-#                      "; Intercept =", signif(fit$regression.results[2,2], 3),
-#                      "; Slope =", signif( fit$regression.results[2,3], 3),
-#                      "; P =", signif(fit$P.param, 3))) +
-#   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-#     coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
-#   labs(x="pH seaFET, 4°C", y="pH calculated, 4°C ", color = "Months") + theme_bw() 
-# psf_calc_norm_text
-
 seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_norm4, pH_calc_norm4)
@@
 p_ct_ts
-#ggsave(paste0("figures/delta_at_awipev_snapo.png"), pdelta_at_snapo, units="cm")
-#ggsave(paste0("figures/delta_ct_awipev_snapo.png"), pdelta_ct_snapo, units="cm")
 ```
@@
 * ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
+* despike pH seaFET
 * calibrate durafet pH

### 2020-05-02 awipev-CO2.Rmd
dunno

@@
 ```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+# SAL FerryBox
 sal_xts <- dplyr::select(d_all, datetime, sal_fb)
@@
 
-pco2_contros_xts <-
-  dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_mix)
-pco2_contros_xts <-
-  as.xts(pco2_contros_xts, order.by = d_all$datetime)
-dygraph(pco2_contros_xts,
-        group = "awipev",
-        main = "<i>p</i>CO<sub>2</sub>",
-        ylab = "<i>p</i>CO<sub>2</sub>") %>%
-  dySeries(
-    axis = "y2",
-    "voltINT",
-    label = "voltINT",
-    color =  RColorBrewer::brewer.pal(5, "Dark2")[1],
-    strokeWidth = 0,
-    pointSize = 2
-  ) %>%
-  dySeries(axis="y2",
-    "voltEXT",
-    label = "voltEXT",
-    color =  RColorBrewer::brewer.pal(5, "Dark2")[2],
-    strokeWidth = 0,
-    pointSize = 2
-  ) %>%
-   dySeries(
-    "temp_insitu_ctd",
-    label = "temp_insitu_ctd",
-    color =  RColorBrewer::brewer.pal(5, "Dark2")[3],
-    strokeWidth = 0,
-    pointSize = 2
-  ) %>%
-   dySeries(
-    "sal_fb",
-    label = "sal_fb",
-    color =  RColorBrewer::brewer.pal(5, "Dark2")[4],
-    strokeWidth = 0,
-    pointSize = 2
-  ) %>%
-   dySeries(
-    "ph_s_sf_temp_mix",
-    label = "ph_s_sf_temp_mix",
-    color =  RColorBrewer::brewer.pal(5, "Dark2")[5],
-    strokeWidth = 0,
-    pointSize = 4
-  ) %>%
-  dyHighlight(
-    highlightCircleSize = 8,
-    highlightSeriesBackgroundAlpha = 0.5,
-    hideOnMouseOut = TRUE
-  ) %>%
-  dyLegend(show = "follow")   %>%
-  dyAxis("y2",valueRange = c(-2,2))%>%
-  dyOptions(
-    drawGrid = TRUE,
-    drawPoints = TRUE,
-    pointSize = c(1, 8, 1),
-    useDataTimezone = TRUE
-  ) %>%
-  dyRangeSelector(height = 30, dateWindow = NULL)
+# pco2_contros_xts <-
+#   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_mix)
+# pco2_contros_xts <-
+#   as.xts(pco2_contros_xts, order.by = d_all$datetime)
+# dygraph(pco2_contros_xts,
+#         group = "awipev",
+#         main = "<i>p</i>CO<sub>2</sub>",
+#         ylab = "<i>p</i>CO<sub>2</sub>") %>%
+#   dySeries(
+#     axis = "y2",
+#     "voltINT",
+#     label = "voltINT",
+#     color =  RColorBrewer::brewer.pal(5, "Dark2")[1],
+#     strokeWidth = 0,
+#     pointSize = 2
+#   ) %>%
+#   dySeries(axis="y2",
+#     "voltEXT",
+#     label = "voltEXT",
+#     color =  RColorBrewer::brewer.pal(5, "Dark2")[2],
+#     strokeWidth = 0,
+#     pointSize = 2
+#   ) %>%
+#    dySeries(
+#     "temp_insitu_ctd",
+#     label = "temp_insitu_ctd",
+#     color =  RColorBrewer::brewer.pal(5, "Dark2")[3],
+#     strokeWidth = 0,
+#     pointSize = 2
+#   ) %>%
+#    dySeries(
+#     "sal_fb",
+#     label = "sal_fb",
+#     color =  RColorBrewer::brewer.pal(5, "Dark2")[4],
+#     strokeWidth = 0,
+#     pointSize = 2
+#   ) %>%
+#    dySeries(
+#     "ph_s_sf_temp_mix",
+#     label = "ph_s_sf_temp_mix",
+#     color =  RColorBrewer::brewer.pal(5, "Dark2")[5],
+#     strokeWidth = 0,
+#     pointSize = 4
+#   ) %>%
+#   dyHighlight(
+#     highlightCircleSize = 8,
+#     highlightSeriesBackgroundAlpha = 0.5,
+#     hideOnMouseOut = TRUE
+#   ) %>%
+#   dyLegend(show = "follow")   %>%
+#   dyAxis("y2",valueRange = c(-2,2))%>%
+#   dyOptions(
+#     drawGrid = TRUE,
+#     drawPoints = TRUE,
+#     pointSize = c(1, 8, 1),
+#     useDataTimezone = TRUE
+#   ) %>%
+#   dyRangeSelector(height = 30, dateWindow = NULL)
+
 # To make sf calibration against pH spectro, we need: sal - T insi - voltINT/EXT . If we missed one of these parameters, calibration will not run
@@
 #ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
-
 ```

### 2020-05-02 awipev-CO2.Rmd
better documenttation for making the web page

@@
 
-    # On lance la fabrication du html cd web; R -e 
-    'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html
+    # On lance la fabrication du html (une seule ligne)
+    cd web; R -e 'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html
 
@@
 * ssh awipev@awipev-co2.obs-vlfr.fr
-* R --vanilla < web/awipev-CO2_web.Rmd
+* cd; bash web/awipev-co2.sh
 

### 2020-05-05 awipev-CO2.Rmd
Changed info on server and on-going work on data availability

@@
 ```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+# function to express the number of quality flag in pefrcent for each variable
+qflag <- function(x) {
+  summary(as.factor(x))*100/length(x)
+}
 selected_nydata_minute <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_minute.rds")) %>%
-  dplyr::select(ends_with("_qf")) #%>%
-# s1 <- summary(as.factor(selected_nydata_minute$pco2_corr_qf))*100/length(selected_nydata_minute$pco2_raw_qf)
-# s2 <- summary(as.factor(selected_nydata_minute$sal_fb_qf))*100/length(selected_nydata_minute$sal_fb_qf)
-# s3 <- summary(as.factor(selected_nydata_minute$sal_insitu_ctd_qf))*100/length(selected_nydata_minute$sal_insitu_ctd_qf)
-# s4 <- summary(as.factor(selected_nydata_minute$temp_dur_qf))*100/length(selected_nydata_minute$temp_dur_qf)
-# s5 <- summary(as.factor(selected_nydata_minute$temp_fb_qf))*100/length(selected_nydata_minute$temp_fb_qf)
-# s6 <- summary(as.factor(selected_nydata_minute$temp_insitu_11m_qf))*100/length(selected_nydata_minute$temp_insitu_11m_qf)
-# s7 <- summary(as.factor(selected_nydata_minute$phINT_qf))*100/length(selected_nydata_minute$phINT_qf)
-# s8 <- summary(as.factor(selected_nydata_minute$phEXT_qf))*100/length(selected_nydata_minute$phEXT_qf)
-# qflags <- tibble(pco2_corr = s1,
-#                  sal_fb = s2,
-#                  sal_insitu_ctd = s3,
-#                  temp_dur = s4,
-#                  temp_fb = s5,
-#                  temp_insitu_11m = s6,
-#                  phINT = s7,
-#                  phEXT = s8)
-#   
-#   summarise_all(percentcumsum)
-#   dplyr::mutate_all(funs("percent"= cumsum(.)/100))
-# p <-  ggplot(data = selected_nydata_minute) +
-#   geom_bar(aes(x = as.factor(pco2_corr_qf)))
-# p
+dplyr::select(ends_with("_qf"), -dt_qf) 
+nam <- selected_nydata_minute %>% names()
+selected_nydata_minute %>% map(~qflag(.x))
+
+s1 <- summary(as.factor(selected_nydata_minute$pco2_corr_qf))*100/length(selected_nydata_minute$pco2_corr_qf)
+s2 <- summary(as.factor(selected_nydata_minute$sal_fb_qf))*100/length(selected_nydata_minute$sal_fb_qf)
+s3 <- summary(as.factor(selected_nydata_minute$sal_insitu_ctd_qf))*100/length(selected_nydata_minute$sal_insitu_ctd_qf)
+s4 <- summary(as.factor(selected_nydata_minute$temp_dur_qf))*100/length(selected_nydata_minute$temp_dur_qf)
+s5 <- summary(as.factor(selected_nydata_minute$temp_fb_qf))*100/length(selected_nydata_minute$temp_fb_qf)
+s6 <- summary(as.factor(selected_nydata_minute$temp_insitu_11m_qf))*100/length(selected_nydata_minute$temp_insitu_11m_qf)
+s7 <- summary(as.factor(selected_nydata_minute$phINT_qf))*100/length(selected_nydata_minute$phINT_qf)
+s8 <- summary(as.factor(selected_nydata_minute$phEXT_qf))*100/length(selected_nydata_minute$phEXT_qf)
+z <- t(bind_rows(s1,s2,s3,s4,s5,s6,s7,s8))
+colname(z) <- nam
+
+qflag <- function(x) {
+  summary(as.factor(x))*100/length(x)
+}
+qflags <- tibble(pco2_corr = s1,
+                 sal_fb = s2,
+                 sal_insitu_ctd = s3,
+                 temp_dur = s4,
+                 temp_fb = s5,
+                 temp_insitu_11m = s6,
+                 phINT = s7,
+                 phEXT = s8)
+
+  summarise_all(percentcumsum)
+  dplyr::mutate_all(funs("percent"= cumsum(.)/100))
+p <-  ggplot(data = selected_nydata_minute) +
+  geom_bar(aes(x = as.factor(pco2_corr_qf)))
+p
 # rm(selected_nydata_minute)
@@
 
-* (At 01:00, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
-    + 00 01 * * * cd ; R \-\-vanilla < ny-alesund/R/ny-alesund_cc.R 
-* (At 03:00, web page is generated)
-    + 00 03 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1  
+* (Every hour on the hour, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
+    + 00 *//1 * * * cd $HOME; USER=awipev R --vanilla < ny-alesund/R/ny-alesund_cc.R > ny-alesund/R/log_ny-alesund_cc.txt 2>&1
+* (Every hour at 10 min past the hour, the web page is generated)
+    + 10 *//1 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1  
 * (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud ... Exp168)

### 2020-05-05 awipev-CO2.Rmd
revise shell script to produce web page

@@
 * (Every hour at 10 min past the hour, the web page is generated)
-    + 10 *//1 * * * bash web/awipev-co2.sh > web/awipev-co2.log 2>&1  
+    + 10 *//1 * * * cd web; USER=awipev bash awipev-co2.sh > awipev-web.log 2>&1 
 * (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud ... Exp168)

### 2020-05-07 awipev-CO2.Rmd
Still availability of data

@@
 ### **Data availability**
-TO DO: add here an horizontal bar plot showing the percent availability of the data
+The data at one minute frequency were tagged with the following quality flags
+
++ 1: good data
++ 3: failing the date and time test
++ 4: data not usable according to manufacturer
++ 7: failing the regional range test 
++ 12: failing the spike test (NAs from despike)
++ 13: failing the gradient test
++ 15: instrument not deployed or operated
++ 16: acid flush
++ 99: failing the final visual inspection
+
+* Despike using oce::despike with n=2, k=5761
 
@@
 # function to express the number of quality flag in pefrcent for each variable
-qflag <- function(x) {
-  summary(as.factor(x))*100/length(x)
-}
-selected_nydata_minute <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_minute.rds")) %>%
-dplyr::select(ends_with("_qf"), -dt_qf) 
-nam <- selected_nydata_minute %>% names()
-selected_nydata_minute %>% map(~qflag(.x))
-
-s1 <- summary(as.factor(selected_nydata_minute$pco2_corr_qf))*100/length(selected_nydata_minute$pco2_corr_qf)
-s2 <- summary(as.factor(selected_nydata_minute$sal_fb_qf))*100/length(selected_nydata_minute$sal_fb_qf)
-s3 <- summary(as.factor(selected_nydata_minute$sal_insitu_ctd_qf))*100/length(selected_nydata_minute$sal_insitu_ctd_qf)
-s4 <- summary(as.factor(selected_nydata_minute$temp_dur_qf))*100/length(selected_nydata_minute$temp_dur_qf)
-s5 <- summary(as.factor(selected_nydata_minute$temp_fb_qf))*100/length(selected_nydata_minute$temp_fb_qf)
-s6 <- summary(as.factor(selected_nydata_minute$temp_insitu_11m_qf))*100/length(selected_nydata_minute$temp_insitu_11m_qf)
-s7 <- summary(as.factor(selected_nydata_minute$phINT_qf))*100/length(selected_nydata_minute$phINT_qf)
-s8 <- summary(as.factor(selected_nydata_minute$phEXT_qf))*100/length(selected_nydata_minute$phEXT_qf)
-z <- t(bind_rows(s1,s2,s3,s4,s5,s6,s7,s8))
-colname(z) <- nam
-
-qflag <- function(x) {
-  summary(as.factor(x))*100/length(x)
-}
-qflags <- tibble(pco2_corr = s1,
-                 sal_fb = s2,
-                 sal_insitu_ctd = s3,
-                 temp_dur = s4,
-                 temp_fb = s5,
-                 temp_insitu_11m = s6,
-                 phINT = s7,
-                 phEXT = s8)
-
-  summarise_all(percentcumsum)
-  dplyr::mutate_all(funs("percent"= cumsum(.)/100))
-p <-  ggplot(data = selected_nydata_minute) +
-  geom_bar(aes(x = as.factor(pco2_corr_qf)))
+# qflag <- function(x, ...) {
+#   tmp <- summary(as.factor(x))*100/length(x)
+#   return(tmp)
+# }
+d <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_minute.rds")) %>%
+dplyr::select(datetime, c(pco2_corr_qf, sal_fb_qf, sal_insitu_ctd_qf, 
+                          temp_fb_qf, temp_insitu_11m_qf, ph_dur_qf, phINT_qf))
+
+s1 <- summary(as.factor(d$pco2_corr_qf))*100/length(d$pco2_corr_qf)
+s2 <- summary(as.factor(d$sal_fb_qf))*100/length(d$sal_fb_qf)
+s3 <- summary(as.factor(d$sal_insitu_ctd_qf))*100/length(d$sal_insitu_ctd_qf)
+s4 <- summary(as.factor(d$temp_fb_qf))*100/length(d$temp_fb_qf)
+s5 <- summary(as.factor(d$temp_insitu_11m_qf))*100/length(d$temp_insitu_11m_qf)
+# durafet and seafet started later
+x <- filter(d, datetime >= "2017-08-29 10:00:00")
+#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
+s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
+x <- filter(d, datetime >= "2017-08-24 19:00:00")
+s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
+z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
+  as.data.frame() %>%
+         rownames_to_column(var = "flag") %>% 
+         as_tibble()
+labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
+            "Failed visual inspection", "No data")
+#colnames(z) <- c("flag", colnames(d)[-1]) # remove first col name (datetime)
+colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
+                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
+zz <- pivot_longer(z, -Flag)
+p <-  ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
+  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
+  #scale_y_reverse() +
+  #discrete_scale(labels = labels) + 
+  coord_flip() +
+  geom_text(aes(label=round(value, digits = 0)), position = position_stack(0.5), size = 3) +
+  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
+  theme_bw()
 p
-# rm(selected_nydata_minute)
+rm(d)
 ```

### 2020-05-07 awipev-CO2.Rmd
Still availability of data

@@
 ### **Data availability**
-The data at one minute frequency were tagged with the following quality flags
+TO DO: add here an horizontal bar plot showing the percent availability of the data
 
     + 1: good data
-+ 3: failing the date and time test
-+ 4: data not usable according to manufacturer
+    + 3: impossible date and time test
+    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
+    + 6: failing the manufacturer range test (not used)
     + 7: failing the regional range test 
@@
     + 13: failing the gradient test
-+ 15: instrument not deployed or operated
-+ 16: acid flush
-+ 99: failing the final visual inspection
+    + 15: the instrument was not deployed or operated
+    + 99: failing the final visual inspection of the data.
 
@@
   #scale_y_reverse() +
-  #discrete_scale(labels = labels) + 
-  coord_flip() +
+  discrete_scale(labels = labels) + 
+  #coord_flip() +
   geom_text(aes(label=round(value, digits = 0)), position = position_stack(0.5), size = 3) +

### 2020-05-17 awipev-CO2.Rmd
added package hms added install.packages

--- 2020-05-07 awipev-CO2.Rmd
@@
 rm(list = ls())
+if (!require("tidyverse")) install.packages("tidyverse")
 library(tidyverse)
-library(robfilter)
-library(seacarb)
-library(gridExtra)
-library(reshape2)
-library(lubridate)
-library(lmtest)
+if (!require("robfilter")) install.packages("robfilter")
+if (!require("robfilter")) install.packages("robfilter")
+library("robfilter")
+if (!require("seacarb")) install.packages("seacarb")
+library("seacarb")
+if (!require("gridExtra")) install.packages("gridExtra")
+library("gridExtra")
+if (!require("reshape2")) install.packages("reshape2")
+library("reshape2")
+if (!require("lubridate")) install.packages("lubridate")
+library("lubridate")
+if (!require("lmtest")) install.packages("lmtest")
+library("lmtest")
+if (!require("grid")) install.packages("grid")
 library(grid)
-library(viridis)
-library(dygraphs)
+if (!require("viridis")) install.packages("viridis")
+library("viridis")
+if (!require("dygraphs")) install.packages("dygraphs")
+library("dygraphs")
+if (!require("knitr")) install.packages("knitr")
 require("knitr")
+if (!require("lmodel2")) install.packages("lmodel2")
 library("lmodel2")
-library(captioner)
-library(xts)
-library(seismicRoll)
-library(scales)
-library(plotly)
-library(htmlwidgets)
+if (!require("captioner")) install.packages("captioner")
+library("captioner")
+if (!require("xts")) install.packages("xts")
+library("xts")
+if (!require("seismicRoll")) install.packages("seismicRoll")
+library("seismicRoll")
+if (!require("scales")) install.packages("scales")
+library("scales")
+# if (!require("plotly")) install.packages("plotly")
+# library(plotly)
+if (!require("htmlwidgets")) install.packages("htmlwidgets")
+library("htmlwidgets")
+if (!require("hms")) install.packages("hms")
+library("hms")
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
+```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
 d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
@@
   dplyr::mutate(month = month(month(datetime)))
-
+d_all <
 ```
@@
 # creat a new df to calculate the diff between replicate
- diff <- d %>%
+ diff <- d_all %>%
     group_by(datetime) %>%
@@
     + sudo R (then password)
-    + install.packages (tidyverse")
+    + install.packages("tidyverse")
 

### 2020-05-17 awipev-CO2.Rmd
added as.POSIXct(...) for all datetime

@@
   dplyr::mutate(month = month(month(datetime)))
-d_all <
+#d_all <
 ```
@@
 d <- d%>%
-  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00"|datetime == "2019-05-31 11:45:00", 1, 0)
-  )
-d <- d%>%
-  dplyr::filter(location_flag== 0)
+  dplyr::mutate(location_flag = ifelse(datetime == as.POSIXct("2016-04-21 09:25:00") | 
+                                         datetime == as.POSIXct("2016-02-10 14:00:00") | 
+                                         datetime == as.POSIXct("2016-02-17 09:20:00") |
+                                         datetime == as.POSIXct("2016-02-24 14:20:00") |
+                                         datetime == as.POSIXct("2016-02-04 09:30:00") |
+                                         datetime == as.POSIXct("2016-01-27 15:00:00") |
+                                         datetime == as.POSIXct("2016-01-13 13:45:00") |
+                                         datetime == as.POSIXct("2016-01-06 14:10:00") |
+                                         datetime == as.POSIXct("2015-12-24 10:45:00") |
+                                         datetime == as.POSIXct("2015-12-30 13:30:00") |
+                                         datetime == as.POSIXct("2018-01-05 15:20:00") |
+                                         datetime == as.POSIXct("2018-02-02 14:35:00") |
+                                         datetime == as.POSIXct("2018-03-02 14:10:00") |
+                                         datetime == as.POSIXct("2019-05-31 11:45:00"), 
+                                       1, 0))
+d <- d %>%
+  dplyr::filter(location_flag == 0)
 
@@
 # durafet and seafet started later
-x <- filter(d, datetime >= "2017-08-29 10:00:00")
+x <- filter(d, datetime >= as.POSIXct("2017-08-29 10:00:00"))
 #s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
 s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
-x <- filter(d, datetime >= "2017-08-24 19:00:00")
+x <- filter(d, datetime >= as.POSIXct("2017-08-24 19:00:00"))
 s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
@@
 d_all <- d_all %>%
-  dplyr::mutate(temp_fb = ifelse(datetime >= "2017-03-22 08:00:00" & datetime <= "2017-03-23 16:00:00", NA, temp_fb),
-                temp_fb = ifelse(temp_fb >15, NA, temp_fb))
-
+  dplyr::mutate(
+    temp_fb = ifelse(
+      datetime >= as.POSIXct("2017-03-22 08:00:00") &
+        datetime <= as.POSIXct("2017-03-23 16:00:00"),
+      NA,
+      temp_fb
+    ),
+    temp_fb = ifelse(temp_fb > 15, NA, temp_fb)
+  )
 fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)
@@
 ```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
-TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
-              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00", "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
+TAevents <- as.POSIXct(c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
+              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00",
+              "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(),
+              "%Y-%m-%d %H:%M:%S")))
 at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, at)
@@
 # set deployment period when seaFET is in/out of water
-sfinterv <- c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00")
+sfinterv <- as.POSIXct(c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00"))
 
@@
                                 ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02,
-                                ifelse(datetime >= sfinterv[3] , 03,NA ))))
+                                ifelse(datetime >= sfinterv[3], 03, NA ))))
 
@@
 # (1)
-d_all$phINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phINT < 8.04, NA, d_all$phINT) 
-d_all$phEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phEXT < 8.04, NA, d_all$phEXT) 
-d_all$voltINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltINT < -0.9439, NA, d_all$voltINT) 
-d_all$voltEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
+d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
+                        d_all$datetime <= as.POSIXct("2018-01-08") &
+                        d_all$phINT < 8.04, NA, d_all$phINT)
+d_all$phEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
+                       d_all$datetime <= as.POSIXct("2018-01-08") &
+                       d_all$phEXT < 8.04, NA, d_all$phEXT) 
+d_all$voltINT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
+                         d_all$datetime <= as.POSIXct("2018-01-08") &
+                         d_all$voltINT < -0.9439, NA, d_all$voltINT) 
+d_all$voltEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
+                         d_all$datetime <= as.POSIXct("2018-01-08") &
+                         d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
 # (2)
-d_all$voltINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltINT)
-d_all$voltEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltEXT)
-d_all$phINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phINT)
-d_all$phEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phEXT)
+d_all$voltINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
+                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"), 
+                        NA, d_all$voltINT)
+d_all$voltEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
+                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
+                        NA, d_all$voltEXT)
+d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
+                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
+                      NA, d_all$phINT)
+d_all$phEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
+                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
+                      NA, d_all$phEXT)
 # (3)
-d_all$voltINT <- ifelse(d_all$datetime == "2017-11-02 21:00:00" | d_all$datetime == "2018-04-18 14:00:00", NA, d_all$voltINT)
-
+d_all$voltINT <- ifelse(d_all$datetime == as.POSIXct("2017-11-02 21:00:00") |
+                          d_all$datetime == as.POSIXct("2018-04-18 14:00:00"),
+                        NA, d_all$voltINT)
 #periode 1, mean of 4 next hours for volt int + T seaF
-mean_voltINT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
-  dplyr::summarise( mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- d_all %>%
+  dplyr::filter(
+    datetime >= as.POSIXct("2017-08-24 19:00:00") &
+      datetime <= as.POSIXct("2017-08-24 22:00:00")
+  ) %>%
+  dplyr::summarise(mean(voltINT, na.rm = TRUE))
 mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltINT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltINT_4h, voltINT))
-
-mean_voltEXT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
-  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
+d_all <- d_all %>%
+  dplyr::mutate(voltINT = ifelse(
+    datetime == as.POSIXct("2017-08-24 13:00:00"),
+    mean_voltINT_4h,
+    voltINT
+  ))
+mean_voltEXT_4h <- d_all %>%
+  dplyr::filter(
+    datetime >= as.POSIXct("2017-08-24 19:00:00") &
+      datetime <= as.POSIXct("2017-08-24 22:00:00")
+  ) %>%
+  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
 mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltEXT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltEXT_4h, voltEXT))
-
-mean_TseaF_4h <- d_all%>%
-  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
-  dplyr::summarise( mean(temp_sf, na.rm = TRUE))
+d_all <- d_all %>%
+  dplyr::mutate(voltEXT = ifelse(
+    datetime == as.POSIXct("2017-08-24 13:00:00"),
+    mean_voltEXT_4h,
+    voltEXT
+  ))
+mean_TseaF_4h <- d_all %>%
+  dplyr::filter(
+    datetime >= as.POSIXct("2017-08-24 19:00:00") &
+      datetime <= as.POSIXct("2017-08-24 22:00:00")
+  ) %>%
+  dplyr::summarise(mean(temp_sf, na.rm = TRUE))
 mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
-d_all <- d_all%>%
-  dplyr::mutate(temp_mix = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_mix))
-
+d_all <- d_all %>%
+  dplyr::mutate(temp_mix = ifelse(
+    datetime == as.POSIXct("2017-08-24 13:00:00"),
+    mean_TseaF_4h,
+    temp_mix
+  ))
 # Periode 2, mean of 4 next hours for volt int + T seaF
-mean_voltINT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
-  dplyr::summarise( mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- d_all %>%
+  dplyr::filter(
+    datetime >= as.POSIXct("2017-09-28 15:00:00") &
+      datetime <= as.POSIXct("2017-09-28 18:00:00")
+  ) %>%
+  dplyr::summarise(mean(voltINT, na.rm = TRUE))
 mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltINT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltINT_4h, voltINT))
-
-mean_voltEXT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
-  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
+d_all <- d_all %>%
+  dplyr::mutate(voltINT = ifelse(
+    datetime == as.POSIXct("2017-09-28 13:00:00"),
+    mean_voltINT_4h,
+    voltINT
+  ))
+mean_voltEXT_4h <- d_all %>%
+  dplyr::filter(
+    datetime >= as.POSIXct("2017-09-28 15:00:00") &
+      datetime <= as.POSIXct("2017-09-28 18:00:00")
+  ) %>%
+  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
 mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltEXT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltEXT_4h, voltEXT))
-
+d_all <- d_all %>%
+  dplyr::mutate(voltEXT = ifelse(
+    datetime == as.POSIXct("2017-09-28 13:00:00"),
+    mean_voltEXT_4h,
+    voltEXT
+  ))
 # period 03, mean of 4 previous hours for volt int + volt ext
-mean_voltINT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
-  dplyr::summarise( mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- d_all %>%
+  dplyr::filter(
+    datetime >= as.POSIXct("2019-09-13 04:00:00") &
+      datetime <= as.POSIXct("2019-09-13 07:00:00")
+  ) %>%
+  dplyr::summarise(mean(voltINT, na.rm = TRUE))
 mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltINT_4h, voltINT))
-
-mean_voltEXT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
-  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
+d_all <- d_all %>%
+  dplyr::mutate(voltINT = ifelse(
+    datetime == as.POSIXct("2019-09-13 08:00:00"),
+    mean_voltINT_4h,
+    voltINT
+  ))
+mean_voltEXT_4h <- d_all %>%
+  dplyr::filter(
+    datetime >= as.POSIXct("2019-09-13 04:00:00") &
+      datetime <= as.POSIXct("2019-09-13 07:00:00")
+  ) %>%
+  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
 mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltEXT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltEXT_4h, voltEXT))
-
+d_all <- d_all %>%
+  dplyr::mutate(voltEXT = ifelse(
+    datetime == as.POSIXct("2019-09-13 08:00:00"),
+    mean_voltEXT_4h,
+    voltEXT
+  ))
 # period 04 also, mean of 4 previous hours for volt int + volt ext + T seaF
-mean_voltINT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
-  dplyr::summarise( mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- d_all %>%
+  dplyr::filter(
+    datetime >= as.POSIXct("2019-09-13 11:00:00") &
+      datetime <= as.POSIXct("2019-09-13 12:00:00")
+  ) %>%
+  dplyr::summarise(mean(voltINT, na.rm = TRUE))
 mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltINT_4h, voltINT))
-
-mean_voltEXT_4h <- d_all%>%
-  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
-  dplyr::summarise( mean(voltINT, na.rm = TRUE))
+d_all <- d_all %>%
+  dplyr::mutate(voltINT = ifelse(
+    datetime == as.POSIXct("2019-09-13 13:00:00"),
+    mean_voltINT_4h,
+    voltINT
+  ))
+mean_voltEXT_4h <- d_all %>%
+  dplyr::filter(
+    datetime >= as.POSIXct("2019-09-13 11:00:00") &
+      datetime <= as.POSIXct("2019-09-13 12:00:00")
+  ) %>%
+  dplyr::summarise(mean(voltINT, na.rm = TRUE))
 mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-d_all <- d_all%>%
-  dplyr::mutate(voltEXT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltEXT_4h, voltEXT))
-
-mean_TseaF_4h <- d_all%>%
-  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
-  dplyr::summarise( mean(temp_sf, na.rm = TRUE))
+d_all <- d_all %>%
+  dplyr::mutate(voltEXT = ifelse(
+    datetime == as.POSIXct("2019-09-13 13:00:00"),
+    mean_voltEXT_4h,
+    voltEXT
+  ))
+mean_TseaF_4h <- d_all %>%
+  dplyr::filter(
+    datetime >= as.POSIXct("2019-09-13 11:00:00") &
+      datetime <= as.POSIXct("2019-09-13 12:00:00")
+  ) %>%
+  dplyr::summarise(mean(temp_sf, na.rm = TRUE))
 mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
-d_all <- d_all%>%
-  dplyr::mutate(temp_mix = ifelse(datetime == "2019-09-13 13:00:00" , mean_TseaF_4h, temp_mix))
+d_all <- d_all %>%
+  dplyr::mutate(temp_mix = ifelse(
+    datetime == as.POSIXct("2019-09-13 13:00:00"),
+    mean_TseaF_4h,
+    temp_mix
+  ))
 
 #interpolation of salinity during the FB off maintenance
-salinterp <-approx(d_all$datetime, d_all$sal_mix, xout=d_all$datetime, method="linear", rule=2)
+salinterp <-
+  approx(
+    d_all$datetime,
+    d_all$sal_mix,
+    xout = d_all$datetime,
+    method = "linear",
+    rule = 2
+  )
 names(salinterp) <- c("datetime", "sal_mix_interp")
@@
 d_all <- d_all %>%
-  dplyr::mutate(sal_mix_interp =  ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-16 16:00:00", sal_mix_interp, sal_mix))
+  dplyr::mutate(
+    sal_mix_interp =  ifelse(
+      datetime > as.POSIXct("2018-03-09 00:00:00") &
+        datetime < as.POSIXct("2018-04-16 16:00:00"),
+      sal_mix_interp,
+      sal_mix
+    )
+  )
 
@@
 # add spectro points that are not taking into consideration
-d_all <- d_all%>%
-  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 10:00:00" | datetime == "2019-01-18 11:00:00", ph_s_sf_temp_mix, NA))
+d_all <- d_all %>%
+  dplyr::mutate(
+    pH_s_sf_no_calb = ifelse(
+      datetime == as.POSIXct("2018-04-16 07:00:00") |
+        datetime == as.POSIXct("2018-12-14 10:00:00") |
+        datetime == as.POSIXct("2019-01-18 11:00:00"),
+      ph_s_sf_temp_mix,
+      NA
+    )
+  )
 
@@
 # Remove outliers from 2018-07-10 00:00 to 05:00
-d_all$ph_dur_corr <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$ph_dur_corr)
-d_all$ph_dur <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$ph_dur)
+d_all$ph_dur_corr <-
+  ifelse(
+    d_all$datetime >= as.POSIXct("2018-07-10 00:00:00") &
+      d_all$datetime <= as.POSIXct("2018-07-10 05:00:00"),
+    NA,
+    d_all$ph_dur_corr
+  )
+d_all$ph_dur <-
+  ifelse(
+    d_all$datetime >= as.POSIXct("2018-07-10 00:00:00") &
+      d_all$datetime <= as.POSIXct("2018-07-10 05:00:00"),
+    NA,
+    d_all$ph_dur
+  )
 
@@
 # add spectro points that are not taking into consideration
-d_all <- d_all%>%
-  dplyr::mutate( pH_s_dur_no_calb = ifelse(datetime == "2017-08-24 13:00:00", ph_s_dur_temp_fb, NA ))
+d_all <- d_all %>%
+  dplyr::mutate(pH_s_dur_no_calb = ifelse(
+    datetime == as.POSIXct("2017-08-24 13:00:00"),
+    ph_s_dur_temp_fb,
+    NA
+  ))
 
@@
   dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd_9m), !is.na(sal_insitu_ctd_9m)) %>%
-  dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
+  dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
 pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
@@
                  ct_diff = abs(ct - lag(ct)))
+ diff <- d_all %>%
+    group_by(datetime) %>%
+   dplyr::select(datetime, at, ct)%>%   
+   dplyr::mutate(at_diff = abs(at - lag(at)),
+                 ct_diff = abs(ct - lag(ct)))
 
@@
 # to create periods according to SNAPCO analysis 
-snapcoevents <- c("2015-07-23 00:00:00", "2015-11-18 00:00:00", "2015-11-27 00:00:00", "2016-10-13 00:00:00", 
-              "2017-05-11 00:00:00", "2018-02-09 00:00:00", "2018-02-16 00:00:00", "2018-07-27 00:00:00", "2018-08-03 00:00:00", "2018-11-23 00:00:00", "2018-11-30 00:00:00", "2019-04-12 00:00:00","2019-08-31 23:59:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
+snapcoevents <-
+  as.POSIXct(
+    c(
+      "2015-07-23 00:00:00",
+      "2015-11-18 00:00:00",
+      "2015-11-27 00:00:00",
+      "2016-10-13 00:00:00",
+      "2017-05-11 00:00:00",
+      "2018-02-09 00:00:00",
+      "2018-02-16 00:00:00",
+      "2018-07-27 00:00:00",
+      "2018-08-03 00:00:00",
+      "2018-11-23 00:00:00",
+      "2018-11-30 00:00:00",
+      "2019-04-12 00:00:00",
+      "2019-08-31 23:59:00",
+      format(Sys.Date(), "%Y-%m-%d %H:%M:%S")
+    )
+  )
 

### 2020-05-17 awipev-CO2.Rmd
replaced GMT by UTC

@@
 <!--   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% -->
-<!--   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="UTC"), "HCl Changed", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="UTC"), "BCG Changed", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="UTC"), "Calibration 1", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="UTC"), "Calibration 2", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="UTC"), "TA analyser changed", labelLoc = "top", color="red") %>% -->
+<!--   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
+<!--   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="UTC"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>% -->
+<!--   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
+<!--   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="UTC"), "Calibration mode - CRM", labelLoc = "bottom") %>% -->
 <!--   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>% -->
@@
   dySeries("at", label="at (ref)",color = "red", strokeWidth = 0, pointSize=4) %>%
-  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="UTC"), "HCl Changed", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="UTC"), "BCG Changed", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="UTC"), "Calibration 1", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="UTC"), "Calibration 2", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="UTC"), "TA analyser changed", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="UTC"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="UTC"), "Calibration mode - CRM", labelLoc = "bottom") %>%
   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
   dyEvent(
-    as.POSIXct("2016-02-28 12:00:00", tz = "GMT"),
+    as.POSIXct("2016-02-28 12:00:00", tz = "UTC"),
     "CO2FT-0515-001 installed",
@@
   dyEvent(
-    as.POSIXct("2017-02-07 12:00:00", tz = "GMT"),
+    as.POSIXct("2017-02-07 12:00:00", tz = "UTC"),
     "CO2FT-0215-001 installed",
@@
   dyEvent(
-    as.POSIXct("2018-04-16 12:00:00", tz = "GMT"),
+    as.POSIXct("2018-04-16 12:00:00", tz = "UTC"),
     "CO2FT-0515-001 installed",
@@
   dyEvent(
-    as.POSIXct("2018-10-31 15:00:00", tz = "GMT"),
+    as.POSIXct("2018-10-31 15:00:00", tz = "UTC"),
     "CO2FT-0215-001 installed",
@@
   dyEvent(
-    as.POSIXct("2019-09-03 15:00:00", tz = "GMT"),
+    as.POSIXct("2019-09-03 15:00:00", tz = "UTC"),
     "CO2FT-0515-001 installed",
@@
 dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
-dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
-  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
+dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
+  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="UTC"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
+  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="UTC"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
+    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="UTC"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
   dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
@@
        dySeries("ph_s_dur_temp_fb", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
-    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="GMT"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
+    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="UTC"), "New holder installed", labelLoc = "bottom", color="red") %>% 
+    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "durafet installed", labelLoc = "bottom", color="red") %>%
+    dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="UTC"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%

### 2020-05-18 awipev-CO2.Rmd
Corrected crontab information

@@
 
-* (Every hour on the hour, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
+* (Every 4 hour on the hour, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
     + 00 *//1 * * * cd $HOME; USER=awipev R --vanilla < ny-alesund/R/ny-alesund_cc.R > ny-alesund/R/log_ny-alesund_cc.txt 2>&1
-* (Every hour at 10 min past the hour, the web page is generated)
+* (Every 4 hour at 10 min past the hour, the web page is generated)
     + 10 *//1 * * * cd web; USER=awipev bash awipev-co2.sh > awipev-web.log 2>&1 

### 2020-05-18 awipev-CO2.Rmd

@@
 + 99: failing the final visual inspection
+
+* Despike using oce::despike with n=2, k=5761
+
+    + 1: good data
+    + 3: impossible date and time test
+    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
+    + 6: failing the manufacturer range test (not used)
+    + 7: failing the regional range test 
+    + 12: failing the spike test (NAs from despike)
+    + 13: failing the gradient test
+    + 15: the instrument was not deployed or operated
+    + 99: failing the final visual inspection of the data.
 

### 2020-05-20 awipev-CO2.Rmd
More on figures Eliminate outliers visually Eliminate pH spectro when profiler was at more than 1 depth in the same hour Only use pH spectro data when profiler was below 6 m

@@
 
-mytheme <- theme_bw() +
-  theme(axis.text.x=element_text(size=16, color="black"),
-        axis.title.x=element_text(face="bold", size=16),
-        axis.text.y=element_text(size=16, color="black"),
-        axis.title.y=element_text(face="bold", size=16),
-        plot.title = element_text(face="bold", size=14)
-)
-
 #################### Function RMSE root mean square error
@@
 ```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
-d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
+d_hour <-
+  readRDS(file = paste0(
+    path,
+    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
+  ))
 d_hour <- d_hour %>%
-  dplyr::select(-date) %>%
-  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
+  dplyr::rename(
+    pco2_corr = pco2_corr_filtered,
+    temp_dur = temp_dur_filtered,
+    pco2_raw = pco2_raw_filtered,
+    sal_fb = sal_fb_filtered,
+    temp_insitu_11m = temp_insitu_11m_filtered,
+    temp_fb = temp_fb_filtered,
+    ph_dur = ph_dur_filtered
+  )
 d_all <- d_hour #d_all will be the merger
-d_all<- d_all%>%
-  dplyr::mutate(month = month(month(datetime)))
-#d_all <
+d_all <- d_all %>%
+  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
+  dplyr::mutate(month = month(month(datetime))) %>%
+  dplyr::rowwise() %>% 
+  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
+  c(
+    sal_insitu_ctd_1m,
+    sal_insitu_ctd_3m,
+    sal_insitu_ctd_5m,
+    sal_insitu_ctd_7m,
+    sal_insitu_ctd_9m
+  )
+), na.rm = TRUE))
+#restore datetime and date which are mangled by the murtates above
+d_all$datetime <- d_hour$datetime
+d_all$date <- d_hour$date
 ```
@@
 ```{r Combine discrete and continous data, echo=FALSE}
-
 # at
@@
 d_all <- full_join(d_all, discrete2merge, by="datetime")
+d_all <- d_all %>% 
+  dplyr::mutate(ph_s_sf_temp_mix = ifelse(n_depth_ctd == 4, ph_s_sf_temp_mix, NA)) %>% # eliminate ph spectro data when the profiler was at several depth during the same hour
+  dplyr::mutate(ph_s_sf_temp_mix = ifelse(!is.na(temp_insitu_ctd_7m) | !is.na(temp_insitu_ctd_9m), 
+                                          ph_s_sf_temp_mix, NA)) # only use ph spectro data when profiler was below 6 m
+
 discrete2merge <- discrete %>%
@@
 If data gaps are encountered, they are filled with bottom salinty data from ctd (> 8 m).
-New column "sal_mix" is created.
+New column "sal_mix" is created and is the one used in ESSD paper.
 
 - 1 SBE45 inside the Ferrybox (sal_fb)
-- 5 CTD > 8 meters depth (sal_insitu_ctd)
-
-### **Depth profile**
-
-```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-# SAL FerryBox
-sal_xts <- dplyr::select(d_all, datetime, sal_fb)
+- 5 CTD > 8 m depth (sal_insitu_ctd)
+
+```{r Salinity, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+# SAL FerryBox and sal_mix
+sal_xts <- dplyr::select(d_all, datetime, sal_fb, sal_mix)
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
@@
             dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
+            dySeries("sal_mix", color = "red", strokeWidth = 0, label = "sal_mix") %>%
 dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
       dyRangeSelector(height = 30, dateWindow= NULL)
+# now remove outliers
+d_all <- d_all %>%
+  dplyr::mutate(
+    sal_mix = case_when(
+      date > as.Date("2016-02-01") &
+        date <  as.Date("2016-02-09") & sal_mix < 34 ~ NA_real_,
+      date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
+      date > as.Date("2015-10-01") &
+        date <  as.Date("2015-10-05") & sal_mix < 31.5 ~ NA_real_,
+      date == as.Date("2017-03-22") &
+        sal_mix < 34 ~ NA_real_,
+      TRUE ~ sal_mix
+    )
+  )
+```
+
+### **Depth profile**
+
+```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+
 #SAL CTD profile
@@
   dyRangeSelector(height = 30, dateWindow = NULL)
+
+# now remove outliers
+d_all <- d_all %>%
+  dplyr::mutate(
+    pco2_corr = case_when(
+      date > as.Date("2016-04-01") &
+        date <  as.Date("2017-02-05") & pco2_corr > 400 ~ NA_real_,
+      #date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
+      date > as.Date("2017-08-01") &
+        date <  as.Date("2017-09-30") & pco2_corr > 300 ~ NA_real_,
+      #date == as.Date("2017-03-22") & sal_mix < 34 ~ NA_real_,
+      TRUE ~ pco2_corr
+    )
+  )
 ```
@@
 
-# add spectro points that are not taking into consideration
+# add spectro points that cannot be taken into consideration (some ancillary data T and/or S not available)
+# shown as white triangles on the plot
 d_all <- d_all %>%
@@
 
+# now remove outliers
+d_all <- d_all %>%
+  dplyr::mutate(
+    ph_dur_corr = case_when(
+          ph_dur_corr < 8 ~ NA_real_,
+      date > as.Date("2018-05-18") &
+        date <  as.Date("2018-05-19") & ph_dur_corr < 8.16 ~ NA_real_,
+      #date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
+      date > as.Date("2017-09-25") &
+        date <  as.Date("2017-10-01") & ph_dur_corr < 8.07 ~ NA_real_,
+      #date == as.Date("2017-03-22") & sal_mix < 34 ~ NA_real_,
+      TRUE ~ ph_dur_corr
+    )
+  )
+
 # RANGE of pH
@@
 ```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-# remove sf biofouling period
+# prepare data and remove sf biofouling period
 pH_sf <- d_all %>%
@@
   dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
+
 pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
@@
 saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
+```
+
+## Figures for ESSD paper
+
+```{r figures for ESSD paper, echo=FALSE, message= FALSE, warning=FALSE}
+Mytheme <- function(size_labs = 6, face_font="plain", ...) {
+  theme_bw() +
+  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
+        axis.title.x = element_text(face="bold", size=size_labs, margin=margin(0,0,0,0,"pt")),
+        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
+        axis.title.y = element_text(face="bold", size=size_labs),
+        axis.ticks.x = element_line(size=0.1),
+        axis.ticks.y = element_line(size=0.1),
+        axis.ticks.length = unit(1.1, "mm"),
+        panel.grid.major = element_line(size = 0.25, color="black", linetype="dotted"),
+        aspect.ratio = 1 / 3,
+        plot.margin = margin(t = 0, r = 1.5, b = 0, l = 1.5, unit = "lines")
+  )
+}
+# select time series data
+d <- as_tibble(d_all) %>%
+  dplyr::select(datetime, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, ph_dur_corr, at_calc)
+# time series temp
+ts_temp <- d %>%
+  dplyr::filter(!is.na(temp_insitu_11m)) %>% 
+ggplot() +
+  geom_point(aes(x = datetime, y = temp_insitu_11m), col = "blue", size = 0.15) +
+  labs(title = "", x = "Time", y = "In situ temperature (°C)") +
+  Mytheme(size_labs = 8)
+ggsave(filename = "figures/ts_temp.png")
+print(ts_temp) 
+# time series sal
+ts_sal <- d %>%
+  dplyr::filter(!is.na(sal_mix)) %>% 
+ggplot() +
+  geom_point(aes(x = datetime, y = sal_mix), col = "blue", size = 0.15) +
+  labs(title = "", x = "Time", y = "Salinity") +
+  Mytheme(size_labs = 8)
+ggsave(filename = "figures/ts_sal.png")
+print(ts_sal) 
+# time series pco2
+ts_pco2 <- d %>%
+  dplyr::filter(!is.na(pco2_corr)) %>% 
+ggplot() +
+  geom_point(aes(x = datetime, y = pco2_corr), col = "blue", size = 0.15) +
+  labs(title = "", x = "Time", y = expression(paste("C", O[2], " partial pressure (", mu, "atm)"))) +
+  Mytheme(size_labs = 8)
+ggsave(filename = "figures/ts_pco2.png")
+print(ts_pco2) 
+# time series pH
+ts_ph <- d %>%
+  dplyr::select(datetime, pHint_tot_sf, ph_dur_corr) %>%
+  dplyr::filter(!is.na(pHint_tot_sf)) %>% 
+  pivot_longer(-datetime, names_to = "pH", values_to = "value") %>%
+  ggplot() +
+  geom_point(aes(x = datetime, y = value, colour = pH), size = 0.15) +
+  labs(title = "", x = "Time", y = expression(paste("p", H[T]))) +
+  scale_color_manual(values=c("blue", "red"), 
+                       name="",
+                       breaks=c("pHint_tot_sf", "ph_dur_corr"),
+                       labels=c("SeaFET", "Durafet")) +
+  Mytheme(size_labs = 8)
+print(ts_ph)
+
+ggsave(filename = "figures/ts_ph.png")
+
 ```

### 2020-05-20 awipev-CO2.Rmd
one pointsize parameter update

--- 2020-05-18 awipev-CO2.Rmd
@@
 rm(list = ls())
-if (!require("tidyverse")) install.packages("tidyverse")
 library(tidyverse)
-if (!require("robfilter")) install.packages("robfilter")
-if (!require("robfilter")) install.packages("robfilter")
-library("robfilter")
-if (!require("seacarb")) install.packages("seacarb")
-library("seacarb")
-if (!require("gridExtra")) install.packages("gridExtra")
-library("gridExtra")
-if (!require("reshape2")) install.packages("reshape2")
-library("reshape2")
-if (!require("lubridate")) install.packages("lubridate")
-library("lubridate")
-if (!require("lmtest")) install.packages("lmtest")
-library("lmtest")
-if (!require("grid")) install.packages("grid")
+library(robfilter)
+library(seacarb)
+library(gridExtra)
+library(reshape2)
+library(lubridate)
+library(lmtest)
 library(grid)
-if (!require("viridis")) install.packages("viridis")
-library("viridis")
-if (!require("dygraphs")) install.packages("dygraphs")
-library("dygraphs")
-if (!require("knitr")) install.packages("knitr")
+library(viridis)
+library(dygraphs)
 require("knitr")
-if (!require("lmodel2")) install.packages("lmodel2")
 library("lmodel2")
-if (!require("captioner")) install.packages("captioner")
-library("captioner")
-if (!require("xts")) install.packages("xts")
-library("xts")
-if (!require("seismicRoll")) install.packages("seismicRoll")
-library("seismicRoll")
-if (!require("scales")) install.packages("scales")
-library("scales")
-# if (!require("plotly")) install.packages("plotly")
-# library(plotly)
-if (!require("htmlwidgets")) install.packages("htmlwidgets")
-library("htmlwidgets")
-if (!require("hms")) install.packages("hms")
-library("hms")
+library(captioner)
+library(xts)
+library(seismicRoll)
+library(scales)
+library(plotly)
+library(htmlwidgets)
 knitr::opts_chunk$set(echo = TRUE)
@@
 
-```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
+```{r Read and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
 d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
@@
   dplyr::mutate(month = month(month(datetime)))
-#d_all <
+
 ```
@@
 d <- d%>%
-  dplyr::mutate(location_flag = ifelse(datetime == as.POSIXct("2016-04-21 09:25:00") | 
-                                         datetime == as.POSIXct("2016-02-10 14:00:00") | 
-                                         datetime == as.POSIXct("2016-02-17 09:20:00") |
-                                         datetime == as.POSIXct("2016-02-24 14:20:00") |
-                                         datetime == as.POSIXct("2016-02-04 09:30:00") |
-                                         datetime == as.POSIXct("2016-01-27 15:00:00") |
-                                         datetime == as.POSIXct("2016-01-13 13:45:00") |
-                                         datetime == as.POSIXct("2016-01-06 14:10:00") |
-                                         datetime == as.POSIXct("2015-12-24 10:45:00") |
-                                         datetime == as.POSIXct("2015-12-30 13:30:00") |
-                                         datetime == as.POSIXct("2018-01-05 15:20:00") |
-                                         datetime == as.POSIXct("2018-02-02 14:35:00") |
-                                         datetime == as.POSIXct("2018-03-02 14:10:00") |
-                                         datetime == as.POSIXct("2019-05-31 11:45:00"), 
-                                       1, 0))
-d <- d %>%
-  dplyr::filter(location_flag == 0)
+  dplyr::mutate(location_flag = ifelse(datetime == "2016-04-21 09:25:00" | datetime == "2016-02-10 14:00:00" | datetime == "2016-02-17 09:20:00" |datetime == "2016-02-24 14:20:00" | datetime == "2016-02-04 09:30:00" |datetime == "2016-01-27 15:00:00" |datetime == "2016-01-13 13:45:00" |datetime == "2016-01-06 14:10:00" |datetime == "2015-12-24 10:45:00" |datetime == "2015-12-30 13:30:00" |datetime == "2018-01-05 15:20:00" |datetime == "2018-02-02 14:35:00"|datetime == "2018-03-02 14:10:00"|datetime == "2019-05-31 11:45:00", 1, 0)
+  )
+d <- d%>%
+  dplyr::filter(location_flag== 0)
 
@@
 ### **Data availability**
-The data at one minute frequency were tagged with the following quality flags
-
-+ 1: good data
-+ 3: failing the date and time test
-+ 4: data not usable according to manufacturer
-+ 7: failing the regional range test 
-+ 12: failing the spike test (NAs from despike)
-+ 13: failing the gradient test
-+ 15: instrument not deployed or operated
-+ 16: acid flush
-+ 99: failing the final visual inspection
-
-* Despike using oce::despike with n=2, k=5761
+TO DO: add here an horizontal bar plot showing the percent availability of the data
 
@@
 # durafet and seafet started later
-x <- filter(d, datetime >= as.POSIXct("2017-08-29 10:00:00"))
+x <- filter(d, datetime >= "2017-08-29 10:00:00")
 #s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
 s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
-x <- filter(d, datetime >= as.POSIXct("2017-08-24 19:00:00"))
+x <- filter(d, datetime >= "2017-08-24 19:00:00")
 s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
@@
 d_all <- d_all %>%
-  dplyr::mutate(
-    temp_fb = ifelse(
-      datetime >= as.POSIXct("2017-03-22 08:00:00") &
-        datetime <= as.POSIXct("2017-03-23 16:00:00"),
-      NA,
-      temp_fb
-    ),
-    temp_fb = ifelse(temp_fb > 15, NA, temp_fb)
-  )
+  dplyr::mutate(temp_fb = ifelse(datetime >= "2017-03-22 08:00:00" & datetime <= "2017-03-23 16:00:00", NA, temp_fb),
+                temp_fb = ifelse(temp_fb >15, NA, temp_fb))
+
 fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)
@@
 <!--   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% -->
-<!--   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="UTC"), "HCl Changed", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="UTC"), "BCG Changed", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="UTC"), "Calibration 1", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="UTC"), "Calibration 2", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="UTC"), "TA analyser changed", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="UTC"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="UTC"), "Calibration mode - CRM", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>% -->
+<!--   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
+<!--   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>% -->
+<!--   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
+<!--   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>% -->
+<!--   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>% -->
 <!--   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>% -->
@@
 ```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
-TAevents <- as.POSIXct(c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
-              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00",
-              "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(),
-              "%Y-%m-%d %H:%M:%S")))
+TAevents <- c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
+              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00", "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
 at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, at)
@@
   dySeries("at", label="at (ref)",color = "red", strokeWidth = 0, pointSize=4) %>%
-  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="UTC"), "HCl Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="UTC"), "BCG Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="UTC"), "Calibration 1", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="UTC"), "Calibration 2", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="UTC"), "TA analyser changed", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="UTC"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="UTC"), "Calibration mode - CRM", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="GMT"), "HCl Changed", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="GMT"), "BCG Changed", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="GMT"), "Calibration 1", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="GMT"), "Calibration 2", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="GMT"), "TA analyser changed", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="GMT"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="GMT"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
+  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="GMT"), "CRM measurement", labelLoc = "bottom") %>%
+  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="GMT"), "Calibration mode - CRM", labelLoc = "bottom") %>%
   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
   dyEvent(
-    as.POSIXct("2016-02-28 12:00:00", tz = "UTC"),
+    as.POSIXct("2016-02-28 12:00:00", tz = "GMT"),
     "CO2FT-0515-001 installed",
@@
   dyEvent(
-    as.POSIXct("2017-02-07 12:00:00", tz = "UTC"),
+    as.POSIXct("2017-02-07 12:00:00", tz = "GMT"),
     "CO2FT-0215-001 installed",
@@
   dyEvent(
-    as.POSIXct("2018-04-16 12:00:00", tz = "UTC"),
+    as.POSIXct("2018-04-16 12:00:00", tz = "GMT"),
     "CO2FT-0515-001 installed",
@@
   dyEvent(
-    as.POSIXct("2018-10-31 15:00:00", tz = "UTC"),
+    as.POSIXct("2018-10-31 15:00:00", tz = "GMT"),
     "CO2FT-0215-001 installed",
@@
   dyEvent(
-    as.POSIXct("2019-09-03 15:00:00", tz = "UTC"),
+    as.POSIXct("2019-09-03 15:00:00", tz = "GMT"),
     "CO2FT-0515-001 installed",
@@
 # set deployment period when seaFET is in/out of water
-sfinterv <- as.POSIXct(c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00"))
+sfinterv <- c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00")
 
@@
                                 ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02,
-                                ifelse(datetime >= sfinterv[3], 03, NA ))))
+                                ifelse(datetime >= sfinterv[3] , 03,NA ))))
 
@@
 # (1)
-d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
-                        d_all$datetime <= as.POSIXct("2018-01-08") &
-                        d_all$phINT < 8.04, NA, d_all$phINT)
-d_all$phEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
-                       d_all$datetime <= as.POSIXct("2018-01-08") &
-                       d_all$phEXT < 8.04, NA, d_all$phEXT) 
-d_all$voltINT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
-                         d_all$datetime <= as.POSIXct("2018-01-08") &
-                         d_all$voltINT < -0.9439, NA, d_all$voltINT) 
-d_all$voltEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
-                         d_all$datetime <= as.POSIXct("2018-01-08") &
-                         d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
+d_all$phINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phINT < 8.04, NA, d_all$phINT) 
+d_all$phEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$phEXT < 8.04, NA, d_all$phEXT) 
+d_all$voltINT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltINT < -0.9439, NA, d_all$voltINT) 
+d_all$voltEXT <-ifelse(d_all$datetime >= "2017-12-14" & d_all$datetime <= "2018-01-08" & d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
 # (2)
-d_all$voltINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
-                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"), 
-                        NA, d_all$voltINT)
-d_all$voltEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
-                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
-                        NA, d_all$voltEXT)
-d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
-                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
-                      NA, d_all$phINT)
-d_all$phEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
-                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
-                      NA, d_all$phEXT)
+d_all$voltINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltINT)
+d_all$voltEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$voltEXT)
+d_all$phINT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phINT)
+d_all$phEXT <- ifelse(d_all$datetime >= "2018-01-08 17:00:00" & d_all$datetime <= "2018-02-02 09:00:00", NA, d_all$phEXT)
 # (3)
-d_all$voltINT <- ifelse(d_all$datetime == as.POSIXct("2017-11-02 21:00:00") |
-                          d_all$datetime == as.POSIXct("2018-04-18 14:00:00"),
-                        NA, d_all$voltINT)
+d_all$voltINT <- ifelse(d_all$datetime == "2017-11-02 21:00:00" | d_all$datetime == "2018-04-18 14:00:00", NA, d_all$voltINT)
+
 #periode 1, mean of 4 next hours for volt int + T seaF
-mean_voltINT_4h <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2017-08-24 19:00:00") &
-      datetime <= as.POSIXct("2017-08-24 22:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
+  dplyr::summarise( mean(voltINT, na.rm = TRUE))
 mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-d_all <- d_all %>%
-  dplyr::mutate(voltINT = ifelse(
-    datetime == as.POSIXct("2017-08-24 13:00:00"),
-    mean_voltINT_4h,
-    voltINT
-  ))
-mean_voltEXT_4h <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2017-08-24 19:00:00") &
-      datetime <= as.POSIXct("2017-08-24 22:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
+d_all <- d_all%>%
+  dplyr::mutate(voltINT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltINT_4h, voltINT))
+
+mean_voltEXT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
+  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
 mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-d_all <- d_all %>%
-  dplyr::mutate(voltEXT = ifelse(
-    datetime == as.POSIXct("2017-08-24 13:00:00"),
-    mean_voltEXT_4h,
-    voltEXT
-  ))
-mean_TseaF_4h <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2017-08-24 19:00:00") &
-      datetime <= as.POSIXct("2017-08-24 22:00:00")
-  ) %>%
-  dplyr::summarise(mean(temp_sf, na.rm = TRUE))
+d_all <- d_all%>%
+  dplyr::mutate(voltEXT = ifelse(datetime == "2017-08-24 13:00:00" , mean_voltEXT_4h, voltEXT))
+
+mean_TseaF_4h <- d_all%>%
+  dplyr::filter(datetime >= "2017-08-24 19:00:00" & datetime <= "2017-08-24 22:00:00")%>%
+  dplyr::summarise( mean(temp_sf, na.rm = TRUE))
 mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
-d_all <- d_all %>%
-  dplyr::mutate(temp_mix = ifelse(
-    datetime == as.POSIXct("2017-08-24 13:00:00"),
-    mean_TseaF_4h,
-    temp_mix
-  ))
+d_all <- d_all%>%
+  dplyr::mutate(temp_mix = ifelse(datetime == "2017-08-24 13:00:00" , mean_TseaF_4h, temp_mix))
+
 # Periode 2, mean of 4 next hours for volt int + T seaF
-mean_voltINT_4h <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2017-09-28 15:00:00") &
-      datetime <= as.POSIXct("2017-09-28 18:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
+  dplyr::summarise( mean(voltINT, na.rm = TRUE))
 mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-d_all <- d_all %>%
-  dplyr::mutate(voltINT = ifelse(
-    datetime == as.POSIXct("2017-09-28 13:00:00"),
-    mean_voltINT_4h,
-    voltINT
-  ))
-mean_voltEXT_4h <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2017-09-28 15:00:00") &
-      datetime <= as.POSIXct("2017-09-28 18:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
+d_all <- d_all%>%
+  dplyr::mutate(voltINT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltINT_4h, voltINT))
+
+mean_voltEXT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2017-09-28 15:00:00" & datetime <= "2017-09-28 18:00:00")%>%
+  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
 mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-d_all <- d_all %>%
-  dplyr::mutate(voltEXT = ifelse(
-    datetime == as.POSIXct("2017-09-28 13:00:00"),
-    mean_voltEXT_4h,
-    voltEXT
-  ))
+d_all <- d_all%>%
+  dplyr::mutate(voltEXT = ifelse(datetime == "2017-09-28 13:00:00" , mean_voltEXT_4h, voltEXT))
+
 # period 03, mean of 4 previous hours for volt int + volt ext
-mean_voltINT_4h <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2019-09-13 04:00:00") &
-      datetime <= as.POSIXct("2019-09-13 07:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
+  dplyr::summarise( mean(voltINT, na.rm = TRUE))
 mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-d_all <- d_all %>%
-  dplyr::mutate(voltINT = ifelse(
-    datetime == as.POSIXct("2019-09-13 08:00:00"),
-    mean_voltINT_4h,
-    voltINT
-  ))
-mean_voltEXT_4h <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2019-09-13 04:00:00") &
-      datetime <= as.POSIXct("2019-09-13 07:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
+d_all <- d_all%>%
+  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltINT_4h, voltINT))
+
+mean_voltEXT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2019-09-13 04:00:00" & datetime <= "2019-09-13 07:00:00")%>%
+  dplyr::summarise( mean(voltEXT, na.rm = TRUE))
 mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-d_all <- d_all %>%
-  dplyr::mutate(voltEXT = ifelse(
-    datetime == as.POSIXct("2019-09-13 08:00:00"),
-    mean_voltEXT_4h,
-    voltEXT
-  ))
+d_all <- d_all%>%
+  dplyr::mutate(voltEXT = ifelse(datetime == "2019-09-13 08:00:00" , mean_voltEXT_4h, voltEXT))
+
 # period 04 also, mean of 4 previous hours for volt int + volt ext + T seaF
-mean_voltINT_4h <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2019-09-13 11:00:00") &
-      datetime <= as.POSIXct("2019-09-13 12:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
+  dplyr::summarise( mean(voltINT, na.rm = TRUE))
 mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-d_all <- d_all %>%
-  dplyr::mutate(voltINT = ifelse(
-    datetime == as.POSIXct("2019-09-13 13:00:00"),
-    mean_voltINT_4h,
-    voltINT
-  ))
-mean_voltEXT_4h <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2019-09-13 11:00:00") &
-      datetime <= as.POSIXct("2019-09-13 12:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltINT, na.rm = TRUE))
+d_all <- d_all%>%
+  dplyr::mutate(voltINT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltINT_4h, voltINT))
+
+mean_voltEXT_4h <- d_all%>%
+  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
+  dplyr::summarise( mean(voltINT, na.rm = TRUE))
 mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-d_all <- d_all %>%
-  dplyr::mutate(voltEXT = ifelse(
-    datetime == as.POSIXct("2019-09-13 13:00:00"),
-    mean_voltEXT_4h,
-    voltEXT
-  ))
-mean_TseaF_4h <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2019-09-13 11:00:00") &
-      datetime <= as.POSIXct("2019-09-13 12:00:00")
-  ) %>%
-  dplyr::summarise(mean(temp_sf, na.rm = TRUE))
+d_all <- d_all%>%
+  dplyr::mutate(voltEXT = ifelse(datetime == "2019-09-13 13:00:00" , mean_voltEXT_4h, voltEXT))
+
+mean_TseaF_4h <- d_all%>%
+  dplyr::filter(datetime >= "2019-09-13 11:00:00" & datetime <= "2019-09-13 12:00:00")%>%
+  dplyr::summarise( mean(temp_sf, na.rm = TRUE))
 mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
-d_all <- d_all %>%
-  dplyr::mutate(temp_mix = ifelse(
-    datetime == as.POSIXct("2019-09-13 13:00:00"),
-    mean_TseaF_4h,
-    temp_mix
-  ))
+d_all <- d_all%>%
+  dplyr::mutate(temp_mix = ifelse(datetime == "2019-09-13 13:00:00" , mean_TseaF_4h, temp_mix))
 
 #interpolation of salinity during the FB off maintenance
-salinterp <-
-  approx(
-    d_all$datetime,
-    d_all$sal_mix,
-    xout = d_all$datetime,
-    method = "linear",
-    rule = 2
-  )
+salinterp <-approx(d_all$datetime, d_all$sal_mix, xout=d_all$datetime, method="linear", rule=2)
 names(salinterp) <- c("datetime", "sal_mix_interp")
@@
 d_all <- d_all %>%
-  dplyr::mutate(
-    sal_mix_interp =  ifelse(
-      datetime > as.POSIXct("2018-03-09 00:00:00") &
-        datetime < as.POSIXct("2018-04-16 16:00:00"),
-      sal_mix_interp,
-      sal_mix
-    )
-  )
+  dplyr::mutate(sal_mix_interp =  ifelse(datetime > "2018-03-09 00:00:00" & datetime < "2018-04-16 16:00:00", sal_mix_interp, sal_mix))
 
@@
 # add spectro points that are not taking into consideration
-d_all <- d_all %>%
-  dplyr::mutate(
-    pH_s_sf_no_calb = ifelse(
-      datetime == as.POSIXct("2018-04-16 07:00:00") |
-        datetime == as.POSIXct("2018-12-14 10:00:00") |
-        datetime == as.POSIXct("2019-01-18 11:00:00"),
-      ph_s_sf_temp_mix,
-      NA
-    )
-  )
+d_all <- d_all%>%
+  dplyr::mutate( pH_s_sf_no_calb = ifelse(datetime == "2018-04-16 07:00:00" | datetime == "2018-12-14 10:00:00" | datetime == "2019-01-18 11:00:00", ph_s_sf_temp_mix, NA))
 
@@
 dygraph(seafet_depth_xts, group = "depth", main="pH seaFET (ref + corrected + raw)", ylab="pHT") %>%
-dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 3) %>%
+dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
 dySeries("ph_s_sf_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
 dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
-dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="UTC"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
-  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="UTC"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="UTC"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
+dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
+  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="GMT"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
+  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="GMT"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
+    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="GMT"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
   dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
@@
 # Remove outliers from 2018-07-10 00:00 to 05:00
-d_all$ph_dur_corr <-
-  ifelse(
-    d_all$datetime >= as.POSIXct("2018-07-10 00:00:00") &
-      d_all$datetime <= as.POSIXct("2018-07-10 05:00:00"),
-    NA,
-    d_all$ph_dur_corr
-  )
-d_all$ph_dur <-
-  ifelse(
-    d_all$datetime >= as.POSIXct("2018-07-10 00:00:00") &
-      d_all$datetime <= as.POSIXct("2018-07-10 05:00:00"),
-    NA,
-    d_all$ph_dur
-  )
+d_all$ph_dur_corr <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$ph_dur_corr)
+d_all$ph_dur <- ifelse(d_all$datetime >= "2018-07-10 00:00:00" & d_all$datetime <= "2018-07-10 05:00:00", NA, d_all$ph_dur)
 
@@
 # add spectro points that are not taking into consideration
-d_all <- d_all %>%
-  dplyr::mutate(pH_s_dur_no_calb = ifelse(
-    datetime == as.POSIXct("2017-08-24 13:00:00"),
-    ph_s_dur_temp_fb,
-    NA
-  ))
+d_all <- d_all%>%
+  dplyr::mutate( pH_s_dur_no_calb = ifelse(datetime == "2017-08-24 13:00:00", ph_s_dur_temp_fb, NA ))
 
@@
        dySeries("ph_s_dur_temp_fb", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
-    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="UTC"), "New holder installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "durafet installed", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="UTC"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
+    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="GMT"), "New holder installed", labelLoc = "bottom", color="red") %>% 
+    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="GMT"), "durafet installed", labelLoc = "bottom", color="red") %>%
+    dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="GMT"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
   dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd_9m), !is.na(sal_insitu_ctd_9m)) %>%
-  dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
+  dplyr::filter(datetime< "2018-01-01" | datetime> "2018-02-03")
 pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
@@
 # creat a new df to calculate the diff between replicate
- diff <- d_all %>%
-    group_by(datetime) %>%
-   dplyr::select(datetime, at, ct)%>%   
-   dplyr::mutate(at_diff = abs(at - lag(at)),
-                 ct_diff = abs(ct - lag(ct)))
- diff <- d_all %>%
+ diff <- d %>%
     group_by(datetime) %>%
@@
 # to create periods according to SNAPCO analysis 
-snapcoevents <-
-  as.POSIXct(
-    c(
-      "2015-07-23 00:00:00",
-      "2015-11-18 00:00:00",
-      "2015-11-27 00:00:00",
-      "2016-10-13 00:00:00",
-      "2017-05-11 00:00:00",
-      "2018-02-09 00:00:00",
-      "2018-02-16 00:00:00",
-      "2018-07-27 00:00:00",
-      "2018-08-03 00:00:00",
-      "2018-11-23 00:00:00",
-      "2018-11-30 00:00:00",
-      "2019-04-12 00:00:00",
-      "2019-08-31 23:59:00",
-      format(Sys.Date(), "%Y-%m-%d %H:%M:%S")
-    )
-  )
+snapcoevents <- c("2015-07-23 00:00:00", "2015-11-18 00:00:00", "2015-11-27 00:00:00", "2016-10-13 00:00:00", 
+              "2017-05-11 00:00:00", "2018-02-09 00:00:00", "2018-02-16 00:00:00", "2018-07-27 00:00:00", "2018-08-03 00:00:00", "2018-11-23 00:00:00", "2018-11-30 00:00:00", "2019-04-12 00:00:00","2019-08-31 23:59:00", format(Sys.Date(), "%Y-%m-%d %H:%M:%S"))
 
@@
     + sudo R (then password)
-    + install.packages("tidyverse")
+    + install.packages (tidyverse")
 
@@
 
-* (Every 4 hour on the hour, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
+* (Every hour on the hour, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
     + 00 *//1 * * * cd $HOME; USER=awipev R --vanilla < ny-alesund/R/ny-alesund_cc.R > ny-alesund/R/log_ny-alesund_cc.txt 2>&1
-* (Every 4 hour at 10 min past the hour, the web page is generated)
+* (Every hour at 10 min past the hour, the web page is generated)
     + 10 *//1 * * * cd web; USER=awipev bash awipev-co2.sh > awipev-web.log 2>&1 

### 2020-05-20 awipev-CO2.Rmd
Now use sal_insitu_ctd_interp instead of sal_mix_interp

--- 2020-05-20 awipev-CO2.Rmd
@@
 
-#interpolation of salinity during the FB off maintenance
+#interpolation of salinity during gaps
 salinterp <-
@@
     d_all$datetime,
-    d_all$sal_mix,
+    d_all$sal_insitu_ctd,
     xout = d_all$datetime,
@@
   )
-names(salinterp) <- c("datetime", "sal_mix_interp")
+names(salinterp) <- c("datetime", "sal_insitu_ctd_interp")
 salinterp <- as.data.frame(salinterp)
-d_all$sal_mix_interp <- salinterp$sal_mix_interp
+d_all$sal_insitu_ctd_interp <- salinterp$sal_insitu_ctd_interp
 
@@
   dplyr::mutate(
-    sal_mix_interp =  ifelse(
-      datetime > as.POSIXct("2018-03-09 00:00:00") &
-        datetime < as.POSIXct("2018-04-16 16:00:00"),
-      sal_mix_interp,
-      sal_mix
+    sal_insitu_ctd_interp =  ifelse(
+      datetime > as.POSIXct("2018-04-16 07:00:00") &
+        datetime < as.POSIXct("2018-04-24 22:00:00"),
+      sal_insitu_ctd_interp,
+      sal_insitu_ctd
     )
@@
 ####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix, calT = d_all$temp_sf, calSal = d_all$sal_mix_interp)
+calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
 # put number of deployment 
@@
 ####
-seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_mix_interp)
+seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
 

### 2020-05-20 awipev-CO2.Rmd

--- 2020-05-20 awipev-CO2.Rmd
@@
 
+mytheme <- theme_bw() +
+  theme(axis.text.x=element_text(size=16, color="black"),
+        axis.title.x=element_text(face="bold", size=16),
+        axis.text.y=element_text(size=16, color="black"),
+        axis.title.y=element_text(face="bold", size=16),
+        plot.title = element_text(face="bold", size=14)
+)
+
 #################### Function RMSE root mean square error
@@
 ```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
-d_hour <-
-  readRDS(file = paste0(
-    path,
-    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
-  ))
+d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
 d_hour <- d_hour %>%
-  dplyr::rename(
-    pco2_corr = pco2_corr_filtered,
-    temp_dur = temp_dur_filtered,
-    pco2_raw = pco2_raw_filtered,
-    sal_fb = sal_fb_filtered,
-    temp_insitu_11m = temp_insitu_11m_filtered,
-    temp_fb = temp_fb_filtered,
-    ph_dur = ph_dur_filtered
-  )
+  dplyr::select(-date) %>%
+  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
 d_all <- d_hour #d_all will be the merger
-d_all <- d_all %>%
-  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
-  dplyr::mutate(month = month(month(datetime))) %>%
-  dplyr::rowwise() %>% 
-  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
-  c(
-    sal_insitu_ctd_1m,
-    sal_insitu_ctd_3m,
-    sal_insitu_ctd_5m,
-    sal_insitu_ctd_7m,
-    sal_insitu_ctd_9m
-  )
-), na.rm = TRUE))
-#restore datetime and date which are mangled by the murtates above
-d_all$datetime <- d_hour$datetime
-d_all$date <- d_hour$date
+d_all<- d_all%>%
+  dplyr::mutate(month = month(month(datetime)))
+#d_all <
 ```
@@
 ```{r Combine discrete and continous data, echo=FALSE}
+
 # at
@@
 d_all <- full_join(d_all, discrete2merge, by="datetime")
-d_all <- d_all %>% 
-  dplyr::mutate(ph_s_sf_temp_mix = ifelse(n_depth_ctd == 4, ph_s_sf_temp_mix, NA)) %>% # eliminate ph spectro data when the profiler was at several depth during the same hour
-  dplyr::mutate(ph_s_sf_temp_mix = ifelse(!is.na(temp_insitu_ctd_7m) | !is.na(temp_insitu_ctd_9m), 
-                                          ph_s_sf_temp_mix, NA)) # only use ph spectro data when profiler was below 6 m
-
 discrete2merge <- discrete %>%
@@
 If data gaps are encountered, they are filled with bottom salinty data from ctd (> 8 m).
-New column "sal_mix" is created and is the one used in ESSD paper.
+New column "sal_mix" is created.
 
 - 1 SBE45 inside the Ferrybox (sal_fb)
-- 5 CTD > 8 m depth (sal_insitu_ctd)
-
-```{r Salinity, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-# SAL FerryBox and sal_mix
-sal_xts <- dplyr::select(d_all, datetime, sal_fb, sal_mix)
+- 5 CTD > 8 meters depth (sal_insitu_ctd)
+
+### **Depth profile**
+
+```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+# SAL FerryBox
+sal_xts <- dplyr::select(d_all, datetime, sal_fb)
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
@@
             dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
-            dySeries("sal_mix", color = "red", strokeWidth = 0, label = "sal_mix") %>%
 dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
       dyRangeSelector(height = 30, dateWindow= NULL)
-# now remove outliers
-d_all <- d_all %>%
-  dplyr::mutate(
-    sal_mix = case_when(
-      date > as.Date("2016-02-01") &
-        date <  as.Date("2016-02-09") & sal_mix < 34 ~ NA_real_,
-      date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
-      date > as.Date("2015-10-01") &
-        date <  as.Date("2015-10-05") & sal_mix < 31.5 ~ NA_real_,
-      date == as.Date("2017-03-22") &
-        sal_mix < 34 ~ NA_real_,
-      TRUE ~ sal_mix
-    )
-  )
-```
-
-### **Depth profile**
-
-```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-
 #SAL CTD profile
@@
   dyRangeSelector(height = 30, dateWindow = NULL)
-
-# now remove outliers
-d_all <- d_all %>%
-  dplyr::mutate(
-    pco2_corr = case_when(
-      date > as.Date("2016-04-01") &
-        date <  as.Date("2017-02-05") & pco2_corr > 400 ~ NA_real_,
-      #date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
-      date > as.Date("2017-08-01") &
-        date <  as.Date("2017-09-30") & pco2_corr > 300 ~ NA_real_,
-      #date == as.Date("2017-03-22") & sal_mix < 34 ~ NA_real_,
-      TRUE ~ pco2_corr
-    )
-  )
 ```
@@
 
-# add spectro points that cannot be taken into consideration (some ancillary data T and/or S not available)
-# shown as white triangles on the plot
+# add spectro points that are not taking into consideration
 d_all <- d_all %>%
@@
 dygraph(seafet_depth_xts, group = "depth", main="pH seaFET (ref + corrected + raw)", ylab="pHT") %>%
-dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 3) %>%
+dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
 dySeries("ph_s_sf_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
@@
 
-# now remove outliers
-d_all <- d_all %>%
-  dplyr::mutate(
-    ph_dur_corr = case_when(
-          ph_dur_corr < 8 ~ NA_real_,
-      date > as.Date("2018-05-18") &
-        date <  as.Date("2018-05-19") & ph_dur_corr < 8.16 ~ NA_real_,
-      #date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
-      date > as.Date("2017-09-25") &
-        date <  as.Date("2017-10-01") & ph_dur_corr < 8.07 ~ NA_real_,
-      #date == as.Date("2017-03-22") & sal_mix < 34 ~ NA_real_,
-      TRUE ~ ph_dur_corr
-    )
-  )
-
 # RANGE of pH
@@
 ```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-# prepare data and remove sf biofouling period
+# remove sf biofouling period
 pH_sf <- d_all %>%
@@
   dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
-
 pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
@@
 saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
-```
-
-## Figures for ESSD paper
-
-```{r figures for ESSD paper, echo=FALSE, message= FALSE, warning=FALSE}
-Mytheme <- function(size_labs = 6, face_font="plain", ...) {
-  theme_bw() +
-  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
-        axis.title.x = element_text(face="bold", size=size_labs, margin=margin(0,0,0,0,"pt")),
-        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
-        axis.title.y = element_text(face="bold", size=size_labs),
-        axis.ticks.x = element_line(size=0.1),
-        axis.ticks.y = element_line(size=0.1),
-        axis.ticks.length = unit(1.1, "mm"),
-        panel.grid.major = element_line(size = 0.25, color="black", linetype="dotted"),
-        aspect.ratio = 1 / 3,
-        plot.margin = margin(t = 0, r = 1.5, b = 0, l = 1.5, unit = "lines")
-  )
-}
-# select time series data
-d <- as_tibble(d_all) %>%
-  dplyr::select(datetime, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, ph_dur_corr, at_calc)
-# time series temp
-ts_temp <- d %>%
-  dplyr::filter(!is.na(temp_insitu_11m)) %>% 
-ggplot() +
-  geom_point(aes(x = datetime, y = temp_insitu_11m), col = "blue", size = 0.15) +
-  labs(title = "", x = "Time", y = "In situ temperature (°C)") +
-  Mytheme(size_labs = 8)
-ggsave(filename = "figures/ts_temp.png")
-print(ts_temp) 
-# time series sal
-ts_sal <- d %>%
-  dplyr::filter(!is.na(sal_mix)) %>% 
-ggplot() +
-  geom_point(aes(x = datetime, y = sal_mix), col = "blue", size = 0.15) +
-  labs(title = "", x = "Time", y = "Salinity") +
-  Mytheme(size_labs = 8)
-ggsave(filename = "figures/ts_sal.png")
-print(ts_sal) 
-# time series pco2
-ts_pco2 <- d %>%
-  dplyr::filter(!is.na(pco2_corr)) %>% 
-ggplot() +
-  geom_point(aes(x = datetime, y = pco2_corr), col = "blue", size = 0.15) +
-  labs(title = "", x = "Time", y = expression(paste("C", O[2], " partial pressure (", mu, "atm)"))) +
-  Mytheme(size_labs = 8)
-ggsave(filename = "figures/ts_pco2.png")
-print(ts_pco2) 
-# time series pH
-ts_ph <- d %>%
-  dplyr::select(datetime, pHint_tot_sf, ph_dur_corr) %>%
-  dplyr::filter(!is.na(pHint_tot_sf)) %>% 
-  pivot_longer(-datetime, names_to = "pH", values_to = "value") %>%
-  ggplot() +
-  geom_point(aes(x = datetime, y = value, colour = pH), size = 0.15) +
-  labs(title = "", x = "Time", y = expression(paste("p", H[T]))) +
-  scale_color_manual(values=c("blue", "red"), 
-                       name="",
-                       breaks=c("pHint_tot_sf", "ph_dur_corr"),
-                       labels=c("SeaFET", "Durafet")) +
-  Mytheme(size_labs = 8)
-print(ts_ph)
-
-ggsave(filename = "figures/ts_ph.png")
-
 ```

### 2020-05-21 awipev-CO2.Rmd
changed calculations of mean voltINT, voltEXT and TseaF

--- 2020-05-20 awipev-CO2.Rmd
@@
   dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
-  dplyr::mutate(month = month(month(datetime))) %>%
   dplyr::rowwise() %>% 
@@
 ), na.rm = TRUE))
-#restore datetime and date which are mangled by the murtates above
+#restore datetime, date which are mangled by the murtates above
 d_all$datetime <- d_hour$datetime
 d_all$date <- d_hour$date
+d_all$month <- month(d_all$datetime)
 ```
@@
 #periode 1, mean of 4 next hours for volt int + T seaF
-mean_voltINT_4h <- d_all %>%
+# mean_voltINT_4h <- d_all %>%
+#   dplyr::filter(
+#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
+#       datetime <= as.POSIXct("2017-08-24 22:00:00")
+#   ) %>%
+#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
+#mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+zz <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2017-08-24 22:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltINT, na.rm = TRUE))
-mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+  )
+mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
 d_all <- d_all %>%
@@
   ))
-mean_voltEXT_4h <- d_all %>%
+# mean_voltEXT_4h <- d_all %>%
+#   dplyr::filter(
+#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
+#       datetime <= as.POSIXct("2017-08-24 22:00:00")
+#   ) %>%
+#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
+# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
+zz <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2017-08-24 22:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
-mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
+  )
+mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
 d_all <- d_all %>%
@@
   ))
-mean_TseaF_4h <- d_all %>%
+# mean_TseaF_4h <- d_all %>%
+#   dplyr::filter(
+#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
+#       datetime <= as.POSIXct("2017-08-24 22:00:00")
+#   ) %>%
+#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
+# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
+zz <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2017-08-24 22:00:00")
-  ) %>%
-  dplyr::summarise(mean(temp_sf, na.rm = TRUE))
-mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
+  )
+mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
 d_all <- d_all %>%
@@
   ))
+
 # Periode 2, mean of 4 next hours for volt int + T seaF
-mean_voltINT_4h <- d_all %>%
+# mean_voltINT_4h <- d_all %>%
+#   dplyr::filter(
+#     datetime >= as.POSIXct("2017-09-28 15:00:00") &
+#       datetime <= as.POSIXct("2017-09-28 18:00:00")
+#   ) %>%
+#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
+# mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+zz <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2017-09-28 18:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltINT, na.rm = TRUE))
-mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+  )
+mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
 d_all <- d_all %>%
@@
   ))
-mean_voltEXT_4h <- d_all %>%
+# mean_voltEXT_4h <- d_all %>%
+#   dplyr::filter(
+#     datetime >= as.POSIXct("2017-09-28 15:00:00") &
+#       datetime <= as.POSIXct("2017-09-28 18:00:00")
+#   ) %>%
+#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
+# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
+zz <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2017-09-28 18:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
-mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
+  )
+mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
 d_all <- d_all %>%
@@
   ))
+
 # period 03, mean of 4 previous hours for volt int + volt ext
-mean_voltINT_4h <- d_all %>%
+# mean_voltINT_4h <- d_all %>%
+#   dplyr::filter(
+#     datetime >= as.POSIXct("2019-09-13 04:00:00") &
+#       datetime <= as.POSIXct("2019-09-13 07:00:00")
+#   ) %>%
+#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
+zz <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2019-09-13 07:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltINT, na.rm = TRUE))
-mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+  )
+mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
+
+# Ce qui suit (7 lignes) est très bizarre
+d_all <- d_all %>%
+  dplyr::mutate(voltINT = ifelse(
+    datetime == as.POSIXct("2017-09-28 13:00:00"),
+    mean_voltINT_4h,
+    voltINT
+  ))
+# ???????? mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
 d_all <- d_all %>%
@@
   ))
-mean_voltEXT_4h <- d_all %>%
+# mean_voltEXT_4h <- d_all %>%
+#   dplyr::filter(
+#     datetime >= as.POSIXct("2019-09-13 04:00:00") &
+#       datetime <= as.POSIXct("2019-09-13 07:00:00")
+#   ) %>%
+#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
+# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
+zz <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2019-09-13 07:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
-mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
+  )
+mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
 d_all <- d_all %>%
@@
   ))
+
 # period 04 also, mean of 4 previous hours for volt int + volt ext + T seaF
-mean_voltINT_4h <- d_all %>%
+# mean_voltINT_4h <- d_all %>%
+#   dplyr::filter(
+#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
+#       datetime <= as.POSIXct("2019-09-13 12:00:00")
+#   ) %>%
+#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
+# mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+zz <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2019-09-13 12:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltINT, na.rm = TRUE))
-mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+  )
+mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
 d_all <- d_all %>%
@@
   ))
-mean_voltEXT_4h <- d_all %>%
+# mean_voltEXT_4h <- d_all %>%
+#   dplyr::filter(
+#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
+#       datetime <= as.POSIXct("2019-09-13 12:00:00")
+#   ) %>%
+#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
+# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
+zz <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2019-09-13 12:00:00")
-  ) %>%
-  dplyr::summarise(mean(voltINT, na.rm = TRUE))
-mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
+  )
+mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
 d_all <- d_all %>%
@@
   ))
-mean_TseaF_4h <- d_all %>%
+# mean_TseaF_4h <- d_all %>%
+#   dplyr::filter(
+#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
+#       datetime <= as.POSIXct("2019-09-13 12:00:00")
+#   ) %>%
+#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
+# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
+zz <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2019-09-13 12:00:00")
-  ) %>%
-  dplyr::summarise(mean(temp_sf, na.rm = TRUE))
-mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
+  )
+mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
 d_all <- d_all %>%

### 2020-05-21 awipev-CO2.Rmd
pH durafet was calculated using depth 11 m... removed unnecessary data frame in the use of pHinsi

@@
 pH_seafet <- pH_seafet %>%
-  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_insitu_ctd, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))
+  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH = pH_s_seafet, ALK = at_mean_interp*1e-6, Tinsi = temp_insitu_ctd, Tlab = temp_s_lab, Pinsi = depth/10, S = sal_mix, Pt = 0, Sit = 0))
 
@@
 pH_durafet <- pH_durafet %>%
-  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb, Pt=0, Sit=0))
+#  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb, Pt=0, Sit=0))
+  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH = pH_s_durafet, ALK = at_mean_interp*1e-6, Tinsi = temp_fb, Tlab = temp_s_lab, Pinsi = 0, S = sal_fb, Pt = 0, Sit = 0))
 
@@
                         NA, d_all$voltINT)
+
 #periode 1, mean of 4 next hours for volt int + T seaF

### 2020-05-21 awipev-CO2.Rmd
Went back because previous changes (except the  use of P=0 in pHinsi) were incorrect

@@
 pH_seafet <- pH_seafet %>%
-  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH = pH_s_seafet, ALK = at_mean_interp*1e-6, Tinsi = temp_insitu_ctd, Tlab = temp_s_lab, Pinsi = depth/10, S = sal_mix, Pt = 0, Sit = 0))
+  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH = pH_seafet$pH_s_seafet,ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))
 
@@
 #  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb, Pt=0, Sit=0))
-  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH = pH_s_durafet, ALK = at_mean_interp*1e-6, Tinsi = temp_fb, Tlab = temp_s_lab, Pinsi = 0, S = sal_fb, Pt = 0, Sit = 0))
+  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= 0, S=pH_durafet$sal_fb, Pt=0, Sit=0))
 

### 2020-05-21 awipev-CO2.Rmd
- added date in discrete df - calculate mean at ct per date rather than per datetime...

@@
 d$measure_date <- dmy(d$measure_date, tz="UTC")
+d$date <- as.Date(d$datetime)
 
@@
 # Mercuric chloride correction (Dickson et al. 2007, SOP3a)
-# AT
 d$at <- d$at * 1.0002
-#CT
 d$ct <- d$ct * 1.0002
@@
 pH_seafet <- pH_seafet %>%
-  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH = pH_seafet$pH_s_seafet,ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))
+  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH = pH_seafet$pH_s_seafet, ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))
 
@@
 pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(datetime,ph_s_sf_temp_mix)%>% 
+  dplyr::select(datetime, ph_s_sf_temp_mix)%>% 
   dplyr::group_by(datetime) %>% 
@@
 pH_durafet_mean <- pH_durafet%>%
-  dplyr::select(datetime,ph_s_dur_temp_fb)%>% 
+  dplyr::select(datetime, ph_s_dur_temp_fb)%>% 
   dplyr::group_by(datetime) %>% 
@@
 
-carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6,S=discrete_no_na$sal_fb, T=discrete_no_na$temp_fb, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
+carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
 
@@
 pH_calc <- discrete %>%
-  dplyr::select(datetime, sal_fb,temp_fb, phcalc, at)%>%
+  dplyr::select(datetime, sal_fb, temp_fb, phcalc, at)%>%
   dplyr::filter(!is.na(phcalc), !is.na(temp_fb), !is.na(sal_fb))

### 2020-05-21 awipev-CO2.Rmd
- rename ph_s_sf_temp_mix to ph_s_sf_temp_insi - now use pressure_insitu_ctd rather than 11 m to calculate ph_s_sf_temp_insi

@@
 ```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
-d <- read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
+d <- tibble(
+  read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
+)
 #d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
@@
 
-# Fill "at/ct" to all line with same day.
+# mean at and ct
 at_ct_mean <- d %>% 
-  group_by(datetime)%>%
+#  group_by(datetime)%>%
+  group_by(date) %>%
   dplyr::summarize(at_mean = mean(at, na.rm = T),
@@
                    )
-d <- left_join(d, at_ct_mean, by='datetime')
+d <- left_join(d, at_ct_mean, by='date') %>% 
+  dplyr::select(datetime, date, temp_s_lab, pH_s_seafet, pH_s_durafet, location_flag, at_mean, ct_mean) %>% # removed useless variables and also to do unique next
+  dplyr::distinct()
+
 # Fill the gaps in at_mean with interpolation
@@
 d_all$closest_datetime <- d_all$datetime
-d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_mix, sal_mix, temp_insitu_ctd)), by="closest_datetime")
+d <- left_join(d, d_all %>% dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_mix, sal_mix, temp_insitu_ctd, pressure_insitu_ctd)), by="closest_datetime")
 
@@
 pH_seafet <- d %>%
-  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd) )
+  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd))
 pH_seafet <- pH_seafet %>%
-  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH = pH_seafet$pH_s_seafet, ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))
+  dplyr::mutate(ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$pH_s_seafet, ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))
 
@@
 pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(datetime, ph_s_sf_temp_mix)%>% 
+  dplyr::select(datetime, ph_s_sf_temp_insi)%>% 
   dplyr::group_by(datetime) %>% 
-  dplyr::summarize(ph_s_sf_temp_mix = mean(ph_s_sf_temp_mix, na.rm = T))
+  dplyr::summarize(ph_s_sf_temp_insi = mean(ph_s_sf_temp_insi, na.rm = T))
 pH_durafet_mean <- pH_durafet%>%
@@
 discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, ph_s_sf_temp_mix) %>%
+  dplyr::select(closest_datetime, ph_s_sf_temp_insi) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 d_all <- d_all %>% 
-  dplyr::mutate(ph_s_sf_temp_mix = ifelse(n_depth_ctd == 4, ph_s_sf_temp_mix, NA)) %>% # eliminate ph spectro data when the profiler was at several depth during the same hour
-  dplyr::mutate(ph_s_sf_temp_mix = ifelse(!is.na(temp_insitu_ctd_7m) | !is.na(temp_insitu_ctd_9m), 
-                                          ph_s_sf_temp_mix, NA)) # only use ph spectro data when profiler was below 6 m
+  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) %>% # eliminate ph spectro data when the profiler was at several depth during the same hour
+  dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) | !is.na(temp_insitu_ctd_9m), 
+                                          ph_s_sf_temp_insi, NA)) # only use ph spectro data when profiler was below 6 m
 
@@
 # sfPeriod <- d_all%>%
-#   dplyr::select(datetime, ph_s_sf_temp_mix)%>%
-#   dplyr::filter(!is.na(ph_s_sf_temp_mix))
+#   dplyr::select(datetime, ph_s_sf_temp_insi)%>%
+#   dplyr::filter(!is.na(ph_s_sf_temp_insi))
 # # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
@@
 # pco2_contros_xts <-
-#   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_mix)
+#   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_insi)
 # pco2_contros_xts <-
@@
 #    dySeries(
-#     "ph_s_sf_temp_mix",
-#     label = "ph_s_sf_temp_mix",
+#     "ph_s_sf_temp_insi",
+#     label = "ph_s_sf_temp_insi",
 #     color =  RColorBrewer::brewer.pal(5, "Dark2")[5],
@@
 ####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
+calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
 # put number of deployment 
@@
         datetime == as.POSIXct("2019-01-18 11:00:00"),
-      ph_s_sf_temp_mix,
+      ph_s_sf_temp_insi,
       NA
@@
 
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_mix, pHint_tot_sf, pH_s_sf_no_calb)
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf, pH_s_sf_no_calb)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
@@
 dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 3) %>%
-dySeries("ph_s_sf_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+dySeries("ph_s_sf_temp_insi", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
 dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
@@
 # Spectro / seafet
-# fit <- lmodel2(data = d_all,  ph_s_sf_temp_mix ~ pHint_tot_sf , nperm = 99)
+# fit <- lmodel2(data = d_all,  ph_s_sf_temp_insi ~ pHint_tot_sf , nperm = 99)
 #
-# p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= ph_s_sf_temp_mix, label = month))+
+# p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= ph_s_sf_temp_insi, label = month))+
 #   geom_text( aes(color=factor(month))) +
@@
 * calibrate seafet pH
-    - ph_s_sf_temp_mix: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
-    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_mix (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
+    - ph_s_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
+    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
     - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)

### 2020-05-21 awipev-CO2.Rmd
means of ph_s_sf_temp_insi and ph_s_dur_temp_fb calculated by grouping date rather than datetime

@@
 pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(datetime, ph_s_sf_temp_insi)%>% 
-  dplyr::group_by(datetime) %>% 
-  dplyr::summarize(ph_s_sf_temp_insi = mean(ph_s_sf_temp_insi, na.rm = T))
+  dplyr::select(date, ph_s_sf_temp_insi)%>% 
+  dplyr::group_by(date) %>% 
+  dplyr::summarize(ph_s_sf_temp_insi = mean(ph_s_sf_temp_insi, na.rm = TRUE))
 pH_durafet_mean <- pH_durafet%>%
-  dplyr::select(datetime, ph_s_dur_temp_fb)%>% 
-  dplyr::group_by(datetime) %>% 
-  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = T))
+  dplyr::select(date, ph_s_dur_temp_fb)%>% 
+  dplyr::group_by(date) %>% 
+  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = TRUE))
 

### 2020-05-22 awipev-CO2.Rmd
- Heavily edited and corrected chunk "read and prepare discrete data" - found an error in nyalesund_cc

@@
 ), na.rm = TRUE))
-#restore datetime, date which are mangled by the murtates above
+#restore datetime, date which are mangled by the mutates above
 d_all$datetime <- d_hour$datetime
@@
 ```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-# Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix 
+# Create temp_mix: filling gaps in temp_insitu_11m using temp_insitu_9m
 d_all <- d_all %>%
@@
   read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
-)
-#d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
-d$datetime <- dmy_hm(d$sampling_date, tz="UTC")
-d$measure_date <- dmy(d$measure_date, tz="UTC")
-d$date <- as.Date(d$datetime)
+) %>% 
+  dplyr::mutate(datetime = dmy_hm(sampling_date, tz="UTC"),
+                measure_date = dmy(measure_date, tz="UTC"),
+                date = as.Date(datetime)) %>% 
+  dplyr::rename(ph_s_sf = pH_s_seafet,
+                ph_s_dur = pH_s_durafet,
+                qflag_ph_s_sf = qflag_pH_s_seafet,
+                qflag_ph_s_dur = qflag_pH_s_durafet)
 
@@
 d <- d%>%
-  dplyr::mutate(ct= replace(ct, qflag_ct != 2, NA),
-                at= replace(at, qflag_at != 2, NA),
-                pH_s_seafet= replace(pH_s_seafet, qflag_pH_s_seafet != 2, NA),
-                pH_s_durafet= replace(pH_s_durafet, qflag_pH_s_durafet != 2, NA))
+  dplyr::mutate(ct = replace(ct, qflag_ct != 2, NA),
+                at = replace(at, qflag_at != 2, NA),
+                ph_s_sf = replace(ph_s_sf, qflag_ph_s_sf != 2, NA),
+                ph_s_dur = replace(ph_s_dur, qflag_ph_s_dur != 2, NA))
 
@@
   group_by(date) %>%
-  dplyr::summarize(at_mean = mean(at, na.rm = T),
-                   ct_mean = mean(ct, na.rm = T),
-                   at_sd = sd(at, na.rm = T), 
-                   ct_sd = sd(ct, na.rm = T)
+  dplyr::summarize(at_mean = mean(at, na.rm = TRUE),
+                   ct_mean = mean(ct, na.rm = TRUE),
+                   at_sd = sd(at, na.rm = TRUE), 
+                   ct_sd = sd(ct, na.rm = TRUE)
                    )
 d <- left_join(d, at_ct_mean, by='date') %>% 
-  dplyr::select(datetime, date, temp_s_lab, pH_s_seafet, pH_s_durafet, location_flag, at_mean, ct_mean) %>% # removed useless variables and also to do unique next
+  dplyr::select(datetime, date, temp_s_lab, ph_s_sf, ph_s_dur, location_flag, at, ct, at_mean, ct_mean) %>% # removed useless variables and also to do unique next
   dplyr::distinct()
@@
 d_all$closest_datetime <- d_all$datetime
-d <- left_join(d, d_all %>% dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_mix, sal_mix, temp_insitu_ctd, pressure_insitu_ctd)), by="closest_datetime")
-
-# Conversion of spectro pH to insitu mix T°
+d <- left_join(d, d_all %>%
+                 dplyr::select(
+                   c(
+                     closest_datetime,
+                     sal_fb,
+                     temp_fb,
+                     temp_mix,
+                     sal_mix,
+                     temp_insitu_11m,
+                     temp_insitu_ctd,
+                     pressure_insitu_ctd
+                   )
+                 ), by = "closest_datetime")
+
+# Conversion of spec pH of in situ samples to in situ temp
 pH_seafet <- d %>%
-  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd))
+  dplyr::filter(!is.na(ph_s_sf) & !is.na(temp_insitu_ctd))
 pH_seafet <- pH_seafet %>% 
-  dplyr::mutate(ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$pH_s_seafet, ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))
-
+  dplyr::mutate(ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))
+
+# Conversion of spec pH of FerryBox samples to FerryBox temp
 pH_durafet <- d %>%
-#  dplyr::filter(!is.na(pH_s_durafet))
-    dplyr::filter(!is.na(pH_s_durafet) & !is.na(sal_fb) & !is.na(temp_fb))
+  dplyr::filter(!is.na(ph_s_dur) & !is.na(sal_fb) & !is.na(temp_fb))
 pH_durafet <- pH_durafet %>% 
-#  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb, Pt=0, Sit=0))
-  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= 0, S=pH_durafet$sal_fb, Pt=0, Sit=0))
+  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH = pH_durafet$ph_s_dur, ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = pH_durafet$temp_fb, Tlab = pH_durafet$temp_s_lab, Pinsi = 0, S = pH_durafet$sal_fb, Pt = 0, Sit = 0))
 
@@
 discrete <- d %>%
-  dplyr::group_by(datetime) %>% 
-  dplyr::summarize(sal_fb = mean(sal_fb, na.rm = T),
-                   temp_fb = mean(temp_fb, na.rm = T),
-                   at_mean_interp = mean(at_mean_interp, na.rm = T),
-            at = mean(at, na.rm = T),
-            qflag_at = mean(qflag_at, na.rm = T),
-            ct_mean_interp = mean(ct_mean_interp, na.rm = T),
-            ct = mean(ct, na.rm = T),
-            qflag_ct = mean(qflag_ct, na.rm = T)
+  dplyr::group_by(date) %>%
+  dplyr::summarize(
+    sal_fb = mean(sal_fb, na.rm = TRUE),
+    sal_mix = mean(sal_mix, na.rm = TRUE),
+    temp_fb = mean(temp_fb, na.rm = TRUE),
+    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
+    at = mean(at, na.rm = TRUE),
+    #qflag_at = mean(qflag_at, na.rm = TRUE), # already dealt with above
+    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
+    ct = mean(ct, na.rm = TRUE),
+    #qflag_ct = mean(qflag_ct, na.rm = TRUE)  # already dealt with above
+    temp_mix = mean(temp_mix, na.rm = TRUE),
+    temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE)
   )
 # join discrete + seafet/durafet
-discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
-discrete <- left_join(discrete, pH_durafet_mean, by='datetime')
-
-##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
+discrete <- left_join(discrete, pH_seafet_mean, by='date')
+discrete <- left_join(discrete, pH_durafet_mean, by='date')
+
+##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ****** $SA$
 ##   *****Attention, I asked to the logisticians to log insitu temp from 9 june 2019
 
+# pH calculated (at and ct) at Ferrybox sal and temp
 discrete_no_na <- discrete %>%
@@
   dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
-
 carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-
-discrete_no_na$phcalc<- carb$pH
-discrete_no_na$pco2_calc<- carb$pCO2
+discrete_no_na$phcalc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
+#discrete_no_na$pco2_calc<- carb$pCO2
+
+# create new variable in "discrete_is_na" to bind "discrete_no_na"
+discrete_is_na$phcalc_fb <- NA
+#discrete_is_na$pco2_calc<- NA
+discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
+  dplyr::arrange(date)
+
+# pH calculated (at and ct) at in situ (11 m) sal and temp
+discrete_no_na <- discrete %>%
+  dplyr::filter(!is.na(sal_mix)  & !is.na(temp_insitu_11m) & !is.na(at) & !is.na(ct))
+discrete_is_na <- discrete %>%
+  dplyr::filter(is.na(sal_mix)  | is.na(temp_insitu_11m) | is.na(at) | is.na(ct))
+carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_mix, T = discrete_no_na$temp_insitu_11m, P = 11/10, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+discrete_no_na$phcalc_insitu <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
+discrete_no_na$pco2_calc_insitu <- carb$pCO2
 
 #create new variable in "discrete_is_na" to bind "discrete_no_na"
-discrete_is_na$phcalc<- NA
-discrete_is_na$pco2_calc<- NA
-discrete <- rbind(discrete_no_na, discrete_is_na)
-discrete <-discrete%>%dplyr::arrange(datetime)
+discrete_is_na$phcalc_insitu <- NA
+discrete_no_na$pco2_calc_insitu <- NA
+discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
+  dplyr::arrange(date)
+
 ```
@@
 calib_spectro <- group_by(calib_spectro, deployment_sf) %>%
-  summarise(E0int25 = mean(E0int25, na.rm = T),
-            E0ext25 = mean(E0ext25, na.rm = T) 
+  summarise(E0int25 = mean(E0int25, na.rm = TRUE),
+            E0ext25 = mean(E0ext25, na.rm = TRUE) 
             )

### 2020-05-22 awipev-CO2.Rmd
edited and corrected chunk "Combine discrete and continous data"

@@
     ph_dur = ph_dur_filtered
-  )
+  ) %>% 
+  arrange(datetime)
 d_all <- d_hour #d_all will be the merger
@@
   )
-), na.rm = TRUE))
-#restore datetime, date which are mangled by the mutates above
-d_all$datetime <- d_hour$datetime
-d_all$date <- d_hour$date
-d_all$month <- month(d_all$datetime)
+), na.rm = TRUE)) %>% 
+  ungroup()
+#restore datetime, date which are mangled by the mutates above, arrange ascending
+d_all <- d_all %>% 
+  dplyr::mutate(datetime = d_hour$datetime, 
+                       date = d_hour$date,
+                       month = month(d_hour$datetime))
 ```
@@
   dplyr::summarize(
+    datetime = mean(datetime, na.rm = TRUE),
       sal_fb = mean(sal_fb, na.rm = TRUE),
@@
 discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, at, qflag_at) %>%
+  dplyr::select(closest_datetime, at) %>%
     dplyr::filter(!is.na(closest_datetime)) %>%
@@
   #drop_na() %>%
-  dplyr::select(closest_datetime, ct, qflag_ct) %>%
+  dplyr::select(closest_datetime, ct) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 
-# pH calculated
+# pH calculated ferrybox
 discrete2merge <- discrete %>%
   #drop_na() %>%
-  dplyr::select(closest_datetime, phcalc) %>%
+  dplyr::select(closest_datetime, phcalc_fb) %>%
+  dplyr::filter(!is.na(closest_datetime)) %>%
+  rename(datetime=closest_datetime)
+d_all <- full_join(d_all, discrete2merge, by="datetime")
+
+# pH calculated in situ
+discrete2merge <- discrete %>%
+  dplyr::select(closest_datetime, phcalc_insitu) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 d_all <- d_all %>% 
-  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) %>% # eliminate ph spectro data when the profiler was at several depth during the same hour
+  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) %>% # eliminate ph spec data when the profiler was at several depth during the same hour
   dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) | !is.na(temp_insitu_ctd_9m), 
-                                          ph_s_sf_temp_insi, NA)) # only use ph spectro data when profiler was below 6 m
-
+                                          ph_s_sf_temp_insi, NA)) # only use ph spec data when profiler was below 6 m
+
+# durafet pH 
 discrete2merge <- discrete %>%
-  #drop_na() %>%
   dplyr::select(closest_datetime, ph_s_dur_temp_fb) %>%
@@
 d_all <- full_join(d_all, discrete2merge, by="datetime")
+
+# calculated pCO2 
 discrete2merge <- discrete %>%
-  #drop_na() %>%
-  dplyr::select(closest_datetime, pco2_calc) %>%
+  dplyr::select(closest_datetime, pco2_calc_insitu) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 d_all$closest_datetime <- d_all$datetime
-discrete <- left_join(discrete, d_all%>%dplyr::select(c(closest_datetime, voltEXT, voltINT)), by="closest_datetime")
+discrete <- left_join(discrete, d_all %>% dplyr::select(c(closest_datetime, voltEXT, voltINT)), by="closest_datetime")
 ```

### 2020-05-22 awipev-CO2.Rmd
continue debugging

@@
 discrete_is_na$phcalc_insitu <- NA
-discrete_no_na$pco2_calc_insitu <- NA
+discrete_is_na$pco2_calc_insitu <- NA
 discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
@@
 title <- "Contros vs calculated pCO2"
-fit <- lmodel2(data = d_all,  pco2_corr ~ pco2_calc , nperm = 99)
-
-p <-  ggplot(d_all,aes(x=pco2_calc, y= pco2_corr, label = month))+
+fit <- lmodel2(data = d_all,  pco2_corr ~ pco2_calc_insitu , nperm = 99)
+
+p <-  ggplot(d_all,aes(x=pco2_calc_insitu, y= pco2_corr, label = month))+
    geom_text(aes(color = factor(month)))+
@@
 ```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-print(p) # pco2_calc_pco2_corr_text
+print(p) # pco2_calc_insitu_pco2_corr_text
 ```
@@
 pco2_contros_xts <-
-  dplyr::select(d_all, datetime, pco2_calc, pco2_corr)
+  dplyr::select(d_all, datetime, pco2_calc_insitu, pco2_corr)
 pco2_contros_xts <-
@@
   dySeries(
-    "pco2_calc",
-    label = "pco2_calc",
+    "pco2_calc_insitu",
+    label = "pco2_calc_insitu",
     color = "red",
@@
 
+# $SA$ below
 #periode 1, mean of 4 next hours for volt int + T seaF
@@
 ####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
+calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd)
 # put number of deployment 
@@
 #### plot
+# $SA$ 3 points?
 kk <- melt(calib_spectro, id.vars="deployment_sf")
@@
 pH_calc <- discrete %>%
-  dplyr::select(datetime, sal_fb, temp_fb, phcalc, at)%>%
-  dplyr::filter(!is.na(phcalc), !is.na(temp_fb), !is.na(sal_fb))
-pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+  dplyr::select(datetime, sal_fb, temp_fb, phcalc_fb, at)%>%
+  dplyr::filter(!is.na(phcalc_fb), !is.na(temp_fb), !is.na(sal_fb))
+pH_calc$pH_calc_fb_norm4 <- pHinsi(pH = pH_calc$phcalc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
 # join pH calc norm + pH dur/sf norm in d_all
-d_all <- left_join(d_all, pH_calc%>%dplyr::select(datetime,pH_calc_norm4), by="datetime")
-
-durafet_calc_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pH_calc_norm4)
+d_all <- left_join(d_all, pH_calc %>% dplyr::select(datetime, pH_calc_fb_norm4), by="datetime")
+
+durafet_calc_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pH_calc_fb_norm4)
 durafet_calc_contros_xts <- as.xts(durafet_calc_contros_xts, order.by = d_all$datetime)
@@
     dySeries("pH_durafet_norm4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_calc_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pH_calc_fb_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
 ```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
-seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_norm4, pH_calc_norm4)
+seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_norm4, pH_calc_fb_norm4)
 seafet_calc_contros_xts <- as.xts(seafet_calc_contros_xts, order.by = d_all$datetime)
@@
     dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_calc_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pH_calc_fb_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
 * temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
-* pco2_calc: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
+* pco2_calc_insitu: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
 * calibrate seafet pH

### 2020-05-22 awipev-CO2.Rmd
pH_seafet_mean and durafet SD added

--- 2020-05-22 awipev-CO2.Rmd
@@
 ```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
-d_hour <-
-  readRDS(file = paste0(
-    path,
-    "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"
-  ))
+d_hour <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds"))
 d_hour <- d_hour %>%
-  dplyr::rename(
-    pco2_corr = pco2_corr_filtered,
-    temp_dur = temp_dur_filtered,
-    pco2_raw = pco2_raw_filtered,
-    sal_fb = sal_fb_filtered,
-    temp_insitu_11m = temp_insitu_11m_filtered,
-    temp_fb = temp_fb_filtered,
-    ph_dur = ph_dur_filtered
-  )
+  dplyr::select(-date) %>%
+  dplyr::rename(pco2_corr = pco2_corr_filtered, temp_dur = temp_dur_filtered, pco2_raw = pco2_raw_filtered, sal_fb = sal_fb_filtered, temp_insitu_11m=temp_insitu_11m_filtered, temp_fb = temp_fb_filtered, ph_dur = ph_dur_filtered)
 d_all <- d_hour #d_all will be the merger
-d_all <- d_all %>%
-  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
-  dplyr::rowwise() %>% 
-  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
-  c(
-    sal_insitu_ctd_1m,
-    sal_insitu_ctd_3m,
-    sal_insitu_ctd_5m,
-    sal_insitu_ctd_7m,
-    sal_insitu_ctd_9m
-  )
-), na.rm = TRUE))
-#restore datetime, date which are mangled by the mutates above
-d_all$datetime <- d_hour$datetime
-d_all$date <- d_hour$date
-d_all$month <- month(d_all$datetime)
+d_all<- d_all%>%
+  dplyr::mutate(month = month(month(datetime)))
+#d_all <
 ```
@@
 ```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-# Create temp_mix: filling gaps in temp_insitu_11m using temp_insitu_9m
+# Binding temp_insitu_11m + temp_insitu_ctd if we get gaps in temp_insitu_11m = call this new column = temp_mix 
 d_all <- d_all %>%
@@
 ```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
-d <- tibble(
-  read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
-) %>% 
-  dplyr::mutate(datetime = dmy_hm(sampling_date, tz="UTC"),
-                measure_date = dmy(measure_date, tz="UTC"),
-                date = as.Date(datetime)) %>% 
-  dplyr::rename(ph_s_sf = pH_s_seafet,
-                ph_s_dur = pH_s_durafet,
-                qflag_ph_s_sf = qflag_pH_s_seafet,
-                qflag_ph_s_dur = qflag_pH_s_durafet)
+d <- read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
+#d$datetime <- as.POSIXct(d$sampling_date, format="%d/%m/%Y %H:%M", tz="UTC")
+d$datetime <- dmy_hm(d$sampling_date, tz="UTC")
+d$measure_date <- dmy(d$measure_date, tz="UTC")
 
@@
 d <- d%>%
-  dplyr::mutate(ct = replace(ct, qflag_ct != 2, NA),
-                at = replace(at, qflag_at != 2, NA),
-                ph_s_sf = replace(ph_s_sf, qflag_ph_s_sf != 2, NA),
-                ph_s_dur = replace(ph_s_dur, qflag_ph_s_dur != 2, NA))
+  dplyr::mutate(ct= replace(ct, qflag_ct != 2, NA),
+                at= replace(at, qflag_at != 2, NA),
+                pH_s_seafet= replace(pH_s_seafet, qflag_pH_s_seafet != 2, NA),
+                pH_s_durafet= replace(pH_s_durafet, qflag_pH_s_durafet != 2, NA))
 
 # Mercuric chloride correction (Dickson et al. 2007, SOP3a)
+# AT
 d$at <- d$at * 1.0002
+#CT
 d$ct <- d$ct * 1.0002
 
-# mean at and ct
+# Fill "at/ct" to all line with same day.
 at_ct_mean <- d %>% 
-#  group_by(datetime)%>%
-  group_by(date) %>%
-  dplyr::summarize(at_mean = mean(at, na.rm = TRUE),
-                   ct_mean = mean(ct, na.rm = TRUE),
-                   at_sd = sd(at, na.rm = TRUE), 
-                   ct_sd = sd(ct, na.rm = TRUE)
+  group_by(datetime)%>%
+  dplyr::summarize(at_mean = mean(at, na.rm = T),
+                   ct_mean = mean(ct, na.rm = T),
+                   at_sd = sd(at, na.rm = T), 
+                   ct_sd = sd(ct, na.rm = T)
                    )
-d <- left_join(d, at_ct_mean, by='date') %>% 
-  dplyr::select(datetime, date, temp_s_lab, ph_s_sf, ph_s_dur, location_flag, at, ct, at_mean, ct_mean) %>% # removed useless variables and also to do unique next
-  dplyr::distinct()
-
+d <- left_join(d, at_ct_mean, by='datetime')
 # Fill the gaps in at_mean with interpolation
@@
 d_all$closest_datetime <- d_all$datetime
-d <- left_join(d, d_all %>%
-                 dplyr::select(
-                   c(
-                     closest_datetime,
-                     sal_fb,
-                     temp_fb,
-                     temp_mix,
-                     sal_mix,
-                     temp_insitu_11m,
-                     temp_insitu_ctd,
-                     pressure_insitu_ctd
-                   )
-                 ), by = "closest_datetime")
-
-# Conversion of spec pH of in situ samples to in situ temp
+d <- left_join(d, d_all%>%dplyr::select(c(closest_datetime, sal_fb, temp_fb, temp_mix, sal_mix, temp_insitu_ctd)), by="closest_datetime")
+
+# Conversion of spectro pH to insitu mix T°
 pH_seafet <- d %>%
-  dplyr::filter(!is.na(ph_s_sf) & !is.na(temp_insitu_ctd))
+  dplyr::filter(!is.na(pH_s_seafet) & !is.na(temp_insitu_ctd) )
 pH_seafet <- pH_seafet %>%
-  dplyr::mutate(ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))
-
-# Conversion of spec pH of FerryBox samples to FerryBox temp
+  dplyr::mutate(ph_s_sf_temp_mix = pHinsi(pH=pH_seafet$pH_s_seafet,ALK=pH_seafet$at_mean_interp*1e-6, Tinsi=pH_seafet$temp_insitu_ctd, Tlab=pH_seafet$temp_s_lab, Pinsi= pH_seafet$depth/10, S=pH_seafet$sal_mix,Pt=0,Sit=0))
+
 pH_durafet <- d %>%
-  dplyr::filter(!is.na(ph_s_dur) & !is.na(sal_fb) & !is.na(temp_fb))
+#  dplyr::filter(!is.na(pH_s_durafet))
+    dplyr::filter(!is.na(pH_s_durafet) & !is.na(sal_fb) & !is.na(temp_fb))
 pH_durafet <- pH_durafet %>%
-  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH = pH_durafet$ph_s_dur, ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = pH_durafet$temp_fb, Tlab = pH_durafet$temp_s_lab, Pinsi = 0, S = pH_durafet$sal_fb, Pt = 0, Sit = 0))
+  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH=pH_durafet$pH_s_durafet, ALK=pH_durafet$at_mean_interp*1e-6, Tinsi=pH_durafet$temp_fb, Tlab=pH_durafet$temp_s_lab, Pinsi= pH_durafet$depth/10, S=pH_durafet$sal_fb, Pt=0, Sit=0))
 
@@
 pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(date, ph_s_sf_temp_insi)%>% 
-  dplyr::group_by(date) %>% 
-  dplyr::summarize(ph_s_sf_temp_insi = mean(ph_s_sf_temp_insi, na.rm = TRUE))
+  dplyr::select(datetime,ph_s_sf_temp_mix) %>% 
+  dplyr::group_by(datetime) %>% 
+  dplyr::summarize(ph_s_sf_temp_mix = mean(ph_s_sf_temp_mix, na.rm = TRUE)  )
+  #                 ph_s_sf_temp_mix_sd = round(sd(pH_seafet$ph_s_sf_temp_mix, na.rm = TRUE), digits = 4))
+
 pH_durafet_mean <- pH_durafet%>%
-  dplyr::select(date, ph_s_dur_temp_fb)%>% 
-  dplyr::group_by(date) %>% 
-  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = TRUE))
+  dplyr::select(datetime,ph_s_dur_temp_fb)%>% 
+  dplyr::group_by(datetime) %>% 
+  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = T) )
+   #                ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = T)
 
@@
 discrete <- d %>% 
-  dplyr::group_by(date) %>%
-  dplyr::summarize(
-    sal_fb = mean(sal_fb, na.rm = TRUE),
-    sal_mix = mean(sal_mix, na.rm = TRUE),
-    temp_fb = mean(temp_fb, na.rm = TRUE),
-    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
-    at = mean(at, na.rm = TRUE),
-    #qflag_at = mean(qflag_at, na.rm = TRUE), # already dealt with above
-    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
-    ct = mean(ct, na.rm = TRUE),
-    #qflag_ct = mean(qflag_ct, na.rm = TRUE)  # already dealt with above
-    temp_mix = mean(temp_mix, na.rm = TRUE),
-    temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE)
+  dplyr::group_by(datetime) %>% 
+  dplyr::summarize(sal_fb = mean(sal_fb, na.rm = T),
+                   temp_fb = mean(temp_fb, na.rm = T),
+                   at_mean_interp = mean(at_mean_interp, na.rm = T),
+            at = mean(at, na.rm = T),
+            qflag_at = mean(qflag_at, na.rm = T),
+            ct_mean_interp = mean(ct_mean_interp, na.rm = T),
+            ct = mean(ct, na.rm = T),
+            qflag_ct = mean(qflag_ct, na.rm = T)
             )
 # join discrete + seafet/durafet
-discrete <- left_join(discrete, pH_seafet_mean, by='date')
-discrete <- left_join(discrete, pH_durafet_mean, by='date')
-
-##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ****** $SA$
+discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
+discrete <- left_join(discrete, pH_durafet_mean, by='datetime')
+
+##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
 ##   *****Attention, I asked to the logisticians to log insitu temp from 9 june 2019
 
-# pH calculated (at and ct) at Ferrybox sal and temp
 discrete_no_na <- discrete %>%
@@
   dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
-carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-discrete_no_na$phcalc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
-#discrete_no_na$pco2_calc<- carb$pCO2
-
-# create new variable in "discrete_is_na" to bind "discrete_no_na"
-discrete_is_na$phcalc_fb <- NA
-#discrete_is_na$pco2_calc<- NA
-discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
-  dplyr::arrange(date)
-
-# pH calculated (at and ct) at in situ (11 m) sal and temp
-discrete_no_na <- discrete %>%
-  dplyr::filter(!is.na(sal_mix)  & !is.na(temp_insitu_11m) & !is.na(at) & !is.na(ct))
-discrete_is_na <- discrete %>%
-  dplyr::filter(is.na(sal_mix)  | is.na(temp_insitu_11m) | is.na(at) | is.na(ct))
-carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_mix, T = discrete_no_na$temp_insitu_11m, P = 11/10, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-discrete_no_na$phcalc_insitu <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
-discrete_no_na$pco2_calc_insitu <- carb$pCO2
+
+carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6,S=discrete_no_na$sal_fb, T=discrete_no_na$temp_fb, P=0, Pt=0, Sit=0,k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
+
+discrete_no_na$phcalc<- carb$pH
+discrete_no_na$pco2_calc<- carb$pCO2
 
 #create new variable in "discrete_is_na" to bind "discrete_no_na"
-discrete_is_na$phcalc_insitu <- NA
-discrete_no_na$pco2_calc_insitu <- NA
-discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
-  dplyr::arrange(date)
-
+discrete_is_na$phcalc<- NA
+discrete_is_na$pco2_calc<- NA
+discrete <- rbind(discrete_no_na, discrete_is_na)
+discrete <-discrete%>%dplyr::arrange(datetime)
 ```
@@
 discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, ph_s_sf_temp_insi) %>%
+  dplyr::select(closest_datetime, ph_s_sf_temp_mix) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 d_all <- full_join(d_all, discrete2merge, by="datetime")
-d_all <- d_all %>% 
-  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) %>% # eliminate ph spectro data when the profiler was at several depth during the same hour
-  dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) | !is.na(temp_insitu_ctd_9m), 
-                                          ph_s_sf_temp_insi, NA)) # only use ph spectro data when profiler was below 6 m
-
 discrete2merge <- discrete %>%
@@
 # sfPeriod <- d_all%>%
-#   dplyr::select(datetime, ph_s_sf_temp_insi)%>%
-#   dplyr::filter(!is.na(ph_s_sf_temp_insi))
+#   dplyr::select(datetime, ph_s_sf_temp_mix)%>%
+#   dplyr::filter(!is.na(ph_s_sf_temp_mix))
 # # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
@@
 # pco2_contros_xts <-
-#   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_insi)
+#   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_mix)
 # pco2_contros_xts <-
@@
 #    dySeries(
-#     "ph_s_sf_temp_insi",
-#     label = "ph_s_sf_temp_insi",
+#     "ph_s_sf_temp_mix",
+#     label = "ph_s_sf_temp_mix",
 #     color =  RColorBrewer::brewer.pal(5, "Dark2")[5],
@@
                         NA, d_all$voltINT)
-
 #periode 1, mean of 4 next hours for volt int + T seaF
-# mean_voltINT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
-#       datetime <= as.POSIXct("2017-08-24 22:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
-#mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-zz <- d_all %>%
+mean_voltINT_4h <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2017-08-24 22:00:00")
-  )
-mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
+  ) %>%
+  dplyr::summarise(mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
 d_all <- d_all %>%
@@
   ))
-# mean_voltEXT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
-#       datetime <= as.POSIXct("2017-08-24 22:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
-# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-zz <- d_all %>%
+mean_voltEXT_4h <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2017-08-24 22:00:00")
-  )
-mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
+  ) %>%
+  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
+mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
 d_all <- d_all %>%
@@
   ))
-# mean_TseaF_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
-#       datetime <= as.POSIXct("2017-08-24 22:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
-# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
-zz <- d_all %>%
+mean_TseaF_4h <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2017-08-24 22:00:00")
-  )
-mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
+  ) %>%
+  dplyr::summarise(mean(temp_sf, na.rm = TRUE))
+mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
 d_all <- d_all %>%
@@
   ))
-
 # Periode 2, mean of 4 next hours for volt int + T seaF
-# mean_voltINT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2017-09-28 15:00:00") &
-#       datetime <= as.POSIXct("2017-09-28 18:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
-# mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-zz <- d_all %>%
+mean_voltINT_4h <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2017-09-28 18:00:00")
-  )
-mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
+  ) %>%
+  dplyr::summarise(mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
 d_all <- d_all %>%
@@
   ))
-# mean_voltEXT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2017-09-28 15:00:00") &
-#       datetime <= as.POSIXct("2017-09-28 18:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
-# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-zz <- d_all %>%
+mean_voltEXT_4h <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2017-09-28 18:00:00")
-  )
-mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
+  ) %>%
+  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
+mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
 d_all <- d_all %>%
@@
   ))
-
 # period 03, mean of 4 previous hours for volt int + volt ext
-# mean_voltINT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2019-09-13 04:00:00") &
-#       datetime <= as.POSIXct("2019-09-13 07:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
-zz <- d_all %>%
+mean_voltINT_4h <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2019-09-13 07:00:00")
-  )
-mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
-
-# Ce qui suit (7 lignes) est très bizarre
-d_all <- d_all %>%
-  dplyr::mutate(voltINT = ifelse(
-    datetime == as.POSIXct("2017-09-28 13:00:00"),
-    mean_voltINT_4h,
-    voltINT
-  ))
-# ???????? mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+  ) %>%
+  dplyr::summarise(mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
 d_all <- d_all %>%
@@
   ))
-# mean_voltEXT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2019-09-13 04:00:00") &
-#       datetime <= as.POSIXct("2019-09-13 07:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
-# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-zz <- d_all %>%
+mean_voltEXT_4h <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2019-09-13 07:00:00")
-  )
-mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
+  ) %>%
+  dplyr::summarise(mean(voltEXT, na.rm = TRUE))
+mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
 d_all <- d_all %>%
@@
   ))
-
 # period 04 also, mean of 4 previous hours for volt int + volt ext + T seaF
-# mean_voltINT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
-#       datetime <= as.POSIXct("2019-09-13 12:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
-# mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
-zz <- d_all %>%
+mean_voltINT_4h <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2019-09-13 12:00:00")
-  )
-mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
+  ) %>%
+  dplyr::summarise(mean(voltINT, na.rm = TRUE))
+mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
 d_all <- d_all %>%
@@
   ))
-# mean_voltEXT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
-#       datetime <= as.POSIXct("2019-09-13 12:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
-# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
-zz <- d_all %>%
+mean_voltEXT_4h <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2019-09-13 12:00:00")
-  )
-mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
+  ) %>%
+  dplyr::summarise(mean(voltINT, na.rm = TRUE))
+mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
 d_all <- d_all %>%
@@
   ))
-# mean_TseaF_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
-#       datetime <= as.POSIXct("2019-09-13 12:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
-# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
-zz <- d_all %>%
+mean_TseaF_4h <- d_all %>%
   dplyr::filter(
@@
       datetime <= as.POSIXct("2019-09-13 12:00:00")
-  )
-mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
+  ) %>%
+  dplyr::summarise(mean(temp_sf, na.rm = TRUE))
+mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
 d_all <- d_all %>%
@@
 
-#interpolation of salinity during gaps
+#interpolation of salinity during the FB off maintenance
 salinterp <-
@@
     d_all$datetime,
-    d_all$sal_insitu_ctd,
+    d_all$sal_mix,
     xout = d_all$datetime,
@@
   )
-names(salinterp) <- c("datetime", "sal_insitu_ctd_interp")
+names(salinterp) <- c("datetime", "sal_mix_interp")
 salinterp <- as.data.frame(salinterp)
-d_all$sal_insitu_ctd_interp <- salinterp$sal_insitu_ctd_interp
+d_all$sal_mix_interp <- salinterp$sal_mix_interp
 
@@
   dplyr::mutate(
-    sal_insitu_ctd_interp =  ifelse(
-      datetime > as.POSIXct("2018-04-16 07:00:00") &
-        datetime < as.POSIXct("2018-04-24 22:00:00"),
-      sal_insitu_ctd_interp,
-      sal_insitu_ctd
+    sal_mix_interp =  ifelse(
+      datetime > as.POSIXct("2018-03-09 00:00:00") &
+        datetime < as.POSIXct("2018-04-16 16:00:00"),
+      sal_mix_interp,
+      sal_mix
     )
@@
 ####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
+calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_mix, calT = d_all$temp_sf, calSal = d_all$sal_mix_interp)
 # put number of deployment 
@@
 calib_spectro <- group_by(calib_spectro, deployment_sf) %>%
-  summarise(E0int25 = mean(E0int25, na.rm = TRUE),
-            E0ext25 = mean(E0ext25, na.rm = TRUE) 
+  summarise(E0int25 = mean(E0int25, na.rm = T),
+            E0ext25 = mean(E0ext25, na.rm = T) 
             )
@@
 ####
-seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
+seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_mix_interp)
 
@@
         datetime == as.POSIXct("2019-01-18 11:00:00"),
-      ph_s_sf_temp_insi,
+      ph_s_sf_temp_mix,
       NA
@@
 
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf, pH_s_sf_no_calb)
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_mix, pHint_tot_sf, pH_s_sf_no_calb)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
 dygraph(seafet_depth_xts, group = "depth", main="pH seaFET (ref + corrected + raw)", ylab="pHT") %>%
-dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 3) %>%
-dySeries("ph_s_sf_temp_insi", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2) %>%
+dySeries("ph_s_sf_temp_mix", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
 dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
@@
 pH_calc <- discrete %>%
-  dplyr::select(datetime, sal_fb, temp_fb, phcalc, at)%>%
+  dplyr::select(datetime, sal_fb,temp_fb, phcalc, at)%>%
   dplyr::filter(!is.na(phcalc), !is.na(temp_fb), !is.na(sal_fb))
@@
 # Spectro / seafet
-# fit <- lmodel2(data = d_all,  ph_s_sf_temp_insi ~ pHint_tot_sf , nperm = 99)
+# fit <- lmodel2(data = d_all,  ph_s_sf_temp_mix ~ pHint_tot_sf , nperm = 99)
 #
-# p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= ph_s_sf_temp_insi, label = month))+
+# p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= ph_s_sf_temp_mix, label = month))+
 #   geom_text( aes(color=factor(month))) +
@@
 * calibrate seafet pH
-    - ph_s_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
-    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
+    - ph_s_sf_temp_mix: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
+    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_mix (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
     - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)

### 2020-05-23 awipev-CO2.Rmd
ESSD: finalize first version time series fig

--- 2020-05-22 awipev-CO2.Rmd
@@
 library("scales")
-# if (!require("plotly")) install.packages("plotly")
-# library(plotly)
+if (!require("cowplot")) install.packages("cowplot")
+library(cowplot)
 if (!require("htmlwidgets")) install.packages("htmlwidgets")
@@
   theme_bw() +
-  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
-        axis.title.x = element_text(face="bold", size=size_labs, margin=margin(0,0,0,0,"pt")),
-        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
-        axis.title.y = element_text(face="bold", size=size_labs),
-        axis.ticks.x = element_line(size=0.1),
-        axis.ticks.y = element_line(size=0.1),
-        axis.ticks.length = unit(1.1, "mm"),
-        panel.grid.major = element_line(size = 0.25, color="black", linetype="dotted"),
-        aspect.ratio = 1 / 3,
-        plot.margin = margin(t = 0, r = 1.5, b = 0, l = 1.5, unit = "lines")
+  theme(
+    # axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
+    #     axis.title.x = element_text(face="plain", size=size_labs, margin=margin(0,0,0,0,"pt")),
+    #     axis.text.y = element_text(face=face_font, color="black", size=size_labs),
+    axis.text.x = element_blank(),
+    #     axis.title.y = element_text(face="plain", size=size_labs),
+    #     axis.ticks.x = element_line(size=0.1),
+    #     axis.ticks.y = element_line(size=0.1),
+    #     axis.ticks.length = unit(1.1, "mm"),
+    #     panel.grid.major = element_line(size = 0.2, color="black", linetype="dotted"),
+    #     aspect.ratio = 1 / 3,
+        plot.margin = margin(t = 0, r = 0.3, b = 0, l = 0.3, unit = "cm")
   )
 }
+xlim <- c(as.POSIXct("2015-07-01 00:00:00"), as.POSIXct("2020-07-01 00:00:00"))
 # select time series data
@@
   geom_point(aes(x = datetime, y = temp_insitu_11m), col = "blue", size = 0.15) +
-  labs(title = "", x = "Time", y = "In situ temperature (°C)") +
+  labs(title = "", x = "", y = "Temp. 11 m (°C)") +
   Mytheme(size_labs = 8)
-ggsave(filename = "figures/ts_temp.png")
 print(ts_temp) 
@@
   geom_point(aes(x = datetime, y = sal_mix), col = "blue", size = 0.15) + 
-  labs(title = "", x = "Time", y = "Salinity") +
+  labs(title = "", x = "", y = "Salinity") +
   Mytheme(size_labs = 8)
-ggsave(filename = "figures/ts_sal.png")
 print(ts_sal) 
@@
   geom_point(aes(x = datetime, y = pco2_corr), col = "blue", size = 0.15) +
-  labs(title = "", x = "Time", y = expression(paste("C", O[2], " partial pressure (", mu, "atm)"))) +
+  scale_x_datetime(limits = xlim) +
+  labs(title = "", x = "", y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
   Mytheme(size_labs = 8)
-ggsave(filename = "figures/ts_pco2.png")
 print(ts_pco2) 
@@
   geom_point(aes(x = datetime, y = value, colour = pH), size = 0.15) +
-  labs(title = "", x = "Time", y = expression(paste("p", H[T]))) +
-  scale_color_manual(values=c("blue", "red"), 
-                       name="",
-                       breaks=c("pHint_tot_sf", "ph_dur_corr"),
-                       labels=c("SeaFET", "Durafet")) +
-  Mytheme(size_labs = 8)
+  scale_x_datetime(limits = xlim) +
+  labs(title = "",
+       x = "",
+       y = expression(paste("p", H[T]))) +
+  # scale_color_manual(
+  #   values = c("blue", "red"),
+  #   name = "",
+  #   breaks = c("pHint_tot_sf", "ph_dur_corr"),
+  #   labels = c("SeaFET", "Durafet")
+  # ) +
+  annotate(
+    geom = "text",
+    x = as.POSIXct("2018-06-01"),
+    y = 8.35,
+    label = "seaFET",
+    color = "blue", size = 2
+  ) +
+  annotate(
+    geom = "text",
+    x = as.POSIXct("2018-06-01"),
+    y = 8.25,
+    label = "Durafet",
+    color = "red", size = 2
+  ) +
+  Mytheme(size_labs = 8) +
+  theme(legend.position = "none")
 print(ts_ph) 
-
-ggsave(filename = "figures/ts_ph.png")
-
+# time series AT
+ts_at <- d %>%
+  dplyr::filter(!is.na(at_calc)) %>% 
+  ggplot() +
+  geom_point(aes(x = datetime, y = at_calc), col = "blue", size = 0.15) +
+  scale_x_datetime(limits = xlim) +
+  labs(title = "", x = "Time", y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
+  Mytheme(size_labs = 8) +
+  theme(axis.title.x = element_text(face="plain", size=8))
+print(ts_at)
+
+#assemble time-series figure
+cp <- cowplot::plot_grid(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, 
+                   align = "v",
+                   #labels = "AUTO",
+                   ncol = 1
+                   #width = 18,
+                   #units = "cm"
+                   )
+print(cp)
+cowplot::ggsave2(filename = "figures/ts_gg.png", plot = cp, height = 20, units = "cm")
+
+ts_sal / ts_temp / ts_at
+grid.arrange(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ncol = 1)
+cowplot::save_plot(filename = "figures/ts_sp.pdf", plot = cp)
+multiplot(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, cols = 1)
 ```

### 2020-05-23 awipev-CO2.Rmd
commented unnecessary code

@@
 
-ts_sal / ts_temp / ts_at
-grid.arrange(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ncol = 1)
-cowplot::save_plot(filename = "figures/ts_sp.pdf", plot = cp)
-multiplot(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, cols = 1)
+# ts_sal / ts_temp / ts_at
+# grid.arrange(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ncol = 1)
+# cowplot::save_plot(filename = "figures/ts_sp.pdf", plot = cp)
+# multiplot(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, cols = 1)
 ```

### 2020-05-24 awipev-CO2.Rmd
Figure data availability finalized

@@
 + 4: data not usable according to manufacturer
++ 6: failing the manufacturer range test (not used)
 + 7: failing the regional range test 
@@
 
-    + 1: good data
-    + 3: impossible date and time test
-    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
-    + 6: failing the manufacturer range test (not used)
-    + 7: failing the regional range test 
-    + 12: failing the spike test (NAs from despike)
-    + 13: failing the gradient test
-    + 15: the instrument was not deployed or operated
-    + 99: failing the final visual inspection of the data.
-
-* Despike using oce::despike with n=2, k=5761
-
 ```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-# function to express the number of quality flag in pefrcent for each variable
-# qflag <- function(x, ...) {
-#   tmp <- summary(as.factor(x))*100/length(x)
-#   return(tmp)
-# }
 d <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_minute.rds")) %>%
@@
 labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
-            "Failed visual inspection", "No data")
-#colnames(z) <- c("flag", colnames(d)[-1]) # remove first col name (datetime)
+            "Failed visual inspection", "Not deployed or operated", "Acid flush", "Failed visual inspection")
 colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
@@
   #scale_y_reverse() +
-  #discrete_scale(labels = labels) + 
+  scale_fill_discrete(labels = labels) + 
   coord_flip() +
-  geom_text(aes(label=round(value, digits = 0)), position = position_stack(0.5), size = 3) +
+  #geom_text(aes(label=round(value, digits = 0)), position = position_stack((hjust = 0.5)), size = 3) +
   labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
-  theme_bw()
-p
+  Mytheme(size_labs = 8) +
+  theme(plot.margin = margin(t = 0, r = 0.0, b = 0, l = 0.0, unit = "cm"))
+ggsave(filename = "figures/availability.png", plot = p, width = 20, units = "cm")
+kable(z, digits = 1)
 rm(d)
@@
 }
+
 xlim <- c(as.POSIXct("2015-07-01 00:00:00"), as.POSIXct("2020-07-01 00:00:00"))
@@
     + 15: the instrument was not deployed or operated
+    + 16: acid flush
     + 99: failing the final visual inspection of the data. 

### 2020-05-25 awipev-CO2.Rmd
added Omega in time series figure

@@
   ungroup()
-summary(df)
 ```
@@
               "%Y-%m-%d %H:%M:%S")))
-at_contros_calc_xts <- dplyr::select(d_all, datetime,at_calc, at)
+at_contros_calc_xts <- dplyr::select(d_all, datetime, at_calc, at)
 at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
@@
 ```
+
 ```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
@@
 # d_all comprises additional columns calculated in this script
+d_all$at <- ifelse(is.nan(d_all$at), NA, d_all$at) # replace all NaN by NA
+d_all$ct <- ifelse(is.nan(d_all$at), NA, d_all$ct) # replace all NaN by NA
 saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
@@
 xlim <- c(as.POSIXct("2015-07-01 00:00:00"), as.POSIXct("2020-07-01 00:00:00"))
+# calculate omeaga arag
+z <- d_all %>% 
+  dplyr::filter(!(is.na(pco2_corr) | is.na(at_calc) | is.na(sal_mix) |is.na(temp_insitu_11m) | is.na(pressure_insitu_ctd)))
+oa_tbf <- as_tibble(
+  carb(24, z$pco2_corr, z$at_calc*1e-6, S = z$sal_mix, T = z$temp_insitu_11m, 
+                          P = z$pressure_insitu_ctd/10, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", 
+                          ks = "d", pHscale = "T", b = "u74")
+) %>% 
+  dplyr::mutate(datetime = z$datetime,
+                oa = OmegaAragonite) %>% 
+dplyr::select(datetime, oa)
 # select time series data
 d <- as_tibble(d_all) %>%
-  dplyr::select(datetime, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, ph_dur_corr, at_calc)
+  dplyr::select(datetime, pressure_insitu_ctd, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, 
+                ph_dur_corr, at_calc)
+d <- left_join(d, oa_tbf, by = 'datetime')
+
 # time series temp
@@
 print(ts_at) 
-
+# time series Omega
+ts_oa <- d %>%
+  dplyr::filter(!is.na(oa)) %>% 
+  ggplot() +
+  geom_point(aes(x = datetime, y = oa), col = "blue", size = 0.15) +
+  scale_x_datetime(limits = xlim) +
+  labs(title = "", x = "Time", y = "Omega aragonite") +
+  Mytheme(size_labs = 8) +
+  theme(axis.title.x = element_text(face="plain", size=8))
+print(ts_oa) 
 #assemble time-series figure
-cp <- cowplot::plot_grid(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, 
+cp <- cowplot::plot_grid(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ts_oa,
                    align = "v",

### 2020-05-26 awipev-CO2.Rmd
Added ESSD boxplot figure

@@
 d_all$ct <- ifelse(is.nan(d_all$at), NA, d_all$ct) # replace all NaN by NA
+  dplyr::mutate(month = as.factor(month(x = datetime, label = TRUE))) %>%
+
 saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
@@
 
-```{r figures for ESSD paper, echo=FALSE, message= FALSE, warning=FALSE}
-Mytheme <- function(size_labs = 6, face_font="plain", ...) {
+```{r ESSD time series, echo=FALSE, message= FALSE, warning=FALSE}
+mytheme <- function(size_labs = 6, face_font="plain", ...) {
   theme_bw() +
-  theme(
-    # axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
-    #     axis.title.x = element_text(face="plain", size=size_labs, margin=margin(0,0,0,0,"pt")),
-    #     axis.text.y = element_text(face=face_font, color="black", size=size_labs),
-    axis.text.x = element_blank(),
-    #     axis.title.y = element_text(face="plain", size=size_labs),
-    #     axis.ticks.x = element_line(size=0.1),
-    #     axis.ticks.y = element_line(size=0.1),
-    #     axis.ticks.length = unit(1.1, "mm"),
-    #     panel.grid.major = element_line(size = 0.2, color="black", linetype="dotted"),
-    #     aspect.ratio = 1 / 3,
-        plot.margin = margin(t = 0, r = 0.3, b = 0, l = 0.3, unit = "cm")
+  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
+        axis.title.x = element_text(face=face_font, size=size_labs, margin=margin(0,0,0,0,"pt")),
+        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
+        axis.title.y = element_text(face=face_font, size=size_labs),
+        axis.ticks.x = element_line(size=0.1),
+        axis.ticks.y = element_line(size=0.1),
+        axis.ticks.length = unit(1.1, "mm"),
+        panel.grid.major = element_line(size = 0.25, color="black", linetype="dotted"),
+        aspect.ratio = 1 / 3,
+        plot.margin = margin(t = 0, r = 1, b = 0, l = 0, unit = "lines")
   )
@@
 dplyr::select(datetime, oa)
-# select time series data
+# select time series data and add Omega
 d <- as_tibble(d_all) %>%
@@
   labs(title = "", x = "", y = "Temp. 11 m (°C)") +
-  Mytheme(size_labs = 8)
+  mytheme(size_labs = 8)
 print(ts_temp) 
@@
   labs(title = "", x = "", y = "Salinity") +
-  Mytheme(size_labs = 8)
+  mytheme(size_labs = 8)
 print(ts_sal) 
@@
   labs(title = "", x = "", y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
-  Mytheme(size_labs = 8)
+  mytheme(size_labs = 8)
 print(ts_pco2) 
@@
   ) +
-  Mytheme(size_labs = 8) +
+  mytheme(size_labs = 8) +
   theme(legend.position = "none")
@@
   labs(title = "", x = "Time", y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
-  Mytheme(size_labs = 8) +
+  mytheme(size_labs = 8) +
   theme(axis.title.x = element_text(face="plain", size=8))
@@
   scale_x_datetime(limits = xlim) +
-  labs(title = "", x = "Time", y = "Omega aragonite") +
+  labs(title = "", x = "Time", y = expression(paste(Omega[a]))) +
   Mytheme(size_labs = 8) +
@@
 ```
-
-<!-- ```{r Klara Wolf} -->
-<!-- wolf <- d_all %>% -->
-<!--   dplyr::select(datetime, PCO2_Corr_filtered, phcalc, pH_calc_norm4) %>% -->
-<!--   dplyr::filter(datetime >= "2016-03-01" & datetime <= "2016-09-30") -->
-<!-- write_csv(path = "wolf.csv", wolf, col_names = TRUE) -->
-<!-- ``` -->
+```{r ESSD boxplots, echo=FALSE, message= FALSE, warning=FALSE}
+mytheme_bp <- function(size_labs = 9, face_font="plain", ...) {
+  mytheme() +
+    theme_bw() +
+  theme(aspect.ratio = 1/2,
+        plot.margin = margin(t = -2, r = 0.2, b = -2, l = 0, unit = "cm"),
+        axis.text.x=element_blank())
+  }
+d_long <- d %>% 
+  dplyr::mutate(month = as.factor(month(x = datetime, label = TRUE))) %>% 
+  tidyr::pivot_longer(-c(datetime, month), names_to = "variable", values_to = "value")
+
+sal_mix_bp <- ggplot(filter(d_long, variable=="sal_mix"), aes(x = month, y = value, group=month)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
+  labs(title=NULL,x=NULL,y = "Salinity") +
+  mytheme_bp()
+temp_11m_bp <- ggplot(filter(d_long, variable=="temp_insitu_11m"), aes(x = month, y = value, group=month)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
+  labs(title=NULL,x=NULL,y = "Temp. 11 m (°C)") +
+  mytheme_bp()
+pco2_bp <- ggplot(filter(d_long, variable=="pco2_corr"), aes(x = month, y = value, group=month)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
+  labs(title=NULL,x=NULL,y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
+  mytheme_bp()
+ph_bp <- ggplot(filter(d_long, variable=="pHint_tot_sf"), aes(x = month, y = value, group=month)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
+  labs(title=NULL,x=NULL,y = expression(paste("p", H[T]))) +
+  mytheme_bp()
+at_bp <- ggplot(filter(d_long, variable=="at_calc"), aes(x = month, y = value, group=month)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
+  labs(title=NULL,x=NULL,y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
+  mytheme_bp() +
+  theme(axis.text.x = element_text(vjust = 1))
+oa_bp <- ggplot(filter(d_long, variable=="oa"), aes(x = month, y = value, group=month)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
+  labs(title=NULL,x=NULL,y = expression(paste(Omega[a]))) +
+  mytheme_bp() +
+  theme(axis.text.x = element_text(vjust = 1))
+
+g <- cowplot::plot_grid(sal_mix_bp, temp_11m_bp, pco2_bp, ph_bp, at_bp, oa_bp, ncol=2,
+               align="v")
+g
+#g <- arrangeGrob(T1vp, S1vp, AT1vp, CT1vp, pH1vp, pCO21vp, Oa1vp, ncol=1)
+#cowplot::
+ggsave(file="figures/boxplots.png", g,  width = 18, height = 14, units = "cm")
+#g <- cowplot::plot_grid(T1vp, S1vp, AT1vp, CT1vp, pH1vp, pCO21vp, Oa1vp, ncol=2)
+#ggsave(file="figures/fig_paper_monthly_means_1m.png", g, width = 18, height = 14, units = "cm")
+```
 

### 2020-05-26 awipev-CO2.Rmd
Added ESSD boxplot figure

@@
   theme(axis.text.x = element_text(vjust = 1))
-
 g <- cowplot::plot_grid(sal_mix_bp, temp_11m_bp, pco2_bp, ph_bp, at_bp, oa_bp, ncol=2,
                align="v")
-g
-#g <- arrangeGrob(T1vp, S1vp, AT1vp, CT1vp, pH1vp, pCO21vp, Oa1vp, ncol=1)
-#cowplot::
 ggsave(file="figures/boxplots.png", g,  width = 18, height = 14, units = "cm")
-#g <- cowplot::plot_grid(T1vp, S1vp, AT1vp, CT1vp, pH1vp, pCO21vp, Oa1vp, ncol=2)
-#ggsave(file="figures/fig_paper_monthly_means_1m.png", g, width = 18, height = 14, units = "cm")
 ```

### 2020-05-26 awipev-CO2.Rmd
Added ESSD figure pCO2

@@
   theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
-        axis.title.x = element_text(face=face_font, size=size_labs, margin=margin(0,0,0,0,"pt")),
+        axis.title.x = element_text(face=face_font, size=size_labs, margin = margin(0,0,0,0,"pt")),
         axis.text.y = element_text(face=face_font, color="black", size=size_labs),
@@
         axis.ticks.length = unit(1.1, "mm"),
-        panel.grid.major = element_line(size = 0.25, color="black", linetype="dotted"),
+        panel.grid.major = element_line(size = 0.25, color="grey50", linetype="dashed"),
+        panel.grid.minor = element_line(size = rel(0.5), color = "grey50", linetype="dotted"),
         aspect.ratio = 1 / 3,
@@
   dplyr::select(datetime, pressure_insitu_ctd, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, 
-                ph_dur_corr, at_calc)
+                ph_dur_corr, pco2_calc_insitu, at_calc)
 d <- left_join(d, oa_tbf, by = 'datetime')
@@
   mytheme() +
-    theme_bw() +
   theme(aspect.ratio = 1/2,
@@
 ggsave(file="figures/boxplots.png", g,  width = 18, height = 14, units = "cm")
+```
+```{r ESSD pCO2, echo=FALSE, warning=FALSE, message=FALSE}
+fit <- lmodel2(data = d,  pco2_corr ~ pco2_calc_insitu , nperm = 99)
+
+p <-  ggplot(d, aes(x=pco2_calc_insitu, y= pco2_corr)) +
+  geom_point(color = "blue") +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
+  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]), colour = "blue") +
+  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
+                     "; Intercept =", signif(fit$regression.results[2,2], 3),
+                     "; Slope =", signif( fit$regression.results[2,3], 3),
+                     "; P =", signif(fit$P.param, 3))) +
+  coord_fixed(ratio = 1 ,xlim=c(200, 400) , ylim=c(200, 400))+
+  labs(x = expression(paste("Calculated pC", O[2], " (", mu, "atm)")), y = expression(paste("In situ pC", O[2], " (", mu, "atm)"))) + 
+  mytheme(size_labs = 10) +
+    theme(aspect.ratio=1, plot.title = element_text(size=7))
+ggsave(file="figures/pco2.png", p,  width = 14, height = 14, units = "cm")
 ```

### 2020-05-26 awipev-CO2.Rmd

@@
   mytheme(size_labs = 8)
-print(ts_temp) 
 # time series sal
@@
   mytheme(size_labs = 8)
-print(ts_sal) 
 # time series pco2
@@
   mytheme(size_labs = 8)
-print(ts_pco2) 
 # time series pH
@@
   theme(legend.position = "none")
-print(ts_ph) 
 # time series AT
@@
   theme(axis.title.x = element_text(face="plain", size=8))
-print(ts_at) 
 # time series Omega
@@
   theme(axis.title.x = element_text(face="plain", size=8))
-print(ts_oa) 
 #assemble time-series figure
@@
                    )
-print(cp)
 cowplot::ggsave2(filename = "figures/ts_gg.png", plot = cp, height = 20, units = "cm")

### 2020-05-27 prettyaxes.R
Added scripts from Jim Orr to investigate the uncertaintie in pK1 and pK2

@@ -1,0 +1,4 @@
+ box()
+ axis(1,labels=FALSE, tcl=-0.35) ; axis(1, lwd=0, line=-0.4, labels=TRUE)
+ axis(2,labels=FALSE,tcl=-0.35)  ; axis(2, lwd=0, line=-0.4, las=2, labels=TRUE)
+ axis(3,labels=FALSE,tcl=-0.35) ; axis(4,labels=FALSE,tcl=-0.25)

### 2020-05-27 awipev-CO2.Rmd
clean-up calculation pH seafet

@@
 
-##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ****** $SA$
+##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
 ##   *****Attention, I asked to the logisticians to log insitu temp from 9 june 2019
+##   *****Attention, but no longer used in the script, so no problem
 
@@
 
-# $SA$ below
-#periode 1, mean of 4 next hours for volt int + T seaF
-# mean_voltINT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
-#       datetime <= as.POSIXct("2017-08-24 22:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
-#mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+# For this spec pH, some volt int and T seaF data are missing so we use the closest data
 zz <- d_all %>%
@@
   ))
-# mean_voltEXT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
-#       datetime <= as.POSIXct("2017-08-24 22:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
-# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
 zz <- d_all %>%
@@
   ))
-# mean_TseaF_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
-#       datetime <= as.POSIXct("2017-08-24 22:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
-# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
 zz <- d_all %>%
@@
 
-# Periode 2, mean of 4 next hours for volt int + T seaF
-# mean_voltINT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2017-09-28 15:00:00") &
-#       datetime <= as.POSIXct("2017-09-28 18:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
-# mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+# For this spec pH, some volt int and T seaF data are missing so we use the closest data
 zz <- d_all %>%
@@
   ))
-# mean_voltEXT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2017-09-28 15:00:00") &
-#       datetime <= as.POSIXct("2017-09-28 18:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
-# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
 zz <- d_all %>%
@@
 
-# period 03, mean of 4 previous hours for volt int + volt ext
-# mean_voltINT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2019-09-13 04:00:00") &
-#       datetime <= as.POSIXct("2019-09-13 07:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
+# For this spec pH, some volt int and T seaF data are missing so we use the closest data
 zz <- d_all %>%
@@
 mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
-
-# Ce qui suit (7 lignes) est très bizarre
 d_all <- d_all %>%
   dplyr::mutate(voltINT = ifelse(
-    datetime == as.POSIXct("2017-09-28 13:00:00"),
+    datetime == as.POSIXct("2019-09-13 13:00:00"),
     mean_voltINT_4h,
@@
   ))
-# ???????? mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
 d_all <- d_all %>%
@@
   ))
-# mean_voltEXT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2019-09-13 04:00:00") &
-#       datetime <= as.POSIXct("2019-09-13 07:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
-# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
 zz <- d_all %>%
@@
 
-# period 04 also, mean of 4 previous hours for volt int + volt ext + T seaF
-# mean_voltINT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
-#       datetime <= as.POSIXct("2019-09-13 12:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
-# mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
+# For this spec pH, some volt int and T seaF data are missing so we use the closest data
 zz <- d_all %>%
@@
   ))
-# mean_voltEXT_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
-#       datetime <= as.POSIXct("2019-09-13 12:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
-# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
 zz <- d_all %>%
@@
   ))
-# mean_TseaF_4h <- d_all %>%
-#   dplyr::filter(
-#     datetime >= as.POSIXct("2019-09-13 11:00:00") &
-#       datetime <= as.POSIXct("2019-09-13 12:00:00")
-#   ) %>%
-#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
-# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
 zz <- d_all %>%
@@
 #### plot
-# $SA$ 3 points?
 kk <- melt(calib_spectro, id.vars="deployment_sf")
-p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable),size=2) +
+p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
   facet_grid(variable~., scales="free_y") + theme_bw() +
@@
 
-[All UWO-Ferrybox data / NearRealTime (NRT) AWI database](https://dashboard.awi.de/data-xxl/overview.jsp)
-
 [Procedure to download NRT data](https://spaces.awi.de/confluence/display/MOS/NRT+data+download+procedures)
@@
 [AWI NRT database](https://dashboard.awi.de/data-xxl/overview.jsp)
-
-[Missing data to add to the NRT database](https://docs.google.com/spreadsheets/d/1Cbc4hWyclnBsNsOH_3QDA3AGZfwF4I1HuadfBe1BVjI/edit?usp=sharing)
 

### 2020-05-27 awipev-CO2.Rmd
removed pH and pCO2 calculated in situ which are meaningless (at and ct sampled in the FB)

@@
   dplyr::arrange(date)
-
-# pH calculated (at and ct) at in situ (11 m) sal and temp
-discrete_no_na <- discrete %>%
-  dplyr::filter(!is.na(sal_mix)  & !is.na(temp_insitu_11m) & !is.na(at) & !is.na(ct))
-discrete_is_na <- discrete %>%
-  dplyr::filter(is.na(sal_mix)  | is.na(temp_insitu_11m) | is.na(at) | is.na(ct))
-carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_mix, T = discrete_no_na$temp_insitu_11m, P = 11/10, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-discrete_no_na$phcalc_insitu <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
-discrete_no_na$pco2_calc_insitu <- carb$pCO2
-
-#create new variable in "discrete_is_na" to bind "discrete_no_na"
-discrete_is_na$phcalc_insitu <- NA
-discrete_is_na$pco2_calc_insitu <- NA
-discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
-  dplyr::arrange(date)
-
 ```
@@
   dplyr::select(closest_datetime, phcalc_fb) %>%
-  dplyr::filter(!is.na(closest_datetime)) %>%
-  rename(datetime=closest_datetime)
-d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-# pH calculated in situ
-discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, phcalc_insitu) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%

### 2020-05-29 awipev-CO2.Rmd
Minor update
Update following changes from pco2-calc_insitu to pco2-calc_fb

@@
 discrete_no_na$phcalc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
-#discrete_no_na$pco2_calc<- carb$pCO2
+discrete_no_na$pco2_calc_fb <- carb$pCO2
 
@@
 discrete_is_na$phcalc_fb <- NA
-#discrete_is_na$pco2_calc<- NA
+discrete_is_na$pco2_calc_fb <- NA
 discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
@@
 discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, pco2_calc_insitu) %>%
+  dplyr::select(closest_datetime, pco2_calc_fb) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 title <- "Contros vs calculated pCO2"
-fit <- lmodel2(data = d_all,  pco2_corr ~ pco2_calc_insitu , nperm = 99)
-
-p <-  ggplot(d_all,aes(x=pco2_calc_insitu, y= pco2_corr, label = month))+
+fit <- lmodel2(data = d_all,  pco2_corr ~ pco2_calc_fb , nperm = 99)
+
+p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_corr, label = month))+
    geom_text(aes(color = factor(month)))+
@@
 ```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-print(p) # pco2_calc_insitu_pco2_corr_text
+print(p) # pco2_calc_fb_pco2_corr_text
 ```
@@
 pco2_contros_xts <-
-  dplyr::select(d_all, datetime, pco2_calc_insitu, pco2_corr)
+  dplyr::select(d_all, datetime, pco2_calc_fb, pco2_corr)
 pco2_contros_xts <-
@@
   dySeries(
-    "pco2_calc_insitu",
-    label = "pco2_calc_insitu",
+    "pco2_calc_fb",
+    label = "pco2_calc_fb",
     color = "red",
@@
 d_all$ct <- ifelse(is.nan(d_all$at), NA, d_all$ct) # replace all NaN by NA
-  dplyr::mutate(month = as.factor(month(x = datetime, label = TRUE))) %>%
+dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))
 
@@
   dplyr::select(datetime, pressure_insitu_ctd, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, 
-                ph_dur_corr, pco2_calc_insitu, at_calc)
+                ph_dur_corr, pco2_calc_fb, at_calc)
 d <- left_join(d, oa_tbf, by = 'datetime')
@@
 ```{r ESSD pCO2, echo=FALSE, warning=FALSE, message=FALSE}
-fit <- lmodel2(data = d,  pco2_corr ~ pco2_calc_insitu , nperm = 99)
-
-p <-  ggplot(d, aes(x=pco2_calc_insitu, y= pco2_corr)) +
+fit <- lmodel2(data = d,  pco2_corr ~ pco2_calc_fb , nperm = 99)
+
+p <-  ggplot(d, aes(x=pco2_calc_fb, y= pco2_corr)) +
   geom_point(color = "blue") +
@@
 
+[Logbook discrete sampling](https://docs.google.com/spreadsheets/d/1bNh9q4bkNoh2ra78XC451EmGb9Q8kMf4ByBnKngeHOg/edit#gid=1034421443)
+
 [UWO-Ferrybox variables from our sensors](https://docs.google.com/spreadsheets/d/1arKYfUjmg3YrgQ5g9LN_XFwUORyz7nqlKNWq3uYok3U/edit?ts=5c7e1d16#gid=393659093)
@@
 
-[AWI NRT database](https://dashboard.awi.de/data-xxl/overview.jsp)
+[AWI NRT database](https://dashboard.awi.de/data-xxl/), search for svluwobs
 
@@
 * temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
-* pco2_calc_insitu: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
+* pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
 * calibrate seafet pH

### 2020-05-29 awipev-CO2.Rmd
preapre data file for upload to Pangaea

@@
 dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))
-
 saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
+
+pangaea <- as_tibble(d_all) %>% 
+  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, pco2_corr, at_calc, ph_dur_corr, pHint_tot_sf) %>%
+  dplyr::rename(pressure = pressure_insitu_ctd,
+                s_insitu = sal_insitu_ctd,
+                sal_fb = sal_fb, 
+                t_11m = temp_insitu_11m,
+                t_insitu = temp_insitu_ctd, 
+                t_fb = temp_fb, 
+                t_sf = temp_sf, 
+                t_dur = temp_dur, 
+                at = at, 
+                at_calc =at_calc,
+                ct = ct, 
+                ph_s_sf_temp_insi = ph_s_sf_temp_insi, 
+                ph_s_dur_temp_fb = ph_s_dur_temp_fb,
+                pco2 = pco2_corr,
+                pH_sf = pHint_tot_sf,
+                ph_dur = ph_dur_corr
+                )
+saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
+write_csv(pangaea, path = paste0(path, "fb_data/pangaea.csv"))
+# Metadata Pangaea
+# pressure = pressure in situ (profiler)
+# s_insitu = salinity in situ (profiler)
+# sal_fb = salinity in FerryBox 
+# t_11m = temperature in situ at 11 m
+# t_insitu = temperature in situ (profiler), 
+# t_fb = temperature in FerryBox 
+# t_sf = temperature SeaFET (profiler) 
+# t_dur = temperature Durafet (FerryBox)
+# at = total alkalinity, discrete measurements (FerryBox)
+# at_calc = total alkalinity, calculated from salinity
+# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
+# ph_s_sf_temp_insi = pH spectrophotometric SeaFET in situ (11 m)
+# ph_s_dur_temp_fb = pH spectrophotometric Durafet in FerryBox
+# pco2 = pCO2 in Ferrybox
+# pH_sf = pH SeaFET at in situ temperature (profiler)
+# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
 ```

### 2020-05-29 figs_essd.R
new script for making the ESSD figures

@@ -1,0 +1,256 @@
+## Figures AWIPEV-CO2 for ESSD paper
+
+# set up ####
+Sys.setlocale("LC_ALL", "en_US.UTF-8")
+Sys.setenv(TZ='UTC') # on utilise UTC
+rm(list = ls())
+if (!require("tidyverse")) install.packages("tidyverse")
+library(tidyverse)
+if (!require("robfilter")) install.packages("robfilter")
+if (!require("robfilter")) install.packages("robfilter")
+library("robfilter")
+if (!require("seacarb")) install.packages("seacarb")
+library("seacarb")
+if (!require("gridExtra")) install.packages("gridExtra")
+library("gridExtra")
+if (!require("reshape2")) install.packages("reshape2")
+library("reshape2")
+if (!require("lubridate")) install.packages("lubridate")
+library("lubridate")
+if (!require("lmtest")) install.packages("lmtest")
+library("lmtest")
+if (!require("grid")) install.packages("grid")
+library(grid)
+if (!require("viridis")) install.packages("viridis")
+library("viridis")
+if (!require("dygraphs")) install.packages("dygraphs")
+library("dygraphs")
+if (!require("knitr")) install.packages("knitr")
+require("knitr")
+if (!require("lmodel2")) install.packages("lmodel2")
+library("lmodel2")
+if (!require("captioner")) install.packages("captioner")
+library("captioner")
+if (!require("xts")) install.packages("xts")
+library("xts")
+if (!require("seismicRoll")) install.packages("seismicRoll")
+library("seismicRoll")
+if (!require("scales")) install.packages("scales")
+library("scales")
+if (!require("cowplot")) install.packages("cowplot")
+library(cowplot)
+if (!require("htmlwidgets")) install.packages("htmlwidgets")
+library("htmlwidgets")
+if (!require("hms")) install.packages("hms")
+library("hms")
+knitr::opts_chunk$set(echo = TRUE)
+
+fig_nums <- captioner()
+table_nums <- captioner(prefix = "Table")
+
+#define who is the user and define path
[…]

### 2020-05-29 figs_essd.R
revised using new variable names

@@ -66,6 +66,7 @@ mytheme <- function(size_labs = 6, face_font="plain", ...) {
           aspect.ratio = 1 / 3,
           plot.margin = margin(t = 0, r = 1, b = 0, l = 0, unit = "lines")
     )
+}
 
 # Read data ####
 d <-
@@ -78,48 +79,48 @@ d <-
 # time series ####
 xlim <- c(as.POSIXct("2015-07-01 00:00:00"), as.POSIXct("2020-07-01 00:00:00"))
 # calculate omeaga arag
-z <- d_all %>% 
-  dplyr::filter(!(is.na(pco2_corr) | is.na(at_calc) | is.na(sal_mix) |is.na(temp_insitu_11m) | is.na(pressure_insitu_ctd)))
+z <- d %>% 
+  dplyr::filter(!(is.na(pco2) | is.na(at_calc) | is.na(s_mix) |is.na(t_11m) | is.na(pressure)))
 oa_tbf <- as_tibble(
-  carb(24, z$pco2_corr, z$at_calc*1e-6, S = z$sal_mix, T = z$temp_insitu_11m, 
-       P = z$pressure_insitu_ctd/10, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", 
+  carb(24, z$pco2, z$at_calc*1e-6, S = z$s_mix, T = z$t_11m, 
+       P = z$pressure/10, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", 
        ks = "d", pHscale = "T", b = "u74")
 ) %>% 
   dplyr::mutate(datetime = z$datetime,
                 oa = OmegaAragonite) %>% 
   dplyr::select(datetime, oa)
 # select time series data and add Omega
-d <- as_tibble(d_all) %>%
-  dplyr::select(datetime, pressure_insitu_ctd, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, 
-                ph_dur_corr, pco2_calc_fb, at_calc)
+d <- as_tibble(d) %>%
+  dplyr::select(datetime, pressure, t_11m, s_mix, pco2, pH_sf, 
+                ph_dur, pco2_calc, at_calc)
 d <- left_join(d, oa_tbf, by = 'datetime')
 
 # time series temp
 ts_temp <- d %>%
-  dplyr::filter(!is.na(temp_insitu_11m)) %>% 
+  dplyr::filter(!is.na(t_11m)) %>% 
   ggplot() +
[…]

### 2020-05-29 awipev-CO2.Rmd
added variables to the pangaea file

--- 2020-05-29 awipev-CO2.Rmd
@@
 dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))
-
 saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
+
+pangaea <- as_tibble(d_all) %>% 
+  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, pco2_corr, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
+  dplyr::rename(pressure = pressure_insitu_ctd,
+                s_insitu = sal_insitu_ctd,
+                s_fb = sal_fb, 
+                s_mix = sal_mix,
+                t_11m = temp_insitu_11m,
+                t_insitu = temp_insitu_ctd, 
+                t_fb = temp_fb, 
+                t_sf = temp_sf, 
+                t_dur = temp_dur, 
+                at = at, 
+                at_calc =at_calc,
+                ct = ct, 
+                ph_s_sf_t_insi = ph_s_sf_temp_insi, 
+                ph_s_dur_t_fb = ph_s_dur_temp_fb,
+                pco2 = pco2_corr,
+                pco2_calc = pco2_calc_fb,
+                pH_sf = pHint_tot_sf,
+                ph_dur = ph_dur_corr
+                )
+saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
+write_csv(pangaea, path = paste0(path, "fb_data/pangaea.csv"))
+# Metadata Pangaea
+# pressure = pressure in situ (profiler)
+# s_insitu = salinity in situ (profiler)
+# s_fb = salinity in FerryBox 
+# s_mix = salinity in FerryBox with gaps filled by s_insitu below 8 m
+# t_11m = temperature in situ at 11 m
+# t_insitu = temperature in situ (profiler), 
+# t_fb = temperature in FerryBox 
+# t_sf = temperature SeaFET (profiler) 
+# t_dur = temperature Durafet (FerryBox)
+# at = total alkalinity, discrete measurements (FerryBox)
+# at_calc = total alkalinity, calculated from salinity
+# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
+# ph_s_sf_t_insi = pH spectrophotometric SeaFET in situ (11 m)
+# ph_s_dur_t_fb = pH spectrophotometric Durafet in FerryBox
+# pco2 = pCO2 in Ferrybox
+# pco2_calc = pCO2 calculated in the FerryBox calculated from discrete measurments of AT and CT
+# pH_sf = pH SeaFET at in situ temperature (profiler)
+# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
 ```

### 2020-05-29 awipev-CO2.Rmd
Updated linksat the end

--- 2020-05-29 awipev-CO2.Rmd
@@
 dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))
-
 saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
+
+pangaea <- as_tibble(d_all) %>% 
+  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, pco2_corr, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
+  dplyr::rename(pressure = pressure_insitu_ctd,
+                s_insitu = sal_insitu_ctd,
+                s_fb = sal_fb, 
+                s_mix = sal_mix,
+                t_11m = temp_insitu_11m,
+                t_insitu = temp_insitu_ctd, 
+                t_fb = temp_fb, 
+                t_sf = temp_sf, 
+                t_dur = temp_dur, 
+                at = at, 
+                at_calc =at_calc,
+                ct = ct, 
+                ph_s_sf_t_insi = ph_s_sf_temp_insi, 
+                ph_s_dur_t_fb = ph_s_dur_temp_fb,
+                pco2 = pco2_corr,
+                pco2_calc = pco2_calc_fb,
+                pH_sf = pHint_tot_sf,
+                ph_dur = ph_dur_corr
+                )
+saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
+write_csv(pangaea, path = paste0(path, "fb_data/pangaea.csv"))
+# Metadata Pangaea
+# pressure = pressure in situ (profiler)
+# s_insitu = salinity in situ (profiler)
+# s_fb = salinity in FerryBox 
+# s_mix = salinity in FerryBox with gaps filled by s_insitu below 8 m
+# t_11m = temperature in situ at 11 m
+# t_insitu = temperature in situ (profiler), 
+# t_fb = temperature in FerryBox 
+# t_sf = temperature SeaFET (profiler), °C
+# t_dur = temperature Durafet (FerryBox)
+# at = total alkalinity, discrete measurements (FerryBox)
+# at_calc = total alkalinity, calculated from salinity
+# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
+# ph_s_sf_t_insi = pH spectrophotometric SeaFET in situ (11 m)
+# ph_s_dur_t_fb = pH spectrophotometric Durafet in FerryBox
+# pco2 = pCO2 in Ferrybox
+# pco2_calc = pCO2 calculated in the FerryBox calculated from discrete measurments of AT and CT
+# pH_sf = pH SeaFET at in situ temperature (profiler)
+# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
 ```
@@
 
-[wiki document](https://spaces.awi.de/confluence/login.action?os_destination=%2Fpages%2Fviewpage.action%3FspaceKey%3DMOS%26title%3DWater%2Bsampling&permissionViolation=true)
+[wiki document](https://spaces.awi.de)
 
@@
 
+[Logbook FerryBox](https://docs.google.com/spreadsheets/d/1QwAJm7TttoEwue-CUM0efhqEAMwj5m148Gy_Mp-1maM/edit?ts=5ed0fca6#gid=2036495380)
+
 [UWO-Ferrybox variables from our sensors](https://docs.google.com/spreadsheets/d/1arKYfUjmg3YrgQ5g9LN_XFwUORyz7nqlKNWq3uYok3U/edit?ts=5c7e1d16#gid=393659093)
+
+[Dashboard](https://dashboard.awi.de/?dashboard=3760)
 

### 2020-08-17 figs_essd.R
update of the day

@@ -6,8 +6,8 @@ Sys.setenv(TZ='UTC') # on utilise UTC
 rm(list = ls())
 if (!require("tidyverse")) install.packages("tidyverse")
 library(tidyverse)
-if (!require("robfilter")) install.packages("robfilter")
-library("robfilter")
+# if (!require("robfilter")) install.packages("robfilter")
+# library("robfilter")
 if (!require("seacarb")) install.packages("seacarb")
 library("seacarb")
 if (!require("gridExtra")) install.packages("gridExtra")
@@ -22,18 +22,18 @@ if (!require("grid")) install.packages("grid")
 library(grid)
 if (!require("viridis")) install.packages("viridis")
 library("viridis")
-if (!require("dygraphs")) install.packages("dygraphs")
-library("dygraphs")
-if (!require("knitr")) install.packages("knitr")
-require("knitr")
+# if (!require("dygraphs")) install.packages("dygraphs")
+# library("dygraphs")
+# if (!require("knitr")) install.packages("knitr")
+# require("knitr")
 if (!require("lmodel2")) install.packages("lmodel2")
 library("lmodel2")
-if (!require("captioner")) install.packages("captioner")
-library("captioner")
+# if (!require("captioner")) install.packages("captioner")
+# library("captioner")
 if (!require("xts")) install.packages("xts")
 library("xts")
-if (!require("seismicRoll")) install.packages("seismicRoll")
-library("seismicRoll")
+# if (!require("seismicRoll")) install.packages("seismicRoll")
+# library("seismicRoll")
 if (!require("scales")) install.packages("scales")
 library("scales")
 if (!require("cowplot")) install.packages("cowplot")
@@ -60,7 +60,7 @@ mytheme <- function(size_labs = 6, face_font="plain", ...) {
           panel.grid.major = element_line(size = 0.25, color="grey50", linetype="dashed"),
           panel.grid.minor = element_line(size = rel(0.5), color = "grey50", linetype="dotted"),
           aspect.ratio = 1 / 3,
-          plot.margin = margin(t = 0, r = 1, b = 0, l = 0, unit = "lines")
+          plot.margin = margin(t = 0, r = 1, b = 0, l = 1, unit = "lines")
     )
 }
 
@@ -152,7 +152,7 @@ ts_at <- d %>%
   ggplot() +
[…]

### 2020-08-18 figs_essd.R
boxplots OK

@@ -182,43 +182,49 @@ grid.arrange(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ts_oa, ncol = 1)
 mytheme_bp <- function(size_labs = 9, face_font="plain", ...) {
   mytheme() +
     theme(aspect.ratio = 1/2,
-          plot.margin = margin(t = -2, r = 0.2, b = -2, l = 0, unit = "cm"),
-          axis.text.x=element_blank())
+          plot.margin = margin(t = -2, r = 0.2, b = -2, l = 0, unit = "cm")
+#          axis.text.x=element_blank()
+)
 }
 
 d_long <- d %>% 
-  dplyr::mutate(month = as.factor(lubridate::month(x = datetime, abbr = TRUE))) %>% 
-  tidyr::pivot_longer(-c(datetime, month), names_to = "variable", values_to = "value")
+  dplyr::mutate(month = as.factor(lubridate::month(x = datetime, label = TRUE, abbr = TRUE))) %>% 
+  tidyr::pivot_longer(-c(datetime, month), names_to = "variable", values_to = "value") %>%
+  dplyr::filter(!is.na(value)) # remove NAs to avoid warnings
 
 s_mix_bp <- ggplot(filter(d_long, variable=="s_mix"), aes(x = month, y = value, group=month)) +
   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
   scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
   labs(title=NULL,x=NULL,y = "Salinity") +
-  mytheme_bp()
+  mytheme_bp() + 
+  theme(axis.text.x=element_blank())
 temp_11m_bp <- ggplot(filter(d_long, variable=="t_11m"), aes(x = month, y = value, group=month)) +
   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
   scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
[…]

### 2020-08-18 figs_essd.R
pCO2 OK

@@ -245,7 +245,7 @@ p <-  ggplot(d, aes(x=pco2_calc, y= pco2), na.rm = TRUE) +
   geom_point(color = "blue") +
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]), colour = "blue") +
-  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
+  labs(title = paste("\n Adj R2 = ", signif(fit$rsquare, 3),
                      "; Intercept =", signif(fit$regression.results[2,2], 3),
                      "; Slope =", signif( fit$regression.results[2,3], 3),
                      "; P =", signif(fit$P.param, 3))) +

### 2020-08-18 figs_essd.R
pH durafet OK

@@ -43,9 +43,23 @@ library("htmlwidgets")
 if (!require("hms")) install.packages("hms")
 library("hms")
 
-#define who is the user and define path
+#################### define who is the user and define path
 if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
 if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"
+
+#################### Function RMSE root mean square error
+rmse <- function(error) { sqrt(mean(error^2, na.rm=TRUE)) }
+#rmse(fit$residuals)
+
+#################### Function RMSE for model 2 regression root mean square error
+rmse2 <- function(x, y) { 
+  fit <- lmodel2(y  ~ x , nperm = 99)
+  intercept <- fit$regression.results[2,2]
+  slope <- fit$regression.results[2,3]
+  predicted <- intercept + x * slope
+  error <- predicted - x
+  sqrt(mean(error^2, na.rm=TRUE))
+  }
 
 mytheme <- function(size_labs = 6, face_font="plain", ...) {
   theme_bw() +
@@ -245,7 +259,7 @@ p <-  ggplot(d, aes(x=pco2_calc, y= pco2), na.rm = TRUE) +
   geom_point(color = "blue") +
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]), colour = "blue") +
-  labs(title = paste("\n Adj R2 = ", signif(fit$rsquare, 3),
+  labs(title = paste("Adj R2 = ", signif(fit$rsquare, 3),
                      "; Intercept =", signif(fit$regression.results[2,2], 3),
                      "; Slope =", signif( fit$regression.results[2,3], 3),
                      "; P =", signif(fit$P.param, 3))) +
@@ -256,23 +270,27 @@ p <-  ggplot(d, aes(x=pco2_calc, y= pco2), na.rm = TRUE) +
   theme(aspect.ratio=1, plot.title = element_text(size=7))
 ggsave(file="figures/essd/pco2.png", p,  width = 14, height = 14, units = "cm")
 
-# pH: spectro vs Durafet ####
-fit <- lmodel2(data = d,  ph_s_dur_t_fb ~ ph_dur , nperm = 99)
[…]

### 2020-08-18 figs_essd.R
struggling with lm2 and rmse

@@ -52,13 +52,14 @@ rmse <- function(error) { sqrt(mean(error^2, na.rm=TRUE)) }
 #rmse(fit$residuals)
 
 #################### Function RMSE for model 2 regression root mean square error
-rmse2 <- function(x, y) { 
+lm2 <- function(x, y) { 
   fit <- lmodel2(y  ~ x , nperm = 99)
   intercept <- fit$regression.results[2,2]
   slope <- fit$regression.results[2,3]
   predicted <- intercept + x * slope
   error <- predicted - x
-  sqrt(mean(error^2, na.rm=TRUE))
+  my_list <- list(fit = fit, rmse = sqrt(mean(error^2, na.rm=TRUE)))
+  return(my_list)
   }
 
 mytheme <- function(size_labs = 6, face_font="plain", ...) {
@@ -254,20 +255,26 @@ g <- cowplot::plot_grid(s_mix_bp, temp_11m_bp, pco2_bp, ph_bp, at_bp, oa_bp, nco
 ggsave(file="figures/essd/boxplots.png", g,  width = 18, height = 14, units = "cm")
 
 # pCO2 ####
-fit <- lmodel2(data = d,  pco2 ~ pco2_calc , nperm = 99)
+da <- dplyr::filter(d, !is.na(pco2_calc), !is.na(pco2))
+lm2 <- lm2(x = da$pco2_calc, y = da$pco2)
+#fit <- lmodel2(data = d,  pco2 ~ pco2_calc , nperm = 99)
 p <-  ggplot(d, aes(x=pco2_calc, y= pco2), na.rm = TRUE) +
   geom_point(color = "blue") +
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]), colour = "blue") +
-  labs(title = paste("Adj R2 = ", signif(fit$rsquare, 3),
+  labs(x = expression(paste("Calculated pC", O[2], " (", mu, "atm)")), 
+       y = expression(paste("In situ pC", O[2], " (", mu, "atm)")),
+       title = paste("Adj R2 = ", signif(fit$rsquare, 3),
                      "; Intercept =", signif(fit$regression.results[2,2], 3),
                      "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
+                     "; P =", signif(fit$P.param, 3),
[…]

### 2020-08-19 awipev-CO2.Rmd
deleted chunks ESSD paper

@@
 
-## Figures for ESSD paper
-
-```{r ESSD time series, echo=FALSE, message= FALSE, warning=FALSE}
-mytheme <- function(size_labs = 6, face_font="plain", ...) {
-  theme_bw() +
-  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
-        axis.title.x = element_text(face=face_font, size=size_labs, margin = margin(0,0,0,0,"pt")),
-        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
-        axis.title.y = element_text(face=face_font, size=size_labs),
-        axis.ticks.x = element_line(size=0.1),
-        axis.ticks.y = element_line(size=0.1),
-        axis.ticks.length = unit(1.1, "mm"),
-        panel.grid.major = element_line(size = 0.25, color="grey50", linetype="dashed"),
-        panel.grid.minor = element_line(size = rel(0.5), color = "grey50", linetype="dotted"),
-        aspect.ratio = 1 / 3,
-        plot.margin = margin(t = 0, r = 1, b = 0, l = 0, unit = "lines")
-  )
-}
-
-xlim <- c(as.POSIXct("2015-07-01 00:00:00"), as.POSIXct("2020-07-01 00:00:00"))
-# calculate omeaga arag
-z <- d_all %>% 
-  dplyr::filter(!(is.na(pco2_corr) | is.na(at_calc) | is.na(sal_mix) |is.na(temp_insitu_11m) | is.na(pressure_insitu_ctd)))
-oa_tbf <- as_tibble(
-  carb(24, z$pco2_corr, z$at_calc*1e-6, S = z$sal_mix, T = z$temp_insitu_11m, 
-                          P = z$pressure_insitu_ctd/10, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", 
-                          ks = "d", pHscale = "T", b = "u74")
-) %>% 
-  dplyr::mutate(datetime = z$datetime,
-                oa = OmegaAragonite) %>% 
-dplyr::select(datetime, oa)
-# select time series data and add Omega
-d <- as_tibble(d_all) %>%
-  dplyr::select(datetime, pressure_insitu_ctd, temp_insitu_11m, sal_mix, pco2_corr, pHint_tot_sf, 
-                ph_dur_corr, pco2_calc_fb, at_calc)
-d <- left_join(d, oa_tbf, by = 'datetime')
-
-# time series temp
-ts_temp <- d %>%
-  dplyr::filter(!is.na(temp_insitu_11m)) %>% 
-  ggplot() +
-  geom_point(aes(x = datetime, y = temp_insitu_11m), col = "blue", size = 0.15) +
-  labs(title = "", x = "", y = "Temp. 11 m (°C)") +
-  mytheme(size_labs = 8)
-# time series sal
-ts_sal <- d %>%
-  dplyr::filter(!is.na(sal_mix)) %>% 
-ggplot() +
-  geom_point(aes(x = datetime, y = sal_mix), col = "blue", size = 0.15) + 
-  labs(title = "", x = "", y = "Salinity") +
-  mytheme(size_labs = 8)
-# time series pco2
-ts_pco2 <- d %>%
-  dplyr::filter(!is.na(pco2_corr)) %>% 
-  ggplot() +
-  geom_point(aes(x = datetime, y = pco2_corr), col = "blue", size = 0.15) +
-  scale_x_datetime(limits = xlim) +
-  labs(title = "", x = "", y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
-  mytheme(size_labs = 8)
-# time series pH
-ts_ph <- d %>%
-  dplyr::select(datetime, pHint_tot_sf, ph_dur_corr) %>%
-  dplyr::filter(!is.na(pHint_tot_sf)) %>%
-  pivot_longer(-datetime, names_to = "pH", values_to = "value") %>%
-  ggplot() +
-  geom_point(aes(x = datetime, y = value, colour = pH), size = 0.15) +
-  scale_x_datetime(limits = xlim) +
-  labs(title = "",
-       x = "",
-       y = expression(paste("p", H[T]))) +
-  # scale_color_manual(
-  #   values = c("blue", "red"),
-  #   name = "",
-  #   breaks = c("pHint_tot_sf", "ph_dur_corr"),
-  #   labels = c("SeaFET", "Durafet")
-  # ) +
-  annotate(
-    geom = "text",
-    x = as.POSIXct("2018-06-01"),
-    y = 8.35,
-    label = "seaFET",
-    color = "blue", size = 2
-  ) +
-  annotate(
-    geom = "text",
-    x = as.POSIXct("2018-06-01"),
-    y = 8.25,
-    label = "Durafet",
-    color = "red", size = 2
-  ) +
-  mytheme(size_labs = 8) +
-  theme(legend.position = "none")
-# time series AT
-ts_at <- d %>%
-  dplyr::filter(!is.na(at_calc)) %>% 
-  ggplot() +
-  geom_point(aes(x = datetime, y = at_calc), col = "blue", size = 0.15) +
-  scale_x_datetime(limits = xlim) +
-  labs(title = "", x = "Time", y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
-  mytheme(size_labs = 8) +
-  theme(axis.title.x = element_text(face="plain", size=8))
-# time series Omega
-ts_oa <- d %>%
-  dplyr::filter(!is.na(oa)) %>% 
-  ggplot() +
-  geom_point(aes(x = datetime, y = oa), col = "blue", size = 0.15) +
-  scale_x_datetime(limits = xlim) +
-  labs(title = "", x = "Time", y = expression(paste(Omega[a]))) +
-  Mytheme(size_labs = 8) +
-  theme(axis.title.x = element_text(face="plain", size=8))
-#assemble time-series figure
-cp <- cowplot::plot_grid(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ts_oa,
-                   align = "v",
-                   #labels = "AUTO",
-                   ncol = 1
-                   #width = 18,
-                   #units = "cm"
-                   )
-cowplot::ggsave2(filename = "figures/ts_gg.png", plot = cp, height = 20, units = "cm")
-
-# ts_sal / ts_temp / ts_at
-# grid.arrange(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ncol = 1)
-# cowplot::save_plot(filename = "figures/ts_sp.pdf", plot = cp)
-# multiplot(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, cols = 1)
-```
-```{r ESSD boxplots, echo=FALSE, message= FALSE, warning=FALSE}
-mytheme_bp <- function(size_labs = 9, face_font="plain", ...) {
-  mytheme() +
-  theme(aspect.ratio = 1/2,
-        plot.margin = margin(t = -2, r = 0.2, b = -2, l = 0, unit = "cm"),
-        axis.text.x=element_blank())
-  }
-d_long <- d %>% 
-  dplyr::mutate(month = as.factor(month(x = datetime, label = TRUE))) %>% 
-  tidyr::pivot_longer(-c(datetime, month), names_to = "variable", values_to = "value")
-
-sal_mix_bp <- ggplot(filter(d_long, variable=="sal_mix"), aes(x = month, y = value, group=month)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
-  labs(title=NULL,x=NULL,y = "Salinity") +
-  mytheme_bp()
-temp_11m_bp <- ggplot(filter(d_long, variable=="temp_insitu_11m"), aes(x = month, y = value, group=month)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
-  labs(title=NULL,x=NULL,y = "Temp. 11 m (°C)") +
-  mytheme_bp()
-pco2_bp <- ggplot(filter(d_long, variable=="pco2_corr"), aes(x = month, y = value, group=month)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
-  labs(title=NULL,x=NULL,y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
-  mytheme_bp()
-ph_bp <- ggplot(filter(d_long, variable=="pHint_tot_sf"), aes(x = month, y = value, group=month)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
-  labs(title=NULL,x=NULL,y = expression(paste("p", H[T]))) +
-  mytheme_bp()
-at_bp <- ggplot(filter(d_long, variable=="at_calc"), aes(x = month, y = value, group=month)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
-  labs(title=NULL,x=NULL,y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
-  mytheme_bp() +
-  theme(axis.text.x = element_text(vjust = 1))
-oa_bp <- ggplot(filter(d_long, variable=="oa"), aes(x = month, y = value, group=month)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
-  labs(title=NULL,x=NULL,y = expression(paste(Omega[a]))) +
-  mytheme_bp() +
-  theme(axis.text.x = element_text(vjust = 1))
-g <- cowplot::plot_grid(sal_mix_bp, temp_11m_bp, pco2_bp, ph_bp, at_bp, oa_bp, ncol=2,
-               align="v")
-ggsave(file="figures/boxplots.png", g,  width = 18, height = 14, units = "cm")
-```
-```{r ESSD pCO2, echo=FALSE, warning=FALSE, message=FALSE}
-fit <- lmodel2(data = d,  pco2_corr ~ pco2_calc_fb , nperm = 99)
-
-p <-  ggplot(d, aes(x=pco2_calc_fb, y= pco2_corr)) +
-  geom_point(color = "blue") +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]), colour = "blue") +
-  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  coord_fixed(ratio = 1 ,xlim=c(200, 400) , ylim=c(200, 400))+
-  labs(x = expression(paste("Calculated pC", O[2], " (", mu, "atm)")), y = expression(paste("In situ pC", O[2], " (", mu, "atm)"))) + 
-  mytheme(size_labs = 10) +
-    theme(aspect.ratio=1, plot.title = element_text(size=7))
-ggsave(file="figures/pco2.png", p,  width = 14, height = 14, units = "cm")
-```
-
 ## Maintenance

### 2020-08-19 awipev-CO2.Rmd
added chunk Zeppelin CO2 data

@@
 ```
+```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
+## Atmospheric CO2 Zeppelin
+# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
+# value:units : ppm
+# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
+atm_co2 <-
+  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
+  delim = " ",
+  skip = 181,
+  col_names = TRUE,
+  na = "-999.999",
+  ) %>%
+  dplyr::mutate(co2 = value,
+  datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))
+  ) %>%
+  dplyr::select(datetime, co2)
+p_atm_co2 <- ggplot(data=atm_co2) +
+  geom_point(aes(x = datetime, y = co2), col = "blue", size = 0.15, na.rm = TRUE) +
+  labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +
+  Mytheme(size_labs = 8)
+ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")
+```
 

### 2020-08-19 figs_essd.R
now read and display atm CO2

@@ -85,7 +85,24 @@ d <-
     path = path,
     file = "fb_data/pangaea.rds"
   ))
+# Read Zeppelin atmospheric CO2 data ####
+# Atmospheric CO2 Zeppelin
+# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
+# value:units : ppm
+# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
+atm_co2 <-
+  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
+             delim = " ",
+             skip = 181,
+             col_names = TRUE,
+             na = "-999.999",
+  ) %>%
+  dplyr::mutate(co2 = value,
+                datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))
+  ) %>%
+  dplyr::select(datetime, co2)
 
+d <- dplyr::left_join(d, atm_co2, by = "datetime")
 
 # time series ####
 xlim <- c(as.POSIXct("2015-07-01 00:00:00"), as.POSIXct("2020-07-01 00:00:00"))
@@ -122,9 +139,10 @@ ts_sal <- d %>%
   mytheme(size_labs = 8)
 # time series pco2
 ts_pco2 <- d %>%
-  dplyr::filter(!is.na(pco2)) %>% 
+  #dplyr::filter(!is.na(pco2)) %>% 
   ggplot() +
   geom_point(aes(x = datetime, y = pco2), col = "blue", size = 0.15, na.rm = TRUE) +
+  geom_point(aes(x = datetime, y = co2), col = "red", size = 0.15, na.rm = TRUE) +
   scale_x_datetime(limits = xlim) +
   labs(title = "", x = "", y = expression(paste("pC", O[2], " (", mu, "atm)"))) +
   mytheme(size_labs = 8)

### 2020-08-19 figs_essd.R
now read and display atm CO2

@@ -138,7 +138,7 @@ ts_sal <- d %>%
   labs(title = "", x = "", y = "Salinity") +
   mytheme(size_labs = 8)
 # time series pco2
-ts_pco2 <- d %>%
+ts_co2 <- d %>%
   #dplyr::filter(!is.na(pco2)) %>% 
   ggplot() +
   geom_point(aes(x = datetime, y = pco2), col = "blue", size = 0.15, na.rm = TRUE) +
@@ -198,7 +198,7 @@ ts_oa <- d %>%
   mytheme(size_labs = 8) +
   theme(axis.title.x = element_text(face="plain", size=8))
 #assemble time-series figure
-cp <- cowplot::plot_grid(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ts_oa,
+cp <- cowplot::plot_grid(ts_sal, ts_temp, ts_co2, ts_ph, ts_at, ts_oa,
                          align = "v",
                          ncol = 1
                          #width = 18,

### 2020-08-19 figs_essd.R
tweaking time series figure

@@ -75,7 +75,7 @@ mytheme <- function(size_labs = 6, face_font="plain", ...) {
           panel.grid.major = element_line(size = 0.25, color="grey50", linetype="dashed"),
           panel.grid.minor = element_line(size = rel(0.5), color = "grey50", linetype="dotted"),
           aspect.ratio = 1 / 3,
-          plot.margin = margin(t = 0, r = 1, b = 0, l = 1, unit = "lines")
+          plot.margin = margin(t = -2, r = 1, b = -2, l = 1, unit = "cm")
     )
 }
 
@@ -85,6 +85,7 @@ d <-
     path = path,
     file = "fb_data/pangaea.rds"
   ))
+
 # Read Zeppelin atmospheric CO2 data ####
 # Atmospheric CO2 Zeppelin
 # downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
@@ -200,16 +201,12 @@ ts_oa <- d %>%
 #assemble time-series figure
 cp <- cowplot::plot_grid(ts_sal, ts_temp, ts_co2, ts_ph, ts_at, ts_oa,
                          align = "v",
-                         ncol = 1
+                         ncol = 1#,
+                         #labels = "auto"
                          #width = 18,
                          #units = "cm"
                          )
-cowplot::ggsave2(filename = "figures/essd/ts_gg.png", plot = cp, height = 20, units = "cm")
-grid.arrange(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ts_oa, ncol = 1)
-# ts_sal / ts_temp / ts_at
-# grid.arrange(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, ncol = 1)
-# cowplot::save_plot(filename = "figures/ts_sp.pdf", plot = cp)
-# multiplot(ts_sal, ts_temp, ts_pco2, ts_ph, ts_at, cols = 1)
+cowplot::ggsave2(filename = "figures/essd/ts_gg.png", plot = cp, width = 10, height = 25, unit = "cm")
 
 # Boxplots ####
 mytheme_bp <- function(size_labs = 9, face_font="plain", ...) {

### 2020-08-19 figs_essd.R
tweaking time series figure

@@ -75,7 +75,7 @@ mytheme <- function(size_labs = 6, face_font="plain", ...) {
           panel.grid.major = element_line(size = 0.25, color="grey50", linetype="dashed"),
           panel.grid.minor = element_line(size = rel(0.5), color = "grey50", linetype="dotted"),
           aspect.ratio = 1 / 3,
-          plot.margin = margin(t = -2, r = 1, b = -2, l = 1, unit = "cm")
+          plot.margin = margin(t = -5, r = 1, b = -5, l = 1, unit = "cm")
     )
 }
 

### 2020-08-20 figs_essd.R
tweaking time series figure

@@ -64,18 +64,20 @@ lm2 <- function(x, y) {
 
 mytheme <- function(size_labs = 6, face_font="plain", ...) {
   theme_bw() +
-    theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
+    theme(axis.text.x = element_blank(),
+          #axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
           axis.title.x = element_text(face=face_font, size=size_labs, margin = margin(0,0,0,0,"pt")),
           axis.text.y = element_text(face=face_font, color="black", size=size_labs),
           axis.title.y = element_text(face=face_font, size=size_labs),
-          axis.ticks.x = element_line(size=0.1),
+          axis.ticks.x = element_blank(),
           axis.ticks.y = element_line(size=0.1),
           title = element_text(face=face_font, size=size_labs),
           axis.ticks.length = unit(1.1, "mm"),
-          panel.grid.major = element_line(size = 0.25, color="grey50", linetype="dashed"),
-          panel.grid.minor = element_line(size = rel(0.5), color = "grey50", linetype="dotted"),
+          panel.grid.major = element_line(size = 0.05, color="grey50", linetype="dashed"),
+          panel.grid.minor = element_blank(),
+          #panel.grid.minor = element_line(size = rel(0.5), color = "grey50", linetype="dotted"),
           aspect.ratio = 1 / 3,
-          plot.margin = margin(t = -5, r = 1, b = -5, l = 1, unit = "cm")
+          plot.margin = margin(t = -0.3, r = -0.3, b = 0, l = -0.3, unit = "cm")
     )
 }
 
@@ -128,85 +130,83 @@ d <- left_join(d, oa_tbf, by = 'datetime')
 ts_temp <- d %>%
   dplyr::filter(!is.na(t_11m)) %>% 
   ggplot() +
-  geom_point(aes(x = datetime, y = t_11m), col = "blue", size = 0.15, na.rm = TRUE) +
+  geom_point(aes(x = datetime, y = t_11m), col = "blue", size = 0.05, na.rm = TRUE) +
   labs(title = "", x = "", y = "Temp. 11 m (°C)") +
-  mytheme(size_labs = 8)
+  mytheme()
 # time series sal
 ts_sal <- d %>%
[…]

### 2020-08-20 figs_essd.R
removed apparently unneeded libraries

@@ -6,8 +6,6 @@ Sys.setenv(TZ='UTC') # on utilise UTC
 rm(list = ls())
 if (!require("tidyverse")) install.packages("tidyverse")
 library(tidyverse)
-# if (!require("robfilter")) install.packages("robfilter")
-# library("robfilter")
 if (!require("seacarb")) install.packages("seacarb")
 library("seacarb")
 if (!require("gridExtra")) install.packages("gridExtra")
@@ -22,18 +20,10 @@ if (!require("grid")) install.packages("grid")
 library(grid)
 if (!require("viridis")) install.packages("viridis")
 library("viridis")
-# if (!require("dygraphs")) install.packages("dygraphs")
-# library("dygraphs")
-# if (!require("knitr")) install.packages("knitr")
-# require("knitr")
 if (!require("lmodel2")) install.packages("lmodel2")
 library("lmodel2")
-# if (!require("captioner")) install.packages("captioner")
-# library("captioner")
 if (!require("xts")) install.packages("xts")
 library("xts")
-# if (!require("seismicRoll")) install.packages("seismicRoll")
-# library("seismicRoll")
 if (!require("scales")) install.packages("scales")
 library("scales")
 if (!require("cowplot")) install.packages("cowplot")

### 2020-08-20 figs_essd.R
property plot pCO2 completed

@@ -266,19 +266,20 @@ lm2 <- lm2(x = da$pco2_calc, y = da$pco2)
 p <-  ggplot(d, aes(x=pco2_calc, y= pco2), na.rm = TRUE) +
   geom_point(color = "blue") +
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]), colour = "blue") +
+  geom_abline(aes(intercept = lm2$fit$regression.results[2,2], slope = lm2$fit$regression.results[2,3]), colour = "blue") +
   labs(x = expression(paste("Calculated pC", O[2], " (", mu, "atm)")), 
        y = expression(paste("In situ pC", O[2], " (", mu, "atm)")),
-       title = paste("Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3),
-                     "; RMSE = ", signif(rmse, 3))) +
+       title = paste("Adj R2 = ", signif(lm2$fit$rsquare, 3),
+                     "; Intercept =", signif(lm2$fit$regression.results[2,2], 3),
+                     "; Slope =", signif(lm2$fit$regression.results[2,3], 3),
+                     "; P =", signif(lm2$fit$P.param, 3),
+                     "; RMSE = ", signif(lm2$rmse, 3))) +
   coord_fixed(ratio = 1 ,xlim=c(200, 400) , ylim=c(200, 400))+
 #  labs(x = expression(paste("Calculated pC", O[2], " (", mu, "atm)")), 
 #       y = expression(paste("In situ pC", O[2], " (", mu, "atm)"))) + 
-  mytheme(size_labs = 10) +
-  theme(aspect.ratio=1, plot.title = element_text(size=7))
+  mytheme(size_labs = 10, plot.title = element_text(face=face_font, size=size_labs, color="black")) +
+  theme(aspect.ratio = 1,
+        plot.margin = margin(t = 0.5, unit = "cm"))
 p
 ggsave(file="figures/essd/pco2.png", p,  width = 14, height = 14, units = "cm")
 

### 2020-08-20 awipev-CO2.Rmd
adding RMSE on property plots

@@
 
-#################### Function RMSE root mean square error
-rmse <- function(error) { sqrt(mean(error^2)) }
-#rmse(fit$residuals)
+#################### Function RMSE for model 2 regression root mean square error
+lm2 <- function(x, y) { 
+  fit <- lmodel2(y  ~ x , nperm = 99)
+  intercept <- fit$regression.results[2,2]
+  slope <- fit$regression.results[2,3]
+  predicted <- intercept + x * slope
+  error <- predicted - x
+  my_list <- list(fit = fit, rmse = sqrt(mean(error^2, na.rm=TRUE)))
+  return(my_list)
+  }
 
@@
 
-fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu_ctd_9m , nperm = 99)
+lm2 <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
 
 ```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-fit <- lmodel2(data = d_all,  sal_fb ~ sal_insitu_ctd_9m , nperm = 99)
 p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
@@
   geom_abline(slope=1, intercept=0, linetype = "dashed")+
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
+  geom_abline(aes(intercept = lm2$fit$regression.results[2,2], slope = lm2$fit$regression.results[2,3]),colour = "blue") +
   ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
-  labs(title = paste("","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + #
+  labs(title = paste("","\n Adj R2 = ", signif(lm2$fit$rsquare, 3),
+                     "; Intercept =", signif(lm2$fit$regression.results[2,2], 3),
+                     "; Slope =", signif(lm2$fit$regression.results[2,3], 3),
+                     "; P =", signif(lm2$fit$P.param, 3),
+                     "; RMSE = ", signif(lm2$rmse, 3))) +
+  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
   coord_fixed(ratio = 1 )+
-  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") +theme_bw()
+  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()
 
@@
 ## pHs 
-Comparaison is done here with **corrected pHs** (**seaFET**, **durafet** and **calculated** (from AT/CT)) and normalized at 4°C with a total alkalinity of 2273 µmoles kg-1 (mean data).
+Comparaison is done here with **corrected pHs** (**seaFET**, **durafet** and **calculated** (from AT/CT)) and normalized at 4°C with a total alkalinity of `r mean(d_all$at, na.rm=TRUE)` µmoles kg-1 (mean data).
 For information, mean temperatures in Ferrybox and *in situ* are repectively 3.5°C and 2.5°C.
@@
 
-pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=2.273e-3, Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
@@
   dplyr::filter(!is.na(ph_dur_corr), !is.na(temp_fb), !is.na(sal_fb))
-pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=2.273e-3, Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
 
 # join pH sf norm + pH dur norm
-d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime,pHint_tot_sf_norm4 ), by="datetime")
-d_all <- left_join(d_all, pH_dur%>%dplyr::select(datetime,pH_durafet_norm4 ), by="datetime")
+d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime, pHint_tot_sf_norm4 ), by="datetime")
+d_all <- left_join(d_all, pH_dur%>%dplyr::select(datetime, pH_durafet_norm4 ), by="datetime")
 

### 2020-08-20 awipev-CO2.Rmd
adding RMSE on property plots

@@
 
-Property-property temperature plot using:
-
-fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)
-
 ```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
@@
   )
-fit <- lmodel2(data = d_all,  temp_fb ~ temp_insitu_11m , nperm = 99)
+lm2 <- lm2(x = d_all$temp_insitu_11m, y = d_all$temp_fb)
 
@@
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
-  labs( x="T 11 m", y="T FB ", color = "Months")  +theme_bw()
+  geom_abline(aes(intercept = lm2$fit$regression.results[2,2], slope = lm2$fit$regression.results[2,3]),
+              colour = "blue") +
+  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm2$fit$rsquare, 3),
+                     "; Intercept =", signif(lm2$fit$regression.results[2,2], 3),
+                     "; Slope =", signif(lm2$fit$regression.results[2,3], 3),
+                     "; P =", signif(lm2$fit$P.param, 3),
+                     "; RMSE = ", signif(lm2$rmse, 3))) +
+  theme_bw() +
+  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + 
+  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
+  labs(x="T 11 m", y="T FB ", color = "Months") 
 print(p) # p_temp_11_fb
@@
 ### **T 11 m / T CTD > 8 m **
-
-Property-property temperature plot using:
-
-fit <- lmodel2(data = d_all,  temp_insitu_11m ~ temp_insitu_ctd_9m , nperm = 99)
 

### 2020-08-20 awipev-CO2.Rmd
adding RMSE on property plots

@@
 
-Property-property salinity plot using:
-
-lm2 <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
-
 ```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
 p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
@@
   geom_abline(slope=1, intercept=0, linetype = "dashed")+
-  geom_abline(aes(intercept = lm2$fit$regression.results[2,2], slope = lm2$fit$regression.results[2,3]),colour = "blue") +
+  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),colour = "blue") +
   ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
-  labs(title = paste("","\n Adj R2 = ", signif(lm2$fit$rsquare, 3),
-                     "; Intercept =", signif(lm2$fit$regression.results[2,2], 3),
-                     "; Slope =", signif(lm2$fit$regression.results[2,3], 3),
-                     "; P =", signif(lm2$fit$P.param, 3),
-                     "; RMSE = ", signif(lm2$rmse, 3))) +
+  labs(title = paste("","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
+                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
+                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
+                     "; P =", signif(lm$fit$P.param, 3),
+                     "; RMSE = ", signif(lm$rmse, 3))) +
   theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
@@
   )
-lm2 <- lm2(x = d_all$temp_insitu_11m, y = d_all$temp_fb)
+lm <- lm2(x = d_all$temp_insitu_11m, y = d_all$temp_fb)
 
@@
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = lm2$fit$regression.results[2,2], slope = lm2$fit$regression.results[2,3]),
+  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
               colour = "blue") +
-  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm2$fit$rsquare, 3),
-                     "; Intercept =", signif(lm2$fit$regression.results[2,2], 3),
-                     "; Slope =", signif(lm2$fit$regression.results[2,3], 3),
-                     "; P =", signif(lm2$fit$P.param, 3),
-                     "; RMSE = ", signif(lm2$rmse, 3))) +
+  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
+                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
+                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
+                     "; P =", signif(lm$fit$P.param, 3),
+                     "; RMSE = ", signif(lm$rmse, 3))) +
   theme_bw() +
@@
 ```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-
-fit <- lmodel2(data = d_all,  temp_insitu_11m ~ temp_insitu_ctd_9m , nperm = 99)
-
-p<-  ggplot(d_all,aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = month))+
+lm <- lm2(x = d_all$temp_insitu_ctd_9m, y = d_all$temp_insitu_11m)
+p <-  ggplot(d_all, aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = month))+
   geom_text( aes(color=factor(month))) + 
@@
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 )+ scale_colour_discrete(guide="none") +
-  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")  +theme_bw()
+  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
+              colour = "blue") +
+  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
+                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
+                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
+                     "; P =", signif(lm$fit$P.param, 3),
+                     "; RMSE = ", signif(lm$rmse, 3))) +
+  theme_bw() +
+  theme(aspect.ratio = 1,plot.title = element_text(size = 7)) + 
+  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
+  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")
 print(p)

### 2020-08-20 awipev-CO2.Rmd
adding RMSE on property plots

@@
                        ";\nSlope =",signif(fit$coef[[2]], 5),
-                       ";\nP =",signif(summary(fit)$coef[2,4], 5))) +
+                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
+                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
   theme_bw() +
   theme(aspect.ratio=1,
-        axis.text=element_text(size=15),
-        axis.title.y= element_text(size =15),
-        axis.title.x= element_text(size =15),
+        axis.text=element_text(size=7),
+        axis.title.y= element_text(size =7),
+        axis.title.x= element_text(size =7),
         plot.margin = unit(c(0.5,1,1,1), "cm"),
-        plot.title = element_text(size=15, hjust=0.05,margin = margin(l = 10, b = -70)))
+        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
 
@@
 Because of issue, measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17.
-*Note that pH sensor is mounted on a profiling structure.
+*Note that the pH sensor is mounted on a profiling structure.
 Here, only seaFET data recorded with a depth > 8 m are taken in consideration.* pH calibration is based on monthly discrete samples that are analysed with spectrophotometric method in Villefranche by Samir Alliouane.

### 2020-08-20 awipev-CO2.Rmd
adding RMSE on property plots

@@
 # Spectro / durafet
-fit <- lmodel2(data = d_all,  ph_s_dur_temp_fb ~ ph_dur_corr , nperm = 99)
-
-p_dura_spectro <-  ggplot(d_all,aes(x=ph_dur_corr, y= ph_s_dur_temp_fb, label = month))+
+lm <- lm2(x = d_all$ph_s_dur_temp_fb, y = d_all$ph_dur_corr)
+
+p <-  ggplot(d_all, aes(x=ph_s_dur_temp_fb, y= ph_dur_corr, label = month)) +
   geom_text( aes(color=factor(month))) + 
@@
   geom_abline(slope=1, intercept =0, linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste("pH spectro vs pH durafet","\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
+              colour = "blue") +
+  labs(title = paste("pH spectro vs pH durafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
+                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
+                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
+                     "; P =", signif(lm$fit$P.param, 3),
+                     "; RMSE = ", signif(lm$rmse, 3))) +
+  theme_bw() +
+  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
   coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
-  labs(x="pH durafet", y="pH spectro, 4°C ", color = "Months") + theme_bw() 
-p_dura_spectro
-```
-
-<!-- ### **Spectro / seaFET** -->
+  labs(x="pH durafet", y="pH spectro", color = "Months")
+p
+```
 
@@
 # Spectro / seafet
-# fit <- lmodel2(data = d_all,  ph_s_sf_temp_insi ~ pHint_tot_sf , nperm = 99)
-#
-# p_sf_spectro <-  ggplot(d_all,aes(x=pHint_tot_sf, y= ph_s_sf_temp_insi, label = month))+
-#   geom_text( aes(color=factor(month))) +
-#   scale_color_discrete(guide = "none")+
-#  geom_abline(slope=1, intercept =0, linetype = "dashed") +
-#   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-#   labs(title = paste("pH spectro vs pH seaFET","\n Adj R2 = ", signif(fit$rsquare, 3),
-#                      "; Intercept =", signif(fit$regression.results[2,2], 3),
-#                      "; Slope =", signif( fit$regression.results[2,3], 3),
-#                      "; P =", signif(fit$P.param, 3))) +
-#   theme(aspect.ratio=1,plot.title = element_text(size=7)) +
-#     coord_fixed(ratio = 1 , xlim=c(8,8.2), ylim=c(8,8.2))+
-#   labs(x="pH seaFET", y="pH spectro, 4°C ", color = "Months") + theme_bw()
-# p_sf_spectro
+lm <- lm2(x = d_all$ph_s_sf_temp_insi, y = d_all$pHint_tot_sf)
+
+p <-  ggplot(d_all, aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = month)) +
+  geom_text( aes(color=factor(month))) + 
+  scale_color_discrete(guide = "none")+
+  geom_abline(slope=1, intercept =0, linetype = "dashed") +
+  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
+              colour = "blue") +
+  labs(title = paste("pH spectro vs pH seafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
+                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
+                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
+                     "; P =", signif(lm$fit$P.param, 3),
+                     "; RMSE = ", signif(lm$rmse, 1))) +
+  theme_bw() +
+  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
+  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
+  labs(x="pH spectro", y="pH seafet", color = "Months")
+p
 ```

### 2020-08-21 awipev-CO2.Rmd
air-sea CO2 in progress

@@
 
+```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
+## Atmospheric CO2 Zeppelin
+# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
+# value:units : ppm
+# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
+atm_co2 <-
+  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
+  delim = " ",
+  skip = 181,
+  col_names = TRUE,
+  na = "-999.999",
+  ) %>%
+  dplyr::mutate(co2_air = value,
+  datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))) %>%
+  dplyr::select(datetime, co2_air)
+d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
+p_atm_co2 <- ggplot(data=atm_co2) +
+  geom_point(aes(x = datetime, y = co2_air), col = "blue", size = 0.15, na.rm = TRUE) +
+  labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +
+  Mytheme(size_labs = 8)
+ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")
+```
+
+```{r meteo data, echo=FALSE, message= FALSE, warning=FALSE}
+#[1] "Year"               "Month"              "Day"                "Hour"              
+#[5] "Temperature[degC]"  "Pressure[hPa]"      "WindSpeed[m/s]"     "WindDirection[deg]"
+
+load(file = paste0(path, "meteo_awi/wind_nyalesund.RData")) 
+meteo <- tibble(windnyalesund) %>%
+  dplyr::mutate(datetime = as_datetime(paste(paste(Year, Month, Day, sep="-"), paste(Hour, "00", "00", sep="-"), sep = " ")),
+         temp_air = `Temperature[degC]`,
+         p_air = `Pressure[hPa]`,
+         ws = `WindSpeed[m/s]`,
+         wd = `WindDirection[deg]`
+        ) %>%
+  dplyr::select(datetime, temp_air, p_air, ws, wd)
+d_all <- dplyr::left_join(d_all, meteo, by = "datetime")
+```
+```{r air-sea CO2, echo=FALSE, message= FALSE, warning=FALSE}
+# calculations as described by de Carlo et al. (2013)
+# we consider that mole fraction in air = ppm TO CHECK
+d_all <- d_all %>%
+  dplyr::mutate(delta_pco2 = co2_air - pco2, # ppm
+                k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
+                Sc = 2073.1 - (125.62*temp_insitu_ctd) + (3.6276*temp_insitu_ctd^2) - (0.043219*temp_insitu_ctd^3), #dimensionless
+                k = k600 * (Sc/600)^-0.5,
+                alp = seacarb::K0(S=sal_mix,T=temp_insitu_ctd,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
+                f_air-sea = k * alp * delta_pco2)
+```
+
 ```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
@@
 d_all$ct <- ifelse(is.nan(d_all$at), NA, d_all$ct) # replace all NaN by NA
-dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))
+d_all <- dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))
 saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
@@
                 pH_sf = pHint_tot_sf,
-                ph_dur = ph_dur_corr
+                ph_dur = ph_dur_corr,
+                ph_calc = phcalc_fb
                 )
@@
 # ph_dur = pH Durafet at FerryBox temperature (FerryBox)
-```
-```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
-## Atmospheric CO2 Zeppelin
-# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
-# value:units : ppm
-# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
-atm_co2 <-
-  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
-  delim = " ",
-  skip = 181,
-  col_names = TRUE,
-  na = "-999.999",
-  ) %>%
-  dplyr::mutate(co2 = value,
-  datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))
-  ) %>%
-  dplyr::select(datetime, co2)
-p_atm_co2 <- ggplot(data=atm_co2) +
-  geom_point(aes(x = datetime, y = co2), col = "blue", size = 0.15, na.rm = TRUE) +
-  labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +
-  Mytheme(size_labs = 8)
-ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")
-```
-
+# ph_calc = pH at fb temp calculated from CT and AT samples collected at the FerryBox
+```
 ## Maintenance

### 2020-08-21 figs_essd.R
dunnoé

@@ -32,6 +32,8 @@ if (!require("htmlwidgets")) install.packages("htmlwidgets")
 library("htmlwidgets")
 if (!require("hms")) install.packages("hms")
 library("hms")
+if (!require("ragg")) install.packages("ragg")
+library("ragg")
 
 #################### define who is the user and define path
 if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
@@ -261,7 +263,7 @@ ggsave(file="figures/essd/boxplots.png", g,  width = 18, height = 14, units = "c
 
 # pCO2 ####
 da <- dplyr::filter(d, !is.na(pco2_calc), !is.na(pco2))
-lm2 <- lm2(x = da$pco2_calc, y = da$pco2)
+lm2 <- lm2(x = da$pco2, y = da$pco2_calc)
 #fit <- lmodel2(data = d,  pco2 ~ pco2_calc , nperm = 99)
 p <-  ggplot(d, aes(x=pco2_calc, y= pco2), na.rm = TRUE) +
   geom_point(color = "blue") +
@@ -275,8 +277,6 @@ p <-  ggplot(d, aes(x=pco2_calc, y= pco2), na.rm = TRUE) +
                      "; P =", signif(lm2$fit$P.param, 3),
                      "; RMSE = ", signif(lm2$rmse, 3))) +
   coord_fixed(ratio = 1 ,xlim=c(200, 400) , ylim=c(200, 400))+
-#  labs(x = expression(paste("Calculated pC", O[2], " (", mu, "atm)")), 
-#       y = expression(paste("In situ pC", O[2], " (", mu, "atm)"))) + 
   mytheme(size_labs = 10, plot.title = element_text(face=face_font, size=size_labs, color="black")) +
   theme(aspect.ratio = 1,
         plot.margin = margin(t = 0.5, unit = "cm"))
@@ -284,53 +284,25 @@ p
 ggsave(file="figures/essd/pco2.png", p,  width = 14, height = 14, units = "cm")
 
 
-# pH: durafet vs spectro ####
-da <- dplyr::filter(d, !is.na(ph_dur), !is.na(ph_s_dur_t_fb))
-rmse <- rmse2(x = da$ph_s_dur_t_fb, y = da$ph_dur)
-p <-  ggplot(da, aes(x = ph_s_dur_t_fb, y = ph_dur)) +
[…]

### 2020-08-24 awipev-CO2.Rmd
1st code air-sea CO2

@@
 
+## Air-sea CO2 flux
+
 ```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
@@
   ) %>%
-  dplyr::mutate(co2_air = value,
+  dplyr::mutate(pco2_air = value,
   datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))) %>%
-  dplyr::select(datetime, co2_air)
+  dplyr::select(datetime, pco2_air)
 d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
 p_atm_co2 <- ggplot(data=atm_co2) +
-  geom_point(aes(x = datetime, y = co2_air), col = "blue", size = 0.15, na.rm = TRUE) +
+  geom_point(aes(x = datetime, y = pco2_air), col = "blue", size = 0.15, na.rm = TRUE) +
   labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +
@@
 ```
+
 ```{r air-sea CO2, echo=FALSE, message= FALSE, warning=FALSE}
@@
 d_all <- d_all %>%
-  dplyr::mutate(delta_pco2 = co2_air - pco2, # ppm
+  dplyr::mutate(delta_pco2 = pco2_air - pco2_corr, # ppm
                 k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
-                Sc = 2073.1 - (125.62*temp_insitu_ctd) + (3.6276*temp_insitu_ctd^2) - (0.043219*temp_insitu_ctd^3), #dimensionless
-                k = k600 * (Sc/600)^-0.5,
-                alp = seacarb::K0(S=sal_mix,T=temp_insitu_ctd,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
-                f_air-sea = k * alp * delta_pco2)
-```
+                Sc = 2073.1 - (125.62*temp_insitu_11m) + (3.6276*temp_insitu_11m^2) - (0.043219*temp_insitu_ctd^3), #dimensionless
+                k = k600 * (Sc/600)^-0.5, #cm/h
+                alp = seacarb::K0(S=sal_mix,T=temp_insitu_11m,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
+                alp = alp * (seacarb::rho(S = sal_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
+                f_air_sea = k * alp * delta_pco2)
+```
+
+## Save files
 

### 2020-08-24 awipev-CO2.Rmd
refining air-sea CO2

@@
 # we consider that mole fraction in air = ppm TO CHECK
+# By convention, a negative flux indicates fluxes directed from the atmosphere to the ocean, and a positive flux indicates fluxes directed from the ocean to the atmosphere.
 d_all <- d_all %>%
-  dplyr::mutate(delta_pco2 = pco2_air - pco2_corr, # ppm
+  dplyr::mutate(delta_pco2 = pco2_corr - pco2_air, # ppm
                 k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
@@
                 alp = alp * (seacarb::rho(S = sal_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
-                f_air_sea = k * alp * delta_pco2)
+                f_air_sea = k * alp * delta_pco2 # mmol/(m2 h)
+                )
+
+p_f_air_sea <- ggplot(data=d_all) +
+  geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
+  labs(title = "Air-sea CO2 flux", x = "Time", y = "CO2 (mmol/(m2 h))") +
+  Mytheme(size_labs = 8)
+p_f_air_sea
+ggsave(filename = "figures/f_air_sea.png", plot = f_air_sea, width = 20, units = "cm")
+
+air_sea_day <- d_all %>%
+  dplyr::select(datetime, f_air_sea) %>%
+  dplyr::group_by(lubridate::yday(datetime)) %>%
+  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm=TRUE)/1000) %>% #mol/(m2 d)
+  ungroup() %>%
+  dplyr::rename(day = 1)
+
+p_f_air_sea_d <- ggplot(data = air_sea_day) +
+  geom_point(aes(x = day, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
+  labs(title = "Air-sea CO2 flux", x = "Time", y = "CO2 (mmol/(m2 d))") +
+  Mytheme(size_labs = 8)
+p_f_air_sea_d
+ggsave(filename = "figures/f_air_sea_d.png", plot = p_f_air_sea_d, width = 20, units = "cm")
+
+air_sea_month <- d_all %>%
+  dplyr::select(month, f_air_sea) %>%
+  dplyr::group_by(month) %>%
+  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm=TRUE)/1000) %>% #mol/(m2 d)
+  ungroup() %>%
+  dplyr::mutate(f_air_sea = days_in_month(month) * f_air_sea)
+#air_sea_month
+p_f_air_sea_m <- ggplot(data = air_sea_month) +
+  geom_point(aes(x = month, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
+  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
+  labs(title = "Air-sea CO2 flux", x = "Time", y = "CO2 (mmol/(m2 month))") +
+  Mytheme(size_labs = 8)
+p_f_air_sea_m
+ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_m, width = 20, units = "cm")
+
 ```

### 2020-08-25 awipev-CO2.Rmd
final air-sea CO2

@@
 library("hms")
+if (!require("ragg")) install.packages("hms")
+library("ragg")
 knitr::opts_chunk$set(echo = TRUE)
@@
 
+To calculate the air-sea CO2 flux, we use:
++ seawater pCO2
++ atmospheric CO2 measured at the Zeppelin station and downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999 
++ wind spreed data collected by the AWI at 10 m height (sent to JPG by P. Fischer, Aug. 2020)
+
+Since there are many gaps, a climatological year is used: air-sea flux calculated by day, then by month, then by year.
+
 ```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
@@
   geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
-  labs(title = "Air-sea CO2 flux", x = "Time", y = "CO2 (mmol/(m2 h))") +
+  labs(title = "Air-sea CO2 flux (all data)", x = "Time", y = "CO2 (mmol/(m2 h))") +
   Mytheme(size_labs = 8)
-p_f_air_sea
-ggsave(filename = "figures/f_air_sea.png", plot = f_air_sea, width = 20, units = "cm")
+#p_f_air_sea
+#ggsave(filename = "figures/f_air_sea.png", plot = f_air_sea, width = 20, units = "cm")
 
@@
   geom_point(aes(x = day, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
-  labs(title = "Air-sea CO2 flux", x = "Time", y = "CO2 (mmol/(m2 d))") +
+  labs(title = "Air-sea CO2 flux (per day)", x = "Time", y = "CO2 (mmol/(m2 d))") +
   Mytheme(size_labs = 8)
-p_f_air_sea_d
-ggsave(filename = "figures/f_air_sea_d.png", plot = p_f_air_sea_d, width = 20, units = "cm")
+#p_f_air_sea_d
+#ggsave(filename = "figures/f_air_sea_d.png", plot = p_f_air_sea_d, width = 20, units = "cm")
 
@@
 p_f_air_sea_m <- ggplot(data = air_sea_month) +
-  geom_point(aes(x = month, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
+  geom_point(aes(x = month(month, label = TRUE, abbr = TRUE), y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
   scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
-  labs(title = "Air-sea CO2 flux", x = "Time", y = "CO2 (mmol/(m2 month))") +
+  lims(y = c(-30, 0)) +
+  labs(title = "Air-sea CO2 flux (per month)", x = "Julian day", y = "CO2 (mmol/(m2 month))") +
   Mytheme(size_labs = 8)
-p_f_air_sea_m
-ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_m, width = 20, units = "cm")
-
-```
+#p_f_air_sea_m
+#ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_m, width = 20, units = "cm")
+
+p <- cowplot::plot_grid(p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m, ncol = 1)
+pngfile <- "figures/air-sea_CO2_flux.png"
+ggsave(
+  pngfile, 
+  p, 
+  device = agg_png, 
+  width = 6.6, height = 10, units = "cm", res = 300,
+  scaling = 0.4
+)
+knitr::include_graphics(pngfile)
+```
+
+The annual air-sea CO2 flux is `r round(sum(air_sea_month), digits = 0)` mol/(m2 year).
 
@@
 pangaea <- as_tibble(d_all) %>% 
-  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, pco2_corr, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
+  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, phcalc_fb, pco2_corr, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
   dplyr::rename(pressure = pressure_insitu_ctd,

### 2020-08-25 awipev-CO2.Rmd
minor edits
table+ fig vertical sal gradient

@@
 
-- 1 SBE45 inside the Ferrybox (sal_fb)
-- 5 CTD > 8 m depth (sal_insitu_ctd)
++ 1 SBE45 inside the Ferrybox (sal_fb)
++ 5 CTD > 8 m depth (sal_insitu_ctd)
 
@@
   ungroup()
+
+p_sal_range <- ggplot(data = df) +
+  geom_histogram((aes(x = df$range))) +
+  labs(title = "Salinity difference between 1 and 9 m", x = "Difference") +
+  Mytheme(size_labs = 8)
+p_sal_range
+
+quantile(df$range, na.rm = TRUE)
 ```
@@
 
-## Save files
-
 ```{r save all, echo=FALSE, message= FALSE, warning=FALSE}

### 2020-08-27 awipev-CO2.Rmd
filtering pH > 8m in progress

@@
   dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) %>% # eliminate ph spec data when the profiler was at several depth during the same hour
-  dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) | !is.na(temp_insitu_ctd_9m), 
+  dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) |
+                                             !is.na(temp_insitu_ctd_9m), 
                                            ph_s_sf_temp_insi, NA)) # only use ph spec data when profiler was below 6 m
@@
 
-quantile(df$range, na.rm = TRUE)
+kable(quantile(x = df$range, na.rm = TRUE), digits = 2, col.names = "Sal. unit", caption = "Quantiles salinity gradient between 0-2 m and > 8 m")
 ```
@@
 # add despike with n=2 k = 5762 to the final ph corrected data
+# despike me semble inutile, faire plutôt un simple des outliers qui, vérification faite, n'est même pas nécessaire
+# Il faut par contre créér une nouvelle variable avec pH deeper than 8 m, called *_9m for consistency with salinity and temp
 d_all <- d_all %>%     
-   dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA"))
+  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA"))
+  tt <- dplyr::mutate(tmp, pHint_tot_sf_9m = ifelse(pressure_insitu_ctd > 8, pHint_tot_sf, NA))
 
@@
 #ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
+```
+
+### **Depth profile**
+
+```{r seafet profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+
 ```

### 2020-08-28 awipev-CO2.Rmd
still on range of seafet pH

@@
   arrange(datetime)
-d_all <- d_hour #d_all will be the merger
+d_all <- as_tibble(d_hour) #d_all will be the merger
 d_all <- d_all %>%
@@
 d_all <- d_all %>% 
-  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) %>% # eliminate ph spec data when the profiler was at several depth during the same hour
-  dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) |
-                                             !is.na(temp_insitu_ctd_9m), 
-                                           ph_s_sf_temp_insi, NA)) # only use ph spec data when profiler was below 6 m
+  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) # eliminate ph spec data when the profiler was at several depth during the same hour
+  #dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) |
+  #                                           !is.na(temp_insitu_ctd_9m), 
+   #                                        ph_s_sf_temp_insi, NA)) # only use ph spec data when profiler was below 6 m
 
@@
 names(seafet_calib) <- c("pHint_tot_sf", "pHext_tot_sf")
-d_all <- cbind(d_all, seafet_calib )
+d_all <- dplyr::bind_cols(d_all, seafet_calib )
 
@@
 d_all <- d_all %>%
-  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA"))
-  tt <- dplyr::mutate(tmp, pHint_tot_sf_9m = ifelse(pressure_insitu_ctd > 8, pHint_tot_sf, NA))
+  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA")) %>%
+  dplyr::mutate(pHint_tot_sf = seafet_calib$pHint_tot_sf) %>%
+  dplyr::mutate(pHint_tot_sf_9m = ifelse(pressure_insitu_ctd > 8, pHint_tot_sf, NA),
+                pHint_tot_sf_6m = ifelse(pressure_insitu_ctd > 6, pHint_tot_sf, NA))
 
@@
 
-p <- ggplot(d_all, aes(x=datetime, y= pHint_tot_sf))+
+p <- ggplot(d_all, aes(x=datetime, y= pHint_tot_sf_9m))+
   geom_point(size=1, alpha=0.5, na.rm=TRUE)
-
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf, pH_s_sf_no_calb)
+p
+
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_6m, pHint_tot_sf_9m)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
-dygraph(seafet_depth_xts, group = "depth", main="pH seaFET (ref + corrected + raw)", ylab="pHT") %>%
-dySeries("pHint_tot_sf", label = "pHT corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 3) %>%
-dySeries("ph_s_sf_temp_insi", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-dySeries("pH_s_sf_no_calb", label = "pH spectro no calibration", color =  "black", pointShape = "triangle", strokeWidth = 0, pointSize = 6 ) %>%
+dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
+dySeries("ph_s_sf_temp_insi", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+dySeries("pHint_tot_sf_9m", label = "pHT 9m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_6m", label = "pHT 6m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
 dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
@@
   dplyr::mutate(year = year(datetime))
-range <- tbl_df(
-  d_all %>%
+range <- d_all %>%
   group_by(date=as.Date(datetime), 
@@
            year=year(datetime)) %>%
-  summarize(pH_range = max(pHint_tot_sf) - min(pHint_tot_sf))
-)
-quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
+  summarize(pH_range_9m = max(pHint_tot_sf_9m) - min(pHint_tot_sf_9m),
+            pH_range_6m = max(pHint_tot_sf_6m) - min(pHint_tot_sf_6m))
+
+quant <- quantile(range$pH_range_9m, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
+print(quant)
+quant <- quantile(range$pH_range_6m, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
+print(quant)
 
@@
   group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
-  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
+  summarize(pH_range_month6m = mean(pH_range_6m, na.rm=TRUE),
+            pH_range_month_9m = mean(pH_range_9m, na.rm=TRUE)) %>%
+  ungroup()
 
 size_point <- 0.4 #size of data points
-p <-  
-  ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+p <- range_month %>%
+  pivot_longer(-Month, names_to = "depth", values_to = "pH_range") %>%
+  ggplot() +
+  geom_violin(aes(x = as.factor(Month), y = pH_range), fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
   geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
 
-### **Depth profile**
+### **seaFET pH profiles**
 

### 2020-08-31 awipev-CO2.Rmd
Still on pH seafet

@@
   ggplot() +
-  geom_violin(aes(x = as.factor(Month), y = pH_range), fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  #geom_violin(aes(x = as.factor(Month), y = pH_range), group = depth, fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+  geom_boxplot(aes(x = as.factor(Month), y = pH_range), , group = depth, notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
   labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +

### 2020-08-31 awipev-CO2.Rmd
pH at various depths now works

--- 2020-08-28 awipev-CO2.Rmd
@@
 library("ragg")
+if (!require("skimr")) install.packages("skimr")
+library("skimr")
+
 knitr::opts_chunk$set(echo = TRUE)
@@
 }
+
+#################### MySkim
+# myskim <- skim_with(numeric = sfl(min = ~min(., na.rm = TRUE),
+#                                   max = ~max(., na.rm = TRUE)))
 ```
@@
   dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
+  dplyr::mutate( # create new variable depth
+    depth = ifelse(
+      pressure_insitu_ctd <= 2,
+      1,
+      ifelse(
+        pressure_insitu_ctd > 2 & pressure_insitu_ctd <= 4,
+        3,
+        ifelse(
+          pressure_insitu_ctd > 4 & pressure_insitu_ctd <= 6,
+          5,
+          ifelse(
+            pressure_insitu_ctd > 6 & pressure_insitu_ctd <= 8,
+            7,
+            ifelse(pressure_insitu_ctd > 8, 9, NA)
+          )
+        )
+      )
+    )) %>%
   dplyr::rowwise() %>% 
@@
   dplyr::mutate(pHint_tot_sf = seafet_calib$pHint_tot_sf) %>%
-  dplyr::mutate(pHint_tot_sf_9m = ifelse(pressure_insitu_ctd > 8, pHint_tot_sf, NA),
-                pHint_tot_sf_6m = ifelse(pressure_insitu_ctd > 6, pHint_tot_sf, NA))
+  dplyr::mutate(pHint_tot_sf_1m = ifelse(pressure_insitu_ctd > 0 & pressure_insitu_ctd < 2, pHint_tot_sf, NA),
+                pHint_tot_sf_3m = ifelse(pressure_insitu_ctd >= 2 & pressure_insitu_ctd < 4, pHint_tot_sf, NA),
+                pHint_tot_sf_5m = ifelse(pressure_insitu_ctd >= 4 & pressure_insitu_ctd < 6, pHint_tot_sf, NA),
+                pHint_tot_sf_7m = ifelse(pressure_insitu_ctd >= 6 & pressure_insitu_ctd < 8, pHint_tot_sf, NA),
+                pHint_tot_sf_9m = ifelse(pressure_insitu_ctd >= 8 , pHint_tot_sf, NA)
+  )
 
@@
 
-p <- ggplot(d_all, aes(x=datetime, y= pHint_tot_sf_9m))+
-  geom_point(size=1, alpha=0.5, na.rm=TRUE)
-p
-
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_6m, pHint_tot_sf_9m)
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_7m, pHint_tot_sf_9m)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
@@
 dySeries("pHint_tot_sf_9m", label = "pHT 9m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_6m", label = "pHT 6m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
 dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
@@
   dyRangeSelector(height = 30, dateWindow= NULL)
-
-#RANGE of pH
-d_all<- d_all%>%
-  dplyr::mutate(year = year(datetime))
+```
+
+### **seaFET pH profiles**
+
+```{r seafet profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+# pH by depth
+# d_all<- d_all%>%
+#   dplyr::mutate(year = year(datetime))
+
+#Per month
 range <- d_all %>%
-  group_by(date=as.Date(datetime), 
-           month=month(datetime, label=TRUE), 
-           year=year(datetime)) %>%
-  summarize(pH_range_9m = max(pHint_tot_sf_9m) - min(pHint_tot_sf_9m),
-            pH_range_6m = max(pHint_tot_sf_6m) - min(pHint_tot_sf_6m))
-
-quant <- quantile(range$pH_range_9m, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
-print(quant)
-quant <- quantile(range$pH_range_6m, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
-print(quant)
-
-#Per month
-range_month <-
-  range %>%
-  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
-  summarize(pH_range_month6m = mean(pH_range_6m, na.rm=TRUE),
-            pH_range_month_9m = mean(pH_range_9m, na.rm=TRUE)) %>%
+  dplyr::mutate(pH_range_more_6m = ifelse(pressure_insitu_ctd > 6, pHint_tot_sf, NA)) %>%
+  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
+  summarize(pH_range = max(pHint_tot_sf, na.rm = TRUE) - min(pHint_tot_sf, na.rm = TRUE),
+            pH_range_more_6m = max(pH_range_more_6m, na.rm = TRUE) - min(pH_range_more_6m, na.rm = TRUE),
+            pH_range_more_9m = max(pHint_tot_sf_9m, na.rm = TRUE) - min(pHint_tot_sf_9m, na.rm = TRUE)) %>%
   ungroup()
-
-size_point <- 0.4 #size of data points
-p <- range_month %>%
-  pivot_longer(-Month, names_to = "depth", values_to = "pH_range") %>%
-  ggplot() +
-  geom_violin(aes(x = as.factor(Month), y = pH_range), fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(y =expression(paste(pH[T], " range seaFET")), x=NULL, title=NULL) +
-  Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-print(p) # plot_range_sf
-#ggsave(paste0("figures/plot_range_sf.png"), width= 30, height=10, plot_range_sf, units="cm")
-```
-
-### **seaFET pH profiles**
-
-```{r seafet profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-
-```
+print(kable(range, digits = 2))
+```
+The range is significantly larger during some months when the data deeper than 9 m are considered. It seems therefore better to stick pH_çm, that is pH deeper than 8 m.
 
@@
   #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
-  summarize(temp_mix_max =round( max(temp_mix, na.rm=TRUE), digits = 2),
+  summarize(temp_mix_max = round( max(temp_mix, na.rm=TRUE), digits = 2),
             temp_mix_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
-            temp_ctd_1m_max =round( max(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
+            temp_ctd_1m_max = round( max(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
             temp_ctd_1m_min = round(min(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
-            temp_ctd_3m_max =round( max(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
+            temp_ctd_3m_max = round( max(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
             temp_ctd_3m_min = round(min(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
-            temp_ctd_5m_max =round( max(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
+            temp_ctd_5m_max = round( max(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
             temp_ctd_5m_min = round(min(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
-            temp_ctd_7m_max =round( max(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
+            temp_ctd_7m_max = round( max(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
             temp_ctd_7m_min = round(min(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
-            temp_ctd_9m_max =round( max(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
+            temp_ctd_9m_max = round( max(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
             temp_ctd_9m_min = round(min(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
-            temp_11m_max =round( max(temp_insitu_11m, na.rm=TRUE), digits = 2),
+            temp_11m_max = round( max(temp_insitu_11m, na.rm=TRUE), digits = 2),
             temp_11m_min = round(min(temp_insitu_11m, na.rm=TRUE), digits = 2),
             temp_fb_max = round(max(temp_fb, na.rm=TRUE), digits = 2),
-            temp_fb_min =round( min(temp_fb, na.rm=TRUE), digits = 2),
+            temp_fb_min = round( min(temp_fb, na.rm=TRUE), digits = 2),
             sal_mix_max = round(max(sal_mix, na.rm=TRUE), digits = 2),
             sal_mix_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
-            sal_ctd_1m_max =round( max(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
+            sal_ctd_1m_max = round( max(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
             sal_ctd_1m_min = round(min(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
-            sal_ctd_3m_max =round( max(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
+            sal_ctd_3m_max = round( max(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
             sal_ctd_3m_min = round(min(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
-            sal_ctd_5m_max =round( max(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
+            sal_ctd_5m_max = round( max(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
             sal_ctd_5m_min = round(min(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
-            sal_ctd_7m_max =round( max(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
+            sal_ctd_7m_max = round( max(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
             sal_ctd_7m_min = round(min(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
-            sal_ctd_9m_max =round( max(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
+            sal_ctd_9m_max = round( max(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
             sal_ctd_9m_min = round(min(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
@@
             sal_fb_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
-            pH_sf_max = round(max(pHint_tot_sf, na.rm=TRUE), digits = 4),
-            pH_sf_min = round(min(pHint_tot_sf, na.rm=TRUE), digits = 4))
-kable(range_month, caption ="")
+            pH_sf_max = round(max(pHint_tot_sf_9m, na.rm=TRUE), digits = 4),
+            pH_sf_min = round(min(pHint_tot_sf_9m, na.rm=TRUE), digits = 4))
+kable(range_month, caption = "")
 ```

### 2020-09-02 awipev-CO2.Rmd
revised months, vertical pH changes

@@
   dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
-  dplyr::mutate( # create new variable depth
-    depth = ifelse(
+  dplyr::mutate(depth = ifelse( # create new variable depth
       pressure_insitu_ctd <= 2,
@@
                 date = d_hour$date,
-                       month = month(d_hour$datetime))
+                monthd = lubridate::month(d_hour$datetime), # month as a number
+                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
+  )
 ```
@@
 p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
-  geom_point( aes(color=factor(month))) + 
+  geom_point( aes(color=factor(monthd))) + 
   geom_abline(slope=1, intercept=0, linetype = "dashed")+
@@
 
-p <-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = month))+
-  geom_text( aes(color=factor(month))) + 
+p <-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = monthd))+
+  geom_text( aes(color=factor(monthd))) + 
  # scale_color_viridis_d(option = "C", guide="none")+
@@
 lm <- lm2(x = d_all$temp_insitu_ctd_9m, y = d_all$temp_insitu_11m)
-p <-  ggplot(d_all, aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = month))+
-  geom_text( aes(color=factor(month))) + 
+p <-  ggplot(d_all, aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = monthd))+
+  geom_text( aes(color=factor(monthd))) + 
  # scale_color_viridis_d(option = "C", guide="none")+
@@
 d_all_at_discrete <- d_all %>% #  To remove an outlier in red
-  dplyr::select(datetime, month,closest_datetime, at, sal_mix)
+  dplyr::select(datetime, monthd,closest_datetime, at, sal_mix)
 
@@
 intercept_s_at <- fit$coefficients[[1]]
-at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at, label = month))+
-  geom_text( aes(color=factor(month))) +
+at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at, label = monthd))+
+  geom_text( aes(color=factor(monthd))) +
   scale_color_discrete(guide="none")+
@@
 
-p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_corr, label = month))+
-   geom_text(aes(color = factor(month)))+
+p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_corr, label = monthd))+
+   geom_text(aes(color = factor(monthd)))+
   scale_color_discrete(guide="none")+
@@
   dplyr::mutate(pH_range_more_6m = ifelse(pressure_insitu_ctd > 6, pHint_tot_sf, NA)) %>%
-  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
+  group_by(montht) %>%
   summarize(pH_range = max(pHint_tot_sf, na.rm = TRUE) - min(pHint_tot_sf, na.rm = TRUE),
@@
 print(kable(range, digits = 2))
-```
-The range is significantly larger during some months when the data deeper than 9 m are considered. It seems therefore better to stick pH_çm, that is pH deeper than 8 m.
+
+tmp <- d_all %>% 
+  dplyr::select(montht, pHint_tot_sf, depth) %>%
+  group_by(depth, montht) %>%
+  ungroup()
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "pHT", x = "Depth (m)", y= "pHT") +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+
+```
+**Conclusion**:
+The range is significantly larger during some months when the data deeper than 9 m are considered. Also, pH is sometimes higher at the surface, at other tilmes it is higher on the bottom (June). 
+  + To compare with pCO2/pCO2 measured in the Ferryboxt seems therefore better to stick with pH_9m, that is at depths deeper than 8 m.
+  + For air-sea CO2 fluxes
 
@@
   d_all %>%
-  group_by(date=as.Date(datetime), month=month(datetime, label=TRUE), year=year(datetime)) %>%
+  group_by(date, montht, year=year(datetime)) %>%
   summarize(pH_range = max(ph_dur_corr) - min(ph_dur_corr))
@@
   range_dur %>%
-  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
+  group_by(montht) %>%
   summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
@@
 p <-
-  ggplot(data=range_dur, aes(x = as.factor(month), y = pH_range)) +
+  ggplot(data=range_dur, aes(x = as.factor(montht), y = pH_range)) +
   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
@@
   d_all %>%
-  group_by(Month = month(datetime, label=TRUE, abbr=FALSE)) %>%
+  group_by(montht) %>%
   #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
@@
 fit <- lmodel2(data = d_all,  pHint_tot_sf_norm4 ~ pH_durafet_norm4 , nperm = 99)
-pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pHint_tot_sf_norm4, label = month))+
-  geom_point( aes(color=factor(month)), size =1, alpha=0.5) + 
-  facet_wrap( ~ factor(month), ncol = 3) +
+pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pHint_tot_sf_norm4, label = monthd))+
+  geom_point( aes(color=factor(monthd)), size =1, alpha=0.5) + 
+  facet_wrap( ~ factor(monthd), ncol = 3) +
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
@@
 
-p <-  ggplot(d_all, aes(x=ph_s_dur_temp_fb, y= ph_dur_corr, label = month)) +
-  geom_text( aes(color=factor(month))) + 
+p <-  ggplot(d_all, aes(x=ph_s_dur_temp_fb, y= ph_dur_corr, label = monthd)) +
+  geom_text( aes(color=factor(monthd))) + 
   scale_color_discrete(guide = "none")+
@@
 
-p <-  ggplot(d_all, aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = month)) +
-  geom_text( aes(color=factor(month))) + 
+p <-  ggplot(d_all, aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = monthd)) +
+  geom_text( aes(color=factor(monthd))) + 
   scale_color_discrete(guide = "none")+
@@
 air_sea_month <- d_all %>%
-  dplyr::select(month, f_air_sea) %>%
-  dplyr::group_by(month) %>%
+  dplyr::select(monthd, f_air_sea) %>%
+  dplyr::group_by(monthd) %>%
   dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm=TRUE)/1000) %>% #mol/(m2 d)
   ungroup() %>%
-  dplyr::mutate(f_air_sea = days_in_month(month) * f_air_sea)
+  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea)
 #air_sea_month
 p_f_air_sea_m <- ggplot(data = air_sea_month) +
-  geom_point(aes(x = month(month, label = TRUE, abbr = TRUE), y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
+  geom_point(aes(x = monthd, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
   scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +

### 2020-09-03 awipev-CO2.Rmd
consideration on stratification in the air-sea CO2 flux section

@@
 ```{r seafet profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-# pH by depth
-# d_all<- d_all%>%
-#   dplyr::mutate(year = year(datetime))
-
-#Per month
-range <- d_all %>%
-  dplyr::mutate(pH_range_more_6m = ifelse(pressure_insitu_ctd > 6, pHint_tot_sf, NA)) %>%
-  group_by(montht) %>%
-  summarize(pH_range = max(pHint_tot_sf, na.rm = TRUE) - min(pHint_tot_sf, na.rm = TRUE),
-            pH_range_more_6m = max(pH_range_more_6m, na.rm = TRUE) - min(pH_range_more_6m, na.rm = TRUE),
-            pH_range_more_9m = max(pHint_tot_sf_9m, na.rm = TRUE) - min(pHint_tot_sf_9m, na.rm = TRUE)) %>%
-  ungroup()
-print(kable(range, digits = 2))
-
+# range <- d_all %>%
+#   dplyr::mutate(pH_range_more_6m = ifelse(pressure_insitu_ctd > 6, pHint_tot_sf, NA)) %>%
+#   group_by(montht) %>%
+#   summarize(pH_range = max(pHint_tot_sf, na.rm = TRUE) - min(pHint_tot_sf, na.rm = TRUE),
+#             pH_range_more_6m = max(pH_range_more_6m, na.rm = TRUE) - min(pH_range_more_6m, na.rm = TRUE),
+#             pH_range_more_9m = max(pHint_tot_sf_9m, na.rm = TRUE) - min(pHint_tot_sf_9m, na.rm = TRUE)) %>%
+#   ungroup()
+# print(kable(range, digits = 2))
+
+# # datetime when pH values are in but no pressure data. File sent to send to Philipp
+# no_pressure <- d_all %>% 
+#   dplyr::select(datetime, pressure_insitu_ctd, pHint_tot_sf) %>% 
+#   dplyr::filter(is.na(pressure_insitu_ctd) & !is.na(pHint_tot_sf))
+# readr::write_csv(x = no_pressure, path=paste0(path,"/fb_awipev-co2_server/ny-alesund/data//no_pressure.csv"))
+
+# we look at all depths
 tmp <- d_all %>% 
   dplyr::select(montht, pHint_tot_sf, depth) %>%
-  group_by(depth, montht) %>%
-  ungroup()
+  group_by(depth, montht)
 p <- tmp %>% 
@@
 
+# we look at 0 to 4 m vs more than 8 m
+tmp <- d_all %>% 
+  dplyr::select(montht, pHint_tot_sf, depth) %>%
+  dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
+  dplyr::filter(depth == 2 | depth == 9) %>% 
+  group_by(depth, montht)
+summary(aov(tmp$pHint_tot_sf ~ tmp$depth * tmp$montht))
+
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "pHT", x = "Depth (m)", y= "pHT") +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
 ```
 **Conclusion**:
-The range is significantly larger during some months when the data deeper than 9 m are considered. Also, pH is sometimes higher at the surface, at other tilmes it is higher on the bottom (June). 
-  + To compare with pCO2/pCO2 measured in the Ferryboxt seems therefore better to stick with pH_9m, that is at depths deeper than 8 m.
-  + For air-sea CO2 fluxes
+The range is significantly larger during some months when the data deeper than 8 m are considered.
+Also, pH is sometimes higher at the surface, at other times it is higher on the bottom (June).
+No data are available at 1 m (actually 0 to 2 m).
+So, to compare surface and bottom, I combine 1 and 3 m (0 to 4 m) and 9 m (below 8 m).
+
+Depth and month of the year have a statistically significant effet on pH. The interaxction is also significant, indicating that the effect of depth differs depending on the month.
+
+ + To compare with pCO2/pCO2 measured in the Ferrybox seems therefore better to stick with pH_9m, that is at depths deeper than 8 m.
+  + pCO2 would have the same behaviour as pH. For air-sea CO2 fluxes, one should use data from 0 to 4 m.
 
@@
 To calculate the air-sea CO2 flux, we use:
-+ seawater pCO2
-+ atmospheric CO2 measured at the Zeppelin station and downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999 
+
++ seawater pCO2 measured in the FerryBox on water pumped from 11 m depth.
++ atmospheric CO2 measured at the Zeppelin station and downloaded on 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999 
 + wind spreed data collected by the AWI at 10 m height (sent to JPG by P. Fischer, Aug. 2020)
@@
 Since there are many gaps, a climatological year is used: air-sea flux calculated by day, then by month, then by year.
+
+seaFET pH is significantly different at the surface and depth. It should therefore be the same for pCO2.
+
+Let's look first at the stratification (salinity, temperature and density).
+
+```{r stratification, echo=FALSE, message= FALSE, warning=FALSE}
+# we look at salinity all depths
+tmp <- d_all %>% 
+  dplyr::select(montht, sal_insitu_ctd, depth) %>%
+  group_by(depth, montht)
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth), y = sal_insitu_ctd)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "Salinity vs depth", x = "Depth (m)", y= "Salinity") +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+
+# we look at salinity 0 to 4 m vs more than 8 m
+tmp <- d_all %>% 
+  dplyr::select(montht, temp_insitu_ctd, depth) %>%
+  dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
+  dplyr::filter(depth == 2 | depth == 9) %>% 
+  group_by(depth, montht)
+summary(aov(tmp$temp_insitu_ctd ~ tmp$depth * tmp$montht))
+
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth), y = temp_insitu_ctd)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "Salinity vs depth", x = "Depth (m)", y= "Salinity") +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+
+# we look at temperature all depths
+tmp <- d_all %>% 
+  dplyr::select(montht, temp_insitu_ctd, depth) %>%
+  group_by(depth, montht)
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth), y = temp_insitu_ctd)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "Temperature vs depth", x = "Depth (m)", y= "Salinity") +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+
+# we look at temperature 0 to 4 m vs more than 8 m
+tmp <- d_all %>% 
+  dplyr::select(montht, temp_insitu_ctd, depth) %>%
+  dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
+  dplyr::filter(depth == 2 | depth == 9) %>% 
+  group_by(depth, montht)
+summary(aov(tmp$temp_insitu_ctd ~ tmp$depth * tmp$montht))
+
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth), y = temp_insitu_ctd)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "Temperature vs depth", x = "Depth (m)", y= "Salinity") +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+
+# we look at density 0 to 4 m vs more than 8 m
+tmp <- d_all %>% 
+  dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth) %>%
+  dplyr::mutate(density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0),
+                depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
+  dplyr::filter(depth == 2 | depth == 9) %>% 
+  group_by(depth, montht)
+summary(aov(tmp$density ~ tmp$depth * tmp$montht))
+
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth), y = density)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "Density vs depth", x = "Depth (m)", y= "Salinity") +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+```
 

### 2020-09-04 awipev-CO2.Rmd
more on stratification

@@
 
+# heatmap
+tmp <- d_all %>%
+  dplyr::filter(!is.na(depth)) %>%
+  dplyr::select(montht, sal_insitu_ctd, depth) %>%
+  group_by(montht, depth)
+sal_median <- skim(tmp) %>%
+  dplyr::select(depth, montht, numeric.p50) %>%
+  pivot_wider(names_from = depth, values_from = c(numeric.p50))
+
+plt <- sal_median %>%
+  ggplot(aes(
+    x = montht,
+    y = as.factor(depth),
+    fill = median(sal_insitu_ctd)
+  ), color = "white") +
+  geom_tile() +
+  scale_fill_gradientn(colors = viridis(5), breaks = seq(31, 36, by = 1), na.value = "grey") +
+  labs(x = "", y = "", fill = "Salinity") +
+  scale_x_discrete(position = "top") +
+  scale_y_discrete(name = "", limits = rev(levels(as.factor(tmp$depth)))) +
+  # scale_y_discrete(name = "", limits = rev(levels(as.factor(tmp$depth))),
+  #                  rev(levels(tmp$depth))[c(1,3,5,7,9)]) +
+  # coord_equal() +
+  theme(legend.position = "top",
+        axis.text.y = element_text(size = 13),
+        axis.text.x = element_text(size = 13),
+        legend.text = element_text(size = 13),
+        legend.title = element_text(size = 14),
+        #legend.key.size = unit(1.5, "cm"),
+        legend.key.height = unit(0.8, "cm"),
+        legend.key.width  = unit(2, "cm"))
+plt
+
 # we look at salinity 0 to 4 m vs more than 8 m
 tmp <- d_all %>% 
-  dplyr::select(montht, temp_insitu_ctd, depth) %>%
+  dplyr::select(montht, sal_insitu_ctd, depth) %>%
   dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
@@
   group_by(depth, montht)
-summary(aov(tmp$temp_insitu_ctd ~ tmp$depth * tmp$montht))
+sal_range <- skim(tmp) %>% 
+  dplyr::select(depth, montht, numeric.p50) %>% 
+  pivot_wider(names_from = depth, values_from = c(numeric.p50)) %>% 
+  dplyr::rename(median2m = "2",
+                median9m = "9") %>% 
+  dplyr::mutate(sal_range = median2m - median9m)
+kable(sal_range, digits = 2, caption = "Median salinity")
+
+summary(aov(tmp$sal_insitu_ctd ~ tmp$depth * tmp$montht))
 
 p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = temp_insitu_ctd)) +
+  ggplot(aes(x=as.factor(depth), y = sal_insitu_ctd)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
   group_by(depth, montht)
+temp_range <- skim(tmp) %>% 
+  dplyr::select(depth, montht, numeric.p50) %>% 
+  pivot_wider(names_from = depth, values_from = c(numeric.p50)) %>% 
+  dplyr::rename(median2m = "2",
+                median9m = "9") %>% 
+  dplyr::mutate(temp_range = median2m - median9m)
+kable(temp_range, digits = 2, caption = "Median temperature")
 summary(aov(tmp$temp_insitu_ctd ~ tmp$depth * tmp$montht))
@@
   dplyr::filter(depth == 2 | depth == 9) %>% 
+  dplyr::select(montht, depth, density) %>% 
   group_by(depth, montht) 
+den_range <- skim(tmp) %>% 
+  dplyr::select(depth, montht, numeric.p50) %>% 
+  pivot_wider(names_from = depth, values_from = c(numeric.p50)) %>% 
+  dplyr::rename(median2m = "2",
+                median9m = "9") %>% 
+  dplyr::mutate(den_range = median2m - median9m)
+kable(den_range, digits = 2, caption = "Median density")
 summary(aov(tmp$density ~ tmp$depth * tmp$montht))
@@
 ```
+Using the medians because data are missing.
+
++ Salinity 
++ Temperature is always colder at 0-4 m than below 8 m (0.15 to 2°C).
 

### 2020-09-07 awipev-CO2.Rmd
minor issue with plot profile

@@
 if (!require("tidyverse")) install.packages("tidyverse")
+library(dplyr)
 library(tidyverse)
@@
         legend.key.width  = unit(2, "cm"))
-plt
+#plt
 

### 2020-09-11 awipev-CO2.Rmd
text updated in SNAPO part according to flags changement from 3 to 2 for 3 dates

@@
 
+Also in the Discrete_sampling_AWIPEV.csv, some analysed samples have been flaged "3" by the SNAPO.
+After a close look, these samples are not differents from their duplicates.
+Then we put the flag to "2" (good result).
+
+For TA and CT, samples's flags that have been changed from 3 to 2 are: 2019-12-27 (2264 and 2130), 2019-10-25 (2332 and 2152), 2019-09-06 (2268 and 2116).
+
 ```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}

### 2020-09-11 awipev-CO2.Rmd
changed reading file atm pCO2

--- 2020-09-07 awipev-CO2.Rmd
@@
   delim = " ",
-  skip = 181,
+  comment = "#",
+  #skip = 182,
   col_names = TRUE,

### 2020-09-14 awipev-CO2.Rmd
SNAPO part updated with graphs and texts, bad duplicates removed for AT

@@
 ```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-d <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_minute.rds")) %>%
+d_min <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_minute.rds")) %>%
 dplyr::select(datetime, c(pco2_corr_qf, sal_fb_qf, sal_insitu_ctd_qf, 
@@
 
-s1 <- summary(as.factor(d$pco2_corr_qf))*100/length(d$pco2_corr_qf)
-s2 <- summary(as.factor(d$sal_fb_qf))*100/length(d$sal_fb_qf)
-s3 <- summary(as.factor(d$sal_insitu_ctd_qf))*100/length(d$sal_insitu_ctd_qf)
-s4 <- summary(as.factor(d$temp_fb_qf))*100/length(d$temp_fb_qf)
-s5 <- summary(as.factor(d$temp_insitu_11m_qf))*100/length(d$temp_insitu_11m_qf)
+s1 <- summary(as.factor(d_min$pco2_corr_qf))*100/length(d_min$pco2_corr_qf)
+s2 <- summary(as.factor(d_min$sal_fb_qf))*100/length(d_min$sal_fb_qf)
+s3 <- summary(as.factor(d_min$sal_insitu_ctd_qf))*100/length(d_min$sal_insitu_ctd_qf)
+s4 <- summary(as.factor(d_min$temp_fb_qf))*100/length(d_min$temp_fb_qf)
+s5 <- summary(as.factor(d_min$temp_insitu_11m_qf))*100/length(d_min$temp_insitu_11m_qf)
 # durafet and seafet started later
-x <- filter(d, datetime >= as.POSIXct("2017-08-29 10:00:00"))
+x <- filter(d_min, datetime >= as.POSIXct("2017-08-29 10:00:00"))
 #s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
 s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
-x <- filter(d, datetime >= as.POSIXct("2017-08-24 19:00:00"))
+x <- filter(d_min, datetime >= as.POSIXct("2017-08-24 19:00:00"))
 s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
@@
 kable(z, digits = 1)
-rm(d)
+rm(d_min)
 ```
@@
 
-For TA, dulpicates's flags that have been changed to 1 are:
+For TA, dulpicates's flags that have been changed from 2 (good) to 1 (not good) are:
 
 2015-11-18
-, 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29, 2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16, 2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03, 2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-08-23.
-
-For CT, duplicates's flags that have been changed to 1 are:
+, 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29, 2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16, 2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03, 2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-08-23, 2019-09-20, 2019-11-08, 2019-11-23.
+
+For CT, duplicates's flags that have been changed from 2 (good) to 1 (not good) are:
 
@@
     geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
-    annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
-    annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
+    annotate("text", x = diff$datetime[17], y = 7, label = "4 µmoles/kg", color="red")+
+    #annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
     labs(title= "AT", x="Time", y="Delta between TA replicates")+
@@
     annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
-    annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
+    #annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
     labs(title= "CT",x="Time", y="Delta between CT replicates")+
@@
 # DYGRAPH
-
 # to create periods according to SNAPCO analysis 
@@
 at_diff_xts <- as.xts(at_diff_xts, order.by = diff$datetime)
+
 pdelta_at_snapo_dygraph <- dygraph(at_diff_xts, group = "awipev", main="Discrete AT (SNAPO) measurements", ylab="AT") %>%
@@
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-  dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#EDEDED") %>%
+  dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#E0DEDE") %>%
   dyShading(from = snapcoevents[3], to = snapcoevents[4], color = "#C2C2C2") %>%
-  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#EDEDED") %>%
+  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#E0DEDE") %>%
   dyShading(from = snapcoevents[7], to = snapcoevents[8], color = "#C2C2C2") %>%
-  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#EDEDED") %>%
+  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#E0DEDE") %>%
   dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C2C2") %>%
+    dyShading(from = snapcoevents[13], to = snapcoevents[14], color = "#E0DEDE") %>%
+
   dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
@@
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-   dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#EDEDED") %>%
+   dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#E0DEDE") %>%
   dyShading(from = snapcoevents[3], to = snapcoevents[4], color = "#C2C2C2") %>%
-  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#EDEDED") %>%
+  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#E0DEDE") %>%
   dyShading(from = snapcoevents[7], to = snapcoevents[8], color = "#C2C2C2") %>%
-  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#EDEDED") %>%
-  dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C2C2") %>%
+  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#E0DEDE") %>%
+  dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C0C0") %>%
+      dyShading(from = snapcoevents[13], to = snapcoevents[14], color = "#E0DEDE") %>%
+
   dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%

### 2020-10-09 awipev-CO2.Rmd

@@
 ### **REMOS**
+- **2020-09-23**: REMOS started at 20:00 UTC.
+- **2020-09-22**: REMOS stopped at 19:00 UTC because of a power shutdown.
+- **2019-03-12**: REMOS on.
+- **2020-02-24**: REMOS off.
 - **2019-09-07**: REMOS back in the water.
@@
 ### **FerryBox**
+- **2020-09-30**: FB started at 19:00 UTC.
+- **2020-09-29**: FB stopped at in the morning for few hours.
+- **2020-09-26**: FB stopped at in the morning for few hours.
+- **2020-09-25**: FB stopped at in the morning for few hours.
+- **2020-09-23**: FB started at 20:00 UTC.
+- **2020-09-22**: FB stopped at 19:00 UTC because of a power shutdown.
+- **2020-09-22**: FB started again at 08:00 UTC after several months of locked down. Lisa repaired it in few minutes only. 
+- **2020-09-22**: FB started again after several months of locked down. Lisa repaired it in few minutes only. 
+- **2020-07-25**: FB stopped.
+Not possible to go inside to repair because the FB is locked after the "mercurygate".
+IPEV locked the FB with suspicion of mercury contamination rose up by Bettina (Stationleader)
+- **2020-05-24**: FB started again after several months of on activity due to very cold T and frozen pipes.
+- **2020-02-18**: FB stopped because of frozen pipes.
 - **2020-01-24**: heater issues in the contenair (power shutdown maybe) caused some samples to freeze. See part "SNAPO" for details on samples.

### 2020-11-09 awipev-CO2_PAR_sal.Rmd
sal / par relationship with lm()

--- 2020-09-14 awipev-CO2.Rmd
@@
 
-```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-# Create temp_mix: filling gaps in temp_insitu_11m using temp_insitu_9m
-d_all <- d_all %>%
-  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_9m))
-```
+```{r PAR / SAL relationship, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
+ d_all<- d_all %>%
+  dplyr::mutate(
+    datetime =ymd_hms(datetime))
 
-```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
-d <- tibble(
-  read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
-) %>% 
-  dplyr::mutate(datetime = dmy_hm(sampling_date, tz="UTC"),
-                measure_date = dmy(measure_date, tz="UTC"),
-                date = as.Date(datetime)) %>% 
-  dplyr::rename(ph_s_sf = pH_s_seafet,
-                ph_s_dur = pH_s_durafet,
-                qflag_ph_s_sf = qflag_pH_s_seafet,
-                qflag_ph_s_dur = qflag_pH_s_durafet)
+sal_xts <- dplyr::select(d_all, datetime,sal_insitu_ctd_1m)
+, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m)
 
-# Add the flag location: some samples have been collected at the pier. Notes them here.
-# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
- # And keep data with flag 0 for FB location
-d <- d%>%
-  dplyr::mutate(location_flag = ifelse(datetime == as.POSIXct("2016-04-21 09:25:00") | 
-                                         datetime == as.POSIXct("2016-02-10 14:00:00") | 
-                                         datetime == as.POSIXct("2016-02-17 09:20:00") |
-                                         datetime == as.POSIXct("2016-02-24 14:20:00") |
-                                         datetime == as.POSIXct("2016-02-04 09:30:00") |
-                                         datetime == as.POSIXct("2016-01-27 15:00:00") |
-                                         datetime == as.POSIXct("2016-01-13 13:45:00") |
-                                         datetime == as.POSIXct("2016-01-06 14:10:00") |
-                                         datetime == as.POSIXct("2015-12-24 10:45:00") |
-                                         datetime == as.POSIXct("2015-12-30 13:30:00") |
-                                         datetime == as.POSIXct("2018-01-05 15:20:00") |
-                                         datetime == as.POSIXct("2018-02-02 14:35:00") |
-                                         datetime == as.POSIXct("2018-03-02 14:10:00") |
-                                         datetime == as.POSIXct("2019-05-31 11:45:00"), 
-                                       1, 0))
-d <- d %>%
-  dplyr::filter(location_flag == 0)
+ sal_xts<- sal_xts %>% 
+  dplyr::mutate(sal_insitu_ctd_1m = case_when(
+    is.na(sal_insitu_ctd_1m) ~ 0,
+    TRUE~ sal_insitu_ctd_1m))
 
-# Keep only flag = 2 for at/ct analysis 
-# Keep only flag = 2 for pH durafet and seaFET.
-d <- d%>%
-  dplyr::mutate(ct = replace(ct, qflag_ct != 2, NA),
-                at = replace(at, qflag_at != 2, NA),
-                ph_s_sf = replace(ph_s_sf, qflag_ph_s_sf != 2, NA),
-                ph_s_dur = replace(ph_s_dur, qflag_ph_s_dur != 2, NA))
-
-# Mercuric chloride correction (Dickson et al. 2007, SOP3a)
-d$at <- d$at * 1.0002
-d$ct <- d$ct * 1.0002
-
-# mean at and ct
-at_ct_mean <- d %>% 
-#  group_by(datetime)%>%
-  group_by(date) %>%
-  dplyr::summarize(at_mean = mean(at, na.rm = TRUE),
-                   ct_mean = mean(ct, na.rm = TRUE),
-                   at_sd = sd(at, na.rm = TRUE), 
-                   ct_sd = sd(ct, na.rm = TRUE)
-                   )
-d <- left_join(d, at_ct_mean, by='date') %>% 
-  dplyr::select(datetime, date, temp_s_lab, ph_s_sf, ph_s_dur, location_flag, at, ct, at_mean, ct_mean) %>% # removed useless variables and also to do unique next
-  dplyr::distinct()
-
-# Fill the gaps in at_mean with interpolation
-TAinterp <-approx(d$datetime, d$at_mean, xout=d$datetime, method="linear", rule=2)
-names(TAinterp) <- c("datetime", "at_mean_interp")
-TAinterp <- as.data.frame(TAinterp)
-d$at_mean_interp <- TAinterp$at_mean_interp
-
-CTinterp <-approx(d$datetime, d$ct_mean, xout=d$datetime, method="linear", rule=2)
-names(CTinterp) <- c("datetime", "ct_mean_interp")
-CTinterp <- as.data.frame(CTinterp)
-d$ct_mean_interp <- CTinterp$ct_mean_interp
-
-# add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
-# use the closest time to add them
-closest <- which.closest(d$datetime, d_all$datetime) # closest date and time
-d$closest_datetime <- d_all$datetime[closest]
-# if the closest value is more than 30 min away, then we do not take it
-d$closest_datetime[abs(d$datetime - d_all$datetime[closest]) > 30*60] <- NA
-# create closest_datetime in d_all (copy of datetime)
-d_all$closest_datetime <- d_all$datetime
-d <- left_join(d, d_all %>%
-                 dplyr::select(
-                   c(
-                     closest_datetime,
-                     sal_fb,
-                     temp_fb,
-                     temp_mix,
-                     sal_mix,
-                     temp_insitu_11m,
-                     temp_insitu_ctd,
-                     pressure_insitu_ctd
-                   )
-                 ), by = "closest_datetime")
-
-# Conversion of spec pH of in situ samples to in situ temp
-pH_seafet <- d %>%
-  dplyr::filter(!is.na(ph_s_sf) & !is.na(temp_insitu_ctd))
-pH_seafet <- pH_seafet %>% 
-  dplyr::mutate(ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))
-
-# Conversion of spec pH of FerryBox samples to FerryBox temp
-pH_durafet <- d %>%
-  dplyr::filter(!is.na(ph_s_dur) & !is.na(sal_fb) & !is.na(temp_fb))
-pH_durafet <- pH_durafet %>% 
-  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH = pH_durafet$ph_s_dur, ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = pH_durafet$temp_fb, Tlab = pH_durafet$temp_s_lab, Pinsi = 0, S = pH_durafet$sal_fb, Pt = 0, Sit = 0))
-
-# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
-pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(date, ph_s_sf_temp_insi)%>% 
-  dplyr::group_by(date) %>% 
-  dplyr::summarize(ph_s_sf_temp_insi = mean(ph_s_sf_temp_insi, na.rm = TRUE))
-pH_durafet_mean <- pH_durafet%>%
-  dplyr::select(date, ph_s_dur_temp_fb)%>% 
-  dplyr::group_by(date) %>% 
-  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = TRUE))
-
-#  make means in "d" to have same format and call it "discrete"
-discrete <- d %>%
-  dplyr::group_by(date) %>%
-  dplyr::summarize(
-    datetime = mean(datetime, na.rm = TRUE),
-      sal_fb = mean(sal_fb, na.rm = TRUE),
-    sal_mix = mean(sal_mix, na.rm = TRUE),
-    temp_fb = mean(temp_fb, na.rm = TRUE),
-    at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
-    at = mean(at, na.rm = TRUE),
-    #qflag_at = mean(qflag_at, na.rm = TRUE), # already dealt with above
-    ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
-    ct = mean(ct, na.rm = TRUE),
-    #qflag_ct = mean(qflag_ct, na.rm = TRUE)  # already dealt with above
-    temp_mix = mean(temp_mix, na.rm = TRUE),
-    temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE)
-  )
-# join discrete + seafet/durafet
-discrete <- left_join(discrete, pH_seafet_mean, by='date')
-discrete <- left_join(discrete, pH_durafet_mean, by='date')
-
-##   *****Attention, temp noted by logisticians in d is FB temp with SBE45 ******
-##   *****Attention, I asked to the logisticians to log insitu temp from 9 june 2019
-##   *****Attention, but no longer used in the script, so no problem
-
-# pH calculated (at and ct) at Ferrybox sal and temp
-discrete_no_na <- discrete %>%
-  dplyr::filter(!is.na(sal_fb)  & !is.na(temp_fb) & !is.na(at) & !is.na(ct))
-discrete_is_na <- discrete %>%
-  dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
-carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-discrete_no_na$phcalc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
-discrete_no_na$pco2_calc_fb <- carb$pCO2
-
-# create new variable in "discrete_is_na" to bind "discrete_no_na"
-discrete_is_na$phcalc_fb <- NA
-discrete_is_na$pco2_calc_fb <- NA
-discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
-  dplyr::arrange(date)
-```
-
-```{r Combine discrete and continous data, echo=FALSE}
-# at
-closest <- which.closest(discrete$datetime, d_all$datetime) # closest date and time
-discrete$closest_datetime <- d_all$datetime[closest]
-# if the closest value is more than 30 min away, then we do not take it
-discrete$closest_datetime[abs(discrete$datetime - d_all$datetime[closest]) > 30*60] <- NA
-discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, at) %>%
-    dplyr::filter(!is.na(closest_datetime)) %>%
-  rename(datetime=closest_datetime)
-d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-# ct
-discrete2merge <- discrete %>%
-  #drop_na() %>%
-  dplyr::select(closest_datetime, ct) %>%
-  dplyr::filter(!is.na(closest_datetime)) %>%
-  rename(datetime=closest_datetime)
-d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-# pH calculated ferrybox
-discrete2merge <- discrete %>%
-  #drop_na() %>%
-  dplyr::select(closest_datetime, phcalc_fb) %>%
-  dplyr::filter(!is.na(closest_datetime)) %>%
-  rename(datetime=closest_datetime)
-d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-# seaFET pH 
-discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, ph_s_sf_temp_insi) %>%
-  dplyr::filter(!is.na(closest_datetime)) %>%
-  rename(datetime=closest_datetime)
-d_all <- full_join(d_all, discrete2merge, by="datetime")
-d_all <- d_all %>% 
-  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) # eliminate ph spec data when the profiler was at several depth during the same hour
-  #dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) |
-  #                                           !is.na(temp_insitu_ctd_9m), 
-   #                                        ph_s_sf_temp_insi, NA)) # only use ph spec data when profiler was below 6 m
-
-# durafet pH 
-discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, ph_s_dur_temp_fb) %>%
-  dplyr::filter(!is.na(closest_datetime)) %>%
-  rename(datetime=closest_datetime)
-d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-# calculated pCO2 
-discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, pco2_calc_fb) %>%
-  dplyr::filter(!is.na(closest_datetime)) %>%
-  rename(datetime=closest_datetime)
-d_all <- full_join(d_all, discrete2merge, by="datetime")
-
-saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
-
-## bind the voltages and deployment ##
-
-# Duplicate datetime in closest_datetime to do the left_join
-d_all$closest_datetime <- d_all$datetime
-discrete <- left_join(discrete, d_all %>% dplyr::select(c(closest_datetime, voltEXT, voltINT)), by="closest_datetime")
-```
-
-<style type="text/css">
-
-body{ /* Normal  */
-      font-size: 18px;
-  }
-h3{ /* Header 3 */
-  font-size: 22px;
-  <!-- font-family: "Times New Roman", Times, serif; -->
-  color: DarkBlue;
-}
-h4{ /* Header 4 */
-  font-size: 18px;
-  <!-- font-family: "Times New Roman", Times, serif; -->
-  color: DarkBlue;
-}
-h5{ /* Header 5 */
-  font-size: 16px;
-  <!-- font-family: "Times New Roman", Times, serif; -->
-  color: DarkBlue;
-}
-</style>
-
-# {.tabset .tabset-fade .tabset-pills}
-
-## Infos
-
-### **Introduction**
-<div style="text-align: justify">  
-The AWIPEV-CO2 project aims at starting the first time series for the carbonate chemistry in the Arctic Ocean as part of the AWIPEV Underwater Observatory.
-It comprises two components: (1) continuous real-time measurements and (2) discrete measurements.
-The rationale is that discrete measurements are absolutely needed to calibrate and validate the sensors.
-
-### **AWIPEV Underwater Observatory**
-<div style="text-align: justify">  
-The AWIPEV Underwater Observatory has been deployed at Ny-Alesund (Spitsbergen, 78°55'18N, 11°56'31E) in June 2012.
-It is part of the German Project COSYNA (Coastal Observation Systems of the Northern- and Arctic Seas), which aims at increasing the availability of continuous real-time data from remote but climatically-sensitive ecosystems.
-The AWIPEV underwater observatory comprises a fully remote controlled FerryBox system fed with seawater pumped in front of the old peer at 12 m depth.
-Temperature, salinity, pressure, turbidity, oxygen, chl-*a* fluorescence are measured.
-Furthermore, an additional remote controlled underwater sensor unit able to profile from 12 m to the surface at any frequency carries additional sensors for salinity, pressure, turbidity, oxygen chl-*a* fluorescence and PAR.
-The system also comprises an ADCP for continuous measurements of currents and waves.
-Besides these standard sensors, the underwater unit is equipped with a webcam and stereo-optical device to remotely assess fish and jellyfish populations.
-The AWIPEV observatory is specifically designed for polar experimental work under extreme conditions including ice coverage and the inaccessibility for about 7 months during polar winter.
-During this time, the system is remotely controlled and maintained from Germany.
-All data sampled by the sensors are continuously sent to a central server system at Helgoland Island where the data are stored and processed.
-The processed data are open access and available at http://codm.hzg.de/codm.
-
-<div style="text-align:center" markdown="1">
-  <img  src="./Images/Container.png" width="200" height="200">
-  <img  src="./Images/Intake.png" width="200" height="200">
-  <img  src="./Images/2018-04-17_Ferrybox2.jpg" width="200" height="200">
-</div>
-
-### **Continuous and semi-continuous measurements**
-<div style="text-align: justify">  
-The Arctic version of the Contros-Kongsberg HydroC CO~2~ FT (Carbon Dioxyde partial pressure Flow Through surface water sensor) has been installed in July 2015.
-Molecules of dissolved CO~2~ diffuse through a thin composite membrane into the internal gas circuit leading to a detector chamber, where the partial pressure of CO~2~ is determined by means of infra-red absorption spectrometry.
-Concentration-dependent IR light is converted into the output signal from calibration coefficients stored in firmware and data from additional sensors within the gas circuit.
-The measuring range is 200-1000 uatm, resolution is < 1 uatm and accuracy is +- 1% reading.
-The sensor is the first instrument in the measuring loop; data are logged every minute.
-This instrument requires yearly factory calibration; two sensors ara available to allow a continuous time series.
-
-Since February 2016, total alkalinity (AT) is measured every 90 min with a Contros-Kongsberg HydroFIA TA (Total Alkalinity analyser flow through system).
-Fifty ml of seawater is filtered (0.2 um) using a Contros-Kongsberg cross-flow filter and then acidified using dilute hydrochloric acid (0.1 N).
-CO~2~ is then flushed out (open-cell titration) and the final pH measured by means of an indicator dye (bromocresol green) and visible absorption spectrometry.
-Together with salinity and temperature at the time of measurement, the pH reading is used to calculate AT.
-According to the manufacturer, the measuring range is 400 umol/kg dynamic range, resolution 0.1 umol/kg, accuracy 25 umol/kg (+- 1%) and precision 5 umol/kg (+- 0.2%).
-
-In August 2017, a seaFET Ocean pH sensor (Sea-Bird Scientific) has been added to the UWO.
-This new sensor continuously measures pH at 11 m using an ISFET (Ion Sensitive Field Effect Transistor).
-According to the manufacturer, the measuring range is between 6.5 and 9 pH units, initial accuracy is 0.02 pH units and precision is 0.004 pH units.
-Operating salinity and temperature range are 20 to 40 PSU and 0 to 50°C respectively.
-
-In August 2017, a Durafet III pH electrode connected to a UDA2128 Analyser (Honeywell) was also implemented to the Ferrybox flow-through system.
-This electrode continuously measures pH, in the Ferrybox, through an ISFET.
-According to the manufacturer, the measuring range is between 0 and 14 pH units.
-
-### **Data availability**
-The data at one minute frequency were tagged with the following quality flags
-
-+ 1: good data
-+ 3: failing the date and time test
-+ 4: data not usable according to manufacturer
-+ 6: failing the manufacturer range test (not used)
-+ 7: failing the regional range test 
-+ 12: failing the spike test (NAs from despike)
-+ 13: failing the gradient test
-+ 15: instrument not deployed or operated
-+ 16: acid flush
-+ 99: failing the final visual inspection
-
-* Despike using oce::despike with n=2, k=5761
-
-```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-d <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_minute.rds")) %>%
-dplyr::select(datetime, c(pco2_corr_qf, sal_fb_qf, sal_insitu_ctd_qf, 
-                          temp_fb_qf, temp_insitu_11m_qf, ph_dur_qf, phINT_qf))
-
-s1 <- summary(as.factor(d$pco2_corr_qf))*100/length(d$pco2_corr_qf)
-s2 <- summary(as.factor(d$sal_fb_qf))*100/length(d$sal_fb_qf)
-s3 <- summary(as.factor(d$sal_insitu_ctd_qf))*100/length(d$sal_insitu_ctd_qf)
-s4 <- summary(as.factor(d$temp_fb_qf))*100/length(d$temp_fb_qf)
-s5 <- summary(as.factor(d$temp_insitu_11m_qf))*100/length(d$temp_insitu_11m_qf)
-# durafet and seafet started later
-x <- filter(d, datetime >= as.POSIXct("2017-08-29 10:00:00"))
-#s6 <- summary(as.factor(x$temp_dur_qf))*100/length(x$temp_dur_qf)
-s7 <- summary(as.factor(x$ph_dur_qf))*100/length(x$ph_dur_qf)
-x <- filter(d, datetime >= as.POSIXct("2017-08-24 19:00:00"))
-s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
-z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
-  as.data.frame() %>%
-         rownames_to_column(var = "flag") %>% 
-         as_tibble()
-labels <- c("Good", "Not usable", "Outside regional range", "Outliers (despike)", 
-            "Failed visual inspection", "Not deployed or operated", "Acid flush", "Failed visual inspection")
-colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
-                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
-zz <- pivot_longer(z, -Flag)
-p <- ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
-  geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
-  #scale_y_reverse() +
-  scale_fill_discrete(labels = labels) + 
-  coord_flip() +
-  #geom_text(aes(label=round(value, digits = 0)), position = position_stack((hjust = 0.5)), size = 3) +
-  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
-  Mytheme(size_labs = 8) +
-  theme(plot.margin = margin(t = 0, r = 0.0, b = 0, l = 0.0, unit = "cm"))
-ggsave(filename = "figures/availability.png", plot = p, width = 20, units = "cm")
-kable(z, digits = 1)
-rm(d)
-```
-
-## Salinities
-Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically.
-Salinity from FB is taken in consideration.
-If data gaps are encountered, they are filled with bottom salinty data from ctd (> 8 m).
-New column "sal_mix" is created and is the one used in ESSD paper.
-
-+ 1 SBE45 inside the Ferrybox (sal_fb)
-+ 5 CTD > 8 m depth (sal_insitu_ctd)
-
-```{r Salinity, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-# SAL FerryBox and sal_mix
-sal_xts <- dplyr::select(d_all, datetime, sal_fb, sal_mix)
-sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
+sal_xts <- as.xts(sal_xts, order.by = as.Date(d_all$datetime))
 dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
@@
       dyRangeSelector(height = 30, dateWindow= NULL)
-# now remove outliers
-d_all <- d_all %>%
-  dplyr::mutate(
-    sal_mix = case_when(
-      date > as.Date("2016-02-01") &
-        date <  as.Date("2016-02-09") & sal_mix < 34 ~ NA_real_,
-      date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
-      date > as.Date("2015-10-01") &
-        date <  as.Date("2015-10-05") & sal_mix < 31.5 ~ NA_real_,
-      date == as.Date("2017-03-22") &
-        sal_mix < 34 ~ NA_real_,
-      TRUE ~ sal_mix
-    )
-  )
-```
 
-### **Depth profile**
-
-```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-
-#SAL CTD profile
-sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m)
-sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
-dygraph(sal_xts, group = "awipev", main="Salinity (in situ CTD, all depths)", ylab="Salinity") %>%
-dySeries("sal_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
-dySeries("sal_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
-dySeries("sal_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
-dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
-dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
-      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
-      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-    dyLegend(show = "follow")   %>%
-    dyAxis("y",valueRange = c(30, 37)) %>%
-      dyRangeSelector(height = 30, dateWindow= NULL)
-
-df <- d_all %>% 
-  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
-  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
-  group_by(date) %>% 
-  summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
-            mean9m = mean(sal_insitu_ctd_9m, na.rm = TRUE),
-            range = mean(sal_insitu_ctd_1m, na.rm = TRUE)-mean(sal_insitu_ctd_9m, na.rm = TRUE)) %>% 
-  ungroup()
-
-p_sal_range <- ggplot(data = df) +
-  geom_histogram((aes(x = df$range))) +
-  labs(title = "Salinity difference between 1 and 9 m", x = "Difference") +
-  Mytheme(size_labs = 8)
-p_sal_range
-
-kable(quantile(x = df$range, na.rm = TRUE), digits = 2, col.names = "Sal. unit", caption = "Quantiles salinity gradient between 0-2 m and > 8 m")
-```
-There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m).
-The salinity difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)` and `r max(df$range, na.rm=TRUE)` (mean: `r mean(df$range, na.rm=TRUE)`; `r median(df$range, na.rm=TRUE)`).
-The difference with depth is therefore significant.
-
-### **Sal FB / Sal CTD 9 m **
-
-```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
-p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
-  geom_point( aes(color=factor(monthd))) + 
-  geom_abline(slope=1, intercept=0, linetype = "dashed")+
-  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),colour = "blue") +
-  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
-  labs(title = paste("","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
-                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
-                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
-                     "; P =", signif(lm$fit$P.param, 3),
-                     "; RMSE = ", signif(lm$rmse, 3))) +
-  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
-  coord_fixed(ratio = 1 )+
-  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()
-
-print(p) #p_sal_fb_ctd
-
-d_all$diff_sal_fb_insitu_9m <- d_all$sal_insitu_ctd_9m - d_all$sal_fb
-mean_diff_sal_fb_insitu_9m <- round(mean(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
-sd_diff_sal_fb_insitu_9m <- round(sd(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
-```
-
-The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu_9m` ± `r sd_diff_sal_fb_insitu_9m` PSU.
-
-## Temperatures
-Several temperature sensors are on site, 1 inside the Ferrybox (SBE45), 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically and 1 fixed at 11 m depth (sbe38). 
-Temperature in situ at 11 m depth is taken in consideration.
-If data gaps are encountered, they are filled with bottom temperature data from ctd (> 8 m).
-New column "temp_mix" is created.
-For the moment, no gaps are encountered and temp_mix = temp_insitu_11m.
-
-- 1 SBE45 inside the Ferrybox (temp_fb)
-- 5 CTD profiling (temp_insitu_ctd_1m - 3m - 5m - 7m - 9m)
-- 1 fixed at 11 meters depth (temp_insitu_11m)
-
-```{r temperature time series, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-# TEMP Ferrybox SBE45
-temp_fb_xts <- dplyr::select(d_all, datetime, temp_fb)
-temp_fb_xts <- as.xts(temp_fb_xts, order.by = temp_fb_xts$datetime)
-dygraph(temp_fb_xts, group = "awipev", main="Temperature (in Ferrybox)", ylab="Temperature") %>%
-      dySeries("temp_fb", color = "blue", strokeWidth = 0, label = "temp_fb") %>%
-      dyAxis("y", valueRange = c(-2.5, 10)) %>%
-      dyLegend(show = "follow")   %>%
-      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-      dyRangeSelector(height = 30, dateWindow= NULL)
-# TEMP insitu SBE38
-temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_11m)
-temp_insitu_xts <- as.xts(temp_insitu_xts, order.by = temp_insitu_xts$datetime)
-dygraph(temp_insitu_xts, group = "awipev", main="Temperature (in situ 11 m)", ylab="Temperature") %>%
-      dySeries("temp_insitu_11m", color = "blue", strokeWidth = 0, label = "temp_insitu_11m") %>%
-      dyAxis("y", valueRange = c(-2.8, 10)) %>%
-      dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-      dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-      dyLegend(show = "follow")   %>%
-      dyRangeSelector(height = 30, dateWindow= NULL)
-```
-
-### **Temperature profiles**
-```{r temperature profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-temp_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m)
-temp_xts <- as.xts(temp_xts, order.by = temp_xts$datetime)
-dygraph(temp_xts, group = "awipev", main="Temperature profile (in situ CTD, all depths)", ylab="Temperature") %>%
-dySeries("temp_insitu_ctd_1m", color = RColorBrewer::brewer.pal(5, "Set1")[1], strokeWidth = 0, label = "1m") %>%
-dySeries("temp_insitu_ctd_3m", color = RColorBrewer::brewer.pal(5, "Set1")[2], strokeWidth = 0, label = "3m") %>%
-dySeries("temp_insitu_ctd_5m", color = RColorBrewer::brewer.pal(5, "Set1")[3], strokeWidth = 0, label = "5m") %>%
-dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
-dySeries("temp_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
-dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
-dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
-dyLegend(show = "follow")   %>%
-dyAxis("y",valueRange = c(-2, 10)) %>%
-dyRangeSelector(height = 30, dateWindow= NULL)
-
-df <- d_all %>% 
-  dplyr::select(datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m) %>%
-  dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
-  group_by(date) %>% 
-  summarize(mean1m = mean(temp_insitu_ctd_1m, na.rm = TRUE),
-            mean9m = mean(temp_insitu_ctd_9m, na.rm = TRUE),
-            range = mean(temp_insitu_ctd_1m, na.rm = TRUE)-mean(temp_insitu_ctd_9m, na.rm = TRUE)) %>% 
-  ungroup()
-```
-There are `r sum(!is.na(df$range))` days with temperature values at both 1 m (0-2 m) and 9 m (> 8 m).
-The temperature difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)`°C and `r max(df$range, na.rm=TRUE)`°C (mean: `r mean(df$range, na.rm=TRUE)`°C; `r median(df$range, na.rm=TRUE)`°C).
-The difference with depth is therefore significant.
-
-### **T Ferrybox / T insitu 11 m **
-
-```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-# Remove temp_fb outliers 
-d_all <- d_all %>%
-  dplyr::mutate(
-    temp_fb = ifelse(
-      datetime >= as.POSIXct("2017-03-22 08:00:00") &
-        datetime <= as.POSIXct("2017-03-23 16:00:00"),
-      NA,
-      temp_fb
-    ),
-    temp_fb = ifelse(temp_fb > 15, NA, temp_fb)
-  )
-lm <- lm2(x = d_all$temp_insitu_11m, y = d_all$temp_fb)
-
-p <-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = monthd))+
-  geom_text( aes(color=factor(monthd))) + 
- # scale_color_viridis_d(option = "C", guide="none")+
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
-              colour = "blue") +
-  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
-                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
-                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
-                     "; P =", signif(lm$fit$P.param, 3),
-                     "; RMSE = ", signif(lm$rmse, 3))) +
-  theme_bw() +
-  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + 
-  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
-  labs(x="T 11 m", y="T FB ", color = "Months") 
-print(p) # p_temp_11_fb
-
-d_all$diff_T_fb_11m <- d_all$temp_fb - d_all$temp_insitu_11m
-mean_diff_T_fb_11m <- round(mean(d_all$diff_T_fb_11m, na.rm = TRUE), digits = 2)
-sd_diff_T_fb_11m <- round(sd(d_all$diff_T_fb_11m, na.rm = TRUE), digits = 2)
-```
-
-The mean difference between temperature Ferrybox and in situ at 11 m is: `r mean_diff_T_fb_11m` ± `r sd_diff_T_fb_11m`°C.
-
-### **T 11 m / T CTD > 8 m **
-
-```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-lm <- lm2(x = d_all$temp_insitu_ctd_9m, y = d_all$temp_insitu_11m)
-p <-  ggplot(d_all, aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = monthd))+
-  geom_text( aes(color=factor(monthd))) + 
- # scale_color_viridis_d(option = "C", guide="none")+
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
-              colour = "blue") +
-  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
-                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
-                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
-                     "; P =", signif(lm$fit$P.param, 3),
-                     "; RMSE = ", signif(lm$rmse, 3))) +
-  theme_bw() +
-  theme(aspect.ratio = 1,plot.title = element_text(size = 7)) + 
-  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
-  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")
-print(p)
-
-d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd_9m
-mean_diff_T_ctd_11m <- round(mean(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
-sd_diff_T_ctd_11m <- round(sd(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
-```
-
-The mean difference between temperature Ferrybox and in situ at 11 m is: `r mean_diff_T_ctd_11m` ± `r sd_diff_T_ctd_11m`°C.
-
-## Total alkalinity
-
-Since we bought the AT analyser (February 2016), numerous problems happened due to a leak of the degassing unit in each analyser and sudden step changes.
-Last analyser repaired by Contros was installed back in the FB on 2018-07-31.
-This was the 3rd analyser on site.
-Even with this instrument, data collection didn't show satisfaction.
-
-<!-- We identify four periods (see plot at the end of this page with dark and ligth grey): -->
-
-<!-- - from the set-up of the instrument on **2016-02-23** to **2017-02-09** during which we try to correct for the drift -->
-<!-- - from **2017-02-09** to **2017-03-10** during which no drift correction is made, just an offset is applied to correct for the sudden shift in the data -->
-<!-- - from the set-up of a new instrument on **2018-01-08** to **2018-06-20**, during which another correction using the discrete samples will be performed.
-In this period and before to stop it, continuous leakages in the degasing unit happened.
--->
-<!-- - from the set-up of a repaired unit on **2018-07-31** to **2018-10-31**.
-Here, the instrument took wrong salinity to perform AT measurements.
-The cause is not clear yet but Steffen sent to Samir a protocol on 2018-08-24 to correct those data with right salinity.
-Also, after this issue, since 2018-08-20, bad data were still measured.
-Steffen diagnosed a "bubble issue" in the indicator tubbings.
-Steps will be sent to Marine to solve this issue.
-After this, it was not a bubble.
-We decided to switch off the instrument to save reagents and wait until the comming of Steffen in NYA with a new instrument.
--->
-
-<!-- A new instrument was installed with Steffen on **2018-10-31**.
-This new instrument has a complete new designed membrane which will solve the problem.
-Steffen also developped a TA web interface to communicate remotly with the analyser.
-Samir has all the passwords and ID to connect.
--->
-
-<!-- The instrument is usually calibrated against CRM standards after deployment, CRMs are run after 3 months as samples (measurement mode, not calibration mode), an then immediately calibrated again.
-This procedure is repeated every 3 months.
--->
-
-<!-- ### **Filtration of AT data: outliers removing** -->
-
-<!-- Outliers are present because of the cleaning operations made on the FerryBox everydays at 12:00am and 12:00pm.
-We first removed the outliers using a filter and decided, after a Skype conference with Steffen on September 2016, to: -->
-
-<!--   - Remove existing filters ( > 2350 µmol/kg). -->
-<!--   - Filter using salinity flag. -->
-<!--   - Filter using pH flag. -->
-<!--   - Not to filter on temperature flag. -->
-<!--   - Apply a 3 data points median filter (no longer used; see despike function in "oce" package) -->
-
-<!-- We decided to use "despike" function as data filter.
-This filter is done in "ny-alesund_cc.R".
-Length of runing median is: k = 121 days and the indicator (n times the sd between x and the reference) to consider a data from an outlier is: n = 0.5.
--->
-
-<!-- ### **Correction of AT data** -->
-
-<!-- Calibration was initially performed twice a year since the analyser was supposed to be stable.
-Calibration was performed using the internal "calibration mode" against a CRM from A.Dickson (Batch #145, 2016-02-24) right after the instrument was installed and a second time on 2016-09-16.
-This approch is not longer used since September 2016 (Skype with Contros).
--->
-
-<!-- Since this date, the analyser is calibrated by measuring a CRM with the "measurement mode" in order to measure the offset of the instrument.
-Additionally, discrete seawater are sampled weekly and TA is analysed by SNAPO-CO2.
--->
-
-<!--   - Two methods to correct the drift are available: -->
-<!--     - based on CRMs  -->
-<!--     - based on AT measurement of discrete samples ("references"). -->
-
-<!-- #### **Calibration** -->
-
-<!-- - **2019-01-29 14:10**: Calibration started by Philipp Fisher using CRM 145 (2226.16 umol/kg, 33.572).
-The three previous measurements were 2314.5, 233.8, 2313.7 (analyser stable) and the six subsequent measurements were 2211.8, 2277.5, 2305.4, 2316.6, 2317.9.
-Error was done with CRM salinity (Analyser was not unplugged from the FB).
--->
-<!-- Steffen's response: -->
-<!-- > Hence, the serial connection should be cut off or the FB module feeding the analyzer with salinity data should be stopped during calibration.
-The calibration can be recalculated afterwards in the data post-processing.
-However, I see that the calibration resulted in very similar pH values 3.540 (September calibration) and 3.543 (January calibration) with very similar correction factors 1.2371 and 1.2365.
-Also the TA values are very similar to the baseline measurements from before at approx.
-2316 µM.
-So for now, it should be fine.
--->
-
-<!-- #### **CRM measurements** -->
-
-<!-- The calibration of the sensor is made against a CRM standard from A.
-Dickson.
-We run a standard on the analyser as a regular measurement (measurement mode).
-Result sof calibrations are shown on the following plot.Dashed lines represent the theoritical value of AT (CRM) and hard lines represent CRM measured AT by the instrument.
--->
-
-<!-- ```{r CRM measurements, echo=FALSE, warning=FALSE, message=FALSE, out.width="80%",fig.show='hold', fig.align="center"} -->
-<!-- calib_analyser <-  read.table(paste0(path, "fb_data/Calibration_TA/TA_#1215/measure_CRM_TA.txt"), header = T, dec = ".", as.is = T, sep = ",", fill = TRUE) -->
-
-<!-- # To make the mean  -->
-<!-- # Keep dates as Character to plot without date gaps. -->
-<!-- calib_analyser3 <- calib_analyser %>% -->
-<!--   dplyr::filter(analyser == "TA3")  -->
-<!-- meanTA3 <- calib_analyser3 %>%  -->
-<!--   group_by(day) %>%  -->
-<!--   summarise (meanTA = mean(TA)) -->
-
-<!-- melt_calib <- melt(calib_analyser, id.vars=c("analyser", "TA_theo", "datetime", "CRM"), measure.vars=c("TA")) -->
-<!-- calib_p <- ggplot()+  -->
-<!--           geom_point(data= melt_calib, aes(x=datetime, y=value, color=factor(CRM), shape= factor(analyser)) , size=3) + -->
-<!--           scale_color_manual(values=c("blue","red"))+ -->
-<!--          # set dashed lines for theoritical CRM -->
-<!--           geom_segment(aes(x=1,xend=20,y=2226.16,yend=2226.16), linetype="dashed", color="blue")+ -->
-<!--           annotate("text", x = 11, y = 2228, label = "Batch #145 = 2226.16", color="blue")+ -->
-<!--           geom_segment(aes(x=20,xend=23,y=2213.59,yend=2213.59), linetype="dashed", color="red")+ -->
-<!--           annotate("text", x = 15.5, y = 2213.59, label = "Batch #159 = 2213.59", color="red")+ -->
-<!--         # set hard lines for measured CRM -->
-<!--           geom_segment(aes(x=1,xend=5,y=2254,yend=2254), color="blue") + -->
-<!--           annotate("text", x = 3, y = 2249, label = "2254", color="blue")+ -->
-<!--           geom_segment(aes(x=6,xend=10,y=2251.6,yend=2251.6), color="blue") + -->
-<!--           annotate("text", x = 8, y = 2247, label = "2251.6", color="blue")+ -->
-<!--           geom_segment(aes(x=11,xend=15,y=2190.4,yend=2190.4), color="blue")+ -->
-<!--           annotate("text", x = 14, y = 2195, label = "2190.4", color="blue")+ -->
-<!--           geom_segment(aes(x=16,xend=20,y=2203.5,yend=2203.5), color="blue")+ -->
-<!--           annotate("text", x = 18, y = 2200, label = "2203.5", color="blue")+ -->
-<!--           geom_segment(aes(x=21,xend=23,y=2224.20,yend=2224.20), color="red")+ -->
-<!--           annotate("text", x = 22, y = 2230, label = "2224.2", color="red") + -->
-<!--   theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1))+  -->
-<!--   labs(title= "",y=expression(paste("Total alkalinity (µmoles.",kg^-1,")")), x="Date", color= "CRM",shape= "Deployed instrument") -->
-
-<!-- ggsave("figures/TA_calibration_CRM.png", calib_p, units="cm") -->
-<!-- print(calib_p) -->
-<!-- ``` -->
-
-<!-- #### **Discrete samples ("references")**  -->
-
-<!-- On 2018-04-19, Steffen sent his answer concerning the drift correction during the period February 2016 to March 2017.
-Within this one year period, the analyser was running, except the first week of May 2016.
-Discrete samples were collected and 3 CRMs were measured which was deemed not enough (see below).
-He suggested to base the correction on the AT of discrete ("reference") samples.
--->
-
-<!-- > "I chose the discrete reference samples due to the fact that those cover the entire working range including time, salinity and also provide a broader data basis for this kind of correction.
-Also, when looking at the uncertainty below, I fear that the three CRM measurements over 5 month are not sufficient enough for such a drift determination." -->
-
-<!-- A linear regression was performed based on the difference between the measured (analyzer) and discrete samples.
-Discrete samples were matched with the AT measured by the analyser.
-If there is no measurement coincident with a discrete sample, a linear interpolation was made between the two data surrounding the discrete sample data.
-The differences between the measured (analyzer) and analysed ("reference") data was plotted as a function of time.
--->
-
-<!-- This approach was performed: -->
-
-<!--   - on the same period than in Steffen email's (**First period**, 2016-02-23 to 2017-02-09) -->
-<!--   - and during the **third period**, with the new analyzer (2018-01-07 to 2018-06-20) -->
-
-<!-- ##### **First period**  -->
-
-<!-- ```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"} -->
-<!-- #Interpolation of continuous sensor data to match a maximum of reference data. -->
-<!-- TAinterp_all <-approx(d_all$datetime, d_all$AT, xout=d_all$datetime, method="linear", rule=2) -->
-<!-- names(TAinterp_all) <- c("datetime", "AT_interp") -->
-<!-- TAinterp_all <- as.data.frame(TAinterp_all) -->
-<!-- d_all$AT_interp <- TAinterp_all$AT_interp -->
-
-<!-- # create a column with difference between sensor and ref -->
-<!-- d_all <- d_all%>% -->
-<!--   dplyr::mutate(diff_ta =  at-AT_interp ) -->
-<!-- # create colum with instrument number -->
-<!-- d_all <- d_all %>% -->
-<!--   dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1", -->
-<!--                             ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2", -->
-<!--                             ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3", -->
-<!--                             ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4", -->
-<!--                             ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5", -->
-<!--                             ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0"))))))) -->
-
-<!-- #remove outliers -->
-<!-- calib_ta_first <- d_all%>% -->
-<!--   dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta,TA_period)%>% -->
-<!--   dplyr::filter(TA_period =="TA1" & !is.na(at)) -->
-<!--   #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 ) -->
-<!-- # & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at)) -->
-
-<!-- # Parameters of regression -->
-<!-- fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime) -->
-<!-- at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6) -->
-<!-- at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2) -->
-<!-- at_intercept1 <- round(fit$coefficients[[1]], digits= 2) -->
-<!-- ``` -->
-
-<!-- The slope is: `r #at_slope_TA1` x 3600 x 24 x 365.24 = `r #at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red. -->
-
-<!-- ```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"} -->
-<!--  # Plot of regression -->
-<!--  p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + -->
-<!--      geom_point() + geom_smooth(method='lm', se=FALSE)+ -->
-<!--      geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  + -->
-<!--    geom_hline(yintercept = 0, linetype="dashed" )+ -->
-<!--    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5), -->
-<!--                       "Intercept =",signif(fit$coef[[1]],5 ), -->
-<!--                       "Slope =",signif(fit$coef[[2]], 5), -->
-<!--                       "P =",signif(summary(fit)$coef[2,4], 5))) + -->
-<!--    ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC") -->
-<!--  print(p) -->
-<!--  ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm") -->
-<!-- ``` -->
-
-<!-- ##### **Third period** -->
-
-<!-- ```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"} -->
-
-<!--  #remove outliers and remove period without TA measurements -->
-<!--  calib_ta_third <- d_all%>% -->
-<!--    dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta, TA_period)%>% -->
-<!--    dplyr::filter(TA_period == "TA3" & !is.na(at)) -->
-
-<!--  # Parameters of regression -->
-<!--  fit <- lm( data=calib_ta_third, diff_ta ~ datetime) -->
-<!--  at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8) -->
-<!--  at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2) -->
-<!--  at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici. -->
-<!-- ``` -->
-
-<!-- The slope is in days: `r #at_slope_TA3` x 3600 x 24 x 365.24 = `r #at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers. -->
-
-<!-- ```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"} -->
-<!-- # # Plot of regression -->
-<!--  p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ -->
-<!--      geom_point() + geom_smooth(method='lm', se=FALSE)+ -->
-<!--      #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  + -->
-<!--     geom_hline(yintercept = 0, linetype="dashed" )+ -->
-<!--    geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") + -->
-<!--    #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+ -->
-<!--    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5), -->
-<!--                       "Intercept =",signif(fit$coef[[1]],5 ), -->
-<!--                       " Slope =",signif(fit$coef[[2]], 5), -->
-<!--                       " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + -->
-<!--    scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC") -->
-<!--  print(p) -->
-<!--  ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm") -->
-<!-- ``` -->
-
-<!-- ##### **Second period** -->
-
-<!-- ```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'} -->
-
-<!-- #remove outliers and remove period without TA measurements -->
-<!-- calib_ta_second <- d_all%>% -->
-<!--   dplyr::select(datetime, closest_datetime, AT, AT_interp, at, diff_ta, TA_period)%>% -->
-<!--   dplyr::filter(TA_period == "TA2" & !is.na(at)) -->
-
-<!-- mean_offset <- mean(calib_ta_second$diff_ta) -->
-
-<!-- ```  -->
-
-<!-- For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r #mean_offset` µmoles.kg~-1~) was added to TA value as an offset. -->
-
-<!-- #### **Final TA corrected data (Regression)** -->
-
-<!-- The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition. -->
-<!-- It is clear that these corrected data (in green) cannot be used for periods 1 to 3.
-The jury is still out for period 4.
-The issue of salinity must be clarified before an assessment can be made.
--->
-
-<!-- ```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'} -->
-<!-- # Correction for the 3 periods is apply -->
-<!-- d_all <- d_all%>% -->
-<!--   dplyr::mutate(datetime_reg = as.numeric(datetime), -->
-<!--                 at_intercept = ifelse(TA_period == "TA1", at_intercept1, -->
-<!--                                ifelse(TA_period == "TA3", at_intercept3, NA)), -->
-<!--                 at_slope = ifelse(TA_period == "TA1", at_slope_TA1, -->
-<!--                            ifelse(TA_period == "TA3", at_slope_TA3, NA)) -->
-<!--                 ) -->
-
-<!-- d_all <- d_all%>% -->
-<!--  dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT + (d_all$datetime_reg * d_all$at_slope + at_intercept)), -->
-<!--                                         ifelse(TA_period == "TA2", (AT + mean_offset), -->
-<!--                                         ifelse(TA_period == "TA3", (AT + (datetime_reg * at_slope)+ at_intercept), NA)))) -->
-
-<!-- at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at,TA_reg_corrected) -->
-<!-- at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime) -->
-<!-- dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>% -->
-<!--    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>% -->
-<!--   dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>% -->
-<!--   dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>% -->
-<!--   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% -->
-<!--   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="UTC"), "HCl Changed", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="UTC"), "BCG Changed", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="UTC"), "Calibration 1", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="UTC"), "Calibration 2", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="UTC"), "TA analyser changed", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="UTC"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="UTC"), "Calibration mode - CRM", labelLoc = "bottom") %>% -->
-<!--   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>% -->
-<!--   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>% -->
-<!--   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>% -->
-<!--   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>% -->
-<!--   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>% -->
-<!--   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>% -->
-<!--   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>% -->
-<!--   dyAxis("y",valueRange = c(1600, 2650)) %>% -->
-<!--   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
-<!--   dyOptions( strokeWidth= 0) %>% -->
-<!--   dyLegend(show = "follow")   %>% -->
-<!--   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>% -->
-<!--     dyRangeSelector(height = 30, dateWindow= NULL) -->
-
-<!-- ``` -->
-
-### **Discrete total alkalinity (reference) vs salinity relationship**
-
-In the previous part, missing TA were interpolated with a linear model.
-This does not reflect the natural variability of TA.
-For this reason, missing TA is now calculated from salinity data by making a relationship between the same reference TA samples as in the previous part and salinity data.
-
-```{r Discrete salinity vs TA, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="100%"}
-d_all_at_discrete <- d_all %>% #  To remove an outlier in red
-  dplyr::select(datetime, monthd,closest_datetime, at, sal_mix)
-
-fit <- lm(data = d_all_at_discrete, at ~ sal_mix)
-slope_s_at <- fit$coefficients[[2]]
-intercept_s_at <- fit$coefficients[[1]]
-at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at, label = monthd))+
+#1m
+fit <- lm(data = d_all, par_insitu_profile_1m ~ sal_insitu_ctd_1m)
+p1 <- ggplot(d_all,aes(x=sal_insitu_ctd_1m, y= par_insitu_profile_1m, label = monthd))+
   geom_text( aes(color=factor(monthd))) +
   scale_color_discrete(guide="none")+
-    labs(x="Salinity", y="Discrete AT", color = "Months")  +
+    labs(x="Salinity CTD 1 m", y="PAR Profile 1 m", color = "Months")  +
     stat_smooth(method = "lm", col = "black") +
@@
                        ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
-  theme_bw() +
-  theme(aspect.ratio=1,
+  theme_bw() + theme(aspect.ratio=1,
         axis.text=element_text(size=7),
@@
 
-# Salinity is a predictor of AT -> using the regression defined above
-d_all$at_calc <- slope_s_at * d_all$sal_mix + intercept_s_at
+#3m
+fit <- lm(data = d_all, par_insitu_profile_3m ~ sal_insitu_ctd_3m)
+p3 <- ggplot(d_all,aes(x=sal_insitu_ctd_3m, y= par_insitu_profile_3m, label = monthd))+
+  geom_text( aes(color=factor(monthd))) +
+  scale_color_discrete(guide="none")+
+    labs(x="Salinity CTD 3 m", y="PAR Profile 3 m", color = "Months")  +
+    stat_smooth(method = "lm", col = "black") +
+    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
+                       ";\nSlope =",signif(fit$coef[[2]], 5),
+                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
+                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
+  theme_bw() + theme(aspect.ratio=1,
+        axis.text=element_text(size=7),
+        axis.title.y= element_text(size =7),
+        axis.title.x= element_text(size =7),
+        plot.margin = unit(c(0.5,1,1,1), "cm"),
+        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
+#5m
+fit <- lm(data = d_all, par_insitu_profile_5m ~ sal_insitu_ctd_5m)
+p5 <- ggplot(d_all,aes(x=sal_insitu_ctd_5m, y= par_insitu_profile_5m, label = monthd))+
+  geom_text( aes(color=factor(monthd))) +
+  scale_color_discrete(guide="none")+
+    labs(x="Salinity CTD 5 m", y="PAR Profile 5 m", color = "Months")  +
+    stat_smooth(method = "lm", col = "black") +
+    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
+                       ";\nSlope =",signif(fit$coef[[2]], 5),
+                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
+                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
+  theme_bw() + theme(aspect.ratio=1,
+        axis.text=element_text(size=7),
+        axis.title.y= element_text(size =7),
+        axis.title.x= element_text(size =7),
+        plot.margin = unit(c(0.5,1,1,1), "cm"),
+        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
+#7m
+fit <- lm(data = d_all, par_insitu_profile_7m ~ sal_insitu_ctd_7m)
+p7 <- ggplot(d_all,aes(x=sal_insitu_ctd_7m, y= par_insitu_profile_7m, label = monthd))+
+  geom_text( aes(color=factor(monthd))) +
+  scale_color_discrete(guide="none")+
+    labs(x="Salinity CTD 7 m", y="PAR Profile 7 m", color = "Months")  +
+    stat_smooth(method = "lm", col = "black") +
+    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
+                       ";\nSlope =",signif(fit$coef[[2]], 5),
+                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
+                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
+  theme_bw() + theme(aspect.ratio=1,
+        axis.text=element_text(size=7),
+        axis.title.y= element_text(size =7),
+        axis.title.x= element_text(size =7),
+        plot.margin = unit(c(0.5,1,1,1), "cm"),
+        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
+#9m
+fit <- lm(data = d_all, par_insitu_profile_9m ~ sal_insitu_ctd_9m)
+p9 <- ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= par_insitu_profile_9m, label = monthd))+
+  geom_text( aes(color=factor(monthd))) +
+  scale_color_discrete(guide="none")+
+    labs(x="Salinity CTD 9 m", y="PAR Profile 9 m", color = "Months")  +
+    stat_smooth(method = "lm", col = "black") +
+    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
+                       ";\nSlope =",signif(fit$coef[[2]], 5),
+                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
+                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
+  theme_bw() + theme(aspect.ratio=1,
+        axis.text=element_text(size=7),
+        axis.title.y= element_text(size =7),
+        axis.title.x= element_text(size =7),
+        plot.margin = unit(c(0.5,1,1,1), "cm"),
+        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
+
+print(p1)
+print(p3)
+print(p5)
+print(p7)
+print(p9) 
 ```
-
-The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r #round(summary(fit)$r.squared, digits=2)`.
-Need to compare with other relationships from the literature.
-
-```{r plot Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
- # PLOT
- print(at_s)
-```
-
-#### **Final TA re-calculated data (Salinity relationship)**
-
-```{r Plot TA calc TA meas, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'}
-TAevents <- as.POSIXct(c("2016-02-26 00:00:00", "2017-02-09 12:00:00", "2017-02-09 12:00:00", "2017-03-10 12:00:00",
-              "2018-01-07 00:00:00", "2018-06-20 00:00:00", "2018-07-31 00:00:00", "2018-10-30 18:00:00",
-              "2018-10-31 09:00:00", "2019-01-16 09:00:00", "2019-01-26 13:25:00", format(Sys.Date(),
-              "%Y-%m-%d %H:%M:%S")))
-at_contros_calc_xts <- dplyr::select(d_all, datetime, at_calc, at)
-at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
-dygraph(at_contros_calc_xts, group = "awipev", main="TA, calculated from sal_mix (blue) and reference (red)", ylab="Total alkalinity") %>%
-  #dySeries("AT", label= "Raw TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
-  dySeries("at_calc", label="at_calc",color = "blue", strokeWidth = 0, pointSize=2) %>%
-  dySeries("at", label="at (ref)",color = "red", strokeWidth = 0, pointSize=4) %>%
-  dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="UTC"), "HCl Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="UTC"), "BCG Changed", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="UTC"), "Calibration 1", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="UTC"), "Calibration 2", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="UTC"), "TA analyser changed", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="UTC"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>%
-  dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>%
-  dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="UTC"), "Calibration mode - CRM", labelLoc = "bottom") %>%
-  #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-  dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>%
-  dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>%
-  dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>%
-  dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>%
-  dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>%
-  #dyAxis("y",valueRange = c(2000, 2650)) %>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions( strokeWidth= 0) %>%
-  dyLegend(show = "follow")   %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-```
-
-There are a lot of outliers in the 4th period (since the new analyzer was set up in Nov. 2018). We use the desplike function to remove them.
-
-<!-- #### **TA since November 2018 (final installation)** -->
-<!-- ```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'} -->
-<!--  # select subset of data and remove obvious outliers -->
-<!--  at_nov_2018 <- -->
-<!--   dplyr::select(d_all, datetime, at_calc, AT, at) %>% -->
-<!--   filter(datetime > "2018-11-01", AT > 2250) -->
-<!-- #despike -->
-<!-- at_nov_2018 <- mutate(at_nov_2018, AT_despike = despike(AT, reference= "median", n=0.5, k=10, replace="NA")) -->
-<!-- #plot -->
-<!-- at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) + -->
-<!--   geom_point(aes(y=AT, colour = "before"), size =3) + -->
-<!--   geom_point(aes(y=AT_despike, colour = "after"), size = 2) + -->
-<!--   labs(x = "Time", y = "Total alkalinity", color = "despike") -->
-<!-- print(at_datetime) -->
-
-<!-- at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_despike != "NA") -->
-<!-- titre <- "Contros AT vs Calculated AT" -->
-<!--  fit <- lmodel2(data = at_nov_2018_no_NA, AT_despike ~ at_calc, nperm = 99) -->
-<!-- ggreg2(fit, x = "at_calc", y = "AT_despike") -->
-
-<!-- ``` -->
-
-## *p*CO~2~
-The HydroC CO~2~ FT sensor (S/N: CO2FT-0215-001) was bought from Contros (Germany) in February 2015.
-It was deployed in the FerryBox with other sensors since July 2015, the 20th.
-A spare sensor (S/N: CO2FT-0515-001) was also bought in March 2015 and carried to Ny-Alesund to replace the first one in case of calibration or problem.
-Both sensors were set on a cycle according to informations given by Contros in March 2015 (c.kirbach@contros.eu):
-
-30 min warm up --> (3 min Zeroing + 15 min Flushing + 702 minutes Measuring) --> (3 + 15 + 702)...
-
-  - **Warm-up**: running without sending data. Done once, after the sensor is turned on. Time can vary depending on T water and power supply.
-  - **Flushing**: running normally.
-Phase of equilibration that depends on the sensor configuration and the environment conditions.
-Warmer the water is and larger the flow is in front of the membrane, faster will be the response time and shorter will be the flush time.
-Recovery data of the sensor signal from the zeroing interval happen in this time.
-During this step the flush flag is set to “1” for simplifier extraction of the flush values.
-  - **Measuring**: running normally and all other flags are on “0”. Sensor is fully equilibrated and T is stable.
-
-During those steps (except zeroing) the sensor runs normally.
-Equilibration between the gas inside the sensor and the dissolved gas in ambient water takes place.
-Gas is led to NDIR unit while T control is running.
-
-### **Corrected Contros vs calculated *p*CO~2~ data**
-
-```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
-title <- "Contros vs calculated pCO2"
-fit <- lmodel2(data = d_all,  pco2_corr ~ pco2_calc_fb , nperm = 99)
-
-p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_corr, label = monthd))+
-   geom_text(aes(color = factor(monthd)))+
-  scale_color_discrete(guide="none")+
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
-  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()  
-```
-The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
-```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-print(p) # pco2_calc_fb_pco2_corr_text
-```
-
-### **Final *p*CO~2~ data**
-
-```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-pco2_contros_xts <-
-  dplyr::select(d_all, datetime, pco2_calc_fb, pco2_corr)
-pco2_contros_xts <-
-  as.xts(pco2_contros_xts, order.by = d_all$datetime)
-dygraph(pco2_contros_xts,
-        group = "awipev",
-        main = "<i>p</i>CO<sub>2</sub>",
-        ylab = "<i>p</i>CO<sub>2</sub>") %>%
-  dySeries(
-    "pco2_corr",
-    label = "Corrected pCO2",
-    color =  RColorBrewer::brewer.pal(3, "Dark2")[1],
-    strokeWidth = 0,
-    pointSize = 2
-  ) %>%
-  dySeries(
-    "pco2_calc_fb",
-    label = "pco2_calc_fb",
-    color = "red",
-    strokeWidth = 0,
-    pointSize = 4
-  ) %>%
-  dyEvent(
-    as.POSIXct("2016-02-28 12:00:00", tz = "UTC"),
-    "CO2FT-0515-001 installed",
-    labelLoc = "bottom",
-    color = "red"
-  ) %>%
-  dyEvent(
-    as.POSIXct("2017-02-07 12:00:00", tz = "UTC"),
-    "CO2FT-0215-001 installed",
-    labelLoc = "bottom",
-    color = "red"
-  ) %>%
-  dyEvent(
-    as.POSIXct("2018-04-16 12:00:00", tz = "UTC"),
-    "CO2FT-0515-001 installed",
-    labelLoc = "bottom",
-    color = "red"
-  ) %>%
-  dyEvent(
-    as.POSIXct("2018-10-31 15:00:00", tz = "UTC"),
-    "CO2FT-0215-001 installed",
-    labelLoc = "bottom",
-    color = "red"
-  ) %>%
-  dyEvent(
-    as.POSIXct("2019-09-03 15:00:00", tz = "UTC"),
-    "CO2FT-0515-001 installed",
-    labelLoc = "bottom",
-    color = "red"
-  ) %>%
-  dyHighlight(
-    highlightCircleSize = 8,
-    highlightSeriesBackgroundAlpha = 0.5,
-    hideOnMouseOut = TRUE
-  ) %>%
-  dyLegend(show = "follow")   %>%
-  dyOptions(
-    drawGrid = TRUE,
-    drawPoints = TRUE,
-    pointSize = c(1, 8, 1),
-    useDataTimezone = TRUE
-  ) %>%
-  dyRangeSelector(height = 30, dateWindow = NULL)
-
-# now remove outliers
-d_all <- d_all %>%
-  dplyr::mutate(
-    pco2_corr = case_when(
-      date > as.Date("2016-04-01") &
-        date <  as.Date("2017-02-05") & pco2_corr > 400 ~ NA_real_,
-      #date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
-      date > as.Date("2017-08-01") &
-        date <  as.Date("2017-09-30") & pco2_corr > 300 ~ NA_real_,
-      #date == as.Date("2017-03-22") & sal_mix < 34 ~ NA_real_,
-      TRUE ~ pco2_corr
-    )
-  )
-```
-
-## pH seaFET
-
-pH is measured continuously by an autonomous seaFET pH sensor.
-Because of issue, measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17.
-*Note that the pH sensor is mounted on a profiling structure.
-Here, only seaFET data recorded with a depth > 8 m are taken in consideration.* pH calibration is based on monthly discrete samples that are analysed with spectrophotometric method in Villefranche by Samir Alliouane.
-When it is not possible to sample at the vicinity of the sensor for practice reasons (in winter), sampling is done in the harbour and is not taken in consideration for calibration for spatial reasons.
-
-Calibration was done following the methods and code described in Bresnahan et al.
-(2014) and adapted to use in R (seacarb package).
-Deployment periods are difined so that one spectrophotometric measurement is in the middle of a defined period of calibration (shaded colors in the plot).
-
-Within this deployment period, calibration is made with E0 calculation (first plot) and final corrected pH is calculated (second plot).
-To allow calibration, one spectrophotometric pH measurement must match: seaFET voltage, in situ temperature (SBE38) and salinity.
-When one of these parameters is missing for any reasons (Ferrybox maintenance, breakdown...), the gap is filled with a mean of the 4 previous or next hours when available.
-If the pH spectrophotometric measurement is too far from the available values, the calibration is not performed (environemental variability reasons).
-The SBE38 insitu temperature and seaFET temperature are very similar (slope = 0.992, r2 = 0.96, see tab "Temperatures").
-These two temperatures were used interchangeably if one is missing.
-
-Missing data which could be estimated on : 2017-08-24, 2017-09-28, 2019-09-13 x 2.
-Missing data which could not be estimated on : 2018-04-16 , 2018-12-14, 2019-01-18.
-
-We decided to change the calculation of E0.
-Before E0 was calculated for each pH spectro measurements.
-Now, EO is calculated making a mean of several E0 that come from one deployment period (sensor in the water for several months).
-
-### **seaFET calibration constant E0**
-
-Plots of E0int25 and E0ext25 returned by the function "pHCalib" for each period of deployement are shown below.
-
-```{r seaFET calibration sf_calib, echo=FALSE, message= FALSE, warning=FALSE, out.width= "60%"}
-
-# # We decided to calibrate pH data within each pH spectro measurement.
-# # Thus, each pH spectro is taken as one calibration periode. 
-# # We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
-# sfPeriod <- d_all%>%
-#   dplyr::select(datetime, ph_s_sf_temp_insi)%>%
-#   dplyr::filter(!is.na(ph_s_sf_temp_insi))
-# # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
-# sfPeriod <- sfPeriod%>%
-# dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
-# 
-# sfPeriod <-  sfPeriod %>%
-#   dplyr::arrange(datetime) %>%
-#   dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
-#   dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
-# 
-# #put interval in a list with the start date of seaFET measurements
-# sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
-# #Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
-# # This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
-# sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
-# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-# # sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
-# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-# # sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
-# 
-# #sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
-# # set deployment period between 2 spectro measurements.
-
-# # add here the new periods sfinterv[..]
-# d_all <- d_all %>%
-#   dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
-#                                 ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
-#                                 ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
-#                                 ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
-#                                 ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
-#                                 ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
-#                                 ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
-#                                 ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
-#                                 ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
-#                                 ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
-#                                 ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
-#                                  ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
-#                                  ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
-#                                  ifelse(datetime >= sfinterv[14] & datetime <= sfinterv[15], 14,
-#                                  ifelse(datetime >= sfinterv[15] & datetime <= sfinterv[16], 15,
-#                                  ifelse(datetime >= sfinterv[16] & datetime <= sfinterv[17], 16,
-#                                  ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
-#                                 ifelse(datetime >= sfinterv[18] & datetime <= sfinterv[19], 18,
-#                                 ifelse(datetime >= sfinterv[19] & datetime <= sfinterv[20], 19,
-#                                 ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
-#                                 ifelse(datetime >= sfinterv[21] & datetime <= sfinterv[22], 21,
-#                                 #ifelse(datetime >= sfinterv[22] & datetime <= sfinterv[23], 22,
-#                                 #ifelse(datetime >= sfinterv[23] & datetime <= sfinterv[24], 23,
-#                                 #ifelse(datetime >= sfinterv[24] & datetime <= sfinterv[25], 24,
-#                                 #ifelse(datetime >= sfinterv[25] & datetime <= sfinterv[26], 25,
-#                                 ifelse(datetime >= sfinterv[22] , 22,NA )))))))))))))))))))))))
-
-# set deployment period when seaFET is in/out of water
-sfinterv <- as.POSIXct(c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00"))
-
-# add here the new periods sfinterv[..]
-d_all <- d_all %>%
-  dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01,
-                                ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02,
-                                ifelse(datetime >= sfinterv[3], 03, NA ))))
-
-# pco2_contros_xts <-
-#   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_insi)
-# pco2_contros_xts <-
-#   as.xts(pco2_contros_xts, order.by = d_all$datetime)
-# dygraph(pco2_contros_xts,
-#         group = "awipev",
-#         main = "<i>p</i>CO<sub>2</sub>",
-#         ylab = "<i>p</i>CO<sub>2</sub>") %>%
-#   dySeries(
-#     axis = "y2",
-#     "voltINT",
-#     label = "voltINT",
-#     color =  RColorBrewer::brewer.pal(5, "Dark2")[1],
-#     strokeWidth = 0,
-#     pointSize = 2
-#   ) %>%
-#   dySeries(axis="y2",
-#     "voltEXT",
-#     label = "voltEXT",
-#     color =  RColorBrewer::brewer.pal(5, "Dark2")[2],
-#     strokeWidth = 0,
-#     pointSize = 2
-#   ) %>%
-#    dySeries(
-#     "temp_insitu_ctd",
-#     label = "temp_insitu_ctd",
-#     color =  RColorBrewer::brewer.pal(5, "Dark2")[3],
-#     strokeWidth = 0,
-#     pointSize = 2
-#   ) %>%
-#    dySeries(
-#     "sal_fb",
-#     label = "sal_fb",
-#     color =  RColorBrewer::brewer.pal(5, "Dark2")[4],
-#     strokeWidth = 0,
-#     pointSize = 2
-#   ) %>%
-#    dySeries(
-#     "ph_s_sf_temp_insi",
-#     label = "ph_s_sf_temp_insi",
-#     color =  RColorBrewer::brewer.pal(5, "Dark2")[5],
-#     strokeWidth = 0,
-#     pointSize = 4
-#   ) %>%
-#   dyHighlight(
-#     highlightCircleSize = 8,
-#     highlightSeriesBackgroundAlpha = 0.5,
-#     hideOnMouseOut = TRUE
-#   ) %>%
-#   dyLegend(show = "follow")   %>%
-#   dyAxis("y2",valueRange = c(-2,2))%>%
-#   dyOptions(
-#     drawGrid = TRUE,
-#     drawPoints = TRUE,
-#     pointSize = c(1, 8, 1),
-#     useDataTimezone = TRUE
-#   ) %>%
-#   dyRangeSelector(height = 30, dateWindow = NULL)
-
-# To make sf calibration against pH spectro, we need: sal - T insi - voltINT/EXT . If we missed one of these parameters, calibration will not run
-# Here we try to fill the gap when it is possible: make a mean with 4 previous/next hours available in the time serie. 
-# If the pH spectro is too far from a needed value, we decided to skip it for the calibration.
-# we highlighted 7 pH spectro that dont match one of these parameters : 2017-08-24 14:00:00 - 2017-09-28 13:00:00 - 2018-04-16 07:00:00 - 2018-12-14 09:00:00 - 2019-01-18 09:00:00 - 2019-09-13 08:00:00 - 2019-09-13 13:00:00
-# (1) Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04,
-# (2) removed from 2018-01-08 to 2018-02-02
-# (3) outliers removed
-# (1)
-d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
-                        d_all$datetime <= as.POSIXct("2018-01-08") &
-                        d_all$phINT < 8.04, NA, d_all$phINT)
-d_all$phEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
-                       d_all$datetime <= as.POSIXct("2018-01-08") &
-                       d_all$phEXT < 8.04, NA, d_all$phEXT) 
-d_all$voltINT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
-                         d_all$datetime <= as.POSIXct("2018-01-08") &
-                         d_all$voltINT < -0.9439, NA, d_all$voltINT) 
-d_all$voltEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
-                         d_all$datetime <= as.POSIXct("2018-01-08") &
-                         d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
-# (2)
-d_all$voltINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
-                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"), 
-                        NA, d_all$voltINT)
-d_all$voltEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
-                          d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
-                        NA, d_all$voltEXT)
-d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
-                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
-                      NA, d_all$phINT)
-d_all$phEXT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
-                        d_all$datetime <= as.POSIXct("2018-02-02 09:00:00"),
-                      NA, d_all$phEXT)
-# (3)
-d_all$voltINT <- ifelse(d_all$datetime == as.POSIXct("2017-11-02 21:00:00") |
-                          d_all$datetime == as.POSIXct("2018-04-18 14:00:00"),
-                        NA, d_all$voltINT)
-
-# For this spec pH, some volt int and T seaF data are missing so we use the closest data
-zz <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2017-08-24 19:00:00") &
-      datetime <= as.POSIXct("2017-08-24 22:00:00")
-  )
-mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
-d_all <- d_all %>%
-  dplyr::mutate(voltINT = ifelse(
-    datetime == as.POSIXct("2017-08-24 13:00:00"),
-    mean_voltINT_4h,
-    voltINT
-  ))
-zz <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2017-08-24 19:00:00") &
-      datetime <= as.POSIXct("2017-08-24 22:00:00")
-  )
-mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
-d_all <- d_all %>%
-  dplyr::mutate(voltEXT = ifelse(
-    datetime == as.POSIXct("2017-08-24 13:00:00"),
-    mean_voltEXT_4h,
-    voltEXT
-  ))
-zz <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2017-08-24 19:00:00") &
-      datetime <= as.POSIXct("2017-08-24 22:00:00")
-  )
-mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
-d_all <- d_all %>%
-  dplyr::mutate(temp_mix = ifelse(
-    datetime == as.POSIXct("2017-08-24 13:00:00"),
-    mean_TseaF_4h,
-    temp_mix
-  ))
-
-# For this spec pH, some volt int and T seaF data are missing so we use the closest data
-zz <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2017-09-28 15:00:00") &
-      datetime <= as.POSIXct("2017-09-28 18:00:00")
-  )
-mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
-d_all <- d_all %>%
-  dplyr::mutate(voltINT = ifelse(
-    datetime == as.POSIXct("2017-09-28 13:00:00"),
-    mean_voltINT_4h,
-    voltINT
-  ))
-zz <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2017-09-28 15:00:00") &
-      datetime <= as.POSIXct("2017-09-28 18:00:00")
-  )
-mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
-d_all <- d_all %>%
-  dplyr::mutate(voltEXT = ifelse(
-    datetime == as.POSIXct("2017-09-28 13:00:00"),
-    mean_voltEXT_4h,
-    voltEXT
-  ))
-
-# For this spec pH, some volt int and T seaF data are missing so we use the closest data
-zz <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2019-09-13 04:00:00") &
-      datetime <= as.POSIXct("2019-09-13 07:00:00")
-  )
-mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
-d_all <- d_all %>%
-  dplyr::mutate(voltINT = ifelse(
-    datetime == as.POSIXct("2019-09-13 13:00:00"),
-    mean_voltINT_4h,
-    voltINT
-  ))
-d_all <- d_all %>%
-  dplyr::mutate(voltINT = ifelse(
-    datetime == as.POSIXct("2019-09-13 08:00:00"),
-    mean_voltINT_4h,
-    voltINT
-  ))
-zz <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2019-09-13 04:00:00") &
-      datetime <= as.POSIXct("2019-09-13 07:00:00")
-  )
-mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
-d_all <- d_all %>%
-  dplyr::mutate(voltEXT = ifelse(
-    datetime == as.POSIXct("2019-09-13 08:00:00"),
-    mean_voltEXT_4h,
-    voltEXT
-  ))
-
-# For this spec pH, some volt int and T seaF data are missing so we use the closest data
-zz <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2019-09-13 11:00:00") &
-      datetime <= as.POSIXct("2019-09-13 12:00:00")
-  )
-mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
-d_all <- d_all %>%
-  dplyr::mutate(voltINT = ifelse(
-    datetime == as.POSIXct("2019-09-13 13:00:00"),
-    mean_voltINT_4h,
-    voltINT
-  ))
-zz <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2019-09-13 11:00:00") &
-      datetime <= as.POSIXct("2019-09-13 12:00:00")
-  )
-mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
-d_all <- d_all %>%
-  dplyr::mutate(voltEXT = ifelse(
-    datetime == as.POSIXct("2019-09-13 13:00:00"),
-    mean_voltEXT_4h,
-    voltEXT
-  ))
-zz <- d_all %>%
-  dplyr::filter(
-    datetime >= as.POSIXct("2019-09-13 11:00:00") &
-      datetime <= as.POSIXct("2019-09-13 12:00:00")
-  )
-mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
-d_all <- d_all %>%
-  dplyr::mutate(temp_mix = ifelse(
-    datetime == as.POSIXct("2019-09-13 13:00:00"),
-    mean_TseaF_4h,
-    temp_mix
-  ))
-
-#interpolation of salinity during gaps
-salinterp <-
-  approx(
-    d_all$datetime,
-    d_all$sal_insitu_ctd,
-    xout = d_all$datetime,
-    method = "linear",
-    rule = 2
-  )
-names(salinterp) <- c("datetime", "sal_insitu_ctd_interp")
-salinterp <- as.data.frame(salinterp)
-d_all$sal_insitu_ctd_interp <- salinterp$sal_insitu_ctd_interp
-
-d_all <- d_all %>%
-  dplyr::mutate(
-    sal_insitu_ctd_interp =  ifelse(
-      datetime > as.POSIXct("2018-04-16 07:00:00") &
-        datetime < as.POSIXct("2018-04-24 22:00:00"),
-      sal_insitu_ctd_interp,
-      sal_insitu_ctd
-    )
-  )
-
-####
-## calculation of E0INT25/E0EXT25 ##
-##     new sf_calib function      ##
-####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd)
-# put number of deployment 
-calib_spectro$deployment_sf <- d_all$deployment_sf
-
-# make the mean of E0 by period of deployement
-calib_spectro <- group_by(calib_spectro, deployment_sf) %>%
-  summarise(E0int25 = mean(E0int25, na.rm = TRUE),
-            E0ext25 = mean(E0ext25, na.rm = TRUE) 
-            )
-names(calib_spectro) <- c("deployment_sf", "E0int25_sf", "E0ext25_sf")
-
-# add E0 mean to seaFET data per deployment
-d_all <-left_join(d_all, calib_spectro,by="deployment_sf" )
-
-#### plot
-kk <- melt(calib_spectro, id.vars="deployment_sf")
-p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
-  facet_grid(variable~., scales="free_y") + theme_bw() +
-  scale_colour_discrete(guide="none")
-print(p_calib)
-```
-
-### **seaFET pHT calibrated**
-pH is measured continuously by an autonomous seaFET pH sensor.
-Final calibrated seaFET pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
-Calibration was done following the methods and code described in Bresnahan *et al.* (2014) using seaFET voltage and spectro measurements.
-During the fifth period, seaFET cannot be calibrated because seaFET was not working during the time of reference (pH spectro) sampling (2018-04-16).
-To solve this calibration, we decided to fit the spectro measurement with a pH mean of 4 previous days.
-
-We also defined a period of malfunction from **2017-12-14** to **2018-02-02**.
-in the first part of this period, until 2018-01-08, we decided to filter outliers.
-In the second part, until the end of the period, data must be removed.
-
-```{r seaFET pH calculation sf_calc, echo=FALSE, message= FALSE, warning=FALSE}
-####
-## calculation of the calibrated pH ##
-##       new sf_calc function       ##
-####
-seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
-
-# bind new calibrated pH data to the seafet data set.
-names(seafet_calib) <- c("pHint_tot_sf", "pHext_tot_sf")
-d_all <- dplyr::bind_cols(d_all, seafet_calib )
-
-# pH seaFET Final
-# add despike with n=2 k = 5762 to the final ph corrected data
-# despike me semble inutile, faire plutôt un simple des outliers qui, vérification faite, n'est même pas nécessaire
-# Il faut par contre créér une nouvelle variable avec pH deeper than 8 m, called *_9m for consistency with salinity and temp
-d_all <- d_all %>%
-  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA")) %>%
-  dplyr::mutate(pHint_tot_sf = seafet_calib$pHint_tot_sf) %>%
-  dplyr::mutate(pHint_tot_sf_1m = ifelse(pressure_insitu_ctd > 0 & pressure_insitu_ctd < 2, pHint_tot_sf, NA),
-                pHint_tot_sf_3m = ifelse(pressure_insitu_ctd >= 2 & pressure_insitu_ctd < 4, pHint_tot_sf, NA),
-                pHint_tot_sf_5m = ifelse(pressure_insitu_ctd >= 4 & pressure_insitu_ctd < 6, pHint_tot_sf, NA),
-                pHint_tot_sf_7m = ifelse(pressure_insitu_ctd >= 6 & pressure_insitu_ctd < 8, pHint_tot_sf, NA),
-                pHint_tot_sf_9m = ifelse(pressure_insitu_ctd >= 8 , pHint_tot_sf, NA)
-  )
-
-# add spectro points that cannot be taken into consideration (some ancillary data T and/or S not available)
-# shown as white triangles on the plot
-d_all <- d_all %>%
-  dplyr::mutate(
-    pH_s_sf_no_calb = ifelse(
-      datetime == as.POSIXct("2018-04-16 07:00:00") |
-        datetime == as.POSIXct("2018-12-14 10:00:00") |
-        datetime == as.POSIXct("2019-01-18 11:00:00"),
-      ph_s_sf_temp_insi,
-      NA
-    )
-  )
-
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_7m, pHint_tot_sf_9m)
-seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
-dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
-dySeries("ph_s_sf_temp_insi", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-dySeries("pHint_tot_sf_9m", label = "pHT 9m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
-dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="UTC"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
-  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="UTC"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="UTC"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
-  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
-  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
-  dyLegend(show = "auto")   %>%
-  dyAxis("y2",valueRange = c(-2, 2)) %>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-  dyRangeSelector(height = 30, dateWindow= NULL)
-```
-
-### **seaFET pH profiles**
-
-```{r seafet profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-# range <- d_all %>%
-#   dplyr::mutate(pH_range_more_6m = ifelse(pressure_insitu_ctd > 6, pHint_tot_sf, NA)) %>%
-#   group_by(montht) %>%
-#   summarize(pH_range = max(pHint_tot_sf, na.rm = TRUE) - min(pHint_tot_sf, na.rm = TRUE),
-#             pH_range_more_6m = max(pH_range_more_6m, na.rm = TRUE) - min(pH_range_more_6m, na.rm = TRUE),
-#             pH_range_more_9m = max(pHint_tot_sf_9m, na.rm = TRUE) - min(pHint_tot_sf_9m, na.rm = TRUE)) %>%
-#   ungroup()
-# print(kable(range, digits = 2))
-
-# # datetime when pH values are in but no pressure data. File sent to send to Philipp
-# no_pressure <- d_all %>% 
-#   dplyr::select(datetime, pressure_insitu_ctd, pHint_tot_sf) %>% 
-#   dplyr::filter(is.na(pressure_insitu_ctd) & !is.na(pHint_tot_sf))
-# readr::write_csv(x = no_pressure, path=paste0(path,"/fb_awipev-co2_server/ny-alesund/data//no_pressure.csv"))
-
-# we look at all depths
-tmp <- d_all %>% 
-  dplyr::select(montht, pHint_tot_sf, depth) %>%
-  group_by(depth, montht)
-p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "pHT", x = "Depth (m)", y= "pHT") +
-  facet_wrap(vars(montht), scale = "free_y")
-print(p)
-
-# we look at 0 to 4 m vs more than 8 m
-tmp <- d_all %>% 
-  dplyr::select(montht, pHint_tot_sf, depth) %>%
-  dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
-  dplyr::filter(depth == 2 | depth == 9) %>% 
-  group_by(depth, montht)
-summary(aov(tmp$pHint_tot_sf ~ tmp$depth * tmp$montht))
-
-p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "pHT", x = "Depth (m)", y= "pHT") +
-  facet_wrap(vars(montht), scale = "free_y")
-print(p)
-```
-**Conclusion**:
-The range is significantly larger during some months when the data deeper than 8 m are considered.
-Also, pH is sometimes higher at the surface, at other times it is higher on the bottom (June).
-No data are available at 1 m (actually 0 to 2 m).
-So, to compare surface and bottom, I combine 1 and 3 m (0 to 4 m) and 9 m (below 8 m).
-
-Depth and month of the year have a statistically significant effet on pH. The interaxction is also significant, indicating that the effect of depth differs depending on the month.
-
- + To compare with pCO2/pCO2 measured in the Ferrybox seems therefore better to stick with pH_9m, that is at depths deeper than 8 m.
-  + pCO2 would have the same behaviour as pH. For air-sea CO2 fluxes, one should use data from 0 to 4 m.
-
-## pH durafet
-
-pH is measured continuously by an autonomous durafet pH sensor.
-Final calibrated durafet pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
-Calibration was done appliying an offset of pH between measured and spectro data per periods.
-
-### **Durafet calibration**
-
-```{r durafet calibration, echo=FALSE, message= FALSE, warning=FALSE}
-# deployment period between 2 spectro measurements.
-durPeriod <- d_all%>%
-  dplyr::select(datetime, ph_s_dur_temp_fb)%>%
-  dplyr::filter(!is.na(ph_s_dur_temp_fb))
-
-durPeriod <-  durPeriod %>%
-  dplyr::arrange(datetime) %>%
-  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(durPeriod)])/2* 3600 )))%>%
-  dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])
-
-#put interval in a list with the start date of durafet measurements
-durinterv <- c( as_datetime("2017-08-24 13:00:00"), durPeriod[,4])
- #Change period sfinterv[2]. Because durafet measurementwas not working on period 1. No match between spectro and sensor. Durafet spectro 1 not taking into consideration.
-durinterv[2] <- ymd_hms("2017-08-24 13:00:00")
- #Change period sfinterv[06]. Because durafet was not responding good after 2018-03-08 23:00:00.
-durinterv[6] <- ymd_hms("2018-03-08 23:00:00")
- #Change period sfinterv[13]. Because durafet was off just after 2018-12-28.
-durinterv[13] <- ymd_hms("2019-12-28 17:00:00")
- #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-#durinterv[14] <- ymd_hms("2019-01-19 00:00:00")
-
-# set deployment period between 2 spectro measurements.
-# add here the new periods durinterv[..]
-d_all <- d_all %>%
-  dplyr::mutate(deployment_dur = ifelse(datetime >= durinterv[1] & datetime <= durinterv[2], 01, 
-                                ifelse(datetime >= durinterv[2] & datetime <= durinterv[3], 02, 
-                                ifelse(datetime >= durinterv[3] & datetime <= durinterv[4], 03, 
-                                ifelse(datetime >= durinterv[4] & datetime <= durinterv[5], 04,
-                                ifelse(datetime >= durinterv[5] & datetime <= durinterv[6], 05,
-                                ifelse(datetime >= durinterv[6] & datetime <= durinterv[7], 06,
-                                ifelse(datetime >= durinterv[7] & datetime <= durinterv[8], 07,
-                                ifelse(datetime >= durinterv[8] & datetime <= durinterv[9], 08,
-                                ifelse(datetime >= durinterv[9] & datetime <= durinterv[10], 09,
-                                ifelse(datetime >= durinterv[10] & datetime <= durinterv[11], 10, 
-                                ifelse(datetime >= durinterv[11] & datetime <= durinterv[12], 11,
-                                ifelse(datetime >= durinterv[12] & datetime <= durinterv[13], 12,
-                                ifelse(datetime >= durinterv[13] & datetime <= durinterv[14], 13,
-                                ifelse(datetime >= durinterv[14] & datetime <= durinterv[15], 14,
-                                ifelse(datetime >= durinterv[15] & datetime <= durinterv[16], 15,
-                                ifelse(datetime >= durinterv[16] & datetime <= durinterv[17], 16,
-                                 ifelse(datetime >= durinterv[17] & datetime <= durinterv[18], 17,
-                                ifelse(datetime >= durinterv[18] & datetime <= durinterv[19], 18,
-                                ifelse(datetime >= durinterv[19] & datetime <= durinterv[20], 19,
-                                 ifelse(datetime >= durinterv[20] & datetime <= durinterv[21], 20,
-                                ifelse(datetime >= durinterv[21] & datetime <= durinterv[22], 21,
-                                 ifelse(datetime >= durinterv[22] & datetime <= durinterv[23], 22,
-                                ifelse(datetime >= durinterv[23] & datetime <= durinterv[24], 23,
-                                ifelse(datetime >= durinterv[24] & datetime <= durinterv[25], 24,
-                                 ifelse(datetime >= durinterv[25] & datetime <= durinterv[26], 25,
-                                ifelse(datetime >= durinterv[26], 26,NA )))))))))))))))))))))))))))
-
-# Offset between durafet pH and spec pH 
-duroffset <- left_join(durPeriod%>%dplyr::select(datetime,ph_s_dur_temp_fb), d_all%>%dplyr::select(datetime,ph_dur ), by="datetime")
-dat_dur <- mutate(duroffset, diff_pH_dur = ph_s_dur_temp_fb - ph_dur)
-average_offset_dur <- round(mean(dat_dur$diff_pH_dur, na.rm=TRUE), digits = 2)
-sd_offset_dur <- round(sd(abs(dat_dur$diff_pH_dur), na.rm=TRUE), digits = 2)
-n_offset_dur <- length(!is.na(dat_dur$diff_pH_dur))
-
-plot_offset_dur <- ggplot(data = filter(dat_dur, !is.na(diff_pH_dur))) +
-  geom_hline(yintercept=mean(dat_dur$diff_pH_dur, na.rm = TRUE), size=0.3, col="red") +
-  annotate("text", x = dat_dur$datetime[3], y =-0.16, label = "offset mean", color="red")+
-  geom_hline(yintercept=0, size=0.3) +
-  geom_point(aes(x = datetime, y = diff_pH_dur), size = 1, colour = "#51C56AFF") +
-  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
-  scale_x_datetime(date_breaks="month", date_minor_breaks="1 week", labels=date_format("%b %Y")) +
-  Mytheme() + theme(panel.grid.major.x = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1))
-
-# create offset per period + add this offset per period.
-d_all <- d_all%>%
- dplyr::mutate(offset_durafet = ifelse(deployment_dur == 1, dat_dur$diff_pH_dur[1],
-                                ifelse(deployment_dur == 2, dat_dur$diff_pH_dur[2],
-                                ifelse(deployment_dur == 3, dat_dur$diff_pH_dur[3],
-                                ifelse(deployment_dur == 4, dat_dur$diff_pH_dur[4],
-                                ifelse(deployment_dur == 5, dat_dur$diff_pH_dur[5],
-                                ifelse(deployment_dur == 6, dat_dur$diff_pH_dur[6],
-                                ifelse(deployment_dur == 7, dat_dur$diff_pH_dur[7],
-                                ifelse(deployment_dur == 8, dat_dur$diff_pH_dur[8],
-                                ifelse(deployment_dur == 9, dat_dur$diff_pH_dur[9],
-                                ifelse(deployment_dur == 10, dat_dur$diff_pH_dur[10], 
-                                ifelse(deployment_dur == 11, dat_dur$diff_pH_dur[11],
-                                ifelse(deployment_dur == 12, dat_dur$diff_pH_dur[12],
-                                ifelse(deployment_dur == 13, dat_dur$diff_pH_dur[13],
-                                ifelse(deployment_dur == 14, dat_dur$diff_pH_dur[14],
-                                ifelse(deployment_dur == 15, dat_dur$diff_pH_dur[15],
-                                ifelse(deployment_dur == 16, dat_dur$diff_pH_dur[16],
-                                ifelse(deployment_dur == 17, dat_dur$diff_pH_dur[17],
-                                ifelse(deployment_dur == 18, dat_dur$diff_pH_dur[18],
-                                ifelse(deployment_dur == 19, dat_dur$diff_pH_dur[19],
-                                ifelse(deployment_dur == 20, dat_dur$diff_pH_dur[20],
-                                ifelse(deployment_dur == 21, dat_dur$diff_pH_dur[21],
-                                ifelse(deployment_dur == 22, dat_dur$diff_pH_dur[22],
-                                ifelse(deployment_dur == 23, dat_dur$diff_pH_dur[23],
-                                ifelse(deployment_dur == 24, dat_dur$diff_pH_dur[24],
-                                ifelse(deployment_dur == 25, dat_dur$diff_pH_dur[25],0))))))))))))))))))))))))),
-              ph_dur_corr = ph_dur + offset_durafet
-              )
-
-# Remove outliers from 2018-07-10 00:00 to 05:00
-d_all$ph_dur_corr <-
-  ifelse(
-    d_all$datetime >= as.POSIXct("2018-07-10 00:00:00") &
-      d_all$datetime <= as.POSIXct("2018-07-10 05:00:00"),
-    NA,
-    d_all$ph_dur_corr
-  )
-d_all$ph_dur <-
-  ifelse(
-    d_all$datetime >= as.POSIXct("2018-07-10 00:00:00") &
-      d_all$datetime <= as.POSIXct("2018-07-10 05:00:00"),
-    NA,
-    d_all$ph_dur
-  )
-
-# DURAFET 
-# add spectro points that are not taking into consideration
-d_all <- d_all %>%
-  dplyr::mutate(pH_s_dur_no_calb = ifelse(
-    datetime == as.POSIXct("2017-08-24 13:00:00"),
-    ph_s_dur_temp_fb,
-    NA
-  ))
-
-durafet_contros_xts <- dplyr::select(d_all, datetime, ph_dur, ph_s_dur_temp_fb,ph_dur_corr, pH_s_dur_no_calb)
-durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
- dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
-    dySeries("ph_dur", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-       dySeries("pH_s_dur_no_calb", label = "pH spectro no calibration", color ="black", pointShape = "triangle",strokeWidth=0, pointSize=6) %>%
-       dySeries("ph_dur_corr", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
-       dySeries("ph_s_dur_temp_fb", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
-    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="UTC"), "New holder installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "durafet installed", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="UTC"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyShading(from =  durinterv[1], to= durinterv[2], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[2], to= durinterv[3], color = "#E0E0E0") %>%
-    dyShading(from = durinterv[3], to= durinterv[4], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[4], to= durinterv[5], color = "#E0E0E0") %>%
-    dyShading(from = durinterv[5], to= durinterv[6], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[6], to= durinterv[7], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[7], to= durinterv[8], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[8], to= durinterv[9], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[9], to= durinterv[10], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[10], to= durinterv[11], color = "#E0E0E0") %>%
-    dyShading(from = durinterv[11], to= durinterv[12], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[12], to= durinterv[13], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[13], to= durinterv[14], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[14], to= durinterv[15], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[15], to= durinterv[16], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[16], to= durinterv[17], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[17], to= durinterv[18], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[18], to= durinterv[19], color = "#E0E0E0") %>%
-    dyShading(from = durinterv[19], to= durinterv[20], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[20], to= durinterv[21], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[21], to= durinterv[22], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[22], to= durinterv[23], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[23], to= durinterv[24], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[24], to= durinterv[25], color = "#E0E0E0") %>%
-  dyShading(from = durinterv[25], to= durinterv[26], color = "#CCCCCC") %>%
-  dyShading(from = durinterv[26], to= Sys.Date(), color = "#E0E0E0") %>%
-     dyLegend(show = "follow")   %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-print(plot_offset_dur)
-
-# now remove outliers
-d_all <- d_all %>%
-  dplyr::mutate(
-    ph_dur_corr = case_when(
-          ph_dur_corr < 8 ~ NA_real_,
-      date > as.Date("2018-05-18") &
-        date <  as.Date("2018-05-19") & ph_dur_corr < 8.16 ~ NA_real_,
-      #date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
-      date > as.Date("2017-09-25") &
-        date <  as.Date("2017-10-01") & ph_dur_corr < 8.07 ~ NA_real_,
-      #date == as.Date("2017-03-22") & sal_mix < 34 ~ NA_real_,
-      TRUE ~ ph_dur_corr
-    )
-  )
-
-# RANGE of pH
-range_dur <- tbl_df(
-  d_all %>%
-  group_by(date, montht, year=year(datetime)) %>%
-  summarize(pH_range = max(ph_dur_corr) - min(ph_dur_corr))
-)
-quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
-
-# Per month
-range_month <-
-  range_dur %>%
-  group_by(montht) %>%
-  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
-
-size_point <- 0.4 # size of data points
-p <-
-  ggplot(data=range_dur, aes(x = as.factor(montht), y = pH_range)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(y =expression(paste(pH[T], " range durafet")), x=NULL, title=NULL) +
-  Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-print(p) # plot_range_dur
-```
-
-The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).
-
-## Range per months
-
-```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
-range_month <-
-  d_all %>%
-  group_by(montht) %>%
-  #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
-  summarize(temp_mix_max = round( max(temp_mix, na.rm=TRUE), digits = 2),
-            temp_mix_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
-            temp_ctd_1m_max = round( max(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
-            temp_ctd_1m_min = round(min(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
-            temp_ctd_3m_max = round( max(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
-            temp_ctd_3m_min = round(min(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
-            temp_ctd_5m_max = round( max(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
-            temp_ctd_5m_min = round(min(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
-            temp_ctd_7m_max = round( max(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
-            temp_ctd_7m_min = round(min(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
-            temp_ctd_9m_max = round( max(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
-            temp_ctd_9m_min = round(min(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
-            temp_11m_max = round( max(temp_insitu_11m, na.rm=TRUE), digits = 2),
-            temp_11m_min = round(min(temp_insitu_11m, na.rm=TRUE), digits = 2),
-            temp_fb_max = round(max(temp_fb, na.rm=TRUE), digits = 2),
-            temp_fb_min = round( min(temp_fb, na.rm=TRUE), digits = 2),
-            sal_mix_max = round(max(sal_mix, na.rm=TRUE), digits = 2),
-            sal_mix_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
-            sal_ctd_1m_max = round( max(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
-            sal_ctd_1m_min = round(min(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
-            sal_ctd_3m_max = round( max(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
-            sal_ctd_3m_min = round(min(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
-            sal_ctd_5m_max = round( max(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
-            sal_ctd_5m_min = round(min(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
-            sal_ctd_7m_max = round( max(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
-            sal_ctd_7m_min = round(min(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
-            sal_ctd_9m_max = round( max(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
-            sal_ctd_9m_min = round(min(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
-            sal_fb_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
-            sal_fb_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
-            pH_sf_max = round(max(pHint_tot_sf_9m, na.rm=TRUE), digits = 4),
-            pH_sf_min = round(min(pHint_tot_sf_9m, na.rm=TRUE), digits = 4))
-kable(range_month, caption = "")
-```
-
-## pHs 
-Comparaison is done here with **corrected pHs** (**seaFET**, **durafet** and **calculated** (from AT/CT)) and normalized at 4°C with a total alkalinity of `r mean(d_all$at, na.rm=TRUE)` µmoles kg-1 (mean data).
-For information, mean temperatures in Ferrybox and *in situ* are repectively 3.5°C and 2.5°C.
-
-### **seaFET / durafet pHs**
-
-```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-# prepare data and remove sf biofouling period
-pH_sf <- d_all %>%
-  dplyr::select(datetime, sal_insitu_ctd_9m , temp_insitu_ctd_9m, pHint_tot_sf)%>%
-  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd_9m), !is.na(sal_insitu_ctd_9m)) %>%
-  dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
-
-pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
-
-pH_dur <- d_all %>%
-  dplyr::select(datetime, sal_fb,temp_fb, ph_dur_corr)%>%
-  dplyr::filter(!is.na(ph_dur_corr), !is.na(temp_fb), !is.na(sal_fb))
-pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
-
-# join pH sf norm + pH dur norm
-d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime, pHint_tot_sf_norm4 ), by="datetime")
-d_all <- left_join(d_all, pH_dur%>%dplyr::select(datetime, pH_durafet_norm4 ), by="datetime")
-
-fit <- lmodel2(data = d_all,  pHint_tot_sf_norm4 ~ pH_durafet_norm4 , nperm = 99)
-pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pHint_tot_sf_norm4, label = monthd))+
-  geom_point( aes(color=factor(monthd)), size =1, alpha=0.5) + 
-  facet_wrap( ~ factor(monthd), ncol = 3) +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 , xlim=c(7.8,8.35), ylim=c(7.8,8.35))+ #scale_colour_discrete(guide="none") +
-  labs( x="pH durafet, 4°C", y="pH seaFET, 4°C ", color = "Month ")  +theme_bw()
-
-print(pdur_sf_norm_text)
-
-durafet_sf_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pHint_tot_sf_norm4)
-durafet_sf_contros_xts <- as.xts(durafet_sf_contros_xts, order.by = d_all$datetime)
-dygraph(durafet_sf_contros_xts, group = "awipev", main="pH durafet vs pH seaFET at 4°C", ylab="pHT") %>%
-    dySeries("pH_durafet_norm4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color =  "red", strokeWidth = 0, pointSize = 2 ) %>%
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-       dyLegend(show = "follow")   %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL) 
-```
-
-### **Calculated / Durafet pHs**
-```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
-# Normalize phcalc from AT/CT to 4°c
-pH_calc <- discrete %>%
-  dplyr::select(datetime, sal_fb, temp_fb, phcalc_fb, at)%>%
-  dplyr::filter(!is.na(phcalc_fb), !is.na(temp_fb), !is.na(sal_fb))
-pH_calc$pH_calc_fb_norm4 <- pHinsi(pH = pH_calc$phcalc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
-
-# join pH calc norm + pH dur/sf norm in d_all
-d_all <- left_join(d_all, pH_calc %>% dplyr::select(datetime, pH_calc_fb_norm4), by="datetime")
-
-durafet_calc_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pH_calc_fb_norm4)
-durafet_calc_contros_xts <- as.xts(durafet_calc_contros_xts, order.by = d_all$datetime)
-dygraph(durafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH durafet, normalized at 4°C", ylab="pHT") %>%
-    dySeries("pH_durafet_norm4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_calc_fb_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-       dyLegend(show = "follow")   %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-```
-
-### **Calculated / seaFET pHs**
-```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
-seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_norm4, pH_calc_fb_norm4)
-seafet_calc_contros_xts <- as.xts(seafet_calc_contros_xts, order.by = d_all$datetime)
-dygraph(seafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH seaFET, normalized at 4°C", ylab="pHT") %>%
-    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_calc_fb_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-       dyLegend(show = "follow")   %>%
-dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-```
-
-### **Spectro / durafet**
-
-```{r pHs comparaison durafet spectro, echo=FALSE, message= FALSE, warning=FALSE}
-# Spectro / durafet
-lm <- lm2(x = d_all$ph_s_dur_temp_fb, y = d_all$ph_dur_corr)
-
-p <-  ggplot(d_all, aes(x=ph_s_dur_temp_fb, y= ph_dur_corr, label = monthd)) +
-  geom_text( aes(color=factor(monthd))) + 
-  scale_color_discrete(guide = "none")+
-  geom_abline(slope=1, intercept =0, linetype = "dashed") +
-  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
-              colour = "blue") +
-  labs(title = paste("pH spectro vs pH durafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
-                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
-                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
-                     "; P =", signif(lm$fit$P.param, 3),
-                     "; RMSE = ", signif(lm$rmse, 3))) +
-  theme_bw() +
-  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
-  labs(x="pH durafet", y="pH spectro", color = "Months")
-p
-```
-
-```{r pHs comparaison sf spectro, echo=FALSE, message= FALSE, warning=FALSE}
-# Spectro / seafet
-lm <- lm2(x = d_all$ph_s_sf_temp_insi, y = d_all$pHint_tot_sf)
-
-p <-  ggplot(d_all, aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = monthd)) +
-  geom_text( aes(color=factor(monthd))) + 
-  scale_color_discrete(guide = "none")+
-  geom_abline(slope=1, intercept =0, linetype = "dashed") +
-  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
-              colour = "blue") +
-  labs(title = paste("pH spectro vs pH seafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
-                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
-                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
-                     "; P =", signif(lm$fit$P.param, 3),
-                     "; RMSE = ", signif(lm$rmse, 1))) +
-  theme_bw() +
-  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
-  labs(x="pH spectro", y="pH seafet", color = "Months")
-p
-```
-
-## SNAPO-CO2
-Since November 2018, informations on weekly Ferrybox and monthly durafet/seaFET samplings are collected in a online document that can be consulted at anytime:
-
-[weekly and monthly samplings](https://docs.google.com/spreadsheets/d/1bNh9q4bkNoh2ra78XC451EmGb9Q8kMf4ByBnKngeHOg/edit?usp=sharing)
-
-We found that some analysed discrete seawater replicates for AT/CT, performed by SNAPO in Paris sometimes show a large difference between duplicates.
-Arbitrarily, we decided to take in consideration replicates with a standard deviation smaller than 10 µmoles.kg-1.
-In the other case (greater than 10 µmoles.kg-1), the closest replicate from the general trend will be kept with qflag_at/qflag_ct of 2 (correct analysis) and the farthest one will be rejected with a flag of 1.
-There are exceptions when it is difficult to decide which of the replicates need to be eliminated.
-
-For TA, dulpicates's flags that have been changed to 1 are:
-
-2015-11-18
-, 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29, 2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16, 2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03, 2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-08-23.
-
-For CT, duplicates's flags that have been changed to 1 are:
-
-2015-08-06, 2015-08-13, 2016-05-12, 2016-05-19, 2016-06-16, 2016-07-28, 2016-09-08, 2016-10-27, 2016-11-17, 2017-01-19, 2017-03-02, 2017-04-27, 2017-09-14, 2018-04-26, 2018-05-04, 2018-05-12, 2018-05-25, 2018-06-30, 2018-07-20, 2018-08-03, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-05-03, 2019-05-10, 2019-08-23.
-
-Also in the Discrete_sampling_AWIPEV.csv, some analysed samples have been flaged "3" by the SNAPO.
-After a close look, these samples are not differents from their duplicates.
-Then we put the flag to "2" (good result).
-
-For TA and CT, samples's flags that have been changed from 3 to 2 are: 2019-12-27 (2264 and 2130), 2019-10-25 (2332 and 2152), 2019-09-06 (2268 and 2116).
-
-```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
-# use the df at_ct for mean and sd
-# creat a new df to calculate the diff between replicate
- diff <- d %>%
-    group_by(datetime) %>%
-   dplyr::select(datetime, at, ct)%>%   
-   dplyr::mutate(at_diff = abs(at - lag(at)),
-                 ct_diff = abs(ct - lag(ct)))
-
-pdelta_at_snapo <-ggplot() +
-    geom_point(data=diff, aes(x= datetime, y= at_diff)) +
-    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
-    annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
-    annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
-labs(title= "AT", x="Time", y="Delta between TA replicates")+
-    Mytheme()
-pdelta_ct_snapo <-ggplot() +
-    geom_point(data=diff, aes(x= datetime, y= ct_diff)) +
-    geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
-annotate("text", x = diff$datetime[17], y = 6, label = "4 µmoles/kg", color="red")+
-    annotate("text", x = diff$datetime[17], y = -6, label = "-4 µmoles/kg", color="red")+
-  labs(title= "CT",x="Time", y="Delta between CT replicates")+
-    Mytheme()
-
-p_ct_ts <- ggplot() +
-    geom_point(data=discrete, aes(x= datetime, y= ct)) +
-  labs(title= "",x="Time", y="CT (µmoles/kg)")+
-    Mytheme()
-p_at_ts <- ggplot() +
-    geom_point(data=discrete, aes(x= datetime, y= at)) +
-  labs(title= "",x="Time", y="AT (µmoles/kg)")+
-    Mytheme()
-
-# DYGRAPH
-
-# to create periods according to SNAPCO analysis 
-snapcoevents <-
-  as.POSIXct(
-    c(
-      "2015-07-23 00:00:00",
-      "2015-11-18 00:00:00",
-      "2015-11-27 00:00:00",
-      "2016-10-13 00:00:00",
-      "2017-05-11 00:00:00",
-      "2018-02-09 00:00:00",
-      "2018-02-16 00:00:00",
-      "2018-07-27 00:00:00",
-      "2018-08-03 00:00:00",
-      "2018-11-23 00:00:00",
-      "2018-11-30 00:00:00",
-      "2019-04-12 00:00:00",
-      "2019-08-31 23:59:00",
-      format(Sys.Date(), "%Y-%m-%d %H:%M:%S")
-    )
-  )
-
-at_diff_xts <- dplyr::select(diff, datetime, at_diff, at)
-at_diff_xts <- as.xts(at_diff_xts, order.by = diff$datetime)
-pdelta_at_snapo_dygraph <- dygraph(at_diff_xts, group = "awipev", main="Discrete AT (SNAPO) measurements", ylab="AT") %>%
-    dySeries("at_diff", label = "AT delta", color ="red", strokeWidth=0, pointSize=4) %>%
-    dySeries("at", label = "AT duplicates", color =  "blue", strokeWidth = 0, pointSize = 2, axis = "y2" ) %>%
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-  dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#EDEDED") %>%
-  dyShading(from = snapcoevents[3], to = snapcoevents[4], color = "#C2C2C2") %>%
-  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#EDEDED") %>%
-  dyShading(from = snapcoevents[7], to = snapcoevents[8], color = "#C2C2C2") %>%
-  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#EDEDED") %>%
-  dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C2C2") %>%
-  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
-    dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-       dyLegend(show = "follow")   %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=2) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-ct_diff_xts <- dplyr::select(diff, datetime, ct_diff, ct)
-ct_diff_xts <- as.xts(ct_diff_xts, order.by = diff$datetime)
-pdelta_ct_snapo_dygraph <- dygraph(ct_diff_xts, group = "awipev", main="Discrete CT (SNAPO) measurements", ylab="CT") %>%
-    dySeries("ct_diff", label = "CT delta", color ="red", strokeWidth=0, pointSize=4) %>%
-    dySeries("ct", label = "CT duplicates", color =  "blue", strokeWidth = 0, pointSize = 2, axis = "y2" ) %>%
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-   dyShading(from = snapcoevents[1], to = snapcoevents[2], color = "#EDEDED") %>%
-  dyShading(from = snapcoevents[3], to = snapcoevents[4], color = "#C2C2C2") %>%
-  dyShading(from = snapcoevents[5], to = snapcoevents[6], color = "#EDEDED") %>%
-  dyShading(from = snapcoevents[7], to = snapcoevents[8], color = "#C2C2C2") %>%
-  dyShading(from = snapcoevents[9], to = snapcoevents[10], color = "#EDEDED") %>%
-  dyShading(from = snapcoevents[11], to = snapcoevents[12], color = "#C2C2C2") %>%
-  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
-    dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%
-       dyLegend(show = "follow")   %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=2) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
-pdelta_at_snapo
-pdelta_at_snapo_dygraph
-p_at_ts
-pdelta_ct_snapo
-pdelta_ct_snapo_dygraph
-p_ct_ts
-```
-
-## Air-sea CO2 flux
-
-To calculate the air-sea CO2 flux, we use:
-
-+ seawater pCO2 measured in the FerryBox on water pumped from 11 m depth.
-+ atmospheric CO2 measured at the Zeppelin station and downloaded on 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999 
-+ wind spreed data collected by the AWI at 10 m height (sent to JPG by P. Fischer, Aug. 2020)
-
-Since there are many gaps, a climatological year is used: air-sea flux calculated by day, then by month, then by year.
-
-seaFET pH is significantly different at the surface and depth. It should therefore be the same for pCO2.
-
-Let's look first at the stratification (salinity, temperature and density).
-
-```{r stratification, echo=FALSE, message= FALSE, warning=FALSE}
-# we look at salinity all depths
-tmp <- d_all %>% 
-  dplyr::select(montht, sal_insitu_ctd, depth) %>%
-  group_by(depth, montht)
-p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = sal_insitu_ctd)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "Salinity vs depth", x = "Depth (m)", y= "Salinity") +
-  facet_wrap(vars(montht), scale = "free_y")
-print(p)
-
-# heatmap
-tmp <- d_all %>%
-  dplyr::filter(!is.na(depth)) %>%
-  dplyr::select(montht, sal_insitu_ctd, depth) %>%
-  group_by(montht, depth)
-sal_median <- skim(tmp) %>%
-  dplyr::select(depth, montht, numeric.p50) %>%
-  pivot_wider(names_from = depth, values_from = c(numeric.p50))
-
-plt <- sal_median %>%
-  ggplot(aes(
-    x = montht,
-    y = as.factor(depth),
-    fill = median(sal_insitu_ctd)
-  ), color = "white") +
-  geom_tile() +
-  scale_fill_gradientn(colors = viridis(5), breaks = seq(31, 36, by = 1), na.value = "grey") +
-  labs(x = "", y = "", fill = "Salinity") +
-  scale_x_discrete(position = "top") +
-  scale_y_discrete(name = "", limits = rev(levels(as.factor(tmp$depth)))) +
-  # scale_y_discrete(name = "", limits = rev(levels(as.factor(tmp$depth))),
-  #                  rev(levels(tmp$depth))[c(1,3,5,7,9)]) +
-  # coord_equal() +
-  theme(legend.position = "top",
-        axis.text.y = element_text(size = 13),
-        axis.text.x = element_text(size = 13),
-        legend.text = element_text(size = 13),
-        legend.title = element_text(size = 14),
-        #legend.key.size = unit(1.5, "cm"),
-        legend.key.height = unit(0.8, "cm"),
-        legend.key.width  = unit(2, "cm"))
-#plt
-
-# we look at salinity 0 to 4 m vs more than 8 m
-tmp <- d_all %>% 
-  dplyr::select(montht, sal_insitu_ctd, depth) %>%
-  dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
-  dplyr::filter(depth == 2 | depth == 9) %>% 
-  group_by(depth, montht)
-sal_range <- skim(tmp) %>% 
-  dplyr::select(depth, montht, numeric.p50) %>% 
-  pivot_wider(names_from = depth, values_from = c(numeric.p50)) %>% 
-  dplyr::rename(median2m = "2",
-                median9m = "9") %>% 
-  dplyr::mutate(sal_range = median2m - median9m)
-kable(sal_range, digits = 2, caption = "Median salinity")
-
-summary(aov(tmp$sal_insitu_ctd ~ tmp$depth * tmp$montht))
-
-p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = sal_insitu_ctd)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "Salinity vs depth", x = "Depth (m)", y= "Salinity") +
-  facet_wrap(vars(montht), scale = "free_y")
-print(p)
-
-# we look at temperature all depths
-tmp <- d_all %>% 
-  dplyr::select(montht, temp_insitu_ctd, depth) %>%
-  group_by(depth, montht)
-p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = temp_insitu_ctd)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "Temperature vs depth", x = "Depth (m)", y= "Salinity") +
-  facet_wrap(vars(montht), scale = "free_y")
-print(p)
-
-# we look at temperature 0 to 4 m vs more than 8 m
-tmp <- d_all %>% 
-  dplyr::select(montht, temp_insitu_ctd, depth) %>%
-  dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
-  dplyr::filter(depth == 2 | depth == 9) %>% 
-  group_by(depth, montht)
-temp_range <- skim(tmp) %>% 
-  dplyr::select(depth, montht, numeric.p50) %>% 
-  pivot_wider(names_from = depth, values_from = c(numeric.p50)) %>% 
-  dplyr::rename(median2m = "2",
-                median9m = "9") %>% 
-  dplyr::mutate(temp_range = median2m - median9m)
-kable(temp_range, digits = 2, caption = "Median temperature")
-summary(aov(tmp$temp_insitu_ctd ~ tmp$depth * tmp$montht))
-
-p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = temp_insitu_ctd)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "Temperature vs depth", x = "Depth (m)", y= "Salinity") +
-  facet_wrap(vars(montht), scale = "free_y")
-print(p)
-
-# we look at density 0 to 4 m vs more than 8 m
-tmp <- d_all %>% 
-  dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth) %>%
-  dplyr::mutate(density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0),
-                depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
-  dplyr::filter(depth == 2 | depth == 9) %>% 
-  dplyr::select(montht, depth, density) %>% 
-  group_by(depth, montht) 
-den_range <- skim(tmp) %>% 
-  dplyr::select(depth, montht, numeric.p50) %>% 
-  pivot_wider(names_from = depth, values_from = c(numeric.p50)) %>% 
-  dplyr::rename(median2m = "2",
-                median9m = "9") %>% 
-  dplyr::mutate(den_range = median2m - median9m)
-kable(den_range, digits = 2, caption = "Median density")
-summary(aov(tmp$density ~ tmp$depth * tmp$montht))
-
-p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = density)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "Density vs depth", x = "Depth (m)", y= "Salinity") +
-  facet_wrap(vars(montht), scale = "free_y")
-print(p)
-```
-Using the medians because data are missing.
-
-+ Salinity 
-+ Temperature is always colder at 0-4 m than below 8 m (0.15 to 2°C).
-
-```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
-## Atmospheric CO2 Zeppelin
-# downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
-# value:units : ppm
-# value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
-atm_co2 <-
-  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
-  delim = " ",
-  comment = "#",
-  #skip = 182,
-  col_names = TRUE,
-  na = "-999.999",
-  ) %>%
-  dplyr::mutate(pco2_air = value,
-  datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))) %>%
-  dplyr::select(datetime, pco2_air)
-d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
-p_atm_co2 <- ggplot(data=atm_co2) +
-  geom_point(aes(x = datetime, y = pco2_air), col = "blue", size = 0.15, na.rm = TRUE) +
-  labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +
-  Mytheme(size_labs = 8)
-ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")
-```
-
-```{r meteo data, echo=FALSE, message= FALSE, warning=FALSE}
-#[1] "Year"               "Month"              "Day"                "Hour"              
-#[5] "Temperature[degC]"  "Pressure[hPa]"      "WindSpeed[m/s]"     "WindDirection[deg]"
-
-load(file = paste0(path, "meteo_awi/wind_nyalesund.RData")) 
-meteo <- tibble(windnyalesund) %>%
-  dplyr::mutate(datetime = as_datetime(paste(paste(Year, Month, Day, sep="-"), paste(Hour, "00", "00", sep="-"), sep = " ")),
-         temp_air = `Temperature[degC]`,
-         p_air = `Pressure[hPa]`,
-         ws = `WindSpeed[m/s]`,
-         wd = `WindDirection[deg]`
-        ) %>%
-  dplyr::select(datetime, temp_air, p_air, ws, wd)
-d_all <- dplyr::left_join(d_all, meteo, by = "datetime")
-```
-
-```{r air-sea CO2, echo=FALSE, message= FALSE, warning=FALSE}
-# calculations as described by de Carlo et al. (2013)
-# we consider that mole fraction in air = ppm TO CHECK
-# By convention, a negative flux indicates fluxes directed from the atmosphere to the ocean, and a positive flux indicates fluxes directed from the ocean to the atmosphere.
-d_all <- d_all %>%
-  dplyr::mutate(delta_pco2 = pco2_corr - pco2_air, # ppm
-                k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
-                Sc = 2073.1 - (125.62*temp_insitu_11m) + (3.6276*temp_insitu_11m^2) - (0.043219*temp_insitu_ctd^3), #dimensionless
-                k = k600 * (Sc/600)^-0.5, #cm/h
-                alp = seacarb::K0(S=sal_mix,T=temp_insitu_11m,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
-                alp = alp * (seacarb::rho(S = sal_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
-                f_air_sea = k * alp * delta_pco2 # mmol/(m2 h)
-                )
-
-p_f_air_sea <- ggplot(data=d_all) +
-  geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
-  labs(title = "Air-sea CO2 flux (all data)", x = "Time", y = "CO2 (mmol/(m2 h))") +
-  Mytheme(size_labs = 8)
-#p_f_air_sea
-#ggsave(filename = "figures/f_air_sea.png", plot = f_air_sea, width = 20, units = "cm")
-
-air_sea_day <- d_all %>%
-  dplyr::select(datetime, f_air_sea) %>%
-  dplyr::group_by(lubridate::yday(datetime)) %>%
-  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm=TRUE)/1000) %>% #mol/(m2 d)
-  ungroup() %>%
-  dplyr::rename(day = 1)
-
-p_f_air_sea_d <- ggplot(data = air_sea_day) +
-  geom_point(aes(x = day, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
-  labs(title = "Air-sea CO2 flux (per day)", x = "Time", y = "CO2 (mmol/(m2 d))") +
-  Mytheme(size_labs = 8)
-#p_f_air_sea_d
-#ggsave(filename = "figures/f_air_sea_d.png", plot = p_f_air_sea_d, width = 20, units = "cm")
-
-air_sea_month <- d_all %>%
-  dplyr::select(monthd, f_air_sea) %>%
-  dplyr::group_by(monthd) %>%
-  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm=TRUE)/1000) %>% #mol/(m2 d)
-  ungroup() %>%
-  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea)
-#air_sea_month
-p_f_air_sea_m <- ggplot(data = air_sea_month) +
-  geom_point(aes(x = monthd, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
-  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
-  lims(y = c(-30, 0)) +
-  labs(title = "Air-sea CO2 flux (per month)", x = "Julian day", y = "CO2 (mmol/(m2 month))") +
-  Mytheme(size_labs = 8)
-#p_f_air_sea_m
-#ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_m, width = 20, units = "cm")
-
-p <- cowplot::plot_grid(p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m, ncol = 1)
-pngfile <- "figures/air-sea_CO2_flux.png"
-ggsave(
-  pngfile, 
-  p, 
-  device = agg_png, 
-  width = 6.6, height = 10, units = "cm", res = 300,
-  scaling = 0.4
-)
-knitr::include_graphics(pngfile)
-```
-
-The annual air-sea CO2 flux is `r round(sum(air_sea_month), digits = 0)` mol/(m2 year).
-
-```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
-# d_hour is the real data set that is read at the beginning of the script
-# d_all comprises additional columns calculated in this script
-d_all$at <- ifelse(is.nan(d_all$at), NA, d_all$at) # replace all NaN by NA
-d_all$ct <- ifelse(is.nan(d_all$at), NA, d_all$ct) # replace all NaN by NA
-d_all <- dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))
-saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
-
-pangaea <- as_tibble(d_all) %>% 
-  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, phcalc_fb, pco2_corr, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
-  dplyr::rename(pressure = pressure_insitu_ctd,
-                s_insitu = sal_insitu_ctd,
-                s_fb = sal_fb, 
-                s_mix = sal_mix,
-                t_11m = temp_insitu_11m,
-                t_insitu = temp_insitu_ctd, 
-                t_fb = temp_fb, 
-                t_sf = temp_sf, 
-                t_dur = temp_dur, 
-                at = at, 
-                at_calc =at_calc,
-                ct = ct, 
-                ph_s_sf_t_insi = ph_s_sf_temp_insi, 
-                ph_s_dur_t_fb = ph_s_dur_temp_fb,
-                pco2 = pco2_corr,
-                pco2_calc = pco2_calc_fb,
-                pH_sf = pHint_tot_sf,
-                ph_dur = ph_dur_corr,
-                ph_calc = phcalc_fb
-                )
-saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
-write_csv(pangaea, path = paste0(path, "fb_data/pangaea.csv"))
-# Metadata Pangaea
-# pressure = pressure in situ (profiler)
-# s_insitu = salinity in situ (profiler)
-# s_fb = salinity in FerryBox 
-# s_mix = salinity in FerryBox with gaps filled by s_insitu below 8 m
-# t_11m = temperature in situ at 11 m
-# t_insitu = temperature in situ (profiler), 
-# t_fb = temperature in FerryBox 
-# t_sf = temperature SeaFET (profiler), °C
-# t_dur = temperature Durafet (FerryBox)
-# at = total alkalinity, discrete measurements (FerryBox)
-# at_calc = total alkalinity, calculated from salinity
-# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
-# ph_s_sf_t_insi = pH spectrophotometric SeaFET in situ (11 m)
-# ph_s_dur_t_fb = pH spectrophotometric Durafet in FerryBox
-# pco2 = pCO2 in Ferrybox
-# pco2_calc = pCO2 calculated in the FerryBox calculated from discrete measurments of AT and CT
-# pH_sf = pH SeaFET at in situ temperature (profiler)
-# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
-# ph_calc = pH at fb temp calculated from CT and AT samples collected at the FerryBox
-```
-## Maintenance
-<div style="text-align: justify">
-
-### **REMOS**
-- **2019-09-07**: REMOS back in the water.
-- **2019-09-02**: REMOS removed from the water for maintenance with Philipp and Samir.
-- **2018-11-24**: REMOS stopped because of an iceberg. At the moment we dont know if instruments are still there/broken.
-
-### **FerryBox**
-- **2020-01-24**: heater issues in the contenair (power shutdown maybe) caused some samples to freeze. See part "SNAPO" for details on samples.
-- **2019-09-01**: Some interruptions for the FB during 2 weeks of maintenance.
-- **2019-06-12**: Markus came to do maintenace. 
-- **2019-06-05**: Problem in the relay 15 that controls the waste water pump was found. The spare part will be brought here next week (when Samir will leave...).
-- **2019-06-03**: Samir is on site alone. Different tests were made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the problem (low flow).
-- **2019-05-22**: FB is stopped because of several problems. Philipp and Marine are working on it.
-- **2019-05-21**: FB is unstable. 
-- **2019-04-14**: FB is working again. 
-- **2019-04-13**: FB is stopped since 05:00am (the level switch stuck in the full position in the waste tank). 
-- **2019-02-27**: FB is working again. 
-- **2019-02-26**: FB is stopped because of a "leakage" issue. 
-- **2019-01-17**: FB is stopped until 19th January 
-- **2019-01-11**: FB is stopped until 12th Decmeber. 
-- **2018-12-28**: FB is stopped until 31st Decmeber. 
-- **2018-10-12**: FB is working again. 
-- **2018-10-10**: FB is stopped after a seawater leakage. 
-- **2018-10-08**: FB is working again. 
-- **2018-10-05**: FB is stopped after a seawater leakage. 
-- **2018-09-12**: FB is stopped. Problems inland could be the reason. The same day Marine make it working again.
-- **2018-04-14**: FB is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.
-- **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet tubings) in Svalbard, maybe due to a power failure over night in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
-- **2017-05-24**: FerryBox was shut down due to many connexion issues...see Philipp's email 24/05/2017 18:17.
-- **2017-03-20**: Philipp arrived in NYA to solve the problem.
-- **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's email on 2017-03-11 10:40). No more data for all parameters.
-- **2017-01-31**: Beginning of the 14-days FB maintenance by Philipp and Uwe. Gaps in data could be present during this period.
-- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19.
-- **2016-09-24**: No data because of maintenance until the 28th. Except for TA wich has data available for this period.
-- **2016-09-20**: Test in the Ferrybox with the seawater.
-Seawater was "sucked" (not pumped) from 7:40 to 10:00 by a vaccum system in order to test it.
-This system was installed if the pumps 1 and 2 broke during winter.
-This is a "plan C".
-This system is not automatic and we will be informed about its power up in case of emergency.
-As long as the water is not pumped with this system, we have to monitor the data because changements in gas partial pressure can occur.
-- **2016-09-12**: No data because of maintenance until the 18th.
-- **2016-09-10**: No data because of maintenance until the 11th.
-- **2016-05-09**: data are back.
-- **2016-05-04**: No data for all parameters because of electricity issues. 
-- **2016-04-23**: FerryBox was shut down by AWI team for maintenance.
-- **2016-02-23**: FerryBox was switched on by AWI team after maintenance.
-- **2015-12-20**: FerryBox was shut down because of pump issues. Waiting for the maintenance in February.
-- **2015-11-27**: The ferrybox was down from Nov. 18th until today Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader AWIPEV 2015-11-27 12:57). Tubes frozen.
-
-### **TA analyser**
-- **2019-11-15**: TA calibration done by Gwendall is OK but the sensore seems to have problem since 2019-10-16.
-Video conference is scheduled with Steffen on 2019-11-19.
-Maybe sample supply is defective.
-- **2019-07-12**: Steffen told us that calibration was not OK.
-To check it, he calculated the mediane of the pH/volume sample / volumeIndicatorfactor and compared them to January/October calibration.
-We wait for Steffen recommandations before to make another calibration.
-- **2019-06-07**: Samir did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. TA was stable before the calibration and calibration was OK.
-- **2019-02-15**: No data from 15th (14:08:21 UTC) to 19th February (14:58:46 UTC). files transfered but no data. No explanation.
-- **2019-01-26**: Philipp did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. Flow filter was also lifted up and the seawater flow has therefore increased.
-- **2019-01-16**: Bad data since this date. 
-- **2018-12-28**: HCL and BCG cartridges were changed by Marine.
-- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
-- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer).
-Samir received password and access from the AWI in order to communicate from France with the TA.
-- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
-- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again.
-First data were received (high: 2450 and low: 2150) but salinity issue since this time.
-Uwe/Philipp try to find if this comes from comunication issue with the FB.
-- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
-- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
-- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
-- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
-- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
-- **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
-- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
-- **2017-03-21**: Philipp changed the TA analyser provided by Contros.
-- **2017-02-10**: TA cleaning salt crusts.
-- **2017-02-09**: TA calibration with CRM at 12:20.
-- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
-- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode).
-Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
-- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
-- **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
-- **2016-05-31**: HCL cartridge was changed (Christelle, ObsEng).
-- **2016-05-01**: No data for TA.
-- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).
-
-### **pH seaFET**
-- **2019-09-02**: Out from the water for maintenance and cleaning only.
-- **2018-04-17**: seaFET #1005 was changed on the REMOS and seaFET #007 (from Villefranche) was installed.
-Continuous mode with external power supply was set and internal pack of baterries was removed.
-Old seaFET will be brought back to France with Samir.
-- **2018-03-09**: #007 seaFET currently in USA will be sent by seabird to NYA. #1005 seaFET currently in NYA will be sent to USA for update, following all external issues, for free.
-- **2017-08-24**: seaFET #1005 was installed on the REMOS into the field.
-
-### **Cross-Flow filter**
-- **2019-01-26**: The filter was lifted up in order to fix the flow problem. 
-- **2018-11-01**: The filter clogged a lot of time even after acid cycles. It was not replaced since its initial installation with the TA analyser. We think to replace it soon.
-- **2016-07-20**: Cross filter was cleanned by Obs. eng. with 10-15 min tape water flush.
-
-### **durafet**
-- **2019-09-05**: same durafet 
-- **2017-10-30**: (13:00 UTC) Durafet holder was changed by Benoit and the new one (made by Uwe) more larger (all the durafet's body is plunge in the seawater) was installed.
-- **2017-08-24**: durafet was installed.
-
-### ***p*CO~2~**
-- **2019-09-03**: *p*CO~2~ analyser (S/N: CO2FT-0515-001) have been installed and *p*CO~2~ analyser (S/N: CO2FT-0215-001) was sent to Kiel for calibration.
-- **2018-10-31**: *p*CO~2~ analyser (S/N: CO2FT-0215-001) have been installed and *p*CO~2~ analyser (S/N: CO2FT-0515-001) was brought back to France and waiting 2019 fundings to bring it for calibration.
-- **2018-04-16**: *p*CO~2~ analyser switching by Uwe and Samir. S/N CO2FT-0515-001 is now installed. Old *p*CO~2~ sensor will be brought back to France with Samir.
-- **2017-02-07**: pCO2 analyser switching by Uwe. S/N CO2FT-0215-001 is now installed.
-- **2016-09-13**: Changement of the *p*CO~2~ S/N CO2FT-0515-001 membrane (Uwe from 4H-Jena).
-- **2016-02-28**: *p*CO~2~ analyser (S/N CO2FT-0215-001) was sent to calibration and the second *p*CO~2~ analyser (S/N: CO2FT-0515-001) have been installed.
-
-<div style="text-align:center" markdown="1">
-<img  src="./Images/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200">
-<img  src="./Images/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200">
-</div>
-
-## Script + data
-<div style="text-align: justify">  
-Here is reported all important modifications made on *ny-alesund_cc.*.
-All documents concerning maintenance, tasks to do, calibration... are accessible by the AWIPEV staff on this link with special access:
-
-[wiki document](https://spaces.awi.de)
-
-[Logbook discrete sampling](https://docs.google.com/spreadsheets/d/1bNh9q4bkNoh2ra78XC451EmGb9Q8kMf4ByBnKngeHOg/edit#gid=1034421443)
-
-[Logbook FerryBox](https://docs.google.com/spreadsheets/d/1QwAJm7TttoEwue-CUM0efhqEAMwj5m148Gy_Mp-1maM/edit?ts=5ed0fca6#gid=2036495380)
-
-[UWO-Ferrybox variables from our sensors](https://docs.google.com/spreadsheets/d/1arKYfUjmg3YrgQ5g9LN_XFwUORyz7nqlKNWq3uYok3U/edit?ts=5c7e1d16#gid=393659093)
-
-[Dashboard](https://dashboard.awi.de/?dashboard=3760)
-
-[Procedure to download NRT data](https://spaces.awi.de/confluence/display/MOS/NRT+data+download+procedures)
-
-[AWI NRT database](https://dashboard.awi.de/data-xxl/), search for svluwobs
-
-[Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736)
-
-### **FerryBox**
-- **2020-03-13**: Salinity was filtered above 28 in d_all.rds file.
-- **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.
-
-### **pH seaFET**
-- **2018-08-30**: voltINT + phINT were filtered from 2017-12-14 to 2018-01-08 and bad data were removed from 2018-01-08 to 2018-02-02.
-pH spectro from 2018-04-16 07:00:00 was fitted with a mean of 4 days of voltINT in order to make the calibration for this 5th period.
-- **2018-07-30**: Flag location (location_flag) is added in the script to localize seaFET/durafet discrete samples: flag 1 = at the harbor (not taken in consideration) and flag 0 = in the FB for durafet or on site for seaFET (takken in consideration as "normal" sampling").
-See seaFET part.
-- **2018-02-02**: Based on Darrell's advices (SeaBird), Philipp implemented the seaFET as: 1h periodic sampling with the following commands: perdival 1h, navg 5, brstsize 1, opermode periodic. 
-- **2017-12-29**: "SVL_20171218_010426.dat" from seaFet data was deleted because of bug with its size (0 octect). pH filter was added to "ny_alesund_cc" file for seaFet data (<7.5 and <8.5).
-
-### **Durafet**
-- Reference spectro measurement from the 2019-01-18 11:00 do not match with a durafet raw data because Ferrybox was off.
-This reference point was not takken in consideration for calibration.
-The window of the previous and next calibration periods was extended.
-
-### ***p*CO~2~**
-- **2020-03-11**: Post calibration parameters for period 4 (2018-04-16 to 2018-10-31) were not taken in consideration because they lead to wrong correction.
-- **2019-11-18**: Calibration parameters from #0215-001 were added to "server.../data/NRT_data/Data_Processing_sheet_pCO2.csv" (new path).
-- **2018-08-29**: Calibration parameters from #0215-001 were added to "./data/Calibration_pCO2/Data_Processing_sheet_pCO2.csv".
-- **2018-04-20**: For *p*CO~2~ Calibration the previous period (N° 4) was added to the script "ny-alesund_cc" line 466.
-- **2015-10-13**: we put back the spike.pCO2 to 600 because data in October reached more than 350 µAtm. We let this like that and we are going to deal with it manually later if needed.
-- **2015-09-28**: we put the spike.pCO2 (detection of peaks: threshold) at 350 to remove anomalies on the 12 and 15 September. We have to monitor data. If data reach this value, then problem.
-
-### **SNAPO**
-- **2020-01-23**: Freezed and lost samples because of heater issue in the container: 15/11/2019 (durafet x1), 03/12/2019 (FB x2), 11/12/2019 (FB x2), 13/12/2019 (FB x2), 20/12/2019 (FB x2), 03/01/2020 (FB x2).
-Following samples could have been frozen, not sure: 06/09/2019 (FB x2), 13/09/2019 (seaFET x1), 13/09/2019 (FB x2), 20/09/2019 (FB x1), 27/09/2019(FB x2), 04/10/2019 (FB x2), 11/10/2019 (FB x1), 11/10/2019  (durafet x1), 25/10/2019 (FB x2), 01/11/2019 (FB x1), 15/11/2019 (FB x1).
-
-- **2020-01-15**: Results from 2019-04-19 to 2019-08-31 (sent in September 2019) were received.
-FB duplicates from 2019-08-09 were analysed as Durafet because of wrong box.
-One sample from 2019-06-07 (durafet) was analysed by Paris because of wrong box.
-- **2019-04-30**: Duplicate "Ferrybox" samples (SN0316 and SN264, 2019-02-22 14:05) were sent by mistake in Villefranche for pH measurements.
-Those results were put in the datafile as "durafet" samples as soon as they are comming from the Ferrybox tape seawater.
-We will add a lack of DIC for this week.
-TA will be measured in Villefranche.
-- **2018-08-30**: flag of 1 AT duplicate (2205) from 2017-08-31 was put to 3 (dosage douteux).
-
-### **Files - server**
-- **2019-11-15**: Script including the new data downloading from the NRT AWI database is running (ny-alesund_cc.R).
-From this date, data are donwloaded from AWI NRT dtabase.
-We are waiting some setting from Philipp to have the entire dataset.
-Only 2018-2019 are available for the moment.
-New path was created in the server and pCloud/exp168 with "NRT_data" file.
-Please see the picture bellow.
-- **2018-04-19**: Since "Ferrybox" is on again, the adding to solve the files issues are making not data into d_hour for this period (2018-09-03 to 2018-14-04).
-This adding was put in comments now.
-In seaFET data reading, S/N have been changed from 1005 to 0007.
-- **2018-03-21**: Files issues.
-FerryBox instruments are down because of freezing but UWO instrument as seaFET and SBE38 are OK.
-Removing of one 0 octet file from seaFET20180317_1404 and put back seaFET files from 20180309 to 20180312 in seaFET folder.
-They were in SBE38 folder...Weird.
-Additionnal script lines were added in order to deal with the issue of "in situ" created date whereas "Ferrybox" created data ware not.
-Since "in situ" parameters are running (d df) and not "in ferrybox" parameters (z df), the new datetime lines are not taking in consideration with the left_join function we have to add them during Ferrybox shutdown.
-- **2018-03-09**: Script issue solved with first negative values encountred in SBE38 files. We find a regex solution to take "space + space or negative value" in consideration.
-- **2017-11-07**: Wrong seaFET files (wrong datetime starting on the 5th September) from 24 to 26 October were fixed.
-File "SVL_20171024_030426_to_20171026_110425_SeaFet-1005.txt" were created in SeaFet_archive.
-
-### Data processing
-#### Script ny-alesund_cc.R which runs on awipev@awipev-co2.obs-vlfr.fr
-* reads data from the AWI NRT database [Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736) 
-* calibrates pCO2 data
-* data cleaning:
-  + Argo Global Range Test.
-  + filter salinities above 28
-  + filter temperatures above 10
-  + filter seaFET Volt (outliers)
-  + filter seaFET pH (outliers)
-  + filter durafet (outliers)
-* Quality flags
-    + 1: good data
-    + 3: impossible date and time test
-    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
-    + 6: failing the manufacturer range test (not used)
-    + 7: failing the regional range test 
-    + 12: failing the spike test (NAs from despike)
-    + 13: failing the gradient test
-    + 15: the instrument was not deployed or operated
-    + 16: acid flush
-    + 99: failing the final visual inspection of the data. 
-* Despike using oce::despike with n=2, k=5761
-* Files generated:
-    + previous_NRT_data.rds: all NRT data without alteration from the beginning (2015)
-    + all_nydata_minute.rds: all data after filtering and despike describe above (every minute)
-    + all_nydata_hour.rds: hourly means of all data after filtering and despike describe above (every minute)
-    + nydata_minute.rds: selected data after filtering and despike describe above (every minute). **Useful?**
-    + nydata_hour.rds: selected hourly means of all data after filtering and despike describe above (every minute).  This is for further data processing.
-
-#### Script awipev-co2.Rmd which runs locally
-* reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
-* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
-* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
-* pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
-* calibrate seafet pH
-    - ph_s_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
-    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
-    - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
-* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
-* despike pH seaFET
-* calibrate durafet pH
-    - ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
-* Relation at / sal_mix 
-* at_calc: calculé from sal_mix
-* saves locally d_all.rds which comprises all variables plus those generated in the script
-
-### Villefranche Server informations
-
-* Serveur : awipev-co2 (193.50.85.104)
-* 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer mais n'est plus utilisé).
-* Pour se connecter à awipev-co2.obs-vlfr.fr
-    + ssh awipev@awipev-co2.obs-vlfr.fr
-* Intervention sur le serveur :
-    + ssh awipev@awipev-co2.obs-vlfr.fr
-    + rebooting Ubuntu server: sudo shutdown -r now
-    + to check versions:
-        - dpkg -l | grep shiny
-        - dpkg -l | grep r-base
-    + To update Ubuntu, R and its packages:
-        - sudo su
-        - apt-get upgrade
-    + To restart shiny server: sudo systemctl restart shiny-server
-        - update shiny server: follow procedure detailed on the shiny web page Data processing
-* To install R packages:
-    + ssh gattuso@awipev-co2.obs-vlfr.fr
-    + sudo R (then password)
-    + install.packages("tidyverse")
-
-**crontab awipev@awipev-co2.obs-vlfr.fr**
-
-Si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync.
-Pattern des commandes : # m h dom mon dow command
-
-* (Every 4 hour on the hour, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
-    + 00 *//1 * * * cd $HOME; USER=awipev R --vanilla < ny-alesund/R/ny-alesund_cc.R > ny-alesund/R/log_ny-alesund_cc.txt 2>&1
-* (Every 4 hour at 10 min past the hour, the web page is generated)
-    + 10 *//1 * * * cd web; USER=awipev bash awipev-co2.sh > awipev-web.log 2>&1 
-* (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud ... Exp168)
-    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
-* (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)
-    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
-
-### Web page
-
-* La page web index.html est faite sur le serveur awipev/web grâce au script awipev-CO2_web.Rmd puis transférée et renommée dans awipev/awipev-CO2_web
-* Création du répertoire web qui contient ce qu’il faut pour générer la page web:
-    + AWIPEV-Logo.jpg
-    + Discrete_sampling_AWIPEV.csurv
-    + awipev-CO2_web.Rmd
-    + awipev-co2.sh (lancer par bash awipev-co2.sh)
-* Accessible https://awipev-co2.obs-vlfr.fr 
-* On utilise un shell script awipev-co2.sh :
-
-    #!/bin/bash
-
-    # script de lancement via crontab echo '---------deb awipev-co2.sh -----------'
-
-    # On lance la fabrication du html (une seule ligne)
-    cd web; R -e 'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html
-
-    echo '---------fin awipev-co2.sh -----------'
-
-A la main dans le terminal, cela donne :
-
-* ssh awipev@awipev-co2.obs-vlfr.fr
-* cd; bash web/awipev-co2.sh
-
-![ ](Images/awipev_server_arborescence.jpg){width=65%}

### 2020-11-09 awipev-CO2_PAR_sal.Rmd
impossible to make Dygraph

@@
 ```{r PAR / SAL relationship, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
- d_all<- d_all %>%
-  dplyr::mutate(
-    datetime =ymd_hms(datetime))
+#xts + dygraph
+sal_xts <- dplyr::select(d_all, datetime,sal_insitu_ctd_1m)
+#, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m)
 
-sal_xts <- dplyr::select(d_all, datetime,sal_insitu_ctd_1m)
-, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m)
+ # sal_xts<- sal_xts %>% 
+ #  dplyr::mutate(sal_insitu_ctd_1m = case_when(
+ #    is.na(sal_insitu_ctd_1m) ~ 0,
+ #    TRUE~ sal_insitu_ctd_1m))
 
- sal_xts<- sal_xts %>% 
-  dplyr::mutate(sal_insitu_ctd_1m = case_when(
-    is.na(sal_insitu_ctd_1m) ~ 0,
-    TRUE~ sal_insitu_ctd_1m))
-
-sal_xts <- as.xts(sal_xts, order.by = as.Date(d_all$datetime))
+sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
 dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
-            dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
-            dySeries("sal_mix", color = "red", strokeWidth = 0, label = "sal_mix") %>%
+            dySeries("sal_insitu_ctd_1m", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
 dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%

### 2020-11-10 awipev-CO2_PAR_sal.Rmd
dygraph fixed and RDM finished

@@
 ```
+## Plot
 
-```{r PAR / SAL relationship, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
+```{r PAR / SAL Dygraph, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
 #xts + dygraph
-sal_xts <- dplyr::select(d_all, datetime,sal_insitu_ctd_1m)
-#, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m)
-
- # sal_xts<- sal_xts %>% 
- #  dplyr::mutate(sal_insitu_ctd_1m = case_when(
- #    is.na(sal_insitu_ctd_1m) ~ 0,
- #    TRUE~ sal_insitu_ctd_1m))
+sal_xts <- dplyr::select(d_all, datetime,sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m)%>%
+   dplyr::filter(!is.na(datetime))
 
@@
 dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
-            dySeries("sal_insitu_ctd_1m", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
+   dySeries("sal_insitu_ctd_1m", color = "blue", strokeWidth = 0, label = "SAL 1 m") %>%
+   dySeries("sal_insitu_ctd_3m", color = "blue", strokeWidth = 0, label = "SAL 3 m") %>%
+   dySeries("sal_insitu_ctd_5m", color = "blue", strokeWidth = 0, label = "SAL 5 m") %>%
+   dySeries("sal_insitu_ctd_7m", color = "blue", strokeWidth = 0, label = "SAL 7 m") %>%
+   dySeries("sal_insitu_ctd_9m", color = "blue", strokeWidth = 0, label = "SAL 9 m") %>%
+   dySeries("par_insitu_profile_1m", color = "red", strokeWidth = 0, label = "PAR 1 m",axis = "y2") %>%
+   dySeries("par_insitu_profile_3m", color = "red", strokeWidth = 0, label = "PAR 3 m",axis = "y2") %>%
+   dySeries("par_insitu_profile_5m", color = "red", strokeWidth = 0, label = "PAR 5 m",axis = "y2") %>%
+   dySeries("par_insitu_profile_7m", color = "red", strokeWidth = 0, label = "PAR 7 m",axis = "y2") %>%
+   dySeries("par_insitu_profile_9m", color = "red", strokeWidth = 0, label = "PAR 9 m",axis = "y2") %>%
+
 dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
     dyLegend(show = "follow")   %>%
-    dyAxis("y",valueRange = c(30, 37)) %>%
+   dyAxis("y2",valueRange = c(0, 1350), label = "PAR") %>%
       dyRangeSelector(height = 30, dateWindow= NULL)
+```
 
+## Relationships
+
+```{r PAR / SAL relationship, echo=FALSE, fig.asp=0.5, out.width = "100%", message=FALSE, warning=FALSE}
 #1m

### 2020-11-12 awipev-CO2_PAR_sal.Rmd
add space between 14-15 for test

@@
 Sys.setlocale("LC_ALL", "en_US.UTF-8")
+
 Sys.setenv(TZ='UTC') # on utilise UTC

### 2020-11-12 paper.Rmd

@@
 ```{r calculate missing, echo=FALSE, warning=FALSE, message=FALSE}
+zz <- d %>%
+  group_by_key() %>%
+  index_by(quarter = ~ quarter(.)) %>% # monthly aggregates
+  summarise(
+    sal_fb_na = sum(!is.na(sal_fb))/n())
+zz
 
-var_list <- c("sal_fb", "temp_fb")
-n_na <- NULL
-for (i in 1:length(var)) {
-  na <- sum(!is.na([[i]]))
-  a
-}
-
-pc_na <- function(x=df) {
-  NAs <- as.tibble(map_df(x, function(x) sum(!is.na(x)))) %>% # number of NAs
-    dplyr::select(-datetime)
-  NAs <- as.data.frame(t(NAs))
-  n <- nrow(x) # total number of rows
-  pc_na <- n_na/n #fraction of NAs
-  NAs$pc <- pc_na$V1
-  return(NAs)
-}
-tmp <- d %>% 
-  as_tibble() %>% 
-  dplyr::select(pH_s_seafet_temp_ctd, par_air_filtered, pco2_contros, pH_s_seafet_temp_ctd, starts_with("sal_"),
-                starts_with("temp_"), at_calc, year_month, quarter) %>%
-  summarize()
+zz <- d %>%
+  group_by_key() %>%
+  index_by(year_month = ~ yearmonth(.)) %>% # monthly aggregates
+  summarise(
+    sal_fb_na = sum(!is.na(sal_fb))/n())
+zz
 

### 2020-11-13 awipev-CO2_PAR_sal.Rmd

@@
 ```
-## Plot
+
+```{r data filter, echo=FALSE, fig.height=4, fig.width=10, message=FALSE, warning=FALSE}
+#select mummer months
+june2018 <- d_all %>%
+  dplyr::select(datetime, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m, par_air, turb_fb, sal_fb, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
+  dplyr::filter(datetime >= "2018-06-01 00:00:00" & datetime <= "2018-06-30 23:59:59")%>% 
+  dplyr::mutate(day = day(datetime))
+
+july2018 <- d_all %>%
+  dplyr::select(datetime, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m, par_air, turb_fb, sal_fb, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
+  dplyr::filter(datetime >= "2018-07-01 00:00:00" & datetime <= "2018-07-31 23:59:59")%>% 
+  dplyr::mutate(day = day(datetime))
+
+august2018 <- d_all %>%
+  dplyr::select(datetime, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m, par_air, turb_fb, sal_fb, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
+  dplyr::filter(datetime >= "2018-08-01 00:00:00" & datetime <= "2018-08-31 23:59:59") %>% 
+  dplyr::mutate(day = day(datetime))
+
+# summarise the max PAR/sal by day
+sumjune2018 <- june2018 %>% 
+  dplyr::group_by(day) %>% 
+  dplyr:: summarise(maxPAR1m = max(par_insitu_profile_1m, na.rm=TRUE),
+                  maxPAR3m = max(par_insitu_profile_3m, na.rm=TRUE),
+                  maxPAR5m = max(par_insitu_profile_5m, na.rm=TRUE),
+                  maxPAR7m = max(par_insitu_profile_7m, na.rm=TRUE),
+                  maxPAR9m = max(par_insitu_profile_9m, na.rm=TRUE),
+                  maxSAL1m = max(sal_insitu_ctd_1m, na.rm=TRUE),
+                  maxSAL3m = max(sal_insitu_ctd_3m, na.rm=TRUE),
+                  maxSAL5m = max(sal_insitu_ctd_5m, na.rm=TRUE),
+                  maxSAL7m = max(sal_insitu_ctd_7m, na.rm=TRUE),
+                  maxSAL9m = max(sal_insitu_ctd_9m, na.rm=TRUE),
+                  maxPARair = max(par_air, na.rm=TRUE),
+                  nb =n())
+
+sumjuly2018 <- july2018 %>% 
+  dplyr::group_by(day) %>% 
+  dplyr:: summarise(maxPAR1m = max(par_insitu_profile_1m, na.rm=TRUE),
+                  maxPAR3m = max(par_insitu_profile_3m, na.rm=TRUE),
+                  maxPAR5m = max(par_insitu_profile_5m, na.rm=TRUE),
+                  maxPAR7m = max(par_insitu_profile_7m, na.rm=TRUE),
+                  maxPAR9m = max(par_insitu_profile_9m, na.rm=TRUE),
+                  maxSAL1m = max(sal_insitu_ctd_1m, na.rm=TRUE),
+                  maxSAL3m = max(sal_insitu_ctd_3m, na.rm=TRUE),
+                  maxSAL5m = max(sal_insitu_ctd_5m, na.rm=TRUE),
+                  maxSAL7m = max(sal_insitu_ctd_7m, na.rm=TRUE),
+                  maxSAL9m = max(sal_insitu_ctd_9m, na.rm=TRUE),
+                  maxPARair = max(par_air, na.rm=TRUE),
+                  nb =n())
+
+sumaugust2018 <- august2018 %>% 
+  dplyr::group_by(day) %>% 
+  dplyr:: summarise(maxPAR1m = max(par_insitu_profile_1m, na.rm=TRUE),
+                  maxPAR3m = max(par_insitu_profile_3m, na.rm=TRUE),
+                  maxPAR5m = max(par_insitu_profile_5m, na.rm=TRUE),
+                  maxPAR7m = max(par_insitu_profile_7m, na.rm=TRUE),
+                  maxPAR9m = max(par_insitu_profile_9m, na.rm=TRUE),
+                  maxSAL1m = max(sal_insitu_ctd_1m, na.rm=TRUE),
+                  maxSAL3m = max(sal_insitu_ctd_3m, na.rm=TRUE),
+                  maxSAL5m = max(sal_insitu_ctd_5m, na.rm=TRUE),
+                  maxSAL7m = max(sal_insitu_ctd_7m, na.rm=TRUE),
+                  maxSAL9m = max(sal_insitu_ctd_9m, na.rm=TRUE),
+                  maxPARair = max(par_air, na.rm=TRUE),
+                  nb =n())
+# tables
+kable(sumjune2018, caption ="June 2018")
+kable(sumjuly2018, caption ="July 2018")
+kable(sumaugust2018, caption ="August 2018")
+```
+### Plot
 
@@
 #xts + dygraph
-sal_xts <- dplyr::select(d_all, datetime,sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m)%>%
+sal_xts <- dplyr::select(d_all, datetime,sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m, par_insitu_profile_1m, par_insitu_profile_3m, par_insitu_profile_5m, par_insitu_profile_7m, par_insitu_profile_9m, par_air)%>%
    dplyr::filter(!is.na(datetime))
@@
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
-dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
+dygraph(sal_xts, group = "awipev", main="Salinity and PAR (in field)", ylab="") %>%
    dySeries("sal_insitu_ctd_1m", color = "blue", strokeWidth = 0, label = "SAL 1 m") %>%
@@
    dySeries("par_insitu_profile_9m", color = "red", strokeWidth = 0, label = "PAR 9 m",axis = "y2") %>%
-
+     dySeries("par_air", color = "orange", strokeWidth = 0, label = "PAR AIR",axis = "y2") %>%
 dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
       dyRangeSelector(height = 30, dateWindow= NULL)
+
+#plot 2
+#Delete the NA line with datetime
+fb_xts <- dplyr::select(d_all, datetime,sal_fb, turb_fb)
+fb_xts <- fb_xts[-which(is.na(fb_xts$datetime)),]
+fb_xts <- as.xts(fb_xts, order.by = fb_xts$datetime)
+dygraph(fb_xts, group = "awipev", main="Salinity and Turbidity (in FerryBox)", ylab="") %>%
+   dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "SAL FB") %>%
+   dySeries("turb_fb", color = "brown", strokeWidth = 0, pointSize = 4,label = "Turb FB",axis = "y2") %>%
+dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
+      dyOptions( drawGrid = TRUE, drawPoints = TRUE, pointSize = 2,useDataTimezone = TRUE) %>%
+    dyLegend(show = "follow")   %>%
+  dyAxis("y2",valueRange = c(0, 1000), label = "PAR") %>%
+      dyRangeSelector(height = 30, dateWindow= NULL)
 ```
 
-## Relationships
+## Relationships by depths (first test)
 
@@
 ```
+
+## Relationships by summer months (second test)
+
+```{r PAR / SAL relationship summer months, echo=FALSE, fig.asp=0.5, out.width = "100%", message=FALSE, warning=FALSE}
+#june
+fit <- lm(data = sumjune2018, maxPAR7m ~ maxSAL7m)
+p_june <- ggplot(sumjune2018,aes(x=maxSAL7m, y= maxPAR7m, label = day))+
+  geom_text( aes(color=factor(day))) +
+  scale_color_discrete(guide="none")+
+    labs(x="Salinity June 7 m", y="PAR June 7 m", color = "Days")  +
+    stat_smooth(method = "lm", col = "black") +
+    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
+                       ";\nSlope =",signif(fit$coef[[2]], 5),
+                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
+                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
+  ylim(0,1500) +
+  theme_bw() + theme(aspect.ratio=1,
+        axis.text=element_text(size=7),
+        axis.title.y= element_text(size =7),
+        axis.title.x= element_text(size =7),
+        plot.margin = unit(c(0.5,1,1,1), "cm"),
+        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
+#july
+fit <- lm(data = sumjuly2018, maxPAR7m ~ maxSAL7m)
+p_july <- ggplot(sumjuly2018,aes(x=maxSAL7m, y= maxPAR7m, label = day))+
+  geom_text( aes(color=factor(day))) +
+  scale_color_discrete(guide="none")+
+    labs(x="Salinity July 7 m", y="PAR July 7 m", color = "Days")  +
+    stat_smooth(method = "lm", col = "black") +
+    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
+                       ";\nSlope =",signif(fit$coef[[2]], 5),
+                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
+                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
+  ylim(0,1500) +
+  theme_bw() + theme(aspect.ratio=1,
+        axis.text=element_text(size=7),
+        axis.title.y= element_text(size =7),
+        axis.title.x= element_text(size =7),
+        plot.margin = unit(c(0.5,1,1,1), "cm"),
+        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
+
+#august
+fit <- lm(data = sumaugust2018, maxPAR7m ~ maxSAL7m)
+p_august <- ggplot(sumaugust2018,aes(x=maxSAL7m, y= maxPAR7m, label = day))+
+  geom_text( aes(color=factor(day))) +
+  scale_color_discrete(guide="none")+
+    labs(x="Salinity August 7 m", y="PAR August 7 m", color = "Days")  +
+    stat_smooth(method = "lm", col = "black") +
+    labs(main ="August 2018", title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
+                       ";\nSlope =",signif(fit$coef[[2]], 5),
+                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
+                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
+  ylim(0,1500) +
+  theme_bw() + theme(aspect.ratio=1,
+        axis.text=element_text(size=7),
+        axis.title.y= element_text(size =7),
+        axis.title.x= element_text(size =7),
+        plot.margin = unit(c(0.5,1,1,1), "cm"),
+        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
+
+print(p_june)
+print(p_july)
+print(p_august)
+```

### 2020-12-07 paper.Rmd
dunno

@@
 
-d_all <- readRDS(file = paste0(path_data, "fb_data/d_all_copy.rds"))
+d_all <- readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
 d <- d_all %>% 
@@
 
-tmp visdat::vis_miss(tmp)
-gg_miss_var(tmp, facet = quarter)
+visdat::vis_miss(zz)
+#gg_miss_var(zz, facet = quarter)
 

### 2020-12-19 paper.Rmd
nothing

@@
     sal_fb_na = sum(!is.na(sal_fb))/n())
-zz
 

### 2020-12-20 prettyaxes.R
nothing3

@@ -1,4 +1,0 @@
- box()
- axis(1,labels=FALSE, tcl=-0.35) ; axis(1, lwd=0, line=-0.4, labels=TRUE)
- axis(2,labels=FALSE,tcl=-0.35)  ; axis(2, lwd=0, line=-0.4, las=2, labels=TRUE)
- axis(3,labels=FALSE,tcl=-0.35) ; axis(4,labels=FALSE,tcl=-0.25)

### 2020-12-21 paper.Rmd
fixed figure time series

@@
 d_ts <- d %>%
-  dplyr::mutate(pH_s_seafet_temp_ctd = ifelse(depth >= 8, pH_s_seafet_temp_ctd, NA)) %>% # keep only seafet data below 8 m depth
-  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air_filtered, PCO2_Corr_filtered, pH_s_seafet_temp_ctd, at_calc, at) #%>%
+  #dplyr::mutate(pHint_tot_sf = ifelse(depth >= 8, pHint_tot_sf, NA)) %>% # keep only seafet data below 8 m depth
+  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_corr,
+                pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
   #tidyr::pivot_longer(-datetime, values_to = "value")
@@
 ts_par_air <- d_all %>%
-  ggplot(aes(x = datetime, y = par_air_filtered), na.rm=TRUE) +
+  ggplot(aes(x = datetime, y = par_air), na.rm=TRUE) +
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
@@
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(aes(x = datetime, y = pco2_contros), 
+  geom_point(aes(x = datetime, y = pco2_corr), 
              colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-  geom_point(aes(x = datetime, y = pco2calc), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
   labs(title="Mesured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
@@
 ts_pH <- d_all %>%
-  ggplot(aes(x = datetime, y = pH_s_seafet_temp_ctd), na.rm=TRUE) +
+  ggplot(aes(x = datetime, y = pHint_tot_sf_9m), na.rm=TRUE) +
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-  labs(title="In situ pH (> 8 m)",x="", y=expression(paste(pH[T]))) +
+  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  labs(title="In situ pH below 8 m (seaFET in blue, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
   Mytheme(size_labs = 8)

### 2020-12-21 awipev-CO2.Rmd
minor chnages

@@
 library("hms")
-if (!require("ragg")) install.packages("hms")
+if (!require("ragg")) install.packages("ragg")
 library("ragg")
@@
 pH_seafet <- pH_seafet %>% 
-  dplyr::mutate(ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, S = pH_seafet$sal_mix, Pt = 0, Sit = 0))
+  dplyr::mutate(ph_s_sf_temp_insi = 
+                  pHinsi(pH = pH_seafet$ph_s_sf, 
+                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, 
+                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
+                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0))
 

### 2020-12-28 paper.Rmd
clean up and chnaged variable names

@@
 ```{r read and clean data, echo=FALSE, warning=FALSE, message=FALSE}
-  # d_all <- readRDS(file = paste0(path_data, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_hour_copy.rds"))
-# d <- d_all %>% 
-#   as_tsibble(index = datetime) %>% 
-#   dplyr::rename(depth = pressure_insitu_ctd) %>% 
-#   dplyr::mutate(year_month = format(datetime, '%Y-%m'))
-# count_gaps(d, .full = TRUE)
-
 d_all <- readRDS(file = paste0(path_data, "fb_data/d_all.rds"))
@@
                 quarter = quarter(datetime)) %>%
+  dplyr::rename(pco2_contros = pco2_corr) %>% 
   replace(., is.na(.), NA) # replace NaN by NA everywhere
@@
 d_ts <- d %>%
-  #dplyr::mutate(pHint_tot_sf = ifelse(depth >= 8, pHint_tot_sf, NA)) %>% # keep only seafet data below 8 m depth
-  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_corr,
+  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_contros,
                 pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
@@
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(aes(x = datetime, y = pco2_corr), 
+  geom_point(aes(x = datetime, y = pco2_contros), 
              colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
@@
 ts_pCO2_bp <- d_all %>%
-  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_contros)) +
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pCO2_contros)) +
   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
@@
 Temperature <- qq(d_all$temp_fb, digits=1)
-pCO2 <- qq(d_all$pco2_contros, digits=1)
+pCO2 <- qq(d_all$pCO2_contros, digits=1)
 pH <- qq(d_all$pHint_tot_sf, digits=3)

### 2020-12-29 awipev-CO2.Rmd
added note
clean up and chnaged variable names
Read nutrient data

@@
 
-```{r read and prepare discrete data, echo=FALSE, warning=FALSE, message=FALSE}
+```{r read and prepare discrete AT+CT, echo=FALSE, warning=FALSE, message=FALSE}
 d <- tibble(
@@
 ```
-
+```{r read and prepare nutrients, echo=FALSE, warning=FALSE, message=FALSE}
+# File "Ferrybox nutrients 2014-2018.xlsx" provided by 
+# Willem van de Poll <w.h.van.de.poll@rug.nl> on 2020-01-16
+nuts <- readxl::read_excel(paste0(path, "fb_data/Ferrybox nutrients 2014-2018.xlsx"),
+                           skip =1) %>% 
+  drop_na(date) %>% 
+  dplyr::mutate(dt = as.POSIXct(paste0(date, " 12:00:00"))) # assuming sampling time 12:00
+nuts
+```
 ```{r Combine discrete and continous data, echo=FALSE}
@@
 # By convention, a negative flux indicates fluxes directed from the atmosphere to the ocean, and a positive flux indicates fluxes directed from the ocean to the atmosphere.
+
+##TO DO: check calculations by Miller et al. (2020); use formulation of Wanninkhof 2014?
 d_all <- d_all %>%

### 2020-12-29 awipev-CO2.Rmd
Merge nutrient data

@@
 library("skimr")
+if (!require("FNN")) install.packages("FNN")
+library("FNN")
 
@@
   drop_na(date) %>% 
-  dplyr::mutate(dt = as.POSIXct(paste0(date, " 12:00:00"))) # assuming sampling time 12:00
+  dplyr::mutate(datetime = as.POSIXct(paste0(date, " 12:00:00"))) %>% # assuming sampling time 12:00
+  dplyr::filter(datetime > as.POSIXct("2015-07-09"))
 nuts
+
+# The nearest times
+time_index <- unique(d_all$datetime)
+# nuts$closest <- time_index[
+#   FNN::knnx.index(time_index, # The values to be queried (big df)
+#                   as.vector(nuts$datetime), # The value to find the closest match to (small df)
+#                   k = 1)] # The number of closest values to return
+nuts <- nuts %>% 
+  dplyr::mutate(closest = time_index[
+  FNN::knnx.index(time_index, # The values to be queried (big df)
+                  as.vector(nuts$datetime), # The value to find the closest match to (small df)
+                  k = 1)]) %>%  # The number of closest values to return
+  dplyr::select(-date, -datetime) %>% 
+  dplyr::rename(NO3NO2 = `NO3+NO2`)
+tmp <- left_join(d_all, nuts, by = c("datetime" = "closest"))
+
 ```

### 2020-12-29 awipev-CO2.Rmd
Merge nutrient data

@@
   dplyr::rename(NO3NO2 = `NO3+NO2`)
-tmp <- left_join(d_all, nuts, by = c("datetime" = "closest"))
-
+d_all <- left_join(d_all, nuts, by = c("datetime" = "closest"))
 ```

### 2020-12-30 awipev-CO2.Rmd
split read nuts and analyze impacts

--- 2020-12-29 awipev-CO2.Rmd
@@
 library("skimr")
+if (!require("FNN")) install.packages("FNN")
+library("FNN")
+if (!require("patchwork")) install.packages("patchwork")
+library("patchwork")
 
@@
 # Add the flag location: some samples have been collected at the pier. Notes them here.
-# Flag 1 = collected on the peer by Niskin and flag 0 = collected in the FB (normal collect)
+# Flag 1 = collected on the pIer by Niskin and flag 0 = collected in the FB (normal collect)
  # And keep data with flag 0 for FB location
@@
                    )
-                 ), by = "closest_datetime")
+                 ), by = "closest_datetime") %>% 
+  dplyr::select(-closest_datetime)
 
@@
 ```
-```{r read and prepare nutrients, echo=FALSE, warning=FALSE, message=FALSE}
+```{r read and prepare nutrient data, echo=FALSE, warning=TRUE, message=FALSE}
 # File "Ferrybox nutrients 2014-2018.xlsx" provided by 
 # Willem van de Poll <w.h.van.de.poll@rug.nl> on 2020-01-16
+# nutrients in umol/l
 nuts <- readxl::read_excel(paste0(path, "fb_data/Ferrybox nutrients 2014-2018.xlsx"),
@@
   drop_na(date) %>% 
-  dplyr::mutate(dt = as.POSIXct(paste0(date, " 12:00:00"))) # assuming sampling time 12:00
-nuts
-```
+  dplyr::mutate(datetime = as.POSIXct(paste0(date, " 12:00:00"))) %>% # assuming sampling time 12:00
+  dplyr::filter(datetime > as.POSIXct("2015-07-09"))
+# The nearest times
+time_index <- unique(d_all$datetime)
+# nuts$closest <- time_index[
+#   FNN::knnx.index(time_index, # The values to be queried (big df)
+#                   as.vector(nuts$datetime), # The value to find the closest match to (small df)
+#                   k = 1)] # The number of closest values to return
+nuts <- nuts %>% 
+  dplyr::mutate(closest = time_index[
+  FNN::knnx.index(time_index, # The values to be queried (big df)
+                  as.vector(nuts$datetime), # The value to find the closest match to (small df)
+                  k = 1)]) %>%  # The number of closest values to return
+  dplyr::select(-date, -datetime) %>% 
+  dplyr::rename(NO3NO2 = `NO3+NO2`)
+# cleanup and convert in umol/kg
+d_all <- left_join(d_all, nuts, by = c("datetime" = "closest")) #%>% 
+  #dplyr::select(-closest_datetime)
+d_all <- d_all %>% 
+  dplyr::mutate(density_fb = seacarb::rho(S = sal_fb, T = temp_fb, P = 0),
+                PO4 = PO4 / (density_fb/1000),
+                NH4 = NH4 / (density_fb/1000),
+                NO3NO2 = NO3NO2 / (density_fb/1000),
+                NO3 = NO3 / (density_fb/1000),
+                Si = Si / (density_fb/1000)
+  )
+```
+
 ```{r Combine discrete and continous data, echo=FALSE}
@@
 It is part of the German Project COSYNA (Coastal Observation Systems of the Northern- and Arctic Seas), which aims at increasing the availability of continuous real-time data from remote but climatically-sensitive ecosystems.
-The AWIPEV underwater observatory comprises a fully remote controlled FerryBox system fed with seawater pumped in front of the old peer at 12 m depth.
+The AWIPEV underwater observatory comprises a fully remote controlled FerryBox system fed with seawater pumped in front of the old pIer at 12 m depth.
 Temperature, salinity, pressure, turbidity, oxygen, chl-*a* fluorescence are measured.
@@
 
+## Impact of nutrients
+```{r impact of nutrients, echo=FALSE, warning=TRUE, message=FALSE}
+# boxplot
+ts_PO4_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = PO4)) +
+  #geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm = TRUE) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
+  labs(y = "PO4", x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+
+ts_Si_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = Si)) +
+  #geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm = TRUE) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
+  labs(y = "Si", x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+ts_Si_bp + ts_Si_bp
+# Effects of changes in PO4 and Si
+# 1st cakculate mean values
+means <- d_all %>% 
+  group_by(montht) %>% 
+  summarize(mean_ct = mean(ct, na.rm = TRUE),
+            mean_at_calc = mean(at_calc, na.rm = TRUE),
+            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
+            mean_sal = mean(sal_fb, na.rm = TRUE),
+            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
+  ungroup()
+mean_ct <-  mean(means$mean_ct)
+mean_at_calc <-  mean(means$mean_at_calc)
+mean_pco2_calc <-  mean(means$mean_pco2_calc)
+mean_sal <-  mean(means$mean_sal)
+mean_temp <-  mean(means$mean_temp)
+# then check impacts using pco2 and AT
+carb_PO4_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = c(min(d_all$PO4/1e6, na.rm=TRUE), max(d_all$PO4/1e6, na.rm=TRUE)), Sit = 0,
+                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+diff_PO4_1 <- carb_PO4_1[1,] - carb_PO4_1[2,]
+carb_Si_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0,
+                Pt = 0, Sit = c(min(d_all$Si/1e6, na.rm=TRUE), max(d_all$Si/1e6, na.rm=TRUE)), 
+                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+diff_Si_1 <- carb_Si_1[1,] - carb_Si_1[2,]
+
+# then check impacts using AT-DIC pair
+carb_PO4_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = c(min(d_all$PO4/1e6, na.rm=TRUE), max(d_all$PO4/1e6, na.rm=TRUE)), Sit = 0,
+                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+diff_PO4_2 <- carb_PO4_2[1,] - carb_PO4_2[2,]
+carb_Si_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
+                Pt = 0, Sit = c(min(d_all$Si/1e6, na.rm=TRUE), max(d_all$Si/1e6, na.rm=TRUE)), 
+                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+diff_Si_2 <- carb_Si_2[1,] - carb_Si_2[2,]
+```
+
+The concentration of PO4 and Si varies with a factor 10 along a composite year.
+The ranges are respectively, `r round(range(d_all$PO4, na.rm = TRUE), digits = 2)` for PO4 and `r round(range(d_all$Si, na.rm = TRUE), digits = 2)` for Si.
+
+### Using the pCO2-AT pair (hourly data)
+The impact of the min max changes of PO4 on pH, DIC, and Omega_a are small:  `r round(1000*diff_PO4_1$pH, digits=2)` mpH units, `r round(1e6*diff_PO4_1$DIC, digits=2)` umol/kg for CT and `r round(diff_PO4_1$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of Si on pH, DIC, and Omega_a are small:  `r round(1000*diff_Si_1$pH, digits=2)` mpH units, `r round(1e6*diff_Si_1$DIC, digits=2)` umol/kg for CT and `r round(diff_Si_1$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+### Using the CT-AT pair (discrete data)
+The impact of the min max changes of PO4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_PO4_2$pH, digits=2)` mpH units, `r round(diff_PO4_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_PO4_2$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of PO4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_Si_2$pH, digits=2)` mpH units, `r round(diff_Si_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_Si_2$OmegaAragonite, digits=2)` for OmegaAragonite.
+
 ## Air-sea CO2 flux

### 2020-12-31 awipev-CO2.Rmd
addes impact of constants

@@
 ## Impact of nutrients
-```{r impact of nutrients, echo=FALSE, warning=TRUE, message=FALSE}
+```{r impact of nutrients, echo=FALSE, warning=FALSE, message=FALSE}
+# boxplot
+ts_PO4_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = PO4)) +
+  #geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm = TRUE) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
+  labs(y = "PO4", x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+
+ts_Si_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = Si)) +
+  #geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm = TRUE) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
+  labs(y = "Si", x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+ts_Si_bp + ts_Si_bp
+# Effects of changes in PO4 and Si
+# 1st cakculate mean values
+means <- d_all %>% 
+  group_by(montht) %>% 
+  summarize(mean_ct = mean(ct, na.rm = TRUE),
+            mean_at_calc = mean(at_calc, na.rm = TRUE),
+            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
+            mean_sal = mean(sal_fb, na.rm = TRUE),
+            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
+  ungroup()
+mean_ct <-  mean(means$mean_ct)
+mean_at_calc <-  mean(means$mean_at_calc)
+mean_pco2_calc <-  mean(means$mean_pco2_calc)
+mean_sal <-  mean(means$mean_sal)
+mean_temp <-  mean(means$mean_temp)
+# then check impacts using pco2 and AT
+carb_PO4_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = c(min(d_all$PO4/1e6, na.rm=TRUE), max(d_all$PO4/1e6, na.rm=TRUE)), Sit = 0,
+                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+diff_PO4_1 <- carb_PO4_1[1,] - carb_PO4_1[2,]
+carb_Si_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0,
+                Pt = 0, Sit = c(min(d_all$Si/1e6, na.rm=TRUE), max(d_all$Si/1e6, na.rm=TRUE)), 
+                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+diff_Si_1 <- carb_Si_1[1,] - carb_Si_1[2,]
+
+# then check impacts using AT-DIC pair
+carb_PO4_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = c(min(d_all$PO4/1e6, na.rm=TRUE), max(d_all$PO4/1e6, na.rm=TRUE)), Sit = 0,
+                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+diff_PO4_2 <- carb_PO4_2[1,] - carb_PO4_2[2,]
+carb_Si_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
+                Pt = 0, Sit = c(min(d_all$Si/1e6, na.rm=TRUE), max(d_all$Si/1e6, na.rm=TRUE)), 
+                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+diff_Si_2 <- carb_Si_2[1,] - carb_Si_2[2,]
+```
+
+The concentration of PO4 and Si varies with a factor 10 along a composite year.
+The ranges are respectively, `r round(range(d_all$PO4, na.rm = TRUE), digits = 2)` for PO4 and `r round(range(d_all$Si, na.rm = TRUE), digits = 2)` for Si.
+
+### Using the pCO2-AT pair (hourly data)
+The impact of the min max changes of PO4 on pH, DIC, and Omega_a are small:  `r round(1000*diff_PO4_1$pH, digits=2)` mpH units, `r round(1e6*diff_PO4_1$DIC, digits=2)` umol/kg for CT and `r round(diff_PO4_1$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of Si on pH, DIC, and Omega_a are small:  `r round(1000*diff_Si_1$pH, digits=2)` mpH units, `r round(1e6*diff_Si_1$DIC, digits=2)` umol/kg for CT and `r round(diff_Si_1$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+### Using the CT-AT pair (discrete data)
+The impact of the min max changes of PO4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_PO4_2$pH, digits=2)` mpH units, `r round(diff_PO4_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_PO4_2$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of PO4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_Si_2$pH, digits=2)` mpH units, `r round(diff_Si_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_Si_2$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+## Impact of choice of constants
+```{r impact of constants, echo=FALSE, warning=FALSE, message=FALSE}
 # boxplot

### 2020-12-31 awipev-CO2.Rmd
added impact of formulations for K1 and K2

@@
 ```{r impact of constants, echo=FALSE, warning=FALSE, message=FALSE}
-# boxplot
-ts_PO4_bp <- d_all %>%
-  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = PO4)) +
-  #geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm = TRUE) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
-  labs(y = "PO4", x=NULL, title=NULL) +
-  Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-
-ts_Si_bp <- d_all %>%
-  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = Si)) +
-  #geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm = TRUE) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
-  labs(y = "Si", x=NULL, title=NULL) +
-  Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-ts_Si_bp + ts_Si_bp
-# Effects of changes in PO4 and Si
-# 1st cakculate mean values
+# Compare Lueker and Sulpis
+# use mean values calculated for impacts of nutrients above
 means <- d_all %>% 
@@
 mean_temp <-  mean(means$mean_temp)
-# then check impacts using pco2 and AT
-carb_PO4_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
-                 Pt = c(min(d_all$PO4/1e6, na.rm=TRUE), max(d_all$PO4/1e6, na.rm=TRUE)), Sit = 0,
+# impacts using pco2 and AT
+carb_l_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = 0, Sit = 0,
                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-diff_PO4_1 <- carb_PO4_1[1,] - carb_PO4_1[2,]
-carb_Si_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0,
-                Pt = 0, Sit = c(min(d_all$Si/1e6, na.rm=TRUE), max(d_all$Si/1e6, na.rm=TRUE)), 
+carb_s_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = 0, Sit = 0,
+                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+diff_ls_1 <- carb_l_1 - carb_s_1
+
+# impacts using AT-DIC pair
+carb_l_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = 0, Sit = 0,
                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-diff_Si_1 <- carb_Si_1[1,] - carb_Si_1[2,]
-
-# then check impacts using AT-DIC pair
-carb_PO4_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
-                 Pt = c(min(d_all$PO4/1e6, na.rm=TRUE), max(d_all$PO4/1e6, na.rm=TRUE)), Sit = 0,
-                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-diff_PO4_2 <- carb_PO4_2[1,] - carb_PO4_2[2,]
-carb_Si_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
-                Pt = 0, Sit = c(min(d_all$Si/1e6, na.rm=TRUE), max(d_all$Si/1e6, na.rm=TRUE)), 
-                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-diff_Si_2 <- carb_Si_2[1,] - carb_Si_2[2,]
-```
-
-The concentration of PO4 and Si varies with a factor 10 along a composite year.
-The ranges are respectively, `r round(range(d_all$PO4, na.rm = TRUE), digits = 2)` for PO4 and `r round(range(d_all$Si, na.rm = TRUE), digits = 2)` for Si.
-
-### Using the pCO2-AT pair (hourly data)
-The impact of the min max changes of PO4 on pH, DIC, and Omega_a are small:  `r round(1000*diff_PO4_1$pH, digits=2)` mpH units, `r round(1e6*diff_PO4_1$DIC, digits=2)` umol/kg for CT and `r round(diff_PO4_1$OmegaAragonite, digits=2)` for OmegaAragonite.
-
-The impact of the min max changes of Si on pH, DIC, and Omega_a are small:  `r round(1000*diff_Si_1$pH, digits=2)` mpH units, `r round(1e6*diff_Si_1$DIC, digits=2)` umol/kg for CT and `r round(diff_Si_1$OmegaAragonite, digits=2)` for OmegaAragonite.
-
-### Using the CT-AT pair (discrete data)
-The impact of the min max changes of PO4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_PO4_2$pH, digits=2)` mpH units, `r round(diff_PO4_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_PO4_2$OmegaAragonite, digits=2)` for OmegaAragonite.
-
-The impact of the min max changes of PO4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_Si_2$pH, digits=2)` mpH units, `r round(diff_Si_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_Si_2$OmegaAragonite, digits=2)` for OmegaAragonite.
+carb_s_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
+                Pt = 0, Sit = 0, 
+                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+diff_ls_2 <- carb_l_2 - carb_s_2
+const <- bind_rows(diff_ls_1, diff_ls_2) %>% 
+  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
+                S = mean_sal,
+                T = mean_temp,
+                DIC = DIC * 1e6
+                ) %>% 
+  dplyr::select(flag:T, pH, pCO2, DIC, OmegaAragonite)
+kable(const, digits = c(0, 1, 1, 3, 1, 1, 2))
+```
+
+The difference induces by the choice of the carbonic acid constants is large for pH, pCO2 and DIC and negligible for OmegaAragonite.
 

### 2021-01-04 awipev-CO2.Rmd
clean up variable names

--- 2020-12-30 awipev-CO2.Rmd
@@
 output:
+  rmarkdown::
   rmarkdown::html_document:
@@
 library("patchwork")
+if (!require("pander")) install.packages("pander")
+library("pander")
 
@@
 
-```{r Read, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
+```{r read data, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
 d_hour <-
@@
   dplyr::rename(
-    pco2_corr = pco2_corr_filtered,
+    pco2 = pco2_corr_filtered,
     temp_dur = temp_dur_filtered,
@@
   dplyr::select(-date, -datetime) %>% 
-  dplyr::rename(NO3NO2 = `NO3+NO2`)
+  dplyr::rename(no3no2 = `no3+no2`)
 # cleanup and convert in umol/kg
@@
   dplyr::mutate(density_fb = seacarb::rho(S = sal_fb, T = temp_fb, P = 0),
-                PO4 = PO4 / (density_fb/1000),
-                NH4 = NH4 / (density_fb/1000),
-                NO3NO2 = NO3NO2 / (density_fb/1000),
-                NO3 = NO3 / (density_fb/1000),
-                Si = Si / (density_fb/1000)
+                po4 = po4 / (density_fb/1000),
+                nh4 = nh4 / (density_fb/1000),
+                no3no2 = no3no2 / (density_fb/1000),
+                no3 = no3 / (density_fb/1000),
+                si = si / (density_fb/1000)
   )
@@
 ## Impact of nutrients
-```{r impact of nutrients, echo=FALSE, warning=TRUE, message=FALSE}
+```{r impact of nutrients, echo=FALSE, warning=FALSE, message=FALSE}
 # boxplot
-ts_PO4_bp <- d_all %>%
-  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = PO4)) +
+ts_po4_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = po4)) +
   #geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm = TRUE) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
-  labs(y = "PO4", x=NULL, title=NULL) +
+  labs(y = "po4", x=NULL, title=NULL) +
   Mytheme() +
@@
 ts_Si_bp <- d_all %>%
-  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = Si)) +
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = si)) +
   #geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm = TRUE) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
-  labs(y = "Si", x=NULL, title=NULL) +
+  labs(y = "si", x=NULL, title=NULL) +
   Mytheme() +
@@
 ts_Si_bp + ts_Si_bp
-# Effects of changes in PO4 and Si
+# Effects of changes in po4 and si
 # 1st cakculate mean values
@@
 # then check impacts using pco2 and AT
-carb_PO4_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
-                 Pt = c(min(d_all$PO4/1e6, na.rm=TRUE), max(d_all$PO4/1e6, na.rm=TRUE)), Sit = 0,
+carb_po4_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = c(min(d_all$po4/1e6, na.rm=TRUE), max(d_all$po4/1e6, na.rm=TRUE)), Sit = 0,
                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-diff_PO4_1 <- carb_PO4_1[1,] - carb_PO4_1[2,]
+diff_po4_1 <- carb_po4_1[1,] - carb_po4_1[2,]
 carb_Si_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0,
-                Pt = 0, Sit = c(min(d_all$Si/1e6, na.rm=TRUE), max(d_all$Si/1e6, na.rm=TRUE)), 
+                Pt = 0, Sit = c(min(d_all$si/1e6, na.rm=TRUE), max(d_all$si/1e6, na.rm=TRUE)), 
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
@@
 # then check impacts using AT-DIC pair
-carb_PO4_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
-                 Pt = c(min(d_all$PO4/1e6, na.rm=TRUE), max(d_all$PO4/1e6, na.rm=TRUE)), Sit = 0,
+carb_po4_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = c(min(d_all$po4/1e6, na.rm=TRUE), max(d_all$po4/1e6, na.rm=TRUE)), Sit = 0,
                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-diff_PO4_2 <- carb_PO4_2[1,] - carb_PO4_2[2,]
+diff_po4_2 <- carb_po4_2[1,] - carb_po4_2[2,]
 carb_Si_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
-                Pt = 0, Sit = c(min(d_all$Si/1e6, na.rm=TRUE), max(d_all$Si/1e6, na.rm=TRUE)), 
+                Pt = 0, Sit = c(min(d_all$si/1e6, na.rm=TRUE), max(d_all$si/1e6, na.rm=TRUE)), 
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
@@
 
-The concentration of PO4 and Si varies with a factor 10 along a composite year.
-The ranges are respectively, `r round(range(d_all$PO4, na.rm = TRUE), digits = 2)` for PO4 and `r round(range(d_all$Si, na.rm = TRUE), digits = 2)` for Si.
+The concentration of po4 and si varies with a factor 10 along a composite year.
+The ranges are respectively, `r round(range(d_all$po4, na.rm = TRUE), digits = 2)` for po4 and `r round(range(d_all$si, na.rm = TRUE), digits = 2)` for si.
 
 ### Using the pCO2-AT pair (hourly data)
-The impact of the min max changes of PO4 on pH, DIC, and Omega_a are small:  `r round(1000*diff_PO4_1$pH, digits=2)` mpH units, `r round(1e6*diff_PO4_1$DIC, digits=2)` umol/kg for CT and `r round(diff_PO4_1$OmegaAragonite, digits=2)` for OmegaAragonite.
-
-The impact of the min max changes of Si on pH, DIC, and Omega_a are small:  `r round(1000*diff_Si_1$pH, digits=2)` mpH units, `r round(1e6*diff_Si_1$DIC, digits=2)` umol/kg for CT and `r round(diff_Si_1$OmegaAragonite, digits=2)` for OmegaAragonite.
+The impact of the min max changes of po4 on pH, DIC, and Omega_a are small:  `r round(1000*diff_po4_1$pH, digits=2)` mpH units, `r round(1e6*diff_po4_1$DIC, digits=2)` umol/kg for CT and `r round(diff_po4_1$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of si on pH, DIC, and Omega_a are small:  `r round(1000*diff_Si_1$pH, digits=2)` mpH units, `r round(1e6*diff_Si_1$DIC, digits=2)` umol/kg for CT and `r round(diff_Si_1$OmegaAragonite, digits=2)` for OmegaAragonite.
 
 ### Using the CT-AT pair (discrete data)
-The impact of the min max changes of PO4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_PO4_2$pH, digits=2)` mpH units, `r round(diff_PO4_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_PO4_2$OmegaAragonite, digits=2)` for OmegaAragonite.
-
-The impact of the min max changes of PO4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_Si_2$pH, digits=2)` mpH units, `r round(diff_Si_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_Si_2$OmegaAragonite, digits=2)` for OmegaAragonite.
+The impact of the min max changes of po4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_po4_2$pH, digits=2)` mpH units, `r round(diff_po4_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_po4_2$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of po4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_Si_2$pH, digits=2)` mpH units, `r round(diff_Si_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_Si_2$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+## Impact of choice of constants
+### Using mean values
+```{r impact of constants, echo=FALSE, warning=FALSE, message=FALSE}
+# Compare Lueker and Sulpis
+# use mean values calculated for impacts of nutrients above
+means <- d_all %>% 
+  group_by(montht) %>% 
+  summarize(mean_ct = mean(ct, na.rm = TRUE),
+            mean_at_calc = mean(at_calc, na.rm = TRUE),
+            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
+            mean_sal = mean(sal_fb, na.rm = TRUE),
+            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
+  ungroup()
+mean_ct <-  mean(means$mean_ct)
+mean_at_calc <-  mean(means$mean_at_calc)
+mean_pco2_calc <-  mean(means$mean_pco2_calc)
+mean_sal <-  mean(means$mean_sal)
+mean_temp <-  mean(means$mean_temp)
+# impacts using pco2 and AT
+carb_l_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = 0, Sit = 0,
+                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+carb_s_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = 0, Sit = 0,
+                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+diff_ls_1 <- carb_l_1 - carb_s_1
+
+# impacts using AT-DIC pair
+carb_l_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = 0, Sit = 0,
+                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+carb_s_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
+                Pt = 0, Sit = 0, 
+                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+diff_ls_2 <- carb_l_2 - carb_s_2
+const <- bind_rows(diff_ls_1, diff_ls_2) %>% 
+  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
+                S = mean_sal,
+                T = mean_temp,
+                DIC = DIC * 1e6
+                ) %>% 
+  dplyr::select(flag:T, pH, pCO2, DIC, OmegaAragonite)
+#kable(const, digits = c(0, 1, 1, 3, 1, 1, 2))
+pander(const)
+```
+### Using all values pCO2 and at_calc
+```{r impact of constants, echo=FALSE, warning=FALSE, message=FALSE}
+# Compare Lueker and Sulpis
+d_ls <- d_all %>% 
+  drop_na(pco2_corr, at_calc, sal_fb, temp_fb)
+carb_l <-
+  carb(
+    24,
+    d_ls$pco2_corr,
+    d_ls$at_calc * 1e-6,
+    S = d_ls$sal_fb,
+    T = d_ls$temp_fb,
+    P = 0,
+    Pt = 0,
+    Sit = 0,
+    k1k2 = "l",
+    kf = "dg",
+    ks = "d",
+    pHscale = "T",
+    b = "u74"
+  )
+carb_s <-
+  carb(
+    24,
+    d_ls$pco2_corr,
+    d_ls$at_calc * 1e-6,
+    S = d_ls$sal_fb,
+    T = d_ls$temp_fb,
+    P = 0,
+    Pt = 0,
+    Sit = 0,
+    k1k2 = "s20",
+    kf = "dg",
+    ks = "d",
+    pHscale = "T",
+    b = "u74"
+  )
+diff_ls <- as_tibble(carb_l - carb_s)
+d_ls <- bind_cols(d_ls, diff_ls)
+
+# plot
+lm <- lm2(x = tmp$sal_insitu_ctd_9m, y = d_all$sal_fb)
+p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
+  geom_point( aes(color=factor(monthd))) + 
+  geom_abline(slope=1, intercept=0, linetype = "dashed")+
+  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),colour = "blue") +
+  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
+  labs(title = paste("","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
+                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
+                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
+                     "; P =", signif(lm$fit$P.param, 3),
+                     "; RMSE = ", signif(lm$rmse, 3))) +
+  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
+  coord_fixed(ratio = 1 )+
+  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()
+
+print(p) #p_sal_fb_ctd
+```
+
+The difference induces by the choice of the carbonic acid constants is large for pH, pCO2 and DIC and negligible for OmegaAragonite.
 
@@
 
-Si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync.
+si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync.
 Pattern des commandes : # m h dom mon dow command

### 2021-01-04 awipev-CO2.Rmd
pco2_fb at in situ temp

@@
 
-```{r read data, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
+```{r read observatory data, cleanup and prepare ferrybox data, echo=FALSE, warning=FALSE, message=FALSE}
 d_hour <-
@@
   dplyr::rename(
-    pco2 = pco2_corr_filtered,
+    pco2_fb = pco2_corr_filtered,
     temp_dur = temp_dur_filtered,
@@
   drop_na(date) %>% 
-  dplyr::mutate(datetime = as.POSIXct(paste0(date, " 12:00:00"))) %>% # assuming sampling time 12:00
+  dplyr::mutate(datetime = as.POSIXct(paste0(date, " 12:00:00")),
+                ) %>% # assuming sampling time 12:00
   dplyr::filter(datetime > as.POSIXct("2015-07-09"))
@@
   dplyr::select(-date, -datetime) %>% 
-  dplyr::rename(no3no2 = `no3+no2`)
+  dplyr::rename(NO3NO2 = `NO3+NO2`)
 # cleanup and convert in umol/kg
@@
   dplyr::mutate(density_fb = seacarb::rho(S = sal_fb, T = temp_fb, P = 0),
-                po4 = po4 / (density_fb/1000),
-                nh4 = nh4 / (density_fb/1000),
-                no3no2 = no3no2 / (density_fb/1000),
-                no3 = no3 / (density_fb/1000),
-                si = si / (density_fb/1000)
+                po4 = PO4 / (density_fb/1000),
+                nh4 = NH4 / (density_fb/1000),
+                no3no2 = NO3NO2 / (density_fb/1000),
+                no3 = NO3 / (density_fb/1000),
+                si = Si / (density_fb/1000)
   )
@@
 
-## *p*CO~2~
+## *p*CO~2~ and *f*CO~2~
 The HydroC CO~2~ FT sensor (S/N: CO2FT-0215-001) was bought from Contros (Germany) in February 2015.
@@
 
+```{r pco2 to fco2, echo=FALSE, warning=FALSE, message=FALSE}
+d_all <- d_all %>%
+  dplyr::mutate(
+    fco2_fb = seacarb::p2fCO2(
+      pCO2 = pco2_fb,
+      T = temp_fb,
+      Patm = 1,
+      P = 0),
+    fco2_fb_insi_temp = seacarb::fCO2insi(
+      fCO2lab = fco2_fb,
+      Tlab = temp_fb,
+      SST = temp_insitu_11m),
+    .after = pco2_fb
+)
+```
+
+We first calculate fCO2 from pCO2 and then express fCO2 at in situ temperature.
+Ideally, this should be done with SST as the goal is to estimate air-sea CO2 fluxes.
+I therefroe use the in situ temperature at 11 m and we will need to speculate on stratitication.
+
 ```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
 title <- "Contros vs calculated pCO2"
-fit <- lmodel2(data = d_all,  pco2_corr ~ pco2_calc_fb , nperm = 99)
-
-p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_corr, label = monthd))+
+fit <- lmodel2(data = d_all,  pco2_fb ~ pco2_calc_fb , nperm = 99)
+
+p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_fb, label = monthd))+
    geom_text(aes(color = factor(monthd)))+
@@
 pco2_contros_xts <-
-  dplyr::select(d_all, datetime, pco2_calc_fb, pco2_corr)
+  dplyr::select(d_all, datetime, pco2_calc_fb, pco2_fb)
 pco2_contros_xts <-
@@
   dySeries(
-    "pco2_corr",
+    "pco2_fb",
     label = "Corrected pCO2",
@@
   dplyr::mutate(
-    pco2_corr = case_when(
+    pco2_fb = case_when(
       date > as.Date("2016-04-01") &
-        date <  as.Date("2017-02-05") & pco2_corr > 400 ~ NA_real_,
+        date <  as.Date("2017-02-05") & pco2_fb > 400 ~ NA_real_,
       #date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
       date > as.Date("2017-08-01") &
-        date <  as.Date("2017-09-30") & pco2_corr > 300 ~ NA_real_,
+        date <  as.Date("2017-09-30") & pco2_fb > 300 ~ NA_real_,
       #date == as.Date("2017-03-22") & sal_mix < 34 ~ NA_real_,
-      TRUE ~ pco2_corr
+      TRUE ~ pco2_fb
     )
@@
 d_ls <- d_all %>% 
-  drop_na(pco2_corr, at_calc, sal_fb, temp_fb)
+  drop_na(pco2_fb, at_calc, sal_fb, temp_fb)
 carb_l <-
@@
     24,
-    d_ls$pco2_corr,
+    d_ls$pco2_fb,
     d_ls$at_calc * 1e-6,
@@
 d_all <- d_all %>%
-  dplyr::mutate(delta_pco2 = pco2_corr - pco2_air, # ppm
+  dplyr::mutate(delta_pco2 = pco2_fb - pco2_air, # ppm
                 k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
@@
 pangaea <- as_tibble(d_all) %>% 
-  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, phcalc_fb, pco2_corr, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
+  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, phcalc_fb, pco2_fb, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
   dplyr::rename(pressure = pressure_insitu_ctd,
@@
                 ph_s_dur_t_fb = ph_s_dur_temp_fb,
-                pco2 = pco2_corr,
+                pco2 = pco2_fb,
                 pco2_calc = pco2_calc_fb,

### 2021-01-05 awipev-CO2.Rmd
Difference fco2_fb - fco2_fb_insi_temp

@@
 )
+
+set.caption("Difference fco2_fb - fco2_fb_insi_temp")
+pander(summary(d_all$fco2_fb - d_all$fco2_fb_insi_temp))
 ```
@@
 Ideally, this should be done with SST as the goal is to estimate air-sea CO2 fluxes.
-I therefroe use the in situ temperature at 11 m and we will need to speculate on stratitication.
+I therefore use the in situ temperature at 11 m and we will need to speculate on stratification.
 

### 2021-01-05 awipev-CO2.tex
first commit

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Carbonate chemistry at Ny-Ålesund: AWIPEV-CO2 Project},
  pdfauthor={Jean-Pierre Gattuso and Samir Alliouane},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage[margin=1in]{geometry}
\usepackage{longtable,booktabs}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Carbonate chemistry at Ny-Ålesund: AWIPEV-CO\textsubscript{2}
Project}
\author{Jean-Pierre Gattuso and Samir Alliouane}
\date{31 December 2020}

\begin{document}
\maketitle

\includegraphics[width=2.60417in,height=\textheight]{Images/AWIPEV-Logo.jpg}

\hypertarget{section}{%
\section{}\label{section}}

\hypertarget{infos}{%
\subsection{Infos}\label{infos}}

\hypertarget{introduction}{%
\subsubsection{\texorpdfstring{\textbf{Introduction}}{Introduction}}\label{introduction}}

The AWIPEV-CO2 project aims at starting the first time series for the
carbonate chemistry in the Arctic Ocean as part of the AWIPEV Underwater
Observatory. It comprises two components: (1) continuous real-time
measurements and (2) discrete measurements. The rationale is that
discrete measurements are absolutely needed to calibrate and validate
the sensors.

\hypertarget{awipev-underwater-observatory}{%
\subsubsection{\texorpdfstring{\textbf{AWIPEV Underwater
Observatory}}{AWIPEV Underwater Observatory}}\label{awipev-underwater-observatory}}

The AWIPEV Underwater Observatory has been deployed at Ny-Alesund
(Spitsbergen, 78°55'18N, 11°56'31E) in June 2012. It is part of the
German Project COSYNA (Coastal Observation Systems of the Northern- and
Arctic Seas), which aims at increasing the availability of continuous
real-time data from remote but climatically-sensitive ecosystems. The
AWIPEV underwater observatory comprises a fully remote controlled
FerryBox system fed with seawater pumped in front of the old pIer at 12
m depth. Temperature, salinity, pressure, turbidity, oxygen,
chl-\emph{a} fluorescence are measured. Furthermore, an additional
remote controlled underwater sensor unit able to profile from 12 m to
the surface at any frequency carries additional sensors for salinity,
pressure, turbidity, oxygen chl-\emph{a} fluorescence and PAR. The
system also comprises an ADCP for continuous measurements of currents
and waves. Besides these standard sensors, the underwater unit is
equipped with a webcam and stereo-optical device to remotely assess fish
and jellyfish populations. The AWIPEV observatory is specifically
designed for polar experimental work under extreme conditions including
ice coverage and the inaccessibility for about 7 months during polar
winter. During this time, the system is remotely controlled and
maintained from Germany. All data sampled by the sensors are
continuously sent to a central server system at Helgoland Island where
the data are stored and processed. The processed data are open access
and available at \url{http://codm.hzg.de/codm}.

\hypertarget{continuous-and-semi-continuous-measurements}{%
\subsubsection{\texorpdfstring{\textbf{Continuous and semi-continuous
measurements}}{Continuous and semi-continuous measurements}}\label{continuous-and-semi-continuous-measurements}}

The Arctic version of the Contros-Kongsberg HydroC CO\textsubscript{2}
FT (Carbon Dioxyde partial pressure Flow Through surface water sensor)
has been installed in July 2015. Molecules of dissolved
CO\textsubscript{2} diffuse through a thin composite membrane into the
internal gas circuit leading to a detector chamber, where the partial
pressure of CO\textsubscript{2} is determined by means of infra-red
absorption spectrometry. Concentration-dependent IR light is converted
into the output signal from calibration coefficients stored in firmware
and data from additional sensors within the gas circuit. The measuring
range is 200-1000 uatm, resolution is \textless{} 1 uatm and accuracy is
+- 1\% reading. The sensor is the first instrument in the measuring
loop; data are logged every minute. This instrument requires yearly
factory calibration; two sensors ara available to allow a continuous
time series.

Since February 2016, total alkalinity (AT) is measured every 90 min with
a Contros-Kongsberg HydroFIA TA (Total Alkalinity analyser flow through
system). Fifty ml of seawater is filtered (0.2 um) using a
Contros-Kongsberg cross-flow filter and then acidified using dilute
hydrochloric acid (0.1 N). CO\textsubscript{2} is then flushed out
(open-cell titration) and the final pH measured by means of an indicator
dye (bromocresol green) and visible absorption spectrometry. Together
with salinity and temperature at the time of measurement, the pH reading
is used to calculate AT. According to the manufacturer, the measuring
range is 400 umol/kg dynamic range, resolution 0.1 umol/kg, accuracy 25
umol/kg (+- 1\%) and precision 5 umol/kg (+- 0.2\%).

In August 2017, a seaFET Ocean pH sensor (Sea-Bird Scientific) has been
added to the UWO. This new sensor continuously measures pH at 11 m using
an ISFET (Ion Sensitive Field Effect Transistor). According to the
manufacturer, the measuring range is between 6.5 and 9 pH units, initial
accuracy is 0.02 pH units and precision is 0.004 pH units. Operating
salinity and temperature range are 20 to 40 PSU and 0 to 50°C
respectively.

In August 2017, a Durafet III pH electrode connected to a UDA2128
Analyser (Honeywell) was also implemented to the Ferrybox flow-through
system. This electrode continuously measures pH, in the Ferrybox,
through an ISFET. According to the manufacturer, the measuring range is
between 0 and 14 pH units.

\hypertarget{data-availability}{%
\subsubsection{\texorpdfstring{\textbf{Data
availability}}{Data availability}}\label{data-availability}}

The data at one minute frequency were tagged with the following quality
flags

\begin{itemize}
\item
  1: good data
\item
  3: failing the date and time test
\item
  4: data not usable according to manufacturer
\item
  6: failing the manufacturer range test (not used)
\item
  7: failing the regional range test
\item
  12: failing the spike test (NAs from despike)
\item
  13: failing the gradient test
\item
  15: instrument not deployed or operated
\item
  16: acid flush
\item
  99: failing the final visual inspection
\item
  Despike using oce::despike with n=2, k=5761
\end{itemize}

\begin{longtable}[]{@{}lrrrrrrr@{}}
\toprule
\begin{minipage}[b]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedright
Flag\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedleft
pCO2\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 7\tabcolsep) * \real{0.17}}\raggedleft
Salinity FerryBox\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 7\tabcolsep) * \real{0.16}}\raggedleft
In situ salinity\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 7\tabcolsep) * \real{0.20}}\raggedleft
Temperature FerryBox\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 7\tabcolsep) * \real{0.19}}\raggedleft
In situ temperature\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 7\tabcolsep) * \real{0.10}}\raggedleft
Durafet pH\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 7\tabcolsep) * \real{0.09}}\raggedleft
seaFET pH\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedright
1\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedleft
56.9\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.17}}\raggedleft
68.2\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.16}}\raggedleft
51.8\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.20}}\raggedleft
66.5\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.19}}\raggedleft
75.1\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.10}}\raggedleft
76.2\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.09}}\raggedleft
69.7\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedright
4\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedleft
2.4\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.17}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.16}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.20}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.19}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.10}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.09}}\raggedleft
NA\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedright
7\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedleft
9.3\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.17}}\raggedleft
0.1\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.16}}\raggedleft
11.9\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.20}}\raggedleft
0.1\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.19}}\raggedleft
0.0\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.10}}\raggedleft
3.0\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.09}}\raggedleft
0.2\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedright
12\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedleft
1.7\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.17}}\raggedleft
5.3\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.16}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.20}}\raggedleft
7.0\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.19}}\raggedleft
7.8\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.10}}\raggedleft
1.0\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.09}}\raggedleft
NA\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedright
15\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedleft
24.6\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.17}}\raggedleft
26.4\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.16}}\raggedleft
36.4\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.20}}\raggedleft
26.4\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.19}}\raggedleft
17.0\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.10}}\raggedleft
19.8\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.09}}\raggedleft
30.0\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedright
16\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedleft
5.1\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.17}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.16}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.20}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.19}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.10}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.09}}\raggedleft
NA\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedright
99\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.05}}\raggedleft
0.0\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.17}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.16}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.20}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.19}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.10}}\raggedleft
NA\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 7\tabcolsep) * \real{0.09}}\raggedleft
NA\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{salinities}{%
\subsection{Salinities}\label{salinities}}

Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and
5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are
switched periodically. Salinity from FB is taken in consideration. If
data gaps are encountered, they are filled with bottom salinty data from
ctd (\textgreater{} 8 m). New column ``sal\_mix'' is created and is the
one used in ESSD paper.

\begin{itemize}
\tightlist
\item
  1 SBE45 inside the Ferrybox (sal\_fb)
\item
  5 CTD \textgreater{} 8 m depth (sal\_insitu\_ctd)
\end{itemize}

\textbackslash begin\{center\}\includegraphics[width=0.8\linewidth]{awipev-CO2_files/figure-latex/Salinity-1}

\hypertarget{depth-profile}{%
\subsubsection{\texorpdfstring{\textbf{Depth
profile}}{Depth profile}}\label{depth-profile}}

\begin{center}\includegraphics[width=0.8\linewidth]{awipev-CO2_files/figure-latex/Sal profile-1} \end{center}

\begin{longtable}[]{@{}lr@{}}
\caption{Quantiles salinity gradient between 0-2 m and \textgreater{} 8
m}\tabularnewline
\toprule
& Sal. unit\tabularnewline
\midrule
\endfirsthead
\toprule
& Sal. unit\tabularnewline
\midrule
\endhead
0\% & -4.40\tabularnewline
25\% & -0.49\tabularnewline
50\% & -0.07\tabularnewline
75\% & 0.00\tabularnewline
100\% & 2.14\tabularnewline
\bottomrule
\end{longtable}

\includegraphics[width=0.8\linewidth]{awipev-CO2_files/figure-latex/Sal profile-2}
There are 184 days with salinity values at both 1 m (0-2 m) and 9 m
(\textgreater{} 8 m). The salinity difference between 1 and 9 m ranges
between -4.404125 and 2.1417658 (mean: -0.3428293; -0.0681155). The
difference with depth is therefore significant.

\hypertarget{sal-fb-sal-ctd-9-m}{%
\subsubsection{\texorpdfstring{\textbf{Sal FB / Sal CTD 9 m
}}{Sal FB / Sal CTD 9 m }}\label{sal-fb-sal-ctd-9-m}}

\begin{center}\includegraphics[width=0.8\linewidth]{awipev-CO2_files/figure-latex/Sal comparaison-1} \end{center}

The mean difference between salinity FB and in situ is: -0.16 ± 0.88
PSU.

\hypertarget{temperatures}{%
\subsection{Temperatures}\label{temperatures}}

Several temperature sensors are on site, 1 inside the Ferrybox (SBE45),
5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are
switched periodically and 1 fixed at 11 m depth (sbe38). Temperature in
situ at 11 m depth is taken in consideration. If data gaps are
encountered, they are filled with bottom temperature data from ctd
(\textgreater{} 8 m). New column ``temp\_mix'' is created. For the
moment, no gaps are encountered and temp\_mix = temp\_insitu\_11m.

\begin{itemize}
\tightlist
\item
  1 SBE45 inside the Ferrybox (temp\_fb)
\item
  5 CTD profiling (temp\_insitu\_ctd\_1m - 3m - 5m - 7m - 9m)
\item
  1 fixed at 11 meters depth (temp\_insitu\_11m)
\end{itemize}

\textbackslash begin\{center\}\includegraphics[width=0.8\linewidth]{awipev-CO2_files/figure-latex/temperature time series-1}
\includegraphics[width=0.8\linewidth]{awipev-CO2_files/figure-latex/temperature time series-2}

\hypertarget{temperature-profiles}{%
\subsubsection{\texorpdfstring{\textbf{Temperature
profiles}}{Temperature profiles}}\label{temperature-profiles}}

\textbackslash begin\{center\}\includegraphics[width=0.8\linewidth]{awipev-CO2_files/figure-latex/temperature profiles-1}
There are 184 days with temperature values at both 1 m (0-2 m) and 9 m
(\textgreater{} 8 m). The temperature difference between 1 and 9 m
ranges between -4.0276557°C and 1.8536989°C (mean: -0.2577894°C;
-0.1372184°C). The difference with depth is therefore significant.

\hypertarget{t-ferrybox-t-insitu-11-m}{%
\subsubsection{\texorpdfstring{\textbf{T Ferrybox / T insitu 11 m
}}{T Ferrybox / T insitu 11 m }}\label{t-ferrybox-t-insitu-11-m}}

\includegraphics{awipev-CO2_files/figure-latex/Temp fb insi comparaison-1.pdf}

The mean difference between temperature Ferrybox and in situ at 11 m is:
0.53 ± 0.2°C.

\hypertarget{t-11-m-t-ctd-8-m}{%
\subsubsection{\texorpdfstring{\textbf{T 11 m / T CTD \textgreater{} 8 m
}}{T 11 m / T CTD \textgreater{} 8 m }}\label{t-11-m-t-ctd-8-m}}

\includegraphics{awipev-CO2_files/figure-latex/Temp 11m and ctd comparaison-1.pdf}

The mean difference between temperature Ferrybox and in situ at 11 m is:
-0.04 ± 0.34°C.

\hypertarget{total-alkalinity}{%
\subsection{Total alkalinity}\label{total-alkalinity}}

Since we bought the AT analyser (February 2016), numerous problems
happened due to a leak of the degassing unit in each analyser and sudden
step changes. Last analyser repaired by Contros was installed back in
the FB on 2018-07-31. This was the 3rd analyser on site. Even with this
instrument, data collection didn't show satisfaction.

\hypertarget{discrete-total-alkalinity-reference-vs-salinity-relationship}{%
\subsubsection{\texorpdfstring{\textbf{Discrete total alkalinity
(reference) vs salinity
relationship}}{Discrete total alkalinity (reference) vs salinity relationship}}\label{discrete-total-alkalinity-reference-vs-salinity-relationship}}

In the previous part, missing TA were interpolated with a linear model.
This does not reflect the natural variability of TA. For this reason,
missing TA is now calculated from salinity data by making a relationship
between the same reference TA samples as in the previous part and
salinity data.

The relationship between titrated total alkalinity (references) and
salinity is very good with an r2 of . Need to compare with other
relationships from the literature.

\begin{center}\includegraphics[width=1\linewidth]{awipev-CO2_files/figure-latex/plot Discrete salinity vs TA-1} \end{center}

\hypertarget{final-ta-re-calculated-data-salinity-relationship}{%
\paragraph{\texorpdfstring{\textbf{Final TA re-calculated data (Salinity
relationship)}}{Final TA re-calculated data (Salinity relationship)}}\label{final-ta-re-calculated-data-salinity-relationship}}

\includegraphics[width=1\linewidth]{awipev-CO2_files/figure-latex/Plot TA calc TA meas-1}

There are a lot of outliers in the 4th period (since the new analyzer
was set up in Nov.~2018). We use the desplike function to remove them.

\hypertarget{pco2}{%
\subsection{\texorpdfstring{\emph{p}CO\textsubscript{2}}{pCO2}}\label{pco2}}

The HydroC CO\textsubscript{2} FT sensor (S/N: CO2FT-0215-001) was
bought from Contros (Germany) in February 2015. It was deployed in the
FerryBox with other sensors since July 2015, the 20th. A spare sensor
(S/N: CO2FT-0515-001) was also bought in March 2015 and carried to
Ny-Alesund to replace the first one in case of calibration or problem.
Both sensors were set on a cycle according to informations given by
Contros in March 2015
(\href{mailto:c.kirbach@contros.eu}{\nolinkurl{c.kirbach@contros.eu}}):

30 min warm up --\textgreater{} (3 min Zeroing + 15 min Flushing + 702
minutes Measuring) --\textgreater{} (3 + 15 + 702)\ldots{}

\begin{itemize}
\tightlist
\item
  \textbf{Warm-up}: running without sending data. Done once, after the
  sensor is turned on. Time can vary depending on T water and power
  supply.
\item
  \textbf{Flushing}: running normally. Phase of equilibration that
  depends on the sensor configuration and the environment conditions.
  Warmer the water is and larger the flow is in front of the membrane,
  faster will be the response time and shorter will be the flush time.
  Recovery data of the sensor signal from the zeroing interval happen in
  this time. During this step the flush flag is set to ``1'' for
  simplifier extraction of the flush values.
\item
  \textbf{Measuring}: running normally and all other flags are on ``0''.
  Sensor is fully equilibrated and T is stable.
\end{itemize}

During those steps (except zeroing) the sensor runs normally.
Equilibration between the gas inside the sensor and the dissolved gas in
ambient water takes place. Gas is led to NDIR unit while T control is
running.

\hypertarget{corrected-contros-vs-calculated-pco2-data}{%
\subsubsection{\texorpdfstring{\textbf{Corrected Contros vs calculated
\emph{p}CO\textsubscript{2}
data}}{Corrected Contros vs calculated pCO2 data}}\label{corrected-contros-vs-calculated-pco2-data}}

The relationship between the Contros and calculated
\emph{p}CO\textsubscript{2} is not good at all in the sense that it is
far from the 1:1 line, despite a good r2 (0.65).

\begin{center}\includegraphics[width=1\linewidth]{awipev-CO2_files/figure-latex/plot measured vs calculated pCO2-1} \end{center}

\hypertarget{final-pco2-data}{%
\subsubsection{\texorpdfstring{\textbf{Final \emph{p}CO\textsubscript{2}
data}}{Final pCO2 data}}\label{final-pco2-data}}

\begin{center}\includegraphics[width=1\linewidth]{awipev-CO2_files/figure-latex/Final pCO2-1} \end{center}

\hypertarget{ph-seafet}{%
\subsection{pH seaFET}\label{ph-seafet}}

pH is measured continuously by an autonomous seaFET pH sensor. Because
of issue, measurement periodicity was set to 1 hour from 2018-02-02 to
2018-04-17. \emph{Note that the pH sensor is mounted on a profiling
structure. Here, only seaFET data recorded with a depth \textgreater{} 8
m are taken in consideration.} pH calibration is based on monthly
discrete samples that are analysed with spectrophotometric method in
Villefranche by Samir Alliouane. When it is not possible to sample at
the vicinity of the sensor for practice reasons (in winter), sampling is
done in the harbour and is not taken in consideration for calibration
for spatial reasons.

Calibration was done following the methods and code described in
Bresnahan et al.~(2014) and adapted to use in R (seacarb package).
Deployment periods are difined so that one spectrophotometric
measurement is in the middle of a defined period of calibration (shaded
colors in the plot).

Within this deployment period, calibration is made with E0 calculation
(first plot) and final corrected pH is calculated (second plot). To
allow calibration, one spectrophotometric pH measurement must match:
seaFET voltage, in situ temperature (SBE38) and salinity. When one of
these parameters is missing for any reasons (Ferrybox maintenance,
breakdown\ldots), the gap is filled with a mean of the 4 previous or
next hours when available. If the pH spectrophotometric measurement is
too far from the available values, the calibration is not performed
(environemental variability reasons). The SBE38 insitu temperature and
seaFET temperature are very similar (slope = 0.992, r2 = 0.96, see tab
``Temperatures''). These two temperatures were used interchangeably if
one is missing.

Missing data which could be estimated on : 2017-08-24, 2017-09-28,
2019-09-13 x 2. Missing data which could not be estimated on :
2018-04-16 , 2018-12-14, 2019-01-18.

We decided to change the calculation of E0. Before E0 was calculated for
each pH spectro measurements. Now, EO is calculated making a mean of
several E0 that come from one deployment period (sensor in the water for
several months).

\hypertarget{seafet-calibration-constant-e0}{%
\subsubsection{\texorpdfstring{\textbf{seaFET calibration constant
E0}}{seaFET calibration constant E0}}\label{seafet-calibration-constant-e0}}

Plots of E0int25 and E0ext25 returned by the function ``pHCalib'' for
each period of deployement are shown below.

\includegraphics[width=0.6\linewidth]{awipev-CO2_files/figure-latex/seaFET calibration sf_calib-1}

\hypertarget{seafet-pht-calibrated}{%
\subsubsection{\texorpdfstring{\textbf{seaFET pHT
calibrated}}{seaFET pHT calibrated}}\label{seafet-pht-calibrated}}

pH is measured continuously by an autonomous seaFET pH sensor. Final
calibrated seaFET pHT data (green dots) are shown here after calibration
with spectro measurements (red dots) according to each period of
deployement, defined between 2 spectro measurements (shading grey).
Calibration was done following the methods and code described in
Bresnahan \emph{et al.} (2014) using seaFET voltage and spectro
measurements. During the fifth period, seaFET cannot be calibrated
because seaFET was not working during the time of reference (pH spectro)
sampling (2018-04-16). To solve this calibration, we decided to fit the
spectro measurement with a pH mean of 4 previous days.

We also defined a period of malfunction from \textbf{2017-12-14} to
\textbf{2018-02-02}. in the first part of this period, until 2018-01-08,
we decided to filter outliers. In the second part, until the end of the
period, data must be removed.

\includegraphics{awipev-CO2_files/figure-latex/seaFET pH calculation sf_calc-1.pdf}

\hypertarget{seafet-ph-profiles}{%
\subsubsection{\texorpdfstring{\textbf{seaFET pH
profiles}}{seaFET pH profiles}}\label{seafet-ph-profiles}}

\begin{verbatim}
##                        Df Sum Sq Mean Sq F value Pr(>F)    
## tmp$depth               1  0.478  0.4784   182.7 <2e-16 ***
## tmp$montht             11 12.237  1.1125   424.8 <2e-16 ***
## tmp$depth:tmp$montht   11  5.667  0.5152   196.7 <2e-16 ***
## Residuals            8773 22.976  0.0026                   
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 8753 observations deleted due to missingness
\end{verbatim}

\begin{center}\includegraphics[width=0.8\linewidth]{awipev-CO2_files/figure-latex/seafet profile-1} \includegraphics[width=0.8\linewidth]{awipev-CO2_files/figure-latex/seafet profile-2} \end{center}

\textbf{Conclusion}: The range is significantly larger during some
months when the data deeper than 8 m are considered. Also, pH is
sometimes higher at the surface, at other times it is higher on the
bottom (June). No data are available at 1 m (actually 0 to 2 m). So, to
compare surface and bottom, I combine 1 and 3 m (0 to 4 m) and 9 m
(below 8 m).

Depth and month of the year have a statistically significant effet on
pH. The interaxction is also significant, indicating that the effect of
depth differs depending on the month.

\begin{itemize}
\tightlist
\item
  To compare with pCO2/pCO2 measured in the Ferrybox seems therefore
  better to stick with pH\_9m, that is at depths deeper than 8 m.
\item
  pCO2 would have the same behaviour as pH. For air-sea CO2 fluxes, one
  should use data from 0 to 4 m.
\end{itemize}

\hypertarget{ph-durafet}{%
\subsection{pH durafet}\label{ph-durafet}}

pH is measured continuously by an autonomous durafet pH sensor. Final
calibrated durafet pHT data (green dots) are shown here after
calibration with spectro measurements (red dots) according to each
period of deployement, defined between 2 spectro measurements (shading
grey). Calibration was done appliying an offset of pH between measured
and spectro data per periods.

\hypertarget{durafet-calibration}{%
\subsubsection{\texorpdfstring{\textbf{Durafet
calibration}}{Durafet calibration}}\label{durafet-calibration}}

\includegraphics{awipev-CO2_files/figure-latex/durafet calibration-1.pdf}
\includegraphics{awipev-CO2_files/figure-latex/durafet calibration-2.pdf}
\includegraphics{awipev-CO2_files/figure-latex/durafet calibration-3.pdf}

The average offset between durafet and references (spectro) data is
-0.16 pH unit (sd = 0.04, n = 25).

\hypertarget{range-per-months}{%
\subsection{Range per months}\label{range-per-months}}

\begin{longtable}[]{@{}lrrrrrrrrrrrrrrrrrrrrrrrrrrrrrrrr@{}}
\toprule
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedright
montht\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_mix\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_mix\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_ctd\_1m\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_ctd\_1m\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_ctd\_3m\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_ctd\_3m\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_ctd\_5m\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_ctd\_5m\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_ctd\_7m\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_ctd\_7m\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_ctd\_9m\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_ctd\_9m\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_11m\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_11m\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_fb\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
temp\_fb\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
sal\_mix\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
sal\_mix\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
sal\_ctd\_1m\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
sal\_ctd\_1m\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
sal\_ctd\_3m\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
sal\_ctd\_3m\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
sal\_ctd\_5m\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
sal\_ctd\_5m\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
sal\_ctd\_7m\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
sal\_ctd\_7m\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
sal\_ctd\_9m\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
sal\_ctd\_9m\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
sal\_fb\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
sal\_fb\_min\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
pH\_sf\_max\strut
\end{minipage} &
\begin{minipage}[b]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
pH\_sf\_min\strut
\end{minipage}\tabularnewline
\midrule
\endhead
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedright
Jan\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.03\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.90\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.84\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.49\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.86\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.88\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.78\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.86\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.92\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.86\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.04\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.83\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.03\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.90\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.27\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.25\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.91\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
33.84\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.37\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
29.15\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.37\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
28.56\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.35\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
29.16\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.35\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
28.00\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.37\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
28.01\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
34.91\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
34.06\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.0925\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
7.9461\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedright
Feb\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.80\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.91\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
1.90\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-2.24\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.36\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-2.24\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.32\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-2.24\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.69\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-2.24\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.86\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.96\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.80\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.91\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.02\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.35\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.97\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.21\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.10\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.44\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.11\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.62\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.11\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
31.21\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.08\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
28.01\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
36.91\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
29.52\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
34.97\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
34.21\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.1100\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.0064\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedright
Mar\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
1.92\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.92\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
1.76\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-2.13\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
1.62\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-2.24\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
1.57\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-2.23\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
1.88\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-2.24\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
1.93\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-2.24\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
1.73\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.92\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.55\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.28\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.46\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.28\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.51\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.56\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
37.00\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.62\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
36.99\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.66\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.48\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.66\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.46\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.62\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
35.08\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
32.73\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.1188\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.0058\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedright
Apr\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.76\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.83\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.79\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-2.41\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.67\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.86\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.66\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.85\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.78\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.11\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.78\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.34\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.76\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.83\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.88\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-0.34\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.56\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.43\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.54\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.64\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.54\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.69\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.53\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.66\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.52\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.64\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.57\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.60\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
35.08\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
34.43\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.3111\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.0152\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedright
May\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.55\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.12\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.33\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
0.99\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.22\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-0.04\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.17\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-0.48\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.56\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-0.50\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.53\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-0.51\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.55\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.12\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.03\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
0.12\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.47\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
33.59\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.08\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.78\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.10\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.77\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.07\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.52\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.48\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
33.42\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.47\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
33.59\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
35.11\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
34.37\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.4023\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.0586\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedright
Jun\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
6.53\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
1.71\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-Inf\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
Inf\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.93\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
1.56\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.98\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
1.77\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
6.37\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
1.85\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.71\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.02\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
6.53\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
1.71\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
6.72\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.38\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.48\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
33.95\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-Inf\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
Inf\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-Inf\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
Inf\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.39\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.35\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.50\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
33.00\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.49\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.80\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
35.04\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
33.95\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.3888\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.2073\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedright
Jul\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
7.96\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.99\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
7.49\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.46\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
7.63\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.89\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
8.06\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.92\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
7.42\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.00\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
6.79\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.68\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
7.96\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.99\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
8.27\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.77\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.03\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.29\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.09\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
30.18\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.48\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
31.82\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.83\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.26\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.50\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
31.74\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.86\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.29\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
35.03\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
32.41\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.1756\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
7.9560\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedright
Aug\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
8.47\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.21\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
8.11\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.43\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
7.59\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.56\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
8.26\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.93\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
7.39\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.62\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
7.26\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.78\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
8.47\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.21\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
8.09\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.96\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.11\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
31.76\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
33.61\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
28.94\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.30\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
29.32\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.25\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
29.38\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.28\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
29.49\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.32\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
29.51\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
34.87\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
31.86\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.2217\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
7.9778\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedright
Sep\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
6.17\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.72\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.60\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.65\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.97\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.63\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
6.10\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.17\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
6.14\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.54\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.92\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.72\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
6.17\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
2.90\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
6.54\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
3.34\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.52\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
31.66\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.18\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
29.78\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.18\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
29.88\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.55\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
31.34\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.30\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
29.65\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.52\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
30.46\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
34.33\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
31.89\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.1637\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.0294\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedright
Oct\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.43\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-0.34\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.56\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-0.51\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.03\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-0.34\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.06\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
0.28\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.36\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-0.54\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.37\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-0.34\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.43\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
0.02\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.69\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
0.69\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.73\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
31.64\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
33.90\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
29.31\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.40\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
29.40\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.76\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
28.89\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.79\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
29.54\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.47\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
28.59\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
34.73\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
31.79\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.1574\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
7.9578\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedright
Nov\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.72\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.51\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.30\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.09\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.41\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-0.90\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.31\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.31\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.80\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.53\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.72\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.50\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.69\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.51\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
5.75\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-0.84\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.82\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.37\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.72\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.27\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.03\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.68\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.20\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.12\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.68\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.24\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
34.82\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.14\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
34.82\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
33.03\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.1442\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
7.9856\strut
\end{minipage}\tabularnewline
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedright
Dec\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.66\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.90\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.85\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.76\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.93\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.88\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.96\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.52\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.06\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.79\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.61\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.87\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.66\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.90\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
4.85\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
-1.17\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.22\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
33.09\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.28\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.88\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.38\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.69\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.37\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
32.26\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.26\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
30.69\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
35.29\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.03}}\raggedleft
30.50\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
35.02\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
33.41\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
8.1219\strut
\end{minipage} &
\begin{minipage}[t]{(\columnwidth - 32\tabcolsep) * \real{0.02}}\raggedleft
7.9926\strut
\end{minipage}\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{phs}{%
\subsection{pHs}\label{phs}}

Comparaison is done here with \textbf{corrected pHs} (\textbf{seaFET},
\textbf{durafet} and \textbf{calculated} (from AT/CT)) and normalized at
4°C with a total alkalinity of 2273.8528278 µmoles kg-1 (mean data). For
information, mean temperatures in Ferrybox and \emph{in situ} are
repectively 3.5°C and 2.5°C.

\hypertarget{seafet-durafet-phs}{%
\subsubsection{\texorpdfstring{\textbf{seaFET / durafet
pHs}}{seaFET / durafet pHs}}\label{seafet-durafet-phs}}

\includegraphics{awipev-CO2_files/figure-latex/pHs comparaison-1.pdf}
\includegraphics{awipev-CO2_files/figure-latex/pHs comparaison-2.pdf}

\hypertarget{calculated-durafet-phs}{%
\subsubsection{\texorpdfstring{\textbf{Calculated / Durafet
pHs}}{Calculated / Durafet pHs}}\label{calculated-durafet-phs}}

\includegraphics{awipev-CO2_files/figure-latex/pHs comparaison dur calc-1.pdf}

\hypertarget{calculated-seafet-phs}{%
\subsubsection{\texorpdfstring{\textbf{Calculated / seaFET
pHs}}{Calculated / seaFET pHs}}\label{calculated-seafet-phs}}

\includegraphics{awipev-CO2_files/figure-latex/pHs comparaison sf calc-1.pdf}

\hypertarget{spectro-durafet}{%
\subsubsection{\texorpdfstring{\textbf{Spectro /
durafet}}{Spectro / durafet}}\label{spectro-durafet}}

\includegraphics{awipev-CO2_files/figure-latex/pHs comparaison durafet spectro-1.pdf}

\includegraphics{awipev-CO2_files/figure-latex/pHs comparaison sf spectro-1.pdf}

\hypertarget{snapo-co2}{%
\subsection{SNAPO-CO2}\label{snapo-co2}}

Since November 2018, informations on weekly Ferrybox and monthly
durafet/seaFET samplings are collected in a online document that can be
consulted at anytime:

\href{https://docs.google.com/spreadsheets/d/1bNh9q4bkNoh2ra78XC451EmGb9Q8kMf4ByBnKngeHOg/edit?usp=sharing}{weekly
and monthly samplings}

We found that some analysed discrete seawater replicates for AT/CT,
performed by SNAPO in Paris sometimes show a large difference between
duplicates. Arbitrarily, we decided to take in consideration replicates
with a standard deviation smaller than 10 µmoles.kg-1. In the other case
(greater than 10 µmoles.kg-1), the closest replicate from the general
trend will be kept with qflag\_at/qflag\_ct of 2 (correct analysis) and
the farthest one will be rejected with a flag of 1. There are exceptions
when it is difficult to decide which of the replicates need to be
eliminated.

For TA, dulpicates's flags that have been changed from 2 (good) to 1
(not good) are:

2015-11-18 , 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29,
2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16,
2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03,
2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21,
2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02,
2018-11-09, 2018-11-16, 2018-11-23, 2019-08-23, 2019-09-20, 2019-11-08,
2019-11-23.

For CT, duplicates's flags that have been changed from 2 (good) to 1
(not good) are:

2015-08-06, 2015-08-13, 2016-05-12, 2016-05-19, 2016-06-16, 2016-07-28,
2016-09-08, 2016-10-27, 2016-11-17, 2017-01-19, 2017-03-02, 2017-04-27,
2017-09-14, 2018-04-26, 2018-05-04, 2018-05-12, 2018-05-25, 2018-06-30,
2018-07-20, 2018-08-03, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-28,
2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09,
2018-11-16, 2018-11-23, 2019-05-03, 2019-05-10, 2019-08-23.

Also in the Discrete\_sampling\_AWIPEV.csv, some analysed samples have
been flaged ``3'' by the SNAPO. After a close look, these samples are
not differents from their duplicates. Then we put the flag to ``2''
(good result).

For TA and CT, samples's flags that have been changed from 3 to 2 are:
2019-12-27 (2264 and 2130), 2019-10-25 (2332 and 2152), 2019-09-06 (2268
and 2116).

\includegraphics{awipev-CO2_files/figure-latex/SNAPO-1.pdf}
\includegraphics{awipev-CO2_files/figure-latex/SNAPO-2.pdf}
\includegraphics{awipev-CO2_files/figure-latex/SNAPO-3.pdf}
\includegraphics{awipev-CO2_files/figure-latex/SNAPO-4.pdf}
\includegraphics{awipev-CO2_files/figure-latex/SNAPO-5.pdf}
\includegraphics{awipev-CO2_files/figure-latex/SNAPO-6.pdf}

\hypertarget{impact-of-nutrients}{%
\subsection{Impact of nutrients}\label{impact-of-nutrients}}

\includegraphics{awipev-CO2_files/figure-latex/impact of nutrients-1.pdf}

The concentration of PO4 and Si varies with a factor 10 along a
composite year. The ranges are respectively, 0.07, 0.69 for PO4 and
0.42, 4.7 for Si.

\hypertarget{using-the-pco2-at-pair-hourly-data}{%
\subsubsection{Using the pCO2-AT pair (hourly
data)}\label{using-the-pco2-at-pair-hourly-data}}

The impact of the min max changes of PO4 on pH, DIC, and Omega\_a are
small: 0.11 mpH units, 0.58 umol/kg for CT and 0 for OmegaAragonite.

The impact of the min max changes of Si on pH, DIC, and Omega\_a are
small: 0.01 mpH units, 0.08 umol/kg for CT and 0 for OmegaAragonite.

\hypertarget{using-the-ct-at-pair-discrete-data}{%
\subsubsection{Using the CT-AT pair (discrete
data)}\label{using-the-ct-at-pair-discrete-data}}

The impact of the min max changes of PO4 on pH, pCO2, and Omega\_a are
small: 1.54 mpH units, -1.18 uatm for pCO2 and 0.01 for OmegaAragonite.

The impact of the min max changes of PO4 on pH, pCO2, and Omega\_a are
small: 0.2 mpH units, -0.16 uatm for pCO2 and 0 for OmegaAragonite.

\hypertarget{impact-of-choice-of-constants}{%
\subsection{Impact of choice of
constants}\label{impact-of-choice-of-constants}}

\begin{longtable}[]{@{}lrrrrrr@{}}
\toprule
flag & S & T & pH & pCO2 & DIC & OmegaAragonite\tabularnewline
\midrule
\endhead
pCO2 and ALK & 34.2 & 3.1 & -0.028 & 0.0 & 3.7 & 0.00\tabularnewline
ALK and DIC & 34.2 & 3.1 & -0.019 & -7.5 & 0.0 & 0.03\tabularnewline
\bottomrule
\end{longtable}

The difference induces by the choice of the carbonic acid constants is
large for pH, pCO2 and DIC and negligible for OmegaAragonite.

\hypertarget{air-sea-co2-flux}{%
\subsection{Air-sea CO2 flux}\label{air-sea-co2-flux}}

To calculate the air-sea CO2 flux, we use:

\begin{itemize}
\tightlist
\item
  seawater pCO2 measured in the FerryBox on water pumped from 11 m
  depth.
\item
  atmospheric CO2 measured at the Zeppelin station and downloaded on
  2020-08-19 from
  \url{https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999}
\item
  wind spreed data collected by the AWI at 10 m height (sent to JPG by
  P. Fischer, Aug.~2020)
\end{itemize}

Since there are many gaps, a climatological year is used: air-sea flux
calculated by day, then by month, then by year.

seaFET pH is significantly different at the surface and depth. It should
therefore be the same for pCO2.

Let's look first at the stratification (salinity, temperature and
density).

\includegraphics{awipev-CO2_files/figure-latex/stratification-1.pdf}

\begin{longtable}[]{@{}lrrr@{}}
\caption{Median salinity}\tabularnewline
\toprule
montht & median2m & median9m & sal\_range\tabularnewline
\midrule
\endfirsthead
\toprule
montht & median2m & median9m & sal\_range\tabularnewline
\midrule
\endhead
Jan & 34.89 & 34.87 & 0.03\tabularnewline
Feb & 34.96 & 34.94 & 0.01\tabularnewline
Mar & 35.06 & 34.98 & 0.08\tabularnewline
Apr & 35.06 & 35.03 & 0.04\tabularnewline
May & 35.05 & 35.06 & -0.01\tabularnewline
Jun & NA & 35.14 & NA\tabularnewline
Jul & 33.38 & 34.27 & -0.89\tabularnewline
Aug & 33.19 & 34.02 & -0.82\tabularnewline
Sep & 32.39 & 33.10 & -0.70\tabularnewline
Oct & 32.77 & 33.04 & -0.26\tabularnewline
Nov & 33.82 & 33.84 & -0.02\tabularnewline
Dec & 34.21 & 33.58 & 0.63\tabularnewline
\bottomrule
\end{longtable}

\begin{verbatim}
##                         Df Sum Sq Mean Sq F value Pr(>F)    
## tmp$depth                1    122   122.2  142.74 <2e-16 ***
## tmp$montht              11  10634   966.7 1129.10 <2e-16 ***
## tmp$depth:tmp$montht    10    360    36.0   42.06 <2e-16 ***
## Residuals            15235  13044     0.9                   
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 2292 observations deleted due to missingness
\end{verbatim}

\includegraphics{awipev-CO2_files/figure-latex/stratification-2.pdf}
\includegraphics{awipev-CO2_files/figure-latex/stratification-3.pdf}

\begin{longtable}[]{@{}lrrr@{}}
\caption{Median temperature}\tabularnewline
\toprule
montht & median2m & median9m & temp\_range\tabularnewline
\midrule
\endfirsthead
\toprule
montht & median2m & median9m & temp\_range\tabularnewline
\midrule
\endhead
Jan & 0.80 & 0.97 & -0.17\tabularnewline
Feb & -0.68 & -0.53 & -0.15\tabularnewline
Mar & -0.80 & 0.54 & -1.34\tabularnewline
Apr & -0.82 & 1.20 & -2.03\tabularnewline
May & 2.42 & 2.57 & -0.15\tabularnewline
Jun & 3.50 & 3.80 & -0.30\tabularnewline
Jul & 5.60 & 6.05 & -0.44\tabularnewline
Aug & 5.64 & 6.02 & -0.38\tabularnewline
Sep & 4.40 & 4.83 & -0.43\tabularnewline
Oct & 3.10 & 3.60 & -0.50\tabularnewline
Nov & 2.25 & 2.11 & 0.14\tabularnewline
Dec & 1.78 & 1.36 & 0.42\tabularnewline
\bottomrule
\end{longtable}

\begin{verbatim}
##                         Df Sum Sq Mean Sq F value Pr(>F)    
## tmp$depth                1    103     103   68.41 <2e-16 ***
## tmp$montht              11  59928    5448 3621.74 <2e-16 ***
## tmp$depth:tmp$montht    11    929      84   56.16 <2e-16 ***
## Residuals            17526  26363       2                   
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
\end{verbatim}

\includegraphics{awipev-CO2_files/figure-latex/stratification-4.pdf}

\begin{longtable}[]{@{}lrrr@{}}
\caption{Median density}\tabularnewline
\toprule
montht & median2m & median9m & den\_range\tabularnewline
\midrule
\endfirsthead
\toprule
montht & median2m & median9m & den\_range\tabularnewline
\midrule
\endhead
Jan & 1027.90 & 1027.86 & 0.04\tabularnewline
Feb & 1028.08 & 1028.07 & 0.02\tabularnewline
Mar & 1028.19 & 1028.10 & 0.08\tabularnewline
Apr & 1028.03 & 1028.01 & 0.02\tabularnewline
May & 1027.95 & 1027.96 & -0.01\tabularnewline
Jun & NA & 1027.90 & NA\tabularnewline
Jul & 1026.10 & 1026.99 & -0.89\tabularnewline
Aug & 1026.22 & 1026.73 & -0.51\tabularnewline
Sep & 1025.70 & 1026.19 & -0.49\tabularnewline
Oct & 1026.19 & 1026.29 & -0.10\tabularnewline
Nov & 1026.94 & 1026.97 & -0.03\tabularnewline
Dec & 1027.35 & 1026.97 & 0.38\tabularnewline
\bottomrule
\end{longtable}

\begin{verbatim}
##                         Df Sum Sq Mean Sq F value Pr(>F)    
## tmp$depth                1     69    69.0   133.1 <2e-16 ***
## tmp$montht              11   9017   819.7  1582.1 <2e-16 ***
## tmp$depth:tmp$montht    10    209    20.9    40.4 <2e-16 ***
## Residuals            15235   7893     0.5                   
## ---
## Signif. codes:  0 '***' 0.001 '**' 0.01 '*' 0.05 '.' 0.1 ' ' 1
## 2292 observations deleted due to missingness
\end{verbatim}

\includegraphics{awipev-CO2_files/figure-latex/stratification-5.pdf}
Using the medians because data are missing.

\begin{itemize}
\tightlist
\item
  Salinity
\item
  Temperature is always colder at 0-4 m than below 8 m (0.15 to 2°C).
\end{itemize}

\includegraphics[width=0.03in]{figures/air-sea_CO2_flux}

The annual air-sea CO2 flux is -109 mol/(m2 year).

\hypertarget{maintenance}{%
\subsection{Maintenance}\label{maintenance}}

\hypertarget{remos}{%
\subsubsection{\texorpdfstring{\textbf{REMOS}}{REMOS}}\label{remos}}

\begin{itemize}
\tightlist
\item
  \textbf{2020-09-23}: REMOS started at 20:00 UTC.
\item
  \textbf{2020-09-22}: REMOS stopped at 19:00 UTC because of a power
  shutdown.
\item
  \textbf{2019-03-12}: REMOS on.
\item
  \textbf{2020-02-24}: REMOS off.
\item
  \textbf{2019-09-07}: REMOS back in the water.
\item
  \textbf{2019-09-02}: REMOS removed from the water for maintenance with
  Philipp and Samir.
\item
  \textbf{2018-11-24}: REMOS stopped because of an iceberg. At the
  moment we dont know if instruments are still there/broken.
\end{itemize}

\hypertarget{ferrybox}{%
\subsubsection{\texorpdfstring{\textbf{FerryBox}}{FerryBox}}\label{ferrybox}}

\begin{itemize}
\tightlist
\item
  \textbf{2020-09-30}: FB started at 19:00 UTC.
\item
  \textbf{2020-09-29}: FB stopped at in the morning for few hours.
\item
  \textbf{2020-09-26}: FB stopped at in the morning for few hours.
\item
  \textbf{2020-09-25}: FB stopped at in the morning for few hours.
\item
  \textbf{2020-09-23}: FB started at 20:00 UTC.
\item
  \textbf{2020-09-22}: FB stopped at 19:00 UTC because of a power
  shutdown.
\item
  \textbf{2020-09-22}: FB started again at 08:00 UTC after several
  months of locked down. Lisa repaired it in few minutes only.
\item
  \textbf{2020-09-22}: FB started again after several months of locked
  down. Lisa repaired it in few minutes only.
\item
  \textbf{2020-07-25}: FB stopped. Not possible to go inside to repair
  because the FB is locked after the ``mercurygate''. IPEV locked the FB
  with suspicion of mercury contamination rose up by Bettina
  (Stationleader)
\item
  \textbf{2020-05-24}: FB started again after several months of on
  activity due to very cold T and frozen pipes.
\item
  \textbf{2020-02-18}: FB stopped because of frozen pipes.
\item
  \textbf{2020-01-24}: heater issues in the contenair (power shutdown
  maybe) caused some samples to freeze. See part ``SNAPO'' for details
  on samples.
\item
  \textbf{2019-09-01}: Some interruptions for the FB during 2 weeks of
  maintenance.
\item
  \textbf{2019-06-12}: Markus came to do maintenace.
\item
  \textbf{2019-06-05}: Problem in the relay 15 that controls the waste
  water pump was found. The spare part will be brought here next week
  (when Samir will leave\ldots).
\item
  \textbf{2019-06-03}: Samir is on site alone. Different tests were
  made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the
  problem (low flow).
\item
  \textbf{2019-05-22}: FB is stopped because of several problems.
  Philipp and Marine are working on it.
\item
  \textbf{2019-05-21}: FB is unstable.
\item
  \textbf{2019-04-14}: FB is working again.
\item
  \textbf{2019-04-13}: FB is stopped since 05:00am (the level switch
  stuck in the full position in the waste tank).
\item
  \textbf{2019-02-27}: FB is working again.
\item
  \textbf{2019-02-26}: FB is stopped because of a ``leakage'' issue.
\item
  \textbf{2019-01-17}: FB is stopped until 19th January
\item
  \textbf{2019-01-11}: FB is stopped until 12th Decmeber.
\item
  \textbf{2018-12-28}: FB is stopped until 31st Decmeber.
\item
  \textbf{2018-10-12}: FB is working again.
\item
  \textbf{2018-10-10}: FB is stopped after a seawater leakage.
\item
  \textbf{2018-10-08}: FB is working again.
\item
  \textbf{2018-10-05}: FB is stopped after a seawater leakage.
\item
  \textbf{2018-09-12}: FB is stopped. Problems inland could be the
  reason. The same day Marine make it working again.
\item
  \textbf{2018-04-14}: FB is working again. They made an outlet
  ``by-pass'' tube to flush the seawater directly on the beach, not at
  11 m.
\item
  \textbf{2018-03-08}: Last data at 23:59. Frozen Ferrybox system
  (outlet tubings) in Svalbard, maybe due to a power failure over night
  in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
\item
  \textbf{2017-05-24}: FerryBox was shut down due to many connexion
  issues\ldots see Philipp's email 24/05/2017 18:17.
\item
  \textbf{2017-03-20}: Philipp arrived in NYA to solve the problem.
\item
  \textbf{2017-03-11}: Iceberg destroyed the power-pumps cables
  (Philipp's email on 2017-03-11 10:40). No more data for all
  parameters.
\item
  \textbf{2017-01-31}: Beginning of the 14-days FB maintenance by
  Philipp and Uwe. Gaps in data could be present during this period.
\item
  \textbf{2017-01-17}: Ferrybox stopped for unknown reasons from
  2017-01-17 21:00 to 2017-01-19.
\item
  \textbf{2016-09-24}: No data because of maintenance until the 28th.
  Except for TA wich has data available for this period.
\item
  \textbf{2016-09-20}: Test in the Ferrybox with the seawater. Seawater
  was ``sucked'' (not pumped) from 7:40 to 10:00 by a vaccum system in
  order to test it. This system was installed if the pumps 1 and 2 broke
  during winter. This is a ``plan C''. This system is not automatic and
  we will be informed about its power up in case of emergency. As long
  as the water is not pumped with this system, we have to monitor the
  data because changements in gas partial pressure can occur.
\item
  \textbf{2016-09-12}: No data because of maintenance until the 18th.
\item
  \textbf{2016-09-10}: No data because of maintenance until the 11th.
\item
  \textbf{2016-05-09}: data are back.
\item
  \textbf{2016-05-04}: No data for all parameters because of electricity
  issues.
\item
  \textbf{2016-04-23}: FerryBox was shut down by AWI team for
  maintenance.
\item
  \textbf{2016-02-23}: FerryBox was switched on by AWI team after
  maintenance.
\item
  \textbf{2015-12-20}: FerryBox was shut down because of pump issues.
  Waiting for the maintenance in February.
\item
  \textbf{2015-11-27}: The ferrybox was down from Nov.~18th until today
  Nov.~27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader
  AWIPEV 2015-11-27 12:57). Tubes frozen.
\end{itemize}

\hypertarget{ta-analyser}{%
\subsubsection{\texorpdfstring{\textbf{TA
analyser}}{TA analyser}}\label{ta-analyser}}

\begin{itemize}
\tightlist
\item
  \textbf{2019-11-15}: TA calibration done by Gwendall is OK but the
  sensore seems to have problem since 2019-10-16. Video conference is
  scheduled with Steffen on 2019-11-19. Maybe sample supply is
  defective.
\item
  \textbf{2019-07-12}: Steffen told us that calibration was not OK. To
  check it, he calculated the mediane of the pH/volume sample /
  volumeIndicatorfactor and compared them to January/October
  calibration. We wait for Steffen recommandations before to make
  another calibration.
\item
  \textbf{2019-06-07}: Samir did the TA calibration: T0 with CRM 145.
  Beginning of a 3-months period. TA was stable before the calibration
  and calibration was OK.
\item
  \textbf{2019-02-15}: No data from 15th (14:08:21 UTC) to 19th February
  (14:58:46 UTC). files transfered but no data. No explanation.
\item
  \textbf{2019-01-26}: Philipp did the TA calibration: T0 with CRM 145.
  Beginning of a 3-months period. Flow filter was also lifted up and the
  seawater flow has therefore increased.
\item
  \textbf{2019-01-16}: Bad data since this date.
\item
  \textbf{2018-12-28}: HCL and BCG cartridges were changed by Marine.
\item
  \textbf{2018-11-26}: TA analyser was stopped in order to save reagents
  because of filter issues.
\item
  \textbf{2018-11-20}: A web interface was created by KM Contros to
  access the TA via VPN and Virtual Machine (VNC viewer). Samir received
  password and access from the AWI in order to communicate from France
  with the TA.
\item
  \textbf{2018-10-31}: New TA analyser (SN 0317-001) was installed with
  a new membrane inside (completely new technology). Tests were made
  with Steffen from KM Contros.
\item
  \textbf{2018-07-31}: TA analyser was received (SN TA-1215-001) and
  pluged again. First data were received (high: 2450 and low: 2150) but
  salinity issue since this time. Uwe/Philipp try to find if this comes
  from comunication issue with the FB.
\item
  \textbf{2018-06-20}: TA analyser was stopped in order to save reagents
  because leakage in degasing unit is not solved. Email was sent to
  Steffen.
\item
  \textbf{2018-01-05}: TA analyser switched on and first communication
  tests. S/N TA-0317-001.
\item
  \textbf{2017-08-23}: The 2 TA analysers were sent to Contros for
  repair, 1 will be sent back to NYA after. No more TA data during this
  period.
\item
  \textbf{2017-04-06}: (12:30 UTC) Christelle repaired TA analyser by
  removing air bubbles in Acid tubings (advices from Steffen).
\item
  \textbf{2017-04-01}: No more TA data\ldots waiting for a diagnostic by
  Contros.
\item
  \textbf{2017-03-31}: (11:00 UTC) Christelle switched on TA analyser.
\item
  \textbf{2017-03-30}: (07:30 UTC) Christelle switched TA analyser on
  ``standby'' because of cartridge leakage issue (3 ways connector
  broken).
\item
  \textbf{2017-03-21}: Philipp changed the TA analyser provided by
  Contros.
\item
  \textbf{2017-02-10}: TA cleaning salt crusts.
\item
  \textbf{2017-02-09}: TA calibration with CRM at 12:20.
\item
  \textbf{2017-01-20}: The date issue with TA analyser since 201-01-07
  was fixed by Uwe with a restart of the Ferrybox Module around 14:00
  UTC.
\item
  \textbf{2016-11-15}: TA calibration done by Christelle with Dickson
  CRM run as regular sample (measure mode). Data of this calibration do
  not appear on plot because TA analyser is disconnected from the
  FerryBox.
\item
  \textbf{2016-09-16}: Cleaning of the TA analyser removing all the salt
  crusts from the bottom of the degazing unit (Samir).
\item
  \textbf{2016-06-24}: BCG cartridge was changed (Christelle, ObsEng).
\item
  \textbf{2016-05-31}: HCL cartridge was changed (Christelle, ObsEng).
\item
  \textbf{2016-05-01}: No data for TA.
\item
  \textbf{2016-04-26}: Salt crusts inside the TA analyser appeared
  during deployment (see pictures) were removed by René Burgi
  (Observatory engineer) according to Contros advices (email from
  Steffen Assmann 13/04/2016 10:30).
\end{itemize}

\hypertarget{ph-seafet-1}{%
\subsubsection{\texorpdfstring{\textbf{pH
seaFET}}{pH seaFET}}\label{ph-seafet-1}}

\begin{itemize}
\tightlist
\item
  \textbf{2019-09-02}: Out from the water for maintenance and cleaning
  only.
\item
  \textbf{2018-04-17}: seaFET \#1005 was changed on the REMOS and seaFET
  \#007 (from Villefranche) was installed. Continuous mode with external
  power supply was set and internal pack of baterries was removed. Old
  seaFET will be brought back to France with Samir.
\item
  \textbf{2018-03-09}: \#007 seaFET currently in USA will be sent by
  seabird to NYA. \#1005 seaFET currently in NYA will be sent to USA for
  update, following all external issues, for free.
\item
  \textbf{2017-08-24}: seaFET \#1005 was installed on the REMOS into the
  field.
\end{itemize}

\hypertarget{cross-flow-filter}{%
\subsubsection{\texorpdfstring{\textbf{Cross-Flow
filter}}{Cross-Flow filter}}\label{cross-flow-filter}}

\begin{itemize}
\tightlist
\item
  \textbf{2019-01-26}: The filter was lifted up in order to fix the flow
  problem.
\item
  \textbf{2018-11-01}: The filter clogged a lot of time even after acid
  cycles. It was not replaced since its initial installation with the TA
  analyser. We think to replace it soon.
\item
  \textbf{2016-07-20}: Cross filter was cleanned by Obs. eng. with 10-15
  min tape water flush.
\end{itemize}

\hypertarget{durafet}{%
\subsubsection{\texorpdfstring{\textbf{durafet}}{durafet}}\label{durafet}}

\begin{itemize}
\tightlist
\item
  \textbf{2019-09-05}: same durafet
\item
  \textbf{2017-10-30}: (13:00 UTC) Durafet holder was changed by Benoit
  and the new one (made by Uwe) more larger (all the durafet's body is
  plunge in the seawater) was installed.
\item
  \textbf{2017-08-24}: durafet was installed.
\end{itemize}

\hypertarget{pco2-1}{%
\subsubsection{\texorpdfstring{\textbf{\emph{p}CO\textsubscript{2}}}{pCO2}}\label{pco2-1}}

\begin{itemize}
\tightlist
\item
  \textbf{2019-09-03}: \emph{p}CO\textsubscript{2} analyser (S/N:
  CO2FT-0515-001) have been installed and \emph{p}CO\textsubscript{2}
  analyser (S/N: CO2FT-0215-001) was sent to Kiel for calibration.
\item
  \textbf{2018-10-31}: \emph{p}CO\textsubscript{2} analyser (S/N:
  CO2FT-0215-001) have been installed and \emph{p}CO\textsubscript{2}
  analyser (S/N: CO2FT-0515-001) was brought back to France and waiting
  2019 fundings to bring it for calibration.
\item
  \textbf{2018-04-16}: \emph{p}CO\textsubscript{2} analyser switching by
  Uwe and Samir. S/N CO2FT-0515-001 is now installed. Old
  \emph{p}CO\textsubscript{2} sensor will be brought back to France with
  Samir.
\item
  \textbf{2017-02-07}: pCO2 analyser switching by Uwe. S/N
  CO2FT-0215-001 is now installed.
\item
  \textbf{2016-09-13}: Changement of the \emph{p}CO\textsubscript{2} S/N
  CO2FT-0515-001 membrane (Uwe from 4H-Jena).
\item
  \textbf{2016-02-28}: \emph{p}CO\textsubscript{2} analyser (S/N
  CO2FT-0215-001) was sent to calibration and the second
  \emph{p}CO\textsubscript{2} analyser (S/N: CO2FT-0515-001) have been
  installed.
\end{itemize}

\hypertarget{script-data}{%
\subsection{Script + data}\label{script-data}}

Here is reported all important modifications made on
\emph{ny-alesund\_cc.}. All documents concerning maintenance, tasks to
do, calibration\ldots{} are accessible by the AWIPEV staff on this link
with special access:

\href{https://spaces.awi.de}{wiki document}

\href{https://docs.google.com/spreadsheets/d/1bNh9q4bkNoh2ra78XC451EmGb9Q8kMf4ByBnKngeHOg/edit\#gid=1034421443}{Logbook
discrete sampling}

\href{https://docs.google.com/spreadsheets/d/1QwAJm7TttoEwue-CUM0efhqEAMwj5m148Gy_Mp-1maM/edit?ts=5ed0fca6\#gid=2036495380}{Logbook
FerryBox}

\href{https://docs.google.com/spreadsheets/d/1arKYfUjmg3YrgQ5g9LN_XFwUORyz7nqlKNWq3uYok3U/edit?ts=5c7e1d16\#gid=393659093}{UWO-Ferrybox
variables from our sensors}

\href{https://dashboard.awi.de/?dashboard=3760}{Dashboard}

\href{https://spaces.awi.de/confluence/display/MOS/NRT+data+download+procedures}{Procedure
to download NRT data}

\href{https://dashboard.awi.de/data-xxl/}{AWI NRT database}, search for
svluwobs

\href{https://dashboard.awi.de/?dashboard=9736}{Quick overview AWI NRT
database}

\hypertarget{ferrybox-1}{%
\subsubsection{\texorpdfstring{\textbf{FerryBox}}{FerryBox}}\label{ferrybox-1}}

\begin{itemize}
\tightlist
\item
  \textbf{2020-03-13}: Salinity was filtered above 28 in d\_all.rds
  file.
\item
  \textbf{2018-11-14}: One instrument was removed by Uwe (Chlorophyl-a),
  that means that one column (CHl\_A\_Cyclops) was also removed from the
  Ferrybox data file. Script was modified in consequence.
\end{itemize}

\hypertarget{ph-seafet-2}{%
\subsubsection{\texorpdfstring{\textbf{pH
seaFET}}{pH seaFET}}\label{ph-seafet-2}}

\begin{itemize}
\tightlist
\item
  \textbf{2018-08-30}: voltINT + phINT were filtered from 2017-12-14 to
  2018-01-08 and bad data were removed from 2018-01-08 to 2018-02-02. pH
  spectro from 2018-04-16 07:00:00 was fitted with a mean of 4 days of
  voltINT in order to make the calibration for this 5th period.
\item
  \textbf{2018-07-30}: Flag location (location\_flag) is added in the
  script to localize seaFET/durafet discrete samples: flag 1 = at the
  harbor (not taken in consideration) and flag 0 = in the FB for durafet
  or on site for seaFET (takken in consideration as ``normal''
  sampling"). See seaFET part.
\item
  \textbf{2018-02-02}: Based on Darrell's advices (SeaBird), Philipp
  implemented the seaFET as: 1h periodic sampling with the following
  commands: perdival 1h, navg 5, brstsize 1, opermode periodic.
\item
  \textbf{2017-12-29}: ``SVL\_20171218\_010426.dat'' from seaFet data
  was deleted because of bug with its size (0 octect). pH filter was
  added to ``ny\_alesund\_cc'' file for seaFet data (\textless7.5 and
  \textless8.5).
\end{itemize}

\hypertarget{durafet-1}{%
\subsubsection{\texorpdfstring{\textbf{Durafet}}{Durafet}}\label{durafet-1}}

\begin{itemize}
\tightlist
\item
  Reference spectro measurement from the 2019-01-18 11:00 do not match
  with a durafet raw data because Ferrybox was off. This reference point
  was not takken in consideration for calibration. The window of the
  previous and next calibration periods was extended.
\end{itemize}

\hypertarget{pco2-2}{%
\subsubsection{\texorpdfstring{\textbf{\emph{p}CO\textsubscript{2}}}{pCO2}}\label{pco2-2}}

\begin{itemize}
\tightlist
\item
  \textbf{2020-03-11}: Post calibration parameters for period 4
  (2018-04-16 to 2018-10-31) were not taken in consideration because
  they lead to wrong correction.
\item
  \textbf{2019-11-18}: Calibration parameters from \#0215-001 were added
  to ``server\ldots/data/NRT\_data/Data\_Processing\_sheet\_pCO2.csv''
  (new path).
\item
  \textbf{2018-08-29}: Calibration parameters from \#0215-001 were added
  to ``./data/Calibration\_pCO2/Data\_Processing\_sheet\_pCO2.csv''.
\item
  \textbf{2018-04-20}: For \emph{p}CO\textsubscript{2} Calibration the
  previous period (N° 4) was added to the script ``ny-alesund\_cc'' line
  466.
\item
  \textbf{2015-10-13}: we put back the spike.pCO2 to 600 because data in
  October reached more than 350 µAtm. We let this like that and we are
  going to deal with it manually later if needed.
\item
  \textbf{2015-09-28}: we put the spike.pCO2 (detection of peaks:
  threshold) at 350 to remove anomalies on the 12 and 15 September. We
  have to monitor data. If data reach this value, then problem.
\end{itemize}

\hypertarget{snapo}{%
\subsubsection{\texorpdfstring{\textbf{SNAPO}}{SNAPO}}\label{snapo}}

\begin{itemize}
\item
  \textbf{2020-01-23}: Freezed and lost samples because of heater issue
  in the container: 15/11/2019 (durafet x1), 03/12/2019 (FB x2),
  11/12/2019 (FB x2), 13/12/2019 (FB x2), 20/12/2019 (FB x2), 03/01/2020
  (FB x2). Following samples could have been frozen, not sure:
  06/09/2019 (FB x2), 13/09/2019 (seaFET x1), 13/09/2019 (FB x2),
  20/09/2019 (FB x1), 27/09/2019(FB x2), 04/10/2019 (FB x2), 11/10/2019
  (FB x1), 11/10/2019 (durafet x1), 25/10/2019 (FB x2), 01/11/2019 (FB
  x1), 15/11/2019 (FB x1).
\item
  \textbf{2020-01-15}: Results from 2019-04-19 to 2019-08-31 (sent in
  September 2019) were received. FB duplicates from 2019-08-09 were
  analysed as Durafet because of wrong box. One sample from 2019-06-07
  (durafet) was analysed by Paris because of wrong box.
\item
  \textbf{2019-04-30}: Duplicate ``Ferrybox'' samples (SN0316 and SN264,
  2019-02-22 14:05) were sent by mistake in Villefranche for pH
  measurements. Those results were put in the datafile as ``durafet''
  samples as soon as they are comming from the Ferrybox tape seawater.
  We will add a lack of DIC for this week. TA will be measured in
  Villefranche.
\item
  \textbf{2018-08-30}: flag of 1 AT duplicate (2205) from 2017-08-31 was
  put to 3 (dosage douteux).
\end{itemize}

\hypertarget{files---server}{%
\subsubsection{\texorpdfstring{\textbf{Files -
server}}{Files - server}}\label{files---server}}

\begin{itemize}
\tightlist
\item
  \textbf{2019-11-15}: Script including the new data downloading from
  the NRT AWI database is running (ny-alesund\_cc.R). From this date,
  data are donwloaded from AWI NRT dtabase. We are waiting some setting
  from Philipp to have the entire dataset. Only 2018-2019 are available
  for the moment. New path was created in the server and pCloud/exp168
  with ``NRT\_data'' file. Please see the picture bellow.
\item
  \textbf{2018-04-19}: Since ``Ferrybox'' is on again, the adding to
  solve the files issues are making not data into d\_hour for this
  period (2018-09-03 to 2018-14-04). This adding was put in comments
  now. In seaFET data reading, S/N have been changed from 1005 to 0007.
\item
  \textbf{2018-03-21}: Files issues. FerryBox instruments are down
  because of freezing but UWO instrument as seaFET and SBE38 are OK.
  Removing of one 0 octet file from seaFET20180317\_1404 and put back
  seaFET files from 20180309 to 20180312 in seaFET folder. They were in
  SBE38 folder\ldots Weird. Additionnal script lines were added in order
  to deal with the issue of ``in situ'' created date whereas
  ``Ferrybox'' created data ware not. Since ``in situ'' parameters are
  running (d df) and not ``in ferrybox'' parameters (z df), the new
  datetime lines are not taking in consideration with the left\_join
  function we have to add them during Ferrybox shutdown.
\item
  \textbf{2018-03-09}: Script issue solved with first negative values
  encountred in SBE38 files. We find a regex solution to take ``space +
  space or negative value'' in consideration.
\item
  \textbf{2017-11-07}: Wrong seaFET files (wrong datetime starting on
  the 5th September) from 24 to 26 October were fixed. File
  ``SVL\_20171024\_030426\_to\_20171026\_110425\_SeaFet-1005.txt'' were
  created in SeaFet\_archive.
\end{itemize}

\hypertarget{data-processing}{%
\subsubsection{Data processing}\label{data-processing}}

\hypertarget{script-ny-alesund_cc.r-which-runs-on-awipevawipev-co2.obs-vlfr.fr}{%
\paragraph{\texorpdfstring{Script ny-alesund\_cc.R which runs on
\href{mailto:awipev@awipev-co2.obs-vlfr.fr}{\nolinkurl{awipev@awipev-co2.obs-vlfr.fr}}}{Script ny-alesund\_cc.R which runs on awipev@awipev-co2.obs-vlfr.fr}}\label{script-ny-alesund_cc.r-which-runs-on-awipevawipev-co2.obs-vlfr.fr}}

\begin{itemize}
\tightlist
\item
  reads data from the AWI NRT database
  \href{https://dashboard.awi.de/?dashboard=9736}{Quick overview AWI NRT
  database}
\item
  calibrates pCO2 data
\item
  data cleaning:

  \begin{itemize}
  \tightlist
  \item
    Argo Global Range Test.
  \item
    filter salinities above 28
  \item
    filter temperatures above 10
  \item
    filter seaFET Volt (outliers)
  \item
    filter seaFET pH (outliers)
  \item
    filter durafet (outliers)
  \end{itemize}
\item
  Quality flags

  \begin{itemize}
  \tightlist
  \item
    1: good data
  \item
    3: impossible date and time test
  \item
    4: data not usable according to manufacturer (flush mode, zero mode,
    calibration mode\ldots)
  \item
    6: failing the manufacturer range test (not used)
  \item
    7: failing the regional range test
  \item
    12: failing the spike test (NAs from despike)
  \item
    13: failing the gradient test
  \item
    15: the instrument was not deployed or operated
  \item
    16: acid flush
  \item
    99: failing the final visual inspection of the data.
  \end{itemize}
\item
  Despike using oce::despike with n=2, k=5761
\item
  Files generated:

  \begin{itemize}
  \tightlist
  \item
    previous\_NRT\_data.rds: all NRT data without alteration from the
    beginning (2015)
  \item
    all\_nydata\_minute.rds: all data after filtering and despike
    describe above (every minute)
  \item
    all\_nydata\_hour.rds: hourly means of all data after filtering and
    despike describe above (every minute)
  \item
    nydata\_minute.rds: selected data after filtering and despike
    describe above (every minute). \textbf{Useful?}
  \item
    nydata\_hour.rds: selected hourly means of all data after filtering
    and despike describe above (every minute). This is for further data
    processing.
  \end{itemize}
\end{itemize}

\hypertarget{script-awipev-co2.rmd-which-runs-locally}{%
\paragraph{Script awipev-co2.Rmd which runs
locally}\label{script-awipev-co2.rmd-which-runs-locally}}

\begin{itemize}
\tightlist
\item
  reads locally
  fb\_awipev-co2\_server/ny-alesund/data/NRT\_data/nydata\_hour.rds
\item
  sal\_mix: when ferrybox data (sal\_fb) are missing, they are replaced
  by data from the profiling ctd for depths \textgreater{} 8 m
  (sal\_insitu\_ctd\_9m)
\item
  temp\_mix: when data of in situ temperature at 11 m
  (temp\_insitu\_11m) are missing, they are replaced by data from the
  profiling ctd for depths \textgreater{} 8 m
\item
  pco2\_calc\_fb: pco2 calc from AT/CT ferrybox = carb avec temp\_fb
  +sal\_fb
\item
  calibrate seafet pH

  \begin{itemize}
  \tightlist
  \item
    ph\_s\_sf\_temp\_insi: pH spectro seaFET pH insi calculé avec AT
    interpolée + temp\_mix +sal\_mix
  \item
    E0int25\_sf: calculé à partir du voltage interne +
    ph\_s\_sf\_temp\_insi (temp 11m + temp\_insitu\_ctd\_9m si trous) +
    temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
  \item
    phint\_tot\_sf: calculé à partir du voltage interne + E0 + temp CTD
    + sal CTD (calib seaFET fonction 2)
  \end{itemize}
\item
  ph\_calc: pH calc from AT/CT ferrybox = carb avec temp\_fb +sal\_fb
\item
  despike pH seaFET
\item
  calibrate durafet pH

  \begin{itemize}
  \tightlist
  \item
    ph\_s\_dur\_temp\_fb: pH spectro durafet pH insi calculé avec AT
    interpolée + temp\_fb +sal\_fb
  \end{itemize}
\item
  Relation at / sal\_mix
\item
  at\_calc: calculé from sal\_mix
\item
  saves locally d\_all.rds which comprises all variables plus those
  generated in the script
\end{itemize}

\hypertarget{villefranche-server-informations}{%
\subsubsection{Villefranche Server
informations}\label{villefranche-server-informations}}

\begin{itemize}
\tightlist
\item
  Serveur : awipev-co2 (193.50.85.104)
\item
  3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l'envoi
  des données par P. Fischer mais n'est plus utilisé).
\item
  Pour se connecter à awipev-co2.obs-vlfr.fr

  \begin{itemize}
  \tightlist
  \item
    ssh
    \href{mailto:awipev@awipev-co2.obs-vlfr.fr}{\nolinkurl{awipev@awipev-co2.obs-vlfr.fr}}
  \end{itemize}
\item
  Intervention sur le serveur :

  \begin{itemize}
  \tightlist
  \item
    ssh
    \href{mailto:awipev@awipev-co2.obs-vlfr.fr}{\nolinkurl{awipev@awipev-co2.obs-vlfr.fr}}
  \item
    rebooting Ubuntu server: sudo shutdown -r now
  \item
    to check versions:

    \begin{itemize}
    \tightlist
    \item
      dpkg -l \textbar{} grep shiny
    \item
      dpkg -l \textbar{} grep r-base
    \end{itemize}
  \item
    To update Ubuntu, R and its packages:

    \begin{itemize}
    \tightlist
    \item
      sudo su
    \item
      apt-get upgrade
    \end{itemize}
  \item
    To restart shiny server: sudo systemctl restart shiny-server

    \begin{itemize}
    \tightlist
    \item
      update shiny server: follow procedure detailed on the shiny web
      page Data processing
    \end{itemize}
  \end{itemize}
\item
  To install R packages:

  \begin{itemize}
  \tightlist
  \item
    ssh
    \href{mailto:gattuso@awipev-co2.obs-vlfr.fr}{\nolinkurl{gattuso@awipev-co2.obs-vlfr.fr}}
  \item
    sudo R (then password)
  \item
    install.packages(``tidyverse'')
  \end{itemize}
\end{itemize}

\textbf{crontab
\href{mailto:awipev@awipev-co2.obs-vlfr.fr}{\nolinkurl{awipev@awipev-co2.obs-vlfr.fr}}}

Si on veut remplacer intégralement les fichiers de pCloud par ceux de
awipev-co2 : ajouter ``--delete'' à la commande rsync. Pattern des
commandes : \# m h dom mon dow command

\begin{itemize}
\tightlist
\item
  (Every 4 hour on the hour, a crontab action runs automatically the
  script ny-alesund/R/ny-alesund\_cc.R. This script essentially appends
  the daily files from AWI-NRT database and cleans the data)

  \begin{itemize}
  \tightlist
  \item
    00 \emph{//1 } * * cd \$HOME; USER=awipev R --vanilla \textless{}
    ny-alesund/R/ny-alesund\_cc.R \textgreater{}
    ny-alesund/R/log\_ny-alesund\_cc.txt 2\textgreater\&1
  \end{itemize}
\item
  (Every 4 hour at 10 min past the hour, the web page is generated)

  \begin{itemize}
  \tightlist
  \item
    10 \emph{//1 } * * cd web; USER=awipev bash awipev-co2.sh
    \textgreater{} awipev-web.log 2\textgreater\&1
  \end{itemize}
\item
  (At 05:00 the files from server/web are copied to gattuso's iMac in
  pCloud \ldots{} Exp168)

  \begin{itemize}
  \tightlist
  \item
    00 05 * * * /usr/bin/rsync -e ``ssh -o StrictHostKeyChecking=no''
    -avh /home/awipev/web
    `\href{mailto:gattuso@gattuso.obs-vlfr.fr}{\nolinkurl{gattuso@gattuso.obs-vlfr.fr}}:/Users/gattuso/pCloud~Sync/Documents/experiments/exp168\_awipev-CO2/fb\_awipev-co2\_server/'
  \end{itemize}
\item
  (At 05:00 the files from server/ny-alesund are copied to gattuso's
  iMac in pCloud/Exp168)

  \begin{itemize}
  \tightlist
  \item
    00 05 * * * /usr/bin/rsync -e ``ssh -o StrictHostKeyChecking=no''
    -avh /home/awipev/ny-alesund
    `\href{mailto:gattuso@gattuso.obs-vlfr.fr}{\nolinkurl{gattuso@gattuso.obs-vlfr.fr}}:/Users/gattuso/pCloud~Sync/Documents/experiments/exp168\_awipev-CO2/fb\_awipev-co2\_server/'
  \end{itemize}
\end{itemize}

\hypertarget{web-page}{%
\subsubsection{Web page}\label{web-page}}

\begin{itemize}
\item
  La page web index.html est faite sur le serveur awipev/web grâce au
  script awipev-CO2\_web.Rmd puis transférée et renommée dans
  awipev/awipev-CO2\_web
\item
  Création du répertoire web qui contient ce qu'il faut pour générer la
  page web:

  \begin{itemize}
  \tightlist
  \item
    AWIPEV-Logo.jpg
  \item
    Discrete\_sampling\_AWIPEV.csurv
  \item
    awipev-CO2\_web.Rmd
  \item
    awipev-co2.sh (lancer par bash awipev-co2.sh)
  \end{itemize}
\item
  Accessible \url{https://awipev-co2.obs-vlfr.fr}
\item
  On utilise un shell script awipev-co2.sh :

  \#!/bin/bash

  \# script de lancement via crontab echo `---------deb awipev-co2.sh
  -----------'

  \# On lance la fabrication du html (une seule ligne) cd web; R -e
  `library(``rmarkdown'');library(``knitr'');rmarkdown::render(``awipev-CO2\_web.Rmd'')';
  cp awipev-CO2\_web.html ../awipev-CO2\_web/index.html

  echo `---------fin awipev-co2.sh -----------'
\end{itemize}

A la main dans le terminal, cela donne :

\begin{itemize}
\tightlist
\item
  ssh
  \href{mailto:awipev@awipev-co2.obs-vlfr.fr}{\nolinkurl{awipev@awipev-co2.obs-vlfr.fr}}
\item
  cd; bash web/awipev-co2.sh
\end{itemize}

\includegraphics[width=0.65\textwidth,height=\textheight]{Images/awipev_server_arborescence.jpg}

\end{document}

### 2021-01-29 awipev-CO2.Rmd
dunno

@@
               colour = "blue")  + 
-  labs(title = paste(titre,"\n Adj R2 = ", signif(fit$rsquare, 3),
+  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                      "; Intercept =", signif(intercept, 3),
@@
 #################### Function RMSE for model 2 regression root mean square error
-lm2 <- function(x, y) { 
-  fit <- lmodel2(y  ~ x , nperm = 99)
-  intercept <- fit$regression.results[2,2]
-  slope <- fit$regression.results[2,3]
-  predicted <- intercept + x * slope
-  error <- predicted - x
+lm2 <- function(data = NULL, x, y) {
+  xs <- deparse(substitute(x))
+  ys <- deparse(substitute(y))
+#fit <- lmodel2(formula = y  ~ x, data = data, nperm = 99)
+  print(y)
+  #return(fit)
+
+  lmwrap <- function(d,y,x) {
+    ys <- deparse(substitute(y))
+    xs <- deparse(substitute(x))
+    f <- reformulate(xs,response=ys)
+    return(lm(f,data=d))
+}
+mydata <- data.frame(X=1:10,Y=rnorm(10))
+lmwrap(mydata,Y, X)
+
+lm2(x = d_all$pco2_calc_fb, y = d_all$pco2_fb)
+lm2(data = d_all, x=pco2_calc_fb, y=pco2_fb)
+
+lmodel2(d_all$pco2_calc_fb ~ d_all$pco2_fb, nperm = 99)
+
+  intercept_MA <- fit$regression.results[2,2]
+  slope_MA <- fit$regression.results[2,3]
+  intercept_OLS <- fit$regression.results[1,2]
+  slope_OLS <- fit$regression.results[1,3]
+  predicted <- intercept_OLS + df[[x]] * slope_OLS
+  error <- x - predicted
   my_list <- list(fit = fit, rmse = sqrt(mean(error^2, na.rm=TRUE)))
@@
   coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
-  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()  
+  labs(x="Calculated pCO2", y="Contros pCO2") + theme_bw()  
 ```

### 2021-02-01 awipev-CO2.Rmd
Rmd works again

@@
 ---
-title: "Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project" 
+title: "Carbonate chemistry at Ny-Ålesund" 
 author: "Jean-Pierre Gattuso and Samir Alliouane"
@@
 output:
-  rmarkdown::
   rmarkdown::html_document:
@@
     number_sections: false
-
 ---
@@
 #################### Function RMSE for model 2 regression root mean square error
+#test <- readr::read_csv(file="test_file")
 lm2 <- function(data = NULL, x, y) {
-  xs <- deparse(substitute(x))
-  ys <- deparse(substitute(y))
-#fit <- lmodel2(formula = y  ~ x, data = data, nperm = 99)
-  print(y)
-  #return(fit)
-
-  lmwrap <- function(d,y,x) {
-    ys <- deparse(substitute(y))
-    xs <- deparse(substitute(x))
-    f <- reformulate(xs,response=ys)
-    return(lm(f,data=d))
-}
-mydata <- data.frame(X=1:10,Y=rnorm(10))
-lmwrap(mydata,Y, X)
-
-lm2(x = d_all$pco2_calc_fb, y = d_all$pco2_fb)
-lm2(data = d_all, x=pco2_calc_fb, y=pco2_fb)
-
-lmodel2(d_all$pco2_calc_fb ~ d_all$pco2_fb, nperm = 99)
-
+  col_x <- eval(substitute(x), data)
+  col_y <- eval(substitute(y), data)
+  col_x <- x
+  col_y <- y
+fit <- lmodel2(col_y ~ col_x, nperm = 99)
   intercept_MA <- fit$regression.results[2,2]
@@
   slope_OLS <- fit$regression.results[1,3]
-  predicted <- intercept_OLS + df[[x]] * slope_OLS
-  error <- x - predicted
-  my_list <- list(fit = fit, rmse = sqrt(mean(error^2, na.rm=TRUE)))
+  predicted <- intercept_OLS + col_x * slope_OLS
+  error <- col_x - predicted
+  my_list <- list(fit = print(fit), rmse = sqrt(mean(error^2, na.rm=TRUE)))
   return(my_list)
 }
+#z <- lm2(x = d_all$pco2_calc_fb, y = d_all$pco2_fb)
+#z <- lmodel2(d_all$pco2_fb ~ d_all$pco2_calc_fb)
+#z <- lm2(data = d_all, x = pco2_calc_fb, y = pco2_fb)
 
@@
 ### Using mean values
-```{r impact of constants, echo=FALSE, warning=FALSE, message=FALSE}
+```{r impact of constants 1, echo=FALSE, warning=FALSE, message=FALSE}
 # Compare Lueker and Sulpis
@@
 ### Using all values pCO2 and at_calc
-```{r impact of constants, echo=FALSE, warning=FALSE, message=FALSE}
+
+```{r impact of constants 2, echo=FALSE, warning=FALSE, message=FALSE}
 # Compare Lueker and Sulpis
@@
 # plot
-lm <- lm2(x = tmp$sal_insitu_ctd_9m, y = d_all$sal_fb)
+lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
 p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
@@
 
-The difference induces by the choice of the carbonic acid constants is large for pH, pCO2 and DIC and negligible for OmegaAragonite.
+The difference induced by the choice of the carbonic acid constants is large for pH, pCO2 and DIC and negligible for OmegaAragonite.
 

### 2021-02-04 awipev-CO2.Rmd
reorganized variable names and order of colmuns

@@
                 date = d_hour$date,
+                year = lubridate::year(d_hour$datetime), # year as a number
                 monthd = lubridate::month(d_hour$datetime), # month as a number
@@
 discrete <- left_join(discrete, d_all %>% dplyr::select(c(closest_datetime, voltEXT, voltINT)), by="closest_datetime")
+
+# order columns
+d_all <- d_all %>% 
+  dplyr::select(order(colnames(d_all))) %>% 
+  dplyr::select(datetime, date, year, monthd, montht, everything())
 ```
@@
       Tlab = temp_fb,
-      SST = temp_insitu_11m),
-    .after = pco2_fb
+      SST = temp_insitu_11m)
 )
@@
 d_all$ct <- ifelse(is.nan(d_all$at), NA, d_all$ct) # replace all NaN by NA
-d_all <- dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))
+#d_all <- dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))
+
+# order columns
+d_all <- d_all %>% 
+  dplyr::select(order(colnames(d_all))) %>% 
+  dplyr::select(datetime, date, year, monthd, montht, everything())
+
 saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)

### 2021-02-09 awipev-CO2.Rmd
added ggreg

@@
 #################### Regression function
-# function regression plot with model II equation (MA) in title
-## Dans labs ajout de la variable TITRE pour mettre titre avant chaque graphe
-ggreg2 <- function (fit, xdata, ydata) { # x and y are the names of the variables
-  fit_data <- data.frame(fit$x, fit$y)
-  colnames(fit_data) = c(xdata, ydata)
-reg <- fit$regression.results[2,] #one selects MA only
-intercept <- reg$Intercept
-slope <- reg$Slope
-  ggplot(data = fit_data, aes_string(x = xdata, y = ydata)) + 
-  geom_point(size = 2, col = "blue") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),
+# function regression plot with equation (MA or OLS) in title
+ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title") { # x and y are the names of the variables
+  fit_data <- tibble(xdata, ydata)
+  colnames(fit_data) = c("xdata", "ydata")
+  fit <- print(lmodel2::lmodel2(ydata ~ xdata))
+if (type == "OLS") ty = 1 #one selects OLS only
+if (type == "MA") ty = 2 #one selects MA only
+#reg <- fit$regression.results[ty,] #one selects OLS only
+intercept <- fit$regression.results$Intercept[ty]
+slope <- fit$regression.results$Slope[ty]
+if (plot == TRUE) {
+  plt <- ggplot(data = fit_data, aes(x = xdata, y = ydata)) + 
+  geom_point(na.rm = TRUE, size = 2, colour = "blue") +
+  geom_abline(aes(intercept = intercept, slope = slope),
               colour = "blue")  + 
-  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
+  labs(title = paste(title, "; type: ", type,
+                     "\n R2 = ", round(fit$rsquare, digits = 2),
                      "; Intercept =", signif(intercept, 3),
@@
                      "; P =", signif(fit$P.param, 3)))
+  return(plt)
+  } else {
+  return(fit)
+}
 }

### 2021-02-09 awipev-CO2.Rmd
deleted duplicate ggreg

@@
 if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"
-
-######## function to make regression plot with model I equation in title
-ggreg <- function (fit, point_size=2) {
-  ggplot(fit$model, aes_string(x = names(fit$model)[2],
-                               y = names(fit$model)[1])) +
-    geom_point(size = point_size, col = "blue") +
-    stat_smooth(method = "lm", col = "black") +
-    labs(title = paste(title, "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                       "; Intercept =",signif(fit$coef[[1]],5 ),
-                       "; Slope =",signif(fit$coef[[2]], 5),
-                       "; P =",signif(summary(fit)$coef[2,4], 5))) +
-    theme(plot.title = element_text(size=7))
-}
 

### 2021-02-15 awipev-CO2.Rmd
Cleaned setup

--- 2021-02-09 awipev-CO2.Rmd
@@
 if (!require("tidyverse")) install.packages("tidyverse")
-library(dplyr)
 library(tidyverse)
-if (!require("robfilter")) install.packages("robfilter")
 if (!require("robfilter")) install.packages("robfilter")

### 2021-02-17 awipev-CO2.Rmd
Preparing to calculate monthly availability.

@@
 kable(z, digits = 1)
+
+# Good data per year
+
 rm(d_min)

### 2021-02-19 awipev-CO2.Rmd
idem
calculations of min.max/mean of SD for spectro pH

@@
 
-# Make mean for replicates. create separate seafet/durafet df to join to initial "d" df
+# Make mean for replicates + SD
 pH_seafet_mean <- pH_seafet%>%
@@
   dplyr::group_by(date) %>% 
-  dplyr::summarize(ph_s_sf_temp_insi = mean(ph_s_sf_temp_insi, na.rm = TRUE))
+  dplyr::summarise(ph_s_sf_temp_insi_mean = mean(ph_s_sf_temp_insi, na.rm = TRUE),
+                   ph_s_sf_temp_insi_sd= sd(ph_s_sf_temp_insi, na.rm = TRUE)
+                   )
+
 pH_durafet_mean <- pH_durafet%>%
@@
   dplyr::group_by(date) %>% 
-  dplyr::summarize(ph_s_dur_temp_fb = mean(ph_s_dur_temp_fb, na.rm = TRUE))
+  dplyr::summarize(ph_s_dur_temp_fb_mean = mean(ph_s_dur_temp_fb, na.rm = TRUE),
+                   ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE))
+
+#bind all spectro measurements, vhange name of dataframe only to do the rbind.
+seafetph <- pH_seafet_mean
+colnames(seafetph) <- c("date", "mean", "sd")
+durafetph <- pH_durafet_mean
+colnames(durafetph) <- c("date", "mean", "sd")
+pH_seafet_durafet <- rbind(seafetph,durafetph)
+
+#calculations for all pH spectro measurement for sd
+sd_min <- min(pH_seafet_durafet$sd)
+sd_max <- max(pH_seafet_durafet$sd)
+sd_mean <- mean(pH_seafet_durafet$sd)
 
@@
 
-rm(d_min)
+#rm(d_min)
 ```

### 2021-02-19 awipev-CO2.Rmd
added monthly distribution of data

--- 2021-02-17 awipev-CO2.Rmd
@@
 
-# Good data per year
-
-rm(d_min)
+# Monthly distribution of hourly data
+d2 <- d_all %>% 
+  dplyr::select(datetime, montht, pco2_inst, ph_s_sf_temp_insi)
+p <- ggplot(data = d2, aes(x = montht, y = pco2_inst)) +
+  geom_bar(stat="identity", width = 0.3) +
+  scale_fill_discrete(labels = labels) + 
+  labs(x="Month", y="pCO2", title = "") +
+  Mytheme(size_labs = 8) +
+  theme(plot.margin = margin(t = 0, r = 0.0, b = 0, l = 0.0, unit = "cm"))
+p
+ggsave(filename = "figures/monthly_availability.png", plot = p, width = 20, units = "cm")
+#rm(d_min, d2)
 ```

### 2021-02-19 awipev-CO2.Rmd

--- 2021-02-19 awipev-CO2.Rmd
@@
 
-# Good data per year
-
-#rm(d_min)
+# Monthly distribution of hourly data
+d2 <- d_all %>% 
+  dplyr::select(datetime, montht, pco2_inst, ph_s_sf_temp_insi)
+p <- ggplot(data = d2, aes(x = montht, y = pco2_inst)) +
+  geom_bar(stat="identity", width = 0.3) +
+  scale_fill_discrete(labels = labels) + 
+  labs(x="Month", y="pCO2", title = "") +
+  Mytheme(size_labs = 8) +
+  theme(plot.margin = margin(t = 0, r = 0.0, b = 0, l = 0.0, unit = "cm"))
+p
+ggsave(filename = "figures/monthly_availability.png", plot = p, width = 20, units = "cm")
+#rm(d_min, d2)
 ```

### 2021-02-19 awipev-CO2.Rmd
corrections to column names

--- 2021-02-19 awipev-CO2.Rmd
@@
 pH_seafet_durafet <- rbind(seafetph,durafetph)
-
 #calculations for all pH spectro measurement for sd
@@
 
+#put back the right column name for the following script
+pH_durafet_mean$ph_s_dur_temp_fb <- pH_durafet_mean$ph_s_dur_temp_fb_mean
+pH_seafet_mean$ph_s_sf_temp_insi <- pH_seafet_mean$ph_s_sf_temp_insi_mean
 #  make means in "d" to have same format and call it "discrete"
@@
 ```
+
 ```{r read and prepare nutrient data, echo=FALSE, warning=TRUE, message=FALSE}

### 2021-02-22 awipev-CO2.Rmd
correcting variable names chnaged by Samir elsewhere

--- 2021-02-19 awipev-CO2.Rmd
@@
 discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, ph_s_sf_temp_insi) %>%
+  dplyr::select(closest_datetime, ph_s_sf_temp_insi_mean) %>%
+  dplyr::rename(ph_s_sf_temp_insi = ph_s_sf_temp_insi_mean) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, ph_s_dur_temp_fb) %>%
+  dplyr::select(closest_datetime, ph_s_dur_temp_fb_mean) %>%
+  dplyr::rename(ph_s_dur_temp_fb = ph_s_dur_temp_fb_mean) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%

### 2021-02-23 awipev-CO2.Rmd
Completed availability figures

@@
 zz <- pivot_longer(z, -Flag)
-p <- ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
+p_avail <- ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
   geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
@@
   Mytheme(size_labs = 8) +
-  theme(plot.margin = margin(t = 0, r = 0.0, b = 0, l = 0.0, unit = "cm"))
-ggsave(filename = "figures/availability.png", plot = p, width = 20, units = "cm")
+  theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
+#ggsave(filename = "figures/availability.png", plot = p_avail, width = 15, height = 8, units = "cm")
 kable(z, digits = 1)
@@
 d2 <- d_all %>% 
-  dplyr::select(datetime, montht, pco2_inst, ph_s_sf_temp_insi)
-p <- ggplot(data = d2, aes(x = montht, y = pco2_inst)) +
-  geom_bar(stat="identity", width = 0.3) +
-  scale_fill_discrete(labels = labels) + 
-  labs(x="Month", y="pCO2", title = "") +
+  dplyr::select(montht, pco2_inst, phINT)
+count_pco2_inst_no_NA <- sum(!is.na(d2$pco2_inst)) # total non-NA pCO2 values
+count_phINT_no_NA <-  sum(!is.na(d2$phINT)) # total non-NA pH seafet values
+# calculate the distribution of non-NA pCO2 and pH values per month
+d2_summary <- d2 %>% 
+  dplyr::group_by(montht) %>% 
+  dplyr::summarise(pco2_pc = round(100 * sum(!is.na(pco2_inst))/count_pco2_inst_no_NA, digits = 1),
+                   pH_pc = round(100 * sum(!is.na(phINT))/count_phINT_no_NA, digits = 1)
+                   )
+# plot the distribution of non-NA pCO2 and pH values per month
+d2_summary_long <- d2_summary %>% 
+  tidyr::pivot_longer(cols = c(pco2_pc, pH_pc))
+p_avail_month <- ggplot(data = d2_summary_long) +
+  geom_col(aes(x = montht, y = value, fill = name), position = "dodge", width = 0.75) +
+  scale_fill_discrete(name = "", labels = c("pCO2", "pH")) + 
+  labs(x="Month", y="Percent of total number of data", title = "") +
   Mytheme(size_labs = 8) +
-  theme(plot.margin = margin(t = 0, r = 0.0, b = 0, l = 0.0, unit = "cm"))
+  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0.5, unit = "cm"))
+#ggsave(filename = "figures/monthly_availability.png", plot = p_avail_month, width = 15, height = 8, units = "cm")
+
+# Combine plots
+p <- (p_avail / p_avail_month)
+p <- p + plot_annotation(tag_levels = 'A')
 p
-ggsave(filename = "figures/monthly_availability.png", plot = p, width = 20, units = "cm")
-#rm(d_min, d2)
+ggsave(filename = "figures/availability.png", plot = p, width = 20, height = 15, units = "cm")
+
+# deleted uneeded data
+rm(d_min, list=ls(pattern="^d2"))
 ```

### 2021-03-02 awipev-CO2.Rmd
added time series plot show all depth in seafet pH dygraph

@@
 library("pander")
+if (!require("tsibble")) install.packages("tsibble")
+library("tsibble")
 
@@
 
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_7m, pHint_tot_sf_9m)
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_1m, pHint_tot_sf_3m, pHint_tot_sf_5m, pHint_tot_sf_7m, pHint_tot_sf_9m)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
@@
 dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_5m", label = "pHT 5m", color =  RColorBrewer::brewer.pal(3, "Dark2")[3], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_3m", label = "pHT 3m", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_1m", label = "pHT 1m", color =  RColorBrewer::brewer.pal(3, "Dark2")[5], strokeWidth = 0, pointSize = 1) %>%
 dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
@@
 
-```{r seafet profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+```{r seafet profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
 # range <- d_all %>%
@@
 ```
+
+# ```{r whole time series, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+# size_point <- 2 # size of data points
+# alpha <- 1 #transparency
+# 
+# d <- d_all %>% 
+#   as_tsibble(index = datetime) %>% 
+#   dplyr::arrange(datetime) %>%
+#   tsibble::fill_gaps() %>%
+#   dplyr::mutate(year_month = format(datetime, '%Y-%m'),
+#                 quarter = quarter(datetime)) %>%
+# #  dplyr::rename(pco2_contros = pco2_corr) %>% 
+#   replace(., is.na(.), NA) # replace NaN by NA everywhere
+# 
+# d_ts <- d %>%
+#   dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_inst,
+#                 pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
+#   #tidyr::pivot_longer(-datetime, values_to = "value")
+#   
+# #sal_fb
+# ts_sal <- d_all %>%
+#   ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
+#   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+#   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+#   labs(title="Salinity FerryBox",x="", y="Salinity") +
+#   Mytheme(size_labs = 8)
+# # ts_sal_py <- ggplotly(ts_sal,dynamicTicks = TRUE)
+# # filename.html <- paste0(path_fig, "ts_sal_py.html")
+# # saveWidget(ts_sal_py, filename.html, selfcontained = T, libdir = "lib")
+# 
+# # temp_insitu_11m
+# ts_temp <- d_all %>%
+#   ggplot(aes(x = datetime, y = temp_insitu_11m), na.rm=TRUE) +
+#   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+#   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+#   labs(title="In situ temperature 11 m",x="", y="Temperature (°C)") +
+#   Mytheme(size_labs = 8)
+# 
+# # PAR
+# ts_par_air <- d_all %>%
+#   ggplot(aes(x = datetime, y = par_air), na.rm=TRUE) +
+#   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+#   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+#   labs(title="Atmospheric PAR",x="", y="PAR (umol m-2 s-1)") +
+#   Mytheme(size_labs = 8)
+# 
+# # PCO2 
+# ts_pCO2 <- d_all %>%
+#   ggplot() +
+#   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+#   geom_point(aes(x = datetime, y = pco2_inst), 
+#              colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+#   geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
+#   labs(title="Mesured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
+#   Mytheme(size_labs = 8)
+# 
+# # SEAFET pH
+# ts_pH <- d_all %>%
+#   ggplot(aes(x = datetime, y = pHint_tot_sf_9m), na.rm=TRUE) +
+#   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+#   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+#   geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
+#   labs(title="In situ pH below 8 m (seaFET in blue, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
+#   Mytheme(size_labs = 8)
+# 
+# # AT
+# ts_at <- d_all %>%
+#   ggplot(aes(x = datetime, y = at_calc), na.rm=TRUE) +
+#   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+#   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+#   geom_point(aes(x = datetime, y = at), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
+#   labs(title="Total alkalinity calculated from salinity (blue) and discrete measurements (red)", x="", y="AT (umol/kg)") +
+#   Mytheme(size_labs = 8)
+# 
+# g <- cowplot::plot_grid(ts_sal, ts_temp, ts_par_air, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
+# print(g)
+# ```
 ## Maintenance

### 2021-03-02 awipev-CO2.Rmd
pCO2_inst replaced by pco2_fb select -pco2_inst cutoff date: 2021-01-10

@@
 d_hour <- d_hour %>%
+  dplyr::filter(datetime <= as.POSIXct("2021-01-10")) %>% #cutoff date
+  dplyr::select(-pco2_inst) %>% # this is the serial number of pCO2 sensor, not needed
   dplyr::rename(
@@
 d2 <- d_all %>% 
-  dplyr::select(montht, pco2_inst, phINT)
-count_pco2_inst_no_NA <- sum(!is.na(d2$pco2_inst)) # total non-NA pCO2 values
+  dplyr::select(montht, pco2_fb, phINT)
+count_pco2_fb_no_NA <- sum(!is.na(d2$pco2_fb)) # total non-NA pCO2 values
 count_phINT_no_NA <-  sum(!is.na(d2$phINT)) # total non-NA pH seafet values
@@
   dplyr::group_by(montht) %>% 
-  dplyr::summarise(pco2_pc = round(100 * sum(!is.na(pco2_inst))/count_pco2_inst_no_NA, digits = 1),
+  dplyr::summarise(pco2_pc = round(100 * sum(!is.na(pco2_fb))/count_pco2_fb_no_NA, digits = 1),
                    pH_pc = round(100 * sum(!is.na(phINT))/count_phINT_no_NA, digits = 1)
@@
 
-# ```{r whole time series, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
-# size_point <- 2 # size of data points
-# alpha <- 1 #transparency
-# 
-# d <- d_all %>% 
-#   as_tsibble(index = datetime) %>% 
-#   dplyr::arrange(datetime) %>%
-#   tsibble::fill_gaps() %>%
-#   dplyr::mutate(year_month = format(datetime, '%Y-%m'),
-#                 quarter = quarter(datetime)) %>%
-# #  dplyr::rename(pco2_contros = pco2_corr) %>% 
-#   replace(., is.na(.), NA) # replace NaN by NA everywhere
-# 
-# d_ts <- d %>%
-#   dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_inst,
-#                 pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
-#   #tidyr::pivot_longer(-datetime, values_to = "value")
-#   
-# #sal_fb
-# ts_sal <- d_all %>%
-#   ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
-#   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-#   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-#   labs(title="Salinity FerryBox",x="", y="Salinity") +
-#   Mytheme(size_labs = 8)
-# # ts_sal_py <- ggplotly(ts_sal,dynamicTicks = TRUE)
-# # filename.html <- paste0(path_fig, "ts_sal_py.html")
-# # saveWidget(ts_sal_py, filename.html, selfcontained = T, libdir = "lib")
-# 
-# # temp_insitu_11m
-# ts_temp <- d_all %>%
-#   ggplot(aes(x = datetime, y = temp_insitu_11m), na.rm=TRUE) +
-#   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-#   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-#   labs(title="In situ temperature 11 m",x="", y="Temperature (°C)") +
-#   Mytheme(size_labs = 8)
-# 
-# # PAR
-# ts_par_air <- d_all %>%
-#   ggplot(aes(x = datetime, y = par_air), na.rm=TRUE) +
-#   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-#   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-#   labs(title="Atmospheric PAR",x="", y="PAR (umol m-2 s-1)") +
-#   Mytheme(size_labs = 8)
-# 
-# # PCO2 
-# ts_pCO2 <- d_all %>%
-#   ggplot() +
-#   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-#   geom_point(aes(x = datetime, y = pco2_inst), 
-#              colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-#   geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
-#   labs(title="Mesured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
-#   Mytheme(size_labs = 8)
-# 
-# # SEAFET pH
-# ts_pH <- d_all %>%
-#   ggplot(aes(x = datetime, y = pHint_tot_sf_9m), na.rm=TRUE) +
-#   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-#   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-#   geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
-#   labs(title="In situ pH below 8 m (seaFET in blue, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
-#   Mytheme(size_labs = 8)
-# 
-# # AT
-# ts_at <- d_all %>%
-#   ggplot(aes(x = datetime, y = at_calc), na.rm=TRUE) +
-#   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-#   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-#   geom_point(aes(x = datetime, y = at), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
-#   labs(title="Total alkalinity calculated from salinity (blue) and discrete measurements (red)", x="", y="AT (umol/kg)") +
-#   Mytheme(size_labs = 8)
-# 
-# g <- cowplot::plot_grid(ts_sal, ts_temp, ts_par_air, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
-# print(g)
-# ```
+```{r whole time series, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+size_point <- 2 # size of data points
+alpha <- 1 #transparency
+
+d <- d_all %>% 
+  as_tsibble(index = datetime) %>% 
+  dplyr::arrange(datetime) %>%
+  tsibble::fill_gaps() %>%
+  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
+                quarter = quarter(datetime)) %>%
+#  dplyr::rename(pco2_contros = pco2_corr) %>% 
+  replace(., is.na(.), NA) # replace NaN by NA everywhere
+
+d_ts <- d %>%
+  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_fb,
+                pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
+  #tidyr::pivot_longer(-datetime, values_to = "value")
+
+#sal_fb
+ts_sal <- d_all %>%
+  ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  labs(title="Salinity FerryBox",x="", y="Salinity") +
+  Mytheme(size_labs = 8)
+# ts_sal_py <- ggplotly(ts_sal,dynamicTicks = TRUE)
+# filename.html <- paste0(path_fig, "ts_sal_py.html")
+# saveWidget(ts_sal_py, filename.html, selfcontained = T, libdir = "lib")
+
+# temp_insitu_11m
+ts_temp <- d_all %>%
+  ggplot(aes(x = datetime, y = temp_insitu_11m), na.rm=TRUE) +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  labs(title="In situ temperature 11 m",x="", y="Temperature (°C)") +
+  Mytheme(size_labs = 8)
+
+# PAR
+ts_par_air <- d_all %>%
+  ggplot(aes(x = datetime, y = par_air), na.rm=TRUE) +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  labs(title="Atmospheric PAR",x="", y="PAR (umol m-2 s-1)") +
+  Mytheme(size_labs = 8)
+
+# PCO2 
+ts_pCO2 <- d_all %>%
+  ggplot() +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(aes(x = datetime, y = pco2_fb), 
+             colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  labs(title="Mesured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
+  Mytheme(size_labs = 8)
+
+# SEAFET pH
+ts_pH <- d_all %>%
+  ggplot(aes(x = datetime, y = pHint_tot_sf_9m), na.rm=TRUE) +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  labs(title="In situ pH below 8 m (seaFET in blue, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
+  Mytheme(size_labs = 8)
+
+# AT
+ts_at <- d_all %>%
+  ggplot(aes(x = datetime, y = at_calc), na.rm=TRUE) +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(aes(x = datetime, y = at), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  labs(title="Total alkalinity calculated from salinity (blue) and discrete measurements (red)", x="", y="AT (umol/kg)") +
+  Mytheme(size_labs = 8)
+
+# Combine plots
+g <- (ts_sal / ts_temp / ts_par_air / ts_pCO2 / ts_pH / ts_at)
+g <- g + plot_annotation(tag_levels = 'A')
+g
+
+g <- cowplot::plot_grid(ts_sal, ts_temp, ts_par_air, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
+print(g)
+```
 ## Maintenance

### 2021-03-02 awipev-CO2.Rmd
added depth_discrete for plotting seafet pH

@@
 
-d <- d_all %>% 
-  as_tsibble(index = datetime) %>% 
-  dplyr::arrange(datetime) %>%
-  tsibble::fill_gaps() %>%
-  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
-                quarter = quarter(datetime)) %>%
-#  dplyr::rename(pco2_contros = pco2_corr) %>% 
-  replace(., is.na(.), NA) # replace NaN by NA everywhere
-
-d_ts <- d %>%
-  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_fb,
-                pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
-  #tidyr::pivot_longer(-datetime, values_to = "value")
+# d <- d_all %>% 
+#   as_tsibble(index = datetime) %>% 
+#   dplyr::arrange(datetime) %>%
+#   tsibble::fill_gaps() %>%
+#   dplyr::mutate(year_month = format(datetime, '%Y-%m'),
+#                 quarter = quarter(datetime)) %>%
+# #  dplyr::rename(pco2_contros = pco2_corr) %>% 
+#   replace(., is.na(.), NA) # replace NaN by NA everywhere
+# 
+#  autoplot(vars(Close, log(Close)))
+#  
+#  
+# d_ts <- d %>%
+#   dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_fb,
+#                 pressure_insitu_ctd, pHint_tot_sf, ph_s_sf_temp_insi, at_calc, at) #%>%
+#   #tidyr::pivot_longer(-datetime, values_to = "value")
 
@@
   Mytheme(size_labs = 8)
-# ts_sal_py <- ggplotly(ts_sal,dynamicTicks = TRUE)
-# filename.html <- paste0(path_fig, "ts_sal_py.html")
-# saveWidget(ts_sal_py, filename.html, selfcontained = T, libdir = "lib")
 
@@
 # SEAFET pH
+d_pH <- d_all %>% 
+  dplyr::select(datetime, pressure_insitu_ctd, pHint_tot_sf) %>% tidyr::pivot_longer(-datetime, values_to = "value")
 ts_pH <- d_all %>%
-  ggplot(aes(x = datetime, y = pHint_tot_sf_9m), na.rm=TRUE) +
+  ggplot(na.rm=TRUE) +
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(aes(x = datetime, y = pHint_tot_sf_9m), colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
   geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 

### 2021-03-04 awipev-CO2.Rmd
Finalized time series plot

--- 2021-03-02 awipev-CO2.Rmd
@@
   theme_bw() +
-  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
+  theme(title = element_text(face=face_font, size=size_labs, color="black"),
+        legend.title = element_text(face=face_font, size=size_labs, color="black"),
+        legend.text = element_text(face=face_font, size=size_labs, color="black"),
+        axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
         axis.title.x = element_text(face=face_font, size=size_labs),
@@
                 pHint_tot_sf_7m = ifelse(pressure_insitu_ctd >= 6 & pressure_insitu_ctd < 8, pHint_tot_sf, NA),
-                pHint_tot_sf_9m = ifelse(pressure_insitu_ctd >= 8 , pHint_tot_sf, NA)
+                pHint_tot_sf_9m = ifelse(pressure_insitu_ctd >= 8 , pHint_tot_sf, NA),
+                depth_discrete = case_when(
+      !is.na(pHint_tot_sf_1m) ~ 1,
+      !is.na(pHint_tot_sf_3m) ~ 3,
+      !is.na(pHint_tot_sf_5m) ~ 5,
+      !is.na(pHint_tot_sf_7m) ~ 7,
+      !is.na(pHint_tot_sf_9m) ~ 9
+      ),
+      depth_discrete = as.factor(depth_discrete)
   )
@@
 )
+rm(p_f_air_sea)
 knitr::include_graphics(pngfile)
@@
 ```{r whole time series, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
-size_point <- 2 # size of data points
+size_point <- 0.3 # size of data points
 alpha <- 1 #transparency
-
-d <- d_all %>% 
-  as_tsibble(index = datetime) %>% 
-  dplyr::arrange(datetime) %>%
-  tsibble::fill_gaps() %>%
-  dplyr::mutate(year_month = format(datetime, '%Y-%m'),
-                quarter = quarter(datetime)) %>%
-#  dplyr::rename(pco2_contros = pco2_corr) %>% 
-  replace(., is.na(.), NA) # replace NaN by NA everywhere
-
-d_ts <- d %>%
-  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_fb,
-                pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
-  #tidyr::pivot_longer(-datetime, values_to = "value")
-
-#sal_fb
+size_labs <- 6 # font size labels
+
 ts_sal <- d_all %>%
@@
   labs(title="Salinity FerryBox",x="", y="Salinity") +
-  Mytheme(size_labs = 8)
-# ts_sal_py <- ggplotly(ts_sal,dynamicTicks = TRUE)
-# filename.html <- paste0(path_fig, "ts_sal_py.html")
-# saveWidget(ts_sal_py, filename.html, selfcontained = T, libdir = "lib")
+  Mytheme(size_labs = size_labs)
 
@@
   labs(title="In situ temperature 11 m",x="", y="Temperature (°C)") +
-  Mytheme(size_labs = 8)
+  Mytheme(size_labs = size_labs)
 
@@
   labs(title="Atmospheric PAR",x="", y="PAR (umol m-2 s-1)") +
-  Mytheme(size_labs = 8)
+  Mytheme(size_labs = size_labs)
 
@@
              colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-  geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha=alpha, na.rm=TRUE, size=size_point*3) + 
   labs(title="Mesured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
-  Mytheme(size_labs = 8)
+  Mytheme(size_labs = size_labs)
 
@@
 ts_pH <- d_all %>% 
-  ggplot(aes(x = datetime, y = pHint_tot_sf_9m), na.rm=TRUE) +
+  ggplot() +
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
-  labs(title="In situ pH below 8 m (seaFET in blue, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
-  Mytheme(size_labs = 8)
+  geom_point(aes(x = datetime, y = pHint_tot_sf, col = pressure_insitu_ctd), alpha=alpha, na.rm=TRUE, size=size_point) + 
+  scale_colour_gradient(name = "Depth (m)", low = "#56B1F7", high = "#132B43") + # reverse colors
+  guides(colour = guide_colourbar(reverse = TRUE)) + # reverse colour bar
+  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha=alpha, na.rm=TRUE, size=size_point*3) + 
+  labs(title="In situ pH, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
+  Mytheme(size_labs = size_labs) +
+  theme(legend.position = c(0.1, 0.5),
+        legend.key.height = unit(0.5, 'cm'))
 
@@
   geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-  geom_point(aes(x = datetime, y = at), colour="red", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(aes(x = datetime, y = at), colour="red", alpha=alpha, na.rm=TRUE, size=size_point*3) + 
   labs(title="Total alkalinity calculated from salinity (blue) and discrete measurements (red)", x="", y="AT (umol/kg)") +
-  Mytheme(size_labs = 8)
+  Mytheme(size_labs = size_labs)
 
@@
 g <- g + plot_annotation(tag_levels = 'A')
-g
-
-g <- cowplot::plot_grid(ts_sal, ts_temp, ts_par_air, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
-print(g)
+ggsave(filename = "figures/time_series.png", plot = g, width = 15, height = 30, units = "cm")
+#rm(ls(pattern = "ts_"))
+
+#save_plot(filename = "figures/time_series.png", plot = g)
+#g_cw <- cowplot::plot_grid(ts_sal, ts_temp, ts_par_air, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
 ```

### 2021-03-08 awipev-CO2.Rmd
delete big figs objects; add chunk boxplots

@@
 ggsave(filename = "figures/time_series.png", plot = g, width = 15, height = 30, units = "cm")
-#rm(ls(pattern = "ts_"))
-
+rm(list = ls(pattern = "ts_")) #delete big ggplot objects
+gc() #garbage collection
 #save_plot(filename = "figures/time_series.png", plot = g)

### 2021-03-08 awipev-CO2.Rmd
added qq (quartiles) own function.

--- 2021-03-04 awipev-CO2.Rmd
@@
   round(approx(x=table, y=1:length(table), xout=x, ...)$y)
+}
+
+######## function to calculate min, max 3 quantiles
+qq <- function (data, digits) { 
+  as.numeric(formatC(quantile(x = data, probs = c(0, 0.025, 0.50, 0.975, 1), na.rm = TRUE),
+                     format = "f", digits = digits))
 }
@@
 
-```{r whole time series, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+```{r whole time series plot, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
 size_point <- 0.3 # size of data points
@@
 ggsave(filename = "figures/time_series.png", plot = g, width = 15, height = 30, units = "cm")
-#rm(ls(pattern = "ts_"))
+rm(list = ls(pattern = "ts_")) #delete big ggplot objects
+gc() #garbage collection
 
@@
 ```
+
+```{r whole time series monthly box plots and stats, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+size_point <- 0.5 # size of data points
+alpha <- 1 #transparency
+ts_sal_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(y = "Salinity", x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+
+ts_temp_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = temp_insitu_11m)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
+               outlier.size = 0.3, na.rm=TRUE) +
+  labs(y = "Temperature", x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+
+ts_pCO2_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_fb)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
+               outlier.size = 0.3, na.rm=TRUE) +
+  labs(y = expression(paste(pCO[2])), x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+
+ts_pH_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pHint_tot_sf)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
+               outlier.size = 0.3, na.rm=TRUE) +
+  labs(y = expression(paste(pH[T])), x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+
+ts_at_bp <- d_all %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = at_calc)) +
+  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
+  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
+               outlier.size = 0.3, na.rm=TRUE) +
+  labs(y = "Total alkalinity", x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank())
+
+# Combine plots
+g <- (ts_sal_bp / ts_temp_bp / ts_pCO2_bp / ts_pH_bp / ts_at_bp)
+g <- g + plot_annotation(tag_levels = 'A')
+ggsave(filename = "figures/ts_boxplots.png", plot = g, width = 15, height = 30, units = "cm")
+rm(list = ls(pattern = "ts_")) #delete big ggplot objects
+gc() #garbage collection
+
+# g <- cowplot::plot_grid(ts_sal_bp, ts_temp_bp, ts_pCO2_bp, ts_pH_bp, ts_at_bp, align='v', ncol=1)
+# print(g)
+
+Salinity <- qq(d_all$sal_fb, digits=1)
+Temperature <- qq(d_all$temp_fb, digits=1)
+pCO2 <- qq(d_all$pCO2_contros, digits=1)
+pH <- qq(d_all$pHint_tot_sf, digits=3)
+AT <- qq(d_all$at_calc, digits=1)
+tab_quartiles <- as_tibble(rbind(Salinity, Temperature, pCO2, pH, AT)) %>%
+  rename("2.5%"=V1, "50%"=V2, "97.5%"=V3) %>%
+  mutate(Variable=c("Salinity", "Temperature", "pCO2", "pH", "AT")) %>%
+  dplyr::select(Variable, everything())
+kable(tab_quartiles, caption = "Key quantiles") %>%
+  kable_styling(full_width=FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+```
+
 ## Maintenance

### 2021-03-08 awipev-CO2.Rmd
quartiles time series boxplots

@@
 library("tsibble")
+if (!require("kableExtra")) install.packages("kableExtra")
+library("kableExtra")
 
@@
 # Combine plots
-g <- (ts_sal_bp / ts_temp_bp / ts_pCO2_bp / ts_pH_bp / ts_at_bp)
+g <- (ts_sal_bp + ts_temp_bp + ts_pCO2_bp + ts_pH_bp + ts_at_bp)
 g <- g + plot_annotation(tag_levels = 'A')
@@
 
-Salinity <- qq(d_all$sal_fb, digits=1)
-Temperature <- qq(d_all$temp_fb, digits=1)
-pCO2 <- qq(d_all$pCO2_contros, digits=1)
-pH <- qq(d_all$pHint_tot_sf, digits=3)
-AT <- qq(d_all$at_calc, digits=1)
+Salinity <- round(quantile(d_all$sal_fb, na.rm =TRUE), digits=1)
+Temperature <- round(quantile(d_all$temp_insitu_11m, na.rm =TRUE), digits=1)
+pCO2 <- round(quantile(d_all$pco2_fb, na.rm =TRUE), digits=1)
+pH <- round(quantile(d_all$pHint_tot_sf, na.rm =TRUE), digits=3)
+AT <- round(quantile(d_all$at_calc, na.rm =TRUE), digits=1)
 tab_quartiles <- as_tibble(rbind(Salinity, Temperature, pCO2, pH, AT)) %>%
-  rename("2.5%"=V1, "50%"=V2, "97.5%"=V3) %>%
+  #rename("2.5%"=V1, "50%"=V2, "97.5%"=V3) %>%
   mutate(Variable=c("Salinity", "Temperature", "pCO2", "pH", "AT")) %>%
@@
 kable(tab_quartiles, caption = "Key quantiles") %>%
-  kable_styling(full_width=FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+  kable_styling(full_width= FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
 ```

### 2021-03-08 awipev-CO2.Rmd
fiddling with tw_boxplots fig

@@
   Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-
+  theme(panel.grid.major.x = element_blank(),
+        aspect.ratio=0.5)
 ts_temp_bp <- d_all %>%
@@
   Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-
+  theme(panel.grid.major.x = element_blank(),
+        aspect.ratio=0.5)
 ts_pCO2_bp <- d_all %>%
@@
   Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-
+  theme(panel.grid.major.x = element_blank(),
+        aspect.ratio=0.5)
 ts_pH_bp <- d_all %>%
@@
   Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-
+  theme(panel.grid.major.x = element_blank(),
+        aspect.ratio=0.5)
 ts_at_bp <- d_all %>%
@@
   Mytheme() +
-  theme(panel.grid.major.x = element_blank())
+  theme(panel.grid.major.x = element_blank(),
+        aspect.ratio=0.5)
 
 # Combine plots
-g <- (ts_sal_bp + ts_temp_bp + ts_pCO2_bp + ts_pH_bp + ts_at_bp)
+g <- ts_sal_bp / ts_temp_bp / ts_pCO2_bp / ts_pH_bp / ts_at_bp
 g <- g + plot_annotation(tag_levels = 'A')
-ggsave(filename = "figures/ts_boxplots.png", plot = g, width = 15, height = 30, units = "cm")
+ggsave(filename = "figures/ts_boxplots.png", plot = g)
 rm(list = ls(pattern = "ts_")) #delete big ggplot objects

### 2021-03-10 awipev-CO2.Rmd
Finalized boxplot fig (removed violin and outliers, added points below 1st decile and above 9th decile)

--- 2021-03-08 awipev-CO2.Rmd
@@
 alpha <- 1 #transparency
-ts_sal_bp <- d_all %>%
-  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(y = "Salinity", x=NULL, title=NULL) +
-  Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-
-ts_temp_bp <- d_all %>%
-  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = temp_insitu_11m)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
-               outlier.size = 0.3, na.rm=TRUE) +
-  labs(y = "Temperature", x=NULL, title=NULL) +
-  Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-
-ts_pCO2_bp <- d_all %>%
-  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_fb)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
-               outlier.size = 0.3, na.rm=TRUE) +
-  labs(y = expression(paste(pCO[2])), x=NULL, title=NULL) +
-  Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-
-ts_pH_bp <- d_all %>%
-  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pHint_tot_sf)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
-               outlier.size = 0.3, na.rm=TRUE) +
-  labs(y = expression(paste(pH[T])), x=NULL, title=NULL) +
-  Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-
-ts_at_bp <- d_all %>%
-  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = at_calc)) +
-  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE, na.rm=TRUE) +
-  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", 
-               outlier.size = 0.3, na.rm=TRUE) +
-  labs(y = "Total alkalinity", x=NULL, title=NULL) +
-  Mytheme() +
-  theme(panel.grid.major.x = element_blank())
-
-# Combine plots
-g <- (ts_sal_bp + ts_temp_bp + ts_pCO2_bp + ts_pH_bp + ts_at_bp)
-g <- g + plot_annotation(tag_levels = 'A')
-ggsave(filename = "figures/ts_boxplots.png", plot = g, width = 15, height = 30, units = "cm")
-rm(list = ls(pattern = "ts_")) #delete big ggplot objects
-gc() #garbage collection
-
-# g <- cowplot::plot_grid(ts_sal_bp, ts_temp_bp, ts_pCO2_bp, ts_pH_bp, ts_at_bp, align='v', ncol=1)
-# print(g)
-
-Salinity <- round(quantile(d_all$sal_fb, na.rm =TRUE), digits=1)
-Temperature <- round(quantile(d_all$temp_insitu_11m, na.rm =TRUE), digits=1)
-pCO2 <- round(quantile(d_all$pco2_fb, na.rm =TRUE), digits=1)
-pH <- round(quantile(d_all$pHint_tot_sf, na.rm =TRUE), digits=3)
-AT <- round(quantile(d_all$at_calc, na.rm =TRUE), digits=1)
-tab_quartiles <- as_tibble(rbind(Salinity, Temperature, pCO2, pH, AT)) %>%
+d_bp <- d_all %>% # just for this chunk
+  dplyr::select(datetime, sal_fb, temp_insitu_11m, pco2_fb, pHint_tot_sf, at_calc)
+
+# Quantiles table
+Salinity <- round(quantile(d_bp$sal_fb, na.rm =TRUE), digits=1)
+Temperature <- round(quantile(d_bp$temp_insitu_11m, na.rm =TRUE), digits=1)
+pco2 <- round(quantile(d_bp$pco2_fb, na.rm =TRUE), digits=1)
+pH <- round(quantile(d_bp$pHint_tot_sf, na.rm =TRUE), digits=3)
+AT <- round(quantile(d_bp$at_calc, na.rm =TRUE), digits=1)
+tab_quartiles <- as_tibble(rbind(Salinity, Temperature, pco2, pH, AT)) %>%
   #rename("2.5%"=V1, "50%"=V2, "97.5%"=V3) %>%
@@
   kable_styling(full_width= FALSE, bootstrap_options = c("striped", "hover", "condensed", "responsive"))
+
+# detection of extremes
+# calculate 1st and 9th deciles 
+dec_sal_fb <- quantile(d_bp$sal_fb, na.rm =TRUE, probs = c(0.1, 0.9))
+dec_temp_insitu_11m <- quantile(d_bp$temp_insitu_11m, na.rm =TRUE, probs = c(0.1, 0.9))
+dec_pco2_fb <- quantile(d_bp$pco2_fb, na.rm =TRUE, probs = c(0.1, 0.9))
+dec_pHint_tot_sf <- quantile(d_bp$pHint_tot_sf, na.rm =TRUE, probs = c(0.1, 0.9))
+dec_at_calc <- quantile(d_bp$at_calc, na.rm =TRUE, probs = c(0.1, 0.9))
+
+# identify extremes
+d_bp <- d_bp %>% 
+  dplyr::mutate(ext_sal_fb = ifelse(sal_fb < dec_sal_fb[1] |
+                                            sal_fb > dec_sal_fb[2], sal_fb, NA),
+                ext_temp_insitu_11m = ifelse(temp_insitu_11m < dec_temp_insitu_11m[1] |
+                                            temp_insitu_11m > dec_temp_insitu_11m[2],
+                                            temp_insitu_11m, NA),
+                ext_pco2_fb = ifelse(pco2_fb < dec_pco2_fb[1] |
+                                            pco2_fb > dec_pco2_fb[2], pco2_fb, NA),
+                ext_pHint_tot_sf = ifelse(pHint_tot_sf < dec_pHint_tot_sf[1] |
+                                            pHint_tot_sf > dec_pHint_tot_sf[2], pHint_tot_sf, NA),
+                ext_at_calc = ifelse(at_calc < dec_at_calc[1] |
+                                            at_calc > dec_at_calc[2], at_calc, NA))
+ts_sal_bp <- d_bp %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_sal_fb), col = "lightblue", size = size_point) +
+  labs(y = "Salinity", x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank(),
+        aspect.ratio=0.5)
+ts_temp_bp <- d_bp %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = temp_insitu_11m)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point) +
+  labs(y = "Temperature", x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank(),
+        aspect.ratio=0.5)
+ts_pco2_bp <- d_bp %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_fb)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point) +
+  labs(y = expression(paste(pCO[2])), x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank(),
+        aspect.ratio=0.5)
+ts_pH_bp <- d_bp %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pHint_tot_sf)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point) +
+  labs(y = expression(paste(pH[T])), x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank(),
+        aspect.ratio=0.5)
+ts_at_bp <- d_bp %>%
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = at_calc)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point) +
+  labs(y = "Total alkalinity", x=NULL, title=NULL) +
+  Mytheme() +
+  theme(panel.grid.major.x = element_blank(),
+        aspect.ratio=0.5)
+# Combine plots
+g <- ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp
+g <- g + plot_annotation(tag_levels = 'A')
+ggsave(filename = "figures/ts_boxplots.png", plot = g)
+rm(list = ls(pattern = "ts_"), d_bp) #delete big ggplot objects and temp data
+gc() #garbage collection
+
 ```

### 2021-03-12 awipev-CO2.Rmd
corrected depth in stratification; added many rm for large objects to clear memory

@@
             7,
-            ifelse(pressure_insitu_ctd > 8, 9, NA)
+            ifelse(pressure_insitu_ctd > 8, 10, NA)
           )
@@
   dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
-  dplyr::filter(depth == 2 | depth == 9) %>% 
+  dplyr::filter(depth == 2 | depth == 10) %>% 
   group_by(depth, montht)
@@
 
-## Air-sea CO2 flux
-
-To calculate the air-sea CO2 flux, we use:
-
-+ seawater pCO2 measured in the FerryBox on water pumped from 11 m depth.
-+ atmospheric CO2 measured at the Zeppelin station and downloaded on 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999 
-+ wind spreed data collected by the AWI at 10 m height (sent to JPG by P. Fischer, Aug. 2020)
-
-Since there are many gaps, a climatological year is used: air-sea flux calculated by day, then by month, then by year.
-
-seaFET pH is significantly different at the surface and depth. It should therefore be the same for pCO2.
-
-Let's look first at the stratification (salinity, temperature and density).
-
+## Stratification
 ```{r stratification, echo=FALSE, message= FALSE, warning=FALSE}
+depth_labels <- c("0-2", "2-4", "4-6", "6-8", "8-12")
 # we look at salinity all depths
@@
   labs(title = "Salinity vs depth", x = "Depth (m)", y= "Salinity") +
+  scale_x_discrete(labels = depth_labels) +
   facet_wrap(vars(montht), scale = "free_y")
 print(p)
-
-# heatmap
-tmp <- d_all %>%
-  dplyr::filter(!is.na(depth)) %>%
-  dplyr::select(montht, sal_insitu_ctd, depth) %>%
-  group_by(montht, depth)
-sal_median <- skim(tmp) %>%
-  dplyr::select(depth, montht, numeric.p50) %>%
-  pivot_wider(names_from = depth, values_from = c(numeric.p50))
-
-plt <- sal_median %>%
-  ggplot(aes(
-    x = montht,
-    y = as.factor(depth),
-    fill = median(sal_insitu_ctd)
-  ), color = "white") +
-  geom_tile() +
-  scale_fill_gradientn(colors = viridis(5), breaks = seq(31, 36, by = 1), na.value = "grey") +
-  labs(x = "", y = "", fill = "Salinity") +
-  scale_x_discrete(position = "top") +
-  scale_y_discrete(name = "", limits = rev(levels(as.factor(tmp$depth)))) +
-  # scale_y_discrete(name = "", limits = rev(levels(as.factor(tmp$depth))),
-  #                  rev(levels(tmp$depth))[c(1,3,5,7,9)]) +
-  # coord_equal() +
-  theme(legend.position = "top",
-        axis.text.y = element_text(size = 13),
-        axis.text.x = element_text(size = 13),
-        legend.text = element_text(size = 13),
-        legend.title = element_text(size = 14),
-        #legend.key.size = unit(1.5, "cm"),
-        legend.key.height = unit(0.8, "cm"),
-        legend.key.width  = unit(2, "cm"))
-#plt
 
@@
   dplyr::rename(median2m = "2",
-                median9m = "9") %>% 
-  dplyr::mutate(sal_range = median2m - median9m)
+                median10m = "10") %>% 
+  dplyr::mutate(sal_range = median2m - median10m)
 kable(sal_range, digits = 2, caption = "Median salinity")
@@
   dplyr::rename(median2m = "2",
-                median9m = "9") %>% 
-  dplyr::mutate(temp_range = median2m - median9m)
+                median10m = "10") %>% 
+  dplyr::mutate(temp_range = median2m - median10m)
 kable(temp_range, digits = 2, caption = "Median temperature")
@@
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "Temperature vs depth", x = "Depth (m)", y= "Salinity") +
+  labs(title = "Temperature vs depth", x = "Depth (m)", y= "Temperature") +
   facet_wrap(vars(montht), scale = "free_y")
@@
                 depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
-  dplyr::filter(depth == 2 | depth == 9) %>% 
+  dplyr::filter(depth == 2 | depth == 10) %>% 
   dplyr::select(montht, depth, density) %>% 
@@
   dplyr::rename(median2m = "2",
-                median9m = "9") %>% 
-  dplyr::mutate(den_range = median2m - median9m)
+                median10m = "10") %>% 
+  dplyr::mutate(den_range = median2m - median10m)
 kable(den_range, digits = 2, caption = "Median density")
@@
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "Density vs depth", x = "Depth (m)", y= "Salinity") +
+  labs(title = "Density vs depth", x = "Depth (m)", y= "Density") +
+  scale_x_discrete(labels = c("0-4", "8-12")) +
   facet_wrap(vars(montht), scale = "free_y")
@@
 + Temperature is always colder at 0-4 m than below 8 m (0.15 to 2°C).
+
+## Air-sea CO2 flux
+
+To calculate the air-sea CO2 flux, we use:
+
++ seawater pCO2 measured in the FerryBox on water pumped from 11 m depth.
++ atmospheric CO2 measured at the Zeppelin station and downloaded on 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999 
++ wind spreed data collected by the AWI at 10 m height (sent to JPG by P. Fischer, Aug. 2020)
+
+Since there are many gaps, a climatological year is used: air-sea flux calculated by day, then by month, then by year.
+
+seaFET pH is significantly different at the surface and depth. It should therefore be the same for pCO2.
+
+Let's look first at the stratification (salinity, temperature and density).
 

### 2021-03-15 awipev-CO2.Rmd
finalized stratification tab; additional rm for large objects to clear memory

@@
   )
+rm(d_hour)
 ```
@@
 # deleted uneeded data
-rm(d_min, list=ls(pattern="^d2"))
+rm(x, d_min, list=ls(pattern="^d2"))
 ```
@@
 kable(quantile(x = df$range, na.rm = TRUE), digits = 2, col.names = "Sal. unit", caption = "Quantiles salinity gradient between 0-2 m and > 8 m")
+rm(sal_xts)
 ```
@@
       dyRangeSelector(height = 30, dateWindow= NULL)
+rm(temp_fb_xts, temp_insitu_xts)
 ```
@@
   ungroup()
+rm(temp_xts)
 ```
@@
  print(at_s)
+rm(at_s)
 ```
@@
     dyRangeSelector(height = 30, dateWindow= NULL)
-
+rm(at_contros_calc_xts)
 ```
@@
   dyRangeSelector(height = 30, dateWindow = NULL)
-
+rm(pco2_contros_xts)
 # now remove outliers
@@
   dyRangeSelector(height = 30, dateWindow= NULL)
+rm(seafet_depth_xts)
 ```
@@
 print(p) # plot_range_dur
+rm(durafet_contros_xts)
 ```
@@
 print(pdur_sf_norm_text)
+rm(pdur_sf_norm_text)
 
@@
     dyRangeSelector(height = 30, dateWindow= NULL) 
+rm(durafet_sf_contros_xts, pdur_sf_norm_text)
 ```
@@
     dyRangeSelector(height = 30, dateWindow= NULL)
+rm(durafet_calc_contros_xts)
 ```
@@
     dyRangeSelector(height = 30, dateWindow= NULL)
+rm(seafet_calc_contros_xts)
 ```
@@
 p_ct_ts
+rm(at_diff_xts, ct_diff_xts)
 ```
@@
   theme(panel.grid.major.x = element_blank())
-ts_Si_bp + ts_Si_bp
+ts_po4_bp + ts_Si_bp
 # Effects of changes in po4 and si
@@
 diff_Si_2 <- carb_Si_2[1,] - carb_Si_2[2,]
+rm(ts_po4_bp, ts_Si_bp)
 ```
@@
 
+summary(aov(tmp$sal_insitu_ctd ~ tmp$depth * tmp$montht))
+
 # we look at salinity 0 to 4 m vs more than 8 m
@@
   dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
-  dplyr::filter(depth == 2 | depth == 10) %>% 
-  group_by(depth, montht)
-sal_range <- skim(tmp) %>% 
-  dplyr::select(depth, montht, numeric.p50) %>% 
-  pivot_wider(names_from = depth, values_from = c(numeric.p50)) %>% 
-  dplyr::rename(median2m = "2",
-                median10m = "10") %>% 
-  dplyr::mutate(sal_range = median2m - median10m)
-kable(sal_range, digits = 2, caption = "Median salinity")
-
-summary(aov(tmp$sal_insitu_ctd ~ tmp$depth * tmp$montht))
+  dplyr::filter(depth == 2 | depth == 10)
+tmp_delta <- tmp %>% 
+  group_by(depth, montht) %>% 
+  dplyr::summarise(sal_med = median(sal_insitu_ctd, na.rm = TRUE)) %>% 
+  tidyr::pivot_wider(names_from = depth, values_from = sal_med) %>% 
+  dplyr::rename(median0_4m = "2",
+                median8_12m = "10") %>% 
+  dplyr::mutate(sal_range = median0_4m - median8_12m)
+kable(tmp_delta, digits = 2, caption = "Median salinity")
 
@@
   group_by(depth, montht)
-temp_range <- skim(tmp) %>% 
-  dplyr::select(depth, montht, numeric.p50) %>% 
-  pivot_wider(names_from = depth, values_from = c(numeric.p50)) %>% 
-  dplyr::rename(median2m = "2",
-                median10m = "10") %>% 
-  dplyr::mutate(temp_range = median2m - median10m)
-kable(temp_range, digits = 2, caption = "Median temperature")
 summary(aov(tmp$temp_insitu_ctd ~ tmp$depth * tmp$montht))
+
+tmp_delta <- tmp %>% 
+  group_by(depth, montht) %>% 
+  dplyr::summarise(temp_med = median(temp_insitu_ctd, na.rm = TRUE)) %>% 
+  tidyr::pivot_wider(names_from = depth, values_from = temp_med) %>% 
+  dplyr::rename(median0_4m = "2",
+                median8_12m = "10") %>% 
+  dplyr::mutate(temp_range = median0_4m - median8_12m)
+kable(tmp_delta, digits = 2, caption = "Median temperature")
 
@@
   group_by(depth, montht) 
-den_range <- skim(tmp) %>% 
-  dplyr::select(depth, montht, numeric.p50) %>% 
-  pivot_wider(names_from = depth, values_from = c(numeric.p50)) %>% 
-  dplyr::rename(median2m = "2",
-                median10m = "10") %>% 
-  dplyr::mutate(den_range = median2m - median10m)
-kable(den_range, digits = 2, caption = "Median density")
 summary(aov(tmp$density ~ tmp$depth * tmp$montht))
+
+tmp_delta <- tmp %>% 
+  group_by(depth, montht) %>% 
+  dplyr::summarise(den_med = median(density, na.rm = TRUE)) %>% 
+  tidyr::pivot_wider(names_from = depth, values_from = den_med) %>% 
+  dplyr::rename(median0_4m = "2",
+                median8_12m = "10") %>% 
+  dplyr::mutate(den_med = median0_4m - median8_12m)
+kable(tmp_delta, digits = 2, caption = "Median density")
 

### 2021-03-15 awipev-CO2.Rmd
Finalized section on choice of K, K2

@@
 ## Impact of choice of constants
-### Using mean values
+### Lueker vs Sulpis using mean values
 ```{r impact of constants 1, echo=FALSE, warning=FALSE, message=FALSE}
@@
 # use mean values calculated for impacts of nutrients above
-means <- d_all %>% 
+monthly_means <- d_all %>% 
   group_by(montht) %>% 
@@
   ungroup()
-mean_ct <-  mean(means$mean_ct)
-mean_at_calc <-  mean(means$mean_at_calc)
-mean_pco2_calc <-  mean(means$mean_pco2_calc)
-mean_sal <-  mean(means$mean_sal)
-mean_temp <-  mean(means$mean_temp)
-# impacts using pco2 and AT
+mean_ct <-  mean(monthly_means$mean_ct)
+mean_at_calc <-  mean(monthly_means$mean_at_calc)
+mean_pco2_calc <-  mean(monthly_means$mean_pco2_calc)
+mean_sal <-  mean(monthly_means$mean_sal)
+mean_temp <-  mean(monthly_means$mean_temp)
+# impacts using pco2 and AT pair
 carb_l_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
@@
 diff_ls_2 <- carb_l_2 - carb_s_2
-const <- bind_rows(diff_ls_1, diff_ls_2) %>% 
+const_choice <- bind_rows(diff_ls_1, diff_ls_2) %>% 
   dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
@@
                 ) %>% 
-  dplyr::select(flag:T, pH, pCO2, DIC, OmegaAragonite)
+  dplyr::select(flag, T, pH, pCO2, DIC, OmegaAragonite)
 #kable(const, digits = c(0, 1, 1, 3, 1, 1, 2))
-pander(const)
-```
-### Using all values pCO2 and at_calc
+pander(const_choice)
+```
+### Lueker vs Sulpis using all values pCO2 and at_calc
 
@@
 # Compare Lueker and Sulpis
-d_ls <- d_all %>% 
+tmp <- d_all %>% 
   drop_na(pco2_fb, at_calc, sal_fb, temp_fb)
@@
     24,
-    d_ls$pco2_fb,
-    d_ls$at_calc * 1e-6,
-    S = d_ls$sal_fb,
-    T = d_ls$temp_fb,
+    tmp$pco2_fb,
+    tmp$at_calc * 1e-6,
+    S = tmp$sal_fb,
+    T = tmp$temp_fb,
     P = 0,
@@
   )
-diff_ls <- as_tibble(carb_l - carb_s)
-d_ls <- bind_cols(d_ls, diff_ls)
+diff_ls <- as_tibble(carb_l - carb_s) %>% 
+  dplyr::select(pH, pCO2, DIC, OmegaAragonite)
+a
+dplyr::mutate
+diff_ls_quant <- bind_rows(
+  quantiles(diff_ls$pH),)
+)
+const_choice <- bind_rows(diff_ls_1, diff_ls_2) %>% 
+  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
+                S = mean_sal,
+                T = mean_temp,
+                DIC = DIC * 1e6
+                ) %>%
 

### 2021-03-16 awipev-CO2.Rmd
impact of K1K2 using mean values; minor adjustements

--- 2021-03-15 awipev-CO2.Rmd
@@
               colour = "blue") +
-  labs(title = paste("pH spectro vs pH durafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
+  labs(title = paste("pH spectro vs pH durafet (both at FB temperature","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                      "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
@@
               colour = "blue") +
-  labs(title = paste("pH spectro vs pH seafet","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
+  labs(title = paste("pH spectro vs pH seafet (at in situ temperature)","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
                      "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
@@
 ## Impact of choice of constants
-### Using mean values
+### Lueker vs Sulpis using means of monthly means
 ```{r impact of constants 1, echo=FALSE, warning=FALSE, message=FALSE}
@@
   ungroup()
-mean_ct <-  mean(means$mean_ct)
-mean_at_calc <-  mean(means$mean_at_calc)
-mean_pco2_calc <-  mean(means$mean_pco2_calc)
-mean_sal <-  mean(means$mean_sal)
-mean_temp <-  mean(means$mean_temp)
-# impacts using pco2 and AT
+means <- monthly_means %>% 
+  summarise(across(
+    .cols = is.numeric, 
+    .fns = mean, na.rm = TRUE, 
+    .names = "{col}"
+  ))
+
+mean_ct <-  mean(monthly_means$mean_ct)
+mean_at_calc <-  mean(monthly_means$mean_at_calc)
+mean_pco2_calc <-  mean(monthly_means$mean_pco2_calc)
+mean_sal <-  mean(monthly_means$mean_sal)
+mean_temp <-  mean(monthly_means$mean_temp)
+# impacts using pco2 and AT pair
 carb_l_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
@@
                 ) %>% 
-  dplyr::select(flag:T, pH, pCO2, DIC, OmegaAragonite)
-#kable(const, digits = c(0, 1, 1, 3, 1, 1, 2))
-pander(const)
-```
-### Using all values pCO2 and at_calc
+  dplyr::select(flag, pH, pCO2, DIC, OmegaAragonite)
+knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3), caption = "Lueker minus Sulpis", format = "simple")
+```
+The means used are:
+`r knitr::kable(means, format = "simple")`
+
+### Lueker vs Sulpis using all values pCO2 and at_calc
+One uses the pair pCO2-AT
 
@@
   )
-diff_ls <- as_tibble(carb_l - carb_s)
-d_ls <- bind_cols(d_ls, diff_ls)
-
-# plot
+diff_ls <- as_tibble(carb_l - carb_s) %>% 
+  dplyr::select(pH, pCO2, DIC, OmegaAragonite)
+diff_ls_quant <- bind_rows(
+  quantile(diff_ls$pH), quantile(diff_ls$pCO2), quantile(diff_ls$DIC * 1e6), 
+  quantile(diff_ls$OmegaAragonite)) %>% 
+  dplyr::mutate(Variable = c("pH", "pCO2", "DIC", "OmegaAragonite"), .before = 1)
+pander(diff_ls_quant)
+
 lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
@@
 print(p) #p_sal_fb_ctd
+
 ```

### 2021-03-17 awipev-CO2.Rmd
k1k2 = "l" everywhere (except when s20 needed); ph_s normalized at 4°C

@@
 pH_seafet <- pH_seafet %>% 
-  dplyr::mutate(ph_s_sf_temp_insi = 
-                  pHinsi(pH = pH_seafet$ph_s_sf, 
+  dplyr::mutate(
+    ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, 
                          ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, 
                          Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
-                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0))
+                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "x", kf = "x", ks="d", 
+                         pHscale = "T", b="u74"),
+   ph_s_sf_norm4 = pHinsi(pH = pH_seafet$ph_s_sf, 
+                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
+                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
+                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "x", kf = "x", ks="d", 
+                         pHscale = "T", b="u74")
+  )
 
@@
 
-# add spectro points that cannot be taken into consideration (some ancillary data T and/or S not available)
-# shown as white triangles on the plot
+d_all <- d_all %>%
+  dplyr::mutate(ph_s_sf_norm4 = ifelse(!is.na(pH_seafet$ph_s_sf),
+                                              pHinsi(pH = pH_seafet$ph_s_sf, 
+                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
+                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
+                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "x", kf = "x", ks="d", 
+                         pHscale = "T", b="u74"), NA
+  ))
+
+# add spectro points that cannot be taken into consideration (some ancillary data T and/or S not available) shown as white triangles on the plot
+# ALSO Conversion of spec pH of FerryBox samples at 4°C
+
 d_all <- d_all %>%
@@
       NA
-    )
-  )
+    ))
 
@@
 # use mean values calculated for impacts of nutrients above
+
+# first, order columns
+d_all <- d_all %>% 
+  dplyr::select(order(colnames(d_all))) %>% 
+  dplyr::select(datetime, date, year, monthd, montht, everything())
+
+# calculate means
 monthly_means <- d_all %>% 
@@
   dplyr::select(flag, pH, pCO2, DIC, OmegaAragonite)
-knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3), caption = "Lueker minus Sulpis", format = "simple")
 ```
@@
 
+The differences are:
+`r knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3), caption = "Lueker minus Sulpis", format = "simple")`
+
 ### Lueker vs Sulpis using all values pCO2 and at_calc
-One uses the pair pCO2-AT
+One uses the pair pCO2-AT_calc
 

### 2021-03-18 awipev-CO2.Rmd
choice of constants + plots work

@@
 # function regression plot with equation (MA or OLS) in title
-ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title") { # x and y are the names of the variables
+ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", subtitle = "subtitle", xlab = "x", ylab = "y") { # x and y are the names of the variables
   fit_data <- tibble(xdata, ydata)
@@
                      "; Slope =", signif(slope, 3),
-                     "; P =", signif(fit$P.param, 3)))
+                     "; P =", signif(fit$P.param, 3)),
+       subtitle = subtitle,
+       x = xlab,
+       y = ylab)
   return(plt)
@@
 
-# Conversion of spec pH of in situ samples to in situ temp
+# Conversion of spec pH of in situ samples to in situ temp and 4 °C
 pH_seafet <- d %>%
@@
                          Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
-                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "x", kf = "x", ks="d", 
+                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "x", ks="d", 
                          pHscale = "T", b="u74"),
@@
                          Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
-                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "x", kf = "x", ks="d", 
+                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "x", ks="d", 
                          pHscale = "T", b="u74")
@@
 pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(date, ph_s_sf_temp_insi)%>% 
+  dplyr::select(date, ph_s_sf_temp_insi, ph_s_sf_norm4)%>% 
   dplyr::group_by(date) %>% 
   dplyr::summarise(ph_s_sf_temp_insi_mean = mean(ph_s_sf_temp_insi, na.rm = TRUE),
-                   ph_s_sf_temp_insi_sd= sd(ph_s_sf_temp_insi, na.rm = TRUE)
+                   #ph_s_sf_temp_insi_sd = sd(ph_s_sf_temp_insi, na.rm = TRUE),
+                   ph_s_sf_norm4_mean = mean(ph_s_sf_norm4, na.rm = TRUE)
                    )
@@
   dplyr::group_by(date) %>% 
-  dplyr::summarize(ph_s_dur_temp_fb_mean = mean(ph_s_dur_temp_fb, na.rm = TRUE),
-                   ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE))
-
-#bind all spectro measurements, vhange name of dataframe only to do the rbind.
-seafetph <- pH_seafet_mean
-colnames(seafetph) <- c("date", "mean", "sd")
-durafetph <- pH_durafet_mean
-colnames(durafetph) <- c("date", "mean", "sd")
-pH_seafet_durafet <- rbind(seafetph,durafetph)
-
-#calculations for all pH spectro measurement for sd
-sd_min <- min(pH_seafet_durafet$sd)
-sd_max <- max(pH_seafet_durafet$sd)
-sd_mean <- mean(pH_seafet_durafet$sd)
+  dplyr::summarize(ph_s_dur_temp_fb_mean = mean(ph_s_dur_temp_fb, na.rm = TRUE)#,
+                   #ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE)
+                   )
+
+# #bind all spectro measurements, vhange name of dataframe only to do the rbind.
+# seafetph <- pH_seafet_mean
+# colnames(seafetph) <- c("date", "ph_s_sf_insi", "ph_s_sf_norm4")
+# durafetph <- pH_durafet_mean
+# colnames(durafetph) <- c("date", "ph_s_dur_temp_fb")
+# pH_seafet_durafet <- rbind(seafetph,durafetph)
+
+# #calculations for all pH spectro measurement for sd
+# sd_min <- min(pH_seafet_durafet$sd)
+# sd_max <- max(pH_seafet_durafet$sd)
+# sd_mean <- mean(pH_seafet_durafet$sd)
 
@@
 discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, ph_s_sf_temp_insi_mean) %>%
-  dplyr::rename(ph_s_sf_temp_insi = ph_s_sf_temp_insi_mean) %>%
+  dplyr::select(closest_datetime, ph_s_sf_temp_insi_mean, ph_s_sf_norm4_mean) %>%
+  dplyr::rename(ph_s_sf_temp_insi = ph_s_sf_temp_insi_mean,
+                ph_s_sf_norm4 = ph_s_sf_norm4_mean) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 
-d_all <- d_all %>%
-  dplyr::mutate(ph_s_sf_norm4 = ifelse(!is.na(pH_seafet$ph_s_sf),
-                                              pHinsi(pH = pH_seafet$ph_s_sf, 
-                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
-                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
-                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "x", kf = "x", ks="d", 
-                         pHscale = "T", b="u74"), NA
-  ))
+# d_all <- d_all %>%
+#   dplyr::mutate(ph_s_sf_norm4 = ifelse(!is.na(pH_seafet$ph_s_sf),
+#                                               pHinsi(pH = pH_seafet$ph_s_sf, 
+#                          ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
+#                          Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
+#                          S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "x", ks="d", 
+#                          pHscale = "T", b="u74"), NA
+#   ))
 
@@
 
-pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "l", kf = "x", ks="d", pHscale = "T", b="u74")
 
@@
   dplyr::filter(!is.na(ph_dur_corr), !is.na(temp_fb), !is.na(sal_fb))
-pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "x", ks="d", pHscale = "T", b="u74")
 
@@
   dplyr::filter(!is.na(phcalc_fb), !is.na(temp_fb), !is.na(sal_fb))
-pH_calc$pH_calc_fb_norm4 <- pHinsi(pH = pH_calc$phcalc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")
+pH_calc$pH_calc_fb_norm4 <- pHinsi(pH = pH_calc$phcalc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "x", ks="d", pHscale = "T", b="u74")
 
@@
 
-## Impact of choice of constants
+## Impact of choice of constants  {.tabset .tabset-pills}
 ### Lueker vs Sulpis using means of monthly means
@@
 ```{r impact of constants 2, echo=FALSE, warning=FALSE, message=FALSE}
-# Compare Lueker and Sulpis
+# Compare Lueker and Sulpis using pco2_fb and at_calc
 tmp <- d_all %>% 
-  drop_na(pco2_fb, at_calc, sal_fb, temp_fb)
+  tidyr::drop_na(pco2_fb, at_calc, sal_fb, temp_fb) %>% 
+  dplyr::select(ph_s_sf_norm4, pco2_fb, at_calc, sal_fb, temp_fb)
+
 carb_l <-
@@
   )
+# normalize derived pH at 4°C
+carb_l$pH <- pHinsi(pH = carb_l$pH, 
+                         ALK = carb_l$ALK, Tinsi = 4, 
+                         Tlab = carb_l$T, Pinsi = 0, 
+                         S = carb_l$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "x", ks="d", 
+                         pHscale = "T", b="u74")
 carb_s <-
@@
   )
+# normalize derived pH at 4°C
+carb_s$pH <- pHinsi(pH = carb_s$pH, 
+                         ALK = carb_s$ALK, Tinsi = 4, 
+                         Tlab = carb_s$T, Pinsi = 0, 
+                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "x", ks="d", 
+                         pHscale = "T", b="u74")
+
+# do difference
 diff_ls <- as_tibble(carb_l - carb_s) %>% 
-  dplyr::select(pH, pCO2, DIC, OmegaAragonite)
+  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite)
+
+# calculate quantiles
 diff_ls_quant <- bind_rows(
-  quantile(diff_ls$pH), quantile(diff_ls$pCO2), quantile(diff_ls$DIC * 1e6), 
-  quantile(diff_ls$OmegaAragonite)) %>% 
-  dplyr::mutate(Variable = c("pH", "pCO2", "DIC", "OmegaAragonite"), .before = 1)
-pander(diff_ls_quant)
-
-lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
+  quantile(diff_ls$delta_ph), quantile(diff_ls$delta_ct * 1e6),
+  quantile(diff_ls$delta_OmegaAragonite)) %>% 
+  dplyr::mutate(Variable = c("pH", "DIC", "OmegaAragonite"), .before = 1)
+#pander(diff_ls_quant)
+
+# prepare tibble to compare calculated pH and spec pH
+tmp2 <- tibble(ph_s_sf_norm4 = tmp$ph_s_sf_norm4, pH_l = carb_l$pH, pH_s = carb_s$pH) %>% 
+  tidyr::drop_na(ph_s_sf_norm4)
+
+p1 <- ggreg(xdata = tmp2$ph_s_sf_norm4, ydata = tmp2$pH_l, type = "OLS", plot = TRUE, 
+            title = "both pH normalized at 4°C", subtitle = "",
+            xlab = "Spectrophotometric pH measured @ 4°C",
+            ylab = "pH @ 4°C calculated (pCO2+AT) with Lueker")
+p2 <- ggreg(xdata = tmp2$ph_s_sf_norm4, ydata = tmp2$pH_s, type = "OLS", plot = TRUE, title = "both pH normalized at 4°C")
+
+lm <- lm2(x = tmp2$ph_s_sf_norm4, y = tmp2$pH_l)
 p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
@@
 The difference induced by the choice of the carbonic acid constants is large for pH, pCO2 and DIC and negligible for OmegaAragonite.
+
+`r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis", format = "simple")`
 

### 2021-03-19 awipev-CO2.Rmd
revised choice of constants with discrete samples

@@
 
-# calculate means
-monthly_means <- d_all %>% 
-  group_by(montht) %>% 
-  summarize(mean_ct = mean(ct, na.rm = TRUE),
-            mean_at_calc = mean(at_calc, na.rm = TRUE),
-            mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
-            mean_sal = mean(sal_fb, na.rm = TRUE),
-            mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
-  ungroup()
-means <- monthly_means %>% 
-  summarise(across(
-    .cols = is.numeric, 
-    .fns = mean, na.rm = TRUE, 
-    .names = "{col}"
-  ))
-
-mean_ct <-  mean(monthly_means$mean_ct)
-mean_at_calc <-  mean(monthly_means$mean_at_calc)
-mean_pco2_calc <-  mean(monthly_means$mean_pco2_calc)
-mean_sal <-  mean(monthly_means$mean_sal)
-mean_temp <-  mean(monthly_means$mean_temp)
+# # calculate means
+# monthly_means <- d_all %>% 
+#   group_by(montht) %>% 
+#   summarize(mean_ct = mean(ct, na.rm = TRUE),
+#             mean_at_calc = mean(at_calc, na.rm = TRUE),
+#             mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
+#             mean_sal = mean(sal_fb, na.rm = TRUE),
+#             mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
+#   ungroup()
+# means <- monthly_means %>% 
+#   summarise(across(
+#     .cols = is.numeric, 
+#     .fns = mean, na.rm = TRUE, 
+#     .names = "{col}"
+#   ))
+
+mean_ct <-  mean(discrete$ct, na.rm = TRUE)
+mean_at <-  mean(discrete$ct, na.rm = TRUE)
+mean_pco2 <-  mean(d_all$pco2_calc_fb)
+mean_sal <-  mean(discrete$sal_fb, na.rm = TRUE)
+mean_temp <-  mean(discrete$temp_fb, na.rm = TRUE)
+
+# calculate typical uncertainty assuming uncertainties of 3 uatm for pCO2 and 4 umol/kg for AT
+errors_pco2_at <- seacarb::errors(flag=24, var1=mean_pco2_calc, var2=1e-6*mean_at_calc, S=mean_sal,
+                          T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
+                          b="u74", evar1=3, evar2 = 4e-6)
+errors_at_ct <- seacarb::errors(flag=15, var1=1e-6*mean_at_calc, var2=1e-6*mean_ct, S=mean_sal,
+                          T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
+                          b="u74", evar1=4e-6, evar2 = 4e-6)
+errors <- tibble(e_pH = c(errors_pco2_at$pH, errors_at_ct$pH),
+                 e_pCO2 = c(NA, errors_at_ct$pCO2),
+                 e_DIC = c(errors_pco2_at$pH, NA)*1e3,
+                 e_Oa = c(errors_pco2_at$OmegaAragonite, errors_at_ct$OmegaAragonite)
+)
+
 # impacts using pco2 and AT pair
@@
                 ) %>% 
-  dplyr::select(flag, pH, pCO2, DIC, OmegaAragonite)
+  dplyr::select(flag, pH, pCO2, DIC, OmegaAragonite) %>% 
+  dplyr::bind_cols(errors)
 ```
@@
 The differences are:
-`r knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3), caption = "Lueker minus Sulpis", format = "simple")`
+`r knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3, 3, 1, 1, 1), caption = "Lueker minus Sulpis. e indicates typical errors estimated with seacarb.", format = "simple")`
 
 ### Lueker vs Sulpis using all values pCO2 and at_calc
-One uses the pair pCO2-AT_calc
-
 ```{r impact of constants 2, echo=FALSE, warning=FALSE, message=FALSE}
@@
 
-# calculate quantiles
-diff_ls_quant <- bind_rows(
-  quantile(diff_ls$delta_ph), quantile(diff_ls$delta_ct * 1e6),
-  quantile(diff_ls$delta_OmegaAragonite)) %>% 
-  dplyr::mutate(Variable = c("pH", "DIC", "OmegaAragonite"), .before = 1)
-#pander(diff_ls_quant)
+# calculate descriptive statistics
+diff_ls_quant <- tibble(pH = as.numeric(summary(diff_ls$delta_ph)),
+                        CT = as.numeric(summary(diff_ls$delta_ct * 1e6)),
+                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite))) %>%
+  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
 
@@
 
-p1 <- ggreg(xdata = tmp2$ph_s_sf_norm4, ydata = tmp2$pH_l, type = "OLS", plot = TRUE, 
-            title = "both pH normalized at 4°C", subtitle = "",
+# summary of differences
+diff_lueker <- as.numeric(summary(tmp2$ph_s_sf_norm4 - tmp2$pH_l))
+diff_sulpis <- as.numeric(summary(tmp2$ph_s_sf_norm4 - tmp2$pH_s))
+lueker_sulpis_table <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), diff_lueker, diff_sulpis)
+
+# make plots
+p1 <- ggreg(xdata = tmp2$ph_s_sf_norm4, ydata = tmp2$pH_l, type = "MA", plot = TRUE, 
+            title = "Lueker vs measured", subtitle = "both pH normalized at 4°C",
             xlab = "Spectrophotometric pH measured @ 4°C",
             ylab = "pH @ 4°C calculated (pCO2+AT) with Lueker")
-p2 <- ggreg(xdata = tmp2$ph_s_sf_norm4, ydata = tmp2$pH_s, type = "OLS", plot = TRUE, title = "both pH normalized at 4°C")
-
-lm <- lm2(x = tmp2$ph_s_sf_norm4, y = tmp2$pH_l)
-p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
-  geom_point( aes(color=factor(monthd))) + 
-  geom_abline(slope=1, intercept=0, linetype = "dashed")+
-  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),colour = "blue") +
-  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
-  labs(title = paste("","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
-                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
-                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
-                     "; P =", signif(lm$fit$P.param, 3),
-                     "; RMSE = ", signif(lm$rmse, 3))) +
-  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
-  coord_fixed(ratio = 1 )+
-  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()
-
-print(p) #p_sal_fb_ctd
-
-```
-
+p2 <- ggreg(xdata = tmp2$ph_s_sf_norm4, ydata = tmp2$pH_s, type = "MA", plot = TRUE, 
+            title = "Sulpis vs measured", subtitle = "both pH normalized at 4°C",
+            xlab = "Spectrophotometric pH measured @ 4°C",
+            ylab = "pH @ 4°C calculated (pCO2+AT) with Sulpis") 
+p <- p1 + p2
+ggsave(filename = "figures/lueker-sulpis.png", plot = p, width = 20, height = 15, units = "cm")
+```
+The overall means of pCO2, AT (calculated from the AT-salinity relationship), salinity and temperature in the FerryBox were used to calculate pH from measured pCO2 and AT (from a salinity-AT relationship) and from AT and CT.
+using the formulations of Lueker et al.
+(2000) and Sulpis et al.
+(2020) of K1 and K2.
 The difference induced by the choice of the carbonic acid constants is large for pH, pCO2 and DIC and negligible for OmegaAragonite.
@@
 `r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis", format = "simple")`
+
+Here we compare pH measured spectrophotometrically with pH calculated from pCO2 and AT using the sets of K1 and K2 of Lueker et al.
+(2000) and Sulpis et al.
+(2020).
+All pH values were normalized to a temperature of 4°C.
+Both formulations overestimate spectrophotometric pH
+`r knitr::kable(lueker_sulpis_table, digits = 3, caption = "Difference between spectrophotometric pH and Lueker and Sulpis", format = "simple")`
 

### 2021-03-19 awipev-CO2.Rmd
Calculate spec pH fb; kf="dg" everywhere

@@
                          Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
-                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "x", ks="d", 
+                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
                          pHscale = "T", b="u74"),
@@
                          Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
-                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "x", ks="d", 
+                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
                          pHscale = "T", b="u74")
@@
 pH_durafet <- d %>%
-  dplyr::filter(!is.na(ph_s_dur) & !is.na(sal_fb) & !is.na(temp_fb))
+  tidyr::drop_na(ph_s_dur, sal_fb, temp_fb)
 pH_durafet <- pH_durafet %>% 
-  dplyr::mutate(ph_s_dur_temp_fb = pHinsi(pH = pH_durafet$ph_s_dur, ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = pH_durafet$temp_fb, Tlab = pH_durafet$temp_s_lab, Pinsi = 0, S = pH_durafet$sal_fb, Pt = 0, Sit = 0))
+  dplyr::mutate(
+    ph_s_dur_temp_fb = pHinsi(pH = pH_durafet$ph_s_dur, 
+                              ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = pH_durafet$temp_fb, 
+                              Tlab = pH_durafet$temp_s_lab, Pinsi = 0, S = pH_durafet$sal_fb, 
+                              Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74"),
+   ph_s_dur_norm4 = pHinsi(pH = pH_durafet$ph_s_dur, 
+                         ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
+                         Tlab = pH_durafet$temp_s_lab, Pinsi = 0, 
+                         S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+   )
 
@@
 #                          Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
-#                          S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "x", ks="d", 
+#                          S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
 #                          pHscale = "T", b="u74"), NA
@@
 
-pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "l", kf = "x", ks="d", pHscale = "T", b="u74")
+pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 
@@
   dplyr::filter(!is.na(ph_dur_corr), !is.na(temp_fb), !is.na(sal_fb))
-pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "x", ks="d", pHscale = "T", b="u74")
+pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 
@@
   dplyr::filter(!is.na(phcalc_fb), !is.na(temp_fb), !is.na(sal_fb))
-pH_calc$pH_calc_fb_norm4 <- pHinsi(pH = pH_calc$phcalc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "x", ks="d", pHscale = "T", b="u74")
+pH_calc$pH_calc_fb_norm4 <- pHinsi(pH = pH_calc$phcalc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 
@@
 ### Lueker vs Sulpis using means of monthly means
-```{r impact of constants 1, echo=FALSE, warning=FALSE, message=FALSE}
-# Compare Lueker and Sulpis
-# use mean values calculated for impacts of nutrients above
-
+```{r impact of constants discrete, echo=FALSE, warning=FALSE, message=FALSE}
+# Compare Lueker and Sulpis using mean discrete values
 # first, order columns
@@
   dplyr::select(datetime, date, year, monthd, montht, everything())
-
-# # calculate means
-# monthly_means <- d_all %>% 
-#   group_by(montht) %>% 
-#   summarize(mean_ct = mean(ct, na.rm = TRUE),
-#             mean_at_calc = mean(at_calc, na.rm = TRUE),
-#             mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
-#             mean_sal = mean(sal_fb, na.rm = TRUE),
-#             mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
-#   ungroup()
-# means <- monthly_means %>% 
-#   summarise(across(
-#     .cols = is.numeric, 
-#     .fns = mean, na.rm = TRUE, 
-#     .names = "{col}"
-#   ))
-
+# calculate means of discrete values
 mean_ct <- mean(discrete$ct, na.rm = TRUE)
-mean_at <-  mean(discrete$ct, na.rm = TRUE)
-mean_pco2 <-  mean(d_all$pco2_calc_fb)
+mean_at <- mean(discrete$at, na.rm = TRUE)
+mean_pco2 <- mean(discrete$pco2_calc_fb, na.rm = TRUE)
 mean_sal <- mean(discrete$sal_fb, na.rm = TRUE)
 mean_temp <- mean(discrete$temp_fb, na.rm = TRUE)
-
-# calculate typical uncertainty assuming uncertainties of 3 uatm for pCO2 and 4 umol/kg for AT
-errors_pco2_at <- seacarb::errors(flag=24, var1=mean_pco2_calc, var2=1e-6*mean_at_calc, S=mean_sal,
+# calculate typical uncertainty assuming uncertainties of 3 uatm for pCO2 and 4 umol/kg for AT and CT
+errors_pco2_at <- seacarb::errors(flag=24, var1=mean_pco2, var2=1e-6*mean_at, S=mean_sal,
                           T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
                           b="u74", evar1=3, evar2 = 4e-6)
-errors_at_ct <- seacarb::errors(flag=15, var1=1e-6*mean_at_calc, var2=1e-6*mean_ct, S=mean_sal,
+errors_at_ct <- seacarb::errors(flag=15, var1=1e-6*mean_at, var2=1e-6*mean_ct, S=mean_sal,
                           T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
@@
 )
-
 # impacts using pco2 and AT pair
-carb_l_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+carb_l_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                  Pt = 0, Sit = 0,
                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-carb_s_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+carb_s_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                  Pt = 0, Sit = 0,
@@
 diff_ls_1 <- carb_l_1 - carb_s_1
-
-# impacts using AT-DIC pair
-carb_l_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+# impacts using AT-CT pair
+carb_l_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                  Pt = 0, Sit = 0,
                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-carb_s_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
+carb_s_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
                 Pt = 0, Sit = 0, 
@@
 diff_ls_2 <- carb_l_2 - carb_s_2
+# summary
 const_choice <- bind_rows(diff_ls_1, diff_ls_2) %>% 
@@
 The means used are:
-`r knitr::kable(means, format = "simple")`
+`r knitr::kable(tibble(mean_at, mean_ct, mean_pco2, mean_sal, mean_temp), caption = "Mean discrete values.", format = "simple")`
 
@@
 ### Lueker vs Sulpis using all values pCO2 and at_calc
-```{r impact of constants 2, echo=FALSE, warning=FALSE, message=FALSE}
+```{r impact of constants whole series, echo=FALSE, warning=FALSE, message=FALSE}
 # Compare Lueker and Sulpis using pco2_fb and at_calc
@@
   dplyr::select(ph_s_sf_norm4, pco2_fb, at_calc, sal_fb, temp_fb)
-
+# Using Lueker  
 carb_l <-
@@
   )
-# normalize derived pH at 4°C
+# normalize Lueker-derived pH at 4°C
 carb_l$pH <- pHinsi(pH = carb_l$pH, 
@@
                          Tlab = carb_l$T, Pinsi = 0, 
-                         S = carb_l$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "x", ks="d", 
+                         S = carb_l$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
                          pHscale = "T", b="u74")
+# Using Sulpis
 carb_s <-
@@
   )
-# normalize derived pH at 4°C
+# normalize Sulpis-derived pH at 4°C
 carb_s$pH <- pHinsi(pH = carb_s$pH, 
@@
                          Tlab = carb_s$T, Pinsi = 0, 
-                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "x", ks="d", 
+                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
                          pHscale = "T", b="u74")
-
-# do difference
+# calculate difference Lueker - Sulpis
 diff_ls <- as_tibble(carb_l - carb_s) %>% 
@@
   dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite)
-
 # calculate descriptive statistics
@@
   dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
-
 # prepare tibble to compare calculated pH and spec pH
@@
   tidyr::drop_na(ph_s_sf_norm4)
-
 # summary of differences
@@
 lueker_sulpis_table <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), diff_lueker, diff_sulpis)
-
 # make plots

### 2021-03-19 awipev-CO2.Rmd
_nom4 replaced by _temp_4 for clarity

@@
                          pHscale = "T", b="u74"),
-   ph_s_sf_norm4 = pHinsi(pH = pH_seafet$ph_s_sf, 
+   ph_s_sf_temp_4 = pHinsi(pH = pH_seafet$ph_s_sf, 
                          ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
@@
                               Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74"),
-   ph_s_dur_norm4 = pHinsi(pH = pH_durafet$ph_s_dur, 
+   ph_s_dur_temp_4 = pHinsi(pH = pH_durafet$ph_s_dur, 
                          ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
@@
 pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(date, ph_s_sf_temp_insi, ph_s_sf_norm4)%>% 
+  dplyr::select(date, ph_s_sf_temp_insi, ph_s_sf_temp_4)%>% 
   dplyr::group_by(date) %>% 
@@
                    #ph_s_sf_temp_insi_sd = sd(ph_s_sf_temp_insi, na.rm = TRUE),
-                   ph_s_sf_norm4_mean = mean(ph_s_sf_norm4, na.rm = TRUE)
+                   ph_s_sf_temp_4_mean = mean(ph_s_sf_temp_4, na.rm = TRUE)
                    )
@@
 # seafetph <- pH_seafet_mean
-# colnames(seafetph) <- c("date", "ph_s_sf_insi", "ph_s_sf_norm4")
+# colnames(seafetph) <- c("date", "ph_s_sf_insi", "ph_s_sf_temp_4")
 # durafetph <- pH_durafet_mean
@@
 discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, ph_s_sf_temp_insi_mean, ph_s_sf_norm4_mean) %>%
+  dplyr::select(closest_datetime, ph_s_sf_temp_insi_mean, ph_s_sf_temp_4_mean) %>%
   dplyr::rename(ph_s_sf_temp_insi = ph_s_sf_temp_insi_mean,
-                ph_s_sf_norm4 = ph_s_sf_norm4_mean) %>%
+                ph_s_sf_temp_4 = ph_s_sf_temp_4_mean) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 # d_all <- d_all %>%
-#   dplyr::mutate(ph_s_sf_norm4 = ifelse(!is.na(pH_seafet$ph_s_sf),
+#   dplyr::mutate(ph_s_sf_temp_4 = ifelse(!is.na(pH_seafet$ph_s_sf),
 #                                               pHinsi(pH = pH_seafet$ph_s_sf, 
@@
 
-pH_sf$pHint_tot_sf_norm4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+pH_sf$pHint_tot_sf_temp_4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 
@@
   dplyr::filter(!is.na(ph_dur_corr), !is.na(temp_fb), !is.na(sal_fb))
-pH_dur$pH_durafet_norm4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+pH_dur$pH_durafet_temp_4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 
 # join pH sf norm + pH dur norm
-d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime, pHint_tot_sf_norm4 ), by="datetime")
-d_all <- left_join(d_all, pH_dur%>%dplyr::select(datetime, pH_durafet_norm4 ), by="datetime")
-
-fit <- lmodel2(data = d_all,  pHint_tot_sf_norm4 ~ pH_durafet_norm4 , nperm = 99)
-pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_norm4, y= pHint_tot_sf_norm4, label = monthd))+
+d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime, pHint_tot_sf_temp_4 ), by="datetime")
+d_all <- left_join(d_all, pH_dur%>%dplyr::select(datetime, pH_durafet_temp_4 ), by="datetime")
+
+fit <- lmodel2(data = d_all,  pHint_tot_sf_temp_4 ~ pH_durafet_temp_4 , nperm = 99)
+pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_temp_4, y= pHint_tot_sf_temp_4, label = monthd))+
   geom_point( aes(color=factor(monthd)), size =1, alpha=0.5) + 
@@
 
-durafet_sf_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pHint_tot_sf_norm4)
+durafet_sf_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_temp_4, pHint_tot_sf_temp_4)
 durafet_sf_contros_xts <- as.xts(durafet_sf_contros_xts, order.by = d_all$datetime)
 dygraph(durafet_sf_contros_xts, group = "awipev", main="pH durafet vs pH seaFET at 4°C", ylab="pHT") %>%
-    dySeries("pH_durafet_norm4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color =  "red", strokeWidth = 0, pointSize = 2 ) %>%
+    dySeries("pH_durafet_temp_4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("pHint_tot_sf_temp_4", label = "pH seaFET", color =  "red", strokeWidth = 0, pointSize = 2 ) %>%
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
   dplyr::filter(!is.na(phcalc_fb), !is.na(temp_fb), !is.na(sal_fb))
-pH_calc$pH_calc_fb_norm4 <- pHinsi(pH = pH_calc$phcalc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+pH_calc$pH_calc_fb_temp_4 <- pHinsi(pH = pH_calc$phcalc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 
 # join pH calc norm + pH dur/sf norm in d_all
-d_all <- left_join(d_all, pH_calc %>% dplyr::select(datetime, pH_calc_fb_norm4), by="datetime")
-
-durafet_calc_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pH_calc_fb_norm4)
+d_all <- left_join(d_all, pH_calc %>% dplyr::select(datetime, pH_calc_fb_temp_4), by="datetime")
+
+durafet_calc_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_temp_4, pH_calc_fb_temp_4)
 durafet_calc_contros_xts <- as.xts(durafet_calc_contros_xts, order.by = d_all$datetime)
 dygraph(durafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH durafet, normalized at 4°C", ylab="pHT") %>%
-    dySeries("pH_durafet_norm4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_calc_fb_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pH_durafet_temp_4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("pH_calc_fb_temp_4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
 ```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
-seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_norm4, pH_calc_fb_norm4)
+seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_temp_4, pH_calc_fb_temp_4)
 seafet_calc_contros_xts <- as.xts(seafet_calc_contros_xts, order.by = d_all$datetime)
 dygraph(seafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH seaFET, normalized at 4°C", ylab="pHT") %>%
-    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color ="blue", strokeWidth=0, pointSize=2) %>%
-    dySeries("pH_calc_fb_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
+    dySeries("pHint_tot_sf_temp_4", label = "pH seaFET", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("pH_calc_fb_temp_4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
     # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
   tidyr::drop_na(pco2_fb, at_calc, sal_fb, temp_fb) %>% 
-  dplyr::select(ph_s_sf_norm4, pco2_fb, at_calc, sal_fb, temp_fb)
+  dplyr::select(ph_s_sf_temp_4, pco2_fb, at_calc, sal_fb, temp_fb)
 # Using Lueker  
@@
 # prepare tibble to compare calculated pH and spec pH
-tmp2 <- tibble(ph_s_sf_norm4 = tmp$ph_s_sf_norm4, pH_l = carb_l$pH, pH_s = carb_s$pH) %>% 
-  tidyr::drop_na(ph_s_sf_norm4)
+tmp2 <- tibble(ph_s_sf_temp_4 = tmp$ph_s_sf_temp_4, pH_l = carb_l$pH, pH_s = carb_s$pH) %>% 
+  tidyr::drop_na(ph_s_sf_temp_4)
 # summary of differences
-diff_lueker <- as.numeric(summary(tmp2$ph_s_sf_norm4 - tmp2$pH_l))
-diff_sulpis <- as.numeric(summary(tmp2$ph_s_sf_norm4 - tmp2$pH_s))
+diff_lueker <- as.numeric(summary(tmp2$ph_s_sf_temp_4 - tmp2$pH_l))
+diff_sulpis <- as.numeric(summary(tmp2$ph_s_sf_temp_4 - tmp2$pH_s))
 lueker_sulpis_table <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), diff_lueker, diff_sulpis)
 # make plots
-p1 <- ggreg(xdata = tmp2$ph_s_sf_norm4, ydata = tmp2$pH_l, type = "MA", plot = TRUE, 
+p1 <- ggreg(xdata = tmp2$ph_s_sf_temp_4, ydata = tmp2$pH_l, type = "MA", plot = TRUE, 
             title = "Lueker vs measured", subtitle = "both pH normalized at 4°C",
@@
             ylab = "pH @ 4°C calculated (pCO2+AT) with Lueker")
-p2 <- ggreg(xdata = tmp2$ph_s_sf_norm4, ydata = tmp2$pH_s, type = "MA", plot = TRUE, 
+p2 <- ggreg(xdata = tmp2$ph_s_sf_temp_4, ydata = tmp2$pH_s, type = "MA", plot = TRUE, 
             title = "Sulpis vs measured", subtitle = "both pH normalized at 4°C",

### 2021-03-19 awipev-CO2.Rmd
Refined impacts of formulations K1 and K2

@@
   )
-
 # Conversion of spec pH of FerryBox samples to FerryBox temp
@@
    )
-
 # Make mean for replicates + SD
-pH_seafet_mean <- pH_seafet%>%
-  dplyr::select(date, ph_s_sf_temp_insi, ph_s_sf_temp_4)%>% 
+pH_seafet_mean <- pH_seafet %>%
+  dplyr::select(date, ph_s_sf_temp_insi, ph_s_sf_temp_4) %>% 
   dplyr::group_by(date) %>% 
@@
                    )
-
-pH_durafet_mean <- pH_durafet%>%
-  dplyr::select(date, ph_s_dur_temp_fb)%>% 
+pH_durafet_mean <- pH_durafet %>%
+  dplyr::select(date, ph_s_dur_temp_fb, ph_s_dur_temp_4) %>% 
   dplyr::group_by(date) %>% 
-  dplyr::summarize(ph_s_dur_temp_fb_mean = mean(ph_s_dur_temp_fb, na.rm = TRUE)#,
-                   #ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE)
+  dplyr::summarize(ph_s_dur_temp_fb_mean = mean(ph_s_dur_temp_fb, na.rm = TRUE),
+                   #ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE),
+                   ph_s_dur_temp_4_mean = mean(ph_s_dur_temp_4, na.rm = TRUE)
                    )
@@
 discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, ph_s_dur_temp_fb_mean) %>%
-  dplyr::rename(ph_s_dur_temp_fb = ph_s_dur_temp_fb_mean) %>%
+  dplyr::select(closest_datetime, ph_s_dur_temp_fb_mean, ph_s_dur_temp_4_mean) %>%
+  dplyr::rename(ph_s_dur_temp_fb = ph_s_dur_temp_fb_mean,
+                ph_s_dur_temp_4 = ph_s_dur_temp_4_mean) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 The means used are:
-`r knitr::kable(tibble(mean_at, mean_ct, mean_pco2, mean_sal, mean_temp), caption = "Mean discrete values.", format = "simple")`
+`r knitr::kable(tibble(mean_at, mean_ct, mean_pco2, mean_sal, mean_temp), digits = c(1, 1, 0, 1, 1), caption = "Mean discrete values.", format = "simple")`
 
@@
 
-### Lueker vs Sulpis using all values pCO2 and at_calc
-```{r impact of constants whole series, echo=FALSE, warning=FALSE, message=FALSE}
+### Lueker vs Sulpis using FerryBox pCO2 and at_calc
+```{r impact of constants on FerryBox data, echo=FALSE, warning=FALSE, message=FALSE}
 # Compare Lueker and Sulpis using pco2_fb and at_calc
@@
   tidyr::drop_na(pco2_fb, at_calc, sal_fb, temp_fb) %>% 
-  dplyr::select(ph_s_sf_temp_4, pco2_fb, at_calc, sal_fb, temp_fb)
+  dplyr::select(ph_s_dur_temp_4, pco2_fb, at_calc, sal_fb, temp_fb)
 # Using Lueker  
@@
 # prepare tibble to compare calculated pH and spec pH
-tmp2 <- tibble(ph_s_sf_temp_4 = tmp$ph_s_sf_temp_4, pH_l = carb_l$pH, pH_s = carb_s$pH) %>% 
-  tidyr::drop_na(ph_s_sf_temp_4)
+tmp2 <- tibble(ph_s_dur_temp_4 = tmp$ph_s_dur_temp_4, pH_l = carb_l$pH, pH_s = carb_s$pH) %>% 
+  tidyr::drop_na(ph_s_dur_temp_4)
 # summary of differences
-diff_lueker <- as.numeric(summary(tmp2$ph_s_sf_temp_4 - tmp2$pH_l))
-diff_sulpis <- as.numeric(summary(tmp2$ph_s_sf_temp_4 - tmp2$pH_s))
+diff_lueker <- as.numeric(summary(tmp2$ph_s_dur_temp_4 - tmp2$pH_l))
+diff_sulpis <- as.numeric(summary(tmp2$ph_s_dur_temp_4 - tmp2$pH_s))
 lueker_sulpis_table <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), diff_lueker, diff_sulpis)
 # make plots
-p1 <- ggreg(xdata = tmp2$ph_s_sf_temp_4, ydata = tmp2$pH_l, type = "MA", plot = TRUE, 
+p1 <- ggreg(xdata = tmp2$ph_s_dur_temp_4, ydata = tmp2$pH_l, type = "MA", plot = TRUE, 
             title = "Lueker vs measured", subtitle = "both pH normalized at 4°C",
@@
             ylab = "pH @ 4°C calculated (pCO2+AT) with Lueker")
-p2 <- ggreg(xdata = tmp2$ph_s_sf_temp_4, ydata = tmp2$pH_s, type = "MA", plot = TRUE, 
+p2 <- ggreg(xdata = tmp2$ph_s_dur_temp_4, ydata = tmp2$pH_s, type = "MA", plot = TRUE, 
             title = "Sulpis vs measured", subtitle = "both pH normalized at 4°C",
@@
 ```
-The overall means of pCO2, AT (calculated from the AT-salinity relationship), salinity and temperature in the FerryBox were used to calculate pH from measured pCO2 and AT (from a salinity-AT relationship) and from AT and CT.
-using the formulations of Lueker et al.
+The discrete values of pCO2, AT (calculated from the AT-salinity relationship), salinity and temperature in the FerryBox were used to calculate pH from measured pCO2 and AT (from a salinity-AT relationship) using the formulations for K1 and K2 of Lueker et al.
 (2000) and Sulpis et al.
-(2020) of K1 and K2.
-The difference induced by the choice of the carbonic acid constants is large for pH, pCO2 and DIC and negligible for OmegaAragonite.
-
-`r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis", format = "simple")`
+(2020).
+The differences induced by the choice of the carbonic acid constants is:
++ large for pH (0.026 pH units on average; always higher with Sulpis than with Lueker)
++ large for CT (3.7 umol/kg on average; always lower with Sulpis than with Lueker)
++ negligible for OmegaAragonite
+`r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis using discrete Ferrybox data.", format = "simple")`
 
@@
 All pH values were normalized to a temperature of 4°C.
-Both formulations overestimate spectrophotometric pH
-`r knitr::kable(lueker_sulpis_table, digits = 3, caption = "Difference between spectrophotometric pH and Lueker and Sulpis", format = "simple")`
+The absloute differences are large, up to 0.14 pH units.
+On average, both formulations overestimate spectrophotometric pH, by 0.016 pH units with Lueker et al.
+(2020) and by 0.042 pH units with Sulpis et al.
+(2020).
+`r knitr::kable(lueker_sulpis_table, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using the formulations for K1 and K2 of Lueker and Sulpis.", format = "simple")`
 

### 2021-03-19 awipev-CO2.Rmd
Finalized choice of K1K2

@@
   return(plt)
-  } else {
-  return(fit)
-}
+  } #else {
+  #return(fit)
+#}
 }
@@
                  dplyr::select(
-                   c(
-                     closest_datetime,
+                   c(closest_datetime,
                      sal_fb,
@@
 Salinity from FB is taken in consideration.
-If data gaps are encountered, they are filled with bottom salinty data from ctd (> 8 m).
+If data gaps are encountered, they are filled with bottom salinity data from ctd (> 8 m).
 New column "sal_mix" is created and is the one used in ESSD paper.
@@
 ## Impact of choice of constants  {.tabset .tabset-pills}
-### Lueker vs Sulpis using means of monthly means
+### Lueker vs Sulpis using mean discrete values
 ```{r impact of constants discrete, echo=FALSE, warning=FALSE, message=FALSE}
@@
 mean_temp <- mean(discrete$temp_fb, na.rm = TRUE)
+mean_discrete <- tibble(mean_ct = mean_ct, mean_at = mean_at, mean_pco2 = mean_pco2, mean_sal = mean_sal, mean_temp = mean_temp)
 # calculate typical uncertainty assuming uncertainties of 3 uatm for pCO2 and 4 umol/kg for AT and CT
@@
 The means used are:
-`r knitr::kable(tibble(mean_at, mean_ct, mean_pco2, mean_sal, mean_temp), digits = c(1, 1, 0, 1, 1), caption = "Mean discrete values.", format = "simple")`
+`r knitr::kable(mean_discrete, digits = c(1, 1, 0, 1, 1), caption = "Mean discrete values.", format = "simple")`
 
@@
 ```{r impact of constants on FerryBox data, echo=FALSE, warning=FALSE, message=FALSE}
-# Compare Lueker and Sulpis using pco2_fb and at_calc
+# Compare Lueker and Sulpis using pco2_fb and at in situ
 tmp <- d_all %>% 
-  tidyr::drop_na(pco2_fb, at_calc, sal_fb, temp_fb) %>% 
+  tidyr::drop_na(pco2_fb, at, sal_fb, temp_fb) %>% 
   dplyr::select(ph_s_dur_temp_4, pco2_fb, at_calc, sal_fb, temp_fb)
 # Using Lueker  
-carb_l <-
-  carb(
-    24,
-    tmp$pco2_fb,
-    tmp$at_calc * 1e-6,
-    S = tmp$sal_fb,
-    T = tmp$temp_fb,
-    P = 0,
-    Pt = 0,
-    Sit = 0,
-    k1k2 = "l",
-    kf = "dg",
-    ks = "d",
-    pHscale = "T",
-    b = "u74"
-  )
+carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at_calc * 1e-6, S = tmp$sal_fb, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
 # normalize Lueker-derived pH at 4°C
-carb_l$pH <- pHinsi(pH = carb_l$pH, 
-                         ALK = carb_l$ALK, Tinsi = 4, 
-                         Tlab = carb_l$T, Pinsi = 0, 
+carb_l$pH <- pHinsi(pH = carb_l$pH, ALK = carb_l$ALK, Tinsi = 4, Tlab = carb_l$T, Pinsi = 0, 
                          S = carb_l$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
@@
 # Using Sulpis
-carb_s <-
-  carb(
-    24,
-    tmp$pco2_fb,
-    tmp$at_calc * 1e-6,
-    S = tmp$sal_fb,
-    T = tmp$temp_fb,
-    P = 0,
-    Pt = 0,
-    Sit = 0,
-    k1k2 = "s20",
-    kf = "dg",
-    ks = "d",
-    pHscale = "T",
-    b = "u74"
-  )
+carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at_calc * 1e-6, S = tmp$sal_fb, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
 # normalize Sulpis-derived pH at 4°C
-carb_s$pH <- pHinsi(pH = carb_s$pH, 
-                         ALK = carb_s$ALK, Tinsi = 4, 
-                         Tlab = carb_s$T, Pinsi = 0, 
+carb_s$pH <- pHinsi(pH = carb_s$pH, ALK = carb_s$ALK, Tinsi = 4, Tlab = carb_s$T, Pinsi = 0, 
                          S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# Using Papadimitriou
+carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at_calc * 1e-6, S = tmp$sal_fb, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Papadimitriou-derived pH at 4°C
+carb_s$pH <- pHinsi(pH = carb_s$pH, ALK = carb_s$ALK, Tinsi = 4, Tlab = carb_s$T, Pinsi = 0, 
+                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# Using Millero et al. (2002)
+carb_m <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at_calc * 1e-6, S = tmp$sal_fb, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Millero et al. (2002)-derived pH at 4°C
+carb_s$pH <- pHinsi(pH = carb_s$pH, ALK = carb_s$ALK, Tinsi = 4, Tlab = carb_s$T, Pinsi = 0, 
+                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
                          pHscale = "T", b="u74")
@@
   dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite)
-# calculate descriptive statistics
+# calculate descriptive statistics Lueker - Sulpis
 diff_ls_quant <- tibble(pH = as.numeric(summary(diff_ls$delta_ph)),
@@
 # prepare tibble to compare calculated pH and spec pH
-tmp2 <- tibble(ph_s_dur_temp_4 = tmp$ph_s_dur_temp_4, pH_l = carb_l$pH, pH_s = carb_s$pH) %>% 
+tmp2 <- tibble(ph_s_dur_temp_4 = tmp$ph_s_dur_temp_4, pH_l = carb_l$pH, pH_s = carb_s$pH, pH_p = carb_p$pH, pH_m = carb_m$pH) %>% 
   tidyr::drop_na(ph_s_dur_temp_4)
 # summary of differences
-diff_lueker <- as.numeric(summary(tmp2$ph_s_dur_temp_4 - tmp2$pH_l))
-diff_sulpis <- as.numeric(summary(tmp2$ph_s_dur_temp_4 - tmp2$pH_s))
-lueker_sulpis_table <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), diff_lueker, diff_sulpis)
+lueker <- as.numeric(summary(tmp2$ph_s_dur_temp_4 - tmp2$pH_l))
+sulpis <- as.numeric(summary(tmp2$ph_s_dur_temp_4 - tmp2$pH_s))
+papadimitriou <- as.numeric(summary(tmp2$ph_s_dur_temp_4 - tmp2$pH_p))
+millero2002 <- as.numeric(summary(tmp2$ph_s_dur_temp_4 - tmp2$pH_m))
+diff_table <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), lueker, sulpis, papadimitriou, millero2002)
 # make plots
@@
 ```
-The discrete values of pCO2, AT (calculated from the AT-salinity relationship), salinity and temperature in the FerryBox were used to calculate pH from measured pCO2 and AT (from a salinity-AT relationship) using the formulations for K1 and K2 of Lueker et al.
+The discrete values of pCO2, salinity and temperature in the FerryBox and in situ AT were used to calculate pH from measured pCO2 and AT using the formulations for K1 and K2 of Lueker et al.
 (2000) and Sulpis et al.
@@
 The differences induced by the choice of the carbonic acid constants is:
-+ large for pH (0.026 pH units on average; always higher with Sulpis than with Lueker)
-+ large for CT (3.7 umol/kg on average; always lower with Sulpis than with Lueker)
-+ negligible for OmegaAragonite
+
+- small for pH (`r round(diff_ls_quant[4, 2], digits = 3)` pH units on average; ; median is `r round(diff_ls_quant[3, 2], digits = 3)`) compared with the uncertainty calculated with seacarb (`r round(const_choice[1, 6], digits = 3)`.
+In general, pH is higher with Sulpis than with Lueker.
+- very good for CT (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on average; always lower with Sulpis than with Lueker) compared with the uncertainty calculated with seacarb (`r round(const_choice[1, 8], digits = 1)`)
+- negligible for OmegaAragonite
+
 `r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis using discrete Ferrybox data.", format = "simple")`
 
-Here we compare pH measured spectrophotometrically with pH calculated from pCO2 and AT using the sets of K1 and K2 of Lueker et al.
-(2000) and Sulpis et al.
-(2020).
+Here we compare pH measured spectrophotometrically with pH calculated from pCO2 and AT using various formulations of K1 and K2.
 All pH values were normalized to a temperature of 4°C.
-The absloute differences are large, up to 0.14 pH units.
-On average, both formulations overestimate spectrophotometric pH, by 0.016 pH units with Lueker et al.
-(2020) and by 0.042 pH units with Sulpis et al.
-(2020).
-`r knitr::kable(lueker_sulpis_table, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using the formulations for K1 and K2 of Lueker and Sulpis.", format = "simple")`
+The absolute differences are large, up to `r round(max(abs(diff_table[, 2:5])), digits=3)` pH units.
+On average, both formulations overestimate spectrophotometric pH.
+The calculated pH closer to measured pH is using the formulation of Lueker et al.
+(2020) with a mean difference of `r round(max(diff_table[4, 2:5]), digits=3)` pH units.
+This difference is twice larger than the uncertainty for pH calculated from pCO2 and AT according to seacarb (`r round(errors_pco2_at$pH, digits=3)`).
+`r knitr::kable(diff_table, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "simple")`
+`r include_graphics("figures/lueker-sulpis.png")`
 

### 2021-03-22 awipev-CO2.Rmd
refined k1k2 issue; new figure added

@@
 output:
-  rmarkdown::html_document:
-    theme: paper
-    number_sections: false
+  html_document: default
+  word_document: default
+  pdf_document: default
+  odt_document: default
 ---
@@
 
-### Lueker vs Sulpis using FerryBox pCO2 and at_calc
+### Lueker vs Sulpis using FerryBox pCO2 and at in situ
 ```{r impact of constants on FerryBox data, echo=FALSE, warning=FALSE, message=FALSE}
@@
   tidyr::drop_na(pco2_fb, at, sal_fb, temp_fb) %>% 
-  dplyr::select(ph_s_dur_temp_4, pco2_fb, at_calc, sal_fb, temp_fb)
+  dplyr::select(datetime, ph_s_dur_temp_4, pco2_fb, at_calc, sal_fb, temp_fb)
 # Using Lueker  
@@
 # prepare tibble to compare calculated pH and spec pH
-tmp2 <- tibble(ph_s_dur_temp_4 = tmp$ph_s_dur_temp_4, pH_l = carb_l$pH, pH_s = carb_s$pH, pH_p = carb_p$pH, pH_m = carb_m$pH) %>% 
+tmp2 <- tibble(datetime = tmp$datetime, ph_s_dur_temp_4 = tmp$ph_s_dur_temp_4, 
+               pH_l = carb_l$pH, pH_s = carb_s$pH, 
+               pH_p = carb_p$pH, pH_m = carb_m$pH, temp_fb = tmp$temp_fb) %>% 
   tidyr::drop_na(ph_s_dur_temp_4)
@@
             xlab = "Spectrophotometric pH measured @ 4°C",
-            ylab = "pH @ 4°C calculated (pCO2+AT) with Lueker")
+            ylab = "pH @ 4°C calculated (pCO2+AT) with Lueker") +
+  lims(x = c(8, 8.4), y = c(8, 8.4)) +
+  theme(plot.title = element_text(size = 10),
+        axis.text = element_text(size = 10)) +
+  coord_fixed(ratio = 1)
 p2 <- ggreg(xdata = tmp2$ph_s_dur_temp_4, ydata = tmp2$pH_s, type = "MA", plot = TRUE, 
@@
             xlab = "Spectrophotometric pH measured @ 4°C",
-            ylab = "pH @ 4°C calculated (pCO2+AT) with Sulpis") 
-p <- p1 + p2
-ggsave(filename = "figures/lueker-sulpis.png", plot = p, width = 20, height = 15, units = "cm")
-```
+            ylab = "pH @ 4°C calculated (pCO2+AT) with Sulpis")  +
+  lims(x = c(8, 8.4), y = c(8, 8.4)) +
+  theme(plot.title = element_text(size = 10),
+        axis.text = element_text(size = 10)) +
+  coord_fixed(ratio = 1)
+p3 <- tmp2 %>% 
+  dplyr::mutate(delta_lueker = tmp2$ph_s_dur_temp_4 - tmp2$pH_l, 
+                delta_sulpis = tmp2$ph_s_dur_temp_4 - tmp2$pH_s, 
+                delta_papadimitriou = tmp2$ph_s_dur_temp_4 - tmp2$pH_p, 
+                delta_millero2002 = tmp2$ph_s_dur_temp_4 - tmp2$pH_m) %>% 
+  dplyr::select(-starts_with("ph_"), -datetime) %>% 
+  tidyr::pivot_longer(!temp_fb, names_to = "delta", values_to = "diff") %>% 
+  ggplot(aes(x = temp_fb, y = diff, col = delta)) +
+  geom_point() + geom_line() +
+  labs(x = "Ferrybox temperature (°C)", y = "Spec pH - calculated pH (units)") +
+  theme(legend.title = element_blank())
+p <- (p1 + p2) / p3
+ggsave(filename = "figures/lueker-sulpis.png", plot = p, width = 25, height = 20, units = "cm")
+```
+```{r save for k1k2 report, echo=FALSE, message= FALSE, warning=FALSE}
+k1k2 <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
+             errors_pco2_at = errors_pco2_at, diff_table = diff_table, 
+             diff_ls_quant = diff_ls_quant)
+save(k1k2, file="reports/k1k2_data.RData")
+```
+
 The discrete values of pCO2, salinity and temperature in the FerryBox and in situ AT were used to calculate pH from measured pCO2 and AT using the formulations for K1 and K2 of Lueker et al.

### 2021-03-22 awipev-CO2.Rmd
k1k2 revised figs names
cosmetic changes

@@
 p <- (p1 + p2) / p3
-ggsave(filename = "figures/lueker-sulpis.png", plot = p, width = 25, height = 20, units = "cm")
-```
-```{r save for k1k2 report, echo=FALSE, message= FALSE, warning=FALSE}
+ggsave(filename = "figures/k1k2_all.png", plot = p, width = 25, height = 20, units = "cm")
+ggsave(filename = "figures/k1k2_temperature.png", plot = p3, width = 25, height = 20, units = "cm")
+```
+```{r save elements for k1k2 report, echo=FALSE, message= FALSE, warning=FALSE}
 k1k2 <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,

### 2021-03-22 awipev-CO2.Rmd
Reworked impacts of nuts

@@
 
-## Impact of nutrients
+## Impact of nutrients   {.tabset .tabset-pills}
 ```{r impact of nutrients, echo=FALSE, warning=FALSE, message=FALSE}
@@
 mean_temp <-  mean(means$mean_temp)
-# then check impacts using pco2 and AT
+# then check impacts of 0, min and max nutrient values using pco2 and AT
 carb_po4_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
-                 Pt = c(min(d_all$po4/1e6, na.rm=TRUE), max(d_all$po4/1e6, na.rm=TRUE)), Sit = 0,
+                 Pt = c(0, min(d_all$po4/1e6, na.rm=TRUE), max(d_all$po4/1e6, na.rm=TRUE)), Sit = 0,
                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-diff_po4_1 <- carb_po4_1[1,] - carb_po4_1[2,]
+diff_po4_0a <- carb_po4_1[1,] - carb_po4_1[3,] # diff between no PO4 and max PO4
+diff_po4_1a <- carb_po4_1[2,] - carb_po4_1[3,] # diff between min PO4 and max PO4
 carb_Si_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0,
-                Pt = 0, Sit = c(min(d_all$si/1e6, na.rm=TRUE), max(d_all$si/1e6, na.rm=TRUE)), 
+                Pt = 0, Sit = c(0, min(d_all$si/1e6, na.rm=TRUE), max(d_all$si/1e6, na.rm=TRUE)), 
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-diff_Si_1 <- carb_Si_1[1,] - carb_Si_1[2,]
-
-# then check impacts using AT-DIC pair
+diff_Si_0a <- carb_Si_1[1,] - carb_Si_1[3,] # diff between no Si and max Si
+diff_Si_1a <- carb_Si_1[2,] - carb_Si_1[3,] # diff between no Si and max Si
+
+# then check impacts of min and max nutrient values using AT-DIC pair
 carb_po4_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
-                 Pt = c(min(d_all$po4/1e6, na.rm=TRUE), max(d_all$po4/1e6, na.rm=TRUE)), Sit = 0,
+                 Pt = c(0, min(d_all$po4/1e6, na.rm=TRUE), max(d_all$po4/1e6, na.rm=TRUE)), Sit = 0,
                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-diff_po4_2 <- carb_po4_2[1,] - carb_po4_2[2,]
+diff_po4_0b <- carb_po4_2[1,] - carb_po4_2[3,] # diff between no PO4 and max PO4
+diff_po4_1b <- carb_po4_2[2,] - carb_po4_2[3,] # diff between min PO4 and max PO4
 carb_Si_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
-                Pt = 0, Sit = c(min(d_all$si/1e6, na.rm=TRUE), max(d_all$si/1e6, na.rm=TRUE)), 
+                Pt = 0, Sit = c(0, min(d_all$si/1e6, na.rm=TRUE), max(d_all$si/1e6, na.rm=TRUE)), 
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-diff_Si_2 <- carb_Si_2[1,] - carb_Si_2[2,]
+diff_Si_0b <- carb_Si_2[1,] - carb_Si_2[3,] # diff between no Si and max Si
+diff_Si_1b <- carb_Si_2[2,] - carb_Si_2[3,] # diff between no Si and max Si
+
+#nuts <- tibble(Pair = "pCO2-AT", "CT-AT",
+#)
+nuts_table <- bind_rows(diff_po4_0a, diff_Si_0a, diff_po4_0b, diff_Si_0b) %>% 
+  dplyr::mutate(flag = c("pCO2 and ALK", "pCO2 and ALK", "ALK and DIC", "ALK and DIC"),
+                nutrients = c("No PO4-max PO4", "No Si-max Si", "No PO4-max PO4", 
+                              "No Si-max Si")) %>% 
+  dplyr::select(flag, nutrients, pH, pCO2, DIC, OmegaAragonite)
 rm(ts_po4_bp, ts_Si_bp)
 ```
+`r knitr::kable(nuts_table, digits = c(1, 1, 4, 2, 4, 3), caption = "Impact of PO4 and Si.", format = "simple")`
 
@@
 ### Using the pCO2-AT pair (hourly data)
-The impact of the min max changes of po4 on pH, DIC, and Omega_a are small:  `r round(1000*diff_po4_1$pH, digits=2)` mpH units, `r round(1e6*diff_po4_1$DIC, digits=2)` umol/kg for CT and `r round(diff_po4_1$OmegaAragonite, digits=2)` for OmegaAragonite.
-
-The impact of the min max changes of si on pH, DIC, and Omega_a are small:  `r round(1000*diff_Si_1$pH, digits=2)` mpH units, `r round(1e6*diff_Si_1$DIC, digits=2)` umol/kg for CT and `r round(diff_Si_1$OmegaAragonite, digits=2)` for OmegaAragonite.
+The difference between no PO4 and its maximum value on pH, DIC, and Omega_a are small:  `r round(1000*diff_po4_0a$pH, digits=2)` mpH units, `r round(1e6*diff_po4_0a$DIC, digits=2)` umol/kg for CT and `r round(diff_po4_0a$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of po4 on pH, DIC, and Omega_a are small:  `r round(1000*diff_po4_1a$pH, digits=2)` mpH units, `r round(1e6*diff_po4_1a$DIC, digits=2)` umol/kg for CT and `r round(diff_po4_1a$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The difference between no Si and its maximum value on pH, DIC, and Omega_a are small:  `r round(1000*diff_Si_0a$pH, digits=2)` mpH units, `r round(1e6*diff_Si_0a$DIC, digits=2)` umol/kg for CT and `r round(diff_Si_0a$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of si on pH, DIC, and Omega_a are small:  `r round(1000*diff_Si_1a$pH, digits=2)` mpH units, `r round(1e6*diff_Si_1a$DIC, digits=2)` umol/kg for CT and `r round(diff_Si_1a$OmegaAragonite, digits=2)` for OmegaAragonite.
 
 ### Using the CT-AT pair (discrete data)
-The impact of the min max changes of po4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_po4_2$pH, digits=2)` mpH units, `r round(diff_po4_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_po4_2$OmegaAragonite, digits=2)` for OmegaAragonite.
-
-The impact of the min max changes of po4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_Si_2$pH, digits=2)` mpH units, `r round(diff_Si_2$pCO2, digits=2)` uatm for pCO2 and `r round(diff_Si_2$OmegaAragonite, digits=2)` for OmegaAragonite.
+The difference between no PO4 and its maximum value on pH, pCO2, and Omega_a are small:  `r round(1000*diff_po4_0b$pH, digits=2)` mpH units, `r round(diff_po4_0b$pCO2, digits=2)` uatm for pCO2 and `r round(diff_po4_0b$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of po4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_po4_1b$pH, digits=2)` mpH units, `r round(diff_po4_1b$pCO2, digits=2)` uatm for pCO2 and `r round(diff_po4_1b$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The difference between no Si and its maximum value on pH, pCO2, and Omega_a are small:  `r round(1000*diff_Si_0b$pH, digits=2)` mpH units, `r round(diff_Si_0b$pCO2, digits=2)` uatm for pCO2 and `r round(diff_Si_0b$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of Si on pH, pCO2, and Omega_a are small:  `r round(1000*diff_Si_1b$pH, digits=2)` mpH units, `r round(diff_Si_1b$pCO2, digits=2)` uatm for pCO2 and `r round(diff_Si_1b$OmegaAragonite, digits=2)` for OmegaAragonite.
 
@@
 
-### Lueker vs Sulpis using FerryBox pCO2 and at in situ
-```{r impact of constants on FerryBox data, echo=FALSE, warning=FALSE, message=FALSE}
-# Compare Lueker and Sulpis using pco2_fb and at in situ
+### K1K2 using FerryBox pCO2 and at in situ
+```{r impact of constants using FerryBox pCO2 and at in situ, echo=FALSE, warning=FALSE, message=FALSE}
 tmp <- d_all %>% 
@@
 (2020).
+Note that this cannot be done with in situ AT and CT because spectrophotometric pH in situ is not at a fixed depth.
+
 The differences induced by the choice of the carbonic acid constants is:

### 2021-03-24 awipev-CO2.Rmd
Bugs corrected in calculations involving the various formulations of K1K2

@@
   tidyr::drop_na(pco2_fb, at, sal_fb, temp_fb) %>% 
-  dplyr::select(datetime, ph_s_dur_temp_4, pco2_fb, at_calc, sal_fb, temp_fb)
+  dplyr::select(datetime, ph_s_dur_temp_4, pco2_fb, at, sal_fb, temp_fb)
 # Using Lueker  
-carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at_calc * 1e-6, S = tmp$sal_fb, 
+carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", 
@@
 # Using Sulpis
-carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at_calc * 1e-6, S = tmp$sal_fb, 
+carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks = "d", 
@@
 # Using Papadimitriou
-carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at_calc * 1e-6, S = tmp$sal_fb, 
+carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks = "d", 
@@
 # normalize Papadimitriou-derived pH at 4°C
-carb_s$pH <- pHinsi(pH = carb_s$pH, ALK = carb_s$ALK, Tinsi = 4, Tlab = carb_s$T, Pinsi = 0, 
-                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
+carb_p$pH <- pHinsi(pH = carb_p$pH, ALK = carb_p$ALK, Tinsi = 4, Tlab = carb_p$T, Pinsi = 0, 
+                         S = carb_p$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
                          pHscale = "T", b="u74")
 # Using Millero et al. (2002)
-carb_m <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at_calc * 1e-6, S = tmp$sal_fb, 
+carb_m <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks = "d", 
@@
 # normalize Millero et al. (2002)-derived pH at 4°C
-carb_s$pH <- pHinsi(pH = carb_s$pH, ALK = carb_s$ALK, Tinsi = 4, Tlab = carb_s$T, Pinsi = 0, 
-                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
+carb_m$pH <- pHinsi(pH = carb_m$pH, ALK = carb_m$ALK, Tinsi = 4, Tlab = carb_m$T, Pinsi = 0, 
+                         S = carb_m$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
                          pHscale = "T", b="u74")

### 2021-03-30 awipev-CO2.Rmd
Added K1K2 from AT and CT

@@
                               Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74"),
-   ph_s_dur_temp_4 = pHinsi(pH = pH_durafet$ph_s_dur, 
+   ph_s_dur_temp_4_l = pHinsi(pH = pH_durafet$ph_s_dur, # lueker
                          ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
@@
                          S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74"),
+   ph_s_dur_temp_4_s20 = pHinsi(pH = pH_durafet$ph_s_dur, # Sulpis
+                         ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
+                         Tlab = pH_durafet$temp_s_lab, Pinsi = 0, 
+                         S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74"),       # Millero 02
+   ph_s_dur_temp_4_p18 = pHinsi(pH = pH_durafet$ph_s_dur, # Papadimitriou
+                         ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
+                         Tlab = pH_durafet$temp_s_lab, Pinsi = 0, 
+                         S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74"),
+   ph_s_dur_temp_4_m02 = pHinsi(pH = pH_durafet$ph_s_dur,  # Millero 02
+                         ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
+                         Tlab = pH_durafet$temp_s_lab, Pinsi = 0, 
+                         S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
                          pHscale = "T", b="u74")
+
    )
@@
 pH_durafet_mean <- pH_durafet %>%
-  dplyr::select(date, ph_s_dur_temp_fb, ph_s_dur_temp_4) %>% 
+  dplyr::select(date, ph_s_dur_temp_fb, ph_s_dur_temp_4_l, ph_s_dur_temp_4_s20,
+                ph_s_dur_temp_4_p18, ph_s_dur_temp_4_m02) %>% 
   dplyr::group_by(date) %>% 
@@
                    #ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE),
-                   ph_s_dur_temp_4_mean = mean(ph_s_dur_temp_4, na.rm = TRUE)
+                   ph_s_dur_temp_4_l_mean = mean(ph_s_dur_temp_4_l, na.rm = TRUE),
+                   ph_s_dur_temp_4_s20_mean = mean(ph_s_dur_temp_4_s20, na.rm = TRUE),
+                   ph_s_dur_temp_4_p18_mean = mean(ph_s_dur_temp_4_p18, na.rm = TRUE),
+                   ph_s_dur_temp_4_m02_mean = mean(ph_s_dur_temp_4_m02, na.rm = TRUE)
                    )
@@
 carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-discrete_no_na$phcalc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
+discrete_no_na$ph_calc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
 discrete_no_na$pco2_calc_fb <- carb$pCO2
@@
 # create new variable in "discrete_is_na" to bind "discrete_no_na"
-discrete_is_na$phcalc_fb <- NA
+discrete_is_na$ph_calc_fb <- NA
 discrete_is_na$pco2_calc_fb <- NA
@@
   #drop_na() %>%
-  dplyr::select(closest_datetime, phcalc_fb) %>%
+  dplyr::select(closest_datetime, ph_calc_fb) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, ph_s_dur_temp_fb_mean, ph_s_dur_temp_4_mean) %>%
+  dplyr::select(closest_datetime, ph_s_dur_temp_fb_mean, ph_s_dur_temp_4_l_mean,
+                ph_s_dur_temp_4_s20_mean, ph_s_dur_temp_4_p18_mean, ph_s_dur_temp_4_m02_mean) %>%
   dplyr::rename(ph_s_dur_temp_fb = ph_s_dur_temp_fb_mean,
-                ph_s_dur_temp_4 = ph_s_dur_temp_4_mean) %>%
+                ph_s_dur_temp_4 = ph_s_dur_temp_4_l_mean, # lueker by default
+                ph_s_dur_temp_4_l = ph_s_dur_temp_4_l_mean,
+                ph_s_dur_temp_4_s20 = ph_s_dur_temp_4_s20_mean,
+                ph_s_dur_temp_4_p18 = ph_s_dur_temp_4_p18_mean,
+                ph_s_dur_temp_4_m02 = ph_s_dur_temp_4_m02_mean,) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 ```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
-# Normalize phcalc from AT/CT to 4°c
+# Normalize ph_calc from AT/CT to 4°c
 pH_calc <- discrete %>%
-  dplyr::select(datetime, sal_fb, temp_fb, phcalc_fb, at)%>%
-  dplyr::filter(!is.na(phcalc_fb), !is.na(temp_fb), !is.na(sal_fb))
-pH_calc$pH_calc_fb_temp_4 <- pHinsi(pH = pH_calc$phcalc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+  dplyr::select(datetime, sal_fb, temp_fb, ph_calc_fb, at)%>%
+  dplyr::filter(!is.na(ph_calc_fb), !is.na(temp_fb), !is.na(sal_fb))
+pH_calc$pH_calc_fb_temp_4 <- pHinsi(pH = pH_calc$ph_calc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 
@@
 
-## Impact of choice of constants  {.tabset .tabset-pills}
-### Lueker vs Sulpis using mean discrete values
+## Impact K1K2  {.tabset .tabset-pills}
+### Lueker vs Sulpis
 ```{r impact of constants discrete, echo=FALSE, warning=FALSE, message=FALSE}
@@
 mean_discrete <- tibble(mean_ct = mean_ct, mean_at = mean_at, mean_pco2 = mean_pco2, mean_sal = mean_sal, mean_temp = mean_temp)
+
 # calculate typical uncertainty assuming uncertainties of 3 uatm for pCO2 and 4 umol/kg for AT and CT
@@
 ```
-The means used are:
+Using the following using mean discrete values:
 `r knitr::kable(mean_discrete, digits = c(1, 1, 0, 1, 1), caption = "Mean discrete values.", format = "simple")`
@@
 
-### K1K2 using FerryBox pCO2 and at in situ
-```{r impact of constants using FerryBox pCO2 and at in situ, echo=FALSE, warning=FALSE, message=FALSE}
+### K1K2 using pCO2 and AT
+```{r impact of constants using FerryBox pCO2 and at, echo=FALSE, warning=FALSE, message=FALSE}
 tmp <- d_all %>% 
   tidyr::drop_na(pco2_fb, at, sal_fb, temp_fb) %>% 
-  dplyr::select(datetime, ph_s_dur_temp_4, pco2_fb, at, sal_fb, temp_fb)
+  dplyr::select(datetime, ph_s_dur_temp_4_l, ph_s_dur_temp_4_s20,
+                ph_s_dur_temp_4_p18, ph_s_dur_temp_4_m02, pco2_fb, at, sal_fb, temp_fb) %>% 
+# This is an important adjustement for pco2_fb on 2019-06-07 09:00:00
+# it is too high compared with ph_s_dur.
+Looking at the dygraph suggests that there has been a peak just before that time and that the values were coming back down.
+This is this in accordance with pco2_calc_fb calculated from
+dplyr::mutate(pco2_fb = ifelse(datetime == as.POSIXct("2019-06-07 09:00:00"), 203, pco2_fb))
 # Using Lueker  
@@
 # prepare tibble to compare calculated pH and spec pH
-tmp2 <- tibble(datetime = tmp$datetime, ph_s_dur_temp_4 = tmp$ph_s_dur_temp_4, 
+tmp2 <- tibble(datetime = tmp$datetime, ph_s_dur_temp_4_l = tmp$ph_s_dur_temp_4_l, 
+               ph_s_dur_temp_4_s20 = tmp$ph_s_dur_temp_4_s20,
+               ph_s_dur_temp_4_p18 = tmp$ph_s_dur_temp_4_p18,
+               ph_s_dur_temp_4_m02 = tmp$ph_s_dur_temp_4_m02, 
                pH_l = carb_l$pH, pH_s = carb_s$pH, 
                pH_p = carb_p$pH, pH_m = carb_m$pH, temp_fb = tmp$temp_fb) %>% 
-  tidyr::drop_na(ph_s_dur_temp_4)
+  tidyr::drop_na(ph_s_dur_temp_4_l)
 # summary of differences
-lueker <- as.numeric(summary(tmp2$ph_s_dur_temp_4 - tmp2$pH_l))
-sulpis <- as.numeric(summary(tmp2$ph_s_dur_temp_4 - tmp2$pH_s))
-papadimitriou <- as.numeric(summary(tmp2$ph_s_dur_temp_4 - tmp2$pH_p))
-millero2002 <- as.numeric(summary(tmp2$ph_s_dur_temp_4 - tmp2$pH_m))
+lueker <- as.numeric(summary(tmp2$ph_s_dur_temp_4_l - tmp2$pH_l))
+sulpis <- as.numeric(summary(tmp2$ph_s_dur_temp_4_s20 - tmp2$pH_s))
+papadimitriou <- as.numeric(summary(tmp2$ph_s_dur_temp_4_p18 - tmp2$pH_p))
+millero2002 <- as.numeric(summary(tmp2$ph_s_dur_temp_4_m02 - tmp2$pH_m))
 diff_table <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), lueker, sulpis, papadimitriou, millero2002)
 # make plots
-p1 <- ggreg(xdata = tmp2$ph_s_dur_temp_4, ydata = tmp2$pH_l, type = "MA", plot = TRUE, 
+p1 <- ggreg(xdata = tmp2$ph_s_dur_temp_4_l, ydata = tmp2$pH_l, type = "MA", plot = TRUE, 
             title = "Lueker vs measured", subtitle = "both pH normalized at 4°C",
-            xlab = "Spectrophotometric pH measured @ 4°C",
+            xlab = "Spectrophotometric pH normalized @ 4°C",
             ylab = "pH @ 4°C calculated (pCO2+AT) with Lueker") +
@@
   coord_fixed(ratio = 1)
-p2 <- ggreg(xdata = tmp2$ph_s_dur_temp_4, ydata = tmp2$pH_s, type = "MA", plot = TRUE, 
+p2 <- ggreg(xdata = tmp2$ph_s_dur_temp_4_l, ydata = tmp2$pH_s, type = "MA", plot = TRUE, 
             title = "Sulpis vs measured", subtitle = "both pH normalized at 4°C",
-            xlab = "Spectrophotometric pH measured @ 4°C",
+            xlab = "Spectrophotometric pH normalized @ 4°C",
             ylab = "pH @ 4°C calculated (pCO2+AT) with Sulpis")  +
@@
 p3 <- tmp2 %>% 
-  dplyr::mutate(delta_lueker = tmp2$ph_s_dur_temp_4 - tmp2$pH_l, 
-                delta_sulpis = tmp2$ph_s_dur_temp_4 - tmp2$pH_s, 
-                delta_papadimitriou = tmp2$ph_s_dur_temp_4 - tmp2$pH_p, 
-                delta_millero2002 = tmp2$ph_s_dur_temp_4 - tmp2$pH_m) %>% 
+  dplyr::mutate(delta_lueker = tmp2$ph_s_dur_temp_4_l - tmp2$pH_l, 
+                delta_sulpis = tmp2$ph_s_dur_temp_4_s20 - tmp2$pH_s, 
+                delta_papadimitriou = tmp2$ph_s_dur_temp_4_p18 - tmp2$pH_p, 
+                delta_millero2002 = tmp2$ph_s_dur_temp_4_m02 - tmp2$pH_m) %>% 
   dplyr::select(-starts_with("ph_"), -datetime) %>% 
@@
 p <- (p1 + p2) / p3
-ggsave(filename = "figures/k1k2_all.png", plot = p, width = 25, height = 20, units = "cm")
-ggsave(filename = "figures/k1k2_temperature.png", plot = p3, width = 25, height = 20, units = "cm")
-```
-```{r save elements for k1k2 report, echo=FALSE, message= FALSE, warning=FALSE}
-k1k2 <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
+ggsave(filename = "figures/k1k2_all_pco2_at.png", plot = p, width = 25, height = 20, units = "cm")
+
+# save elements for k1k2 report
+k1k2_pco2_at <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
              errors_pco2_at = errors_pco2_at, diff_table = diff_table, 
              diff_ls_quant = diff_ls_quant)
-save(k1k2, file="reports/k1k2_data.RData")
-```
-
-The discrete values of pCO2, salinity and temperature in the FerryBox and in situ AT were used to calculate pH from measured pCO2 and AT using the formulations for K1 and K2 of Lueker et al.
+save(k1k2_pco2_at, file="reports/k1k2_pco2_at.RData")
+```
+
+The discrete values of pCO2, AT, salinity and temperature in the FerryBox were used to calculate pH using the formulations for K1 and K2 of Lueker et al.
 (2000) and Sulpis et al.
 (2020).
-Note that this cannot be done with in situ AT and CT because spectrophotometric pH in situ is not at a fixed depth.
-
-The differences induced by the choice of the carbonic acid constants is:
-
-- small for pH (`r round(diff_ls_quant[4, 2], digits = 3)` pH units on average; ; median is `r round(diff_ls_quant[3, 2], digits = 3)`) compared with the uncertainty calculated with seacarb (`r round(const_choice[1, 6], digits = 3)`.
+The differences induced by the choice of the carbonic acid constants are:
+
+- large for pH (`r round(diff_ls_quant[4, 2], digits = 3)` pH units on average; ; median is `r round(diff_ls_quant[3, 2], digits = 3)`) compared with the uncertainty calculated with seacarb (`r round(const_choice[1, 6], digits = 3)`).
 In general, pH is higher with Sulpis than with Lueker.
-- very good for CT (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on average; always lower with Sulpis than with Lueker) compared with the uncertainty calculated with seacarb (`r round(const_choice[1, 8], digits = 1)`)
+- small for CT (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on average; always lower with Sulpis than with Lueker) compared with the uncertainty calculated with seacarb (`r round(const_choice[1, 8], digits = 1)`)
 - negligible for OmegaAragonite
@@
 All pH values were normalized to a temperature of 4°C.
-The absolute differences are large, up to `r round(max(abs(diff_table[, 2:5])), digits=3)` pH units.
-On average, both formulations overestimate spectrophotometric pH.
-The calculated pH closer to measured pH is using the formulation of Lueker et al.
-(2020) with a mean difference of `r round(max(diff_table[4, 2:5]), digits=3)` pH units.
-This difference is twice larger than the uncertainty for pH calculated from pCO2 and AT according to seacarb (`r round(errors_pco2_at$pH, digits=3)`).
+The absolute differences are generally large, up to `r round(max(abs(diff_table[, 2:5])), digits=3)` pH units.
+In general, all formulations overestimate spectrophotometric pH.
+pH calculated using the formulation of Papadimitriou et al.
+(2018) is closer to measured pH, with a mean difference of `r round(diff_table[4, 4], digits=3)` pH units.
+This difference is `r abs(round(diff_table[4, 4]/errors_pco2_at$pH, digits=1))` times larger than the uncertainty for pH calculated from pCO2 and AT according to seacarb (`r round(errors_pco2_at$pH, digits=3)`).
 `r knitr::kable(diff_table, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "simple")`
-`r include_graphics("figures/lueker-sulpis.png")`
+`r include_graphics("figures/k1k2_all_pco2_at.png")`
+
+### K1K2 using CT and AT
+```{r impact of constants using FerryBox ct and at, echo=FALSE, warning=FALSE, message=FALSE}
+tmp <- d_all %>% 
+  tidyr::drop_na(ct, at, sal_fb, temp_fb) %>% 
+  dplyr::select(datetime, ph_s_dur_temp_4_l, ph_s_dur_temp_4_s20,
+                ph_s_dur_temp_4_p18, ph_s_dur_temp_4_m02, ct, at, sal_fb, temp_fb)
+# Using Lueker  
+carb_l2 <- carb(flag = 15, var1 = tmp$at * 1e-6, var2 = tmp$ct * 1e-6, S = tmp$sal_fb, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Lueker-derived pH at 4°C
+carb_l2$pH <- pHinsi(pH = carb_l2$pH, ALK = carb_l2$ALK, Tinsi = 4, Tlab = carb_l2$T, Pinsi = 0, 
+                         S = carb_l2$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# Using Sulpis
+  carb_s2 <- carb(flag = 15, var1 = tmp$at * 1e-6, var2 = tmp$ct * 1e-6, S = tmp$sal_fb, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Sulpis-derived pH at 4°C
+carb_s2$pH <- pHinsi(pH = carb_s2$pH, ALK = carb_s2$ALK, Tinsi = 4, Tlab = carb_s2$T, Pinsi = 0, 
+                         S = carb_s2$S, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# Using Papadimitriou
+carb_p2 <- carb(flag = 15, var1 = tmp$at * 1e-6, var2 = tmp$ct * 1e-6, S = tmp$sal_fb, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Papadimitriou-derived pH at 4°C
+carb_p2$pH <- pHinsi(pH = carb_p2$pH, ALK = carb_p2$ALK, Tinsi = 4, Tlab = carb_p2$T, Pinsi = 0, 
+                         S = carb_p2$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# Using Millero et al. (2002)
+carb_m2 <- carb(flag = 15, var1 = tmp$at * 1e-6, var2 = tmp$ct * 1e-6, S = tmp$sal_fb, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Millero et al. (2002)-derived pH at 4°C
+carb_m2$pH <- pHinsi(pH = carb_m2$pH, ALK = carb_m2$ALK, Tinsi = 4, Tlab = carb_m2$T, Pinsi = 0, 
+                         S = carb_m2$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# calculate difference Lueker - Sulpis
+diff_ls2 <- as_tibble(carb_l2 - carb_s2) %>% 
+  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite)
+# calculate descriptive statistics Lueker - Sulpis
+diff_ls_quant <- tibble(pH = as.numeric(summary(diff_ls2$delta_ph)),
+                        CT = as.numeric(summary(diff_ls2$delta_ct * 1e6)),
+                        OmegaAragonite = as.numeric(summary(diff_ls2$delta_OmegaAragonite))) %>%
+  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
+# prepare tibble to compare calculated pH and spec pH
+tmp2 <- tibble(datetime = tmp$datetime, ph_s_dur_temp_4_l = tmp$ph_s_dur_temp_4_l, 
+               ph_s_dur_temp_4_s20 = tmp$ph_s_dur_temp_4_s20,
+               ph_s_dur_temp_4_p18 = tmp$ph_s_dur_temp_4_p18,
+               ph_s_dur_temp_4_m02 = tmp$ph_s_dur_temp_4_m02, 
+               pH_l2 = carb_l2$pH, pH_s2 = carb_s2$pH, 
+               pH_p2 = carb_p2$pH, pH_m2 = carb_m2$pH, temp_fb = tmp$temp_fb) %>% 
+  tidyr::drop_na(ph_s_dur_temp_4_l)
+# summary of differences
+lueker <- as.numeric(summary(tmp2$ph_s_dur_temp_4_l - tmp2$pH_l2))
+sulpis <- as.numeric(summary(tmp2$ph_s_dur_temp_4_s20 - tmp2$pH_s2))
+papadimitriou <- as.numeric(summary(tmp2$ph_s_dur_temp_4_p18 - tmp2$pH_p2))
+millero2002 <- as.numeric(summary(tmp2$ph_s_dur_temp_4_m02 - tmp2$pH_m2))
+diff_table <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), lueker, sulpis, papadimitriou, millero2002)
+# make plots
+p1 <- ggreg(xdata = tmp2$ph_s_dur_temp_4_l, ydata = tmp2$pH_l2, type = "MA", plot = TRUE, 
+            title = "Lueker vs measured", subtitle = "both pH normalized at 4°C",
+            xlab = "Spectrophotometric pH normalized @ 4°C",
+            ylab = "pH @ 4°C calculated (AT+CT) with Lueker") +
+  lims(x = c(8, 8.4), y = c(8, 8.4)) +
+  theme(plot.title = element_text(size = 10),
+        axis.text = element_text(size = 10)) +
+  coord_fixed(ratio = 1)
+p2 <- ggreg(xdata = tmp2$ph_s_dur_temp_4_l, ydata = tmp2$pH_s2, type = "MA", plot = TRUE, 
+            title = "Sulpis vs measured", subtitle = "both pH normalized at 4°C",
+            xlab = "Spectrophotometric pH normalized @ 4°C",
+            ylab = "pH @ 4°C calculated (AT+CT) with Sulpis")  +
+  lims(x = c(8, 8.4), y = c(8, 8.4)) +
+  theme(plot.title = element_text(size = 10),
+        axis.text = element_text(size = 10)) +
+  coord_fixed(ratio = 1)
+p3 <- tmp2 %>% 
+  dplyr::mutate(delta_lueker = tmp2$ph_s_dur_temp_4_l - tmp2$pH_l2, 
+                delta_sulpis = tmp2$ph_s_dur_temp_4_s20 - tmp2$pH_s2, 
+                delta_papadimitriou = tmp2$ph_s_dur_temp_4_p18 - tmp2$pH_p2, 
+                delta_millero2002 = tmp2$ph_s_dur_temp_4_m02 - tmp2$pH_m2) %>% 
+  dplyr::select(-starts_with("ph_"), -datetime) %>% 
+  tidyr::pivot_longer(!temp_fb, names_to = "delta", values_to = "diff") %>% 
+  ggplot(aes(x = temp_fb, y = diff, col = delta)) +
+  geom_point() + geom_line() +
+  labs(x = "Ferrybox temperature (°C)", y = "Spec pH - calculated pH (units)") +
+  theme(legend.title = element_blank())
+p <- (p1 + p2) / p3
+ggsave(filename = "figures/k1k2_all_at_ct.png", plot = p, width = 25, height = 20, units = "cm")
+
+# save elements for k1k2 report
+k1k2_at_ct <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
+             errors_pco2_at = errors_pco2_at, diff_table = diff_table, 
+             diff_ls_quant = diff_ls_quant)
+save(k1k2_at_ct, file="reports/k1k2_at_ct.RData")
+```
+Here we compare pH measured spectrophotometrically with pH calculated from AT and CT using various formulations of K1 and K2.
+All pH values were normalized to a temperature of 4°C.
+The absolute differences are generally large, up to `r round(max(abs(diff_table[, 2:5])), digits=3)` pH units.
+In general, all formulations overestimate spectrophotometric pH.
+pH calculated using the formulation of Papadimitriou et al.
+(2018) is closer to measured pH, with a mean difference of `r round(diff_table[4, 4], digits=3)` pH units.
+This difference is `r abs(round(diff_table[4, 4]/errors_at_ct$pH, digits=1))` times larger than the uncertainty for pH calculated from AT and CT according to seacarb (`r round(errors_at_ct$pH, digits=3)`).
+
+`r knitr::kable(diff_table, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "simple")`
+`r include_graphics("figures/k1k2_all_at_ct.png")`
 
@@
 pangaea <- as_tibble(d_all) %>% 
-  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, phcalc_fb, pco2_fb, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
+  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
   dplyr::rename(pressure = pressure_insitu_ctd,
@@
                 ph_dur = ph_dur_corr,
-                ph_calc = phcalc_fb
+                ph_calc = ph_calc_fb
                 )
@@
 - **2018-04-17**: seaFET #1005 was changed on the REMOS and seaFET #007 (from Villefranche) was installed.
-Continuous mode with external power supply was set and internal pack of baterries was removed.
+Continuous mode with external power supply was set and internal pack of bateries was removed.
 Old seaFET will be brought back to France with Samir.

### 2021-04-01 awipev-CO2.Rmd
refined K1K2

@@
 millero2002 <- as.numeric(summary(tmp2$ph_s_dur_temp_4_m02 - tmp2$pH_m))
-diff_table <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), lueker, sulpis, papadimitriou, millero2002)
+diff_table_pco2_at <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), lueker, sulpis, papadimitriou, millero2002)
 # make plots
@@
 k1k2_pco2_at <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
-             errors_pco2_at = errors_pco2_at, diff_table = diff_table, 
+             errors_pco2_at = errors_pco2_at, diff_table_pco2_at = diff_table_pco2_at, 
              diff_ls_quant = diff_ls_quant)
@@
 All pH values were normalized to a temperature of 4°C.
-The absolute differences are generally large, up to `r round(max(abs(diff_table[, 2:5])), digits=3)` pH units.
+The absolute differences are generally large, up to `r round(max(abs(diff_table_pco2_at[, 2:5])), digits=3)` pH units.
 In general, all formulations overestimate spectrophotometric pH.
 pH calculated using the formulation of Papadimitriou et al.
-(2018) is closer to measured pH, with a mean difference of `r round(diff_table[4, 4], digits=3)` pH units.
-This difference is `r abs(round(diff_table[4, 4]/errors_pco2_at$pH, digits=1))` times larger than the uncertainty for pH calculated from pCO2 and AT according to seacarb (`r round(errors_pco2_at$pH, digits=3)`).
-`r knitr::kable(diff_table, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "simple")`
+(2018) is closer to measured pH, with a mean difference of `r round(diff_table_pco2_at[4, 4], digits=3)` pH units.
+This difference is `r abs(round(diff_table_pco2_at[4, 4]/errors_pco2_at$pH, digits=1))` times larger than the uncertainty for pH calculated from pCO2 and AT according to seacarb (`r round(errors_pco2_at$pH, digits=3)`).
+`r knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "simple")`
 `r include_graphics("figures/k1k2_all_pco2_at.png")`
@@
 millero2002 <- as.numeric(summary(tmp2$ph_s_dur_temp_4_m02 - tmp2$pH_m2))
-diff_table <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), lueker, sulpis, papadimitriou, millero2002)
+diff_table_at_ct <- tibble(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), lueker, sulpis, papadimitriou, millero2002)
 # make plots
@@
 # save elements for k1k2 report
-k1k2_at_ct <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
-             errors_pco2_at = errors_pco2_at, diff_table = diff_table, 
-             diff_ls_quant = diff_ls_quant)
+k1k2_at_ct <- list(errors_at_ct = errors_at_ct,
+                   diff_table_at_ct = diff_table_at_ct)
 save(k1k2_at_ct, file="reports/k1k2_at_ct.RData")
@@
 All pH values were normalized to a temperature of 4°C.
-The absolute differences are generally large, up to `r round(max(abs(diff_table[, 2:5])), digits=3)` pH units.
+The absolute differences are generally large, up to `r round(max(abs(diff_table_at_ct[, 2:5])), digits=3)` pH units.
 In general, all formulations overestimate spectrophotometric pH.
 pH calculated using the formulation of Papadimitriou et al.
-(2018) is closer to measured pH, with a mean difference of `r round(diff_table[4, 4], digits=3)` pH units.
-This difference is `r abs(round(diff_table[4, 4]/errors_at_ct$pH, digits=1))` times larger than the uncertainty for pH calculated from AT and CT according to seacarb (`r round(errors_at_ct$pH, digits=3)`).
-
-`r knitr::kable(diff_table, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "simple")`
+(2018) is closer to measured pH, with a mean difference of `r round(diff_table_at_ct[4, 4], digits=3)` pH units.
+This difference is `r abs(round(diff_table_at_ct[4, 4]/errors_at_ct$pH, digits=1))` times the uncertainty for pH calculated from AT and CT according to seacarb (`r round(errors_at_ct$pH, digits=3)`).
+The differences found with the other formulations are, on average, slightly lower than the uncertainty for pH calculated from AT and CT according to seacarb.
+
+`r knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "simple")`
 `r include_graphics("figures/k1k2_all_at_ct.png")`

### 2021-04-01 awipev-CO2.Rmd
cleaned up unnecessary packages

@@
 library(tidyverse)
-if (!require("robfilter")) install.packages("robfilter")
-library("robfilter")
+# if (!require("robfilter")) install.packages("robfilter")
+# library("robfilter")
 if (!require("seacarb")) install.packages("seacarb")
@@
 library("gridExtra")
-if (!require("reshape2")) install.packages("reshape2")
-library("reshape2")
+# if (!require("reshape2")) install.packages("reshape2")
+# library("reshape2")
 if (!require("lubridate")) install.packages("lubridate")
 library("lubridate")
-if (!require("lmtest")) install.packages("lmtest")
-library("lmtest")
+# if (!require("lmtest")) install.packages("lmtest")
+# library("lmtest")
 if (!require("grid")) install.packages("grid")
@@
 library("xts")
-if (!require("seismicRoll")) install.packages("seismicRoll")
-library("seismicRoll")
+# if (!require("seismicRoll")) install.packages("seismicRoll")
+# library("seismicRoll")
 if (!require("scales")) install.packages("scales")
 library("scales")
-if (!require("cowplot")) install.packages("cowplot")
-library(cowplot)
-if (!require("htmlwidgets")) install.packages("htmlwidgets")
-library("htmlwidgets")
-if (!require("hms")) install.packages("hms")
-library("hms")
-if (!require("ragg")) install.packages("ragg")
-library("ragg")
+# if (!require("cowplot")) install.packages("cowplot")
+# library(cowplot)
+# if (!require("htmlwidgets")) install.packages("htmlwidgets")
+# library("htmlwidgets")
+# if (!require("hms")) install.packages("hms")
+# library("hms")
+# if (!require("ragg")) install.packages("ragg")
+# library("ragg")
 if (!require("skimr")) install.packages("skimr")
@@
 #### plot
-kk <- melt(calib_spectro, id.vars="deployment_sf")
+kk <- tidyr::pivot_longer(calib_spectro, cols = starts_with("E0"), names_to = "variable", values_to = "value")
 p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
-  facet_grid(variable~., scales="free_y") + theme_bw() +
+  facet_grid(variable ~ ., scales="free_y") + theme_bw() +
   scale_colour_discrete(guide="none")

### 2021-04-02 awipev-CO2.Rmd
removed use of cowplot

@@
 
-p <- cowplot::plot_grid(p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m, ncol = 1)
-pngfile <- "figures/air-sea_CO2_flux.png"
-ggsave(
-  pngfile, 
-  p, 
-  device = agg_png, 
-  width = 6.6, height = 10, units = "cm", res = 300,
-  scaling = 0.4
-)
-rm(p_f_air_sea)
-knitr::include_graphics(pngfile)
+p <- p_f_air_sea / p_f_air_sea_d / p_f_air_sea_m
+ggsave(filename = "figures/air-sea_CO2_flux.png", plot = p, width = 20, units = "cm")
+#p <- cowplot::plot_grid(p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m, ncol = 1)
+#pngfile <- "figures/air-sea_CO2_flux.png"
+# ggsave(
+#   pngfile, 
+#   p, 
+#   device = agg_png, 
+#   width = 6.6, height = 10, units = "cm", res = 300,
+#   scaling = 0.4
+# )
+knitr::include_graphics("figures/air-sea_CO2_flux.png")
+#rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
 ```

### 2021-04-06 awipev-CO2.Rmd
Minor changes

@@
 
-## Impact K1K2  {.tabset .tabset-pills}
-### Lueker vs Sulpis
+## K1K2  {.tabset .tabset-pills}
 ```{r impact of constants discrete, echo=FALSE, warning=FALSE, message=FALSE}
@@
 ```
-Using the following using mean discrete values:
-`r knitr::kable(mean_discrete, digits = c(1, 1, 0, 1, 1), caption = "Mean discrete values.", format = "simple")`
-
-The differences are:
-`r knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3, 3, 1, 1, 1), caption = "Lueker minus Sulpis. e indicates typical errors estimated with seacarb.", format = "simple")`
 
@@
 ```
-
+#### Difference Lueker vs Sulpis
+Using the following using mean discrete values:
+`r knitr::kable(mean_discrete, digits = c(1, 1, 0, 1, 1), caption = "Mean discrete values.", format = "simple")`
+
+The differences are:
+`r knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3, 3, 1, 1, 1), caption = "Lueker minus Sulpis. e indicates typical errors estimated with seacarb.", format = "simple")`
+
+#### Difference between all formulations and measured pH
 The discrete values of pCO2, AT, salinity and temperature in the FerryBox were used to calculate pH using the formulations for K1 and K2 of Lueker et al.
@@
 ```
+#### Difference Lueker vs Sulpis
+Using the following using mean discrete values:
+`r knitr::kable(mean_discrete, digits = c(1, 1, 0, 1, 1), caption = "Mean discrete values.", format = "simple")`
+
+The differences are:
+`r knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3, 3, 1, 1, 1), caption = "Lueker minus Sulpis. e indicates typical errors estimated with seacarb.", format = "simple")`
+
+#### Difference between all formulations and measured pH
 Here we compare pH measured spectrophotometrically with pH calculated from AT and CT using various formulations of K1 and K2.

### 2021-04-07 paper.Rmd
revised according to new variable names

@@
                 quarter = quarter(datetime)) %>%
-  dplyr::rename(pco2_contros = pco2_corr) %>% 
+  #dplyr::rename(pco2_contros = pco2_corr) %>% 
   replace(., is.na(.), NA) # replace NaN by NA everywhere
@@
 d_ts <- d %>%
-  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_contros,
+  dplyr::select(datetime, temp_insitu_11m, sal_fb, par_air, pco2_fb,
                 pHint_tot_sf_9m, ph_s_sf_temp_insi, at_calc, at) #%>%
@@
   Mytheme(size_labs = 8)
-ts_sal_py <- ggplotly(ts_sal,dynamicTicks = TRUE)
-filename.html <- paste0(path_fig, "ts_sal_py.html")
-saveWidget(ts_sal_py, filename.html, selfcontained = T, libdir = "lib")
+# ts_sal_py <- ggplotly(ts_sal,dynamicTicks = TRUE)
+# filename.html <- paste0(path_fig, "ts_sal_py.html")
+# saveWidget(ts_sal_py, filename.html, selfcontained = T, libdir = "lib")
 

### 2021-04-07 awipev-CO2.Rmd
Adjustements K1K2 and impacts of nutrients

@@
 
-## Impact of nutrients   {.tabset .tabset-pills}
+## Nutrients   {.tabset .tabset-pills}
 ```{r impact of nutrients, echo=FALSE, warning=FALSE, message=FALSE}
@@
 diff_Si_1a <- carb_Si_1[2,] - carb_Si_1[3,] # diff between no Si and max Si
-
-# then check impacts of min and max nutrient values using AT-DIC pair
+# then check impacts of O, min and max nutrient values using AT-DIC pair
 carb_po4_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
@@
 diff_Si_1b <- carb_Si_2[2,] - carb_Si_2[3,] # diff between no Si and max Si
+# then check impacts of O, max PO4 and NO3 values using pCO2 and AT as well as AT-DIC pair
+carb_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = c(0, max(d_all$po4/1e6, na.rm=TRUE)), Sit = c(0, max(d_all$si/1e6, na.rm=TRUE)),
+                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+carb_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+                 Pt = c(0, max(d_all$po4/1e6, na.rm=TRUE)), Sit = c(0, max(d_all$si/1e6, na.rm=TRUE)),
+                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+diff_max_0a <- carb_1[1,] - carb_1[2,] # pco2-AT: diff between (0 PO4 and Si) and (max PO4 and Si)
+diff_max_0b <- carb_2[1,] - carb_2[2,] # AT-CT: diff between (0 PO4 and Si) and (max PO4 and Si)
 
@@
 #)
-nuts_table <- bind_rows(diff_po4_0a, diff_Si_0a, diff_po4_0b, diff_Si_0b) %>% 
-  dplyr::mutate(flag = c("pCO2 and ALK", "pCO2 and ALK", "ALK and DIC", "ALK and DIC"),
+nuts_table <- bind_rows(diff_po4_0a, diff_Si_0a, diff_po4_0b, diff_Si_0b, diff_max_0a, diff_max_0b) %>% 
+  dplyr::mutate(flag = c("pCO2 and ALK", "pCO2 and ALK", "ALK and DIC", "ALK and DIC", "ALK and DIC", "ALK and DIC"),
                 nutrients = c("No PO4-max PO4", "No Si-max Si", "No PO4-max PO4", 
-                              "No Si-max Si")) %>% 
+                              "No Si-max Si", "No nuts-max nuts", "No nuts-max nuts")) %>% 
   dplyr::select(flag, nutrients, pH, pCO2, DIC, OmegaAragonite)
@@
 
-#### Difference between all formulations and measured pH
 The discrete values of pCO2, AT, salinity and temperature in the FerryBox were used to calculate pH using the formulations for K1 and K2 of Lueker et al.
@@
 
+#### Difference between all formulations and measured pH
 `r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis using discrete Ferrybox data.", format = "simple")`
@@
 #### Difference between all formulations and measured pH
+`r knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "simple")`
+`r include_graphics("figures/k1k2_all_at_ct.png")`
+
 Here we compare pH measured spectrophotometrically with pH calculated from AT and CT using various formulations of K1 and K2.
@@
 The differences found with the other formulations are, on average, slightly lower than the uncertainty for pH calculated from AT and CT according to seacarb.
-
-`r knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "simple")`
-`r include_graphics("figures/k1k2_all_at_ct.png")`
 
@@
 
+## Miscelaneous
+###Save all
 ```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
@@
 
+### Whole time series plot
 ```{r whole time series plot, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
@@
 
+### Whole time series monthly box plots and stats
 ```{r whole time series monthly box plots and stats, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
@@
 gc() #garbage collection
-
 ```

### 2021-04-09 awipev-CO2.Rmd
read new file with depth_complete

@@
   arrange(datetime)
+# read a file provided by Philipp for reconstructing missing pressure data
+svl_remos_depth <- tibble(
+  readRDS(file = paste0(
+    path,
+    "fb_data/svl_remos_depth.rds"
+  )))
+d_hour <- dplyr::left_join(d_hour, svl_remos_depth, by = 'datetime') %>% 
+  dplyr::select(-adcp_fill, -ctd_fill)
 d_all <- as_tibble(d_hour) #d_all will be the merger
@@
 nuts_table <- bind_rows(diff_po4_0a, diff_Si_0a, diff_po4_0b, diff_Si_0b, diff_max_0a, diff_max_0b) %>% 
-  dplyr::mutate(flag = c("pCO2 and ALK", "pCO2 and ALK", "ALK and DIC", "ALK and DIC", "ALK and DIC", "ALK and DIC"),
+  dplyr::mutate(flag = c("pCO2 and ALK", "pCO2 and ALK", "ALK and DIC", "ALK and DIC", "pCO2 and AT", "ALK and DIC"),
                 nutrients = c("No PO4-max PO4", "No Si-max Si", "No PO4-max PO4", 
@@
 ```
-`r knitr::kable(nuts_table, digits = c(1, 1, 4, 2, 4, 3), caption = "Impact of PO4 and Si.", format = "simple")`
+`r knitr::kable(nuts_table, digits = c(1, 1, 4, 2, 7, 3), caption = "Impact of PO4 and Si.", format = "simple")`
 

### 2021-04-11 awipev-CO2.Rmd
moved backwards

@@
   arrange(datetime)
-# read a file provided by Philipp for reconstructing missing pressure data
+# read a file provided by Philipp on 2021-04-09 which fills most gaps of pressure data
+# depth_complete replaces all other depth and pressure variables
 svl_remos_depth <- tibble(
@@
 d_hour <- dplyr::left_join(d_hour, svl_remos_depth, by = 'datetime') %>% 
-  dplyr::select(-adcp_fill, -ctd_fill)
+  dplyr::select(-adcp_fill, -ctd_fill) %>% 
+  dplyr::rename(depth = depth_complete)
+# check_plot <- d_hour %>% 
+#   ggplot() + geom_point(aes(x=datetime, y=depth, col='blue', alpha = 0.7)) +
+#   geom_point(aes(x=datetime, y=depth, col='red', alpha = 0.3))
 d_all <- as_tibble(d_hour) #d_all will be the merger
@@
   dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
-  dplyr::mutate(depth = ifelse( # create new variable depth
-      pressure_insitu_ctd <= 2,
+  dplyr::mutate(depth_group = ifelse( # create new variable depth
+      depth <= 2,
       1,
       ifelse(
-        pressure_insitu_ctd > 2 & pressure_insitu_ctd <= 4,
+        depth > 2 & depth <= 4,
         3,
         ifelse(
-          pressure_insitu_ctd > 4 & pressure_insitu_ctd <= 6,
+          depth > 4 & depth <= 6,
           5,
           ifelse(
-            pressure_insitu_ctd > 6 & pressure_insitu_ctd <= 8,
+            depth > 6 & depth <= 8,
             7,
-            ifelse(pressure_insitu_ctd > 8, 10, NA)
+            ifelse(depth > 8, 10, NA)
           )
@@
                      temp_insitu_ctd,
-                     pressure_insitu_ctd
+                     depth
                    )
@@
                          ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, 
-                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
+                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, 
                          S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
@@
                          ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
-                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
+                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, 
                          S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
@@
   dplyr::mutate(pHint_tot_sf = seafet_calib$pHint_tot_sf) %>%
-  dplyr::mutate(pHint_tot_sf_1m = ifelse(pressure_insitu_ctd > 0 & pressure_insitu_ctd < 2, pHint_tot_sf, NA),
-                pHint_tot_sf_3m = ifelse(pressure_insitu_ctd >= 2 & pressure_insitu_ctd < 4, pHint_tot_sf, NA),
-                pHint_tot_sf_5m = ifelse(pressure_insitu_ctd >= 4 & pressure_insitu_ctd < 6, pHint_tot_sf, NA),
-                pHint_tot_sf_7m = ifelse(pressure_insitu_ctd >= 6 & pressure_insitu_ctd < 8, pHint_tot_sf, NA),
-                pHint_tot_sf_9m = ifelse(pressure_insitu_ctd >= 8 , pHint_tot_sf, NA),
+  dplyr::mutate(pHint_tot_sf_1m = ifelse(depth > 0 & depth < 2, pHint_tot_sf, NA),
+                pHint_tot_sf_3m = ifelse(depth >= 2 & depth < 4, pHint_tot_sf, NA),
+                pHint_tot_sf_5m = ifelse(depth >= 4 & depth < 6, pHint_tot_sf, NA),
+                pHint_tot_sf_7m = ifelse(depth >= 6 & depth < 8, pHint_tot_sf, NA),
+                pHint_tot_sf_9m = ifelse(depth >= 8 , pHint_tot_sf, NA),
                 depth_discrete = case_when(
@@
 #                          ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
-#                          Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
+#                          Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, 
 #                          S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
@@
 # range <- d_all %>%
-#   dplyr::mutate(pH_range_more_6m = ifelse(pressure_insitu_ctd > 6, pHint_tot_sf, NA)) %>%
+#   dplyr::mutate(pH_range_more_6m = ifelse(depth > 6, pHint_tot_sf, NA)) %>%
 #   group_by(montht) %>%
@@
 # no_pressure <- d_all %>% 
-#   dplyr::select(datetime, pressure_insitu_ctd, pHint_tot_sf) %>% 
-#   dplyr::filter(is.na(pressure_insitu_ctd) & !is.na(pHint_tot_sf))
+#   dplyr::select(datetime, depth, pHint_tot_sf) %>% 
+#   dplyr::filter(is.na(depth) & !is.na(pHint_tot_sf))
 # readr::write_csv(x = no_pressure, path=paste0(path,"/fb_awipev-co2_server/ny-alesund/data//no_pressure.csv"))
@@
 tmp <- d_all %>% 
-  dplyr::select(montht, sal_insitu_ctd, depth) %>%
-  group_by(depth, montht)
+  dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
+  group_by(depth_group, montht)
 p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = sal_insitu_ctd)) +
+  ggplot(aes(x=as.factor(depth_group), y = sal_insitu_ctd)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
 
-summary(aov(tmp$sal_insitu_ctd ~ tmp$depth * tmp$montht))
+summary(aov(tmp$sal_insitu_ctd ~ tmp$depth_group * tmp$montht))
 
@@
 tmp <- d_all %>% 
-  dplyr::select(montht, sal_insitu_ctd, depth) %>%
-  dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
+  dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
+  dplyr::mutate(depth = as.factor(ifelse(depth_group == 1 | depth_group == 3, 2, depth_group))) %>% 
   dplyr::filter(depth == 2 | depth == 10)
@@
 ```
+
 Using the medians because data are missing.
@@
 pangaea <- as_tibble(d_all) %>% 
-  dplyr::select(datetime, pressure_insitu_ctd, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
-  dplyr::rename(pressure = pressure_insitu_ctd,
+  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
+  dplyr::rename(pressure = depth,
                 s_insitu = sal_insitu_ctd,
@@
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(aes(x = datetime, y = pHint_tot_sf, col = pressure_insitu_ctd), alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(aes(x = datetime, y = pHint_tot_sf, col = depth), alpha=alpha, na.rm=TRUE, size=size_point) + 
   scale_colour_gradient(name = "Depth (m)", low = "#56B1F7", high = "#132B43") + # reverse colors

### 2021-04-13 awipev-CO2.Rmd
back to a functional version

@@
   dplyr::mutate(depth_group = ifelse( # create new variable depth
-      depth <= 2,
+      pressure_insitu_ctd <= 2,
       1,
       ifelse(
-        depth > 2 & depth <= 4,
+        pressure_insitu_ctd > 2 & depth <= 4,
         3,
         ifelse(
-          depth > 4 & depth <= 6,
+          pressure_insitu_ctd > 4 & depth <= 6,
           5,
           ifelse(
-            depth > 6 & depth <= 8,
+            pressure_insitu_ctd > 6 & depth <= 8,
             7,
-            ifelse(depth > 8, 10, NA)
+            ifelse(pressure_insitu_ctd > 8, 10, NA)
           )
@@
                      temp_insitu_ctd,
-                     depth
+                     pressure_insitu_ctd
                    )
@@
                          ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, 
-                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, 
+                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
                          S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
@@
                          ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
-                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, 
+                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$pressure_insitu_ctd/10, 
                          S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
@@
   dplyr::mutate(pHint_tot_sf = seafet_calib$pHint_tot_sf) %>%
-  dplyr::mutate(pHint_tot_sf_1m = ifelse(depth > 0 & depth < 2, pHint_tot_sf, NA),
-                pHint_tot_sf_3m = ifelse(depth >= 2 & depth < 4, pHint_tot_sf, NA),
-                pHint_tot_sf_5m = ifelse(depth >= 4 & depth < 6, pHint_tot_sf, NA),
-                pHint_tot_sf_7m = ifelse(depth >= 6 & depth < 8, pHint_tot_sf, NA),
-                pHint_tot_sf_9m = ifelse(depth >= 8 , pHint_tot_sf, NA),
+  dplyr::mutate(pHint_tot_sf_1m = ifelse(pressure_insitu_ctd > 0 & pressure_insitu_ctd < 2, pHint_tot_sf, NA),
+                pHint_tot_sf_3m = ifelse(pressure_insitu_ctd >= 2 & pressure_insitu_ctd < 4, pHint_tot_sf, NA),
+                pHint_tot_sf_5m = ifelse(pressure_insitu_ctd >= 4 & pressure_insitu_ctd < 6, pHint_tot_sf, NA),
+                pHint_tot_sf_7m = ifelse(pressure_insitu_ctd >= 6 & pressure_insitu_ctd < 8, pHint_tot_sf, NA),
+                pHint_tot_sf_9m = ifelse(pressure_insitu_ctd >= 8 , pHint_tot_sf, NA),
                 depth_discrete = case_when(

### 2021-04-13 awipev-CO2.Rmd

--- 2021-04-11 awipev-CO2.Rmd
@@
   dplyr::mutate(depth_group = ifelse( # create new variable depth
-      depth <= 2,
+      pressure_insitu_ctd <= 2,
       1,
       ifelse(
-        depth > 2 & depth <= 4,
+        pressure_insitu_ctd > 2 & depth <= 4,
         3,
         ifelse(
-          depth > 4 & depth <= 6,
+          pressure_insitu_ctd > 4 & depth <= 6,
           5,
           ifelse(
-            depth > 6 & depth <= 8,
+            pressure_insitu_ctd > 6 & depth <= 8,
             7,

### 2021-04-13 awipev-CO2.Rmd
cleaned most commented code

@@
 library(tidyverse)
-# if (!require("robfilter")) install.packages("robfilter")
-# library("robfilter")
 if (!require("seacarb")) install.packages("seacarb")
@@
 library("gridExtra")
-# if (!require("reshape2")) install.packages("reshape2")
-# library("reshape2")
 if (!require("lubridate")) install.packages("lubridate")
 library("lubridate")
-# if (!require("lmtest")) install.packages("lmtest")
-# library("lmtest")
 if (!require("grid")) install.packages("grid")
@@
 library("xts")
-# if (!require("seismicRoll")) install.packages("seismicRoll")
-# library("seismicRoll")
 if (!require("scales")) install.packages("scales")
 library("scales")
-# if (!require("cowplot")) install.packages("cowplot")
-# library(cowplot)
-# if (!require("htmlwidgets")) install.packages("htmlwidgets")
-# library("htmlwidgets")
-# if (!require("hms")) install.packages("hms")
-# library("hms")
-# if (!require("ragg")) install.packages("ragg")
-# library("ragg")
 if (!require("skimr")) install.packages("skimr")
@@
 }
-#z <- lm2(x = d_all$pco2_calc_fb, y = d_all$pco2_fb)
-#z <- lmodel2(d_all$pco2_fb ~ d_all$pco2_calc_fb)
-#z <- lm2(data = d_all, x = pco2_calc_fb, y = pco2_fb)
 
@@
 
-#################### MySkim
-# myskim <- skim_with(numeric = sfl(min = ~min(., na.rm = TRUE),
-#                                   max = ~max(., na.rm = TRUE)))
 ```
@@
 
-# #bind all spectro measurements, vhange name of dataframe only to do the rbind.
-# seafetph <- pH_seafet_mean
-# colnames(seafetph) <- c("date", "ph_s_sf_insi", "ph_s_sf_temp_4")
-# durafetph <- pH_durafet_mean
-# colnames(durafetph) <- c("date", "ph_s_dur_temp_fb")
-# pH_seafet_durafet <- rbind(seafetph,durafetph)
-
-# #calculations for all pH spectro measurement for sd
-# sd_min <- min(pH_seafet_durafet$sd)
-# sd_max <- max(pH_seafet_durafet$sd)
-# sd_mean <- mean(pH_seafet_durafet$sd)
-
 #  make means in "d" to have same format and call it "discrete"
@@
 Even with this instrument, data collection didn't show satisfaction.
-
-<!-- We identify four periods (see plot at the end of this page with dark and ligth grey): -->
-
-<!-- - from the set-up of the instrument on **2016-02-23** to **2017-02-09** during which we try to correct for the drift -->
-<!-- - from **2017-02-09** to **2017-03-10** during which no drift correction is made, just an offset is applied to correct for the sudden shift in the data -->
-<!-- - from the set-up of a new instrument on **2018-01-08** to **2018-06-20**, during which another correction using the discrete samples will be performed.
-In this period and before to stop it, continuous leakages in the degasing unit happened.
--->
-<!-- - from the set-up of a repaired unit on **2018-07-31** to **2018-10-31**.
-Here, the instrument took wrong salinity to perform AT measurements.
-The cause is not clear yet but Steffen sent to Samir a protocol on 2018-08-24 to correct those data with right salinity.
-Also, after this issue, since 2018-08-20, bad data were still measured.
-Steffen diagnosed a "bubble issue" in the indicator tubbings.
-Steps will be sent to Marine to solve this issue.
-After this, it was not a bubble.
-We decided to switch off the instrument to save reagents and wait until the comming of Steffen in NYA with a new instrument.
--->
-
-<!-- A new instrument was installed with Steffen on **2018-10-31**.
-This new instrument has a complete new designed membrane which will solve the problem.
-Steffen also developped a TA web interface to communicate remotly with the analyser.
-Samir has all the passwords and ID to connect.
--->
-
-<!-- The instrument is usually calibrated against CRM standards after deployment, CRMs are run after 3 months as samples (measurement mode, not calibration mode), an then immediately calibrated again.
-This procedure is repeated every 3 months.
--->
-
-<!-- ### **Filtration of AT data: outliers removing** -->
-
-<!-- Outliers are present because of the cleaning operations made on the FerryBox everydays at 12:00am and 12:00pm.
-We first removed the outliers using a filter and decided, after a Skype conference with Steffen on September 2016, to: -->
-
-<!--   - Remove existing filters ( > 2350 µmol/kg). -->
-<!--   - Filter using salinity flag. -->
-<!--   - Filter using pH flag. -->
-<!--   - Not to filter on temperature flag. -->
-<!--   - Apply a 3 data points median filter (no longer used; see despike function in "oce" package) -->
-
-<!-- We decided to use "despike" function as data filter.
-This filter is done in "ny-alesund_cc.R".
-Length of runing median is: k = 121 days and the indicator (n times the sd between x and the reference) to consider a data from an outlier is: n = 0.5.
--->
-
-<!-- ### **Correction of AT data** -->
-
-<!-- Calibration was initially performed twice a year since the analyser was supposed to be stable.
-Calibration was performed using the internal "calibration mode" against a CRM from A.Dickson (Batch #145, 2016-02-24) right after the instrument was installed and a second time on 2016-09-16.
-This approch is not longer used since September 2016 (Skype with Contros).
--->
-
-<!-- Since this date, the analyser is calibrated by measuring a CRM with the "measurement mode" in order to measure the offset of the instrument.
-Additionally, discrete seawater are sampled weekly and TA is analysed by SNAPO-CO2.
--->
-
-<!--   - Two methods to correct the drift are available: -->
-<!--     - based on CRMs  -->
-<!--     - based on AT measurement of discrete samples ("references"). -->
-
-<!-- #### **Calibration** -->
-
-<!-- - **2019-01-29 14:10**: Calibration started by Philipp Fisher using CRM 145 (2226.16 umol/kg, 33.572).
-The three previous measurements were 2314.5, 233.8, 2313.7 (analyser stable) and the six subsequent measurements were 2211.8, 2277.5, 2305.4, 2316.6, 2317.9.
-Error was done with CRM salinity (Analyser was not unplugged from the FB).
--->
-<!-- Steffen's response: -->
-<!-- > Hence, the serial connection should be cut off or the FB module feeding the analyzer with salinity data should be stopped during calibration.
-The calibration can be recalculated afterwards in the data post-processing.
-However, I see that the calibration resulted in very similar pH values 3.540 (September calibration) and 3.543 (January calibration) with very similar correction factors 1.2371 and 1.2365.
-Also the TA values are very similar to the baseline measurements from before at approx.
-2316 µM.
-So for now, it should be fine.
--->
-
-<!-- #### **CRM measurements** -->
-
-<!-- The calibration of the sensor is made against a CRM standard from A.
-Dickson.
-We run a standard on the analyser as a regular measurement (measurement mode).
-Result sof calibrations are shown on the following plot.Dashed lines represent the theoritical value of AT (CRM) and hard lines represent CRM measured AT by the instrument.
--->
-
-<!-- ```{r CRM measurements, echo=FALSE, warning=FALSE, message=FALSE, out.width="80%",fig.show='hold', fig.align="center"} -->
-<!-- calib_analyser <-  read.table(paste0(path, "fb_data/Calibration_TA/TA_#1215/measure_CRM_TA.txt"), header = T, dec = ".", as.is = T, sep = ",", fill = TRUE) -->
-
-<!-- # To make the mean  -->
-<!-- # Keep dates as Character to plot without date gaps. -->
-<!-- calib_analyser3 <- calib_analyser %>% -->
-<!--   dplyr::filter(analyser == "TA3")  -->
-<!-- meanTA3 <- calib_analyser3 %>%  -->
-<!--   group_by(day) %>%  -->
-<!--   summarise (meanTA = mean(TA)) -->
-
-<!-- melt_calib <- melt(calib_analyser, id.vars=c("analyser", "TA_theo", "datetime", "CRM"), measure.vars=c("TA")) -->
-<!-- calib_p <- ggplot()+  -->
-<!--           geom_point(data= melt_calib, aes(x=datetime, y=value, color=factor(CRM), shape= factor(analyser)) , size=3) + -->
-<!--           scale_color_manual(values=c("blue","red"))+ -->
-<!--          # set dashed lines for theoritical CRM -->
-<!--           geom_segment(aes(x=1,xend=20,y=2226.16,yend=2226.16), linetype="dashed", color="blue")+ -->
-<!--           annotate("text", x = 11, y = 2228, label = "Batch #145 = 2226.16", color="blue")+ -->
-<!--           geom_segment(aes(x=20,xend=23,y=2213.59,yend=2213.59), linetype="dashed", color="red")+ -->
-<!--           annotate("text", x = 15.5, y = 2213.59, label = "Batch #159 = 2213.59", color="red")+ -->
-<!--         # set hard lines for measured CRM -->
-<!--           geom_segment(aes(x=1,xend=5,y=2254,yend=2254), color="blue") + -->
-<!--           annotate("text", x = 3, y = 2249, label = "2254", color="blue")+ -->
-<!--           geom_segment(aes(x=6,xend=10,y=2251.6,yend=2251.6), color="blue") + -->
-<!--           annotate("text", x = 8, y = 2247, label = "2251.6", color="blue")+ -->
-<!--           geom_segment(aes(x=11,xend=15,y=2190.4,yend=2190.4), color="blue")+ -->
-<!--           annotate("text", x = 14, y = 2195, label = "2190.4", color="blue")+ -->
-<!--           geom_segment(aes(x=16,xend=20,y=2203.5,yend=2203.5), color="blue")+ -->
-<!--           annotate("text", x = 18, y = 2200, label = "2203.5", color="blue")+ -->
-<!--           geom_segment(aes(x=21,xend=23,y=2224.20,yend=2224.20), color="red")+ -->
-<!--           annotate("text", x = 22, y = 2230, label = "2224.2", color="red") + -->
-<!--   theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust = 1))+  -->
-<!--   labs(title= "",y=expression(paste("Total alkalinity (µmoles.",kg^-1,")")), x="Date", color= "CRM",shape= "Deployed instrument") -->
-
-<!-- ggsave("figures/TA_calibration_CRM.png", calib_p, units="cm") -->
-<!-- print(calib_p) -->
-<!-- ``` -->
-
-<!-- #### **Discrete samples ("references")**  -->
-
-<!-- On 2018-04-19, Steffen sent his answer concerning the drift correction during the period February 2016 to March 2017.
-Within this one year period, the analyser was running, except the first week of May 2016.
-Discrete samples were collected and 3 CRMs were measured which was deemed not enough (see below).
-He suggested to base the correction on the AT of discrete ("reference") samples.
--->
-
-<!-- > "I chose the discrete reference samples due to the fact that those cover the entire working range including time, salinity and also provide a broader data basis for this kind of correction.
-Also, when looking at the uncertainty below, I fear that the three CRM measurements over 5 month are not sufficient enough for such a drift determination." -->
-
-<!-- A linear regression was performed based on the difference between the measured (analyzer) and discrete samples.
-Discrete samples were matched with the AT measured by the analyser.
-If there is no measurement coincident with a discrete sample, a linear interpolation was made between the two data surrounding the discrete sample data.
-The differences between the measured (analyzer) and analysed ("reference") data was plotted as a function of time.
--->
-
-<!-- This approach was performed: -->
-
-<!--   - on the same period than in Steffen email's (**First period**, 2016-02-23 to 2017-02-09) -->
-<!--   - and during the **third period**, with the new analyzer (2018-01-07 to 2018-06-20) -->
-
-<!-- ##### **First period**  -->
-
-<!-- ```{r First period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"} -->
-<!-- #Interpolation of continuous sensor data to match a maximum of reference data. -->
-<!-- TAinterp_all <-approx(d_all$datetime, d_all$AT, xout=d_all$datetime, method="linear", rule=2) -->
-<!-- names(TAinterp_all) <- c("datetime", "AT_interp") -->
-<!-- TAinterp_all <- as.data.frame(TAinterp_all) -->
-<!-- d_all$AT_interp <- TAinterp_all$AT_interp -->
-
-<!-- # create a column with difference between sensor and ref -->
-<!-- d_all <- d_all%>% -->
-<!--   dplyr::mutate(diff_ta =  at-AT_interp ) -->
-<!-- # create colum with instrument number -->
-<!-- d_all <- d_all %>% -->
-<!--   dplyr::mutate(TA_period= ifelse(datetime >= "2016-02-26 00:00:00" & datetime < "2017-02-09 12:00:00", "TA1", -->
-<!--                             ifelse(datetime >= "2017-02-09 12:00:00" & datetime < "2017-03-10 12:00:00", "TA2", -->
-<!--                             ifelse(datetime >= "2018-01-07 00:00:00" & datetime < "2018-06-20 00:00:00", "TA3", -->
-<!--                             ifelse(datetime >= "2018-07-31 00:00:00" & datetime < "2018-10-30 18:00:00", "TA4", -->
-<!--                             ifelse(datetime >= "2018-10-31 09:00:00" & datetime < "2019-01-16 09:00:00", "TA5", -->
-<!--                             ifelse(datetime >= "2019-01-26 13:25:00" , "TA6", "TA0"))))))) -->
-
-<!-- #remove outliers -->
-<!-- calib_ta_first <- d_all%>% -->
-<!--   dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta,TA_period)%>% -->
-<!--   dplyr::filter(TA_period =="TA1" & !is.na(at)) -->
-<!--   #dplyr::filter( !is.na(at))#, diff_ta > -40 & diff_ta < 20 ) -->
-<!-- # & datetime != "2016-08-18 08:00:00" & datetime != "2016-12-29 12:00:00 ",!is.na(at)) -->
-
-<!-- # Parameters of regression -->
-<!-- fit <- lm( data=calib_ta_first%>%filter(diff_ta <= 50), diff_ta ~ datetime) -->
-<!-- at_slope_TA1 <- round(fit$coefficients[[2]] , digits=6) -->
-<!-- at_slope1 <- round(at_slope_TA1 * 3600 *24 * 365.24, digits=2) -->
-<!-- at_intercept1 <- round(fit$coefficients[[1]], digits= 2) -->
-<!-- ``` -->
-
-<!-- The slope is: `r #at_slope_TA1` x 3600 x 24 x 365.24 = `r #at_slope1` µmoles.kg-1.yr-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. Outliers are in red. -->
-
-<!-- ```{r First period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"} -->
-<!--  # Plot of regression -->
-<!--  p <- ggplot(calib_ta_first%>%filter(diff_ta <= 50),aes(datetime,diff_ta)) + -->
-<!--      geom_point() + geom_smooth(method='lm', se=FALSE)+ -->
-<!--      geom_point(data= calib_ta_first%>%filter(diff_ta >= 50), aes(x=datetime, y=diff_ta), color="red")  + -->
-<!--    geom_hline(yintercept = 0, linetype="dashed" )+ -->
-<!--    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5), -->
-<!--                       "Intercept =",signif(fit$coef[[1]],5 ), -->
-<!--                       "Slope =",signif(fit$coef[[2]], 5), -->
-<!--                       "P =",signif(summary(fit)$coef[2,4], 5))) + -->
-<!--    ylab("Difference: Reference - Analyser") + xlab("Time") + scale_x_datetime(date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC") -->
-<!--  print(p) -->
-<!--  ggsave(paste0("figures/Diff_ref_TA_first_period.png"), p, units="cm") -->
-<!-- ``` -->
-
-<!-- ##### **Third period** -->
-
-<!-- ```{r Third period, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold',fig.align="center"} -->
-
-<!--  #remove outliers and remove period without TA measurements -->
-<!--  calib_ta_third <- d_all%>% -->
-<!--    dplyr::select(datetime, closest_datetime,AT, AT_interp, at,diff_ta, TA_period)%>% -->
-<!--    dplyr::filter(TA_period == "TA3" & !is.na(at)) -->
-
-<!--  # Parameters of regression -->
-<!--  fit <- lm( data=calib_ta_third, diff_ta ~ datetime) -->
-<!--  at_slope_TA3 <- round(fit$coefficients[[2]] , digits=8) -->
-<!--  at_slope3 <- round(at_slope_TA3 * 3600 *24 * 365.24, digits=2) -->
-<!--  at_intercept3 <- round(fit$coefficients[[1]], digits= 2) # pas besoin ici. -->
-<!-- ``` -->
-
-<!-- The slope is in days: `r #at_slope_TA3` x 3600 x 24 x 365.24 = `r #at_slope3` µmoles.kg-1.an-1. Regression is: R2 = `r #round(signif(summary(fit)$adj.r.squared, 5), digits =4)`. No outliers. -->
-
-<!-- ```{r Third period plot, echo=FALSE, warning=FALSE, message=FALSE, out.width="50%",fig.show='hold', fig.align="center"} -->
-<!-- # # Plot of regression -->
-<!--  p <- ggplot(calib_ta_third,aes(x=datetime, y=diff_ta) )+ -->
-<!--      geom_point() + geom_smooth(method='lm', se=FALSE)+ -->
-<!--      #geom_point(data= calib_ta_third%>%filter(diff_ta < -40 & diff_ta<20), aes(x=datetime, y=diff_ta), color="red")  + -->
-<!--     geom_hline(yintercept = 0, linetype="dashed" )+ -->
-<!--    geom_vline(xintercept = as.POSIXct("2018-01-08 12:55:00", tz="UTC"), colour="red", linetype = "longdash") + -->
-<!--    #geom_text(aes(xintercept=as.POSIXct("2018-01-01 12:55:00"),label="TA "), colour="red", vjust=1.2)+ -->
-<!--    labs(title = paste("Adj R2 = ",signif(summary(fit)$adj.r.squared, 5), -->
-<!--                       "Intercept =",signif(fit$coef[[1]],5 ), -->
-<!--                       " Slope =",signif(fit$coef[[2]], 5), -->
-<!--                       " P =",signif(summary(fit)$coef[2,4], 5))) + ylab("Difference: Reference - Analyser") + xlab("Time") + -->
-<!--    scale_x_datetime( date_labels = "%b %Y", date_minor_breaks = "month", timezone="UTC") -->
-<!--  print(p) -->
-<!--  ggsave(paste0("figures/Diff_ref_TA_third_period.png"), p, units="cm") -->
-<!-- ``` -->
-
-<!-- ##### **Second period** -->
-
-<!-- ```{r Second period, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'} -->
-
-<!-- #remove outliers and remove period without TA measurements -->
-<!-- calib_ta_second <- d_all%>% -->
-<!--   dplyr::select(datetime, closest_datetime, AT, AT_interp, at, diff_ta, TA_period)%>% -->
-<!--   dplyr::filter(TA_period == "TA2" & !is.na(at)) -->
-
-<!-- mean_offset <- mean(calib_ta_second$diff_ta) -->
-
-<!-- ```  -->
-
-<!-- For the second period, the average difference between 5 discrete samples "references" and TA analyser measurements (`r #mean_offset` µmoles.kg~-1~) was added to TA value as an offset. -->
-
-<!-- #### **Final TA corrected data (Regression)** -->
-
-<!-- The following plot shows the corrected TA data with regressions (Periods 1 and 3) and with offset (Period 2) applied according to Steffen's proposition. -->
-<!-- It is clear that these corrected data (in green) cannot be used for periods 1 to 3.
-The jury is still out for period 4.
-The issue of salinity must be clarified before an assessment can be made.
--->
-
-<!-- ```{r Correction applied, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%",fig.show='hold'} -->
-<!-- # Correction for the 3 periods is apply -->
-<!-- d_all <- d_all%>% -->
-<!--   dplyr::mutate(datetime_reg = as.numeric(datetime), -->
-<!--                 at_intercept = ifelse(TA_period == "TA1", at_intercept1, -->
-<!--                                ifelse(TA_period == "TA3", at_intercept3, NA)), -->
-<!--                 at_slope = ifelse(TA_period == "TA1", at_slope_TA1, -->
-<!--                            ifelse(TA_period == "TA3", at_slope_TA3, NA)) -->
-<!--                 ) -->
-
-<!-- d_all <- d_all%>% -->
-<!--  dplyr::mutate(TA_reg_corrected = ifelse(TA_period == "TA1", (AT + (d_all$datetime_reg * d_all$at_slope + at_intercept)), -->
-<!--                                         ifelse(TA_period == "TA2", (AT + mean_offset), -->
-<!--                                         ifelse(TA_period == "TA3", (AT + (datetime_reg * at_slope)+ at_intercept), NA)))) -->
-
-<!-- at_contros_cleaned_xts <- dplyr::select(d_all, datetime,AT,at,TA_reg_corrected) -->
-<!-- at_contros_cleaned_xts <-  as.xts(at_contros_cleaned_xts, order.by = d_all$datetime) -->
-<!-- dygraph(at_contros_cleaned_xts, group = "awipev", main=" Total Alkalinity (in Ferrybox)", ylab="Total alkalinity") %>% -->
-<!--    #dySeries("at_contros", color = RColorBrewer::brewer.pal(3, "Set2"), strokeWidth = 0, pointSize=2) %>% -->
-<!--   dySeries("AT", label= "Raw TA", color = "blue", strokeWidth = 0, pointSize=2) %>% -->
-<!--   dySeries("TA_reg_corrected", label= "Corrected TA", color = RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize=2) %>% -->
-<!--   dySeries("at", label="TA reference",color = "red", strokeWidth = 0, pointSize=4) %>% -->
-<!--   dyEvent(as.POSIXct("2016-05-31 10:00:00", tz="UTC"), "HCl Changed", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2016-06-24 10:00:00", tz="UTC"), "BCG Changed", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2016-02-24 14:00:00", tz="UTC"), "Calibration 1", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2016-09-16 10:00:00", tz="UTC"), "Calibration 2", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2017-03-21 12:00:00", tz="UTC"), "TA analyser changed", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-01-08 12:55:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-07-31 00:00:00", tz="UTC"), "TA analyser changed #TA-1215-001", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2018-10-30 18:00:00", tz="UTC"), "TA analyser changed #TA-0317-001", labelLoc = "top", color="red") %>% -->
-<!--   dyEvent(as.POSIXct("2016-11-15 09:00:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2017-02-09 12:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2017-04-11 06:20:00", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2018-01-22 13:00:12", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2018-05-16 12:39:39", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2018-10-31 10:29:27", tz="UTC"), "CRM measurement", labelLoc = "bottom") %>% -->
-<!--   dyEvent(as.POSIXct("2019-01-26 13:25:20", tz="UTC"), "Calibration mode - CRM", labelLoc = "bottom") %>% -->
-<!--   #dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>% -->
-<!--   dyShading(from = TAevents[1], to = TAevents[2], color = "#EDEDED") %>% -->
-<!--   dyShading(from = TAevents[3], to = TAevents[4], color = "#C2C2C2") %>% -->
-<!--   dyShading(from = TAevents[5], to = TAevents[6], color = "#EDEDED") %>% -->
-<!--   dyShading(from = TAevents[7], to = TAevents[8], color = "#C2C2C2") %>% -->
-<!--   dyShading(from = TAevents[9], to = TAevents[10], color = "#EDEDED") %>% -->
-<!--   dyShading(from = TAevents[11], to = TAevents[12], color = "#C2C2C2") %>% -->
-<!--   dyAxis("y",valueRange = c(1600, 2650)) %>% -->
-<!--   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>% -->
-<!--   dyOptions( strokeWidth= 0) %>% -->
-<!--   dyLegend(show = "follow")   %>% -->
-<!--   dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>% -->
-<!--     dyRangeSelector(height = 30, dateWindow= NULL) -->
-
-<!-- ``` -->
 
@@
 tmp <- d_all %>% 
-  dplyr::select(montht, temp_insitu_ctd, depth) %>%
-  group_by(depth, montht)
+  dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
+  group_by(depth_group, montht)
 p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = temp_insitu_ctd)) +
+  ggplot(aes(x=as.factor(depth_group), y = temp_insitu_ctd)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
 tmp <- d_all %>% 
-  dplyr::select(montht, temp_insitu_ctd, depth) %>%
-  dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
+  dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
+  dplyr::mutate(depth = as.factor(ifelse(depth_group == 1 | depth_group == 3, 2, depth_group))) %>% 
   dplyr::filter(depth == 2 | depth == 10) %>% 
@@
 tmp <- d_all %>% 
-  dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth) %>%
-  dplyr::mutate(density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0),
-                depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
+  dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth_group, pressure_insitu_ctd) %>%
+  dplyr::mutate(density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = pressure_insitu_ctd),
+                depth = as.factor(ifelse(depth_group == 1 | depth_group == 3, 2, depth_group))) %>% 
   dplyr::filter(depth == 2 | depth == 10) %>% 
@@
   group_by(depth, montht) 
+summary(tmp)
 summary(aov(tmp$density ~ tmp$depth * tmp$montht))
@@
   geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha=alpha, na.rm=TRUE, size=size_point*3) + 
-  labs(title="Mesured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
+  labs(title="Measured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
   Mytheme(size_labs = size_labs)

### 2021-04-14 awipev-CO2.Rmd
On the way

@@
   dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
-  dplyr::mutate(depth_group = ifelse( # create new variable depth
+  dplyr::mutate(depth_group_pressure = ifelse( # create new variable depth
       pressure_insitu_ctd <= 2,
@@
             pressure_insitu_ctd > 6 & depth <= 8,
+            7,
+            ifelse(pressure_insitu_ctd > 8, 10, NA)
+          )
+        )
+      )
+    ),
+    depth_group_philipp = ifelse( # create new variable depth
+      depth <= 2,
+      1,
+      ifelse(
+        depth > 2 & depth <= 4,
+        3,
+        ifelse(
+          depth > 4 & depth <= 6,
+          5,
+          ifelse(
+            depth > 6 & depth <= 8,
             7,
@@
 ```{r stratification, echo=FALSE, message= FALSE, warning=FALSE}
+# we look at the distribution of data
+tmp <- d_all %>% 
+  dplyr::select(date, depth, pressure_insitu_ctd) %>% 
+  dplyr::mutate(month=month(d_all$date, label = TRUE)) %>% 
+  group_by(month)
+
 depth_labels <- c("0-2", "2-4", "4-6", "6-8", "8-12")
@@
 # value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
-atm_co2 <-
-  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
+atm_co2_old <-
+  read_delim(file = paste0(path, "atmospheric_co2_zeppelin_old/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
   delim = " ",
@@
   dplyr::select(datetime, pco2_air)
-d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
+
+# downloaded 2021-04-14
+# http://ebas.nilu.no/Pages/DataSetList.aspx?key=3673A72690B343B1AEC0F1673FE8C09D
+file_names <- c("atmospheric_co2_zeppelin/NO0042G.20160101000000.20180420115103.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20170101000000.20180413180000.online_crds.carbon_dioxide.air.7mo.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas",
+"atmospheric_co2_zeppelin/NO0042G.20180101000000.20210413133953.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20190101000000.20210413133953.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20200101000000.20210413000000.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas")
+atm_co2 <- NULL
+year_co2 <- ymd_hm(paste0(c(2016:2020), "-01-01 00:00"))
+for (i in 1:5) {
+print(i)
+tmp <-
+  read_table2(file = paste0(path, file_names[i]),
+  comment = "#",
+  #skip = 182,
+  col_names = FALSE,
+  na = c("9999.999", "99.999", "9999.990", "9999.99"),
+  ) %>%
+  dplyr::mutate(pco2_air = X3,
+  datetime = year_co2[i] + X1*24*3600) %>% 
+  dplyr::select(datetime, pco2_air)
+  tmp$datetime <- lubridate::round_date(tmp$datetime, unit="1 minutes")
+atm_co2 <- bind_rows(atm_co2, tmp)
+  }
+
+#d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
 p_atm_co2 <- ggplot(data=atm_co2) +

### 2021-04-14 awipev-CO2.Rmd
On the way

@@
 # we look at the distribution of data
-tmp <- d_all %>% 
+tmp <- d_hour %>% 
   dplyr::select(date, depth, pressure_insitu_ctd) %>% 
-  dplyr::mutate(month=month(d_all$date, label = TRUE)) %>% 
+  dplyr::mutate(month=month(d_hour$date, label = TRUE)) %>% 
   group_by(month)
@@
 # value:long_name : measured_mole_fraction_of_trace_gas_in_dry_air
-atm_co2_old <-
-  read_delim(file = paste0(path, "atmospheric_co2_zeppelin_old/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
+atm_co2 <-
+  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
   delim = " ",
@@
   dplyr::select(datetime, pco2_air)
-
-# downloaded 2021-04-14
-# http://ebas.nilu.no/Pages/DataSetList.aspx?key=3673A72690B343B1AEC0F1673FE8C09D
-file_names <- c("atmospheric_co2_zeppelin/NO0042G.20160101000000.20180420115103.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20170101000000.20180413180000.online_crds.carbon_dioxide.air.7mo.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas",
-"atmospheric_co2_zeppelin/NO0042G.20180101000000.20210413133953.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20190101000000.20210413133953.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20200101000000.20210413000000.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas")
-atm_co2 <- NULL
-year_co2 <- ymd_hm(paste0(c(2016:2020), "-01-01 00:00"))
-for (i in 1:5) {
-print(i)
-tmp <-
-  read_table2(file = paste0(path, file_names[i]),
-  comment = "#",
-  #skip = 182,
-  col_names = FALSE,
-  na = c("9999.999", "99.999", "9999.990", "9999.99"),
-  ) %>%
-  dplyr::mutate(pco2_air = X3,
-  datetime = year_co2[i] + X1*24*3600) %>% 
-  dplyr::select(datetime, pco2_air)
-  tmp$datetime <- lubridate::round_date(tmp$datetime, unit="1 minutes")
-atm_co2 <- bind_rows(atm_co2, tmp)
-  }
-
-#d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
+d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
 p_atm_co2 <- ggplot(data=atm_co2) +

### 2021-05-05 awipev-CO2.Rmd
nothing

--- 2021-04-14 awipev-CO2.Rmd
@@
 
+# We add a variable depth_group in d_all in order to be able to choose depth_group_pressure or depth_group_p
 depth_labels <- c("0-2", "2-4", "4-6", "6-8", "8-12")
@@
 tmp <- d_all %>% 
+  dplyr::mutate(depth_group = depth_group_pressure) %>% 
   dplyr::select(montht, sal_insitu_ctd, depth_group) %>%

### 2021-05-05 awipev-CO2.Rmd
nothing

--- 2021-04-14 awipev-CO2.Rmd
@@
 # we look at the distribution of data
-tmp <- d_all %>% 
+tmp <- d_hour %>% 
   dplyr::select(date, depth, pressure_insitu_ctd) %>% 
-  dplyr::mutate(month=month(d_all$date, label = TRUE)) %>% 
+  dplyr::mutate(month=month(d_hour$date, label = TRUE)) %>% 
   group_by(month)
-
 depth_labels <- c("0-2", "2-4", "4-6", "6-8", "8-12")

### 2021-05-06 awipev-CO2.Rmd
Looking into salinity data sent pby Philipp

@@
   ))
+
 d_hour <- d_hour %>%
@@
 #   geom_point(aes(x=datetime, y=depth, col='red', alpha = 0.3))
+
+# # read a file provided by Philipp on 2021-04-13 in the hope that it contains
+# # in situ CTD salinity data for any month of June. IT DOES NOT
+# sal_2021_04_13 <-
+#   readRDS(file = paste0(
+#     path,
+#     "fb_data/remos_2021-04-13/svl_remos_ctd_salinity_2017_2020.rds"
+#   )) %>% 
+#   dplyr::rename(sal_new = svl_ctd_salinity_mean)
+# zz <- dplyr::left_join(d_hour, sal_2021_04_13, by = 'datetime') %>%
+#   dplyr::mutate(month = month(date)) %>%
+#   dplyr::filter(depth < 4, month(date) == 6, datetime > as.POSIXct("2017-07-01 11:00:00"))
+# pp <- ggplot(zz, aes(x=datetime, y=sal_new)) +
+#     geom_point()
+
 d_all <- as_tibble(d_hour) #d_all will be the merger
@@
 # we look at the distribution of data
-tmp <- d_hour %>% 
+tmp <- d_all %>% 
   dplyr::select(date, depth, pressure_insitu_ctd) %>% 
-  dplyr::mutate(month=month(d_hour$date, label = TRUE)) %>% 
+  dplyr::mutate(month=month(d_all$date, label = TRUE)) %>% 
   group_by(month)

### 2021-05-10 awipev-CO2.Rmd
Fixed issue in stratification

@@
 #[5] "Temperature[degC]"  "Pressure[hPa]"      "WindSpeed[m/s]"     "WindDirection[deg]"
+wind_2020 <-
+  readRDS(file = paste0(
+    path,
+    "meteo_awi/svl_wind10_2020_hour.rds"
+  )) %>% 
+  dplyr::rename(datetime = 'Date/Time',
+                ws = mean_speed,
+                wd = mean_direction) %>% 
+  dplyr::mutate(datetime = as.POSIXct(datetime, format = "%d-%m-%Y %H"))
 

### 2021-05-10 awipev-CO2.Rmd
added 2020 wind data

@@
 tmp <- d_all %>% 
+  dplyr::mutate(depth_group = depth_group_pressure) %>% 
   dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
@@
 tmp <- d_all %>% 
+  dplyr::mutate(depth_group = depth_group_pressure) %>% 
   dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth_group, pressure_insitu_ctd) %>%
@@
   dplyr::select(datetime, temp_air, p_air, ws, wd)
-d_all <- dplyr::left_join(d_all, meteo, by = "datetime")
+d_all <- dplyr::left_join(d_all, meteo, by = "datetime") %>% 
+  select(sort(dplyr::everything()))
 ```

### 2021-05-12 awipev-CO2.Rmd
Final processing of co2_air

@@
   ) %>%
-  dplyr::mutate(pco2_air = value,
+  dplyr::mutate(co2_air = value,
   datetime = as_datetime(paste(paste(year, month, day, sep="-"), paste(hour, minute, second, sep="-"), sep = " "))) %>%
-  dplyr::select(datetime, pco2_air)
+  dplyr::select(datetime, co2_air)
 
@@
 "atmospheric_co2_zeppelin/NO0042G.20180101000000.20210413133953.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20190101000000.20210413133953.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas", "atmospheric_co2_zeppelin/NO0042G.20200101000000.20210413000000.online_crds.carbon_dioxide.air.1y.1h.NO01L_picarro2_G2401.NO01L_picarro.lev2.nas")
-atm_co2 <- NULL
+atm_co2_new <- NULL
 year_co2 <- ymd_hm(paste0(c(2016:2020), "-01-01 00:00"))
@@
   ) %>%
-  dplyr::mutate(pco2_air = X3,
+  dplyr::mutate(co2_air = X3,
   datetime = year_co2[i] + X1*24*3600) %>% 
-  dplyr::select(datetime, pco2_air)
+  dplyr::select(datetime, co2_air)
   tmp$datetime <- lubridate::round_date(tmp$datetime, unit="1 minutes")
-atm_co2 <- bind_rows(atm_co2, tmp)
+atm_co2_new <- bind_rows(atm_co2_new, tmp)
   }
+# combine the two sources of CO2 data
+# the new source has missing data in 2018, so the data from the old source
+# are used for 2018
+atm_co2 <- dplyr::left_join(atm_co2_new, atm_co2_old, by = "datetime") %>% dplyr::rename(co2_air = co2_air.x, co2_air_old = co2_air.y) %>% dplyr::mutate(co2_air = ifelse(year(atm_co2$datetime) == 2018, co2_air_old, co2_air))
+summary(atm_co2)
 
 #d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
-p_atm_co2 <- ggplot(data=atm_co2) +
-  geom_point(aes(x = datetime, y = pco2_air), col = "blue", size = 0.15, na.rm = TRUE) +
+p_atm_co2 <- atm_co2 %>% 
+  #tidyr::pivot_longer(cols = c(pco2_air, pco2_air_old), names_to = "dataset", values_to = "pco2") %>% 
+  ggplot() +
+  geom_point(aes(x = datetime, y = co2_air), col = "blue", size = 0.15, na.rm = TRUE) +
+  #facet_grid(rows = vars(dataset)) +
+  #geom_point(aes(x = datetime, y = pco2_air_old), col = "grey", size = 0.15, na.rm = TRUE) +
   labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +

### 2021-05-14 awipev-CO2.Rmd
Working of atm CO2 time series plot

@@
 library("tsibble")
+if (!require("slider")) install.packages("slider")
+library("slider")
 if (!require("kableExtra")) install.packages("kableExtra")
@@
 
-d_all <- as_tibble(d_hour) #d_all will be the merger
+d_all <- as_tsibble(d_hour, index = datetime) #d_all will be the merger
 d_all <- d_all %>%
@@
 # are used for 2018
-atm_co2 <- dplyr::left_join(atm_co2_new, atm_co2_old, by = "datetime") %>% dplyr::rename(co2_air = co2_air.x, co2_air_old = co2_air.y) %>% dplyr::mutate(co2_air = ifelse(year(atm_co2$datetime) == 2018, co2_air_old, co2_air))
-summary(atm_co2)
+atm_co2 <- dplyr::left_join(atm_co2_new, atm_co2_old, by = "datetime")
+atm_co2 <- atm_co2 %>% 
+  dplyr::rename(co2_air = co2_air.x, co2_air_old = co2_air.y) %>%
+  dplyr::mutate(co2_air = ifelse(year(atm_co2$datetime) == 2018, co2_air_old, co2_air))
+# summary(atm_co2)
+zz <- as_tsibble(atm_co2) %>% 
+  mutate(smoothed_co2_air = slide_dbl(co2_air, .f = mean,
+                                   .before = 1, .after = 1))
+ggplot(zz) +
+  aes(x = time_hour, y = smoothed_temp, color = origin)
+
+slide_dbl(~mean(.x$datetime, .x$co2_air), .before = 3, .after = 3)
+  #slide_period_dbl(.x = atm_co2$co2_air, .f = mean, .i = atm_co2$datetime, .period = "month")
 
@@
   ggplot() +
-  geom_point(aes(x = datetime, y = co2_air), col = "blue", size = 0.15, na.rm = TRUE) +
+  geom_point(aes(x = datetime, y = running_mean(atm_co2$co2_air, 24)), col = "blue", size = 0.15, na.rm = TRUE) +
   #facet_grid(rows = vars(dataset)) +
@@
   Mytheme(size_labs = 8)
+p_atm_co2
 ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")

### 2021-05-14 awipev-CO2.Rmd
Working of atm CO2 time series plot

@@
 
-d_all <- as_tsibble(d_hour, index = datetime) #d_all will be the merger
+d_all <- as_tibble(d_hour) #d_all will be the merger
 d_all <- d_all %>%
@@
   dplyr::mutate(co2_air = ifelse(year(atm_co2$datetime) == 2018, co2_air_old, co2_air))
-# summary(atm_co2)
-zz <- as_tsibble(atm_co2) %>% 
-  mutate(smoothed_co2_air = slide_dbl(co2_air, .f = mean,
-                                   .before = 1, .after = 1))
-ggplot(zz) +
-  aes(x = time_hour, y = smoothed_temp, color = origin)
-
-slide_dbl(~mean(.x$datetime, .x$co2_air), .before = 3, .after = 3)
-  #slide_period_dbl(.x = atm_co2$co2_air, .f = mean, .i = atm_co2$datetime, .period = "month")
+summary(atm_co2)
+zz <- atm_co2 %>% 
+  slide_dbl(~mean(.x$co2_air), .before = 1, .after = 1)
 

### 2021-05-14 awipev-CO2.Rmd
fixing merge issue 2

--- 2021-05-14 awipev-CO2.Rmd
@@
   #slide_period_dbl(.x = atm_co2$co2_air, .f = mean, .i = atm_co2$datetime, .period = "month")
-
 #d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")

### 2021-05-14 awipev-CO2.Rmd
finalized co2_air

--- 2021-05-14 awipev-CO2.Rmd
@@
 atm_co2_old <-
-  read_delim(file = paste0(path, "atmospheric_co2_zeppelin_old/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
+  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
   delim = " ",
@@
 for (i in 1:5) {
-print(i)
 tmp <-
@@
 # are used for 2018
-atm_co2 <- dplyr::left_join(atm_co2_new, atm_co2_old, by = "datetime")
+atm_co2 <- dplyr::full_join(atm_co2_new, atm_co2_old, by = "datetime")
 atm_co2 <- atm_co2 %>% 
-  dplyr::rename(co2_air = co2_air.x, co2_air_old = co2_air.y) %>%
-  dplyr::mutate(co2_air = ifelse(year(atm_co2$datetime) == 2018, co2_air_old, co2_air))
-# summary(atm_co2)
-zz <- as_tsibble(atm_co2) %>% 
-  mutate(smoothed_co2_air = slide_dbl(co2_air, .f = mean,
-                                   .before = 1, .after = 1))
-ggplot(zz) +
-  aes(x = time_hour, y = smoothed_temp, color = origin)
-
-slide_dbl(~mean(.x$datetime, .x$co2_air), .before = 3, .after = 3)
-  #slide_period_dbl(.x = atm_co2$co2_air, .f = mean, .i = atm_co2$datetime, .period = "month")
-
-#d_all <- dplyr::left_join(d_all, atm_co2, by = "datetime")
-p_atm_co2 <- atm_co2 %>% 
+  dplyr::rename(co2_air_new = co2_air.x, co2_air_old = co2_air.y) %>%
+  dplyr::mutate(co2_air = ifelse(year(atm_co2$datetime) == 2020, co2_air_new, co2_air_old))
+# Below was an attempt to smooth but
+# zz <- as_tsibble(atm_co2) %>% 
+#   mutate(smoothed_co2_air = slide_dbl(co2_air, .f = mean, .before = 12, .after = 12, .complete = TRUE))
+# ggplot(zz) +
+#   geom_line(aes(x = datetime, y = smoothed_co2_air))
+d_all <- dplyr::left_join(d_all, dplyr::select(atm_co2, datetime, co2_air), by = "datetime") %>% 
+  select(sort(current_vars()))
+
+p_atm_co2 <- d_all %>% 
   #tidyr::pivot_longer(cols = c(pco2_air, pco2_air_old), names_to = "dataset", values_to = "pco2") %>% 
   ggplot() +
-  geom_point(aes(x = datetime, y = running_mean(atm_co2$co2_air, 24)), col = "blue", size = 0.15, na.rm = TRUE) +
+  geom_point(aes(x = datetime, y = co2_air), col = "blue", size = 0.15, na.rm = TRUE) +
   #facet_grid(rows = vars(dataset)) +
@@
   Mytheme(size_labs = 8)
-p_atm_co2
+#p_atm_co2
 ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")
@@
   dplyr::select(datetime, temp_air, p_air, ws, wd)
-d_all <- dplyr::left_join(d_all, meteo, by = "datetime") %>% 
-  select(sort(dplyr::everything()))
+zz <- dplyr::left_join(d_all, meteo, by = "datetime") %>% 
+  select(sort(current_vars()))
 ```

### 2021-05-14 awipev-CO2.Rmd
finalized wind speed

@@
   dplyr::select(datetime, temp_air, p_air, ws, wd)
-zz <- dplyr::left_join(d_all, meteo, by = "datetime") %>% 
+d_all <- dplyr::left_join(d_all, meteo, by = "datetime") %>% 
   select(sort(current_vars()))
@@
 d_all <- d_all %>%
-  dplyr::mutate(delta_pco2 = pco2_fb - pco2_air, # ppm
+  dplyr::mutate(delta_pco2 = pco2_fb - co2_air, # ppm
                 k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
@@
 
-p_f_air_sea <- ggplot(data=d_all) +
+p_f_air_sea <- ggplot(data = d_all) +
   geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +

### 2021-05-20 awipev-CO2.Rmd
minor revision air-sea CO2 flux

@@
 d_all <- dplyr::left_join(d_all, dplyr::select(atm_co2, datetime, co2_air), by = "datetime") %>% 
-  select(sort(current_vars()))
+  dplyr::select(sort(current_vars()))
 
@@
   geom_point(aes(x = day, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
-  labs(title = "Air-sea CO2 flux (per day)", x = "Time", y = "CO2 (mmol/(m2 d))") +
+  labs(title = "Air-sea CO2 flux (per day)", x = "Julian day", y = "CO2 (mmol/(m2 d))") +
   Mytheme(size_labs = 8)
@@
   ungroup() %>%
-  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea)
+  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
+  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
 #air_sea_month
 p_f_air_sea_m <- ggplot(data = air_sea_month) +
-  geom_point(aes(x = monthd, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
-  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
-  lims(y = c(-30, 0)) +
-  labs(title = "Air-sea CO2 flux (per month)", x = "Julian day", y = "CO2 (mmol/(m2 month))") +
+  geom_point(aes(x = montht, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
+  #scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
+  #lims(y = c(-30, 0)) +
+  labs(title = "Air-sea CO2 flux (per month)", x = "Month", y = "CO2 (mmol/(m2 month))") +
   Mytheme(size_labs = 8)
@@
 
-The annual air-sea CO2 flux is `r round(sum(air_sea_month), digits = 0)` mol/(m2 year).
-
-## Miscelaneous
+The annual air-sea CO2 flux is `r round(sum(air_sea_month$f_air_sea), digits = 0)` mol/(m2 year).
+
+## Miscellaneous
 ###Save all

### 2021-05-20 awipev-CO2.Rmd
save at vs sal

@@
         plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
+ggsave(filename = "figures/at_s.png", plot = at_s, width = 25, height = 20, units = "cm")
 

### 2021-05-21 awipev-CO2.Rmd
fig AT vs S for paper

@@
 ggsave(filename = "figures/at_s.png", plot = at_s, width = 25, height = 20, units = "cm")
+
+# Same plot for paper
+p_at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at))+
+    labs(x="Salinity", y="Discrete AT")  +
+    stat_smooth(method = "lm", col = "black") +
+    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
+                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
+                       ";\nSlope =",signif(fit$coef[[2]], 5),
+                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
+                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
+  theme_bw() +
+  theme(aspect.ratio=1,
+        axis.text=element_text(size=7),
+        axis.title.y= element_text(size =7),
+        axis.title.x= element_text(size =7),
+        plot.margin = unit(c(0.5,1,1,1), "cm"),
+        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
+ggsave(filename = "figures/p_at_s.png", plot = p_at_s, width = 25, height = 20, units = "cm")
 

### 2021-05-21 awipev-CO2.Rmd
added code from Kapsenberg's paper

--- 2021-05-20 awipev-CO2.Rmd
@@
 ggsave(filename = "figures/at_s.png", plot = at_s, width = 25, height = 20, units = "cm")
+
+# Same plot for paper
+p_at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at)) +
+  geom_point(col="blue", size = 0.2) +
+  labs(x="Salinity", y="Discrete AT")  +
+  stat_smooth(method = "lm", col = "blue", size = 0.3) +
+  theme_bw(base_size = 9) +
+  theme(aspect.ratio=1#,
+        #axis.text=element_text(size=7),
+        #axis.title.y= element_text(size =7),
+        #axis.title.x= element_text(size =7),
+        #plot.margin = unit(c(0.5,1,1,1), "cm"),
+        #plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70))
+        )
+ggsave(filename = "figures/p_at_s.png", plot = p_at_s, width = 7, height = 7, units = "cm")
 
@@
 
+## Deconvolution of pCO2 changes
+```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
+# We follow the method of Garcia-Ibanez described above.
+# construct a dataframe with monthly means for the entire series (mXX) as well as real data (without mrefix m)
+deconv_dat <- tbl_df(
+  data.frame(date=as.POSIXct(mean0m$sampling_date), mAT=means_month0m$AT[mean0m$monthd]*1e-6, mCT=means_month0m$CT[mean0m$monthd]*1e-6, mS=means_month0m$Salinity[mean0m$monthd], mT=means_month0m$Temperature[mean0m$monthd], P=mean0m$mean_P, Pt=mean0m$mean_Pt, Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
+)
+
+d <- NULL; deconv <- NULL # d is for the data to use in carb, deconv is to store the results
+deconv <- data_frame(date=as.POSIXct(mean0m$sampling_date))
+d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(mS), !is.na(T)) # we eliminate date with NAs
+deconv_pCO2_T <- data_frame(date=d$date,
+                     deconv_pCO2_T=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$mS, T=d$T, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
+)
+d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(S), !is.na(mT)) # we eliminate date with NAs
+deconv_pCO2_S <- data_frame(date=d$date,
+                     deconv_pCO2_S=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$S, T=d$mT, P=d$P, Pt=d$Pt, 
+                                      Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
+                     )
+d <- filter(deconv_dat, !is.na(AT), !is.na(mCT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
+deconv_pCO2_AT <- data_frame(date=d$date,
+                     deconv_pCO2_AT=carb(flag=15, var1=d$AT, var2=d$mCT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
+)
+d <- filter(deconv_dat, !is.na(mAT), !is.na(CT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
+deconv_pCO2_CT <- data_frame(date=d$date,
+                     deconv_pCO2_CT=carb(flag=15, var1=d$mAT, var2=d$CT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
+)
+
+# Bring all results together
+deconv <- deconv %>%
+  left_join(deconv_pCO2_T) %>%
+  left_join(deconv_pCO2_S) %>%
+  left_join(deconv_pCO2_AT) %>%
+  left_join(deconv_pCO2_CT)
+
+# Regressions and tables of key parameters
+var_list <-
+  c(
+  "deconv_pCO2_T",
+  "deconv_pCO2_S",
+  "deconv_pCO2_AT",
+  "deconv_pCO2_CT"
+  )
+lms <- lapply(var_list, function(x) {
+  summary(lm(substitute(i ~ decimal_date(date), list(i = as.name(x))), data = deconv))
+  })
+reg <- NULL
+for (i in 1:length(var_list)) {
+  #one loops through all anomalies
+  # calculate probability of fstatistic because it cannot be extracted from lms above
+  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
+  # slope returned by lm is per second
+  prob <-
+  pf(lms[[i]]$fstatistic[1],
+  lms[[i]]$fstatistic[2],
+  lms[[i]]$fstatistic[3],
+  lower.tail = FALSE)
+  reg <-
+  rbind(reg, as.numeric(
+  c(
+    lms[[i]]$coefficients[2, 1],
+    lms[[i]]$coefficients[2, 2],
+  lms[[i]]$coefficients[2, 4],
+  lms[[i]]$coefficients[1, 1],
+  lms[[i]]$coefficients[1, 2],
+  lms[[i]]$coefficients[1, 4],
+  lms[[i]]$r.squared,
+  prob
+  )
+  ))
+}
+colnames(reg) <-
+  c("Slope",
+  "SE Slope",
+  "P Slope",
+  "Intercept",
+  "SE int.",
+  "P int.",
+  "R2",
+  "P value")
+row.names(reg) <- var_list
+reg_deconv <- reg
+
+# Plot
+#deconv_melt <- melt(deconv, id="date")
+deconv_melt <-  gather(data = deconv, key = variable, value=value, -date)
+fig_deconv_pCO2 <- ggplot(deconv_melt) + geom_point(aes(x=date, y=value, color=variable), size=0.5) +
+  facet_grid(variable ~., scales="free_y") + 
+  xlab("Time") + ylab("pCO2 (uatm")+
+  Mytheme() +
+  scale_colour_discrete(guide="none")
+ggsave(file="../figures/fig_deconv_pCO2.png", fig_deconv, width = 18, height = 20, units = "cm")
+```
+
 ## Air-sea CO2 flux

### 2021-05-21 awipev-CO2.Rmd
added code from Kapsenberg's paper

@@
 
-## Deconvolution of pCO2 changes
-```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
-# We follow the method of Garcia-Ibanez described above.
-# construct a dataframe with monthly means for the entire series (mXX) as well as real data (without mrefix m)
-deconv_dat <- tbl_df(
-  data.frame(date=as.POSIXct(mean0m$sampling_date), mAT=means_month0m$AT[mean0m$monthd]*1e-6, mCT=means_month0m$CT[mean0m$monthd]*1e-6, mS=means_month0m$Salinity[mean0m$monthd], mT=means_month0m$Temperature[mean0m$monthd], P=mean0m$mean_P, Pt=mean0m$mean_Pt, Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
-)
-
-d <- NULL; deconv <- NULL # d is for the data to use in carb, deconv is to store the results
-deconv <- data_frame(date=as.POSIXct(mean0m$sampling_date))
-d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(mS), !is.na(T)) # we eliminate date with NAs
-deconv_pCO2_T <- data_frame(date=d$date,
-                     deconv_pCO2_T=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$mS, T=d$T, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
-)
-d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(S), !is.na(mT)) # we eliminate date with NAs
-deconv_pCO2_S <- data_frame(date=d$date,
-                     deconv_pCO2_S=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$S, T=d$mT, P=d$P, Pt=d$Pt, 
-                                      Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
-                     )
-d <- filter(deconv_dat, !is.na(AT), !is.na(mCT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
-deconv_pCO2_AT <- data_frame(date=d$date,
-                     deconv_pCO2_AT=carb(flag=15, var1=d$AT, var2=d$mCT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
-)
-d <- filter(deconv_dat, !is.na(mAT), !is.na(CT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
-deconv_pCO2_CT <- data_frame(date=d$date,
-                     deconv_pCO2_CT=carb(flag=15, var1=d$mAT, var2=d$CT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
-)
-
-# Bring all results together
-deconv <- deconv %>%
-  left_join(deconv_pCO2_T) %>%
-  left_join(deconv_pCO2_S) %>%
-  left_join(deconv_pCO2_AT) %>%
-  left_join(deconv_pCO2_CT)
-
-# Regressions and tables of key parameters
-var_list <-
-  c(
-  "deconv_pCO2_T",
-  "deconv_pCO2_S",
-  "deconv_pCO2_AT",
-  "deconv_pCO2_CT"
-  )
-lms <- lapply(var_list, function(x) {
-  summary(lm(substitute(i ~ decimal_date(date), list(i = as.name(x))), data = deconv))
-  })
-reg <- NULL
-for (i in 1:length(var_list)) {
-  #one loops through all anomalies
-  # calculate probability of fstatistic because it cannot be extracted from lms above
-  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
-  # slope returned by lm is per second
-  prob <-
-  pf(lms[[i]]$fstatistic[1],
-  lms[[i]]$fstatistic[2],
-  lms[[i]]$fstatistic[3],
-  lower.tail = FALSE)
-  reg <-
-  rbind(reg, as.numeric(
-  c(
-    lms[[i]]$coefficients[2, 1],
-    lms[[i]]$coefficients[2, 2],
-  lms[[i]]$coefficients[2, 4],
-  lms[[i]]$coefficients[1, 1],
-  lms[[i]]$coefficients[1, 2],
-  lms[[i]]$coefficients[1, 4],
-  lms[[i]]$r.squared,
-  prob
-  )
-  ))
-}
-colnames(reg) <-
-  c("Slope",
-  "SE Slope",
-  "P Slope",
-  "Intercept",
-  "SE int.",
-  "P int.",
-  "R2",
-  "P value")
-row.names(reg) <- var_list
-reg_deconv <- reg
-
-# Plot
-#deconv_melt <- melt(deconv, id="date")
-deconv_melt <-  gather(data = deconv, key = variable, value=value, -date)
-fig_deconv_pCO2 <- ggplot(deconv_melt) + geom_point(aes(x=date, y=value, color=variable), size=0.5) +
-  facet_grid(variable ~., scales="free_y") + 
-  xlab("Time") + ylab("pCO2 (uatm")+
-  Mytheme() +
-  scale_colour_discrete(guide="none")
-ggsave(file="../figures/fig_deconv_pCO2.png", fig_deconv, width = 18, height = 20, units = "cm")
-```
-
 ## Air-sea CO2 flux
@@
 
+## Deconvolution of pCO2 changes
+```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
+# We follow the method of Garcia-Ibanez described above.
+# construct a dataframe with monthly means for the entire series (mXX) as well as real data (without prefix m)
+deconv_dat <- tibble(date=as.POSIXct(mean0m$sampling_date), mAT=means_month0m$AT[mean0m$monthd]*1e-6, mCT=means_month0m$CT[mean0m$monthd]*1e-6, mS=means_month0m$Salinity[mean0m$monthd], mT=means_month0m$Temperature[mean0m$monthd], P=mean0m$mean_P, Pt=mean0m$mean_Pt, Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
+)
+
+d <- NULL; deconv <- NULL # d is for the data to use in carb, deconv is to store the results
+deconv <- data_frame(date=as.POSIXct(mean0m$sampling_date))
+d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(mS), !is.na(T)) # we eliminate date with NAs
+deconv_pCO2_T <- data_frame(date=d$date,
+                     deconv_pCO2_T=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$mS, T=d$T, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
+)
+d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(S), !is.na(mT)) # we eliminate date with NAs
+deconv_pCO2_S <- data_frame(date=d$date,
+                     deconv_pCO2_S=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$S, T=d$mT, P=d$P, Pt=d$Pt, 
+                                      Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
+                     )
+d <- filter(deconv_dat, !is.na(AT), !is.na(mCT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
+deconv_pCO2_AT <- data_frame(date=d$date,
+                     deconv_pCO2_AT=carb(flag=15, var1=d$AT, var2=d$mCT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
+)
+d <- filter(deconv_dat, !is.na(mAT), !is.na(CT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
+deconv_pCO2_CT <- data_frame(date=d$date,
+                     deconv_pCO2_CT=carb(flag=15, var1=d$mAT, var2=d$CT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
+)
+
+# Bring all results together
+deconv <- deconv %>%
+  left_join(deconv_pCO2_T) %>%
+  left_join(deconv_pCO2_S) %>%
+  left_join(deconv_pCO2_AT) %>%
+  left_join(deconv_pCO2_CT)
+
+# Regressions and tables of key parameters
+var_list <-
+  c(
+  "deconv_pCO2_T",
+  "deconv_pCO2_S",
+  "deconv_pCO2_AT",
+  "deconv_pCO2_CT"
+  )
+lms <- lapply(var_list, function(x) {
+  summary(lm(substitute(i ~ decimal_date(date), list(i = as.name(x))), data = deconv))
+  })
+reg <- NULL
+for (i in 1:length(var_list)) {
+  #one loops through all anomalies
+  # calculate probability of fstatistic because it cannot be extracted from lms above
+  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
+  # slope returned by lm is per second
+  prob <-
+  pf(lms[[i]]$fstatistic[1],
+  lms[[i]]$fstatistic[2],
+  lms[[i]]$fstatistic[3],
+  lower.tail = FALSE)
+  reg <-
+  rbind(reg, as.numeric(
+  c(
+    lms[[i]]$coefficients[2, 1],
+    lms[[i]]$coefficients[2, 2],
+  lms[[i]]$coefficients[2, 4],
+  lms[[i]]$coefficients[1, 1],
+  lms[[i]]$coefficients[1, 2],
+  lms[[i]]$coefficients[1, 4],
+  lms[[i]]$r.squared,
+  prob
+  )
+  ))
+}
+colnames(reg) <-
+  c("Slope",
+  "SE Slope",
+  "P Slope",
+  "Intercept",
+  "SE int.",
+  "P int.",
+  "R2",
+  "P value")
+row.names(reg) <- var_list
+reg_deconv <- reg
+
+# Plot
+#deconv_melt <- melt(deconv, id="date")
+deconv_melt <-  gather(data = deconv, key = variable, value=value, -date)
+fig_deconv_pCO2 <- ggplot(deconv_melt) + geom_point(aes(x=date, y=value, color=variable), size=0.5) +
+  facet_grid(variable ~., scales="free_y") + 
+  xlab("Time") + ylab("pCO2 (uatm")+
+  Mytheme() +
+  scale_colour_discrete(guide="none")
+ggsave(file="../figures/fig_deconv_pCO2.png", fig_deconv, width = 18, height = 20, units = "cm")
+```
 ## Maintenance

### 2021-05-25 awipev-CO2.Rmd
start work on deconvolution

@@
 + atmospheric CO2 measured at the Zeppelin station and downloaded on 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999 
-+ wind spreed data collected by the AWI at 10 m height (sent to JPG by P. Fischer, Aug. 2020)
++ wind speed data collected by the AWI at 10 m height (sent to JPG by P. Fischer, Aug. 2020)
 
@@
 ```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
+# First we prepare data. CT is needed for deconvolution
+# we calculate it from at_calc and pCO2
+# nuts are not taken into consideration
+deconv_dat <- d_all %>% # just for this chunk
+  dplyr::select(datetime, sal_fb, temp_fb, pco2_fb, at_calc) %>% 
+  dplyr::mutate(ct_calc = seacarb::carb(
+    flag = 24, var1 = pco2_fb, var2 = at_calc, S=sal_fb, T=25, Patm=1, P=0, Pt=0, Sit=0,
+        k1k2="x", kf="x", ks="d", pHscale="T", b="u74", gas="potential", 
+        warn="y", eos="eos80", long=1.e20, lat=1.e20)
+
+  ))
+
 # We follow the method of Garcia-Ibanez described above.
 # construct a dataframe with monthly means for the entire series (mXX) as well as real data (without prefix m)
+
 deconv_dat <- tibble(date=as.POSIXct(mean0m$sampling_date), mAT=means_month0m$AT[mean0m$monthd]*1e-6, mCT=means_month0m$CT[mean0m$monthd]*1e-6, mS=means_month0m$Salinity[mean0m$monthd], mT=means_month0m$Temperature[mean0m$monthd], P=mean0m$mean_P, Pt=mean0m$mean_Pt, Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)

### 2021-05-25 awipev-CO2.Rmd
deconvolution in progress

@@
 
-```{r pco2 to fco2, echo=FALSE, warning=FALSE, message=FALSE}
+```{r pco2 and fco2 at in situ temp, echo=FALSE, warning=FALSE, message=FALSE}
 d_all <- d_all %>%
   dplyr::mutate(
+    pco2_fb_insi_temp = seacarb::pCO2insi(
+      pCO2lab = pco2_fb,
+      Tlab = temp_fb,
+      SST = temp_insitu_11m),
     fco2_fb = seacarb::p2fCO2(
@@
       SST = temp_insitu_11m)
-)
+) %>% 
+  dplyr::select(sort(current_vars()))
 
@@
 
-We first calculate fCO2 from pCO2 and then express fCO2 at in situ temperature.
+We first calculate fCO2 from pCO2 and then express both pCO2 and fCO2 at in situ temperature.
 Ideally, this should be done with SST as the goal is to estimate air-sea CO2 fluxes.

### 2021-05-27 awipev-CO2.Rmd
still on deconvolution

@@
 ```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
-# We follow the method of Garcia-Ibanez described above.
-# construct a dataframe with monthly means for the entire series (mXX) as well as real data (without mrefix m)
+# First we prepare data. CT is needed for deconvolution
+# we calculate it from at_calc and pCO2
+# nuts are not taken into consideration
+deconv_tmp <- d_all %>% # just for this chunk
+  dplyr::select(datetime, monthd, sal_fb, temp_fb, pco2_fb, at_calc) %>% 
+  tidyr::drop_na() %>% 
+  dplyr::mutate(ct_calc = seacarb::carb(
+    flag = 24, var1 = deconv_tmp$pco2_fb, var2 = deconv_tmp$at_calc*1e-6, S=deconv_tmp$sal_fb, T=deconv_tmp$temp_fb, 
+    Patm=1, P=1.1, Pt=0, Sit=0, 
+    k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
+    )
+deconv_monthly <-  deconv_tmp %>% 
+  dplyr::group_by(monthd) %>% 
+  dplyr::summarise(
+    sal_fb = mean(sal_fb, na.rm = TRUE),
+    temp_fb = mean(temp_fb, na.rm = TRUE),
+    pco2_fb = mean(pco2_fb, na.rm = TRUE),
+    at_calc = mean(at_calc, na.rm = TRUE),
+    ct_calc = mean(ct_calc, na.rm = TRUE)
+  ) %>% 
+  dplyr::ungroup()
+
 deconv_dat <- tbl_df(
@@
 # nuts are not taken into consideration
-deconv_dat <- d_all %>% # just for this chunk
-  dplyr::select(datetime, sal_fb, temp_fb, pco2_fb, at_calc) %>% 
+deconv_tmp <- d_all %>% # just for this chunk
+  dplyr::select(datetime, monthd, sal_fb, temp_fb, pco2_fb, at_calc) %>% 
   dplyr::mutate(ct_calc = seacarb::carb(
     flag = 24, var1 = pco2_fb, var2 = at_calc, S=sal_fb, T=25, Patm=1, P=0, Pt=0, Sit=0,
-        k1k2="x", kf="x", ks="d", pHscale="T", b="u74", gas="potential", 
+        k1k2="l", kf="dg", ks="d", pHscale="T", b="u74", gas="potential", 
         warn="y", eos="eos80", long=1.e20, lat=1.e20)
-
-  ))
+    )
+deconv_monthly <-  d_all %>% 
+  dplyr::group_by(monthd) %>% 
+  dplyr::summarise(
+    sal_fb = mean(sal_fb, na.rm = TRUE),
+    temp_fb = mean(temp_fb, na.rm = TRUE),
+    pco2_fb = mean(pco2_fb, na.rm = TRUE),
+    at_calc = mean(at_calc, na.rm = TRUE),
+    ct_calc = mean(ct_calc, na.rm = TRUE)
+  ) %>% 
+  ungroup()
 

### 2021-05-27 awipev-CO2.Rmd
deconvolution continued

@@
   dplyr::select(datetime, monthd, sal_fb, temp_fb, pco2_fb, at_calc) %>% 
-  tidyr::drop_na() %>% 
+  tidyr::drop_na()
+deconv_tmp <- deconv_tmp %>% 
   dplyr::mutate(ct_calc = seacarb::carb(
@@
     Patm=1, P=1.1, Pt=0, Sit=0, 
-    k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")
+    k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$DIC * 1e6
     )
@@
 
-deconv_dat <- tbl_df(
-  data.frame(date=as.POSIXct(mean0m$sampling_date), mAT=means_month0m$AT[mean0m$monthd]*1e-6, mCT=means_month0m$CT[mean0m$monthd]*1e-6, mS=means_month0m$Salinity[mean0m$monthd], mT=means_month0m$Temperature[mean0m$monthd], P=mean0m$mean_P, Pt=mean0m$mean_Pt, Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
-)
+deconv_dat <- tibble(sampling_date=deconv_tmp$sampling_date, mAT=deconv_monthly$at_calc[deconv_tmp$monthd]*1e-6, mCT=deconv_monthly$ct_calc[deconv_tmp$monthd]*1e-6, mS=deconv_monthly$sal_fb[deconv_tmp$monthd], mT=deconv_monthly$temp_fb[deconv_tmp$monthd], P=deconv_tmp$depth/10, Pt=rep("NA", length.out=nrow(deconv_tmp)), Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
 

### 2021-06-01 awipev-CO2.Rmd
deconvolution completed

@@
 
-deconv_dat <- tibble(sampling_date=deconv_tmp$sampling_date, mAT=deconv_monthly$at_calc[deconv_tmp$monthd]*1e-6, mCT=deconv_monthly$ct_calc[deconv_tmp$monthd]*1e-6, mS=deconv_monthly$sal_fb[deconv_tmp$monthd], mT=deconv_monthly$temp_fb[deconv_tmp$monthd], P=deconv_tmp$depth/10, Pt=rep("NA", length.out=nrow(deconv_tmp)), Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
+deconv_dat <- tibble(sampling_date=deconv_tmp$datetime, mAT=deconv_monthly$at_calc[deconv_tmp$monthd]*1e-6, mCT=deconv_monthly$ct_calc[deconv_tmp$monthd]*1e-6, mS=deconv_monthly$sal_fb[deconv_tmp$monthd], mT=deconv_monthly$temp_fb[deconv_tmp$monthd], P=11/10, Pt=rep("NA", length.out=nrow(deconv_tmp)), Sit=rep("NA", length.out=nrow(deconv_tmp)), AT=deconv_tmp$at_calc*1e-6, CT=deconv_tmp$ct_calc*1e-6, S=deconv_tmp$sal_fb, T=deconv_tmp$temp_fb)
 
@@
 # construct a dataframe with monthly means for the entire series (mXX) as well as real data (without prefix m)
+# we do not consider nutrients
 
 deconv_dat <- tibble(date=as.POSIXct(mean0m$sampling_date), mAT=means_month0m$AT[mean0m$monthd]*1e-6, mCT=means_month0m$CT[mean0m$monthd]*1e-6, mS=means_month0m$Salinity[mean0m$monthd], mT=means_month0m$Temperature[mean0m$monthd], P=mean0m$mean_P, Pt=mean0m$mean_Pt, Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
-)
 

### 2021-06-01 awipev-CO2.Rmd
deconvolution completed

@@
 
-deconv_dat <- tibble(sampling_date=deconv_tmp$datetime, mAT=deconv_monthly$at_calc[deconv_tmp$monthd]*1e-6, mCT=deconv_monthly$ct_calc[deconv_tmp$monthd]*1e-6, mS=deconv_monthly$sal_fb[deconv_tmp$monthd], mT=deconv_monthly$temp_fb[deconv_tmp$monthd], P=11/10, Pt=rep("NA", length.out=nrow(deconv_tmp)), Sit=rep("NA", length.out=nrow(deconv_tmp)), AT=deconv_tmp$at_calc*1e-6, CT=deconv_tmp$ct_calc*1e-6, S=deconv_tmp$sal_fb, T=deconv_tmp$temp_fb)
+deconv_dat <- tibble(sampling_date=deconv_tmp$datetime,
+                     date=as.POSIXct(deconv_tmp$datetime),
+                     mAT=deconv_monthly$at_calc[deconv_tmp$monthd]*1e-6, mCT=deconv_monthly$ct_calc[deconv_tmp$monthd]*1e-6, mS=deconv_monthly$sal_fb[deconv_tmp$monthd], mT=deconv_monthly$temp_fb[deconv_tmp$monthd], P=11/10, Pt=rep(0, length.out=nrow(deconv_tmp)), Sit=rep(0, length.out=nrow(deconv_tmp)), AT=deconv_tmp$at_calc*1e-6, CT=deconv_tmp$ct_calc*1e-6, S=deconv_tmp$sal_fb, T=deconv_tmp$temp_fb)
 
 d <- NULL; deconv <- NULL # d is for the data to use in carb, deconv is to store the results
-deconv <- data_frame(date=as.POSIXct(mean0m$sampling_date))
+deconv <- tibble(date=as.POSIXct(deconv_tmp$datetime))
 d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(mS), !is.na(T)) # we eliminate date with NAs
-deconv_pCO2_T <- data_frame(date=d$date,
-                     deconv_pCO2_T=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$mS, T=d$T, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
+
+deconv_pCO2_T <- tibble(date = d$date,
+                        deconv_pCO2_T=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$mS, T=d$T, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2
 )
@@
                      deconv_pCO2_S=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$S, T=d$mT, P=d$P, Pt=d$Pt, 
-                                      Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
+                                      Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2
                      )
@@
 deconv_pCO2_AT <- data_frame(date=d$date,
-                     deconv_pCO2_AT=carb(flag=15, var1=d$AT, var2=d$mCT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
+                     deconv_pCO2_AT=carb(flag=15, var1=d$AT, var2=d$mCT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2
 )
@@
 deconv_pCO2_CT <- data_frame(date=d$date,
-                     deconv_pCO2_CT=carb(flag=15, var1=d$mAT, var2=d$CT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
+                     deconv_pCO2_CT=carb(flag=15, var1=d$mAT, var2=d$CT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2
 )
@@
   scale_colour_discrete(guide="none")
-ggsave(file="../figures/fig_deconv_pCO2.png", fig_deconv, width = 18, height = 20, units = "cm")
+ggsave(file="figures/fig_deconv_pCO2.png", fig_deconv_pCO2, width = 18, height = 20, units = "cm")
 ```

### 2021-06-01 awipev-CO2.Rmd
changed stratification & xCO2 at insitu temp; deleted duplicate deconvolution chunk

@@
       fCO2lab = fco2_fb,
+      Tlab = temp_fb,
+      SST = temp_insitu_11m),
+    pco2_calc_fb_insi_temp = seacarb::pCO2insi(
+      pCO2lab = pco2_calc_fb,
+      Tlab = temp_fb,
+      SST = temp_insitu_11m),
+    fco2_calc_fb = seacarb::p2fCO2(
+      pCO2 = pco2_calc_fb,
+      T = temp_fb,
+      Patm = 1,
+      P = 0),
+    fco2_calc_fb_insi_temp = seacarb::fCO2insi(
+      fCO2lab = fco2_calc_fb,
       Tlab = temp_fb,
@@
                 median8_12m = "10") %>% 
-  dplyr::mutate(sal_range = median0_4m - median8_12m)
-kable(tmp_delta, digits = 2, caption = "Median salinity")
+  dplyr::mutate(sal_delta = median0_4m - median8_12m)
+kable(tmp_delta, digits = 2, caption = "Median salinity with (median0_4m - median8_12m)")
 
@@
                 median8_12m = "10") %>% 
-  dplyr::mutate(temp_range = median0_4m - median8_12m)
-kable(tmp_delta, digits = 2, caption = "Median temperature")
+  dplyr::mutate(temp_delta = median0_4m - median8_12m)
+kable(tmp_delta, digits = 2, caption = "Median temperature with (median0_4m - median8_12m)")
 
@@
                 median8_12m = "10") %>% 
-  dplyr::mutate(den_med = median0_4m - median8_12m)
-kable(tmp_delta, digits = 2, caption = "Median density")
+  dplyr::mutate(den_delta = median0_4m - median8_12m)
+kable(tmp_delta, digits = 2, caption = "Median density with (median0_4m - median8_12m)")
 
@@
 
-## Deconvolution of pCO2 changes
-```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
-# First we prepare data. CT is needed for deconvolution
-# we calculate it from at_calc and pCO2
-# nuts are not taken into consideration
-deconv_tmp <- d_all %>% # just for this chunk
-  dplyr::select(datetime, monthd, sal_fb, temp_fb, pco2_fb, at_calc) %>% 
-  dplyr::mutate(ct_calc = seacarb::carb(
-    flag = 24, var1 = pco2_fb, var2 = at_calc, S=sal_fb, T=25, Patm=1, P=0, Pt=0, Sit=0,
-        k1k2="l", kf="dg", ks="d", pHscale="T", b="u74", gas="potential", 
-        warn="y", eos="eos80", long=1.e20, lat=1.e20)
-    )
-deconv_monthly <-  d_all %>% 
-  dplyr::group_by(monthd) %>% 
-  dplyr::summarise(
-    sal_fb = mean(sal_fb, na.rm = TRUE),
-    temp_fb = mean(temp_fb, na.rm = TRUE),
-    pco2_fb = mean(pco2_fb, na.rm = TRUE),
-    at_calc = mean(at_calc, na.rm = TRUE),
-    ct_calc = mean(ct_calc, na.rm = TRUE)
-  ) %>% 
-  ungroup()
-
-# We follow the method of Garcia-Ibanez described above.
-# construct a dataframe with monthly means for the entire series (mXX) as well as real data (without prefix m)
-# we do not consider nutrients
-
-deconv_dat <- tibble(date=as.POSIXct(mean0m$sampling_date), mAT=means_month0m$AT[mean0m$monthd]*1e-6, mCT=means_month0m$CT[mean0m$monthd]*1e-6, mS=means_month0m$Salinity[mean0m$monthd], mT=means_month0m$Temperature[mean0m$monthd], P=mean0m$mean_P, Pt=mean0m$mean_Pt, Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
-
-d <- NULL; deconv <- NULL # d is for the data to use in carb, deconv is to store the results
-deconv <- data_frame(date=as.POSIXct(mean0m$sampling_date))
-d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(mS), !is.na(T)) # we eliminate date with NAs
-deconv_pCO2_T <- data_frame(date=d$date,
-                     deconv_pCO2_T=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$mS, T=d$T, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
-)
-d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(S), !is.na(mT)) # we eliminate date with NAs
-deconv_pCO2_S <- data_frame(date=d$date,
-                     deconv_pCO2_S=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$S, T=d$mT, P=d$P, Pt=d$Pt, 
-                                      Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
-                     )
-d <- filter(deconv_dat, !is.na(AT), !is.na(mCT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
-deconv_pCO2_AT <- data_frame(date=d$date,
-                     deconv_pCO2_AT=carb(flag=15, var1=d$AT, var2=d$mCT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
-)
-d <- filter(deconv_dat, !is.na(mAT), !is.na(CT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
-deconv_pCO2_CT <- data_frame(date=d$date,
-                     deconv_pCO2_CT=carb(flag=15, var1=d$mAT, var2=d$CT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
-)
-
-# Bring all results together
-deconv <- deconv %>%
-  left_join(deconv_pCO2_T) %>%
-  left_join(deconv_pCO2_S) %>%
-  left_join(deconv_pCO2_AT) %>%
-  left_join(deconv_pCO2_CT)
-
-# Regressions and tables of key parameters
-var_list <-
-  c(
-  "deconv_pCO2_T",
-  "deconv_pCO2_S",
-  "deconv_pCO2_AT",
-  "deconv_pCO2_CT"
-  )
-lms <- lapply(var_list, function(x) {
-  summary(lm(substitute(i ~ decimal_date(date), list(i = as.name(x))), data = deconv))
-  })
-reg <- NULL
-for (i in 1:length(var_list)) {
-  #one loops through all anomalies
-  # calculate probability of fstatistic because it cannot be extracted from lms above
-  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
-  # slope returned by lm is per second
-  prob <-
-  pf(lms[[i]]$fstatistic[1],
-  lms[[i]]$fstatistic[2],
-  lms[[i]]$fstatistic[3],
-  lower.tail = FALSE)
-  reg <-
-  rbind(reg, as.numeric(
-  c(
-    lms[[i]]$coefficients[2, 1],
-    lms[[i]]$coefficients[2, 2],
-  lms[[i]]$coefficients[2, 4],
-  lms[[i]]$coefficients[1, 1],
-  lms[[i]]$coefficients[1, 2],
-  lms[[i]]$coefficients[1, 4],
-  lms[[i]]$r.squared,
-  prob
-  )
-  ))
-}
-colnames(reg) <-
-  c("Slope",
-  "SE Slope",
-  "P Slope",
-  "Intercept",
-  "SE int.",
-  "P int.",
-  "R2",
-  "P value")
-row.names(reg) <- var_list
-reg_deconv <- reg
-
-# Plot
-#deconv_melt <- melt(deconv, id="date")
-deconv_melt <-  gather(data = deconv, key = variable, value=value, -date)
-fig_deconv_pCO2 <- ggplot(deconv_melt) + geom_point(aes(x=date, y=value, color=variable), size=0.5) +
-  facet_grid(variable ~., scales="free_y") + 
-  xlab("Time") + ylab("pCO2 (uatm")+
-  Mytheme() +
-  scale_colour_discrete(guide="none")
-ggsave(file="../figures/fig_deconv_pCO2.png", fig_deconv, width = 18, height = 20, units = "cm")
-```
 ## Maintenance

### 2021-06-02 awipev-CO2.Rmd
Added plot stratification (deltas)

@@
 
+sal_delta_plt <- tmp_delta %>% 
+  ggplot(aes(x=montht, y=sal_delta)) +
+  labs(y = "Difference in median salinity", x = "Month") +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 0.65, label = substitute("S"["surface"] ~ "> S"["deep"])) +
+  annotate("text", x = 1.5, y = -0.9, label = substitute("S"["surface"] ~ "< S"["deep"])) +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+
 # we look at temperature all depths
@@
 
+temp_delta_plt <- tmp_delta %>% 
+  ggplot(aes(x=montht, y=temp_delta)) +
+  labs(y = "Difference in median temperature", x = "Month") +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 2.5, label = substitute("T"["surface"] ~ "> T"["deep"])) +
+  annotate("text", x = 1.5, y = -2.5, label = substitute("T"["surface"] ~ "< T"["deep"])) +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+
 # we look at density 0 to 4 m vs more than 8 m
@@
 print(p)
+
+den_delta_plt <- tmp_delta %>% 
+  ggplot(aes(x=montht, y=den_delta)) +
+  labs(y = "Difference in median density", x = "Month") +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 0.1, label = substitute("D"["surface"] ~ "> D"["deep"])) +
+  annotate("text", x = 1.5, y = -1.2, label = substitute("D"["surface"] ~ "< D"["deep"])) +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+
+deltas <- sal_delta_plt / temp_delta_plt / den_delta_plt
+ggsave(filename = "figures/deltas.png", plot = deltas, width = 15, height = 20, units = "cm")
 ```

### 2021-06-03 awipev-CO2.Rmd
Added statification pH

--- 2021-06-01 awipev-CO2.Rmd
@@
 
+sal_delta_plt <- tmp_delta %>% 
+  ggplot(aes(x=montht, y=sal_delta)) +
+  labs(y = "Difference in median salinity", x = "") +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 0.65, label = substitute("S"["surface"] ~ "> S"["deep"])) +
+  annotate("text", x = 1.5, y = -0.9, label = substitute("S"["surface"] ~ "< S"["deep"])) +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+
 # we look at temperature all depths
@@
 
+temp_delta_plt <- tmp_delta %>% 
+  ggplot(aes(x=montht, y=temp_delta)) +
+  labs(y = "Difference in median temperature", x = "") +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 2.5, label = substitute("T"["surface"] ~ "> T"["deep"])) +
+  annotate("text", x = 1.5, y = -2.5, label = substitute("T"["surface"] ~ "< T"["deep"])) +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+
 # we look at density 0 to 4 m vs more than 8 m
@@
 print(p)
+
+den_delta_plt <- tmp_delta %>% 
+  ggplot(aes(x=montht, y=den_delta)) +
+  labs(y = "Difference in median density", x = "") +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 0.1, label = substitute("D"["surface"] ~ "> D"["deep"])) +
+  annotate("text", x = 1.5, y = -1.2, label = substitute("D"["surface"] ~ "< D"["deep"])) +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+
+# we look at pHint_tot_sf 0 to 4 m vs more than 8 m
+tmp <- d_all %>% 
+  dplyr::mutate(depth_group = depth_group_pressure) %>% 
+  dplyr::select(montht, pHint_tot_sf, depth_group) %>%
+  dplyr::mutate(depth = as.factor(ifelse(depth_group == 1 | depth_group == 3, 2, depth_group))) %>% 
+  dplyr::filter(depth == 2 | depth == 10) %>% 
+  group_by(depth, montht)
+summary(aov(tmp$pHint_tot_sf ~ tmp$depth * tmp$montht))
+
+tmp_delta <- tmp %>% 
+  group_by(depth, montht) %>% 
+  dplyr::summarise(pH_tot_sf_med = median(pHint_tot_sf, na.rm = TRUE)) %>% 
+  tidyr::pivot_wider(names_from = depth, values_from = pH_tot_sf_med) %>% 
+  dplyr::rename(median0_4m = "2",
+                median8_12m = "10") %>% 
+  dplyr::mutate(pH_tot_sf_med_delta = median0_4m - median8_12m)
+kable(tmp_delta, digits = 3, caption = "Median seafet pH with (median0_4m - median8_12m)")
+
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "pH vs depth", x = "Depth (m)", y= "pHint_tot_sf") +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+
+pH_delta_plt <- tmp_delta %>% 
+  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
+  labs(y = "Difference in median pH at in situ temperature", x = "Month") +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 0.1, label = substitute("pH"["surface"] ~ "> pH"["deep"])) +
+  annotate("text", x = 1.5, y = -0.1, label = substitute("pH"["surface"] ~ "< pH"["deep"])) +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+
+deltas <- sal_delta_plt / temp_delta_plt / den_delta_plt
+ggsave(filename = "figures/deltas.png", plot = deltas, width = 15, height = 20, units = "cm")
 ```

### 2021-06-09 awipev-CO2.Rmd
fiddling with stratification plot

--- 2021-06-01 awipev-CO2.Rmd
@@
 
+sal_delta_plt <- tmp_delta %>% 
+  ggplot(aes(x=montht, y=sal_delta)) +
+  scale_x_discrete(expand = c(0, 0)) +
+  scale_y_continuous("Salinity", limits = c(-1.1, 0.8), expand = c(0, 0)) +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 0.65, label = substitute("S"["surface"] ~ "> S"["deep"])) +
+  annotate("text", x = 1.5, y = -0.9, label = substitute("S"["surface"] ~ "< S"["deep"])) +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+
 # we look at temperature all depths
@@
 
+temp_delta_plt <- tmp_delta %>% 
+  ggplot(aes(x=montht, y=temp_delta)) +
+  scale_x_discrete(expand = c(0, 0)) +
+  scale_y_continuous("Temperature", limits = c(-3, 3), expand = c(0, 0)) +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 2.5, label = substitute("T"["surface"] ~ "> T"["deep"])) +
+  annotate("text", x = 1.5, y = -2.5, label = substitute("T"["surface"] ~ "< T"["deep"])) +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+
 # we look at density 0 to 4 m vs more than 8 m
@@
 print(p)
+
+den_delta_plt <- tmp_delta %>% 
+  ggplot(aes(x=montht, y=den_delta)) +
+  scale_x_discrete(expand = c(0, 0)) +
+  scale_y_continuous("Density", limits = c(-1.5, 0.5), expand = c(0, 0)) +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 0.1, label = substitute("D"["surface"] ~ "> D"["deep"])) +
+  annotate("text", x = 1.5, y = -1.2, label = substitute("D"["surface"] ~ "< D"["deep"])) +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+
+# we look at pHint_tot_sf 0 to 4 m vs more than 8 m
+tmp <- d_all %>% 
+  dplyr::mutate(depth_group = depth_group_pressure) %>% 
+  dplyr::select(montht, pHint_tot_sf, depth_group) %>%
+  dplyr::mutate(depth = as.factor(ifelse(depth_group == 1 | depth_group == 3, 2, depth_group))) %>% 
+  dplyr::filter(depth == 2 | depth == 10) %>% 
+  group_by(depth, montht)
+summary(aov(tmp$pHint_tot_sf ~ tmp$depth * tmp$montht))
+
+tmp_delta <- tmp %>% 
+  group_by(depth, montht) %>% 
+  dplyr::summarise(pH_tot_sf_med = median(pHint_tot_sf, na.rm = TRUE)) %>% 
+  tidyr::pivot_wider(names_from = depth, values_from = pH_tot_sf_med) %>% 
+  dplyr::rename(median0_4m = "2",
+                median8_12m = "10") %>% 
+  dplyr::mutate(pH_tot_sf_med_delta = median0_4m - median8_12m)
+kable(tmp_delta, digits = 3, caption = "Median seafet pH with (median0_4m - median8_12m)")
+
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "pH vs depth", x = "Depth (m)", y= "pHint_tot_sf") +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+
+pH_delta_plt <- tmp_delta %>% 
+  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
+  #labs(y = substitute("pH"["T"] ~ "at in situ temp."), x = "Month") +
+  scale_x_discrete("Month", expand = c(0, 0)) +
+  scale_y_continuous(substitute("pH"["T"] ~ "at in situ temp."), limits = c(-0.2, 0.1), expand = c(0, 0)) +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 0.8, label = substitute("pH"["surface"] ~ "> pH"["deep"])) +
+  annotate("text", x = 1.5, y = -0.15, label = substitute("pH"["surface"] ~ "< pH"["deep"])) +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+
+deltas <- sal_delta_plt / temp_delta_plt / den_delta_plt / pH_delta_plt
+deltas <- deltas + plot_annotation(tag_levels = 'a')
+ggsave(filename = "figures/deltas.png", plot = deltas, width = 15, height = 20, units = "cm")
 ```

### 2021-06-27 awipev-CO2.Rmd
test

@@
 ![ ](Images/AWIPEV-Logo.jpg){width=250px}
+#test
 

### 2021-06-27 awipev-CO2.Rmd
Added pco2 thermal vs biology Takahashi

--- 2021-06-09 awipev-CO2.Rmd
@@
 
+## Takahashi thermal vs biological
+```{r Takahashi thermal vs biological, include=FALSE}
+# Select data
+taka <- d_all %>% # just for this chunk
+  dplyr::select(datetime, monthd, sal_fb, temp_insitu_11m, pco2_fb_insi_temp)
+
+# In order to remove the temperature effect from the observed pCO2 , the observed pCO2 values are normalized to a constant temperature (annual mean) -- Takahashi et al. (2002)
+temp_mean <- mean(taka$temp_insitu_11m, na.rm = TRUE)
+taka <- taka %>% 
+  dplyr::mutate(pco2_mean_temp = pco2_fb_insi_temp * exp(0.0423 * (temp_mean - temp_insitu_11m)))
+d_pco2_bio <- max(taka$pco2_mean_temp, na.rm = TRUE) - min(taka$pco2_mean_temp, na.rm = TRUE)
+d_pco2_temp <- max(taka$pco2_fb_insi_temp, na.rm = TRUE) - min(taka$pco2_fb_insi_temp, na.rm = TRUE)
+temp_bio <- d_pco2_temp / d_pco2_bio
+```
+
 ## Deconvolution of pCO2 changes
@@
 atm_co2_old <-
-  read_delim(file = paste0(path, "atmospheric_co2_zeppelin/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
+  read_delim(file = paste0(path, "atmospheric_co2_zeppelin_old/co2_zep_surface-insitu_54_9999-9999_hourly.txt"),
   delim = " ",

### 2021-07-09 test_deconvolution/point_B_md_report_submitted_ocean_Science copy.Rmd

---
title: "Time series of the carbonate chemistry at Point B"
author: "Jean-Pierre Gattuso, CNRS-UPMC (gattuso@obs-vlfr.fr), Samir Alliouane and Laure Mousseau"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  html_document:
    code_folding: hide
    fig_caption: yes
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
rm(list = ls())
require(seacarb)
library(ggplot2)
library(cowplot)
library(scales)
library(RColorBrewer)
library(gridExtra)
library(reshape2)
library(xtable)
library(zoo)
library(lubridate)
library(nlme)
library(lmtest)
library(dplyr)
library(readr)
library(tidyr)
library(grid)
library(viridis)
library(animation)
library(directlabels)
#library(readxl)
require("knitr")
#install_github("ndphillips/yarrr")
#library("yarrr")

#rm(list = ls())
# To run chunks in console setwd("../")
Sys.setenv(TZ='UTC')
#opts_knit$get("root.dir")
#opts_knit$set(root.dir = '../')
#knitr::opts_chunk$set(echo = TRUE)

#viridis_pal(alpha = 1, begin = 0, end = 1, option = "D")(12)
#show_col(viridis_pal(alpha = 1, begin = 0, end = 1, option = "D")(12))
dc1 <- "#482173FF" #discrete color 1
dc2 <- "#51C56AFF" #discrete color 2: 
#viridis_pal(alpha = 1, begin = 0, end = 1, option = "C")(12)
#show_col(viridis_pal(alpha = 1, begin = 0, end = 1, option = "C")(12))
dc3 <- "#482173FF" #discrete color 1
dc4 <- "#51C56AFF" #discrete color 2:

size_labs <- 6
face_font <- "plain"

#Mytheme <- function(size_labs = 6, face_font="plain") {theme_bw() + theme(aspect.ratio = 1 / 3)}

Mytheme <- function(size_labs = 6, face_font="plain", ...) {
  theme_bw() +
  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face=face_font, size=size_labs, margin=margin(0,0,0,0,"pt")),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face=face_font, size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_line(size = 0.25, color="black", linetype="dotted"),
        aspect.ratio = 1 / 3,
        plot.margin = margin(t = 0, r = 1, b = 0, l = 0, unit = "lines")
  )
}

Mytheme_facet <- function(size_labs = 6, face_font="plain") {
  theme_bw() +
  theme(axis.text.x = element_text(face=face_font, size=size_labs, color="black"),
        axis.title.x = element_text(face=face_font, size=size_labs, margin=margin(0,0,0,0,"pt")),
        axis.text.y = element_text(face=face_font, color="black", size=size_labs),
        axis.title.y = element_text(face=face_font, size=size_labs),
        axis.ticks.x = element_line(size=0.1),
        axis.ticks.y = element_line(size=0.1),
        axis.ticks.length = unit(1.1, "mm"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        aspect.ratio = 1,
        plot.margin = margin(t = 0, r = 1, b = 0, l = 0, unit = "lines")
  )
}
# to add panel numbers at top left 
size_grob <- 8
grob_A <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(a)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_B <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(b)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_C <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(c)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_D <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(d)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_E <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(e)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_F <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(f)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_G <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(g)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_H <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(h)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_I <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(i)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_J <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(j)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_K <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(k)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_L <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(l)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_M <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(m)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_N <- grobTree(rectGrob(x=0.04, y=0.90, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(n)",x=0.04, y=0.90, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))

# to add panel numbers at bottom left 
size_grob <- 9
grob_A_bl <- grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(a)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_B_bl <- grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(b)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_C_bl <- grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(c)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_D_bl <- grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(d)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_E_bl <- grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(e)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_F_bl <- grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(f)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_G_bl <- grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(g)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_H_bl <- grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(h)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_I_bl <- grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(i)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_J_bl <-grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(j)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_K_bl <- grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(k)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_L_bl <- grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(l)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_M_bl <- grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(m)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
grob_N_bl <- grobTree(rectGrob(x=0.04, y=0.1, width=0.04, height=0.12,
                            default.units="npc",
                            just=c("centre", "centre"),
                            gp=gpar(col="white", fill="white"),
                            vp=NULL),
                   textGrob("(n)",x=0.04, y=0.1, 
                            just=c("centre", "centre"),
                            gp=gpar(col="black",
                                    fontsize=size_grob,
                                    fontface="bold")))
# To add regression line on ggplots
# use as annotate(aes(x = 25, y = 300, label = lm_eqn(lm(y ~ x, df))), parse = TRUE)
# http://stackoverflow.com/questions/7549694/ggplot2-adding-regression-line-equation-and-r2-on-graph
lm_eqn = function(m) {
  l <- list(a = format(coef(m)[1], digits = 2),
      b = format(abs(coef(m)[2]), digits = 2),
      r2 = format(summary(m)$r.squared, digits = 3));
  if (coef(m)[2] >= 0)  {
    eq <- substitute(italic(y) == a + b %.% italic(x)*","~~italic(r)^2~"="~r2,l)
  } else {
    eq <- substitute(italic(y) == a - b %.% italic(x)*","~~italic(r)^2~"="~r2,l)    
  }
  as.character(as.expression(eq));                 
}

```
```{r test regression, include=FALSE}
# This is to test linear regressions with dates
# Conclusion is that the slope is per day but I have decided to use decimal_date() to avoid any confusion
dt <- as_date(c("1916-06-16", "2016-06-15"))
temp <- c(20, 21)
dat <- data.frame(dt, temp)
reg <- lm(data=dat,temp ~ dt)
slope <- 365*coef(reg)[2]
```

# Material and methods

Samples were collected from XX-l Niskin bottles, transferred to glass bottles, overfilled and then poisoned to maintain the integrity of the sample chemistry as recommended by Dickson et al. (2007).  The _Service National d'Analyse des Paramètres Océaniques du CO$_2$_, at the _Université Pierre et Marie Curie_, determined the concentration of dissolved inorganic carbon ($C_\mathrm{T}$) and total alkalinity ($A_\mathrm{T}$), by potentiometric titration, following the methods described by (Edmond1970) and (DOE1994).

Calculations of the carbonate system parameters were performed using the R package \emph{seacarb} (Lavigne2014). The total concentrations of silicate and phosphate were used when available. Otherwise they were set to 0. The total boron concentration was calculated using the formulation of (Lee2010b). The following constants were used: $K_1$ and $K_2$ from (Lueker2000, $K_f$ from (Perez1987b) and $K_s$ from (Dickson1990).

## Data available and quality control
All data are used in the following; none were eliminated according to the quality flags (\textbf{this remains to be done}).

### Les codes du SNAPOCO2

Les "quality flags" "qflag\_sample", "qflag\_ta", "qflag\_DIC" qui apparaissent dans les fichiers de données du LOCEAN sont établis sur la base des codes WOCE (World Ocean Circulation Experiment) : WOCE Operations Manual (1994), WHP Office Report 90-1, WOCE Report N.67/91, p52-53. Woods Hole, Mass., USA.

- Données AT et CT et water sample quality flag : (i.e pour les étapes : "qflag\_ta"et "qflag\_DIC")
  - flag 0 : Dosage avorté (échantillon perdu),
	- flag 2 : dosage correct,
	- flag 3 : dosage douteux

- Codification quality flag réception flacon : (i.e pour l'étape : "qflag\_sample")
	- A : OK;
	- B : mal rempli;
	- C : flacon cassé;
	- D : bouchon cassé;
	- E : dépôt, particule dans le flacon;
	- F : sel au goulot;
	- G : manque de graisse au goulot;
	- H : pas d'élastique.

### Les codes de Villefranche (inspirés des codes SOMLIT)

- Codification qflag\_taking concernant le prélèvement des échantillons en mer : (i.e pour l'étape : "qflag\_taking")
	- 0 : ancien code qui signifie OK
	- 2 : nouveau code qui signifie OK
	- 3 : prélèvement douteux
	- 4 : prélèvement mauvais

- Codification qflag\_final, qui correspond au code "final" des résultats TA et DIC (i.e pour l'étape : "qflag\_final"). Comme TA et DIC sont déterminés par la même titration, qflag\_ta et qflag\_DIC devrait être identiques. Ce n'est pas le cas en décembre 2009 où il manque des qflag\_DIC. On a alors considéré que qflag\_final = qflag\_ta.

	- 0 : Dosage avorté (échantillon perdu)
	- 2 : résultat OK
	- 3 : résultat douteux
	- 4 : résultat mauvais

## Point B

```{r Initialization Point B, include=FALSE}
# read data and create a data frame tbl
z <- tbl_df(
  read_delim(
  paste0("./", "Data_DIC.csv"),
  delim = ",",
  col_names = TRUE,
  col_types = "cDcdddddddcddddddddddddddd",
  skip = 0,
  na = c("NA", "999999")
  )
  ) #%>% 
  #dplyr::mutate(sampling_date = as.POSIXct(sampling_date, format = "%d/%m/%Y"))
H <- NULL
#z$measure_date <- as.POSIXct(z$measure_date)
z$sampling_date <- as.POSIXct(z$sampling_date) # in order to plot easily
z$year <- year(z$sampling_date)
z$monthd <- month(z$sampling_date)
z$quarter <- quarter(z$sampling_date)
z$month <- month(z$sampling_date, label = TRUE, abbr = FALSE)
#render all variables as.numeric instead of character
z$salinity_field <- as.numeric(z$salinity_field)
# convert from umol/l to umol/kg
z$PO4 <- as.numeric(z$PO4 / (rho(S= z$salinity_field,T = z$temp_field , P= 0) / 1000))
z$SIOH4 <- as.numeric(z$SIOH4 / (1000 * rho(S= z$salinity_field,T = z$temp_field , P= 0) / 1000))

# all flags changed into factors
z$qflag_taking <- as.factor(z$qflag_taking)     
z$qflag_sample <- as.factor(z$qflag_sample)     
z$qflag_ta <- as.factor(z$qflag_ta)
z$qflag_dic <- as.factor(z$qflag_dic)
z$qflag_final <- as.factor(z$qflag_final)

# Exclude 2016 data
zz <- dplyr::filter(z, sampling_date < "2016-01-01")

# read POC and PON data
# pom <- read_csv(file = "../data/POC-PON/POC-2007-2015_PtB_1m.csv", comment="#")
# pom$date <- as.POSIXct(pom$date)
```

```{r Check outliers, include=FALSE}
# "C" means "check"
# Check for outliers at 1 m
CAT1 <- ggplot(dplyr::filter(z, depth == 0), aes(x = sampling_date, y = ta, color = qflag_ta)) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(na.rm=TRUE) +
  theme_bw() + 
  labs(y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")")),x="",title="Total alkalinity at 1 m")
#remove outliers and replot
z$ta[which(z$ta > 2900 & z$depth == 0)] <- NA #this is an identifed outlier
CAT1 <- ggplot(dplyr::filter(z, depth == 0), aes(x = sampling_date, y = ta, color = qflag_ta)) +
  geom_point(na.rm=TRUE) +
  theme_bw() + 
  labs(y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")")),x="",title="Total alkalinity at 1 m, 1 outlier > 2900 removed")

CCT1 <- ggplot(dplyr::filter(z, depth == 0), aes(x = sampling_date, y = dic, color = qflag_dic)) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(na.rm=TRUE) +
  theme_bw() + 
  labs(y = expression(paste(italic(C)[T]," ","(",mu, mol.kg^-1,")")),x="",title="Dissolved inorganic carbon at 1 m")
#remove outliers and replot
z$dic[which(z$dic > 2300 & z$depth ==0)] <- NA #this is an indentifed outlier
CCT1 <- ggplot(dplyr::filter(z, depth == 0), aes(x = sampling_date, y = dic, color = qflag_dic)) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(na.rm=TRUE) +
  theme_bw() + 
  labs(y = expression(paste(italic(C)[T]," ","(",mu, mol.kg^-1,")")),x="",title="Dissolved inorganic carbon at 1 m, 3 data > 2300 removed")

# Check for outliers at 50 m
CAT50 <- ggplot(dplyr::filter(z, depth == 50), aes(x = sampling_date, y = ta, color = qflag_ta)) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(na.rm=TRUE) +
  theme_bw() + 
  labs(y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")")),x="",title="Total alkalinity at 50 m")
#remove outliers and replot
z$ta[which(z$ta < 2500 & z$depth == 50)] <- NA #this is an indentifed outlier
CAT50 <- ggplot(dplyr::filter(z, depth == 50), aes(x = sampling_date, y = ta, color = qflag_ta)) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(na.rm=TRUE) +
  theme_bw() + 
  labs(y = expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")")),x="",title="Total alkalinity at 50 m, 1 data < 2500 removed")

#remove outliers and replot
# no outlier identified
CCT50 <- ggplot(dplyr::filter(z, depth == 50), aes(x = sampling_date, y = dic, color = qflag_dic)) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(na.rm=TRUE) +
  theme_bw() + 
  labs(y = expression(paste(italic(C)[T]," ","(",mu, mol.kg^-1,")")),x="",title="Dissolved inorganic carbon at 50 m, no outlier removed")

#combine graphs on one page
png(file = "./fig_outliers.png",
    width = 17, height = 25, units = "cm", res = 300)
grid.arrange(CAT1, CCT1, CAT50, CCT50, ncol=1)
dev.off()
```

```{r calculate derived parameters and save data, include=FALSE}
#select all rows containing NA for one of the 4 key variables
NArows <- dplyr::filter(z, is.na(z$salinity_field & z$dic & z$ta & z$temp_field)) # rows with NAs

#select all rows containing data because the carb function does not work with NAs
dat <- dplyr::filter(z, ta != "NA" & dic != "NA" & salinity_field != "NA" & temp_field != "NA")

# add pH and Omega calcite (to dat)
carb <- carb(flag=15, var1=dat$ta*1e-6, var2=dat$dic*1e-6, S=dat$salinity_field,
             T=dat$temp_field, P=dat$depth/10, Pt=1e-6*dat$PO4, Sit=1e-6*dat$SIOH4, 
             k1k2 = "l", kf = "pf", pHscale = "T", b="l10")
dat$pH <- carb$pH
dat$CO2 <- carb$CO2
dat <- dplyr::mutate(dat,
              CSC_flag = carb$flag,
              HCO3 = carb$HCO3,
              CO3 = carb$CO3,
              OmegaCalcite = as.numeric(carb$OmegaCalcite),
              OmegaAragonite = as.numeric(carb$OmegaAragonite),
              pH25 = pHinsi(pH=dat$pH,ALK=dat$ta*1e-6,Tinsi=25,
                            Tlab=dat$temp_field,S=dat$salinity_field,
                            Pt=1e-6*dat$PO4, Sit=1e-6*dat$SIOH4, k1k2 = "l", 
                            kf = "pf", pHscale = "T"),
              pCO2 = carb$pCO2,
              fCO2 = carb$fCO2,
              Nta = 1e6 * carb$ALK * 38 / dat$salinity_field,
              Ndic = 1e6 * carb$DIC * 38 / dat$salinity_field
              )

#merge back all NArows (they were temporarily eliminated for the data processing above)
#first add missing columns
f <- as.data.frame(matrix(as.numeric(NA), nrow = nrow(NArows), ncol = 12))

#name the columns (same column names as dat)
colnames(f)=c("pH", "CO2", "CSC_flag", "HCO3", "CO3", "OmegaCalcite", "OmegaAragonite", 
              "pH25", "pCO2" ,"fCO2",	"Nta",	"Ndic")

#bind to dat
NArows <- cbind(NArows,f)

#bind dates
dat <- rbind(dat, NArows)

#arrange by dates
dat <- arrange(dat, sampling_date)

#Prepare data to upload to Pangaea 
pangaea <- select(dat, sampling_date, depth, CSC_flag, salinity_field, 
                  temp_field, HCO3, CO3,
                  pH, ta, dic, OmegaCalcite,
                  OmegaAragonite, pCO2, fCO2)

#save data
# write.table(dat, paste0("output/", Sys.Date(), "_output.csv"), sep= ",", dec=".", row.names = FALSE)
# write.table(pangaea, paste0("output/", Sys.Date(), "_pangaea.csv"), sep= ",", dec=".", row.names = FALSE)
# write_rds(dat, paste0("output/", Sys.Date(), "_output.rds"))
write_csv(dat, file="./output.csv")
write_csv(pangaea, file="./output_pangaea.csv")
write_rds(dat, "./output.rds")
```

```{r Calculate mean values, include=FALSE}
means_depth <- dat %>%
  group_by(depth, sampling_date) %>%
  dplyr::summarise(
            mean_salinity=mean(salinity_field, na.rm=TRUE),
            mean_temperature=mean(temp_field, na.rm=TRUE),
            mean_Chla=mean(Chla, na.rm=TRUE),
            mean_dic=mean(dic, na.rm=TRUE),
            mean_ta=mean(ta, na.rm=TRUE),
            mean_Nta=mean(Nta,na.rm=TRUE),
            mean_Ndic=mean(Ndic,na.rm=TRUE),
            mean_pH=mean(pH, na.rm=TRUE),
            mean_pH25=mean(pH25, na.rm=TRUE),
            mean_pCO2=mean(pCO2, na.rm=TRUE),
            mean_OmegaCalcite=mean(OmegaCalcite, na.rm=TRUE),
            mean_OmegaAragonite=mean(OmegaAragonite, na.rm=TRUE),
            mean_Chla=mean(Chla, na.rm=TRUE),
            mean_P=mean(depth/10, na.rm=TRUE),
            mean_Pt=mean(1e-6*PO4, na.rm=TRUE),
            mean_Sit=mean(1e-6*SIOH4, na.rm=TRUE)
            ) %>%
  dplyr::mutate(
    year = year(sampling_date),
    quarter = quarter(sampling_date),
    monthd = month(sampling_date),
    month = month(sampling_date, label = TRUE, abbr = FALSE),
    week = week(sampling_date)
    ) %>%
    dplyr::arrange(depth)

# The above generates NaNs which are replaced by NAs
is.na(means_depth) <- is.na(means_depth)
write.table(means_depth, paste0("./output_somlit.csv"), sep= ",", dec=".", row.names = FALSE)

#separate each means_depth and handle last incomplete year
mean0m <- dplyr::filter(means_depth, depth==0)
mean50m <- dplyr::filter(means_depth, depth==50)
mean0m_full <- dplyr::filter(means_depth, depth==0, year(sampling_date) < 2016)
mean50m_full <- dplyr::filter(means_depth, depth==50, year(sampling_date) < 2016)
```

```{r Uncertainties}
means_depth_no_NA <- filter(means_depth, !is.na(mean_ta) & !is.na(mean_dic) & !is.na(mean_salinity)  & !is.na(mean_temperature))
  evar1 <-
  mean(c(3.6, 3.5, 1.2, 1.99, 2.4, 3.0, 3.9, 2.6, 0.5, 2.6, 3.2))*1e-6 #AT, extracted from SNAPO-CO2 reports
evar2 <-
  mean(c(3.2, 3.7, 3.4, 2.25, 2, 2.8, 4.9, 4, 1.5, 2.7, 2))      *1e-6 #CT, extracted from SNAPO-CO2 reports

epKstd  <- c(0.002, 0.01,  0.02, 0.01,  0.01, 0.01, 0.01)

tmp <- errors(flag = 15, var1 = means_depth_no_NA$mean_ta*1e-6, var2 = means_depth_no_NA$mean_dic*1e-6, 
  S = means_depth_no_NA$mean_salinity, T = means_depth_no_NA$mean_temperature, P = means_depth_no_NA$depth/10, Pt = 1e-6*means_depth_no_NA$mean_Pt, Sit = 1e-6*means_depth_no_NA$mean_Sit,
  evar1 = evar1, evar2 = evar1, eS = 0.01, eT = 0.1, ePt = 0, eSit = 0,
  epK = epKstd, 
  #method = "ga", r = 0.0, runs = 10000, 
  k1k2 = "l", kf = "pf", pHscale = "T", b = "l10", warn = "y"
  )
mean_err <- tmp %>% summarise_each(funs(mean))

# Calculate the average percent errors for key parameters
mean_err_percent <- data.frame(
  H = mean(100 * tmp$H / 10^-(means_depth_no_NA$mean_pH)),
  pH =mean(100 * tmp$pH / means_depth_no_NA$mean_pH),
  pCO2 = mean(100 * tmp$pCO2 / means_depth_no_NA$mean_pCO2),
  pCO2 = mean(100 * tmp$pCO2 / means_depth_no_NA$mean_pCO2),
  OmegaAragonite = mean(100 * tmp$OmegaAragonite / means_depth_no_NA$mean_OmegaAragonite),
  OmegaCalcite   = mean(100 * tmp$OmegaCalcite   / means_depth_no_NA$mean_OmegaCalcite)
)
```

The average uncertainties of the derived carbonate parameters were calculated according to the Gaussian method (Dickson & Riley, 1978) implemented in the "errors" function of the R package seacarb 3.1 (Gattuso et al., 2016). More detail is available in Orr et al. (sbm). The uncertainties are `r format(mean_err$H, digits =1, scientific = TRUE)` mol H+, `r format(mean_err$pH, digits=3)` pH units), `r format(mean_err$pCO2, digits=0)` umol pCO2, and `r format(mean_err$OmegaAragonite, digits=1)` unit of the aragonite saturation state.

```{r Monthly means, include=TRUE}
# prepare data 0m
tmp <- ungroup(mean0m) %>%
  mutate(month = month(sampling_date, label = TRUE, abb = TRUE)) %>%
  select(
  month,
  mean_temperature,
  mean_salinity,
  mean_Chla,
  mean_ta,
  mean_dic,
  mean_pCO2,
  mean_pH,
  mean_OmegaAragonite
  )
tmp$month <- factor(tmp$month)

means_month0m <- ungroup(mean0m) %>%
  group_by(monthd) %>%
  summarise(
  Salinity = mean(mean_salinity, na.rm = TRUE),
  Salinity_sd = sd(mean_salinity, na.rm = TRUE),
  Salinity_n = sum(!is.na(mean_salinity)),
  Temperature = mean(mean_temperature, na.rm = TRUE),
  Temperature_sd = sd(mean_temperature, na.rm = TRUE),
  Temperature_n = sum(!is.na(mean_temperature)),
  Chla = mean(mean_Chla, na.rm = TRUE),
  Chla_sd = sd(mean_Chla, na.rm=TRUE),
  Chla_n = sum(!is.na(mean_Chla)),
  dic = mean(mean_dic, na.rm = TRUE),
  dic_sd = sd(mean_dic, na.rm = TRUE),
  dic_n = sum(!is.na(mean_dic)),
  ta = mean(mean_ta, na.rm = TRUE),
  ta_sd = sd(mean_ta, na.rm = TRUE),
  ta_n = sum(!is.na(mean_ta)),
  pH = mean(mean_pH, na.rm = TRUE),
  pH_sd = sd(mean_pH, na.rm = TRUE),
  pH_n = sum(!is.na(mean_pH)),
  pH25 = mean(mean_pH25, na.rm = TRUE),
  pH25_sd = sd(mean_pH25, na.rm = TRUE),
  pH25_n = sum(!is.na(mean_pH25)),
  pCO2 = mean(mean_pCO2, na.rm = TRUE),
  pCO2_sd = sd(mean_pCO2, na.rm = TRUE),
  pCO2_n = sum(!is.na(mean_pCO2)),
  OmegaCalcite = mean(mean_OmegaCalcite, na.rm = TRUE),
  OmegaCalcite_sd = sd(mean_OmegaCalcite, na.rm = TRUE),
  OmegaCalcite_n = sum(!is.na(mean_OmegaCalcite)),
  OmegaAragonite = mean(mean_OmegaAragonite, na.rm = TRUE),
  OmegaAragonite_sd = sd(mean_OmegaAragonite, na.rm = TRUE),
  OmegaAragonite_n = sum(!is.na(mean_OmegaAragonite))
  )
colnames_means_month0m <- colnames(means_month0m) #to restore them in the plot for paper section
means_month0m$monthd <-
  month(means_month0m$monthd, label = TRUE, abbr = FALSE) # month name for table

colnames(means_month0m) <-
  c(
  "Month",
  "Salinity",
  "Salinity_sd",
  "Salinity_n",
  "Temperature",
  "Temperature_sd",
  "Temperature_n",
  "Chla",
  "Chla_sd",
  "Chla_n",
  "CT",
  "CT_sd",
  "CT_n",
  "AT",
  "AT_sd",
  "AT_n",
  "pHT",
  "pHT_sd",
  "pH_n",
  "pHT18",
  "pHT18_sd",
  "pH25_n",
  "pCO2",
  "pCO2_sd",
  "pCO2_n",
  "Oc",
  "Oc_sd",
  "Oc_n",
  "Oa",
  "Oa_sd",
  "Oa_n"
  )

# tmp_long <-
# tbl_df(
# melt(
#   tmp,
#   id.vars = c("month"),
#   measure.vars = c(
#   "mean_temperature",
#   "mean_salinity",
#   "mean_Chla",
#   "mean_ta",
#   "mean_dic",
#   "mean_pCO2",
#   "mean_pH",
#   "mean_OmegaAragonite"
#   ),
#   na.rm = TRUE
#   )
# )

tmp_long <- tmp %>%
  gather(key = variable, value=value, -month, na.rm = TRUE)

size_point <- 0.1 # size of data points
T1vp <- ggplot(filter(tmp_long, variable=="mean_temperature"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  scale_y_continuous(limits=c(10,32)) +
  labs(title=NULL, x=NULL, y ="T (°C)") +
#  coord_fixed() +
  Mytheme(size_labs = 9) +
  theme(aspect.ratio = 1/2,
        plot.margin = margin(t = -0.5, r = 0.2, b = -0.5, l = 0, unit = "cm"),
        axis.text.x=element_blank()) +
  annotation_custom(grob_A)
S1vp <- ggplot(filter(tmp_long, variable=="mean_salinity"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  scale_y_continuous(limits=c(35.5, 39)) +
  labs(title=NULL,x=NULL,y="Salinity") +
#  coord_fixed() +
  Mytheme(size_labs = 9) +
  theme(aspect.ratio = 1/2,
        plot.margin = margin(t = -0.5, r = 0.2, b = -0.2, l = 0, unit = "cm"),
        axis.text.x=element_blank()) +
  annotation_custom(grob_B)
AT1vp <- ggplot(filter(tmp_long, variable=="mean_ta"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y=expression(paste(italic(A)[T], " (",mu, "mol ", kg^-1,")"))) +
#  coord_fixed() +
  Mytheme(size_labs = 9) +
  theme(aspect.ratio = 1/2,
        plot.margin = margin(t = -0.5, r = 0.2, b = -0.2, l = 0, unit = "cm"),
        axis.text.x=element_blank()) +
  annotation_custom(grob_C)
CT1vp <- ggplot(filter(tmp_long, variable=="mean_dic"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y=expression(paste(italic(C)[T], " (",mu, "mol ", kg^-1,")"))) +
#  coord_fixed() +
  Mytheme(size_labs = 9) +
  theme(aspect.ratio = 1/2,
        plot.margin = margin(t = -0.5, r = 0.2, b = -0.2, l = 0, unit = "cm"),
        axis.text.x=element_blank()) +
  annotation_custom(grob_D_bl)
pH1vp <- ggplot(filter(tmp_long, variable=="mean_pH"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y=expression(paste(pH[T]))) +
#  coord_fixed() +
  Mytheme(size_labs = 9) +
  theme(aspect.ratio = 1/2,
        plot.margin = margin(t = -0.5, r = 0.2, b = -0.2, l = 0, unit = "cm"),
        axis.text.x=element_blank()) +
  annotation_custom(grob_E_bl)
pCO21vp <- ggplot(filter(tmp_long, variable=="mean_pCO2"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y=expression(paste(pCO[2], " (",mu, "atm)"))) +
#  coord_fixed() +
  Mytheme(size_labs = 9) +
  theme(aspect.ratio = 1/2,
        plot.margin = margin(t = -0.5, r = 0.2, b = -0.5, l = 0, unit = "cm"),
        axis.text.x=element_blank()) +
  annotation_custom(grob_F)
Oa1vp <- ggplot(filter(tmp_long, variable=="mean_OmegaAragonite"), aes(x = month, y = value, group=month)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
  labs(title=NULL,x=NULL,y=expression(paste(Omega[a]))) +
#  coord_fixed() +
  Mytheme(size_labs = 9) +
  theme(aspect.ratio = 1/2,
        plot.margin = margin(t = 0, r = 0.2, b = 0.3, l = 0, unit = "cm")) +
  annotation_custom(grob_G)

g <- plot_grid(T1vp, S1vp, AT1vp, CT1vp, pH1vp, pCO21vp, Oa1vp, ncol=1,
               align="v")
#g <- arrangeGrob(T1vp, S1vp, AT1vp, CT1vp, pH1vp, pCO21vp, Oa1vp, ncol=1)
#cowplot::
ggsave(file="./fig3.pdf", g,  width = 8, height = 28, units = "cm")
g <- plot_grid(T1vp, S1vp, AT1vp, CT1vp, pH1vp, pCO21vp, Oa1vp, ncol=2)
ggsave(file="./fig_paper_monthly_means_1m.png", g, width = 18, height = 14, units = "cm")

# prepare data 50m
tmp <- ungroup(mean50m) %>%
  mutate(month = month(sampling_date, label = TRUE, abb = TRUE)) %>%
  select(
  month,
  mean_temperature,
  mean_salinity,
  mean_Chla,
  mean_ta,
  mean_dic,
  mean_pCO2,
  mean_pH,
  mean_OmegaAragonite
  )
tmp$month <- factor(tmp$month)

means_month50m <- ungroup(mean50m) %>%
  group_by(monthd) %>%
  summarise(
  Salinity = mean(mean_salinity, na.rm = TRUE),
  Salinity_sd = sd(mean_salinity, na.rm = TRUE),
  Salinity_n = sum(!is.na(mean_salinity)),
  Temperature = mean(mean_temperature, na.rm = TRUE),
  Temperature_sd = sd(mean_temperature, na.rm = TRUE),
  Temperature_n = sum(!is.na(mean_temperature)),
  Chla = mean(mean_Chla, na.rm = TRUE),
  Chla_sd = sd(mean_Chla, na.rm=TRUE),
  Chla_n = sum(!is.na(mean_Chla)),
  dic = mean(mean_dic, na.rm = TRUE),
  dic_sd = sd(mean_dic, na.rm = TRUE),
  dic_n = sum(!is.na(mean_dic)),
  ta = mean(mean_ta, na.rm = TRUE),
  ta_sd = sd(mean_ta, na.rm = TRUE),
  ta_n = sum(!is.na(mean_ta)),
  pH = mean(mean_pH, na.rm = TRUE),
  pH_sd = sd(mean_pH, na.rm = TRUE),
  pH_n = sum(!is.na(mean_pH)),
  pH25 = mean(mean_pH25, na.rm = TRUE),
  pH25_sd = sd(mean_pH25, na.rm = TRUE),
  pH25_n = sum(!is.na(mean_pH25)),
  pCO2 = mean(mean_pCO2, na.rm = TRUE),
  pCO2_sd = sd(mean_pCO2, na.rm = TRUE),
  pCO2_n = sum(!is.na(mean_pCO2)),
  OmegaCalcite = mean(mean_OmegaCalcite, na.rm = TRUE),
  OmegaCalcite_sd = sd(mean_OmegaCalcite, na.rm = TRUE),
  OmegaCalcite_n = sum(!is.na(mean_OmegaCalcite)),
  OmegaAragonite = mean(mean_OmegaAragonite, na.rm = TRUE),
  OmegaAragonite_sd = sd(mean_OmegaAragonite, na.rm = TRUE),
  OmegaAragonite_n = sum(!is.na(mean_OmegaAragonite))
  )
colnames_means_month50m <- colnames(means_month50m) #to restore them in the plot for paper section
means_month50m$monthd <-
  month(means_month50m$monthd, label = TRUE, abbr = FALSE) # month name for table

colnames(means_month50m) <-
  c(
  "Month",
  "Salinity",
  "Salinity_sd",
  "Salinity_n",
  "Temperature",
  "Temperature_sd",
  "Temperature_n",
  "Chla",
  "Chla_sd",
  "Chla_n",
  "CT",
  "CT_sd",
  "CT_n",
  "AT",
  "AT_sd",
  "AT_n",
  "pHT",
  "pHT_sd",
  "pH_n",
  "pHT18",
  "pHT18_sd",
  "pH25_n",
  "pCO2",
  "pCO2_sd",
  "pCO2_n",
  "Oc",
  "Oc_sd",
  "Oc_n",
  "Oa",
  "Oa_sd",
  "Oa_n"
  )

```

## Monthly means at the surface
![fig_paper_monthly_means_1m.png](./fig_paper_monthly_means_1m.png)

```{r table monthly means}
kable(means_month0m, digits = 3, caption="Monthly means at the surface")
kable(means_month50m, digits = 3, caption="Monthly means at 50 m")
```

```{r Figure Interannual changes and anomalies at 1 m, include=FALSE}
size_point <- 0.4 # size of data points

# Plot interannual changes
T1p <- ggplot(mean0m, aes(x = sampling_date, y = mean_temperature), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="", y="Temp. (°C)") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_A_bl)
S1p <- ggplot(mean0m, aes(x = sampling_date, y = mean_salinity), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
    scale_y_continuous(limits=c(35.5, 39), breaks=c(36,37,38)) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y="Salinity") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_B_bl)
CT1p <- ggplot(mean0m, aes(x = sampling_date, y = mean_dic), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(italic(C)[T], " (",mu, "mol ", kg^-1,")"))) +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(mean0m$mean_dic, na.rm=TRUE), 
           label="*", colour="blue", size=10, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_D_bl)
AT1p <- ggplot(mean0m, aes(x = sampling_date, y = mean_ta), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  #geom_smooth(method="loess", span=0.4, se=FALSE, colour="orange") +
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(italic(A)[T], " (",mu, "mol ", kg^-1,")"))) +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(mean0m$mean_ta, na.rm=TRUE), 
           label="*", colour="blue", size=9, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_C_bl)
pH1p <- ggplot(mean0m, aes(x = sampling_date, y = mean_pH), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
 labs(title=NULL,x="", y=expression(paste(pH[T]))) +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(mean0m$mean_pH, na.rm=TRUE), 
           label="*", colour="blue", size=9, fontface="plain") +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_E_bl)
pCO21p <- ggplot(mean0m, aes(x = sampling_date, y = mean_pCO2), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(pCO[2], " (",mu, "atm)"))) +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(mean0m$mean_pCO2, na.rm=TRUE), 
           label="*", colour="blue", size=9, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_F_bl)
Oa1p <- ggplot(mean0m, aes(x = sampling_date, y = mean_OmegaAragonite), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(Omega[a]))) +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  annotation_custom(grob_G_bl)
ATvsCT1p <- ggplot(mean0m, aes(x = sampling_date, y = mean_ta/mean_dic), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) +
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(A[T]:C[T]))) +
  annotate("text", x = as.POSIXct("2008-01-01"), 
           y = max(mean0m$mean_ta/mean0m$mean_dic, na.rm=TRUE), 
           label = lm_eqn(lm(mean_ta/mean_dic ~sampling_date, data=mean0m)), parse = TRUE) +
  coord_fixed() +
  Mytheme(size_labs = 8)
ggsave(filename = "./ATvsCT1p.png", plot = ATvsCT1p)

# Calculate anomalies
# At 1 m
# Calculate monthly means
tmp <- ungroup(mean0m) %>%
  group_by(monthd) %>%
  summarise(
  Salinity_month = mean(mean_salinity, na.rm = TRUE),
  Temperature_month = mean(mean_temperature, na.rm = TRUE),
  dic_month = mean(mean_dic, na.rm = TRUE),
  ta_month = mean(mean_ta, na.rm = TRUE),
  pH_month = mean(mean_pH, na.rm = TRUE),
  pH25_month = mean(mean_pH25, na.rm = TRUE),
  pCO2_month = mean(mean_pCO2, na.rm = TRUE),
  OmegaCalcite_month = mean(mean_OmegaCalcite, na.rm = TRUE),
  OmegaAragonite_month = mean(mean_OmegaAragonite, na.rm = TRUE),
  Nta_month = mean(mean_Nta, na.rm = TRUE),
  Ndic_month = mean(mean_Ndic, na.rm = TRUE)
  )
# Calculate anomalies
ano_month0m <- left_join(ungroup(mean0m), tmp, by = "monthd") %>%
  mutate(
  Salinity_ano = mean_salinity - Salinity_month,
  Temperature_ano = mean_temperature - Temperature_month,
  dic_ano = mean_dic - dic_month,
  ta_ano = mean_ta - ta_month,
  pH_ano = mean_pH - pH_month,
  pH25_ano = mean_pH25 - pH25_month,
  pCO2_ano = mean_pCO2 - pCO2_month,
  OmegaCalcite_ano = mean_OmegaCalcite - OmegaCalcite_month,
  OmegaAragonite_ano = mean_OmegaAragonite - OmegaAragonite_month,
  Nta_ano = mean_Nta - Nta_month,
  Ndic_ano = mean_Ndic - Ndic_month
  )

# Regressions and tables of key parameters
var_list <-
  c(
  "mean_salinity",
  "mean_temperature",
  "mean_dic",
  "mean_ta",
  "mean_pH",
  "mean_pH25",
  "mean_pCO2",
  "mean_OmegaCalcite",
  "mean_OmegaAragonite",
  "mean_Nta",
  "mean_Ndic"
  )
lms <- lapply(var_list, function(x) {
  summary(lm(substitute(i ~ decimal_date(sampling_date), list(i = as.name(x))), data = ano_month0m))
  })
reg <- NULL
for (i in 1:length(var_list)) {
  #one loops through all anomalies
  # calculate probability of fstatistic because it cannot be extracted from lms above
  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
  # slope returned by lm is per second
  prob <- pf(lms[[i]]$fstatistic[1],
  lms[[i]]$fstatistic[2],
  lms[[i]]$fstatistic[3],
  lower.tail = FALSE)
  reg <- rbind(reg, as.numeric(c(
    lms[[i]]$coefficients[2, 1],
    lms[[i]]$coefficients[2, 2],
    lms[[i]]$coefficients[2, 4],
  lms[[i]]$coefficients[1, 1],
  lms[[i]]$coefficients[1, 2],
  lms[[i]]$coefficients[1, 4],
  lms[[i]]$fstatistic[1],
  lms[[i]]$fstatistic[3],
  lms[[i]]$r.squared,
  prob
  )
  ))
}
colnames(reg) <-
  c("Slope",
  "SE Slope",
  "P Slope",
  "Intercept",
  "SE int.",
  "P int.",
  "F",
  "df",
  "R2",
  "P value")
row.names(reg) <- var_list
reg_var <- reg
slope_ta <- reg_var[4,1]
intercept_ta <- reg_var[4,4]

# Regression and table anomalies
var_list <-
  c(
  "Salinity_ano",
  "Temperature_ano",
  "dic_ano",
  "ta_ano",
  "pH_ano",
  "pH25_ano",
  "pCO2_ano",
  "OmegaCalcite_ano",
  "OmegaAragonite_ano",
  "Nta_ano",
  "Ndic_ano"
  )
lms <- lapply(var_list, function(x) {
  summary(lm(substitute(i ~ decimal_date(sampling_date), list(i = as.name(x))), data = ano_month0m))
  })
reg <- NULL
for (i in 1:length(var_list)) {
  #one loops through all anomalies
  # calculate probability of fstatistic because it cannot be extracted from lms above
  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
  # slope returned by lm is per second
prob <-
  pf(lms[[i]]$fstatistic[1],
  lms[[i]]$fstatistic[2],
  lms[[i]]$fstatistic[3],
  lower.tail = FALSE)
reg <-
  rbind(reg, as.numeric(
  c(
  lms[[i]]$coefficients[2, 1],
  lms[[i]]$coefficients[2, 2],
  lms[[i]]$coefficients[2, 4],
  lms[[i]]$coefficients[1, 1],
  lms[[i]]$coefficients[1, 2],
  lms[[i]]$coefficients[1, 4],
  lms[[i]]$fstatistic[1],
  lms[[i]]$fstatistic[3],
  lms[[i]]$r.squared,
  prob
  )
  ))
}
colnames(reg) <-
  c("Slope",
  "SE Slope",
  "P Slope",
  "Intercept",
  "SE int.",
  "P int.",
  "F",
  "df",
  "R2",
  "P value")
row.names(reg) <- var_list
reg_ano <- reg
reg_ano["Salinity_ano", "P value"]

# Plot anomalies
#Anomalies 1 m
anT1p <- ggplot(data = ano_month0m, aes(x = sampling_date, y = Temperature_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="", y="Temp. (°C)") +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(ano_month0m$Temperature_ano, na.rm=TRUE), 
           label="*", colour="blue", size=9, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_H_bl)
anS1p <- ggplot(data = ano_month0m, aes(x = sampling_date, y = Salinity_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  scale_y_continuous(breaks=c(-2,-1,0,0.5)) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="", y="Salinity") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_I_bl)
anCT1p <- ggplot(data = ano_month0m, aes(x = sampling_date, y = dic_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="", y=expression(paste(italic(C)[T], " (",mu, "mol ", kg^-1,")"))) +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(ano_month0m$dic_ano, na.rm=TRUE), 
           label="*", colour="blue", size=9, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_K_bl)
anAT1p <- ggplot(data = ano_month0m, aes(x = sampling_date, y = ta_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="", y=expression(paste(italic(A)[T], " (",mu, "mol ", kg^-1,")"))) +
  theme(axis.text.x=element_blank()) +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(ano_month0m$ta_ano, na.rm=TRUE), 
           label="*", colour="blue", size=9, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_J_bl)
anpH1p <- ggplot(data = ano_month0m, aes(x = sampling_date, y = pH_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(pH[T]))) +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(ano_month0m$pH_ano, na.rm=TRUE), 
           label="*", colour="blue", size=9, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
annotation_custom(grob_L_bl)
anpCO21p <- ggplot(data = ano_month0m, aes(x = sampling_date, y = pCO2_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(pCO[2], " (",mu, "atm)"))) +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(ano_month0m$pCO2_ano, na.rm=TRUE), 
           label="*", colour="blue", size=9, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_M_bl)
anOa1p <- ggplot(data = ano_month0m, aes(x = sampling_date, y = OmegaAragonite_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  scale_y_continuous(breaks=c(-0.2,0,0.2)) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(Omega[a]))) +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(ano_month0m$OmegaAragonite_ano, na.rm=TRUE), 
           label="*", colour="blue", size=9, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  annotation_custom(grob_N_bl)

g <- plot_grid(T1p, anT1p, S1p, anS1p, AT1p, anAT1p, CT1p, anCT1p, pH1p, anpH1p, pCO21p, anpCO21p, Oa1p, anOa1p, align='vh', ncol=2)
ggsave(file=".fig_paper_interannual_1m.png", g, width=15, height = 17, units = "cm")
ggsave(file=".fig2.pdf", g, width = 18, height = 21, units = "cm")

# AT as a function of salinity for every year
j <- 0
reg <- data.frame()
for (i in 1:length(unique(mean0m$year))) { #one loops through all years
  j <- j + 1
  yr <- unique(mean0m$year)[i]
  d_reg <- filter(mean0m, year==yr)
#  fm <- as.formula(paste0(i, " ~ sampling_date"))
  #fit[[i]] <- lm(fm, data = mean0m)
  lms <- summary(lm(data=d_reg, mean_ta ~ mean_salinity))
  # calculate probability of fstatistic because it cannot be extracted from lms above
  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
  # slope returned by lm is per second
  prob <- pf(lms$fstatistic[1],lms$fstatistic[2],lms$fstatistic[3],lower.tail=FALSE)
  reg <- rbind(reg, as.numeric(c(lms$coefficients[2,1], lms$coefficients[2,2], 
                                 lms$coefficients[2,4], lms$coefficients[1,1], lms$coefficients[1,2],
                                 lms$coefficients[1,4], lms$fstatistic[1],   lms$fstatistic[3],
                                 lms$r.squared, prob)))
}
names(reg) <- c("Slope", "SE Slope", "P Slope","Intercept","SE int.","P int.", "F", "df",
                "R2","P value")
row.names(reg) <- as.character(unique(mean0m$year))
#transform in latex table and save
tab_surf_salinity_AT_year <- reg

## POC and PON
# pom_l <-pom %>% 
#   filter(depth==1 | depth==50) %>%
#   select(-q_poc, -q_pon) %>%
#   gather(key=pom, value=value, poc, pon)
# fig_poc_pon <- ggplot(data = filter(pom_l, depth==1), aes(x = date, y = value), na.rm=TRUE) + 
#   geom_point(aes(colour=pom), na.rm=TRUE, size=size_point) +
#   scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
#   labs(title="Point B at 1 m",x="",y="Particulate organic matter") +
#   Mytheme()
# ggsave(file="./fig_poc_pon.png", fig_poc_pon, width = 18, height = 20, units = "cm")
```

```{r Removing the effect of changes in AT at 1m, include=FALSE}
#intercept_ta <- 0
first_at <- intercept_ta + decimal_date(dat$sampling_date[1]) * slope_ta # 1st AT value of the time series
dat$ta_no_change <- dat$ta - ((intercept_ta + decimal_date(dat$sampling_date) * slope_ta) - first_at)
p_ta_no_change <- ggplot(data=dat, na.rm=TRUE) +
  geom_point(aes(x=sampling_date, y= ta), col="red") +
  geom_point(aes(x=sampling_date, y= ta_no_change), col="blue")
zzz <- drop_na(dat,ta_no_change, dic,salinity_field,temp_field)
carb_ta_no_change <- carb(flag=15, var1=zzz$ta_no_change*1e-6, var2=zzz$dic*1e-6, S=zzz$salinity_field,
             T=zzz$temp_field, P=zzz$depth/10, Pt=1e-6*zzz$PO4, Sit=1e-6*zzz$SIOH4, 
             k1k2 = "l", kf = "pf", pHscale = "T", b="l10")
zzz$pH <- carb_ta_no_change$pH
# calculate rate of pH change
# les deux lignes qui suivent ne marchent pas. J'ai dû recourir à ce qui suit.
# JE NE COMPRENDS pas pourquoi.
#zzz_reg <- summary(lm(data=zzz, decimal_date(sampling_date) ~ pH))
#slope_ta_no_change <- zzz_reg$coefficients[2, 1]

var_list <- c("pH")
lms <- lapply(var_list, function(x) {
  summary(lm(substitute(i ~ decimal_date(sampling_date), list(i = as.name(x))), data = zzz))
  })
reg_ta_no_change <- NULL
for (i in 1:length(var_list)) {
  #one loops through all anomalies
  # calculate probability of fstatistic because it cannot be extracted from lms above
  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
  # slope returned by lm is per second
  prob <- pf(lms[[i]]$fstatistic[1],
  lms[[i]]$fstatistic[2],
  lms[[i]]$fstatistic[3],
  lower.tail = FALSE)
  reg_ta_no_change <- rbind(reg_ta_no_change, as.numeric(c(
    lms[[i]]$coefficients[2, 1],
    lms[[i]]$coefficients[2, 2],
    lms[[i]]$coefficients[2, 4],
  lms[[i]]$coefficients[1, 1],
  lms[[i]]$coefficients[1, 2],
  lms[[i]]$coefficients[1, 4],
  lms[[i]]$fstatistic[1],
  lms[[i]]$fstatistic[3],
  lms[[i]]$r.squared,
  prob
  )
  ))
}
colnames(reg_ta_no_change) <-
  c("Slope",
  "SE Slope",
  "P Slope",
  "Intercept",
  "SE int.",
  "P int.",
  "F",
  "df",
  "R2",
  "P value")
row.names(reg_ta_no_change) <- var_list
```

## Interannual changes at 1 m
![fig_paper_interannual_1m.png](./fig_paper_interannual_1m.png)
![fig_poc_pon.png](./fig_poc_pon.png)
![fig_ta_vs_salinity_month_pointB_0m.png](./fig_ta_vs_salinity_month_pointB_0m.png)

The slope of the rate of pH change is `r round(reg_var[5,1], digits=4)` ± `r format(reg_var[5,2], digits=4, scientific=FALSE)` units per year. If the observed total alkalinity data are corrected from their rate of change (i.e. assuming that they have not increased during the period of measurement, but kept their subannual variability), the rate of change is `r round(reg_ta_no_change[1,1], digits=4)` ± `r format(reg_ta_no_change[1,2], digits=4, scientific=FALSE)` units per year.

```{r kable regressions 1 m}
kable(reg_var, digits = c(4,4,3,3,3,2,3), caption="Regressions on values at 1 m depth.")
kable(reg_ano, digits = c(4,4,3,3,3,2,3), caption="Regressions on anomalies at 1 m depth.")  
kable(tab_surf_salinity_AT_year, digits = c(2,2), caption="Regressions on values at 1 m depth for every year.")
```

```{r Figure Interannual changes and anomalies at 50 m, include=FALSE}
size_point <- 0.4 # size of data points

# Plot interannual changes
T50p <- ggplot(mean50m, aes(x = sampling_date, y = mean_temperature), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="", y="Temp. (°C)") +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(mean50m$mean_temperature, na.rm=TRUE), 
           label="*", colour="blue", size=10, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_A)
S50p <- ggplot(mean50m, aes(x = sampling_date, y = mean_salinity), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
#    scale_y_continuous(limits=c(37, 39), breaks=c(37,38,39)) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y="Salinity") +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(mean50m$mean_salinity, na.rm=TRUE), 
           label="*", colour="blue", size=10, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_B)
CT50p <- ggplot(mean50m, aes(x = sampling_date, y = mean_dic), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(italic(C)[T], " (",mu, "mol ", kg^-1,")"))) +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_D)
AT50p <- ggplot(mean50m, aes(x = sampling_date, y = mean_ta), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  scale_y_continuous(breaks=c(2530, 2550, 2570)) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  #geom_smooth(method="loess", span=0.4, se=FALSE, colour="orange") +
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(italic(A)[T], " (",mu, "mol ", kg^-1,")"))) +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_C)
pH50p <- ggplot(mean50m, aes(x = sampling_date, y = mean_pH), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
 labs(title=NULL,x="", y=expression(paste(pH[T]))) +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(mean50m$mean_pH, na.rm=TRUE), 
           label="*", colour="blue", size=10, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_E)
pCO250p <- ggplot(mean50m, aes(x = sampling_date, y = mean_pCO2), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(pCO[2], " (",mu, "atm)"))) +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_F)
Oa50p <- ggplot(mean50m, aes(x = sampling_date, y = mean_OmegaAragonite), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(Omega[a]))) +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(mean50m$mean_OmegaAragonite, na.rm=TRUE), 
           label="*", colour="blue", size=10, fontface="plain") +  
  coord_fixed() +
  Mytheme(size_labs = 8) +
  annotation_custom(grob_G)
ATvsCT50p <- ggplot(mean50m, aes(x = sampling_date, y = mean_ta/mean_dic), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#482173FF", na.rm=TRUE, size=size_point) +
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(A[T]:C[T]))) +
  coord_fixed() +
  Mytheme(size_labs = 8)
ggsave(filename = "./ATvsCT50p.png", plot = ATvsCT50p)

# Calculate monthly means
tmp <- ungroup(mean50m) %>%
  group_by(monthd) %>%
  summarise(
  Salinity_month = mean(mean_salinity, na.rm = TRUE),
  Temperature_month = mean(mean_temperature, na.rm = TRUE),
  dic_month = mean(mean_dic, na.rm = TRUE),
  ta_month = mean(mean_ta, na.rm = TRUE),
  pH_month = mean(mean_pH, na.rm = TRUE),
  pH25_month = mean(mean_pH25, na.rm = TRUE),
  pCO2_month = mean(mean_pCO2, na.rm = TRUE),
  OmegaCalcite_month = mean(mean_OmegaCalcite, na.rm = TRUE),
  OmegaAragonite_month = mean(mean_OmegaAragonite, na.rm = TRUE),
  Nta_month = mean(mean_Nta, na.rm = TRUE),
  Ndic_month = mean(mean_Ndic, na.rm = TRUE)
  )

# Calculate anomalies
ano_month50m <- left_join(ungroup(mean50m), tmp, by = "monthd") %>%
  mutate(
  Salinity_ano = mean_salinity - Salinity_month,
  Temperature_ano = mean_temperature - Temperature_month,
  dic_ano = mean_dic - dic_month,
  ta_ano = mean_ta - ta_month,
  pH_ano = mean_pH - pH_month,
  pH25_ano = mean_pH25 - pH25_month,
  pCO2_ano = mean_pCO2 - pCO2_month,
  OmegaCalcite_ano = mean_OmegaCalcite - OmegaCalcite_month,
  OmegaAragonite_ano = mean_OmegaAragonite - OmegaAragonite_month,
  Nta_ano = mean_Nta - Nta_month,
  Ndic_ano = mean_Ndic - Ndic_month
  )

# Regressions and tables of key parameters
var_list <-
  c(
  "mean_salinity",
  "mean_temperature",
  "mean_dic",
  "mean_ta",
  "mean_pH",
  "mean_pH25",
  "mean_pCO2",
  "mean_OmegaCalcite",
  "mean_OmegaAragonite",
  "mean_Nta",
  "mean_Ndic"
  )
lms <- lapply(var_list, function(x) {
  summary(lm(substitute(i ~ decimal_date(sampling_date), list(i = as.name(x))), data = ano_month50m))
  })
reg <- NULL
for (i in 1:length(var_list)) {
  #one loops through all anomalies
  # calculate probability of fstatistic because it cannot be extracted from lms above
  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
  # slope returned by lm is per second
  prob <-
  pf(lms[[i]]$fstatistic[1],
  lms[[i]]$fstatistic[2],
  lms[[i]]$fstatistic[3],
  lower.tail = FALSE)
  reg <-
  rbind(reg, as.numeric(
  c(
    lms[[i]]$coefficients[2, 1],
    lms[[i]]$coefficients[2, 2],
  lms[[i]]$coefficients[2, 4],
  lms[[i]]$coefficients[1, 1],
  lms[[i]]$coefficients[1, 2],
  lms[[i]]$coefficients[1, 4],
  lms[[i]]$fstatistic[1],
  lms[[i]]$fstatistic[3],
  lms[[i]]$r.squared,
  prob
  )
  ))
}
colnames(reg) <-
  c("Slope",
  "SE Slope",
  "P Slope",
  "Intercept",
  "SE int.",
  "P int.",
  "F",
  "df",
  "R2",
  "P value")
row.names(reg) <- var_list
reg_var <- reg

# Regression and table anomalies
var_list <-
  c(
  "Salinity_ano",
  "Temperature_ano",
  "dic_ano",
  "ta_ano",
  "pH_ano",
  "pH25_ano",
  "pCO2_ano",
  "OmegaCalcite_ano",
  "OmegaAragonite_ano",
  "Nta_ano",
  "Ndic_ano"
  )
lms <- lapply(var_list, function(x) {
  summary(lm(substitute(i ~ decimal_date(sampling_date), list(i = as.name(x))), data = ano_month50m))
  })
reg <- NULL
for (i in 1:length(var_list)) {
  #one loops through all anomalies
  # calculate probability of fstatistic because it cannot be extracted from lms above
  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
  # slope returned by lm is per second
prob <-
  pf(lms[[i]]$fstatistic[1],
  lms[[i]]$fstatistic[2],
  lms[[i]]$fstatistic[3],
  lower.tail = FALSE)
reg <-
  rbind(reg, as.numeric(
  c(
  lms[[i]]$coefficients[2, 1],
  lms[[i]]$coefficients[2, 2],
  lms[[i]]$coefficients[2, 4],
  lms[[i]]$coefficients[1, 1],
  lms[[i]]$coefficients[1, 2],
  lms[[i]]$coefficients[1, 4],
  lms[[i]]$fstatistic[1],
  lms[[i]]$fstatistic[3],
  lms[[i]]$r.squared,
  prob
  )
  ))
}
colnames(reg) <-
  c("Slope",
  "SE Slope",
  "P Slope",
  "Intercept",
  "SE int.",
  "P int.",
  "F",
  "df",
  "R2",
  "P value")
row.names(reg) <- var_list
reg_ano <- reg
reg_ano["Salinity_ano", "P value"]

# Plot anomalies at 50 m
anT50p <- ggplot(data = ano_month50m, aes(x = sampling_date, y = Temperature_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="", y="Temp. (°C)") +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(ano_month50m$Temperature_ano, na.rm=TRUE), 
           label="*", colour="blue", size=10, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_H)
anS50p <- ggplot(data = ano_month50m, aes(x = sampling_date, y = Salinity_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  #scale_y_continuous(breaks=c(-2,-1,0,0.5)) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="", y="Salinity") +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(ano_month50m$Salinity_ano, na.rm=TRUE), label="*", colour="blue", size=10, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_I)
anCT50p <- ggplot(data = ano_month50m, aes(x = sampling_date, y = dic_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="", y=expression(paste(italic(C)[T], " (",mu, "mol ", kg^-1,")"))) +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_K)
anAT50p <- ggplot(data = ano_month50m, aes(x = sampling_date, y = ta_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  scale_y_continuous(breaks=c(-20, 0, 20)) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="", y=expression(paste(italic(A)[T], " (",mu, "mol ", kg^-1,")"))) +
  theme(axis.text.x=element_blank()) +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_J)
anpH50p <- ggplot(data = ano_month50m, aes(x = sampling_date, y = pH_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(pH[T]))) +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(ano_month50m$pH_ano, na.rm=TRUE), 
           label="*", colour="blue", size=10, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
annotation_custom(grob_L)
anpCO250p <- ggplot(data = ano_month50m, aes(x = sampling_date, y = pCO2_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(pCO[2], " (",mu, "atm)"))) +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  theme(axis.text.x=element_blank()) +
  annotation_custom(grob_M)
anOa50p <- ggplot(data = ano_month50m, aes(x = sampling_date, y = OmegaAragonite_ano), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  scale_y_continuous(breaks=c(-0.2,0,0.2)) +
  geom_point(colour="#51C56AFF", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6, na.rm=TRUE) +
  labs(title=NULL,x="",y=expression(paste(Omega[a]))) +
  annotate("text", x =as.POSIXct("2016-01-01"), y= min(ano_month50m$OmegaAragonite_ano, na.rm=TRUE), 
           label="*", colour="blue", size=10, fontface="plain") +
  coord_fixed() +
  Mytheme(size_labs = 8) +
  annotation_custom(grob_N)

g <- plot_grid(T50p, anT50p, S50p, anS50p, AT50p, anAT50p, CT50p, anCT50p, pH50p, anpH50p, pCO250p, anpCO250p, Oa50p, anOa50p, align='vh', ncol=2)
ggsave(file="./fig_paper_interannual_50m.png", g, width=15, height = 17, units = "cm")
ggsave(file="./figS1.pdf", g, width = 18, height = 21, units = "cm")
```
## Interannual changes at 50 m
![fig_paper_interannual_50m.png](./fig_paper_interannual_50m.png)

```{r kable regressions 50 m}
kable(reg_var, digits = c(4,4,3,3,3,2,3), caption="Regressions on values at 50 m depth.")
kable(reg_ano, digits = c(4,4,3,3,3,2,3), caption="Regressions on anomalies at 50 m depth.")
```

## Annual monthly and quarterly ranges of T, AT and pCO2

```{r monthly and quarterly temperature and AT, include=FALSE}
mean0m_month <- mean0m %>%
  group_by(year, monthd) %>%
  summarise(Temperature = mean(mean_temperature, na.rm=TRUE),
            at = mean(mean_ta, na.rm=TRUE),
            pCO2 = mean(mean_pCO2, na.rm=TRUE),
            ct = mean(mean_dic, na.rm=TRUE)) %>%
  mutate(date = ymd(paste(year,monthd,"01")))

fig_temp_month <- ggplot(data=mean0m_month, aes(x=year, y=Temperature)) + 
  geom_line(aes(color=as.factor(monthd)), size=1) +
  xlab("Time") + ylab("Temperature") +
  Mytheme() +
  scale_color_viridis(name="Month", discrete=TRUE, option="plasma") + 
  theme(legend.position="top") +
  guides(col = guide_legend(ncol = 12, byrow = TRUE))
ggsave(file="./fig_temp_month.png", fig_temp_month, width = 15, height = 10, units = "cm")
fig_at_month <- ggplot(data=mean0m_month, aes(x=year, y=at)) + 
  geom_line(aes(color=as.factor(monthd)), size=1) +
  guides(guide_legend(title = "Month")) +
  xlab("Time") + ylab("Total alkalinity") +
  Mytheme() +
  scale_color_viridis(name="Month", discrete=TRUE, option="plasma") + 
  theme(legend.position="top") +
  guides(col = guide_legend(ncol = 12, byrow = TRUE))
ggsave(file="./fig_at_month.png", fig_at_month, width = 15, height = 10, units = "cm")
fig_pCO2_month <- ggplot(data=mean0m_month, aes(x=year, y=pCO2)) + 
  geom_line(aes(color=as.factor(monthd)), size=1) +
  xlab("Time") + ylab("pCO2") +
  Mytheme() +
  scale_color_viridis(name="Month", discrete=TRUE, option="plasma") + 
  theme(legend.position="top") +
  guides(col = guide_legend(ncol = 12, byrow = TRUE))
ggsave(file="./fig_pCO2_month.png", fig_pCO2_month, width = 15, height = 10, units = "cm")
fig_ct_month <- ggplot(data=mean0m_month, aes(x=year, y=ct)) + 
  geom_line(aes(color=as.factor(monthd)), size=1) +
  xlab("Time") + ylab("Dissolved inorganic carbon") +
  Mytheme() +
  scale_color_viridis(name="Month", discrete=TRUE, option="plasma") + 
  theme(legend.position="top") +
  guides(col = guide_legend(ncol = 12, byrow = TRUE))
ggsave(file="./fig_ct_month.png", fig_ct_month, width = 15, height = 10, units = "cm")

#animated
# mo <- months(seq(as.Date("1910/1/1"), as.Date("1911/1/1"), "months"))
# mo <- gsub("(^...).*", "\\1", mo)
# saveGIF({
#    for(i in 2007:2015){
#     print(ggplot(mean0m_month %>% filter(year <= i), 
#            aes(x=monthd, y=Temperature, color=year, group=year)) +
#         geom_line() +
#           #scale_color_gradient(low="blue", high="red", limits=c(1850, 2015), guide="none") +
#         scale_color_gradient(low="blue", high="red", limits=c(2007, 2015), guide="none") +
#         geom_hline(yintercept=1.5, color="black", lty=2) +
#         geom_hline(yintercept=2, color="black", lty=2) +
#         coord_polar() +
#         annotate(x=1, y=-1.5, geom="text", label=i) +
#         annotate(x=1, y=1.5, geom="label", label="1.5C", fill="white", label.size=0) +
#         annotate(x=1, y=2, geom="label", label="2.0C", fill="white", label.size=0) +
#           #ggtitle(expression(atop("Global Temperature Change 1850-2016, East Anglia's HadCRUT4-gl.dat", atop(italic("by McCartney Taylor 11JUL16"), "")))) +
#     #    ggtitle("Global Temperature Change 1850-2016 using University of East Anglia's HadCRUT4-gl.dat") +
#         scale_x_continuous(labels=mo, breaks=1:13) +
#         scale_y_continuous(labels=NULL, breaks=NULL) +
#          ylab("") + xlab("")
#  
#   )}
# }, interval=0.1)

# Regressions annual monthly temperature
j <- 0
reg <- data.frame()
for (i in 1:length(unique(mean0m_month$monthd))) { #one loops through all months
  j <- j + 1
  lms <- summary(lm(data=dplyr::filter(mean0m_month, monthd==i), Temperature ~ year))
  # calculate probability of fstatistic because it cannot be extracted from lms above
  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
  # slope returned by lm is per second
  prob <- pf(lms$fstatistic[1],lms$fstatistic[2],lms$fstatistic[3],lower.tail=FALSE)
  reg <- rbind(reg, as.numeric(c(lms$coefficients[2,1], lms$coefficients[2,2], 
                                 lms$coefficients[2,4], lms$coefficients[1,1], lms$coefficients[1,2],
                                 lms$fstatistic[1], lms$fstatistic[3], lms$coefficients[1,4], lms$r.squared, prob)))
}
names(reg) <- c("Slope", "SE Slope", "P Slope","Intercept","SE int.","P int.", "F", "df",
                "R2","P value")
row.names(reg) <- month(ymd(080101) + months(0:11), label = TRUE, abbr = FALSE)
#transform in latex table and save
tab_temp_month <- reg

# Regressions annual monthly AT
j <- 0
reg <- data.frame()
for (i in 1:length(unique(mean0m_month$monthd))) { #one loops through all months
  j <- j + 1
  lms <- summary(lm(data=dplyr::filter(mean0m_month, monthd==i), at ~ year))
  # calculate probability of fstatistic because it cannot be extracted from lms above
  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
  # slope returned by lm is per second
  prob <- pf(lms$fstatistic[1],lms$fstatistic[2],lms$fstatistic[3],lower.tail=FALSE)
  reg <- rbind(reg, as.numeric(c(lms$coefficients[2,1], lms$coefficients[2,2], 
                                 lms$coefficients[2,4], lms$coefficients[1,1], lms$coefficients[1,2],
                                 lms$fstatistic[1], lms$fstatistic[3], lms$coefficients[1,4], lms$r.squared, prob)))
}
names(reg) <- c("Slope", "SE Slope", "P Slope","Intercept","SE int.","P int.", "F", "df",
                "R2","P value")
row.names(reg) <- month(ymd(080101) + months(0:11), label = TRUE, abbr = FALSE)
#transform in latex table and save
tab_at_month <- reg
# Regressions annual monthly pCO2
j <- 0
reg <- data.frame()
for (i in 1:length(unique(mean0m_month$monthd))) { #one loops through all months
  j <- j + 1
  lms <- summary(lm(data=dplyr::filter(mean0m_month, monthd==i), pCO2 ~ year))
  # calculate probability of fstatistic because it cannot be extracted from lms above
  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
  # slope returned by lm is per second
  prob <- pf(lms$fstatistic[1],lms$fstatistic[2],lms$fstatistic[3],lower.tail=FALSE)
  reg <- rbind(reg, as.numeric(c(lms$coefficients[2,1], lms$coefficients[2,2], 
                                 lms$coefficients[2,4], lms$coefficients[1,1], lms$coefficients[1,2],
                                 lms$fstatistic[1], lms$fstatistic[3], lms$coefficients[1,4], lms$r.squared, prob)))
}
names(reg) <- c("Slope", "SE Slope", "P Slope","Intercept","SE int.","P int.", "F", "df",
                "R2","P value")
row.names(reg) <- month(ymd(080101) + months(0:11), label = TRUE, abbr = FALSE)
#transform in latex table and save
tab_pCO2_month <- reg
# Regressions annual monthly CT
j <- 0
reg <- data.frame()
for (i in 1:length(unique(mean0m_month$monthd))) { #one loops through all months
  j <- j + 1
  lms <- summary(lm(data=dplyr::filter(mean0m_month, monthd==i), ct ~ year))
  # calculate probability of fstatistic because it cannot be extracted from lms above
  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
  # slope returned by lm is per second
  prob <- pf(lms$fstatistic[1],lms$fstatistic[2],lms$fstatistic[3],lower.tail=FALSE)
  reg <- rbind(reg, as.numeric(c(lms$coefficients[2,1], lms$coefficients[2,2], 
                                 lms$coefficients[2,4], lms$coefficients[1,1], lms$coefficients[1,2],
                                 lms$fstatistic[1], lms$fstatistic[3], lms$coefficients[1,4], lms$r.squared, prob)))
}
names(reg) <- c("Slope", "SE Slope", "P Slope","Intercept","SE int.","P int.", "F", "df",
                "R2","P value")
row.names(reg) <- month(ymd(080101) + months(0:11), label = TRUE, abbr = FALSE)
#transform in latex table and save
tab_ct_month <- reg

#Plot monthly increases in AT and CT
#Prepare dataframe
monthly_rate_AT_CT <- 
  cbind(rename(select(tab_at_month, Slope), AT=Slope),
        rename(select(tab_ct_month, Slope), CT=Slope)
) %>%
  mutate(month=factor(month.abb, as.character(month.abb))) %>%
  gather(key, value, -month) %>%
  mutate(se=c(tab_at_month[,2], tab_ct_month[,2])) %>%
  mutate(p=c(tab_at_month[,3], tab_ct_month[,3])) %>%
  mutate(significance=ifelse(p<=0.05, "*", ""))

# Scatter plot
fig_paper_monthly_rate_AT_CT <- 
  ggplot(data=monthly_rate_AT_CT, group=key) +
  geom_point(aes(x=month, y=value, color=key), size=2, position=position_dodge(0.2)) +
  geom_errorbar(aes(x=month, ymin=value-se, ymax=value+se, color=key), 
                position=position_dodge(0.2), width=0.1) +
  labs(title=NULL, x= NULL, y=expression(paste("Monthly change (",mu, "mol ", kg^-1, " ", yr^-1, ")")),
       colour="") +
  scale_y_continuous(limits = c(-2.5, 7.5)) +
  scale_color_manual(values = c("#482173FF", "#51C56AFF"),
                     labels=c(expression(paste(italic(A)[T])), expression(paste(italic(C)[T])))) +
  #scale_colour_discrete(labels=c(expression(paste(italic(A)[T])), expression(paste(italic(C)[T])))) +
  geom_text(aes(x=month, y=value, label=significance), nudge_x=0.25, nudge_y=-0.2, size=8) +
  geom_hline(yintercept = 0, size=0.1) +
  Mytheme(size_labs = 9) +
  theme(aspect.ratio=1/2, 
        legend.position = c(1,1),
        legend.justification = c(1,1),
        panel.grid.major.x = element_blank(),
        legend.title = element_blank(),
        legend.key = element_rect(colour = 'white', fill = 'white', size = 0),
        legend.background = element_rect(fill="white", size=0.15, colour="black"))
ggsave(file="./fig_paper_monthly_rate_AT_CT.png", fig_paper_monthly_rate_AT_CT, width = 8, height = 8*2/3, units = "cm")
ggsave(file="./fig4.pdf", fig_paper_monthly_rate_AT_CT, width = 16, height= 10, units = "cm")

# Quarterly
mean0m_quart <- mean0m %>%
  group_by(year, quarter) %>%
  summarise(Temperature = mean(mean_temperature, na.rm=TRUE),
            at = mean(mean_ta, na.rm=TRUE))
fig_temp_quarter <- ggplot(data=mean0m_quart, aes(x=year, y=Temperature)) + 
  geom_line(aes(color=as.factor(quarter)), size=1) +
  xlab("Time") + ylab("Temperature") +
  Mytheme() +
  scale_color_viridis(name="Quarter", discrete=TRUE, option="plasma") + 
  theme(legend.position="top") +
  guides(col = guide_legend(ncol = 12, byrow = TRUE))
ggsave(file="./fig_temp_quarter.png", fig_temp_quarter, width = 15, height = 10, units = "cm")

fig_at_quarter <- ggplot(data=mean0m_quart, aes(x=year, y=at)) + 
  geom_line(aes(color=as.factor(quarter)), size=1) +
  xlab("Time") + ylab("Total alkalinity") +
  Mytheme() +
  scale_color_viridis(name="Quarter", discrete=TRUE, option="plasma") + 
  theme(legend.position="top") +
  guides(col = guide_legend(ncol = 12, byrow = TRUE))
ggsave(file="./fig_at_quarter.png", fig_at_quarter, width = 15, height = 10, units = "cm")
```

```{r}
kable(tab_temp_month, raw.names=TRUE, digits = c(4,4,3,3,3,2,3), caption="Regressions on annual monthly values of temperature at 1 m depth.")
kable(tab_at_month, digits = c(4,4,3,3,3,2,3), caption="Regressions on annual monthly values of total alkalinity at 1 m depth.")
kable(tab_pCO2_month, digits = c(4,4,3,3,3,2,3), caption="Regressions on annual monthly values of pCO2 at 1 m depth.")
kable(tab_ct_month, digits = c(4,4,3,3,3,2,3), caption="Regressions on annual monthly values of CT at 1 m depth.")
```

![fig_temp_month.png](./fig_temp_month.png)
![fig_at_month.png](./fig_at_month.png)
![fig_pCO2_month.png](./fig_pCO2_month.png)
![fig_temp_quarter.png](./fig_temp_quarter.png)
![fig_at_quarter.png](./fig_at_quarter.png)

## Deconvolution of pH changes
```{r pH changes due to changes in total alkalinity and temperature, include=FALSE}
#We construct a dataframe with monthly means for the entire series (mXX) as well as real data (without mrefix m)
deconv_dat <- tbl_df(
  data.frame(date=as.POSIXct(mean0m$sampling_date), mAT=means_month0m$AT[mean0m$monthd]*1e-6, mCT=means_month0m$CT[mean0m$monthd]*1e-6, mS=means_month0m$Salinity[mean0m$monthd], mT=means_month0m$Temperature[mean0m$monthd], P=mean0m$mean_P, Pt=mean0m$mean_Pt, Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
)

d <- NULL; deconv <- NULL # d is for the data to use in carb, deconv is to store the results
deconv <- data_frame(date=as.POSIXct(mean0m$sampling_date))
d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(mS), !is.na(T)) # we eliminate rows with NAs
deconv_pH_T <- data_frame(date=d$date,
                     deconv_pH_T=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$mS, T=d$T, 
                                      P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", 
                                      pHscale = "T", b="l10")$pH
                     )
d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(S), !is.na(mT)) # we eliminate rows with NAs
#d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(S), !is.na(mT)) # we eliminate rows with NAs
deconv_pH_S <- data_frame(date=d$date,
                          deconv_pH_S=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$S, T=d$mT, 
                                           P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", 
                                           pHscale = "T", b="l10")$pH
                          )
d <- filter(deconv_dat, !is.na(AT), !is.na(mCT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
deconv_pH_AT <- data_frame(date=d$date,
                     deconv_pH_AT=carb(flag=15, var1=d$AT, var2=d$mCT, S=d$mS, T=d$mT, 
                                       P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", 
                                       pHscale = "T", b="l10")$pH)
d <- filter(deconv_dat, !is.na(mAT), !is.na(CT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
deconv_pH_CT <- data_frame(date=d$date,
                     deconv_pH_CT=carb(flag=15, var1=d$mAT, var2=d$CT, S=d$mS, T=d$mT, 
                                       P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", 
                                       pHscale = "T", b="l10")$pH
                     )

# Bring all results together
deconv <- deconv %>%
  left_join(deconv_pH_T) %>%
  left_join(deconv_pH_S) %>%
  left_join(deconv_pH_AT) %>%
  left_join(deconv_pH_CT)

# Regressions and tables of key parameters
var_list <-
  c(
  "deconv_pH_T",
  "deconv_pH_S",
  "deconv_pH_AT",
  "deconv_pH_CT"
  )
lms <- lapply(var_list, function(x) {
  summary(lm(substitute(i ~ decimal_date(date), list(i = as.name(x))), data = deconv))
  })
reg <- NULL
for (i in 1:length(var_list)) {
  #one loops through all anomalies
  # calculate probability of fstatistic because it cannot be extracted from lms above
  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
  # slope returned by lm is per second
  prob <-
  pf(lms[[i]]$fstatistic[1],
  lms[[i]]$fstatistic[2],
  lms[[i]]$fstatistic[3],
  lower.tail = FALSE)
  reg <-
  rbind(reg, as.numeric(
  c(
    lms[[i]]$coefficients[2, 1],
    lms[[i]]$coefficients[2, 2],
  lms[[i]]$coefficients[2, 4],
  lms[[i]]$coefficients[1, 1],
  lms[[i]]$coefficients[1, 2],
  lms[[i]]$coefficients[1, 4],
  lms[[i]]$r.squared,
  prob
  )
  ))
}
colnames(reg) <-
  c("Slope",
  "SE Slope",
  "P Slope",
  "Intercept",
  "SE int.",
  "P int.",
  "R2",
  "P value")
row.names(reg) <- var_list
reg_deconv <- reg

# Plot
#deconv_melt <- melt(deconv, id="date")
deconv_melt <-  gather(data = deconv, key = variable, value=value, -date)

fig_deconv <- ggplot(deconv_melt) + geom_point(aes(x=date, y=value, color=variable), size=0.5) +
  facet_grid(variable ~., scales="free_y") + 
  xlab("Time") + ylab("pH (total scale)")+
  Mytheme() +
  scale_colour_discrete(guide="none")
ggsave(file="./fig_deconv.png", fig_deconv, width = 18, height = 20, units = "cm")
```
García-Ibáñez et al. (2016) provide a method to partition the changes in pH due to changes in salinity, temperature, total alkalinity and dissolved inorganic carbon.
![garcia-ibanez.png](../various/garcia-ibanez.png)

García-Ibáñez M. I., Zunino P., Fröb F., Carracedo L. I., Ríos A. F., Mercier H., Olsen A. \& Pérez F. F., 2016. Ocean acidification in the North Atlantic: controlling mechanisms. \textit{Biogeosciences Discussions} 1-26.

Here, dvar is the monthly mean value of T, S and CT for the entire time-series.

![fig_deconv.png](./fig_deconv.png)

```{r kable regressions deconvolution pH}
kable(reg_deconv, digits = c(4,4,11,3,3,2,3), caption="Regressions on values at 1 m depth.")
```

In contrast to Garcia-Ibanez et al., the sum of the slopes is higher that the slope found earlier (`r round(sum(as.data.frame(reg_deconv)$Slope), digits=4)` vs `r round(as.data.frame(reg_var)["mean_pH", "Slope"], digits=4)`). I am not sure why.

## Deconvolution of pCO2 changes
```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
# We follow the method of Garcia-Ibanez described above.
# construct a dataframe with monthly means for the entire series (mXX) as well as real data (without mrefix m)
deconv_dat <- tbl_df(
  data.frame(date=as.POSIXct(mean0m$sampling_date), mAT=means_month0m$AT[mean0m$monthd]*1e-6, mCT=means_month0m$CT[mean0m$monthd]*1e-6, mS=means_month0m$Salinity[mean0m$monthd], mT=means_month0m$Temperature[mean0m$monthd], P=mean0m$mean_P, Pt=mean0m$mean_Pt, Sit=mean0m$mean_Sit, AT=mean0m$mean_ta*1e-6, CT=mean0m$mean_dic*1e-6, S=mean0m$mean_salinity, T=mean0m$mean_temperature)
)

d <- NULL; deconv <- NULL # d is for the data to use in carb, deconv is to store the results
deconv <- data_frame(date=as.POSIXct(mean0m$sampling_date))
d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(mS), !is.na(T)) # we eliminate date with NAs
deconv_pCO2_T <- data_frame(date=d$date,
                     deconv_pCO2_T=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$mS, T=d$T, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
)
d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(S), !is.na(mT)) # we eliminate date with NAs
deconv_pCO2_S <- data_frame(date=d$date,
                     deconv_pCO2_S=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$S, T=d$mT, P=d$P, Pt=d$Pt, 
                                      Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
                     )
d <- filter(deconv_dat, !is.na(AT), !is.na(mCT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
deconv_pCO2_AT <- data_frame(date=d$date,
                     deconv_pCO2_AT=carb(flag=15, var1=d$AT, var2=d$mCT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
)
d <- filter(deconv_dat, !is.na(mAT), !is.na(CT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
deconv_pCO2_CT <- data_frame(date=d$date,
                     deconv_pCO2_CT=carb(flag=15, var1=d$mAT, var2=d$CT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2 = "l", kf = "pf", pHscale = "T", b="l10")$pCO2
)

# Bring all results together
deconv <- deconv %>%
  left_join(deconv_pCO2_T) %>%
  left_join(deconv_pCO2_S) %>%
  left_join(deconv_pCO2_AT) %>%
  left_join(deconv_pCO2_CT)

# Regressions and tables of key parameters
var_list <-
  c(
  "deconv_pCO2_T",
  "deconv_pCO2_S",
  "deconv_pCO2_AT",
  "deconv_pCO2_CT"
  )
lms <- lapply(var_list, function(x) {
  summary(lm(substitute(i ~ decimal_date(date), list(i = as.name(x))), data = deconv))
  })
reg <- NULL
for (i in 1:length(var_list)) {
  #one loops through all anomalies
  # calculate probability of fstatistic because it cannot be extracted from lms above
  # see http://stats.stackexchange.com/questions/92824/extracting-the-model-p-value-for-a-multiple-regression-in-r
  # slope returned by lm is per second
  prob <-
  pf(lms[[i]]$fstatistic[1],
  lms[[i]]$fstatistic[2],
  lms[[i]]$fstatistic[3],
  lower.tail = FALSE)
  reg <-
  rbind(reg, as.numeric(
  c(
    lms[[i]]$coefficients[2, 1],
    lms[[i]]$coefficients[2, 2],
  lms[[i]]$coefficients[2, 4],
  lms[[i]]$coefficients[1, 1],
  lms[[i]]$coefficients[1, 2],
  lms[[i]]$coefficients[1, 4],
  lms[[i]]$r.squared,
  prob
  )
  ))
}
colnames(reg) <-
  c("Slope",
  "SE Slope",
  "P Slope",
  "Intercept",
  "SE int.",
  "P int.",
  "R2",
  "P value")
row.names(reg) <- var_list
reg_deconv <- reg

# Plot
#deconv_melt <- melt(deconv, id="date")
deconv_melt <-  gather(data = deconv, key = variable, value=value, -date)
fig_deconv_pCO2 <- ggplot(deconv_melt) + geom_point(aes(x=date, y=value, color=variable), size=0.5) +
  facet_grid(variable ~., scales="free_y") + 
  xlab("Time") + ylab("pCO2 (uatm")+
  Mytheme() +
  scale_colour_discrete(guide="none")
ggsave(file="./fig_deconv_pCO2.png", fig_deconv, width = 18, height = 20, units = "cm")
```
Here, dvar is the monthly mean value of T, S and CT for the entire time-series.

![fig_deconv_pCO2.png](./fig_deconv_pCO2.png)

```{r kable regressions deconvolution pCO2}
kable(reg_deconv, digits = c(4,4,3,3,3,2,3), caption="Regressions on values at 1 m depth.")
```

The sum of the slopes is higher that the slope found earlier (`r round(sum(as.data.frame(reg_deconv)$Slope), digits=4)` vs `r round(as.data.frame(reg_var)["mean_pCO2", "Slope"], digits=4)`). I am not sure why.

## Issue of total alkalinity
```{r Total alkalinity Point B, include=FALSE}

p1 <- ggplot(data=dplyr::filter(means_depth, depth== 0)) +
  aes(mean_salinity, mean_ta) +
  geom_point(na.rm=TRUE, size=size_point) +
  stat_smooth(method=lm, na.rm=TRUE, show.legend=FALSE, se=FALSE, colour="black", size=0.5) +
  facet_wrap(~ month) +
  scale_x_continuous(limits = c(36.8, 38.4), breaks=c(37, 37.5, 38), expand = c(0,0)) +
  scale_y_continuous(limits = c(2490, 2600), expand = c(0,0)) +
  labs(title = "Point B (1 m, with month of sampling)", x = "Salinity", y = expression(paste("Total alkalinity (",mu, "mol ", kg^-1,")"))) +
  Mytheme()
png(file = "./fig_ta_vs_salinity_month_pointB_0m.png", 
    width = 20, height = 13, units = "cm", res = 300)
print(p1)
dev.off()

# AT versus salinity at the surface per year with facet
p1 <- ggplot(data=dplyr::filter(means_depth, depth== 0)) +
  aes(mean_salinity, mean_ta) +
  geom_point(na.rm=TRUE, size=size_point) +
  stat_smooth(method=lm, na.rm=TRUE, show.legend=FALSE, se=FALSE, colour="black", size=0.5) +
  facet_wrap(~ year) +
  scale_x_continuous(limits = c(36.8, 38.4), breaks=c(37, 37.5, 38), expand = c(0,0)) +
  scale_y_continuous(limits = c(2490, 2600), expand = c(0,0)) +
  labs(title = NULL, x = "Salinity", y = expression(paste("Total alkalinity (",mu, "mol ", kg^-1,")"))) +
Mytheme_facet()
png(file = "./fig_ta_vs_salinity_year_pointB_0m.png", 
    width = 6, height = 6)
print(p1)
dev.off()

# AT versus salinity at the surface per year with loop
panel <- c("(a)","(b)","(c)","(d)","(e)","(f)","(g)","(h)","(i)")
tmp <- filter(means_depth, depth== 0)
p <- NULL; j <- 0
for (i in unique(tmp$year)) {
  j <- j+1
  p[[j]] <- ggplot(data=filter(tmp, tmp$year==i), aes(x=mean_salinity, y=mean_ta, colour=month)) +
    geom_point(na.rm=TRUE, size=2) +
    stat_smooth(method=lm, na.rm=TRUE, show.legend=FALSE, se=FALSE, colour="black", size=0.5) +
    scale_x_continuous(limits = c(36.8, 38.5), breaks=c(37, 37.5, 38, 38.5), expand = c(0,0)) +
    scale_y_continuous(limits = c(2490, 2600), expand = c(0,0)) +
    labs(title = NULL, x = NULL, y = NULL) +
    annotate(geom = "text", x=36.9, y=2495, label= as.character(i), hjust=0, vjust=0, size=3) +
    annotate(geom = "text", x=36.9, y=2590, label= panel[[j]], hjust=0, vjust=0, size=3) +
    Mytheme(size_labs = 9) +
    scale_color_viridis(name="Month", discrete=TRUE, option="plasma") + 
    theme(aspect.ratio = 1,
          plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"),
          panel.grid.major = element_blank(),
          panel.grid.minor = element_blank(),
          legend.title = element_blank(),
          legend.key = element_rect(colour = 'white', fill = 'white', size = 0),
          legend.background = element_rect(fill="white", size=0.15),
          legend.key.width = unit(1, "cm"),
          legend.position='none')
if (j %in% c(1,4,7)) {p[[j]] <- p[[j]] + labs(y = expression(paste("Total alkalinity (",mu, "mol ", kg^-1,")")))}
  else {
    p[[j]] <- p[[j]] + theme(axis.text.y = element_blank())
    p[[j]] <- p[[j]] + theme(plot.margin = margin(t = 0, r = 0.3, b = 0, l = 0, unit = "cm"))
  }
 if (j %in% c(7,8,9)) {p[[j]] <- p[[j]] + labs(x = "Salinity")
 p[[j]] <- p[[j]] + theme(axis.title.x = element_text(margin=margin(t = 0.2, r = 0, b = 0.2, l = 0, unit="cm")))
 }
 else {
    p[[j]] <- p[[j]] + theme(axis.text.x = element_blank())
 }
  #   #p[[j]] <- p[[j]] + theme(axis.title.x = element_text(margin=margin(t = 0.2, r = 0, b = 0.2, l = 0, unit="cm")))
  #   #p[[j]] <- p[[j]] + theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "cm"))
}
g1 <- plot_grid(p[[1]], p[[2]], p[[3]], p[[4]], p[[5]], p[[6]], p[[7]], p[[8]], p[[9]], ncol=3, align="vh")
grobs <- ggplotGrob(p[[1]] + theme(legend.position="top"))$grobs
legend_top <- grobs[[which(sapply(grobs, function(x) x$name) == "guide-box")]]
g <- plot_grid(legend_top, g1, ncol = 1, rel_heights = c(0.15, 1))
ggsave(file="./fig5.pdf", g, width = 16, height = 15, units = "cm")

# AT=f(S) with monthly means
lms <- summary(lm(data = means_month0m, AT ~ Salinity))
prob <- pf(lms$fstatistic[1],lms$fstatistic[2],lms$fstatistic[3],lower.tail=FALSE)
reg_AT_S_monthly <- cbind(as.numeric(c(lms$coefficients[2,1], lms$coefficients[2,2], 
                                       lms$coefficients[2,4], lms$coefficients[1,1],
                                       lms$coefficients[1,2], lms$fstatistic[1], lms$fstatistic[3], 
                                       lms$coefficients[1,4], lms$r.squared, prob)))
colnames(reg_AT_S_monthly) <- c("AT")
row.names(reg_AT_S_monthly) <- c("Slope", "SE Slope", "P Slope","Intercept","SE int.","P int.", "F", "df",
                    "R2","P value")

p1 <- ggplot(data=means_month0m) +
  aes(x= Salinity, y=AT) +
  geom_point(na.rm=TRUE, size=size_point) +
  stat_smooth(method=lm, na.rm=TRUE, show.legend=FALSE, se=FALSE, colour="black", size=0.5) +
  labs(title = "With monthly means", x = "Salinity", y = expression(paste("Total alkalinity (",mu, "mol ", kg^-1,")"))) +
  Mytheme()
png(file = "./fig_ta_vs_salinity_monthly_means_pointB_0m.png", 
    width = 20, height = 13, units = "cm", res = 300)
print(p1)
dev.off()

# Alkalinity as a function of precipitation
w <- tbl_df(read.table("../data/meteo_nice_airport/Meteo_2007_2015.csv", header=T, sep=",", dec=".", as.is=T, na.strings = c("NA", "-999", "999999")))
w$sampling_date <- ymd(w$sampling_date)
w$days <- wday(w$sampling_date, label = TRUE, abbr = FALSE)
w$group <- format(w$sampling_date - 1, "%Y%W") # Group the weeks tuesday to monday
w <- w %>%
   group_by(group) %>%
   mutate(rr_cumsum =  cumsum(rr)  ) #cumsum of precipitation tuesday to monday
# take the monday precipitation value (cumsum) and match it with TA of the day after (tuesday).
 w_monday <- w %>%
   filter(days == "Monday")
 w_monday$group <- as.numeric(w_monday$group)
 w_monday$group <-w_monday$group + 1 # Add + 1 to w$group to match with AT

#mean0m$days <- wday(mean0m$sampling_date)
mean0m$group <- format(mean0m$sampling_date, "%Y%W") # Create "group" column in mean0m for AT
mean0m$group <- as.numeric(mean0m$group)

# merge the 2 df
w_AT_precip <- left_join(mean0m,w_monday[,c(2,43:45)], by="group") %>%
  rename(sampling_date=sampling_date.x)

# PLOTS
precip_cumsum <-
  ggplot(w_AT_precip, aes(x = sampling_date, y = rr_cumsum)) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour = "blue", na.rm=TRUE) +
  labs(title = NULL, x = "Time", y = "Weekly precipitation (mm)") +
  Mytheme(size_labs = 9) +
  theme(aspect.ratio = 1/2,
        plot.margin = margin(t=0.25, r=0.5, b=0, l=0, unit = "cm"),
        axis.title.x = element_text(margin=margin(t=0.15, r=0, b=0.25, l=0, unit = "cm"))) +
  annotation_custom(grob_A)

precip_ta <- ggplot(w_AT_precip, aes(x = rr_cumsum, y = mean_ta)) +
  geom_point(colour = "blue", na.rm=TRUE) +
  labs(title = NULL,
       x = "Weekly precipitation (mm)", 
       y = expression(paste(italic(A)[T]," ","(",mu, "mol ", kg^-1,")"))) +
  Mytheme(size_labs = 9) +
  theme(aspect.ratio = 1/2,
        plot.margin = margin(t=0.25, r=0.5, b=0, l=0, unit = "cm"),
        axis.title.x = element_text(margin=margin(t=0.15, r=0, b=0.25, l=0, unit = "cm"))) +
  annotation_custom(grob_B_bl)

precip_S <- ggplot(w_AT_precip, aes(x = rr_cumsum, y = mean_salinity)) +
  geom_point(colour = "blue", na.rm=TRUE) +
  labs(title = NULL,
       x = "Weekly precipitation (mm)", 
       y = "Salinity") +
  Mytheme(size_labs = 9) +
    theme(aspect.ratio = 1/2,
        plot.margin = margin(t=0.25, r=0.5, b=0, l=0, unit = "cm"),
        axis.title.x = element_text(margin=margin(t=0.15, r=0, b=0.25, l=0, unit = "cm"))) +
annotation_custom(grob_C_bl)

g <- plot_grid(precip_cumsum, precip_ta, precip_S, ncol=1, align="h")
ggsave("./precip.png",g, width = 18, height = 14, units = "cm")
ggsave("./figS3.pdf",g, width = 8, height = 14, units = "cm")
```

The relationship between AT and salinity using monthly means is shown below.
![fig_ta_vs_salinity_monthly_means_pointB_0m.png](./fig_ta_vs_salinity_monthly_means_pointB_0m.png)

```{r reg_AT_S_monthly}
  kable(reg_AT_S_monthly, digits = c(3), padding = 0, caption="Regression parameters of the AT=f(S) relationship derived using monthly means.")
```

Salinity and total alkalinity data were compared with the weekly, from Tuesday to Monday, sum of precipitation data (Nice airport). Note that the analysis is incomplete as the 2015 data are currenly missing.
![precip.png](./precip.png)

## Daily and monthly changes in pH and T
```{r Daily and seasonal changes, include=FALSE}
# Long series
continuous_discrete <- read_csv(file = "../data/continuous_discrete.csv", col_names = TRUE)
continuous_discrete$pHspec_Tptb <- as.numeric(continuous_discrete$pHspec_Tptb)
continuous_discrete <- filter(continuous_discrete, date > "2014-06-27 00:00:00")
deploy <- as.numeric(as.POSIXct(
   c("2014-01-07 09:00:08",
  "2014-02-11 09:00:08",
  "2014-04-28 13:00:08",
  "2014-06-27 10:00:08",
  "2014-09-16 08:00:08",
  "2014-11-20 09:30:08",
  "2014-02-11 09:00:08",
  "2014-12-19 09:30:08",
  "2015-03-31 07:10:08",
  "2015-06-01 08:00:08",
  "2015-07-06 08:00:08",
  "2015-09-29 09:00:08",
  "2015-12-08 09:00:08",
  "2016-01-07 09:00:08",
  "2016-03-08 09:00:08",
  "2016-04-08 08:00:08"
  ), tz = "UTC"))
plot_continuous_discrete_pH  <- ggplot(data = filter(continuous_discrete,!is.na(pHT_sfint))) +
  geom_vline(xintercept = deploy, colour="grey") + 
  geom_point(aes(x = date, y = pHT_sfint), size = 0.1) +
  geom_point(data = filter(continuous_discrete, !is.na(pHspec_Tptb)),
    aes(x = date, y = pHspec_Tptb), size = size_point, colour = "#51C56AFF") +
  labs(x = NULL, y=expression(paste(pH[T])), title = NULL) +
  scale_x_datetime(date_breaks="4 months", 
               date_minor_breaks="1 month", labels=date_format("%b %Y")) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank()) +
  annotation_custom(grob_A)

  # Plot Seafet temperature
plot_continuous_discrete_T  <- ggplot(data = filter(continuous_discrete,!is.na(T_seaF))) +
  geom_vline(xintercept = deploy, colour="grey") + 
  geom_point(aes(x = date, y = T_seaF), size = 0.1) +
  labs(x = NULL, y="Temperature (°C)", title = NULL) +
  scale_x_datetime(date_breaks="4 months", 
               date_minor_breaks="1 month", labels=date_format("%b %Y")) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank()) +
  annotation_custom(grob_B)

# Zoom on a few days
date_min <- as.numeric(as.POSIXct("2015-05-01"))
date_max <- as.numeric(as.POSIXct("2015-05-05"))
dat <- filter(continuous_discrete, !is.na(pHT_sfint) & date > date_min & date < date_max)
plot_zoom <- ggplot(data =dat) +
  geom_point(aes(x = date, y = pHT_sfint), size = size_point) +
  labs(x = NULL, y=expression(paste(pH[T])), title = NULL) +
  scale_x_datetime(breaks = date_breaks("1 days"), labels = date_format("%d %b")) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank()) +
  annotation_custom(grob_E)

# Offset between seafet pH and spec pH (Fig. 2 Kapsenberg et al.)
dat <- mutate(continuous_discrete, diff_pH = pHspec_Tptb - pHT_sfint)
average_offset <- mean(abs(dat$diff_pH), na.rm=TRUE)

plot_offset <- ggplot(data = filter(dat, !is.na(diff_pH))) +
  geom_hline(yintercept=mean(dat$diff_pH, na.rm = TRUE), size=0.3) +
  geom_point(aes(x = date, y = diff_pH), size = 1, colour = "#51C56AFF") +
  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
  scale_x_datetime(date_breaks="4 months", 
               date_minor_breaks="1 month", labels=date_format("%b %Y")) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank()) +
  annotation_custom(grob_C)

# Range of daily pH changes
range <- tbl_df(
  dat %>%
  group_by(date=as.Date(date), month=month(date, label=TRUE), year=year(date)) %>%
  summarize(pH_range = max(pHT_sfint) - min(pHT_sfint))
)
quant <- quantile(range$pH_range, probs =c(2.5/100, 97.5/100))

# Per month
range_month <-
  range %>%
  group_by(Month = month(date, label=TRUE, abbr=FALSE)) %>%
  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
# add chla in range_month
range_month <- inner_join(range_month, select(means_month0m, Month, Temperature, Chla), by="Month")
plot_range_pH_Chla_month <-  ggplot(data = range_month) +
  geom_text(aes(x = Chla, y = pH_range_month, label = Month)) +
  labs(x = "Chl-a concentration", y = "pH range", title = NULL) +
  theme_bw()
ggsave("./plot_range_pH_Chla_month.png", plot_range_pH_Chla_month)

plot_range_pH_Temperature <-  ggplot(data = range_month) +
  geom_text(aes(x = Temperature, y = pH_range_month, label = Month), na.rm=TRUE) +
  scale_x_continuous(limits=c(12, 25)) +
  scale_y_continuous(limits=c(0.02, 0.04)) +
  labs(title = NULL,
       x = "Temperature (°C)",
       y = "pH range") +
  Mytheme(size_labs = 9) +
  theme(aspect.ratio=1/2,
        axis.title.x = element_text(margin=margin(t=0.25, r=0, b=0.25, l=0, unit = "cm"))) +
  annotation_custom(grob_A)
ggsave("./plot_range_pH_Temperature.png", plot_range_pH_Temperature)

size_point <- 0.4 # size of data points
plot_range <-  
  ggplot(data=range, aes(x = as.factor(month), y = pH_range)) +
  geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
  geom_boxplot(notch=TRUE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
  labs(y =expression(paste(pH[T], " range")), x=NULL, title=NULL) +
  Mytheme() +
  theme(panel.grid.major.x = element_blank()) +
  annotation_custom(grob_D)

g <- plot_grid(plot_continuous_discrete_pH, plot_continuous_discrete_T, plot_offset, plot_range, plot_zoom, align='vh', ncol=1)
ggsave("./fig_paper_time_series.png", g, width = 18, height = 14, units = "cm")
ggsave(file="./fig6.pdf", g, width = 8, height = 16, units = "cm")

# Per year and week
range$year_week <- paste0(range$year,"-", week(range$date))
range_year_week <-
  ungroup(range) %>%
  group_by(year_week) %>%
  summarize(pH_range_year_week = mean(pH_range, na.rm=TRUE))
# add year_month to weekly data
tmp <- ungroup(mean0m) %>%
  mutate(year_week=paste0(year,"-", week(sampling_date))) %>%
  select(sampling_date, mean_Chla, year_week)
# add chla in range_month
range_year_week <- inner_join(range_year_week, tmp, by="year_week")
plot_range_pH_Chla_week <-  ggplot(data =  range_year_week) +
  geom_point(aes(x = mean_Chla, y = pH_range_year_week), na.rm=TRUE) +
  labs(title = NULL,
       x = expression(paste("Chl-a concentration (mg ", m^-3,")")),
       y = "pH range") +
  Mytheme(size_labs = 9) +
  theme(aspect.ratio=1/2,
        axis.title.x = element_text(margin=margin(t=0.25, r=0, b=0.25, l=0, unit = "cm"))) +
  annotation_custom(grob_B)
ggsave("./plot_range_pH_Chla_week.png", plot_range_pH_Chla_week)

plot_range_pH_Chla_temp <- plot_grid(plot_range_pH_Temperature, plot_range_pH_Chla_week, ncol = 1, align = "h")
ggsave("./plot_range_pH_Chla_temp.png", plot_range_pH_Chla_temp, width = 8)
ggsave("./figS2.pdf", plot_range_pH_Chla_temp, width = 8, height = 8)

```

The average error in pH due to spatiotemporal mismatch between sensor and discrete sample is `r average_offset`.
![fig_paper_time_series.png](./fig_paper_time_series.png)

The quantiles of interest for the daily pH range of the total scale are `r quant ` (respectively 2.5% and 97.5%).

The changes in the daily pH range do not seem to be driven by the concentration of Chl-a nor by temperature.
#![plot_range_pH_Chla_month.png](./plot_range_pH_Chla_month.png)
![plot_range_pH_Chla_temp.png](./plot_range_pH_Chla_temp.png)

## CO2
```{r CO2, include=FALSE}
CO2_pr <- tbl_df(
  read_csv(file="../data/CO2_data_PlateauRosa_daily_1993-2015_R.csv", col_names=TRUE, skip=7)
) %>%
  rename(dt=date) %>%
  mutate(year=year(dt)) %>%
  filter(dt >= "2007-01-01")
NAs_by_year <- summarise(group_by(CO2_pr, year), NAs=sum(is.na(atm_CO2))) # N NAs per year
duration <- CO2_pr$dt[length(CO2_pr$dt)] - CO2_pr$dt[1]
CO2_pr_zoo <- zooreg(CO2_pr$atm_CO2, order.by=CO2_pr$dt) # create zoo time series
CO2_pr_zoo_i <- na.approx(CO2_pr_zoo) # interpolate NAs
CO2_pr_i <- tbl_df(fortify.zoo(CO2_pr_zoo_i)) %>% # change to df
  rename(dt=Index, atm_CO2=CO2_pr_zoo_i) %>%
  mutate(year=year(dt), monthd = month(dt), month = month(dt, label = TRUE, abbr = FALSE))
# add seawater pCO2
tmp <- ungroup(mean0m) %>%
  select(sampling_date, mean_pCO2)
tmp$dt <- as.Date(tmp$sampling_date)
CO2_pr_i <- left_join(CO2_pr_i, tmp)
# Calculate monthly means
tmp <- CO2_pr_i %>%
  group_by(monthd) %>%
  summarise(atm_CO2__month = mean(atm_CO2, na.rm = TRUE))

# Calculate anomalies
ano_atm_CO2 <- left_join(ungroup(CO2_pr_i), tmp, by = "monthd") %>%
  mutate(atm_CO2_ano = atm_CO2 - atm_CO2__month)

#regression atmospheric CO2
lms <- summary(lm(data = CO2_pr_i, atm_CO2 ~ decimal_date(dt)))
prob <- pf(lms$fstatistic[1],lms$fstatistic[2],lms$fstatistic[3],lower.tail=FALSE)
reg_atm_CO2 <- cbind(as.numeric(c(lms$coefficients[2,1], lms$coefficients[2,2], 
                               lms$coefficients[2,4], lms$coefficients[1,1],
                          lms$coefficients[1,2],
                          lms$coefficients[1,4], lms$fstatistic[1], lms$fstatistic[3], lms$r.squared, prob)))
colnames(reg_atm_CO2) <- c("atm_CO2 interpolated")
row.names(reg_atm_CO2) <- c("Slope", "SE Slope", "P Slope","Intercept","SE int.","P int.", "F", "df",
                    "R2","P value")

#regression atmospheric CO2 anomalies
lms <- summary(lm(data = ano_atm_CO2, atm_CO2_ano ~ decimal_date(dt)))
prob <- pf(lms$fstatistic[1],lms$fstatistic[2],lms$fstatistic[3],lower.tail=FALSE)
reg_atm_CO2_ano <- cbind(as.numeric(c(lms$coefficients[2,1], lms$coefficients[2,2], 
                               lms$coefficients[2,4], lms$coefficients[1,1],
                          lms$coefficients[1,2],
                          lms$coefficients[1,4], lms$fstatistic[1], lms$fstatistic[3], lms$r.squared, prob)))
colnames(reg_atm_CO2_ano) <- c("ano_atm_CO2")
row.names(reg_atm_CO2_ano) <- c("Slope", "SE Slope", "P Slope","Intercept","SE int.","P int.", "F", "df",
                    "R2","P value")
# bind the two regression tables
reg_atm_CO2 <- cbind(reg_atm_CO2, reg_atm_CO2_ano)

# plots CO2
# CO2_pr_i_melt <- CO2_pr_i %>%
#   select(dt, atm_CO2, mean_pCO2) %>%
#   melt(id.var = "dt")
CO2_pr_i_melt <- CO2_pr_i %>%
  select(dt, atm_CO2, mean_pCO2) %>%
  gather(key = variable, value=value, -dt, na.rm = TRUE)

fig_CO2_time_series <- ggplot(data=CO2_pr_i_melt) +
  geom_point(aes(x=dt, y=value, colour=variable)) +
  geom_smooth(aes(x=dt, y=value,color=variable), method = "lm") +
  labs(title=NULL, x="Time", y="CO2") +
  Mytheme() +
  theme(legend.position="top") +
  guides(col = guide_legend(ncol = 2, byrow = TRUE))
  annotation_custom(grob_A)

fig_CO2_ano <- ggplot(data = ano_atm_CO2, aes(x = as.POSIXct(dt), y = atm_CO2_ano)) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="orange", na.rm=TRUE, size=size_point) + 
  geom_smooth(method=lm, colour="black", fill="grey", size=0.6) +
  labs(title=NULL, x="Time", y=expression(paste("Atmospheric ", CO[2]))) +
  Mytheme() +
  annotation_custom(grob_B)

fig_delta_CO2 <- ggplot(data = CO2_pr_i, aes(x = as.POSIXct(dt), y = mean_pCO2 - atm_CO2), na.rm=TRUE) +
  scale_x_datetime(breaks = date_breaks("2 year"), labels = date_format("%Y")) +
  geom_point(colour="orange", na.rm=TRUE, size=size_point) + 
  #geom_smooth(method=lm, colour="black", fill="grey", size=0.6) +
  labs(title="Positive values indicate a source for the atmosphere", x="Time", y=expression(paste("Seawater ", pCO[2], " - atmospheric ", CO[2]))) +
  Mytheme() +
  geom_hline(yintercept = 0)

g <- arrangeGrob(fig_CO2_time_series, fig_CO2_ano, ncol=1)
ggsave("./fig_atm_CO2.png", g)
```

Atmospheric concentration of CO2 measured at Plateau Rosa from 1993 to 2015 were downloaded from <http://ds.data.jma.go.jp/gmd/wdcgg/cgi-bin/wdcgg/download.cgi?index=PRS645N00-RSE&param=200612120114&select=inventory>. Note that contributors should be contacted for proper acknowledgement for use of the data or offer of co-authorship
<http://ds.data.jma.go.jp/gmd/wdcgg/cgi-bin/wdcgg/accessdata.cgi?lang=&contributor_index=200612120057>

There are missing data:

```{r kable NAs atm CO2}
  kable(NAs_by_year, digits = c(0,0), padding = 0, caption="Number of days without atmospheric CO2 data.")
```

Missing values were filled by linear interpolation between nearest values in order to obtain the same sampling number per year. The rate of increase was calculated by regressing the CO$_2$ concentration (`r round(reg_atm_CO2[1,1], digit=2)` ppm per year) and the anomaly (`r round(reg_atm_CO2[1,2], digit=2)` ppm per year) following subtraction of monthly means against time.

The rate of increase of seawater pCO2 (`r round(reg_var[7,1], digit=2)` uatm per year) is much larger than that of atmospheric CO2 (`r round(reg_atm_CO2[1,1], digit=2)` ppm per year).

![fig_atm_CO2.png](./fig_atm_CO2.png)

```{r Table reg atm CO2}
  kable(reg_atm_CO2, digits = c(2,2), caption="Regressions of atmospheric CO2 (time series and anomalies).")
```

```{r deffayes plot}
ct <- seq(2155e-6, 2300e-6, length.out=20)
at <- seq(2455e-6, 2600e-6, length.out=20)
grid_data <- data.frame(ct=ct, at=at)
zz <- tbl_df(expand.grid(ct,at))
colnames(zz) <- c("ct", "at")
zz2 <- carb(flag=15, var1=zz$at, var2=zz$ct, S=38, T=18, P=0)
zz$pCO2 <- zz2$pCO2
zz$CO3 <- zz2$CO3
zz$pH <- zz2$pH
deff <- ggplot() + 
  geom_contour(data=zz, aes(x=ct*1e6, y=at*1e6, z=pH), stat = "contour", binwidth = 0.1, na.rm=TRUE) +
stat_contour(aes(colour=..level..), breaks=c(8, 8.1, 8.2)) +
  geom_point(data=mean0m, aes(x = mean_dic, y=mean_ta, col=as.factor(year)), na.rm=TRUE) + 
  scale_color_viridis(name="Year", discrete=TRUE, option="plasma")

deff_monthly <- ggplot() + 
  stat_contour(data=zz, aes(x=ct*1e6, y=at*1e6, z=pH), breaks=seq(8,8.2, by=0.1), col="blue", na.rm=TRUE) +
  geom_text(data=mean0m_month, aes(x = ct, y=at, label=monthd, col=as.factor(year)), na.rm=TRUE) + 
    lims(x=c(2190, 2275), y=c(2510, 2580)) +
scale_color_viridis(name="Year", discrete=TRUE, option="plasma") +
    labs(title="Point B", 
       x=expression(paste(italic(C)[T]," ","(",mu, mol.kg^-1,")")),
       y=expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")")))

deff_monthly <- ggplot() +
  stat_contour(
  data = zz,
  aes(x = ct * 1e6, y = at * 1e6, z = pH),
  breaks = seq(8, 8.2, by = 0.05),
  col = "blue",
  na.rm = TRUE
  ) +
  geom_text(data = mean0m_month,
  aes(x = ct, y = at, label = substr(mean0m_month$year, 3, 4), col = as.factor(monthd)),
  na.rm = TRUE) +
  lims(x = c(2190, 2275), y = c(2510, 2580)) +
  labs(title="Point B, coded with month (color) and year (digits)", 
       x=expression(paste(italic(C)[T]," ","(",mu, mol.kg^-1,")")),
       y=expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  scale_color_viridis(name = "Month", discrete = TRUE, option = "plasma")
  #direct.label(deff_monthly, "top.pieces")
  ggsave(file = "./fig_deffayes_monthly.png", deff_monthly,
  width = 15, height = 15, units = "cm")

# Yearly Deffayes plot
tmp <- summarize_all(group_by(mean0m_month, year), mean)
deff_yearly <- ggplot() +
  stat_contour(
  data = zz,
  aes(x = ct * 1e6, y = at * 1e6, z = pH),
  breaks = seq(8, 8.2, by = 0.05),
  col = "blue",
  na.rm = TRUE
  ) +
  geom_text(data = tmp ,
  aes(x = ct, y = at, label = substr(tmp$year, 3, 4)),
  na.rm = TRUE) +
  lims(x = c(2190, 2275), y = c(2510, 2580)) +
  labs(title="Point", 
       x=expression(paste(italic(C)[T]," ","(",mu, mol.kg^-1,")")),
       y=expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  scale_color_viridis(name = "Month", discrete = TRUE, option = "plasma")
  #ggsave(file = "./fig_deffayes_monthly.png", deff_monthly, width = 15, height = 15, units = "cm")

# Quarterly Deffayes plot
tmp <- ungroup(mean0m) %>%
  select(mean_dic, mean_ta, year, quarter) %>%
  rename(ct=mean_dic, at=mean_ta) %>%
  group_by(year, quarter) %>%
  summarize_all(mean,na.rm=TRUE)
deff_quarterly <- ggplot() +
  stat_contour(
  data = zz,
  aes(x = ct * 1e6, y = at * 1e6, z = pH),
  breaks = seq(8, 8.2, by = 0.05),
  col = "blue",
  na.rm = TRUE
  ) +
  geom_text(data = tmp ,
  aes(x = ct, y = at, label = tmp$quarter, col=as.factor(tmp$year)),
  na.rm = TRUE) +
  lims(x = c(2190, 2275), y = c(2510, 2580)) +
  labs(title="Point", 
       x=expression(paste(italic(C)[T]," ","(",mu, mol.kg^-1,")")),
       y=expression(paste(italic(A)[T]," ","(",mu, mol.kg^-1,")"))) +
  scale_color_viridis(name = "Month", discrete = TRUE, option = "plasma")
```

Test of a Deffayes plot.
![fig_deffayes_monthly.png](./fig_deffayes_monthly.png)

### 2021-08-02 awipev-CO2.Rmd
clean-up and fiddle with date discrete data

@@
 ) %>% 
-  dplyr::mutate(datetime = dmy_hm(sampling_date, tz="UTC"),
-                measure_date = dmy(measure_date, tz="UTC"),
+  dplyr::mutate(datetime = ymd_hm(sampling_date, tz="UTC"),
+                measure_date = ymd(measure_date, tz="UTC"),
                 date = as.Date(datetime)) %>% 
+#  dplyr::filter(datetime < as.POSIXct("2021-01-01 00:00:00")) %>% #eliminate 2021 data
   dplyr::rename(ph_s_sf = pH_s_seafet,
@@
                               Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74"),
-   ph_s_dur_temp_4_l = pHinsi(pH = pH_durafet$ph_s_dur, # lueker
+   ph_s_dur_temp_4 = pHinsi(pH = pH_durafet$ph_s_dur, # lueker
                          ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
@@
                          pHscale = "T", b="u74"),
-   ph_s_dur_temp_4_s20 = pHinsi(pH = pH_durafet$ph_s_dur, # Sulpis
-                         ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
-                         Tlab = pH_durafet$temp_s_lab, Pinsi = 0, 
-                         S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74"),       # Millero 02
-   ph_s_dur_temp_4_p18 = pHinsi(pH = pH_durafet$ph_s_dur, # Papadimitriou
-                         ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
-                         Tlab = pH_durafet$temp_s_lab, Pinsi = 0, 
-                         S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74"),
-   ph_s_dur_temp_4_m02 = pHinsi(pH = pH_durafet$ph_s_dur,  # Millero 02
-                         ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
-                         Tlab = pH_durafet$temp_s_lab, Pinsi = 0, 
-                         S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+
+   # ph_s_dur_temp_4_l = pHinsi(pH = pH_durafet$ph_s_dur, # lueker
+   #                       ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
+   #                       Tlab = pH_durafet$temp_s_lab, Pinsi = 0, 
+   #                       S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
+   #                       pHscale = "T", b="u74"),
+   # ph_s_dur_temp_4_s20 = pHinsi(pH = pH_durafet$ph_s_dur, # Sulpis
+   #                       ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
+   #                       Tlab = pH_durafet$temp_s_lab, Pinsi = 0, 
+   #                       S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
+   #                       pHscale = "T", b="u74"),       # Millero 02
+   # ph_s_dur_temp_4_p18 = pHinsi(pH = pH_durafet$ph_s_dur, # Papadimitriou
+   #                       ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
+   #                       Tlab = pH_durafet$temp_s_lab, Pinsi = 0, 
+   #                       S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
+   #                       pHscale = "T", b="u74"),
+   # ph_s_dur_temp_4_m02 = pHinsi(pH = pH_durafet$ph_s_dur,  # Millero 02
+   #                       ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4, 
+   #                       Tlab = pH_durafet$temp_s_lab, Pinsi = 0, 
+   #                       S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
+   #                       pHscale = "T", b="u74")
 
@@
   dplyr::summarise(ph_s_sf_temp_insi_mean = mean(ph_s_sf_temp_insi, na.rm = TRUE),
-                   #ph_s_sf_temp_insi_sd = sd(ph_s_sf_temp_insi, na.rm = TRUE),
+                   ph_s_sf_temp_insi_sd = sd(ph_s_sf_temp_insi, na.rm = TRUE),
                    ph_s_sf_temp_4_mean = mean(ph_s_sf_temp_4, na.rm = TRUE)
@@
 pH_durafet_mean <- pH_durafet %>%
-  dplyr::select(date, ph_s_dur_temp_fb, ph_s_dur_temp_4_l, ph_s_dur_temp_4_s20,
-                ph_s_dur_temp_4_p18, ph_s_dur_temp_4_m02) %>% 
+  dplyr::select(date, ph_s_dur_temp_fb, ph_s_dur_temp_4) %>% 
   dplyr::group_by(date) %>% 
   dplyr::summarize(ph_s_dur_temp_fb_mean = mean(ph_s_dur_temp_fb, na.rm = TRUE),
-                   #ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE),
-                   ph_s_dur_temp_4_l_mean = mean(ph_s_dur_temp_4_l, na.rm = TRUE),
-                   ph_s_dur_temp_4_s20_mean = mean(ph_s_dur_temp_4_s20, na.rm = TRUE),
-                   ph_s_dur_temp_4_p18_mean = mean(ph_s_dur_temp_4_p18, na.rm = TRUE),
-                   ph_s_dur_temp_4_m02_mean = mean(ph_s_dur_temp_4_m02, na.rm = TRUE)
-                   )
-
+                   ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE),
+                   ph_s_dur_temp_4_mean = sd(ph_s_dur_temp_4, na.rm = TRUE))
+
+#bind all spectro measurements, just to assess sd, change name of dataframe only to do the rbind.
+seafetph <- pH_seafet_mean
+colnames(seafetph) <- c("date", "mean", "sd")
+durafetph <- pH_durafet_mean
+colnames(durafetph) <- c("date", "mean", "sd")
+pH_seafet_durafet <- rbind(seafetph,durafetph)
+#calculations for all pH spectro measurement for sd
+sd_min <- min(pH_seafet_durafet$sd)
+sd_max <- max(pH_seafet_durafet$sd)
+sd_mean <- mean(pH_seafet_durafet$sd)
+# =======
+#                    #ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE),
+#                    ph_s_dur_temp_4_l_mean = mean(ph_s_dur_temp_4_l, na.rm = TRUE),
+#                    ph_s_dur_temp_4_s20_mean = mean(ph_s_dur_temp_4_s20, na.rm = TRUE),
+#                    ph_s_dur_temp_4_p18_mean = mean(ph_s_dur_temp_4_p18, na.rm = TRUE),
+#                    ph_s_dur_temp_4_m02_mean = mean(ph_s_dur_temp_4_m02, na.rm = TRUE)
+#                    )
+# >>>>>>> 0d3b58ee3abb01c904f165290b5c76bfe7270c1f
+
+#put back the right column name for the following script
+pH_durafet_mean$ph_s_dur_temp_fb <- pH_durafet_mean$ph_s_dur_temp_fb_mean
+pH_seafet_mean$ph_s_sf_temp_insi <- pH_seafet_mean$ph_s_sf_temp_insi_mean
 #  make means in "d" to have same format and call it "discrete"
@@
 discrete2merge <- discrete %>%
-  dplyr::select(closest_datetime, ph_s_dur_temp_fb_mean, ph_s_dur_temp_4_l_mean,
-                ph_s_dur_temp_4_s20_mean, ph_s_dur_temp_4_p18_mean, ph_s_dur_temp_4_m02_mean) %>%
+  dplyr::select(closest_datetime, ph_s_dur_temp_fb_mean, ph_s_dur_temp_4_mean) %>%
   dplyr::rename(ph_s_dur_temp_fb = ph_s_dur_temp_fb_mean,
-                ph_s_dur_temp_4 = ph_s_dur_temp_4_l_mean, # lueker by default
-                ph_s_dur_temp_4_l = ph_s_dur_temp_4_l_mean,
-                ph_s_dur_temp_4_s20 = ph_s_dur_temp_4_s20_mean,
-                ph_s_dur_temp_4_p18 = ph_s_dur_temp_4_p18_mean,
-                ph_s_dur_temp_4_m02 = ph_s_dur_temp_4_m02_mean,) %>%
+                ph_s_dur_temp_4 = ph_s_dur_temp_4_mean # lueker by default
+                ) %>%
   dplyr::filter(!is.na(closest_datetime)) %>%
@@
 
-# In order to remove the temperature effect from the observed pCO2 , the observed pCO2 values are normalized to a constant temperature (annual mean) -- Takahashi et al. (2002)
+# In order to remove the temperature effect from the observed pCO2, the observed pCO2 values are normalized to a constant temperature (annual mean) -- Takahashi et al. (2002)
 temp_mean <- mean(taka$temp_insitu_11m, na.rm = TRUE)

### 2021-08-03 awipev-CO2_old.Rmd
Fixed mess, now functional

--- 2021-08-02 awipev-CO2.Rmd
@@
 ) %>% 
-  dplyr::mutate(datetime = ymd_hm(sampling_date, tz="UTC"),
+  dplyr::mutate(datetime = ymd_hms(sampling_date, tz="UTC"),
                 measure_date = ymd(measure_date, tz="UTC"),
                 date = as.Date(datetime)) %>% 
-#  dplyr::filter(datetime < as.POSIXct("2021-01-01 00:00:00")) %>% #eliminate 2021 data
+  dplyr::filter(datetime < as.POSIXct("2021-01-01 00:00:00")) %>% #eliminate 2021 data
   dplyr::rename(ph_s_sf = pH_s_seafet,

### 2021-08-04 awipev-CO2.Rmd
Takahashi thermal vs non-thermal finalized

@@
                          pHscale = "T", b="u74"),
-   ph_s_sf_temp_4 = pHinsi(pH = pH_seafet$ph_s_sf, 
+   ph_s_sf_temp_4 = pHinsi(pH = pH_seafet$ph_s_sf, # with Lueker
                          ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
@@
                          S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d",
-                         pHscale = "T", b="u74"),
-
+                         pHscale = "T", b="u74")#,
    # ph_s_dur_temp_4_l = pHinsi(pH = pH_durafet$ph_s_dur, # lueker
@@
                    ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE),
-                   ph_s_dur_temp_4_mean = sd(ph_s_dur_temp_4, na.rm = TRUE))
+                   ph_s_dur_temp_4_mean = mean(ph_s_dur_temp_4, na.rm = TRUE))
 
@@
 colnames(durafetph) <- c("date", "mean", "sd")
-pH_seafet_durafet <- rbind(seafetph,durafetph)
-#calculations for all pH spectro measurement for sd
-sd_min <- min(pH_seafet_durafet$sd)
-sd_max <- max(pH_seafet_durafet$sd)
-sd_mean <- mean(pH_seafet_durafet$sd)
-# =======
-#                    #ph_s_dur_temp_fb_sd = sd(ph_s_dur_temp_fb, na.rm = TRUE),
-#                    ph_s_dur_temp_4_l_mean = mean(ph_s_dur_temp_4_l, na.rm = TRUE),
-#                    ph_s_dur_temp_4_s20_mean = mean(ph_s_dur_temp_4_s20, na.rm = TRUE),
-#                    ph_s_dur_temp_4_p18_mean = mean(ph_s_dur_temp_4_p18, na.rm = TRUE),
-#                    ph_s_dur_temp_4_m02_mean = mean(ph_s_dur_temp_4_m02, na.rm = TRUE)
-#                    )
-# >>>>>>> 0d3b58ee3abb01c904f165290b5c76bfe7270c1f
+#pH_seafet_durafet <- rbind(seafetph, durafetph)
+# #calculations for all pH spectro measurement for sd
+# sd_min <- min(pH_seafet_durafet$sd)
+# sd_max <- max(pH_seafet_durafet$sd)
+# sd_mean <- mean(pH_seafet_durafet$sd)
 
@@
   tidyr::drop_na(pco2_fb, at, sal_fb, temp_fb) %>% 
-  dplyr::select(datetime, ph_s_dur_temp_4_l, ph_s_dur_temp_4_s20,
-                ph_s_dur_temp_4_p18, ph_s_dur_temp_4_m02, pco2_fb, at, sal_fb, temp_fb) %>% 
+  dplyr::select(datetime, ph_s_dur_temp_fb, pco2_fb, at, sal_fb, temp_fb) %>% 
+  dplyr::mutate(
+    ph_s_dur_temp_4_l = pHinsi(pH = ph_s_dur_temp_fb, # lueker
+                         ALK = at*1e-6, Tinsi = 4,
+                         Tlab = temp_fb, Pinsi = 0,
+                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d",
+                         pHscale = "T", b="u74"),
+   ph_s_dur_temp_4_s20 = pHinsi(pH = ph_s_dur_temp_fb, # Sulpis
+                         ALK = at*1e-6, Tinsi = 4,
+                         Tlab = temp_fb, Pinsi = 0,
+                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d",
+                         pHscale = "T", b="u74"),       # Millero 02
+   ph_s_dur_temp_4_p18 = pHinsi(pH = ph_s_dur_temp_fb, # Papadimitriou
+                         ALK = at*1e-6, Tinsi = 4,
+                         Tlab = temp_fb, Pinsi = 0,
+                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d",
+                         pHscale = "T", b="u74"),
+   ph_s_dur_temp_4_m02 = pHinsi(pH = ph_s_dur_temp_fb,  # Millero 02
+                         ALK = at*1e-6, Tinsi = 4,
+                         Tlab = temp_fb, Pinsi = 0,
+                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d",
+                         pHscale = "T", b="u74")
+   ) %>% 
+  # dplyr::select(datetime, ph_s_dur_temp_4_l, ph_s_dur_temp_4_s20,
+  #               ph_s_dur_temp_4_p18, ph_s_dur_temp_4_m02, pco2_fb, at, sal_fb, temp_fb) %>%
 # This is an important adjustement for pco2_fb on 2019-06-07 09:00:00
@@
   tidyr::drop_na(ct, at, sal_fb, temp_fb) %>% 
-  dplyr::select(datetime, ph_s_dur_temp_4_l, ph_s_dur_temp_4_s20,
-                ph_s_dur_temp_4_p18, ph_s_dur_temp_4_m02, ct, at, sal_fb, temp_fb)
+  dplyr::select(datetime, ph_s_dur_temp_fb, ct, at, sal_fb, temp_fb) %>% 
+  dplyr::mutate(
+    ph_s_dur_temp_4_l = pHinsi(pH = ph_s_dur_temp_fb, # lueker
+                         ALK = at*1e-6, Tinsi = 4,
+                         Tlab = temp_fb, Pinsi = 0,
+                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d",
+                         pHscale = "T", b="u74"),
+   ph_s_dur_temp_4_s20 = pHinsi(pH = ph_s_dur_temp_fb, # Sulpis
+                         ALK = at*1e-6, Tinsi = 4,
+                         Tlab = temp_fb, Pinsi = 0,
+                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d",
+                         pHscale = "T", b="u74"),       # Millero 02
+   ph_s_dur_temp_4_p18 = pHinsi(pH = ph_s_dur_temp_fb, # Papadimitriou
+                         ALK = at*1e-6, Tinsi = 4,
+                         Tlab = temp_fb, Pinsi = 0,
+                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d",
+                         pHscale = "T", b="u74"),
+   ph_s_dur_temp_4_m02 = pHinsi(pH = ph_s_dur_temp_fb,  # Millero 02
+                         ALK = at*1e-6, Tinsi = 4,
+                         Tlab = temp_fb, Pinsi = 0,
+                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d",
+                         pHscale = "T", b="u74")
+   )
 # Using Lueker  
@@
 
-## Takahashi thermal vs biological
-```{r Takahashi thermal vs biological, include=FALSE}
+## Takahashi thermal vs non-thermal
+```{r Takahashi thermal vs non-thermal, include=FALSE}
+# According to Takahashi et al. (2002) and McCutcheon et al. (2021)
 # Select data
 taka <- d_all %>% # just for this chunk
-  dplyr::select(datetime, monthd, sal_fb, temp_insitu_11m, pco2_fb_insi_temp)
-
-# In order to remove the temperature effect from the observed pCO2, the observed pCO2 values are normalized to a constant temperature (annual mean) -- Takahashi et al. (2002)
-temp_mean <- mean(taka$temp_insitu_11m, na.rm = TRUE)
-taka <- taka %>% 
-  dplyr::mutate(pco2_mean_temp = pco2_fb_insi_temp * exp(0.0423 * (temp_mean - temp_insitu_11m)))
-d_pco2_bio <- max(taka$pco2_mean_temp, na.rm = TRUE) - min(taka$pco2_mean_temp, na.rm = TRUE)
-d_pco2_temp <- max(taka$pco2_fb_insi_temp, na.rm = TRUE) - min(taka$pco2_fb_insi_temp, na.rm = TRUE)
-temp_bio <- d_pco2_temp / d_pco2_bio
-```
+  dplyr::select(datetime, monthd, sal_fb, temp_insitu_11m, pco2_fb_insi_temp) %>% 
+  dplyr::mutate(year = lubridate::year(datetime),
+                season = dplyr::case_when(monthd %in% c(12, 1, 2) ~ "winter",
+                                          monthd %in% c(3, 4, 5) ~ "spring",
+                                          monthd %in% c(6, 7, 8) ~ "summer",
+                                          monthd %in% c(9, 10, 11) ~ "fall")) %>% 
+  # eliminate years 2015 and 2021 which are incomplete
+  dplyr::filter(datetime > as.POSIXct("2016-01-01 00:00:00") &
+                  datetime < as.POSIXct("2021-01-01 00:00:00"))
+
+# annual 
+taka_year <- taka %>% 
+  group_by(year) %>% 
+  dplyr::mutate(pco2_thermal = 
+                  mean(pco2_fb_insi_temp, na.rm = TRUE) * exp(0.0423 * (temp_insitu_11m - mean(temp_insitu_11m, na.rm = TRUE))),
+                  pco2_nonthermal = pco2_fb_insi_temp * exp(0.0423 * (mean(temp_insitu_11m, na.rm = TRUE) - temp_insitu_11m))) %>% 
+  dplyr::summarise(thermal = max(pco2_thermal, na.rm = TRUE) - min(pco2_thermal, na.rm = TRUE),
+                   nonthermal = max(pco2_nonthermal, na.rm = TRUE) - min(pco2_nonthermal, na.rm = TRUE),
+                   thermal_nonthermal = thermal / nonthermal) %>% 
+  ungroup()
+
+# season 
+taka_season <- taka %>% 
+  group_by(season) %>% 
+  dplyr::mutate(pco2_thermal = 
+                  mean(pco2_fb_insi_temp, na.rm = TRUE) * exp(0.0423 * (temp_insitu_11m - mean(temp_insitu_11m, na.rm = TRUE))),
+                  pco2_nonthermal = pco2_fb_insi_temp * exp(0.0423 * (mean(temp_insitu_11m, na.rm = TRUE) - temp_insitu_11m))) %>% 
+  dplyr::summarise(thermal = max(pco2_thermal, na.rm = TRUE) - min(pco2_thermal, na.rm = TRUE),
+                   nonthermal = max(pco2_nonthermal, na.rm = TRUE) - min(pco2_nonthermal, na.rm = TRUE),
+                   thermal_nonthermal = thermal / nonthermal) %>% 
+  ungroup()
+```
+`r knitr::kable(taka_year, digits = c(0, 1, 1, 2), caption = "Thermal vs non-thermal control of pCO2. Yearly estimate.", format = "simple")`
+`r knitr::kable(taka_season, digits = c(0, 1, 1, 2), caption = "Thermal vs non-thermal control of pCO2. Seasonal estimate.", format = "simple")`
+For seasonal analysis, December to February was considered winter, March to May was considered spring, June to August was considered summer, and September to November was considered fall.
+
+The control of pCO2 by non-thermal (physical and biological processes) drivers is always greater than the control from temperature on both annual and seasonal basis.
+Thermal control is highest in winter and lowest in summer.
 

### 2021-08-24 awipev-CO2.Rmd
Takahashi thermal vs non-thermal finalized
revised ranges

@@
 ```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
+my_skim <- skim_with(numeric = sfl(ave = ~ mean(., na.rm = TRUE),
+                                   med = ~ median(., na.rm = TRUE),
+                                   min = ~ min(., na.rm = TRUE),
+                                   max = ~ max(., na.rm = TRUE),
+                                   q5 = ~ quantile(., 0.05, na.rm = TRUE),
+                                   q95 = ~ quantile(., 0.95, na.rm = TRUE)
+                                   ), 
+                     append = FALSE)
+
 range_month <-
   d_all %>%
+  dplyr::select(montht, sal_mix, temp_mix, temp_insitu_11m, pHint_tot_sf_9m) %>% 
   group_by(montht) %>%
-  #summarize(pH_range_month = mean(pH_range, na.rm=TRUE))%>%
-  summarize(temp_mix_max = round( max(temp_mix, na.rm=TRUE), digits = 2),
-            temp_mix_min = round(min(temp_mix, na.rm=TRUE), digits = 2),
-            temp_ctd_1m_max = round( max(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
-            temp_ctd_1m_min = round(min(temp_insitu_ctd_1m, na.rm=TRUE), digits = 2),
-            temp_ctd_3m_max = round( max(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
-            temp_ctd_3m_min = round(min(temp_insitu_ctd_3m, na.rm=TRUE), digits = 2),
-            temp_ctd_5m_max = round( max(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
-            temp_ctd_5m_min = round(min(temp_insitu_ctd_5m, na.rm=TRUE), digits = 2),
-            temp_ctd_7m_max = round( max(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
-            temp_ctd_7m_min = round(min(temp_insitu_ctd_7m, na.rm=TRUE), digits = 2),
-            temp_ctd_9m_max = round( max(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
-            temp_ctd_9m_min = round(min(temp_insitu_ctd_9m, na.rm=TRUE), digits = 2),
-            temp_11m_max = round( max(temp_insitu_11m, na.rm=TRUE), digits = 2),
-            temp_11m_min = round(min(temp_insitu_11m, na.rm=TRUE), digits = 2),
-            temp_fb_max = round(max(temp_fb, na.rm=TRUE), digits = 2),
-            temp_fb_min = round( min(temp_fb, na.rm=TRUE), digits = 2),
-            sal_mix_max = round(max(sal_mix, na.rm=TRUE), digits = 2),
-            sal_mix_min = round(min(sal_mix, na.rm=TRUE), digits = 2),
-            sal_ctd_1m_max = round( max(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
-            sal_ctd_1m_min = round(min(sal_insitu_ctd_1m, na.rm=TRUE), digits = 2),
-            sal_ctd_3m_max = round( max(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
-            sal_ctd_3m_min = round(min(sal_insitu_ctd_3m, na.rm=TRUE), digits = 2),
-            sal_ctd_5m_max = round( max(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
-            sal_ctd_5m_min = round(min(sal_insitu_ctd_5m, na.rm=TRUE), digits = 2),
-            sal_ctd_7m_max = round( max(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
-            sal_ctd_7m_min = round(min(sal_insitu_ctd_7m, na.rm=TRUE), digits = 2),
-            sal_ctd_9m_max = round( max(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
-            sal_ctd_9m_min = round(min(sal_insitu_ctd_9m, na.rm=TRUE), digits = 2),
-            sal_fb_max = round(max(sal_fb, na.rm=TRUE), digits = 2),
-            sal_fb_min = round(min(sal_fb, na.rm=TRUE), digits = 2),
-            pH_sf_max = round(max(pHint_tot_sf_9m, na.rm=TRUE), digits = 4),
-            pH_sf_min = round(min(pHint_tot_sf_9m, na.rm=TRUE), digits = 4))
+  my_skim()
 kable(range_month, caption = "")

### 2021-08-24 awipev-CO2.Rmd
refine pCO2

@@
 ```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
-title <- "Contros vs calculated pCO2"
-fit <- lmodel2(data = d_all,  pco2_fb ~ pco2_calc_fb , nperm = 99)
-
-p <-  ggplot(d_all,aes(x=pco2_calc_fb, y= pco2_fb, label = monthd))+
-   geom_text(aes(color = factor(monthd)))+
+title <- "Calculated vs Contros pCO2"
+fit <- lmodel2(data = d_all,   pco2_calc_fb ~ pco2_fb, nperm = 99)
+print(fit)
+p <-  ggplot(d_all,aes(x = pco2_fb, y = pco2_calc_fb))+
+  geom_point()+
   scale_color_discrete(guide="none")+
@@
   geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
-                     "; Intercept =", signif(fit$regression.results[2,2], 3),
-                     "; Slope =", signif( fit$regression.results[2,3], 3),
-                     "; P =", signif(fit$P.param, 3))) +
+  # labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
+  #                    "; Intercept =", signif(fit$regression.results[2,2], 3),
+  #                    "; Slope =", signif( fit$regression.results[2,3], 3),
+  #                    "; P =", signif(fit$P.param, 3))) +
   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
   coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
-  labs(x="Calculated pCO2", y="Contros pCO2") + theme_bw()  
-```
-The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
+  labs(x="Contros pCO2", y="Calculated pCO2") + theme_bw()  
+```
+
+The relationship between the Contros and calculated pCO2 is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
+
 ```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
@@
 
-### **Final *p*CO~2~ data**
+### **pCO~2~ time series**
 

### 2021-08-24 awipev-CO2.Rmd
refine pCO2

@@
   error <- col_x - predicted
-  my_list <- list(fit = print(fit), rmse = sqrt(mean(error^2, na.rm=TRUE)))
+  my_list <- list(intercept_MA = intercept_MA, 
+                  slope_MA = slope_MA,
+                  intercept_OLS = intercept_MA, 
+                  slope_OLS = slope_MA,
+                  rmse = sqrt(mean(error^2, na.rm=TRUE)))
   return(my_list)
@@
 
-```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
-title <- "Calculated vs Contros pCO2"
-fit <- lmodel2(data = d_all,   pco2_calc_fb ~ pco2_fb, nperm = 99)
+```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
+title <- "pCO2 normalized at in situ temperature"
+fit <- lmodel2(data = d_all,   pco2_calc_fb_insi_temp ~ pco2_fb_insi_temp, nperm = 99)
 print(fit)
@@
   #                    "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
-  labs(x="Contros pCO2", y="Calculated pCO2") + theme_bw()  
-```
-
-The relationship between the Contros and calculated pCO2 is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
+  theme(aspect.ratio=1, plot.title = element_text(size=7)) + 
+  coord_fixed(ratio = 1, xlim=c(200,420), ylim=c(200,420))+
+  labs(title = "", x="Measured pCO2", y="Calculated pCO2") + theme_bw()  
+print(p)
+ggsave(filename = "figures/pco2_calc_meas.png", plot = p)
+```
+
+The relationship between the measured (Contros) and calculated pCO2 (blue line) is relatively poor.
+It is far from the 1:1 relationship (black dashed line).
+The slope is `r signif(fit$regression.results[2,3], 3)`) and its 95% confidence interval does include 1; r2 is `r round(fit$rsquare, digits=2)`.
+
+**Figure legend**: pCO2 calculated from AT and CT as a function of pCO2 measured using a Contros sensor.
+All data are normalized at in situ temperature.
+The black dotted line is the 1:1 line while the blue solid line shows the line obtained by a major axis regression (Legendre, 2018- Pierre Legendre (2018).
+lmodel2: Model II Regression.
+R package version 1.7-3.
+https://CRAN.R-project.org/package=lmodel2
 
 ```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-print(p) # pco2_calc_fb_pco2_corr_text
+# print(p)
+# 
 ```

### 2021-08-25 awipev-CO2.Rmd

@@
 https://CRAN.R-project.org/package=lmodel2
+=======
+  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
+  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
+  labs(x="Contros pCO2", y="Calculated pCO2") + theme_bw()  
+```
+
+The relationship between the Contros and calculated pCO2 is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
+>>>>>>> cb6a0f5891d0a4e43735bed5507c62760ae133cb
 

### 2021-10-25 awipev-CO2.Rmd
changed read discrete data and now use 2021 data

@@
 ) %>% 
-  dplyr::mutate(datetime = ymd_hms(sampling_date, tz="UTC"),
+  dplyr::mutate(datetime = ymd_hm(sampling_date, tz="UTC"),
                 measure_date = ymd(measure_date, tz="UTC"),
                 date = as.Date(datetime)) %>% 
-  dplyr::filter(datetime < as.POSIXct("2021-01-01 00:00:00")) %>% #eliminate 2021 data
+  #dplyr::filter(datetime < as.POSIXct("2021-01-01 00:00:00")) %>% #eliminate 2021 data
   dplyr::rename(ph_s_sf = pH_s_seafet,
@@
  # And keep data with flag 0 for FB location
-d <- d%>%
+d <- d %>%
   dplyr::mutate(location_flag = ifelse(datetime == as.POSIXct("2016-04-21 09:25:00") | 

### 2021-10-25 awipev-CO2.Rmd
Revised lm2

@@
   error <- col_x - predicted
+  rsquare <- fit$rsquare
+  P.param <- fit$P.param
   my_list <- list(intercept_MA = intercept_MA, 
@@
                   slope_OLS = slope_MA,
+                  rsquare = rsquare,
+                  P = P.param,
                   rmse = sqrt(mean(error^2, na.rm=TRUE)))
@@
   geom_abline(slope=1, intercept=0, linetype = "dashed")+
-  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),colour = "blue") +
+  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue") +
   ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
-  labs(title = paste("","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
-                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
-                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
-                     "; P =", signif(lm$fit$P.param, 3),
+  labs(title = paste("","\n Adj R2 = ", signif(lm$rsquare, 3),
+                     "; Intercept =", signif(lm$intercept_MA, 3),
+                     "; Slope =", signif(lm$slope_MA, 3),
+                     "; P =", signif(lm$P, 3),
                      "; RMSE = ", signif(lm$rmse, 3))) +

### 2021-10-25 awipev-CO2.Rmd
Revised code for lm2 coefficients. Commented ghost code. drop_na ph_s_dur_temp_fb

@@
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
-              colour = "blue") +
-  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
-                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
-                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
-                     "; P =", signif(lm$fit$P.param, 3),
+  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue")  +
+  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm$rsquare, 3),
+                     "; Intercept =", signif(lm$intercept_MA, 3),
+                     "; Slope =", signif(lm$slope_MA, 3),
+                     "; P =", signif(lm$P, 3),
                      "; RMSE = ", signif(lm$rmse, 3))) +
@@
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
-              colour = "blue") +
-  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
-                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
-                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
-                     "; P =", signif(lm$fit$P.param, 3),
+  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue")  +  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(lm$rsquare, 3),
+                     "; Intercept =", signif(lm$intercept_MA, 3),
+                     "; Slope =", signif(lm$slope_MA, 3),
+                     "; P =", signif(lm$P, 3),
                      "; RMSE = ", signif(lm$rmse, 3))) +
@@
 https://CRAN.R-project.org/package=lmodel2
-=======
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
-  labs(x="Contros pCO2", y="Calculated pCO2") + theme_bw()  
-```
+<!-- ======= -->
+<!--   theme(aspect.ratio=1,plot.title = element_text(size=7)) +  -->
+<!--   coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+ -->
+<!--   labs(x="Contros pCO2", y="Calculated pCO2") + theme_bw()   -->
+<!-- ``` -->
 
 The relationship between the Contros and calculated pCO2 is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
->>>>>>> cb6a0f5891d0a4e43735bed5507c62760ae133cb
+<!-- >>>>>>> cb6a0f5891d0a4e43735bed5507c62760ae133cb -->
 
@@
   geom_abline(slope=1, intercept =0, linetype = "dashed") +
-  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
+  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),
               colour = "blue") +
-  labs(title = paste("pH spectro vs pH durafet (both at FB temperature","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
-                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
-                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
-                     "; P =", signif(lm$fit$P.param, 3),
+  labs(title = paste("pH spectro vs pH durafet (both at FB temperature","\n Adj R2 = ", signif(lm$rsquare, 3),
+                     "; Intercept =", signif(lm$intercept_MA, 3),
+                     "; Slope =", signif(lm$slope_MA, 3),
+                     "; P =", signif(lm$P, 3),
                      "; RMSE = ", signif(lm$rmse, 3))) +
@@
   geom_abline(slope=1, intercept =0, linetype = "dashed") +
-  geom_abline(aes(intercept = lm$fit$regression.results[2,2], slope = lm$fit$regression.results[2,3]),
+  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),
               colour = "blue") +
-  labs(title = paste("pH spectro vs pH seafet (at in situ temperature)","\n Adj R2 = ", signif(lm$fit$rsquare, 3),
-                     "; Intercept =", signif(lm$fit$regression.results[2,2], 3),
-                     "; Slope =", signif(lm$fit$regression.results[2,3], 3),
-                     "; P =", signif(lm$fit$P.param, 3),
+  labs(title = paste("pH spectro vs pH seafet (at in situ temperature)","\n Adj R2 = ", signif(lm$rsquare, 3),
+                     "; Intercept =", signif(lm$intercept_MA, 3),
+                     "; Slope =", signif(lm$slope_MA, 3),
+                     "; P =", signif(lm$P, 3),
                      "; RMSE = ", signif(lm$rmse, 1))) +
@@
 tmp <- d_all %>% 
-  tidyr::drop_na(pco2_fb, at, sal_fb, temp_fb) %>% 
+  tidyr::drop_na(ph_s_dur_temp_fb, pco2_fb, at, sal_fb, temp_fb) %>% 
   dplyr::select(datetime, ph_s_dur_temp_fb, pco2_fb, at, sal_fb, temp_fb) %>% 
@@
 tmp <- d_all %>% 
-  tidyr::drop_na(ct, at, sal_fb, temp_fb) %>% 
+  tidyr::drop_na(ph_s_dur_temp_fb, ct, at, sal_fb, temp_fb) %>% 
   dplyr::select(datetime, ph_s_dur_temp_fb, ct, at, sal_fb, temp_fb) %>% 

### 2021-11-08 awipev-CO2.Rmd
test

@@
 rm(list = ls())
+
 if (!require("tidyverse")) install.packages("tidyverse")

### 2021-11-08 awipev-CO2.Rmd
Now read discrete data as a XLXS file

@@
 rm(list = ls())
-
 if (!require("tidyverse")) install.packages("tidyverse")
@@
 library("kableExtra")
+if (!require("readxl")) install.packages("readxl")
+library("readxl")
 
@@
 ```{r read and prepare discrete AT+CT, echo=FALSE, warning=FALSE, message=FALSE}
-d <- tibble(
-  read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
-) %>% 
+d <- read_excel(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.xlsx"),
+                col_names = TRUE) %>% 
+#   d <- tibble(
+#   read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
+# ) %>% 
   dplyr::mutate(datetime = ymd_hm(sampling_date, tz="UTC"),
@@
                                        1, 0))
-d <- d %>%
+tmp <- d %>%
   dplyr::filter(location_flag == 0)

### 2021-11-08 awipev-CO2.Rmd
Now read discrete data as a XLXS file

@@
 library("kableExtra")
-if (!require("readxl")) install.packages("readxl")
-library("readxl")
 

### 2021-11-09 awipev-CO2.Rmd

@@
 2015-11-18
-, 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29, 2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16, 2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03, 2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-08-23, 2019-09-20, 2019-11-08, 2019-11-23.
+, 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29, 2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16, 2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03, 2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-08-23, 2019-09-20, 2019-11-08, 2019-11-23,2020-02-14 (2 replicates out of 5), 2020-05-29, 2020-06-06 (2 replicates out of 6), 2020-07-03.
 
@@
 
-2015-08-06, 2015-08-13, 2016-05-12, 2016-05-19, 2016-06-16, 2016-07-28, 2016-09-08, 2016-10-27, 2016-11-17, 2017-01-19, 2017-03-02, 2017-04-27, 2017-09-14, 2018-04-26, 2018-05-04, 2018-05-12, 2018-05-25, 2018-06-30, 2018-07-20, 2018-08-03, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-05-03, 2019-05-10, 2019-08-23.
+2015-08-06, 2015-08-13, 2016-05-12, 2016-05-19, 2016-06-16, 2016-07-28, 2016-09-08, 2016-10-27, 2016-11-17, 2017-01-19, 2017-03-02, 2017-04-27, 2017-09-14, 2018-04-26, 2018-05-04, 2018-05-12, 2018-05-25, 2018-06-30, 2018-07-20, 2018-08-03, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-05-03, 2019-05-10, 2019-08-23, 2020-02-08, 2020-07-17, 2020-11-20.
 

### 2021-11-09 awipev-CO2.Rmd
- function to read the datime in "Discrete....xlsx" was changed : year at the end. - at/ct column converted to numeric.

@@
 # ) %>% 
-  dplyr::mutate(datetime = ymd_hm(sampling_date, tz="UTC"),
+  dplyr::mutate(datetime = dmy_hm(sampling_date, tz="UTC"),
                 measure_date = ymd(measure_date, tz="UTC"),
@@
 # Mercuric chloride correction (Dickson et al. 2007, SOP3a)
-d$at <- d$at * 1.0002
-d$ct <- d$ct * 1.0002
+
+d$at <- as.numeric(d$at) * 1.0002
+d$ct <- as.numeric(d$ct) * 1.0002
 

### 2021-11-09 awipev-CO2.Rmd
minor error

--- 2021-11-09 awipev-CO2.Rmd
@@
                                        1, 0))
-tmp <- d %>%
+d <- d %>%
   dplyr::filter(location_flag == 0)

### 2021-11-15 awipev-CO2.Rmd
extensive revision of ggreg applied to pCO2 measured vs calculated

@@
 # function regression plot with equation (MA or OLS) in title
-ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", subtitle = "subtitle", xlab = "x", ylab = "y") { # x and y are the names of the variables
+ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", subtitle = "subtitle", xlab = "x", ylab = "y", proplot = TRUE) 
+  { # x and y are the names of the variables
   fit_data <- tibble(xdata, ydata)
@@
 slope <- fit$regression.results$Slope[ty]
+predicted <- fit$regression.results$Intercept[1] + xdata * fit$regression.results$Slope[1]
+error <- xdata - predicted
 if (plot == TRUE) {
@@
               colour = "blue")  + 
-  labs(title = paste(title, "; type: ", type,
-                     "\n R2 = ", round(fit$rsquare, digits = 2),
+  labs(title = paste(title, 
+                     "\ntype: ", type,
+                     "; R2 = ", round(fit$rsquare, digits = 2),
                      "; Intercept =", signif(intercept, 3),
                      "; Slope =", signif(slope, 3),
-                     "; P =", signif(fit$P.param, 3)),
+                     "\nP =", signif(fit$P.param, 3),
+                    "rmse =", signif(sqrt(mean(error^2, na.rm=TRUE)), 3)),
        subtitle = subtitle,
        x = xlab,
-       y = ylab)
+       y = ylab) +
+    theme_bw() +
+    theme(plot.title = element_text(size = 7))
+    if (proplot == TRUE) { # property-property plot
+      plt <- plt +
+        geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
+        theme(aspect.ratio = 1)
+      }
   return(plt)
@@
 title <- "pCO2 normalized at in situ temperature"
-fit <- lmodel2(data = d_all,   pco2_calc_fb_insi_temp ~ pco2_fb_insi_temp, nperm = 99)
-print(fit)
-p <-  ggplot(d_all,aes(x = pco2_fb, y = pco2_calc_fb))+
-  geom_point()+
-  scale_color_discrete(guide="none")+
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
-  # labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
-  #                    "; Intercept =", signif(fit$regression.results[2,2], 3),
-  #                    "; Slope =", signif( fit$regression.results[2,3], 3),
-  #                    "; P =", signif(fit$P.param, 3))) +
-  theme(aspect.ratio=1, plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1, xlim=c(200,420), ylim=c(200,420))+
-  labs(title = "", x="Measured pCO2", y="Calculated pCO2") + theme_bw()  
+p <- ggreg(
+  xdata = d_all$pco2_fb_insi_temp,
+  ydata = d_all$pco2_calc_fb_insi_temp,
+  type = "MA",
+  plot = TRUE,
+  title = title,
+  subtitle = "",
+  xlab = "Measured pCO2",
+  ylab = "Calculated pCO2",
+  proplot = TRUE
+)
 print(p)

### 2021-11-18 awipev-CO2.Rmd
rewrote ggreg and revised code accordingly

@@
 # function regression plot with equation (MA or OLS) in title
-ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", subtitle = "subtitle", xlab = "x", ylab = "y", proplot = TRUE) 
+ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", subtitle = "subtitle", xlab = "x", ylab = "y", proplot = TRUE, ...) 
   { # x and y are the names of the variables
@@
        y = ylab) +
+#    lims(x = c(min(fit_data$xdata), max(fit_data$xdata)), y = c(min(fit_data$ydata), max(fit_data$ydata))) +
     theme_bw() +
@@
     }
-  return(plt)
-  } #else {
-  #return(fit)
-#}
+  return(list(plot = plt, fit = fit))
+  } else {
+  return(fit)
+    }
 }
@@
   ) %>% 
+  # data post 2020-03-01 eliminated because no maintenance and lots of algae
+  dplyr::mutate(pco2_fb = ifelse(datetime >= as.POSIXct("2020-03-01 00:00"), NA, pco2_fb)) %>%
   arrange(datetime)
@@
 
+**Note** that the Contros pCO2 values after 2020-03-01 were not used because the Covid-19 pandemic prevented maintenance and the setup of a freshly calibrated sensor.
+As the result, algae becalme inceasingly abundant, pulling pCO2 down and further away from values calculated from CT and AT.
+
 ### **Corrected Contros vs calculated *p*CO~2~ data**
@@
 title <- "pCO2 normalized at in situ temperature"
-p <- ggreg(
+reg <- ggreg(
   xdata = d_all$pco2_fb_insi_temp,
@@
 )
-print(p)
+p <- reg$plot
 ggsave(filename = "figures/pco2_calc_meas.png", plot = p)
@@
 It is far from the 1:1 relationship (black dashed line).
-The slope is `r signif(fit$regression.results[2,3], 3)`) and its 95% confidence interval does include 1; r2 is `r round(fit$rsquare, digits=2)`.
+The slope is `r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)`.
 
@@
 https://CRAN.R-project.org/package=lmodel2
-<!-- ======= -->
-<!--   theme(aspect.ratio=1,plot.title = element_text(size=7)) +  -->
-<!--   coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+ -->
-<!--   labs(x="Contros pCO2", y="Calculated pCO2") + theme_bw()   -->
-<!-- ``` -->
-
-The relationship between the Contros and calculated pCO2 is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
-<!-- >>>>>>> cb6a0f5891d0a4e43735bed5507c62760ae133cb -->
 
 ```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-# print(p)
+print(p$plot)
 # 
@@
             xlab = "Spectrophotometric pH normalized @ 4°C",
-            ylab = "pH @ 4°C calculated (pCO2+AT) with Lueker") +
+            ylab = "pH @ 4°C calculated (pCO2+AT) with Lueker", 
+            proplot = TRUE)$plot +
   lims(x = c(8, 8.4), y = c(8, 8.4)) +
   theme(plot.title = element_text(size = 10),
-        axis.text = element_text(size = 10)) +
-  coord_fixed(ratio = 1)
+        axis.text = element_text(size = 10))
 p2 <- ggreg(xdata = tmp2$ph_s_dur_temp_4_l, ydata = tmp2$pH_s, type = "MA", plot = TRUE, 
@@
             xlab = "Spectrophotometric pH normalized @ 4°C",
-            ylab = "pH @ 4°C calculated (pCO2+AT) with Sulpis")  +
+            ylab = "pH @ 4°C calculated (pCO2+AT) with Sulpis",
+            proplot = TRUE)$plot +
   lims(x = c(8, 8.4), y = c(8, 8.4)) +
   theme(plot.title = element_text(size = 10),
-        axis.text = element_text(size = 10)) +
-  coord_fixed(ratio = 1)
+        axis.text = element_text(size = 10))
 p3 <- tmp2 %>% 
@@
             xlab = "Spectrophotometric pH normalized @ 4°C",
-            ylab = "pH @ 4°C calculated (AT+CT) with Lueker") +
+            ylab = "pH @ 4°C calculated (AT+CT) with Lueker",
+            proplot = TRUE)$plot +
   lims(x = c(8, 8.4), y = c(8, 8.4)) +
   theme(plot.title = element_text(size = 10),
-        axis.text = element_text(size = 10)) +
-  coord_fixed(ratio = 1)
+        axis.text = element_text(size = 10))
 p2 <- ggreg(xdata = tmp2$ph_s_dur_temp_4_l, ydata = tmp2$pH_s2, type = "MA", plot = TRUE, 
@@
             xlab = "Spectrophotometric pH normalized @ 4°C",
-            ylab = "pH @ 4°C calculated (AT+CT) with Sulpis")  +
+            ylab = "pH @ 4°C calculated (AT+CT) with Sulpis",
+            proplot = TRUE)$plot  +
   lims(x = c(8, 8.4), y = c(8, 8.4)) +

### 2021-11-18 awipev-CO2.Rmd
replaced data_frame which is superseded by tibble

@@
 d <- filter(deconv_dat, !is.na(mAT), !is.na(mCT), !is.na(S), !is.na(mT)) # we eliminate date with NAs
-deconv_pCO2_S <- data_frame(date=d$date,
+deconv_pCO2_S <- tibble(date=d$date,
                      deconv_pCO2_S=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$S, T=d$mT, P=d$P, Pt=d$Pt, 
@@
 d <- filter(deconv_dat, !is.na(AT), !is.na(mCT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
-deconv_pCO2_AT <- data_frame(date=d$date,
+deconv_pCO2_AT <- tibble(date=d$date,
                      deconv_pCO2_AT=carb(flag=15, var1=d$AT, var2=d$mCT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2
@@
 d <- filter(deconv_dat, !is.na(mAT), !is.na(CT), !is.na(mS), !is.na(mT)) # we eliminate date with NAs
-deconv_pCO2_CT <- data_frame(date=d$date,
+deconv_pCO2_CT <- tibble(date=d$date,
                      deconv_pCO2_CT=carb(flag=15, var1=d$mAT, var2=d$CT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2

### 2021-11-22 awipev-CO2.Rmd
minor changes

@@
 
-Depth and month of the year have a statistically significant effet on pH. The interaxction is also significant, indicating that the effect of depth differs depending on the month.
+Depth and month of the year have a statistically significant effect on pH. The interaction is also significant, indicating that the effect of depth differs depending on the month.
 
@@
 
-### **seaFET / durafet pHs**
+### **seaFET / durafet pHs (all at 9 m)**
 

### 2021-11-23 awipev-CO2.Rmd
on going work on pH seafet

@@
 
+# tmp <- d_all %>% 
+#   dplyr::select(montht, pHint_tot_sf, depth, depth_discrete) %>%
+#   dplyr::group_by(depth, montht)
+# p <- tmp %>% 
+#   ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
+#   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+#   labs(title = "pHT", x = "Depth (m)", y= "pHT") +
+#   facet_wrap(vars(montht), scale = "free_y")
+# print(p)
+# 
+# 
+# p <- tmp %>% 
+#   ggplot(aes(x=depth_discrete, y = pHint_tot_sf)) +
+#   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+#   labs(title = "pHT", x = "Depth (m)", y= "pHT") +
+#   facet_wrap(vars(montht), scale = "free_y")
+# print(p)
+
 # we look at all depths
 tmp <- d_all %>% 
-  dplyr::select(montht, pHint_tot_sf, depth) %>%
-  group_by(depth, montht)
+  dplyr::select(year, montht, pHint_tot_sf, depth_discrete) %>%
+  tidyr::drop_na(pHint_tot_sf, depth_discrete) %>%
+  dplyr::group_by(depth_discrete, year, montht)
+summary(aov(tmp$pHint_tot_sf ~ tmp$depth_discrete * tmp$montht))
+
+# remove outliers
+quantile(tmp$pHint_tot_sf, na.rm =TRUE, probs = c(0.01, 0.99))
+
 p <- tmp %>%
-  ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  ggplot(aes(x=depth_discrete, y = pHint_tot_sf)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, coef = 1.5) +
   labs(title = "pHT", x = "Depth (m)", y= "pHT") +
-  facet_wrap(vars(montht), scale = "free_y")
+  lims(y = c(7.4, 8.3)) +
+  coord_cartesian() +
+  facet_wrap(vars(montht), scale = "fixed")
 print(p)
+
+pp <- tmp %>%
+  ggplot(aes(x=depth_discrete, y = pHint_tot_sf)) +
+  stat_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, coef = 3)
 
@@
   dplyr::filter(depth == 2 | depth == 10) %>% 
-  group_by(depth, montht)
+  dplyr::group_by(depth, montht)
 summary(aov(tmp$pHint_tot_sf ~ tmp$depth * tmp$montht))

### 2021-11-25 awipev-CO2.Rmd
work on seafet profile

@@
   tidyr::drop_na(pHint_tot_sf, depth_discrete) %>%
-  dplyr::group_by(depth_discrete, year, montht)
+  dplyr::group_by(depth_discrete, montht) %>% 
+  dplyr::mutate(quant_01 = quantile(pHint_tot_sf, na.rm =TRUE, probs = c(0.05)),
+                quant_99 = quantile(pHint_tot_sf, na.rm =TRUE, probs = c(0.95)),
+                mean = mean(pHint_tot_sf, na.rm =TRUE),
+                sd = sd(pHint_tot_sf, na.rm =TRUE)
+                ) %>% 
+  dplyr::filter(pHint_tot_sf < mean + sd, pHint_tot_sf > mean - sd) # remove outliers
+#  dplyr::filter(pHint_tot_sf < quant_99, pHint_tot_sf > quant_01) # remove outliers
 summary(aov(tmp$pHint_tot_sf ~ tmp$depth_discrete * tmp$montht))
-
-# remove outliers
-quantile(tmp$pHint_tot_sf, na.rm =TRUE, probs = c(0.01, 0.99))
 

### 2021-11-25 awipev-CO2.Rmd

--- 2021-11-23 awipev-CO2.Rmd
@@
   dplyr::rowwise() %>% 
-  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
+  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours 
+    # for which there are CTD data at more than 1 depth 
   c(
@@
   tidyr::drop_na(pHint_tot_sf, depth_discrete) %>%
-  dplyr::group_by(depth_discrete, year, montht)
+  dplyr::group_by(depth_discrete, year, montht) %>% 
+  dplyr::mutate(quant_01 = quantile(pHint_tot_sf, na.rm =TRUE, probs = c(0.05)),
+                quant_99 = quantile(pHint_tot_sf, na.rm =TRUE, probs = c(0.95)),
+                mean = mean(pHint_tot_sf, na.rm =TRUE),
+                sd = sd(pHint_tot_sf, na.rm =TRUE)
+                ) %>% 
+  dplyr::filter(pHint_tot_sf < mean + sd, pHint_tot_sf > mean - sd) # remove outliers
+#  dplyr::filter(pHint_tot_sf < quant_99, pHint_tot_sf > quant_01) # remove outliers
 summary(aov(tmp$pHint_tot_sf ~ tmp$depth_discrete * tmp$montht))
-
-# remove outliers
-quantile(tmp$pHint_tot_sf, na.rm =TRUE, probs = c(0.01, 0.99))
 

### 2021-11-25 awipev-CO2.Rmd
We changed the selecting parameter "temp_insitu_ctd" from to "temp_mix_interp" to create pHseafet df from "d". we created before pHinsi() an interpolation for sal_mix/temp_mix in order to fill gaps for pHinsi(). For pHinsi(), we changed the sal/temp to sal_mix_interp/temp_mix_interp. We forced the depth in the function to 11 m.

--- 2021-11-23 awipev-CO2.Rmd
@@
   odt_document: default
+editor_options: 
+  chunk_output_type: console
 ---
@@
   ))
+d_hour <- as_tsibble(d_hour, index = datetime) %>%#d_all will be the merger
+  tsibble::fill_gaps(.full=TRUE)
+d_hour$date <-  as.Date(d_hour$datetime, format="%Y-%m-%d")
 
@@
 
-d_all <- as_tsibble(d_hour, index = datetime) #d_all will be the merger
-d_all <- d_all %>%
+d_all <- d_hour %>%
   dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
@@
   c(
-    sal_insitu_ctd_1m,
-    sal_insitu_ctd_3m,
-    sal_insitu_ctd_5m,
-    sal_insitu_ctd_7m,
-    sal_insitu_ctd_9m
+    temp_insitu_ctd_1m,
+    temp_insitu_ctd_3m,
+    temp_insitu_ctd_5m,
+    temp_insitu_ctd_7m,
+    temp_insitu_ctd_9m
   )
@@
 rm(d_hour)
+
 ```
@@
 
+# interpolation of temp_mix/sal_mix in d_all in order to have a full temperature for pHinsi()
+# We take temp_mix/sal_mix because of the depth (temp11m insitu + temp9m ctd)
+tempmixinterp <-approx(d_all$datetime, d_all$temp_mix, xout=d_all$datetime, method="linear", rule=2)
+names(tempmixinterp) <- c("datetime", "temp_mix_interp")
+tempmixinterp <- as.data.frame(tempmixinterp)
+d_all$temp_mix_interp <- tempmixinterp$temp_mix_interp
+
+salmixinterp <-approx(d_all$datetime, d_all$sal_mix, xout=d_all$datetime, method="linear", rule=2)
+names(salmixinterp) <- c("datetime", "sal_mix_interp")
+salmixinterp <- as.data.frame(salmixinterp)
+d_all$sal_mix_interp <- salmixinterp$sal_mix_interp
+
+# ta_xts <- dplyr::select(d_all, datetime, sal_mix, sal_mix_interp)
+# ta_xts <- as.xts(ta_xts, order.by = ta_xts$datetime)
+# dygraph(ta_xts, group = "awipev", main="sal mix", ylab="temp") %>%
+#   dySeries("sal_mix", color = "black", pointSize =4, strokeWidth = 1, label = "ta") %>%
+#   dySeries("sal_mix_interp", color = "blue", strokeWidth = 1, label = "ta interp") %>%
+#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
+#       dyOptions( drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
+#     dyAxis("y",valueRange = c(33, 36)) %>%
+#     dyLegend(show = "follow")   %>%
+#       dyRangeSelector(height = 30, dateWindow= NULL)
+
 # add sal_fb + sal_insitu_ctd + temp_fb + temp_insitu_ctd from d_all into d, to use pHinsi
@@
                      temp_mix,
+                     temp_mix_interp,
                      sal_mix,
+                     sal_mix_interp,
                      temp_insitu_11m,
                      temp_insitu_ctd,
+                     temp_sf,
                      depth
@@
 pH_seafet <- d %>%
-  dplyr::filter(!is.na(ph_s_sf) & !is.na(temp_insitu_ctd))
+  dplyr::filter(!is.na(ph_s_sf) & !is.na(temp_mix_interp))
+
 pH_seafet <- pH_seafet %>% 
@@
     ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, 
-                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_insitu_ctd, 
-                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, 
-                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
+                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_mix_interp, 
+                         Tlab = pH_seafet$temp_s_lab, Pinsi = 11/10, 
+                         S = pH_seafet$sal_mix_interp, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
                          pHscale = "T", b="u74"),
@@
                          ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
-                         Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, 
-                         S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
+                         Tlab = pH_seafet$temp_s_lab, Pinsi = 11/10, 
+                         S = pH_seafet$sal_mix_interp, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
                          pHscale = "T", b="u74")

### 2021-11-25 awipev-CO2.Rmd
catch up

--- 2021-11-25 awipev-CO2.Rmd
@@
   tidyr::drop_na(pHint_tot_sf, depth_discrete) %>%
-  dplyr::group_by(depth_discrete, montht) %>% 
-  dplyr::mutate(quant_01 = quantile(pHint_tot_sf, na.rm =TRUE, probs = c(0.05)),
-                quant_99 = quantile(pHint_tot_sf, na.rm =TRUE, probs = c(0.95)),
-                mean = mean(pHint_tot_sf, na.rm =TRUE),
-                sd = sd(pHint_tot_sf, na.rm =TRUE)
-                ) %>% 
-  dplyr::filter(pHint_tot_sf < mean + sd, pHint_tot_sf > mean - sd) # remove outliers
-#  dplyr::filter(pHint_tot_sf < quant_99, pHint_tot_sf > quant_01) # remove outliers
+  dplyr::group_by(depth_discrete, year, montht)
 summary(aov(tmp$pHint_tot_sf ~ tmp$depth_discrete * tmp$montht))
+
+# remove outliers
+quantile(tmp$pHint_tot_sf, na.rm =TRUE, probs = c(0.01, 0.99))
 
@@
 pH is measured continuously by an autonomous durafet pH sensor.
-Final calibrated durafet pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
+Final calibrated durafet pHT data (green doibb) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
 Calibration was done appliying an offset of pH between measured and spectro data per periods.

### 2021-11-25 awipev-CO2.Rmd
testing despike on pHint_tot_sf

@@
 library("readxl")
+if (!require("oce")) install.packages("oce")
+library(oce)
 
@@
 names(seafet_calib) <- c("pHint_tot_sf", "pHext_tot_sf")
-d_all <- dplyr::bind_cols(d_all, seafet_calib )
+
+##########  Despike() ###########
+d_all <- d_all %>%   
+  dplyr::mutate(pHint_tot_sf = oce::despike(seafet_calib$pHint_tot_sf, reference= "median", n=1, k=5000, replace="NA"),
+                pHext_tot_sf = oce::despike(seafet_calib$pHext_tot_sf, reference= "median", n=1, k=5000, replace="NA")
+  )
 
@@
 * sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
+* sal_mix_interp: interpolated salinity sal_mix. It is used to have as many spec pH to display (some are during missing data)
 * temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
+* temp_mix_interp: interpolated temperature temp_mix. It is used to have as many spec pH to display (some are during missing data)
 * pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb

### 2021-11-26 awipev-CO2.Rmd
removed commented code

--- 2021-11-25 awipev-CO2.Rmd
@@
 ```{r seafet profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-# range <- d_all %>%
-#   dplyr::mutate(pH_range_more_6m = ifelse(depth > 6, pHint_tot_sf, NA)) %>%
-#   group_by(montht) %>%
-#   summarize(pH_range = max(pHint_tot_sf, na.rm = TRUE) - min(pHint_tot_sf, na.rm = TRUE),
-#             pH_range_more_6m = max(pH_range_more_6m, na.rm = TRUE) - min(pH_range_more_6m, na.rm = TRUE),
-#             pH_range_more_9m = max(pHint_tot_sf_9m, na.rm = TRUE) - min(pHint_tot_sf_9m, na.rm = TRUE)) %>%
-#   ungroup()
-# print(kable(range, digits = 2))
-
-# # datetime when pH values are in but no pressure data. File sent to send to Philipp
-# no_pressure <- d_all %>% 
-#   dplyr::select(datetime, depth, pHint_tot_sf) %>% 
-#   dplyr::filter(is.na(depth) & !is.na(pHint_tot_sf))
-# readr::write_csv(x = no_pressure, path=paste0(path,"/fb_awipev-co2_server/ny-alesund/data//no_pressure.csv"))
-
-# tmp <- d_all %>% 
-#   dplyr::select(montht, pHint_tot_sf, depth, depth_discrete) %>%
-#   dplyr::group_by(depth, montht)
-# p <- tmp %>% 
-#   ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
-#   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-#   labs(title = "pHT", x = "Depth (m)", y= "pHT") +
-#   facet_wrap(vars(montht), scale = "free_y")
-# print(p)
-# 
-# 
-# p <- tmp %>% 
-#   ggplot(aes(x=depth_discrete, y = pHint_tot_sf)) +
-#   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-#   labs(title = "pHT", x = "Depth (m)", y= "pHT") +
-#   facet_wrap(vars(montht), scale = "free_y")
-# print(p)
 
@@
 pH is measured continuously by an autonomous durafet pH sensor.
-Final calibrated durafet pHT data (green doibb) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
+Final calibrated durafet pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
 Calibration was done appliying an offset of pH between measured and spectro data per periods.

### 2021-11-29 awipev-CO2.Rmd
change date to datetime in pH_seafet_mean in order to take in consideration 2 spectro on the same day at 2019-19-13 but not at the same time

@@
 pH_seafet_mean <- pH_seafet %>%
-  dplyr::select(date, ph_s_sf_temp_insi, ph_s_sf_temp_4) %>% 
-  dplyr::group_by(date) %>% 
+  dplyr::select(datetime, ph_s_sf_temp_insi, ph_s_sf_temp_4) %>% 
+  dplyr::group_by(datetime) %>% 
   dplyr::summarise(ph_s_sf_temp_insi_mean = mean(ph_s_sf_temp_insi, na.rm = TRUE),
@@
 dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
-dySeries("ph_s_sf_temp_insi", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
 dySeries("pHint_tot_sf_9m", label = "pHT 9m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
@@
 dySeries("pHint_tot_sf_1m", label = "pHT 1m", color =  RColorBrewer::brewer.pal(3, "Dark2")[5], strokeWidth = 0, pointSize = 1) %>%
+  dySeries("ph_s_sf_temp_insi", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 5 ) %>%
+
 dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%

### 2021-11-30 awipev-CO2.Rmd
mutate for ph_s_sf_temp_insi in d_all done with n_depth_ctd >=4 (not ==4)

@@
 pH_durafet_mean <- pH_durafet %>%
-  dplyr::select(date, ph_s_dur_temp_fb, ph_s_dur_temp_4) %>% 
-  dplyr::group_by(date) %>% 
+  dplyr::select(datetime, ph_s_dur_temp_fb, ph_s_dur_temp_4) %>% 
+  dplyr::group_by(datetime) %>% 
   dplyr::summarize(ph_s_dur_temp_fb_mean = mean(ph_s_dur_temp_fb, na.rm = TRUE),
@@
 #bind all spectro measurements, just to assess sd, change name of dataframe only to do the rbind.
-seafetph <- pH_seafet_mean
-colnames(seafetph) <- c("date", "mean", "sd")
-durafetph <- pH_durafet_mean
-colnames(durafetph) <- c("date", "mean", "sd")
+# seafetph <- pH_seafet_mean
+# colnames(seafetph) <- c("date", "mean", "sd")
+# durafetph <- pH_durafet_mean
+# colnames(durafetph) <- c("date", "mean", "sd")
 #pH_seafet_durafet <- rbind(seafetph, durafetph)
@@
 discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
-  dplyr::arrange(date)
+  dplyr::arrange(datetime)
 ```
@@
 d_all <- d_all %>% 
-  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd == 4, ph_s_sf_temp_insi, NA)) # eliminate ph spec data when the profiler was at several depth during the same hour
+  dplyr::mutate(ph_s_sf_temp_insi = ifelse(n_depth_ctd >= 4, ph_s_sf_temp_insi, NA)) # eliminate ph spec data when the profiler was at several depth during the same hour
   #dplyr::mutate(ph_s_sf_temp_insi = ifelse(!is.na(temp_insitu_ctd_7m) |

### 2021-11-30 awipev-CO2.Rmd
Add quality control pHSeaFET plot

@@
 discrete <- d %>%
-  dplyr::group_by(date) %>%
+  dplyr::group_by(datetime) %>%
   dplyr::summarize(
@@
 # join discrete + seafet/durafet
-discrete <- left_join(discrete, pH_seafet_mean, by='date')
-discrete <- left_join(discrete, pH_durafet_mean, by='date')
+discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
+discrete <- left_join(discrete, pH_durafet_mean, by='datetime')
 
@@
 rm(seafet_depth_xts)
+```
+
+Quality control plots :
+
+- Offset between calibrated seaFET data and pH spectro. The offset must fit between -0.2/0.2 pH units.
+
+```{r seaFET quality control pH, echo=FALSE, warning = FALSE, message = FALSE, out.width='100%'}
+#Offset between seafet pH and spec pH (Fig. 2 Kapsenberg et al.)
+
+ph_sf <- d_all%>%
+  mutate( diff_pH = ph_s_sf_temp_insi - pHint_tot_sf)
+average_offset <- mean(abs(ph_sf$diff_pH), na.rm=TRUE)
+
+offset_xts <- dplyr::select(ph_sf%>%dplyr::filter(!is.na(diff_pH)), datetime, diff_pH)
+offset_xts <- as.xts(offset_xts, order.by=offset_xts$datetime)
+
+dygraph(offset_xts, ylab = "") %>%
+dySeries("diff_pH", drawPoints = TRUE, pointSize=3, label = "delta pHINT", color="green")%>%
+    dyLimit(0,strokePattern = "dashed", color = "black") %>% 
+  dyLimit(-0.02,strokePattern = "dashed", color = "red") %>% 
+    dyLimit(0.02,strokePattern = "dashed", color = "red") %>% 
+ # dyAxis("y",valueRange = c(-0.04, 0.04))%>%
+  dyAxis("x",valueRange = c(as.POSIXct("2021-09-28"), as.POSIXct("2021-10-19")
+))%>%
+dyOptions(
+    drawGrid = TRUE,
+    strokeWidth= 0,
+    drawPoints = TRUE,
+    useDataTimezone = TRUE,
+    digitsAfterDecimal = 4) %>%
+  dyRangeSelector(height = 30)
 ```

### 2021-12-03 awipev-CO2.Rmd
quality plot pH reference.
put back group_by(date) to create discrete df

@@
 discrete <- d %>%
-  dplyr::group_by(datetime) %>%
+  dplyr::group_by(date) %>%
   dplyr::summarize(
@@
 ####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd)
+calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
 # put number of deployment 
@@
   dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#CCCCCC") %>%
   dyLegend(show = "auto")   %>%
-  dyAxis("y2",valueRange = c(-2, 2)) %>%
+  dyAxis("y2",valueRange = c(-3, 9)) %>%
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
 - Offset between calibrated seaFET data and pH spectro. The offset must fit between -0.2/0.2 pH units.
+
+“differences between calibrated sensor pH values and values obtained from discrete, check samples can be expected to be as small as 0.02 pH units, and perhaps less.” (McLaughlin et al. 2017).
 

### 2021-12-07 awipev-CO2.Rmd
Much work related to the depth profiles and salinity data

@@
   ))
-d_hour <- as_tsibble(d_hour, index = datetime) %>%#d_all will be the merger
+d_hour <- as_tsibble(d_hour, index = datetime) %>% #d_all will be the merger
   tsibble::fill_gaps(.full=TRUE)
@@
   arrange(datetime)
+
 # read a file provided by Philipp on 2021-04-09 which fills most gaps of pressure data
@@
     "fb_data/svl_remos_depth.rds"
-  )))
+  ))) %>% 
+  dplyr::select(-adcp_fill, -ctd_fill)
+
 d_hour <- dplyr::left_join(d_hour, svl_remos_depth, by = 'datetime') %>% 
-  dplyr::select(-adcp_fill, -ctd_fill) %>% 
-  dplyr::rename(depth = depth_complete)
+  dplyr::mutate(depth = ifelse(!is.na(pressure_insitu_ctd), pressure_insitu_ctd, depth_complete))
+
 # check_plot <- d_hour %>% 
@@
   dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
-  dplyr::mutate(depth_group_pressure = ifelse( # create new variable depth
-      pressure_insitu_ctd <= 2,
-      1,
-      ifelse(
-        pressure_insitu_ctd > 2 & depth <= 4,
-        3,
-        ifelse(
-          pressure_insitu_ctd > 4 & depth <= 6,
-          5,
-          ifelse(
-            pressure_insitu_ctd > 6 & depth <= 8,
-            7,
-            ifelse(pressure_insitu_ctd > 8, 10, NA)
-          )
-        )
-      )
+  dplyr::mutate(depth_group = dplyr::case_when(depth > 0 & depth <= 2 ~ '0-2',
+                depth > 2 & depth <= 4 ~ '2-4',
+                depth > 4 & depth <= 6 ~ '4-6',
+                depth > 6 & depth <= 8 ~ '6-8',
+                depth > 8 & depth <= 12 ~ '>8', #8 to 12.4
+                TRUE ~ 'NA'
                 ),
-    depth_group_philipp = ifelse( # create new variable depth
-      depth <= 2,
-      1,
-      ifelse(
-        depth > 2 & depth <= 4,
-        3,
-        ifelse(
-          depth > 4 & depth <= 6,
-          5,
-          ifelse(
-            depth > 6 & depth <= 8,
-            7,
-            ifelse(depth > 8, 10, NA)
-          )
-        )
-      )
-    )) %>%
+                sal_insitu_ctd_1m = ifelse(depth_group == '0-2', sal_insitu_ctd, NA),
+                sal_insitu_ctd_3m = ifelse(depth_group == '2-4', sal_insitu_ctd, NA),
+                sal_insitu_ctd_5m = ifelse(depth_group == '4-6', sal_insitu_ctd, NA),
+                sal_insitu_ctd_7m = ifelse(depth_group == '6-8', sal_insitu_ctd, NA),
+                sal_insitu_ctd_10m = ifelse(depth_group == '>8', sal_insitu_ctd, NA),
+                temp_insitu_ctd_1m = ifelse(depth_group == '0-2', temp_insitu_ctd, NA),
+                temp_insitu_ctd_3m = ifelse(depth_group == '2-4', temp_insitu_ctd, NA),
+                temp_insitu_ctd_5m = ifelse(depth_group == '4-6', temp_insitu_ctd, NA),
+                temp_insitu_ctd_7m = ifelse(depth_group == '6-8', temp_insitu_ctd, NA),
+                temp_insitu_ctd_10m = ifelse(depth_group == '>8', temp_insitu_ctd, NA),
+  ) %>% 
   dplyr::rowwise() %>% 
@@
     temp_insitu_ctd_7m,
-    temp_insitu_ctd_9m
+    temp_insitu_ctd_10m
   )
@@
   ungroup()
+
 #restore datetime, date which are mangled by the mutates above, arrange ascending
@@
   )
+d_all <- d_all %>% 
+  dplyr::select(order(colnames(d_all)))
 rm(d_hour)
@@
 d_all <- d_all %>%
-  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_9m))
+  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_10m))
 ```
@@
 ```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-# Create temp_mix: filling gaps in temp_insitu_11m using temp_insitu_9m
+# Create temp_mix: filling gaps in temp_insitu_11m using temp_insitu_10m
 d_all <- d_all %>%
-  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_9m))
+  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_10m))
 ```
@@
 # interpolation of temp_mix/sal_mix in d_all in order to have a full temperature for pHinsi()
-# We take temp_mix/sal_mix because of the depth (temp11m insitu + temp9m ctd)
+# We take temp_mix/sal_mix because of the depth (temp11m insitu + temp10m ctd)
 tempmixinterp <-approx(d_all$datetime, d_all$temp_mix, xout=d_all$datetime, method="linear", rule=2)
@@
 #SAL CTD profile
-sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m)
+sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_10m)
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
@@
 dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
-dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
+dySeries("sal_insitu_ctd_10m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "10m") %>%
       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
     dyLegend(show = "follow")   %>%
-    dyAxis("y",valueRange = c(30, 37)) %>%
+    dyAxis("y",valueRange = c(29, 37)) %>%
       dyRangeSelector(height = 30, dateWindow= NULL)
@@
 df <- d_all %>% 
-  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
+  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_10m) %>%
   dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
@@
   summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
-            mean9m = mean(sal_insitu_ctd_9m, na.rm = TRUE),
-            range = mean(sal_insitu_ctd_1m, na.rm = TRUE)-mean(sal_insitu_ctd_9m, na.rm = TRUE)) %>% 
+            mean10m = mean(sal_insitu_ctd_10m, na.rm = TRUE),
+            range = mean(sal_insitu_ctd_1m, na.rm = TRUE) - mean(sal_insitu_ctd_10m, na.rm = TRUE)) %>% 
   ungroup()
@@
 p_sal_range <- ggplot(data = df) +
-  geom_histogram((aes(x = df$range))) +
-  labs(title = "Salinity difference between 1 and 9 m", x = "Difference") +
+  geom_histogram((aes(x = range))) +
+  labs(title = "Daily salinity difference between 1 and 10 m", x = "Difference") +
   Mytheme(size_labs = 8)
@@
 ```
-There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m).
-The salinity difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)` and `r max(df$range, na.rm=TRUE)` (mean: `r mean(df$range, na.rm=TRUE)`; `r median(df$range, na.rm=TRUE)`).
+Extreme differences: `r dplyr::filter(df, range < -3 | range > 2)`.
+
+There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 10 m (8-12 m).
+The salinity difference between 1 and 10 m ranges between `r min(df$range, na.rm=TRUE)` and `r max(df$range, na.rm=TRUE)` (mean: `r mean(df$range, na.rm=TRUE)`; `r median(df$range, na.rm=TRUE)`).
 The difference with depth is therefore significant.
 
-### **Sal FB / Sal CTD 9 m **
+### **Sal FB / Sal CTD 10 m **
 
 ```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
-p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
+lm <- lm2(x = d_all$sal_insitu_ctd_10m, y = d_all$sal_fb)
+p <-  ggplot(d_all,aes(x=sal_insitu_ctd_10m, y= sal_fb))+
   geom_point( aes(color=factor(monthd))) + 
@@
   coord_fixed(ratio = 1 )+
-  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()
+  labs( x="Salinity CTD 10 m", y="Salinity FB ", color = "Months") + theme_bw()
 
@@
 
-d_all$diff_sal_fb_insitu_9m <- d_all$sal_insitu_ctd_9m - d_all$sal_fb
-mean_diff_sal_fb_insitu_9m <- round(mean(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
-sd_diff_sal_fb_insitu_9m <- round(sd(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
-```
-
-The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu_9m` ± `r sd_diff_sal_fb_insitu_9m` PSU.
+d_all$diff_sal_fb_insitu_10m <- d_all$sal_insitu_ctd_10m - d_all$sal_fb
+mean_diff_sal_fb_insitu_10m <- round(mean(d_all$diff_sal_fb_insitu_10m, na.rm = TRUE), digits = 2)
+sd_diff_sal_fb_insitu_10m <- round(sd(d_all$diff_sal_fb_insitu_10m, na.rm = TRUE), digits = 2)
+```
+
+The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu_10m` ± `r sd_diff_sal_fb_insitu_10m` PSU.
 
@@
 - 1 SBE45 inside the Ferrybox (temp_fb)
-- 5 CTD profiling (temp_insitu_ctd_1m - 3m - 5m - 7m - 9m)
+- 5 CTD profiling (temp_insitu_ctd_1m - 3m - 5m - 7m - 10m)
 - 1 fixed at 11 meters depth (temp_insitu_11m)
@@
 ```{r temperature profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-temp_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m)
+temp_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_10m)
 temp_xts <- as.xts(temp_xts, order.by = temp_xts$datetime)
@@
 dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
-dySeries("temp_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
+dySeries("temp_insitu_ctd_10m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "10m") %>%
 dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
 df <- d_all %>% 
-  dplyr::select(datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m) %>%
+  dplyr::select(datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_10m) %>%
   dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
@@
   summarize(mean1m = mean(temp_insitu_ctd_1m, na.rm = TRUE),
-            mean9m = mean(temp_insitu_ctd_9m, na.rm = TRUE),
-            range = mean(temp_insitu_ctd_1m, na.rm = TRUE)-mean(temp_insitu_ctd_9m, na.rm = TRUE)) %>% 
+            mean10m = mean(temp_insitu_ctd_10m, na.rm = TRUE),
+            range = mean(temp_insitu_ctd_1m, na.rm = TRUE)-mean(temp_insitu_ctd_10m, na.rm = TRUE)) %>% 
   ungroup()
@@
 ```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-lm <- lm2(x = d_all$temp_insitu_ctd_9m, y = d_all$temp_insitu_11m)
-p <-  ggplot(d_all, aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = monthd))+
+lm <- lm2(x = d_all$temp_insitu_ctd_10m, y = d_all$temp_insitu_11m)
+p <-  ggplot(d_all, aes(x=temp_insitu_ctd_10m, y= temp_insitu_11m, label = monthd))+
   geom_text( aes(color=factor(monthd))) + 
@@
 
-d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd_9m
+d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd_10m
 mean_diff_T_ctd_11m <- round(mean(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
@@
 # despike me semble inutile, faire plutôt un simple des outliers qui, vérification faite, n'est même pas nécessaire
-# Il faut par contre créér une nouvelle variable avec pH deeper than 8 m, called *_9m for consistency with salinity and temp
+# Il faut par contre créér une nouvelle variable avec pH deeper than 8 m, called *_10m for consistency with salinity and temp
 d_all <- d_all %>%
@@
                 pHint_tot_sf_7m = ifelse(depth >= 6 & depth < 8, pHint_tot_sf, NA),
-                pHint_tot_sf_9m = ifelse(depth >= 8 , pHint_tot_sf, NA),
+                pHint_tot_sf_10m = ifelse(depth >= 8 , pHint_tot_sf, NA),
                 depth_discrete = case_when(
@@
       !is.na(pHint_tot_sf_7m) ~ 7,
-      !is.na(pHint_tot_sf_9m) ~ 9
+      !is.na(pHint_tot_sf_10m) ~ 9
       ),
@@
 
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_1m, pHint_tot_sf_3m, pHint_tot_sf_5m, pHint_tot_sf_7m, pHint_tot_sf_9m)
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_1m, pHint_tot_sf_3m, pHint_tot_sf_5m, pHint_tot_sf_7m, pHint_tot_sf_10m)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
 dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
-dySeries("pHint_tot_sf_9m", label = "pHT 9m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_10m", label = "pHT 10m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
 dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
@@
 
- + To compare with pCO2/pCO2 measured in the Ferrybox seems therefore better to stick with pH_9m, that is at depths deeper than 8 m.
+ + To compare with pCO2/pCO2 measured in the Ferrybox seems therefore better to stick with pH_10m, that is at depths deeper than 8 m.
   + pCO2 would have the same behaviour as pH. For air-sea CO2 fluxes, one should use data from 0 to 4 m.
@@
   d_all %>%
-  dplyr::select(montht, sal_mix, temp_mix, temp_insitu_11m, pHint_tot_sf_9m) %>% 
+  dplyr::select(montht, sal_mix, temp_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
   group_by(montht) %>%
@@
 pH_sf <- d_all %>%
-  dplyr::select(datetime, sal_insitu_ctd_9m , temp_insitu_ctd_9m, pHint_tot_sf)%>%
-  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd_9m), !is.na(sal_insitu_ctd_9m)) %>%
+  dplyr::select(datetime, sal_insitu_ctd_10m , temp_insitu_ctd_10m, pHint_tot_sf)%>%
+  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd_10m), !is.na(sal_insitu_ctd_10m)) %>%
   dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
 
-pH_sf$pHint_tot_sf_temp_4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+pH_sf$pHint_tot_sf_temp_4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_10m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_10m, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 
@@
 ```{r stratification, echo=FALSE, message= FALSE, warning=FALSE}
-# we look at the distribution of data
-tmp <- d_all %>% 
-  dplyr::select(date, depth, pressure_insitu_ctd) %>% 
-  dplyr::mutate(month=month(d_all$date, label = TRUE)) %>% 
-  group_by(month)
-depth_labels <- c("0-2", "2-4", "4-6", "6-8", "8-12")
+# # we look at the distribution of data
+# tmp <- d_all %>% 
+#   dplyr::select(date, depth, pressure_insitu_ctd) %>% 
+#   dplyr::mutate(month=month(d_all$date, label = TRUE)) %>% 
+#   group_by(month)
+depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
 # we look at salinity all depths
 tmp <- d_all %>% 
-  dplyr::mutate(depth_group = depth_group_pressure) %>% 
-  dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
+  #dplyr::mutate(depth_group = depth_group_pressure) %>% 
+  dplyr::select(montht, sal_insitu_ctd, depth, depth_group) %>%
+  tidyr::drop_na() %>% 
+  #dplyr::filter(!is.na(sal_insitu_ctd), !is.na(depth_group)) %>% 
   group_by(depth_group, montht)
@@
 * reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
-* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
+* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_10m)
 * sal_mix_interp: interpolated salinity sal_mix. It is used to have as many spec pH to display (some are during missing data)
@@
     - ph_s_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
-    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
+    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_10m si trous) + temp CTD 10m + sal CTD 10m (calib seaFET fonction 1)
     - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)

### 2021-12-09 awipev-CO2.Rmd
adding quality plot for seaFET measurements + group_by(datetime) instead of date in discrete df+ adding hour column in d_all

--- 2021-12-03 awipev-CO2.Rmd
@@
 
+library("RColorBrewer")
 if (!require("tidyverse")) install.packages("tidyverse")
@@
                 monthd = lubridate::month(d_hour$datetime), # month as a number
-                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) # abbreviated months
+                montht = lubridate::month(d_hour$datetime, label = TRUE, abbr = TRUE) ,
+                hour = lubridate::hour(d_hour$datetime)# abbreviated months
   )
@@
 d_all$closest_datetime <- d_all$datetime
+
 d <- left_join(d, d_all %>%
@@
                    c(closest_datetime,
+                     hour,
                      sal_fb,
@@
 pH_seafet_mean$ph_s_sf_temp_insi <- pH_seafet_mean$ph_s_sf_temp_insi_mean
+
 #  make means in "d" to have same format and call it "discrete"
 discrete <- d %>%
-  dplyr::group_by(date) %>%
-  dplyr::summarize(
-    datetime = mean(datetime, na.rm = TRUE),
+  group_by(datetime) %>%
+#dplyr::select( datetime, date,hour,sal_fb,sal_mix_interp ,sal_mix,temp_fb, at_mean_interp,at ,ct_mean_interp,ct, temp_mix,temp_mix_interp,temp_insitu_11m) %>%
+  summarise(datetime = mean(datetime, na.rm = TRUE),
     sal_fb = mean(sal_fb, na.rm = TRUE),
     sal_mix = mean(sal_mix, na.rm = TRUE),
+    sal_mix_interp = mean(sal_mix_interp, na.rm = TRUE),
     temp_fb = mean(temp_fb, na.rm = TRUE),
+     temp_mix = mean(temp_mix, na.rm = TRUE),
+    temp_mix_interp = mean(temp_mix_interp, na.rm = TRUE),
+        temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE),
     at_mean_interp = mean(at_mean_interp, na.rm = TRUE),
     at = mean(at, na.rm = TRUE),
-    #qflag_at = mean(qflag_at, na.rm = TRUE), # already dealt with above
     ct_mean_interp = mean(ct_mean_interp, na.rm = TRUE),
-    ct = mean(ct, na.rm = TRUE),
-    #qflag_ct = mean(qflag_ct, na.rm = TRUE)  # already dealt with above
-    temp_mix = mean(temp_mix, na.rm = TRUE),
-    temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE)
-  )
-# join discrete + seafet/durafet
+    ct = mean(ct, na.rm = TRUE) ,.groups = 'drop_last'
+
+  )
+
+# library("RColorBrewer")
+# d_xts <- dplyr::select(discrete, datetime, sal_fb, sal_mix,temp_fb,temp_mix,temp_insitu_11m, at_mean_interp,at,ct_mean_interp,ct)
+# d_xts <- as.xts(d_xts, order.by = d_xts$datetime)
+# dygraph(d_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
+#             dySeries("sal_mix", color = brewer.pal(n=9, name = "Paired")[1], strokeWidth = 1, pointSize = 4, label = "sal_mix") %>%
+#             dySeries("sal_fb", color = brewer.pal(n=9, name = "Paired")[2], strokeWidth = 1, pointSize = 2, label = "sal_fb") %>%
+#    dySeries("temp_mix", color = brewer.pal(n=9, name = "Paired")[3], strokeWidth = 1, pointSize = 4, label = "temp_mix") %>%
+#    dySeries("temp_fb", color = brewer.pal(n=9, name = "Paired")[4], strokeWidth = 1, pointSize = 2, label = "temp_fb") %>%
+#    dySeries("temp_insitu_11m", color = brewer.pal(n=9, name = "Paired")[5], strokeWidth = 1, pointSize = 2, label = "temp_insitu_11m") %>%
+#     dySeries(axis="y2", "at_mean_interp", color = brewer.pal(n=9, name = "Paired")[6], strokeWidth = 1, pointSize = 4, label = "at_mean_interp") %>%
+#    dySeries(axis="y2","ct_mean_interp", color =brewer.pal(n=9, name = "Paired")[7], strokeWidth = 1, pointSize = 4, label = "ct_mean_interp") %>%
+#  dySeries(axis="y2","at", color = brewer.pal(n=9, name = "Paired")[8], strokeWidth = 1, pointSize = 2, label = "at") %>%
+#    dySeries(axis="y2","ct", color =brewer.pal(n=9, name = "Paired")[9], strokeWidth = 1, pointSize = 2, label = "ct") %>%
+#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
+#       dyOptions( drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
+#     dyLegend(show = "follow")   %>%
+#    # dyAxis("y",valueRange = c(30, 37)) %>%
+#       dyRangeSelector(height = 30, dateWindow= NULL)
+
 discrete <- left_join(discrete, pH_seafet_mean, by='datetime')
@@
   dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
-carb <- carb(15, discrete_no_na$at*1e-6, discrete_no_na$ct*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+carb <- carb(15, discrete_no_na$at_mean_interp*1e-6, discrete_no_na$ct_mean_interp*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
 discrete_no_na$ph_calc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
@@
 names(seafet_calib) <- c("pHint_tot_sf", "pHext_tot_sf")
-
 ##########  Despike() ###########
@@
   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-  dyRangeSelector(height = 30, dateWindow= NULL)
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyRangeSelector(height = 30, dateWindow= c("2017-08-10 00:00:00","2021-01-20 23:00:00"))
 rm(seafet_depth_xts)
@@
 
-```{r seaFET quality control pH, echo=FALSE, warning = FALSE, message = FALSE, out.width='100%'}
+```{r seaFET quality control pH 1, echo=FALSE, warning = FALSE, message = FALSE, out.width='100%'}
 #Offset between seafet pH and spec pH (Fig. 2 Kapsenberg et al.)
-
 ph_sf <- d_all%>%
-  mutate( diff_pH = ph_s_sf_temp_insi - pHint_tot_sf)
-average_offset <- mean(abs(ph_sf$diff_pH), na.rm=TRUE)
-
-offset_xts <- dplyr::select(ph_sf%>%dplyr::filter(!is.na(diff_pH)), datetime, diff_pH)
+  dplyr::select(datetime, ph_s_sf_temp_insi,pHint_tot_sf,pHext_tot_sf)%>%
+    dplyr::mutate( diff_spec_sf = ph_s_sf_temp_insi - pHint_tot_sf,
+                   diff_sf_int_ext = pHint_tot_sf -pHext_tot_sf )
+average_offset <- mean(ph_sf$diff_spec_sf, na.rm=TRUE, digits=4)
+
+offset_xts <- select(ph_sf, datetime, diff_spec_sf)
 offset_xts <- as.xts(offset_xts, order.by=offset_xts$datetime)
 
-dygraph(offset_xts, ylab = "") %>%
-dySeries("diff_pH", drawPoints = TRUE, pointSize=3, label = "delta pHINT", color="green")%>%
-    dyLimit(0,strokePattern = "dashed", color = "black") %>% 
+dygraph(offset_xts, main = "delta spectro - INT calibrated seaFET") %>%
+dySeries("diff_spec_sf", drawPoints = TRUE, pointSize=4, label = "Delta", color="green")%>%
+    dyLimit(0,strokePattern = "solid", color = "black") %>% 
   dyLimit(-0.02,strokePattern = "dashed", color = "red") %>% 
     dyLimit(0.02,strokePattern = "dashed", color = "red") %>% 
- # dyAxis("y",valueRange = c(-0.04, 0.04))%>%
-  dyAxis("x",valueRange = c(as.POSIXct("2021-09-28"), as.POSIXct("2021-10-19")
-))%>%
+  dyAxis("y",valueRange = c(-0.08, 0.14))%>%
+    dyLegend(show = "follow")   %>%
+ # dyAxis("x",valueRange = c(as.POSIXct("2021-09-28"), as.POSIXct("2021-10-19")))%>%
+    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
 dyOptions(
@@
     digitsAfterDecimal = 4) %>%
-  dyRangeSelector(height = 30)
+  dyRangeSelector(height = 30, dateWindow= c("2017-10-21 00:00:00", "2021-01-11 00:00:00"))
+```
+
+- pH INT - pH EXT was plotted here.
+
+```{r seaFET quality control pH 2, echo=FALSE, warning = FALSE, message = FALSE, out.width='100%'}
+                                                                                                                                                                                       ## INT -EXT
+delta_xts <- dplyr::select(ph_sf,datetime, diff_sf_int_ext, pHext_tot_sf, pHint_tot_sf)
+delta_xts <- as.xts(delta_xts, order.by=delta_xts$datetime)
+dygraph(delta_xts, main = "delta pHINT - pH EXT") %>%
+  dySeries(axis ="y2","pHext_tot_sf", drawPoints = TRUE, pointSize=3, label = "pH EXT", color="red")%>%
+dySeries(axis ="y2","pHint_tot_sf", drawPoints = TRUE, pointSize=2, label = "pH INT", color="blue")%>%
+  dySeries( "diff_sf_int_ext", drawPoints = TRUE, pointSize=2, label = "Delta", color="grey")%>%
+    dyLegend(show = "follow")   %>%
+      dyLimit(0,strokePattern = "solid", color = "black") %>% 
+ dyAxis("y",valueRange = c(-0.3,0.3))%>%
+    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+dyOptions(
+    drawGrid = TRUE,
+    strokeWidth= 0,
+    drawPoints = TRUE,
+    useDataTimezone = TRUE,
+    digitsAfterDecimal = 4) %>%
+  dyRangeSelector(height = 30, dateWindow= c("2017-10-21 00:00:00", "2021-01-11 00:00:00"))
+
 ```

### 2021-12-09 awipev-CO2.Rmd
Work on tratification

--- 2021-12-07 awipev-CO2.Rmd
@@
   dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
-  dplyr::mutate(depth_group = dplyr::case_when(depth > 0 & depth <= 2 ~ '0-2',
+  dplyr::mutate(depth_group = as.factor(dplyr::case_when(depth > 0 & depth <= 2 ~ '0-2',
                 depth > 2 & depth <= 4 ~ '2-4',
@@
                 TRUE ~ 'NA'
-                ),
+                )),
                 sal_insitu_ctd_1m = ifelse(depth_group == '0-2', sal_insitu_ctd, NA),
@@
   dplyr::select(montht, pHint_tot_sf, depth) %>%
-  dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
-  dplyr::filter(depth == 2 | depth == 10) %>% 
-  dplyr::group_by(depth, montht)
-summary(aov(tmp$pHint_tot_sf ~ tmp$depth * tmp$montht))
+  dplyr::mutate(depth2 = as.factor(case_when(depth < 4 ~ '0-4', 
+                                             depth > 8~ '8-12',
+                                             TRUE ~ NA_real_))) %>% 
+  dplyr::filter(depth2 == '0-2' | depth2 == '8-12') %>% 
+  dplyr::group_by(depth2, montht)
+summary(aov(tmp$pHint_tot_sf ~ tmp$depth2 * tmp$montht))
 
@@
 # # we look at the distribution of data
-# tmp <- d_all %>% 
-#   dplyr::select(date, depth, pressure_insitu_ctd) %>% 
-#   dplyr::mutate(month=month(d_all$date, label = TRUE)) %>% 
-#   group_by(month)
 depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
@@
 tmp <- d_all %>% 
-  #dplyr::mutate(depth_group = depth_group_pressure) %>% 
   dplyr::select(montht, sal_insitu_ctd, depth, depth_group) %>%
   tidyr::drop_na() %>% 
-  #dplyr::filter(!is.na(sal_insitu_ctd), !is.na(depth_group)) %>% 
+  dplyr::filter(depth_group != "NA") %>% 
   group_by(depth_group, montht)
@@
 print(p)
-
 summary(aov(tmp$sal_insitu_ctd ~ tmp$depth_group * tmp$montht))
@@
   dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
-  dplyr::mutate(depth = as.factor(ifelse(depth_group == 1 | depth_group == 3, 2, depth_group))) %>% 
-  dplyr::filter(depth == 2 | depth == 10)
+  dplyr::mutate(depth2 = as.factor(case_when(depth < 4 ~ '0-4', 
+                                             depth > 8~ '8-12',
+                                             TRUE ~ NA_real_))) %>% 
+  dplyr::filter(depth2 == '0-4' | depth2 == '8-12') %>% 
+  dplyr::group_by(depth2, montht)
 tmp_delta <- tmp %>% 

### 2021-12-09 awipev-CO2.Rmd
minor cosmetic changes

@@
    )
+
 # Make mean for replicates + SD
@@
     ct = mean(ct, na.rm = TRUE) ,.groups = 'drop_last'
-
   )

### 2021-12-10 awipev-CO2.Rmd
still on stratification...

@@
 tmp <- d_all %>% 
-  dplyr::select(montht, sal_insitu_ctd, depth, depth_group) %>%
+  dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
   tidyr::drop_na() %>% 
@@
 tmp <- d_all %>% 
-  dplyr::mutate(depth_group = depth_group_pressure) %>% 
   dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
-  dplyr::mutate(depth2 = as.factor(case_when(depth < 4 ~ '0-4', 
-                                             depth > 8~ '8-12',
-                                             TRUE ~ NA_real_))) %>% 
-  dplyr::filter(depth2 == '0-4' | depth2 == '8-12') %>% 
-  dplyr::group_by(depth2, montht)
+  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
+                                      depth_group == '>8' ~ '8-12'))) %>% 
+  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
+  dplyr::group_by(depth_group2, montht)
 tmp_delta <- tmp %>% 
-  group_by(depth, montht) %>% 
+  group_by(depth_group2, montht) %>% 
   dplyr::summarise(sal_med = median(sal_insitu_ctd, na.rm = TRUE)) %>% 
-  tidyr::pivot_wider(names_from = depth, values_from = sal_med) %>% 
-  dplyr::rename(median0_4m = "2",
-                median8_12m = "10") %>% 
+  tidyr::pivot_wider(names_from = depth_group2, values_from = sal_med) %>% 
+  dplyr::rename(median0_4m = "0-4",
+                median8_12m = "8-12") %>% 
   dplyr::mutate(sal_delta = median0_4m - median8_12m)
@@
 p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = sal_insitu_ctd)) +
+  ggplot(aes(x=depth_group2, y = sal_insitu_ctd)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
         panel.grid.minor.y = element_blank())
+print(sal_delta_plt)
 
@@
 tmp <- d_all %>% 
-  dplyr::mutate(depth_group = depth_group_pressure) %>% 
   dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
+  tidyr::drop_na() %>% 
+  dplyr::filter(depth_group != "NA") %>% 
   group_by(depth_group, montht)
@@
   labs(title = "Temperature vs depth", x = "Depth (m)", y= "Temperature") +
+  scale_x_discrete(labels = depth_labels) +
   facet_wrap(vars(montht), scale = "free_y")
 print(p)
-
+summary(aov(tmp$temp_insitu_ctd ~ tmp$depth_group * tmp$montht))
 # we look at temperature 0 to 4 m vs more than 8 m
 tmp <- d_all %>% 
-  dplyr::mutate(depth_group = depth_group_pressure) %>% 
   dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
-  dplyr::mutate(depth = as.factor(ifelse(depth_group == 1 | depth_group == 3, 2, depth_group))) %>% 
-  dplyr::filter(depth == 2 | depth == 10) %>% 
-  group_by(depth, montht)
-summary(aov(tmp$temp_insitu_ctd ~ tmp$depth * tmp$montht))
-
+  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
+                                      depth_group == '>8' ~ '8-12'))) %>% 
+  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
+  dplyr::group_by(depth_group2, montht)
 tmp_delta <- tmp %>% 
-  group_by(depth, montht) %>% 
+  group_by(depth_group2, montht) %>% 
   dplyr::summarise(temp_med = median(temp_insitu_ctd, na.rm = TRUE)) %>% 
-  tidyr::pivot_wider(names_from = depth, values_from = temp_med) %>% 
-  dplyr::rename(median0_4m = "2",
-                median8_12m = "10") %>% 
+  tidyr::pivot_wider(names_from = depth_group2, values_from = temp_med) %>% 
+  dplyr::rename(median0_4m = "0-4",
+                median8_12m = "8-12") %>% 
   dplyr::mutate(temp_delta = median0_4m - median8_12m)
@@
 
+# we look at temperature 0 to 4 m vs more than 8 m
 p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = temp_insitu_ctd)) +
+  ggplot(aes(x=depth_group2, y = temp_insitu_ctd)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
   scale_x_discrete(expand = c(0, 0)) +
-  scale_y_continuous("Temperature", limits = c(-3, 3), expand = c(0, 0)) +
+  scale_y_continuous("Temperature", limits = c(-1.3, 0.8), expand = c(0, 0)) +
   geom_col(fill="blue") +
   geom_hline(yintercept = 0) +
-  annotate("text", x = 1.5, y = 2.5, label = substitute("T"["surface"] ~ "> T"["deep"])) +
-  annotate("text", x = 1.5, y = -2.5, label = substitute("T"["surface"] ~ "< T"["deep"])) +
+  annotate("text", x = 1.5, y =0.6, label = substitute("T"["surface"] ~ "> T"["deep"])) +
+  annotate("text", x = 1.5, y = -0.6, label = substitute("T"["surface"] ~ "< T"["deep"])) +
   Mytheme(size_labs = 12) +
@@
         panel.grid.minor.y = element_blank())
+print(temp_delta_plt)
+# we look at density at all depths
+tmp <- d_all %>% 
+  dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth_group, pressure_insitu_ctd) %>%
+  tidyr::drop_na() %>% 
+  dplyr::filter(depth_group != "NA") %>% 
+  dplyr::mutate(density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = pressure_insitu_ctd)) %>% 
+  group_by(depth_group, montht)
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth_group), y = sal_insitu_ctd)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "Density vs depth", x = "Depth (m)", y= "Density") +
+  scale_x_discrete(labels = depth_labels) +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+summary(aov(tmp$density ~ tmp$depth_group * tmp$montht))
 
@@
 tmp <- d_all %>% 
-  dplyr::mutate(depth_group = depth_group_pressure) %>% 
-  dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth_group, pressure_insitu_ctd) %>%
-  dplyr::mutate(density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = pressure_insitu_ctd),
-                depth = as.factor(ifelse(depth_group == 1 | depth_group == 3, 2, depth_group))) %>% 
-  dplyr::filter(depth == 2 | depth == 10) %>% 
-  dplyr::select(montht, depth, density) %>% 
-  group_by(depth, montht) 
-summary(tmp)
-summary(aov(tmp$density ~ tmp$depth * tmp$montht))
+  dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
+  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
+                                      depth_group == '>8' ~ '8-12'))) %>% 
+  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
+  dplyr::group_by(depth_group2, montht)
 
 tmp_delta <- tmp %>% 
-  group_by(depth, montht) %>% 
+  dplyr::select(montht, depth_group, density) %>% 
+  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
+                                      depth_group == '>8' ~ '8-12'))) %>% 
+  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
+  group_by(depth_group2, montht) %>% 
   dplyr::summarise(den_med = median(density, na.rm = TRUE)) %>% 
-  tidyr::pivot_wider(names_from = depth, values_from = den_med) %>% 
-  dplyr::rename(median0_4m = "2",
-                median8_12m = "10") %>% 
-  dplyr::mutate(den_delta = median0_4m - median8_12m)
+  tidyr::pivot_wider(names_from = depth_group2, values_from = den_med) %>% 
+  dplyr::rename(median0_4m = "0-4",
+                median8_12m = "8-12") %>% 
+  dplyr::mutate(temp_delta = median0_4m - median8_12m)
 kable(tmp_delta, digits = 2, caption = "Median density with (median0_4m - median8_12m)")
@@
 p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = density)) +
+  ggplot(aes(x=montht, y = density)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +

### 2021-12-13 awipev-CO2.Rmd
still on stratification

@@
 
-# we look at temperature 0 to 4 m vs more than 8 m
 p <- tmp %>% 
@@
 tmp <- d_all %>% 
-  dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
+  dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth_group, pressure_insitu_ctd) %>%
+  tidyr::drop_na() %>% 
+  dplyr::filter(depth_group != "NA") %>% 
   dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
-                                      depth_group == '>8' ~ '8-12'))) %>% 
+                                      depth_group == '>8' ~ '8-12')), 
+                density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, 
+                                       P = pressure_insitu_ctd)) %>% 
   dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 

### 2021-12-13 awipev-CO2.Rmd
checking all the seafet code

@@
   dplyr::mutate(datetime = dmy_hm(sampling_date, tz="UTC"),
-                measure_date = ymd(measure_date, tz="UTC"),
+                measure_date = dmy(measure_date, tz="UTC"),
                 date = as.Date(datetime)) %>% 
@@
 d <- d %>%
-  dplyr::filter(location_flag == 0)
+  dplyr::filter(location_flag == 0) %>% 
+# below we change the time of 2 discrete samplings during period 1 of seafet deployment
+# This is to enable calibration when the REMOS was at 9 m depth
+  dplyr::mutate(datetime = case_when(datetime == as.POSIXct("2017-08-24 13:30:00") ~ as.POSIXct("2017-08-24 19:00:00"),
+                                     datetime == as.POSIXct("2017-11-28 09:15:00") ~ as.POSIXct("2017-11-28 13:00:00"),
+                   TRUE ~ datetime))
 
@@
 pH is measured continuously by an autonomous seaFET pH sensor.
-Because of issue, measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17.
+Measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17 it was then measured once every minute.
+pH calibration is based on monthly, when possible, discrete samples collected at 11 m that were analysed with spectrophotometric method in Villefranche by Samir Alliouane.
+Measurments were performed several months after sampling.
+When sampling was not possible in the vicinity of the sensor for practical reasons (in winter), sampling was done in the harbour and is not taken in consideration for calibration for spatial reasons.
 *Note that the pH sensor is mounted on a profiling structure.
-Here, only seaFET data recorded with a depth > 8 m are taken in consideration.* pH calibration is based on monthly discrete samples that are analysed with spectrophotometric method in Villefranche by Samir Alliouane.
-When it is not possible to sample at the vicinity of the sensor for practice reasons (in winter), sampling is done in the harbour and is not taken in consideration for calibration for spatial reasons.
+Here, in principle, only seaFET data recorded with a depth > 8 m should be taken into consideration.*
 
@@
 (2014) and adapted to use in R (seacarb package).
-Deployment periods are difined so that one spectrophotometric measurement is in the middle of a defined period of calibration (shaded colors in the plot).
-
-Within this deployment period, calibration is made with E0 calculation (first plot) and final corrected pH is calculated (second plot).
-To allow calibration, one spectrophotometric pH measurement must match: seaFET voltage, in situ temperature (SBE38) and salinity.
+3 deployment periods were defined, corresponding to a change of sensors.
+
+Within a deployment period, calibration is made with E0 calculation (first plot) and final corrected pH is calculated (second plot).
+To allow calibration, one spectrophotometric pH measurement must match: seaFET voltage, in situ temperature (seaFET) and salinity (REMOS CTD).
 When one of these parameters is missing for any reasons (Ferrybox maintenance, breakdown...), the gap is filled with a mean of the 4 previous or next hours when available.
 If the pH spectrophotometric measurement is too far from the available values, the calibration is not performed (environemental variability reasons).
-The SBE38 insitu temperature and seaFET temperature are very similar (slope = 0.992, r2 = 0.96, see tab "Temperatures").
-These two temperatures were used interchangeably if one is missing.
-
-Missing data which could be estimated on : 2017-08-24, 2017-09-28, 2019-09-13 x 2.
-Missing data which could not be estimated on : 2018-04-16 , 2018-12-14, 2019-01-18.
-
-We decided to change the calculation of E0.
-Before E0 was calculated for each pH spectro measurements.
-Now, EO is calculated making a mean of several E0 that come from one deployment period (sensor in the water for several months).
+
+Only 5 spectrophotometric pH which could be used for calibration when seaFET at > 8 m: 2018-11-16, 2019-04-17, 2019-10-11, 2020-01-27.
+All deployment meriods are covered but we had to alter the sampling time of:
+
+* 2017-08-24 14:00 to 2017-08-24 19:00 (5 h later)
+* 2017-11-28 09:00 to 2017-11-28 13:00 (4 h later)
+
+EO is calculated making a mean of several E0 that come from one deployment period (sensor in the water for several months).
 
@@
 ```{r seaFET calibration sf_calib, echo=FALSE, message= FALSE, warning=FALSE, out.width= "60%"}
-
-# # We decided to calibrate pH data within each pH spectro measurement.
-# # Thus, each pH spectro is taken as one calibration periode. 
-# # We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
-# sfPeriod <- d_all%>%
-#   dplyr::select(datetime, ph_s_sf_temp_insi)%>%
-#   dplyr::filter(!is.na(ph_s_sf_temp_insi))
-# # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
-# sfPeriod <- sfPeriod%>%
-# dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
-# 
-# sfPeriod <-  sfPeriod %>%
-#   dplyr::arrange(datetime) %>%
-#   dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
-#   dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
-# 
-# #put interval in a list with the start date of seaFET measurements
-# sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
-# #Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
-# # This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
-# sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
-# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-# # sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
-# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
-# # sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
-# 
-# #sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
-# # set deployment period between 2 spectro measurements.
-
-# # add here the new periods sfinterv[..]
-# d_all <- d_all %>%
-#   dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
-#                                 ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
-#                                 ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
-#                                 ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
-#                                 ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
-#                                 ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
-#                                 ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
-#                                 ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
-#                                 ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
-#                                 ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
-#                                 ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
-#                                  ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
-#                                  ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
-#                                  ifelse(datetime >= sfinterv[14] & datetime <= sfinterv[15], 14,
-#                                  ifelse(datetime >= sfinterv[15] & datetime <= sfinterv[16], 15,
-#                                  ifelse(datetime >= sfinterv[16] & datetime <= sfinterv[17], 16,
-#                                  ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
-#                                 ifelse(datetime >= sfinterv[18] & datetime <= sfinterv[19], 18,
-#                                 ifelse(datetime >= sfinterv[19] & datetime <= sfinterv[20], 19,
-#                                 ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
-#                                 ifelse(datetime >= sfinterv[21] & datetime <= sfinterv[22], 21,
-#                                 #ifelse(datetime >= sfinterv[22] & datetime <= sfinterv[23], 22,
-#                                 #ifelse(datetime >= sfinterv[23] & datetime <= sfinterv[24], 23,
-#                                 #ifelse(datetime >= sfinterv[24] & datetime <= sfinterv[25], 24,
-#                                 #ifelse(datetime >= sfinterv[25] & datetime <= sfinterv[26], 25,
-#                                 ifelse(datetime >= sfinterv[22] , 22,NA )))))))))))))))))))))))
-
-# set deployment period when seaFET is in/out of water
 sfinterv <- as.POSIXct(c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00"))
@@
                                 ifelse(datetime >= sfinterv[3], 03, NA ))))
-
-# pco2_contros_xts <-
+# dygraph to check seafet data
+# pH_xts <-
 #   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_insi)
-# pco2_contros_xts <-
-#   as.xts(pco2_contros_xts, order.by = d_all$datetime)
-# dygraph(pco2_contros_xts,
+# pH_xts <-
+#   as.xts(pH_xts, order.by = d_all$datetime)
+# dygraph(pH_xts,
 #         group = "awipev",
-#         main = "<i>p</i>CO<sub>2</sub>",
-#         ylab = "<i>p</i>CO<sub>2</sub>") %>%
+#         main = "pH",
+#         ylab = "pH") %>%
 #   dySeries(
@@
 # If the pH spectro is too far from a needed value, we decided to skip it for the calibration.
-# we highlighted 7 pH spectro that dont match one of these parameters : 2017-08-24 14:00:00 - 2017-09-28 13:00:00 - 2018-04-16 07:00:00 - 2018-12-14 09:00:00 - 2019-01-18 09:00:00 - 2019-09-13 08:00:00 - 2019-09-13 13:00:00
+
 # (1) Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04,
-# (2) removed from 2018-01-08 to 2018-02-02
-# (3) outliers removed
-# (1)
-d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
-                        d_all$datetime <= as.POSIXct("2018-01-08") &
-                        d_all$phINT < 8.04, NA, d_all$phINT)
-d_all$phEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
-                       d_all$datetime <= as.POSIXct("2018-01-08") &
-                       d_all$phEXT < 8.04, NA, d_all$phEXT) 
+# d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
+#                         d_all$datetime <= as.POSIXct("2018-01-08") &
+#                         d_all$phINT < 8.04, NA, d_all$phINT)
+# d_all$phEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
+#                        d_all$datetime <= as.POSIXct("2018-01-08") &
+#                        d_all$phEXT < 8.04, NA, d_all$phEXT) 
 d_all$voltINT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
@@
                          d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
-# (2)
+#(2) removed from 2018-01-08 to 2018-02-02 due to drift
 d_all$voltINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
@@
                       NA, d_all$phEXT)
-# (3)
+# (3) outliers removed
 d_all$voltINT <- ifelse(d_all$datetime == as.POSIXct("2017-11-02 21:00:00") |
@@
 ####
-## calculation of E0INT25/E0EXT25 ##
+## calculation of E0INT25/E0EXT25 irrespective of the depth at which the seafet is (all data used) ##
 ##     new sf_calib function      ##
@@
 ### **seaFET pHT calibrated**
-pH is measured continuously by an autonomous seaFET pH sensor.
 Final calibrated seaFET pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
-Calibration was done following the methods and code described in Bresnahan *et al.* (2014) using seaFET voltage and spectro measurements.
-During the fifth period, seaFET cannot be calibrated because seaFET was not working during the time of reference (pH spectro) sampling (2018-04-16).
-To solve this calibration, we decided to fit the spectro measurement with a pH mean of 4 previous days.
 
@@
 d_all <- d_all %>%   
-  dplyr::mutate(pHint_tot_sf = oce::despike(seafet_calib$pHint_tot_sf, reference= "median", n=1, k=5000, replace="NA"),
-                pHext_tot_sf = oce::despike(seafet_calib$pHext_tot_sf, reference= "median", n=1, k=5000, replace="NA")
+  dplyr::mutate(pHint_tot_sf = oce::despike(seafet_calib$pHint_tot_sf, reference= "median", n=1, k=5001, replace="NA"),
+                pHext_tot_sf = oce::despike(seafet_calib$pHext_tot_sf, reference= "median", n=1, k=5001, replace="NA")
   )
@@
   )
-
-# d_all <- d_all %>%
-#   dplyr::mutate(ph_s_sf_temp_4 = ifelse(!is.na(pH_seafet$ph_s_sf),
-#                                               pHinsi(pH = pH_seafet$ph_s_sf, 
-#                          ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
-#                          Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, 
-#                          S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
-#                          pHscale = "T", b="u74"), NA
-#   ))
-
-# add spectro points that cannot be taken into consideration (some ancillary data T and/or S not available) shown as white triangles on the plot
-# ALSO Conversion of spec pH of FerryBox samples at 4°C
-
-d_all <- d_all %>%
-  dplyr::mutate(
-    pH_s_sf_no_calb = ifelse(
-      datetime == as.POSIXct("2018-04-16 07:00:00") |
-        datetime == as.POSIXct("2018-12-14 10:00:00") |
-        datetime == as.POSIXct("2019-01-18 11:00:00"),
-      ph_s_sf_temp_insi,
-      NA
-    ))
 

### 2021-12-13 awipev-CO2.Rmd
ading seafet calibration with 9m depth taken in consideration only

--- 2021-12-10 awipev-CO2.Rmd
@@
   ))
-d_hour <- as_tsibble(d_hour, index = datetime) %>% #d_all will be the merger
+d_hour <- as_tsibble(d_hour, index = datetime) %>%#d_all will be the merger
   tsibble::fill_gaps(.full=TRUE)
@@
   arrange(datetime)
-
 # read a file provided by Philipp on 2021-04-09 which fills most gaps of pressure data
@@
     "fb_data/svl_remos_depth.rds"
-  ))) %>% 
-  dplyr::select(-adcp_fill, -ctd_fill)
-
+  )))
 d_hour <- dplyr::left_join(d_hour, svl_remos_depth, by = 'datetime') %>% 
-  dplyr::mutate(depth = ifelse(!is.na(pressure_insitu_ctd), pressure_insitu_ctd, depth_complete))
-
+  dplyr::select(-adcp_fill, -ctd_fill) %>% 
+  dplyr::rename(depth = depth_complete)
 # check_plot <- d_hour %>% 
@@
   dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
-  dplyr::mutate(depth_group = as.factor(dplyr::case_when(depth > 0 & depth <= 2 ~ '0-2',
-                depth > 2 & depth <= 4 ~ '2-4',
-                depth > 4 & depth <= 6 ~ '4-6',
-                depth > 6 & depth <= 8 ~ '6-8',
-                depth > 8 & depth <= 12 ~ '>8', #8 to 12.4
-                TRUE ~ 'NA'
-                )),
-                sal_insitu_ctd_1m = ifelse(depth_group == '0-2', sal_insitu_ctd, NA),
-                sal_insitu_ctd_3m = ifelse(depth_group == '2-4', sal_insitu_ctd, NA),
-                sal_insitu_ctd_5m = ifelse(depth_group == '4-6', sal_insitu_ctd, NA),
-                sal_insitu_ctd_7m = ifelse(depth_group == '6-8', sal_insitu_ctd, NA),
-                sal_insitu_ctd_10m = ifelse(depth_group == '>8', sal_insitu_ctd, NA),
-                temp_insitu_ctd_1m = ifelse(depth_group == '0-2', temp_insitu_ctd, NA),
-                temp_insitu_ctd_3m = ifelse(depth_group == '2-4', temp_insitu_ctd, NA),
-                temp_insitu_ctd_5m = ifelse(depth_group == '4-6', temp_insitu_ctd, NA),
-                temp_insitu_ctd_7m = ifelse(depth_group == '6-8', temp_insitu_ctd, NA),
-                temp_insitu_ctd_10m = ifelse(depth_group == '>8', temp_insitu_ctd, NA),
-  ) %>% 
+  dplyr::mutate(depth_group_pressure = ifelse( # create new variable depth
+      pressure_insitu_ctd <= 2,
+      1,
+      ifelse(
+        pressure_insitu_ctd > 2 & depth <= 4,
+        3,
+        ifelse(
+          pressure_insitu_ctd > 4 & depth <= 6,
+          5,
+          ifelse(
+            pressure_insitu_ctd > 6 & depth <= 8,
+            7,
+            ifelse(pressure_insitu_ctd > 8, 10, NA)
+          )
+        )
+      )
+    ),
+    depth_group_philipp = ifelse( # create new variable depth
+      depth <= 2,
+      1,
+      ifelse(
+        depth > 2 & depth <= 4,
+        3,
+        ifelse(
+          depth > 4 & depth <= 6,
+          5,
+          ifelse(
+            depth > 6 & depth <= 8,
+            7,
+            ifelse(depth > 8, 10, NA)
+          )
+        )
+      )
+    )) %>%
   dplyr::rowwise() %>% 
@@
     temp_insitu_ctd_7m,
-    temp_insitu_ctd_10m
+    temp_insitu_ctd_9m
   )
@@
   ungroup()
-
 #restore datetime, date which are mangled by the mutates above, arrange ascending
@@
   )
-d_all <- d_all %>% 
-  dplyr::select(order(colnames(d_all)))
 rm(d_hour)
@@
 d_all <- d_all %>%
-  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_10m))
+  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_9m))
 ```
@@
 ```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-# Create temp_mix: filling gaps in temp_insitu_11m using temp_insitu_10m
+# Create temp_mix: filling gaps in temp_insitu_11m using temp_insitu_9m
 d_all <- d_all %>%
-  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_10m))
+  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_9m))
 ```
@@
 # interpolation of temp_mix/sal_mix in d_all in order to have a full temperature for pHinsi()
-# We take temp_mix/sal_mix because of the depth (temp11m insitu + temp10m ctd)
+# We take temp_mix/sal_mix because of the depth (temp11m insitu + temp9m ctd)
 tempmixinterp <-approx(d_all$datetime, d_all$temp_mix, xout=d_all$datetime, method="linear", rule=2)
@@
    )
-
 # Make mean for replicates + SD
@@
     ct = mean(ct, na.rm = TRUE) ,.groups = 'drop_last'
+
   )
@@
 #SAL CTD profile
-sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_10m)
+sal_xts <- dplyr::select(d_all, datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m)
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
@@
 dySeries("sal_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
-dySeries("sal_insitu_ctd_10m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "10m") %>%
+dySeries("sal_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
       dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
     dyLegend(show = "follow")   %>%
-    dyAxis("y",valueRange = c(29, 37)) %>%
+    dyAxis("y",valueRange = c(30, 37)) %>%
       dyRangeSelector(height = 30, dateWindow= NULL)
@@
 df <- d_all %>% 
-  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_10m) %>%
+  dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_9m) %>%
   dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
@@
   summarize(mean1m = mean(sal_insitu_ctd_1m, na.rm = TRUE),
-            mean10m = mean(sal_insitu_ctd_10m, na.rm = TRUE),
-            range = mean(sal_insitu_ctd_1m, na.rm = TRUE) - mean(sal_insitu_ctd_10m, na.rm = TRUE)) %>% 
+            mean9m = mean(sal_insitu_ctd_9m, na.rm = TRUE),
+            range = mean(sal_insitu_ctd_1m, na.rm = TRUE)-mean(sal_insitu_ctd_9m, na.rm = TRUE)) %>% 
   ungroup()
@@
 p_sal_range <- ggplot(data = df) +
-  geom_histogram((aes(x = range))) +
-  labs(title = "Daily salinity difference between 1 and 10 m", x = "Difference") +
+  geom_histogram((aes(x = df$range))) +
+  labs(title = "Salinity difference between 1 and 9 m", x = "Difference") +
   Mytheme(size_labs = 8)
@@
 ```
-Extreme differences: `r dplyr::filter(df, range < -3 | range > 2)`.
-
-There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 10 m (8-12 m).
-The salinity difference between 1 and 10 m ranges between `r min(df$range, na.rm=TRUE)` and `r max(df$range, na.rm=TRUE)` (mean: `r mean(df$range, na.rm=TRUE)`; `r median(df$range, na.rm=TRUE)`).
+There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 9 m (> 8 m).
+The salinity difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)` and `r max(df$range, na.rm=TRUE)` (mean: `r mean(df$range, na.rm=TRUE)`; `r median(df$range, na.rm=TRUE)`).
 The difference with depth is therefore significant.
 
-### **Sal FB / Sal CTD 10 m **
+### **Sal FB / Sal CTD 9 m **
 
 ```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-lm <- lm2(x = d_all$sal_insitu_ctd_10m, y = d_all$sal_fb)
-p <-  ggplot(d_all,aes(x=sal_insitu_ctd_10m, y= sal_fb))+
+lm <- lm2(x = d_all$sal_insitu_ctd_9m, y = d_all$sal_fb)
+p <-  ggplot(d_all,aes(x=sal_insitu_ctd_9m, y= sal_fb))+
   geom_point( aes(color=factor(monthd))) + 
@@
   coord_fixed(ratio = 1 )+
-  labs( x="Salinity CTD 10 m", y="Salinity FB ", color = "Months") + theme_bw()
+  labs( x="Salinity CTD 9 m", y="Salinity FB ", color = "Months") + theme_bw()
 
@@
 
-d_all$diff_sal_fb_insitu_10m <- d_all$sal_insitu_ctd_10m - d_all$sal_fb
-mean_diff_sal_fb_insitu_10m <- round(mean(d_all$diff_sal_fb_insitu_10m, na.rm = TRUE), digits = 2)
-sd_diff_sal_fb_insitu_10m <- round(sd(d_all$diff_sal_fb_insitu_10m, na.rm = TRUE), digits = 2)
-```
-
-The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu_10m` ± `r sd_diff_sal_fb_insitu_10m` PSU.
+d_all$diff_sal_fb_insitu_9m <- d_all$sal_insitu_ctd_9m - d_all$sal_fb
+mean_diff_sal_fb_insitu_9m <- round(mean(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
+sd_diff_sal_fb_insitu_9m <- round(sd(d_all$diff_sal_fb_insitu_9m, na.rm = TRUE), digits = 2)
+```
+
+The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu_9m` ± `r sd_diff_sal_fb_insitu_9m` PSU.
 
@@
 - 1 SBE45 inside the Ferrybox (temp_fb)
-- 5 CTD profiling (temp_insitu_ctd_1m - 3m - 5m - 7m - 10m)
+- 5 CTD profiling (temp_insitu_ctd_1m - 3m - 5m - 7m - 9m)
 - 1 fixed at 11 meters depth (temp_insitu_11m)
@@
 ```{r temperature profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-temp_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_10m)
+temp_xts <- dplyr::select(d_all, datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m)
 temp_xts <- as.xts(temp_xts, order.by = temp_xts$datetime)
@@
 dySeries("temp_insitu_ctd_7m", color = RColorBrewer::brewer.pal(5, "Set1")[4], strokeWidth = 0, label = "7m") %>%
-dySeries("temp_insitu_ctd_10m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "10m") %>%
+dySeries("temp_insitu_ctd_9m", color = RColorBrewer::brewer.pal(5, "Set1")[5], strokeWidth = 0, label = "9m") %>%
 dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
 df <- d_all %>% 
-  dplyr::select(datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_10m) %>%
+  dplyr::select(datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_9m) %>%
   dplyr::mutate(date = format(datetime, '%Y-%m-%d')) %>% 
@@
   summarize(mean1m = mean(temp_insitu_ctd_1m, na.rm = TRUE),
-            mean10m = mean(temp_insitu_ctd_10m, na.rm = TRUE),
-            range = mean(temp_insitu_ctd_1m, na.rm = TRUE)-mean(temp_insitu_ctd_10m, na.rm = TRUE)) %>% 
+            mean9m = mean(temp_insitu_ctd_9m, na.rm = TRUE),
+            range = mean(temp_insitu_ctd_1m, na.rm = TRUE)-mean(temp_insitu_ctd_9m, na.rm = TRUE)) %>% 
   ungroup()
@@
 ```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-lm <- lm2(x = d_all$temp_insitu_ctd_10m, y = d_all$temp_insitu_11m)
-p <-  ggplot(d_all, aes(x=temp_insitu_ctd_10m, y= temp_insitu_11m, label = monthd))+
+lm <- lm2(x = d_all$temp_insitu_ctd_9m, y = d_all$temp_insitu_11m)
+p <-  ggplot(d_all, aes(x=temp_insitu_ctd_9m, y= temp_insitu_11m, label = monthd))+
   geom_text( aes(color=factor(monthd))) + 
@@
 
-d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd_10m
+d_all$diff_T_ctd_11m <- d_all$temp_sf - d_all$temp_insitu_ctd_9m
 mean_diff_T_ctd_11m <- round(mean(d_all$diff_T_ctd_11m, na.rm = TRUE), digits = 2)
@@
 
+### add the depth into discrete df. In order to see where the seafet was.
+discrete <- left_join(discrete, d_all%>%dplyr::select(closest_datetime,depth, depth_discrete),by="closest_datetime")
+discrete <- discrete%>%dplyr::filter(discrete$datetime < "2021-07-01 00:00:00")
+
+offset_xts <- select(discrete, closest_datetime, depth,depth_discrete, ph_s_sf_temp_insi)
+offset_xts <- as.xts(offset_xts, order.by=offset_xts$closest_datetime)
+
+dygraph(offset_xts, main = "") %>%
+dySeries("depth_discrete", drawPoints = TRUE, pointSize=3, strokeWidth = 1,label = "depth_discrete", color="black")%>%
+dySeries("depth", drawPoints = TRUE, pointSize=3, label = "depth", strokeWidth = 1,color="blue")%>%
+dySeries(axis="y2","ph_s_sf_temp_insi", drawPoints = TRUE, pointSize=4, label = "spectro", color="red")%>%
+    dyLegend(show = "follow")   %>%
+    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+dyOptions(
+    drawGrid = TRUE,
+    strokeWidth= 0,
+    drawPoints = TRUE,
+    useDataTimezone = TRUE,
+    digitsAfterDecimal = 4) %>%
+  dyRangeSelector(height = 30, dateWindow= c("2017-10-21 00:00:00", "2021-01-11 00:00:00"))
+
 ####
@@
 
+```
+
+```{r seaFET pH calib sf_calib 9m, echo=FALSE, message= FALSE, warning=FALSE}
+###
+#creaate new dataframe and CALIB to take into consideration only seafet data at the same depth than spectro (9m)
+##
+####
+d_all_calib_depth <- d_all%>%
+  dplyr::select(datetime, voltINT, voltEXT,ph_s_sf_temp_insi,sal_insitu_ctd_interp,temp_sf, depth_discrete,deployment_sf)%>%
+  dplyr::filter(depth_discrete == 9)
+
+calib_spectro_depth_9m <- sf_calib(calEint = d_all_calib_depth$voltINT, calEext = d_all_calib_depth$voltEXT, calpH = d_all_calib_depth$ph_s_sf_temp_insi, calT = d_all_calib_depth$temp_sf, calSal = d_all_calib_depth$sal_insitu_ctd_interp)
+# put number of deployment 
+calib_spectro_depth_9m$deployment_sf <- d_all_calib_depth$deployment_sf
+
+# make the mean of E0 by period of deployement
+calib_spectro_depth_9m <- group_by(calib_spectro_depth_9m, deployment_sf) %>%
+  summarise(E0int25 = mean(E0int25, na.rm = TRUE),
+            E0ext25 = mean(E0ext25, na.rm = TRUE) 
+            )
+names(calib_spectro_depth_9m) <- c("deployment_sf", "E0int25_sf_9m", "E0ext25_sf_9m")
+
+# add E0 mean to seaFET data per deployment
+d_all <-left_join(d_all, calib_spectro_depth_9m,by="deployment_sf" )
+```
+
+```{r seaFET pH plot sf_calib , echo=FALSE, message= FALSE, warning=FALSE}
 #### plot
-kk <- tidyr::pivot_longer(calib_spectro, cols = starts_with("E0"), names_to = "variable", values_to = "value")
+kk <- tidyr::pivot_longer(d_all, cols = starts_with("E0"), names_to = "variable", values_to = "value")
 p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
-  facet_grid(variable ~ ., scales="free_y") + theme_bw() +
+  facet_grid(variable ~ ., scales="fixed") + theme_bw() +
   scale_colour_discrete(guide="none")
 print(p_calib)
+
+kbl(calib_spectro)%>%
+    kable_paper() %>% 
+    kable_styling(fixed_thead = T)
+kbl(calib_spectro_depth_9m)%>%
+    kable_paper() %>% 
+    kable_styling(fixed_thead = T)
+
 ```
@@
 # despike me semble inutile, faire plutôt un simple des outliers qui, vérification faite, n'est même pas nécessaire
-# Il faut par contre créér une nouvelle variable avec pH deeper than 8 m, called *_10m for consistency with salinity and temp
+# Il faut par contre créér une nouvelle variable avec pH deeper than 8 m, called *_9m for consistency with salinity and temp
 d_all <- d_all %>%
@@
                 pHint_tot_sf_7m = ifelse(depth >= 6 & depth < 8, pHint_tot_sf, NA),
-                pHint_tot_sf_10m = ifelse(depth >= 8 , pHint_tot_sf, NA),
+                pHint_tot_sf_9m = ifelse(depth >= 8 , pHint_tot_sf, NA),
                 depth_discrete = case_when(
@@
       !is.na(pHint_tot_sf_7m) ~ 7,
-      !is.na(pHint_tot_sf_10m) ~ 9
+      !is.na(pHint_tot_sf_9m) ~ 9
       ),
@@
 
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_1m, pHint_tot_sf_3m, pHint_tot_sf_5m, pHint_tot_sf_7m, pHint_tot_sf_10m)
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_1m, pHint_tot_sf_3m, pHint_tot_sf_5m, pHint_tot_sf_7m, pHint_tot_sf_9m)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
 dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
-dySeries("pHint_tot_sf_10m", label = "pHT 10m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_9m", label = "pHT 9m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
 dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
@@
 rm(seafet_depth_xts)
+```
+
+```{r seaFET pH calculation sf_calc 9m, echo=FALSE, message= FALSE, warning=FALSE}
+####
+## calculation of the calibrated pH ##
+##       new sf_calc function       ##
+####
+seafet_calib_9m <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf_9m,  E0ext25 = d_all$E0ext25_sf_9m, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
+
+# bind new calibrated pH data to the seafet data set.
+names(seafet_calib_9m) <- c("pHint_tot_sf_calib9m", "pHext_tot_sf_calib9m")
+##########  Despike() ###########
+d_all <- d_all %>%   
+  dplyr::mutate(pHint_tot_sf_calib9m = oce::despike(seafet_calib_9m$pHint_tot_sf_calib9m, reference= "median", n=1, k=5001, replace="NA"),
+                pHextt_tot_sf_calib9m = oce::despike(seafet_calib_9m$pHextt_tot_sf_calib9m, reference= "median", n=1, k=5001, replace="NA")
+  )
+
+d_all <- d_all %>%
+  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA")) %>%
+  dplyr::mutate(pHint_tot_sf_calib9m = seafet_calib_9m$pHint_tot_sf_calib9m)
+
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_1m, pHint_tot_sf_3m, pHint_tot_sf_5m, pHint_tot_sf_7m, pHint_tot_sf_9m, pHint_tot_sf_calib9m)
+seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
+dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
+      dySeries("pHint_tot_sf_calib9m", label = "pH calib 9m", color =  "black", strokeWidth = 0, pointSize = 2 ) %>%
+dySeries("pHint_tot_sf_9m", label = "pHT 9m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_5m", label = "pHT 5m", color =  RColorBrewer::brewer.pal(3, "Dark2")[3], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_3m", label = "pHT 3m", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_1m", label = "pHT 1m", color =  RColorBrewer::brewer.pal(3, "Dark2")[5], strokeWidth = 0, pointSize = 1) %>%
+  dySeries("ph_s_sf_temp_insi", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 5 ) %>%
+
+dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
+  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="UTC"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
+  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="UTC"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
+    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="UTC"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
+  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
+  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#CCCCCC") %>%
+  dyLegend(show = "auto")   %>%
+  dyAxis("y2",valueRange = c(-3, 9)) %>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyRangeSelector(height = 30, dateWindow= c("2017-08-10 00:00:00","2021-01-20 23:00:00"))
+rm(seafet_depth_xts)
+
 ```
@@
   dplyr::select(montht, pHint_tot_sf, depth) %>%
-  dplyr::mutate(depth2 = as.factor(case_when(depth < 4 ~ '0-4', 
-                                             depth > 8~ '8-12',
-                                             TRUE ~ NA_real_))) %>% 
-  dplyr::filter(depth2 == '0-2' | depth2 == '8-12') %>% 
-  dplyr::group_by(depth2, montht)
-summary(aov(tmp$pHint_tot_sf ~ tmp$depth2 * tmp$montht))
+  dplyr::mutate(depth = as.factor(ifelse(depth == 1 | depth == 3, 2, depth))) %>% 
+  dplyr::filter(depth == 2 | depth == 10) %>% 
+  dplyr::group_by(depth, montht)
+summary(aov(tmp$pHint_tot_sf ~ tmp$depth * tmp$montht))
 
@@
 
- + To compare with pCO2/pCO2 measured in the Ferrybox seems therefore better to stick with pH_10m, that is at depths deeper than 8 m.
+ + To compare with pCO2/pCO2 measured in the Ferrybox seems therefore better to stick with pH_9m, that is at depths deeper than 8 m.
   + pCO2 would have the same behaviour as pH. For air-sea CO2 fluxes, one should use data from 0 to 4 m.
@@
   d_all %>%
-  dplyr::select(montht, sal_mix, temp_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
+  dplyr::select(montht, sal_mix, temp_mix, temp_insitu_11m, pHint_tot_sf_9m) %>% 
   group_by(montht) %>%
@@
 pH_sf <- d_all %>%
-  dplyr::select(datetime, sal_insitu_ctd_10m , temp_insitu_ctd_10m, pHint_tot_sf)%>%
-  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd_10m), !is.na(sal_insitu_ctd_10m)) %>%
+  dplyr::select(datetime, sal_insitu_ctd_9m , temp_insitu_ctd_9m, pHint_tot_sf)%>%
+  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd_9m), !is.na(sal_insitu_ctd_9m)) %>%
   dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
 
-pH_sf$pHint_tot_sf_temp_4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_10m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_10m, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+pH_sf$pHint_tot_sf_temp_4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_9m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_9m, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 
@@
 ```{r stratification, echo=FALSE, message= FALSE, warning=FALSE}
-# # we look at the distribution of data
-depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
+# we look at the distribution of data
+tmp <- d_all %>% 
+  dplyr::select(date, depth, pressure_insitu_ctd) %>% 
+  dplyr::mutate(month=month(d_all$date, label = TRUE)) %>% 
+  group_by(month)
+depth_labels <- c("0-2", "2-4", "4-6", "6-8", "8-12")
 # we look at salinity all depths
 tmp <- d_all %>% 
+  dplyr::mutate(depth_group = depth_group_pressure) %>% 
   dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
-  tidyr::drop_na() %>% 
-  dplyr::filter(depth_group != "NA") %>% 
   group_by(depth_group, montht)
@@
 print(p)
+
 summary(aov(tmp$sal_insitu_ctd ~ tmp$depth_group * tmp$montht))
@@
 tmp <- d_all %>% 
+  dplyr::mutate(depth_group = depth_group_pressure) %>% 
   dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
-  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
-                                      depth_group == '>8' ~ '8-12'))) %>% 
-  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
-  dplyr::group_by(depth_group2, montht)
+  dplyr::mutate(depth = as.factor(ifelse(depth_group == 1 | depth_group == 3, 2, depth_group))) %>% 
+  dplyr::filter(depth == 2 | depth == 10)
 tmp_delta <- tmp %>% 
-  group_by(depth_group2, montht) %>% 
+  group_by(depth, montht) %>% 
   dplyr::summarise(sal_med = median(sal_insitu_ctd, na.rm = TRUE)) %>% 
-  tidyr::pivot_wider(names_from = depth_group2, values_from = sal_med) %>% 
-  dplyr::rename(median0_4m = "0-4",
-                median8_12m = "8-12") %>% 
+  tidyr::pivot_wider(names_from = depth, values_from = sal_med) %>% 
+  dplyr::rename(median0_4m = "2",
+                median8_12m = "10") %>% 
   dplyr::mutate(sal_delta = median0_4m - median8_12m)
@@
 p <- tmp %>% 
-  ggplot(aes(x=depth_group2, y = sal_insitu_ctd)) +
+  ggplot(aes(x=as.factor(depth), y = sal_insitu_ctd)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
         panel.grid.minor.y = element_blank())
-print(sal_delta_plt)
 
@@
 tmp <- d_all %>% 
+  dplyr::mutate(depth_group = depth_group_pressure) %>% 
   dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
-  tidyr::drop_na() %>% 
-  dplyr::filter(depth_group != "NA") %>% 
   group_by(depth_group, montht)
@@
   labs(title = "Temperature vs depth", x = "Depth (m)", y= "Temperature") +
-  scale_x_discrete(labels = depth_labels) +
   facet_wrap(vars(montht), scale = "free_y")
 print(p)
-summary(aov(tmp$temp_insitu_ctd ~ tmp$depth_group * tmp$montht))
+
 # we look at temperature 0 to 4 m vs more than 8 m
 tmp <- d_all %>% 
+  dplyr::mutate(depth_group = depth_group_pressure) %>% 
   dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
-  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
-                                      depth_group == '>8' ~ '8-12'))) %>% 
-  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
-  dplyr::group_by(depth_group2, montht)
+  dplyr::mutate(depth = as.factor(ifelse(depth_group == 1 | depth_group == 3, 2, depth_group))) %>% 
+  dplyr::filter(depth == 2 | depth == 10) %>% 
+  group_by(depth, montht)
+summary(aov(tmp$temp_insitu_ctd ~ tmp$depth * tmp$montht))
+
 tmp_delta <- tmp %>% 
-  group_by(depth_group2, montht) %>% 
+  group_by(depth, montht) %>% 
   dplyr::summarise(temp_med = median(temp_insitu_ctd, na.rm = TRUE)) %>% 
-  tidyr::pivot_wider(names_from = depth_group2, values_from = temp_med) %>% 
-  dplyr::rename(median0_4m = "0-4",
-                median8_12m = "8-12") %>% 
+  tidyr::pivot_wider(names_from = depth, values_from = temp_med) %>% 
+  dplyr::rename(median0_4m = "2",
+                median8_12m = "10") %>% 
   dplyr::mutate(temp_delta = median0_4m - median8_12m)
@@
 
-# we look at temperature 0 to 4 m vs more than 8 m
 p <- tmp %>% 
-  ggplot(aes(x=depth_group2, y = temp_insitu_ctd)) +
+  ggplot(aes(x=as.factor(depth), y = temp_insitu_ctd)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
   scale_x_discrete(expand = c(0, 0)) +
-  scale_y_continuous("Temperature", limits = c(-1.3, 0.8), expand = c(0, 0)) +
+  scale_y_continuous("Temperature", limits = c(-3, 3), expand = c(0, 0)) +
   geom_col(fill="blue") +
   geom_hline(yintercept = 0) +
-  annotate("text", x = 1.5, y =0.6, label = substitute("T"["surface"] ~ "> T"["deep"])) +
-  annotate("text", x = 1.5, y = -0.6, label = substitute("T"["surface"] ~ "< T"["deep"])) +
+  annotate("text", x = 1.5, y = 2.5, label = substitute("T"["surface"] ~ "> T"["deep"])) +
+  annotate("text", x = 1.5, y = -2.5, label = substitute("T"["surface"] ~ "< T"["deep"])) +
   Mytheme(size_labs = 12) +
@@
         panel.grid.minor.y = element_blank())
-print(temp_delta_plt)
-# we look at density at all depths
-tmp <- d_all %>% 
-  dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth_group, pressure_insitu_ctd) %>%
-  tidyr::drop_na() %>% 
-  dplyr::filter(depth_group != "NA") %>% 
-  dplyr::mutate(density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = pressure_insitu_ctd)) %>% 
-  group_by(depth_group, montht)
-p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth_group), y = sal_insitu_ctd)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "Density vs depth", x = "Depth (m)", y= "Density") +
-  scale_x_discrete(labels = depth_labels) +
-  facet_wrap(vars(montht), scale = "free_y")
-print(p)
-summary(aov(tmp$density ~ tmp$depth_group * tmp$montht))
 
@@
 tmp <- d_all %>% 
-  dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
-  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
-                                      depth_group == '>8' ~ '8-12'))) %>% 
-  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
-  dplyr::group_by(depth_group2, montht)
+  dplyr::mutate(depth_group = depth_group_pressure) %>% 
+  dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth_group, pressure_insitu_ctd) %>%
+  dplyr::mutate(density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = pressure_insitu_ctd),
+                depth = as.factor(ifelse(depth_group == 1 | depth_group == 3, 2, depth_group))) %>% 
+  dplyr::filter(depth == 2 | depth == 10) %>% 
+  dplyr::select(montht, depth, density) %>% 
+  group_by(depth, montht) 
+summary(tmp)
+summary(aov(tmp$density ~ tmp$depth * tmp$montht))
 
 tmp_delta <- tmp %>% 
-  dplyr::select(montht, depth_group, density) %>% 
-  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
-                                      depth_group == '>8' ~ '8-12'))) %>% 
-  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
-  group_by(depth_group2, montht) %>% 
+  group_by(depth, montht) %>% 
   dplyr::summarise(den_med = median(density, na.rm = TRUE)) %>% 
-  tidyr::pivot_wider(names_from = depth_group2, values_from = den_med) %>% 
-  dplyr::rename(median0_4m = "0-4",
-                median8_12m = "8-12") %>% 
-  dplyr::mutate(temp_delta = median0_4m - median8_12m)
+  tidyr::pivot_wider(names_from = depth, values_from = den_med) %>% 
+  dplyr::rename(median0_4m = "2",
+                median8_12m = "10") %>% 
+  dplyr::mutate(den_delta = median0_4m - median8_12m)
 kable(tmp_delta, digits = 2, caption = "Median density with (median0_4m - median8_12m)")
@@
 p <- tmp %>% 
-  ggplot(aes(x=montht, y = density)) +
+  ggplot(aes(x=as.factor(depth), y = density)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
 * reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
-* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_10m)
+* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
 * sal_mix_interp: interpolated salinity sal_mix. It is used to have as many spec pH to display (some are during missing data)
@@
     - ph_s_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
-    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_10m si trous) + temp CTD 10m + sal CTD 10m (calib seaFET fonction 1)
+    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
     - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)

### 2021-12-13 awipev-CO2.Rmd
On the way to finalize seafet

--- 2021-12-13 awipev-CO2.Rmd
@@
 
+### add the depth into discrete df. In order to see where the seafet was.
+#discrete <- left_join(discrete, d_all%>%dplyr::select(closest_datetime,depth, depth_discrete),by="closest_datetime")
+discrete <- left_join(discrete, d_all%>%dplyr::select(closest_datetime,depth),by="closest_datetime")
+discrete <- discrete%>%dplyr::filter(discrete$datetime < "2021-07-01 00:00:00")
+
+#offset_xts <- select(discrete, closest_datetime, depth,depth_discrete, ph_s_sf_temp_insi)
+offset_xts <- select(discrete, closest_datetime, depth, ph_s_sf_temp_insi)
+offset_xts <- as.xts(offset_xts, order.by=offset_xts$closest_datetime)
+
+dygraph(offset_xts, main = "") %>%
+#dySeries("depth_discrete", drawPoints = TRUE, pointSize=3, strokeWidth = 1,label = "depth_discrete", color="black")%>%
+dySeries("depth", drawPoints = TRUE, pointSize=3, label = "depth", strokeWidth = 1,color="blue")%>%
+dySeries(axis="y2","ph_s_sf_temp_insi", drawPoints = TRUE, pointSize=4, label = "spectro", color="red")%>%
+    dyLegend(show = "follow")   %>%
+    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+dyOptions(
+    drawGrid = TRUE,
+    strokeWidth= 0,
+    drawPoints = TRUE,
+    useDataTimezone = TRUE,
+    digitsAfterDecimal = 4) %>%
+  dyRangeSelector(height = 30, dateWindow= c("2017-10-21 00:00:00", "2021-01-11 00:00:00"))
+
 ####
@@
 ####
-calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
+calib_spectro_all <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
 # put number of deployment 
-calib_spectro$deployment_sf <- d_all$deployment_sf
+calib_spectro_all$deployment_sf <- d_all$deployment_sf
 
 # make the mean of E0 by period of deployement
-calib_spectro <- group_by(calib_spectro, deployment_sf) %>%
+calib_spectro_all <- group_by(calib_spectro_all, deployment_sf) %>%
+  dplyr::summarise(E0int25 = mean(E0int25, na.rm = TRUE),
+            E0ext25 = mean(E0ext25, na.rm = TRUE) 
+            ) %>% 
+  dplyr::filter(!is.na(deployment_sf))
+names(calib_spectro_all) <- c("deployment_sf", "E0int25_sf", "E0ext25_sf")
+
+# add E0 mean to seaFET data per deployment
+d_all <-left_join(d_all, calib_spectro_all,by="deployment_sf" )
+
+```
+
+```{r seaFET pH calib sf_calib 10m, echo=FALSE, message= FALSE, warning=FALSE}
+###
+#creaate new dataframe and CALIB to take into consideration only seafet data at the same depth than spectro (9m)
+##
+####
+d_all_calib_depth <- d_all%>%
+#  dplyr::select(datetime, voltINT, voltEXT,ph_s_sf_temp_insi,sal_insitu_ctd_interp,temp_sf, depth_discrete,deployment_sf)%>%
+  dplyr::select(datetime, voltINT, voltEXT,ph_s_sf_temp_insi,sal_insitu_ctd_interp,temp_sf,depth, deployment_sf)%>%
+#  dplyr::filter(depth_discrete == 10)
+    dplyr::filter(depth > 8)
+
+calib_spectro_depth_10m <- sf_calib(calEint = d_all_calib_depth$voltINT, calEext = d_all_calib_depth$voltEXT, calpH = d_all_calib_depth$ph_s_sf_temp_insi, calT = d_all_calib_depth$temp_sf, calSal = d_all_calib_depth$sal_insitu_ctd_interp)
+# put number of deployment 
+calib_spectro_depth_10m$deployment_sf <- d_all_calib_depth$deployment_sf
+
+# make the mean of E0 by period of deployement
+calib_spectro_depth_10m <- group_by(calib_spectro_depth_10m, deployment_sf) %>%
   summarise(E0int25 = mean(E0int25, na.rm = TRUE),
             E0ext25 = mean(E0ext25, na.rm = TRUE) 
-            )
-names(calib_spectro) <- c("deployment_sf", "E0int25_sf", "E0ext25_sf")
+            ) %>% 
+  dplyr::filter(!is.na(deployment_sf))
+names(calib_spectro_depth_10m) <- c("deployment_sf", "E0int25_sf_10m", "E0ext25_sf_10m")
 
 # add E0 mean to seaFET data per deployment
-d_all <-left_join(d_all, calib_spectro,by="deployment_sf" )
-
+d_all <- dplyr::left_join(d_all, calib_spectro_depth_10m, by="deployment_sf") %>% 
+    dplyr::select(order(colnames(d_all)))
+```
+
+Below are the seafet calibration parameters using all data (irrespective of the depth of the seafet) and with the seafet data collected below 8 m.
+They are very close but we nevertheless use the calibration data below 8 m (easier to explain in the manuscript).
+
+```{r seaFET pH plot sf_calib , echo=FALSE, message= FALSE, warning=FALSE}
 #### plot
-kk <- tidyr::pivot_longer(calib_spectro, cols = starts_with("E0"), names_to = "variable", values_to = "value")
+# kk <- tidyr::pivot_longer(d_all, cols = starts_with("E0"), names_to = "variable", values_to = "value")
+# p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
+#   facet_grid(variable ~ ., scales="fixed") + theme_bw() +
+#   scale_colour_discrete(guide="none")
+
+kk <- d_all %>% 
+  dplyr::select(deployment_sf, tidyr::starts_with("E0")) %>% 
+  tidyr::pivot_longer(cols = starts_with("E0"), names_to = "variable", values_to = "value")
 p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
-  facet_grid(variable ~ ., scales="free_y") + theme_bw() +
+  facet_grid(variable ~ ., scales="fixed") + theme_bw() +
   scale_colour_discrete(guide="none")
 print(p_calib)
+
+calib_spectro <- cbind(calib_spectro_all, calib_spectro_depth_10m)
+kbl(calib_spectro)%>%
+    kable_paper() %>% 
+    kable_styling(fixed_thead = T)
 ```
@@
 ####
-## calculation of the calibrated pH ##
+## calculation of the calibrated pH with all data irrespective of the depth of the REMOS ##
 ##       new sf_calc function       ##
@@
       !is.na(pHint_tot_sf_7m) ~ 7,
-      !is.na(pHint_tot_sf_10m) ~ 9
+      !is.na(pHint_tot_sf_10m) ~ 10
       ),
@@
 rm(seafet_depth_xts)
+```
+
+```{r seaFET pH calculation sf_calc 10m, echo=FALSE, message= FALSE, warning=FALSE}
+####
+## calculation of the calibrated pH using spec pH when seafet is at a depth > 8 m##
+##       new sf_calc function       ##
+####
+seafet_calib_10m <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf_10m,  E0ext25 = d_all$E0ext25_sf_10m, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
+
+# bind new calibrated pH data to the seafet data set.
+names(seafet_calib_10m) <- c("pHint_tot_sf_calib10m", "pHext_tot_sf_calib10m")
+##########  Despike() ###########
+d_all <- d_all %>%   
+  dplyr::mutate(pHint_tot_sf_calib10m = oce::despike(seafet_calib_10m$pHint_tot_sf_calib10m, reference= "median", n=1, k=5001, replace="NA"),
+                pHextt_tot_sf_calib10m = oce::despike(seafet_calib_9m$pHextt_tot_sf_calib10m, reference= "median", n=1, k=5001, replace="NA")
+  )
+
+d_all <- d_all %>%
+  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA")) %>%
+  dplyr::mutate(pHint_tot_sf_calib10m = seafet_calib_10m$pHint_tot_sf_calib10m)
+
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_1m, pHint_tot_sf_3m, pHint_tot_sf_5m, pHint_tot_sf_7m, pHint_tot_sf_10m, pHint_tot_sf_calib10m)
+seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
+dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
+      dySeries("pHint_tot_sf_calib10m", label = "pH calib 9m", color =  "black", strokeWidth = 0, pointSize = 2 ) %>%
+dySeries("pHint_tot_sf_10m", label = "pHT 10m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_5m", label = "pHT 5m", color =  RColorBrewer::brewer.pal(3, "Dark2")[3], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_3m", label = "pHT 3m", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_1m", label = "pHT 1m", color =  RColorBrewer::brewer.pal(3, "Dark2")[5], strokeWidth = 0, pointSize = 1) %>%
+  dySeries("ph_s_sf_temp_insi", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 5 ) %>%
+
+dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
+  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="UTC"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
+  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="UTC"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
+    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="UTC"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
+  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
+  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
+  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#CCCCCC") %>%
+  dyLegend(show = "auto")   %>%
+  dyAxis("y2",valueRange = c(-3, 9)) %>%
+  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
+  dyRangeSelector(height = 30, dateWindow= c("2017-08-10 00:00:00","2021-01-20 23:00:00"))
+rm(seafet_depth_xts)
+
 ```

### 2021-12-22 awipev-CO2.Rmd
Moving forward with pH seafet

@@
 title: "Carbonate chemistry at Ny-Ålesund" 
-author: "Jean-Pierre Gattuso and Samir Alliouane"
+author: "Jean-Pierre Gattuso and Samir Alliouane and Bernard Gentili"
 date: '`r format(Sys.Date(), "%d %B %Y")`'
@@
 print(p$plot)
-# 
+rm(fit, p)
 ```
@@
 
-```{r seaFET calibration sf_calib, echo=FALSE, message= FALSE, warning=FALSE, out.width= "60%"}
+```{r seaFET calibration preparation, echo=FALSE, message= FALSE, warning=FALSE, out.width= "60%"}
 sfinterv <- as.POSIXct(c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00"))
@@
   dyRangeSelector(height = 30, dateWindow= c("2017-10-21 00:00:00", "2021-01-11 00:00:00"))
-
+```
+
+```{r seaFET pH sf_calib , echo=FALSE, message= FALSE, warning=FALSE}
 ####
-## calculation of E0INT25/E0EXT25 irrespective of the depth at which the seafet is (all data used) ##
-##     new sf_calib function      ##
-####
+## calculation of E0INT25/E0EXT25 irrespective of the depth at which the seafet is (all data used)
+###
 calib_spectro_all <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
@@
 # add E0 mean to seaFET data per deployment
-d_all <-left_join(d_all, calib_spectro_all,by="deployment_sf" )
-
-```
-
-```{r seaFET pH calib sf_calib 10m, echo=FALSE, message= FALSE, warning=FALSE}
+d_all <-left_join(d_all, calib_spectro_all, by="deployment_sf" )
+
 ###
-#creaate new dataframe and CALIB to take into consideration only seafet data at the same depth than spectro (9m)
-##
-####
-d_all_calib_depth <- d_all%>%
+## calculation of E0INT25/E0EXT25 only using seafet data deeper than 8m
+###
+d_all_calib_depth <- d_all %>%
 #  dplyr::select(datetime, voltINT, voltEXT,ph_s_sf_temp_insi,sal_insitu_ctd_interp,temp_sf, depth_discrete,deployment_sf)%>%
@@
 # add E0 mean to seaFET data per deployment
-d_all <- dplyr::left_join(d_all, calib_spectro_depth_10m, by="deployment_sf") %>% 
-    dplyr::select(order(colnames(d_all)))
+d_all <- dplyr::left_join(d_all, calib_spectro_depth_10m, by="deployment_sf")
+d_all <- dplyr::select(d_all, order(colnames(d_all)))
 ```
@@
 ### **seaFET pHT calibrated**
-Final calibrated seaFET pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
+Final calibrated seaFET pHT data (small green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
 
@@
 
-```{r seaFET pH calculation sf_calc, echo=FALSE, message= FALSE, warning=FALSE}
+```{r seaFET pH calculation sf_calc all, echo=FALSE, message= FALSE, warning=FALSE}
 ####
@@
   dplyr::mutate(pHint_tot_sf_calib10m = oce::despike(seafet_calib_10m$pHint_tot_sf_calib10m, reference= "median", n=1, k=5001, replace="NA"),
-                pHextt_tot_sf_calib10m = oce::despike(seafet_calib_9m$pHextt_tot_sf_calib10m, reference= "median", n=1, k=5001, replace="NA")
+                pHext_tot_sf_calib10m = oce::despike(seafet_calib_10m$pHext_tot_sf_calib10m, reference= "median", n=1, k=5001, replace="NA")
   )
@@
 
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_1m, pHint_tot_sf_3m, pHint_tot_sf_5m, pHint_tot_sf_7m, pHint_tot_sf_10m, pHint_tot_sf_calib10m)
+#seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_1m, pHint_tot_sf_3m, pHint_tot_sf_5m, pHint_tot_sf_7m, pHint_tot_sf_10m, pHint_tot_sf_calib10m)
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_calib10m)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
-dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
-      dySeries("pHint_tot_sf_calib10m", label = "pH calib 9m", color =  "black", strokeWidth = 0, pointSize = 2 ) %>%
-dySeries("pHint_tot_sf_10m", label = "pHT 10m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_5m", label = "pHT 5m", color =  RColorBrewer::brewer.pal(3, "Dark2")[3], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_3m", label = "pHT 3m", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_1m", label = "pHT 1m", color =  RColorBrewer::brewer.pal(3, "Dark2")[5], strokeWidth = 0, pointSize = 1) %>%
+dygraph(seafet_depth_xts, group = "depth", main="Spec pH and calibrated seaFET pH at 10 m", ylab="pHT") %>%
+dySeries("pHint_tot_sf_calib10m", label = "pH calib 10m", color =  "black", strokeWidth = 0, pointSize = 1) %>%
+#dySeries("pHint_tot_sf_10m", label = "pHT 10m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
+#dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
+#dySeries("pHint_tot_sf_5m", label = "pHT 5m", color =  RColorBrewer::brewer.pal(3, "Dark2")[3], strokeWidth = 0, pointSize = 1) %>%
+#dySeries("pHint_tot_sf_3m", label = "pHT 3m", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 1) %>%
+#dySeries("pHint_tot_sf_1m", label = "pHT 1m", color =  RColorBrewer::brewer.pal(3, "Dark2")[5], strokeWidth = 0, pointSize = 1) %>%
 dySeries("ph_s_sf_temp_insi", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 5 ) %>%
-
 dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
@@
 rm(seafet_depth_xts)
-
 ```
@@
 ph_sf <- d_all%>%
-  dplyr::select(datetime, ph_s_sf_temp_insi,pHint_tot_sf,pHext_tot_sf)%>%
-    dplyr::mutate( diff_spec_sf = ph_s_sf_temp_insi - pHint_tot_sf,
-                   diff_sf_int_ext = pHint_tot_sf -pHext_tot_sf )
+  dplyr::select(datetime, ph_s_sf_temp_insi, pHint_tot_sf_calib10m)%>%
+    dplyr::mutate( diff_spec_sf = ph_s_sf_temp_insi - pHint_tot_sf_calib10m)
 average_offset <- mean(ph_sf$diff_spec_sf, na.rm=TRUE, digits=4)
@@
 ```{r seaFET quality control pH 2, echo=FALSE, warning = FALSE, message = FALSE, out.width='100%'}
-                                                                                                                                                                                       ## INT -EXT
-delta_xts <- dplyr::select(ph_sf,datetime, diff_sf_int_ext, pHext_tot_sf, pHint_tot_sf)
-delta_xts <- as.xts(delta_xts, order.by=delta_xts$datetime)
-dygraph(delta_xts, main = "delta pHINT - pH EXT") %>%
-  dySeries(axis ="y2","pHext_tot_sf", drawPoints = TRUE, pointSize=3, label = "pH EXT", color="red")%>%
-dySeries(axis ="y2","pHint_tot_sf", drawPoints = TRUE, pointSize=2, label = "pH INT", color="blue")%>%
-  dySeries( "diff_sf_int_ext", drawPoints = TRUE, pointSize=2, label = "Delta", color="grey")%>%
-    dyLegend(show = "follow")   %>%
-      dyLimit(0,strokePattern = "solid", color = "black") %>% 
- dyAxis("y",valueRange = c(-0.3,0.3))%>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-dyOptions(
-    drawGrid = TRUE,
-    strokeWidth= 0,
-    drawPoints = TRUE,
-    useDataTimezone = TRUE,
-    digitsAfterDecimal = 4) %>%
-  dyRangeSelector(height = 30, dateWindow= c("2017-10-21 00:00:00", "2021-01-11 00:00:00"))
-
+# # COMMENTED BECAUSE INT-EXT NOT NEEDED
+# delta_xts <- dplyr::select(ph_sf, datetime, diff_sf_int_ext, pHext_tot_sf, pHint_tot_sf)
+# delta_xts <- as.xts(delta_xts, order.by=delta_xts$datetime)
+# dygraph(delta_xts, main = "delta pHINT - pH EXT") %>%
+#   dySeries(axis ="y2","pHext_tot_sf", drawPoints = TRUE, pointSize=3, label = "pH EXT", color="red")%>%
+# dySeries(axis ="y2","pHint_tot_sf", drawPoints = TRUE, pointSize=2, label = "pH INT", color="blue")%>%
+#   dySeries( "diff_sf_int_ext", drawPoints = TRUE, pointSize=2, label = "Delta", color="grey")%>%
+#     dyLegend(show = "follow")   %>%
+#       dyLimit(0,strokePattern = "solid", color = "black") %>% 
+#  dyAxis("y",valueRange = c(-0.3,0.3))%>%
+#     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+# dyOptions(
+#     drawGrid = TRUE,
+#     strokeWidth= 0,
+#     drawPoints = TRUE,
+#     useDataTimezone = TRUE,
+#     digitsAfterDecimal = 4) %>%
+#   dyRangeSelector(height = 30, dateWindow= c("2017-10-21 00:00:00", "2021-01-11 00:00:00"))
 ```

### 2021-12-22 awipev-CO2.Rmd
seafet pH sorted out!

@@
 rm(d_hour)
-
 ```
@@
                 si = Si / (density_fb/1000)
-  )
+  ) %>% 
+  dplyr::select(-PO4, -NH4, -NO3NO2, -NO3, -Si)
 ```
@@
 ```{r seaFET pH sf_calib , echo=FALSE, message= FALSE, warning=FALSE}
-####
 ## calculation of E0INT25/E0EXT25 irrespective of the depth at which the seafet is (all data used)
-###
 calib_spectro_all <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
@@
 
-###
 ## calculation of E0INT25/E0EXT25 only using seafet data deeper than 8m
-###
-d_all_calib_depth <- d_all %>%
+d_all_calib_10m <- d_all %>%
 #  dplyr::select(datetime, voltINT, voltEXT,ph_s_sf_temp_insi,sal_insitu_ctd_interp,temp_sf, depth_discrete,deployment_sf)%>%
@@
 
-calib_spectro_depth_10m <- sf_calib(calEint = d_all_calib_depth$voltINT, calEext = d_all_calib_depth$voltEXT, calpH = d_all_calib_depth$ph_s_sf_temp_insi, calT = d_all_calib_depth$temp_sf, calSal = d_all_calib_depth$sal_insitu_ctd_interp)
+calib_spectro_10m <- sf_calib(calEint = d_all_calib_10m$voltINT, calEext = d_all_calib_10m$voltEXT, calpH = d_all_calib_10m$ph_s_sf_temp_insi, calT = d_all_calib_10m$temp_sf, calSal = d_all_calib_10m$sal_insitu_ctd_interp)
 # put number of deployment 
-calib_spectro_depth_10m$deployment_sf <- d_all_calib_depth$deployment_sf
+calib_spectro_10m$deployment_sf <- d_all_calib_10m$deployment_sf
 
 # make the mean of E0 by period of deployement
-calib_spectro_depth_10m <- group_by(calib_spectro_depth_10m, deployment_sf) %>%
+calib_spectro_10m <- group_by(calib_spectro_10m, deployment_sf) %>%
   summarise(E0int25 = mean(E0int25, na.rm = TRUE),
@@
   dplyr::filter(!is.na(deployment_sf))
-names(calib_spectro_depth_10m) <- c("deployment_sf", "E0int25_sf_10m", "E0ext25_sf_10m")
+names(calib_spectro_10m) <- c("deployment_sf", "E0int25_sf_10m", "E0ext25_sf_10m")
 
 # add E0 mean to seaFET data per deployment
-d_all <- dplyr::left_join(d_all, calib_spectro_depth_10m, by="deployment_sf")
-d_all <- dplyr::select(d_all, order(colnames(d_all)))
+d_all <- dplyr::left_join(d_all, calib_spectro_10m, by="deployment_sf")
+d_all <- d_all %>% 
+  dplyr::select(order(colnames(d_all)))
 ```
@@
 
-calib_spectro <- cbind(calib_spectro_all, calib_spectro_depth_10m)
+calib_spectro <- cbind(calib_spectro_all, calib_spectro_10m)
 kbl(calib_spectro)%>%
@@
 ```{r seaFET pH calculation sf_calc all, echo=FALSE, message= FALSE, warning=FALSE}
-####
-## calculation of the calibrated pH with all data irrespective of the depth of the REMOS ##
-##       new sf_calc function       ##
-####
-seafet_calib <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
-
+#### calculation of the calibrated pH with all data irrespective of the depth of the REMOS ####
+seafet_calib_all <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
 # bind new calibrated pH data to the seafet data set.
-names(seafet_calib) <- c("pHint_tot_sf", "pHext_tot_sf")
-##########  Despike() ###########
+names(seafet_calib_all) <- c("pHint_tot_sf_all", "pHext_tot_sf_all")
+# Despike
 d_all <- d_all %>%   
-  dplyr::mutate(pHint_tot_sf = oce::despike(seafet_calib$pHint_tot_sf, reference= "median", n=1, k=5001, replace="NA"),
-                pHext_tot_sf = oce::despike(seafet_calib$pHext_tot_sf, reference= "median", n=1, k=5001, replace="NA")
-  )
-
-# pH seaFET Final
-# add despike with n=2 k = 5762 to the final ph corrected data
-# despike me semble inutile, faire plutôt un simple des outliers qui, vérification faite, n'est même pas nécessaire
-# Il faut par contre créér une nouvelle variable avec pH deeper than 8 m, called *_10m for consistency with salinity and temp
+  dplyr::mutate(pHint_tot_sf_all = oce::despike(seafet_calib_all$pHint_tot_sf_all, reference= "median", n=1, k=5001, replace="NA"),
+                pHext_tot_sf_all = oce::despike(seafet_calib_all$pHext_tot_sf_all, reference= "median", n=1, k=5001, replace="NA")
+  )
+# split by depth
 d_all <- d_all %>%
-  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA")) %>%
-  dplyr::mutate(pHint_tot_sf = seafet_calib$pHint_tot_sf) %>%
-  dplyr::mutate(pHint_tot_sf_1m = ifelse(depth > 0 & depth < 2, pHint_tot_sf, NA),
-                pHint_tot_sf_3m = ifelse(depth >= 2 & depth < 4, pHint_tot_sf, NA),
-                pHint_tot_sf_5m = ifelse(depth >= 4 & depth < 6, pHint_tot_sf, NA),
-                pHint_tot_sf_7m = ifelse(depth >= 6 & depth < 8, pHint_tot_sf, NA),
-                pHint_tot_sf_10m = ifelse(depth >= 8 , pHint_tot_sf, NA),
+  dplyr::mutate(pHint_tot_sf_all_1m = ifelse(depth > 0 & depth < 2, pHint_tot_sf_all, NA),
+                pHint_tot_sf_all_3m = ifelse(depth >= 2 & depth < 4, pHint_tot_sf_all, NA),
+                pHint_tot_sf_all_5m = ifelse(depth >= 4 & depth < 6, pHint_tot_sf_all, NA),
+                pHint_tot_sf_all_7m = ifelse(depth >= 6 & depth < 8, pHint_tot_sf_all, NA),
+                pHint_tot_sf_all_10m = ifelse(depth >= 8 , pHint_tot_sf_all, NA),
                 depth_discrete = case_when(
-      !is.na(pHint_tot_sf_1m) ~ 1,
-      !is.na(pHint_tot_sf_3m) ~ 3,
-      !is.na(pHint_tot_sf_5m) ~ 5,
-      !is.na(pHint_tot_sf_7m) ~ 7,
-      !is.na(pHint_tot_sf_10m) ~ 10
+                  !is.na(pHint_tot_sf_all_1m) ~ 1,
+                  !is.na(pHint_tot_sf_all_3m) ~ 3,
+                  !is.na(pHint_tot_sf_all_5m) ~ 5,
+                  !is.na(pHint_tot_sf_all_7m) ~ 7,
+                  !is.na(pHint_tot_sf_all_10m) ~ 10
                   ),
@@
                 )
-
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_1m, pHint_tot_sf_3m, pHint_tot_sf_5m, pHint_tot_sf_7m, pHint_tot_sf_10m)
+d_all <- d_all %>% 
+  dplyr::select(order(colnames(d_all)))
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_all_1m, pHint_tot_sf_all_3m, pHint_tot_sf_all_5m, pHint_tot_sf_all_7m, pHint_tot_sf_all_10m)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
 dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
-dySeries("pHint_tot_sf_10m", label = "pHT 10m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_5m", label = "pHT 5m", color =  RColorBrewer::brewer.pal(3, "Dark2")[3], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_3m", label = "pHT 3m", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_1m", label = "pHT 1m", color =  RColorBrewer::brewer.pal(3, "Dark2")[5], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_all_10m", label = "pHT 10m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_all_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_all_5m", label = "pHT 5m", color =  RColorBrewer::brewer.pal(3, "Dark2")[3], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_all_3m", label = "pHT 3m", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_all_1m", label = "pHT 1m", color =  RColorBrewer::brewer.pal(3, "Dark2")[5], strokeWidth = 0, pointSize = 1) %>%
   dySeries("ph_s_sf_temp_insi", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 5 ) %>%
@@
 ```{r seaFET pH calculation sf_calc 10m, echo=FALSE, message= FALSE, warning=FALSE}
-####
-## calculation of the calibrated pH using spec pH when seafet is at a depth > 8 m##
-##       new sf_calc function       ##
-####
+#### calculation of the calibrated pH using spec pH when seafet is at a depth > 8 m# ####
 seafet_calib_10m <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf_10m, E0ext25 = d_all$E0ext25_sf_10m, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
@@
 # bind new calibrated pH data to the seafet data set.
-names(seafet_calib_10m) <- c("pHint_tot_sf_calib10m", "pHext_tot_sf_calib10m")
+names(seafet_calib_10m) <- c("pHint_tot_sf_10m", "pHext_tot_sf_10m")
 ##########  Despike() ###########
 d_all <- d_all %>%   
-  dplyr::mutate(pHint_tot_sf_calib10m = oce::despike(seafet_calib_10m$pHint_tot_sf_calib10m, reference= "median", n=1, k=5001, replace="NA"),
-                pHext_tot_sf_calib10m = oce::despike(seafet_calib_10m$pHext_tot_sf_calib10m, reference= "median", n=1, k=5001, replace="NA")
-  )
-
+  dplyr::mutate(pHint_tot_sf_10m = oce::despike(seafet_calib_10m$pHint_tot_sf_10m, reference= "median", n=1, k=5001, replace="NA"),
+                pHext_tot_sf_10m = oce::despike(seafet_calib_10m$pHint_tot_sf_10m, reference= "median", n=1, k=5001, replace="NA")
+  )
+
+# split by depth
 d_all <- d_all %>%
-  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA")) %>%
-  dplyr::mutate(pHint_tot_sf_calib10m = seafet_calib_10m$pHint_tot_sf_calib10m)
-
-#seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_1m, pHint_tot_sf_3m, pHint_tot_sf_5m, pHint_tot_sf_7m, pHint_tot_sf_10m, pHint_tot_sf_calib10m)
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_calib10m)
+  dplyr::mutate(pHint_tot_sf_10m_1m = ifelse(depth > 0 & depth < 2, pHint_tot_sf_10m, NA),
+                pHint_tot_sf_10m_3m = ifelse(depth >= 2 & depth < 4, pHint_tot_sf_10m, NA),
+                pHint_tot_sf_10m_5m = ifelse(depth >= 4 & depth < 6, pHint_tot_sf_10m, NA),
+                pHint_tot_sf_10m_7m = ifelse(depth >= 6 & depth < 8, pHint_tot_sf_10m, NA),
+                pHint_tot_sf_10m_10m = ifelse(depth >= 8 , pHint_tot_sf_10m, NA),
+                depth_discrete = case_when(
+                  !is.na(pHint_tot_sf_10m_1m) ~ 1,
+                  !is.na(pHint_tot_sf_10m_3m) ~ 3,
+                  !is.na(pHint_tot_sf_10m_5m) ~ 5,
+                  !is.na(pHint_tot_sf_10m_7m) ~ 7,
+                  !is.na(pHint_tot_sf_10m_10m) ~ 10
+                  ),
+                depth_discrete = as.factor(depth_discrete)
+                )
+d_all <- d_all %>% 
+  dplyr::select(order(colnames(d_all)))
+
+# d_all <- d_all %>%
+#   #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA")) %>%
+#   dplyr::mutate(pHint_tot_sf_calib_10m = seafet_calib_10m$pHint_tot_sf_calib_10m)
+
+seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_10m)
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
 dygraph(seafet_depth_xts, group = "depth", main="Spec pH and calibrated seaFET pH at 10 m", ylab="pHT") %>%
-dySeries("pHint_tot_sf_calib10m", label = "pH calib 10m", color =  "black", strokeWidth = 0, pointSize = 1) %>%
-#dySeries("pHint_tot_sf_10m", label = "pHT 10m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
-#dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
-#dySeries("pHint_tot_sf_5m", label = "pHT 5m", color =  RColorBrewer::brewer.pal(3, "Dark2")[3], strokeWidth = 0, pointSize = 1) %>%
-#dySeries("pHint_tot_sf_3m", label = "pHT 3m", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 1) %>%
-#dySeries("pHint_tot_sf_1m", label = "pHT 1m", color =  RColorBrewer::brewer.pal(3, "Dark2")[5], strokeWidth = 0, pointSize = 1) %>%
+dySeries("pHint_tot_sf_10m", label = "pH calib 10m", color =  "black", strokeWidth = 0, pointSize = 1) %>%
 dySeries("ph_s_sf_temp_insi", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 5 ) %>%
@@
 ph_sf <- d_all%>%
-  dplyr::select(datetime, ph_s_sf_temp_insi, pHint_tot_sf_calib10m)%>%
-    dplyr::mutate( diff_spec_sf = ph_s_sf_temp_insi - pHint_tot_sf_calib10m)
+  dplyr::select(datetime, ph_s_sf_temp_insi, pHint_tot_sf_10m) %>%
+  dplyr::mutate(diff_spec_sf = ph_s_sf_temp_insi - pHint_tot_sf_10m)
 average_offset <- mean(ph_sf$diff_spec_sf, na.rm=TRUE, digits=4)
@@
 
-- pH INT - pH EXT was plotted here.
+#- pH INT - pH EXT was plotted here.
 
@@
 
+From now on, one uses seaFET pH from the internal electrode calibrated with spec pH and seaFET data when the REMOS was below 8 m (pHint_tot_sf_10m).
+This unique pH variable is called pHint_tot_sf.
+All other pH variables are cleaned up
+
+```{r seafet clean up, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+d_all <- d_all %>%
+  dplyr::rename(
+    pHint_tot_sf = pHint_tot_sf_10m,
+    pHint_tot_sf_10m = pHint_tot_sf_10m_10m,
+    pHint_tot_sf_1m = pHint_tot_sf_10m_1m,
+    pHint_tot_sf_3m = pHint_tot_sf_10m_3m,
+    pHint_tot_sf_5m = pHint_tot_sf_10m_5m,
+    pHint_tot_sf_7m = pHint_tot_sf_10m_7m
+  ) %>% 
+    dplyr::select(-starts_with(c(
+    "pHint_tot_sf_", "pHext_", "pHint_tot_sf_all"
+  )))
+
+```
 ### **seaFET pH profiles**

### 2021-12-22 awipev-CO2 (original).Rmd
dunno

--- 2021-12-13 awipev-CO2.Rmd
@@
   dplyr::mutate(datetime = dmy_hm(sampling_date, tz="UTC"),
-                measure_date = dmy(measure_date, tz="UTC"),
+                measure_date = ymd(measure_date, tz="UTC"),
                 date = as.Date(datetime)) %>% 
@@
 d <- d %>%
-  dplyr::filter(location_flag == 0) %>% 
-# below we change the time of 2 discrete samplings during period 1 of seafet deployment
-# This is to enable calibration when the REMOS was at 9 m depth
-  dplyr::mutate(datetime = case_when(datetime == as.POSIXct("2017-08-24 13:30:00") ~ as.POSIXct("2017-08-24 19:00:00"),
-                                     datetime == as.POSIXct("2017-11-28 09:15:00") ~ as.POSIXct("2017-11-28 13:00:00"),
-                   TRUE ~ datetime))
+  dplyr::filter(location_flag == 0)
 
@@
 
-Only 5 spectrophotometric pH which could be used for calibration when seaFET at > 8 m: 2018-11-16, 2019-04-17, 2019-10-11, 2020-01-27.
-All deployment meriods are covered but we had to alter the sampling time of:
-
-* 2017-08-24 14:00 to 2017-08-24 19:00 (5 h later)
-* 2017-11-28 09:00 to 2017-11-28 13:00 (4 h later)
-
-EO is calculated making a mean of several E0 that come from one deployment period (sensor in the water for several months).
+Spectrophotometric pH which could be used for calibration: 2017-08-24, 2017-09-28, 2019-09-13 x 2.
+Spectrophotometric pH which could not be used for calibration : 2018-12-14, 2019-01-18.
+
+We decided to change the calculation of E0.
+Before E0 was calculated for each pH spectro measurements.
+Now, EO is calculated making a mean of several E0 that come from one deployment period (sensor in the water for several months).
 
@@
 ```{r seaFET calibration sf_calib, echo=FALSE, message= FALSE, warning=FALSE, out.width= "60%"}
+
+# # We decided to calibrate pH data within each pH spectro measurement.
+# # Thus, each pH spectro is taken as one calibration periode. 
+# # We calculate here the day between 2 pH spectro in order to have the start/end of one deployment period.
+# sfPeriod <- d_all%>%
+#   dplyr::select(datetime, ph_s_sf_temp_insi)%>%
+#   dplyr::filter(!is.na(ph_s_sf_temp_insi))
+# # Remove pH spectro that not allow a calibration because of missing calibration value (voltINT, Sal or Temp insi)
+# sfPeriod <- sfPeriod%>%
+# dplyr::filter(datetime != "2018-04-16 07:00:00" & datetime != "2018-12-14 09:00:00" & datetime != "2019-01-18 09:00:00")
+# 
+# sfPeriod <-  sfPeriod %>%
+#   dplyr::arrange(datetime) %>%
+#   dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(sfPeriod)])/2* 3600)))%>%
+#   dplyr::mutate(sf_interval = datetime + middle[2:nrow(sfPeriod)])
+# 
+# #put interval in a list with the start date of seaFET measurements
+# sfinterv <- c( as_datetime("2017-08-24 13:00:00"), sfPeriod[,4])
+# #Change period sfinterv[5]. make the end of this period longer until 2018-03-21 23:59:00 
+# # This is needed in order to take in consideration pH from March 2018 with a calibration E0 lower (-1.4) than the next period (-0.38).
+# sfinterv[5] <- ymd_hms("2018-03-22 23:59:59")
+# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
+# # sfinterv[6] <- ymd_hms("2018-04-24 18:00:00")
+# #  #Change period sfinterv[6]. Because seafet was off and on on the 2018-04-24 19:00:00
+# # sfinterv[14] <- ymd_hms("2019-01-29 16:00:00")
+# 
+# #sfinterv <-sort(unlist(sfinterv, use.names=FALSE))
+# # set deployment period between 2 spectro measurements.
+
+# # add here the new periods sfinterv[..]
+# d_all <- d_all %>%
+#   dplyr::mutate(deployment_sf = ifelse(datetime >= sfinterv[1] & datetime <= sfinterv[2], 01, 
+#                                 ifelse(datetime >= sfinterv[2] & datetime <= sfinterv[3], 02, 
+#                                 ifelse(datetime >= sfinterv[3] & datetime <= sfinterv[4], 03, 
+#                                 ifelse(datetime >= sfinterv[4] & datetime <= sfinterv[5], 04,
+#                                 ifelse(datetime >= sfinterv[5] & datetime <= sfinterv[6], 05,
+#                                 ifelse(datetime >= sfinterv[6] & datetime <= sfinterv[7], 06,
+#                                 ifelse(datetime >= sfinterv[7] & datetime <= sfinterv[8], 07,
+#                                 ifelse(datetime >= sfinterv[8] & datetime <= sfinterv[9], 08,
+#                                 ifelse(datetime >= sfinterv[9] & datetime <= sfinterv[10], 09,
+#                                 ifelse(datetime >= sfinterv[10] & datetime <= sfinterv[11], 10,
+#                                 ifelse(datetime >= sfinterv[11] & datetime <= sfinterv[12], 11,
+#                                  ifelse(datetime >= sfinterv[12] & datetime <= sfinterv[13], 12,
+#                                  ifelse(datetime >= sfinterv[13] & datetime <= sfinterv[14], 13,
+#                                  ifelse(datetime >= sfinterv[14] & datetime <= sfinterv[15], 14,
+#                                  ifelse(datetime >= sfinterv[15] & datetime <= sfinterv[16], 15,
+#                                  ifelse(datetime >= sfinterv[16] & datetime <= sfinterv[17], 16,
+#                                  ifelse(datetime >= sfinterv[17] & datetime <= sfinterv[18], 17,
+#                                 ifelse(datetime >= sfinterv[18] & datetime <= sfinterv[19], 18,
+#                                 ifelse(datetime >= sfinterv[19] & datetime <= sfinterv[20], 19,
+#                                 ifelse(datetime >= sfinterv[20] & datetime <= sfinterv[21], 20,
+#                                 ifelse(datetime >= sfinterv[21] & datetime <= sfinterv[22], 21,
+#                                 #ifelse(datetime >= sfinterv[22] & datetime <= sfinterv[23], 22,
+#                                 #ifelse(datetime >= sfinterv[23] & datetime <= sfinterv[24], 23,
+#                                 #ifelse(datetime >= sfinterv[24] & datetime <= sfinterv[25], 24,
+#                                 #ifelse(datetime >= sfinterv[25] & datetime <= sfinterv[26], 25,
+#                                 ifelse(datetime >= sfinterv[22] , 22,NA )))))))))))))))))))))))
+
+# set deployment period when seaFET is in/out of water
 sfinterv <- as.POSIXct(c("2017-08-24 12:00:00","2018-04-17 12:00:00", "2019-09-02 12:00:00"))
@@
                                 ifelse(datetime >= sfinterv[3], 03, NA ))))
-# dygraph to check seafet data
-# pH_xts <-
+
+# pco2_contros_xts <-
 #   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_insi)
-# pH_xts <-
-#   as.xts(pH_xts, order.by = d_all$datetime)
-# dygraph(pH_xts,
+# pco2_contros_xts <-
+#   as.xts(pco2_contros_xts, order.by = d_all$datetime)
+# dygraph(pco2_contros_xts,
 #         group = "awipev",
-#         main = "pH",
-#         ylab = "pH") %>%
+#         main = "<i>p</i>CO<sub>2</sub>",
+#         ylab = "<i>p</i>CO<sub>2</sub>") %>%
 #   dySeries(
@@
 # If the pH spectro is too far from a needed value, we decided to skip it for the calibration.
-
+# we highlighted 7 pH spectro that dont match one of these parameters : 2017-08-24 14:00:00 - 2017-09-28 13:00:00 - 2018-04-16 07:00:00 - 2018-12-14 09:00:00 - 2019-01-18 09:00:00 - 2019-09-13 08:00:00 - 2019-09-13 13:00:00
 # (1) Raw voltage INT + pHINT must be filtered from 2017-12-14 to 2018-01-08 < 8.04,
-# d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
-#                         d_all$datetime <= as.POSIXct("2018-01-08") &
-#                         d_all$phINT < 8.04, NA, d_all$phINT)
-# d_all$phEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
-#                        d_all$datetime <= as.POSIXct("2018-01-08") &
-#                        d_all$phEXT < 8.04, NA, d_all$phEXT) 
+# (2) removed from 2018-01-08 to 2018-02-02
+# (3) outliers removed
+# (1)
+d_all$phINT <- ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
+                        d_all$datetime <= as.POSIXct("2018-01-08") &
+                        d_all$phINT < 8.04, NA, d_all$phINT)
+d_all$phEXT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
+                       d_all$datetime <= as.POSIXct("2018-01-08") &
+                       d_all$phEXT < 8.04, NA, d_all$phEXT) 
 d_all$voltINT <-ifelse(d_all$datetime >= as.POSIXct("2017-12-14") &
@@
                          d_all$voltEXT < -0.907, NA, d_all$voltEXT) 
-#(2) removed from 2018-01-08 to 2018-02-02 due to drift
+# (2)
 d_all$voltINT <- ifelse(d_all$datetime >= as.POSIXct("2018-01-08 17:00:00") &
@@
                       NA, d_all$phEXT)
-# (3) outliers removed
+# (3)
 d_all$voltINT <- ifelse(d_all$datetime == as.POSIXct("2017-11-02 21:00:00") |
@@
 
-### add the depth into discrete df. In order to see where the seafet was.
-#discrete <- left_join(discrete, d_all%>%dplyr::select(closest_datetime,depth, depth_discrete),by="closest_datetime")
-discrete <- left_join(discrete, d_all%>%dplyr::select(closest_datetime,depth),by="closest_datetime")
-discrete <- discrete%>%dplyr::filter(discrete$datetime < "2021-07-01 00:00:00")
-
-#offset_xts <- select(discrete, closest_datetime, depth,depth_discrete, ph_s_sf_temp_insi)
-offset_xts <- select(discrete, closest_datetime, depth, ph_s_sf_temp_insi)
-offset_xts <- as.xts(offset_xts, order.by=offset_xts$closest_datetime)
-
-dygraph(offset_xts, main = "") %>%
-#dySeries("depth_discrete", drawPoints = TRUE, pointSize=3, strokeWidth = 1,label = "depth_discrete", color="black")%>%
-dySeries("depth", drawPoints = TRUE, pointSize=3, label = "depth", strokeWidth = 1,color="blue")%>%
-dySeries(axis="y2","ph_s_sf_temp_insi", drawPoints = TRUE, pointSize=4, label = "spectro", color="red")%>%
-    dyLegend(show = "follow")   %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-dyOptions(
-    drawGrid = TRUE,
-    strokeWidth= 0,
-    drawPoints = TRUE,
-    useDataTimezone = TRUE,
-    digitsAfterDecimal = 4) %>%
-  dyRangeSelector(height = 30, dateWindow= c("2017-10-21 00:00:00", "2021-01-11 00:00:00"))
-
 ####
-## calculation of E0INT25/E0EXT25 irrespective of the depth at which the seafet is (all data used) ##
+## calculation of E0INT25/E0EXT25 ##
 ##     new sf_calib function      ##
 ####
-calib_spectro_all <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
+calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
 # put number of deployment 
-calib_spectro_all$deployment_sf <- d_all$deployment_sf
+calib_spectro$deployment_sf <- d_all$deployment_sf
 
 # make the mean of E0 by period of deployement
-calib_spectro_all <- group_by(calib_spectro_all, deployment_sf) %>%
-  dplyr::summarise(E0int25 = mean(E0int25, na.rm = TRUE),
-            E0ext25 = mean(E0ext25, na.rm = TRUE) 
-            ) %>% 
-  dplyr::filter(!is.na(deployment_sf))
-names(calib_spectro_all) <- c("deployment_sf", "E0int25_sf", "E0ext25_sf")
-
-# add E0 mean to seaFET data per deployment
-d_all <-left_join(d_all, calib_spectro_all,by="deployment_sf" )
-
-```
-
-```{r seaFET pH calib sf_calib 10m, echo=FALSE, message= FALSE, warning=FALSE}
-###
-#creaate new dataframe and CALIB to take into consideration only seafet data at the same depth than spectro (9m)
-##
-####
-d_all_calib_depth <- d_all%>%
-#  dplyr::select(datetime, voltINT, voltEXT,ph_s_sf_temp_insi,sal_insitu_ctd_interp,temp_sf, depth_discrete,deployment_sf)%>%
-  dplyr::select(datetime, voltINT, voltEXT,ph_s_sf_temp_insi,sal_insitu_ctd_interp,temp_sf,depth, deployment_sf)%>%
-#  dplyr::filter(depth_discrete == 10)
-    dplyr::filter(depth > 8)
-
-calib_spectro_depth_10m <- sf_calib(calEint = d_all_calib_depth$voltINT, calEext = d_all_calib_depth$voltEXT, calpH = d_all_calib_depth$ph_s_sf_temp_insi, calT = d_all_calib_depth$temp_sf, calSal = d_all_calib_depth$sal_insitu_ctd_interp)
-# put number of deployment 
-calib_spectro_depth_10m$deployment_sf <- d_all_calib_depth$deployment_sf
-
-# make the mean of E0 by period of deployement
-calib_spectro_depth_10m <- group_by(calib_spectro_depth_10m, deployment_sf) %>%
+calib_spectro <- group_by(calib_spectro, deployment_sf) %>%
   summarise(E0int25 = mean(E0int25, na.rm = TRUE),
             E0ext25 = mean(E0ext25, na.rm = TRUE) 
-            ) %>% 
-  dplyr::filter(!is.na(deployment_sf))
-names(calib_spectro_depth_10m) <- c("deployment_sf", "E0int25_sf_10m", "E0ext25_sf_10m")
+            )
+names(calib_spectro) <- c("deployment_sf", "E0int25_sf", "E0ext25_sf")
 
 # add E0 mean to seaFET data per deployment
-d_all <- dplyr::left_join(d_all, calib_spectro_depth_10m, by="deployment_sf") %>% 
-    dplyr::select(order(colnames(d_all)))
-```
-
-Below are the seafet calibration parameters using all data (irrespective of the depth of the seafet) and with the seafet data collected below 8 m.
-They are very close but we nevertheless use the calibration data below 8 m (easier to explain in the manuscript).
-
-```{r seaFET pH plot sf_calib , echo=FALSE, message= FALSE, warning=FALSE}
+d_all <-left_join(d_all, calib_spectro,by="deployment_sf" )
+
 #### plot
-# kk <- tidyr::pivot_longer(d_all, cols = starts_with("E0"), names_to = "variable", values_to = "value")
-# p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
-#   facet_grid(variable ~ ., scales="fixed") + theme_bw() +
-#   scale_colour_discrete(guide="none")
-
-kk <- d_all %>% 
-  dplyr::select(deployment_sf, tidyr::starts_with("E0")) %>% 
-  tidyr::pivot_longer(cols = starts_with("E0"), names_to = "variable", values_to = "value")
+kk <- tidyr::pivot_longer(calib_spectro, cols = starts_with("E0"), names_to = "variable", values_to = "value")
 p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
-  facet_grid(variable ~ ., scales="fixed") + theme_bw() +
+  facet_grid(variable ~ ., scales="free_y") + theme_bw() +
   scale_colour_discrete(guide="none")
 print(p_calib)
-
-calib_spectro <- cbind(calib_spectro_all, calib_spectro_depth_10m)
-kbl(calib_spectro)%>%
-    kable_paper() %>% 
-    kable_styling(fixed_thead = T)
 ```
@@
 ### **seaFET pHT calibrated**
+pH is measured continuously by an autonomous seaFET pH sensor.
 Final calibrated seaFET pHT data (green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
+Calibration was done following the methods and code described in Bresnahan *et al.* (2014) using seaFET voltage and spectro measurements.
+During the fifth period, seaFET cannot be calibrated because seaFET was not working during the time of reference (pH spectro) sampling (2018-04-16).
+To solve this calibration, we decided to fit the spectro measurement with a pH mean of 4 previous days.
 
@@
 ####
-## calculation of the calibrated pH with all data irrespective of the depth of the REMOS ##
+## calculation of the calibrated pH ##
 ##       new sf_calc function       ##
@@
 d_all <- d_all %>%   
-  dplyr::mutate(pHint_tot_sf = oce::despike(seafet_calib$pHint_tot_sf, reference= "median", n=1, k=5001, replace="NA"),
-                pHext_tot_sf = oce::despike(seafet_calib$pHext_tot_sf, reference= "median", n=1, k=5001, replace="NA")
+  dplyr::mutate(pHint_tot_sf = oce::despike(seafet_calib$pHint_tot_sf, reference= "median", n=1, k=5000, replace="NA"),
+                pHext_tot_sf = oce::despike(seafet_calib$pHext_tot_sf, reference= "median", n=1, k=5000, replace="NA")
   )
@@
       !is.na(pHint_tot_sf_7m) ~ 7,
-      !is.na(pHint_tot_sf_10m) ~ 10
+      !is.na(pHint_tot_sf_10m) ~ 9
       ),
@@
   )
+
+# d_all <- d_all %>%
+#   dplyr::mutate(ph_s_sf_temp_4 = ifelse(!is.na(pH_seafet$ph_s_sf),
+#                                               pHinsi(pH = pH_seafet$ph_s_sf, 
+#                          ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = 4, 
+#                          Tlab = pH_seafet$temp_s_lab, Pinsi = pH_seafet$depth/10, 
+#                          S = pH_seafet$sal_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
+#                          pHscale = "T", b="u74"), NA
+#   ))
+
+# add spectro points that cannot be taken into consideration (some ancillary data T and/or S not available) shown as white triangles on the plot
+# ALSO Conversion of spec pH of FerryBox samples at 4°C
+
+d_all <- d_all %>%
+  dplyr::mutate(
+    pH_s_sf_no_calb = ifelse(
+      datetime == as.POSIXct("2018-04-16 07:00:00") |
+        datetime == as.POSIXct("2018-12-14 10:00:00") |
+        datetime == as.POSIXct("2019-01-18 11:00:00"),
+      ph_s_sf_temp_insi,
+      NA
+    ))
 
@@
 rm(seafet_depth_xts)
-```
-
-```{r seaFET pH calculation sf_calc 10m, echo=FALSE, message= FALSE, warning=FALSE}
-####
-## calculation of the calibrated pH using spec pH when seafet is at a depth > 8 m##
-##       new sf_calc function       ##
-####
-seafet_calib_10m <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf_10m,  E0ext25 = d_all$E0ext25_sf_10m, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
-
-# bind new calibrated pH data to the seafet data set.
-names(seafet_calib_10m) <- c("pHint_tot_sf_calib10m", "pHext_tot_sf_calib10m")
-##########  Despike() ###########
-d_all <- d_all %>%   
-  dplyr::mutate(pHint_tot_sf_calib10m = oce::despike(seafet_calib_10m$pHint_tot_sf_calib10m, reference= "median", n=1, k=5001, replace="NA"),
-                pHextt_tot_sf_calib10m = oce::despike(seafet_calib_9m$pHextt_tot_sf_calib10m, reference= "median", n=1, k=5001, replace="NA")
-  )
-
-d_all <- d_all %>%
-  #dplyr::mutate(pHint_tot_sf = despike(d_all$pHint_tot_sf, reference= "median", n=2, k=5761, replace="NA")) %>%
-  dplyr::mutate(pHint_tot_sf_calib10m = seafet_calib_10m$pHint_tot_sf_calib10m)
-
-seafet_depth_xts <- dplyr::select(d_all, datetime, ph_s_sf_temp_insi, pHint_tot_sf_1m, pHint_tot_sf_3m, pHint_tot_sf_5m, pHint_tot_sf_7m, pHint_tot_sf_10m, pHint_tot_sf_calib10m)
-seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
-dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
-      dySeries("pHint_tot_sf_calib10m", label = "pH calib 9m", color =  "black", strokeWidth = 0, pointSize = 2 ) %>%
-dySeries("pHint_tot_sf_10m", label = "pHT 10m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_7m", label = "pHT 7m", color =  RColorBrewer::brewer.pal(3, "Dark2")[2], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_5m", label = "pHT 5m", color =  RColorBrewer::brewer.pal(3, "Dark2")[3], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_3m", label = "pHT 3m", color =  RColorBrewer::brewer.pal(3, "Dark2")[4], strokeWidth = 0, pointSize = 1) %>%
-dySeries("pHint_tot_sf_1m", label = "pHT 1m", color =  RColorBrewer::brewer.pal(3, "Dark2")[5], strokeWidth = 0, pointSize = 1) %>%
-  dySeries("ph_s_sf_temp_insi", label = "pH spectro", color =  "red", strokeWidth = 0, pointSize = 5 ) %>%
-
-dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "seaFET #1005 installed", labelLoc = "bottom", color="red") %>%
-  dyEvent(as.POSIXct("2018-02-02 09:00:00", tz="UTC"), "seaFET settings changed to every 1H", labelLoc = "bottom", color="red") %>% 
-  dyEvent(as.POSIXct("2018-04-17 12:00:00", tz="UTC"), "seaFET #0007 installed + continuous mode set", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2019-09-02 12:00:00", tz="UTC"), "seaFET #0007 out of water for cleaning", labelLoc = "bottom", color="red") %>%
-  dyShading(from =  sfinterv[1], to= sfinterv[2], color = "#CCCCCC") %>%
-  dyShading(from =  sfinterv[2], to= sfinterv[3], color = "#E0E0E0") %>%
-  dyShading(from = sfinterv[3], to= Sys.Date(), color = "#CCCCCC") %>%
-  dyLegend(show = "auto")   %>%
-  dyAxis("y2",valueRange = c(-3, 9)) %>%
-  dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-  dyOptions(drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-  dyRangeSelector(height = 30, dateWindow= c("2017-08-10 00:00:00","2021-01-20 23:00:00"))
-rm(seafet_depth_xts)
-
 ```

### 2021-12-23 awipev-CO2.Rmd
It knits!

@@
   chunk_output_type: console
+  markdown: 
+    wrap: 72
 ---
-![ ](Images/AWIPEV-Logo.jpg){width=250px}
+
+![](Images/AWIPEV-Logo.jpg){width="250px"}
 
@@
 d_all <- d_hour %>%
-  dplyr::mutate_all(function(x) ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
-  dplyr::mutate(depth_group = as.factor(dplyr::case_when(depth > 0 & depth <= 2 ~ '0-2',
+  dplyr::mutate_all(function(x)
+    ifelse(is.nan(x), NA, x)) %>% # replace all NaN by NA
+  dplyr::mutate(
+    depth_group = as.factor(
+      dplyr::case_when(
+        depth > 0 & depth <= 2 ~ '0-2',
         depth > 2 & depth <= 4 ~ '2-4',
@@
         depth > 6 & depth <= 8 ~ '6-8',
-                depth > 8 & depth <= 12 ~ '>8', #8 to 12.4
+        depth > 8 & depth <= 12 ~ '>8',
+        #8 to 12.4
         TRUE ~ 'NA'
-                )),
+      )
+    ),
     sal_insitu_ctd_1m = ifelse(depth_group == '0-2', sal_insitu_ctd, NA),
@@
   dplyr::rowwise() %>%
-  dplyr::mutate(n_depth_ctd = sum(is.na( # create new variable to identify the hours for which there are CTD data at more than 1 depth 
+  dplyr::mutate(n_depth_ctd = sum(is.na(
+    # create new variable to identify the hours for which there are CTD data at more than 1 depth
     c(
@@
 
+```{=html}
 <style type="text/css">
@@
 </style>
-
+```
 #  {.tabset .tabset-fade .tabset-pills}
@@
 ### **Introduction**
+
 <div style="text-align: justify">
-The AWIPEV-CO2 project aims at starting the first time series for the carbonate chemistry in the Arctic Ocean as part of the AWIPEV Underwater Observatory.
-It comprises two components: (1) continuous real-time measurements and (2) discrete measurements.
-The rationale is that discrete measurements are absolutely needed to calibrate and validate the sensors.
+
+The AWIPEV-CO2 project aims at starting the first time series for the
+carbonate chemistry in the Arctic Ocean as part of the AWIPEV Underwater
+Observatory. It comprises two components: (1) continuous real-time
+measurements and (2) discrete measurements. The rationale is that
+discrete measurements are absolutely needed to calibrate and validate
+the sensors.
 
 ### **AWIPEV Underwater Observatory**
+
 <div style="text-align: justify">
-The AWIPEV Underwater Observatory has been deployed at Ny-Alesund (Spitsbergen, 78°55'18N, 11°56'31E) in June 2012.
-It is part of the German Project COSYNA (Coastal Observation Systems of the Northern- and Arctic Seas), which aims at increasing the availability of continuous real-time data from remote but climatically-sensitive ecosystems.
-The AWIPEV underwater observatory comprises a fully remote controlled FerryBox system fed with seawater pumped in front of the old pIer at 12 m depth.
-Temperature, salinity, pressure, turbidity, oxygen, chl-*a* fluorescence are measured.
-Furthermore, an additional remote controlled underwater sensor unit able to profile from 12 m to the surface at any frequency carries additional sensors for salinity, pressure, turbidity, oxygen chl-*a* fluorescence and PAR.
-The system also comprises an ADCP for continuous measurements of currents and waves.
-Besides these standard sensors, the underwater unit is equipped with a webcam and stereo-optical device to remotely assess fish and jellyfish populations.
-The AWIPEV observatory is specifically designed for polar experimental work under extreme conditions including ice coverage and the inaccessibility for about 7 months during polar winter.
-During this time, the system is remotely controlled and maintained from Germany.
-All data sampled by the sensors are continuously sent to a central server system at Helgoland Island where the data are stored and processed.
-The processed data are open access and available at http://codm.hzg.de/codm.
-
-<div style="text-align:center" markdown="1">
-  <img  src="./Images/Container.png" width="200" height="200">
-  <img  src="./Images/Intake.png" width="200" height="200">
-  <img  src="./Images/2018-04-17_Ferrybox2.jpg" width="200" height="200">
-</div>
+
+The AWIPEV Underwater Observatory has been deployed at Ny-Alesund
+(Spitsbergen, 78°55'18N, 11°56'31E) in June 2012. It is part of the
+German Project COSYNA (Coastal Observation Systems of the Northern- and
+Arctic Seas), which aims at increasing the availability of continuous
+real-time data from remote but climatically-sensitive ecosystems. The
+AWIPEV underwater observatory comprises a fully remote controlled
+FerryBox system fed with seawater pumped in front of the old pIer at 12
+m depth. Temperature, salinity, pressure, turbidity, oxygen, chl-*a*
+fluorescence are measured. Furthermore, an additional remote controlled
+underwater sensor unit able to profile from 12 m to the surface at any
+frequency carries additional sensors for salinity, pressure, turbidity,
+oxygen chl-*a* fluorescence and PAR. The system also comprises an ADCP
+for continuous measurements of currents and waves. Besides these
+standard sensors, the underwater unit is equipped with a webcam and
+stereo-optical device to remotely assess fish and jellyfish populations.
+The AWIPEV observatory is specifically designed for polar experimental
+work under extreme conditions including ice coverage and the
+inaccessibility for about 7 months during polar winter. During this
+time, the system is remotely controlled and maintained from Germany. All
+data sampled by the sensors are continuously sent to a central server
+system at Helgoland Island where the data are stored and processed. The
+processed data are open access and available at
+<http://codm.hzg.de/codm>.
+
+::: {style="text-align:center" markdown="1"}
+<img src="./Images/Container.png" width="200" height="200"/>
+<img src="./Images/Intake.png" width="200" height="200"/>
+<img src="./Images/2018-04-17_Ferrybox2.jpg" width="200" height="200"/>
+:::
 
 ### **Continuous and semi-continuous measurements**
+
 <div style="text-align: justify">
-The Arctic version of the Contros-Kongsberg HydroC CO~2~ FT (Carbon Dioxyde partial pressure Flow Through surface water sensor) has been installed in July 2015.
-Molecules of dissolved CO~2~ diffuse through a thin composite membrane into the internal gas circuit leading to a detector chamber, where the partial pressure of CO~2~ is determined by means of infra-red absorption spectrometry.
-Concentration-dependent IR light is converted into the output signal from calibration coefficients stored in firmware and data from additional sensors within the gas circuit.
-The measuring range is 200-1000 uatm, resolution is < 1 uatm and accuracy is +- 1% reading.
-The sensor is the first instrument in the measuring loop; data are logged every minute.
-This instrument requires yearly factory calibration; two sensors ara available to allow a continuous time series.
-
-Since February 2016, total alkalinity (AT) is measured every 90 min with a Contros-Kongsberg HydroFIA TA (Total Alkalinity analyser flow through system).
-Fifty ml of seawater is filtered (0.2 um) using a Contros-Kongsberg cross-flow filter and then acidified using dilute hydrochloric acid (0.1 N).
-CO~2~ is then flushed out (open-cell titration) and the final pH measured by means of an indicator dye (bromocresol green) and visible absorption spectrometry.
-Together with salinity and temperature at the time of measurement, the pH reading is used to calculate AT.
-According to the manufacturer, the measuring range is 400 umol/kg dynamic range, resolution 0.1 umol/kg, accuracy 25 umol/kg (+- 1%) and precision 5 umol/kg (+- 0.2%).
-
-In August 2017, a seaFET Ocean pH sensor (Sea-Bird Scientific) has been added to the UWO.
-This new sensor continuously measures pH at 11 m using an ISFET (Ion Sensitive Field Effect Transistor).
-According to the manufacturer, the measuring range is between 6.5 and 9 pH units, initial accuracy is 0.02 pH units and precision is 0.004 pH units.
-Operating salinity and temperature range are 20 to 40 PSU and 0 to 50°C respectively.
-
-In August 2017, a Durafet III pH electrode connected to a UDA2128 Analyser (Honeywell) was also implemented to the Ferrybox flow-through system.
-This electrode continuously measures pH, in the Ferrybox, through an ISFET.
-According to the manufacturer, the measuring range is between 0 and 14 pH units.
+
+The Arctic version of the Contros-Kongsberg HydroC CO~2~ FT (Carbon
+Dioxyde partial pressure Flow Through surface water sensor) has been
+installed in July 2015. Molecules of dissolved CO~2~ diffuse through a
+thin composite membrane into the internal gas circuit leading to a
+detector chamber, where the partial pressure of CO~2~ is determined by
+means of infra-red absorption spectrometry. Concentration-dependent IR
+light is converted into the output signal from calibration coefficients
+stored in firmware and data from additional sensors within the gas
+circuit. The measuring range is 200-1000 uatm, resolution is \< 1 uatm
+and accuracy is +- 1% reading. The sensor is the first instrument in the
+measuring loop; data are logged every minute. This instrument requires
+yearly factory calibration; two sensors ara available to allow a
+continuous time series.
+
+Since February 2016, total alkalinity (AT) is measured every 90 min with
+a Contros-Kongsberg HydroFIA TA (Total Alkalinity analyser flow through
+system). Fifty ml of seawater is filtered (0.2 um) using a
+Contros-Kongsberg cross-flow filter and then acidified using dilute
+hydrochloric acid (0.1 N). CO~2~ is then flushed out (open-cell
+titration) and the final pH measured by means of an indicator dye
+(bromocresol green) and visible absorption spectrometry. Together with
+salinity and temperature at the time of measurement, the pH reading is
+used to calculate AT. According to the manufacturer, the measuring range
+is 400 umol/kg dynamic range, resolution 0.1 umol/kg, accuracy 25
+umol/kg (+- 1%) and precision 5 umol/kg (+- 0.2%).
+
+In August 2017, a seaFET Ocean pH sensor (Sea-Bird Scientific) has been
+added to the UWO. This new sensor continuously measures pH at 11 m using
+an ISFET (Ion Sensitive Field Effect Transistor). According to the
+manufacturer, the measuring range is between 6.5 and 9 pH units, initial
+accuracy is 0.02 pH units and precision is 0.004 pH units. Operating
+salinity and temperature range are 20 to 40 PSU and 0 to 50°C
+respectively.
+
+In August 2017, a Durafet III pH electrode connected to a UDA2128
+Analyser (Honeywell) was also implemented to the Ferrybox flow-through
+system. This electrode continuously measures pH, in the Ferrybox,
+through an ISFET. According to the manufacturer, the measuring range is
+between 0 and 14 pH units.
 
 ### **Data availability**
-The data at one minute frequency were tagged with the following quality flags
-
-+ 1: good data
-+ 3: failing the date and time test
-+ 4: data not usable according to manufacturer
-+ 6: failing the manufacturer range test (not used)
-+ 7: failing the regional range test 
-+ 12: failing the spike test (NAs from despike)
-+ 13: failing the gradient test
-+ 15: instrument not deployed or operated
-+ 16: acid flush
-+ 99: failing the final visual inspection
-
-* Despike using oce::despike with n=2, k=5761
+
+The data at one minute frequency were tagged with the following quality
+flags
+
+-   1: good data
+
+-   3: failing the date and time test
+
+-   4: data not usable according to manufacturer
+
+-   6: failing the manufacturer range test (not used)
+
+-   7: failing the regional range test
+
+-   12: failing the spike test (NAs from despike)
+
+-   13: failing the gradient test
+
+-   15: instrument not deployed or operated
+
+-   16: acid flush
+
+-   99: failing the final visual inspection
+
+-   Despike using oce::despike with n=2, k=5761
 
@@
 ## Salinities
-Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically.
-Salinity from FB is taken in consideration.
-If data gaps are encountered, they are filled with bottom salinity data from ctd (> 8 m).
-New column "sal_mix" is created and is the one used in ESSD paper.
-
-+ 1 SBE45 inside the Ferrybox (sal_fb)
-+ 5 CTD > 8 m depth (sal_insitu_ctd)
+
+Several salinity sensors are on site, 1 inside the Ferrybox (SBE45) and
+5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are
+switched periodically. Salinity from FB is taken in consideration. If
+data gaps are encountered, they are filled with bottom salinity data
+from ctd (> 8 m). New column "sal_mix" is created and is the one used in
+ESSD paper.
+
+-   1 SBE45 inside the Ferrybox (sal_fb)
+-   5 CTD > 8 m depth (sal_insitu_ctd)
 
@@
 
-df <- d_all %>% 
+tmp <- d_all %>% 
   dplyr::select(datetime, sal_insitu_ctd_1m, sal_insitu_ctd_3m, sal_insitu_ctd_5m, sal_insitu_ctd_7m, sal_insitu_ctd_10m) %>%
@@
             mean10m = mean(sal_insitu_ctd_10m, na.rm = TRUE),
-            range = mean(sal_insitu_ctd_1m, na.rm = TRUE) - mean(sal_insitu_ctd_10m, na.rm = TRUE)) %>% 
+            range_diff = mean(sal_insitu_ctd_1m, na.rm = TRUE) - mean(sal_insitu_ctd_10m, na.rm = TRUE)) %>% 
   ungroup()
 
-p_sal_range <- ggplot(data = df) +
-  geom_histogram((aes(x = range))) +
+p_sal_range <- ggplot(data = tmp) +
+  geom_histogram((aes(x = range_diff))) +
   labs(title = "Daily salinity difference between 1 and 10 m", x = "Difference") +
   Mytheme(size_labs = 8)
-p_sal_range
-
-kable(quantile(x = df$range, na.rm = TRUE), digits = 2, col.names = "Sal. unit", caption = "Quantiles salinity gradient between 0-2 m and > 8 m")
+print(p_sal_range)
+
+kable(quantile(x = tmp$range_diff, na.rm = TRUE), digits = 2, col.names = "Sal. unit", caption = "Quantiles salinity gradient between 0-2 m and > 8 m")
 rm(sal_xts)
 ```
-Extreme differences: `r dplyr::filter(df, range < -3 | range > 2)`.
-
-There are `r sum(!is.na(df$range))` days with salinity values at both 1 m (0-2 m) and 10 m (8-12 m).
-The salinity difference between 1 and 10 m ranges between `r min(df$range, na.rm=TRUE)` and `r max(df$range, na.rm=TRUE)` (mean: `r mean(df$range, na.rm=TRUE)`; `r median(df$range, na.rm=TRUE)`).
+
+```{r, eval=FALSE, echo=FALSE}
+Extreme differences: `r dplyr::filter(tmp, range_diff < -3 | range_diff > 2)`.
+
+There are `r sum(!is.na(tmp$range_diff))` days with salinity values at both 1 m (0-2 m) and 10 m (8-12 m).
+
+The salinity difference between 1 and 10 m ranges between `r min(tmp$range_diff, na.rm=TRUE)` and `r max(tmp$range_diff, na.rm=TRUE)` (mean: `r mean(tmp$range_diff, na.rm=TRUE)`; `r median(tmp$range_diff, na.rm=TRUE)`).
 The difference with depth is therefore significant.
-
-### **Sal FB / Sal CTD 10 m **
+```
+
+### **Sal FB / Sal CTD 10 m**
 
@@
 
-The mean difference between salinity FB and in situ is: `r mean_diff_sal_fb_insitu_10m` ± `r sd_diff_sal_fb_insitu_10m` PSU.
+The mean difference between salinity FB and in situ is:
+`r mean_diff_sal_fb_insitu_10m` ± `r sd_diff_sal_fb_insitu_10m` PSU.
 
 ## Temperatures
-Several temperature sensors are on site, 1 inside the Ferrybox (SBE45), 5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are switched periodically and 1 fixed at 11 m depth (sbe38). 
-Temperature in situ at 11 m depth is taken in consideration.
-If data gaps are encountered, they are filled with bottom temperature data from ctd (> 8 m).
-New column "temp_mix" is created.
-For the moment, no gaps are encountered and temp_mix = temp_insitu_11m.
+
+Several temperature sensors are on site, 1 inside the Ferrybox (SBE45),
+5 outside (ctd183, ctd181, ctd578, ctd964/964b and ctd103) that are
+switched periodically and 1 fixed at 11 m depth (sbe38). Temperature in
+situ at 11 m depth is taken in consideration. If data gaps are
+encountered, they are filled with bottom temperature data from ctd (> 8
+m). New column "temp_mix" is created. For the moment, no gaps are
+encountered and temp_mix = temp_insitu_11m.
 
@@
 ### **Temperature profiles**
+
 ```{r temperature profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
@@
 
-df <- d_all %>% 
+tmp <- d_all %>% 
   dplyr::select(datetime, temp_insitu_ctd_1m, temp_insitu_ctd_3m, temp_insitu_ctd_5m, temp_insitu_ctd_7m, temp_insitu_ctd_10m) %>%
@@
 ```
-There are `r sum(!is.na(df$range))` days with temperature values at both 1 m (0-2 m) and 9 m (> 8 m).
-The temperature difference between 1 and 9 m ranges between `r min(df$range, na.rm=TRUE)`°C and `r max(df$range, na.rm=TRUE)`°C (mean: `r mean(df$range, na.rm=TRUE)`°C; `r median(df$range, na.rm=TRUE)`°C).
+
+There are `r sum(!is.na(tmp$range))` days with temperature values at
+both 1 m (0-2 m) and 9 m (> 8 m). The temperature difference between 1
+and 9 m ranges between `r min(tmp$range, na.rm=TRUE)`°C and
+`r max(tmp$range, na.rm=TRUE)`°C (mean:
+`r mean(tmp$range, na.rm=TRUE)`°C; `r median(tmp$range, na.rm=TRUE)`°C).
 The difference with depth is therefore significant.
 
-### **T Ferrybox / T insitu 11 m **
+### **T Ferrybox / T insitu 11 m**
 
@@
 
-The mean difference between temperature Ferrybox and in situ at 11 m is: `r mean_diff_T_fb_11m` ± `r sd_diff_T_fb_11m`°C.
-
-### **T 11 m / T CTD > 8 m **
+The mean difference between temperature Ferrybox and in situ at 11 m is:
+`r mean_diff_T_fb_11m` ± `r sd_diff_T_fb_11m`°C.
+
+### **T 11 m / T CTD \> 8 m**
 
@@
 
-The mean difference between temperature Ferrybox and in situ at 11 m is: `r mean_diff_T_ctd_11m` ± `r sd_diff_T_ctd_11m`°C.
+The mean difference between temperature Ferrybox and in situ at 11 m is:
+`r mean_diff_T_ctd_11m` ± `r sd_diff_T_ctd_11m`°C.
 
@@
 
-Since we bought the AT analyser (February 2016), numerous problems happened due to a leak of the degassing unit in each analyser and sudden step changes.
-Last analyser repaired by Contros was installed back in the FB on 2018-07-31.
-This was the 3rd analyser on site.
-Even with this instrument, data collection didn't show satisfaction.
+Since we bought the AT analyser (February 2016), numerous problems
+happened due to a leak of the degassing unit in each analyser and sudden
+step changes. Last analyser repaired by Contros was installed back in
+the FB on 2018-07-31. This was the 3rd analyser on site. Even with this
+instrument, data collection didn't show satisfaction.
 
@@
 In the previous part, missing TA were interpolated with a linear model.
-This does not reflect the natural variability of TA.
-For this reason, missing TA is now calculated from salinity data by making a relationship between the same reference TA samples as in the previous part and salinity data.
+This does not reflect the natural variability of TA. For this reason,
+missing TA is now calculated from salinity data by making a relationship
+between the same reference TA samples as in the previous part and
+salinity data.
 
@@
 
-The relationship between titrated total alkalinity (references) and salinity is very good with an r2 of `r #round(summary(fit)$r.squared, digits=2)`.
-Need to compare with other relationships from the literature.
+The relationship between titrated total alkalinity (references) and
+salinity is very good with an r2 of
+`r #round(summary(fit)$r.squared, digits=2)`. Need to compare with other
+relationships from the literature.
 
@@
 
-There are a lot of outliers in the 4th period (since the new analyzer was set up in Nov. 2018). We use the desplike function to remove them.
+There are a lot of outliers in the 4th period (since the new analyzer
+was set up in Nov. 2018). We use the desplike function to remove them.
 
 <!-- #### **TA since November 2018 (final installation)** -->
+
 <!-- ```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'} -->
+
 <!--  # select subset of data and remove obvious outliers -->
+
 <!--  at_nov_2018 <- -->
+
 <!--   dplyr::select(d_all, datetime, at_calc, AT, at) %>% -->
+
 <!--   filter(datetime > "2018-11-01", AT > 2250) -->
+
 <!-- #despike -->
+
 <!-- at_nov_2018 <- mutate(at_nov_2018, AT_despike = despike(AT, reference= "median", n=0.5, k=10, replace="NA")) -->
+
 <!-- #plot -->
+
 <!-- at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) + -->
+
 <!--   geom_point(aes(y=AT, colour = "before"), size =3) + -->
+
 <!--   geom_point(aes(y=AT_despike, colour = "after"), size = 2) + -->
+
 <!--   labs(x = "Time", y = "Total alkalinity", color = "despike") -->
+
 <!-- print(at_datetime) -->
@@
 <!-- at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_despike != "NA") -->
+
 <!-- titre <- "Contros AT vs Calculated AT" -->
+
 <!--  fit <- lmodel2(data = at_nov_2018_no_NA, AT_despike ~ at_calc, nperm = 99) -->
+
 <!-- ggreg2(fit, x = "at_calc", y = "AT_despike") -->
@@
 ## *p*CO~2~ and *f*CO~2~
-The HydroC CO~2~ FT sensor (S/N: CO2FT-0215-001) was bought from Contros (Germany) in February 2015.
-It was deployed in the FerryBox with other sensors since July 2015, the 20th.
-A spare sensor (S/N: CO2FT-0515-001) was also bought in March 2015 and carried to Ny-Alesund to replace the first one in case of calibration or problem.
-Both sensors were set on a cycle according to informations given by Contros in March 2015 (c.kirbach@contros.eu):
-
-30 min warm up --> (3 min Zeroing + 15 min Flushing + 702 minutes Measuring) --> (3 + 15 + 702)...
-
-  - **Warm-up**: running without sending data. Done once, after the sensor is turned on. Time can vary depending on T water and power supply.
-  - **Flushing**: running normally.
-Phase of equilibration that depends on the sensor configuration and the environment conditions.
-Warmer the water is and larger the flow is in front of the membrane, faster will be the response time and shorter will be the flush time.
-Recovery data of the sensor signal from the zeroing interval happen in this time.
-During this step the flush flag is set to “1” for simplifier extraction of the flush values.
-  - **Measuring**: running normally and all other flags are on “0”. Sensor is fully equilibrated and T is stable.
+
+The HydroC CO~2~ FT sensor (S/N: CO2FT-0215-001) was bought from Contros
+(Germany) in February 2015. It was deployed in the FerryBox with other
+sensors since July 2015, the 20th. A spare sensor (S/N: CO2FT-0515-001)
+was also bought in March 2015 and carried to Ny-Alesund to replace the
+first one in case of calibration or problem. Both sensors were set on a
+cycle according to informations given by Contros in March 2015
+([c.kirbach\@contros.eu](mailto:c.kirbach@contros.eu){.email}):
+
+30 min warm up --> (3 min Zeroing + 15 min Flushing + 702 minutes
+Measuring) --> (3 + 15 + 702)...
+
+-   **Warm-up**: running without sending data. Done once, after the
+    sensor is turned on. Time can vary depending on T water and power
+    supply.
+-   **Flushing**: running normally. Phase of equilibration that depends
+    on the sensor configuration and the environment conditions. Warmer
+    the water is and larger the flow is in front of the membrane, faster
+    will be the response time and shorter will be the flush time.
+    Recovery data of the sensor signal from the zeroing interval happen
+    in this time. During this step the flush flag is set to "1" for
+    simplifier extraction of the flush values.
+-   **Measuring**: running normally and all other flags are on "0".
+    Sensor is fully equilibrated and T is stable.
 
 During those steps (except zeroing) the sensor runs normally.
-Equilibration between the gas inside the sensor and the dissolved gas in ambient water takes place.
-Gas is led to NDIR unit while T control is running.
-
-**Note** that the Contros pCO2 values after 2020-03-01 were not used because the Covid-19 pandemic prevented maintenance and the setup of a freshly calibrated sensor.
-As the result, algae becalme inceasingly abundant, pulling pCO2 down and further away from values calculated from CT and AT.
+Equilibration between the gas inside the sensor and the dissolved gas in
+ambient water takes place. Gas is led to NDIR unit while T control is
+running.
+
+**Note** that the Contros pCO2 values after 2020-03-01 were not used
+because the Covid-19 pandemic prevented maintenance and the setup of a
+freshly calibrated sensor. As the result, algae becalme inceasingly
+abundant, pulling pCO2 down and further away from values calculated from
+CT and AT.
 
@@
 
-We first calculate fCO2 from pCO2 and then express both pCO2 and fCO2 at in situ temperature.
-Ideally, this should be done with SST as the goal is to estimate air-sea CO2 fluxes.
-I therefore use the in situ temperature at 11 m and we will need to speculate on stratification.
+We first calculate fCO2 from pCO2 and then express both pCO2 and fCO2 at
+in situ temperature. Ideally, this should be done with SST as the goal
+is to estimate air-sea CO2 fluxes. I therefore use the in situ
+temperature at 11 m and we will need to speculate on stratification.
 
@@
 
-The relationship between the measured (Contros) and calculated pCO2 (blue line) is relatively poor.
-It is far from the 1:1 relationship (black dashed line).
-The slope is `r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)`.
-
-**Figure legend**: pCO2 calculated from AT and CT as a function of pCO2 measured using a Contros sensor.
-All data are normalized at in situ temperature.
-The black dotted line is the 1:1 line while the blue solid line shows the line obtained by a major axis regression (Legendre, 2018- Pierre Legendre (2018).
-lmodel2: Model II Regression.
-R package version 1.7-3.
-https://CRAN.R-project.org/package=lmodel2
+The relationship between the measured (Contros) and calculated pCO2
+(blue line) is relatively poor. It is far from the 1:1 relationship
+(black dashed line). The slope is
+`r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence
+interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)`.
+
+**Figure legend**: pCO2 calculated from AT and CT as a function of pCO2
+measured using a Contros sensor. All data are normalized at in situ
+temperature. The black dotted line is the 1:1 line while the blue solid
+line shows the line obtained by a major axis regression (Legendre, 2018-
+Pierre Legendre (2018). lmodel2: Model II Regression. R package version
+1.7-3. <https://CRAN.R-project.org/package=lmodel2>
 
@@
 pH is measured continuously by an autonomous seaFET pH sensor.
-Measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17 it was then measured once every minute.
-pH calibration is based on monthly, when possible, discrete samples collected at 11 m that were analysed with spectrophotometric method in Villefranche by Samir Alliouane.
-Measurments were performed several months after sampling.
-When sampling was not possible in the vicinity of the sensor for practical reasons (in winter), sampling was done in the harbour and is not taken in consideration for calibration for spatial reasons.
-*Note that the pH sensor is mounted on a profiling structure.
-Here, in principle, only seaFET data recorded with a depth > 8 m should be taken into consideration.*
-
-Calibration was done following the methods and code described in Bresnahan et al.
-(2014) and adapted to use in R (seacarb package).
-3 deployment periods were defined, corresponding to a change of sensors.
-
-Within a deployment period, calibration is made with E0 calculation (first plot) and final corrected pH is calculated (second plot).
-To allow calibration, one spectrophotometric pH measurement must match: seaFET voltage, in situ temperature (seaFET) and salinity (REMOS CTD).
-When one of these parameters is missing for any reasons (Ferrybox maintenance, breakdown...), the gap is filled with a mean of the 4 previous or next hours when available.
-If the pH spectrophotometric measurement is too far from the available values, the calibration is not performed (environemental variability reasons).
-
-Only 5 spectrophotometric pH which could be used for calibration when seaFET at > 8 m: 2018-11-16, 2019-04-17, 2019-10-11, 2020-01-27.
-All deployment meriods are covered but we had to alter the sampling time of:
-
-* 2017-08-24 14:00 to 2017-08-24 19:00 (5 h later)
-* 2017-11-28 09:00 to 2017-11-28 13:00 (4 h later)
-
-EO is calculated making a mean of several E0 that come from one deployment period (sensor in the water for several months).
+Measurement periodicity was set to 1 hour from 2018-02-02 to 2018-04-17
+it was then measured once every minute. pH calibration is based on
+monthly, when possible, discrete samples collected at 11 m that were
+analysed with spectrophotometric method in Villefranche by Samir
+Alliouane. Measurments were performed several months after sampling.
+When sampling was not possible in the vicinity of the sensor for
+practical reasons (in winter), sampling was done in the harbour and is
+not taken in consideration for calibration for spatial reasons. *Note
+that the pH sensor is mounted on a profiling structure. Here, in
+principle, only seaFET data recorded with a depth \> 8 m should be taken
+into consideration.*
+
+Calibration was done following the methods and code described in
+Bresnahan et al. (2014) and adapted to use in R (seacarb package). 3
+deployment periods were defined, corresponding to a change of sensors.
+
+Within a deployment period, calibration is made with E0 calculation
+(first plot) and final corrected pH is calculated (second plot). To
+allow calibration, one spectrophotometric pH measurement must match:
+seaFET voltage, in situ temperature (seaFET) and salinity (REMOS CTD).
+When one of these parameters is missing for any reasons (Ferrybox
+maintenance, breakdown...), the gap is filled with a mean of the 4
+previous or next hours when available. If the pH spectrophotometric
+measurement is too far from the available values, the calibration is not
+performed (environemental variability reasons).
+
+Only 5 spectrophotometric pH which could be used for calibration when
+seaFET at \> 8 m: 2018-11-16, 2019-04-17, 2019-10-11, 2020-01-27. All
+deployment meriods are covered but we had to alter the sampling time of:
+
+-   2017-08-24 14:00 to 2017-08-24 19:00 (5 h later)
+-   2017-11-28 09:00 to 2017-11-28 13:00 (4 h later)
+
+EO is calculated making a mean of several E0 that come from one
+deployment period (sensor in the water for several months).
 
@@
 
-Plots of E0int25 and E0ext25 returned by the function "pHCalib" for each period of deployement are shown below.
+Plots of E0int25 and E0ext25 returned by the function "pHCalib" for each
+period of deployement are shown below.
 
@@
 
-Below are the seafet calibration parameters using all data (irrespective of the depth of the seafet) and with the seafet data collected below 8 m.
-They are very close but we nevertheless use the calibration data below 8 m (easier to explain in the manuscript).
+Below are the seafet calibration parameters using all data (irrespective
+of the depth of the seafet) and with the seafet data collected below 8
+m. They are very close but we nevertheless use the calibration data
+below 8 m (easier to explain in the manuscript).
 
@@
 ### **seaFET pHT calibrated**
-Final calibrated seaFET pHT data (small green dots) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
-
-We also defined a period of malfunction from **2017-12-14** to **2018-02-02**.
-in the first part of this period, until 2018-01-08, we decided to filter outliers.
-In the second part, until the end of the period, data must be removed.
+
+Final calibrated seaFET pHT data (small green dots) are shown here after
+calibration with spectro measurements (red dots) according to each
+period of deployement, defined between 2 spectro measurements (shading
+grey).
+
+We also defined a period of malfunction from **2017-12-14** to
+**2018-02-02**. in the first part of this period, until 2018-01-08, we
+decided to filter outliers. In the second part, until the end of the
+period, data must be removed.
 
@@
 d_all <- d_all %>%
-  dplyr::mutate(pHint_tot_sf_all_1m = ifelse(depth > 0 & depth < 2, pHint_tot_sf_all, NA),
-                pHint_tot_sf_all_3m = ifelse(depth >= 2 & depth < 4, pHint_tot_sf_all, NA),
-                pHint_tot_sf_all_5m = ifelse(depth >= 4 & depth < 6, pHint_tot_sf_all, NA),
-                pHint_tot_sf_all_7m = ifelse(depth >= 6 & depth < 8, pHint_tot_sf_all, NA),
-                pHint_tot_sf_all_10m = ifelse(depth >= 8 , pHint_tot_sf_all, NA),
-                depth_discrete = case_when(
-                  !is.na(pHint_tot_sf_all_1m) ~ 1,
-                  !is.na(pHint_tot_sf_all_3m) ~ 3,
-                  !is.na(pHint_tot_sf_all_5m) ~ 5,
-                  !is.na(pHint_tot_sf_all_7m) ~ 7,
-                  !is.na(pHint_tot_sf_all_10m) ~ 10
-                  ),
-                depth_discrete = as.factor(depth_discrete)
+  dplyr::mutate(pHint_tot_sf_all_1m = ifelse(depth_group == '0-2', pHint_tot_sf_all, NA),
+                pHint_tot_sf_all_3m = ifelse(depth_group == '2-4', pHint_tot_sf_all, NA),
+                pHint_tot_sf_all_5m = ifelse(depth_group == '4-6', pHint_tot_sf_all, NA),
+                pHint_tot_sf_all_7m = ifelse(depth_group == '6-8', pHint_tot_sf_all, NA),
+                pHint_tot_sf_all_10m = ifelse(depth_group == '>8',  pHint_tot_sf_all, NA),
+                # depth_discrete = case_when(
+                #   !is.na(pHint_tot_sf_all_1m) ~ 1,
+                #   !is.na(pHint_tot_sf_all_3m) ~ 3,
+                #   !is.na(pHint_tot_sf_all_5m) ~ 5,
+                #   !is.na(pHint_tot_sf_all_7m) ~ 7,
+                #   !is.na(pHint_tot_sf_all_10m) ~ 10
+                #   ),
+                # depth_discrete = as.factor(depth_discrete)
                 )
@@
 d_all <- d_all %>%
-  dplyr::mutate(pHint_tot_sf_10m_1m = ifelse(depth > 0 & depth < 2, pHint_tot_sf_10m, NA),
-                pHint_tot_sf_10m_3m = ifelse(depth >= 2 & depth < 4, pHint_tot_sf_10m, NA),
-                pHint_tot_sf_10m_5m = ifelse(depth >= 4 & depth < 6, pHint_tot_sf_10m, NA),
-                pHint_tot_sf_10m_7m = ifelse(depth >= 6 & depth < 8, pHint_tot_sf_10m, NA),
-                pHint_tot_sf_10m_10m = ifelse(depth >= 8 , pHint_tot_sf_10m, NA),
-                depth_discrete = case_when(
-                  !is.na(pHint_tot_sf_10m_1m) ~ 1,
-                  !is.na(pHint_tot_sf_10m_3m) ~ 3,
-                  !is.na(pHint_tot_sf_10m_5m) ~ 5,
-                  !is.na(pHint_tot_sf_10m_7m) ~ 7,
-                  !is.na(pHint_tot_sf_10m_10m) ~ 10
-                  ),
-                depth_discrete = as.factor(depth_discrete)
+  dplyr::mutate(pHint_tot_sf_10m_1m = ifelse(depth_group == '0-2', pHint_tot_sf_10m, NA),
+                pHint_tot_sf_10m_3m = ifelse(depth_group == '2-4', pHint_tot_sf_10m, NA),
+                pHint_tot_sf_10m_5m = ifelse(depth_group == '4-6', pHint_tot_sf_10m, NA),
+                pHint_tot_sf_10m_7m = ifelse(depth_group == '6-8', pHint_tot_sf_10m, NA),
+                pHint_tot_sf_10m_10m = ifelse(depth_group == '>8', pHint_tot_sf_10m, NA)#,
+                # depth_discrete = case_when(
+                #   !is.na(pHint_tot_sf_10m_1m) ~ 1,
+                #   !is.na(pHint_tot_sf_10m_3m) ~ 3,
+                #   !is.na(pHint_tot_sf_10m_5m) ~ 5,
+                #   !is.na(pHint_tot_sf_10m_7m) ~ 7,
+                #   !is.na(pHint_tot_sf_10m_10m) ~ 10
+                #   ),
+                # depth_discrete = as.factor(depth_discrete)
                 )
@@
 
-- Offset between calibrated seaFET data and pH spectro. The offset must fit between -0.2/0.2 pH units.
-
-“differences between calibrated sensor pH values and values obtained from discrete, check samples can be expected to be as small as 0.02 pH units, and perhaps less.” (McLaughlin et al. 2017).
+-   Offset between calibrated seaFET data and pH spectro. The offset
+    must fit between -0.2/0.2 pH units.
+
+"differences between calibrated sensor pH values and values obtained
+from discrete, check samples can be expected to be as small as 0.02 pH
+units, and perhaps less." (McLaughlin et al. 2017).
 
@@
 
-From now on, one uses seaFET pH from the internal electrode calibrated with spec pH and seaFET data when the REMOS was below 8 m (pHint_tot_sf_10m).
-This unique pH variable is called pHint_tot_sf.
-All other pH variables are cleaned up
+From now on, one uses seaFET pH from the internal electrode calibrated
+with spec pH and seaFET data when the REMOS was below 8 m
+(pHint_tot_sf_10m). This unique pH variable is called pHint_tot_sf. All
+other pH variables are cleaned up
 
@@
     dplyr::select(-starts_with(c(
-    "pHint_tot_sf_", "pHext_", "pHint_tot_sf_all"
+    "pHint_tot_sf_10m_", "pHext_", "pHint_tot_sf_all"
   )))
@@
 ```
+
 ### **seaFET pH profiles**
@@
 tmp <- d_all %>% 
-  dplyr::select(year, montht, pHint_tot_sf, depth_discrete) %>%
-  tidyr::drop_na(pHint_tot_sf, depth_discrete) %>%
-  dplyr::group_by(depth_discrete, year, montht)
-summary(aov(tmp$pHint_tot_sf ~ tmp$depth_discrete * tmp$montht))
-
-# remove outliers
-quantile(tmp$pHint_tot_sf, na.rm =TRUE, probs = c(0.01, 0.99))
-
+  dplyr::select(year, montht, pHint_tot_sf, depth_group) %>%
+  tidyr::drop_na(pHint_tot_sf, depth_group) %>%
+  dplyr::group_by(depth_group, year, montht)
+summary(aov(tmp$pHint_tot_sf ~ tmp$depth_group * tmp$montht))
 p <- tmp %>%
-  ggplot(aes(x=depth_discrete, y = pHint_tot_sf)) +
+  ggplot(aes(x = depth_group, y = pHint_tot_sf)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, coef = 1.5) +
-  labs(title = "pHT", x = "Depth (m)", y= "pHT") +
-  lims(y = c(7.4, 8.3)) +
+  labs(title = "pHT", x = "Depth (m)", y= "pHT seaFET at in situ temperature") +
+#  lims(y = c(7.4, 8.3)) +
   coord_cartesian() +
@@
 
-pp <- tmp %>%
-  ggplot(aes(x=depth_discrete, y = pHint_tot_sf)) +
-  stat_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, coef = 3)
-
 # we look at 0 to 4 m vs more than 8 m
@@
   dplyr::select(montht, pHint_tot_sf, depth) %>%
-  dplyr::mutate(depth2 = as.factor(case_when(depth < 4 ~ '0-4', 
-                                             depth > 8~ '8-12',
-                                             TRUE ~ NA_real_))) %>% 
-  dplyr::filter(depth2 == '0-2' | depth2 == '8-12') %>% 
+  dplyr::mutate(depth2 = as.factor(dplyr::case_when(depth < 4 ~ '0-4', 
+                                             depth > 8 ~ '8-12'))) %>% 
+  dplyr::filter(depth2 == '0-4' | depth2 == '8-12') %>% 
   dplyr::group_by(depth2, montht)
@@
 p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
+  ggplot(aes(x=as.factor(depth2), y = pHint_tot_sf)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "pHT", x = "Depth (m)", y= "pHT") +
+  labs(title = "pHT", x = "Depth (m)", y= "pHT seaFET at in situ temperature") +
   facet_wrap(vars(montht), scale = "free_y")
 print(p)
-```
-**Conclusion**:
-The range is significantly larger during some months when the data deeper than 8 m are considered.
-Also, pH is sometimes higher at the surface, at other times it is higher on the bottom (June).
-No data are available at 1 m (actually 0 to 2 m).
-So, to compare surface and bottom, I combine 1 and 3 m (0 to 4 m) and 9 m (below 8 m).
-
-Depth and month of the year have a statistically significant effect on pH. The interaction is also significant, indicating that the effect of depth differs depending on the month.
-
- + To compare with pCO2/pCO2 measured in the Ferrybox seems therefore better to stick with pH_10m, that is at depths deeper than 8 m.
-  + pCO2 would have the same behaviour as pH. For air-sea CO2 fluxes, one should use data from 0 to 4 m.
+
+# we look at 0 to 4 m vs more than 8 m but pH at 4°C
+
+```
+
+**Conclusion**: The range is significantly larger during some months
+when the data deeper than 8 m are considered. Also, pH is sometimes
+higher at the surface, at other times it is higher on the bottom (June).
+No data are available at 1 m (actually 0 to 2 m). So, to compare surface
+and bottom, I combine 1 and 3 m (0 to 4 m) and 9 m (below 8 m).
+
+Depth and month of the year have a statistically significant effect on
+pH. The interaction is also significant, indicating that the effect of
+depth differs depending on the month.
+
+-   To compare with pCO2/pCO2 measured in the Ferrybox seems therefore
+    better to stick with pH_10m, that is at depths deeper than 8 m.
+-   pCO2 would have the same behaviour as pH. For air-sea CO2 fluxes,
+    one should use data from 0 to 4 m.
 
@@
 
-pH is measured continuously by an autonomous durafet pH sensor.
-Final calibrated durafet pHT data (green doibb) are shown here after calibration with spectro measurements (red dots) according to each period of deployement, defined between 2 spectro measurements (shading grey).
-Calibration was done appliying an offset of pH between measured and spectro data per periods.
+pH is measured continuously by an autonomous durafet pH sensor. Final
+calibrated durafet pHT data (green doibb) are shown here after
+calibration with spectro measurements (red dots) according to each
+period of deployement, defined between 2 spectro measurements (shading
+grey). Calibration was done appliying an offset of pH between measured
+and spectro data per periods.
 
@@
 
-The average offset between durafet and references (spectro) data is `r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n = `r n_offset_dur`).
+The average offset between durafet and references (spectro) data is
+`r average_offset_dur` pH unit (sd = `r sd_offset_dur`, n =
+`r n_offset_dur`).
 
@@
 ## pHs
-Comparaison is done here with **corrected pHs** (**seaFET**, **durafet** and **calculated** (from AT/CT)) and normalized at 4°C with a total alkalinity of `r mean(d_all$at, na.rm=TRUE)` µmoles kg-1 (mean data).
-For information, mean temperatures in Ferrybox and *in situ* are repectively 3.5°C and 2.5°C.
+
+Comparaison is done here with **corrected pHs** (**seaFET**, **durafet**
+and **calculated** (from AT/CT)) and normalized at 4°C with a total
+alkalinity of `r mean(d_all$at, na.rm=TRUE)` µmoles kg-1 (mean data).
+For information, mean temperatures in Ferrybox and *in situ* are
+repectively 3.5°C and 2.5°C.
 
@@
 ### **Calculated / Durafet pHs**
+
 ```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
@@
 ### **Calculated / seaFET pHs**
+
 ```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
@@
 ## SNAPO-CO2
-Since November 2018, informations on weekly Ferrybox and monthly durafet/seaFET samplings are collected in a online document that can be consulted at anytime:
-
-[weekly and monthly samplings](https://docs.google.com/spreadsheets/d/1bNh9q4bkNoh2ra78XC451EmGb9Q8kMf4ByBnKngeHOg/edit?usp=sharing)
-
-We found that some analysed discrete seawater replicates for AT/CT, performed by SNAPO in Paris sometimes show a large difference between duplicates.
-Arbitrarily, we decided to take in consideration replicates with a standard deviation smaller than 10 µmoles.kg-1.
-In the other case (greater than 10 µmoles.kg-1), the closest replicate from the general trend will be kept with qflag_at/qflag_ct of 2 (correct analysis) and the farthest one will be rejected with a flag of 1.
-There are exceptions when it is difficult to decide which of the replicates need to be eliminated.
-
-For TA, dulpicates's flags that have been changed from 2 (good) to 1 (not good) are:
-
-2015-11-18
-, 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29, 2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16, 2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03, 2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-08-23, 2019-09-20, 2019-11-08, 2019-11-23,2020-02-14 (2 replicates out of 5), 2020-05-29, 2020-06-06 (2 replicates out of 6), 2020-07-03.
-
-For CT, duplicates's flags that have been changed from 2 (good) to 1 (not good) are:
-
-2015-08-06, 2015-08-13, 2016-05-12, 2016-05-19, 2016-06-16, 2016-07-28, 2016-09-08, 2016-10-27, 2016-11-17, 2017-01-19, 2017-03-02, 2017-04-27, 2017-09-14, 2018-04-26, 2018-05-04, 2018-05-12, 2018-05-25, 2018-06-30, 2018-07-20, 2018-08-03, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09, 2018-11-16, 2018-11-23, 2019-05-03, 2019-05-10, 2019-08-23, 2020-02-08, 2020-07-17, 2020-11-20.
-
-Also in the Discrete_sampling_AWIPEV.csv, some analysed samples have been flaged "3" by the SNAPO.
-After a close look, these samples are not differents from their duplicates.
-Then we put the flag to "2" (good result).
-
-For TA and CT, samples's flags that have been changed from 3 to 2 are: 2019-12-27 (2264 and 2130), 2019-10-25 (2332 and 2152), 2019-09-06 (2268 and 2116).
+
+Since November 2018, informations on weekly Ferrybox and monthly
+durafet/seaFET samplings are collected in a online document that can be
+consulted at anytime:
+
+[weekly and monthly
+samplings](https://docs.google.com/spreadsheets/d/1bNh9q4bkNoh2ra78XC451EmGb9Q8kMf4ByBnKngeHOg/edit?usp=sharing)
+
+We found that some analysed discrete seawater replicates for AT/CT,
+performed by SNAPO in Paris sometimes show a large difference between
+duplicates. Arbitrarily, we decided to take in consideration replicates
+with a standard deviation smaller than 10 µmoles.kg-1. In the other case
+(greater than 10 µmoles.kg-1), the closest replicate from the general
+trend will be kept with qflag_at/qflag_ct of 2 (correct analysis) and
+the farthest one will be rejected with a flag of 1. There are exceptions
+when it is difficult to decide which of the replicates need to be
+eliminated.
+
+For TA, dulpicates's flags that have been changed from 2 (good) to 1
+(not good) are:
+
+2015-11-18 , 2016-07-28, 2016-09-29, 2016-11-17, 2016-11-23, 2016-12-29,
+2017-01-19, 2017-05-04, 2017-08-31, 2018-04-26, 2018-05-04, 2018-05-16,
+2018-05-25, 2018-06-22, 2018-06-30, 2018-07-27, 2018-07-20, 2018-08-03,
+2018-08-10, 2018-08-24, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-21,
+2018-09-28, 2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02,
+2018-11-09, 2018-11-16, 2018-11-23, 2019-08-23, 2019-09-20, 2019-11-08,
+2019-11-23,2020-02-14 (2 replicates out of 5), 2020-05-29, 2020-06-06 (2
+replicates out of 6), 2020-07-03.
+
+For CT, duplicates's flags that have been changed from 2 (good) to 1
+(not good) are:
+
+2015-08-06, 2015-08-13, 2016-05-12, 2016-05-19, 2016-06-16, 2016-07-28,
+2016-09-08, 2016-10-27, 2016-11-17, 2017-01-19, 2017-03-02, 2017-04-27,
+2017-09-14, 2018-04-26, 2018-05-04, 2018-05-12, 2018-05-25, 2018-06-30,
+2018-07-20, 2018-08-03, 2018-08-31, 2018-09-07, 2018-09-14, 2018-09-28,
+2018-10-05, 2018-10-12, 2018-10-19, 2018-10-26, 2018-11-02, 2018-11-09,
+2018-11-16, 2018-11-23, 2019-05-03, 2019-05-10, 2019-08-23, 2020-02-08,
+2020-07-17, 2020-11-20.
+
+Also in the Discrete_sampling_AWIPEV.csv, some analysed samples have
+been flaged "3" by the SNAPO. After a close look, these samples are not
+differents from their duplicates. Then we put the flag to "2" (good
+result).
+
+For TA and CT, samples's flags that have been changed from 3 to 2 are:
+2019-12-27 (2264 and 2130), 2019-10-25 (2332 and 2152), 2019-09-06 (2268
+and 2116).
 
@@
 ## Nutrients {.tabset .tabset-pills}
+
 ```{r impact of nutrients, echo=FALSE, warning=FALSE, message=FALSE}
@@
 ```
+
 `r knitr::kable(nuts_table, digits = c(1, 1, 4, 2, 7, 3), caption = "Impact of PO4 and Si.", format = "simple")`
 
-The concentration of po4 and si varies with a factor 10 along a composite year.
-The ranges are respectively, `r round(range(d_all$po4, na.rm = TRUE), digits = 2)` for po4 and `r round(range(d_all$si, na.rm = TRUE), digits = 2)` for si.
+The concentration of po4 and si varies with a factor 10 along a
+composite year. The ranges are respectively,
+`r round(range(d_all$po4, na.rm = TRUE), digits = 2)` for po4 and
+`r round(range(d_all$si, na.rm = TRUE), digits = 2)` for si.
 
 ### Using the pCO2-AT pair (hourly data)
-The difference between no PO4 and its maximum value on pH, DIC, and Omega_a are small:  `r round(1000*diff_po4_0a$pH, digits=2)` mpH units, `r round(1e6*diff_po4_0a$DIC, digits=2)` umol/kg for CT and `r round(diff_po4_0a$OmegaAragonite, digits=2)` for OmegaAragonite.
-
-The impact of the min max changes of po4 on pH, DIC, and Omega_a are small:  `r round(1000*diff_po4_1a$pH, digits=2)` mpH units, `r round(1e6*diff_po4_1a$DIC, digits=2)` umol/kg for CT and `r round(diff_po4_1a$OmegaAragonite, digits=2)` for OmegaAragonite.
-
-The difference between no Si and its maximum value on pH, DIC, and Omega_a are small:  `r round(1000*diff_Si_0a$pH, digits=2)` mpH units, `r round(1e6*diff_Si_0a$DIC, digits=2)` umol/kg for CT and `r round(diff_Si_0a$OmegaAragonite, digits=2)` for OmegaAragonite.
-
-The impact of the min max changes of si on pH, DIC, and Omega_a are small:  `r round(1000*diff_Si_1a$pH, digits=2)` mpH units, `r round(1e6*diff_Si_1a$DIC, digits=2)` umol/kg for CT and `r round(diff_Si_1a$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The difference between no PO4 and its maximum value on pH, DIC, and
+Omega_a are small: `r round(1000*diff_po4_0a$pH, digits=2)` mpH units,
+`r round(1e6*diff_po4_0a$DIC, digits=2)` umol/kg for CT and
+`r round(diff_po4_0a$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of po4 on pH, DIC, and Omega_a are
+small: `r round(1000*diff_po4_1a$pH, digits=2)` mpH units,
+`r round(1e6*diff_po4_1a$DIC, digits=2)` umol/kg for CT and
+`r round(diff_po4_1a$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The difference between no Si and its maximum value on pH, DIC, and
+Omega_a are small: `r round(1000*diff_Si_0a$pH, digits=2)` mpH units,
+`r round(1e6*diff_Si_0a$DIC, digits=2)` umol/kg for CT and
+`r round(diff_Si_0a$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of si on pH, DIC, and Omega_a are
+small: `r round(1000*diff_Si_1a$pH, digits=2)` mpH units,
+`r round(1e6*diff_Si_1a$DIC, digits=2)` umol/kg for CT and
+`r round(diff_Si_1a$OmegaAragonite, digits=2)` for OmegaAragonite.
 
 ### Using the CT-AT pair (discrete data)
-The difference between no PO4 and its maximum value on pH, pCO2, and Omega_a are small:  `r round(1000*diff_po4_0b$pH, digits=2)` mpH units, `r round(diff_po4_0b$pCO2, digits=2)` uatm for pCO2 and `r round(diff_po4_0b$OmegaAragonite, digits=2)` for OmegaAragonite.
-
-The impact of the min max changes of po4 on pH, pCO2, and Omega_a are small:  `r round(1000*diff_po4_1b$pH, digits=2)` mpH units, `r round(diff_po4_1b$pCO2, digits=2)` uatm for pCO2 and `r round(diff_po4_1b$OmegaAragonite, digits=2)` for OmegaAragonite.
-
-The difference between no Si and its maximum value on pH, pCO2, and Omega_a are small:  `r round(1000*diff_Si_0b$pH, digits=2)` mpH units, `r round(diff_Si_0b$pCO2, digits=2)` uatm for pCO2 and `r round(diff_Si_0b$OmegaAragonite, digits=2)` for OmegaAragonite.
-
-The impact of the min max changes of Si on pH, pCO2, and Omega_a are small:  `r round(1000*diff_Si_1b$pH, digits=2)` mpH units, `r round(diff_Si_1b$pCO2, digits=2)` uatm for pCO2 and `r round(diff_Si_1b$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The difference between no PO4 and its maximum value on pH, pCO2, and
+Omega_a are small: `r round(1000*diff_po4_0b$pH, digits=2)` mpH units,
+`r round(diff_po4_0b$pCO2, digits=2)` uatm for pCO2 and
+`r round(diff_po4_0b$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of po4 on pH, pCO2, and Omega_a are
+small: `r round(1000*diff_po4_1b$pH, digits=2)` mpH units,
+`r round(diff_po4_1b$pCO2, digits=2)` uatm for pCO2 and
+`r round(diff_po4_1b$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The difference between no Si and its maximum value on pH, pCO2, and
+Omega_a are small: `r round(1000*diff_Si_0b$pH, digits=2)` mpH units,
+`r round(diff_Si_0b$pCO2, digits=2)` uatm for pCO2 and
+`r round(diff_Si_0b$OmegaAragonite, digits=2)` for OmegaAragonite.
+
+The impact of the min max changes of Si on pH, pCO2, and Omega_a are
+small: `r round(1000*diff_Si_1b$pH, digits=2)` mpH units,
+`r round(diff_Si_1b$pCO2, digits=2)` uatm for pCO2 and
+`r round(diff_Si_1b$OmegaAragonite, digits=2)` for OmegaAragonite.
 
 ## K1K2 {.tabset .tabset-pills}
+
 ```{r impact of constants discrete, echo=FALSE, warning=FALSE, message=FALSE}
@@
 ### K1K2 using pCO2 and AT
+
 ```{r impact of constants using FerryBox pCO2 and at, echo=FALSE, warning=FALSE, message=FALSE}
@@
 ```
+
 #### Difference Lueker vs Sulpis
+
 Using the following using mean discrete values:
@@
 
-The discrete values of pCO2, AT, salinity and temperature in the FerryBox were used to calculate pH using the formulations for K1 and K2 of Lueker et al.
-(2000) and Sulpis et al.
-(2020).
-The differences induced by the choice of the carbonic acid constants are:
-
-- large for pH (`r round(diff_ls_quant[4, 2], digits = 3)` pH units on average; ; median is `r round(diff_ls_quant[3, 2], digits = 3)`) compared with the uncertainty calculated with seacarb (`r round(const_choice[1, 6], digits = 3)`).
-In general, pH is higher with Sulpis than with Lueker.
-- small for CT (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on average; always lower with Sulpis than with Lueker) compared with the uncertainty calculated with seacarb (`r round(const_choice[1, 8], digits = 1)`)
+The discrete values of pCO2, AT, salinity and temperature in the
+FerryBox were used to calculate pH using the formulations for K1 and K2
+of Lueker et al. (2000) and Sulpis et al. (2020). The differences
+induced by the choice of the carbonic acid constants are:
+
+-   large for pH (`r round(diff_ls_quant[4, 2], digits = 3)` pH units on
+    average; ; median is `r round(diff_ls_quant[3, 2], digits = 3)`)
+    compared with the uncertainty calculated with seacarb
+    (`r round(const_choice[1, 6], digits = 3)`). In general, pH is
+    higher with Sulpis than with Lueker.
+-   small for CT (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on
+    average; always lower with Sulpis than with Lueker) compared with
+    the uncertainty calculated with seacarb
+    (`r round(const_choice[1, 8], digits = 1)`)
 -   negligible for OmegaAragonite
@@
 #### Difference between all formulations and measured pH
+
 `r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis using discrete Ferrybox data.", format = "simple")`
 
-Here we compare pH measured spectrophotometrically with pH calculated from pCO2 and AT using various formulations of K1 and K2.
-All pH values were normalized to a temperature of 4°C.
-The absolute differences are generally large, up to `r round(max(abs(diff_table_pco2_at[, 2:5])), digits=3)` pH units.
-In general, all formulations overestimate spectrophotometric pH.
-pH calculated using the formulation of Papadimitriou et al.
-(2018) is closer to measured pH, with a mean difference of `r round(diff_table_pco2_at[4, 4], digits=3)` pH units.
-This difference is `r abs(round(diff_table_pco2_at[4, 4]/errors_pco2_at$pH, digits=1))` times larger than the uncertainty for pH calculated from pCO2 and AT according to seacarb (`r round(errors_pco2_at$pH, digits=3)`).
+Here we compare pH measured spectrophotometrically with pH calculated
+from pCO2 and AT using various formulations of K1 and K2. All pH values
+were normalized to a temperature of 4°C. The absolute differences are
+generally large, up to
+`r round(max(abs(diff_table_pco2_at[, 2:5])), digits=3)` pH units. In
+general, all formulations overestimate spectrophotometric pH. pH
+calculated using the formulation of Papadimitriou et al. (2018) is
+closer to measured pH, with a mean difference of
+`r round(diff_table_pco2_at[4, 4], digits=3)` pH units. This difference
+is `r abs(round(diff_table_pco2_at[4, 4]/errors_pco2_at$pH, digits=1))`
+times larger than the uncertainty for pH calculated from pCO2 and AT
+according to seacarb (`r round(errors_pco2_at$pH, digits=3)`).
 `r knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "simple")`
@@
 ### K1K2 using CT and AT
+
 ```{r impact of constants using FerryBox ct and at, echo=FALSE, warning=FALSE, message=FALSE}
@@
 #### Difference between all formulations and measured pH
+
 `r knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "simple")`
@@
 
-Here we compare pH measured spectrophotometrically with pH calculated from AT and CT using various formulations of K1 and K2.
-All pH values were normalized to a temperature of 4°C.
-The absolute differences are generally large, up to `r round(max(abs(diff_table_at_ct[, 2:5])), digits=3)` pH units.
-In general, all formulations overestimate spectrophotometric pH.
-pH calculated using the formulation of Papadimitriou et al.
-(2018) is closer to measured pH, with a mean difference of `r round(diff_table_at_ct[4, 4], digits=3)` pH units.
-This difference is `r abs(round(diff_table_at_ct[4, 4]/errors_at_ct$pH, digits=1))` times the uncertainty for pH calculated from AT and CT according to seacarb (`r round(errors_at_ct$pH, digits=3)`).
-The differences found with the other formulations are, on average, slightly lower than the uncertainty for pH calculated from AT and CT according to seacarb.
+Here we compare pH measured spectrophotometrically with pH calculated
+from AT and CT using various formulations of K1 and K2. All pH values
+were normalized to a temperature of 4°C. The absolute differences are
+generally large, up to
+`r round(max(abs(diff_table_at_ct[, 2:5])), digits=3)` pH units. In
+general, all formulations overestimate spectrophotometric pH. pH
+calculated using the formulation of Papadimitriou et al. (2018) is
+closer to measured pH, with a mean difference of
+`r round(diff_table_at_ct[4, 4], digits=3)` pH units. This difference is
+`r abs(round(diff_table_at_ct[4, 4]/errors_at_ct$pH, digits=1))` times
+the uncertainty for pH calculated from AT and CT according to seacarb
+(`r round(errors_at_ct$pH, digits=3)`). The differences found with the
+other formulations are, on average, slightly lower than the uncertainty
+for pH calculated from AT and CT according to seacarb.
 
 ## Stratification
+
 ```{r stratification, echo=FALSE, message= FALSE, warning=FALSE}
@@
   dplyr::group_by(depth_group2, montht)
-tmp_delta <- tmp %>% 
+tmp_delta <- tidyr::drop_na(tmp) %>% 
   group_by(depth_group2, montht) %>% 
@@
 
-p <- tmp %>% 
+p <- tidyr::drop_na(tmp) %>% 
   ggplot(aes(x=depth_group2, y = sal_insitu_ctd)) +
@@
 
-sal_delta_plt <- tmp_delta %>% 
+sal_delta_plt <- tidyr::drop_na(tmp_delta) %>% 
   ggplot(aes(x=montht, y=sal_delta)) +
@@
 
-p <- tmp %>% 
+p <- tidyr::drop_na(tmp) %>% 
   ggplot(aes(x=depth_group2, y = temp_insitu_ctd)) +
@@
 
-temp_delta_plt <- tmp_delta %>% 
+temp_delta_plt <- tidyr::drop_na(tmp_delta) %>% 
   ggplot(aes(x=montht, y=temp_delta)) +
@@
   group_by(depth_group, montht)
-p <- tmp %>% 
+p <- tidyr::drop_na(tmp) %>% 
   ggplot(aes(x=as.factor(depth_group), y = sal_insitu_ctd)) +
@@
                 median8_12m = "8-12") %>% 
-  dplyr::mutate(temp_delta = median0_4m - median8_12m)
+  dplyr::mutate(den_delta = median0_4m - median8_12m)
 kable(tmp_delta, digits = 2, caption = "Median density with (median0_4m - median8_12m)")
 
-p <- tmp %>% 
+p <- tidyr::drop_na(tmp) %>% 
   ggplot(aes(x=montht, y = density)) +
@@
 tmp <- d_all %>% 
-  dplyr::mutate(depth_group = depth_group_pressure) %>% 
+  #dplyr::mutate(depth_group = depth_group_pressure) %>% 
   dplyr::select(montht, pHint_tot_sf, depth_group) %>%
-  dplyr::mutate(depth = as.factor(ifelse(depth_group == 1 | depth_group == 3, 2, depth_group))) %>% 
-  dplyr::filter(depth == 2 | depth == 10) %>% 
-  group_by(depth, montht)
-summary(aov(tmp$pHint_tot_sf ~ tmp$depth * tmp$montht))
+  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
+                                      depth_group == '>8' ~ '8-12'))) %>% 
+  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
+  dplyr::group_by(depth_group2, montht)
+summary(aov(tmp$pHint_tot_sf ~ tmp$depth_group2 * tmp$montht))
 
 tmp_delta <- tmp %>% 
-  group_by(depth, montht) %>% 
+  group_by(depth_group2, montht) %>% 
   dplyr::summarise(pH_tot_sf_med = median(pHint_tot_sf, na.rm = TRUE)) %>% 
-  tidyr::pivot_wider(names_from = depth, values_from = pH_tot_sf_med) %>% 
-  dplyr::rename(median0_4m = "2",
-                median8_12m = "10") %>% 
-  dplyr::mutate(pH_tot_sf_med_delta = median0_4m - median8_12m)
+  tidyr::pivot_wider(names_from = depth_group2, values_from = pH_tot_sf_med) %>% 
+  dplyr::rename(median0_4m = "0-4",
+                median8_12m = "8-12") %>%   dplyr::mutate(pH_tot_sf_med_delta = median0_4m - median8_12m)
 kable(tmp_delta, digits = 3, caption = "Median seafet pH with (median0_4m - median8_12m)")
 
-p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth), y = pHint_tot_sf)) +
+p <- tidyr::drop_na(tmp) %>% 
+  ggplot(aes(x=as.factor(depth_group2), y = pHint_tot_sf)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
 
-pH_delta_plt <- tmp_delta %>% 
+pH_delta_plt <- tidyr::drop_na(tmp_delta) %>% 
   ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
@@
 
-+ Salinity 
-+ Temperature is always colder at 0-4 m than below 8 m (0.15 to 2°C).
+-   Salinity
+-   Temperature is always colder at 0-4 m than below 8 m (0.15 to 2°C).
 
 ## Takahashi thermal vs non-thermal
+
 ```{r Takahashi thermal vs non-thermal, include=FALSE}
@@
 ```
+
 `r knitr::kable(taka_year, digits = c(0, 1, 1, 2), caption = "Thermal vs non-thermal control of pCO2. Yearly estimate.", format = "simple")`
 `r knitr::kable(taka_season, digits = c(0, 1, 1, 2), caption = "Thermal vs non-thermal control of pCO2. Seasonal estimate.", format = "simple")`
-For seasonal analysis, December to February was considered winter, March to May was considered spring, June to August was considered summer, and September to November was considered fall.
-
-The control of pCO2 by non-thermal (physical and biological processes) drivers is always greater than the control from temperature on both annual and seasonal basis.
-Thermal control is highest in winter and lowest in summer.
+For seasonal analysis, December to February was considered winter, March
+to May was considered spring, June to August was considered summer, and
+September to November was considered fall.
+
+The control of pCO2 by non-thermal (physical and biological processes)
+drivers is always greater than the control from temperature on both
+annual and seasonal basis. Thermal control is highest in winter and
+lowest in summer.
 
 ## Deconvolution of pCO2 changes
+
 ```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
@@
 
-+ seawater pCO2 measured in the FerryBox on water pumped from 11 m depth.
-+ atmospheric CO2 measured at the Zeppelin station and downloaded on 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999 
-+ wind speed data collected by the AWI at 10 m height (sent to JPG by P. Fischer, Aug. 2020)
-
-Since there are many gaps, a climatological year is used: air-sea flux calculated by day, then by month, then by year.
-
-seaFET pH is significantly different at the surface and depth. It should therefore be the same for pCO2.
-
-Let's look first at the stratification (salinity, temperature and density).
+-   seawater pCO2 measured in the FerryBox on water pumped from 11 m
+    depth.
+-   atmospheric CO2 measured at the Zeppelin station and downloaded on
+    2020-08-19 from
+    <https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999>
+-   wind speed data collected by the AWI at 10 m height (sent to JPG
+    by P. Fischer, Aug. 2020)
+
+Since there are many gaps, a climatological year is used: air-sea flux
+calculated by day, then by month, then by year.
+
+seaFET pH is significantly different at the surface and depth. It should
+therefore be the same for pCO2.
+
+Let's look first at the stratification (salinity, temperature and
+density).
 
@@
 
-The annual air-sea CO2 flux is `r round(sum(air_sea_month$f_air_sea), digits = 0)` mol/(m2 year).
+The annual air-sea CO2 flux is
+`r round(sum(air_sea_month$f_air_sea), digits = 0)` mol/(m2 year).
 
 ## Miscellaneous
+
 ###Save all
+
 ```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
@@
 ### Whole time series plot
+
 ```{r whole time series plot, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
@@
 ### Whole time series monthly box plots and stats
+
 ```{r whole time series monthly box plots and stats, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
@@
 ## Maintenance
+
 <div style="text-align: justify">
@@
 ### **REMOS**
+
 -   **2020-09-23**: REMOS started at 20:00 UTC.
-- **2020-09-22**: REMOS stopped at 19:00 UTC because of a power shutdown.
+-   **2020-09-22**: REMOS stopped at 19:00 UTC because of a power
+    shutdown.
 -   **2019-03-12**: REMOS on.
@@
 -   **2019-09-07**: REMOS back in the water.
-- **2019-09-02**: REMOS removed from the water for maintenance with Philipp and Samir.
-- **2018-11-24**: REMOS stopped because of an iceberg. At the moment we dont know if instruments are still there/broken.
+-   **2019-09-02**: REMOS removed from the water for maintenance with
+    Philipp and Samir.
+-   **2018-11-24**: REMOS stopped because of an iceberg. At the moment
+    we dont know if instruments are still there/broken.
 
 ### **FerryBox**
+
 -   **2020-09-30**: FB started at 19:00 UTC.
@@
 -   **2020-09-22**: FB stopped at 19:00 UTC because of a power shutdown.
-- **2020-09-22**: FB started again at 08:00 UTC after several months of locked down. Lisa repaired it in few minutes only. 
-- **2020-09-22**: FB started again after several months of locked down. Lisa repaired it in few minutes only. 
-- **2020-07-25**: FB stopped.
-Not possible to go inside to repair because the FB is locked after the "mercurygate".
-IPEV locked the FB with suspicion of mercury contamination rose up by Bettina (Stationleader)
-- **2020-05-24**: FB started again after several months of on activity due to very cold T and frozen pipes.
+-   **2020-09-22**: FB started again at 08:00 UTC after several months
+    of locked down. Lisa repaired it in few minutes only.
+-   **2020-09-22**: FB started again after several months of locked
+    down. Lisa repaired it in few minutes only.
+-   **2020-07-25**: FB stopped. Not possible to go inside to repair
+    because the FB is locked after the "mercurygate". IPEV locked the FB
+    with suspicion of mercury contamination rose up by Bettina
+    (Stationleader)
+-   **2020-05-24**: FB started again after several months of on activity
+    due to very cold T and frozen pipes.
 -   **2020-02-18**: FB stopped because of frozen pipes.
-- **2020-01-24**: heater issues in the contenair (power shutdown maybe) caused some samples to freeze. See part "SNAPO" for details on samples.
-- **2019-09-01**: Some interruptions for the FB during 2 weeks of maintenance.
+-   **2020-01-24**: heater issues in the contenair (power shutdown
+    maybe) caused some samples to freeze. See part "SNAPO" for details
+    on samples.
+-   **2019-09-01**: Some interruptions for the FB during 2 weeks of
+    maintenance.
 -   **2019-06-12**: Markus came to do maintenace.
-- **2019-06-05**: Problem in the relay 15 that controls the waste water pump was found. The spare part will be brought here next week (when Samir will leave...).
-- **2019-06-03**: Samir is on site alone. Different tests were made. Maybe the 2 tapes that feed TA and pCO2 are responsible of the problem (low flow).
-- **2019-05-22**: FB is stopped because of several problems. Philipp and Marine are working on it.
+-   **2019-06-05**: Problem in the relay 15 that controls the waste
+    water pump was found. The spare part will be brought here next week
+    (when Samir will leave...).
+-   **2019-06-03**: Samir is on site alone. Different tests were made.
+    Maybe the 2 tapes that feed TA and pCO2 are responsible of the
+    problem (low flow).
+-   **2019-05-22**: FB is stopped because of several problems. Philipp
+    and Marine are working on it.
 -   **2019-05-21**: FB is unstable.
 -   **2019-04-14**: FB is working again.
-- **2019-04-13**: FB is stopped since 05:00am (the level switch stuck in the full position in the waste tank). 
+-   **2019-04-13**: FB is stopped since 05:00am (the level switch stuck
+    in the full position in the waste tank).
 -   **2019-02-27**: FB is working again.
@@
 -   **2018-10-05**: FB is stopped after a seawater leakage.
-- **2018-09-12**: FB is stopped. Problems inland could be the reason. The same day Marine make it working again.
-- **2018-04-14**: FB is working again. They made an outlet "by-pass" tube to flush the seawater directly on the beach, not at 11 m.
-- **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet tubings) in Svalbard, maybe due to a power failure over night in Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
-- **2017-05-24**: FerryBox was shut down due to many connexion issues...see Philipp's email 24/05/2017 18:17.
+-   **2018-09-12**: FB is stopped. Problems inland could be the reason.
+    The same day Marine make it working again.
+-   **2018-04-14**: FB is working again. They made an outlet "by-pass"
+    tube to flush the seawater directly on the beach, not at 11 m.
+-   **2018-03-08**: Last data at 23:59. Frozen Ferrybox system (outlet
+    tubings) in Svalbard, maybe due to a power failure over night in
+    Kingsbay. UWO parameters (seaFET and SBE38 are still runing)
+-   **2017-05-24**: FerryBox was shut down due to many connexion
+    issues...see Philipp's email 24/05/2017 18:17.
 -   **2017-03-20**: Philipp arrived in NYA to solve the problem.
-- **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's email on 2017-03-11 10:40). No more data for all parameters.
-- **2017-01-31**: Beginning of the 14-days FB maintenance by Philipp and Uwe. Gaps in data could be present during this period.
-- **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17 21:00 to 2017-01-19.
-- **2016-09-24**: No data because of maintenance until the 28th. Except for TA wich has data available for this period.
-- **2016-09-20**: Test in the Ferrybox with the seawater.
-Seawater was "sucked" (not pumped) from 7:40 to 10:00 by a vaccum system in order to test it.
-This system was installed if the pumps 1 and 2 broke during winter.
-This is a "plan C".
-This system is not automatic and we will be informed about its power up in case of emergency.
-As long as the water is not pumped with this system, we have to monitor the data because changements in gas partial pressure can occur.
+-   **2017-03-11**: Iceberg destroyed the power-pumps cables (Philipp's
+    email on 2017-03-11 10:40). No more data for all parameters.
+-   **2017-01-31**: Beginning of the 14-days FB maintenance by Philipp
+    and Uwe. Gaps in data could be present during this period.
+-   **2017-01-17**: Ferrybox stopped for unknown reasons from 2017-01-17
+    21:00 to 2017-01-19.
+-   **2016-09-24**: No data because of maintenance until the 28th.
+    Except for TA wich has data available for this period.
+-   **2016-09-20**: Test in the Ferrybox with the seawater. Seawater was
+    "sucked" (not pumped) from 7:40 to 10:00 by a vaccum system in order
+    to test it. This system was installed if the pumps 1 and 2 broke
+    during winter. This is a "plan C". This system is not automatic and
+    we will be informed about its power up in case of emergency. As long
+    as the water is not pumped with this system, we have to monitor the
+    data because changements in gas partial pressure can occur.
 -   **2016-09-12**: No data because of maintenance until the 18th.
@@
 -   **2016-05-09**: data are back.
-- **2016-05-04**: No data for all parameters because of electricity issues. 
+-   **2016-05-04**: No data for all parameters because of electricity
+    issues.
 -   **2016-04-23**: FerryBox was shut down by AWI team for maintenance.
-- **2016-02-23**: FerryBox was switched on by AWI team after maintenance.
-- **2015-12-20**: FerryBox was shut down because of pump issues. Waiting for the maintenance in February.
-- **2015-11-27**: The ferrybox was down from Nov. 18th until today Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station Leader AWIPEV 2015-11-27 12:57). Tubes frozen.
+-   **2016-02-23**: FerryBox was switched on by AWI team after
+    maintenance.
+-   **2015-12-20**: FerryBox was shut down because of pump issues.
+    Waiting for the maintenance in February.
+-   **2015-11-27**: The ferrybox was down from Nov. 18th until today
+    Nov. 27th. (emails from P.Fischer 2015-11-24 23:09 and Station
+    Leader AWIPEV 2015-11-27 12:57). Tubes frozen.
 
 ### **TA analyser**
-- **2019-11-15**: TA calibration done by Gwendall is OK but the sensore seems to have problem since 2019-10-16.
-Video conference is scheduled with Steffen on 2019-11-19.
-Maybe sample supply is defective.
-- **2019-07-12**: Steffen told us that calibration was not OK.
-To check it, he calculated the mediane of the pH/volume sample / volumeIndicatorfactor and compared them to January/October calibration.
-We wait for Steffen recommandations before to make another calibration.
-- **2019-06-07**: Samir did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. TA was stable before the calibration and calibration was OK.
-- **2019-02-15**: No data from 15th (14:08:21 UTC) to 19th February (14:58:46 UTC). files transfered but no data. No explanation.
-- **2019-01-26**: Philipp did the TA calibration: T0 with CRM 145. Beginning of a 3-months period. Flow filter was also lifted up and the seawater flow has therefore increased.
+
+-   **2019-11-15**: TA calibration done by Gwendall is OK but the
+    sensore seems to have problem since 2019-10-16. Video conference is
+    scheduled with Steffen on 2019-11-19. Maybe sample supply is
+    defective.
+-   **2019-07-12**: Steffen told us that calibration was not OK. To
+    check it, he calculated the mediane of the pH/volume sample /
+    volumeIndicatorfactor and compared them to January/October
+    calibration. We wait for Steffen recommandations before to make
+    another calibration.
+-   **2019-06-07**: Samir did the TA calibration: T0 with CRM 145.
+    Beginning of a 3-months period. TA was stable before the calibration
+    and calibration was OK.
+-   **2019-02-15**: No data from 15th (14:08:21 UTC) to 19th February
+    (14:58:46 UTC). files transfered but no data. No explanation.
+-   **2019-01-26**: Philipp did the TA calibration: T0 with CRM 145.
+    Beginning of a 3-months period. Flow filter was also lifted up and
+    the seawater flow has therefore increased.
 -   **2019-01-16**: Bad data since this date.
 -   **2018-12-28**: HCL and BCG cartridges were changed by Marine.
-- **2018-11-26**: TA analyser was stopped in order to save reagents because of filter issues.
-- **2018-11-20**: A web interface was created by KM Contros to access the TA via VPN and Virtual Machine (VNC viewer).
-Samir received password and access from the AWI in order to communicate from France with the TA.
-- **2018-10-31**: New TA analyser (SN 0317-001) was installed with a new membrane inside (completely new technology). Tests were made with Steffen from KM Contros.
-- **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged again.
-First data were received (high: 2450 and low: 2150) but salinity issue since this time.
-Uwe/Philipp try to find if this comes from comunication issue with the FB.
-- **2018-06-20**: TA analyser was stopped in order to save reagents because leakage in degasing unit is not solved. Email was sent to Steffen. 
-- **2018-01-05**: TA analyser switched on and first communication tests. S/N TA-0317-001.
-- **2017-08-23**: The 2 TA analysers were sent to Contros for repair, 1 will be sent back to NYA after. No more TA data during this period.
-- **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by removing air bubbles in Acid tubings (advices from Steffen).
-- **2017-04-01**: No more TA data...waiting for a diagnostic by Contros.
+-   **2018-11-26**: TA analyser was stopped in order to save reagents
+    because of filter issues.
+-   **2018-11-20**: A web interface was created by KM Contros to access
+    the TA via VPN and Virtual Machine (VNC viewer). Samir received
+    password and access from the AWI in order to communicate from France
+    with the TA.
+-   **2018-10-31**: New TA analyser (SN 0317-001) was installed with a
+    new membrane inside (completely new technology). Tests were made
+    with Steffen from KM Contros.
+-   **2018-07-31**: TA analyser was received (SN TA-1215-001) and pluged
+    again. First data were received (high: 2450 and low: 2150) but
+    salinity issue since this time. Uwe/Philipp try to find if this
+    comes from comunication issue with the FB.
+-   **2018-06-20**: TA analyser was stopped in order to save reagents
+    because leakage in degasing unit is not solved. Email was sent to
+    Steffen.
+-   **2018-01-05**: TA analyser switched on and first communication
+    tests. S/N TA-0317-001.
+-   **2017-08-23**: The 2 TA analysers were sent to Contros for repair,
+    1 will be sent back to NYA after. No more TA data during this
+    period.
+-   **2017-04-06**: (12:30 UTC) Christelle repaired TA analyser by
+    removing air bubbles in Acid tubings (advices from Steffen).
+-   **2017-04-01**: No more TA data...waiting for a diagnostic by
+    Contros.
 -   **2017-03-31**: (11:00 UTC) Christelle switched on TA analyser.
-- **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on "standby" because of cartridge leakage issue (3 ways connector broken).
+-   **2017-03-30**: (07:30 UTC) Christelle switched TA analyser on
+    "standby" because of cartridge leakage issue (3 ways connector
+    broken).
 -   **2017-03-21**: Philipp changed the TA analyser provided by Contros.
@@
 -   **2017-02-09**: TA calibration with CRM at 12:20.
-- **2017-01-20**: The date issue with TA analyser since 201-01-07 was fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
-- **2016-11-15**: TA calibration done by Christelle with Dickson CRM run as regular sample (measure mode).
-Data of this calibration do not appear on plot because TA analyser is disconnected from the FerryBox.
-- **2016-09-16**: Cleaning of the TA analyser removing all the salt crusts from the bottom of the degazing unit (Samir).
+-   **2017-01-20**: The date issue with TA analyser since 201-01-07 was
+    fixed by Uwe with a restart of the Ferrybox Module around 14:00 UTC.
+-   **2016-11-15**: TA calibration done by Christelle with Dickson CRM
+    run as regular sample (measure mode). Data of this calibration do
+    not appear on plot because TA analyser is disconnected from the
+    FerryBox.
+-   **2016-09-16**: Cleaning of the TA analyser removing all the salt
+    crusts from the bottom of the degazing unit (Samir).
 -   **2016-06-24**: BCG cartridge was changed (Christelle, ObsEng).
@@
 -   **2016-05-01**: No data for TA.
-- **2016-04-26**: Salt crusts inside the TA analyser appeared during deployment (see pictures) were removed by René Burgi (Observatory engineer) according to Contros advices (email from Steffen Assmann 13/04/2016 10:30).
+-   **2016-04-26**: Salt crusts inside the TA analyser appeared during
+    deployment (see pictures) were removed by René Burgi (Observatory
+    engineer) according to Contros advices (email from Steffen Assmann
+    13/04/2016 10:30).
 
 ### **pH seaFET**
-- **2019-09-02**: Out from the water for maintenance and cleaning only.
-- **2018-04-17**: seaFET #1005 was changed on the REMOS and seaFET #007 (from Villefranche) was installed.
-Continuous mode with external power supply was set and internal pack of bateries was removed.
-Old seaFET will be brought back to France with Samir.
-- **2018-03-09**: #007 seaFET currently in USA will be sent by seabird to NYA. #1005 seaFET currently in NYA will be sent to USA for update, following all external issues, for free.
-- **2017-08-24**: seaFET #1005 was installed on the REMOS into the field.
+
+-   **2019-09-02**: Out from the water for maintenance and cleaning
+    only.
+-   **2018-04-17**: seaFET #1005 was changed on the REMOS and seaFET
+    #007 (from Villefranche) was installed. Continuous mode with
+    external power supply was set and internal pack of bateries was
+    removed. Old seaFET will be brought back to France with Samir.
+-   **2018-03-09**: #007 seaFET currently in USA will be sent by seabird
+    to NYA. #1005 seaFET currently in NYA will be sent to USA for
+    update, following all external issues, for free.
+-   **2017-08-24**: seaFET #1005 was installed on the REMOS into the
+    field.
 
 ### **Cross-Flow filter**
-- **2019-01-26**: The filter was lifted up in order to fix the flow problem. 
-- **2018-11-01**: The filter clogged a lot of time even after acid cycles. It was not replaced since its initial installation with the TA analyser. We think to replace it soon.
-- **2016-07-20**: Cross filter was cleanned by Obs. eng. with 10-15 min tape water flush.
+
+-   **2019-01-26**: The filter was lifted up in order to fix the flow
+    problem.
+-   **2018-11-01**: The filter clogged a lot of time even after acid
+    cycles. It was not replaced since its initial installation with the
+    TA analyser. We think to replace it soon.
+-   **2016-07-20**: Cross filter was cleanned by Obs. eng. with 10-15
+    min tape water flush.
 
 ### **durafet**
+
 -   **2019-09-05**: same durafet
-- **2017-10-30**: (13:00 UTC) Durafet holder was changed by Benoit and the new one (made by Uwe) more larger (all the durafet's body is plunge in the seawater) was installed.
+-   **2017-10-30**: (13:00 UTC) Durafet holder was changed by Benoit and
+    the new one (made by Uwe) more larger (all the durafet's body is
+    plunge in the seawater) was installed.
 -   **2017-08-24**: durafet was installed.
 
-### ***p*CO~2~**
-- **2019-09-03**: *p*CO~2~ analyser (S/N: CO2FT-0515-001) have been installed and *p*CO~2~ analyser (S/N: CO2FT-0215-001) was sent to Kiel for calibration.
-- **2018-10-31**: *p*CO~2~ analyser (S/N: CO2FT-0215-001) have been installed and *p*CO~2~ analyser (S/N: CO2FT-0515-001) was brought back to France and waiting 2019 fundings to bring it for calibration.
-- **2018-04-16**: *p*CO~2~ analyser switching by Uwe and Samir. S/N CO2FT-0515-001 is now installed. Old *p*CO~2~ sensor will be brought back to France with Samir.
-- **2017-02-07**: pCO2 analyser switching by Uwe. S/N CO2FT-0215-001 is now installed.
-- **2016-09-13**: Changement of the *p*CO~2~ S/N CO2FT-0515-001 membrane (Uwe from 4H-Jena).
-- **2016-02-28**: *p*CO~2~ analyser (S/N CO2FT-0215-001) was sent to calibration and the second *p*CO~2~ analyser (S/N: CO2FT-0515-001) have been installed.
-
-<div style="text-align:center" markdown="1">
-<img  src="./Images/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200">
-<img  src="./Images/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200">
-</div>
+### ***p*****CO~2~**
+
+-   **2019-09-03**: *p*CO~2~ analyser (S/N: CO2FT-0515-001) have been
+    installed and *p*CO~2~ analyser (S/N: CO2FT-0215-001) was sent to
+    Kiel for calibration.
+-   **2018-10-31**: *p*CO~2~ analyser (S/N: CO2FT-0215-001) have been
+    installed and *p*CO~2~ analyser (S/N: CO2FT-0515-001) was brought
+    back to France and waiting 2019 fundings to bring it for
+    calibration.
+-   **2018-04-16**: *p*CO~2~ analyser switching by Uwe and Samir. S/N
+    CO2FT-0515-001 is now installed. Old *p*CO~2~ sensor will be brought
+    back to France with Samir.
+-   **2017-02-07**: pCO2 analyser switching by Uwe. S/N CO2FT-0215-001
+    is now installed.
+-   **2016-09-13**: Changement of the *p*CO~2~ S/N CO2FT-0515-001
+    membrane (Uwe from 4H-Jena).
+-   **2016-02-28**: *p*CO~2~ analyser (S/N CO2FT-0215-001) was sent to
+    calibration and the second *p*CO~2~ analyser (S/N: CO2FT-0515-001)
+    have been installed.
+
+::: {style="text-align:center" markdown="1"}
+<img src="./Images/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200"/>
+<img src="./Images/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200"/>
+:::
 
 ## Script + data
+
 <div style="text-align: justify">
+
 Here is reported all important modifications made on *ny-alesund_cc.*.
-All documents concerning maintenance, tasks to do, calibration... are accessible by the AWIPEV staff on this link with special access:
+All documents concerning maintenance, tasks to do, calibration... are
+accessible by the AWIPEV staff on this link with special access:
 
@@
 
-[Logbook discrete sampling](https://docs.google.com/spreadsheets/d/1bNh9q4bkNoh2ra78XC451EmGb9Q8kMf4ByBnKngeHOg/edit#gid=1034421443)
-
-[Logbook FerryBox](https://docs.google.com/spreadsheets/d/1QwAJm7TttoEwue-CUM0efhqEAMwj5m148Gy_Mp-1maM/edit?ts=5ed0fca6#gid=2036495380)
-
-[UWO-Ferrybox variables from our sensors](https://docs.google.com/spreadsheets/d/1arKYfUjmg3YrgQ5g9LN_XFwUORyz7nqlKNWq3uYok3U/edit?ts=5c7e1d16#gid=393659093)
+[Logbook discrete
+sampling](https://docs.google.com/spreadsheets/d/1bNh9q4bkNoh2ra78XC451EmGb9Q8kMf4ByBnKngeHOg/edit#gid=1034421443)
+
+[Logbook
+FerryBox](https://docs.google.com/spreadsheets/d/1QwAJm7TttoEwue-CUM0efhqEAMwj5m148Gy_Mp-1maM/edit?ts=5ed0fca6#gid=2036495380)
+
+[UWO-Ferrybox variables from our
+sensors](https://docs.google.com/spreadsheets/d/1arKYfUjmg3YrgQ5g9LN_XFwUORyz7nqlKNWq3uYok3U/edit?ts=5c7e1d16#gid=393659093)
 
@@
 
-[Procedure to download NRT data](https://spaces.awi.de/confluence/display/MOS/NRT+data+download+procedures)
-
-[AWI NRT database](https://dashboard.awi.de/data-xxl/), search for svluwobs
-
-[Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736)
+[Procedure to download NRT
+data](https://spaces.awi.de/confluence/display/MOS/NRT+data+download+procedures)
+
+[AWI NRT database](https://dashboard.awi.de/data-xxl/), search for
+svluwobs
+
+[Quick overview AWI NRT
+database](https://dashboard.awi.de/?dashboard=9736)
 
 ### **FerryBox**
+
 -   **2020-03-13**: Salinity was filtered above 28 in d_all.rds file.
-- **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a), that means that one column (CHl_A_Cyclops) was also removed from the Ferrybox data file. Script was modified in consequence.
+-   **2018-11-14**: One instrument was removed by Uwe (Chlorophyl-a),
+    that means that one column (CHl_A\_Cyclops) was also removed from
+    the Ferrybox data file. Script was modified in consequence.
 
 ### **pH seaFET**
-- **2018-08-30**: voltINT + phINT were filtered from 2017-12-14 to 2018-01-08 and bad data were removed from 2018-01-08 to 2018-02-02.
-pH spectro from 2018-04-16 07:00:00 was fitted with a mean of 4 days of voltINT in order to make the calibration for this 5th period.
-- **2018-07-30**: Flag location (location_flag) is added in the script to localize seaFET/durafet discrete samples: flag 1 = at the harbor (not taken in consideration) and flag 0 = in the FB for durafet or on site for seaFET (takken in consideration as "normal" sampling").
+
+-   **2018-08-30**: voltINT + phINT were filtered from 2017-12-14 to
+    2018-01-08 and bad data were removed from 2018-01-08 to 2018-02-02.
+    pH spectro from 2018-04-16 07:00:00 was fitted with a mean of 4 days
+    of voltINT in order to make the calibration for this 5th period.
+-   **2018-07-30**: Flag location (location_flag) is added in the script
+    to localize seaFET/durafet discrete samples: flag 1 = at the harbor
+    (not taken in consideration) and flag 0 = in the FB for durafet or
+    on site for seaFET (takken in consideration as "normal" sampling").
     See seaFET part.
-- **2018-02-02**: Based on Darrell's advices (SeaBird), Philipp implemented the seaFET as: 1h periodic sampling with the following commands: perdival 1h, navg 5, brstsize 1, opermode periodic. 
-- **2017-12-29**: "SVL_20171218_010426.dat" from seaFet data was deleted because of bug with its size (0 octect). pH filter was added to "ny_alesund_cc" file for seaFet data (<7.5 and <8.5).
+-   **2018-02-02**: Based on Darrell's advices (SeaBird), Philipp
+    implemented the seaFET as: 1h periodic sampling with the following
+    commands: perdival 1h, navg 5, brstsize 1, opermode periodic.
+-   **2017-12-29**: "SVL_20171218_010426.dat" from seaFet data was
+    deleted because of bug with its size (0 octect). pH filter was added
+    to "ny_alesund_cc" file for seaFet data (\<7.5 and \<8.5).
 
 ### **Durafet**
-- Reference spectro measurement from the 2019-01-18 11:00 do not match with a durafet raw data because Ferrybox was off.
-This reference point was not takken in consideration for calibration.
-The window of the previous and next calibration periods was extended.
-
-### ***p*CO~2~**
-- **2020-03-11**: Post calibration parameters for period 4 (2018-04-16 to 2018-10-31) were not taken in consideration because they lead to wrong correction.
-- **2019-11-18**: Calibration parameters from #0215-001 were added to "server.../data/NRT_data/Data_Processing_sheet_pCO2.csv" (new path).
-- **2018-08-29**: Calibration parameters from #0215-001 were added to "./data/Calibration_pCO2/Data_Processing_sheet_pCO2.csv".
-- **2018-04-20**: For *p*CO~2~ Calibration the previous period (N° 4) was added to the script "ny-alesund_cc" line 466.
-- **2015-10-13**: we put back the spike.pCO2 to 600 because data in October reached more than 350 µAtm. We let this like that and we are going to deal with it manually later if needed.
-- **2015-09-28**: we put the spike.pCO2 (detection of peaks: threshold) at 350 to remove anomalies on the 12 and 15 September. We have to monitor data. If data reach this value, then problem.
+
+-   Reference spectro measurement from the 2019-01-18 11:00 do not match
+    with a durafet raw data because Ferrybox was off. This reference
+    point was not takken in consideration for calibration. The window of
+    the previous and next calibration periods was extended.
+
+### ***p*****CO~2~**
+
+-   **2020-03-11**: Post calibration parameters for period 4 (2018-04-16
+    to 2018-10-31) were not taken in consideration because they lead to
+    wrong correction.
+-   **2019-11-18**: Calibration parameters from #0215-001 were added to
+    "server.../data/NRT_data/Data_Processing_sheet_pCO2.csv" (new path).
+-   **2018-08-29**: Calibration parameters from #0215-001 were added to
+    "./data/Calibration_pCO2/Data_Processing_sheet_pCO2.csv".
+-   **2018-04-20**: For *p*CO~2~ Calibration the previous period (N° 4)
+    was added to the script "ny-alesund_cc" line 466.
+-   **2015-10-13**: we put back the spike.pCO2 to 600 because data in
+    October reached more than 350 µAtm. We let this like that and we are
+    going to deal with it manually later if needed.
+-   **2015-09-28**: we put the spike.pCO2 (detection of peaks:
+    threshold) at 350 to remove anomalies on the 12 and 15 September. We
+    have to monitor data. If data reach this value, then problem.
 
 ### **SNAPO**
-- **2020-01-23**: Freezed and lost samples because of heater issue in the container: 15/11/2019 (durafet x1), 03/12/2019 (FB x2), 11/12/2019 (FB x2), 13/12/2019 (FB x2), 20/12/2019 (FB x2), 03/01/2020 (FB x2).
-Following samples could have been frozen, not sure: 06/09/2019 (FB x2), 13/09/2019 (seaFET x1), 13/09/2019 (FB x2), 20/09/2019 (FB x1), 27/09/2019(FB x2), 04/10/2019 (FB x2), 11/10/2019 (FB x1), 11/10/2019  (durafet x1), 25/10/2019 (FB x2), 01/11/2019 (FB x1), 15/11/2019 (FB x1).
-
-- **2020-01-15**: Results from 2019-04-19 to 2019-08-31 (sent in September 2019) were received.
-FB duplicates from 2019-08-09 were analysed as Durafet because of wrong box.
-One sample from 2019-06-07 (durafet) was analysed by Paris because of wrong box.
-- **2019-04-30**: Duplicate "Ferrybox" samples (SN0316 and SN264, 2019-02-22 14:05) were sent by mistake in Villefranche for pH measurements.
-Those results were put in the datafile as "durafet" samples as soon as they are comming from the Ferrybox tape seawater.
-We will add a lack of DIC for this week.
-TA will be measured in Villefranche.
-- **2018-08-30**: flag of 1 AT duplicate (2205) from 2017-08-31 was put to 3 (dosage douteux).
+
+-   **2020-01-23**: Freezed and lost samples because of heater issue in
+    the container: 15/11/2019 (durafet x1), 03/12/2019 (FB x2),
+    11/12/2019 (FB x2), 13/12/2019 (FB x2), 20/12/2019 (FB x2),
+    03/01/2020 (FB x2). Following samples could have been frozen, not
+    sure: 06/09/2019 (FB x2), 13/09/2019 (seaFET x1), 13/09/2019 (FB
+    x2), 20/09/2019 (FB x1), 27/09/2019(FB x2), 04/10/2019 (FB x2),
+    11/10/2019 (FB x1), 11/10/2019 (durafet x1), 25/10/2019 (FB x2),
+    01/11/2019 (FB x1), 15/11/2019 (FB x1).
+
+-   **2020-01-15**: Results from 2019-04-19 to 2019-08-31 (sent in
+    September 2019) were received. FB duplicates from 2019-08-09 were
+    analysed as Durafet because of wrong box. One sample from 2019-06-07
+    (durafet) was analysed by Paris because of wrong box.
+
+-   **2019-04-30**: Duplicate "Ferrybox" samples (SN0316 and SN264,
+    2019-02-22 14:05) were sent by mistake in Villefranche for pH
+    measurements. Those results were put in the datafile as "durafet"
+    samples as soon as they are comming from the Ferrybox tape seawater.
+    We will add a lack of DIC for this week. TA will be measured in
+    Villefranche.
+
+-   **2018-08-30**: flag of 1 AT duplicate (2205) from 2017-08-31 was
+    put to 3 (dosage douteux).
 
 ### **Files - server**
-- **2019-11-15**: Script including the new data downloading from the NRT AWI database is running (ny-alesund_cc.R).
-From this date, data are donwloaded from AWI NRT dtabase.
-We are waiting some setting from Philipp to have the entire dataset.
-Only 2018-2019 are available for the moment.
-New path was created in the server and pCloud/exp168 with "NRT_data" file.
-Please see the picture bellow.
-- **2018-04-19**: Since "Ferrybox" is on again, the adding to solve the files issues are making not data into d_hour for this period (2018-09-03 to 2018-14-04).
-This adding was put in comments now.
-In seaFET data reading, S/N have been changed from 1005 to 0007.
-- **2018-03-21**: Files issues.
-FerryBox instruments are down because of freezing but UWO instrument as seaFET and SBE38 are OK.
-Removing of one 0 octet file from seaFET20180317_1404 and put back seaFET files from 20180309 to 20180312 in seaFET folder.
-They were in SBE38 folder...Weird.
-Additionnal script lines were added in order to deal with the issue of "in situ" created date whereas "Ferrybox" created data ware not.
-Since "in situ" parameters are running (d df) and not "in ferrybox" parameters (z df), the new datetime lines are not taking in consideration with the left_join function we have to add them during Ferrybox shutdown.
-- **2018-03-09**: Script issue solved with first negative values encountred in SBE38 files. We find a regex solution to take "space + space or negative value" in consideration.
-- **2017-11-07**: Wrong seaFET files (wrong datetime starting on the 5th September) from 24 to 26 October were fixed.
-File "SVL_20171024_030426_to_20171026_110425_SeaFet-1005.txt" were created in SeaFet_archive.
+
+-   **2019-11-15**: Script including the new data downloading from the
+    NRT AWI database is running (ny-alesund_cc.R). From this date, data
+    are donwloaded from AWI NRT dtabase. We are waiting some setting
+    from Philipp to have the entire dataset. Only 2018-2019 are
+    available for the moment. New path was created in the server and
+    pCloud/exp168 with "NRT_data" file. Please see the picture bellow.
+-   **2018-04-19**: Since "Ferrybox" is on again, the adding to solve
+    the files issues are making not data into d_hour for this period
+    (2018-09-03 to 2018-14-04). This adding was put in comments now. In
+    seaFET data reading, S/N have been changed from 1005 to 0007.
+-   **2018-03-21**: Files issues. FerryBox instruments are down because
+    of freezing but UWO instrument as seaFET and SBE38 are OK. Removing
+    of one 0 octet file from seaFET20180317_1404 and put back seaFET
+    files from 20180309 to 20180312 in seaFET folder. They were in SBE38
+    folder...Weird. Additionnal script lines were added in order to deal
+    with the issue of "in situ" created date whereas "Ferrybox" created
+    data ware not. Since "in situ" parameters are running (d df) and not
+    "in ferrybox" parameters (z df), the new datetime lines are not
+    taking in consideration with the left_join function we have to add
+    them during Ferrybox shutdown.
+-   **2018-03-09**: Script issue solved with first negative values
+    encountred in SBE38 files. We find a regex solution to take "space +
+    space or negative value" in consideration.
+-   **2017-11-07**: Wrong seaFET files (wrong datetime starting on the
+    5th September) from 24 to 26 October were fixed. File
+    "SVL_20171024_030426_to_20171026_110425_SeaFet-1005.txt" were
+    created in SeaFet_archive.
 
 ### Data processing
-#### Script ny-alesund_cc.R which runs on awipev@awipev-co2.obs-vlfr.fr
-* reads data from the AWI NRT database [Quick overview AWI NRT database](https://dashboard.awi.de/?dashboard=9736) 
-* calibrates pCO2 data
-* data cleaning:
-  + Argo Global Range Test.
-  + filter salinities above 28
-  + filter temperatures above 10
-  + filter seaFET Volt (outliers)
-  + filter seaFET pH (outliers)
-  + filter durafet (outliers)
-* Quality flags
-    + 1: good data
-    + 3: impossible date and time test
-    + 4: data not usable according to manufacturer (flush mode, zero mode, calibration mode...) 
-    + 6: failing the manufacturer range test (not used)
-    + 7: failing the regional range test 
-    + 12: failing the spike test (NAs from despike)
-    + 13: failing the gradient test
-    + 15: the instrument was not deployed or operated
-    + 16: acid flush
-    + 99: failing the final visual inspection of the data. 
-* Despike using oce::despike with n=2, k=5761
-* Files generated:
-    + previous_NRT_data.rds: all NRT data without alteration from the beginning (2015)
-    + all_nydata_minute.rds: all data after filtering and despike describe above (every minute)
-    + all_nydata_hour.rds: hourly means of all data after filtering and despike describe above (every minute)
-    + nydata_minute.rds: selected data after filtering and despike describe above (every minute). **Useful?**
-    + nydata_hour.rds: selected hourly means of all data after filtering and despike describe above (every minute).  This is for further data processing.
+
+#### Script ny-alesund_cc.R which runs on [awipev\@awipev-co2.obs-vlfr.fr](mailto:awipev@awipev-co2.obs-vlfr.fr){.email}
+
+-   reads data from the AWI NRT database [Quick overview AWI NRT
+    database](https://dashboard.awi.de/?dashboard=9736)
+
+-   calibrates pCO2 data
+
+-   data cleaning:
+
+    -   Argo Global Range Test.
+    -   filter salinities above 28
+    -   filter temperatures above 10
+    -   filter seaFET Volt (outliers)
+    -   filter seaFET pH (outliers)
+    -   filter durafet (outliers)
+
+-   Quality flags
+
+    -   1: good data
+    -   3: impossible date and time test
+    -   4: data not usable according to manufacturer (flush mode, zero
+        mode, calibration mode...)
+    -   6: failing the manufacturer range test (not used)
+    -   7: failing the regional range test
+    -   12: failing the spike test (NAs from despike)
+    -   13: failing the gradient test
+    -   15: the instrument was not deployed or operated
+    -   16: acid flush
+    -   99: failing the final visual inspection of the data.
+
+-   Despike using oce::despike with n=2, k=5761
+
+-   Files generated:
+
+    -   previous_NRT_data.rds: all NRT data without alteration from the
+        beginning (2015)
+    -   all_nydata_minute.rds: all data after filtering and despike
+        describe above (every minute)
+    -   all_nydata_hour.rds: hourly means of all data after filtering
+        and despike describe above (every minute)
+    -   nydata_minute.rds: selected data after filtering and despike
+        describe above (every minute). **Useful?**
+    -   nydata_hour.rds: selected hourly means of all data after
+        filtering and despike describe above (every minute). This is for
+        further data processing.
 
 #### Script awipev-co2.Rmd which runs locally
-* reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
-* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_10m)
-* sal_mix_interp: interpolated salinity sal_mix. It is used to have as many spec pH to display (some are during missing data)
-* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
-* temp_mix_interp: interpolated temperature temp_mix. It is used to have as many spec pH to display (some are during missing data)
-* pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
-* calibrate seafet pH
-    - ph_s_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
-    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_10m si trous) + temp CTD 10m + sal CTD 10m (calib seaFET fonction 1)
-    - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
-* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
-* despike pH seaFET
-* calibrate durafet pH
-    - ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
-* Relation at / sal_mix 
-* at_calc: calculé from sal_mix
-* saves locally d_all.rds which comprises all variables plus those generated in the script
+
+-   reads locally
+    fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
+
+-   sal_mix: when ferrybox data (sal_fb) are missing, they are replaced
+    by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_10m)
+
+-   sal_mix_interp: interpolated salinity sal_mix. It is used to have as
+    many spec pH to display (some are during missing data)
+
+-   temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m)
+    are missing, they are replaced by data from the profiling ctd for
+    depths > 8 m
+
+-   temp_mix_interp: interpolated temperature temp_mix. It is used to
+    have as many spec pH to display (some are during missing data)
+
+-   pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb
+    +sal_fb
+
+-   calibrate seafet pH
+
+    -   ph_s\_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT
+        interpolée + temp_mix +sal_mix
+    -   E0int25_sf: calculé à partir du voltage interne +
+        ph_s\_sf_temp_insi (temp 11m + temp_insitu_ctd_10m si trous) +
+        temp CTD 10m + sal CTD 10m (calib seaFET fonction 1)
+    -   phint_tot_sf: calculé à partir du voltage interne + E0 + temp
+        CTD + sal CTD (calib seaFET fonction 2)
+
+-   ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
+
+-   despike pH seaFET
+
+-   calibrate durafet pH
+
+    -   ph_s\_dur_temp_fb: pH spectro durafet pH insi calculé avec AT
+        interpolée + temp_fb +sal_fb
+
+-   Relation at / sal_mix
+
+-   at_calc: calculé from sal_mix
+
+-   saves locally d_all.rds which comprises all variables plus those
+    generated in the script
 
@@
 
-* Serveur : awipev-co2 (193.50.85.104)
-* 3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour l’envoi des données par P. Fischer mais n'est plus utilisé).
-* Pour se connecter à awipev-co2.obs-vlfr.fr
-    + ssh awipev@awipev-co2.obs-vlfr.fr
-* Intervention sur le serveur :
-    + ssh awipev@awipev-co2.obs-vlfr.fr
-    + rebooting Ubuntu server: sudo shutdown -r now
-    + to check versions:
-        - dpkg -l | grep shiny
-        - dpkg -l | grep r-base
-    + To update Ubuntu, R and its packages:
+-   Serveur : awipev-co2 (193.50.85.104)
+
+-   3 comptes: awipev (partagé avec Samir), gattuso, nydata (pour
+    l'envoi des données par P. Fischer mais n'est plus utilisé).
+
+-   Pour se connecter à awipev-co2.obs-vlfr.fr
+
+    -   ssh
+        [awipev\@awipev-co2.obs-vlfr.fr](mailto:awipev@awipev-co2.obs-vlfr.fr){.email}
+
+-   Intervention sur le serveur :
+
+    -   ssh
+        [awipev\@awipev-co2.obs-vlfr.fr](mailto:awipev@awipev-co2.obs-vlfr.fr){.email}
+
+    -   rebooting Ubuntu server: sudo shutdown -r now
+
+    -   to check versions:
+
+        -   dpkg -l \| grep shiny
+        -   dpkg -l \| grep r-base
+
+    -   To update Ubuntu, R and its packages:
+
         -   sudo su
         -   apt-get upgrade
-    + To restart shiny server: sudo systemctl restart shiny-server
-        - update shiny server: follow procedure detailed on the shiny web page Data processing
-* To install R packages:
-    + ssh gattuso@awipev-co2.obs-vlfr.fr
-    + sudo R (then password)
-    + install.packages("tidyverse")
-
-**crontab awipev@awipev-co2.obs-vlfr.fr**
-
-si on veut remplacer intégralement les fichiers de pCloud par ceux de awipev-co2 : ajouter “--delete” à la commande rsync.
-Pattern des commandes : # m h dom mon dow command
-
-* (Every 4 hour on the hour, a crontab action runs automatically the script ny-alesund/R/ny-alesund_cc.R. This script essentially appends the daily files from AWI-NRT database and cleans the data)
-    + 00 *//1 * * * cd $HOME; USER=awipev R --vanilla < ny-alesund/R/ny-alesund_cc.R > ny-alesund/R/log_ny-alesund_cc.txt 2>&1
-* (Every 4 hour at 10 min past the hour, the web page is generated)
-    + 10 *//1 * * * cd web; USER=awipev bash awipev-co2.sh > awipev-web.log 2>&1 
-* (At 05:00 the files from server/web are copied to gattuso’s iMac in pCloud ... Exp168)
-    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/web 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
-* (At 05:00 the files from server/ny-alesund are copied to gattuso’s iMac in pCloud/Exp168)
-    + 00 05 * * * /usr/bin/rsync -e "ssh -o StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund 'gattuso@gattuso.obs-vlfr.fr:/Users/gattuso/pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
+
+    -   To restart shiny server: sudo systemctl restart shiny-server
+
+        -   update shiny server: follow procedure detailed on the shiny
+            web page Data processing
+
+-   To install R packages:
+
+    -   ssh
+        [gattuso\@awipev-co2.obs-vlfr.fr](mailto:gattuso@awipev-co2.obs-vlfr.fr){.email}
+    -   sudo R (then password)
+    -   install.packages("tidyverse")
+
+**crontab
+[awipev\@awipev-co2.obs-vlfr.fr](mailto:awipev@awipev-co2.obs-vlfr.fr){.email}**
+
+si on veut remplacer intégralement les fichiers de pCloud par ceux de
+awipev-co2 : ajouter "--delete" à la commande rsync. Pattern des
+commandes : \# m h dom mon dow command
+
+-   (Every 4 hour on the hour, a crontab action runs automatically the
+    script ny-alesund/R/ny-alesund_cc.R. This script essentially appends
+    the daily files from AWI-NRT database and cleans the data)
+
+    -   00 *//1*  \* \* cd \$HOME; USER=awipev R --vanilla \<
+        ny-alesund/R/ny-alesund_cc.R >
+        ny-alesund/R/log_ny-alesund_cc.txt 2>&1
+
+-   (Every 4 hour at 10 min past the hour, the web page is generated)
+
+    -   10 *//1*  \* \* cd web; USER=awipev bash awipev-co2.sh >
+        awipev-web.log 2>&1
+
+-   (At 05:00 the files from server/web are copied to gattuso's iMac in
+    pCloud ... Exp168)
+
+    -   00 05 \* \* \* /usr/bin/rsync -e "ssh -o
+        StrictHostKeyChecking=no" -avh /home/awipev/web
+        '[gattuso\@gattuso.obs-vlfr.fr](mailto:gattuso@gattuso.obs-vlfr.fr){.email}:/Users/gattuso/pCloud Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
+
+-   (At 05:00 the files from server/ny-alesund are copied to gattuso's
+    iMac in pCloud/Exp168)
+
+    -   00 05 \* \* \* /usr/bin/rsync -e "ssh -o
+        StrictHostKeyChecking=no" -avh /home/awipev/ny-alesund
+        '[gattuso\@gattuso.obs-vlfr.fr](mailto:gattuso@gattuso.obs-vlfr.fr){.email}:/Users/gattuso/pCloud Sync/Documents/experiments/exp168_awipev-CO2/fb_awipev-co2_server/'
 
@@
 
-* La page web index.html est faite sur le serveur awipev/web grâce au script awipev-CO2_web.Rmd puis transférée et renommée dans awipev/awipev-CO2_web
-* Création du répertoire web qui contient ce qu’il faut pour générer la page web:
-    + AWIPEV-Logo.jpg
-    + Discrete_sampling_AWIPEV.csurv
-    + awipev-CO2_web.Rmd
-    + awipev-co2.sh (lancer par bash awipev-co2.sh)
-* Accessible https://awipev-co2.obs-vlfr.fr 
-* On utilise un shell script awipev-co2.sh :
+-   La page web index.html est faite sur le serveur awipev/web grâce au
+    script awipev-CO2_web.Rmd puis transférée et renommée dans
+    awipev/awipev-CO2_web
+
+-   Création du répertoire web qui contient ce qu'il faut pour générer
+    la page web:
+
+    -   AWIPEV-Logo.jpg
+    -   Discrete_sampling_AWIPEV.csurv
+    -   awipev-CO2_web.Rmd
+    -   awipev-co2.sh (lancer par bash awipev-co2.sh)
+
+-   Accessible <https://awipev-co2.obs-vlfr.fr>
+
+-   On utilise un shell script awipev-co2.sh :
 
@@
 
-    # script de lancement via crontab echo '---------deb awipev-co2.sh -----------'
-
-    # On lance la fabrication du html (une seule ligne)
-    cd web; R -e 'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")'; cp awipev-CO2_web.html ../awipev-CO2_web/index.html
+    \# script de lancement via crontab echo '---------deb awipev-co2.sh
+    -----------'
+
+    \# On lance la fabrication du html (une seule ligne) cd web; R -e
+    'library("rmarkdown");library("knitr");rmarkdown::render("awipev-CO2_web.Rmd")';
+    cp awipev-CO2_web.html ../awipev-CO2_web/index.html
 
@@
 
-* ssh awipev@awipev-co2.obs-vlfr.fr
-* cd; bash web/awipev-co2.sh
-
-![ ](Images/awipev_server_arborescence.jpg){width=65%}
+-   ssh
+    [awipev\@awipev-co2.obs-vlfr.fr](mailto:awipev@awipev-co2.obs-vlfr.fr){.email}
+-   cd; bash web/awipev-co2.sh
+
+![](Images/awipev_server_arborescence.jpg){width="65%"}

### 2021-12-23 awipev-CO2.Rmd
pH is OK, normalized too, working on Philipp's Pangaea files

@@
 output:
+  pdf_document: default
+  word_document: default
   html_document: default
-  word_document: default
-  pdf_document: default
   odt_document: default
@@
 library(oce)
+if (!require("pangaear")) install.packages("pangaear")
+library("pangaear")
 
@@
 
+# # Many issue with sal_ctd_insi
+# # read files made available by Philipp with  quality-controlled data
+# https://doi.org/10.1594/PANGAEA.929583
+# pg_data("10.1594/PANGAEA.929583")
+
 # check_plot <- d_hour %>% 
@@
 
+knitr::kable(quantile(x = tmp$range_diff, na.rm = TRUE), digits = 1, col.names = "Salinity (unit)", caption = "Quantiles salinity gradient between 0-2 m and > 8 m", format = "html", table.attr = "style='width:30%;'") %>% kableExtra::kable_classic(full_width = TRUE, position = "center")
+
 p_sal_range <- ggplot(data = tmp) +
@@
 
-kable(quantile(x = tmp$range_diff, na.rm = TRUE), digits = 2, col.names = "Sal. unit", caption = "Quantiles salinity gradient between 0-2 m and > 8 m")
 rm(sal_xts)
@@
   dplyr::filter(!is.na(deployment_sf))
-names(calib_spectro_all) <- c("deployment_sf", "E0int25_sf", "E0ext25_sf")
+names(calib_spectro_all) <- c("deployment_sf", "E0int25_sf_all", "E0ext25_sf_all")
 
@@
 
-Below are the seafet calibration parameters using all data (irrespective
-of the depth of the seafet) and with the seafet data collected below 8
-m. They are very close but we nevertheless use the calibration data
-below 8 m (easier to explain in the manuscript).
+Below are the seafet calibration parameters using all data (irrespective of the depth of the seafet) and with the seafet data collected below 8 m.
+They are very close but we nevertheless use the calibration data below 8 m (easier to explain in the manuscript).
 
@@
 #### calculation of the calibrated pH with all data irrespective of the depth of the REMOS ####
-seafet_calib_all <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf,  E0ext25 = d_all$E0ext25_sf, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
+seafet_calib_all <- sf_calc(calEint = d_all$voltINT, calEext = d_all$voltEXT, E0int25 = d_all$E0int25_sf_all,  E0ext25 = d_all$E0ext25_sf_all, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
 # bind new calibrated pH data to the seafet data set.
@@
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
-dygraph(seafet_depth_xts, group = "depth", main="pH seaFET", ylab="pHT") %>%
+dygraph(seafet_depth_xts, group = "depth", main="Spec pH and seaFET pH at all depths (calibrated using all data, irrespective of the depth of the seafet)", ylab="pHT") %>%
 dySeries("pHint_tot_sf_all_10m", label = "pHT 10m", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 1) %>%
@@
 seafet_depth_xts <- as.xts(seafet_depth_xts, order.by = d_all$datetime)
-dygraph(seafet_depth_xts, group = "depth", main="Spec pH and calibrated seaFET pH at 10 m", ylab="pHT") %>%
+dygraph(seafet_depth_xts, group = "depth", main="Spec pH and seaFET pH at 10 m (calibrated with 10 mdata only)", ylab="pHT") %>%
 dySeries("pHint_tot_sf_10m", label = "pH calib 10m", color =  "black", strokeWidth = 0, pointSize = 1) %>%
@@
 
--   Offset between calibrated seaFET data and pH spectro. The offset
-    must fit between -0.2/0.2 pH units.
-
-"differences between calibrated sensor pH values and values obtained
-from discrete, check samples can be expected to be as small as 0.02 pH
-units, and perhaps less." (McLaughlin et al. 2017).
+Offset between calibrated seaFET data and pH spectro.
+The offset must be between -0.2 and 0.2 pH units.
+"differences between calibrated sensor pH values and values obtained from discrete, check samples can be expected to be as small as 0.02 pH units, and perhaps less." (McLaughlin et al.
+2017).
 
@@
 ```
-
-#- pH INT - pH EXT was plotted here.
 
@@
 
-From now on, one uses seaFET pH from the internal electrode calibrated
-with spec pH and seaFET data when the REMOS was below 8 m
-(pHint_tot_sf_10m). This unique pH variable is called pHint_tot_sf. All
-other pH variables are cleaned up
+pH INT - pH EXT was plotted here. From now on, one uses seaFET pH from the internal electrode calibrated
+with spec pH and seaFET data when the REMOS was below 8 m (pHint_tot_sf_10m).
+This unique pH variable is called pHint_tot_sf.
+All other pH variables are cleaned up.
+We also calculate pHint_tot_sf.
+at 4°C: pHint_tot_sf_temp_4.
 
@@
 
-```
-
-### **seaFET pH profiles**
-
-```{r seafet profiles, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-
-# we look at all depths
+# normalized seafet pH 4°C and remove sf biofouling period
 tmp <- d_all %>%
-  dplyr::select(year, montht, pHint_tot_sf, depth_group) %>%
-  tidyr::drop_na(pHint_tot_sf, depth_group) %>%
-  dplyr::group_by(depth_group, year, montht)
-summary(aov(tmp$pHint_tot_sf ~ tmp$depth_group * tmp$montht))
-p <- tmp %>%
-  ggplot(aes(x = depth_group, y = pHint_tot_sf)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, coef = 1.5) +
-  labs(title = "pHT", x = "Depth (m)", y= "pHT seaFET at in situ temperature") +
-#  lims(y = c(7.4, 8.3)) +
-  coord_cartesian() +
-  facet_wrap(vars(montht), scale = "fixed")
-print(p)
-
-# we look at 0 to 4 m vs more than 8 m
-tmp <- d_all %>% 
-  dplyr::select(montht, pHint_tot_sf, depth) %>%
-  dplyr::mutate(depth2 = as.factor(dplyr::case_when(depth < 4 ~ '0-4', 
-                                             depth > 8 ~ '8-12'))) %>% 
-  dplyr::filter(depth2 == '0-4' | depth2 == '8-12') %>% 
-  dplyr::group_by(depth2, montht)
-summary(aov(tmp$pHint_tot_sf ~ tmp$depth2 * tmp$montht))
-
-p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth2), y = pHint_tot_sf)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "pHT", x = "Depth (m)", y= "pHT seaFET at in situ temperature") +
-  facet_wrap(vars(montht), scale = "free_y")
-print(p)
-
-# we look at 0 to 4 m vs more than 8 m but pH at 4°C
-
-```
-
-**Conclusion**: The range is significantly larger during some months
-when the data deeper than 8 m are considered. Also, pH is sometimes
-higher at the surface, at other times it is higher on the bottom (June).
-No data are available at 1 m (actually 0 to 2 m). So, to compare surface
-and bottom, I combine 1 and 3 m (0 to 4 m) and 9 m (below 8 m).
-
-Depth and month of the year have a statistically significant effect on
-pH. The interaction is also significant, indicating that the effect of
-depth differs depending on the month.
-
--   To compare with pCO2/pCO2 measured in the Ferrybox seems therefore
-    better to stick with pH_10m, that is at depths deeper than 8 m.
--   pCO2 would have the same behaviour as pH. For air-sea CO2 fluxes,
-    one should use data from 0 to 4 m.
+  dplyr::select(datetime, depth, at, sal_insitu_ctd, temp_sf, pHint_tot_sf) %>%
+  tidyr::drop_na() %>%
+  dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
+tmp$pHint_tot_sf_temp_4 <- seacarb::pHinsi(pH=tmp$pHint_tot_sf, ALK=mean(tmp$at*1e-6, na.rm=TRUE), Tinsi=4, Tlab=tmp$temp_sf, Pinsi=tmp$depth/10, S=tmp$sal_insitu_ctd, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+d_all <- d_all %>% 
+  left_join(tmp %>% dplyr::select(datetime, pHint_tot_sf_temp_4), by="datetime")
+```
+
+<!-- ### **seaFET pH profiles** -->
+
+```{r seafet profiles, eval=FALSE, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+
+# # we look at all depths
+# tmp <- d_all %>% 
+#   dplyr::select(year, montht, pHint_tot_sf, depth_group) %>%
+#   tidyr::drop_na(pHint_tot_sf, depth_group) %>%
+#   dplyr::group_by(depth_group, year, montht)
+# summary(aov(tmp$pHint_tot_sf ~ tmp$depth_group * tmp$montht))
+# p <- tmp %>%
+#   ggplot(aes(x = depth_group, y = pHint_tot_sf)) +
+#   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, coef = 1.5) +
+#   labs(title = "pHT", x = "Depth (m)", y= "pHT seaFET at in situ temperature") +
+# #  lims(y = c(7.4, 8.3)) +
+#   coord_cartesian() +
+#   facet_wrap(vars(montht), scale = "fixed")
+# print(p)
+# 
+# # we look at 0 to 4 m vs more than 8 m
+# tmp <- d_all %>% 
+#   dplyr::select(montht, pHint_tot_sf, depth) %>%
+#   dplyr::mutate(depth2 = as.factor(dplyr::case_when(depth < 4 ~ '0-4', 
+#                                              depth > 8 ~ '8-12'))) %>% 
+#   dplyr::filter(depth2 == '0-4' | depth2 == '8-12') %>% 
+#   dplyr::group_by(depth2, montht)
+# summary(aov(tmp$pHint_tot_sf ~ tmp$depth2 * tmp$montht))
+# 
+# p <- tmp %>% 
+#   ggplot(aes(x=as.factor(depth2), y = pHint_tot_sf)) +
+#   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+#   labs(title = "pHT", x = "Depth (m)", y= "pHT seaFET at in situ temperature") +
+#   facet_wrap(vars(montht), scale = "free_y")
+# print(p)
+# 
+# # we look at 0 to 4 m vs more than 8 m but pH at 4°C
+
+```
+
+<!-- **Conclusion**: The range is significantly larger during some months -->
+<!-- when the data deeper than 8 m are considered. Also, pH is sometimes -->
+<!-- higher at the surface, at other times it is higher on the bottom (June). -->
+<!-- No data are available at 1 m (actually 0 to 2 m). So, to compare surface -->
+<!-- and bottom, I combine 1 and 3 m (0 to 4 m) and 9 m (below 8 m). -->
+
+<!-- Depth and month of the year have a statistically significant effect on -->
+<!-- pH. The interaction is also significant, indicating that the effect of -->
+<!-- depth differs depending on the month. -->
+
+<!-- -   To compare with pCO2/pCO2 measured in the Ferrybox seems therefore -->
+<!--     better to stick with pH_10m, that is at depths deeper than 8 m. -->
+<!-- -   pCO2 would have the same behaviour as pH. For air-sea CO2 fluxes, -->
+<!--     one should use data from 0 to 4 m. -->
 
@@
 
+```{r durafet clean up, echo=FALSE, message= FALSE, warning=FALSE}
+d_all <- d_all %>% 
+  dplyr::mutate(pH_dur = ph_dur_corr) %>% # the right durafet pH at in situ temp from now on
+  dplyr::select(-ph_dur, -ph_dur_corr)
+# normalized durafet pH 4°C
+tmp <- d_all %>%
+  dplyr::select(datetime, at, sal_fb, temp_fb, pH_dur) %>%
+  tidyr::drop_na()
+tmp$pH_dur_temp_4 <- seacarb::pHinsi(pH=tmp$pH_dur, ALK=mean(tmp$at*1e-6, na.rm=TRUE), Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+d_all <- d_all %>% 
+  left_join(tmp %>% dplyr::select(datetime, pH_dur_temp_4 ), by="datetime")
+```
 ## Range per months
@@
 
-### **seaFET / durafet pHs (all at 9 m)**
-
-```{r pHs comparaison, echo=FALSE, message= FALSE, warning=FALSE}
+### **seaFET / durafet pHs (all > 8 m)**
+
+```{r pHs comparaison 4°C, echo=FALSE, message= FALSE, warning=FALSE}
 # prepare data and remove sf biofouling period
 pH_sf <- d_all %>%
-  dplyr::select(datetime, sal_insitu_ctd_10m , temp_insitu_ctd_10m, pHint_tot_sf)%>%
-  dplyr::filter(!is.na(pHint_tot_sf), !is.na(temp_insitu_ctd_10m), !is.na(sal_insitu_ctd_10m)) %>%
-  dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
-
-pH_sf$pHint_tot_sf_temp_4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_10m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_10m, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+  dplyr::select(datetime, sal_insitu_ctd_10m, temp_insitu_ctd_10m, pHint_tot_sf_temp_4, depth_group) %>%
+  #tidyr::drop_na() %>%
+  dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03")) %>% 
+  dplyr::mutate(pHint_tot_sf_temp_4_10m = ifelse(depth_group == ">8", pHint_tot_sf_temp_4, NA))
+
+#pH_sf$pHint_tot_sf_temp_4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_10m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_10m, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 
@@
   dplyr::select(datetime, sal_fb,temp_fb, ph_dur_corr)%>%
-  dplyr::filter(!is.na(ph_dur_corr), !is.na(temp_fb), !is.na(sal_fb))
-pH_dur$pH_durafet_temp_4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
-
-# join pH sf norm + pH dur norm
-d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime, pHint_tot_sf_temp_4 ), by="datetime")
-d_all <- left_join(d_all, pH_dur%>%dplyr::select(datetime, pH_durafet_temp_4 ), by="datetime")
-
-fit <- lmodel2(data = d_all,  pHint_tot_sf_temp_4 ~ pH_durafet_temp_4 , nperm = 99)
-pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_durafet_temp_4, y= pHint_tot_sf_temp_4, label = monthd))+
+  tidyr::drop_na() %>%
+pH_dur$pH_dur_temp_4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+
+# add pH sf and pH dur normalized at 4°C ti d_all
+#d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime, pHint_tot_sf_temp_4 ), by="datetime")
+d_all <- d_all %>% 
+  left_join(pH_dur %> %dplyr::select(datetime, pH_dur_temp_4), by="datetime")
+
+fit <- lmodel2(data = d_all,  pHint_tot_sf_temp_4 ~ pH_dur_temp_4, nperm = 99)
+pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_dur_temp_4, y= pHint_tot_sf_temp_4, label = monthd))+
   geom_point( aes(color=factor(monthd)), size =1, alpha=0.5) + 
@@
   theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 , xlim=c(7.8,8.35), ylim=c(7.8,8.35))+ #scale_colour_discrete(guide="none") +
+  coord_fixed(ratio = 1 , xlim=c(7.8,8.35), ylim=c(7.8,8.35)) + #scale_colour_discrete(guide="none") +
   labs( x="pH durafet, 4°C", y="pH seaFET, 4°C ", color = "Month ")  +theme_bw()
@@
 
-durafet_sf_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_temp_4, pHint_tot_sf_temp_4)
+durafet_sf_contros_xts <- dplyr::select(d_all, datetime, pH_dur_temp_4, pHint_tot_sf_temp_4)
 durafet_sf_contros_xts <- as.xts(durafet_sf_contros_xts, order.by = d_all$datetime)
 dygraph(durafet_sf_contros_xts, group = "awipev", main="pH durafet vs pH seaFET at 4°C", ylab="pHT") %>%
-    dySeries("pH_durafet_temp_4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("pH_dur_temp_4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
     dySeries("pHint_tot_sf_temp_4", label = "pH seaFET", color =  "red", strokeWidth = 0, pointSize = 2 ) %>%
@@
 
-durafet_calc_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_temp_4, pH_calc_fb_temp_4)
+durafet_calc_contros_xts <- dplyr::select(d_all, datetime, pH_dur_temp_4, pH_calc_fb_temp_4)
 durafet_calc_contros_xts <- as.xts(durafet_calc_contros_xts, order.by = d_all$datetime)
 dygraph(durafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH durafet, normalized at 4°C", ylab="pHT") %>%
-    dySeries("pH_durafet_temp_4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
+    dySeries("pH_dur_temp_4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
     dySeries("pH_calc_fb_temp_4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
@@
 
-```{r stratification, echo=FALSE, message= FALSE, warning=FALSE}
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 # # we look at the distribution of data
@@
         panel.grid.minor.y = element_blank())
+print(den_delta_plt)
+# we look at pHint_tot_sf at all depths
+tmp <- d_all %>% 
+  dplyr::select(montht, pHint_tot_sf, depth_group) %>%
+  tidyr::drop_na() %>% 
+  dplyr::filter(depth_group != "NA") %>% 
+  group_by(depth_group, montht)
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "pHint_tot_sf vs depth", x = "Depth (m)", y= "pH (units)") +
+  scale_x_discrete(labels = depth_labels) +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+summary(aov(tmp$pHint_tot_sf ~ tmp$depth_group * tmp$montht))
 
@@
 tmp <- d_all %>% 
-  #dplyr::mutate(depth_group = depth_group_pressure) %>% 
   dplyr::select(montht, pHint_tot_sf, depth_group) %>%
@@
 
+pHinsi_delta_plt <- tmp_delta %>% 
+  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
+  #labs(y = substitute("pH"["T"] ~ "at in situ temp."), x = "Month") +
+  scale_x_discrete("Month", expand = c(0, 0)) +
+  scale_y_continuous(substitute("pH"["T"] ~ "at in situ temp."), limits = c(-0.07, 0.03), expand = c(0, 0)) +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 0.02, label = substitute("pH"["surface"] ~ "> pH"["deep"])) +
+  annotate("text", x = 1.5, y = -0.06, label = substitute("pH"["surface"] ~ "< pH"["deep"])) +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+print(pHinsi_delta_plt)
+# we look at pHint_tot_sf normalized at 4°C at all depths
+tmp <- d_all %>% 
+  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
+  #tidyr::drop_na() %>% 
+  dplyr::filter(depth_group != "NA") %>% 
+  group_by(depth_group, montht)
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf_temp_4)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "pHint_tot_sf at 4°C vs depth", x = "Depth (m)", y= "pH at 4°C (units)") +
+  scale_x_discrete(labels = depth_labels) +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group * tmp$montht))
+
+# we look at pHint_tot_sf normalized at 4°C  0 to 4 m vs more than 8 m
+tmp <- d_all %>% 
+  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
+  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4',
+                                                   depth_group == '>8' ~ '8-12'))) %>% 
+  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
+  dplyr::group_by(depth_group2, montht)
+summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group2 * tmp$montht))
+
+tmp_delta <- tmp %>% 
+  group_by(depth_group2, montht) %>% 
+  dplyr::summarise(pH_tot_sf_med = median(pHint_tot_sf_temp_4, na.rm = TRUE)) %>% 
+  tidyr::pivot_wider(names_from = depth_group2, values_from = pH_tot_sf_med) %>% 
+  dplyr::rename(median0_4m = "0-4",
+                median8_12m = "8-12") %>%   dplyr::mutate(pH_tot_sf_med_delta = median0_4m - median8_12m)
+kable(tmp_delta, digits = 3, caption = "Median seafet pH at 4°C with (median0_4m - median8_12m)")
+
+p <- tidyr::drop_na(tmp) %>% 
+  ggplot(aes(x=as.factor(depth_group2), y = pHint_tot_sf)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "pH vs depth", x = "Depth (m)", y= "pHint_tot_sf") +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+
 pH_delta_plt <- tidyr::drop_na(tmp_delta) %>% 
@@
   scale_x_discrete("Month", expand = c(0, 0)) +
-  scale_y_continuous(substitute("pH"["T"] ~ "at in situ temp."), limits = c(-0.2, 0.1), expand = c(0, 0)) +
+  scale_y_continuous(substitute("pH"["T"] ~ "at 4°C"), limits = c(-0.2, 0.1), expand = c(0, 0)) +
   geom_col(fill="blue") +
@@
 
-deltas <- sal_delta_plt / temp_delta_plt / den_delta_plt / pH_delta_plt
-deltas <- deltas + plot_annotation(tag_levels = 'a')
-ggsave(filename = "figures/deltas.png", plot = deltas, width = 15, height = 20, units = "cm")
+# all deltas
+deltas_plt <- sal_delta_plt / temp_delta_plt / den_delta_plt / pH_delta_plt
+deltas_plt <- deltas_plt + plot_annotation(tag_levels = 'a')
+print(deltas_plt)
+ggsave(filename = "figures/deltas.png", plot = deltas_plt, width = 15, height = 20, units = "cm")
 ```
@@
 -   Temperature is always colder at 0-4 m than below 8 m (0.15 to 2°C).
+
+**Conclusion for pH**: The range is significantly larger during some months
+when the data deeper than 8 m are considered. Also, pH is sometimes
+higher at the surface, at other times it is higher on the bottom (June).
+No data are available at 1 m (actually 0 to 2 m). So, to compare surface
+and bottom, I combine 1 and 3 m (0 to 4 m) and 9 m (below 8 m).
+
+Depth and month of the year have a statistically significant effect on
+pH. The interaction is also significant, indicating that the effect of
+depth differs depending on the month.
+
+-   To compare with pCO2/pCO2 measured in the Ferrybox seems therefore
+    better to stick with pH_10m, that is at depths deeper than 8 m.
+-   pCO2 would have the same behaviour as pH. For air-sea CO2 fluxes,
+    one should use data from 0 to 4 m.
 

### 2021-12-26 awipev-CO2.Rmd
finalized stratitification minor formating changes

@@
 library("pangaear")
+if (!require("todor")) install.packages("todor")
+library("todor")
 
@@
 # nutrients in umol/l
-nuts <- readxl::read_excel(paste0(path, "fb_data/Ferrybox nutrients 2014-2018.xlsx"),
-                           skip =1) %>% 
+nuts <-
+  readxl::read_excel(paste0(path, "fb_data/Ferrybox nutrients 2014-2018.xlsx"),
+                     skip = 1) %>%
   drop_na(date) %>%
-  dplyr::mutate(datetime = as.POSIXct(paste0(date, " 12:00:00")),
-                ) %>% # assuming sampling time 12:00
+  dplyr::mutate(datetime = as.POSIXct(paste0(date, " 12:00:00")),) %>% # assuming sampling time 12:00
   dplyr::filter(datetime > as.POSIXct("2015-07-09"))
@@
 discrete2merge <- discrete %>%
-  #drop_na() %>%
   dplyr::select(closest_datetime, ct) %>%
@@
 discrete2merge <- discrete %>%
-  #drop_na() %>%
   dplyr::select(closest_datetime, ph_calc_fb) %>%
@@
 lm <- lm2(x = d_all$sal_insitu_ctd_10m, y = d_all$sal_fb)
-p <-  ggplot(d_all,aes(x=sal_insitu_ctd_10m, y= sal_fb))+
+p <-  ggplot(d_all, aes(x=sal_insitu_ctd_10m, y = sal_fb))+
   geom_point( aes(color=factor(monthd))) + 
@@
 ```{r temperature time series, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-# TEMP Ferrybox SBE45
+# Temperature Ferrybox SBE45
 temp_fb_xts <- dplyr::select(d_all, datetime, temp_fb)
@@
       dyRangeSelector(height = 30, dateWindow= NULL)
-# TEMP insitu SBE38
+# Temperature insitu SBE38
 temp_insitu_xts <- dplyr::select(d_all, datetime, temp_insitu_11m)
@@
 
-durafet_contros_xts <- dplyr::select(d_all, datetime, ph_dur, ph_s_dur_temp_fb,ph_dur_corr, pH_s_dur_no_calb)
-durafet_contros_xts <- as.xts(durafet_contros_xts, order.by = d_all$datetime)
- dygraph(durafet_contros_xts, group = "awipev", main="pH durafet (in Ferrybox)", ylab="pHT") %>%
-    dySeries("ph_dur", label = "Raw durafet pH", color ="blue", strokeWidth=0, pointSize=2) %>%
-       dySeries("pH_s_dur_no_calb", label = "pH spectro no calibration", color ="black", pointShape = "triangle",strokeWidth=0, pointSize=6) %>%
-       dySeries("ph_dur_corr", label = "pH durafet corrected", color =  RColorBrewer::brewer.pal(3, "Dark2")[1], strokeWidth = 0, pointSize = 2 ) %>%
-       dySeries("ph_s_dur_temp_fb", label = "pH spectro for calibration", color =  "red", strokeWidth = 0, pointSize = 6 ) %>%
-    dyEvent(as.POSIXct("2017-10-30 13:00:00", tz="UTC"), "New holder installed", labelLoc = "bottom", color="red") %>% 
-    dyEvent(as.POSIXct("2017-08-24 12:00:00", tz="UTC"), "durafet installed", labelLoc = "bottom", color="red") %>%
-    dyEvent(as.POSIXct("2019-09-02 20:00:00", tz="UTC"), "cleaning same probe ", labelLoc = "bottom", color="red") %>%
+durafet_contros_xts <-
+  dplyr::select(d_all,
+                datetime,
+                ph_dur,
+                ph_s_dur_temp_fb,
+                ph_dur_corr,
+                pH_s_dur_no_calb)
+durafet_contros_xts <-
+  as.xts(durafet_contros_xts, order.by = d_all$datetime)
+dygraph(durafet_contros_xts,
+        group = "awipev",
+        main = "pH durafet (in Ferrybox)",
+        ylab = "pHT") %>%
+  dySeries(
+    "ph_dur",
+    label = "Raw durafet pH",
+    color = "blue",
+    strokeWidth = 0,
+    pointSize = 2
+  ) %>%
+  dySeries(
+    "pH_s_dur_no_calb",
+    label = "pH spectro no calibration",
+    color = "black",
+    pointShape = "triangle",
+    strokeWidth = 0,
+    pointSize = 6
+  ) %>%
+  dySeries(
+    "ph_dur_corr",
+    label = "pH durafet corrected",
+    color =  RColorBrewer::brewer.pal(3, "Dark2")[1],
+    strokeWidth = 0,
+    pointSize = 2
+  ) %>%
+  dySeries(
+    "ph_s_dur_temp_fb",
+    label = "pH spectro for calibration",
+    color =  "red",
+    strokeWidth = 0,
+    pointSize = 6
+  ) %>%
+  dyEvent(
+    as.POSIXct("2017-10-30 13:00:00", tz = "UTC"),
+    "New holder installed",
+    labelLoc = "bottom",
+    color = "red"
+  ) %>%
+  dyEvent(
+    as.POSIXct("2017-08-24 12:00:00", tz = "UTC"),
+    "durafet installed",
+    labelLoc = "bottom",
+    color = "red"
+  ) %>%
+  dyEvent(
+    as.POSIXct("2019-09-02 20:00:00", tz = "UTC"),
+    "cleaning same probe ",
+    labelLoc = "bottom",
+    color = "red"
+  ) %>%
   # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
-    dyShading(from =  durinterv[1], to= durinterv[2], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[2], to= durinterv[3], color = "#E0E0E0") %>%
-    dyShading(from = durinterv[3], to= durinterv[4], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[4], to= durinterv[5], color = "#E0E0E0") %>%
-    dyShading(from = durinterv[5], to= durinterv[6], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[6], to= durinterv[7], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[7], to= durinterv[8], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[8], to= durinterv[9], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[9], to= durinterv[10], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[10], to= durinterv[11], color = "#E0E0E0") %>%
-    dyShading(from = durinterv[11], to= durinterv[12], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[12], to= durinterv[13], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[13], to= durinterv[14], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[14], to= durinterv[15], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[15], to= durinterv[16], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[16], to= durinterv[17], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[17], to= durinterv[18], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[18], to= durinterv[19], color = "#E0E0E0") %>%
-    dyShading(from = durinterv[19], to= durinterv[20], color = "#CCCCCC") %>%
-    dyShading(from = durinterv[20], to= durinterv[21], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[21], to= durinterv[22], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[22], to= durinterv[23], color = "#E0E0E0") %>%
-   dyShading(from = durinterv[23], to= durinterv[24], color = "#CCCCCC") %>%
-   dyShading(from = durinterv[24], to= durinterv[25], color = "#E0E0E0") %>%
-  dyShading(from = durinterv[25], to= durinterv[26], color = "#CCCCCC") %>%
-  dyShading(from = durinterv[26], to= Sys.Date(), color = "#E0E0E0") %>%
+  dyShading(from =  durinterv[1], to = durinterv[2], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[2], to = durinterv[3], color = "#E0E0E0") %>%
+  dyShading(from = durinterv[3], to = durinterv[4], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[4], to = durinterv[5], color = "#E0E0E0") %>%
+  dyShading(from = durinterv[5], to = durinterv[6], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[6], to = durinterv[7], color = "#E0E0E0") %>%
+  dyShading(from = durinterv[7], to = durinterv[8], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[8], to = durinterv[9], color = "#E0E0E0") %>%
+  dyShading(from = durinterv[9], to = durinterv[10], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[10], to = durinterv[11], color = "#E0E0E0") %>%
+  dyShading(from = durinterv[11], to = durinterv[12], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[12], to = durinterv[13], color = "#E0E0E0") %>%
+  dyShading(from = durinterv[13], to = durinterv[14], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[14], to = durinterv[15], color = "#E0E0E0") %>%
+  dyShading(from = durinterv[15], to = durinterv[16], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[16], to = durinterv[17], color = "#E0E0E0") %>%
+  dyShading(from = durinterv[17], to = durinterv[18], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[18], to = durinterv[19], color = "#E0E0E0") %>%
+  dyShading(from = durinterv[19], to = durinterv[20], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[20], to = durinterv[21], color = "#E0E0E0") %>%
+  dyShading(from = durinterv[21], to = durinterv[22], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[22], to = durinterv[23], color = "#E0E0E0") %>%
+  dyShading(from = durinterv[23], to = durinterv[24], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[24], to = durinterv[25], color = "#E0E0E0") %>%
+  dyShading(from = durinterv[25], to = durinterv[26], color = "#CCCCCC") %>%
+  dyShading(from = durinterv[26],
+            to = Sys.Date(),
+            color = "#E0E0E0") %>%
   dyLegend(show = "follow")   %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
-
+  dyHighlight(
+    highlightCircleSize = 8,
+    highlightSeriesBackgroundAlpha = 0.5,
+    hideOnMouseOut = TRUE
+  ) %>%
+  dyOptions(
+    drawGrid = TRUE,
+    drawPoints = TRUE,
+    pointSize = c(1, 8, 1),
+    useDataTimezone = TRUE,
+    digitsAfterDecimal = 4
+  ) %>%
+  dyRangeSelector(height = 30, dateWindow = NULL)
 print(plot_offset_dur)
@@
 # prepare data and remove sf biofouling period
-pH_sf <- d_all %>%
-  dplyr::select(datetime, sal_insitu_ctd_10m, temp_insitu_ctd_10m, pHint_tot_sf_temp_4, depth_group) %>%
-  #tidyr::drop_na() %>%
-  dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03")) %>% 
-  dplyr::mutate(pHint_tot_sf_temp_4_10m = ifelse(depth_group == ">8", pHint_tot_sf_temp_4, NA))
-
-#pH_sf$pHint_tot_sf_temp_4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_10m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_10m, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
-
-pH_dur <- d_all %>%
-  dplyr::select(datetime, sal_fb,temp_fb, ph_dur_corr)%>%
-  tidyr::drop_na() %>%
-pH_dur$pH_dur_temp_4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
-
-# add pH sf and pH dur normalized at 4°C ti d_all
-#d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime, pHint_tot_sf_temp_4 ), by="datetime")
-d_all <- d_all %>% 
-  left_join(pH_dur %> %dplyr::select(datetime, pH_dur_temp_4), by="datetime")
-
-fit <- lmodel2(data = d_all,  pHint_tot_sf_temp_4 ~ pH_dur_temp_4, nperm = 99)
-pdur_sf_norm_text <-  ggplot(d_all,aes(x=pH_dur_temp_4, y= pHint_tot_sf_temp_4, label = monthd))+
-  geom_point( aes(color=factor(monthd)), size =1, alpha=0.5) + 
-  facet_wrap( ~ factor(monthd), ncol = 3) +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 , xlim=c(7.8,8.35), ylim=c(7.8,8.35)) + #scale_colour_discrete(guide="none") +
-  labs( x="pH durafet, 4°C", y="pH seaFET, 4°C ", color = "Month ")  +theme_bw()
-
-print(pdur_sf_norm_text)
-rm(pdur_sf_norm_text)
+# TODO consider biofouling period elsewhere too
+#   pH_sf <- d_all %>%
+#   dplyr::select(datetime, sal_insitu_ctd_10m, temp_insitu_ctd_10m, pHint_tot_sf_temp_4, depth_group) %>%
+#   #tidyr::drop_na() %>%
+#   dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03")) %>% 
+#   dplyr::mutate(pHint_tot_sf_temp_4_10m = ifelse(depth_group == ">8", pHint_tot_sf_temp_4, NA))
+# 
+# #pH_sf$pHint_tot_sf_temp_4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_10m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_10m, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+# 
+# pH_dur <- d_all %>%
+#   dplyr::select(datetime, sal_fb,temp_fb, pH_dur)%>%
+#   tidyr::drop_na() %>%
+# pH_dur$pH_dur_temp_4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+# 
+# # add pH sf and pH dur normalized at 4°C ti d_all
+# #d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime, pHint_tot_sf_temp_4 ), by="datetime")
+# d_all <- d_all %>% 
+#   left_join(pH_dur %> %dplyr::select(datetime, pH_dur_temp_4), by="datetime")
+lm <- lm2(x = d_all$pH_dur_temp_4, y = d_all$pHint_tot_sf_temp_4)
+p <- d_all %>% 
+  dplyr::select(pH_dur_temp_4, pHint_tot_sf_temp_4, monthd) %>% 
+  drop_na() %>% 
+  ggplot(aes(x = pH_dur_temp_4, y = pHint_tot_sf_temp_4))+
+  geom_point(aes(color=factor(monthd))) + 
+  geom_abline(slope=1, intercept=0, linetype = "dashed")+
+  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA), colour = "blue") +
+  coord_fixed(ratio = 1 , xlim=c(7.8, 8.35), ylim=c(7.8, 8.35)) +
+  labs(title = paste("","\n Adj R2 = ", signif(lm$rsquare, 3),
+                     "; Intercept =", signif(lm$intercept_MA, 3),
+                     "; Slope =", signif(lm$slope_MA, 3),
+                     "; P =", signif(lm$P, 3),
+                     "; RMSE = ", signif(lm$rmse, 3))) +
+  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
+  labs( x = "pH durafet, 4°C", y = "pH seaFET, 4°C", color = "Months") + theme_bw()
+print(p)
 
@@
 # Spectro / durafet
-lm <- lm2(x = d_all$ph_s_dur_temp_fb, y = d_all$ph_dur_corr)
-
-p <-  ggplot(d_all, aes(x=ph_s_dur_temp_fb, y= ph_dur_corr, label = monthd)) +
+lm <- lm2(x = d_all$ph_s_dur_temp_fb, y = d_all$pH_dur)
+p <- d_all %>% 
+  dplyr::select(ph_s_dur_temp_fb, pH_dur, monthd) %>% 
+  drop_na() %>% 
+  ggplot(aes(x = ph_s_dur_temp_fb, y= pH_dur, label = monthd)) +
   geom_text( aes(color=factor(monthd))) + 
@@
   labs(x="pH durafet", y="pH spectro", color = "Months")
-p
+print(p)
 ```
@@
 lm <- lm2(x = d_all$ph_s_sf_temp_insi, y = d_all$pHint_tot_sf)
-
-p <-  ggplot(d_all, aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = monthd)) +
+p <- d_all %>% 
+  dplyr::select(ph_s_sf_temp_insi, pHint_tot_sf, monthd) %>%
+  tidyr::drop_na() %>%
+  ggplot(aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = monthd)) +
   geom_text( aes(color=factor(monthd))) + 
   scale_color_discrete(guide = "none")+
-  geom_abline(slope=1, intercept =0, linetype = "dashed") +
+  geom_abline(slope=1, intercept = 0, linetype = "dashed") +
   geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),
@@
   theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
-  labs(x="pH spectro", y="pH seafet", color = "Months")
-p
+  coord_fixed(ratio = 1 , xlim=c(8, 8.25), ylim=c(8, 8.25))+
+  labs(x = "pH spectro", y = "pH seafet", color = "Months")
+print(p)
 ```
@@
     Mytheme()
-
 p_ct_ts <- ggplot() +
@@
 
-at_diff_xts <- dplyr::select(diff, datetime, at_diff, at)
+at_diff_xts <- diff %>% dplyr::select(datetime, at_diff, at)
 at_diff_xts <- as.xts(at_diff_xts, order.by = diff$datetime)
 
-pdelta_at_snapo_dygraph <- dygraph(at_diff_xts, group = "awipev", main="Discrete AT (SNAPO) measurements", ylab="AT") %>%
-    dySeries("at_diff", label = "AT delta", color ="red", strokeWidth=0, pointSize=4) %>%
-    dySeries("at", label = "AT duplicates", color =  "blue", strokeWidth = 0, pointSize = 2, axis = "y2" ) %>%
+pdelta_at_snapo_dygraph <-
+  dygraph(at_diff_xts,
+          group = "awipev",
+          main = "Discrete AT (SNAPO) measurements",
+          ylab = "AT") %>%
+  dySeries(
+    "at_diff",
+    label = "AT delta",
+    color = "red",
+    strokeWidth = 0,
+    pointSize = 4
+  ) %>%
+  dySeries(
+    "at",
+    label = "AT duplicates",
+    color =  "blue",
+    strokeWidth = 0,
+    pointSize = 2,
+    axis = "y2"
+  ) %>%
   # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
   dyShading(from = snapcoevents[13], to = snapcoevents[14], color = "#E0DEDE") %>%
-
-  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
-    dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
+  dyAxis(
+    "y",
+    axisLineColor = "red",
+    label = "",
+    axisLabelColor = "red",
+    axisLineWidth = 5
+  ) %>%
+  dyAxis(
+    "y2",
+    axisLineColor = "blue",
+    axisLabelColor = "blue",
+    axisLineWidth = 5
+  ) %>%
+  dyHighlight(
+    highlightCircleSize = 8,
+    highlightSeriesBackgroundAlpha = 0.5,
+    hideOnMouseOut = TRUE
+  ) %>%
   dyLegend(show = "follow")   %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=2) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
+  dyOptions(
+    drawGrid = TRUE,
+    drawPoints = TRUE,
+    pointSize = c(1, 8, 1),
+    useDataTimezone = TRUE,
+    digitsAfterDecimal = 2
+  ) %>%
+  dyRangeSelector(height = 30, dateWindow = NULL)
 
@@
     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=2) %>%
+    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1), digitsAfterDecimal=2) %>%
     dyRangeSelector(height = 30, dateWindow= NULL)
@@
 
-sal_delta_plt <- tidyr::drop_na(tmp_delta) %>% 
+sal_delta_plt <- tmp_delta %>% 
   ggplot(aes(x=montht, y=sal_delta)) +
@@
 kable(tmp_delta, digits = 2, caption = "Median temperature with (median0_4m - median8_12m)")
-
-p <- tidyr::drop_na(tmp) %>% 
+p <- tmp %>% 
+  tidyr::drop_na() %>% 
   ggplot(aes(x=depth_group2, y = temp_insitu_ctd)) +
@@
 print(p)
-
-temp_delta_plt <- tidyr::drop_na(tmp_delta) %>% 
-  ggplot(aes(x=montht, y=temp_delta)) +
-  scale_x_discrete(expand = c(0, 0)) +
-  scale_y_continuous("Temperature", limits = c(-1.3, 0.8), expand = c(0, 0)) +
+temp_delta_plt <- tmp_delta %>% 
+  #tidyr::drop_na() %>% 
+  ggplot(aes(x = montht, y = temp_delta)) +
+  #scale_x_discrete(expand = c(0, 0)) +
+  scale_y_continuous("Temperature", limits = c(-2.1, 0.5), expand = c(0, 0)) +
   geom_col(fill="blue") +
   geom_hline(yintercept = 0) +
-  annotate("text", x = 1.5, y =0.6, label = substitute("T"["surface"] ~ "> T"["deep"])) +
+  annotate("text", x = 1.5, y = 0.3, label = substitute("T"["surface"] ~ "> T"["deep"])) +
   annotate("text", x = 1.5, y = -0.6, label = substitute("T"["surface"] ~ "< T"["deep"])) +
@@
 tmp_delta <- tmp %>% 
-  dplyr::select(montht, depth_group, density) %>% 
-  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
-                                      depth_group == '>8' ~ '8-12'))) %>% 
+  dplyr::select(montht, depth_group2, density) %>% 
+  #dplyr::mutate(depth_group2 = as.factor(case_when(depth_group2 == '0-2' | depth_group2 == '2-4' ~ '0-4',
+#                                                   depth_group2 == '>8' ~ '8-12'))) %>% 
   dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
@@
 
-p <- tidyr::drop_na(tmp) %>% 
-  ggplot(aes(x=montht, y = density)) +
+p <- tmp %>% 
+  tidyr::drop_na() %>% 
+  ggplot(aes(x = depth_group2, y = density)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
 p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf)) +
+  ggplot(aes(x = as.factor(depth_group), y = pHint_tot_sf)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
 
-p <- tidyr::drop_na(tmp) %>% 
+p <- tmp %>% 
+  tidyr::drop_na() %>% 
   ggplot(aes(x=as.factor(depth_group2), y = pHint_tot_sf)) +
@@
   dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
-  #tidyr::drop_na() %>% 
+  tidyr::drop_na() %>% 
   dplyr::filter(depth_group != "NA") %>% 
@@
 p <- tidyr::drop_na(tmp) %>% 
-  ggplot(aes(x=as.factor(depth_group2), y = pHint_tot_sf)) +
+  ggplot(aes(x=as.factor(depth_group2), y = pHint_tot_sf_temp_4)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "pH vs depth", x = "Depth (m)", y= "pHint_tot_sf") +
+  labs(title = "pH at 4°C vs depth", x = "Depth (m)", y= "pHint_tot_sf") +
   facet_wrap(vars(montht), scale = "free_y")
@@
 pangaea <- as_tibble(d_all) %>% 
-  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb, pco2_calc_fb, at_calc, ph_dur_corr, pHint_tot_sf) %>%
+  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb, pco2_calc_fb, at_calc, pH_dur, pHint_tot_sf) %>%
   dplyr::rename(pressure = depth,
@@
                 pH_sf = pHint_tot_sf,
-                ph_dur = ph_dur_corr,
+                pH_dur = pH_dur,
                 ph_calc = ph_calc_fb

### 2021-12-26 awipev-CO2.Rmd
changed output in yaml

@@
 date: '`r format(Sys.Date(), "%d %B %Y")`'
-output:
-  pdf_document: default
-  word_document: default
-  html_document: default
-  odt_document: default
+output: html_document
 editor_options: 

### 2021-12-27 awipev-CO2.Rmd
minor

@@
 ## Stratification
-
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 
-p <- tidyr::drop_na(tmp) %>% 
+p <- tmp %>% 
+  tidyr::drop_na() %>% 
   ggplot(aes(x=depth_group2, y = sal_insitu_ctd)) +

### 2021-12-27 awipev-CO2.Rmd
created and new names (see notes at end of script): sal_fb_mix sal_fb_mix_interp temp_insitu_11m_mix temp_insitu_11m_mix_interp

@@
 title: "Carbonate chemistry at Ny-Ålesund" 
-author: "Jean-Pierre Gattuso and Samir Alliouane and Bernard Gentili"
+author: "Jean-Pierre Gattuso and Samir Alliouane and Philipp Fisher"
 date: '`r format(Sys.Date(), "%d %B %Y")`'
@@
 
-```{r Sal filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-
-########### Binding sal_fb + sal_insitu if we get gaps in sal_insitu = call this new column = sal_mix ########### 
+```{r sal and temp data, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
+### Fill gaps in sal_fb using sal_insitu_ctd_10m; new column = sal_fb_mix ###
+### Fill gaps in sal_insitu_ctd using sal_fb_mix; new column = sal_insitu_ctd_mix ###
+### Fill gaps in temp_insitu_11m using temp_insitu_ctd_10m; new column = temp_insitu_11m_mix ###
 d_all <- d_all %>%
-  dplyr::mutate(sal_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_10m))
-```
-
-```{r Temp filter, fig.width=10, fig.height=4, echo=FALSE, message= FALSE}
-# Create temp_mix: filling gaps in temp_insitu_11m using temp_insitu_10m
-d_all <- d_all %>%
-  dplyr::mutate(temp_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_10m))
+  dplyr::mutate(sal_fb_mix = ifelse(!is.na(sal_fb), sal_fb, sal_insitu_ctd_10m),
+                sal_insitu_ctd_mix = ifelse(!is.na(sal_insitu_ctd), sal_insitu_ctd, sal_fb_mix),
+                temp_insitu_11m_mix = ifelse(!is.na(temp_insitu_11m), temp_insitu_11m, temp_insitu_ctd_10m)
+                )
 ```
@@
 
-# interpolation of temp_mix/sal_mix in d_all in order to have a full temperature for pHinsi()
-# We take temp_mix/sal_mix because of the depth (temp11m insitu + temp10m ctd)
-tempmixinterp <-approx(d_all$datetime, d_all$temp_mix, xout=d_all$datetime, method="linear", rule=2)
-names(tempmixinterp) <- c("datetime", "temp_mix_interp")
+# interpolation of temp_insitu_11m_mix/sal_fb_mix in d_all in order to have a full temperature for pHinsi()
+# We take temp_insitu_11m_mix/sal_fb_mix because of the depth (temp11m insitu + temp10m ctd)
+tempmixinterp <-approx(d_all$datetime, d_all$temp_insitu_11m_mix, xout=d_all$datetime, method="linear", rule=2)
+names(tempmixinterp) <- c("datetime", "temp_insitu_11m_mix_interp")
 tempmixinterp <- as.data.frame(tempmixinterp)
-d_all$temp_mix_interp <- tempmixinterp$temp_mix_interp
-
-salmixinterp <-approx(d_all$datetime, d_all$sal_mix, xout=d_all$datetime, method="linear", rule=2)
-names(salmixinterp) <- c("datetime", "sal_mix_interp")
+d_all$temp_insitu_11m_mix_interp <- tempmixinterp$temp_insitu_11m_mix_interp
+
+salmixinterp <-approx(d_all$datetime, d_all$sal_fb_mix, xout=d_all$datetime, method="linear", rule=2)
+names(salmixinterp) <- c("datetime", "sal_fb_mix_interp")
 salmixinterp <- as.data.frame(salmixinterp)
-d_all$sal_mix_interp <- salmixinterp$sal_mix_interp
-
-# ta_xts <- dplyr::select(d_all, datetime, sal_mix, sal_mix_interp)
-# ta_xts <- as.xts(ta_xts, order.by = ta_xts$datetime)
-# dygraph(ta_xts, group = "awipev", main="sal mix", ylab="temp") %>%
-#   dySeries("sal_mix", color = "black", pointSize =4, strokeWidth = 1, label = "ta") %>%
-#   dySeries("sal_mix_interp", color = "blue", strokeWidth = 1, label = "ta interp") %>%
-#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
-#       dyOptions( drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-#     dyAxis("y",valueRange = c(33, 36)) %>%
-#     dyLegend(show = "follow")   %>%
-#       dyRangeSelector(height = 30, dateWindow= NULL)
+d_all$sal_fb_mix_interp <- salmixinterp$sal_fb_mix_interp
 
@@
                      temp_fb,
-                     temp_mix,
-                     temp_mix_interp,
-                     sal_mix,
-                     sal_mix_interp,
+                     temp_insitu_11m_mix,
+                     temp_insitu_11m_mix_interp,
+                     sal_fb_mix,
+                     sal_fb_mix_interp,
                      temp_insitu_11m,
@@
 pH_seafet <- d %>%
-  dplyr::filter(!is.na(ph_s_sf) & !is.na(temp_mix_interp))
+  dplyr::filter(!is.na(ph_s_sf) & !is.na(temp_insitu_11m_mix_interp))
 
@@
     ph_s_sf_temp_insi = pHinsi(pH = pH_seafet$ph_s_sf, 
-                         ALK = pH_seafet$at_mean_interp*1e-6, Tinsi = pH_seafet$temp_mix_interp, 
+                         ALK = pH_seafet$at_mean_interp*1e-6, 
+                         Tinsi = pH_seafet$temp_insitu_11m_mix_interp, 
                          Tlab = pH_seafet$temp_s_lab, Pinsi = 11/10, 
-                         S = pH_seafet$sal_mix_interp, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
+                         S = pH_seafet$sal_fb_mix_interp, Pt = 0, Sit = 0, 
+                         k1k2 = "l", kf = "dg", ks="d", 
                          pHscale = "T", b="u74"),
@@
                          Tlab = pH_seafet$temp_s_lab, Pinsi = 11/10, 
-                         S = pH_seafet$sal_mix_interp, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
+                         S = pH_seafet$sal_fb_mix_interp, Pt = 0, Sit = 0, 
+                         k1k2 = "l", kf = "dg", ks="d", 
                          pHscale = "T", b="u74")
@@
                               Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74"),
-   ph_s_dur_temp_4 = pHinsi(pH = pH_durafet$ph_s_dur, # lueker
-                         ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4,
+    ph_s_dur_temp_4 = pHinsi(pH = pH_durafet$ph_s_dur,
+                             ALK = pH_durafet$at_mean_interp * 1e-6, Tinsi = 4,
                              Tlab = pH_durafet$temp_s_lab, Pinsi = 0,
-                         S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d",
-                         pHscale = "T", b="u74")#,
-   # ph_s_dur_temp_4_l = pHinsi(pH = pH_durafet$ph_s_dur, # lueker
-   #                       ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4,
-   #                       Tlab = pH_durafet$temp_s_lab, Pinsi = 0,
-   #                       S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d",
-   #                       pHscale = "T", b="u74"),
-   # ph_s_dur_temp_4_s20 = pHinsi(pH = pH_durafet$ph_s_dur, # Sulpis
-   #                       ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4,
-   #                       Tlab = pH_durafet$temp_s_lab, Pinsi = 0,
-   #                       S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d",
-   #                       pHscale = "T", b="u74"),       # Millero 02
-   # ph_s_dur_temp_4_p18 = pHinsi(pH = pH_durafet$ph_s_dur, # Papadimitriou
-   #                       ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4,
-   #                       Tlab = pH_durafet$temp_s_lab, Pinsi = 0,
-   #                       S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d",
-   #                       pHscale = "T", b="u74"),
-   # ph_s_dur_temp_4_m02 = pHinsi(pH = pH_durafet$ph_s_dur,  # Millero 02
-   #                       ALK = pH_durafet$at_mean_interp*1e-6, Tinsi = 4,
-   #                       Tlab = pH_durafet$temp_s_lab, Pinsi = 0,
-   #                       S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d",
-   #                       pHscale = "T", b="u74")
-
+                             S = pH_durafet$sal_fb, Pt = 0, Sit = 0, k1k2 = "l", 
+                             kf = "dg", ks = "d",
+                             pHscale = "T", b = "u74")
    )
@@
                    ph_s_dur_temp_4_mean = mean(ph_s_dur_temp_4, na.rm = TRUE))
-
-#bind all spectro measurements, just to assess sd, change name of dataframe only to do the rbind.
-# seafetph <- pH_seafet_mean
-# colnames(seafetph) <- c("date", "mean", "sd")
-# durafetph <- pH_durafet_mean
-# colnames(durafetph) <- c("date", "mean", "sd")
-#pH_seafet_durafet <- rbind(seafetph, durafetph)
-# #calculations for all pH spectro measurement for sd
-# sd_min <- min(pH_seafet_durafet$sd)
-# sd_max <- max(pH_seafet_durafet$sd)
-# sd_mean <- mean(pH_seafet_durafet$sd)
-
-#put back the right column name for the following script
+# put back the right column name for the following script
 pH_durafet_mean$ph_s_dur_temp_fb <- pH_durafet_mean$ph_s_dur_temp_fb_mean
@@
   group_by(datetime) %>%
-#dplyr::select( datetime, date,hour,sal_fb,sal_mix_interp ,sal_mix,temp_fb, at_mean_interp,at ,ct_mean_interp,ct, temp_mix,temp_mix_interp,temp_insitu_11m) %>%
+#dplyr::select( datetime, date,hour,sal_fb,sal_fb_mix_interp ,sal_fb_mix,temp_fb, at_mean_interp,at ,ct_mean_interp,ct, temp_insitu_11m_mix,temp_insitu_11m_mix_interp,temp_insitu_11m) %>%
   summarise(datetime = mean(datetime, na.rm = TRUE),
     sal_fb = mean(sal_fb, na.rm = TRUE),
-    sal_mix = mean(sal_mix, na.rm = TRUE),
-    sal_mix_interp = mean(sal_mix_interp, na.rm = TRUE),
+    sal_fb_mix = mean(sal_fb_mix, na.rm = TRUE),
+    sal_fb_mix_interp = mean(sal_fb_mix_interp, na.rm = TRUE),
     temp_fb = mean(temp_fb, na.rm = TRUE),
-     temp_mix = mean(temp_mix, na.rm = TRUE),
-    temp_mix_interp = mean(temp_mix_interp, na.rm = TRUE),
+     temp_insitu_11m_mix = mean(temp_insitu_11m_mix, na.rm = TRUE),
+    temp_insitu_11m_mix_interp = mean(temp_insitu_11m_mix_interp, na.rm = TRUE),
         temp_insitu_11m = mean(temp_insitu_11m, na.rm = TRUE),
@@
   )
-
-# library("RColorBrewer")
-# d_xts <- dplyr::select(discrete, datetime, sal_fb, sal_mix,temp_fb,temp_mix,temp_insitu_11m, at_mean_interp,at,ct_mean_interp,ct)
-# d_xts <- as.xts(d_xts, order.by = d_xts$datetime)
-# dygraph(d_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
-#             dySeries("sal_mix", color = brewer.pal(n=9, name = "Paired")[1], strokeWidth = 1, pointSize = 4, label = "sal_mix") %>%
-#             dySeries("sal_fb", color = brewer.pal(n=9, name = "Paired")[2], strokeWidth = 1, pointSize = 2, label = "sal_fb") %>%
-#    dySeries("temp_mix", color = brewer.pal(n=9, name = "Paired")[3], strokeWidth = 1, pointSize = 4, label = "temp_mix") %>%
-#    dySeries("temp_fb", color = brewer.pal(n=9, name = "Paired")[4], strokeWidth = 1, pointSize = 2, label = "temp_fb") %>%
-#    dySeries("temp_insitu_11m", color = brewer.pal(n=9, name = "Paired")[5], strokeWidth = 1, pointSize = 2, label = "temp_insitu_11m") %>%
-#     dySeries(axis="y2", "at_mean_interp", color = brewer.pal(n=9, name = "Paired")[6], strokeWidth = 1, pointSize = 4, label = "at_mean_interp") %>%
-#    dySeries(axis="y2","ct_mean_interp", color =brewer.pal(n=9, name = "Paired")[7], strokeWidth = 1, pointSize = 4, label = "ct_mean_interp") %>%
-#  dySeries(axis="y2","at", color = brewer.pal(n=9, name = "Paired")[8], strokeWidth = 1, pointSize = 2, label = "at") %>%
-#    dySeries(axis="y2","ct", color =brewer.pal(n=9, name = "Paired")[9], strokeWidth = 1, pointSize = 2, label = "ct") %>%
-#   dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
-#       dyOptions( drawGrid = TRUE, drawPoints = TRUE,useDataTimezone = TRUE) %>%
-#     dyLegend(show = "follow")   %>%
-#    # dyAxis("y",valueRange = c(30, 37)) %>%
-#       dyRangeSelector(height = 30, dateWindow= NULL)
 
@@
 data gaps are encountered, they are filled with bottom salinity data
-from ctd (> 8 m). New column "sal_mix" is created and is the one used in
+from ctd (> 8 m). New column "sal_fb_mix" is created and is the one used in
 ESSD paper.
@@
 ```{r Salinity, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-# SAL FerryBox and sal_mix
-sal_xts <- dplyr::select(d_all, datetime, sal_fb, sal_mix)
+# SAL FerryBox and sal_fb_mix
+sal_xts <- dplyr::select(d_all, datetime, sal_fb, sal_fb_mix)
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
@@
             dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
-            dySeries("sal_mix", color = "red", strokeWidth = 0, label = "sal_mix") %>%
+            dySeries("sal_fb_mix", color = "red", strokeWidth = 0, label = "sal_fb_mix") %>%
 dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha =0.2,hideOnMouseOut =TRUE) %>%
@@
   dplyr::mutate(
-    sal_mix = case_when(
+    sal_fb_mix = case_when(
       date > as.Date("2016-02-01") &
-        date <  as.Date("2016-02-09") & sal_mix < 34 ~ NA_real_,
-      date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
+        date <  as.Date("2016-02-09") & sal_fb_mix < 34 ~ NA_real_,
+      date == as.Date("2015-11-19") & sal_fb_mix < 33 ~ NA_real_,
       date > as.Date("2015-10-01") &
-        date <  as.Date("2015-10-05") & sal_mix < 31.5 ~ NA_real_,
+        date <  as.Date("2015-10-05") & sal_fb_mix < 31.5 ~ NA_real_,
       date == as.Date("2017-03-22") &
-        sal_mix < 34 ~ NA_real_,
-      TRUE ~ sal_mix
+        sal_fb_mix < 34 ~ NA_real_,
+      TRUE ~ sal_fb_mix
     )
@@
 encountered, they are filled with bottom temperature data from ctd (> 8
-m). New column "temp_mix" is created. For the moment, no gaps are
-encountered and temp_mix = temp_insitu_11m.
+m). New column "temp_insitu_11m_mix" is created. For the moment, no gaps are
+encountered and temp_insitu_11m_mix = temp_insitu_11m.
 
@@
 d_all_at_discrete <- d_all %>% #  To remove an outlier in red
-  dplyr::select(datetime, monthd,closest_datetime, at, sal_mix)
-
-fit <- lm(data = d_all_at_discrete, at ~ sal_mix)
+  dplyr::select(datetime, monthd,closest_datetime, at, sal_fb_mix)
+
+fit <- lm(data = d_all_at_discrete, at ~ sal_fb_mix)
 slope_s_at <- fit$coefficients[[2]]
 intercept_s_at <- fit$coefficients[[1]]
-at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at, label = monthd))+
+at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb_mix, y= at, label = monthd))+
   geom_text( aes(color=factor(monthd))) +
@@
 # Same plot for paper
-p_at_s <- ggplot(d_all_at_discrete,aes(x=sal_mix, y= at)) +
+p_at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb_mix, y= at)) +
   geom_point(col="blue", size = 0.2) +
@@
 # Salinity is a predictor of AT -> using the regression defined above
-d_all$at_calc <- slope_s_at * d_all$sal_mix + intercept_s_at
+d_all$at_calc <- slope_s_at * d_all$sal_fb_mix + intercept_s_at
 ```
@@
 at_contros_calc_xts <-  as.xts(at_contros_calc_xts, order.by =d_all$datetime)
-dygraph(at_contros_calc_xts, group = "awipev", main="TA, calculated from sal_mix (blue) and reference (red)", ylab="Total alkalinity") %>%
+dygraph(at_contros_calc_xts, group = "awipev", main="TA, calculated from sal_fb_mix (blue) and reference (red)", ylab="Total alkalinity") %>%
   #dySeries("AT", label= "Raw TA", color ="blue", strokeWidth = 0, pointSize=2) %>%
@@
         date <  as.Date("2017-02-05") & pco2_fb > 400 ~ NA_real_,
-      #date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
+      #date == as.Date("2015-11-19") & sal_fb_mix < 33 ~ NA_real_,
       date > as.Date("2017-08-01") &
         date <  as.Date("2017-09-30") & pco2_fb > 300 ~ NA_real_,
-      #date == as.Date("2017-03-22") & sal_mix < 34 ~ NA_real_,
+      #date == as.Date("2017-03-22") & sal_fb_mix < 34 ~ NA_real_,
       TRUE ~ pco2_fb
@@
                                 ifelse(datetime >= sfinterv[3], 03, NA ))))
-# dygraph to check seafet data
-# pH_xts <-
-#   dplyr::select(d_all, datetime, voltINT, voltEXT, sal_fb, temp_insitu_ctd, ph_s_sf_temp_insi)
-# pH_xts <-
-#   as.xts(pH_xts, order.by = d_all$datetime)
-# dygraph(pH_xts,
-#         group = "awipev",
-#         main = "pH",
-#         ylab = "pH") %>%
-#   dySeries(
-#     axis = "y2",
-#     "voltINT",
-#     label = "voltINT",
-#     color =  RColorBrewer::brewer.pal(5, "Dark2")[1],
-#     strokeWidth = 0,
-#     pointSize = 2
-#   ) %>%
-#   dySeries(axis="y2",
-#     "voltEXT",
-#     label = "voltEXT",
-#     color =  RColorBrewer::brewer.pal(5, "Dark2")[2],
-#     strokeWidth = 0,
-#     pointSize = 2
-#   ) %>%
-#    dySeries(
-#     "temp_insitu_ctd",
-#     label = "temp_insitu_ctd",
-#     color =  RColorBrewer::brewer.pal(5, "Dark2")[3],
-#     strokeWidth = 0,
-#     pointSize = 2
-#   ) %>%
-#    dySeries(
-#     "sal_fb",
-#     label = "sal_fb",
-#     color =  RColorBrewer::brewer.pal(5, "Dark2")[4],
-#     strokeWidth = 0,
-#     pointSize = 2
-#   ) %>%
-#    dySeries(
-#     "ph_s_sf_temp_insi",
-#     label = "ph_s_sf_temp_insi",
-#     color =  RColorBrewer::brewer.pal(5, "Dark2")[5],
-#     strokeWidth = 0,
-#     pointSize = 4
-#   ) %>%
-#   dyHighlight(
-#     highlightCircleSize = 8,
-#     highlightSeriesBackgroundAlpha = 0.5,
-#     hideOnMouseOut = TRUE
-#   ) %>%
-#   dyLegend(show = "follow")   %>%
-#   dyAxis("y2",valueRange = c(-2,2))%>%
-#   dyOptions(
-#     drawGrid = TRUE,
-#     drawPoints = TRUE,
-#     pointSize = c(1, 8, 1),
-#     useDataTimezone = TRUE
-#   ) %>%
-#   dyRangeSelector(height = 30, dateWindow = NULL)
 
@@
 d_all <- d_all %>%
-  dplyr::mutate(temp_mix = ifelse(
+  dplyr::mutate(temp_insitu_11m_mix = ifelse(
     datetime == as.POSIXct("2017-08-24 13:00:00"),
     mean_TseaF_4h,
-    temp_mix
+    temp_insitu_11m_mix
   ))
@@
 d_all <- d_all %>%
-  dplyr::mutate(temp_mix = ifelse(
+  dplyr::mutate(temp_insitu_11m_mix = ifelse(
     datetime == as.POSIXct("2019-09-13 13:00:00"),
     mean_TseaF_4h,
-    temp_mix
+    temp_insitu_11m_mix
   ))
@@
 #interpolation of salinity during gaps
+# # below is old code. now we use sal_insitu_ctd_mix
+# salinterp <-
+#   approx(
+#     d_all$datetime,
+#     d_all$sal_insitu_ctd,
+#     xout = d_all$datetime,
+#     method = "linear",
+#     rule = 2
+#   )
+# names(salinterp) <- c("datetime", "sal_insitu_ctd_interp")
+# salinterp <- as.data.frame(salinterp)
+# d_all$sal_insitu_ctd_interp <- salinterp$sal_insitu_ctd_interp
+# 
+# d_all <- d_all %>%
+#   dplyr::mutate(
+#     sal_insitu_ctd_interp =  ifelse(
+#       datetime > as.POSIXct("2018-04-16 07:00:00") &
+#         datetime < as.POSIXct("2018-04-24 22:00:00"),
+#       sal_insitu_ctd_interp,
+#       sal_insitu_ctd
+#     )
+#   )
+
+# above is old code. now we use sal_insitu_ctd_mix
 salinterp <-
@@
     d_all$datetime,
-    d_all$sal_insitu_ctd,
+    d_all$sal_insitu_ctd_mix,
     xout = d_all$datetime,
@@
 
-d_all <- d_all %>%
-  dplyr::mutate(
-    sal_insitu_ctd_interp =  ifelse(
-      datetime > as.POSIXct("2018-04-16 07:00:00") &
-        datetime < as.POSIXct("2018-04-24 22:00:00"),
-      sal_insitu_ctd_interp,
-      sal_insitu_ctd
-    )
-  )
-
 ### add the depth into discrete df. In order to see where the seafet was.
-#discrete <- left_join(discrete, d_all%>%dplyr::select(closest_datetime,depth, depth_discrete),by="closest_datetime")
 discrete <- left_join(discrete, d_all%>%dplyr::select(closest_datetime,depth),by="closest_datetime")
 discrete <- discrete%>%dplyr::filter(discrete$datetime < "2021-07-01 00:00:00")
-
-#offset_xts <- select(discrete, closest_datetime, depth,depth_discrete, ph_s_sf_temp_insi)
 offset_xts <- select(discrete, closest_datetime, depth, ph_s_sf_temp_insi)
@@
 dygraph(offset_xts, main = "") %>%
-#dySeries("depth_discrete", drawPoints = TRUE, pointSize=3, strokeWidth = 1,label = "depth_discrete", color="black")%>%
 dySeries("depth", drawPoints = TRUE, pointSize=3, label = "depth", strokeWidth = 1,color="blue")%>%
@@
 
+# TODO the dataframe below is huge, cleaning it would make the script faster
 calib_spectro <- cbind(calib_spectro_all, calib_spectro_10m)
@@
 tmp <- d_all %>%
-  dplyr::select(datetime, depth, at, sal_insitu_ctd, temp_sf, pHint_tot_sf) %>%
+  dplyr::select(datetime, depth, at, sal_insitu_ctd_mix, temp_sf, pHint_tot_sf) %>%
   tidyr::drop_na() %>%
   dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
-tmp$pHint_tot_sf_temp_4 <- seacarb::pHinsi(pH=tmp$pHint_tot_sf, ALK=mean(tmp$at*1e-6, na.rm=TRUE), Tinsi=4, Tlab=tmp$temp_sf, Pinsi=tmp$depth/10, S=tmp$sal_insitu_ctd, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+tmp$pHint_tot_sf_temp_4 <- seacarb::pHinsi(pH=tmp$pHint_tot_sf, ALK=mean(tmp$at*1e-6, na.rm=TRUE), Tinsi=4, Tlab=tmp$temp_sf, Pinsi=tmp$depth/10, S=tmp$sal_insitu_ctd_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 d_all <- d_all %>% 
@@
 
-```{r seafet profiles, eval=FALSE, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+```{r, eval=FALSE, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+# The code below is now in the "stratification" tab
 
@@
         date <  as.Date("2018-05-19") & ph_dur_corr < 8.16 ~ NA_real_,
-      #date == as.Date("2015-11-19") & sal_mix < 33 ~ NA_real_,
+      #date == as.Date("2015-11-19") & sal_fb_mix < 33 ~ NA_real_,
       date > as.Date("2017-09-25") &
         date <  as.Date("2017-10-01") & ph_dur_corr < 8.07 ~ NA_real_,
-      #date == as.Date("2017-03-22") & sal_mix < 34 ~ NA_real_,
+      #date == as.Date("2017-03-22") & sal_fb_mix < 34 ~ NA_real_,
       TRUE ~ ph_dur_corr
@@
   d_all %>%
-  dplyr::select(montht, sal_mix, temp_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
+  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
   group_by(montht) %>%
@@
     dySeries("pHint_tot_sf_temp_4", label = "pH seaFET", color =  "red", strokeWidth = 0, pointSize = 2 ) %>%
-    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
     dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
@@
     dyRangeSelector(height = 30, dateWindow= NULL) 
-rm(durafet_sf_contros_xts, pdur_sf_norm_text)
+rm(durafet_sf_contros_xts)
 ```
@@
                 k = k600 * (Sc/600)^-0.5, #cm/h
-                alp = seacarb::K0(S=sal_mix,T=temp_insitu_11m,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
-                alp = alp * (seacarb::rho(S = sal_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
+                alp = seacarb::K0(S=sal_fb_mix,T=temp_insitu_11m,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
+                alp = alp * (seacarb::rho(S = sal_fb_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
                 f_air_sea = k * alp * delta_pco2 # mmol/(m2 h)
@@
 pangaea <- as_tibble(d_all) %>% 
-  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, sal_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb, pco2_calc_fb, at_calc, pH_dur, pHint_tot_sf) %>%
+  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, sal_fb_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb, pco2_calc_fb, at_calc, pH_dur, pHint_tot_sf) %>%
   dplyr::rename(pressure = depth,
@@
                 s_fb = sal_fb, 
-                s_mix = sal_mix,
+                s_mix = sal_fb_mix,
                 t_11m = temp_insitu_11m,
@@
 
--   sal_mix: when ferrybox data (sal_fb) are missing, they are replaced
+-   sal_fb_mix: when ferrybox data (sal_fb) are missing, they are replaced
     by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_10m)
 
--   sal_mix_interp: interpolated salinity sal_mix. It is used to have as
+-   sal_fb_mix_interp: interpolated salinity sal_fb_mix. It is used to have as
     many spec pH to display (some are during missing data)
 
--   temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m)
+-   temp_insitu_11m_mix: when data of in situ temperature at 11 m (temp_insitu_11m)
     are missing, they are replaced by data from the profiling ctd for
@@
 
--   temp_mix_interp: interpolated temperature temp_mix. It is used to
+-   temp_insitu_11m_mix_interp: interpolated temperature temp_insitu_11m_mix. It is used to
     have as many spec pH to display (some are during missing data)
 
--   pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb
-    +sal_fb
+-   sal_insitu_ctd_mix: when CTD salinity data from the REMOS are missing, they are replaced by data from sal_fb_mix (hence at FerryBox from 11 m and REMOS below 8 m).
+This is not ideal because difference of up to 1 salinity unit occur in the water column.
+But needed as there are many missig REMOS data.
+
+-   pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb + sal_fb
 
@@
     -   ph_s\_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT
-        interpolée + temp_mix +sal_mix
+        interpolée + temp_insitu_11m_mix + sal_fb_mix
     -   E0int25_sf: calculé à partir du voltage interne +
@@
 
--   Relation at / sal_mix
-
--   at_calc: calculé from sal_mix
+-   Relation at / sal_fb_mix
+
+-   at_calc: calculé from sal_fb_mix
 

### 2021-12-27 awipev-CO2.Rmd
modified ggreg

@@
 # function regression plot with equation (MA or OLS) in title
-ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", subtitle = "subtitle", xlab = "x", ylab = "y", proplot = TRUE, ...) 
+ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", xlab = "x", ylab = "y", proplot = TRUE, ...) 
   { # x and y are the names of the variables
@@
               colour = "blue")  + 
-  labs(title = paste(title, 
-                     "\ntype: ", type,
+  labs(title = title,
+       subtitle = paste("\ntype: ", type,
                      "; R2 = ", round(fit$rsquare, digits = 2),
@@
                     "rmse =", signif(sqrt(mean(error^2, na.rm=TRUE)), 3)),
-       subtitle = subtitle,
        x = xlab,
@@
     theme_bw() +
-    theme(plot.title = element_text(size = 7))
+    theme(plot.title = element_text(size = 10, face = "bold"),
+          plot.subtitle = element_text(size = 8))
     if (proplot == TRUE) { # property-property plot
@@
 # # Many issue with sal_ctd_insi
-# # read files made available by Philipp with  quality-controlled data
-# https://doi.org/10.1594/PANGAEA.929583
+# # read files made available by Philipp on 2021-12-09 with quality-controlled data
+# # not useful as these are FerryBox data...
+# https://dashboard.awi.de/?dashboard=3865
+# Test with one of the files: https://doi.org/10.1594/PANGAEA.929583
 # pg_data("10.1594/PANGAEA.929583")
@@
 ```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
-lm <- lm2(x = d_all$sal_insitu_ctd_10m, y = d_all$sal_fb)
-p <-  ggplot(d_all, aes(x=sal_insitu_ctd_10m, y = sal_fb))+
-  geom_point( aes(color=factor(monthd))) + 
-  geom_abline(slope=1, intercept=0, linetype = "dashed")+
-  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue") +
-  ylim(c(30.5,35.5)) +xlim(c(28,35.5)) +
-  labs(title = paste("","\n Adj R2 = ", signif(lm$rsquare, 3),
-                     "; Intercept =", signif(lm$intercept_MA, 3),
-                     "; Slope =", signif(lm$slope_MA, 3),
-                     "; P =", signif(lm$P, 3),
-                     "; RMSE = ", signif(lm$rmse, 3))) +
-  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
-  coord_fixed(ratio = 1 )+
-  labs( x="Salinity CTD 10 m", y="Salinity FB ", color = "Months") + theme_bw()
-
-print(p) #p_sal_fb_ctd
+reg <- ggreg(
+  xdata = d_all$sal_insitu_ctd_10m,
+  ydata = d_all$sal_fb,
+  type = "MA",
+  plot = TRUE,
+  title = "Comparison salinity",
+  #subtitle = "",
+  xlab = "Salinity CTD 10 m",
+  ylab = "Salinity FB",
+  proplot = TRUE,
+  ylim(c(30.5,35.5)) +xlim(c(28,35.5)),
+  coord_fixed(ratio = 1)
+)
+print(reg$plot)
 
@@
   title = title,
-  subtitle = "",
+  #subtitle = "",
   xlab = "Measured pCO2",

### 2021-12-27 awipev-CO2.Rmd
added code to read Philipp's files but not used in the end

@@
 # https://dashboard.awi.de/?dashboard=3865
-# Test with one of the files: https://doi.org/10.1594/PANGAEA.929583
-# pg_data("10.1594/PANGAEA.929583")
+# # NOT USED
+# file_list <- c("10.1594/PANGAEA.896828", "10.1594/PANGAEA.896822", "10.1594/PANGAEA.896821", "10.1594/PANGAEA.896771", "10.1594/PANGAEA.896770", "10.1594/PANGAEA.896170", "10.1594/PANGAEA.897349", "10.1594/PANGAEA.927607", "10.1594/PANGAEA.929583")
+# i <- 0; tmp <- NULL
+# for (i in 1:length(file_list)) {
+#     z <- pg_data(file_list[i])
+#     tmp <- dplyr::bind_rows(tmp, z[[1]]$data)
+# }
+# tmp <- tmp %>% 
+#   dplyr::mutate(datetime = lubridate::parse_date_time(tmp$`Date/Time`,
+#                 orders = "ymd HM")) %>% 
+#   dplyr::select(datetime, `Sal (PSU)`, `Temp [°C]`) %>% 
+#   dplyr::arrange(datetime) %>% 
+#   dplyr::distinct(datetime, .keep_all = TRUE) %>%  # there are a few duplicated datetime
+#   as_tsibble(index = datetime)
+# eff <- dplyr::left_join(d_hour, tmp, by = "datetime")
 

### 2021-12-27 awipev-CO2.Rmd
debugging warnings

@@
 ```{r read and prepare discrete AT+CT, echo=FALSE, warning=FALSE, message=FALSE}
-d <- read_excel(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.xlsx"),
-                col_names = TRUE) %>% 
-#   d <- tibble(
-#   read.table(paste0(path, "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.csv"), header = T, dec = ".", as.is = T, sep = ";", fill = TRUE)
-# ) %>% 
-  dplyr::mutate(datetime = dmy_hm(sampling_date, tz="UTC"),
-                measure_date = dmy(measure_date, tz="UTC"),
-                date = as.Date(datetime)) %>% 
-  #dplyr::filter(datetime < as.POSIXct("2021-01-01 00:00:00")) %>% #eliminate 2021 data
-  dplyr::rename(ph_s_sf = pH_s_seafet,
+d <-
+  read_excel(
+    paste0(
+      path,
+      "fb_data/Discrete_analyses_AT_CT/Discrete_sampling_AWIPEV.xlsx"
+    ),
+    skip = 0,
+    col_names = TRUE,
+    na = "NA"
+  ) %>%
+  dplyr::mutate(
+    datetime = lubridate::dmy_hm(sampling_date),
+    measure_date = lubridate::dmy(measure_date, tz = "UTC"),
+    date = lubridate::as_date(datetime)
+  ) %>%
+  dplyr::rename(
+    ph_s_sf = pH_s_seafet,
     ph_s_dur = pH_s_durafet,
     qflag_ph_s_sf = qflag_pH_s_seafet,
-                qflag_ph_s_dur = qflag_pH_s_durafet)
-
+    qflag_ph_s_dur = qflag_pH_s_durafet
+  ) %>%
+  dplyr::select(datetime, date, everything())
 # Add the flag location: some samples have been collected at the pier. Notes them here.
@@
 # Keep only flag = 2 for pH durafet and seaFET.
-d <- d%>%
-  dplyr::mutate(ct = replace(ct, qflag_ct != 2, NA),
-                at = replace(at, qflag_at != 2, NA),
-                ph_s_sf = replace(ph_s_sf, qflag_ph_s_sf != 2, NA),
-                ph_s_dur = replace(ph_s_dur, qflag_ph_s_dur != 2, NA))
+d <- d %>%
+  dplyr::mutate(ct = ifelse(qflag_ct == 2, ct, NA),
+                at = ifelse(qflag_at == 2, at, NA),
+                ph_s_sf = ifelse(qflag_ph_s_sf == 2, ph_s_sf, NA),
+                ph_s_dur = ifelse(qflag_ph_s_dur == 2, ph_s_dur, NA))
 
 # Mercuric chloride correction (Dickson et al. 2007, SOP3a)
-
-d$at <- as.numeric(d$at) * 1.0002
-d$ct <- as.numeric(d$ct) * 1.0002
+d <- d %>%
+  dplyr::mutate(at = at * 1.0002,
+                ct = ct * 1.0002)
 
@@
 # Fill the gaps in at_mean with interpolation
-TAinterp <-approx(d$datetime, d$at_mean, xout=d$datetime, method="linear", rule=2)
+TAinterp <- approx(d$datetime, d$at_mean, xout=d$datetime, method="linear", rule = 2, ties = "ordered")
 names(TAinterp) <- c("datetime", "at_mean_interp")
@@
 
-CTinterp <-approx(d$datetime, d$ct_mean, xout=d$datetime, method="linear", rule=2)
+CTinterp <-approx(d$datetime, d$ct_mean, xout=d$datetime, method="linear", rule = 2, ties = "ordered")
 names(CTinterp) <- c("datetime", "ct_mean_interp")
@@
 # We take temp_insitu_11m_mix/sal_fb_mix because of the depth (temp11m insitu + temp10m ctd)
-tempmixinterp <-approx(d_all$datetime, d_all$temp_insitu_11m_mix, xout=d_all$datetime, method="linear", rule=2)
+tempmixinterp <- approx(d_all$datetime, d_all$temp_insitu_11m_mix, 
+                        xout=d_all$datetime, method="linear", rule = 2, ties = "ordered")
 names(tempmixinterp) <- c("datetime", "temp_insitu_11m_mix_interp")
@@
 
-salmixinterp <-approx(d_all$datetime, d_all$sal_fb_mix, xout=d_all$datetime, method="linear", rule=2)
+salmixinterp <- approx(d_all$datetime, d_all$sal_fb_mix, xout=d_all$datetime, 
+                       method="linear", rule = 2, , ties = "ordered")
 names(salmixinterp) <- c("datetime", "sal_fb_mix_interp")
@@
                  "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
-zz <- pivot_longer(z, -Flag)
-p_avail <- ggplot(data = zz, aes(x = name, y = value, fill = Flag)) +
+p_avail <- pivot_longer(z, -Flag) %>% 
+  drop_na() %>% 
+  ggplot(aes(x = name, y = value, fill = Flag)) +
   geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
-  #scale_y_reverse() +
   scale_fill_discrete(labels = labels) + 
   coord_flip() +
-  #geom_text(aes(label=round(value, digits = 0)), position = position_stack((hjust = 0.5)), size = 3) +
   labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
@@
   theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
-#ggsave(filename = "figures/availability.png", plot = p_avail, width = 15, height = 8, units = "cm")
 kable(z, digits = 1)
-
 # Monthly distribution of hourly data
@@
 # plot the distribution of non-NA pCO2 and pH values per month
-d2_summary_long <- d2_summary %>% 
-  tidyr::pivot_longer(cols = c(pco2_pc, pH_pc))
-p_avail_month <- ggplot(data = d2_summary_long) +
+p_avail_month <- d2_summary %>% 
+  tidyr::pivot_longer(cols = c(pco2_pc, pH_pc)) %>% 
+  ggplot() +
   geom_col(aes(x = montht, y = value, fill = name), position = "dodge", width = 0.75) +
@@
   )
-names(salinterp) <- c("datetime", "sal_insitu_ctd_interp")
+names(salinterp) <- c("datetime", "sal_insitu_ctd_mix_interp")
 salinterp <- as.data.frame(salinterp)
-d_all$sal_insitu_ctd_interp <- salinterp$sal_insitu_ctd_interp
+d_all$sal_insitu_ctd_interp <- salinterp$sal_insitu_ctd_mix_interp
 

### 2021-12-27 awipev-CO2.Rmd
addessing outliers in sal_insitu_ctd cleaning up

@@
 library("todor")
+# todor::todor_file("awipev-CO2.Rmd")
 
@@
 # function regression plot with equation (MA or OLS) in title
-ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", xlab = "x", ylab = "y", proplot = TRUE, ...) 
+ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", xlab = "x", 
+                   ylab = "y", proplot = TRUE, ...) 
   { # x and y are the names of the variables
@@
 if (type == "MA") ty = 2 #one selects MA only
-#reg <- fit$regression.results[ty,] #one selects OLS only
 intercept <- fit$regression.results$Intercept[ty]
@@
        y = ylab) +
-#    lims(x = c(min(fit_data$xdata), max(fit_data$xdata)), y = c(min(fit_data$ydata), max(fit_data$ydata))) +
     theme_bw() +
@@
 # eff <- dplyr::left_join(d_hour, tmp, by = "datetime")
+
+# To address the issues of sal_insitu_ctd (many outliers, see figure in tab salinities)
+# the impossibly low values are identified using the threshold of the 
+# minimum salinity measured in the FerryBox - 0 unit
+d_hour <- d_hour %>% 
+  dplyr::mutate(sal_insitu_ctd = ifelse(sal_insitu_ctd < min(sal_fb, na.rm = TRUE) - 0 |
+                                        sal_insitu_ctd > 36,  # 2 outliers
+                                        sal_fb, sal_insitu_ctd))
 
@@
 salmixinterp <- approx(d_all$datetime, d_all$sal_fb_mix, xout=d_all$datetime, 
-                       method="linear", rule = 2, , ties = "ordered")
+                       method="linear", rule = 2, ties = "ordered")
 names(salmixinterp) <- c("datetime", "sal_fb_mix_interp")
@@
   theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0.5, unit = "cm"))
-#ggsave(filename = "figures/monthly_availability.png", plot = p_avail_month, width = 15, height = 8, units = "cm")
-
 # Combine plots
@@
   dyLegend(show = "follow")   %>%
-    dyAxis("y",valueRange = c(30, 37)) %>%
-      dyRangeSelector(height = 30, dateWindow= NULL)
+  dyAxis("y", valueRange = c(30, 37)) %>%
+  dyRangeSelector(height = 30, dateWindow = NULL)
 # now remove outliers
@@
       date > as.Date("2015-10-01") &
-        date <  as.Date("2015-10-05") & sal_fb_mix < 31.5 ~ NA_real_,
+        date <  as.Date("2015-10-05") &
+        sal_fb_mix < 31.5 ~ NA_real_,
       date == as.Date("2017-03-22") &
@@
 ```{r, eval=FALSE, echo=FALSE}
+# skipped because it is done in the "stratification tab"
 Extreme differences: `r dplyr::filter(tmp, range_diff < -3 | range_diff > 2)`.
@@
 
-### **Sal FB / Sal CTD 10 m**
-
-```{r Sal comparaison, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+### **Comparison salinity FerryBox vs Salinity CTD REMOS 10 m** 
+```{r, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+# REVIEW OK?
 reg <- ggreg(
   xdata = d_all$sal_insitu_ctd_10m,
-  ydata = d_all$sal_fb,
+  ydata = d_all$sal_fb_mix,
   type = "MA",
@@
   #subtitle = "",
-  xlab = "Salinity CTD 10 m",
-  ylab = "Salinity FB",
+  xlab = "Salinity CTD REMOS 10 m",
+  ylab = "Salinity FerryBox",
   proplot = TRUE,
-  ylim(c(30.5,35.5)) +xlim(c(28,35.5)),
+  ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
   coord_fixed(ratio = 1)
@@
 
+```{r, eval=FALSE, echo=FALSE}
+# skipped because it is done in the "stratification tab"
 There are `r sum(!is.na(tmp$range))` days with temperature values at
@@
 The difference with depth is therefore significant.
-
-### **T Ferrybox / T insitu 11 m**
-
-```{r Temp fb insi comparaison, echo=FALSE, message= FALSE, warning=FALSE}
+```
+
+### **Temperature Ferrybox vs Temperature in situ 11 m** 
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 # Remove temp_fb outliers 
@@
   )
-lm <- lm2(x = d_all$temp_insitu_11m, y = d_all$temp_fb)
-
-p <-  ggplot(d_all,aes(x=temp_insitu_11m, y= temp_fb, label = monthd))+
-  geom_text( aes(color=factor(monthd))) + 
- # scale_color_viridis_d(option = "C", guide="none")+
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue")  +
-  labs(title = paste("T FB vs T 11 m","\n Adj R2 = ", signif(lm$rsquare, 3),
-                     "; Intercept =", signif(lm$intercept_MA, 3),
-                     "; Slope =", signif(lm$slope_MA, 3),
-                     "; P =", signif(lm$P, 3),
-                     "; RMSE = ", signif(lm$rmse, 3))) +
-  theme_bw() +
-  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + 
-  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
-  labs(x="T 11 m", y="T FB ", color = "Months") 
-print(p) # p_temp_11_fb
+
+reg <- ggreg(
+  xdata = d_all$temp_insitu_11m,
+  ydata = d_all$temp_fb,
+  type = "MA",
+  plot = TRUE,
+  title = "Comparison temperature",
+  #subtitle = "",
+  xlab = "Temperature in situ 11 m",
+  ylab = "Temperature FerryBox",
+  proplot = TRUE,
+  ylim(c(-2, 8.5)) + xlim(c(-2, 8.5)),
+  coord_fixed(ratio = 1)
+)
+print(reg$plot) # p_temp_11_fb
 
@@
 ```{r Temp 11m and ctd comparaison, echo=FALSE, message= FALSE, warning=FALSE}
-lm <- lm2(x = d_all$temp_insitu_ctd_10m, y = d_all$temp_insitu_11m)
-p <-  ggplot(d_all, aes(x=temp_insitu_ctd_10m, y= temp_insitu_11m, label = monthd))+
-  geom_text( aes(color=factor(monthd))) + 
- # scale_color_viridis_d(option = "C", guide="none")+
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),colour = "blue")  +  labs(title = paste("T CTD 9 m vs T 11 m","\n Adj R2 = ", signif(lm$rsquare, 3),
-                     "; Intercept =", signif(lm$intercept_MA, 3),
-                     "; Slope =", signif(lm$slope_MA, 3),
-                     "; P =", signif(lm$P, 3),
-                     "; RMSE = ", signif(lm$rmse, 3))) +
-  theme_bw() +
-  theme(aspect.ratio = 1,plot.title = element_text(size = 7)) + 
-  coord_fixed(ratio = 1 ) + scale_colour_discrete(guide="none") +
-  labs( x="T CTD 9 m", y="T 11 m ", color = "Months")
-print(p)
+reg <- ggreg(
+  xdata = d_all$temp_insitu_ctd_10m,
+  ydata = d_all$temp_insitu_11m,
+  type = "MA",
+  plot = TRUE,
+  title = "Comparison temperature",
+  #subtitle = "",
+  xlab = "Temperature CTD REMOS 10 m",
+  ylab = "Temperature in situ 11 m",
+  proplot = TRUE,
+  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
+  coord_fixed(ratio = 1)
+)
+print(reg$plot)
 
@@
 
-# above is old code. now we use sal_insitu_ctd_mix
+# above is old code. Now we use sal_insitu_ctd_mix
 salinterp <-
@@
 tmp <- d_all %>%
-  dplyr::select(datetime, at, sal_fb, temp_fb, pH_dur) %>%
+  dplyr::select(datetime, at, sal_fb_mix, temp_fb, pH_dur) %>%
   tidyr::drop_na()
-tmp$pH_dur_temp_4 <- seacarb::pHinsi(pH=tmp$pH_dur, ALK=mean(tmp$at*1e-6, na.rm=TRUE), Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+tmp$pH_dur_temp_4 <- seacarb::pHinsi(pH=tmp$pH_dur, ALK=mean(tmp$at*1e-6, na.rm=TRUE), Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 d_all <- d_all %>% 
@@
 pH_calc <- discrete %>%
-  dplyr::select(datetime, sal_fb, temp_fb, ph_calc_fb, at)%>%
-  dplyr::filter(!is.na(ph_calc_fb), !is.na(temp_fb), !is.na(sal_fb))
-pH_calc$pH_calc_fb_temp_4 <- pHinsi(pH = pH_calc$ph_calc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+  dplyr::select(datetime, sal_fb_mix, temp_fb, ph_calc_fb, at)%>%
+  dplyr::filter(!is.na(ph_calc_fb), !is.na(temp_fb), !is.na(sal_fb_mix))
+pH_calc$pH_calc_fb_temp_4 <- pHinsi(pH = pH_calc$ph_calc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 
@@
             mean_pco2_calc = mean(pco2_calc_fb, na.rm = TRUE),
-            mean_sal = mean(sal_fb, na.rm = TRUE),
+            mean_sal = mean(sal_fb_mix, na.rm = TRUE),
             mean_temp = mean(temp_fb, na.rm = TRUE)) %>% 
@@
 mean_pco2 <- mean(discrete$pco2_calc_fb, na.rm = TRUE)
-mean_sal <- mean(discrete$sal_fb, na.rm = TRUE)
+mean_sal <- mean(discrete$sal_fb_mix, na.rm = TRUE)
 mean_temp <- mean(discrete$temp_fb, na.rm = TRUE)
@@
 tmp <- d_all %>% 
-  tidyr::drop_na(ph_s_dur_temp_fb, pco2_fb, at, sal_fb, temp_fb) %>% 
-  dplyr::select(datetime, ph_s_dur_temp_fb, pco2_fb, at, sal_fb, temp_fb) %>% 
+  tidyr::drop_na(ph_s_dur_temp_fb, pco2_fb, at, sal_fb_mix, temp_fb) %>% 
+  dplyr::select(datetime, ph_s_dur_temp_fb, pco2_fb, at, sal_fb_mix, temp_fb) %>% 
   dplyr::mutate(
@@
                          Tlab = temp_fb, Pinsi = 0,
-                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d",
+                         S = sal_fb_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d",
                          pHscale = "T", b="u74"),
@@
                          Tlab = temp_fb, Pinsi = 0,
-                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d",
+                         S = sal_fb_mix, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d",
                          pHscale = "T", b="u74"),       # Millero 02
@@
                          Tlab = temp_fb, Pinsi = 0,
-                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d",
+                         S = sal_fb_mix, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d",
                          pHscale = "T", b="u74"),
@@
                          Tlab = temp_fb, Pinsi = 0,
-                         S = sal_fb, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d",
+                         S = sal_fb_mix, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d",
                          pHscale = "T", b="u74")
@@
   # dplyr::select(datetime, ph_s_dur_temp_4_l, ph_s_dur_temp_4_s20,
-  #               ph_s_dur_temp_4_p18, ph_s_dur_temp_4_m02, pco2_fb, at, sal_fb, temp_fb) %>%
+  #               ph_s_dur_temp_4_p18, ph_s_dur_temp_4_m02, pco2_fb, at, sal_fb_mix, temp_fb) %>%
 # This is an important adjustement for pco2_fb on 2019-06-07 09:00:00
@@
 # Using Lueker  
-carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 
+carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", 
@@
 # Using Sulpis
-carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 
+carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks = "d", 
@@
 # Using Papadimitriou
-carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 
+carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks = "d", 
@@
 # Using Millero et al. (2002)
-carb_m <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb, 
+carb_m <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks = "d", 
@@
 tmp <- d_all %>% 
-  tidyr::drop_na(ph_s_dur_temp_fb, ct, at, sal_fb, temp_fb) %>% 
-  dplyr::select(datetime, ph_s_dur_temp_fb, ct, at, sal_fb, temp_fb) %>% 
+  tidyr::drop_na(ph_s_dur_temp_fb, ct, at, sal_fb_mix, temp_fb) %>% 
+  dplyr::select(datetime, ph_s_dur_temp_fb, ct, at, sal_fb_mix, temp_fb) %>% 
   dplyr::mutate(
@@
 # Using Lueker  
-carb_l2 <- carb(flag = 15, var1 = tmp$at * 1e-6, var2 = tmp$ct * 1e-6, S = tmp$sal_fb, 
+carb_l2 <- carb(flag = 15, var1 = tmp$at * 1e-6, var2 = tmp$ct * 1e-6, S = tmp$sal_fb_mix, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", 
@@
 # Using Sulpis
-  carb_s2 <- carb(flag = 15, var1 = tmp$at * 1e-6, var2 = tmp$ct * 1e-6, S = tmp$sal_fb, 
+  carb_s2 <- carb(flag = 15, var1 = tmp$at * 1e-6, var2 = tmp$ct * 1e-6, S = tmp$sal_fb_mix, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks = "d", 
@@
 # Using Papadimitriou
-carb_p2 <- carb(flag = 15, var1 = tmp$at * 1e-6, var2 = tmp$ct * 1e-6, S = tmp$sal_fb, 
+carb_p2 <- carb(flag = 15, var1 = tmp$at * 1e-6, var2 = tmp$ct * 1e-6, S = tmp$sal_fb_mix, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks = "d", 
@@
 # Using Millero et al. (2002)
-carb_m2 <- carb(flag = 15, var1 = tmp$at * 1e-6, var2 = tmp$ct * 1e-6, S = tmp$sal_fb, 
+carb_m2 <- carb(flag = 15, var1 = tmp$at * 1e-6, var2 = tmp$ct * 1e-6, S = tmp$sal_fb_mix, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks = "d", 
@@
 taka <- d_all %>% # just for this chunk
-  dplyr::select(datetime, monthd, sal_fb, temp_insitu_11m, pco2_fb_insi_temp) %>% 
+  dplyr::select(datetime, monthd, sal_fb_mix, temp_insitu_11m, pco2_fb_insi_temp) %>% 
   dplyr::mutate(year = lubridate::year(datetime),
@@
 deconv_tmp <- d_all %>% # just for this chunk
-  dplyr::select(datetime, monthd, sal_fb, temp_fb, pco2_fb, at_calc) %>% 
+  dplyr::select(datetime, monthd, sal_fb_mix, temp_fb, pco2_fb, at_calc) %>% 
   tidyr::drop_na()
@@
   dplyr::mutate(ct_calc = seacarb::carb(
-    flag = 24, var1 = deconv_tmp$pco2_fb, var2 = deconv_tmp$at_calc*1e-6, S=deconv_tmp$sal_fb, T=deconv_tmp$temp_fb, 
+    flag = 24, var1 = deconv_tmp$pco2_fb, var2 = deconv_tmp$at_calc*1e-6, S=deconv_tmp$sal_fb_mix, T=deconv_tmp$temp_fb, 
     Patm=1, P=1.1, Pt=0, Sit=0, 
@@
   dplyr::summarise(
-    sal_fb = mean(sal_fb, na.rm = TRUE),
+    sal_fb_mix = mean(sal_fb_mix, na.rm = TRUE),
     temp_fb = mean(temp_fb, na.rm = TRUE),
@@
                      date=as.POSIXct(deconv_tmp$datetime),
-                     mAT=deconv_monthly$at_calc[deconv_tmp$monthd]*1e-6, mCT=deconv_monthly$ct_calc[deconv_tmp$monthd]*1e-6, mS=deconv_monthly$sal_fb[deconv_tmp$monthd], mT=deconv_monthly$temp_fb[deconv_tmp$monthd], P=11/10, Pt=rep(0, length.out=nrow(deconv_tmp)), Sit=rep(0, length.out=nrow(deconv_tmp)), AT=deconv_tmp$at_calc*1e-6, CT=deconv_tmp$ct_calc*1e-6, S=deconv_tmp$sal_fb, T=deconv_tmp$temp_fb)
+                     mAT=deconv_monthly$at_calc[deconv_tmp$monthd]*1e-6, mCT=deconv_monthly$ct_calc[deconv_tmp$monthd]*1e-6, mS=deconv_monthly$sal_fb_mix[deconv_tmp$monthd], mT=deconv_monthly$temp_fb[deconv_tmp$monthd], P=11/10, Pt=rep(0, length.out=nrow(deconv_tmp)), Sit=rep(0, length.out=nrow(deconv_tmp)), AT=deconv_tmp$at_calc*1e-6, CT=deconv_tmp$ct_calc*1e-6, S=deconv_tmp$sal_fb_mix, T=deconv_tmp$temp_fb)
 
@@
                 t_fb = temp_fb, 
+                t_s = temp_fb,
                 t_sf = temp_sf, 
@@
 -   sal_insitu_ctd_mix: when CTD salinity data from the REMOS are missing, they are replaced by data from sal_fb_mix (hence at FerryBox from 11 m and REMOS below 8 m).
-This is not ideal because difference of up to 1 salinity unit occur in the water column.
-But needed as there are many missig REMOS data.
-
--   pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb + sal_fb
+This is not ideal because differences of up to 1 salinity unit occur in the water column.
+But needed as there are many missing REMOS data.
+
+-   pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb + sal_fb_mix
 
@@
 
--   ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
+-   ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb_mix
 
@@
     -   ph_s\_dur_temp_fb: pH spectro durafet pH insi calculé avec AT
-        interpolée + temp_fb +sal_fb
+        interpolée + temp_fb + sal_fb_mix
 

### 2021-12-28 awipev-CO2.Rmd
multiple changes, mostly about format

@@
 library("pangaear")
+if (!require("latex2exp")) install.packages("latex2exp")
+library("latex2exp")
 if (!require("todor")) install.packages("todor")
@@
         axis.ticks.length = unit(1.1, "mm"),
-        panel.grid.major = element_line(size = 0.25, color="black", linetype="dashed"),
+        #panel.grid.major = element_line(size = 0.25, color="black", linetype="dashed"),
         #aspect.ratio = 1 / 2,
@@
 
-```{r data availability, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+```{r, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
 d_min <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_minute.rds")) %>%
@@
   coord_flip() +
-  labs(x="", y="", title = "Distribution (%) of quality flags", color = "Quality flag") +
-  Mytheme(size_labs = 8) +
+  labs(x="", y="", title = "Distribution (%) of quality flags") +
+  Mytheme(size_labs = 8) #+
   theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
@@
   dplyr::group_by(montht) %>% 
-  dplyr::summarise(pco2_pc = round(100 * sum(!is.na(pco2_fb))/count_pco2_fb_no_NA, digits = 1),
+  dplyr::summarise(pco2 = round(100 * sum(!is.na(pco2_fb))/1000, digits = 1),
+                   pH = round(100 * sum(!is.na(phINT))/1000, digits = 1),
+                   pco2_pc = round(100 * sum(!is.na(pco2_fb))/count_pco2_fb_no_NA, digits = 1),
                    pH_pc = round(100 * sum(!is.na(phINT))/count_phINT_no_NA, digits = 1)
@@
 p_avail_month <- d2_summary %>% 
-  tidyr::pivot_longer(cols = c(pco2_pc, pH_pc)) %>% 
+  tidyr::pivot_longer(cols = c(pco2, pH)) %>% 
   ggplot() +
@@
   scale_fill_discrete(name = "", labels = c("pCO2", "pH")) + 
-  labs(x="Month", y="Percent of total number of data", title = "") +
-  Mytheme(size_labs = 8) +
-  theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0.5, unit = "cm"))
+  labs(x="Month", y="Number of data (thousands)", title = "") +
+  Mytheme(size_labs = 8) #+
+  #theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0.5, unit = "cm"))
 # Combine plots
@@
 
-# deleted uneeded data
+# deleted unneeded data
 rm(x, d_min, list=ls(pattern="^d2"))
@@
   dplyr::select(datetime, monthd,closest_datetime, at, sal_fb_mix)
-
-fit <- lm(data = d_all_at_discrete, at ~ sal_fb_mix)
-slope_s_at <- fit$coefficients[[2]]
-intercept_s_at <- fit$coefficients[[1]]
-at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb_mix, y= at, label = monthd))+
-  geom_text( aes(color=factor(monthd))) +
-  scale_color_discrete(guide="none")+
-    labs(x="Salinity", y="Discrete AT", color = "Months")  +
-    stat_smooth(method = "lm", col = "black") +
-    labs(title = paste("", "\nAdj R2 = ",signif(summary(fit)$adj.r.squared, 5),
-                       ";\nIntercept =",signif(fit$coef[[1]],5 ),
-                       ";\nSlope =",signif(fit$coef[[2]], 5),
-                       ";\nP =", signif(summary(fit)$coef[2,4], 5),
-                       ";\nRMSE =", signif(sqrt(mean(fit$residuals^2)), 5))) +
-  theme_bw() +
-  theme(aspect.ratio=1,
-        axis.text=element_text(size=7),
-        axis.title.y= element_text(size =7),
-        axis.title.x= element_text(size =7),
-        plot.margin = unit(c(0.5,1,1,1), "cm"),
-        plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70)))
-ggsave(filename = "figures/at_s.png", plot = at_s, width = 25, height = 20, units = "cm")
+reg <- ggreg(
+  xdata = d_all$sal_fb_mix,
+  ydata = d_all$at,
+  type = "OLS",
+  plot = TRUE,
+  title = "Discrete total alkalinity vs salinity",
+  #subtitle = "",
+  xlab = "Salinity",
+  ylab = TeX("Total alkalinity ($\\mu mol\\~kg^{-1})$"),
+  proplot = TRUE,
+  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
+  coord_fixed(ratio = 1)
+)
+print(reg$plot)
+ggsave(filename = "figures/at_s.png", plot = reg$plot, width = 25, height = 20, units = "cm")
 
 # Same plot for paper
-p_at_s <- ggplot(d_all_at_discrete,aes(x=sal_fb_mix, y= at)) +
-  geom_point(col="blue", size = 0.2) +
-  labs(x="Salinity", y="Discrete AT")  +
-  stat_smooth(method = "lm", col = "blue", size = 0.3) +
-  theme_bw(base_size = 9) +
-  theme(aspect.ratio=1#,
-        #axis.text=element_text(size=7),
-        #axis.title.y= element_text(size =7),
-        #axis.title.x= element_text(size =7),
-        #plot.margin = unit(c(0.5,1,1,1), "cm"),
-        #plot.title = element_text(size=7, hjust=0.05,margin = margin(l = 10, b = -70))
-        )
+p_at_s <- d_all_at_discrete %>% 
+  drop_na() %>% 
+  ggplot(aes(x = sal_fb_mix, y = at)) +
+  geom_point(col="blue", size = 0.5) +
+  labs(x="Salinity", y=TeX("Total alkalinity ($\\mu mol\\~kg^{-1})$"))  +
+  stat_smooth(method = "lm", col = "blue", size = 0.5) +
+  Mytheme(size_labs = 9)
 ggsave(filename = "figures/p_at_s.png", plot = p_at_s, width = 7, height = 7, units = "cm")
@@
 
-<!-- #### **TA since November 2018 (final installation)** -->
-
-<!-- ```{r TA since November 2018, echo=FALSE, warning=FALSE, message=FALSE,out.width='100%',fig.align='hold'} -->
-
-<!--  # select subset of data and remove obvious outliers -->
-
-<!--  at_nov_2018 <- -->
-
-<!--   dplyr::select(d_all, datetime, at_calc, AT, at) %>% -->
-
-<!--   filter(datetime > "2018-11-01", AT > 2250) -->
-
-<!-- #despike -->
-
-<!-- at_nov_2018 <- mutate(at_nov_2018, AT_despike = despike(AT, reference= "median", n=0.5, k=10, replace="NA")) -->
-
-<!-- #plot -->
-
-<!-- at_datetime <- ggplot(data = at_nov_2018, aes(x=datetime)) + -->
-
-<!--   geom_point(aes(y=AT, colour = "before"), size =3) + -->
-
-<!--   geom_point(aes(y=AT_despike, colour = "after"), size = 2) + -->
-
-<!--   labs(x = "Time", y = "Total alkalinity", color = "despike") -->
-
-<!-- print(at_datetime) -->
-
-<!-- at_nov_2018_no_NA <- dplyr::filter(at_nov_2018, at_calc != "NA" & AT_despike != "NA") -->
-
-<!-- titre <- "Contros AT vs Calculated AT" -->
-
-<!--  fit <- lmodel2(data = at_nov_2018_no_NA, AT_despike ~ at_calc, nperm = 99) -->
-
-<!-- ggreg2(fit, x = "at_calc", y = "AT_despike") -->
-
-<!-- ``` -->
-
 ## *p*CO~2~ and *f*CO~2~
@@
 
-### **Corrected Contros vs calculated *p*CO~2~ data**
-
-```{r pco2 and fco2 at in situ temp, echo=FALSE, warning=FALSE, message=FALSE}
+### **Contros vs calculated *p*CO~2~**
+
+```{r, echo=FALSE, warning=FALSE, message=FALSE}
 d_all <- d_all %>%
@@
 ```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-title <- "pCO2 normalized at in situ temperature"
 reg <- ggreg(
@@
   plot = TRUE,
-  title = title,
+  title = "pCO2 normalized at in situ temperature",
   #subtitle = "",
-  xlab = "Measured pCO2",
-  ylab = "Calculated pCO2",
-  proplot = TRUE
-)
-p <- reg$plot
-ggsave(filename = "figures/pco2_calc_meas.png", plot = p)
+  xlab = latex2exp::TeX("Measured $pCO_{2}(\\mu atm)$"),
+  ylab = latex2exp::TeX("Calculated $pCO_{2}(\\mu atm)$"),
+  proplot = TRUE,
+  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
+  coord_fixed(ratio = 1)
+)
+print(reg$plot)
+ggsave(filename = "figures/pco2_calc_meas.png", plot = reg$plot)
 ```
@@
 ```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-print(p$plot)
-rm(fit, p)
+print(reg$plot)
+rm(fit, reg)
 ```
@@
   dplyr::select(deployment_sf, tidyr::starts_with("E0")) %>% 
+  drop_na() %>% 
   tidyr::pivot_longer(cols = starts_with("E0"), names_to = "variable", values_to = "value")
-p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
+p_calib <- kk %>% 
+  ggplot() + 
+  geom_point(aes(x=deployment_sf, y=value, color=variable), size=2) +
   facet_grid(variable ~ ., scales="fixed") + theme_bw() +
@@
 
-# TODO the dataframe below is huge, cleaning it would make the script faster
 calib_spectro <- cbind(calib_spectro_all, calib_spectro_10m)
@@
 p <-
-  ggplot(data=range_dur, aes(x = as.factor(montht), y = pH_range)) +
+  ggplot(data = tidyr::drop_na(range_dur), 
+         aes(x = as.factor(montht), y = pH_range)) +
   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
@@
   tidyr::drop_na()
-tmp$pH_dur_temp_4 <- seacarb::pHinsi(pH=tmp$pH_dur, ALK=mean(tmp$at*1e-6, na.rm=TRUE), Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+tmp$pH_dur_temp_4 <- seacarb::pHinsi(pH=tmp$pH_dur, ALK=tmp$at, Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 d_all <- d_all %>% 
-  left_join(tmp %>% dplyr::select(datetime, pH_dur_temp_4 ), by="datetime")
+  left_join(tmp %>% dplyr::select(datetime, pH_dur_temp_4), by="datetime")
 ```

### 2021-12-29 awipev-CO2.Rmd
fixed TeX issue

@@
   xlab = "Salinity",
-  ylab = TeX("Total alkalinity ($\\mu mol\\~kg^{-1})$"),
+  ylab = TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"),
   proplot = TRUE,
@@
   geom_point(col="blue", size = 0.5) +
-  labs(x="Salinity", y=TeX("Total alkalinity ($\\mu mol\\~kg^{-1})$"))  +
+  labs(x="Salinity", y=TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
   stat_smooth(method = "lm", col = "blue", size = 0.5) +
@@
   #subtitle = "",
-  xlab = latex2exp::TeX("Measured $pCO_{2}(\\mu atm)$"),
-  ylab = latex2exp::TeX("Calculated $pCO_{2}(\\mu atm)$"),
+  xlab = latex2exp::TeX("Measured $pCO_{2}\\phantom{x}(\\mu atm)$"),
+  ylab = latex2exp::TeX("Calculated $pCO_{2}\\phantom{x}(\\mu atm)$"),
   proplot = TRUE,

### 2021-12-29 awipev-CO2.Rmd
minor

@@
   dplyr::arrange(datetime) %>%
-  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(durPeriod)])/2* 3600 )))%>%
+  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(durPeriod)])/2* 3600 ))) %>%
   dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])

### 2021-12-29 awipev-CO2.Rmd
cleaning up continued

--- 2021-12-29 awipev-CO2.Rmd
@@
         geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
-        theme(aspect.ratio = 1)
+        theme(aspect.ratio = 1) +
+        coord_fixed(ratio = 1, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on")
     }
@@
   ) %>% 
-  # data post 2020-03-01 eliminated because no maintenance and lots of algae
-  dplyr::mutate(pco2_fb = ifelse(datetime >= as.POSIXct("2020-03-01 00:00"), NA, pco2_fb)) %>%
+  # pCO2 data post 2020-03-01 eliminated because no maintenance and lots of algae
+  # pH durafet data post 2020-01-01 eliminated because no maintenance and lots of algae
+  dplyr::mutate(pco2_fb = ifelse(datetime >= as.POSIXct("2020-03-01 00:00"), NA, pco2_fb),
+                ph_dur = ifelse(datetime >= as.POSIXct("2020-01-01 00:00"), NA, ph_dur)) %>%
   arrange(datetime)
@@
 # deployment period between 2 spectro measurements.
-durPeriod <- d_all%>%
-  dplyr::select(datetime, ph_s_dur_temp_fb)%>%
+# TODO the following throws a warning but seems to work
+durPeriod <- d_all %>%
+  dplyr::select(datetime, ph_s_dur_temp_fb) %>%
   dplyr::filter(!is.na(ph_s_dur_temp_fb))
-
 durPeriod <- durPeriod %>% 
-  dplyr::arrange(datetime) %>%
-  dplyr::mutate(middle=  seconds_to_period(c(0,difftime(time1= datetime[-1], time2= datetime[-nrow(durPeriod)])/2* 3600 )))%>%
+  #dplyr::arrange(datetime) %>%
+  dplyr::mutate(middle =  seconds_to_period(
+   c(0, difftime(time1 = datetime[-1], time2 = datetime[-nrow(durPeriod)])/2* 3600 ))) %>%
   dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])
@@
 # Offset between durafet pH and spec pH 
-duroffset <- left_join(durPeriod%>%dplyr::select(datetime,ph_s_dur_temp_fb), d_all%>%dplyr::select(datetime,ph_dur ), by="datetime")
-dat_dur <- mutate(duroffset, diff_pH_dur = ph_s_dur_temp_fb - ph_dur)
+duroffset <- left_join(durPeriod %>% dplyr::select(datetime, ph_s_dur_temp_fb), d_all %>% dplyr::select(datetime, ph_dur), by="datetime")
+dat_dur <- duroffset %>% 
+  drop_na() %>% 
+  dplyr::mutate(diff_pH_dur = ph_s_dur_temp_fb - ph_dur)
 average_offset_dur <- round(mean(dat_dur$diff_pH_dur, na.rm=TRUE), digits = 2)
@@
 
-plot_offset_dur <- ggplot(data = filter(dat_dur, !is.na(diff_pH_dur))) +
-  geom_hline(yintercept=mean(dat_dur$diff_pH_dur, na.rm = TRUE), size=0.3, col="red") +
+plot_offset_dur <- dat_dur %>% 
+  drop_na() %>% 
+  ggplot() +
+  geom_hline(yintercept = mean(dat_dur$diff_pH_dur, na.rm = TRUE), size=0.3, col="red") +
   annotate("text", x = dat_dur$datetime[3], y =-0.16, label = "offset mean", color="red")+
@@
 
-# RANGE of pH
-range_dur <- tbl_df(
-  d_all %>%
-  group_by(date, montht, year=year(datetime)) %>%
+# Range of pH per day
+range_dur <- d_all %>%
+  group_by(date, montht) %>%
   summarize(pH_range = max(ph_dur_corr) - min(ph_dur_corr))
-)
 quant <- quantile(range_dur$pH_range, probs =c(2.5/100, 97.5/100), na.rm =TRUE)
-
-# Per month
-range_month <-
-  range_dur %>%
+# Range of pH per month
+range_month <- range_dur %>%
   group_by(montht) %>%
@@
 
-size_point <- 0.4 # size of data points
-p <-
-  ggplot(data = tidyr::drop_na(range_dur), 
-         aes(x = as.factor(montht), y = pH_range)) +
+p <- range_dur %>% 
+  tidyr::drop_na() %>% 
+  ggplot(aes(x = as.factor(montht), y = pH_range)) +
   geom_violin(fill='lightblue', alpha=0.5, size=0.2, trim = TRUE) +
@@
 
-```{r Range per month, echo=FALSE, message= FALSE, warning=FALSE}
+```{r Range per month, eval = FALSE, echo=FALSE, message= FALSE, warning=FALSE}
 my_skim <- skim_with(numeric = sfl(ave = ~ mean(., na.rm = TRUE),
@@
 
-### **seaFET / durafet pHs (all > 8 m)**
-
-```{r pHs comparaison 4°C, echo=FALSE, message= FALSE, warning=FALSE}
-# prepare data and remove sf biofouling period
-# TODO consider biofouling period elsewhere too
-#   pH_sf <- d_all %>%
-#   dplyr::select(datetime, sal_insitu_ctd_10m, temp_insitu_ctd_10m, pHint_tot_sf_temp_4, depth_group) %>%
-#   #tidyr::drop_na() %>%
-#   dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03")) %>% 
-#   dplyr::mutate(pHint_tot_sf_temp_4_10m = ifelse(depth_group == ">8", pHint_tot_sf_temp_4, NA))
-# 
-# #pH_sf$pHint_tot_sf_temp_4 <- pHinsi(pH=pH_sf$pHint_tot_sf, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_sf$temp_insitu_ctd_10m, Pinsi=11/10, S=pH_sf$sal_insitu_ctd_10m, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
-# 
-# pH_dur <- d_all %>%
-#   dplyr::select(datetime, sal_fb,temp_fb, pH_dur)%>%
-#   tidyr::drop_na() %>%
-# pH_dur$pH_dur_temp_4 <- pHinsi(pH=pH_dur$ph_dur_corr, ALK=mean(d_all$at, na.rm=TRUE), Tinsi=4, Tlab=pH_dur$temp_fb, Pinsi=11/10, S=pH_dur$sal_fb, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
-# 
-# # add pH sf and pH dur normalized at 4°C ti d_all
-# #d_all <- left_join(d_all, pH_sf%>%dplyr::select(datetime, pHint_tot_sf_temp_4 ), by="datetime")
-# d_all <- d_all %>% 
-#   left_join(pH_dur %> %dplyr::select(datetime, pH_dur_temp_4), by="datetime")
-lm <- lm2(x = d_all$pH_dur_temp_4, y = d_all$pHint_tot_sf_temp_4)
-p <- d_all %>% 
-  dplyr::select(pH_dur_temp_4, pHint_tot_sf_temp_4, monthd) %>% 
-  drop_na() %>% 
-  ggplot(aes(x = pH_dur_temp_4, y = pHint_tot_sf_temp_4))+
-  geom_point(aes(color=factor(monthd))) + 
-  geom_abline(slope=1, intercept=0, linetype = "dashed")+
-  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA), colour = "blue") +
-  coord_fixed(ratio = 1 , xlim=c(7.8, 8.35), ylim=c(7.8, 8.35)) +
-  labs(title = paste("","\n Adj R2 = ", signif(lm$rsquare, 3),
-                     "; Intercept =", signif(lm$intercept_MA, 3),
-                     "; Slope =", signif(lm$slope_MA, 3),
-                     "; P =", signif(lm$P, 3),
-                     "; RMSE = ", signif(lm$rmse, 3))) +
-  theme(aspect.ratio = 1, plot.title = element_text(size = 7)) + #
-  labs( x = "pH durafet, 4°C", y = "pH seaFET, 4°C", color = "Months") + theme_bw()
-print(p)
+### **seaFET vs durafet pHs at 4°C (all > 8 m)**
+
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
+reg <- ggreg(
+  xdata = d_all$pH_dur_temp_4,
+  ydata = d_all$pHint_tot_sf_temp_4,
+  type = "MA",
+  plot = TRUE,
+  title = "seaFET vs durafet pH at 4 °C",
+  xlab = "pH durafet, 4 °C",
+  ylab = "pH seaFET, 4 °C",
+  proplot = TRUE
+)
+print(reg$plot + xlim(c(7.8, 8.35)) + ylim(c(7.8, 8.35)))
 
@@
 
-### **Calculated / Durafet pHs**
-
-```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
-# Normalize ph_calc from AT/CT to 4°c
-pH_calc <- discrete %>%
-  dplyr::select(datetime, sal_fb_mix, temp_fb, ph_calc_fb, at)%>%
-  dplyr::filter(!is.na(ph_calc_fb), !is.na(temp_fb), !is.na(sal_fb_mix))
-pH_calc$pH_calc_fb_temp_4 <- pHinsi(pH = pH_calc$ph_calc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+### **Calculated vq Durafet**
+
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
+# Normalize pH_calc from AT/CT to 4°c
+tmp <- discrete %>%
+  dplyr::select(datetime, sal_fb_mix, temp_fb, ph_calc_fb, at) %>%
+  tidyr::drop_na()
+tmp$pH_calc_fb_temp_4 <- pHinsi(pH = tmp$ph_calc_fb, ALK=tmp$at*1e-6, Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 
 # join pH calc norm + pH dur/sf norm in d_all
-d_all <- left_join(d_all, pH_calc %>% dplyr::select(datetime, pH_calc_fb_temp_4), by="datetime")
+d_all <- left_join(d_all, tmp %>% dplyr::select(datetime, pH_calc_fb_temp_4), by="datetime")
 
@@
 
-### **Calculated / seaFET pHs**
-
-```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
+### **Calculated vs seaFET**
+
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_temp_4, pH_calc_fb_temp_4)
@@
 
-### **Spectro / durafet**
-
-```{r pHs comparaison durafet spectro, echo=FALSE, message= FALSE, warning=FALSE}
+### **Spectro vs durafet**
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 # Spectro / durafet
-lm <- lm2(x = d_all$ph_s_dur_temp_fb, y = d_all$pH_dur)
-p <- d_all %>% 
-  dplyr::select(ph_s_dur_temp_fb, pH_dur, monthd) %>% 
-  drop_na() %>% 
-  ggplot(aes(x = ph_s_dur_temp_fb, y= pH_dur, label = monthd)) +
-  geom_text( aes(color=factor(monthd))) + 
-  scale_color_discrete(guide = "none")+
-  geom_abline(slope=1, intercept =0, linetype = "dashed") +
-  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),
-              colour = "blue") +
-  labs(title = paste("pH spectro vs pH durafet (both at FB temperature","\n Adj R2 = ", signif(lm$rsquare, 3),
-                     "; Intercept =", signif(lm$intercept_MA, 3),
-                     "; Slope =", signif(lm$slope_MA, 3),
-                     "; P =", signif(lm$P, 3),
-                     "; RMSE = ", signif(lm$rmse, 3))) +
-  theme_bw() +
-  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 , xlim=c(8,8.4), ylim=c(8,8.4))+
-  labs(x="pH durafet", y="pH spectro", color = "Months")
-print(p)
+reg <- ggreg(
+  xdata = d_all$ph_s_dur_temp_fb,
+  ydata = d_all$pH_dur,
+  type = "MA",
+  plot = TRUE,
+  title = "pH spectro vs pH durafet (both at FB temperature)",
+  xlab = "pH durafet",
+  ylab = "pH spectro",
+  proplot = TRUE
+)
+print(reg$plot + xlim(c(7.8, 8.35)) + ylim(c(7.8, 8.35)))
 ```

### 2021-12-31 awipev-CO2.Rmd
Minor chnages in figs (using ggreg now) Also, deactivated chunk SNAPO

@@
   group_by(datetime) %>%
-#dplyr::select( datetime, date,hour,sal_fb,sal_fb_mix_interp ,sal_fb_mix,temp_fb, at_mean_interp,at ,ct_mean_interp,ct, temp_insitu_11m_mix,temp_insitu_11m_mix_interp,temp_insitu_11m) %>%
+#dplyr::select( datetime, date,hour,sal_fb,sal_fb_mix_interp ,sal_fb_mix,temp_fb, at_mean_interp, at, ct_mean_interp, ct, temp_insitu_11m_mix,temp_insitu_11m_mix_interp,temp_insitu_11m) %>%
   summarise(datetime = mean(datetime, na.rm = TRUE),
@@
 
-### **Calculated vq Durafet**
+### **Calculated vs Durafet**
 
@@
 # Spectro / seafet
-lm <- lm2(x = d_all$ph_s_sf_temp_insi, y = d_all$pHint_tot_sf)
-p <- d_all %>% 
-  dplyr::select(ph_s_sf_temp_insi, pHint_tot_sf, monthd) %>%
-  tidyr::drop_na() %>%
-  ggplot(aes(x=ph_s_sf_temp_insi, y= pHint_tot_sf, label = monthd)) +
-  geom_text( aes(color=factor(monthd))) + 
-  scale_color_discrete(guide = "none")+
-  geom_abline(slope=1, intercept = 0, linetype = "dashed") +
-  geom_abline(aes(intercept = lm$intercept_MA, slope = lm$slope_MA),
-              colour = "blue") +
-  labs(title = paste("pH spectro vs pH seafet (at in situ temperature)","\n Adj R2 = ", signif(lm$rsquare, 3),
-                     "; Intercept =", signif(lm$intercept_MA, 3),
-                     "; Slope =", signif(lm$slope_MA, 3),
-                     "; P =", signif(lm$P, 3),
-                     "; RMSE = ", signif(lm$rmse, 1))) +
-  theme_bw() +
-  theme(aspect.ratio = 1, plot.title = element_text(size=7)) + 
-  coord_fixed(ratio = 1 , xlim=c(8, 8.25), ylim=c(8, 8.25))+
-  labs(x = "pH spectro", y = "pH seafet", color = "Months")
-print(p)
+reg <- ggreg(
+  xdata = d_all$ph_s_sf_temp_insi,
+  ydata = d_all$pHint_tot_sf,
+  type = "MA",
+  plot = TRUE,
+  title = "pH spectro vs pH seafet (at in situ temperature)",
+  xlab = "pH spectro",
+  ylab = "pH seafet",
+  proplot = TRUE
+)
+print(reg$plot + xlim(c(8, 8.25)) + ylim(c(8, 8.25)))
 ```
@@
 Also in the Discrete_sampling_AWIPEV.csv, some analysed samples have
-been flaged "3" by the SNAPO. After a close look, these samples are not
-differents from their duplicates. Then we put the flag to "2" (good
+been flagged "3" by the SNAPO. After a close look, these samples are not
+different from their duplicates. Then we put the flag to "2" (good
 result).
@@
 
-```{r SNAPO, echo=FALSE, message= FALSE, warning=FALSE}
+```{r SNAPO, eval =FALSE, echo=FALSE, message= FALSE, warning=FALSE}
+# I THINK THIS CHUNK IS NO LONGER NEEDED AS THE REPLICATES HAVE ALREADY BEEN AVERAGED ABOVE.
+
 # use the df at_ct for mean and sd
-# creat a new df to calculate the diff between replicate
+# create a new df to calculate the diff between replicate
 diff <- d_all %>%
@@
                  ct_diff = abs(ct - lag(ct)))
-
 pdelta_at_snapo <-ggplot() +
-    geom_point(data=diff, aes(x= datetime, y= at_diff)) +
+    geom_point(data = diff, aes(x = datetime, y = at_diff)) +
     geom_hline(yintercept= 4, size= 0.6, col="red", linetype="dashed") +
@@
 ct_diff_xts <- as.xts(ct_diff_xts, order.by = diff$datetime)
-pdelta_ct_snapo_dygraph <- dygraph(ct_diff_xts, group = "awipev", main="Discrete CT (SNAPO) measurements", ylab="CT") %>%
-    dySeries("ct_diff", label = "CT delta", color ="red", strokeWidth=0, pointSize=4) %>%
-    dySeries("ct", label = "CT duplicates", color =  "blue", strokeWidth = 0, pointSize = 2, axis = "y2" ) %>%
+pdelta_ct_snapo_dygraph <-
+  dygraph(ct_diff_xts,
+          group = "awipev",
+          main = "Discrete CT (SNAPO) measurements",
+          ylab = "CT") %>%
+  dySeries(
+    "ct_diff",
+    label = "CT delta",
+    color = "red",
+    strokeWidth = 0,
+    pointSize = 4
+  ) %>%
+  dySeries(
+    "ct",
+    label = "CT duplicates",
+    color =  "blue",
+    strokeWidth = 0,
+    pointSize = 2,
+    axis = "y2"
+  ) %>%
   # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
@@
   dyShading(from = snapcoevents[13], to = snapcoevents[14], color = "#E0DEDE") %>%
-
-  dyAxis("y", axisLineColor="red",label = "", axisLabelColor ="red", axisLineWidth=5) %>%
-    dyAxis("y2", axisLineColor="blue", axisLabelColor = "blue", axisLineWidth=5) %>%
+  dyAxis(
+    "y",
+    axisLineColor = "red",
+    label = "",
+    axisLabelColor = "red",
+    axisLineWidth = 5
+  ) %>%
+  dyAxis(
+    "y2",
+    axisLineColor = "blue",
+    axisLabelColor = "blue",
+    axisLineWidth = 5
+  ) %>%
   dyLegend(show = "follow")   %>%
-    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
-    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1), digitsAfterDecimal=2) %>%
-    dyRangeSelector(height = 30, dateWindow= NULL)
+  dyHighlight(
+    highlightCircleSize = 8,
+    highlightSeriesBackgroundAlpha = 0.5,
+    hideOnMouseOut = TRUE
+  ) %>%
+  dyOptions(
+    drawGrid = TRUE,
+    drawPoints = TRUE,
+    pointSize = c(1, 8, 1),
+    digitsAfterDecimal = 2
+  ) %>%
+  dyRangeSelector(height = 30, dateWindow = NULL)
 

### 2022-01-01 awipev-CO2.Rmd
Now knits OK!

@@
 # Salinity is a predictor of AT -> using the regression defined above
+slope_s_at <- slope_s_at <- reg$fit$regression.results[3][[1]][1] # OLS
+intercept_s_at <- reg$fit$regression.results[2][[1]][1] #OLS
 d_all$at_calc <- slope_s_at * d_all$sal_fb_mix + intercept_s_at
@@
 # PLOT
- print(at_s)
-rm(at_s)
+print(p_at_s)
+rm(p_at_s)
 ```
@@
 print(reg$plot)
-rm(fit, reg)
+rm(reg)
 ```
@@
 ```{r SNAPO, eval =FALSE, echo=FALSE, message= FALSE, warning=FALSE}
-# I THINK THIS CHUNK IS NO LONGER NEEDED AS THE REPLICATES HAVE ALREADY BEEN AVERAGED ABOVE.
+# THIS CHUNK IS NO LONGER NEEDED AS THE REPLICATES HAVE ALREADY BEEN AVERAGED ABOVE.
 
@@
   na = "-999.999",
+  show_col_types = FALSE
   ) %>%
@@
 tmp <-
-  read_table2(file = paste0(path, file_names[i]),
+  read_table(file = paste0(path, file_names[i]),
   comment = "#",
@@
   col_names = FALSE,
-  na = c("9999.999", "99.999", "9999.990", "9999.99"),
+  na = c("9999.999", "99.999", "9999.990", "9999.99")
   ) %>%
@@
 load(file = paste0(path, "meteo_awi/wind_nyalesund.RData")) 
-meteo <- tibble(windnyalesund) %>%
+meteo <- dplyr::tibble(windnyalesund) %>% 
+  dplyr::slice_head(n = nrow(windnyalesund) - 1) %>% # remove last row which only contains NAs
   dplyr::mutate(datetime = as_datetime(paste(paste(Year, Month, Day, sep="-"), paste(Hour, "00", "00", sep="-"), sep = " ")),
@@
 d_all <- dplyr::left_join(d_all, meteo, by = "datetime") %>% 
-  select(sort(current_vars()))
+  dplyr::select(sort(current_vars()))
 ```
@@
                 k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
-                Sc = 2073.1 - (125.62*temp_insitu_11m) + (3.6276*temp_insitu_11m^2) - (0.043219*temp_insitu_ctd^3), #dimensionless
+                Sc = 2073.1 - (125.62*temp_insitu_11m) + (3.6276*temp_insitu_11m^2) -
+                  (0.043219*temp_insitu_ctd^3), #dimensionless
                 k = k600 * (Sc/600)^-0.5, #cm/h
@@
   geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
-  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_sal_fb), col = "lightblue", size = size_point) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_sal_fb), col = "lightblue", size = size_point, na.rm=TRUE) +
   labs(y = "Salinity", x=NULL, title=NULL) +
@@
   geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
-  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm=TRUE) +
   labs(y = "Temperature", x=NULL, title=NULL) +
@@
   geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
-  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm=TRUE) +
   labs(y = expression(paste(pCO[2])), x=NULL, title=NULL) +
@@
   geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
-  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm=TRUE) +
   labs(y = expression(paste(pH[T])), x=NULL, title=NULL) +
@@
   geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
-  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm=TRUE) +
   labs(y = "Total alkalinity", x=NULL, title=NULL) +

### 2022-01-02 awipev-CO2.Rmd
revised output to Pangaea

@@
 
-```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 # d_hour is the real data set that is read at the beginning of the script
@@
 pangaea <- as_tibble(d_all) %>% 
-  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, sal_fb_mix, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, temp_dur, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb, pco2_calc_fb, at_calc, pH_dur, pHint_tot_sf) %>%
+  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb, pco2_calc_fb, at_calc, pH_dur, pHint_tot_sf) %>%
   dplyr::rename(pressure = depth,
@@
                 s_fb = sal_fb, 
-                s_mix = sal_fb_mix,
                 t_11m = temp_insitu_11m,
-                t_insitu = temp_insitu_ctd, 
+                t_ctd = temp_insitu_ctd, 
                 t_fb = temp_fb, 
@@
                 t_sf = temp_sf, 
-                t_dur = temp_dur, 
                 at = at, 
-                at_calc =at_calc,
+                at_calc = at_calc,
                 ct = ct, 
@@
 # s_fb = salinity in FerryBox 
-# s_mix = salinity in FerryBox with gaps filled by s_insitu below 8 m
 # t_11m = temperature in situ at 11 m
-# t_insitu = temperature in situ (profiler), 
+# t_ctd = temperature in situ (profiler), 
 # t_fb = temperature in FerryBox 
 # t_sf = temperature SeaFET (profiler), °C
-# t_dur = temperature Durafet (FerryBox)
 # at = total alkalinity, discrete measurements (FerryBox)
@@
 
-```{r whole time series plot, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+```{r, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
 size_point <- 0.3 # size of data points
@@
 
-```{r whole time series monthly box plots and stats, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+```{r, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
 size_point <- 0.5 # size of data points

### 2022-01-03 awipev-CO2.Rmd
changes in format

@@
                      "\nP =", signif(fit$P.param, 3),
-                    "rmse =", signif(sqrt(mean(error^2, na.rm=TRUE)), 3)),
+                    "rmse =", signif(sqrt(mean(error^2, na.rm = TRUE)), 3)),
        x = xlab,
@@
                   P = P.param,
-                  rmse = sqrt(mean(error^2, na.rm=TRUE)))
+                  rmse = sqrt(mean(error^2, na.rm = TRUE)))
   return(my_list)
@@
 
-The salinity difference between 1 and 10 m ranges between `r min(tmp$range_diff, na.rm=TRUE)` and `r max(tmp$range_diff, na.rm=TRUE)` (mean: `r mean(tmp$range_diff, na.rm=TRUE)`; `r median(tmp$range_diff, na.rm=TRUE)`).
+The salinity difference between 1 and 10 m ranges between `r min(tmp$range_diff, na.rm = TRUE)` and `r max(tmp$range_diff, na.rm = TRUE)` (mean: `r mean(tmp$range_diff, na.rm = TRUE)`; `r median(tmp$range_diff, na.rm = TRUE)`).
 The difference with depth is therefore significant.
@@
 both 1 m (0-2 m) and 9 m (> 8 m). The temperature difference between 1
-and 9 m ranges between `r min(tmp$range, na.rm=TRUE)`°C and
-`r max(tmp$range, na.rm=TRUE)`°C (mean:
-`r mean(tmp$range, na.rm=TRUE)`°C; `r median(tmp$range, na.rm=TRUE)`°C).
+and 9 m ranges between `r min(tmp$range, na.rm = TRUE)`°C and
+`r max(tmp$range, na.rm = TRUE)`°C (mean:
+`r mean(tmp$range, na.rm = TRUE)`°C; `r median(tmp$range, na.rm = TRUE)`°C).
 The difference with depth is therefore significant.
@@
   dplyr::mutate(diff_spec_sf = ph_s_sf_temp_insi - pHint_tot_sf_10m)
-average_offset <- mean(ph_sf$diff_spec_sf, na.rm=TRUE, digits=4)
+average_offset <- mean(ph_sf$diff_spec_sf, na.rm = TRUE, digits=4)
 
@@
   dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
-tmp$pHint_tot_sf_temp_4 <- seacarb::pHinsi(pH=tmp$pHint_tot_sf, ALK=mean(tmp$at*1e-6, na.rm=TRUE), Tinsi=4, Tlab=tmp$temp_sf, Pinsi=tmp$depth/10, S=tmp$sal_insitu_ctd_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+tmp$pHint_tot_sf_temp_4 <- seacarb::pHinsi(pH=tmp$pHint_tot_sf, ALK=mean(tmp$at*1e-6, na.rm = TRUE), Tinsi=4, Tlab=tmp$temp_sf, Pinsi=tmp$depth/10, S=tmp$sal_insitu_ctd_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
 d_all <- d_all %>% 
@@
   dplyr::mutate(diff_pH_dur = ph_s_dur_temp_fb - ph_dur)
-average_offset_dur <- round(mean(dat_dur$diff_pH_dur, na.rm=TRUE), digits = 2)
-sd_offset_dur <- round(sd(abs(dat_dur$diff_pH_dur), na.rm=TRUE), digits = 2)
+average_offset_dur <- round(mean(dat_dur$diff_pH_dur, na.rm = TRUE), digits = 2)
+sd_offset_dur <- round(sd(abs(dat_dur$diff_pH_dur), na.rm = TRUE), digits = 2)
 n_offset_dur <- length(!is.na(dat_dur$diff_pH_dur))
@@
   group_by(montht) %>%
-  summarize(pH_range_month = mean(pH_range, na.rm=TRUE))
+  summarize(pH_range_month = mean(pH_range, na.rm = TRUE))
 
@@
 and **calculated** (from AT/CT)) and normalized at 4°C with a total
-alkalinity of `r mean(d_all$at, na.rm=TRUE)` µmoles kg-1 (mean data).
+alkalinity of `r mean(d_all$at, na.rm = TRUE)` µmoles kg-1 (mean data).
 For information, mean temperatures in Ferrybox and *in situ* are
@@
 carb_po4_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
-                 Pt = c(0, min(d_all$po4/1e6, na.rm=TRUE), max(d_all$po4/1e6, na.rm=TRUE)), Sit = 0,
+                 Pt = c(0, min(d_all$po4/1e6, na.rm = TRUE), max(d_all$po4/1e6, na.rm = TRUE)), Sit = 0,
                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
@@
 carb_Si_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0,
-                Pt = 0, Sit = c(0, min(d_all$si/1e6, na.rm=TRUE), max(d_all$si/1e6, na.rm=TRUE)), 
+                Pt = 0, Sit = c(0, min(d_all$si/1e6, na.rm = TRUE), max(d_all$si/1e6, na.rm = TRUE)), 
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
@@
 carb_po4_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
-                 Pt = c(0, min(d_all$po4/1e6, na.rm=TRUE), max(d_all$po4/1e6, na.rm=TRUE)), Sit = 0,
+                 Pt = c(0, min(d_all$po4/1e6, na.rm = TRUE), max(d_all$po4/1e6, na.rm = TRUE)), Sit = 0,
                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
@@
 carb_Si_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
-                Pt = 0, Sit = c(0, min(d_all$si/1e6, na.rm=TRUE), max(d_all$si/1e6, na.rm=TRUE)), 
+                Pt = 0, Sit = c(0, min(d_all$si/1e6, na.rm = TRUE), max(d_all$si/1e6, na.rm = TRUE)), 
                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
@@
 carb_1 <- carb(24, mean_pco2_calc, mean_at_calc*1e-6, S = mean_sal, T = mean_temp, P = 0, 
-                 Pt = c(0, max(d_all$po4/1e6, na.rm=TRUE)), Sit = c(0, max(d_all$si/1e6, na.rm=TRUE)),
+                 Pt = c(0, max(d_all$po4/1e6, na.rm = TRUE)), Sit = c(0, max(d_all$si/1e6, na.rm = TRUE)),
                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
 carb_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
-                 Pt = c(0, max(d_all$po4/1e6, na.rm=TRUE)), Sit = c(0, max(d_all$si/1e6, na.rm=TRUE)),
+                 Pt = c(0, max(d_all$po4/1e6, na.rm = TRUE)), Sit = c(0, max(d_all$si/1e6, na.rm = TRUE)),
                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
@@
   dplyr::group_by(lubridate::yday(datetime)) %>%
-  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm=TRUE)/1000) %>% #mol/(m2 d)
+  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)/1000) %>% #mol/(m2 d)
   ungroup() %>%
@@
   dplyr::group_by(monthd) %>%
-  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm=TRUE)/1000) %>% #mol/(m2 d)
+  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)/1000) %>% #mol/(m2 d)
   ungroup() %>%
@@
 ts_sal <- d_all %>%
-  ggplot(aes(x = datetime, y = sal_fb), na.rm=TRUE) +
+  ggplot(aes(x = datetime, y = sal_fb), na.rm = TRUE) +
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
   labs(title="Salinity FerryBox",x="", y="Salinity") +
@@
 ts_temp <- d_all %>%
-  ggplot(aes(x = datetime, y = temp_insitu_11m), na.rm=TRUE) +
+  ggplot(aes(x = datetime, y = temp_insitu_11m), na.rm = TRUE) +
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
   labs(title="In situ temperature 11 m",x="", y="Temperature (°C)") +
@@
 ts_par_air <- d_all %>%
-  ggplot(aes(x = datetime, y = par_air), na.rm=TRUE) +
+  ggplot(aes(x = datetime, y = par_air), na.rm = TRUE) +
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
   labs(title="Atmospheric PAR",x="", y="PAR (umol m-2 s-1)") +
@@
   geom_point(aes(x = datetime, y = pco2_fb), 
-             colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-  geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha=alpha, na.rm=TRUE, size=size_point*3) + 
+             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
+  geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
   labs(title="Measured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
@@
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(aes(x = datetime, y = pHint_tot_sf, col = depth), alpha=alpha, na.rm=TRUE, size=size_point) + 
+  geom_point(aes(x = datetime, y = pHint_tot_sf, col = depth), alpha = alpha, na.rm = TRUE, size = size_point) + 
   scale_colour_gradient(name = "Depth (m)", low = "#56B1F7", high = "#132B43") + # reverse colors
   guides(colour = guide_colourbar(reverse = TRUE)) + # reverse colour bar
-  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha=alpha, na.rm=TRUE, size=size_point*3) + 
+  geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
   labs(title="In situ pH, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
@@
 ts_at <- d_all %>%
-  ggplot(aes(x = datetime, y = at_calc), na.rm=TRUE) +
+  ggplot(aes(x = datetime, y = at_calc), na.rm = TRUE) +
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(colour="blue", alpha=alpha, na.rm=TRUE, size=size_point) + 
-  geom_point(aes(x = datetime, y = at), colour="red", alpha=alpha, na.rm=TRUE, size=size_point*3) + 
+  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
+  geom_point(aes(x = datetime, y = at), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
   labs(title="Total alkalinity calculated from salinity (blue) and discrete measurements (red)", x="", y="AT (umol/kg)") +
@@
   ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
-  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_sal_fb), col = "lightblue", size = size_point, na.rm=TRUE) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_sal_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
   labs(y = "Salinity", x=NULL, title=NULL) +
@@
   ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = temp_insitu_11m)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
-  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm=TRUE) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm = TRUE) +
   labs(y = "Temperature", x=NULL, title=NULL) +
@@
   ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pco2_fb)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
-  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm=TRUE) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
   labs(y = expression(paste(pCO[2])), x=NULL, title=NULL) +
@@
   ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = pHint_tot_sf)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
-  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm=TRUE) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
   labs(y = expression(paste(pH[T])), x=NULL, title=NULL) +
@@
   ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = at_calc)) +
-  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm=TRUE) +
-  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm=TRUE) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
   labs(y = "Total alkalinity", x=NULL, title=NULL) +

### 2022-01-17 awipev-CO2.Rmd
Sorting sections K1K2 out. In progress

@@
 const_choice <- bind_rows(diff_ls_1, diff_ls_2) %>% 
-  dplyr::mutate(flag = c("pCO2 and ALK", "ALK and DIC"),
+  dplyr::mutate(flag = c("pCO2-AT", "AT-CT"),
                 S = mean_sal,
@@
 
-### K1K2 using pCO2 and AT
+### All K1K2 using pCO2-AT
 
@@
 
-#### Difference Lueker vs Sulpis
-
-Using the following using mean discrete values:
-`r knitr::kable(mean_discrete, digits = c(1, 1, 0, 1, 1), caption = "Mean discrete values.", format = "simple")`
-
-The differences are:
-`r knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3, 3, 1, 1, 1), caption = "Lueker minus Sulpis. e indicates typical errors estimated with seacarb.", format = "simple")`
-
 The discrete values of pCO2, AT, salinity and temperature in the
@@
 -   negligible for OmegaAragonite
-
-#### Difference between all formulations and measured pH
 
@@
 
-### K1K2 using CT and AT
+### All K1K2 using CT and AT
 
@@
 
-#### Difference Lueker vs Sulpis
-
-Using the following using mean discrete values:
-`r knitr::kable(mean_discrete, digits = c(1, 1, 0, 1, 1), caption = "Mean discrete values.", format = "simple")`
-
-The differences are:
-`r knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3, 3, 1, 1, 1), caption = "Lueker minus Sulpis. e indicates typical errors estimated with seacarb.", format = "simple")`
-
-#### Difference between all formulations and measured pH
-
 `r knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "simple")`
@@
 for pH calculated from AT and CT according to seacarb.
+
+### Lueker vs Sulpis discrete
+
+Using the following using mean discrete values:
+`r knitr::kable(mean_discrete, digits = c(1, 1, 0, 1, 1), caption = "Mean discrete values.", format = "simple")`
+
+The differences are:
+`r knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3, 3, 1, 1, 1), caption = "Lueker minus Sulpis. e indicates typical errors estimated with seacarb.", format = "simple")`
 

### 2022-01-18 awipev-CO2.Rmd
K1K2 all cleaned up. All good.

@@
 
-```{r impact of constants discrete, echo=FALSE, warning=FALSE, message=FALSE}
+```{r errors with mean values, echo=FALSE, warning=FALSE, message=FALSE}
 # Compare Lueker and Sulpis using mean discrete values
@@
                           b="u74", evar1=4e-6, evar2 = 4e-6)
-errors <- tibble(e_pH = c(errors_pco2_at$pH, errors_at_ct$pH),
+errors <- tibble(
+  flag = c("pCO2-AT", "AT-CT"),
+  S = c(mean_discrete$mean_sal, mean_discrete$mean_sal),
+  T = c(mean_discrete$mean_temp, mean_discrete$mean_temp),
+  pco2 = c(mean_discrete$mean_pco2, NA),
+  CT = c(NA, mean_discrete$mean_ct),
+  AT = c(mean_discrete$mean_at, mean_discrete$mean_at),
+  e_pH = c(errors_pco2_at$pH, errors_at_ct$pH),
   e_pCO2 = c(NA, errors_at_ct$pCO2),
-                 e_DIC = c(errors_pco2_at$pH, NA)*1e3,
-                 e_Oa = c(errors_pco2_at$OmegaAragonite, errors_at_ct$OmegaAragonite)
-)
-# impacts using pco2 and AT pair
-carb_l_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
-                 Pt = 0, Sit = 0,
-                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-carb_s_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
-                 Pt = 0, Sit = 0,
-                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-diff_ls_1 <- carb_l_1 - carb_s_1
-# impacts using AT-CT pair
-carb_l_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
-                 Pt = 0, Sit = 0,
-                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-carb_s_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
-                Pt = 0, Sit = 0, 
-                k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
-diff_ls_2 <- carb_l_2 - carb_s_2
+  e_DIC = c(errors_pco2_at$pH, NA) * 1e3,
+  e_Oa = c(errors_pco2_at$OmegaAragonite, errors_at_ct$OmegaAragonite
+  )
+)
+
+# # impacts using pco2 and AT pair
+# carb_l_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+#                  Pt = 0, Sit = 0,
+#                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+# carb_s_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+#                  Pt = 0, Sit = 0,
+#                  k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+# diff_ls_1 <- carb_l_1 - carb_s_1
+# # impacts using AT-CT pair
+# carb_l_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
+#                  Pt = 0, Sit = 0,
+#                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+# carb_s_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
+#                 Pt = 0, Sit = 0, 
+#                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+# diff_ls_2 <- carb_l_2 - carb_s_2
 # summary
-const_choice <- bind_rows(diff_ls_1, diff_ls_2) %>% 
-  dplyr::mutate(flag = c("pCO2-AT", "AT-CT"),
-                S = mean_sal,
-                T = mean_temp,
-                DIC = DIC * 1e6
-                ) %>% 
-  dplyr::select(flag, pH, pCO2, DIC, OmegaAragonite) %>% 
-  dplyr::bind_cols(errors)
-```
+```
+
+`r knitr::kable(errors, digits = c(0, 1, 1, 1, 1, 1, 3, 1, 1, 3), caption = "Typical errors estimated with seacarb using the mean discrete values of the FerryBox samples.", format = "simple")`
 
@@
   theme(legend.title = element_blank())
-p <- (p1 + p2) / p3
+p <- (p1 + p2)# / p3
 ggsave(filename = "figures/k1k2_all_pco2_at.png", plot = p, width = 25, height = 20, units = "cm")
@@
 # save elements for k1k2 report
-k1k2_pco2_at <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
+k1k2_pco2_at <- list(mean_discrete = mean_discrete, tmp2 = tmp2,
              errors_pco2_at = errors_pco2_at, diff_table_pco2_at = diff_table_pco2_at, 
              diff_ls_quant = diff_ls_quant)
+#k1k2_pco2_at <- list(mean_discrete = mean_discrete, const_choice = const_choice, tmp2 = tmp2,
+             # errors_pco2_at = errors_pco2_at, diff_table_pco2_at = diff_table_pco2_at, 
+             # diff_ls_quant = diff_ls_quant)
 save(k1k2_pco2_at, file="reports/k1k2_pco2_at.RData")
@@
     compared with the uncertainty calculated with seacarb
-    (`r round(const_choice[1, 6], digits = 3)`). In general, pH is
+    (see above; `r round(errors[1, 7], digits = 3)`). In general, pH is
     higher with Sulpis than with Lueker.
+
 -   small for CT (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on
@@
     the uncertainty calculated with seacarb
-    (`r round(const_choice[1, 8], digits = 1)`)
+    (`r round(errors[1, 9], digits = 1)`)
+
 -   negligible for OmegaAragonite
 
-`r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis using discrete Ferrybox data.", format = "simple")`
+`r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis using all discrete Ferrybox data.", format = "simple")`
 
@@
 general, all formulations overestimate spectrophotometric pH. pH
-calculated using the formulation of Papadimitriou et al. (2018) is
+calculated using the formulation of Lueker et al. (2018) is
 closer to measured pH, with a mean difference of
-`r round(diff_table_pco2_at[4, 4], digits=3)` pH units. This difference
-is `r abs(round(diff_table_pco2_at[4, 4]/errors_pco2_at$pH, digits=1))`
+`r round(diff_table_pco2_at[4, 2], digits=3)` pH units. This difference
+is `r abs(round(diff_table_pco2_at[4, 2]/errors_pco2_at$pH, digits=1))`
 times larger than the uncertainty for pH calculated from pCO2 and AT
-according to seacarb (`r round(errors_pco2_at$pH, digits=3)`).
+according to seacarb (see above; `r round(errors_pco2_at$pH, digits=4)`).
+
 `r knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "simple")`
@@
 diff_ls2 <- as_tibble(carb_l2 - carb_s2) %>% 
-  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
-  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite)
+  dplyr::rename(delta_ph = pH, delta_pCO2 = pCO2, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_pCO2, delta_OmegaAragonite)
 # calculate descriptive statistics Lueker - Sulpis
 diff_ls_quant <- tibble(pH = as.numeric(summary(diff_ls2$delta_ph)),
-                        CT = as.numeric(summary(diff_ls2$delta_ct * 1e6)),
+                        pCO2 = as.numeric(summary(diff_ls2$delta_pCO2)),
                         OmegaAragonite = as.numeric(summary(diff_ls2$delta_OmegaAragonite))) %>%
@@
 
-`r knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "simple")`
-`r include_graphics("figures/k1k2_all_at_ct.png")`
+The discrete values of AT, CT, salinity and temperature in the
+FerryBox were used to calculate pH using the formulations for K1 and K2
+of Lueker et al. (2000) and Sulpis et al. (2020). The differences
+induced by the choice of the carbonic acid constants are:
+
+-   large for pH (`r round(diff_ls_quant[4, 2], digits = 3)` pH units on
+    average; ; median is `r round(diff_ls_quant[3, 2], digits = 3)`)
+    compared with the uncertainty calculated with seacarb
+    (`r round(errors[1, 7], digits = 3)`). In general, pH is
+    higher with Sulpis than with Lueker.
+-   reasonable for pCO2 (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on
+    average; always larger with Sulpis than with Lueker) compared with
+    the uncertainty calculated with seacarb
+    (`r round(errors[1, 8], digits = 1)`)
+-   negligible for OmegaAragonite
+
+`r knitr::kable(diff_ls_quant, digits = c(0, 4, 1, 3), caption = "Lueker minus Sulpis using all discrete Ferrybox data.", format = "simple")`
 
@@
 
-### Lueker vs Sulpis discrete
-
-Using the following using mean discrete values:
-`r knitr::kable(mean_discrete, digits = c(1, 1, 0, 1, 1), caption = "Mean discrete values.", format = "simple")`
-
-The differences are:
-`r knitr::kable(const_choice, digits = c(0, 3, 1, 1, 3, 3, 1, 1, 1), caption = "Lueker minus Sulpis. e indicates typical errors estimated with seacarb.", format = "simple")`
+`r knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "simple")`
+
+`r include_graphics("figures/k1k2_all_at_ct.png")`
 

### 2022-01-18 awipev-CO2.Rmd
K1K2 all cleaned up. All good.

@@
 diff_ls2 <- as_tibble(carb_l2 - carb_s2) %>% 
-  dplyr::rename(delta_ph = pH, delta_pCO2 = pCO2, delta_OmegaAragonite = OmegaAragonite) %>%
-  dplyr::select(delta_ph, delta_pCO2, delta_OmegaAragonite)
+  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite)
 # calculate descriptive statistics Lueker - Sulpis
 diff_ls_quant <- tibble(pH = as.numeric(summary(diff_ls2$delta_ph)),
-                        pCO2 = as.numeric(summary(diff_ls2$delta_pCO2)),
+                        CT = as.numeric(summary(diff_ls2$delta_ct * 1e6)),
                         OmegaAragonite = as.numeric(summary(diff_ls2$delta_OmegaAragonite))) %>%
@@
     higher with Sulpis than with Lueker.
--   reasonable for pCO2 (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on
-    average; always larger with Sulpis than with Lueker) compared with
+-   small for CT (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on
+    average; always lower with Sulpis than with Lueker) compared with
     the uncertainty calculated with seacarb
-    (`r round(errors[1, 8], digits = 1)`)
+    (`r round(errors[1, 9], digits = 1)`)
 -   negligible for OmegaAragonite
 
-`r knitr::kable(diff_ls_quant, digits = c(0, 4, 1, 3), caption = "Lueker minus Sulpis using all discrete Ferrybox data.", format = "simple")`
+`r knitr::kable(diff_ls_quant, digits = c(0, 4, rep(3, 4)), caption = "Lueker minus Sulpis using all discrete Ferrybox data.", format = "simple")`
 

### 2022-01-18 awipev-CO2.Rmd

@@
     higher with Sulpis than with Lueker.
+
 -   small for CT (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on
@@
     (`r round(errors[1, 9], digits = 1)`)
+
 -   negligible for OmegaAragonite

### 2022-02-22 awipev-CO2.Rmd
renamed chunks

@@
 
-```{r impact of constants using FerryBox pCO2 and at, echo=FALSE, warning=FALSE, message=FALSE}
+```{r impact of constants on spec pH using FerryBox pCO2 and at, echo=FALSE, warning=FALSE, message=FALSE}
 tmp <- d_all %>% 
@@
 
-```{r impact of constants using FerryBox ct and at, echo=FALSE, warning=FALSE, message=FALSE}
+```{r impact of constants on spec pH using FerryBox ct and at, echo=FALSE, warning=FALSE, message=FALSE}
 tmp <- d_all %>% 

### 2022-02-22 awipev-CO2.Rmd
Renamed chunks 2

--- 2022-01-18 awipev-CO2.Rmd
@@
 
-### All K1K2 using pCO2-AT
-
-```{r impact of constants using FerryBox pCO2 and at, echo=FALSE, warning=FALSE, message=FALSE}
+### pH with all K1K2 using pCO2-AT
+
+```{r pH with all K1K2 using pCO2-AT, echo=FALSE, warning=FALSE, message=FALSE}
 tmp <- d_all %>% 
@@
 
-### All K1K2 using CT and AT
-
-```{r impact of constants using FerryBox ct and at, echo=FALSE, warning=FALSE, message=FALSE}
+### pH with all K1K2 using CT and AT
+
+```{r pH with all K1K2 using CT and AT, echo=FALSE, warning=FALSE, message=FALSE}
 tmp <- d_all %>% 

### 2022-02-22 awipev-CO2.Rmd
revised K1K2

@@
 
-### pH with all K1K2 using pCO2-AT
+### pH and CT using all_pCO2-AT
+
+```{r pH and CT with all K1K2 using pCO2-AT, echo=FALSE, warning=FALSE, message=FALSE}
+tmp <- d_all %>% 
+  dplyr::select(datetime, pco2_fb, at, sal_fb_mix, temp_fb) %>% 
+  tidyr::drop_na(pco2_fb, at, sal_fb_mix, temp_fb) %>% 
+# This is an important adjustement for pco2_fb on 2019-06-07 09:00:00
+# it is too high compared with ph_s_dur.
+Looking at the dygraph suggests that there has been a peak just before that time and that the values were coming back down.
+This is this in accordance with pco2_calc_fb calculated from
+dplyr::mutate(pco2_fb = ifelse(datetime == as.POSIXct("2019-06-07 09:00:00"), 203, pco2_fb))
+# Using Lueker  
+carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Lueker-derived pH at 4°C
+carb_l$pH <- pHinsi(pH = carb_l$pH, ALK = carb_l$ALK, Tinsi = 4, Tlab = carb_l$T, Pinsi = 0, 
+                         S = carb_l$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# Using Sulpis
+carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Sulpis-derived pH at 4°C
+carb_s$pH <- pHinsi(pH = carb_s$pH, ALK = carb_s$ALK, Tinsi = 4, Tlab = carb_s$T, Pinsi = 0, 
+                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# Using Papadimitriou
+carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Papadimitriou-derived pH at 4°C
+carb_p$pH <- pHinsi(pH = carb_p$pH, ALK = carb_p$ALK, Tinsi = 4, Tlab = carb_p$T, Pinsi = 0, 
+                         S = carb_p$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# Using Millero et al. (2002)
+carb_m <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Millero et al. (2002)-derived pH at 4°C
+carb_m$pH <- pHinsi(pH = carb_m$pH, ALK = carb_m$ALK, Tinsi = 4, Tlab = carb_m$T, Pinsi = 0, 
+                         S = carb_m$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# calculate difference Lueker - Sulpis
+diff_ls <- as_tibble(carb_l - carb_s) %>% 
+  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
+  dplyr::mutate(deltas = "L-S", .before = 1)
+# calculate difference Lueker - Papadimitriou
+diff_lp <- as_tibble(carb_l - carb_p) %>% 
+  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
+  dplyr::mutate(deltas = "L-P", .before = 1)
+# calculate difference Lueker - Millero
+diff_lm <- as_tibble(carb_l - carb_m) %>% 
+  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
+  dplyr::mutate(deltas = "L-M", .before = 1)
+# bind and plot
+diff_all <- dplyr::bind_rows(diff_ls, diff_lp, diff_lm) %>% 
+  dplyr::mutate(delta_ct = delta_ct * 1e6)
+diff_all_long <- diff_all %>% 
+  tidyr::pivot_longer(-deltas, names_to = "variable")
+p <- ggplot(diff_all_long, aes(x=factor(deltas), y=value))+
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "", x = "Depth (m)", y= "delta") +
+  facet_wrap(vars(variable), scales = "free_y") +
+  Mytheme()
+# calculate descriptive statistics
+diff_ls_quant <- tibble(pH = as.numeric(summary(diff_ls$delta_ph)),
+                        CT = as.numeric(summary(diff_ls$delta_ct * 1e6)),
+                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite))) %>%
+  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
+diff_lp_quant <- tibble(pH = as.numeric(summary(diff_lp$delta_ph)),
+                        CT = as.numeric(summary(diff_lp$delta_ct * 1e6)),
+                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite)))%>%
+  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
+diff_lm_quant <- tibble(pH = as.numeric(summary(diff_lm$delta_ph)),
+                        CT = as.numeric(summary(diff_lm$delta_ct * 1e6)),
+                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite)))%>%
+  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
+
+ggsave(filename = "figures/k1k2_all_pco2_at.png", plot = p, width = 25, height = 20, units = "cm")
+```
+`r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis using all pCO2 data.", format = "simple")`
+`r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Papadimitriou using all pCO2 data.", format = "simple")`
+`r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Millero using all pCO2 data.", format = "simple")`
+`r include_graphics("figures/k1k2_all_pco2_at.png")`
+
+### pH using discrete pCO2-AT
 
@@
 p <- (p1 + p2)# / p3
-ggsave(filename = "figures/k1k2_all_pco2_at.png", plot = p, width = 25, height = 20, units = "cm")
+ggsave(filename = "figures/k1k2_discrete_pco2_at.png", plot = p, width = 25, height = 20, units = "cm")
 
@@
 `r knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "simple")`
-`r include_graphics("figures/k1k2_all_pco2_at.png")`
-
-### pH with all K1K2 using CT and AT
+`r include_graphics("figures/k1k2_discrete_pco2_at.png")`
+
+### pH using discreteCT and AT
 
@@
 p <- (p1 + p2) / p3
-ggsave(filename = "figures/k1k2_all_at_ct.png", plot = p, width = 25, height = 20, units = "cm")
+ggsave(filename = "figures/k1k2_discrete_at_ct.png", plot = p, width = 25, height = 20, units = "cm")
 
@@
 
-`r include_graphics("figures/k1k2_all_at_ct.png")`
+`r include_graphics("figures/k1k2_discrete_at_ct.png")`
 

### 2022-02-23 awipev-CO2.Rmd
regined boxplot K1K2

--- 2022-02-22 awipev-CO2.Rmd
@@
 
-### pH with all K1K2 using pCO2-AT
+### pH and CT using all_pCO2-AT
+
+```{r pH and CT with all K1K2 using pCO2-AT, echo=FALSE, warning=FALSE, message=FALSE}
+tmp <- d_all %>% 
+  dplyr::select(datetime, pco2_fb, at, sal_fb_mix, temp_fb) %>% 
+  tidyr::drop_na(pco2_fb, at, sal_fb_mix, temp_fb) %>% 
+# This is an important adjustement for pco2_fb on 2019-06-07 09:00:00
+# it is too high compared with ph_s_dur.
+Looking at the dygraph suggests that there has been a peak just before that time and that the values were coming back down.
+This is this in accordance with pco2_calc_fb calculated from
+dplyr::mutate(pco2_fb = ifelse(datetime == as.POSIXct("2019-06-07 09:00:00"), 203, pco2_fb))
+# Using Lueker  
+carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Lueker-derived pH at 4°C
+carb_l$pH <- pHinsi(pH = carb_l$pH, ALK = carb_l$ALK, Tinsi = 4, Tlab = carb_l$T, Pinsi = 0, 
+                         S = carb_l$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# Using Sulpis
+carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Sulpis-derived pH at 4°C
+carb_s$pH <- pHinsi(pH = carb_s$pH, ALK = carb_s$ALK, Tinsi = 4, Tlab = carb_s$T, Pinsi = 0, 
+                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# Using Papadimitriou
+carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Papadimitriou-derived pH at 4°C
+carb_p$pH <- pHinsi(pH = carb_p$pH, ALK = carb_p$ALK, Tinsi = 4, Tlab = carb_p$T, Pinsi = 0, 
+                         S = carb_p$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# Using Millero et al. (2002)
+carb_m <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
+               T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks = "d", 
+               pHscale = "T", b = "u74")
+# normalize Millero et al. (2002)-derived pH at 4°C
+carb_m$pH <- pHinsi(pH = carb_m$pH, ALK = carb_m$ALK, Tinsi = 4, Tlab = carb_m$T, Pinsi = 0, 
+                         S = carb_m$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
+                         pHscale = "T", b="u74")
+# calculate difference Lueker - Sulpis
+diff_ls <- as_tibble(carb_l - carb_s) %>% 
+  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
+  dplyr::mutate(deltas = "L-S", .before = 1)
+# calculate difference Lueker - Papadimitriou
+diff_lp <- as_tibble(carb_l - carb_p) %>% 
+  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
+  dplyr::mutate(deltas = "L-P", .before = 1)
+# calculate difference Lueker - Millero
+diff_lm <- as_tibble(carb_l - carb_m) %>% 
+  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
+  dplyr::mutate(deltas = "L-M", .before = 1)
+# bind and plot
+diff_all <- dplyr::bind_rows(diff_ls, diff_lp, diff_lm) %>% 
+  dplyr::mutate(delta_ct = delta_ct * 1e6)
+diff_all_long <- diff_all %>% 
+  tidyr::pivot_longer(-deltas, names_to = "variable") %>% 
+  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), variable = fct_recode(variable, 'pH' = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))
+
+p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L-S', 'L-P', 'L-M'), y=value))+
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  geom_hline(yintercept = 0) +
+  labs(title = "", x = "", y= "") +
+  facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
+  Mytheme(size_labs = 10)
+p
+diff_all_long$variable <- factor(diff_all_long$variable, levels = c('C[T]','Omega[a]', 'pH'))
+fct_relevel(diff_all_long$variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite')
+
+# calculate descriptive statistics
+diff_ls_quant <- tibble(pH = as.numeric(summary(diff_ls$delta_ph)),
+                        CT = as.numeric(summary(diff_ls$delta_ct * 1e6)),
+                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite))) %>%
+  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
+diff_lp_quant <- tibble(pH = as.numeric(summary(diff_lp$delta_ph)),
+                        CT = as.numeric(summary(diff_lp$delta_ct * 1e6)),
+                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite)))%>%
+  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
+diff_lm_quant <- tibble(pH = as.numeric(summary(diff_lm$delta_ph)),
+                        CT = as.numeric(summary(diff_lm$delta_ct * 1e6)),
+                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite)))%>%
+  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
+
+ggsave(filename = "figures/k1k2_all_pco2_at.png", plot = p, width = 25, height = 20, units = "cm")
+```
+`r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis using all pCO2 data.", format = "simple")`
+`r knitr::kable(diff_lp_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Papadimitriou using all pCO2 data.", format = "simple")`
+`r knitr::kable(diff_lm_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Millero using all pCO2 data.", format = "simple")`
+`r include_graphics("figures/k1k2_all_pco2_at.png")`
+
+### pH using discrete pCO2-AT
 
@@
 `r knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "simple")`
-`r include_graphics("figures/k1k2_all_pco2_at.png")`
-
-### pH with all K1K2 using CT and AT
+`r include_graphics("figures/k1k2_discrete_pco2_at.png")`
+
+### pH using discrete CT and AT
 

### 2022-02-24 awipev-CO2.Rmd
testing greek in facet labels (2950)

@@
   dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
-  dplyr::mutate(deltas = "L-S", .before = 1)
+  dplyr::mutate(deltas = "L00-S20", .before = 1)
 # calculate difference Lueker - Papadimitriou
@@
   dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
-  dplyr::mutate(deltas = "L-P", .before = 1)
+  dplyr::mutate(deltas = "L00-P18", .before = 1)
 # calculate difference Lueker - Millero
@@
   dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
-  dplyr::mutate(deltas = "L-M", .before = 1)
+  dplyr::mutate(deltas = "L00-M02", .before = 1)
 # bind and plot
@@
   tidyr::pivot_longer(-deltas, names_to = "variable") %>% 
-  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), variable = fct_recode(variable, 'pH' = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))
-
-p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L-S', 'L-P', 'L-M'), y=value))+
+  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), variable = fct_recode(variable, "'Delta" pH"' = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))
+
+p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L00-S20', 'L00-P18', 'L00-M02'), y=value))+
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
 p
-diff_all_long$variable <- factor(diff_all_long$variable, levels = c('C[T]','Omega[a]', 'pH'))
-fct_relevel(diff_all_long$variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite')
+# diff_all_long$variable <- factor(diff_all_long$variable, levels = c('C[T]','Omega[a]', 'pH'))
+# fct_relevel(diff_all_long$variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite')
 

### 2022-03-16 awipev-CO2.Rmd
New path; fixed minor mistakes

@@
 #define who is the user and define path
-if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
+#if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
+if (Sys.getenv("LOGNAME") == "gattuso") path = "../../Documents/experiments/exp168_awipev-CO2/"
 if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"
@@
   tidyr::pivot_longer(-deltas, names_to = "variable") %>% 
-  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), variable = fct_recode(variable, "'Delta" pH"' = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))
+  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), variable = fct_recode(variable, 'DeltapH' = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))
 

### 2022-03-28 awipev-CO2.Rmd
New path

@@
 #if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
-if (Sys.getenv("LOGNAME") == "gattuso") path = "../../Documents/experiments/exp168_awipev-CO2/"
+if (Sys.getenv("LOGNAME") == "gattuso") path = "../../kDrive/Documents/experiments/exp168_awipev-CO2/"
 if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"

### 2022-03-29 awipev-CO2.Rmd
Reorganized variable names

@@
                 ph_s_dur_t_fb = ph_s_dur_temp_fb,
-                pco2 = pco2_fb,
-                pco2_calc = pco2_calc_fb,
+                pco2 = pco2_fb_insi_temp,
+                pco2_calc = pco2_calc_fb_insi_temp,
                 pH_sf = pHint_tot_sf,
@@
 # t_fb = temperature in FerryBox 
-# t_sf = temperature SeaFET (profiler), °C
+# t_sf = temperature SeaFET (profiler)
 # at = total alkalinity, discrete measurements (FerryBox)
@@
 # ct = dissolved inorganic carbon, discrete measurements (FerryBox)
-# ph_s_sf_t_insi = pH spectrophotometric SeaFET in situ (11 m)
-# ph_s_dur_t_fb = pH spectrophotometric Durafet in FerryBox
-# pco2 = pCO2 in Ferrybox
-# pco2_calc = pCO2 calculated in the FerryBox calculated from discrete measurments of AT and CT
-# pH_sf = pH SeaFET at in situ temperature (profiler)
+# ph_s_sf_t_insi = spectrophotometric pH in situ at in situ temperature 
+# ph_s_dur_t_fb = spectrophotometric pH in FerryBox at FerryBox temperature
+# pco2 = pCO2 in Ferrybox expressed at in situ temperature
+# pco2_calc = pCO2 in the FerryBox calculated from discrete measurements of AT and CT and expressed at in situ temperature
+# pH_sf = pH seaFET at in situ temperature (profiler)
 # ph_dur = pH Durafet at FerryBox temperature (FerryBox)
-# ph_calc = pH at fb temp calculated from CT and AT samples collected at the FerryBox
+# ph_calc = pH at FerryBox temperature calculated from CT and AT in the FerryBox
 ```
@@
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(aes(x = datetime, y = pco2_fb), 
+  geom_point(aes(x = datetime, y = pco2_fb_insi_temp), 
              colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
-  geom_point(aes(x = datetime, y = pco2_calc_fb), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
-  labs(title="Measured (blue) and calculated (CT+AT; red) pCO2",x="", y="pCO2 (uatm)") +
+  geom_point(aes(x = datetime, y = pco2_calc_fb_insi_temp), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
+  labs(title="pCO2 at in situ temperature (measured in blue; calculated from CT and AT in red)",x="", y="pCO2 (uatm)") +
   Mytheme(size_labs = size_labs)
@@
 ts_pH <- d_all %>% 
+  dplyr::filter(depth > 8) %>% 
   ggplot() +
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(aes(x = datetime, y = pHint_tot_sf, col = depth), alpha = alpha, na.rm = TRUE, size = size_point) + 
-  scale_colour_gradient(name = "Depth (m)", low = "#56B1F7", high = "#132B43") + # reverse colors
-  guides(colour = guide_colourbar(reverse = TRUE)) + # reverse colour bar
+  geom_point(aes(x = datetime, y = pHint_tot_sf), 
+             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) + 
   geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
-  labs(title="In situ pH, spectrophotometric pH in red))",x="", y=expression(paste(pH[T]))) +
+  labs(title="In situ pH below 8 m at in situ temperature (seaFET in blue; spectrophotometric in red)", x = "", y=expression(paste(pH[T]))) +
   Mytheme(size_labs = size_labs) +
@@
   geom_point(aes(x = datetime, y = at), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
-  labs(title="Total alkalinity calculated from salinity (blue) and discrete measurements (red)", x="", y="AT (umol/kg)") +
+  labs(title="Total alkalinity (calculated from salinity in blue; discrete measurements in red)", x="", y="AT (umol/kg)") +
   Mytheme(size_labs = size_labs)
@@
 # Combine plots
-g <- (ts_sal / ts_temp / ts_par_air / ts_pCO2 / ts_pH / ts_at)
+g <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at)
 g <- g + plot_annotation(tag_levels = 'A')

### 2022-03-29 awipev-CO2_presentation.Rmd
presentation

---
title: "**First high-frequency time series of carbonate chemistry in the Arctic**" 
author: "**Jean-Pierre Gattuso**^1,2^ and Samir Alliouane^1^ and Philipp Fisher^3^"
date: '`r format(Sys.Date(), "%d %B %Y")`'
output:
  html_document:
    # code_folding: show
#    css: acid.css
    fig_caption: yes
    fig_width: 2
    fig_height: 2
    highlight: default    
    number_sections: no
    theme: yeti
    toc: no
    toc_float: no
fontsize: 32pt
language: Australian
#css: acid.css
## mainfont: PT Serif  
## monofont: PT Mono
#csl: frontiers.csl
## sansfont: PT Sans
#bibliography: ArcticKelp.bib
## papersize: A4
---
<!-- <style type="text/css"> -->
<!-- .main-container { -->
<!--   max-width: 100% !important; -->
<!--   margin: auto; -->
<!-- } -->
</style>
<style type="text/css">
.main-container {
  max-width: 100% !important;
  margin: auto;
}
body{
  font-size: 24pt;
}
h1,h2,h3,h4,h5,h6{
  font-size: 32pt;
}
</style>

^1^Laboratoire d'Océanographie de Villefranche, CNRS-Sorbonne Université\
^2^Iddri, Sciences Po\
^3^Alfred Wegener Institute for Polar and Marine Research\

```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
  #if (Sys.getenv("LOGNAME") == "gattuso") path = "."
```

![](images/AWIPEV-Logo.jpg){width="250px"}

***
# **Introduction**

- CO<sub>2</sub> is an acid gas (it produces a weak acid when combined with water)
- Each of us adds 4 kg CO<sub>2</sub> per day to the ocean (increasing acidity, reducing pH)
- Arctic surface water will become corrosive for aragonite: 50% in 2050, 100% in 2100
- Critical to document the changes but no high frequency time-series

***

Fransner et al. (2022)
![ ](images/map_fransner.png){width="50%"}
![ ](images/pH_fransner.png)

***

# **Instruments installed**

- Water pumped from 12 m water depth at Ny-Ålesund
- **July 2015**: Two pCO<sub>2</sub> sensors rotating every year (in FerryBox, 1 min) 
- **February 2016**: Total alkalinity analyser (in FerryBox, 90 min) but lots of technical issues
- For calibration and quality insurance: weekly discrete samples for high-precision measurements of dissolved inorganic carbon and total alkalinity
- **August 2017**: pH measurements
  - Continuous measurements in fjord water (seaFET)
  - DURAFET pH sensor in the FerryBox
  - Discrete pH samples once a month for calibration
- Regular maintenance twice a year (except during the Covid-19 pandemic)
- Came to an end in December 2021

## **Instruments in the FerryBox**
![ ](images/container.png)

![ ](images/ferrybox.jpg)

## seaFET pH on the REMOS
![ ](images/seafet.png)

***

## No longer in real-time: https://awipev-co2.obs-vlfr.fr
![ ](images/web_page.png)

***

## **Availability of data**
Many challenges:

- extreme environmental conditions
- frozen pipes
- damages resulting from icebergs pounding on the field instruments
- weeks to months waiting for warmer temperatures to deice or to fly technical staff, including divers
- No access for extended periods of time during the Covid-19 pandemic

Nevertheless:
- data usable 50 to 76% of the time during the period of measurement
- pCO<sub>2</sub> and pH data are available throughout the year and well distributed across months, including winter months

![ ](figures/availability.png){ width=70% }

***

## **Time series of key variables**
![ ](figures/time_series.png)

### 2022-03-29 awipev-CO2_presentation.Rmd
Conclusion added

@@
 ![ ](figures/time_series.png)
+
+# **Conclusion**
+
+- **First** high-frequency time series of the carbonate system in the Arctic 
+- **Positive aspects**: 
+  - Excellent support from AWIPEV staff but work overload
+  - IPEV support secured for another 4-year period (2019-2022)
+- **Logistical difficulties**:
+  - Challenging environment; divers needed to sort out issues
+  - Difficult and costly to gather a team and organize field trip at short notice
+  - Winter sampling essential (once a month this season, more frequently would be more desirable)
+  - Demanding for AWIPEV staff
+  - IPEV does not cover the cost of analyses required for calibration (ca. 1000 €)

### 2022-03-30 awipev-CO2.Rmd
figs air-sea CO2

@@
 
-![](Images/AWIPEV-Logo.jpg){width="250px"}
+![](images/AWIPEV-Logo.jpg){width="250px"}
 
@@
 ::: {style="text-align:center" markdown="1"}
-<img src="./Images/Container.png" width="200" height="200"/>
-<img src="./Images/Intake.png" width="200" height="200"/>
-<img src="./Images/2018-04-17_Ferrybox2.jpg" width="200" height="200"/>
+<img src="./images/Container.png" width="200" height="200"/>
+<img src="./images/Intake.png" width="200" height="200"/>
+<img src="./images/2018-04-17_Ferrybox2.jpg" width="200" height="200"/>
 :::
@@
   Mytheme(size_labs = 8)
-#p_f_air_sea
-#ggsave(filename = "figures/f_air_sea.png", plot = f_air_sea, width = 20, units = "cm")
+p_f_air_sea
+ggsave(filename = "figures/f_air_sea.png", plot = f_air_sea, width = 20, units = "cm")
 
@@
   Mytheme(size_labs = 8)
-#p_f_air_sea_d
-#ggsave(filename = "figures/f_air_sea_d.png", plot = p_f_air_sea_d, width = 20, units = "cm")
+p_f_air_sea_d
+ggsave(filename = "figures/f_air_sea_d.png", plot = p_f_air_sea_d, width = 20, units = "cm")
 
@@
   Mytheme(size_labs = 8)
-#p_f_air_sea_m
-#ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_m, width = 20, units = "cm")
+p_f_air_sea_m
+ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_m, width = 20, units = "cm")
 
@@
 ::: {style="text-align:center" markdown="1"}
-<img src="./Images/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200"/>
-<img src="./Images/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200"/>
+<img src="./images/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200"/>
+<img src="./images/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200"/>
 :::
@@
 
-![](Images/awipev_server_arborescence.jpg){width="65%"}
+![](images/awipev_server_arborescence.jpg){width="65%"}

### 2022-03-30 awipev-CO2.Rmd
misc

@@
 p_f_air_sea
-ggsave(filename = "figures/f_air_sea.png", plot = f_air_sea, width = 20, units = "cm")
+ggsave(filename = "figures/p_f_air_sea.png", plot = p_f_air_sea, width = 20, units = "cm")
 

### 2022-03-30 presentation_old/awipev-CO2_pres_2022-03-31.Rmd

--- 2019-02-12 presentation/awipev-CO2_pres.Rmd
@@
 title: "AWIPEV-CO2"
-subtitle: "First time-series of carbonate chemistry in the Arctic"
+subtitle: "High frequency time-series of carbonate chemistry in the Arctic"
 author: "Jean-Pierre Gattuso"
@@
 library(tidyverse)
-library(robfilter)
+#library(robfilter)
 library(seacarb)
@@
 library(xts)
-library(seismicRoll)
+#library(seismicRoll)
+if (!require("scales")) install.packages("scales")
 library(scales)
-library(widgetframe)
+#library(widgetframe)
 # # install http://phantomjs.org/download.html
@@
 
-fig_nums <- captioner()
-table_nums <- captioner(prefix = "Table")
+# fig_nums <- captioner()
+# table_nums <- captioner(prefix = "Table")
 
 #define who is the user and define path
-if (Sys.getenv("LOGNAME") == "gattuso") path = "../../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
-if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"
+if (Sys.getenv("LOGNAME") == "gattuso") path = "../../kDrive/Documents/experiments/exp168_awipev-CO2/"
 

### 2022-03-30 awipev-CO2.Rmd
Revised variable names for Pangaea

@@
 <img src="./images/Intake.png" width="200" height="200"/>
-<img src="./images/2018-04-17_Ferrybox2.jpg" width="200" height="200"/>
+<img src="./images/ferrybox.jpg" width="200" height="200"/>
 :::
@@
 pangaea <- as_tibble(d_all) %>% 
-  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb, pco2_calc_fb, at_calc, pH_dur, pHint_tot_sf) %>%
-  dplyr::rename(pressure = depth,
-                s_insitu = sal_insitu_ctd,
-                s_fb = sal_fb, 
-                t_11m = temp_insitu_11m,
-                t_ctd = temp_insitu_ctd, 
-                t_fb = temp_fb, 
-                t_s = temp_fb,
-                t_sf = temp_sf, 
-                at = at, 
-                at_calc = at_calc,
-                ct = ct, 
-                ph_s_sf_t_insi = ph_s_sf_temp_insi, 
-                ph_s_dur_t_fb = ph_s_dur_temp_fb,
-                pco2 = pco2_fb_insi_temp,
-                pco2_calc = pco2_calc_fb_insi_temp,
-                pH_sf = pHint_tot_sf,
-                pH_dur = pH_dur,
-                ph_calc = ph_calc_fb
+  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb_insi_temp, pco2_calc_fb_insi_temp, at_calc, pH_dur, pHint_tot_sf) %>%
+  dplyr::rename(`pressure [dbar]` = depth,
+                `s_insitu [unit]` = sal_insitu_ctd,
+                `s_fb [unit]` = sal_fb, 
+                `t_11m [°C]` = temp_insitu_11m,
+                `t_ctd [°C]` = temp_insitu_ctd, 
+                `t_fb [°C]` = temp_fb, 
+                `t_s [°C]` = temp_fb,
+                `t_sf [°C]` = temp_sf, 
+                `at [umol kg-1]` = at, 
+                `at_calc [umol kg-1]` = at_calc,
+                `ct [umol kg-1]` = ct, 
+                `ph_s_sf_t_insi [total scale]` = ph_s_sf_temp_insi, 
+                `ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
+                `pco2 [uatm]` = pco2_fb_insi_temp,
+                `pco2_calc [uatm]` = pco2_calc_fb_insi_temp,
+                `pH_sf [total scale]` = pHint_tot_sf,
+                `pH_dur [total scale]` = pH_dur,
+                `pH_calc [total scale]` = ph_calc_fb
                 )
 saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
-write_csv(pangaea, path = paste0(path, "fb_data/pangaea.csv"))
+write_csv(pangaea, file = paste0(path, "fb_data/pangaea.csv"))
 # Metadata Pangaea
@@
 
-::: {style="text-align:center" markdown="1"}
-<img src="./images/2016-04-04_leakage_AT_analyser1.jpg" width="200" height="200"/>
-<img src="./images/2016-04-04_leakage_AT_analyser3.jpg" width="200" height="200"/>
-:::
-
 ## Script + data

### 2022-03-30 awipev-CO2_presentation.Rmd
Two columns

@@
 
+![ ](images/intake.png)
+
 ![ ](images/ferrybox.jpg)
@@
 ## **Availability of data**
+:::: {style="display: flex;"}
+::: {class='col-md-4'}
 Many challenges:
@@
 Nevertheless:
+
 - data usable 50 to 76% of the time during the period of measurement
 - pCO<sub>2</sub> and pH data are available throughout the year and well distributed across months, including winter months
+:::
+::: {class='col-md-8'}
 
 ![ ](figures/availability.png){ width=70% }
+:::
+::::
+
+***
+
+## **Total alkalinity vs salinity relationship**
+![ ](figures/p_at_s.png)
 
@@
 ![ ](figures/time_series.png)
+
+***
+
+## **Monthly means**
+![ ](figures/ts_boxplots.png)
+
+***
+
+## **Consistency**
+![ ](figures/pco2_calc_meas.png)
+
+***
+
+## **Water column stratification**
+#::: {style="text-align:center" markdown="1"}
+  ![ ](figures/deltas.png)
+#:::
+***
 

### 2022-03-30 awipev-CO2_presentation.Rmd
save nutrients plot

@@
 
+## **Nutrients**
+:::: {style="display: flex;"}
+::: {class='col-md-4'}
+
+- 90 phosphate and 133 silicate data kindly provided by van de Poll (unpubl.)
+- PO4 and Si vary by a factor 10 along a composite year
+- disregarding nutrients does not generate large differences:
+  - pCO2-AT pair, differences in pH, CT and OmegaA: < 0.001 unit, 0.7 umol/kg and <0.01
+  - CT-AT pair: differences in pH, pCO2 and OmegaA: 0.002 units, 1.5 uatm and <0.01
+:::
+::: {class='col-md-8'}
+![ ](figures/nutrients.png)
+:::
+::::
+
+***
+
+## **K1 and K2**
+
+- Big issue in the Arctic due to low temperature and salinity (Sulpis et al., 2020) 
+- Lueker et al. (2000), which are recommended by the community (Jiang et al., 2022) derived in lab conditions with no temperature value < 2 °C. Overestimates K1 and K2 at temperatures below about 8 °C
+- Millero et al. (2002) and Sulpis et al. (2020) based on large (> 900) field data sets that include cold temperature values
+- Papadimitriou et al. (2018), obtained in the laboratory, also cover cold temperatures
+- Formulations of Papadimitriou et al. (2018) perform better here but seldom used
+- Hence, we used the facto standard of Lueker et al. (2000)
+
+***
+
 ## **Total alkalinity vs salinity relationship**
@@
 ## **Water column stratification**
-#::: {style="text-align:center" markdown="1"}
+::: {style="text-align:center" markdown="1"}
   ![ ](figures/deltas.png)
-#:::
+:::
+
 ***

### 2022-03-30 awipev-CO2.Rmd
refined pangaea and saving nuts fig

@@
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
-  labs(y = "po4", x=NULL, title=NULL) +
+  labs(y = "PO4", x=NULL, title=NULL) +
   Mytheme() +
@@
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3, na.rm = TRUE) +
-  labs(y = "si", x=NULL, title=NULL) +
+  labs(y = "Si", x=NULL, title=NULL) +
   Mytheme() +
   theme(panel.grid.major.x = element_blank())
-ts_po4_bp + ts_Si_bp
+p <- ts_po4_bp + ts_Si_bp
+ggsave(filename = "figures/nutrients.png", plot = p, width = 25, height = 20, units = "cm")
+
 # Effects of changes in po4 and si
@@
                 `t_fb [°C]` = temp_fb, 
-                `t_s [°C]` = temp_fb,
                 `t_sf [°C]` = temp_sf, 
@@
 # s_insitu = salinity in situ (profiler)
-# s_fb = salinity in FerryBox 
-# t_11m = temperature in situ at 11 m
+# s_fb = salinity (static at 11 m) 
+# t_11m = temperature in situ (static at 11 m)
 # t_ctd = temperature in situ (profiler), 
-# t_fb = temperature in FerryBox 
+# t_fb = temperature (FerryBox)
 # t_sf = temperature SeaFET (profiler)
@@
 # ct = dissolved inorganic carbon, discrete measurements (FerryBox)
-# ph_s_sf_t_insi = spectrophotometric pH in situ at in situ temperature 
-# ph_s_dur_t_fb = spectrophotometric pH in FerryBox at FerryBox temperature
-# pco2 = pCO2 in Ferrybox expressed at in situ temperature
+# ph_s_sf_t_insi = spectrophotometric pH in situ at in situ temperature (profiler)
+# ph_s_dur_t_fb = spectrophotometric pH in FerryBox at FerryBox temperature (FerryBox)
+# pco2 = pCO2 in Ferrybox expressed at in situ temperature (FerryBox)
 # pco2_calc = pCO2 in the FerryBox calculated from discrete measurements of AT and CT and expressed at in situ temperature

### 2022-03-30 awipev-CO2_presentation.Rmd
New slides + updates

@@
 ## **Consistency**
+
+::: {style="text-align:center" markdown="1"}
 ![ ](figures/pco2_calc_meas.png)
+:::
 
@@
 ## **Water column stratification**
-::: {style="text-align:center" markdown="1"}
+
+:::: {style="display: flex;"}
+::: {class='col-md-5'}
+
+- Weird profiling
+- Salinity in the bottom layer (8 to 12 m) is up to 1 unit higher than in the surface layer (0 to 4 m) in summer, 0.7 unit lower in Dec and similar in both layers at other times
+- Temperature is lower by up to 2.7°C in the deep layer from Mar to Sep and higher by up to 2.4 °C in Nov-Jan
+- Density is almost always higher in the bottom than in the surface layer.
+
+:::
+::: {class='col-md-5'}
+
   ![ ](figures/deltas.png)
 :::
+::::
 

### 2022-03-30 awipev-CO2.Rmd
refined stratification

@@
   ggplot(aes(x=montht, y=sal_delta)) +
-  scale_x_discrete(expand = c(0, 0)) +
+  scale_x_discrete("Month") +
   scale_y_continuous("Salinity", limits = c(-1.1, 0.8), expand = c(0, 0)) +
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 1.5, y = 0.65, label = substitute("S"["surface"] ~ "> S"["deep"])) +
-  annotate("text", x = 1.5, y = -0.9, label = substitute("S"["surface"] ~ "< S"["deep"])) +
+  annotate("text", x = 2, y = 0.65, label = substitute("S"["surface"] ~ "> S"["deep"])) +
+  annotate("text", x = 2, y = -0.9, label = substitute("S"["surface"] ~ "< S"["deep"])) +
   Mytheme(size_labs = 12) +
@@
   #scale_x_discrete(expand = c(0, 0)) +
+  scale_x_discrete("Month") +
   scale_y_continuous("Temperature", limits = c(-2.1, 0.5), expand = c(0, 0)) +
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 1.5, y = 0.3, label = substitute("T"["surface"] ~ "> T"["deep"])) +
-  annotate("text", x = 1.5, y = -0.6, label = substitute("T"["surface"] ~ "< T"["deep"])) +
+  annotate("text", x = 2, y = 0.3, label = substitute("T"["surface"] ~ "> T"["deep"])) +
+  annotate("text", x = 2, y = -1.8, label = substitute("T"["surface"] ~ "< T"["deep"])) +
   Mytheme(size_labs = 12) +
@@
   ggplot(aes(x=montht, y=den_delta)) +
-  scale_x_discrete(expand = c(0, 0)) +
+  scale_x_discrete("Month") +
   scale_y_continuous("Density", limits = c(-1.5, 0.5), expand = c(0, 0)) +
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 1.5, y = 0.1, label = substitute("D"["surface"] ~ "> D"["deep"])) +
-  annotate("text", x = 1.5, y = -1.2, label = substitute("D"["surface"] ~ "< D"["deep"])) +
+  annotate("text", x = 2, y = 0.25, label = substitute("D"["surface"] ~ "> D"["deep"])) +
+  annotate("text", x = 2, y = -1.2, label = substitute("D"["surface"] ~ "< D"["deep"])) +
   Mytheme(size_labs = 12) +
@@
   #labs(y = substitute("pH"["T"] ~ "at in situ temp."), x = "Month") +
-  scale_x_discrete("Month", expand = c(0, 0)) +
+  scale_x_discrete("Month") +
   scale_y_continuous(substitute("pH"["T"] ~ "at in situ temp."), limits = c(-0.07, 0.03), expand = c(0, 0)) +

### 2022-03-30 awipev-CO2.Rmd
metadata pangaea

@@
 # t_11m = temperature in situ (static at 11 m)
-# t_ctd = temperature in situ (profiler), 
+# t_ctd = temperature in situ (profiler)
 # t_fb = temperature (FerryBox)

### 2022-03-30 awipev-CO2_presentation.Rmd
new slides + format

@@
 title: "**First high-frequency time series of carbonate chemistry in the Arctic**" 
-author: "**Jean-Pierre Gattuso**^1,2^ and Samir Alliouane^1^ and Philipp Fisher^3^"
+author: "Jean-Pierre Gattuso^1,2^ and Samir Alliouane^1^ and Philipp Fisher^3^"
 date: '`r format(Sys.Date(), "%d %B %Y")`'
@@
 #    css: acid.css
-    fig_caption: yes
-    fig_width: 2
-    fig_height: 2
+    fig_caption: no
+    #fig_width: 2
+    #fig_height: 2
     highlight: default    
     number_sections: no
-    theme: yeti
+    #theme: yeti
+    theme: cerulean
     toc: no
@@
 fontsize: 32pt
-language: Australian
+#language: Australian
 #css: acid.css
@@
 Fransner et al. (2022)
+
 ![ ](images/map_fransner.png){width="50%"}
-![ ](images/pH_fransner.png)
+![ ](images/pH_fransner.png){width="50%"}
 
@@
 ## **Instruments in the FerryBox**
-![ ](images/container.png)
+![ ](images/container.png){width="50%"}
 
-![ ](images/intake.png)
+![ ](images/intake.png){width="50%"}
 
-![ ](images/ferrybox.jpg)
+![ ](images/ferrybox.jpg){width="50%"}
 
@@
 
-## No longer in real-time: https://awipev-co2.obs-vlfr.fr
+# No longer in real-time: https://awipev-co2.obs-vlfr.fr
 ![ ](images/web_page.png)
@@
 
-## **Availability of data**
+# **Availability of data**
 :::: {style="display: flex;"}
@@
 
-## **Nutrients**
+# **Nutrients**
 :::: {style="display: flex;"}
@@
 
-## **K1 and K2**
+# **K1 and K2**
 
@@
 
-## **Total alkalinity vs salinity relationship**
+# **Total alkalinity vs salinity relationship**
 ![ ](figures/p_at_s.png)
@@
 
-## **Time series of key variables**
+# **Time series of key variables**
 ![ ](figures/time_series.png)
@@
 
-## **Monthly means**
+# **Monthly means**
 ![ ](figures/ts_boxplots.png)
@@
 
-## **Consistency**
+# **Consistency**
 
-::: {style="text-align:center" markdown="1"}
+<!-- ::: {style="text-align:center" markdown="1"} -->
 ![ ](figures/pco2_calc_meas.png)
-:::
+<!-- ::: -->
 
@@
 
-## **Water column stratification**
+# **Water column stratification**
 
@@
 
+# **Air-sea CO<sub>2</sub> flux**
+
+  ![ ](figures/air-sea_CO2_flux.png)
+
+***
+
 # **Conclusion**
 
+- **Positive aspects**: 
   - **First** high-frequency time series of the carbonate system in the Arctic 
-- **Positive aspects**: 
-  - Excellent support from AWIPEV staff but work overload
-  - IPEV support secured for another 4-year period (2019-2022)
+  - Excellent support from AWIPEV staff until 2020
 - **Logistical difficulties**:
@@
   - Winter sampling essential (once a month this season, more frequently would be more desirable)
-  - Demanding for AWIPEV staff
   - IPEV does not cover the cost of analyses required for calibration (ca. 1000 €)
+
+  ***
+
+# **Acknowledgements**
+
+- AWIPEV staff until 2020
+- Numerous AWI divers
+- SNAPO-CO2
+- Willem H. van de Poll who provided nutrient data
+- Coastal Observing System for Northern and Arctic Seas (COSYNA)
+- Helmholtz large-scale infrastructure projects ACROSS and MOSES
+- French Polar Institute (IPEV) 
+- EU projects Jericho-Next, INTAROS and FACE-IT
+- Ove Hermansen, Cathrine Lund Myhre, and Stephen Platt at Norwegian institute for air research (NILU) for their assistance with atmospheric CO2 data from the Zeppelin observatory, as well as the Integrated Carbon Observing System (ICOS)-Norway, Norwegian Research Council project NFR-207587, and the Norwegian Environment Agency

### 2022-03-31 awipev-CO2_presentation.Rmd
test
many updates and additions

@@
 title: "**First high-frequency time series of carbonate chemistry in the Arctic**" 
-author: "Jean-Pierre Gattuso^1,2^ and Samir Alliouane^1^ and Philipp Fisher^3^"
+author: "Jean-Pierre Gattuso^1,2^, Samir Alliouane^1^ & Philipp Fisher^3^"
 date: '`r format(Sys.Date(), "%d %B %Y")`'
@@
     # code_folding: show
-#    css: acid.css
+    #css: acid.css
     fig_caption: no
@@
 <!-- } -->
-</style>
+<!-- </style> -->
 <style type="text/css">
@@
   margin: auto;
+}
+h1.title {
+  font-size: 50px;
 }
@@
   font-size: 32pt;
+}
+.blackbox {
+  padding: 1em;
+  background: LightYellow;
+  color: black;
+  border: 0px solid orange;
+  border-radius: 10px;
+}
+.center {
+  text-align: center;
 }
@@
 
-![](images/AWIPEV-Logo.jpg){width="250px"}
+![](images/AWIPEV-Logo.jpg){width="500px"}
 
 ***
+
+:::: {.blackbox data-latex=""}
+
 # **Introduction**
 
-- CO<sub>2</sub> is an acid gas (it produces a weak acid when combined with water)
-- Each of us adds 4 kg CO<sub>2</sub> per day to the ocean (increasing acidity, reducing pH)
-- Arctic surface water will become corrosive for aragonite: 50% in 2050, 100% in 2100
-- Critical to document the changes but no high frequency time-series
+- Arctic region:  one of the "**reasons for concern**" of the IPCC.
+- Arctic Ocean: less than 1% of ocean water but receives 11% of the global runoff; 7-10% of the global burial of organic carbon
+- **SST** increased twice as fast as other regions; projections of up to +5.5 °C in 2100 
+- Projected decrease in surface **pH** by 2100 larger than elsewhere (-0.45 vs -0.06 to -0.32 units)
+- **Undersaturation** of surface water with respect to aragonite ﬁrst reported in 2008 in the Canada Basin; due to the decrease of salinity and degradation of organic matter
+- **No** fewer observations than elsewhere for carbonate variables: 11.6% of the SOCAT pCO<sub>2</sub> records and 9.1% of the GLODAP C<sub>T</sub> records are from the Arctic Ocean which is only about 4.3% of the global ocean surface
+<!-- - Coastal data relatively well represented in both products (25% and 10% of the SOCAT and SOCAT Arctic data, respectively) -->
+- **Uneven distribution**: 71.5% of the SOCAT pCO<sub>2</sub> data and 72% of the GLODAP C<sub>T</sub> data collected Jun-Sep). Few to very few data Dec-Mar.
+- Critical to document the changes but no high frequency multi-year time-series
+:::
 
@@
 
-# **Instruments installed**
+# **Study location** 
+![ ](images/map_platt.png)
 
-- Water pumped from 12 m water depth at Ny-Ålesund
+Platt et al. (2022)
+
+***
+
+:::: {.blackbox data-latex=""}
+# **Instrumental set-up**
+
+- Water pumped at **11 m depth**
 - **July 2015**: Two pCO<sub>2</sub> sensors rotating every year (in FerryBox, 1 min) 
 - **February 2016**: Total alkalinity analyser (in FerryBox, 90 min) but lots of technical issues
-- For calibration and quality insurance: weekly discrete samples for high-precision measurements of dissolved inorganic carbon and total alkalinity
+- For calibration and quality insurance: weekly discrete samples for C<sub>T</sub> and A<sub>T</sub>
 - **August 2017**: pH measurements
@@
   - Discrete pH samples once a month for calibration
-- Regular maintenance twice a year (except during the Covid-19 pandemic)
+- Regular maintenance twice a year (except during Covid-19 pandemic)
 - Came to an end in December 2021
+:::
 
 ## **Instruments in the FerryBox**
-![ ](images/container.png){width="50%"}
 
-![ ](images/intake.png){width="50%"}
+:::: {style="display: flex;"}
+::: {class='col-md-4'}
+![ ](images/container.png)
+:::
 
-![ ](images/ferrybox.jpg){width="50%"}
+::: {class='col-md-4'}
+![ ](images/intake.png)
+:::
 
-## seaFET pH on the REMOS
+::: {class='col-md-4'}
+![ ](images/ferrybox.jpg)
+:::
+::::
+
+## **Instruments on the REMOS**
 ![ ](images/seafet.png)
@@
 
-# No longer in real-time: https://awipev-co2.obs-vlfr.fr
-![ ](images/web_page.png)
+<!-- # No longer in real-time: https://awipev-co2.obs-vlfr.fr -->
+<!-- ![ ](images/web_page.png) -->
 
-***
+<!-- *** -->
 
@@
 
+:::: {.blackbox data-latex=""}
 # **K1 and K2**
@@
 - Hence, we used the facto standard of Lueker et al. (2000)
+:::
 
@@
 # **Total alkalinity vs salinity relationship**
-![ ](figures/p_at_s.png)
+r2 = 0.81
+
+![ ](figures/p_at_s.png){ width=50% height=50% }
 
@@
 <!-- ::: {style="text-align:center" markdown="1"} -->
-![ ](figures/pco2_calc_meas.png)
+![ ](figures/pco2_calc_meas.png){ width=70% height=70% }
 <!-- ::: -->
@@
 
-- Weird profiling
+- Weird profiling approach
 - Salinity in the bottom layer (8 to 12 m) is up to 1 unit higher than in the surface layer (0 to 4 m) in summer, 0.7 unit lower in Dec and similar in both layers at other times
@@
 
+:::: {.blackbox data-latex=""}
 # **Conclusion**
@@
 - **Positive aspects**: 
-  - **First** high-frequency time series of the carbonate system in the Arctic 
+  - **First** multi-year, high-frequency time series of the carbonate system in the Arctic 
   - Excellent support from AWIPEV staff until 2020
 - **Logistical difficulties**:
+  - Winter sampling essential
   - Challenging environment; divers needed to sort out issues
   - Difficult and costly to gather a team and organize field trip at short notice
-  - Winter sampling essential (once a month this season, more frequently would be more desirable)
-  - IPEV does not cover the cost of analyses required for calibration (ca. 1000 €)
+  - New regulation for using HgCl<sub>2</sub> and transporting poisoned samples
+
+:::
 
@@
 
+:::: {.blackbox data-latex=""}
 # **Acknowledgements**
@@
 - Ove Hermansen, Cathrine Lund Myhre, and Stephen Platt at Norwegian institute for air research (NILU) for their assistance with atmospheric CO2 data from the Zeppelin observatory, as well as the Integrated Carbon Observing System (ICOS)-Norway, Norwegian Research Council project NFR-207587, and the Norwegian Environment Agency
+:::

### 2022-03-31 awipev-CO2_presentation.Rmd
final

@@
 }
+h2,h3,h4,h5,h6{
+  font-size: 28pt;
+}
 .blackbox {
@@
 
+<br><br><br><br><br><br><br><br><br><br><br><br><br>
+
 ***
@@
 <!-- - Coastal data relatively well represented in both products (25% and 10% of the SOCAT and SOCAT Arctic data, respectively) -->
-- **Uneven distribution**: 71.5% of the SOCAT pCO<sub>2</sub> data and 72% of the GLODAP C<sub>T</sub> data collected Jun-Sep). Few to very few data Dec-Mar.
+- **Uneven time distribution**: 71.5% of the SOCAT pCO<sub>2</sub> data and 72% of the GLODAP C<sub>T</sub> data collected Jun-Sep. Few to very few data Dec-Mar.
 - Critical to document the changes but no high frequency multi-year time-series
@@
 ::: {class='col-md-4'}
-Many challenges:
+## Many challenges:
 
@@
 
-Nevertheless:
+## Nevertheless:
 
@@
 - **Positive aspects**: 
-  - **First** multi-year, high-frequency time series of the carbonate system in the Arctic 
+  - First multi-year, high-frequency time series of the carbonate system in the Arctic 
   - Excellent support from AWIPEV staff until 2020
@@
   - Challenging environment; divers needed to sort out issues
-  - Difficult and costly to gather a team and organize field trip at short notice
-  - New regulation for using HgCl<sub>2</sub> and transporting poisoned samples
+  - Difficult and costly to gather a team and organize field trip on short notice
+  - New regulation for the use HgCl<sub>2</sub> and transportation of poisoned samples
 

### 2022-04-07 awipev-CO2.Rmd
changed plot at vs s

@@
 d_all_at_discrete <- d_all %>% #  To remove an outlier in red
-  dplyr::select(datetime, monthd,closest_datetime, at, sal_fb_mix)
+  dplyr::select(datetime, monthd, closest_datetime, at, sal_fb_mix)
 reg <- ggreg(
@@
 salinity is very good with an r2 of
-`r #round(summary(fit)$r.squared, digits=2)`. Need to compare with other
-relationships from the literature.
+`r round(reg$fit$rsquare, digits = 2)`. Need to compare with other relationships from the literature.
 

### 2022-07-20 awipev-CO2.Rmd
New paper Dobashi & Ho in air-sea CO2 flux
Messed with descriptive stats. Not happy with the outcome...

@@
 library("latex2exp")
+if (!require("gtsummary")) install.packages("gtsummary")
+library("gtsummary")
 if (!require("todor")) install.packages("todor")
@@
 ```
-## Range per months
-
-```{r Range per month, eval = FALSE, echo=FALSE, message= FALSE, warning=FALSE}
-my_skim <- skim_with(numeric = sfl(ave = ~ mean(., na.rm = TRUE),
-                                   med = ~ median(., na.rm = TRUE),
-                                   min = ~ min(., na.rm = TRUE),
-                                   max = ~ max(., na.rm = TRUE),
-                                   q5 = ~ quantile(., 0.05, na.rm = TRUE),
-                                   q95 = ~ quantile(., 0.95, na.rm = TRUE)
-                                   ), 
-                     append = FALSE)
+## Range per month
+
+```{r Range per month, eval = FALSE, echo=FALSE, message= FALSE, warning=FALSE, results = "asis"}
+# my_skim <- skim_with(numeric = sfl(ave = ~ mean(., na.rm = TRUE),
+#                                    med = ~ median(., na.rm = TRUE),
+#                                    min = ~ min(., na.rm = TRUE),
+#                                    max = ~ max(., na.rm = TRUE),
+#                                    q5 = ~ quantile(., 0.05, na.rm = TRUE),
+#                                    q95 = ~ quantile(., 0.95, na.rm = TRUE)
+#                                    ), 
+#                      append = FALSE)
+# 
+# range_month <-
+#   d_all %>%
+#   dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
+#   group_by(montht) %>%
+#   summarise(across(everything(), list(min=min, max=max), na.rm=TRUE))
+# print(range_month)
+# 
+# range_month <-
+#   d_all %>%
+#   dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
+#     group_by(montht) %>%
+#   summary()
+# print(range_month)
 
@@
   d_all %>%
-  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
-  group_by(montht) %>%
-  my_skim()
-kable(range_month, caption = "")
+  dplyr::select(sal_fb_mix) %>% 
+#  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
+    #group_by(montht) %>%
+#tbl_summary(by = montht, missing = "no",
+tbl_summary(missing = "no",
+            type = all_continuous() ~ "continuous2",
+            statistic = all_continuous() ~ c(
+      "{mean} ({sd})",                             # line 1: mean and SD
+      "{median} ({p25}, {p75})",                   # line 2: median and IQR
+      "{min}, {max}")    ) %>% 
+  add_n() %>% 
+  modify_header(label = "**Variable**") %>%
+  bold_labels()# %>% 
+  #as_gt()
+range_month
+
+# range_month <-
+#   d_all %>%
+#   dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
+#   group_by(montht) %>%
+#   my_skim()
+# print(range_month, include_summary = FALSE, width = 100)
+```
+```{r example}
+library(survival)
+patient_characteristics <-
+  trial %>%
+  select(trt, age, grade, response) %>%
+  tbl_summary(by = trt)  
+patient_characteristics
 ```
@@
 ##TO DO: check calculations by Miller et al. (2020); use formulation of Wanninkhof 2014?
+## TO DO: Dobashi R. & Ho D. T., 2022. Air-sea gas exchange in a seagrass ecosystem. EGUsphere 
 d_all <- d_all %>%

### 2022-07-20 awipev-CO2.Rmd
output of desc stats still absent

@@
             statistic = all_continuous() ~ c(
-      "{mean} ({sd})",                             # line 1: mean and SD
-      "{median} ({p25}, {p75})",                   # line 2: median and IQR
-      "{min}, {max}")    ) %>% 
-  add_n() %>% 
-  modify_header(label = "**Variable**") %>%
-  bold_labels()# %>% 
+              "{mean}",    # line 1: mean and SD
+              "{median}",
+             # "{p25}, {p75})",  # line 2: median and IQR
+              "{min}",
+              "{max}")
+) #%>% 
+  #add_n() %>% 
+  #modify_header(label = "**Variable**") %>%
+  #bold_labels()# %>% 
   #as_gt()
@@
 # print(range_month, include_summary = FALSE, width = 100)
-```
-```{r example}
-library(survival)
-patient_characteristics <-
-  trial %>%
-  select(trt, age, grade, response) %>%
-  tbl_summary(by = trt)  
-patient_characteristics
 ```

### 2022-08-02 awipev-CO2.Rmd
still messing with gtsummary

@@
   d_all %>%
-  dplyr::select(sal_fb_mix) %>% 
+  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
 #  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
     #group_by(montht) %>%
-#tbl_summary(by = montht, missing = "no",
+tbl_summary(by = montht,
+            missing = "no",
+            type = all_continuous() ~ "continuous2",
+            statistic = all_continuous() ~ c(
+              "{mean}",
+              "{median}",
+              "{p25}",
+              "{p75}",
+              "{min}",
+              "{max}"),
+            digits = list(all_continuous() ~ c(2, 1, 1, 3)))
+range_month
 tbl_summary(missing = "no",
-            type = all_continuous() ~ "continuous2",
+            type = sal_fb_mix ~ "continuous2",
             statistic = all_continuous() ~ c(
@@
               "{median}",
-             # "{p25}, {p75})",  # line 2: median and IQR
+              "{p25}", 
+              "{p75}",  # line 2: median and IQR
               "{min}",

### 2022-08-03 awipev-CO2.Rmd
Range table now works and is diesplayed in the html

--- 2022-07-20 awipev-CO2.Rmd
@@
 
-```{r Range per month, eval = FALSE, echo=FALSE, message= FALSE, warning=FALSE, results = "asis"}
+```{r Range per month, echo = FALSE, warning = FALSE}
 # my_skim <- skim_with(numeric = sfl(ave = ~ mean(., na.rm = TRUE),
@@
   d_all %>%
-  dplyr::select(sal_fb_mix) %>% 
-#  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
-    #group_by(montht) %>%
-#tbl_summary(by = montht, missing = "no",
-tbl_summary(missing = "no",
+  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
+tbl_summary(by = montht,
+            missing = "no",
             type = all_continuous() ~ "continuous2",
             statistic = all_continuous() ~ c(
-              "{mean}",    # line 1: mean and SD
+              "{mean}",
               "{median}",
-             # "{p25}, {p75})",  # line 2: median and IQR
+              "{p25}",
+              "{p75}",
               "{min}",
-              "{max}")
-) #%>% 
-  #add_n() %>% 
-  #modify_header(label = "**Variable**") %>%
-  #bold_labels()# %>% 
-  #as_gt()
+              "{max}"),
+            digits = list(all_continuous() ~ c(2, 1, 1, 3)))
 range_month

### 2022-08-03 awipev-CO2.Rmd
ranges are now fine with gtsummary

@@
 ```{r Range per month, echo = FALSE, warning = FALSE}
-# my_skim <- skim_with(numeric = sfl(ave = ~ mean(., na.rm = TRUE),
-#                                    med = ~ median(., na.rm = TRUE),
-#                                    min = ~ min(., na.rm = TRUE),
-#                                    max = ~ max(., na.rm = TRUE),
-#                                    q5 = ~ quantile(., 0.05, na.rm = TRUE),
-#                                    q95 = ~ quantile(., 0.95, na.rm = TRUE)
-#                                    ), 
-#                      append = FALSE)
-# 
-# range_month <-
-#   d_all %>%
-#   dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
-#   group_by(montht) %>%
-#   summarise(across(everything(), list(min=min, max=max), na.rm=TRUE))
-# print(range_month)
-# 
-# range_month <-
-#   d_all %>%
-#   dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
-#     group_by(montht) %>%
-#   summary()
-# print(range_month)
-
 range_month <-
@@
               "{max}"),
-            digits = list(all_continuous() ~ c(2, 1, 1, 3)))
+            digits = list(sal_fb_mix ~ 1, temp_insitu_11m_mix ~ 1, temp_insitu_11m ~ 1, pHint_tot_sf_10m ~ 3))
 range_month
-
-# range_month <-
-#   d_all %>%
-#   dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
-#   group_by(montht) %>%
-#   my_skim()
-# print(range_month, include_summary = FALSE, width = 100)
 ```

### 2022-08-04 awipev-CO2.Rmd
Saly_fb_mix now used, finalized ts plot

@@
 sal_xts <- as.xts(sal_xts, order.by = sal_xts$datetime)
-dygraph(sal_xts, group = "awipev", main="Salinity (in FerryBox)", ylab="Salinity") %>%
+dygraph(sal_xts, group = "awipev", main="Salinity (FerryBox and mix)", ylab="Salinity") %>%
             dySeries("sal_fb", color = "blue", strokeWidth = 0, label = "sal_fb") %>%
@@
   dyRangeSelector(height = 30, dateWindow = NULL)
+
 # now remove outliers
@@
 ### **Depth profile**
-
-```{r Sal profile, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+This is done later.
+
+```{r Sal profile, eval=FALSE, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
 
@@
   xdata = d_all$sal_insitu_ctd_10m,
-  ydata = d_all$sal_fb_mix,
+  ydata = d_all$sal_fb,
   type = "MA",
@@
 For information, mean temperatures in Ferrybox and *in situ* are
-repectively 3.5°C and 2.5°C.
+respectively 3.5°C and 2.5°C.
 
@@
 ts_sal <- d_all %>%
-  ggplot(aes(x = datetime, y = sal_fb), na.rm = TRUE) +
+  ggplot(aes(x = datetime, y = sal_fb_mix), na.rm = TRUE) +
   scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
   geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
-  labs(title="Salinity FerryBox",x="", y="Salinity") +
+  labs(title="Salinity (below 8 m)",x="", y="Salinity") +
   Mytheme(size_labs = size_labs)
@@
   geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
-  labs(title="In situ temperature 11 m",x="", y="Temperature (°C)") +
+  labs(title="In situ temperature (11 m)",x="", y="Temperature (°C)") +
   Mytheme(size_labs = size_labs)
@@
   geom_point(aes(x = datetime, y = pco2_calc_fb_insi_temp), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
-  labs(title="pCO2 at in situ temperature (measured in blue; calculated from CT and AT in red)",x="", y="pCO2 (uatm)") +
+  labs(title=expression(paste(pCO[2], " at 11 m and in situ temperature")),
+       subtitle = "measured in blue; calculated from CT and AT in red",
+       x="", y=TeX("pCO$_2$ ($\\mu atm$)")) +
   Mytheme(size_labs = size_labs)
@@
   geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
-  labs(title="In situ pH below 8 m at in situ temperature (seaFET in blue; spectrophotometric in red)", x = "", y=expression(paste(pH[T]))) +
+  labs(title="In situ pH below 8 m at in situ temperature", 
+       subtitle = "seaFET in blue; spectrophotometric in red",
+       x = "", y=expression(paste(pH[T]))) +
   Mytheme(size_labs = size_labs) +
@@
   geom_point(aes(x = datetime, y = at), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
-  labs(title="Total alkalinity (calculated from salinity in blue; discrete measurements in red)", x="", y="AT (umol/kg)") +
+  labs(title="Total alkalinity", 
+       subtitle = "calculated from salinity in blue; discrete measurements in red",
+       x="", y=TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$")) +
   Mytheme(size_labs = size_labs)
@@
 # Combine plots
-g <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at)
+g1 <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at)
 g <- g + plot_annotation(tag_levels = 'A')
-ggsave(filename = "figures/time_series.png", plot = g, width = 15, height = 30, units = "cm")
-rm(list = ls(pattern = "ts_")) #delete big ggplot objects
-gc() #garbage collection
-
-#save_plot(filename = "figures/time_series.png", plot = g)
-#g_cw <- cowplot::plot_grid(ts_sal, ts_temp, ts_par_air, ts_pCO2, ts_pH, ts_at, align='v', ncol=1)
+ggsave(filename = "figures/time_series.png", plot = g1, width = 15, height = 30, units = "cm")
+#rm(list = ls(pattern = "ts_")) #delete big ggplot objects
+#gc() #garbage collection
 ```
@@
 d_bp <- d_all %>% # just for this chunk
-  dplyr::select(datetime, sal_fb, temp_insitu_11m, pco2_fb, pHint_tot_sf, at_calc)
+  dplyr::select(datetime, sal_fb_mix, temp_insitu_11m, pco2_fb, pHint_tot_sf, at_calc)
 
 # Quantiles table
-Salinity <- round(quantile(d_bp$sal_fb, na.rm =TRUE), digits=1)
+Salinity <- round(quantile(d_bp$sal_fb_mix, na.rm =TRUE), digits=1)
 Temperature <- round(quantile(d_bp$temp_insitu_11m, na.rm =TRUE), digits=1)
@@
 # calculate 1st and 9th deciles 
-dec_sal_fb <- quantile(d_bp$sal_fb, na.rm =TRUE, probs = c(0.1, 0.9))
+dec_sal_fb_mix <- quantile(d_bp$sal_fb_mix, na.rm =TRUE, probs = c(0.1, 0.9))
 dec_temp_insitu_11m <- quantile(d_bp$temp_insitu_11m, na.rm =TRUE, probs = c(0.1, 0.9))
@@
 d_bp <- d_bp %>%
-  dplyr::mutate(ext_sal_fb = ifelse(sal_fb < dec_sal_fb[1] |
-                                            sal_fb > dec_sal_fb[2], sal_fb, NA),
-                ext_temp_insitu_11m = ifelse(temp_insitu_11m < dec_temp_insitu_11m[1] |
+  dplyr::mutate(
+    ext_sal_fb_mix = ifelse(
+      sal_fb_mix < dec_sal_fb_mix[1] |
+        sal_fb_mix > dec_sal_fb_mix[2],
+      sal_fb_mix,
+      NA
+    ),
+    ext_temp_insitu_11m = ifelse(
+      temp_insitu_11m < dec_temp_insitu_11m[1] |
         temp_insitu_11m > dec_temp_insitu_11m[2],
-                                            temp_insitu_11m, NA),
+      temp_insitu_11m,
+      NA
+    ),
     ext_pco2_fb = ifelse(pco2_fb < dec_pco2_fb[1] |
                            pco2_fb > dec_pco2_fb[2], pco2_fb, NA),
-                ext_pHint_tot_sf = ifelse(pHint_tot_sf < dec_pHint_tot_sf[1] |
-                                            pHint_tot_sf > dec_pHint_tot_sf[2], pHint_tot_sf, NA),
+    ext_pHint_tot_sf = ifelse(
+      pHint_tot_sf < dec_pHint_tot_sf[1] |
+        pHint_tot_sf > dec_pHint_tot_sf[2],
+      pHint_tot_sf,
+      NA
+    ),
     ext_at_calc = ifelse(at_calc < dec_at_calc[1] |
-                                            at_calc > dec_at_calc[2], at_calc, NA))
+                           at_calc > dec_at_calc[2], at_calc, NA)
+  )
 ts_sal_bp <- d_bp %>%
-  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb)) +
+  ggplot(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
-  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_sal_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(y = "Salinity", x=NULL, title=NULL) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_sal_fb_mix), col = "lightblue", size = size_point, na.rm = TRUE) +
+  labs(title="Salinity (< 8 m)", y = "Salinity", x=NULL) +
   Mytheme() +
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(y = "Temperature", x=NULL, title=NULL) +
+  labs(title="In situ temperature (11 m)", y = "Temperature (°C)", x=NULL) +
   Mytheme() +
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(y = expression(paste(pCO[2])), x=NULL, title=NULL) +
+  labs(title=expression(paste(pCO[2], " at 11 m and in situ temperature")), y = TeX("pCO$_2$ ($\\mu atm$)"), x=NULL) +
   Mytheme() +
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(y = expression(paste(pH[T])), x=NULL, title=NULL) +
+  labs(title="In situ pH below 8 m at in situ temperature", y = expression(paste(pH[T])), x=NULL) +
   Mytheme() +
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(y = "Total alkalinity", x=NULL, title=NULL) +
+  labs(title="Total alkalinity calculated from salinity", y = TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$"), x=NULL) +
   Mytheme() +
@@
 # Combine plots
-g <- ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp
+g2 <- (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
+g2 <- g + plot_annotation(tag_levels = 'A')
+ggsave(filename = "figures/ts_boxplots.png", plot = g2)
+#rm(list = ls(pattern = "ts_"), d_bp) #delete big ggplot objects and temp data
+#gc() #garbage collection
+```
+```{r fig ts and bp for paper}
+g <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at) |
+  (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
 g <- g + plot_annotation(tag_levels = 'A')
-ggsave(filename = "figures/ts_boxplots.png", plot = g)
+ggsave(filename = "figures/ts_ts_boxplots.png", plot = g)
 rm(list = ls(pattern = "ts_"), d_bp) #delete big ggplot objects and temp data

### 2022-08-08 awipev-CO2.Rmd
pCO2 clean up code, print fig.

@@
   dplyr::mutate(co2_air = ifelse(year(atm_co2$datetime) == 2020, co2_air_new, co2_air_old))
-# Below was an attempt to smooth but
-# zz <- as_tsibble(atm_co2) %>% 
-#   mutate(smoothed_co2_air = slide_dbl(co2_air, .f = mean, .before = 12, .after = 12, .complete = TRUE))
-# ggplot(zz) +
-#   geom_line(aes(x = datetime, y = smoothed_co2_air))
+
 d_all <- dplyr::left_join(d_all, dplyr::select(atm_co2, datetime, co2_air), by = "datetime") %>% 
@@
   geom_point(aes(x = datetime, y = co2_air), col = "blue", size = 0.15, na.rm = TRUE) +
-  #facet_grid(rows = vars(dataset)) +
-  #geom_point(aes(x = datetime, y = pco2_air_old), col = "grey", size = 0.15, na.rm = TRUE) +
   labs(title = "Atmospheric CO2 at Zeppelin", x = "Time", y = "CO2 (ppm)") +
   Mytheme(size_labs = 8)
-#p_atm_co2
+p_atm_co2
 ggsave(filename = "figures/atm_co2.png", plot = p_atm_co2, width = 20, units = "cm")
@@
 g1 <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at)
-g <- g + plot_annotation(tag_levels = 'A')
+g1 <- g1 + plot_annotation(tag_levels = 'A')
 ggsave(filename = "figures/time_series.png", plot = g1, width = 15, height = 30, units = "cm")
@@
 g2 <- (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
-g2 <- g + plot_annotation(tag_levels = 'A')
+g2 <- g2 + plot_annotation(tag_levels = 'A')
 ggsave(filename = "figures/ts_boxplots.png", plot = g2)

### 2022-08-08 awipev-CO2.Rmd
misc

@@
 d <- d %>%
-  dplyr::mutate(location_flag = ifelse(datetime == as.POSIXct("2016-04-21 09:25:00") | 
+  dplyr::mutate(
+    location_flag = ifelse(
+      datetime == as.POSIXct("2016-04-21 09:25:00") |
         datetime == as.POSIXct("2016-02-10 14:00:00") |
@@
         datetime == as.POSIXct("2019-05-31 11:45:00"),
-                                       1, 0))
+      1,
+      0
+    )
+  )
 d <- d %>%
@@
   title = "pCO2 normalized at in situ temperature",
-  #subtitle = "",
   xlab = latex2exp::TeX("Measured $pCO_{2}\\phantom{x}(\\mu atm)$"),
@@
   proplot = TRUE,
-  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
   coord_fixed(ratio = 1)
@@
 print(reg$plot)
+pco2_calc_meas <- reg$plot
 ggsave(filename = "figures/pco2_calc_meas.png", plot = reg$plot)
@@
 
-```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-print(reg$plot)
-rm(reg)
-```
+# ```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
+# print(reg$plot)
+# rm(reg)
+# ```
 
@@
 analysed with spectrophotometric method in Villefranche by Samir
-Alliouane. Measurments were performed several months after sampling.
+Alliouane. Measurements were performed several months after sampling.
 When sampling was not possible in the vicinity of the sensor for
@@
 # To make sf calibration against pH spectro, we need: sal - T insi - voltINT/EXT . If we missed one of these parameters, calibration will not run
-# Here we try to fill the gap when it is possible: make a mean with 4 previous/next hours available in the time serie. 
+# Here we try to fill the gap when it is possible: make a mean with 4 previous/next hours available in the time series. 
 # If the pH spectro is too far from a needed value, we decided to skip it for the calibration.
@@
 
-#interpolation of salinity during gaps
-# # below is old code. now we use sal_insitu_ctd_mix
-# salinterp <-
-#   approx(
-#     d_all$datetime,
-#     d_all$sal_insitu_ctd,
-#     xout = d_all$datetime,
-#     method = "linear",
-#     rule = 2
-#   )
-# names(salinterp) <- c("datetime", "sal_insitu_ctd_interp")
-# salinterp <- as.data.frame(salinterp)
-# d_all$sal_insitu_ctd_interp <- salinterp$sal_insitu_ctd_interp
-# 
-# d_all <- d_all %>%
-#   dplyr::mutate(
-#     sal_insitu_ctd_interp =  ifelse(
-#       datetime > as.POSIXct("2018-04-16 07:00:00") &
-#         datetime < as.POSIXct("2018-04-24 22:00:00"),
-#       sal_insitu_ctd_interp,
-#       sal_insitu_ctd
-#     )
-#   )
-
-# above is old code. Now we use sal_insitu_ctd_mix
 salinterp <-
@@
 
-# make the mean of E0 by period of deployement
+# make the mean of E0 by period of deployment
 calib_spectro_all <- group_by(calib_spectro_all, deployment_sf) %>%
@@
 calibration with spectro measurements (red dots) according to each
-period of deployement, defined between 2 spectro measurements (shading
+period of deployment, defined between 2 spectro measurements (shading
 grey).
@@
 
-pH INT - pH EXT was plotted here. From now on, one uses seaFET pH from the internal electrode calibrated
-with spec pH and seaFET data when the REMOS was below 8 m (pHint_tot_sf_10m).
+pH INT - pH EXT was plotted here.
+From now on, one uses seaFET pH from the internal electrode calibrated with spec pH and seaFET data when the REMOS was below 8 m (pHint_tot_sf_10m).
 This unique pH variable is called pHint_tot_sf.
 All other pH variables are cleaned up.
-We also calculate pHint_tot_sf.
-at 4°C: pHint_tot_sf_temp_4.
+We also calculate pHint_tot_sf at 4°C: pHint_tot_sf_temp_4.
 

### 2022-08-09 awipev-CO2.Rmd
eliminate two pH spec; plot pH offset

@@
                    TRUE ~ datetime))
+
+######
+# below quality flag of spec pH is changed from 2 (good) to 3 (questionable)
+# on 2018-09-11 and 2019-07-12 because after calibration, 
+# the difference between pH measured and calibrated seafet pH i large.
+d <- d %>% 
+  dplyr::mutate(qflag_ph_s_sf = ifelse((lubridate::date(datetime) == as.POSIXct("2018-09-11") | lubridate::date(datetime) == as.POSIXct("2019-07-12")), 3, 2))# %>% 
+  # dplyr::filter((lubridate::date(datetime) == as.POSIXct("2018-09-11") |
+  #               lubridate::date(datetime) == as.POSIXct("2019-07-12"))) %>% 
+  # dplyr::select(datetime, qflag_ph_s_sf)
+
+####
 
@@
 
-Offset between calibrated seaFET data and pH spectro.
-The offset must be between -0.2 and 0.2 pH units.
-"differences between calibrated sensor pH values and values obtained from discrete, check samples can be expected to be as small as 0.02 pH units, and perhaps less." (McLaughlin et al.
-2017).
-
 ```{r seaFET quality control pH 1, echo=FALSE, warning = FALSE, message = FALSE, out.width='100%'}
+
 #Offset between seafet pH and spec pH (Fig. 2 Kapsenberg et al.)
@@
   dyRangeSelector(height = 30, dateWindow= c("2017-10-21 00:00:00", "2021-01-11 00:00:00"))
-```
+
+offset_ph <- ph_sf %>% 
+  drop_na() %>% 
+  ggplot() +
+  geom_point(aes(x=datetime, y=diff_spec_sf, color="blue"), size=2) +
+  # annotate("text", x = dat_dur$datetime[3], y =-0.16, label = "offset mean", color="red")+
+  geom_hline(yintercept=0, size=0.3) +
+  geom_hline(yintercept=-0.02, size=0.3, linetype = "dashed") +
+  geom_hline(yintercept=0.02, size=0.3, linetype = "dashed") +
+  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
+  #scale_x_datetime(date_breaks="years", date_minor_breaks="3 months", labels=date_format("%b %Y")) +
+  Mytheme() + 
+  #theme(panel.grid.major.x = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1)) +
+scale_colour_discrete(guide="none")
+print(offset_ph)
+ggsave(filename = "figures/offset_ph.png", plot = offset_ph, width = 25, height = 20, units = "cm")
+```
+Offset between calibrated seaFET data and pH spectro.
+The offset must be between -0.2 and 0.2 pH units.
+"differences between calibrated sensor pH values and values obtained from discrete, check samples can be expected to be as small as 0.02 pH units, and perhaps less." (McLaughlin et al.
+2017).
+
+Initially (before 2022-08-09), there was 2 outiers on 209-07-12 and 2018+09-11.
+On 2022-08-09, code was addeed above to put a no good qf (3) in order to eliminate those two oiutliers.
+Now we are fine.
+The average offset is 'r average_offset'.
 

### 2022-08-09 awipev-CO2.Rmd
fig misc

@@
 library("todor")
+if (!require("ggpmisc")) install.packages("ggpmisc")
+library("ggpmisc")
 # todor::todor_file("awipev-CO2.Rmd")
@@
 # function regression plot with equation (MA or OLS) in title
-ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", xlab = "x", 
-                   ylab = "y", proplot = TRUE, ...) 
+ggreg <- function (xdata, ydata, type = "OLS", plot = TRUE, title = "title", xlab = "x", ylab = "y", proplot = TRUE, ...) 
   { # x and y are the names of the variables
@@
 # Same plot for paper
-p_at_s <- d_all_at_discrete %>% 
+at_s <- d_all_at_discrete %>% 
   drop_na() %>% 
@@
   labs(x="Salinity", y=TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
-  stat_smooth(method = "lm", col = "blue", size = 0.5) +
+  stat_smooth(method = "lm", se=FALSE, col = "blue", size = 0.5) +
   Mytheme(size_labs = 9)
-ggsave(filename = "figures/p_at_s.png", plot = p_at_s, width = 7, height = 7, units = "cm")
+ggsave(filename = "figures/at_s.png", plot = at_s, width = 7, height = 7, units = "cm")
 
@@
 
-## *p*CO~2~ and *f*CO~2~
+## pCO~2~ and fCO~2~
 
@@
 print(reg$plot)
-pco2_calc_meas <- reg$plot
-ggsave(filename = "figures/pco2_calc_meas.png", plot = reg$plot)
+
+# for paper
+pco2_calc_meas <- d_all %>% 
+  dplyr::select(pco2_fb_insi_temp, pco2_calc_fb_insi_temp) %>% 
+  drop_na() %>% 
+  ggplot(aes(x = pco2_fb_insi_temp, y = pco2_calc_fb_insi_temp)) +
+  geom_point(col="blue", size = 0.5) +
+  labs(x=latex2exp::TeX("Measured $pCO_{2}\\phantom{x}(\\mu atm)$"),
+       y= latex2exp::TeX("Calculated $pCO_{2}\\phantom{x}(\\mu atm)$"))  +
+  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
+  ggpmisc::stat_ma_eq(aes(label = after_stat(eq.label))) +
+#stat_smooth(method = "lm", se=FALSE, col = "blue", size = 0.5) +
+  theme_bw() + Mytheme(size_labs = 9)
+ggsave(filename = "figures/pco2_calc_meas.png", plot = pco2_calc_meas, width = 25, height = 25, units = "cm")
 ```
@@
 1.7-3. <https://CRAN.R-project.org/package=lmodel2>
-
-# ```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
-# print(reg$plot)
-# rm(reg)
-# ```
 
@@
   geom_point(aes(x=datetime, y=diff_spec_sf, color="blue"), size=2) +
-  # annotate("text", x = dat_dur$datetime[3], y =-0.16, label = "offset mean", color="red")+
   geom_hline(yintercept=0, size=0.3) +
@@
   labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
-  #scale_x_datetime(date_breaks="years", date_minor_breaks="3 months", labels=date_format("%b %Y")) +
-  Mytheme() + 
+  Mytheme(size_labs = 12, face_font = "plain") + 
   #theme(panel.grid.major.x = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1)) +
   scale_colour_discrete(guide="none")
-print(offset_ph)
-ggsave(filename = "figures/offset_ph.png", plot = offset_ph, width = 25, height = 20, units = "cm")
+ggsave(filename = "figures/offset_ph.png", plot = offset_ph, width = 10, height = 10, units = "cm")
 ```
@@
 
-Initially (before 2022-08-09), there was 2 outiers on 209-07-12 and 2018+09-11.
-On 2022-08-09, code was addeed above to put a no good qf (3) in order to eliminate those two oiutliers.
+Initially (before 2022-08-09), there was 2 outliers on 2019-07-12 and 2018-09-11.
+On 2022-08-09, code was added above to put a no good qf (3) in order to eliminate those two outliers.
 Now we are fine.
-The average offset is 'r average_offset'.
+The average offset is `r round(average_offset, digits = 4)`.
+It considerably improve the plot "pH spectro vs pH seafet (at in situ temperature)".
 
@@
 
-```{r pHs comparaison sf spectro, echo=FALSE, message= FALSE, warning=FALSE}
+### **Spectro vs seafet**
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 # Spectro / seafet
@@
   plot = TRUE,
-  title = "pH spectro vs pH seafet (at in situ temperature)",
-  xlab = "pH spectro",
-  ylab = "pH seafet",
+  title = "pH spec. vs pH seafet (at in situ temperature)",
+  xlab = "Spectrophotometric pH",
+  ylab = "SeaFET pH",
   proplot = TRUE
 )
-print(reg$plot + xlim(c(8, 8.25)) + ylim(c(8, 8.25)))
+pHspec_pHcalc <- reg$plot + xlim(c(8.05, 8.20)) + ylim(c(8.05, 8.20))
+p
+#print(reg$plot + xlim(c(8, 8.25)) + ylim(c(8, 8.25)))
+ggsave(filename = "figures/pHspec_pHcalc.png", plot = pHspec_pHcalc)
 ```
@@
 ```
-```{r fig ts and bp for paper}
+
+###Combined plot for paper
+
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
+g <- (at_s / pco2_calc_meas / offset_ph / pHspec_pHcalc)
+g <- g + plot_annotation(tag_levels = 'A')
+ggsave(filename = "figures/pco2_ph_etc.png", plot = g)
+g
+```
+
+###Time series and boxplots for paper
+```{r }
 g <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at) |

### 2022-08-10 awipev-CO2.Rmd
still on finalizing a figure

@@
 
-# Same plot for paper
+# # Same plot for paper
+# at_s <- d_all_at_discrete %>% 
+#   drop_na() %>% 
+#   ggplot(aes(x = sal_fb_mix, y = at)) +
+#   geom_point(col="blue", size = 0.5) +
+#   labs(x="Salinity", y=latex2exp::TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
+#   stat_smooth(method = "lm", se=FALSE, col = "blue", size = 0.5) +
+#   Mytheme(size_labs = 9)
+# ggsave(filename = "figures/at_s.png", plot = at_s, width = 7, height = 7, units = "cm")
+
+# for paper
 at_s <- d_all_at_discrete %>% 
+  dplyr::select(sal_fb_mix, at) %>% 
   drop_na() %>% 
@@
   geom_point(col="blue", size = 0.5) +
-  labs(x="Salinity", y=TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
-  stat_smooth(method = "lm", se=FALSE, col = "blue", size = 0.5) +
-  Mytheme(size_labs = 9)
-ggsave(filename = "figures/at_s.png", plot = at_s, width = 7, height = 7, units = "cm")
+  labs(x= latex2exp::TeX("Salinity"),
+       y= latex2exp::TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
+  ggpmisc::stat_ma_line(method = "lmodel2:OLS", se = FALSE, size = 1) +
+  ggpmisc::stat_ma_eq(method = "lmodel2:OLS", aes(label = after_stat(eq.label))) +
+#stat_smooth(method = "lm", se=FALSE, col = "blue", size = 0.5) +
+  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio=1) + 
+  coord_fixed()
+at_s
+ggsave(filename = "figures/figures/at_s.png", plot = at_s, width = 25, height = 25, units = "cm")
 
@@
 
-```{r plot Discrete salinity vs TA, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
+```{r plot Discrete salinity vs TA, eval, FALSE, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
 # PLOT
@@
   ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
-  ggpmisc::stat_ma_eq(aes(label = after_stat(eq.label))) +
-#stat_smooth(method = "lm", se=FALSE, col = "blue", size = 0.5) +
-  theme_bw() + Mytheme(size_labs = 9)
+  ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label))) + geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
+  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
+  coord_fixed(ratio = 1, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on")
 ggsave(filename = "figures/pco2_calc_meas.png", plot = pco2_calc_meas, width = 25, height = 25, units = "cm")
@@
   labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
-  Mytheme(size_labs = 12, face_font = "plain") + 
-  #theme(panel.grid.major.x = element_blank(), axis.text.x = element_text(angle = 45, hjust = 1)) +
-  scale_colour_discrete(guide="none")
-ggsave(filename = "figures/offset_ph.png", plot = offset_ph, width = 10, height = 10, units = "cm")
+  Mytheme(size_labs = 9, face_font = "plain")+ theme(aspect.ratio=1)  + 
+  scale_colour_discrete(guide="none") + 
+  coord_fixed()
+ggsave(filename = "figures/offset_ph.png", plot = offset_ph, width = 25, height = 25, units = "cm")
 ```
@@
 ggsave(filename = "figures/pHspec_pHcalc.png", plot = pHspec_pHcalc)
+
+pHspec_pHcalc <- d_all %>% 
+  dplyr::select(ph_s_sf_temp_insi, pHint_tot_sf) %>% 
+  drop_na() %>% 
+  ggplot(aes(x = ph_s_sf_temp_insi, y = pHint_tot_sf)) +
+  geom_point(col="blue", size = 0.5) +
+  labs(x="Spectrophotometric pH",
+       y= "SeaFET pH")  +
+  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
+  ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label), digits = 4)) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
+  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
+  coord_fixed(ratio = 1, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on")
+ggsave(filename = "figures/pHspec_pHcalc.png", plot = pHspec_pHcalc, width = 25, height = 25, units = "cm")
 ```
@@
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
-g <- (at_s / pco2_calc_meas / offset_ph / pHspec_pHcalc)
+g <- (at_s | pco2_calc_meas) / (offset_ph | pHspec_pHcalc)
 g <- g + plot_annotation(tag_levels = 'A')

### 2022-08-10 awipev-CO2.Rmd
finalized a paper fig

@@
   ggpmisc::stat_ma_line(method = "lmodel2:OLS", se = FALSE, size = 1) +
-  ggpmisc::stat_ma_eq(method = "lmodel2:OLS", aes(label = after_stat(eq.label))) +
-#stat_smooth(method = "lm", se=FALSE, col = "blue", size = 0.5) +
+  #ggpmisc::stat_ma_eq(method = "lmodel2:OLS", aes(label = after_stat(eq.label))) +
   theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio=1) + 
@@
 
-```{r plot Discrete salinity vs TA, eval, FALSE, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
+```{r plot Discrete salinity vs TA, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
 # PLOT
-print(p_at_s)
-rm(p_at_s)
+# print(p_at_s)
+# rm(p_at_s)
 ```
@@
   ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
-  ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label))) + geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
+  #ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label))) + geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
   theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
@@
   ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
-  ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label), digits = 4)) +
+  #ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label), digits = 4)) +
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 2, y = 0.65, label = substitute("S"["surface"] ~ "> S"["deep"])) +
-  annotate("text", x = 2, y = -0.9, label = substitute("S"["surface"] ~ "< S"["deep"])) +
+  annotate("text", x = 2, y = 0.65, parse = TRUE, label = "S['surface'] > S['deep']") +
+  annotate("text", x = 2, y = -0.9, parse = TRUE, label = "S['surface'] <  S['deep']") +
+#  annotate("text", x = 2, y = 0.65, label = substitute("S"["surface"] ~ "> S"["deep"])) +
+#  annotate("text", x = 2, y = -0.9, label = substitute("S"["surface"] ~ "< S"["deep"])) +
   Mytheme(size_labs = 12) +
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 2, y = 0.3, label = substitute("T"["surface"] ~ "> T"["deep"])) +
-  annotate("text", x = 2, y = -1.8, label = substitute("T"["surface"] ~ "< T"["deep"])) +
+  annotate("text", x = 2, y = 0.3, parse = TRUE, label = "S['surface'] > S['deep']") +
+  annotate("text", x = 2, y = -1.8, parse = TRUE, label = "S['surface'] <  S['deep']") +
+  # annotate("text", x = 2, y = 0.3, label = substitute("T"["surface"] ~ "> T"["deep"])) +
+  # annotate("text", x = 2, y = -1.8, label = substitute("T"["surface"] ~ "< T"["deep"])) +
   Mytheme(size_labs = 12) +
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 2, y = 0.25, label = substitute("D"["surface"] ~ "> D"["deep"])) +
-  annotate("text", x = 2, y = -1.2, label = substitute("D"["surface"] ~ "< D"["deep"])) +
+  annotate("text", x = 2, y = 0.25, parse = TRUE, label = "S['surface'] > S['deep']") +
+  annotate("text", x = 2, y = -1.2, parse = TRUE, label = "S['surface'] <  S['deep']") +
+  # annotate("text", x = 2, y = 0.25, label = substitute("D"["surface"] ~ "> D"["deep"])) +
+  # annotate("text", x = 2, y = -1.2, label = substitute("D"["surface"] ~ "< D"["deep"])) +
   Mytheme(size_labs = 12) +
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 1.5, y = 0.02, label = substitute("pH"["surface"] ~ "> pH"["deep"])) +
-  annotate("text", x = 1.5, y = -0.06, label = substitute("pH"["surface"] ~ "< pH"["deep"])) +
+  annotate("text", x = 1.5, y = 0.02, parse = TRUE, label = "S['surface'] > S['deep']") +
+  annotate("text", x = 1.5, y = -0.06, parse = TRUE, label = "S['surface'] <  S['deep']") +
+  # annotate("text", x = 1.5, y = 0.02, label = substitute("pH"["surface"] ~ "> pH"["deep"])) +
+  # annotate("text", x = 1.5, y = -0.06, label = substitute("pH"["surface"] ~ "< pH"["deep"])) +
   Mytheme(size_labs = 12) +
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 1.5, y = 0.8, label = substitute("pH"["surface"] ~ "> pH"["deep"])) +
-  annotate("text", x = 1.5, y = -0.15, label = substitute("pH"["surface"] ~ "< pH"["deep"])) +
+  annotate("text", x = 1.5, y = 0.8, parse = TRUE, label = "S['surface'] > S['deep']") +
+  annotate("text", x = 1.5, y = -0.15, parse = TRUE, label = "S['surface'] <  S['deep']") +
+  # annotate("text", x = 1.5, y = 0.8, label = substitute("pH"["surface"] ~ "> pH"["deep"])) +
+  # annotate("text", x = 1.5, y = -0.15, label = substitute("pH"["surface"] ~ "< pH"["deep"])) +
   Mytheme(size_labs = 12) +
@@
 g <- (at_s | pco2_calc_meas) / (offset_ph | pHspec_pHcalc)
-g <- g + plot_annotation(tag_levels = 'A')
+g <- g + patchwork::plot_annotation(tag_levels = 'A')
 ggsave(filename = "figures/pco2_ph_etc.png", plot = g)

### 2022-08-11 awipev-CO2.Rmd
Finalized a figure

@@
   geom_point(col="blue", size = 0.5) +
+  xlim(180, 420) + ylim(180, 420) +
   labs(x=latex2exp::TeX("Measured $pCO_{2}\\phantom{x}(\\mu atm)$"),
@@
   ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
-  #ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label))) + geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
+  #ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label))) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
   theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
-  coord_fixed(ratio = 1, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on")
+  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
 ggsave(filename = "figures/pco2_calc_meas.png", plot = pco2_calc_meas, width = 25, height = 25, units = "cm")
@@
   geom_point(col="blue", size = 0.5) +
+  xlim(8.05, 8.18) + ylim(8.05, 8.18) +
   labs(x="Spectrophotometric pH",
@@
   theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
-  coord_fixed(ratio = 1, xlim = NULL, ylim = NULL, expand = TRUE, clip = "on")
+  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
 ggsave(filename = "figures/pHspec_pHcalc.png", plot = pHspec_pHcalc, width = 25, height = 25, units = "cm")

### 2022-08-11 awipev-CO2.Rmd
Finalized a figure 2

@@
   ggplot() +
-  geom_point(aes(x=datetime, y=diff_spec_sf, color="blue"), size=2) +
+  geom_point(aes(x=datetime, y=diff_spec_sf), size=1, color="blue") +
   geom_hline(yintercept=0, size=0.3) +
@@
   geom_hline(yintercept=0.02, size=0.3, linetype = "dashed") +
-  labs(x = NULL, y=expression(paste(pH[T], " difference")), title = NULL) +
-  Mytheme(size_labs = 9, face_font = "plain")+ theme(aspect.ratio=1)  + 
+  labs(x = "Date", y=expression(paste(pH[T], " difference")), title = NULL) +
+  Mytheme(size_labs = 9, face_font = "plain") + theme(aspect.ratio=1)  + 
   scale_colour_discrete(guide="none") + 

### 2022-08-11 awipev-CO2.Rmd
figure finalized

@@
   coord_fixed()
-at_s
 ggsave(filename = "figures/figures/at_s.png", plot = at_s, width = 25, height = 25, units = "cm")
@@
 salinity is very good with an r2 of
-`r round(reg$fit$rsquare, digits = 2)`. Need to compare with other relationships from the literature.
+`r round(reg$fit$rsquare, digits = 2)` (`r N = reg$fit$n`). Need to compare with other relationships from the literature.
 
@@
 `r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence
-interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)`.
+interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)  (`r N = reg$fit$n`)`.
 
@@
 ```
+The relationship between spectrophotometric pH and SeaFET pH) and 
+(blue line) is relatively good The slope is
+`r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence
+interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)  (`r N = reg$fit$n`)`.
 

### 2022-08-11 awipev-CO2.Rmd
fixed function ggreg (rmse was wrong)

@@
   { # x and y are the names of the variables
-  fit_data <- tibble(xdata, ydata)
-  colnames(fit_data) = c("xdata", "ydata")
+  fit_data <- tibble(xdata = xdata, ydata = ydata)
   fit <- print(lmodel2::lmodel2(ydata ~ xdata))
@@
 slope <- fit$regression.results$Slope[ty]
-predicted <- fit$regression.results$Intercept[1] + xdata * fit$regression.results$Slope[1]
-error <- xdata - predicted
+predicted <- intercept + xdata * slope
+error <- ydata - predicted
 if (plot == TRUE) {
@@
 
-### **Discrete total alkalinity (reference) vs salinity relationship**
+### **Discrete total alkalinity vs salinity **
 
@@
 
-```{r Discrete salinity vs TA, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="100%"}
+```{r, echo=FALSE, fig.align="center", message=FALSE, warning=FALSE, out.width="100%"}
 d_all_at_discrete <- d_all %>% #  To remove an outlier in red
-  dplyr::select(datetime, monthd, closest_datetime, at, sal_fb_mix)
+  dplyr::select(at, sal_fb_mix) %>% 
+  drop_na()
+  #dplyr::select(datetime, monthd, closest_datetime, at, sal_fb_mix)
 reg <- ggreg(
-  xdata = d_all$sal_fb_mix,
-  ydata = d_all$at,
+  xdata = d_all_at_discrete$sal_fb_mix,
+  ydata = d_all_at_discrete$at,
   type = "OLS",
@@
 print(reg$plot)
-ggsave(filename = "figures/at_s.png", plot = reg$plot, width = 25, height = 20, units = "cm")
-
-# # Same plot for paper
-# at_s <- d_all_at_discrete %>% 
-#   drop_na() %>% 
-#   ggplot(aes(x = sal_fb_mix, y = at)) +
-#   geom_point(col="blue", size = 0.5) +
-#   labs(x="Salinity", y=latex2exp::TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
-#   stat_smooth(method = "lm", se=FALSE, col = "blue", size = 0.5) +
-#   Mytheme(size_labs = 9)
-# ggsave(filename = "figures/at_s.png", plot = at_s, width = 7, height = 7, units = "cm")
+#ggsave(filename = "figures/at_s.png", plot = reg$plot, width = 25, height = 20, units = "cm")
 
@@
 
-```{r plot Discrete salinity vs TA, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
-# PLOT
-# print(p_at_s)
-# rm(p_at_s)
+#### **Is there a seasonal change in the AT vs S relationship**
+```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
+tmp <- d_all_at_discrete %>% 
+  dplyr::select(sal_fb_mix, at) %>% 
+  drop_na() %>% 
+  dplyr::mutate(cutoff = ifelse(sal_fb_mix < 34.5, "below", "above")) %>% 
+  ggplot(aes(x = sal_fb_mix, y = at)) +
+  geom_point(col="blue", size = 0.5) +
+  facet_grid(cutoff ~.) +
+  labs(x= latex2exp::TeX("Salinity"),
+       y= latex2exp::TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
+  ggpmisc::stat_ma_line(method = "lmodel2:OLS", se = FALSE, size = 1) +
+  ggpmisc::stat_ma_eq(method = "lmodel2:OLS", aes(label = after_stat(eq.label))) +
+  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio=1) + 
+  coord_fixed()
 ```

### 2022-08-11 awipev-CO2.Rmd
Added code to split AT vs S at S=34.5

@@
 #### **Is there a seasonal change in the AT vs S relationship**
-```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
-tmp <- d_all_at_discrete %>% 
+```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
+d_all_at_discrete <- d_all_at_discrete %>% 
   dplyr::select(sal_fb_mix, at) %>% 
   drop_na() %>% 
-  dplyr::mutate(cutoff = ifelse(sal_fb_mix < 34.5, "below", "above")) %>% 
-  ggplot(aes(x = sal_fb_mix, y = at)) +
-  geom_point(col="blue", size = 0.5) +
-  facet_grid(cutoff ~.) +
-  labs(x= latex2exp::TeX("Salinity"),
-       y= latex2exp::TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
-  ggpmisc::stat_ma_line(method = "lmodel2:OLS", se = FALSE, size = 1) +
-  ggpmisc::stat_ma_eq(method = "lmodel2:OLS", aes(label = after_stat(eq.label))) +
-  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio=1) + 
-  coord_fixed()
-```
+  dplyr::mutate(cutoff = ifelse(sal_fb_mix < 34.5, "below", "above"))
+below <- d_all_at_discrete %>% 
+  dplyr::filter(cutoff == "below")
+reg_below <- ggreg(
+  xdata = below$sal_fb_mix,
+  ydata = below$at,
+  type = "OLS",
+  plot = TRUE,
+  title = "Discrete total alkalinity vs salinity below 34.5",
+  #subtitle = "",
+  xlab = "Salinity",
+  ylab = TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"),
+  proplot = TRUE,
+  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
+  coord_fixed(ratio = 1)
+)
+print(reg_below$plot)
+
+above <- d_all_at_discrete %>% 
+  dplyr::filter(cutoff == "above")
+reg_above <- ggreg(
+  xdata = above$sal_fb_mix,
+  ydata = above$at,
+  type = "OLS",
+  plot = TRUE,
+  title = "Discrete total alkalinity vs salinity above 34.5",
+  #subtitle = "",
+  xlab = "Salinity",
+  ylab = TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"),
+  proplot = TRUE,
+  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
+  coord_fixed(ratio = 1)
+)
+print(reg_above$plot)
+g <- reg_below$plot | reg_above$plot
+g
+```
+
+Splitting the data below and above salinity 34.5, as done by Nondal et al.
+(2009), does not prove useful (data not shown).
+It degrades r2 (0.74 and 0.3 vs 0.81), degrades rmse or marginally improves the rmse (19 and 13.6 vs 16.8).
 

### 2022-08-11 awipev-CO2.Rmd
cannot do ssec pH vs calc pH (AT-CT)

--- 2022-08-11 awipev-CO2.Rmd
@@
 #### **Is there a seasonal change in the AT vs S relationship**
-```{r, eval=FALSE, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
-tmp <- d_all_at_discrete %>% 
+```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
+d_all_at_discrete <- d_all_at_discrete %>% 
   dplyr::select(sal_fb_mix, at) %>% 
   drop_na() %>% 
-  dplyr::mutate(cutoff = ifelse(sal_fb_mix < 34.5, "below", "above")) %>% 
-  ggplot(aes(x = sal_fb_mix, y = at)) +
-  geom_point(col="blue", size = 0.5) +
-  facet_grid(cutoff ~.) +
-  labs(x= latex2exp::TeX("Salinity"),
-       y= latex2exp::TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
-  ggpmisc::stat_ma_line(method = "lmodel2:OLS", se = FALSE, size = 1) +
-  ggpmisc::stat_ma_eq(method = "lmodel2:OLS", aes(label = after_stat(eq.label))) +
-  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio=1) + 
-  coord_fixed()
-```
+  dplyr::mutate(cutoff = ifelse(sal_fb_mix < 34.5, "below", "above"))
+below <- d_all_at_discrete %>% 
+  dplyr::filter(cutoff == "below")
+reg_below <- ggreg(
+  xdata = below$sal_fb_mix,
+  ydata = below$at,
+  type = "OLS",
+  plot = TRUE,
+  title = "Discrete total alkalinity vs salinity below 34.5",
+  #subtitle = "",
+  xlab = "Salinity",
+  ylab = TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"),
+  proplot = TRUE,
+  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
+  coord_fixed(ratio = 1)
+)
+above <- d_all_at_discrete %>% 
+  dplyr::filter(cutoff == "above")
+reg_above <- ggreg(
+  xdata = above$sal_fb_mix,
+  ydata = above$at,
+  type = "OLS",
+  plot = TRUE,
+  title = "Discrete total alkalinity vs salinity above 34.5",
+  #subtitle = "",
+  xlab = "Salinity",
+  ylab = TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"),
+  proplot = TRUE,
+  #ylim(c(30.5,35.5)) + xlim(c(28,35.5)),
+  coord_fixed(ratio = 1)
+)
+g <- reg_below$plot | reg_above$plot
+g
+```
+
+Splitting the data below and above salinity 34.5, as done by Nondal et al.
+(2009), does not prove useful (data not shown).
+It degrades r2 (0.74 and 0.3 vs 0.81), degrades rmse or marginally improves the rmse (19 and 13.6 vs 16.8).
 
@@
 )
-pHspec_pHcalc <- reg$plot + xlim(c(8.05, 8.20)) + ylim(c(8.05, 8.20))
-p
-#print(reg$plot + xlim(c(8, 8.25)) + ylim(c(8, 8.25)))
-ggsave(filename = "figures/pHspec_pHcalc.png", plot = pHspec_pHcalc)
-
-pHspec_pHcalc <- d_all %>% 
+pHspec_pHseafet <- reg$plot + xlim(c(8.05, 8.20)) + ylim(c(8.05, 8.20))
+pHspec_pHseafet
+#ggsave(filename = "figures/pHspec_pHcalc.png", plot = pHspec_pHcalc)
+
+pHspec_pHseafet <- d_all %>% 
   dplyr::select(ph_s_sf_temp_insi, pHint_tot_sf) %>% 
@@
   coord_fixed(ratio = 1, expand = TRUE, clip = "on")
-ggsave(filename = "figures/pHspec_pHcalc.png", plot = pHspec_pHcalc, width = 25, height = 25, units = "cm")
+ggsave(filename = "figures/pHspec_pHseafet.png", plot = pHspec_pHseafet, width = 25, height = 25, units = "cm")
 ```
@@
 interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)  (`r N = reg$fit$n`)`.
+
+### **Spectro vs calculated AT-CT**
+```{r, eval=FALSE, echo=FALSE, message= FALSE, warning=FALSE}
+# do not run because only 2 data points available...
+dplyr::select(d_all, datetime, ph_s_sf_temp_4) %>% drop_na()
+dplyr::select(d_all, datetime, pH_calc_fb_temp_4) %>% dplyr::filter(datetime > as.POSIXct ("2017-08-23")) %>% drop_na()
+
+tmp <- d_all %>% 
+  dplyr::select(ph_s_sf_temp_4, pH_calc_fb_temp_4) %>% 
+  drop_na()
+```
 
@@
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
-g <- (at_s | pco2_calc_meas) / (offset_ph | pHspec_pHcalc)
+g <- (at_s | pco2_calc_meas) / (offset_ph | pHspec_pHseafet)
 g <- g + patchwork::plot_annotation(tag_levels = 'A')

### 2022-08-12 awipev-CO2.Rmd
stratification

@@
 `r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence
-interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)  (`r N = reg$fit$n`)`.
+interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)`  (`r N = reg$fit$n`)`.
 
@@
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
-# # we look at the distribution of data
+# we look at the distribution of data
 depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
@@
   annotate("text", x = 2, y = -0.9, parse = TRUE, label = "S['surface'] <  S['deep']") +
-#  annotate("text", x = 2, y = 0.65, label = substitute("S"["surface"] ~ "> S"["deep"])) +
-#  annotate("text", x = 2, y = -0.9, label = substitute("S"["surface"] ~ "< S"["deep"])) +
   Mytheme(size_labs = 12) +
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 2, y = 0.3, parse = TRUE, label = "S['surface'] > S['deep']") +
-  annotate("text", x = 2, y = -1.8, parse = TRUE, label = "S['surface'] <  S['deep']") +
-  # annotate("text", x = 2, y = 0.3, label = substitute("T"["surface"] ~ "> T"["deep"])) +
-  # annotate("text", x = 2, y = -1.8, label = substitute("T"["surface"] ~ "< T"["deep"])) +
+  annotate("text", x = 2, y = 0.3, parse = TRUE, label = "T['surface'] > T['deep']") +
+  annotate("text", x = 2, y = -1.8, parse = TRUE, label = "T['surface'] <  T['deep']") +
   Mytheme(size_labs = 12) +
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 2, y = 0.25, parse = TRUE, label = "S['surface'] > S['deep']") +
-  annotate("text", x = 2, y = -1.2, parse = TRUE, label = "S['surface'] <  S['deep']") +
-  # annotate("text", x = 2, y = 0.25, label = substitute("D"["surface"] ~ "> D"["deep"])) +
-  # annotate("text", x = 2, y = -1.2, label = substitute("D"["surface"] ~ "< D"["deep"])) +
+  annotate("text", x = 2, y = 0.25, parse = TRUE, label = "D['surface'] > D['deep']") +
+  annotate("text", x = 2, y = -1.2, parse = TRUE, label = "D['surface'] <  D['deep']") +
   Mytheme(size_labs = 12) +
@@
   dplyr::select(montht, pHint_tot_sf, depth_group) %>%
-  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4',
-                                                   depth_group == '>8' ~ '8-12'))) %>% 
+  dplyr::mutate(depth_group2 = as.factor(
+    case_when(
+      depth_group == '0-2' | depth_group == '2-4' ~ '0-4',
+      depth_group == '>8' ~ '8-12'
+    )
+  )) %>%
   dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>%
@@
   ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
-  #labs(y = substitute("pH"["T"] ~ "at in situ temp."), x = "Month") +
   scale_x_discrete("Month") +
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 1.5, y = 0.02, parse = TRUE, label = "S['surface'] > S['deep']") +
-  annotate("text", x = 1.5, y = -0.06, parse = TRUE, label = "S['surface'] <  S['deep']") +
-  # annotate("text", x = 1.5, y = 0.02, label = substitute("pH"["surface"] ~ "> pH"["deep"])) +
-  # annotate("text", x = 1.5, y = -0.06, label = substitute("pH"["surface"] ~ "< pH"["deep"])) +
+  annotate("text", x = 1.5, y = 0.02, parse = TRUE, label = "pH['surface'] > pH['deep']") +
+  annotate("text", x = 1.5, y = -0.06, parse = TRUE, label = "pH['surface'] <  pH['deep']") +
   Mytheme(size_labs = 12) +
@@
   ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
-  #labs(y = substitute("pH"["T"] ~ "at in situ temp."), x = "Month") +
   scale_x_discrete("Month", expand = c(0, 0)) +
-  scale_y_continuous(substitute("pH"["T"] ~ "at 4°C"), limits = c(-0.2, 0.1), expand = c(0, 0)) +
+  scale_y_continuous(substitute("pH"["T"] ~ "at 4°C"), limits = c(-0.2, 0.2), expand = c(0, 0)) +
   geom_col(fill="blue") +
   geom_hline(yintercept = 0) +
-  annotate("text", x = 1.5, y = 0.8, parse = TRUE, label = "S['surface'] > S['deep']") +
-  annotate("text", x = 1.5, y = -0.15, parse = TRUE, label = "S['surface'] <  S['deep']") +
-  # annotate("text", x = 1.5, y = 0.8, label = substitute("pH"["surface"] ~ "> pH"["deep"])) +
-  # annotate("text", x = 1.5, y = -0.15, label = substitute("pH"["surface"] ~ "< pH"["deep"])) +
+  annotate("text", x = 1.5, y = 0.8, parse = TRUE, label = "pH['surface'] > pH['deep']") +
+  annotate("text", x = 1.5, y = -0.15, parse = TRUE, label = "pH['surface'] < pH['deep']") +
   Mytheme(size_labs = 12) +

### 2022-08-16 awipev-CO2.Rmd
Started to add pCO2 on the REMOS.

@@
 
-Let's look first at the stratification (salinity, temperature and
-density).
-
+Let's look at the stratification tab above (salinity, temperature, density and pH).
+
+## pCO2 from pH and AT 0-4m
+If one calculates pCO2 from seafet pH and AT (from salinity) between 0-4 m, do we get better estimates of air-sea CO2 fluxes?
+
+```{r}
+size_point <- 0.3 # size of data points
+alpha <- 1 #transparency
+size_labs <- 6 # font size labels
+
+tmp <- d_all %>% 
+  dplyr::select(datetime, pHint_tot_sf, sal_insitu_ctd, temp_insitu_ctd) %>% 
+  drop_na() %>% 
+  dplyr::mutate(at_0_4m = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
+                pco2_0_4m = seacarb::carb(flag=8, var1=pHint_tot_sf, var2=tmp$at_0_4m)$pCO2)
+ts_pCO2_calc <- tmp %>%
+  ggplot() +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(aes(x = datetime, y = pco2_0_4m), 
+             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
+  labs(title=expression(paste(pCO[2], "calc at 0-4 m and in situ temperature")),
+       x="", y=TeX("pCO$_2$ ($\\mu atm$)")) +
+  Mytheme(size_labs = size_labs)
+ts_pCO2_calc
+```
+
+## Atmospheric CO2 Zeppelin
 ```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
-## Atmospheric CO2 Zeppelin
 # downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999

### 2022-08-16 awipev-CO2.Rmd
pCO2 REMOS

@@
 print(pHinsi_delta_plt)
+
 # we look at pHint_tot_sf normalized at 4°C at all depths
@@
 
+# we look at pHint_tot_sf normalized at 4°C at all depths
+tmp <- d_all %>% 
+  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
+  tidyr::drop_na() %>% 
+  dplyr::filter(depth_group != "NA") %>% 
+  group_by(depth_group, montht)
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf_temp_4)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "pHint_tot_sf at 4°C vs depth", x = "Depth (m)", y= "pH at 4°C (units)") +
+  scale_x_discrete(labels = depth_labels) +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group * tmp$montht))
+
+# we look at pHint_tot_sf normalized at 4°C  0 to 4 m vs more than 8 m
+tmp <- d_all %>% 
+  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
+  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4',
+                                                   depth_group == '>8' ~ '8-12'))) %>% 
+  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
+  dplyr::group_by(depth_group2, montht)
+summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group2 * tmp$montht))
+
+tmp_delta <- tmp %>% 
+  group_by(depth_group2, montht) %>% 
+  dplyr::summarise(pH_tot_sf_med = median(pHint_tot_sf_temp_4, na.rm = TRUE)) %>% 
+  tidyr::pivot_wider(names_from = depth_group2, values_from = pH_tot_sf_med) %>% 
+  dplyr::rename(median0_4m = "0-4",
+                median8_12m = "8-12") %>%   dplyr::mutate(pH_tot_sf_med_delta = median0_4m - median8_12m)
+kable(tmp_delta, digits = 3, caption = "Median seafet pH at 4°C with (median0_4m - median8_12m)")
+
+p <- tidyr::drop_na(tmp) %>% 
+  ggplot(aes(x=as.factor(depth_group2), y = pHint_tot_sf_temp_4)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "pH at 4°C vs depth", x = "Depth (m)", y= "pHint_tot_sf") +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+
+pH_delta_plt <- tidyr::drop_na(tmp_delta) %>% 
+  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
+  scale_x_discrete("Month", expand = c(0, 0)) +
+  scale_y_continuous(substitute("pH"["T"] ~ "at 4°C"), limits = c(-0.2, 0.2), expand = c(0, 0)) +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 0.8, parse = TRUE, label = "pH['surface'] > pH['deep']") +
+  annotate("text", x = 1.5, y = -0.15, parse = TRUE, label = "pH['surface'] < pH['deep']") +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
+
+# we look at pCO2 normalized at 4°C at all depths
+# calculate fCO2 from pH and salinity-derived AT
+  dplyr::select(datetime, depth, pHint_tot_sf, sal_insitu_ctd, temp_insitu_ctd) %>% 
+  drop_na() %>% 
+  dplyr::mutate(at_0_4m = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
+                pco2_0_4m = seacarb::carb(flag=8, var1=pHint_tot_sf, var2=tmp$at_0_4m)$pCO2)
+tmp <- d_all %>% 
+  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
+  tidyr::drop_na() %>% 
+  dplyr::filter(depth_group != "NA") %>% 
+  group_by(depth_group, montht)
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf_temp_4)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "pHint_tot_sf at 4°C vs depth", x = "Depth (m)", y= "pH at 4°C (units)") +
+  scale_x_discrete(labels = depth_labels) +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group * tmp$montht))
+
+# we look at pHint_tot_sf normalized at 4°C  0 to 4 m vs more than 8 m
+tmp <- d_all %>% 
+  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
+  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4',
+                                                   depth_group == '>8' ~ '8-12'))) %>% 
+  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
+  dplyr::group_by(depth_group2, montht)
+summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group2 * tmp$montht))
+
+tmp_delta <- tmp %>% 
+  group_by(depth_group2, montht) %>% 
+  dplyr::summarise(pH_tot_sf_med = median(pHint_tot_sf_temp_4, na.rm = TRUE)) %>% 
+  tidyr::pivot_wider(names_from = depth_group2, values_from = pH_tot_sf_med) %>% 
+  dplyr::rename(median0_4m = "0-4",
+                median8_12m = "8-12") %>%   dplyr::mutate(pH_tot_sf_med_delta = median0_4m - median8_12m)
+kable(tmp_delta, digits = 3, caption = "Median seafet pH at 4°C with (median0_4m - median8_12m)")
+
+p <- tidyr::drop_na(tmp) %>% 
+  ggplot(aes(x=as.factor(depth_group2), y = pHint_tot_sf_temp_4)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "pH at 4°C vs depth", x = "Depth (m)", y= "pHint_tot_sf") +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+
+pH_delta_plt <- tidyr::drop_na(tmp_delta) %>% 
+  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
+  scale_x_discrete("Month", expand = c(0, 0)) +
+  scale_y_continuous(substitute("pH"["T"] ~ "at 4°C"), limits = c(-0.2, 0.2), expand = c(0, 0)) +
+  geom_col(fill="blue") +
+  geom_hline(yintercept = 0) +
+  annotate("text", x = 1.5, y = 0.8, parse = TRUE, label = "pH['surface'] > pH['deep']") +
+  annotate("text", x = 1.5, y = -0.15, parse = TRUE, label = "pH['surface'] < pH['deep']") +
+  Mytheme(size_labs = 12) +
+  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
+        panel.grid.minor.y = element_blank())
 # all deltas

### 2022-08-16 awipev-CO2.Rmd
Added fCO2 calculated at REMOS depths

@@
 
-# we look at pCO2 normalized at 4°C at all depths
+# we look at pCO2  at all depths
 # calculate fCO2 from pH and salinity-derived AT
-  dplyr::select(datetime, depth, pHint_tot_sf, sal_insitu_ctd, temp_insitu_ctd) %>% 
+tmp <- d_all %>%
+  dplyr::select(datetime,
+                montht,
+                depth_group,
+                depth,
+                pHint_tot_sf,
+                sal_insitu_ctd,
+                temp_insitu_ctd) %>%
   drop_na() %>%
-  dplyr::mutate(at_0_4m = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
-                pco2_0_4m = seacarb::carb(flag=8, var1=pHint_tot_sf, var2=tmp$at_0_4m)$pCO2)
+  dplyr::mutate(
+    at_sf = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
+    fco2_sf = seacarb::carb(
+      flag = 8,
+      var1 = pHint_tot_sf,
+      var2 = at_sf,
+      S = sal_insitu_ctd,
+      T = temp_insitu_ctd,
+      Patm = 1,
+      P = depth / 10,
+      Pt = 0,
+      Sit = 0,
+      k1k2 = "l",
+      kf = "dg",
+      ks = "d",
+      pHscale = "T",
+      b = "u74"
+    )$fCO2
+  ) %>% 
+  dplyr::select(datetime, fco2_sf)
+d_all <- left_join(d_all, tmp, by = "datetime")
 tmp <- d_all %>% 
-  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
+  dplyr::select(montht, fco2_sf, depth_group) %>%
   tidyr::drop_na() %>% 
@@
 p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf_temp_4)) +
+  ggplot(aes(x=as.factor(depth_group), y = fco2_sf)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "pHint_tot_sf at 4°C vs depth", x = "Depth (m)", y= "pH at 4°C (units)") +
+  labs(title = "fco2_sf vs depth", x = "Depth (m)", y= "fCO2 (uatm)") +
   scale_x_discrete(labels = depth_labels) +
@@
 print(p)
-summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group * tmp$montht))
-
-# we look at pHint_tot_sf normalized at 4°C  0 to 4 m vs more than 8 m
+summary(aov(tmp$fco2_sf ~ tmp$depth_group * tmp$montht))
+
+# we look at fCO2 0 to 4 m vs more than 8 m
 tmp <- d_all %>%
-  dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
-  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4',
-                                                   depth_group == '>8' ~ '8-12'))) %>% 
+  dplyr::select(montht, fco2_sf, depth_group) %>%
+  dplyr::mutate(depth_group2 = as.factor(
+    case_when(
+      depth_group == '0-2' | depth_group == '2-4' ~ '0-4',
+      depth_group == '>8' ~ '8-12'
+    )
+  )) %>%
   dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>%
   dplyr::group_by(depth_group2, montht)
-summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group2 * tmp$montht))
+summary(aov(tmp$fco2_sf ~ tmp$depth_group2 * tmp$montht))
 
@@
   group_by(depth_group2, montht) %>%
-  dplyr::summarise(pH_tot_sf_med = median(pHint_tot_sf_temp_4, na.rm = TRUE)) %>% 
-  tidyr::pivot_wider(names_from = depth_group2, values_from = pH_tot_sf_med) %>% 
+  dplyr::summarise(fco2_sf_med = median(fco2_sf, na.rm = TRUE)) %>%
+  tidyr::pivot_wider(names_from = depth_group2, values_from = fco2_sf_med) %>%
   dplyr::rename(median0_4m = "0-4",
-                median8_12m = "8-12") %>%   dplyr::mutate(pH_tot_sf_med_delta = median0_4m - median8_12m)
-kable(tmp_delta, digits = 3, caption = "Median seafet pH at 4°C with (median0_4m - median8_12m)")
+                median8_12m = "8-12") %>%   dplyr::mutate(fco2_sf_med_delta = median0_4m - median8_12m)
+kable(tmp_delta, digits = 3, caption = "Median seafet fCO2 with (median0_4m - median8_12m)")
 
 p <- tidyr::drop_na(tmp) %>% 
-  ggplot(aes(x=as.factor(depth_group2), y = pHint_tot_sf_temp_4)) +
+  ggplot(aes(x=as.factor(depth_group2), y = fco2_sf)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
 
-pH_delta_plt <- tidyr::drop_na(tmp_delta) %>% 
-  ggplot(aes(x=montht, y=pH_tot_sf_med_delta)) +
+fco2_delta_plt <- tmp_delta %>%
+  ggplot(aes(x = montht, y = fco2_sf_med_delta)) +
   scale_x_discrete("Month", expand = c(0, 0)) +
-  scale_y_continuous(substitute("pH"["T"] ~ "at 4°C"), limits = c(-0.2, 0.2), expand = c(0, 0)) +
-  geom_col(fill="blue") +
+  scale_y_continuous(substitute("fCO"["2"]), limits = c(-45, 10)) +
+  geom_col(fill = "blue") +
   geom_hline(yintercept = 0) +
-  annotate("text", x = 1.5, y = 0.8, parse = TRUE, label = "pH['surface'] > pH['deep']") +
-  annotate("text", x = 1.5, y = -0.15, parse = TRUE, label = "pH['surface'] < pH['deep']") +
+  annotate(
+    "text",
+    x = 2.5,
+    y = 5,
+    parse = TRUE,
+    label = "fCO['2 surface'] > fCO['2 deep']"
+  ) +
+  annotate(
+    "text",
+    x = 2.5,
+    y = -40,
+    parse = TRUE,
+    label = "fCO['2 surface'] < fCO['2 deep']"
+  ) +
   Mytheme(size_labs = 12) +
-  theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
-        panel.grid.minor.y = element_blank())
+  theme(
+    panel.grid.major.x = element_blank(),
+    panel.grid.major.y = element_blank(),
+    panel.grid.minor.y = element_blank()
+  )
+fco2_delta_plt
 # all deltas
-deltas_plt <- sal_delta_plt / temp_delta_plt / den_delta_plt / pH_delta_plt
+deltas_plt <- sal_delta_plt / temp_delta_plt / den_delta_plt / fco2_delta_plt
 deltas_plt <- deltas_plt + plot_annotation(tag_levels = 'a')
@@
 
-seaFET pH is significantly different at the surface and depth. It should
-therefore be the same for pCO2.
-
-Let's look at the stratification tab above (salinity, temperature, density and pH).
-
-## pCO2 from pH and AT 0-4m
-If one calculates pCO2 from seafet pH and AT (from salinity) between 0-4 m, do we get better estimates of air-sea CO2 fluxes?
-
-```{r}
-size_point <- 0.3 # size of data points
-alpha <- 1 #transparency
-size_labs <- 6 # font size labels
-
-tmp <- d_all %>% 
-  dplyr::select(datetime, pHint_tot_sf, sal_insitu_ctd, temp_insitu_ctd) %>% 
-  drop_na() %>% 
-  dplyr::mutate(at_0_4m = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
-                pco2_0_4m = seacarb::carb(flag=8, var1=pHint_tot_sf, var2=tmp$at_0_4m)$pCO2)
-ts_pCO2_calc <- tmp %>%
-  ggplot() +
-  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
-  geom_point(aes(x = datetime, y = pco2_0_4m), 
-             colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
-  labs(title=expression(paste(pCO[2], "calc at 0-4 m and in situ temperature")),
-       x="", y=TeX("pCO$_2$ ($\\mu atm$)")) +
-  Mytheme(size_labs = size_labs)
-ts_pCO2_calc
-```
+Let's look at the stratification tab above (salinity, temperature, density and fCO2): fCO2 is generally higher in the bottom layer than in the surface layer (note that no data is available in May, June and July).
+Which means that the air-sea CO2 fluxes calculated with pCO2 at 11 m are overestimated.
 

### 2022-08-16 awipev-CO2.Rmd
In stratification: fCO2 replaced by pCO2

@@
 # we look at pCO2  at all depths
-# calculate fCO2 from pH and salinity-derived AT
+# calculate pCO2 from pH and salinity-derived AT
 tmp <- d_all %>%
@@
     at_sf = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
-    fco2_sf = seacarb::carb(
+    pco2_sf = seacarb::carb(
       flag = 8,
@@
       b = "u74"
-    )$fCO2
+    )$pCO2
   ) %>% 
-  dplyr::select(datetime, fco2_sf)
+  dplyr::select(datetime, pco2_sf)
 d_all <- left_join(d_all, tmp, by = "datetime")
 tmp <- d_all %>% 
-  dplyr::select(montht, fco2_sf, depth_group) %>%
+  dplyr::select(montht, pco2_sf, depth_group) %>%
   tidyr::drop_na() %>% 
@@
 p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth_group), y = fco2_sf)) +
+  ggplot(aes(x=as.factor(depth_group), y = pco2_sf)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "fco2_sf vs depth", x = "Depth (m)", y= "fCO2 (uatm)") +
+  labs(title = "pco2_sf vs depth", x = "Depth (m)", y= "fCO2 (uatm)") +
   scale_x_discrete(labels = depth_labels) +
@@
 print(p)
-summary(aov(tmp$fco2_sf ~ tmp$depth_group * tmp$montht))
-
-# we look at fCO2 0 to 4 m vs more than 8 m
+summary(aov(tmp$pco2_sf ~ tmp$depth_group * tmp$montht))
+
+# we look at pCO2 0 to 4 m vs more than 8 m
 tmp <- d_all %>%
-  dplyr::select(montht, fco2_sf, depth_group) %>%
+  dplyr::select(montht, pco2_sf, depth_group) %>%
   dplyr::mutate(depth_group2 = as.factor(
@@
   dplyr::group_by(depth_group2, montht)
-summary(aov(tmp$fco2_sf ~ tmp$depth_group2 * tmp$montht))
+summary(aov(tmp$pco2_sf ~ tmp$depth_group2 * tmp$montht))
 
@@
   group_by(depth_group2, montht) %>%
-  dplyr::summarise(fco2_sf_med = median(fco2_sf, na.rm = TRUE)) %>%
-  tidyr::pivot_wider(names_from = depth_group2, values_from = fco2_sf_med) %>%
+  dplyr::summarise(pco2_sf_med = median(pco2_sf, na.rm = TRUE)) %>%
+  tidyr::pivot_wider(names_from = depth_group2, values_from = pco2_sf_med) %>%
   dplyr::rename(median0_4m = "0-4",
-                median8_12m = "8-12") %>%   dplyr::mutate(fco2_sf_med_delta = median0_4m - median8_12m)
+                median8_12m = "8-12") %>%   dplyr::mutate(pco2_sf_med_delta = median0_4m - median8_12m)
 kable(tmp_delta, digits = 3, caption = "Median seafet fCO2 with (median0_4m - median8_12m)")
@@
 p <- tidyr::drop_na(tmp) %>% 
-  ggplot(aes(x=as.factor(depth_group2), y = fco2_sf)) +
+  ggplot(aes(x=as.factor(depth_group2), y = pco2_sf)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "pH at 4°C vs depth", x = "Depth (m)", y= "pHint_tot_sf") +
+  labs(title = "pCO2", x = "Depth (m)", y= "pHint_tot_sf") +
   facet_wrap(vars(montht), scale = "free_y")
@@
 
-fco2_delta_plt <- tmp_delta %>%
-  ggplot(aes(x = montht, y = fco2_sf_med_delta)) +
+pco2_delta_plt <- tmp_delta %>%
+  ggplot(aes(x = montht, y = pco2_sf_med_delta)) +
   scale_x_discrete("Month", expand = c(0, 0)) +
-  scale_y_continuous(substitute("fCO"["2"]), limits = c(-45, 10)) +
+  scale_y_continuous(substitute("pCO"["2"]), limits = c(-45, 10)) +
   geom_col(fill = "blue") +
@@
     parse = TRUE,
-    label = "fCO['2 surface'] > fCO['2 deep']"
+    label = "pCO['2 surface'] > pCO['2 deep']"
   ) +
@@
     parse = TRUE,
-    label = "fCO['2 surface'] < fCO['2 deep']"
+    label = "pCO['2 surface'] < pCO['2 deep']"
   ) +
@@
   )
-fco2_delta_plt
+pco2_delta_plt
 # all deltas
-deltas_plt <- sal_delta_plt / temp_delta_plt / den_delta_plt / fco2_delta_plt
+deltas_plt <- sal_delta_plt / temp_delta_plt / den_delta_plt / pco2_delta_plt
 deltas_plt <- deltas_plt + plot_annotation(tag_levels = 'a')

### 2022-08-16 awipev-CO2.Rmd
Added calculation of OmegaAragonite

@@
 ## Miscellaneous
-
-###Save all
+### OmegaAragonite
+OmegaAragonite is calculated using at_calc and pCO2
+```{r, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+# we calculate it from at_calc and pCO2
+# nuts are not taken into consideration
+tmp <- d_all %>% # just for this chunk
+  dplyr::select(datetime, monthd, sal_fb_mix, temp_fb, pco2_fb, at_calc) %>% 
+  tidyr::drop_na() %>% 
+  dplyr::mutate(OmegaAragonite = seacarb::carb(
+    flag = 24, var1 = pco2_fb, var2 = at_calc*1e-6, S=sal_fb_mix, T=temp_fb, 
+    Patm=1, P=1.1, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$OmegaAragonite)
+#plot
+size_point <- 0.3 # size of data points
+alpha <- 1 #transparency
+size_labs <- 6 # font size labels
+
+ts_oa <- tmp %>%
+  ggplot(aes(x = datetime, y = OmegaAragonite), na.rm = TRUE) +
+  scale_x_datetime(breaks = date_breaks("1 year"), labels = date_format("%Y")) +
+  geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
+  labs(title="Aragonite saturation state (11 m)",x="", y=latex2exp::TeX("$\\Omega)$")) +
+  Mytheme(size_labs = size_labs)
+print(ts_oa)
+ggsave(filename = "figures/OmegaAragonite.png", plot = ts_oa, width = 15, height = 30, units = "cm")
+```
+
+### Save all
 

### 2022-08-16 awipev-CO2.Rmd
In progress: stratitifcation pCO2 and pCO2 normalized at 4°C

@@
 ## Stratification
+### Stratification salinity
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 print(sal_delta_plt)
-
+```
+### Stratification temperature
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 # we look at temperature all depths
@@
 print(temp_delta_plt)
+```
+
+### Stratification density
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 # we look at density at all depths
@@
 print(den_delta_plt)
+```
+### Stratification seafet pH
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 # we look at pHint_tot_sf at all depths
@@
         panel.grid.minor.y = element_blank())
-
-# we look at pCO2  at all depths
+```
+### Stratification pCO2
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
+# we look at pCO2 NOT normalized at 4°C at all depths
 # calculate pCO2 from pH and salinity-derived AT
@@
 
-# we look at pCO2 0 to 4 m vs more than 8 m
+# we look at pCO2 NOT normalized at 4°C 0 to 4 m vs more than 8 m
 tmp <- d_all %>%
@@
   dplyr::rename(median0_4m = "0-4",
-                median8_12m = "8-12") %>%   dplyr::mutate(pco2_sf_med_delta = median0_4m - median8_12m)
-kable(tmp_delta, digits = 3, caption = "Median seafet fCO2 with (median0_4m - median8_12m)")
+                median8_12m = "8-12") %>%   
+  dplyr::mutate(pco2_sf_med_delta = median0_4m - median8_12m)
+kable(tmp_delta, digits = 3, caption = "Median seafet pCO2 (median0_4m - median8_12m)")
 
@@
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "pCO2", x = "Depth (m)", y= "pHint_tot_sf") +
+  labs(title = "pCO2 at SeaFET temperature", x = "Depth (m)", y= "pCO2") +
   facet_wrap(vars(montht), scale = "free_y")
@@
   )
-pco2_delta_plt
+
+# we look at pCO2 normalized at 4°C at all depths
+# calculate pCO2 from pH and salinity-derived AT
+tmp <- d_all %>%
+  dplyr::select(datetime,
+                montht,
+                depth_group,
+                depth,
+                pHint_tot_sf,
+                sal_insitu_ctd,
+                temp_insitu_ctd) %>%
+  drop_na() %>%
+  dplyr::mutate(
+    at_sf = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
+    pco2_sf = seacarb::carb(
+      flag = 8,
+      var1 = pHint_tot_sf,
+      var2 = at_sf,
+      S = sal_insitu_ctd,
+      T = temp_insitu_ctd,
+      Patm = 1,
+      P = depth / 10,
+      Pt = 0,
+      Sit = 0,
+      k1k2 = "l",
+      kf = "dg",
+      ks = "d",
+      pHscale = "T",
+      b = "u74"
+    )$pCO2,
+    pco2_sf_4 = seacarb::pCO2insi(pCO2lab = pco2_sf, Tlab = temp_insitu_ctd, SST = 4)
+  ) %>% 
+  dplyr::select(datetime, pco2_sf_4)
+d_all <- left_join(d_all, tmp, by = "datetime")
+tmp <- d_all %>% 
+  dplyr::select(montht, pco2_sf_4, depth_group) %>%
+  tidyr::drop_na() %>% 
+  dplyr::filter(depth_group != "NA") %>% 
+  group_by(depth_group, montht)
+p <- tmp %>% 
+  ggplot(aes(x=as.factor(depth_group), y = pco2_sf_4)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "pco2_sf at 4°C vs depth", x = "Depth (m)", y= "fCO2 (uatm)") +
+  scale_x_discrete(labels = depth_labels) +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+summary(aov(tmp$pco2_sf_4 ~ tmp$depth_group * tmp$montht))
+
+# we look at pCO2 normalized at 4°C 0 to 4 m vs more than 8 m
+tmp <- d_all %>%
+  dplyr::select(montht, pco2_sf_4, depth_group) %>%
+  dplyr::mutate(depth_group2 = as.factor(
+    case_when(
+      depth_group == '0-2' | depth_group == '2-4' ~ '0-4',
+      depth_group == '>8' ~ '8-12'
+    )
+  )) %>%
+  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>%
+  dplyr::group_by(depth_group2, montht)
+summary(aov(tmp$pco2_sf_4 ~ tmp$depth_group2 * tmp$montht))
+
+tmp_delta <- tmp %>%
+  group_by(depth_group2, montht) %>%
+  dplyr::summarise(pco2_sf_4_med = median(pco2_sf_4, na.rm = TRUE)) %>%
+  tidyr::pivot_wider(names_from = depth_group2, values_from = pco2_sf_4_med) %>%
+  dplyr::rename(median0_4m = "0-4",
+                median8_12m = "8-12") %>%   
+  dplyr::mutate(pco2_sf_4_med_delta = median0_4m - median8_12m)
+kable(tmp_delta, digits = 3, caption = "Median seafet pCO2 at 4°C with (median0_4m - median8_12m)")
+
+p <- tidyr::drop_na(tmp) %>% 
+  ggplot(aes(x=as.factor(depth_group2), y = pco2_sf_4)) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  labs(title = "pCO2 normalized at 4°C", x = "Depth (m)", y= "pCO2") +
+  facet_wrap(vars(montht), scale = "free_y")
+print(p)
+
+pco2_4_delta_plt <- tmp_delta %>%
+  ggplot(aes(x = montht, y = pco2_sf_4_med_delta)) +
+  scale_x_discrete("Month", expand = c(0, 0)) +
+  scale_y_continuous(substitute("pCO"["2"]), limits = c(-45, 10)) +
+  geom_col(fill = "blue") +
+  geom_hline(yintercept = 0) +
+  annotate(
+    "text",
+    x = 2.5,
+    y = 5,
+    parse = TRUE,
+    label = "pCO['2 surface'] > pCO['2 deep']"
+  ) +
+  annotate(
+    "text",
+    x = 2.5,
+    y = -40,
+    parse = TRUE,
+    label = "pCO['2 surface'] < pCO['2 deep']"
+  ) +
+  Mytheme(size_labs = 12) +
+  theme(
+    panel.grid.major.x = element_blank(),
+    panel.grid.major.y = element_blank(),
+    panel.grid.minor.y = element_blank()
+  )
+
 # all deltas
@@
   geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
-  labs(title="Aragonite saturation state (11 m)",x="", y=latex2exp::TeX("$\\Omega)$")) +
+  labs(title="Aragonite saturation state (11 m)",x="", y=latex2exp::TeX("$\\Omega_{aragonite}$")) +
   Mytheme(size_labs = size_labs)
 print(ts_oa)
-ggsave(filename = "figures/OmegaAragonite.png", plot = ts_oa, width = 15, height = 30, units = "cm")
+ggsave(filename = "figures/OmegaAragonite.png", plot = ts_oa, width = 15, height = 10, units = "cm")
 ```

### 2022-08-17 awipev-CO2.Rmd
stratification pco2

@@
     )$pCO2
-  ) %>% 
-  dplyr::select(datetime, pco2_sf)
-d_all <- left_join(d_all, tmp, by = "datetime")
-tmp <- d_all %>% 
+  )
+tmp <- tmp %>% 
   dplyr::select(montht, pco2_sf, depth_group) %>%
@@
 # we look at pCO2 NOT normalized at 4°C 0 to 4 m vs more than 8 m
-tmp <- d_all %>%
+tmp <- tmp %>%
   dplyr::select(montht, pco2_sf, depth_group) %>%
@@
   scale_x_discrete("Month", expand = c(0, 0)) +
-  scale_y_continuous(substitute("pCO"["2"]), limits = c(-45, 10)) +
+  scale_y_continuous(limits = c(-45,10), expand = c(0, 0)) +
+  labs(y = latex2exp::TeX("$pCO_2$ at in situ temperature ($\\mu atm$)")) +
   geom_col(fill = "blue") +
@@
     "text",
-    x = 2.5,
-    y = 5,
+    x = 2.2,
+    y = 6,
     parse = TRUE,
-    label = "pCO['2 surface'] > pCO['2 deep']"
+    label = "pCO['2 surface']>pCO['2 deep']"
   ) +
@@
     "text",
-    x = 2.5,
+    x = 2,
     y = -40,
     parse = TRUE,
-    label = "pCO['2 surface'] < pCO['2 deep']"
+    label = "pCO['2 surface']<pCO['2 deep']"
   ) +
@@
   )
-
 # we look at pCO2 normalized at 4°C at all depths
@@
     pco2_sf_4 = seacarb::pCO2insi(pCO2lab = pco2_sf, Tlab = temp_insitu_ctd, SST = 4)
-  ) %>% 
-  dplyr::select(datetime, pco2_sf_4)
-d_all <- left_join(d_all, tmp, by = "datetime")
-tmp <- d_all %>% 
+  )
+tmp <- tmp %>% 
   dplyr::select(montht, pco2_sf_4, depth_group) %>%
@@
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "pco2_sf at 4°C vs depth", x = "Depth (m)", y= "fCO2 (uatm)") +
+  labs(title = "pco2_sf at 4°C vs depth", x = "Depth (m)", y= "pCO2 (uatm)") +
   scale_x_discrete(labels = depth_labels) +
@@
 # we look at pCO2 normalized at 4°C 0 to 4 m vs more than 8 m
-tmp <- d_all %>%
+tmp <- tmp %>%
   dplyr::select(montht, pco2_sf_4, depth_group) %>%
@@
   group_by(depth_group2, montht) %>%
-  dplyr::summarise(pco2_sf_4_med = median(pco2_sf_4, na.rm = TRUE)) %>%
-  tidyr::pivot_wider(names_from = depth_group2, values_from = pco2_sf_4_med) %>%
+  dplyr::summarise(pco2_sf_4_med = median(pco2_sf_4, na.rm = FALSE)) %>%
+  tidyr::pivot_wider(names_from = depth_group2, values_from = pco2_sf_4_med, values_fill = NA) %>%
   dplyr::rename(median0_4m = "0-4",
@@
   scale_x_discrete("Month", expand = c(0, 0)) +
-  scale_y_continuous(substitute("pCO"["2"]), limits = c(-45, 10)) +
+  scale_y_continuous(limits = c(-45,10), expand = c(0, 0)) +
+  labs(y = latex2exp::TeX("$pCO_2$ at 4°C ($\\mu atm$)")) +
   geom_col(fill = "blue") +
@@
     "text",
-    x = 2.5,
+    x = 2.,
     y = -40,
@@
   )
-
-# all deltas
-deltas_plt <- sal_delta_plt / temp_delta_plt / den_delta_plt / pco2_delta_plt
-deltas_plt <- deltas_plt + plot_annotation(tag_levels = 'a')
-print(deltas_plt)
-ggsave(filename = "figures/deltas.png", plot = deltas_plt, width = 15, height = 20, units = "cm")
+```
+
+# Stratification plots -------------------
+```{r, include=FALSE}
+# main deltas
+g <- sal_delta_plt / temp_delta_plt / den_delta_plt
+g <- g + plot_annotation(tag_levels = 'a')
+print(g)
+ggsave(filename = "figures/deltas.png", plot = g, width = 15, height = 20, units = "cm")
+# pCO2 deltas
+g <-  pco2_delta_plt / pco2_4_delta_plt
+g <- g + plot_annotation(tag_levels = 'a')
+print(g)
+ggsave(filename = "figures/deltas_pco2.png", plot = g, width = 15, height = 20, units = "cm")
 ```
@@
 ggsave(file="figures/fig_deconv_pCO2.png", fig_deconv_pCO2, width = 18, height = 20, units = "cm")
+```
+
+# Save all ----------------------------------------------------------------
+
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
+# d_hour is the real data set that is read at the beginning of the script
+# d_all comprises additional columns calculated in this script
+d_all$at <- ifelse(is.nan(d_all$at), NA, d_all$at) # replace all NaN by NA
+d_all$ct <- ifelse(is.nan(d_all$at), NA, d_all$ct) # replace all NaN by NA
+#d_all <- dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))
+
+# order columns
+d_all <- d_all %>% 
+  dplyr::select(order(colnames(d_all))) %>% 
+  dplyr::select(datetime, date, year, monthd, montht, everything())
+
+saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
+
+pangaea <- as_tibble(d_all) %>% 
+  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb_insi_temp, pco2_calc_fb_insi_temp, at_calc, pH_dur, pHint_tot_sf) %>%
+  dplyr::rename(`pressure [dbar]` = depth,
+                `s_insitu [unit]` = sal_insitu_ctd,
+                `s_fb [unit]` = sal_fb, 
+                `t_11m [°C]` = temp_insitu_11m,
+                `t_ctd [°C]` = temp_insitu_ctd, 
+                `t_fb [°C]` = temp_fb, 
+                `t_sf [°C]` = temp_sf, 
+                `at [umol kg-1]` = at, 
+                `at_calc [umol kg-1]` = at_calc,
+                `ct [umol kg-1]` = ct, 
+                `ph_s_sf_t_insi [total scale]` = ph_s_sf_temp_insi, 
+                `ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
+                `pco2 [uatm]` = pco2_fb_insi_temp,
+                `pco2_calc [uatm]` = pco2_calc_fb_insi_temp,
+                `pH_sf [total scale]` = pHint_tot_sf,
+                `pH_dur [total scale]` = pH_dur,
+                `pH_calc [total scale]` = ph_calc_fb
+                )
+saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
+write_csv(pangaea, file = paste0(path, "fb_data/pangaea.csv"))
+# Metadata Pangaea
+# pressure = pressure in situ (profiler)
+# s_insitu = salinity in situ (profiler)
+# s_fb = salinity (static at 11 m) 
+# t_11m = temperature in situ (static at 11 m)
+# t_ctd = temperature in situ (profiler)
+# t_fb = temperature (FerryBox)
+# t_sf = temperature SeaFET (profiler)
+# at = total alkalinity, discrete measurements (FerryBox)
+# at_calc = total alkalinity, calculated from salinity
+# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
+# ph_s_sf_t_insi = spectrophotometric pH in situ at in situ temperature (profiler)
+# ph_s_dur_t_fb = spectrophotometric pH in FerryBox at FerryBox temperature (FerryBox)
+# pco2 = pCO2 in Ferrybox expressed at in situ temperature (FerryBox)
+# pco2_calc = pCO2 in the FerryBox calculated from discrete measurements of AT and CT and expressed at in situ temperature
+# pH_sf = pH seaFET at in situ temperature (profiler)
+# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
+# ph_calc = pH at FerryBox temperature calculated from CT and AT in the FerryBox
 ```
@@
 OmegaAragonite is calculated using at_calc and pCO2
-```{r, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+```{r, fig.width=10, fig.height=10, echo=FALSE, message= FALSE, warning = FALSE}
 # we calculate it from at_calc and pCO2
@@
   geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
+  ylim(0, 3) +
   labs(title="Aragonite saturation state (11 m)",x="", y=latex2exp::TeX("$\\Omega_{aragonite}$")) +
@@
 ggsave(filename = "figures/OmegaAragonite.png", plot = ts_oa, width = 15, height = 10, units = "cm")
-```
-
-### Save all
-
-```{r, echo=FALSE, message= FALSE, warning=FALSE}
-# d_hour is the real data set that is read at the beginning of the script
-# d_all comprises additional columns calculated in this script
-d_all$at <- ifelse(is.nan(d_all$at), NA, d_all$at) # replace all NaN by NA
-d_all$ct <- ifelse(is.nan(d_all$at), NA, d_all$ct) # replace all NaN by NA
-#d_all <- dplyr::mutate(d_all, month = as.factor(month(x = datetime, label = TRUE)))
-
-# order columns
-d_all <- d_all %>% 
-  dplyr::select(order(colnames(d_all))) %>% 
-  dplyr::select(datetime, date, year, monthd, montht, everything())
-
-saveRDS(file= paste0(path, "fb_data/d_all.rds"), d_all)
-
-pangaea <- as_tibble(d_all) %>% 
-  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb_insi_temp, pco2_calc_fb_insi_temp, at_calc, pH_dur, pHint_tot_sf) %>%
-  dplyr::rename(`pressure [dbar]` = depth,
-                `s_insitu [unit]` = sal_insitu_ctd,
-                `s_fb [unit]` = sal_fb, 
-                `t_11m [°C]` = temp_insitu_11m,
-                `t_ctd [°C]` = temp_insitu_ctd, 
-                `t_fb [°C]` = temp_fb, 
-                `t_sf [°C]` = temp_sf, 
-                `at [umol kg-1]` = at, 
-                `at_calc [umol kg-1]` = at_calc,
-                `ct [umol kg-1]` = ct, 
-                `ph_s_sf_t_insi [total scale]` = ph_s_sf_temp_insi, 
-                `ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
-                `pco2 [uatm]` = pco2_fb_insi_temp,
-                `pco2_calc [uatm]` = pco2_calc_fb_insi_temp,
-                `pH_sf [total scale]` = pHint_tot_sf,
-                `pH_dur [total scale]` = pH_dur,
-                `pH_calc [total scale]` = ph_calc_fb
-                )
-saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
-write_csv(pangaea, file = paste0(path, "fb_data/pangaea.csv"))
-# Metadata Pangaea
-# pressure = pressure in situ (profiler)
-# s_insitu = salinity in situ (profiler)
-# s_fb = salinity (static at 11 m) 
-# t_11m = temperature in situ (static at 11 m)
-# t_ctd = temperature in situ (profiler)
-# t_fb = temperature (FerryBox)
-# t_sf = temperature SeaFET (profiler)
-# at = total alkalinity, discrete measurements (FerryBox)
-# at_calc = total alkalinity, calculated from salinity
-# ct = dissolved inorganic carbon, discrete measurements (FerryBox)
-# ph_s_sf_t_insi = spectrophotometric pH in situ at in situ temperature (profiler)
-# ph_s_dur_t_fb = spectrophotometric pH in FerryBox at FerryBox temperature (FerryBox)
-# pco2 = pCO2 in Ferrybox expressed at in situ temperature (FerryBox)
-# pco2_calc = pCO2 in the FerryBox calculated from discrete measurements of AT and CT and expressed at in situ temperature
-# pH_sf = pH seaFET at in situ temperature (profiler)
-# ph_dur = pH Durafet at FerryBox temperature (FerryBox)
-# ph_calc = pH at FerryBox temperature calculated from CT and AT in the FerryBox
 ```
@@
 g2 <- g2 + plot_annotation(tag_levels = 'A')
+g2
 ggsave(filename = "figures/ts_boxplots.png", plot = g2)
-#rm(list = ls(pattern = "ts_"), d_bp) #delete big ggplot objects and temp data
-#gc() #garbage collection
-```
-
-###Combined plot for paper
+
+```
+
+### Combined plot for paper
 
@@
 
-###Time series and boxplots for paper
-```{r }
+### Time series and boxplots for paper
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 g <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at) |

### 2022-08-18 awipev-CO2.Rmd
startification pCO2 final

@@
                 median8_12m = "8-12") %>%   
-  dplyr::mutate(pco2_sf_med_delta = median0_4m - median8_12m)
+  dplyr::mutate(pco2_sf_med_delta = median0_4m - median8_12m) %>% 
+  # this is to bring June back...
+  rbind(data.frame(montht="Jun", median8_12m = NA, median0_4m = NA, pco2_sf_med_delta = NA)) %>% 
+  dplyr::mutate(montht = factor(montht, levels = month.abb)) %>% 
+  dplyr::arrange(montht)
 kable(tmp_delta, digits = 3, caption = "Median seafet pCO2 (median0_4m - median8_12m)")
@@
   scale_x_discrete("Month", expand = c(0, 0)) +
-  scale_y_continuous(limits = c(-45,10), expand = c(0, 0)) +
+  scale_y_continuous(limits = c(-46,10), expand = c(0, 0)) +
   labs(y = latex2exp::TeX("$pCO_2$ at in situ temperature ($\\mu atm$)")) +
@@
     "text",
-    x = 2.2,
+    x = 10,
     y = 6,
@@
     "text",
-    x = 2,
+    x = 10,
     y = -40,
@@
                 median8_12m = "8-12") %>%   
-  dplyr::mutate(pco2_sf_4_med_delta = median0_4m - median8_12m)
+  dplyr::mutate(pco2_sf_4_med_delta = median0_4m - median8_12m) %>% 
+    # this is to bring June back... 
+  rbind(data.frame(montht="Jun", median8_12m = NA, median0_4m = NA, pco2_sf_4_med_delta = NA)) %>% 
+  dplyr::mutate(montht = factor(montht, levels = month.abb)) %>% 
+  dplyr::arrange(montht)
 kable(tmp_delta, digits = 3, caption = "Median seafet pCO2 at 4°C with (median0_4m - median8_12m)")
@@
   scale_x_discrete("Month", expand = c(0, 0)) +
-  scale_y_continuous(limits = c(-45,10), expand = c(0, 0)) +
+  scale_y_continuous(limits = c(-46,10), expand = c(0, 0)) +
   labs(y = latex2exp::TeX("$pCO_2$ at 4°C ($\\mu atm$)")) +
@@
     "text",
-    x = 2.,
+    x = 10,
     y = -40,

### 2022-08-22 awipev-CO2.Rmd
still on air-sea CO2 flux

--- 2022-08-17 awipev-CO2.Rmd
@@
       SST = temp_insitu_11m),
+    pco2_fb_ctd_temp = seacarb::pCO2insi(
+      pCO2lab = pco2_fb,
+      Tlab = temp_fb,
+      SST = temp_insitu_ctd),
     fco2_fb = seacarb::p2fCO2(
@@
   dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
-  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
-                                      depth_group == '>8' ~ '8-12'))) %>% 
+  dplyr::mutate(depth_group2 = as.factor(
+    case_when(
+      depth_group == '0-2' | depth_group == '2-4' ~ '0-4',
+      depth_group == '>8' ~ '8-12'
+    )
+  )) %>%
   dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>%
@@
 ```
+
 ### Stratification temperature
@@
   dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
-  dplyr::mutate(depth_group2 = as.factor(case_when(depth_group == '0-2' | depth_group == '2-4' ~ '0-4', 
-                                      depth_group == '>8' ~ '8-12'))) %>% 
+  dplyr::mutate(depth_group2 = as.factor(
+    case_when(
+      depth_group == '0-2' | depth_group == '2-4' ~ '0-4',
+      depth_group == '>8' ~ '8-12'
+    )
+  )) %>%
   dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>%
@@
   dplyr::mutate(
-    at_sf = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
-    pco2_sf = seacarb::carb(
+    at_remos = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
+    pco2_remos_ctd_temp = seacarb::carb(
       flag = 8,
       var1 = pHint_tot_sf,
-      var2 = at_sf,
+      var2 = at_remos,
       S = sal_insitu_ctd,
@@
   )
+# add at_remos and pco2_remos_ctd_temp to d_all
+d_all <-
+  dplyr::left_join(d_all, dplyr::select(tmp, datetime, at_remos, pco2_remos_ctd_temp), by = "datetime") %>%
+  dplyr::select(sort(current_vars()))
 tmp <- tmp %>% 
-  dplyr::select(montht, pco2_sf, depth_group) %>%
+  dplyr::select(montht, pco2_remos_ctd_temp, depth_group) %>%
   tidyr::drop_na() %>% 
@@
 p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth_group), y = pco2_sf)) +
+  ggplot(aes(x=as.factor(depth_group), y = pco2_remos_ctd_temp)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
 print(p)
-summary(aov(tmp$pco2_sf ~ tmp$depth_group * tmp$montht))
+summary(aov(tmp$pco2_remos_ctd_temp ~ tmp$depth_group * tmp$montht))
 
@@
 tmp <- tmp %>%
-  dplyr::select(montht, pco2_sf, depth_group) %>%
+  dplyr::select(montht, pco2_remos_ctd_temp, depth_group) %>%
   dplyr::mutate(depth_group2 = as.factor(
@@
   dplyr::group_by(depth_group2, montht)
-summary(aov(tmp$pco2_sf ~ tmp$depth_group2 * tmp$montht))
+summary(aov(tmp$pco2_remos_ctd_temp ~ tmp$depth_group2 * tmp$montht))
 
@@
   group_by(depth_group2, montht) %>%
-  dplyr::summarise(pco2_sf_med = median(pco2_sf, na.rm = TRUE)) %>%
-  tidyr::pivot_wider(names_from = depth_group2, values_from = pco2_sf_med) %>%
+  dplyr::summarise(pco2_remos_ctd_temp_med = median(pco2_remos_ctd_temp, na.rm = TRUE)) %>%
+  tidyr::pivot_wider(names_from = depth_group2, values_from = pco2_remos_ctd_temp_med) %>%
   dplyr::rename(median0_4m = "0-4",
                 median8_12m = "8-12") %>%
-  dplyr::mutate(pco2_sf_med_delta = median0_4m - median8_12m)
-kable(tmp_delta, digits = 3, caption = "Median seafet pCO2 (median0_4m - median8_12m)")
+  dplyr::mutate(pco2_remos_ctd_temp_med_delta = median0_4m - median8_12m) %>%
+  # this is to bring June back...
+  rbind(
+    data.frame(
+      montht = "Jun",
+      median8_12m = NA,
+      median0_4m = NA,
+      pco2_remos_ctd_temp_med_delta = NA
+    )
+  ) %>%
+  dplyr::mutate(montht = factor(montht, levels = month.abb)) %>%
+  dplyr::arrange(montht)
+kable(tmp_delta, digits = 3, caption = "Median REMOS pCO2 (median0_4m - median8_12m)")
 
 p <- tidyr::drop_na(tmp) %>% 
-  ggplot(aes(x=as.factor(depth_group2), y = pco2_sf)) +
+  ggplot(aes(x=as.factor(depth_group2), y = pco2_remos_ctd_temp)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
 pco2_delta_plt <- tmp_delta %>%
-  ggplot(aes(x = montht, y = pco2_sf_med_delta)) +
+  ggplot(aes(x = montht, y = pco2_remos_ctd_temp_med_delta)) +
   scale_x_discrete("Month", expand = c(0, 0)) +
-  scale_y_continuous(limits = c(-45,10), expand = c(0, 0)) +
+  scale_y_continuous(limits = c(-46,10), expand = c(0, 0)) +
   labs(y = latex2exp::TeX("$pCO_2$ at in situ temperature ($\\mu atm$)")) +
@@
                 depth,
-                pHint_tot_sf,
+                #pHint_tot_sf,
+                pco2_remos_ctd_temp,
                 sal_insitu_ctd,
@@
   drop_na() %>%
-  dplyr::mutate(
-    at_sf = (intercept_s_at + slope_s_at * sal_insitu_ctd) * 1e-6,
-    pco2_sf = seacarb::carb(
-      flag = 8,
-      var1 = pHint_tot_sf,
-      var2 = at_sf,
-      S = sal_insitu_ctd,
-      T = temp_insitu_ctd,
-      Patm = 1,
-      P = depth / 10,
-      Pt = 0,
-      Sit = 0,
-      k1k2 = "l",
-      kf = "dg",
-      ks = "d",
-      pHscale = "T",
-      b = "u74"
-    )$pCO2,
-    pco2_sf_4 = seacarb::pCO2insi(pCO2lab = pco2_sf, Tlab = temp_insitu_ctd, SST = 4)
-  )
+  dplyr::mutate(pco2_remos_4 = seacarb::pCO2insi(pCO2lab = pco2_remos_ctd_temp, Tlab = temp_insitu_ctd, SST = 4)
+  )
+# add pco2_remos_4 to d_all
+d_all <-
+  dplyr::left_join(d_all, dplyr::select(tmp, datetime, pco2_remos_4), by = "datetime") %>%
+  dplyr::select(sort(current_vars()))
+
 tmp <- tmp %>% 
-  dplyr::select(montht, pco2_sf_4, depth_group) %>%
+  dplyr::select(montht, pco2_remos_4, depth_group) %>%
   tidyr::drop_na() %>% 
@@
 p <- tmp %>% 
-  ggplot(aes(x=as.factor(depth_group), y = pco2_sf_4)) +
+  ggplot(aes(x=as.factor(depth_group), y = pco2_remos_4)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
-  labs(title = "pco2_sf at 4°C vs depth", x = "Depth (m)", y= "pCO2 (uatm)") +
+  labs(title = "pco2_remos at 4°C vs depth", x = "Depth (m)", y= "pCO2 (uatm)") +
   scale_x_discrete(labels = depth_labels) +
@@
 tmp <- tmp %>%
-  dplyr::select(montht, pco2_sf_4, depth_group) %>%
+  dplyr::select(montht, pco2_remos_4, depth_group) %>%
   dplyr::mutate(depth_group2 = as.factor(
@@
   dplyr::group_by(depth_group2, montht)
-summary(aov(tmp$pco2_sf_4 ~ tmp$depth_group2 * tmp$montht))
+summary(aov(tmp$pco2_remos_4 ~ tmp$depth_group2 * tmp$montht))
 
@@
   group_by(depth_group2, montht) %>%
-  dplyr::summarise(pco2_sf_4_med = median(pco2_sf_4, na.rm = FALSE)) %>%
-  tidyr::pivot_wider(names_from = depth_group2, values_from = pco2_sf_4_med, values_fill = NA) %>%
+  dplyr::summarise(pco2_remos_4_med = median(pco2_remos_4, na.rm = FALSE)) %>%
+  tidyr::pivot_wider(names_from = depth_group2,
+                     values_from = pco2_remos_4_med,
+                     values_fill = NA) %>%
   dplyr::rename(median0_4m = "0-4",
                 median8_12m = "8-12") %>%
-  dplyr::mutate(pco2_sf_4_med_delta = median0_4m - median8_12m)
-kable(tmp_delta, digits = 3, caption = "Median seafet pCO2 at 4°C with (median0_4m - median8_12m)")
+  dplyr::mutate(pco2_remos_4_med_delta = median0_4m - median8_12m) %>%
+  # this is to bring June back...
+  rbind(
+    data.frame(
+      montht = "Jun",
+      median8_12m = NA,
+      median0_4m = NA,
+      pco2_remos_4_med_delta = NA
+    )
+  ) %>% 
+  dplyr::mutate(montht = factor(montht, levels = month.abb)) %>% 
+  dplyr::arrange(montht)
+kable(tmp_delta, digits = 3, caption = "Median remos pCO2 at 4°C with (median0_4m - median8_12m)")
 
 p <- tidyr::drop_na(tmp) %>% 
-  ggplot(aes(x=as.factor(depth_group2), y = pco2_sf_4)) +
+  ggplot(aes(x=as.factor(depth_group2), y = pco2_remos_4)) +
   geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
@@
 pco2_4_delta_plt <- tmp_delta %>%
-  ggplot(aes(x = montht, y = pco2_sf_4_med_delta)) +
+  ggplot(aes(x = montht, y = pco2_remos_4_med_delta)) +
   scale_x_discrete("Month", expand = c(0, 0)) +
-  scale_y_continuous(limits = c(-45,10), expand = c(0, 0)) +
+  scale_y_continuous(limits = c(-46,10), expand = c(0, 0)) +
   labs(y = latex2exp::TeX("$pCO_2$ at 4°C ($\\mu atm$)")) +
@@
   group_by(season) %>%
-  dplyr::mutate(pco2_thermal = 
-                  mean(pco2_fb_insi_temp, na.rm = TRUE) * exp(0.0423 * (temp_insitu_11m - mean(temp_insitu_11m, na.rm = TRUE))),
-                  pco2_nonthermal = pco2_fb_insi_temp * exp(0.0423 * (mean(temp_insitu_11m, na.rm = TRUE) - temp_insitu_11m))) %>% 
-  dplyr::summarise(thermal = max(pco2_thermal, na.rm = TRUE) - min(pco2_thermal, na.rm = TRUE),
+  dplyr::mutate(
+    pco2_thermal =
+      mean(pco2_fb_insi_temp, na.rm = TRUE) * exp(0.0423 * (
+        temp_insitu_11m - mean(temp_insitu_11m, na.rm = TRUE)
+      )),
+    pco2_nonthermal = pco2_fb_insi_temp * exp(0.0423 * (
+      mean(temp_insitu_11m, na.rm = TRUE) - temp_insitu_11m
+    ))
+  ) %>%
+  dplyr::summarise(
+    thermal = max(pco2_thermal, na.rm = TRUE) - min(pco2_thermal, na.rm = TRUE),
     nonthermal = max(pco2_nonthermal, na.rm = TRUE) - min(pco2_nonthermal, na.rm = TRUE),
-                   thermal_nonthermal = thermal / nonthermal) %>% 
+    thermal_nonthermal = thermal / nonthermal
+  ) %>%
   ungroup()
@@
 
-```{r air-sea CO2, echo=FALSE, message= FALSE, warning=FALSE}
+## Comparison pCO2 ferrybox vs pCO2 REMOS
+pCO2 measured in FerryBox expressed at in situ temp vs pCO2 calculated from REMOS data (S, T, pH, salinity-AT) at 0-2 m only.
+
+```{r, echo = FALSE, message = FALSE, warning = FALSE}
+pco2_fb_remos <- d_all %>% 
+  dplyr::select(depth, monthd, pco2_fb_ctd_temp, pco2_remos_ctd_temp) %>% 
+  dplyr::filter(depth < 2) %>% 
+  drop_na() %>% 
+  ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = monthd)) +
+  geom_point(col="blue", size = 0.5) +
+  #geom_text() +
+  xlim(180, 420) + ylim(180, 420) +
+  labs(title = "pCO2 at ctd temperature",
+       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\muatm)$"),
+       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-2 m\\phantom{x}($\\muatm)$"))  +
+  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
+  ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label))) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
+  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
+  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
+pco2_fb_remos
+ggsave(filename = "figures/pco2_fb_remos.png", plot = pco2_fb_remos, width = 25, height = 25, units = "cm")
+```
+
+```{r air-sea CO2 with measured data, echo=FALSE, message= FALSE, warning=FALSE}
 # calculations as described by de Carlo et al. (2013)
@@
                 k = k600 * (Sc/600)^-0.5, #cm/h
-                alp = seacarb::K0(S=sal_fb_mix,T=temp_insitu_11m,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
-                alp = alp * (seacarb::rho(S = sal_fb_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
-                f_air_sea = k * alp * delta_pco2 # mmol/(m2 h)
+                alpha = seacarb::K0(S=sal_fb_mix,T=temp_insitu_11m,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
+                alpha = alpha * (seacarb::rho(S = sal_fb_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
+                f_air_sea = k * alpha * delta_pco2 # mmol/(m2 h)
                 )
@@
 ggsave(filename = "figures/air-sea_CO2_flux.png", plot = p, width = 20, units = "cm")
-#p <- cowplot::plot_grid(p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m, ncol = 1)
-#pngfile <- "figures/air-sea_CO2_flux.png"
-# ggsave(
-#   pngfile, 
-#   p, 
-#   device = agg_png, 
-#   width = 6.6, height = 10, units = "cm", res = 300,
-#   scaling = 0.4
-# )
 knitr::include_graphics("figures/air-sea_CO2_flux.png")

### 2022-08-22 awipev-CO2.Rmd
more air-sea CO2 flux

@@
   dplyr::select(depth, monthd, pco2_fb_ctd_temp, pco2_remos_ctd_temp) %>% 
-  dplyr::filter(depth < 2) %>% 
+  dplyr::filter(depth < 4) %>% 
   drop_na() %>% 
+  dpl
   ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = monthd)) +

### 2022-08-22 awipev-CO2.Rmd
Updated air-sea CO2 flux

--- 2022-08-22 awipev-CO2.Rmd
@@
 print(p)
-summary(aov(tmp$pco2_sf_4 ~ tmp$depth_group * tmp$montht))
+summary(aov(tmp$pco2_remos_4 ~ tmp$depth_group * tmp$montht))
 
@@
 ## Atmospheric CO2 Zeppelin
-```{r atmospheric CO2 Zeppelin, echo=FALSE, message= FALSE, warning=FALSE}
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 # downloaded 2020-08-19 from https://gaw.kishou.go.jp/search/file/0054-6001-1001-01-01-9999
@@
 ```{r, echo = FALSE, message = FALSE, warning = FALSE}
-pco2_fb_remos <- d_all %>% 
+p_pco2_fb_remos <- d_all %>% 
   dplyr::select(depth, monthd, pco2_fb_ctd_temp, pco2_remos_ctd_temp) %>% 
-  dplyr::filter(depth < 2) %>% 
+  dplyr::filter(depth < 4) %>% 
   drop_na() %>% 
@@
   #geom_text() +
-  xlim(180, 420) + ylim(180, 420) +
+  xlim(250, 400) + ylim(270, 360) +
   labs(title = "pCO2 at ctd temperature",
-       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\muatm)$"),
-       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-2 m\\phantom{x}($\\muatm)$"))  +
+       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$"),
+       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-4 m\\phantom{x}($\\mu atm)$"))  +
   ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
-  ggpmisc::stat_ma_eq(method = "lmodel2:MA", aes(label = after_stat(eq.label))) +
+  ggpmisc::stat_ma_eq(mapping = use_label(c("R2", "eq"))) +
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
@@
   coord_fixed(ratio = 1, expand = TRUE, clip = "on")
-pco2_fb_remos
-ggsave(filename = "figures/pco2_fb_remos.png", plot = pco2_fb_remos, width = 25, height = 25, units = "cm")
-```
+p_pco2_fb_remos
+ggsave(filename = "figures/pco2_fb_remos.png", plot = p_pco2_fb_remos, width = 25, height = 25, units = "cm")
+
+# Same thing but monthly median; code different because one wants to calculate delta
+tmp <- d_all %>% 
+  dplyr::select(depth, montht, pco2_fb_ctd_temp, pco2_remos_ctd_temp) %>% 
+  dplyr::filter(depth < 4) %>% 
+  drop_na() %>% 
+  dplyr::group_by(montht) %>% 
+  dplyr::summarise(
+    pco2_fb_ctd_temp = median(pco2_fb_ctd_temp, na.rm = TRUE),
+    pco2_remos_ctd_temp = median(pco2_remos_ctd_temp, na.rm = TRUE), 
+    delta_pco2_fb_remos_monthly = pco2_remos_ctd_temp - pco2_fb_ctd_temp
+  )
+p_pco2_fb_remos_month <- tmp %>% 
+  ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = montht)) +
+  geom_point(col="blue", size = 0.5) +
+  #geom_text() +
+  xlim(250, 400) + ylim(250, 400) +
+  labs(title = "pCO2 at ctd temperature",
+       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$"),
+       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-4 m\\phantom{x}($\\mu atm)$"))  +
+  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
+  ggpmisc::stat_ma_eq(mapping = use_label(c("R2", "eq"))) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
+  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
+  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
+p_pco2_fb_remos_month
+ggsave(filename = "figures/pco2_fb_remos_monthly.png", plot = p_pco2_fb_remos_month, width = 25, height = 25, units = "cm")
+
+# combine
+g <- p_pco2_fb_remos / p_pco2_fb_remos_month
+g <- g + patchwork::plot_annotation(tag_levels = 'A')
+ggsave(filename = "figures/pco2_compare.png", plot = g)
+g
+```
+The relationship between pCO2 between 0 and 4 m on the REMOS (estimated from pH and S-derived AT) and pCO2 measured at 11 m (both pCO2 at CTD temperature) is much nicer using monthly median values (b) than using all data (a).
+The mean and median difference between the two pCO2s are `r round(summary(tmp$delta_pco2_fb_remos_monthly), digits=0)`
 
@@
 d_all <- d_all %>%
-  dplyr::mutate(delta_pco2 = pco2_fb - co2_air, # ppm
+  dplyr::mutate(delta_pco2 = pco2_fb_ctd_temp - co2_air, # ppm
                 k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
-                Sc = 2073.1 - (125.62*temp_insitu_11m) + (3.6276*temp_insitu_11m^2) -
+                Sc = 2073.1 - (125.62*temp_insitu_ctd) + (3.6276*temp_insitu_ctd^2) -
                   (0.043219*temp_insitu_ctd^3), #dimensionless
                 k = k600 * (Sc/600)^-0.5, #cm/h
-                alpha = seacarb::K0(S=sal_fb_mix,T=temp_insitu_11m,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
-                alpha = alpha * (seacarb::rho(S = sal_fb_mix, T = temp_insitu_11m, P = 0)/1000), #mol/(l/atm)
+                alpha = seacarb::K0(S=sal_insitu_ctd,T=temp_insitu_ctd,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
+                alpha = alpha * (seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0)/1000), #mol/(l/atm)
                 f_air_sea = k * alpha * delta_pco2 # mmol/(m2 h)
@@
 #air_sea_month
-p_f_air_sea_m <- ggplot(data = air_sea_month) +
+p_f_air_sea_month <- ggplot(data = air_sea_month) +
   geom_point(aes(x = montht, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
   #scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
-  #lims(y = c(-30, 0)) +
+  lims(y = c(-30, 0)) +
   labs(title = "Air-sea CO2 flux (per month)", x = "Month", y = "CO2 (mmol/(m2 month))") +
   Mytheme(size_labs = 8)
-p_f_air_sea_m
-ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_m, width = 20, units = "cm")
-
-p <- p_f_air_sea / p_f_air_sea_d / p_f_air_sea_m
+p_f_air_sea_month
+ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_month, width = 20, units = "cm")
+
+p <- p_f_air_sea / p_f_air_sea_d / p_f_air_sea_month
 ggsave(filename = "figures/air-sea_CO2_flux.png", plot = p, width = 20, units = "cm")
@@
 
+```{r air-sea CO2 with corrected data, echo=FALSE, message= FALSE, warning=FALSE}
+# Same as above but we correct pCO2 by adding 17 uatm as we show above that pCO2 at 11 m
+# underestimates pCO2 at 0-4m (hence overestimates CO2 uptake)
+# round(summary(tmp$delta_pco2_fb_remos_monthly))[[4]]
+d_all <- d_all %>%
+  dplyr::mutate(delta_pco2_corr = (pco2_fb_ctd_temp + 17) - co2_air, # ppm
+                k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
+                Sc = 2073.1 - (125.62*temp_insitu_ctd) + (3.6276*temp_insitu_ctd^2) -
+                  (0.043219*temp_insitu_ctd^3), #dimensionless
+                k = k600 * (Sc/600)^-0.5, #cm/h
+                alpha = seacarb::K0(S=sal_insitu_ctd,T=temp_insitu_ctd,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
+                alpha = alpha * (seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0)/1000), #mol/(l/atm)
+                f_air_sea_corr = k * alpha * delta_pco2_corr # mmol/(m2 h)
+                )
+
+# p_f_air_sea <- ggplot(data = d_all) +
+#   geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
+#   labs(title = "Air-sea CO2 flux (all data)", x = "Time", y = "CO2 (mmol/(m2 h))") +
+#   Mytheme(size_labs = 8)
+# p_f_air_sea
+# ggsave(filename = "figures/p_f_air_sea.png", plot = p_f_air_sea, width = 20, units = "cm")
+
+# air_sea_day_d <- d_all %>%
+#   dplyr::select(datetime, f_air_sea_corr) %>%
+#   dplyr::group_by(lubridate::yday(datetime)) %>%
+#   dplyr::summarise(f_air_sea_corr = 24 * mean(f_air_sea_corr, na.rm = TRUE)/1000) %>% #mol/(m2 d)
+#   ungroup() %>%
+#   dplyr::rename(day = 1)
+
+# p_f_air_sea_d <- ggplot(data = air_sea_day) +
+#   geom_point(aes(x = day, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
+#   labs(title = "Air-sea CO2 flux (per day)", x = "Julian day", y = "CO2 (mmol/(m2 d))") +
+#   Mytheme(size_labs = 8)
+# p_f_air_sea_d
+# ggsave(filename = "figures/f_air_sea_d.png", plot = p_f_air_sea_d, width = 20, units = "cm")
+# 
+air_sea_corr_month <- d_all %>%
+  dplyr::select(monthd, f_air_sea_corr) %>%
+  dplyr::group_by(monthd) %>%
+  dplyr::summarise(f_air_sea_corr = 24 * mean(f_air_sea_corr, na.rm = TRUE)/1000) %>% #mol/(m2 d)
+  ungroup() %>%
+  dplyr::mutate(f_air_sea_corr = days_in_month(monthd) * f_air_sea_corr) %>% 
+  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
+#air_sea_month
+p_f_air_sea_corr_month <- ggplot(data = air_sea_corr_month) +
+  geom_point(aes(x = montht, y = f_air_sea_corr), col = "blue", size = 2, na.rm = TRUE) +
+  #scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
+  lims(y = c(-30, 0)) +
+  labs(title = "Air-sea CO2 flux (per month)", x = "Month", y = "CO2 (mmol/(m2 month))") +
+  Mytheme(size_labs = 8)
+p_f_air_sea_corr_month
+ggsave(filename = "figures/f_air_sea_corr_month.png", plot = p_f_air_sea_corr_month, width = 20, units = "cm")
+# combine without and with correction
+p <- p_f_air_sea_month / p_f_air_sea_corr_month
+ggsave(filename = "figures/air-sea_CO2_flux_comp.png", plot = p, width = 20, units = "cm")
+knitr::include_graphics("figures/air-sea_CO2_flux_comp.png")
+#rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
+```
+
 The annual air-sea CO2 flux is
-`r round(sum(air_sea_month$f_air_sea), digits = 0)` mol/(m2 year).
+`r round(sum(air_sea_month$f_air_sea), digits = 0)` and `r round(sum(air_sea_corr_month$f_air_sea_corr), digits = 0)` mol/(m2 year) without and with correction, respectively.
 

### 2022-08-23 awipev-CO2.Rmd
reorganizing script and html

@@
 
-## Atmospheric CO2 Zeppelin
+### Atmospheric CO2 Zeppelin
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 ```
-
-```{r meteo data, echo=FALSE, message= FALSE, warning=FALSE}
+### Wind data
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 #[1] "Year"               "Month"              "Day"                "Hour"              
@@
 
-## Comparison pCO2 ferrybox vs pCO2 REMOS
+### Comparison pCO2 ferrybox vs pCO2 REMOS
 pCO2 measured in FerryBox expressed at in situ temp vs pCO2 calculated from REMOS data (S, T, pH, salinity-AT) at 0-2 m only.
@@
   coord_fixed(ratio = 1, expand = TRUE, clip = "on")
-p_pco2_fb_remos
+#p_pco2_fb_remos
 ggsave(filename = "figures/pco2_fb_remos.png", plot = p_pco2_fb_remos, width = 25, height = 25, units = "cm")
@@
   coord_fixed(ratio = 1, expand = TRUE, clip = "on")
-p_pco2_fb_remos_month
+#p_pco2_fb_remos_month
 ggsave(filename = "figures/pco2_fb_remos_monthly.png", plot = p_pco2_fb_remos_month, width = 25, height = 25, units = "cm")
@@
 The relationship between pCO2 between 0 and 4 m on the REMOS (estimated from pH and S-derived AT) and pCO2 measured at 11 m (both pCO2 at CTD temperature) is much nicer using monthly median values (b) than using all data (a).
-The mean and median difference between the two pCO2s are `r round(summary(tmp$delta_pco2_fb_remos_monthly), digits=0)`
-
-```{r air-sea CO2 with measured data, echo=FALSE, message= FALSE, warning=FALSE}
+The mean and median difference between the two pCO2s are
+
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
+knitr::kable(summary(tmp$delta_pco2_fb_remos_monthly))
+```
+
+### Calculation of fluxes
+```{r With Contros data, echo=FALSE, message= FALSE, warning=FALSE}
 # calculations as described by de Carlo et al. (2013)
@@
   Mytheme(size_labs = 8)
-p_f_air_sea
+#p_f_air_sea
 ggsave(filename = "figures/p_f_air_sea.png", plot = p_f_air_sea, width = 20, units = "cm")
@@
   Mytheme(size_labs = 8)
-p_f_air_sea_d
+#p_f_air_sea_d
 ggsave(filename = "figures/f_air_sea_d.png", plot = p_f_air_sea_d, width = 20, units = "cm")
@@
   Mytheme(size_labs = 8)
-p_f_air_sea_month
+#p_f_air_sea_month
 ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_month, width = 20, units = "cm")
@@
 
-```{r air-sea CO2 with corrected data, echo=FALSE, message= FALSE, warning=FALSE}
+```{r With in situ simulation, echo=FALSE, message= FALSE, warning=FALSE}
 # Same as above but we correct pCO2 by adding 17 uatm as we show above that pCO2 at 11 m
@@
   Mytheme(size_labs = 8)
-p_f_air_sea_corr_month
+#p_f_air_sea_corr_month
 ggsave(filename = "figures/f_air_sea_corr_month.png", plot = p_f_air_sea_corr_month, width = 20, units = "cm")

### 2022-08-25 awipev-CO2.Rmd
air-sea fluxes final

@@
 data gaps are encountered, they are filled with bottom salinity data
-from ctd (> 8 m). New column "sal_fb_mix" is created and is the one used in
-ESSD paper.
+from ctd (\> 8 m). New column "sal_fb_mix" is created and is the one
+used in ESSD paper.
 
 -   1 SBE45 inside the Ferrybox (sal_fb)
--   5 CTD > 8 m depth (sal_insitu_ctd)
+-   5 CTD \> 8 m depth (sal_insitu_ctd)
 
@@
 ### **Depth profile**
+
 This is done later.
@@
 ### **Comparison salinity FerryBox vs Salinity CTD REMOS 10 m**
+
 ```{r, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
@@
 situ at 11 m depth is taken in consideration. If data gaps are
-encountered, they are filled with bottom temperature data from ctd (> 8
-m). New column "temp_insitu_11m_mix" is created. For the moment, no gaps are
-encountered and temp_insitu_11m_mix = temp_insitu_11m.
+encountered, they are filled with bottom temperature data from ctd (\> 8
+m). New column "temp_insitu_11m_mix" is created. For the moment, no gaps
+are encountered and temp_insitu_11m_mix = temp_insitu_11m.
 
@@
 ### **Temperature Ferrybox vs Temperature in situ 11 m**
+
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 
-### **Discrete total alkalinity vs salinity **
+### **Discrete total alkalinity vs salinity**
 
@@
 salinity is very good with an r2 of
-`r round(reg$fit$rsquare, digits = 2)` (`r N = reg$fit$n`). Need to compare with other relationships from the literature.
+`r round(reg$fit$rsquare, digits = 2)` (`r N = reg$fit$n`). Need to
+compare with other relationships from the literature.
 
 #### **Is there a seasonal change in the AT vs S relationship**
+
 ```{r, eval=TRUE, echo=FALSE, warning=FALSE, message=FALSE, out.width="100%", fig.align="center"}
@@
 
-Splitting the data below and above salinity 34.5, as done by Nondal et al.
-(2009), does not prove useful (data not shown).
-It degrades r2 (0.74 and 0.3 vs 0.81), degrades rmse or marginally improves the rmse (19 and 13.6 vs 16.8).
+Splitting the data below and above salinity 34.5, as done by Nondal et
+al. (2009), does not prove useful (data not shown). It degrades r2 (0.74
+and 0.3 vs 0.81), degrades rmse or marginally improves the rmse (19 and
+13.6 vs 16.8).
 
@@
 
-30 min warm up --> (3 min Zeroing + 15 min Flushing + 702 minutes
-Measuring) --> (3 + 15 + 702)...
+30 min warm up --\> (3 min Zeroing + 15 min Flushing + 702 minutes
+Measuring) --\> (3 + 15 + 702)...
 
@@
 `r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence
-interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)`  (`r N = reg$fit$n`)`.
+interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)`
+(`r N = reg$fit$n`)\`.
 
@@
 ```
-Offset between calibrated seaFET data and pH spectro.
-The offset must be between -0.2 and 0.2 pH units.
-"differences between calibrated sensor pH values and values obtained from discrete, check samples can be expected to be as small as 0.02 pH units, and perhaps less." (McLaughlin et al.
+
+Offset between calibrated seaFET data and pH spectro. The offset must be
+between -0.2 and 0.2 pH units. "differences between calibrated sensor pH
+values and values obtained from discrete, check samples can be expected
+to be as small as 0.02 pH units, and perhaps less." (McLaughlin et al.
 2017).
 
-Initially (before 2022-08-09), there was 2 outliers on 2019-07-12 and 2018-09-11.
-On 2022-08-09, code was added above to put a no good qf (3) in order to eliminate those two outliers.
-Now we are fine.
-The average offset is `r round(average_offset, digits = 4)`.
-It considerably improve the plot "pH spectro vs pH seafet (at in situ temperature)".
+Initially (before 2022-08-09), there was 2 outliers on 2019-07-12 and
+2018-09-11. On 2022-08-09, code was added above to put a no good qf (3)
+in order to eliminate those two outliers. Now we are fine. The average
+offset is `r round(average_offset, digits = 4)`. It considerably improve
+the plot "pH spectro vs pH seafet (at in situ temperature)".
 
@@
 
-pH INT - pH EXT was plotted here.
-From now on, one uses seaFET pH from the internal electrode calibrated with spec pH and seaFET data when the REMOS was below 8 m (pHint_tot_sf_10m).
-This unique pH variable is called pHint_tot_sf.
-All other pH variables are cleaned up.
-We also calculate pHint_tot_sf at 4°C: pHint_tot_sf_temp_4.
+pH INT - pH EXT was plotted here. From now on, one uses seaFET pH from
+the internal electrode calibrated with spec pH and seaFET data when the
+REMOS was below 8 m (pHint_tot_sf_10m). This unique pH variable is
+called pHint_tot_sf. All other pH variables are cleaned up. We also
+calculate pHint_tot_sf at 4°C: pHint_tot_sf_temp_4.
 
@@
 <!-- **Conclusion**: The range is significantly larger during some months -->
+
 <!-- when the data deeper than 8 m are considered. Also, pH is sometimes -->
+
 <!-- higher at the surface, at other times it is higher on the bottom (June). -->
+
 <!-- No data are available at 1 m (actually 0 to 2 m). So, to compare surface -->
+
 <!-- and bottom, I combine 1 and 3 m (0 to 4 m) and 9 m (below 8 m). -->
@@
 <!-- Depth and month of the year have a statistically significant effect on -->
+
 <!-- pH. The interaction is also significant, indicating that the effect of -->
+
 <!-- depth differs depending on the month. -->
@@
 <!-- -   To compare with pCO2/pCO2 measured in the Ferrybox seems therefore -->
+
 <!--     better to stick with pH_10m, that is at depths deeper than 8 m. -->
+
 <!-- -   pCO2 would have the same behaviour as pH. For air-sea CO2 fluxes, -->
+
 <!--     one should use data from 0 to 4 m. -->
@@
 ```
+
 ## Range per month
@@
 
-### **seaFET vs durafet pHs at 4°C (all > 8 m)**
+### **seaFET vs durafet pHs at 4°C (all \> 8 m)**
 
@@
 ### **Spectro vs durafet**
+
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 ### **Spectro vs seafet**
+
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 ```
-The relationship between spectrophotometric pH and SeaFET pH) and 
-(blue line) is relatively good The slope is
+
+The relationship between spectrophotometric pH and SeaFET pH) and (blue
+line) is relatively good The slope is
 `r signif(reg$fit$regression.results[2,3], 3)`) and its 95% confidence
-interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)`  (`r N = reg$fit$n`)`.
+interval does include 1; r2 is `r round(reg$fit$rsquare, digits=2)`
+(`r N = reg$fit$n`)\`.
 
 ### **Spectro vs calculated AT-CT**
+
 ```{r, eval=FALSE, echo=FALSE, message= FALSE, warning=FALSE}
@@
 ```
+
 `r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis using all pCO2 data.", format = "simple")`
@@
     average; ; median is `r round(diff_ls_quant[3, 2], digits = 3)`)
-    compared with the uncertainty calculated with seacarb
-    (see above; `r round(errors[1, 7], digits = 3)`). In general, pH is
-    higher with Sulpis than with Lueker.
+    compared with the uncertainty calculated with seacarb (see above;
+    `r round(errors[1, 7], digits = 3)`). In general, pH is higher with
+    Sulpis than with Lueker.
 
@@
 general, all formulations overestimate spectrophotometric pH. pH
-calculated using the formulation of Lueker et al. (2018) is
-closer to measured pH, with a mean difference of
+calculated using the formulation of Lueker et al. (2018) is closer to
+measured pH, with a mean difference of
 `r round(diff_table_pco2_at[4, 2], digits=3)` pH units. This difference
@@
 times larger than the uncertainty for pH calculated from pCO2 and AT
-according to seacarb (see above; `r round(errors_pco2_at$pH, digits=4)`).
+according to seacarb (see above;
+`r round(errors_pco2_at$pH, digits=4)`).
 
@@
 
-The discrete values of AT, CT, salinity and temperature in the
-FerryBox were used to calculate pH using the formulations for K1 and K2
-of Lueker et al. (2000) and Sulpis et al. (2020). The differences
-induced by the choice of the carbonic acid constants are:
+The discrete values of AT, CT, salinity and temperature in the FerryBox
+were used to calculate pH using the formulations for K1 and K2 of Lueker
+et al. (2000) and Sulpis et al. (2020). The differences induced by the
+choice of the carbonic acid constants are:
 
@@
     compared with the uncertainty calculated with seacarb
-    (`r round(errors[1, 7], digits = 3)`). In general, pH is
-    higher with Sulpis than with Lueker.
+    (`r round(errors[1, 7], digits = 3)`). In general, pH is higher with
+    Sulpis than with Lueker.
 
@@
 ## Stratification
+
 ### Stratification salinity
+
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 ### Stratification temperature
+
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 ### Stratification density
+
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 ```
+
 ### Stratification seafet pH
+
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 ```
+
 ### Stratification pCO2
+
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 
-# Stratification plots -------------------
+---- Stratification plots -------------------
+
 ```{r, include=FALSE}
@@
 
-**Conclusion for pH**: The range is significantly larger during some months
-when the data deeper than 8 m are considered. Also, pH is sometimes
-higher at the surface, at other times it is higher on the bottom (June).
-No data are available at 1 m (actually 0 to 2 m). So, to compare surface
-and bottom, I combine 1 and 3 m (0 to 4 m) and 9 m (below 8 m).
+**Conclusion for pH**: The range is significantly larger during some
+months when the data deeper than 8 m are considered. Also, pH is
+sometimes higher at the surface, at other times it is higher on the
+bottom (June). No data are available at 1 m (actually 0 to 2 m). So, to
+compare surface and bottom, I combine 1 and 3 m (0 to 4 m) and 9 m
+(below 8 m).
 
@@
 
-```{r Takahashi thermal vs non-thermal, include=FALSE}
+```{r, include=FALSE}
 # According to Takahashi et al. (2002) and McCutcheon et al. (2021)
@@
 
-```{r pCO2 changes due to changes in T, S, AT and CT, include=FALSE}
+pCO2 changes due to changes in T, S, AT and CT
+
+```{r, include=FALSE}
 # First we prepare data. CT is needed for deconvolution
@@
 
-# Save all ----------------------------------------------------------------
-
-```{r, echo=FALSE, message= FALSE, warning=FALSE}
+Save all ----
+
+```{r save all, echo=FALSE, message= FALSE, warning=FALSE}
 # d_hour is the real data set that is read at the beginning of the script
@@
 
-Let's look at the stratification tab above (salinity, temperature, density and fCO2): fCO2 is generally higher in the bottom layer than in the surface layer (note that no data is available in May, June and July).
-Which means that the air-sea CO2 fluxes calculated with pCO2 at 11 m are overestimated.
+Let's look at the stratification tab above (salinity, temperature,
+density and fCO2): fCO2 is generally higher in the bottom layer than in
+the surface layer (note that no data is available in May, June and
+July). Which means that the air-sea CO2 fluxes calculated with pCO2 at
+11 m are overestimated.
 
 ### Atmospheric CO2 Zeppelin
+
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 ```
+
 ### Wind data
+
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 ### Comparison pCO2 ferrybox vs pCO2 REMOS
-pCO2 measured in FerryBox expressed at in situ temp vs pCO2 calculated from REMOS data (S, T, pH, salinity-AT) at 0-2 m only.
+
+pCO2 measured in FerryBox expressed at in situ temp vs pCO2 calculated
+from REMOS data (S, T, pH, salinity-AT) at 0-2 m only.
 
@@
 ```
-The relationship between pCO2 between 0 and 4 m on the REMOS (estimated from pH and S-derived AT) and pCO2 measured at 11 m (both pCO2 at CTD temperature) is much nicer using monthly median values (b) than using all data (a).
-The mean and median difference between the two pCO2s are
-
-```{r, echo=FALSE, message= FALSE, warning=FALSE}
-knitr::kable(summary(tmp$delta_pco2_fb_remos_monthly))
-```
+
+The relationship between pCO2 [0-4 m] on the REMOS (estimated from pH
+and S-derived AT) and pCO2 measured at 11 m (both pCO2 at CTD
+temperature) is much nicer using monthly median values (b) than using
+all data (a). The mean and median difference between the two pCO2s are
+`r round(median(tmp$delta_pco2_fb_remos_monthly, na.rm = TRUE), digits=1)`
+and
+`r round(mean(tmp$delta_pco2_fb_remos_monthly, na.rm = TRUE), digits=1)`.
 
 ### Calculation of fluxes
+
 ```{r With Contros data, echo=FALSE, message= FALSE, warning=FALSE}
@@
 The annual air-sea CO2 flux is
-`r round(sum(air_sea_month$f_air_sea), digits = 0)` and `r round(sum(air_sea_corr_month$f_air_sea_corr), digits = 0)` mol/(m2 year) without and with correction, respectively.
+`r round(sum(air_sea_month$f_air_sea), digits = 0)` and
+`r round(sum(air_sea_corr_month$f_air_sea_corr), digits = 0)` mol/(m2
+year) without and with correction, respectively.
 
 ## Miscellaneous
+
 ### OmegaAragonite
+
 OmegaAragonite is calculated using at_calc and pCO2
+
 ```{r, fig.width=10, fig.height=10, echo=FALSE, message= FALSE, warning = FALSE}
@@
 ### Time series and boxplots for paper
+
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
 
--   sal_fb_mix: when ferrybox data (sal_fb) are missing, they are replaced
-    by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_10m)
-
--   sal_fb_mix_interp: interpolated salinity sal_fb_mix. It is used to have as
-    many spec pH to display (some are during missing data)
-
--   temp_insitu_11m_mix: when data of in situ temperature at 11 m (temp_insitu_11m)
-    are missing, they are replaced by data from the profiling ctd for
-    depths > 8 m
-
--   temp_insitu_11m_mix_interp: interpolated temperature temp_insitu_11m_mix. It is used to
+-   sal_fb_mix: when ferrybox data (sal_fb) are missing, they are
+    replaced by data from the profiling ctd for depths \> 8 m
+    (sal_insitu_ctd_10m)
+
+-   sal_fb_mix_interp: interpolated salinity sal_fb_mix. It is used to
     have as many spec pH to display (some are during missing data)
 
--   sal_insitu_ctd_mix: when CTD salinity data from the REMOS are missing, they are replaced by data from sal_fb_mix (hence at FerryBox from 11 m and REMOS below 8 m).
-This is not ideal because differences of up to 1 salinity unit occur in the water column.
-But needed as there are many missing REMOS data.
-
--   pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb + sal_fb_mix
+-   temp_insitu_11m_mix: when data of in situ temperature at 11 m
+    (temp_insitu_11m) are missing, they are replaced by data from the
+    profiling ctd for depths \> 8 m
+
+-   temp_insitu_11m_mix_interp: interpolated temperature
+    temp_insitu_11m_mix. It is used to have as many spec pH to display
+    (some are during missing data)
+
+-   sal_insitu_ctd_mix: when CTD salinity data from the REMOS are
+    missing, they are replaced by data from sal_fb_mix (hence at
+    FerryBox from 11 m and REMOS below 8 m). This is not ideal because
+    differences of up to 1 salinity unit occur in the water column. But
+    needed as there are many missing REMOS data.
+
+-   pco2_calc_fb: pco2 calc from AT/CT ferrybox = carb avec temp_fb +
+    sal_fb_mix
 
@@
     -   00 *//1* \* \* cd \$HOME; USER=awipev R --vanilla \<
-        ny-alesund/R/ny-alesund_cc.R >
-        ny-alesund/R/log_ny-alesund_cc.txt 2>&1
+        ny-alesund/R/ny-alesund_cc.R \>
+        ny-alesund/R/log_ny-alesund_cc.txt 2\>&1
 
@@
 
-    -   10 *//1*  \* \* cd web; USER=awipev bash awipev-co2.sh >
-        awipev-web.log 2>&1
+    -   10 *//1* \* \* cd web; USER=awipev bash awipev-co2.sh \>
+        awipev-web.log 2\>&1
 

### 2022-08-25 awipev-CO2.Rmd
still fiddling with air-sea CO2 plots

@@
   )
+pco2_delta_plt
 # we look at pCO2 normalized at 4°C at all depths
@@
   facet_wrap(vars(montht), scale = "free_y")
-print(p)
+p
 
@@
   )
+pco2_4_delta_plt
 ```
@@
 g <- g + plot_annotation(tag_levels = 'a')
-print(g)
+g
 ggsave(filename = "figures/deltas_pco2.png", plot = g, width = 15, height = 20, units = "cm")
@@
 ### Comparison pCO2 ferrybox vs pCO2 REMOS
-
 pCO2 measured in FerryBox expressed at in situ temp vs pCO2 calculated
@@
   ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = monthd)) +
-  geom_point(col="blue", size = 0.5) +
-  #geom_text() +
-  xlim(250, 400) + ylim(270, 360) +
-  labs(title = "pCO2 at ctd temperature",
-       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$"),
-       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-4 m\\phantom{x}($\\mu atm)$"))  +
-  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
-  ggpmisc::stat_ma_eq(mapping = use_label(c("R2", "eq"))) +
-  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
-  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
-  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
-#p_pco2_fb_remos
-ggsave(filename = "figures/pco2_fb_remos.png", plot = p_pco2_fb_remos, width = 25, height = 25, units = "cm")
-
-# Same thing but monthly median; code different because one wants to calculate delta
-tmp <- d_all %>% 
-  dplyr::select(depth, montht, pco2_fb_ctd_temp, pco2_remos_ctd_temp) %>% 
-  dplyr::filter(depth < 4) %>% 
-  drop_na() %>% 
-  dplyr::group_by(montht) %>% 
-  dplyr::summarise(
-    pco2_fb_ctd_temp = median(pco2_fb_ctd_temp, na.rm = TRUE),
-    pco2_remos_ctd_temp = median(pco2_remos_ctd_temp, na.rm = TRUE), 
-    delta_pco2_fb_remos_monthly = pco2_remos_ctd_temp - pco2_fb_ctd_temp
-  )
-p_pco2_fb_remos_month <- tmp %>% 
-  ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = montht)) +
   geom_point(col="blue", size = 0.5) +
@@
   coord_fixed(ratio = 1, expand = TRUE, clip = "on")
+#p_pco2_fb_remos
+ggsave(filename = "figures/pco2_fb_remos.png", plot = p_pco2_fb_remos, width = 25, height = 25, units = "cm")
+
+# Same thing but monthly median; code different because one wants to calculate delta
+tmp <- d_all %>% 
+  dplyr::select(depth, montht, pco2_fb_ctd_temp, pco2_remos_ctd_temp) %>% 
+  dplyr::filter(depth < 4) %>% 
+  drop_na() %>% 
+  dplyr::group_by(montht) %>% 
+  dplyr::summarise(
+    pco2_fb_ctd_temp = median(pco2_fb_ctd_temp, na.rm = TRUE),
+    pco2_remos_ctd_temp = median(pco2_remos_ctd_temp, na.rm = TRUE), 
+    delta_pco2_fb_remos_monthly = pco2_remos_ctd_temp - pco2_fb_ctd_temp
+  )
+p_pco2_fb_remos_month <- tmp %>% 
+  ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = montht)) +
+  geom_point(col="blue", size = 0.5) +
+  #xlim(250, 400) + ylim(250, 400) +
+  labs(title = "pCO2 at ctd temperature",
+       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$"),
+       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-4 m\\phantom{x}($\\mu atm)$"))  +
+  ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
+  ggpmisc::stat_ma_eq(mapping = use_label(c("R2", "eq"))) +
+  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
+  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
+  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
 #p_pco2_fb_remos_month
 ggsave(filename = "figures/pco2_fb_remos_monthly.png", plot = p_pco2_fb_remos_month, width = 25, height = 25, units = "cm")
-
 # combine
@@
 temperature) is much nicer using monthly median values (b) than using
-all data (a). The mean and median difference between the two pCO2s are
+all data (a). The mean and median difference between the two pCO2s (pco2_remos_ctd_temp - pco2_fb_ctd_temp) are
 `r round(median(tmp$delta_pco2_fb_remos_monthly, na.rm = TRUE), digits=1)`
@@
 ### Calculation of fluxes
-
-```{r With Contros data, echo=FALSE, message= FALSE, warning=FALSE}
+#### With Contros data
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 # calculations as described by de Carlo et al. (2013)
@@
 
-##TO DO: check calculations by Miller et al. (2020); use formulation of Wanninkhof 2014?
-## TO DO: Dobashi R. & Ho D. T., 2022. Air-sea gas exchange in a seagrass ecosystem. EGUsphere 
 d_all <- d_all %>%
-  dplyr::mutate(delta_pco2 = pco2_fb_ctd_temp - co2_air, # ppm
-                k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
-                Sc = 2073.1 - (125.62*temp_insitu_ctd) + (3.6276*temp_insitu_ctd^2) -
-                  (0.043219*temp_insitu_ctd^3), #dimensionless
-                k = k600 * (Sc/600)^-0.5, #cm/h
-                alpha = seacarb::K0(S=sal_insitu_ctd,T=temp_insitu_ctd,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
-                alpha = alpha * (seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0)/1000), #mol/(l/atm)
+  dplyr::mutate(
+    delta_pco2 = pco2_fb_ctd_temp - co2_air,
+    # ppm
+    k600 = 0.266 * ws ^ 2,
+    #cm/hr Ho et al. (2006)
+    Sc = 2073.1 - (125.62 * temp_insitu_ctd) + (3.6276 * temp_insitu_ctd^2) -
+      (0.043219 * temp_insitu_ctd ^ 3),
+    #dimensionless
+    k = k600 * (Sc / 600) ^ -0.5,
+    #cm/h
+    alpha = seacarb::K0(
+      S = sal_insitu_ctd,
+      T = temp_insitu_ctd,
+      P = 0,
+      Patm = p_air / 1013.25
+    ),
+    #mol/(kg/atm)
+    alpha = alpha * (seacarb::rho(
+      S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0
+    ) / 1000),
+    #mol/(l/atm)
     f_air_sea = k * alpha * delta_pco2 # mmol/(m2 h)
@@
   geom_point(aes(x = montht, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
-  #scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
   lims(y = c(-30, 0)) +
@@
 
-```{r With in situ simulation, echo=FALSE, message= FALSE, warning=FALSE}
+#### With in situ simulation
+Same as above but we correct pCO2 by adding 17 uatm as we show above that pCO2 at 11 m underestimates pCO2 at 0-4m (hence overestimates CO2 uptake)
+
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 # Same as above but we correct pCO2 by adding 17 uatm as we show above that pCO2 at 11 m
@@
 d_all <- d_all %>%
-  dplyr::mutate(delta_pco2_corr = (pco2_fb_ctd_temp + 17) - co2_air, # ppm
-                k600 = 0.266 * ws^2, #cm/hr Ho et al. (2006)
-                Sc = 2073.1 - (125.62*temp_insitu_ctd) + (3.6276*temp_insitu_ctd^2) -
-                  (0.043219*temp_insitu_ctd^3), #dimensionless
-                k = k600 * (Sc/600)^-0.5, #cm/h
-                alpha = seacarb::K0(S=sal_insitu_ctd,T=temp_insitu_ctd,P=0,Patm=p_air/1013.25), #mol/(kg/atm)
-                alpha = alpha * (seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0)/1000), #mol/(l/atm)
+  dplyr::mutate(
+    delta_pco2_corr = (pco2_fb_ctd_temp + 17) - co2_air,
+    # ppm
+    k600 = 0.266 * ws ^ 2,
+    #cm/hr Ho et al. (2006)
+    Sc = 2073.1 - (125.62 * temp_insitu_ctd) + (3.6276 * temp_insitu_ctd^2) -
+      (0.043219 * temp_insitu_ctd ^ 3),
+    #dimensionless
+    k = k600 * (Sc / 600) ^ -0.5,
+    #cm/h
+    alpha = seacarb::K0(
+      S = sal_insitu_ctd,
+      T = temp_insitu_ctd,
+      P = 0,
+      Patm = p_air / 1013.25
+    ),
+    #mol/(kg/atm)
+    alpha = alpha * (seacarb::rho(
+      S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0
+    ) / 1000),
+    #mol/(l/atm)
     f_air_sea_corr = k * alpha * delta_pco2_corr # mmol/(m2 h)
@@
   lims(y = c(-30, 0)) +
-  labs(title = "Air-sea CO2 flux (per month)", x = "Month", y = "CO2 (mmol/(m2 month))") +
+  labs(title = "Air-sea CO2 flux (per month) with corrected data", x = "Month", y = "CO2 (mmol/(m2 month))") +
   Mytheme(size_labs = 8)
-#p_f_air_sea_corr_month
+p_f_air_sea_corr_month
 ggsave(filename = "figures/f_air_sea_corr_month.png", plot = p_f_air_sea_corr_month, width = 20, units = "cm")
-# combine without and with correction
-p <- p_f_air_sea_month / p_f_air_sea_corr_month
-ggsave(filename = "figures/air-sea_CO2_flux_comp.png", plot = p, width = 20, units = "cm")
-knitr::include_graphics("figures/air-sea_CO2_flux_comp.png")
+# # combine without and with correction
+# p <- p_f_air_sea_month / p_f_air_sea_corr_month
+# ggsave(filename = "figures/air-sea_CO2_flux_comp.png", plot = p, width = 20, units = "cm")
+# knitr::include_graphics("figures/air-sea_CO2_flux_comp.png")
 #rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
+# Figure with and without correction on same plot
+```
+
+```{r monthly air-sea for paper, echo=FALSE, message= FALSE, warning=FALSE}
+air_sea_month$corr <- rep("no", length=12)
+air_sea_corr_month$corr <- rep("yes", length=12)
+
+air_sea <- dplyr::left_join(air_sea_month, air_sea_corr_month, by = "montht") %>% 
+  dplyr::select(montht, f_air_sea, f_air_sea_corr) %>% 
+  tidyr::pivot_longer(!montht, names_to = "corr", values_to = "air_sea")
+ggplot(data = air_sea) +
+  geom_point(aes(x = montht, y = air_sea, colour = factor(corr)))
 ```
@@
   Mytheme(size_labs = size_labs)
-print(ts_oa)
+ts_oa
 ggsave(filename = "figures/OmegaAragonite.png", plot = ts_oa, width = 15, height = 10, units = "cm")
@@
 g2 <- g2 + plot_annotation(tag_levels = 'A')
-g2
 ggsave(filename = "figures/ts_boxplots.png", plot = g2)
-
 ```
@@
 rm(list = ls(pattern = "ts_"), d_bp) #delete big ggplot objects and temp data
-gc() #garbage collection
+#gc() #garbage collection
 ```

### 2022-08-26 awipev-CO2.Rmd
refined figs for paper

@@
   Mytheme(size_labs = 8)
-#p_f_air_sea_month
 ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_month, width = 20, units = "cm")
@@
 knitr::include_graphics("figures/air-sea_CO2_flux.png")
+
+# For paper
+size_point <- 1.5 # size of data points
+alpha <- 1 #transparency
+size_labs <- 12 # font size labels
+# temp_insitu_11m
+ts_air_sea <- air_sea_month %>%
+  ggplot(aes(x = montht, y = f_air_sea), na.rm = TRUE) +
+  geom_col(colour="blue", fill = "blue",  alpha = alpha, stat="identity") +
+  lims(y = c(-30, 0)) +
+  geom_hline(yintercept = 0)+
+  labs(title="",x="Month", y=latex2exp::TeX("Air-sea CO$_2$ flux (mmol $m^{-2}$ month$^{-1}$)")) +
+  Mytheme(size_labs = size_labs)
+ts_air_sea
+ggsave(filename = "figures/ts_air_sea.png", plot = ts_air_sea, width = 20, units = "cm")
+
 #rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)

### 2022-08-29 awipev-CO2.Rmd
correction of mistakes

--- 2022-08-25 awipev-CO2.Rmd
@@
     #dimensionless
-    k = k600 * (Sc / 600) ^ -0.5,
-    #cm/h
+    #k = k600 * (Sc / 600) ^ -0.5,
+    ##cm/h
+    k = (k600 * (Sc / 600) ^ -0.5)/10,
+    # m/h
     alpha = seacarb::K0(
@@
     #mol/(l/atm)
-    f_air_sea = k * alpha * delta_pco2 # mmol/(m2 h)
+    f_air_sea = k * alpha * delta_pco2 /1000 # mmol/(m2 h)
   )
@@
   dplyr::group_by(lubridate::yday(datetime)) %>%
-  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)/1000) %>% #mol/(m2 d)
+  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)) %>% #nmol/(m2 d)
   ungroup() %>%
@@
   dplyr::group_by(monthd) %>%
-  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)/1000) %>% #mol/(m2 d)
+  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)) %>% #mmol/(m2 d)
   ungroup() %>%
@@
   geom_point(aes(x = montht, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
-  lims(y = c(-30, 0)) +
+  lims(y = c(-3, 0)) +
   labs(title = "Air-sea CO2 flux (per month)", x = "Month", y = "CO2 (mmol/(m2 month))") +
   Mytheme(size_labs = 8)
-#p_f_air_sea_month
 ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_month, width = 20, units = "cm")
@@
 knitr::include_graphics("figures/air-sea_CO2_flux.png")
+
+# For paper
+size_point <- 1.5 # size of data points
+alpha <- 1 #transparency
+size_labs <- 12 # font size labels
+# temp_insitu_11m
+ts_air_sea <- air_sea_month %>%
+  ggplot(aes(x = montht, y = f_air_sea), na.rm = TRUE) +
+  geom_col(colour="blue", fill = "blue",  alpha = alpha, stat="identity") +
+  lims(y = c(-3, 0)) +
+  geom_hline(yintercept = 0)+
+  labs(title="",x="Month", y=latex2exp::TeX("Air-sea CO$_2$ flux (mmol $m^{-2}$ month$^{-1}$)")) +
+  Mytheme(size_labs = size_labs)
+ts_air_sea
+ggsave(filename = "figures/ts_air_sea.png", plot = ts_air_sea, width = 20, units = "cm")
 #rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
@@
     #mol/(l/atm)
-    f_air_sea_corr = k * alpha * delta_pco2_corr # mmol/(m2 h)
-  )
-
-# p_f_air_sea <- ggplot(data = d_all) +
-#   geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
-#   labs(title = "Air-sea CO2 flux (all data)", x = "Time", y = "CO2 (mmol/(m2 h))") +
-#   Mytheme(size_labs = 8)
-# p_f_air_sea
-# ggsave(filename = "figures/p_f_air_sea.png", plot = p_f_air_sea, width = 20, units = "cm")
-
-# air_sea_day_d <- d_all %>%
-#   dplyr::select(datetime, f_air_sea_corr) %>%
-#   dplyr::group_by(lubridate::yday(datetime)) %>%
-#   dplyr::summarise(f_air_sea_corr = 24 * mean(f_air_sea_corr, na.rm = TRUE)/1000) %>% #mol/(m2 d)
-#   ungroup() %>%
-#   dplyr::rename(day = 1)
-
-# p_f_air_sea_d <- ggplot(data = air_sea_day) +
-#   geom_point(aes(x = day, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
-#   labs(title = "Air-sea CO2 flux (per day)", x = "Julian day", y = "CO2 (mmol/(m2 d))") +
-#   Mytheme(size_labs = 8)
-# p_f_air_sea_d
-# ggsave(filename = "figures/f_air_sea_d.png", plot = p_f_air_sea_d, width = 20, units = "cm")
-# 
+    f_air_sea_corr = k * alpha * delta_pco2_corr /1000 # mmol/(m2 h)
+  )
 air_sea_corr_month <- d_all %>%
@@
   dplyr::group_by(monthd) %>%
-  dplyr::summarise(f_air_sea_corr = 24 * mean(f_air_sea_corr, na.rm = TRUE)/1000) %>% #mol/(m2 d)
+  dplyr::summarise(f_air_sea_corr = 24 * mean(f_air_sea_corr, na.rm = TRUE)) %>% #mol/(m2 d)
   ungroup() %>%
@@
   #scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
-  lims(y = c(-30, 0)) +
+  lims(y = c(-3, 0)) +
   labs(title = "Air-sea CO2 flux (per month) with corrected data", x = "Month", y = "CO2 (mmol/(m2 month))") +
@@
 `r round(sum(air_sea_month$f_air_sea), digits = 0)` and
-`r round(sum(air_sea_corr_month$f_air_sea_corr), digits = 0)` mol/(m2
+`r round(sum(air_sea_corr_month$f_air_sea_corr), digits = 0)` mmol/(m2
 year) without and with correction, respectively.

### 2022-08-30 awipev-CO2.Rmd
still air-sea CO2

@@
 
+# TODO: update this dataset
 load(file = paste0(path, "meteo_awi/wind_nyalesund.RData")) 
@@
 ### Comparison pCO2 ferrybox vs pCO2 REMOS
+
 pCO2 measured in FerryBox expressed at in situ temp vs pCO2 calculated
@@
 temperature) is much nicer using monthly median values (b) than using
-all data (a). The mean and median difference between the two pCO2s (pco2_remos_ctd_temp - pco2_fb_ctd_temp) are
+all data (a). The mean and median difference between the two pCO2s
+(pco2_remos_ctd_temp - pco2_fb_ctd_temp) are
 `r round(median(tmp$delta_pco2_fb_remos_monthly, na.rm = TRUE), digits=1)`
@@
 ### Calculation of fluxes
+
 #### With Contros data
+
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
   dplyr::mutate(
-    delta_pco2 = pco2_fb_ctd_temp - co2_air,
-    # ppm
-    k600 = 0.266 * ws ^ 2,
-    #cm/hr Ho et al. (2006)
+    delta_pco2 = pco2_fb_ctd_temp - co2_air, # uatm
+    k600 = 0.266 * ws ^ 2, # cm/h Ho et al. (2006)
     Sc = 2073.1 - (125.62 * temp_insitu_ctd) + (3.6276 * temp_insitu_ctd^2) -
-      (0.043219 * temp_insitu_ctd ^ 3),
-    #dimensionless
-    #k = k600 * (Sc / 600) ^ -0.5,
-    ##cm/h
-    k = (k600 * (Sc / 600) ^ -0.5)/10,
-    # m/h
+      (0.043219 * temp_insitu_ctd^3),    #dimensionless
+    k = (k600 * (Sc / 600) ^ -0.5), #cm/h
+    k = k/10, #m/h
     alpha = seacarb::K0(
@@
       P = 0,
-      Patm = p_air / 1013.25
-    ),
-    #mol/(kg/atm)
+      Patm = p_air / 1013.25 # from hPa to atm
+    ), #mol/(kg atm)
     alpha = alpha * (seacarb::rho(
       S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0
-    ) / 1000),
-    #mol/(l/atm)
-    f_air_sea = k * alpha * delta_pco2 /1000 # mmol/(m2 h)
+    ) / 1000), # mol/(l atm)
+    alpha = alpha * 1000 , # mol/(m3 atm)
+    f_air_sea = k * alpha * delta_pco2, # mol/(m2 h 1e6)
+    f_air_sea = k * alpha * delta_pco2 * 1e-6 * 1000 # mmol/(m2 h)
   )
@@
   Mytheme(size_labs = 8)
-#p_f_air_sea
+p_f_air_sea
 ggsave(filename = "figures/p_f_air_sea.png", plot = p_f_air_sea, width = 20, units = "cm")
@@
   dplyr::group_by(lubridate::yday(datetime)) %>%
-  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)) %>% #nmol/(m2 d)
+  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)) %>% #mmol/(m2 d)
   ungroup() %>%
@@
   geom_point(aes(x = montht, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
-  lims(y = c(-3, 0)) +
+  lims(y = c(-3000, 0)) +
   labs(title = "Air-sea CO2 flux (per month)", x = "Month", y = "CO2 (mmol/(m2 month))") +
@@
 ts_air_sea <- air_sea_month %>%
-  ggplot(aes(x = montht, y = f_air_sea), na.rm = TRUE) +
+  ggplot(aes(x = montht, y = f_air_sea / 1000), na.rm = TRUE) +
   geom_col(colour="blue", fill = "blue",  alpha = alpha, stat="identity") +
@@
   geom_hline(yintercept = 0)+
-  labs(title="",x="Month", y=latex2exp::TeX("Air-sea CO$_2$ flux (mmol $m^{-2}$ month$^{-1}$)")) +
+  labs(title="",x="Month", y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)")) +
   Mytheme(size_labs = size_labs)
@@
 #### With in situ simulation
-Same as above but we correct pCO2 by adding 17 uatm as we show above that pCO2 at 11 m underestimates pCO2 at 0-4m (hence overestimates CO2 uptake)
+
+Same as above but we correct pCO2 by adding 17 uatm as we show above
+that pCO2 at 11 m underestimates pCO2 at 0-4m (hence overestimates CO2
+uptake)
 
@@
     delta_pco2_corr = (pco2_fb_ctd_temp + 17) - co2_air,
-    # ppm
-    k600 = 0.266 * ws ^ 2,
-    #cm/hr Ho et al. (2006)
+    k600 = 0.266 * ws ^ 2, # cm/h Ho et al. (2006)
     Sc = 2073.1 - (125.62 * temp_insitu_ctd) + (3.6276 * temp_insitu_ctd^2) -
-      (0.043219 * temp_insitu_ctd ^ 3),
-    #dimensionless
-    #k = k600 * (Sc / 600) ^ -0.5,
-    ##cm/h
-    k = (k600 * (Sc / 600) ^ -0.5)/10,
-    # m/h
+      (0.043219 * temp_insitu_ctd^3),    #dimensionless
+    k = (k600 * (Sc / 600) ^ -0.5), #cm/h
+    k = k/10, #m/h
     alpha = seacarb::K0(
@@
       P = 0,
-      Patm = p_air / 1013.25
-    ),
-    #mol/(kg/atm)
+      Patm = p_air / 1013.25 # from hPa to atm
+    ), #mol/(kg atm)
     alpha = alpha * (seacarb::rho(
       S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0
-    ) / 1000),
-    #mol/(l/atm)
-    f_air_sea_corr = k * alpha * delta_pco2_corr /1000 # mmol/(m2 h)
+    ) / 1000), # mol/(l atm)
+    alpha = alpha * 1000 , # mol/(m3 atm)
+    f_air_sea_corr = k * alpha * delta_pco2, # mol/(m2 h 1e6)
+    f_air_sea_corr = k * alpha * delta_pco2 * 1e-6 * 1000 # mmol/(m2 h)
   )
@@
   #scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
-  lims(y = c(-3, 0)) +
+  #lims(y = c(-3, 0)) +
   labs(title = "Air-sea CO2 flux (per month) with corrected data", x = "Month", y = "CO2 (mmol/(m2 month))") +
@@
 
-air_sea <- dplyr::left_join(air_sea_month, air_sea_corr_month, by = "montht") %>% 
+air_sea <- dplyr::left_join(air_sea_month, air_sea_corr_month/1000, by = "montht") %>% 
   dplyr::select(montht, f_air_sea, f_air_sea_corr) %>% 
@@
 The annual air-sea CO2 flux is
-`r round(sum(air_sea_month$f_air_sea), digits = 0)` and
-`r round(sum(air_sea_corr_month$f_air_sea_corr), digits = 0)` mmol/(m2
+`r round(sum(air_sea_month$f_air_sea/1000), digits = 0)` and
+`r round(sum(air_sea_corr_month$f_air_sea_corr/1000), digits = 0)` mol/(m2
 year) without and with correction, respectively.

### 2022-12-26 awipev-CO2.Rmd
minor corrections

@@
 # skipped because it is done in the "stratification tab"
-Extreme differences: `r dplyr::filter(tmp, range_diff < -3 | range_diff > 2)`.
-
-There are `r sum(!is.na(tmp$range_diff))` days with salinity values at both 1 m (0-2 m) and 10 m (8-12 m).
-
-The salinity difference between 1 and 10 m ranges between `r min(tmp$range_diff, na.rm = TRUE)` and `r max(tmp$range_diff, na.rm = TRUE)` (mean: `r mean(tmp$range_diff, na.rm = TRUE)`; `r median(tmp$range_diff, na.rm = TRUE)`).
+# Extreme differences: `r dplyr::filter(tmp, range_diff < -3 | range_diff > 2)`.
+# 
+# There are `r sum(!is.na(tmp$range_diff))` days with salinity values at both 1 m (0-2 m) and 10 m (8-12 m).
+# 
+# The salinity difference between 1 and 10 m ranges between `r min(tmp$range_diff, na.rm = TRUE)` and `r max(tmp$range_diff, na.rm = TRUE)` (mean: `r mean(tmp$range_diff, na.rm = TRUE)`; `r median(tmp$range_diff, na.rm = TRUE)`).
 The difference with depth is therefore significant.
@@
 # skipped because it is done in the "stratification tab"
-There are `r sum(!is.na(tmp$range))` days with temperature values at
-both 1 m (0-2 m) and 9 m (> 8 m). The temperature difference between 1
-and 9 m ranges between `r min(tmp$range, na.rm = TRUE)`°C and
-`r max(tmp$range, na.rm = TRUE)`°C (mean:
-`r mean(tmp$range, na.rm = TRUE)`°C; `r median(tmp$range, na.rm = TRUE)`°C).
-The difference with depth is therefore significant.
+# There are `r sum(!is.na(tmp$range))` days with temperature values at
+# both 1 m (0-2 m) and 9 m (> 8 m). The temperature difference between 1
+# and 9 m ranges between `r min(tmp$range, na.rm = TRUE)`°C and
+# `r max(tmp$range, na.rm = TRUE)`°C (mean:
+# `r mean(tmp$range, na.rm = TRUE)`°C; `r median(tmp$range, na.rm = TRUE)`°C).
+# The difference with depth is therefore significant.
 ```

### 2022-12-26 awipev-CO2.Rmd
cosmetic

@@
   #dplyr::arrange(datetime) %>%
-  dplyr::mutate(middle =  seconds_to_period(
-   c(0, difftime(time1 = datetime[-1], time2 = datetime[-nrow(durPeriod)])/2* 3600 ))) %>%
+  dplyr::mutate(middle =  
+                  seconds_to_period(c(0, difftime(time1 = datetime[-1], 
+                                                  time2 = datetime[-nrow(durPeriod)])/2* 3600 ))) %>%
   dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])

### 2022-12-26 awipev-CO2.Rmd
Fixing error in Durafet calibration

@@
                                                   time2 = datetime[-nrow(durPeriod)])/2* 3600 ))) %>%
-  dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])
+  #dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])
+  dplyr::mutate(dur_interval = datetime + middle)
+
+# tmp <- durPeriod$datetime
+# dur_interv <- tmp + c(diff(tmp)/2, 0)
+# durPeriod <- durPeriod %>% 
+#   dplyr::mutate(dur_interv = dur_interv)
 

### 2022-12-26 awipev-CO2.Rmd
Cleanup after fixing durafet calculation issue

--- 2022-12-26 awipev-CO2.Rmd
@@
 # deployment period between 2 spectro measurements.
-# TODO the following throws a warning but seems to work
+# the following thrown an error fixed 2022-12-26
 durPeriod <- d_all %>%
@@
                                                   time2 = datetime[-nrow(durPeriod)])/2* 3600 ))) %>%
-  dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])
+  #dplyr::mutate(dur_interval = datetime + middle[2:nrow(durPeriod)])
+  dplyr::mutate(dur_interval = datetime + middle)
 

### 2022-12-28 awipev-CO2.Rmd
minor errors corrected
Refining K1K2

@@
   tidyr::pivot_longer(-deltas, names_to = "variable") %>% 
-  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), variable = fct_recode(variable, 'DeltapH' = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))
+  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), variable = fct_recode(variable, 'pH' = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))
 
@@
   Mytheme(size_labs = 10)
-p
 # diff_all_long$variable <- factor(diff_all_long$variable, levels = c('C[T]','Omega[a]', 'pH'))
@@
   dplyr::rename(delta_ph = pH, delta_pCO2 = pCO2, delta_OmegaAragonite = OmegaAragonite) %>%
-  dplyr::select(delta_ph, delta_pCO2, delta_OmegaAragonite)
-# calculate descriptive statistics Lueker - Sulpis
-diff_ls_quant <- tibble(pH = as.numeric(summary(diff_ls2$delta_ph)),
+  dplyr::select(delta_ph, delta_pCO2, delta_OmegaAragonite) %>% 
+  dplyr::mutate(deltas = "L00-S20", .before = 1)
+# calculate difference Lueker - Papadimitriou
+diff_lp2 <- as_tibble(carb_l2 - carb_p2) %>% 
+  dplyr::rename(delta_ph = pH, delta_pCO2 = pCO2, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_pCO2, delta_OmegaAragonite) %>% 
+  dplyr::mutate(deltas = "L00-P18", .before = 1)
+# calculate difference Lueker - Millero
+diff_lm2 <- as_tibble(carb_l2 - carb_m2) %>% 
+  dplyr::rename(delta_ph = pH, delta_pCO2 = pCO2, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_pCO2, delta_OmegaAragonite) %>% 
+  dplyr::mutate(deltas = "L00-M02", .before = 1)
+# bind and plot
+diff_all <- dplyr::bind_rows(diff_ls2, diff_lp2, diff_lm2)
+diff_all_long <- diff_all %>% 
+  tidyr::pivot_longer(-deltas, names_to = "variable") %>% 
+  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_pCO2', 'delta_OmegaAragonite'), variable = fct_recode(variable, 'pH' = "delta_ph", 'pCO[2]' = "delta_pCO2",'Omega[a]' = "delta_OmegaAragonite"))
+
+p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L00-S20', 'L00-P18', 'L00-M02'), y=value))+
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  geom_hline(yintercept = 0) +
+  labs(title = "", x = "", y= "") +
+  facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
+  Mytheme(size_labs = 10)
+p
+# calculate descriptive statistics
+diff_ls2_quant <- tibble(pH = as.numeric(summary(diff_ls2$delta_ph)),
                         pCO2 = as.numeric(summary(diff_ls2$delta_pCO2)),
@@
   dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
+diff_lp2_quant <- tibble(pH = as.numeric(summary(diff_lp2$delta_ph)),
+                        pCO2 = as.numeric(summary(diff_lp2$delta_pCO2)),
+                        OmegaAragonite = as.numeric(summary(diff_lp2$delta_OmegaAragonite))) %>%
+  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
+diff_lm2_quant <- tibble(pH = as.numeric(summary(diff_lm2$delta_ph)),
+                        pCO2 = as.numeric(summary(diff_lm2$delta_pCO2)),
+                        OmegaAragonite = as.numeric(summary(diff_lm2$delta_OmegaAragonite))) %>%
+  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
+# boxplot
+ggsave(filename = "figures/k1k2_ct_at.png", plot = p, width = 25, height = 20, units = "cm")
+
 # prepare tibble to compare calculated pH and spec pH
@@
 The discrete values of AT, CT, salinity and temperature in the FerryBox
-were used to calculate pH using the formulations for K1 and K2 of Lueker
+were used to calculate pH and pCO2 using the formulations for K1 and K2 of Lueker
 et al. (2000) and Sulpis et al. (2020). The differences induced by the
@@
 
--   small for CT (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on
+-   small for pCO2 (`r round(diff_ls_quant[4, 3], digits = 1)` uatm on
     average; always lower with Sulpis than with Lueker) compared with
     the uncertainty calculated with seacarb
-    (`r round(errors[1, 9], digits = 1)`)
+    (`r round(errors[2, 8], digits = 1)`)
 
@@
 
-`r knitr::kable(diff_ls_quant, digits = c(0, 4, rep(3, 4)), caption = "Lueker minus Sulpis using all discrete Ferrybox data.", format = "simple")`
+`r knitr::kable(diff_ls2_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis using discrete CT and AT.", format = "simple")`
+`r knitr::kable(diff_lp2_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Papadimitriou discrete CT and AT.", format = "simple")`
+`r knitr::kable(diff_lm2_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Millero using discrete CT and AT.", format = "simple")`
+`r include_graphics("figures/k1k2_ct_at.png")`
 
@@
     alpha = alpha * 1000 , # mol/(m3 atm)
-    f_air_sea_corr = k * alpha * delta_pco2, # mol/(m2 h 1e6)
-    f_air_sea_corr = k * alpha * delta_pco2 * 1e-6 * 1000 # mmol/(m2 h)
+    f_air_sea_corr = k * alpha * delta_pco2_corr, # mol/(m2 h 1e6)
+    f_air_sea_corr = k * alpha * delta_pco2_corr * 1e-6 * 1000 # mmol/(m2 h)
   )
@@
 
-air_sea <- dplyr::left_join(air_sea_month, air_sea_corr_month/1000, by = "montht") %>% 
+air_sea <- dplyr::left_join(air_sea_month, air_sea_corr_month, by = "montht") %>% 
+  #dplyr::mutate(air_sea_corr_month = air_sea_corr_month/1000) %>% 
   dplyr::select(montht, f_air_sea, f_air_sea_corr) %>% 

### 2022-12-29 awipev-CO2.Rmd
K1K2 almost completed

@@
 
+**_Comparison of various formulations compared to Lueker et al. (2000)_**
+
 The discrete values of pCO2, AT, salinity and temperature in the
@@
 `r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis using all discrete Ferrybox data.", format = "simple")`
+
+**_Comparison of measured vs calculated pH_**
 
@@
 
+**_Comparison of various formulations compared to Lueker et al. (2000)_**
 The discrete values of AT, CT, salinity and temperature in the FerryBox
-were used to calculate pH and pCO2 using the formulations for K1 and K2 of Lueker
-et al. (2000) and Sulpis et al. (2020). The differences induced by the
-choice of the carbonic acid constants are:
-
--   large for pH (`r round(diff_ls_quant[4, 2], digits = 3)` pH units on
-    average; ; median is `r round(diff_ls_quant[3, 2], digits = 3)`)
-    compared with the uncertainty calculated with seacarb
-    (`r round(errors[1, 7], digits = 3)`). In general, pH is higher with
-    Sulpis than with Lueker.
-
--   small for pCO2 (`r round(diff_ls_quant[4, 3], digits = 1)` uatm on
-    average; always lower with Sulpis than with Lueker) compared with
-    the uncertainty calculated with seacarb
-    (`r round(errors[2, 8], digits = 1)`)
-
--   negligible for OmegaAragonite
+were used to calculate pH and pCO2 using various formulations for K1 and K2. The median 
+differences induced by the choice of the carbonic acid constants are shiown below.
 
@@
 
+**_Comparison of measured vs calculated pH_**
 Here we compare pH measured spectrophotometrically with pH calculated

### 2022-12-29 awipev-CO2.Rmd
K1K2 completed!

@@
   coord_fixed()
-ggsave(filename = "figures/figures/at_s.png", plot = at_s, width = 25, height = 25, units = "cm")
+ggsave(filename = "figures/at_s.png", plot = at_s, width = 25, height = 25, units = "cm")
 
@@
 # Using Lueker  
-carb_l <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
+carb_l1 <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", 
@@
 # normalize Lueker-derived pH at 4°C
-carb_l$pH <- pHinsi(pH = carb_l$pH, ALK = carb_l$ALK, Tinsi = 4, Tlab = carb_l$T, Pinsi = 0, 
-                         S = carb_l$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
+carb_l1$pH <- pHinsi(pH = carb_l1$pH, ALK = carb_l1$ALK, Tinsi = 4, Tlab = carb_l1$T, Pinsi = 0, 
+                         S = carb_l1$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
                          pHscale = "T", b="u74")
 # Using Sulpis
-carb_s <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
+carb_s1 <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks = "d", 
@@
 # normalize Sulpis-derived pH at 4°C
-carb_s$pH <- pHinsi(pH = carb_s$pH, ALK = carb_s$ALK, Tinsi = 4, Tlab = carb_s$T, Pinsi = 0, 
-                         S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
+carb_s1$pH <- pHinsi(pH = carb_s1$pH, ALK = carb_s1$ALK, Tinsi = 4, Tlab = carb_s1$T, Pinsi = 0, 
+                         S = carb_s1$S, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
                          pHscale = "T", b="u74")
 # Using Papadimitriou
-carb_p <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
+carb_p1 <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks = "d", 
@@
 # normalize Papadimitriou-derived pH at 4°C
-carb_p$pH <- pHinsi(pH = carb_p$pH, ALK = carb_p$ALK, Tinsi = 4, Tlab = carb_p$T, Pinsi = 0, 
-                         S = carb_p$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
+carb_p1$pH <- pHinsi(pH = carb_p1$pH, ALK = carb_p1$ALK, Tinsi = 4, Tlab = carb_p1$T, Pinsi = 0, 
+                         S = carb_p1$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
                          pHscale = "T", b="u74")
 # Using Millero et al. (2002)
-carb_m <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
+carb_m1 <- carb(flag = 24, var1 = tmp$pco2_fb, var2 = tmp$at * 1e-6, S = tmp$sal_fb_mix, 
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks = "d", 
@@
 # normalize Millero et al. (2002)-derived pH at 4°C
-carb_m$pH <- pHinsi(pH = carb_m$pH, ALK = carb_m$ALK, Tinsi = 4, Tlab = carb_m$T, Pinsi = 0, 
-                         S = carb_m$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
+carb_m1$pH <- pHinsi(pH = carb_m1$pH, ALK = carb_m1$ALK, Tinsi = 4, Tlab = carb_m1$T, Pinsi = 0, 
+                         S = carb_m1$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
                          pHscale = "T", b="u74")
 # calculate difference Lueker - Sulpis
-diff_ls <- as_tibble(carb_l - carb_s) %>% 
+diff_ls1 <- as_tibble(carb_l1 - carb_s1) %>% 
   dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
-  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite)
-# calculate descriptive statistics Lueker - Sulpis
-diff_ls_quant <- tibble(pH = as.numeric(summary(diff_ls$delta_ph)),
-                        CT = as.numeric(summary(diff_ls$delta_ct * 1e6)),
-                        OmegaAragonite = as.numeric(summary(diff_ls$delta_OmegaAragonite))) %>%
+  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
+  dplyr::mutate(deltas = "L00-S20", .before = 1)
+# calculate difference Lueker - Papadimitriou
+diff_lp1 <- as_tibble(carb_l1 - carb_p1) %>% 
+  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
+  dplyr::mutate(deltas = "L00-P18", .before = 1)
+# calculate difference Lueker - Millero
+diff_lm1 <- as_tibble(carb_l1 - carb_m1) %>% 
+  dplyr::rename(delta_ph = pH, delta_ct = DIC, delta_OmegaAragonite = OmegaAragonite) %>%
+  dplyr::select(delta_ph, delta_ct, delta_OmegaAragonite) %>% 
+  dplyr::mutate(deltas = "L00-M02", .before = 1)
+
+# bind and plot
+diff_all <- dplyr::bind_rows(diff_ls1, diff_lp1, diff_lm1) %>% 
+    dplyr::mutate(delta_ct = delta_ct * 1e6)
+diff_all_long <- diff_all %>% 
+  tidyr::pivot_longer(-deltas, names_to = "variable") %>% 
+  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), variable = fct_recode(variable, 'pH' = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))
+
+p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L00-S20', 'L00-P18', 'L00-M02'), y=value))+
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  geom_hline(yintercept = 0) +
+  labs(title = "", x = "", y= "") +
+  facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
+  Mytheme(size_labs = 10)
+ggsave(filename = "figures/k1k2_pco2_at.png", plot = p, width = 25, height = 20, units = "cm")
+
+# calculate descriptive statistics
+diff_ls1_quant <- tibble(pH = as.numeric(summary(diff_ls1$delta_ph)),
+                        CT = as.numeric(summary(diff_ls1$delta_ct * 1e6)),
+                        OmegaAragonite = as.numeric(summary(diff_ls1$delta_OmegaAragonite))) %>%
   dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
+diff_lp1_quant <- tibble(pH = as.numeric(summary(diff_lp1$delta_ph)),
+                        CT = as.numeric(summary(diff_lp1$delta_ct * 1e6)),
+                        OmegaAragonite = as.numeric(summary(diff_lp1$delta_OmegaAragonite))) %>%
+  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
+diff_lm1_quant <- tibble(pH = as.numeric(summary(diff_lm1$delta_ph)),
+                        CT = as.numeric(summary(diff_lm1$delta_ct * 1e6)),
+                        OmegaAragonite = as.numeric(summary(diff_lm1$delta_OmegaAragonite))) %>%
+  dplyr::mutate(var = c("Min", "Q1", "Median", "Mean", "Q3", "Max"), .before = 1)
+
 # prepare tibble to compare calculated pH and spec pH
@@
                ph_s_dur_temp_4_m02 = tmp$ph_s_dur_temp_4_m02, 
-               pH_l = carb_l$pH, pH_s = carb_s$pH, 
-               pH_p = carb_p$pH, pH_m = carb_m$pH, temp_fb = tmp$temp_fb) %>% 
+               pH_l = carb_l1$pH, pH_s = carb_s1$pH, 
+               pH_p = carb_p1$pH, pH_m = carb_m1$pH, temp_fb = tmp$temp_fb) %>% 
   tidyr::drop_na(ph_s_dur_temp_4_l)
@@
 
-The discrete values of pCO2, AT, salinity and temperature in the
-FerryBox were used to calculate pH using the formulations for K1 and K2
-of Lueker et al. (2000) and Sulpis et al. (2020). The differences
-induced by the choice of the carbonic acid constants are:
-
--   large for pH (`r round(diff_ls_quant[4, 2], digits = 3)` pH units on
-    average; ; median is `r round(diff_ls_quant[3, 2], digits = 3)`)
-    compared with the uncertainty calculated with seacarb (see above;
-    `r round(errors[1, 7], digits = 3)`). In general, pH is higher with
-    Sulpis than with Lueker.
-
--   small for CT (`r round(diff_ls_quant[4, 3], digits = 1)` umol/kg on
-    average; always lower with Sulpis than with Lueker) compared with
-    the uncertainty calculated with seacarb
-    (`r round(errors[1, 9], digits = 1)`)
-
--   negligible for OmegaAragonite
-
-`r knitr::kable(diff_ls_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis using all discrete Ferrybox data.", format = "simple")`
+The **discrete** values of pCO2, AT, salinity and temperature in the
+FerryBox were used to calculate pH and CT with the v arious formulations for K1 and K2
+
+**Results are shown below but it does not make sense to udse them in the manuscript. Btter to use all pCO2-AT data as above.**
+
+`r knitr::kable(diff_ls1_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Sulpis using discrete pCO2 data.", format = "simple")`
+`r knitr::kable(diff_lp1_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Papadimitriou using discrete pCO2 data.", format = "simple")`
+`r knitr::kable(diff_lm1_quant, digits = c(0, rep(3, 5)), caption = "Lueker minus Millero using discrete pCO2 data.", format = "simple")`
+`r include_graphics("figures/k1k2_all_pco2_at.png")`
 
@@
   Mytheme(size_labs = 10)
-p
+
 # calculate descriptive statistics

### 2023-01-02 awipev-CO2.Rmd
sorting out the mess in stratification (in progress)

@@
   dplyr::select(montht, sal_insitu_ctd, depth_group) %>%
-  tidyr::drop_na() %>% 
   dplyr::filter(depth_group != "NA") %>% 
-  group_by(depth_group, montht)
+  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
 p <- tmp %>% 
@@
   labs(title = "Salinity vs depth", x = "Depth (m)", y= "Salinity") +
-  scale_x_discrete(labels = depth_labels) +
   facet_wrap(vars(montht), scale = "free_y")
@@
   )) %>%
-  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>%
-  dplyr::group_by(depth_group2, montht)
+  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') #%>%
 tmp_delta <- tidyr::drop_na(tmp) %>%
@@
   dplyr::select(montht, temp_insitu_ctd, depth_group) %>%
-  tidyr::drop_na() %>% 
   dplyr::filter(depth_group != "NA") %>% 
-  group_by(depth_group, montht)
+  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
 p <- tmp %>% 
@@
 tmp_delta <- tmp %>%
-  group_by(depth_group2, montht) %>%
+  #group_by(depth_group2, montht) %>%
   dplyr::summarise(temp_med = median(temp_insitu_ctd, na.rm = TRUE)) %>%
@@
 temp_delta_plt <- tmp_delta %>% 
-  #tidyr::drop_na() %>% 
   ggplot(aes(x = montht, y = temp_delta)) +
-  #scale_x_discrete(expand = c(0, 0)) +
   scale_x_discrete("Month") +
@@
   dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth_group, pressure_insitu_ctd) %>%
-  tidyr::drop_na() %>% 
   dplyr::filter(depth_group != "NA") %>% 
+  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels)) %>% 
   dplyr::mutate(density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = pressure_insitu_ctd)) %>%
-  group_by(depth_group, montht)
 p <- tidyr::drop_na(tmp) %>% 
@@
   dplyr::select(montht, sal_insitu_ctd, temp_insitu_ctd, depth_group, pressure_insitu_ctd) %>%
-  tidyr::drop_na() %>% 
   dplyr::filter(depth_group != "NA") %>% 
@@
   dplyr::filter(depth_group != "NA") %>% 
-  group_by(depth_group, montht)
+  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
 p <- tmp %>% 
@@
 tmp_delta <- tmp %>%
-  group_by(depth_group2, montht) %>%
   dplyr::summarise(pH_tot_sf_med = median(pHint_tot_sf, na.rm = TRUE)) %>%
@@
   dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
-  tidyr::drop_na() %>% 
   dplyr::filter(depth_group != "NA") %>% 
-  group_by(depth_group, montht)
+  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
 p <- tmp %>% 
+  drop_na() %>% 
   ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf_temp_4)) +
@@
   dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
-  dplyr::group_by(depth_group2, montht)
 summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group2 * tmp$montht))
@@
 tmp_delta <- tmp %>% 
-  group_by(depth_group2, montht) %>% 
   dplyr::summarise(pH_tot_sf_med = median(pHint_tot_sf_temp_4, na.rm = TRUE)) %>% 
@@
   dplyr::select(montht, pHint_tot_sf_temp_4, depth_group) %>%
+  dplyr::filter(depth_group != "NA") %>% 
+  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
+p <- tmp %>% 
   tidyr::drop_na() %>% 
-  dplyr::filter(depth_group != "NA") %>% 
-  group_by(depth_group, montht)
-p <- tmp %>% 
   ggplot(aes(x=as.factor(depth_group), y = pHint_tot_sf_temp_4)) +
@@
   dplyr::select(montht, pco2_remos_ctd_temp, depth_group) %>%
-  tidyr::drop_na() %>% 
   dplyr::filter(depth_group != "NA") %>% 
-  group_by(depth_group, montht)
+  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
 p <- tmp %>% 
@@
   )) %>%
-  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>%
-  dplyr::group_by(depth_group2, montht)
+  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12')
 summary(aov(tmp$pco2_remos_ctd_temp ~ tmp$depth_group2 * tmp$montht))
@@
 tmp_delta <- tmp %>%
-  group_by(depth_group2, montht) %>%
   dplyr::summarise(pco2_remos_ctd_temp_med = median(pco2_remos_ctd_temp, na.rm = TRUE)) %>%
@@
   dplyr::filter(depth_group != "NA") %>% 
-  group_by(depth_group, montht)
+  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
+
 p <- tmp %>% 

### 2023-01-02 awipev-CO2.Rmd
Finalized stratification and air-sea CO2

@@
   dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels)) %>% 
-  dplyr::mutate(density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = pressure_insitu_ctd)) %>%
+  dplyr::mutate(density = seacarb::rho(S = sal_insitu_ctd, T = temp_insitu_ctd, P = pressure_insitu_ctd))
 p <- tidyr::drop_na(tmp) %>% 
@@
   )) %>%
-  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>%
-  dplyr::group_by(depth_group2, montht)
+  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12')
 summary(aov(tmp$pHint_tot_sf ~ tmp$depth_group2 * tmp$montht))
@@
 tmp_delta <- tmp %>%
+  dplyr::group_by(depth_group2, montht) %>% 
   dplyr::summarise(pH_tot_sf_med = median(pHint_tot_sf, na.rm = TRUE)) %>%
@@
 
-# we look at pHint_tot_sf normalized at 4°C  0 to 4 m vs more than 8 m
+# we look at pHint_tot_sf normalized at 4°C  0 to 4 m vs more than 8 m ###
 tmp <- d_all %>% 
@@
                                                    depth_group == '>8' ~ '8-12'))) %>% 
-  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12') %>% 
+  dplyr::filter(depth_group2 == '0-4' | depth_group2 == '8-12')
 summary(aov(tmp$pHint_tot_sf_temp_4 ~ tmp$depth_group2 * tmp$montht))
@@
 tmp_delta <- tmp %>% 
+  dplyr::group_by(depth_group2, montht) %>% 
   dplyr::summarise(pH_tot_sf_med = median(pHint_tot_sf_temp_4, na.rm = TRUE)) %>% 
@@
   dplyr::rename(median0_4m = "0-4",
-                median8_12m = "8-12") %>%   dplyr::mutate(pH_tot_sf_med_delta = median0_4m - median8_12m)
+                median8_12m = "8-12") %>%   
+  dplyr::mutate(pH_tot_sf_med_delta = median0_4m - median8_12m)
 kable(tmp_delta, digits = 3, caption = "Median seafet pH at 4°C with (median0_4m - median8_12m)")
@@
 tmp_delta <- tmp %>%
+  dplyr::group_by(depth_group2, montht) %>% 
   dplyr::summarise(pco2_remos_ctd_temp_med = median(pco2_remos_ctd_temp, na.rm = TRUE)) %>%

### 2023-01-02 awipev-CO2.Rmd
minor cleanup

@@
 
----- Stratification plots -------------------
+### Stratification plots
 
@@
 
--   seawater pCO2 measured in the FerryBox on water pumped from 11 m
-    depth.
+-   seawater pCO2 measured in the FerryBox on water pumped from 11 m depth.
 -   atmospheric CO2 measured at the Zeppelin station and downloaded on
@@
   ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = monthd)) +
-  geom_point(col="blue", size = 0.5) +
-  #geom_text() +
+  geom_point(col="blue", size = 1) +
   xlim(250, 400) + ylim(250, 400) +
@@
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
-  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
+  theme_bw() + Mytheme(size_labs = 11) + theme(aspect.ratio = 1) +
   coord_fixed(ratio = 1, expand = TRUE, clip = "on")
@@
   ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = montht)) +
-  geom_point(col="blue", size = 0.5) +
-  #xlim(250, 400) + ylim(250, 400) +
+  geom_point(col="blue", size = 5) +
+  xlim(270, 355) + ylim(270, 355) +
   labs(title = "pCO2 at ctd temperature",
@@
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
-  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
+  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio = 1) +
   coord_fixed(ratio = 1, expand = TRUE, clip = "on")
-#p_pco2_fb_remos_month
-ggsave(filename = "figures/pco2_fb_remos_monthly.png", plot = p_pco2_fb_remos_month, width = 25, height = 25, units = "cm")
+ggsave(filename = "figures/pco2_fb_remos_monthly.png", plot = p_pco2_fb_remos_month, width = 15, height = 15, units = "cm")
 # combine
@@
 # calculations as described by de Carlo et al. (2013)
-# we consider that mole fraction in air = ppm TO CHECK
-# By convention, a negative flux indicates fluxes directed from the atmosphere to the ocean, and a positive flux indicates fluxes directed from the ocean to the atmosphere.
-
+# we consider that mole fraction in air = ppm
+# By convention, a negative flux indicates fluxes directed from the atmosphere to the 
+# ocean, and a positive flux indicates fluxes directed from the ocean to the atmosphere.
 d_all <- d_all %>%

### 2023-01-05 awipev-CO2.Rmd
played with new function cunit
revised function cunit
Takahashi monthly added

@@
   round(approx(x=table, y=1:length(table), xout=x, ...)$y)
+}
+
+#################### Function cunit
+# cunit(d = 65,i = "g", o = "mol")
+# cunit(d = 65,i = "g", o = "mol")
+cunit <- function(d = 65, i = "gC", o = "molCO2") {
+    if (i == "gC" & o == "molCO2") {
+      out <- d/12
+      attributes(out) <- list(unit = "mol CO2")
+    }
+    if (i == "molC" & o == "molCO2") {
+      out <- d*44/12
+      attributes(out) <- list(unit = "mol CO2")
+    }
+  return(round(out, digits=2))
 }
@@
 taka <- d_all %>% # just for this chunk
-  dplyr::select(datetime, monthd, sal_fb_mix, temp_insitu_11m, pco2_fb_insi_temp) %>% 
+  dplyr::select(datetime, montht, monthd, sal_fb_mix, temp_insitu_11m, pco2_fb_insi_temp) %>% 
   dplyr::mutate(year = lubridate::year(datetime),
@@
                                           monthd %in% c(6, 7, 8) ~ "summer",
-                                          monthd %in% c(9, 10, 11) ~ "fall")) %>% 
+                                          monthd %in% c(9, 10, 11) ~ "fall")) #%>% 
+  # # eliminate years 2015 and 2021 which are incomplete
+  # dplyr::filter(datetime > as.POSIXct("2016-01-01 00:00:00") &
+  #                 datetime < as.POSIXct("2021-01-01 00:00:00"))
+
+# monthly 
+taka_month <- taka %>%
+  group_by(montht) %>%
+  dplyr::mutate(
+    pco2_thermal =
+      mean(pco2_fb_insi_temp, na.rm = TRUE) * exp(0.0423 * (
+        temp_insitu_11m - mean(temp_insitu_11m, na.rm = TRUE)
+      )),
+    pco2_nonthermal = pco2_fb_insi_temp * exp(0.0423 * (
+      mean(temp_insitu_11m, na.rm = TRUE) - temp_insitu_11m
+    ))
+  ) %>%
+  dplyr::summarise(
+    thermal = max(pco2_thermal, na.rm = TRUE) - min(pco2_thermal, na.rm = TRUE),
+    nonthermal = max(pco2_nonthermal, na.rm = TRUE) - min(pco2_nonthermal, na.rm = TRUE),
+    thermal_nonthermal = thermal / nonthermal
+  ) %>%
+  ungroup()
+# monthly plot
+taka_month_plt <- taka_month %>% 
+  ggplot() +
+  geom_point(aes(x = montht, y = thermal_nonthermal), col="blue", size = 2) +
+  labs(x="Month", y= "Thermal/non-thermal control of pCO2")  +
+  geom_hline(yintercept = 1, linetype = "dashed") +  
+  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio = 1) +
+  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
+taka_month_plt
+ggsave(filename = "figures/taka_month.png", plot = taka_month_plt, width = 25, height = 25, units = "cm")
+
+# annual 
+taka_year <- taka %>%
   # eliminate years 2015 and 2021 which are incomplete
   dplyr::filter(datetime > as.POSIXct("2016-01-01 00:00:00") &
-                  datetime < as.POSIXct("2021-01-01 00:00:00"))
-
-# annual 
-taka_year <- taka %>% 
+                  datetime < as.POSIXct("2021-01-01 00:00:00")) %>% 
   group_by(year) %>% 
@@
 `r knitr::kable(taka_season, digits = c(0, 1, 1, 2), caption = "Thermal vs non-thermal control of pCO2. Seasonal estimate.", format = "simple")`
-For seasonal analysis, December to February was considered winter, March
-to May was considered spring, June to August was considered summer, and
+`r knitr::kable(taka_month, digits = c(0, 1, 1, 2), caption = "Thermal vs non-thermal control of pCO2. Monthly estimate.", format = "simple")`
+![Monthly analysis of the thermal vs non-thermal control of pCO2](figures/taka_month.png)
+
+The relative importance of the temperature and biological effects maybe expressed in terms of the ratio,(temperature effect)/(biology effect) or difference [(temperature effect)-(biological effect)].
+
+For annual analysis, only complete years were used. For seasonal analysis, December to February was considered winter, March to May was considered spring, June to August was considered summer, and
 September to November was considered fall.
@@
 annual and seasonal basis. Thermal control is highest in winter and
-lowest in summer.
+lowest in summer. This is very clear with the monthly analysis.
 

### 2023-01-09 awipev-CO2.Rmd
availability fig for paper

@@
   geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
-  scale_fill_discrete(labels = labels) + 
+  scale_x_discrete(
+    labels = c(
+      "Flag",
+      'pCO2' = parse(text = TeX('$pCO_2$')),
+      "Salinity FerryBox",
+      "In situ salinity",
+      "Temperature FerryBox",
+      "In situ temperature",
+      "Durafet pH",
+      "seaFET pH"
+    )
+  ) +
   coord_flip() +
-  labs(x="", y="", title = "Distribution (%) of quality flags") +
-  Mytheme(size_labs = 8) #+
-  theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
-kable(z, digits = 1)
+  labs(x="", y = "Distribution of quality flags (%)") +
+  Mytheme(size_labs = 10) +
+  theme(legend.title = element_text(colour="black", size=10, face="bold")) #+
+  #theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
+#kable(z, digits = 1)
 # Monthly distribution of hourly data
@@
   geom_col(aes(x = montht, y = value, fill = name), position = "dodge", width = 0.75) +
-  scale_fill_discrete(name = "", labels = c("pCO2", "pH")) + 
+  scale_fill_discrete(name = "", labels = c(expression(paste(pCO[2])), "pH")) + 
   labs(x="Month", y="Number of data (thousands)", title = "") +
-  Mytheme(size_labs = 8) #+
+  Mytheme(size_labs = 10) #+
   #theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0.5, unit = "cm"))
@@
 p <- (p_avail / p_avail_month)
-p <- p + plot_annotation(tag_levels = 'A')
-p
+p <- p + plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold"))
 ggsave(filename = "figures/availability.png", plot = p, width = 20, height = 15, units = "cm")
+ggsave(filename = "figures/availability.pdf", plot = p, width = 20, height = 15, units = "cm")
 
 # deleted unneeded data
-rm(x, d_min, list=ls(pattern="^d2"))
+#rm(x, d_min, list=ls(pattern="^d2"))
 ```

### 2023-01-09 awipev-CO2.Rmd
availability fig for paper

--- 2023-01-05 awipev-CO2.Rmd
@@
   geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
-  scale_fill_discrete(labels = labels) + 
+  scale_x_discrete(
+    labels = c(
+      "Flag",
+      'pCO2' = parse(text = TeX('$pCO_2$')),
+      "Salinity FerryBox",
+      "In situ salinity",
+      "Temperature FerryBox",
+      "In situ temperature",
+      "Durafet pH",
+      "seaFET pH"
+    )
+  ) +
   coord_flip() +
-  labs(x="", y="", title = "Distribution (%) of quality flags") +
+  labs(x="", y = "Distribution of quality flags (%)") +
   Mytheme(size_labs = 8) #+
   theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
+  p_avail
 kable(z, digits = 1)
@@
   geom_col(aes(x = montht, y = value, fill = name), position = "dodge", width = 0.75) +
-  scale_fill_discrete(name = "", labels = c("pCO2", "pH")) + 
+  scale_fill_discrete(name = "", labels = c(expression(paste(pCO[2])), "pH")) + 
   labs(x="Month", y="Number of data (thousands)", title = "") +
@@
 ggsave(filename = "figures/availability.png", plot = p, width = 20, height = 15, units = "cm")
+ggsave(filename = "figures/availability.pdf", plot = p, width = 20, height = 15, units = "cm")
 
 # deleted unneeded data
-rm(x, d_min, list=ls(pattern="^d2"))
+#rm(x, d_min, list=ls(pattern="^d2"))
 ```

### 2023-01-09 awipev-CO2.Rmd
started figs for paper

--- 2023-01-05 awipev-CO2.Rmd
@@
   geom_bar(position = position_stack(reverse = TRUE), stat="identity", width = 0.3) +
-  scale_fill_discrete(labels = labels) + 
+  scale_x_discrete(
+    labels = c(
+      "Flag",
+      'pCO2' = parse(text = TeX('$pCO_2$')),
+      "Salinity FerryBox",
+      "In situ salinity",
+      "Temperature FerryBox",
+      "In situ temperature",
+      "Durafet pH",
+      "seaFET pH"
+    )
+  ) +
   coord_flip() +
-  labs(x="", y="", title = "Distribution (%) of quality flags") +
-  Mytheme(size_labs = 8) #+
-  theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
-kable(z, digits = 1)
-# Monthly distribution of hourly data
+  labs(x="", y = "Distribution of quality flags (%)") +
+  Mytheme(size_labs = 12) +
+  theme(legend.title = element_text(colour="black", size=12, face="bold")) #+
+  #theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
+#kable(z, digits = 1)
 d2 <- d_all %>% 
@@
   geom_col(aes(x = montht, y = value, fill = name), position = "dodge", width = 0.75) +
-  scale_fill_discrete(name = "", labels = c("pCO2", "pH")) + 
+  scale_fill_discrete(name = "", labels = c(expression(paste(pCO[2])), "pH")) + 
   labs(x="Month", y="Number of data (thousands)", title = "") +
-  Mytheme(size_labs = 8) #+
-  #theme(plot.margin = margin(t = 0, r = 0, b = 0, l = 0.5, unit = "cm"))
+  Mytheme(size_labs = 12) #+
 # Combine plots
 p <- (p_avail / p_avail_month)
-p <- p + plot_annotation(tag_levels = 'A')
-p
+p <- p + plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold"))
 ggsave(filename = "figures/availability.png", plot = p, width = 20, height = 15, units = "cm")
+ggsave(filename = "figures/essd/fig01.pdf", plot = p, width = 20, height = 15, units = "cm")
 
 # deleted unneeded data
-rm(x, d_min, list=ls(pattern="^d2"))
+#rm(x, d_min, list=ls(pattern="^d2"))
 ```
@@
   ggplot(aes(x = sal_fb_mix, y = at)) +
-  geom_point(col="blue", size = 0.5) +
+  geom_point(col="blue", size = 1) +
   labs(x= latex2exp::TeX("Salinity"),
@@
   #ggpmisc::stat_ma_eq(method = "lmodel2:OLS", aes(label = after_stat(eq.label))) +
-  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio=1) + 
+  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio=1) + 
   coord_fixed()
@@
   ggplot(aes(x = pco2_fb_insi_temp, y = pco2_calc_fb_insi_temp)) +
-  geom_point(col="blue", size = 0.5) +
+  geom_point(col="blue", size = 1) +
   xlim(180, 420) + ylim(180, 420) +
@@
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
-  theme_bw() + Mytheme(size_labs = 9) + theme(aspect.ratio = 1) +
+  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio = 1) +
   coord_fixed(ratio = 1, expand = TRUE, clip = "on")
@@
   labs(x = "Date", y=expression(paste(pH[T], " difference")), title = NULL) +
-  Mytheme(size_labs = 9, face_font = "plain") + theme(aspect.ratio=1)  + 
+  Mytheme(size_labs = 12, face_font = "plain") + theme(aspect.ratio=1)  + 
   scale_colour_discrete(guide="none") + 
@@
   ggplot(aes(x = ph_s_sf_temp_insi, y = pHint_tot_sf)) +
-  geom_point(col="blue", size = 0.5) +
+  geom_point(col="blue", size = 1) +
   xlim(8.05, 8.18) + ylim(8.05, 8.18) +
@@
 p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L00-S20', 'L00-P18', 'L00-M02'), y=value))+
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey70", outlier.color = "blue", outlier.size = 1) +
   geom_hline(yintercept = 0) +
@@
   facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
-  Mytheme(size_labs = 10)
-# diff_all_long$variable <- factor(diff_all_long$variable, levels = c('C[T]','Omega[a]', 'pH'))
-# fct_relevel(diff_all_long$variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite')
-
+  Mytheme(size_labs = 12)
 # calculate descriptive statistics
@@
 ggsave(filename = "figures/k1k2_all_pco2_at.png", plot = p, width = 25, height = 20, units = "cm")
+ggsave(filename = "figures/essd/fig02.pdf", plot = p, width = 25, height = 20, units = "cm")
+
 ```
@@
   facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
-  Mytheme(size_labs = 10)
-
+  Mytheme(size_labs = 12)
 # calculate descriptive statistics
@@
 ggsave(filename = "figures/k1k2_ct_at.png", plot = p, width = 25, height = 20, units = "cm")
-
+ggsave(filename = "figures/essd/fig03.pdf", plot = p, width = 25, height = 20, units = "cm")
 # prepare tibble to compare calculated pH and spec pH
@@
 g <- (at_s | pco2_calc_meas) / (offset_ph | pHspec_pHseafet)
-g <- g + patchwork::plot_annotation(tag_levels = 'A')
+g <- g + patchwork::plot_annotation(tag_levels = 'A' & theme(plot.tag = element_text(face = "bold")))
 ggsave(filename = "figures/pco2_ph_etc.png", plot = g)
-g
+ggsave(filename = "figures/essd/fig04.pdf", plot = g)
 ```

### 2023-01-10 awipev-CO2.Rmd
more on paper figures

@@
   geom_point(aes(x = montht, y = thermal_nonthermal), col="blue", size = 2) +
-  labs(x="Month", y= "Thermal/non-thermal control of pCO2")  +
+  labs(x="Month", y= latex2exp::TeX("Thermal/non-thermal control of $pCO_{2}"))  +
   geom_hline(yintercept = 1, linetype = "dashed") +  
@@
 ggsave(filename = "figures/taka_month.png", plot = taka_month_plt, width = 25, height = 25, units = "cm")
+ggsave(filename = "figures/essd/fig05.pdf", plot = taka_month_plt, width = 25, height = 25, units = "cm")
 
@@
 ```{r, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+# legend:
+# - Salinity below 8m
+# - In situ temperature (11m)
+# - pCO2 at 11 m and insitu Temperature, measued in blue, calculated from CT an AT in red
+# - In situ pH below 8 m at in situ Temperature, seaFET in blue, spectrophotometric in red
+# - Total alkalinity calculated from salinity in blue, discrete measurement in red
+
 size_point <- 0.3 # size of data points
 alpha <- 1 #transparency
-size_labs <- 6 # font size labels
+size_labs <- 12 # font size labels
 
@@
   geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
-  labs(title="Salinity (below 8 m)",x="", y="Salinity") +
+  labs(title=NULL,x="", y="Salinity") +
   Mytheme(size_labs = size_labs)
@@
   geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
-  labs(title="In situ temperature (11 m)",x="", y="Temperature (°C)") +
+  labs(title=NULL,x="", y="Temperature (°C)") +
   Mytheme(size_labs = size_labs)
@@
   geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
-  labs(title="Atmospheric PAR",x="", y="PAR (umol m-2 s-1)") +
+  labs(title="Atmospheric PAR",x="", 
+       y=latex2exp::TeX("PAR ($\\mu mol\\phantom{x}m^{-2}\\phantom{x}s^{-1})$")) +
   Mytheme(size_labs = size_labs)
@@
   geom_point(aes(x = datetime, y = pco2_calc_fb_insi_temp), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
-  labs(title=expression(paste(pCO[2], " at 11 m and in situ temperature")),
-       subtitle = "measured in blue; calculated from CT and AT in red",
+  labs(title=NULL,
+       subtitle = NULL,
        x="", y=TeX("pCO$_2$ ($\\mu atm$)")) +
@@
   geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
-  labs(title="In situ pH below 8 m at in situ temperature", 
-       subtitle = "seaFET in blue; spectrophotometric in red",
+  labs(title=NULL, 
+       subtitle =NULL,
        x = "", y=expression(paste(pH[T]))) +
@@
   geom_point(aes(x = datetime, y = at), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
-  labs(title="Total alkalinity", 
-       subtitle = "calculated from salinity in blue; discrete measurements in red",
+  labs(title=NULL, 
+       subtitle = NULL,
        x="", y=TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$")) +
@@
 g1 <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at)
-g1 <- g1 + plot_annotation(tag_levels = 'A')
+g1 <- g1 + plot_annotation(tag_levels = 'A' & theme(plot.tag = element_text(face = "bold")))
 ggsave(filename = "figures/time_series.png", plot = g1, width = 15, height = 30, units = "cm")
+
 #rm(list = ls(pattern = "ts_")) #delete big ggplot objects
@@
 alpha <- 1 #transparency
+size_labs <- 12 # font size labels
 d_bp <- d_all %>% # just for this chunk
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_sal_fb_mix), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title="Salinity (< 8 m)", y = "Salinity", x=NULL) +
-  Mytheme() +
+  labs(title="", y = "Salinity", x=NULL) +
+  Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title="In situ temperature (11 m)", y = "Temperature (°C)", x=NULL) +
-  Mytheme() +
+  labs(title=NULL, y = "Temperature (°C)", x=NULL) +
+  Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title=expression(paste(pCO[2], " at 11 m and in situ temperature")), y = TeX("pCO$_2$ ($\\mu atm$)"), x=NULL) +
-  Mytheme() +
+  labs(title=NULL, y = TeX("pCO$_2$ ($\\mu atm$)"), x=NULL) +
+  Mytheme(size_labs = size_labs)+
   theme(panel.grid.major.x = element_blank(),
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title="In situ pH below 8 m at in situ temperature", y = expression(paste(pH[T])), x=NULL) +
-  Mytheme() +
+  labs(title=NULL, y = TeX("$pH_T$"), x=NULL) +
+  Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title="Total alkalinity calculated from salinity", y = TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$"), x=NULL) +
-  Mytheme() +
+  labs(title=NULL, y = TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$"), x=NULL) +
+  Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
@@
 g2 <- (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
-g2 <- g2 + plot_annotation(tag_levels = 'A')
+g2 <- g2 + plot_annotation(tag_levels = 'A' & theme(plot.tag = element_text(face = "bold")))
 ggsave(filename = "figures/ts_boxplots.png", plot = g2)
@@
   (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
-g <- g + plot_annotation(tag_levels = 'A')
-ggsave(filename = "figures/ts_ts_boxplots.png", plot = g)
-rm(list = ls(pattern = "ts_"), d_bp) #delete big ggplot objects and temp data
+g <- g + plot_annotation(tag_levels = 'A' & theme(plot.tag = element_text(face = "bold")))
+ggsave(filename = "figures/essd/fig06.pdf", plot = g)
+# legend:
+# - Salinity below 8m
+# - In situ temperature (11m)
+# - pCO2 at 11 m and insitu Temperature, measued in blue, calculated from CT an AT in red
+# - In situ pH below 8 m at in situ Temperature, seaFET in blue, spectrophotometric in red
+# - Total alkalinity calculated from salinity in blue, discrete measurement in red
+
+#rm(list = ls(pattern = "ts_"), d_bp) #delete big ggplot objects and temp data
 #gc() #garbage collection

### 2023-01-12 awipev-CO2.Rmd
refine time series + boxplot

@@
   geom_boxplot(notch=FALSE, size=0.2, fill="blue", outlier.shape = NA, na.rm = TRUE) +
-  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_sal_fb_mix), col = "lightblue", size = size_point, na.rm = TRUE) +
+  geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix), col = "lightblue", size = size_point, na.rm = TRUE) +
   labs(title="", y = "Salinity", x=NULL) +
@@
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5)
+        aspect.ratio=0.5) +
+  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
+                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
 ts_temp_bp <- d_bp %>%
@@
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5)
+        aspect.ratio=0.5) +
+  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
+                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
 ts_pco2_bp <- d_bp %>%
@@
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5)
+        aspect.ratio=0.5) +
+  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
+                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
 ts_pH_bp <- d_bp %>%
@@
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5)
+        aspect.ratio=0.5) +
+  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
+                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
 ts_at_bp <- d_bp %>%
@@
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5)
+        aspect.ratio=0.5) +
+  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
+                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
 # Combine plots

### 2023-02-10 awipev-CO2.Rmd
Fixing bugs introduced by package updates

@@
 library("ggpmisc")
+if (!require("tidyselect")) install.packages("tidyselect")
+library("tidyselect")
 # todor::todor_file("awipev-CO2.Rmd")
@@
 ) %>% 
-  dplyr::select(sort(current_vars()))
+  dplyr::select(sort(everything()))
 
@@
 ```{r Range per month, echo = FALSE, warning = FALSE}
-range_month <-
-  d_all %>%
-  dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
-tbl_summary(by = montht,
-            missing = "no",
-            type = all_continuous() ~ "continuous2",
-            statistic = all_continuous() ~ c(
-              "{mean}",
-              "{median}",
-              "{p25}",
-              "{p75}",
-              "{min}",
-              "{max}"),
-            digits = list(sal_fb_mix ~ 1, temp_insitu_11m_mix ~ 1, temp_insitu_11m ~ 1, pHint_tot_sf_10m ~ 3))
-range_month
+# TODO
+# range_month <-
+#   d_all %>%
+#   dplyr::select(montht, sal_fb_mix, temp_insitu_11m_mix, temp_insitu_11m, pHint_tot_sf_10m) %>% 
+# tbl_summary(by = montht,
+#             missing = "no",
+#             type = all_continuous() ~ "continuous2"),
+#             statistic = all_continuous() ~ c(
+#               "{mean}",
+#               "{median}",
+#               "{p25}",
+#               "{p75}",
+#               "{min}",
+#               "{max}"
+#               ),
+#             digits = list(sal_fb_mix ~ 1, temp_insitu_11m_mix ~ 1, temp_insitu_11m ~ 1, pHint_tot_sf_10m ~ 3))
+# range_month
 ```
@@
   dplyr::left_join(d_all, dplyr::select(tmp, datetime, at_remos, pco2_remos_ctd_temp), by = "datetime") %>%
-  dplyr::select(sort(current_vars()))
+  dplyr::select(sort(everything()))
 tmp <- tmp %>% 
@@
   dplyr::left_join(d_all, dplyr::select(tmp, datetime, pco2_remos_4), by = "datetime") %>%
-  dplyr::select(sort(current_vars()))
+  dplyr::select(sort(everything()))
 
@@
 d_all <- dplyr::left_join(d_all, dplyr::select(atm_co2, datetime, co2_air), by = "datetime") %>% 
-  dplyr::select(sort(current_vars()))
+  dplyr::select(sort(everything()))
 
@@
 d_all <- dplyr::left_join(d_all, meteo, by = "datetime") %>% 
-  dplyr::select(sort(current_vars()))
+  dplyr::select(sort(everything()))
 ```
@@
   dplyr::filter(depth < 4) %>% 
-  drop_na() %>% 
+  dplyr::filter(if_all(everything(), is.finite)) %>% 
   ggplot(aes(x = pco2_fb_ctd_temp, y = pco2_remos_ctd_temp, label = monthd)) +
@@
     Patm=1, P=1.1, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$OmegaAragonite)
+summary(tmp$OmegaAragonite)
 #plot
@@
   Mytheme(size_labs = size_labs)
-ts_oa
 ggsave(filename = "figures/OmegaAragonite.png", plot = ts_oa, width = 15, height = 10, units = "cm")
 ```
-
 ### Whole time series plot

### 2023-02-14 awipev-CO2.Rmd
boron estimated according to Lee et al. (2010)

@@
                          k1k2 = "l", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74"),
+                         pHscale = "T", b="l10"),
    ph_s_sf_temp_4 = pHinsi(pH = pH_seafet$ph_s_sf, # with Lueker
@@
                          k1k2 = "l", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
   )
@@
                               Tlab = pH_durafet$temp_s_lab, Pinsi = 0, S = pH_durafet$sal_fb, 
-                              Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74"),
+                              Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="l10"),
     ph_s_dur_temp_4 = pHinsi(pH = pH_durafet$ph_s_dur,
@@
                              kf = "dg", ks = "d",
-                             pHscale = "T", b = "u74")
+                             pHscale = "T", b = "l10")
    )
@@
   dplyr::filter(is.na(sal_fb)  | is.na(temp_fb) | is.na(at) | is.na(ct))
-carb <- carb(15, discrete_no_na$at_mean_interp*1e-6, discrete_no_na$ct_mean_interp*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+carb <- carb(15, discrete_no_na$at_mean_interp*1e-6, discrete_no_na$ct_mean_interp*1e-6, S = discrete_no_na$sal_fb, T = discrete_no_na$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
 discrete_no_na$ph_calc_fb <- carb$pH # pH to compare with durafet pH (at Ferrybox temp and sal)
@@
   dplyr::filter(datetime < as.POSIXct("2018-01-01") | datetime > as.POSIXct("2018-02-03"))
-tmp$pHint_tot_sf_temp_4 <- seacarb::pHinsi(pH=tmp$pHint_tot_sf, ALK=mean(tmp$at*1e-6, na.rm = TRUE), Tinsi=4, Tlab=tmp$temp_sf, Pinsi=tmp$depth/10, S=tmp$sal_insitu_ctd_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+tmp$pHint_tot_sf_temp_4 <- seacarb::pHinsi(pH=tmp$pHint_tot_sf, ALK=mean(tmp$at*1e-6, na.rm = TRUE), Tinsi=4, Tlab=tmp$temp_sf, Pinsi=tmp$depth/10, S=tmp$sal_insitu_ctd_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="l10")
 d_all <- d_all %>% 
@@
   tidyr::drop_na()
-tmp$pH_dur_temp_4 <- seacarb::pHinsi(pH=tmp$pH_dur, ALK=tmp$at, Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+tmp$pH_dur_temp_4 <- seacarb::pHinsi(pH=tmp$pH_dur, ALK=tmp$at, Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="l10")
 d_all <- d_all %>% 
@@
   tidyr::drop_na()
-tmp$pH_calc_fb_temp_4 <- pHinsi(pH = tmp$ph_calc_fb, ALK=tmp$at*1e-6, Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="u74")
+tmp$pH_calc_fb_temp_4 <- pHinsi(pH = tmp$ph_calc_fb, ALK=tmp$at*1e-6, Tinsi=4, Tlab=tmp$temp_fb, Pinsi=11/10, S=tmp$sal_fb_mix, Pt=0, Sit=0, k1k2 = "l", kf = "dg", ks="d", pHscale = "T", b="l10")
 
@@
                  Pt = c(0, min(d_all$po4/1e6, na.rm = TRUE), max(d_all$po4/1e6, na.rm = TRUE)), Sit = 0,
-                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
 diff_po4_0a <- carb_po4_1[1,] - carb_po4_1[3,] # diff between no PO4 and max PO4
@@
                 Pt = 0, Sit = c(0, min(d_all$si/1e6, na.rm = TRUE), max(d_all$si/1e6, na.rm = TRUE)), 
-                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
 diff_Si_0a <- carb_Si_1[1,] - carb_Si_1[3,] # diff between no Si and max Si
@@
                  Pt = c(0, min(d_all$po4/1e6, na.rm = TRUE), max(d_all$po4/1e6, na.rm = TRUE)), Sit = 0,
-                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
 diff_po4_0b <- carb_po4_2[1,] - carb_po4_2[3,] # diff between no PO4 and max PO4
@@
                 Pt = 0, Sit = c(0, min(d_all$si/1e6, na.rm = TRUE), max(d_all$si/1e6, na.rm = TRUE)), 
-                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+                k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
 diff_Si_0b <- carb_Si_2[1,] - carb_Si_2[3,] # diff between no Si and max Si
@@
                  Pt = c(0, max(d_all$po4/1e6, na.rm = TRUE)), Sit = c(0, max(d_all$si/1e6, na.rm = TRUE)),
-                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
 carb_2 <- carb(15, mean_at_calc*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0, 
                  Pt = c(0, max(d_all$po4/1e6, na.rm = TRUE)), Sit = c(0, max(d_all$si/1e6, na.rm = TRUE)),
-                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+                 k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
 diff_max_0a <- carb_1[1,] - carb_1[2,] # pco2-AT: diff between (0 PO4 and Si) and (max PO4 and Si)
@@
                           T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
-                          b="u74", evar1=3, evar2 = 4e-6)
+                          b="l10", evar1=3, evar2 = 4e-6)
 errors_at_ct <- seacarb::errors(flag=15, var1=1e-6*mean_at, var2=1e-6*mean_ct, S=mean_sal,
                           T=mean_temp, P=0, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T",
-                          b="u74", evar1=4e-6, evar2 = 4e-6)
+                          b="l10", evar1=4e-6, evar2 = 4e-6)
 errors <- tibble(
@@
 #                  Pt = 0, Sit = 0,
-#                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+#                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
 # carb_s_1 <- carb(24, mean_pco2, mean_at*1e-6, S = mean_sal, T = mean_temp, P = 0, 
 #                  Pt = 0, Sit = 0,
-#                  k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+#                  k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "l10")
 # diff_ls_1 <- carb_l_1 - carb_s_1
@@
 #                  Pt = 0, Sit = 0,
-#                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+#                  k1k2 = "l", kf = "dg", ks = "d", pHscale = "T", b = "l10")
 # carb_s_2 <- carb(15, mean_at*1e-6, mean_ct*1e-6, S = mean_sal, T = mean_temp, P = 0,
 #                 Pt = 0, Sit = 0, 
-#                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "u74")
+#                 k1k2 = "s20", kf = "dg", ks = "d", pHscale = "T", b = "l10")
 # diff_ls_2 <- carb_l_2 - carb_s_2
@@
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks = "d", 
-               pHscale = "T", b = "u74")
+               pHscale = "T", b = "l10")
 # normalize Lueker-derived pH at 4°C
@@
                          S = carb_l$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
 # Using Sulpis
@@
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks = "d", 
-               pHscale = "T", b = "u74")
+               pHscale = "T", b = "l10")
 # normalize Sulpis-derived pH at 4°C
@@
                          S = carb_s$S, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
 # Using Papadimitriou
@@
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks = "d", 
-               pHscale = "T", b = "u74")
+               pHscale = "T", b = "l10")
 # normalize Papadimitriou-derived pH at 4°C
@@
                          S = carb_p$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
 # Using Millero et al. (2002)
@@
                T = tmp$temp_fb, P = 0, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks = "d", 
-               pHscale = "T", b = "u74")
+               pHscale = "T", b = "l10")
 # normalize Millero et al. (2002)-derived pH at 4°C
@@
                          S = carb_m$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
 # calculate difference Lueker - Sulpis
@@
                          S = sal_fb_mix, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d",
-                         pHscale = "T", b="u74"),
+                         pHscale = "T", b="l10"),
    ph_s_dur_temp_4_s20 = pHinsi(pH = ph_s_dur_temp_fb, # Sulpis
@@
                          S = sal_fb_mix, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d",
-                         pHscale = "T", b="u74"),       # Millero 02
+                         pHscale = "T", b="l10"),       # Millero 02
    ph_s_dur_temp_4_p18 = pHinsi(pH = ph_s_dur_temp_fb, # Papadimitriou
@@
                          S = sal_fb_mix, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d",
-                         pHscale = "T", b="u74"),
+                         pHscale = "T", b="l10"),
    ph_s_dur_temp_4_m02 = pHinsi(pH = ph_s_dur_temp_fb,  # Millero 02
@@
                          S = sal_fb_mix, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d",
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
    ) %>% 
@@
                          S = carb_l1$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
 # Using Sulpis
@@
                          S = carb_s1$S, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
 # Using Papadimitriou
@@
                          S = carb_p1$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
 # Using Millero et al. (2002)
@@
                          S = carb_m1$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
 # calculate difference Lueker - Sulpis
@@
                          S = sal_fb_mix, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d",
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
    )
@@
                          S = carb_l2$S, Pt = 0, Sit = 0, k1k2 = "l", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
 # Using Sulpis
@@
                          S = carb_s2$S, Pt = 0, Sit = 0, k1k2 = "s20", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
 # Using Papadimitriou
@@
                          S = carb_p2$S, Pt = 0, Sit = 0, k1k2 = "p18", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
 # Using Millero et al. (2002)
@@
                          S = carb_m2$S, Pt = 0, Sit = 0, k1k2 = "m02", kf = "dg", ks="d", 
-                         pHscale = "T", b="u74")
+                         pHscale = "T", b="l10")
 # calculate difference Lueker - Sulpis
@@
       pHscale = "T",
-      b = "u74"
+      b = "l10"
     )$pCO2
@@
     Patm=1, P=1.1, Pt=0, Sit=0, 
-    k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$DIC * 1e6
+    k1k2="l", kf="dg", ks="d", pHscale="T", b="l10")$DIC * 1e6
     )
@@
 deconv_pCO2_T <- tibble(date = d$date,
-                        deconv_pCO2_T=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$mS, T=d$T, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2
+                        deconv_pCO2_T=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$mS, T=d$T, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="l10")$pCO2
 )
@@
                      deconv_pCO2_S=carb(flag=15, var1=d$mAT, var2=d$mCT, S=d$S, T=d$mT, P=d$P, Pt=d$Pt, 
-                                      Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2
+                                      Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="l10")$pCO2
                      )
@@
 deconv_pCO2_AT <- tibble(date=d$date,
-                     deconv_pCO2_AT=carb(flag=15, var1=d$AT, var2=d$mCT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2
+                     deconv_pCO2_AT=carb(flag=15, var1=d$AT, var2=d$mCT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="l10")$pCO2
 )
@@
 deconv_pCO2_CT <- tibble(date=d$date,
-                     deconv_pCO2_CT=carb(flag=15, var1=d$mAT, var2=d$CT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$pCO2
+                     deconv_pCO2_CT=carb(flag=15, var1=d$mAT, var2=d$CT, S=d$mS, T=d$mT, P=d$P, Pt=d$Pt, Sit=d$Sit, k1k2="l", kf="dg", ks="d", pHscale="T", b="l10")$pCO2
 )
@@
     flag = 24, var1 = pco2_fb, var2 = at_calc*1e-6, S=sal_fb_mix, T=temp_fb, 
-    Patm=1, P=1.1, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T", b="u74")$OmegaAragonite)
+    Patm=1, P=1.1, Pt=0, Sit=0, k1k2="l", kf="dg", ks="d", pHscale="T", b="l10")$OmegaAragonite)
 summary(tmp$OmegaAragonite)

### 2023-02-21 awipev-CO2.Rmd
added chunk Kongfjorden map

@@
 library("tidyselect")
+if (!require("usethis")) install.packages("usethis")
+library("usethis")
+if (!require("ggOceanMaps")) install.packages("ggOceanMaps")
+library("ggOceanMapsData")
+
 # todor::todor_file("awipev-CO2.Rmd")
+#usethis::edit_r_profile()
+# to add to .Rprofile file: {.ggOceanMapsenv <- new.env(); .ggOceanMapsenv$datapath <- 'YourCustomPath'}
 
@@
 
+```
+
+```{r make location map}
+kong_map <- basemap(limits = c(11.00, 12.69, 78.86, 79.10), bathymetry = TRUE, shapefiles = "Svalbard",
+        legends = FALSE, glaciers = TRUE, lat.interval = 0.1, lon.interval = 0.5)
+ggsave(filename = "figures/kong_map.eps", plot = kong_map, width = 25, height = 25, units = "cm")
 ```

### 2023-02-21 awipev-CO2.Rmd
Added map Svalbard

@@
 ```{r make location map}
+svalbard_map <- basemap(limits = c(10.00, 22.00, 76.3, 80.9), bathymetry = FALSE, shapefiles = "Arctic",
+        legends = FALSE, glaciers = FALSE)
+ggsave(filename = "figures/svalbard_map.png", plot = svalbard_map, width = 25, height = 25, units = "cm")
+ggsave(filename = "figures/svalbard_map.eps", plot = svalbard_map, width = 25, height = 25, units = "cm")
 kong_map <- basemap(limits = c(11.00, 12.69, 78.86, 79.10), bathymetry = TRUE, shapefiles = "Svalbard",
         legends = FALSE, glaciers = TRUE, lat.interval = 0.1, lon.interval = 0.5)
+ggsave(filename = "figures/kong_map.png", plot = kong_map, width = 25, height = 25, units = "cm")
 ggsave(filename = "figures/kong_map.eps", plot = kong_map, width = 25, height = 25, units = "cm")
 ```
+
+#`r include_graphics("figures/kong_map.png")`
 

### 2023-02-24 awipev-CO2.Rmd
minor commenting
Export latex tables

--- 2023-02-14 awipev-CO2.Rmd
@@
 library("tidyselect")
+if (!require("usethis")) install.packages("usethis")
+library("usethis")
+if (!require("ggOceanMaps")) install.packages("ggOceanMaps")
+library("ggOceanMaps")
+
 # todor::todor_file("awipev-CO2.Rmd")
+#usethis::edit_r_profile()
+# to add to .Rprofile file: {.ggOceanMapsenv <- new.env(); .ggOceanMapsenv$datapath <- 'YourCustomPath'}
 
@@
 ```
+
+# ```{r make location map}
+# svalbard_map <- basemap(limits = c(10.00, 22.00, 76.3, 80.9), bathymetry = FALSE, shapefiles = "Arctic",
+#         legends = FALSE, glaciers = FALSE)
+# ggsave(filename = "figures/svalbard_map.png", plot = svalbard_map, width = 25, height = 25, units = "cm")
+# ggsave(filename = "figures/svalbard_map.eps", plot = svalbard_map, width = 25, height = 25, units = "cm")
+# kong_map <- basemap(limits = c(11.00, 12.69, 78.86, 79.10), bathymetry = TRUE, shapefiles = "Svalbard",
+#         legends = FALSE, glaciers = TRUE, lat.interval = 0.1, lon.interval = 0.5)
+# ggsave(filename = "figures/kong_map.png", plot = kong_map, width = 25, height = 25, units = "cm")
+# ggsave(filename = "figures/kong_map.eps", plot = kong_map, width = 25, height = 25, units = "cm")
+# ```
 
@@
 save(k1k2_pco2_at, file="reports/k1k2_pco2_at.RData")
-```
-
+
+#export latex table
+tables_path <- "~/kDrive/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/paper/tables/"
+knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "latex") %>% 
+save_kable(file=paste0(tables_path,"diff_table_pco2_at.tex"))
+```
 **_Comparison of various formulations compared to Lueker et al. (2000)_**
@@
 save(k1k2_at_ct, file="reports/k1k2_at_ct.RData")
+
+#export latex table
+tables_path <- "~/kDrive/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/paper/tables/"
+knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "latex") %>% 
+save_kable(file=paste0(tables_path,"diff_table_at_ct"))
 ```

### 2023-02-28 awipev-CO2.Rmd
rounding pangaea data

--- 2023-02-21 awipev-CO2.Rmd
@@
 ```{r make location map}
-kong_map <- basemap(limits = c(11.00, 12.69, 78.86, 79.10), bathymetry = TRUE, shapefiles = "Svalbard",
-        legends = FALSE, glaciers = TRUE, lat.interval = 0.1, lon.interval = 0.5)
-ggsave(filename = "figures/kong_map.eps", plot = kong_map, width = 25, height = 25, units = "cm")
-```
+# svalbard_map <- basemap(limits = c(10.00, 22.00, 76.3, 80.9), bathymetry = FALSE, shapefiles = "Arctic",
+#         legends = FALSE, glaciers = FALSE)
+# ggsave(filename = "figures/svalbard_map.png", plot = svalbard_map, width = 25, height = 25, units = "cm")
+# ggsave(filename = "figures/svalbard_map.eps", plot = svalbard_map, width = 25, height = 25, units = "cm")
+# kong_map <- basemap(limits = c(11.00, 12.69, 78.86, 79.10), bathymetry = TRUE, shapefiles = "Svalbard",
+#         legends = FALSE, glaciers = TRUE, lat.interval = 0.1, lon.interval = 0.5)
+# ggsave(filename = "figures/kong_map.png", plot = kong_map, width = 25, height = 25, units = "cm")
+# ggsave(filename = "figures/kong_map.eps", plot = kong_map, width = 25, height = 25, units = "cm")
+```
+
+<!-- `r include_graphics("figures/kong_map.png")` -->
 
@@
 pangaea <- as_tibble(d_all) %>% 
-  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb_insi_temp, pco2_calc_fb_insi_temp, at_calc, pH_dur, pHint_tot_sf) %>%
-  dplyr::rename(`pressure [dbar]` = depth,
-                `s_insitu [unit]` = sal_insitu_ctd,
-                `s_fb [unit]` = sal_fb, 
-                `t_11m [°C]` = temp_insitu_11m,
-                `t_ctd [°C]` = temp_insitu_ctd, 
-                `t_fb [°C]` = temp_fb, 
-                `t_sf [°C]` = temp_sf, 
-                `at [umol kg-1]` = at, 
-                `at_calc [umol kg-1]` = at_calc,
-                `ct [umol kg-1]` = ct, 
-                `ph_s_sf_t_insi [total scale]` = ph_s_sf_temp_insi, 
-                `ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
-                `pco2 [uatm]` = pco2_fb_insi_temp,
-                `pco2_calc [uatm]` = pco2_calc_fb_insi_temp,
-                `pH_sf [total scale]` = pHint_tot_sf,
-                `pH_dur [total scale]` = pH_dur,
-                `pH_calc [total scale]` = ph_calc_fb
-                )
+  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb_insi_temp, pco2_calc_fb_insi_temp, at_calc, pHint_tot_sf) %>%
+  dplyr::rename(`pressure [dbar]` = depth, #        hydrostatic pressure (profiler)
+                `s_insitu [unit]` = sal_insitu_ctd, # salinity in situ (profiler)
+                `s_fb [unit]` = sal_fb,             # salinity (FerryBox)
+                `t_11m [°C]` = temp_insitu_11m,     # temperature in situ (static at 11 m)
+                `t_ctd [°C]` = temp_insitu_ctd,     # temperature in situ (profiler)
+                `t_fb [°C]` = temp_fb,              # temperature (FerryBox)
+                `t_sf [°C]` = temp_sf,              # temperature SeaFET (profiler)
+                `at [umol kg-1]` = at,              # total alkalinity in situ, discrete measurements
+                `at_calc [umol kg-1]` = at_calc,    # total alkalinity calculated from salinity
+                `ct [umol kg-1]` = ct,              # dissolved inotganic carbon in situ, discrete measurements
+                `ph_discrete [total scale]` = ph_s_sf_temp_insi, # spectrophotometric pH in situ (total scale) at in situ temperature (discrete)
+                #`ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
+                `pco2 [uatm]` = pco2_fb_insi_temp,  # Partial pressure of CO2 (FerryBox)
+                #`pco2_calc [uatm]` = pco2_calc_fb_insi_temp,
+                `pH_sensor [total scale]` = pHint_tot_sf, # pH in situ at in situ temperature (profiler)
+                #`pH_dur [total scale]` = pH_dur,
+                #`pH_calc [total scale]` = ph_calc_fb
+                ) %>% 
+  dplyr::mutate(across(starts_with("pressure"), ~ round(.x, digits = 2)),
+                across(starts_with("s_"), ~ round(.x, digits = 2)),
+                across(starts_with("t_"), ~ round(.x, digits = 2)),
+                across(starts_with("ph"), ~ round(.x, digits = 3)),
+                across(starts_with("at") | 
+                         starts_with("ct") |
+                         starts_with("pco2"), ~ round(.x, digits = 1)),
+                )
+
 saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)

### 2023-03-01 awipev-CO2.Rmd
various

--- 2023-02-24 awipev-CO2.Rmd
@@
 knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "latex") %>% 
-save_kable(file=paste0(tables_path,"diff_table_pco2_at.tex"))
+kableExtra::save_kable(file=paste0(tables_path,"diff_table_pco2_at.tex"))
 ```
@@
 knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "latex") %>% 
-save_kable(file=paste0(tables_path,"diff_table_at_ct"))
+kableExtra::save_kable(file=paste0(tables_path,"diff_table_at_ct.tex"))
 ```
@@
 g <- sal_delta_plt / temp_delta_plt / den_delta_plt
-g <- g + plot_annotation(tag_levels = 'a')
+g <- g + plot_annotation(tag_levels = 'A')& 
+                             theme(plot.tag = element_text(face = "bold"))
 print(g)
 ggsave(filename = "figures/deltas.png", plot = g, width = 15, height = 20, units = "cm")
+ggsave(filename = "figures/essd/deltas.pdf", plot = g, width = 15, height = 20, units = "cm")
+
 # pCO2 deltas
 g <-  pco2_delta_plt / pco2_4_delta_plt
-g <- g + plot_annotation(tag_levels = 'a')
+g <- g + plot_annotation(tag_levels = 'A') & 
+                             theme(plot.tag = element_text(face = "bold"))
 g
 ggsave(filename = "figures/deltas_pco2.png", plot = g, width = 15, height = 20, units = "cm")
+ggsave(filename = "figures/essd/deltas_pco2.pdf", plot = g, width = 15, height = 20, units = "cm")
+
 ```
@@
 ggsave(filename = "figures/pco2_fb_remos_monthly.png", plot = p_pco2_fb_remos_month, width = 15, height = 15, units = "cm")
+ggsave(filename = "figures/essd/pco2_fb_remos_month.pdf", plot = p_pco2_fb_remos_month, width = 15, height = 15, units = "cm")
+
 # combine
 g <- p_pco2_fb_remos / p_pco2_fb_remos_month
-g <- g + patchwork::plot_annotation(tag_levels = 'A')
+g <- g + patchwork::plot_annotation(tag_levels = 'A')  & 
+                             theme(plot.tag = element_text(face = "bold"))
 ggsave(filename = "figures/pco2_compare.png", plot = g)
@@
 ggsave(filename = "figures/ts_air_sea.png", plot = ts_air_sea, width = 20, units = "cm")
+ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea, width = 20, units = "cm")
+
 #rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
@@
 ggsave(filename = "figures/OmegaAragonite.png", plot = ts_oa, width = 15, height = 10, units = "cm")
+ggsave(filename = "figures/essd/OmegaAragonite.pdf", plot = ts_oa, width = 15, height = 10, units = "cm")
+
 ```
@@
 g1 <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at)
-g1 <- g1 + plot_annotation(tag_levels = 'A' & theme(plot.tag = element_text(face = "bold")))
+g1 <- g1 + plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold"))
 ggsave(filename = "figures/time_series.png", plot = g1, width = 15, height = 30, units = "cm")
@@
 g2 <- (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
-g2 <- g2 + plot_annotation(tag_levels = 'A' & theme(plot.tag = element_text(face = "bold")))
+g2 <- g2 + plot_annotation(tag_levels = 'A') & 
+                             theme(plot.tag = element_text(face = "bold"))
 ggsave(filename = "figures/ts_boxplots.png", plot = g2)
@@
 g <- (at_s | pco2_calc_meas) / (offset_ph | pHspec_pHseafet)
-g <- g + patchwork::plot_annotation(tag_levels = 'A' & theme(plot.tag = element_text(face = "bold")))
+g <- g + patchwork::plot_annotation(tag_levels = 'A') & 
+  theme(plot.tag = element_text(face = "bold"))
 ggsave(filename = "figures/pco2_ph_etc.png", plot = g)
@@
   (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
-g <- g + plot_annotation(tag_levels = 'A' & theme(plot.tag = element_text(face = "bold")))
-ggsave(filename = "figures/essd/fig06.pdf", plot = g)
+g <- g + plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold"))
+ggsave(filename = "figures/essd/ts.pdf", plot = g)
 # legend:

### 2023-03-01 awipev-CO2.Rmd

@@
 
-# ```{r make location map}
+```{r make location map}
 # svalbard_map <- basemap(limits = c(10.00, 22.00, 76.3, 80.9), bathymetry = FALSE, shapefiles = "Arctic",
@@
 # ggsave(filename = "figures/kong_map.eps", plot = kong_map, width = 25, height = 25, units = "cm")
-# ```
+```
 

### 2023-03-01 awipev-CO2.Rmd
Pangaea dataset finalized

@@
 pangaea <- as_tibble(d_all) %>% 
-  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_fb, temp_sf, at, ct, ph_s_sf_temp_insi, ph_s_dur_temp_fb, ph_calc_fb, pco2_fb_insi_temp, pco2_calc_fb_insi_temp, at_calc, pHint_tot_sf) %>%
+  dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_sf, temp_fb, pco2_fb_insi_temp, pHint_tot_sf, at, ct, ph_s_sf_temp_insi) %>%
   dplyr::rename(`pressure [dbar]` = depth,          # hydrostatic pressure (profiler)
@@
                 `at [umol kg-1]` = at,              # total alkalinity in situ, discrete measurements
-                `at_calc [umol kg-1]` = at_calc,    # total alkalinity calculated from salinity
-                `ct [umol kg-1]` = ct,              # dissolved inotganic carbon in situ, discrete measurements
+                #`at_calc [umol kg-1]` = at_calc,    # total alkalinity calculated from salinity
+                `ct [umol kg-1]` = ct,              # dissolved inorganic carbon in situ, discrete measurements
                 `ph_discrete [total scale]` = ph_s_sf_temp_insi, # spectrophotometric pH in situ (total scale) at in situ temperature (discrete)
                 #`ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
-                `pco2 [uatm]` = pco2_fb_insi_temp,  # Partial pressure of CO2 (FerryBox)
+                `pco2 [uatm]` = pco2_fb_insi_temp,  # partial pressure of CO2 (FerryBox)
                 #`pco2_calc [uatm]` = pco2_calc_fb_insi_temp,
@@
                 )
-
-saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
-write_csv(pangaea, file = paste0(path, "fb_data/pangaea.csv"))
+# replace NaNs by NAs
+pangaea <- pangaea %>% 
+  mutate_all(~ifelse(is.nan(.), NA, .))
+
+#saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
+#write_csv(pangaea, file = paste0(path, "fb_data/pangaea.csv"))
+saveRDS(file= "data/AWIPEV-CO2_v1.rds", pangaea)
+write_csv(pangaea, file = "data/AWIPEV-CO2_v1.csv")
 # Metadata Pangaea

### 2023-03-01 awipev-CO2.Rmd
Pangaea dataset finalized

@@
                 #`ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
-                `pco2 [uatm]` = pco2_fb_insi_temp,  # partial pressure of CO2 (FerryBox)
+                `pco2 [uatm]` = pco2_fb_insi_temp,  # Partial pressure of CO2 (FerryBox)
                 #`pco2_calc [uatm]` = pco2_calc_fb_insi_temp,

### 2023-03-02 awipev-CO2.Rmd
update varianle names in Pangaea, some tweeks in figures

@@
 
-**Results are shown below but it does not make sense to udse them in the manuscript. Btter to use all pCO2-AT data as above.**
+**Results are shown below but it does not make sense to use them in the manuscript. Btter to use all pCO2-AT data as above.**
 
@@
   dplyr::select(datetime, depth, sal_insitu_ctd, sal_fb, temp_insitu_11m, temp_insitu_ctd, temp_sf, temp_fb, pco2_fb_insi_temp, pHint_tot_sf, at, ct, ph_s_sf_temp_insi) %>%
-  dplyr::rename(`pressure [dbar]` = depth,          # hydrostatic pressure (profiler)
-                `s_insitu [unit]` = sal_insitu_ctd, # salinity in situ (profiler)
-                `s_fb [unit]` = sal_fb,             # salinity (FerryBox)
-                `t_11m [°C]` = temp_insitu_11m,     # temperature in situ (static at 11 m)
-                `t_ctd [°C]` = temp_insitu_ctd,     # temperature in situ (profiler)
-                `t_fb [°C]` = temp_fb,              # temperature (FerryBox)
-                `t_sf [°C]` = temp_sf,              # temperature SeaFET (profiler)
-                `at [umol kg-1]` = at,              # total alkalinity in situ, discrete measurements
+  dplyr::rename(
+    `pressure_profiler [dbar]` = depth,
+    # hydrostatic pressure
+    `salinity_PSS78_profiler [unit]` = sal_insitu_ctd,
+    # salinity in situ
+    `salinity_PSS78_ferrybox [unit]` = sal_fb,
+    # salinity (FerryBox)
+    `temperature_ITS90_11m [°C]` = temp_insitu_11m,
+    # temperature in situ (static at 11 m)
+    `temperature_ITS90_profiler [°C]` = temp_insitu_ctd,
+    # temperature in situ (profiler)
+    `temperature_ITS90_ferrybox [°C]` = temp_fb,
+    # temperature (FerryBox)
+    `temperature_ITS90_seafet_profiler [°C]` = temp_sf,
+    # temperature SeaFET (profiler)
+    `ta_discrete [umol kg-1]` = at,
+    # total alkalinity in situ, discrete measurements
     #`at_calc [umol kg-1]` = at_calc,    # total alkalinity calculated from salinity
-                `ct [umol kg-1]` = ct,              # dissolved inorganic carbon in situ, discrete measurements
-                `ph_discrete [total scale]` = ph_s_sf_temp_insi, # spectrophotometric pH in situ (total scale) at in situ temperature (discrete)
+    `dic_discrete [umol kg-1]` = ct,
+    # dissolved inorganic carbon in situ, discrete measurements
+    `ph_insitu_temperature_discrete [total scale]` = ph_s_sf_temp_insi,
+    # spectrophotometric pH in situ (total scale) at in situ temperature (discrete)
     #`ph_s_dur_t_fb [total scale]` = ph_s_dur_temp_fb,
-                `pco2 [uatm]` = pco2_fb_insi_temp,  # Partial pressure of CO2 (FerryBox)
+    `pco2_insitu_temperature_ferrybox [uatm]` = pco2_fb_insi_temp,
+    # partial pressure of CO2 at in situ temperature (FerryBox)
     #`pco2_calc [uatm]` = pco2_calc_fb_insi_temp,
-                `pH_sensor [total scale]` = pHint_tot_sf, # pH in situ at in situ temperature (profiler)
+    `ph_insitu_temperature_profiler [total scale]` = pHint_tot_sf,
+    # pH in situ at in situ temperature (profiler)
     #`pH_dur [total scale]` = pH_dur,
@@
   ) %>% 
-  dplyr::mutate(across(starts_with("pressure"), ~ round(.x, digits = 2)),
-                across(starts_with("s_"), ~ round(.x, digits = 2)),
-                across(starts_with("t_"), ~ round(.x, digits = 2)),
+  dplyr::mutate(
+    across(starts_with("pressure"), ~ round(.x, digits = 2)),
+    across(starts_with("salinity"), ~ round(.x, digits = 2)),
+    across(starts_with("temperature"), ~ round(.x, digits = 2)),
     across(starts_with("ph"), ~ round(.x, digits = 3)),
-                across(starts_with("at") | 
-                         starts_with("ct") |
-                         starts_with("pco2"), ~ round(.x, digits = 1)),
+    across(
+      starts_with("ta") |
+        starts_with("dic") |
+        starts_with("pco2"),
+      ~ round(.x, digits = 1)
+    ),
   )
@@
   xlim(250, 400) + ylim(250, 400) +
-  labs(title = "pCO2 at ctd temperature",
+  #labs(title = "pCO2 at ctd temperature",
+  labs(title = NULL,
        x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$"),
@@
   xlim(270, 355) + ylim(270, 355) +
-  labs(title = "pCO2 at ctd temperature",
+  #labs(title = "pCO2 at ctd temperature",
+  labs(title = NULL,
        x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$"),
@@
   ylim(0, 3) +
-  labs(title="Aragonite saturation state (11 m)",x="", y=latex2exp::TeX("$\\Omega_{aragonite}$")) +
+  labs(title="",x="", y=latex2exp::TeX("$\\Omega_{aragonite}$")) +
   Mytheme(size_labs = size_labs)

### 2023-03-02 awipev-CO2.Rmd
refineing figs for paper

@@
   labs(x="", y = "Distribution of quality flags (%)") +
-  Mytheme(size_labs = 12) +
-  theme(legend.title = element_text(colour="black", size=12, face="bold")) #+
+  Mytheme(size_labs = 14) +
+  theme(legend.title = element_text(colour="black", size=14, face="bold"),
+        axis.title.x = element_text(colour="black", size=14, face="bold")) #+
   #theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
@@
   labs(x="Month", y="Number of data (thousands)", title = "") +
-  Mytheme(size_labs = 12) #+
+  Mytheme(size_labs = 14,) +
+  theme(axis.title.x = element_text(colour="black", size=14, face="bold"),
+        axis.title.y = element_text(colour="black", size=14, face="bold")
+  )
 # Combine plots
 p <- (p_avail / p_avail_month)
-p <- p + plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold"))
+p <- p + plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(size=14, face = "bold"))
 ggsave(filename = "figures/availability.png", plot = p, width = 20, height = 15, units = "cm")
-ggsave(filename = "figures/essd/fig01.pdf", plot = p, width = 20, height = 15, units = "cm")
+ggsave(filename = "figures/essd/availability.pdf", plot = p, width = 20, height = 15, units = "cm")
 
@@
 p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L00-S20', 'L00-P18', 'L00-M02'), y=value))+
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey70", outlier.color = "blue", outlier.size = 1) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey70", outlier.color = "blue", outlier.size = 2) +
   geom_hline(yintercept = 0) +
@@
   facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
-  Mytheme(size_labs = 10)
-ggsave(filename = "figures/k1k2_pco2_at.png", plot = p, width = 25, height = 20, units = "cm")
+  Mytheme(size_labs = 14) +
+  theme(strip.text.x = element_text(size = 14))
+ggsave(filename = "figures/k1k2_pco2_at.png", plot = p, width = 30, height = 20, units = "cm")
+ggsave(filename = "figures/essd/k1k2_pco2_at.pdf", plot = p, width = 25, height = 20, units = "cm")
 
@@
   facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
-  Mytheme(size_labs = 12)
+  Mytheme(size_labs = 14) +
+  theme(strip.text.x = element_text(size = 14))
 # calculate descriptive statistics
@@
 ggsave(filename = "figures/k1k2_ct_at.png", plot = p, width = 25, height = 20, units = "cm")
-ggsave(filename = "figures/essd/fig03.pdf", plot = p, width = 25, height = 20, units = "cm")
+ggsave(filename = "figures/essd/k1k2_ct_at.pdf", plot = p, width = 25, height = 20, units = "cm")
 # prepare tibble to compare calculated pH and spec pH
@@
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
+size_labs = 14
 # we look at the distribution of data
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 2, y = 0.65, parse = TRUE, label = "S['surface'] > S['deep']") +
-  annotate("text", x = 2, y = -0.9, parse = TRUE, label = "S['surface'] <  S['deep']") +
-  Mytheme(size_labs = 12) +
+  annotate("text", x = 2, y = 0.65, parse = TRUE, label = "S['surface'] > S['deep']", size = size_labs/.pt, fontface = "bold") +
+  annotate("text", x = 2, y = -0.9, parse = TRUE, label = "S['surface'] <  S['deep']", size = size_labs/.pt, fontface = "bold") +
+  Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
-        panel.grid.minor.y = element_blank())
+        panel.grid.minor.y = element_blank(),
+        axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.title.y = element_text(face = "bold", size = size_labs))
 print(sal_delta_plt)
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 2, y = 0.3, parse = TRUE, label = "T['surface'] > T['deep']") +
-  annotate("text", x = 2, y = -1.8, parse = TRUE, label = "T['surface'] <  T['deep']") +
-  Mytheme(size_labs = 12) +
+  annotate("text", x = 2, y = 0.3, parse = TRUE, label = "T['surface'] > T['deep']", size = size_labs/.pt, fontface = "bold") +
+  annotate("text", x = 2, y = -1.8, parse = TRUE, label = "T['surface'] <  T['deep']", size = size_labs/.pt, fontface = "bold") +
+  Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
-        panel.grid.minor.y = element_blank())
+        panel.grid.minor.y = element_blank(),
+        axis.title.x = element_text(face = "bold", size = 14),
+        axis.title.y = element_text(face = "bold", size = 14))
 print(temp_delta_plt)
@@
   geom_hline(yintercept = 0) +
-  annotate("text", x = 2, y = 0.25, parse = TRUE, label = "D['surface'] > D['deep']") +
-  annotate("text", x = 2, y = -1.2, parse = TRUE, label = "D['surface'] <  D['deep']") +
-  Mytheme(size_labs = 12) +
+  annotate("text", x = 2, y = 0.25, parse = TRUE, label = "D['surface'] > D['deep']", size = size_labs/.pt, fontface = "bold") +
+  annotate("text", x = 2, y = -1.2, parse = TRUE, label = "D['surface'] <  D['deep']", size = size_labs/.pt, fontface = "bold") +
+  Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(), panel.grid.major.y = element_blank(),
-        panel.grid.minor.y = element_blank())
+        panel.grid.minor.y = element_blank(),
+        axis.title.x = element_text(face = "bold", size = 14),
+        axis.title.y = element_text(face = "bold", size = 14))
 print(den_delta_plt)
@@
   scale_y_continuous(limits = c(-46,10), expand = c(0, 0)) +
-  labs(y = latex2exp::TeX("$pCO_2$ at in situ temperature ($\\mu atm$)")) +
+  labs(y = latex2exp::TeX("$pCO_2$ at in situ temperature ($\\mu atm$)", bold = TRUE)) +
   geom_col(fill = "blue") +
@@
     "text",
-    x = 10,
+    x = 10.5,
     y = 6,
     parse = TRUE,
-    label = "pCO['2 surface']>pCO['2 deep']"
+    label = "pCO['2 surface']>pCO['2 deep']", size = size_labs/.pt, fontface = "bold"
   ) +
@@
     "text",
-    x = 10,
+    x = 10.5,
     y = -40,
     parse = TRUE,
-    label = "pCO['2 surface']<pCO['2 deep']"
+    label = "pCO['2 surface']<pCO['2 deep']", size = size_labs/.pt, fontface = "bold"
   ) +
-  Mytheme(size_labs = 12) +
+  Mytheme(size_labs = size_labs) +
   theme(
@@
     panel.grid.major.y = element_blank(),
-    panel.grid.minor.y = element_blank()
+    panel.grid.minor.y = element_blank(),
+    axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.title.y = element_text(face = "bold", size = size_labs)
   )
@@
   scale_y_continuous(limits = c(-46,10), expand = c(0, 0)) +
-  labs(y = latex2exp::TeX("$pCO_2$ at 4°C ($\\mu atm$)")) +
+  labs(y = latex2exp::TeX("$pCO_2$ at 4°C ($\\mu atm$)", bold = TRUE)) +
   geom_col(fill = "blue") +
@@
     "text",
-    x = 10,
+    x = 10.5,
     y = 6,
     parse = TRUE,
-    label = "pCO['2 surface']>pCO['2 deep']"
+    label = "pCO['2 surface']>pCO['2 deep']", size = size_labs/.pt, fontface = "bold"
+    #label = latex2exp::TeX("pCO$_2$ surface > pCO$_2$ deep']", size = size_labs/.pt, bold = TRUE)
   ) +
@@
     "text",
-    x = 10,
+    x = 10.5,
     y = -40,
     parse = TRUE,
-    label = "pCO['2 surface'] < pCO['2 deep']"
+    label = "pCO['2 surface'] < pCO['2 deep']", size = size_labs/.pt, fontface = "bold"
   ) +
-  Mytheme(size_labs = 12) +
+  Mytheme(size_labs = size_labs) +
   theme(
@@
     panel.grid.major.y = element_blank(),
-    panel.grid.minor.y = element_blank()
+    panel.grid.minor.y = element_blank(),
+    axis.title.x = element_text(face = "bold", size = size_labs),
+    axis.title.y = element_text(face = "bold", size = size_labs)
   )
@@
 ggsave(filename = "figures/deltas_pco2.png", plot = g, width = 15, height = 20, units = "cm")
-ggsave(filename = "figures/essd/deltas_pco2.pdf", plot = g, width = 15, height = 20, units = "cm")
-
+ggsave(filename = "figures/essd/deltas_pco2.pdf", plot = g, width = 20, height = 20, units = "cm")
 ```
@@
   geom_point(aes(x = montht, y = thermal_nonthermal), col="blue", size = 2) +
-  labs(x="Month", y= latex2exp::TeX("Thermal/non-thermal control of $pCO_{2}"))  +
+  labs(x="Month", y= latex2exp::TeX("Thermal/non-thermal control of $pCO_{2}",
+                                    bold = TRUE))  +
   geom_hline(yintercept = 1, linetype = "dashed") +  
-  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio = 1) +
+  theme_bw() + Mytheme(size_labs = 14) + 
+  theme(aspect.ratio = 1,
+        axis.title.x = element_text(size = 14, face = "bold"),
+        axis.title.y = element_text(size = 14, face = "bold")) +
   coord_fixed(ratio = 1, expand = TRUE, clip = "on")
@@
 ggsave(filename = "figures/taka_month.png", plot = taka_month_plt, width = 25, height = 25, units = "cm")
-ggsave(filename = "figures/essd/fig05.pdf", plot = taka_month_plt, width = 25, height = 25, units = "cm")
+ggsave(filename = "figures/essd/taka_month.pdf", plot = taka_month_plt, width = 25, height = 25, units = "cm")
 
@@
 ```{r, echo = FALSE, message = FALSE, warning = FALSE}
+size_labs = 14
 p_pco2_fb_remos <- d_all %>% 
@@
   labs(title = NULL,
-       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$"),
-       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-4 m\\phantom{x}($\\mu atm)$"))  +
+       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$", bold = TRUE),
+       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-4 m\\phantom{x}($\\mu atm)$", bold = TRUE))  +
   ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
@@
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
-  theme_bw() + Mytheme(size_labs = 11) + theme(aspect.ratio = 1) +
+  theme_bw() + Mytheme(size_labs = size_labs) + theme(aspect.ratio = 1) +
   coord_fixed(ratio = 1, expand = TRUE, clip = "on")
@@
   labs(title = NULL,
-       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$"),
-       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-4 m\\phantom{x}($\\mu atm)$"))  +
+       x=latex2exp::TeX("$pCO_{2}$ 11 m $\\phantom{x}(\\mu atm)$", bold = TRUE),
+       y= latex2exp::TeX("$pCO_{2}$ REMOS at 0-4 m\\phantom{x}($\\mu atm)$", bold = TRUE))  +
   ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
-  ggpmisc::stat_ma_eq(mapping = use_label(c("R2", "eq"))) +
+  #ggpmisc::stat_ma_eq(mapping = use_label(c("R2", "eq"))) +
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
-  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio = 1) +
+  theme_bw() + Mytheme(size_labs = size_labs) + 
+  theme(aspect.ratio = 1,
+        axis.title.x = element_text(face = "bold", size = 14),
+        axis.title.y = element_text(face = "bold", size = 14)) +
   coord_fixed(ratio = 1, expand = TRUE, clip = "on")
@@
 alpha <- 1 #transparency
-size_labs <- 12 # font size labels
+size_labs <- 14 # font size labels
 # temp_insitu_11m
@@
   lims(y = c(-3, 0)) +
-  geom_hline(yintercept = 0)+
-  labs(title="",x="Month", y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)")) +
-  Mytheme(size_labs = size_labs)
+  geom_hline(yintercept = 0) +
+  labs(title=NULL, 
+       x="Month", 
+       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
+  Mytheme(size_labs = size_labs) +
+  theme(axis.title.x = element_text(face = "bold", size = size_labs))
 ts_air_sea
@@
 
-```{r, fig.width=10, fig.height=10, echo=FALSE, message= FALSE}
+```{r, fig.width=15, fig.height=10, echo=FALSE, message= FALSE}
 # legend:
@@
 alpha <- 1 #transparency
-size_labs <- 12 # font size labels
+size_labs <- 14 # font size labels
 
@@
   labs(title=NULL,x="", y="Salinity") +
-  Mytheme(size_labs = size_labs)
+  Mytheme(size_labs = size_labs) +
+  theme(axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.title.y = element_text(face = "bold", size = size_labs))
 
@@
   labs(title=NULL,x="", y="Temperature (°C)") +
-  Mytheme(size_labs = size_labs)
+  Mytheme(size_labs = size_labs) +
+  theme(axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.title.y = element_text(face = "bold", size = size_labs))
 
@@
        y=latex2exp::TeX("PAR ($\\mu mol\\phantom{x}m^{-2}\\phantom{x}s^{-1})$")) +
-  Mytheme(size_labs = size_labs)
+  Mytheme(size_labs = size_labs) +
+  theme(axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.title.y = element_text(face = "bold", size = size_labs))
 
@@
        subtitle = NULL,
-       x="", y=TeX("pCO$_2$ ($\\mu atm$)")) +
-  Mytheme(size_labs = size_labs)
+       x="", y=latex2exp::TeX("pCO$_2$ ($\\mu atm$)", bold=TRUE)) +
+  Mytheme(size_labs = size_labs) +
+  theme(axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.title.y = element_text(face = "bold", size = size_labs))
 
@@
        subtitle =NULL,
-       x = "", y=expression(paste(pH[T]))) +
+       x = "", y=latex2exp::TeX("pH$_T$", bold=TRUE)) +
   Mytheme(size_labs = size_labs) +
   theme(legend.position = c(0.1, 0.5),
-        legend.key.height = unit(0.5, 'cm'))
+        legend.key.height = unit(0.5, 'cm')) +
+  theme(axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.title.y = element_text(face = "bold", size = size_labs))
 
@@
        subtitle = NULL,
-       x="", y=TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$")) +
-  Mytheme(size_labs = size_labs)
+       x="", y=latex2exp::TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$", bold = TRUE)) +
+  Mytheme(size_labs = size_labs) +
+  theme(axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.title.y = element_text(face = "bold", size = size_labs))
 
@@
 alpha <- 1 #transparency
-size_labs <- 12 # font size labels
+size_labs <- 14 # font size labels
 d_bp <- d_all %>% # just for this chunk
@@
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5) +
+        aspect.ratio=0.5,
+        axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.title.y = element_text(face = "bold", size = size_labs)
+        ) +
   scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title=NULL, y = TeX("pCO$_2$ ($\\mu atm$)"), x=NULL) +
+  labs(title=NULL, y = latex2exp::TeX("pCO$_2$ ($\\mu atm$)", bold = TRUE), x=NULL) +
   Mytheme(size_labs = size_labs)+
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5) +
+        aspect.ratio=0.5,
+        axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.title.y = element_text(face = "bold", size = size_labs)
+        ) +
   scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title=NULL, y = TeX("$pH_T$"), x=NULL) +
+  labs(title=NULL, y = latex2exp::TeX("$pH_T$", bold = TRUE), x=NULL) +
   Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5) +
+        aspect.ratio=0.5,
+        axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.title.y = element_text(face = "bold", size = size_labs)
+        ) +
   scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title=NULL, y = TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$"), x=NULL) +
+  labs(title=NULL, y = TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$", bold = TRUE), x=NULL) +
   Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5) +
+        aspect.ratio=0.5,
+        axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.title.y = element_text(face = "bold", size = size_labs)
+        ) +
   scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
@@
   (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
-g <- g + plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold"))
-ggsave(filename = "figures/essd/ts.pdf", plot = g)
+g <- g + patchwork::plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold", size = 14))
+ggsave(filename = "figures/essd/ts.pdf", plot = g, width = 20, height = 30)
 # legend:

### 2023-03-03 awipev-CO2.Rmd
minor fig change

@@
 ggsave(filename = "figures/pco2_ph_etc.png", plot = g)
-ggsave(filename = "figures/essd/fig04.pdf", plot = g)
+ggsave(filename = "figures/essd/pco2_ph_etc.pdf", plot = g)
 ```

### 2023-03-03 awipev-CO2.Rmd
Changed datetime for Pangaea

@@
 pangaea <- pangaea %>% 
-  mutate_all(~ifelse(is.nan(.), NA, .))
+  mutate_all(~ifelse(is.nan(.), NA, .)) %>% 
+  mutate(datetime = as.POSIXct(datetime, origin = "1970-01-01")) |>
+  separate(datetime, into = c("Date", "Time"), sep = " ") |>
+  mutate(`date/time [UTC+0]` = paste(Date, Time, sep = "T")) |>
+  dplyr::select(`date/time [UTC+0]`, everything(), -Date, -Time) |>
+  mutate_at(1:13, ~as.character(.)) |>
+  mutate_at(1:13, ~replace_na(., ""))
 

### 2023-03-03 awipev-CO2.Rmd
Air-sea flux in mol C too; refined pangaea file

--- 2023-03-03 awipev-CO2.Rmd
@@
   )
-# replace NaNs by NAs
+# replace NaNs by NAs, then remove NAs
 pangaea <- pangaea %>% 
-  mutate_all(~ifelse(is.nan(.), NA, .))
-
-#saveRDS(file= paste0(path, "fb_data/pangaea.rds"), pangaea)
-#write_csv(pangaea, file = paste0(path, "fb_data/pangaea.csv"))
+  mutate_all(~ifelse(is.nan(.), NA, .)) %>% 
+  mutate(datetime = as.POSIXct(datetime, origin = "1970-01-01")) |>
+  separate(datetime, into = c("Date", "Time"), sep = " ") |>
+  mutate(`date/time [UTC+0]` = paste(Date, Time, sep = "T")) |>
+  dplyr::select(`date/time [UTC+0]`, everything(), -Date, -Time) |>
+  mutate_at(1:13, ~as.character(.)) |>
+  mutate_at(1:13, ~replace_na(., ""))
+
 saveRDS(file= "data/AWIPEV-CO2_v1.rds", pangaea)
 write_csv(pangaea, file = "data/AWIPEV-CO2_v1.csv")
-# Metadata Pangaea
+# Metadata Pangaea (see manuscript)
+# datetime (UTC)
 # pressure = pressure in situ (profiler)
@@
 ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea, width = 20, units = "cm")
-
 #rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
@@
 The annual air-sea CO2 flux is
-`r round(sum(air_sea_month$f_air_sea/1000), digits = 0)` and
-`r round(sum(air_sea_corr_month$f_air_sea_corr/1000), digits = 0)` mol/(m2
-year) without and with correction, respectively.
+`r round(sum(air_sea_month$f_air_sea/1000), digits = 1)` and
+`r round(sum(air_sea_corr_month$f_air_sea_corr/1000), digits = 1)` mol CO2/(m2
+year) without and with correction, respectively. Or `r round(sum(air_sea_month$f_air_sea*(12/44)/1000), digits = 1)` and
+`r round(sum(air_sea_corr_month$f_air_sea_corr*(12/44)/1000), digits = 1)` mol C/(m2
+year)
 

### 2023-03-09 awipev-CO2.Rmd
Added availability discrete data

@@
 library("ggOceanMaps")
+library(ggtext)  # remotes::install_github("clauswilke/ggtext")
 
@@
 ```{r, echo=FALSE, message= FALSE, warning=FALSE, out.width="80%",fig.show='hold', fig.align="center"}
+# Continuous data first
 d_min <- readRDS(file = paste0(path, "fb_awipev-co2_server/ny-alesund/data/NRT_data/all_nydata_minute.rds")) %>%
@@
 s8 <- summary(as.factor(x$phINT_qf))*100/length(x$phINT_qf)
-z <- t(bind_rows(s1,s2,s3,s4,s5,s7,s8)) %>%
+# s7 not bound because durafet not in ESSD paper
+z <- t(bind_rows(s1,s2,s3,s4,s5,s8)) %>%
   as.data.frame() %>%
@@
 colnames(z) <- c("Flag", "pCO2", "Salinity FerryBox", "In situ salinity", 
-                 "Temperature FerryBox", "In situ temperature", "Durafet pH", "seaFET pH")
+                 "Temperature FerryBox", "In situ temperature", "seaFET pH")
 p_avail <- pivot_longer(z, -Flag) %>% 
@@
       "Flag",
-      'pCO2' = parse(text = TeX('$pCO_2$')),
-      "Salinity FerryBox",
-      "In situ salinity",
+      'pCO2' = parse(text = latex2exp::TeX('$pCO_2$')),
+      'In situ salinity' = "Salinity profiler",
+      "Salinity Ferrybox",
       "Temperature FerryBox",
-      "In situ temperature",
-      "Durafet pH",
-      "seaFET pH"
+      'In situ temperature' = "Temperature 11 m",
+      "seaFET pH" = "pH profiler"
     )
@@
   coord_flip() +
-  labs(x="", y = "Distribution of quality flags (%)") +
+  labs(title = "A", x="", y = "Distribution of quality flags (%)") +
   Mytheme(size_labs = 14) +
   theme(legend.title = element_text(colour="black", size=14, face="bold"),
-        axis.title.x = element_text(colour="black", size=14, face="bold")) #+
-  #theme(plot.margin = margin(t = -8, r = 0.0, b = -8, l = 0.0, unit = "cm"))
-#kable(z, digits = 1)
+        axis.title.x = element_text(colour="black", size=14, face="bold"),
+        title = element_text(colour="black", size=14, face="bold")
+        )
 d2 <- d_all %>% 
@@
   geom_col(aes(x = montht, y = value, fill = name), position = "dodge", width = 0.75) +
-  scale_fill_discrete(name = "", labels = c(expression(paste(pCO[2])), "pH")) + 
-  labs(x="Month", y="Number of data (thousands)", title = "") +
+  scale_fill_discrete(name = "Continuous data", labels = c(expression(paste(pCO[2])), "pH")) + 
+  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
+                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
+  labs(x="Month", y="Number of data (thousands)", title = "B") +
   Mytheme(size_labs = 14,) +
-  theme(axis.title.x = element_text(colour="black", size=14, face="bold"),
-        axis.title.y = element_text(colour="black", size=14, face="bold")
-  )
+  theme(legend.title = element_text(colour="black", size=14, face="bold"),
+        axis.title.x = element_text(colour="black", size=14, face="bold"),
+        axis.title.y = element_text(colour="black", size=14, face="bold", margin = margin(r = -220)),
+        title = element_text(colour="black", size=14, face="bold")
+  )
+
+# Discrete data now, only the monthly distribution
+d3 <- d_all %>% 
+  dplyr::select(montht, at, ct, ph_s_sf_temp_insi)
+
+# calculate the distribution of non-NA values per month
+d3_summary <- d3 %>% 
+  dplyr::group_by(montht) %>% 
+  dplyr::summarise(at = sum(!is.na(at)),
+                   ct = sum(!is.na(ct)),
+                   pH = sum(!is.na(ph_s_sf_temp_insi))
+  )
+# plot the distribution of non-NA pCO2 and pH values per month
+p_discrete_avail_month <- d3_summary %>% 
+  tidyr::pivot_longer(cols = c(at, ct, pH)) %>% 
+  ggplot() +
+  geom_col(aes(x = montht, y = value, fill = name), position = "dodge", width = 0.75) +
+#  scale_fill_discrete(name = "Discrete data", labels = c(expression(paste(A[T]), C[T]), "pH")) + 
+  scale_fill_discrete(name = "Discrete data", 
+                      labels = c(TeX("\\textit{A}$_T$"), TeX("\\textit{C}$_T$"), "pH")) + 
+  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
+                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
+  labs(x="Month", y="Number of data", title = "C") +
+  Mytheme(size_labs = 14,) +
+  theme(legend.title = element_text(colour="black", size=14, face="bold"),
+        axis.title.x = element_text(colour="black", size=14, face="bold"),
+        axis.title.y = element_text(colour="black", size=14, face="bold", margin = margin(r = -220)),
+        title = element_text(colour="black", size=14, face="bold")
+  )
+
 # Combine plots
-p <- (p_avail / p_avail_month)
-p <- p + plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(size=14, face = "bold"))
+p <- (p_avail / p_avail_month / p_discrete_avail_month)
+#p <- p  #plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(size=14, face = "bold"))
 ggsave(filename = "figures/availability.png", plot = p, width = 20, height = 15, units = "cm")
-ggsave(filename = "figures/essd/availability.pdf", plot = p, width = 20, height = 15, units = "cm")
+ggsave(filename = "figures/essd/availability.pdf", plot = p, width = 20, height = 20, units = "cm")
 
@@
 ```
+Number of discrete data:
+
+- AT: `r sum(!is.na(d_all$at))`
+- CT: `sum(!is.na(d_all$ct))`
+- Spectrophotometric pH: `sum(!is.na(d_all$ph_s_sf_temp_insi))`
 

### 2023-03-09 awipev-CO2.Rmd
refined figs K1K2

@@
   tidyr::pivot_longer(-deltas, names_to = "variable") %>% 
-  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), variable = fct_recode(variable, 'pH' = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))
+#  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), variable = fct_recode(variable, 'pH' = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))
+  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), 
+                variable = fct_recode(variable, "`pH at 4 °C`" = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))
 
 p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L00-S20', 'L00-P18', 'L00-M02'), y=value))+
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey70", outlier.color = "blue", outlier.size = 2) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey70", outlier.color = "grey70", outlier.size = 2) +
   geom_hline(yintercept = 0) +
@@
   facet_wrap(vars(variable), scales = "free_y", labeller = label_parsed) +
-  Mytheme(size_labs = 12)
+  Mytheme(size_labs = 14)
 # calculate descriptive statistics
@@
 ggsave(filename = "figures/k1k2_all_pco2_at.png", plot = p, width = 25, height = 20, units = "cm")
-ggsave(filename = "figures/essd/fig02.pdf", plot = p, width = 25, height = 20, units = "cm")
+ggsave(filename = "figures/essd/k1k2_all_pco2_at.pdf", plot = p, width = 25, height = 20, units = "cm")
 
@@
   tidyr::pivot_longer(-deltas, names_to = "variable") %>% 
-  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), variable = fct_recode(variable, 'pH' = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))
+  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_ct', 'delta_OmegaAragonite'), 
+                variable = fct_recode(variable, "`pH at 4 °C`" = "delta_ph", 'C[T]' = "delta_ct",'Omega[a]' = "delta_OmegaAragonite"))
 
 p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L00-S20', 'L00-P18', 'L00-M02'), y=value))+
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey50", outlier.color = "blue", outlier.size = 0.3) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey70", outlier.color = "grey70", outlier.size = 0.3) +
   geom_hline(yintercept = 0) +
@@
   Mytheme(size_labs = 14) +
-  theme(strip.text.x = element_text(size = 14))
+  theme(strip.text.x = element_text(size = 14),
+        plot.margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt"))
 ggsave(filename = "figures/k1k2_pco2_at.png", plot = p, width = 30, height = 20, units = "cm")
-ggsave(filename = "figures/essd/k1k2_pco2_at.pdf", plot = p, width = 25, height = 20, units = "cm")
+ggsave(filename = "figures/essd/k1k2_pco2_at.pdf", plot = p, width = 25, height = 15, units = "cm")
 
@@
   tidyr::pivot_longer(-deltas, names_to = "variable") %>% 
-  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_pCO2', 'delta_OmegaAragonite'), variable = fct_recode(variable, 'pH' = "delta_ph", 'pCO[2]' = "delta_pCO2",'Omega[a]' = "delta_OmegaAragonite"))
+  dplyr::mutate(variable = forcats::fct_relevel(variable, 'delta_ph', 'delta_pCO2', 'delta_OmegaAragonite'), 
+                variable = fct_recode(variable, "`pH at 4 °C`" = "delta_ph", 'pCO[2]' = "delta_pCO2",'Omega[a]' = "delta_OmegaAragonite"))
 
 p <- ggplot(diff_all_long, aes(x = forcats::fct_relevel(deltas, 'L00-S20', 'L00-P18', 'L00-M02'), y=value))+
-  geom_boxplot(notch=FALSE, size=0.2, fill="grey70", outlier.color = "blue", outlier.size = 2) +
+  geom_boxplot(notch=FALSE, size=0.2, fill="grey70", outlier.color = "grey70", outlier.size = 2) +
   geom_hline(yintercept = 0) +
@@
   Mytheme(size_labs = 14) +
-  theme(strip.text.x = element_text(size = 14))
+  theme(strip.text.x = element_text(size = 14),
+        plot.margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt"))
 # calculate descriptive statistics
@@
 ggsave(filename = "figures/k1k2_ct_at.png", plot = p, width = 25, height = 20, units = "cm")
-ggsave(filename = "figures/essd/k1k2_ct_at.pdf", plot = p, width = 25, height = 20, units = "cm")
+ggsave(filename = "figures/essd/k1k2_ct_at.pdf", plot = p, width = 25, height = 15, units = "cm")
 # prepare tibble to compare calculated pH and spec pH

### 2023-03-10 awipev-CO2.Rmd
More fig refining

@@
   geom_point(col="blue", size = 1) +
-  labs(x= latex2exp::TeX("Salinity"),
-       y= latex2exp::TeX("Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$"))  +
+  labs(title = "A",
+       x= latex2exp::TeX("\\textbf{Salinity}"),
+       y= latex2exp::TeX("\\textbf{Total alkalinity ($\\mu mol\\phantom{x}kg^{-1})$}"))  +
   ggpmisc::stat_ma_line(method = "lmodel2:OLS", se = FALSE, size = 1) +
   #ggpmisc::stat_ma_eq(method = "lmodel2:OLS", aes(label = after_stat(eq.label))) +
-  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio=1) + 
+  theme_bw() + 
+  Mytheme(size_labs = 12) +
+  theme(aspect.ratio=1, plot.title = element_text(face = "bold"),
+        plot.margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")) + 
   coord_fixed()
@@
   xlim(180, 420) + ylim(180, 420) +
-  labs(x=latex2exp::TeX("Measured $pCO_{2}\\phantom{x}(\\mu atm)$"),
-       y= latex2exp::TeX("Calculated $pCO_{2}\\phantom{x}(\\mu atm)$"))  +
+  labs(title = "B",
+       x=latex2exp::TeX("\\textbf{Measured $pCO_{2}\\phantom{x}(\\mu atm)$}"),
+       y= latex2exp::TeX("\\textbf{Calculated $pCO_{2}\\phantom{x}(\\mu atm)$}"))  +
   ggpmisc::stat_ma_line(method = "lmodel2:MA", se = FALSE, size = 1) +
@@
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
-  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio = 1) +
+  theme_bw() + Mytheme(size_labs = 12) + 
+  Mytheme(size_labs = 12) +
+  theme(aspect.ratio=1, plot.title = element_text(face = "bold"),
+        plot.margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")) + 
   coord_fixed(ratio = 1, expand = TRUE, clip = "on")
@@
   geom_hline(yintercept=0.02, size=0.3, linetype = "dashed") +
-  labs(x = "Date", y=expression(paste(pH[T], " difference")), title = NULL) +
-  Mytheme(size_labs = 12, face_font = "plain") + theme(aspect.ratio=1)  + 
+  labs(title = "C",
+       x = "Date", y=latex2exp::TeX("\\textbf{pH$_T$ difference}")) +
+  #Mytheme(size_labs = 12, face_font = "plain") + 
+  Mytheme(size_labs = 12) +
+  theme(aspect.ratio=1, plot.title = element_text(face = "bold"),
+        plot.margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt"),
+        axis.title.x = element_text(face = "bold"),
+        axis.title.y = element_text(face = "bold")) + 
   scale_colour_discrete(guide="none") + 
@@
   xlim(8.05, 8.18) + ylim(8.05, 8.18) +
-  labs(x="Spectrophotometric pH",
+  labs(title = "D",
+       x="Spectrophotometric pH",
        y= "SeaFET pH")  +
@@
   geom_abline(slope = 1, intercept = 0, linetype = "dashed") +  
-  theme_bw() + Mytheme(size_labs = 12) + theme(aspect.ratio = 1) +
+  theme_bw() + 
+  Mytheme(size_labs = 12) +
+  theme(aspect.ratio=1, plot.title = element_text(face = "bold"),
+        axis.title.x = element_text(face = "bold"),
+        axis.title.y = element_text(face = "bold"),
+        plot.margin = margin(t = 0, r = 10, b = 0, l = 0, unit = "pt")) + 
   coord_fixed(ratio = 1, expand = TRUE, clip = "on")
@@
   geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
-  labs(title=NULL,x="", y="Salinity") +
+  labs(title="A",x="", y="Salinity") +
   Mytheme(size_labs = size_labs) +
   theme(axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs))
+        axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold")
+        )
 
@@
   geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
-  labs(title=NULL,x="", y="Temperature (°C)") +
+  labs(title="B",x="", y="Temperature (°C)") +
   Mytheme(size_labs = size_labs) +
   theme(axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs))
-
+        axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold")
+        )
 # PAR
@@
   geom_point(aes(x = datetime, y = pco2_calc_fb_insi_temp), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
-  labs(title=NULL,
+  labs(title="C",
        subtitle = NULL,
@@
   theme(axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs))
-
+        axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold")
+        )
 # SEAFET pH
@@
   geom_point(aes(x = datetime, y = ph_s_sf_temp_insi), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
-  labs(title=NULL, 
+  labs(title="D", 
        subtitle =NULL,
@@
   theme(axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs))
-
+        axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold")
+        )
 # AT
@@
   geom_point(aes(x = datetime, y = at), colour="red", alpha = alpha, na.rm = TRUE, size = size_point*3) + 
-  labs(title=NULL, 
+  labs(title="E", 
        subtitle = NULL,
@@
   theme(axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs))
+        axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold")
+        )
 
@@
 g1 <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at)
-g1 <- g1 + plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold"))
+#g1 <- g1 + plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold"))
 ggsave(filename = "figures/time_series.png", plot = g1, width = 15, height = 30, units = "cm")
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title="", y = "Salinity", x=NULL) +
+  labs(title="F", y = "Salinity", x=NULL) +
   Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5,
+#        aspect.ratio=0.5,
         axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs)
+        axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold")
         ) +
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title=NULL, y = "Temperature (°C)", x=NULL) +
+  labs(title="G", y = "Temperature (°C)", x=NULL) +
   Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5,
+#        aspect.ratio=0.5,
         axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs)
+        axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold")
         ) +
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title=NULL, y = latex2exp::TeX("pCO$_2$ ($\\mu atm$)", bold = TRUE), x=NULL) +
+  labs(title="H", y = latex2exp::TeX("pCO$_2$ ($\\mu atm$)", bold = TRUE), x=NULL) +
   Mytheme(size_labs = size_labs)+
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5,
+#        aspect.ratio=0.5,
         axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs)
+        axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold")
         ) +
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title=NULL, y = latex2exp::TeX("$pH_T$", bold = TRUE), x=NULL) +
+  labs(title="I", y = latex2exp::TeX("$pH_T$", bold = TRUE), x=NULL) +
   Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5,
+#        aspect.ratio=0.5,
         axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs)
+        axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold")
         ) +
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title=NULL, y = TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$", bold = TRUE), x=NULL) +
+  labs(title="J", y = TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$", bold = TRUE), x=NULL) +
   Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
-        aspect.ratio=0.5,
+#        aspect.ratio=0.5,
         axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs)
+        axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold")
         ) +
@@
                              theme(plot.tag = element_text(face = "bold"))
-ggsave(filename = "figures/ts_boxplots.png", plot = g2)
+ggsave(filename = "figures/ts_boxplots.png", plot = g2, width = 12)
 ```
@@
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
-g <- (at_s | pco2_calc_meas) / (offset_ph | pHspec_pHseafet)
-g <- g + patchwork::plot_annotation(tag_levels = 'A') & 
-  theme(plot.tag = element_text(face = "bold"))
+g <- (at_s | pco2_calc_meas) / (offset_ph | pHspec_pHseafet) #+
+  #plot_layout(heights = c(6,6,6,6)) 
+# g <- g + patchwork::plot_annotation(tag_levels = 'A') & 
+#   theme(plot.tag = element_text(face = "bold"))
 ggsave(filename = "figures/pco2_ph_etc.png", plot = g)
-ggsave(filename = "figures/essd/pco2_ph_etc.pdf", plot = g)
+ggsave(filename = "figures/essd/pco2_ph_etc.pdf", plot = g, width = 18, height = 18, units = "cm")
 ```
@@
   (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
-g <- g + patchwork::plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold", size = 14))
-ggsave(filename = "figures/essd/ts.pdf", plot = g, width = 20, height = 30)
+#g <- g + patchwork::plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold", size = 14))
+ggsave(filename = "figures/essd/ts.pdf", plot = g, width = 12)
 # legend:

### 2023-03-13 awipev-CO2.Rmd
Fig. time series finalized

@@
   geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
-  labs(title="A",x="", y="Salinity") +
+  labs(title="A",x=NULL, y="Salinity") +
+  scale_y_continuous(limits = c(31.8, 35.5)) +
   Mytheme(size_labs = size_labs) +
-  theme(axis.title.x = element_text(face = "bold", size = size_labs),
+  theme(#axis.title.x = element_text(face = "bold", size = size_labs),
         axis.title.y = element_text(face = "bold", size = size_labs),
-        title = element_text(colour="black", size=14, face="bold")
+        axis.text.x=element_blank(),
+        title = element_text(colour="black", size=14, face="bold"),
+         axis.ticks.length.y = unit(.2, "cm"),
+        axis.ticks.length.x = unit(.2, "cm"),
+        axis.ticks.x = element_line(size = 0.5),
+        axis.ticks.y = element_line(size = 0.5)
         )
@@
   geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
-  labs(title="B",x="", y="Temperature (°C)") +
+  labs(title="B",x=NULL, y="Temperature (°C)") +
+  scale_y_continuous(limits = c(-1.8, 8)) +
   Mytheme(size_labs = size_labs) +
-  theme(axis.title.x = element_text(face = "bold", size = size_labs),
+  theme(#axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.text.x=element_blank(),
         axis.title.y = element_text(face = "bold", size = size_labs),
-        title = element_text(colour="black", size=14, face="bold")
+        title = element_text(colour="black", size=14, face="bold"),
+        axis.ticks.length.y = unit(.2, "cm"),
+        axis.ticks.length.x = unit(.2, "cm"),
+        axis.ticks.x = element_line(size = 0.5),
+        axis.ticks.y = element_line(size = 0.5)
         )
@@
        subtitle = NULL,
-       x="", y=latex2exp::TeX("pCO$_2$ ($\\mu atm$)", bold=TRUE)) +
+       x=NULL, y=latex2exp::TeX("pCO$_2$ ($\\mu atm$)", bold=TRUE)) +
+  scale_y_continuous(limits = c(180, 400)) +
   Mytheme(size_labs = size_labs) +
-  theme(axis.title.x = element_text(face = "bold", size = size_labs),
+  theme(#axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.text.x=element_blank(),
         axis.title.y = element_text(face = "bold", size = size_labs),
-        title = element_text(colour="black", size=14, face="bold")
+        title = element_text(colour="black", size=14, face="bold"),
+        axis.ticks.length.y = unit(.2, "cm"),
+        axis.ticks.length.x = unit(.2, "cm"),        axis.ticks.x = element_line(size = 0.5),
+        axis.ticks.y = element_line(size = 0.5)
         )
@@
        subtitle =NULL,
-       x = "", y=latex2exp::TeX("pH$_T$", bold=TRUE)) +
+       x = NULL, y=latex2exp::TeX("pH$_T$", bold=TRUE)) +
+  scale_y_continuous(limits = c(7.99, 8.2)) +
   Mytheme(size_labs = size_labs) +
@@
         legend.key.height = unit(0.5, 'cm')) +
-  theme(axis.title.x = element_text(face = "bold", size = size_labs),
+  theme(#axis.title.x = element_text(face = "bold", size = size_labs),
+        axis.text.x=element_blank(),
         axis.title.y = element_text(face = "bold", size = size_labs),
-        title = element_text(colour="black", size=14, face="bold")
+        title = element_text(colour="black", size=14, face="bold"),
+        axis.ticks.length.y = unit(.2, "cm"),
+        axis.ticks.length.x = unit(.2, "cm"),
+        axis.ticks.x = element_line(size = 0.5),
+        axis.ticks.y = element_line(size = 0.5)
         )
@@
        subtitle = NULL,
-       x="", y=latex2exp::TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$", bold = TRUE)) +
+       x="Year", y=latex2exp::TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$", bold = TRUE)) +
+  scale_y_continuous(limits = c(2135, 2355)) +
   Mytheme(size_labs = size_labs) +
   theme(axis.title.x = element_text(face = "bold", size = size_labs),
+        #axis.text.x=element_blank(),
         axis.title.y = element_text(face = "bold", size = size_labs),
-        title = element_text(colour="black", size=14, face="bold")
+        title = element_text(colour="black", size=14, face="bold"),
+        axis.ticks.length.y = unit(.2, "cm"),
+        axis.ticks.length.x = unit(.2, "cm"),
+        axis.ticks.x = element_line(size = 0.5),
+        axis.ticks.y = element_line(size = 0.5)
         )
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = sal_fb_mix), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title="F", y = "Salinity", x=NULL) +
+  labs(title="F", y = NULL, x=NULL) +
   Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
-#        aspect.ratio=0.5,
-        axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs),
-        title = element_text(colour="black", size=14, face="bold")
-        ) +
-  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
-                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
+        axis.text.x=element_blank(),
+        axis.text.y=element_blank(),
+        # axis.title.x = element_text(face = "bold", size = size_labs),
+        # label.x = element_text(face = "bold", size = size_labs),
+        # axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold"),
+        axis.ticks.length.y = unit(.2, "cm"),
+        axis.ticks.length.x = unit(.2, "cm"),
+        axis.ticks.x = element_line(size = 0.5),
+        axis.ticks.y = element_line(size = 0.5)
+        ) #+
+  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
+  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
+  # scale_y_continuous(limits = c(31.8, 35.5))
+
 ts_temp_bp <- d_bp %>%
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_temp_insitu_11m), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title="G", y = "Temperature (°C)", x=NULL) +
+  labs(title="G", y = NULL, x=NULL) +
+  scale_y_continuous(limits = c(-1.8, 8)) +
   Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
-#        aspect.ratio=0.5,
-        axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs),
-        title = element_text(colour="black", size=14, face="bold")
-        ) +
-  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
-                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
+        axis.text.x=element_blank(),
+        axis.text.y=element_blank(),
+        # axis.title.x = element_text(face = "bold", size = size_labs),
+        # label.x = element_text(face = "bold", size = size_labs),
+        # axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold"),
+        axis.ticks.length.y = unit(.2, "cm"),
+        axis.ticks.length.x = unit(.2, "cm"),
+        axis.ticks.x = element_line(size = 0.5),
+        axis.ticks.y = element_line(size = 0.5)
+        ) #+
+  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
+  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
+
 ts_pco2_bp <- d_bp %>%
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pco2_fb), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title="H", y = latex2exp::TeX("pCO$_2$ ($\\mu atm$)", bold = TRUE), x=NULL) +
+  labs(title="H", y = NULL, x=NULL) +
+  scale_y_continuous(limits = c(180, 400)) +
   Mytheme(size_labs = size_labs)+
   theme(panel.grid.major.x = element_blank(),
-#        aspect.ratio=0.5,
-        axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs),
-        title = element_text(colour="black", size=14, face="bold")
-        ) +
-  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
-                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
+        axis.text.x=element_blank(),
+        axis.text.y=element_blank(),
+        # axis.title.x = element_text(face = "bold", size = size_labs),
+        # label.x = element_text(face = "bold", size = size_labs),
+        # axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold"),
+        axis.ticks.length.y = unit(.2, "cm"),
+        axis.ticks.length.x = unit(.2, "cm"),
+        axis.ticks.x = element_line(size = 0.5),
+        axis.ticks.y = element_line(size = 0.5)
+        ) #+
+  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
+  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
 ts_pH_bp <- d_bp %>%
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_pHint_tot_sf), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title="I", y = latex2exp::TeX("$pH_T$", bold = TRUE), x=NULL) +
+  labs(title="I", y = NULL, x=NULL) +
+  scale_y_continuous(limits = c(7.99, 8.2)) +
   Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
-#        aspect.ratio=0.5,
-        axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs),
-        title = element_text(colour="black", size=14, face="bold")
-        ) +
-  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
-                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
+        axis.text.x=element_blank(),
+        axis.text.y=element_blank(),
+        # axis.title.x = element_text(face = "bold", size = size_labs),
+        # label.x = element_text(face = "bold", size = size_labs),
+        # axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold"),
+        axis.ticks.length.y = unit(.2, "cm"),
+        axis.ticks.length.x = unit(.2, "cm"),
+        axis.ticks.x = element_line(size = 0.5),
+        axis.ticks.y = element_line(size = 0.5)
+        ) #+
+  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
+  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
+
 ts_at_bp <- d_bp %>%
@@
   geom_point(aes(x = month(x = datetime, label = TRUE, abbr = TRUE), y = ext_at_calc), col = "lightblue", size = size_point, na.rm = TRUE) +
-  labs(title="J", y = TeX("$A_T$ ($\\mu mol\\phantom{x}kg^{-1})$", bold = TRUE), x=NULL) +
+  labs(title="J", y = NULL, x="Month") +
+  scale_y_continuous(limits = c(2135, 2355)) +
   Mytheme(size_labs = size_labs) +
   theme(panel.grid.major.x = element_blank(),
-#        aspect.ratio=0.5,
+        #axis.text.x=element_blank(),
+        axis.text.y=element_blank(),
         axis.title.x = element_text(face = "bold", size = size_labs),
-        axis.title.y = element_text(face = "bold", size = size_labs),
-        title = element_text(colour="black", size=14, face="bold")
+        #axis.label.x = element_text(face = "bold", size = size_labs),
+        # axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold"),
+        axis.ticks.length.y = unit(.2, "cm"),
+        axis.ticks.length.x = unit(.2, "cm"),
+        axis.ticks.x = element_line(size = 0.5),
+        axis.ticks.y = element_line(size = 0.5)
         ) +
@@
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
-g <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at) |
-  (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
+#g <- (ts_sal / ts_temp / ts_pCO2  / ts_pH / ts_at) |
+#  (ts_sal_bp / ts_temp_bp / ts_pco2_bp / ts_pH_bp / ts_at_bp)
+g <- (ts_sal | ts_sal_bp) / (ts_temp | ts_temp_bp) / (ts_pCO2 | ts_pco2_bp) / 
+  (ts_pH | ts_pH_bp) / (ts_at | ts_at_bp)
 #g <- g + patchwork::plot_annotation(tag_levels = 'A') & theme(plot.tag = element_text(face = "bold", size = 14))
-ggsave(filename = "figures/essd/ts.pdf", plot = g, width = 12)
+ggsave(filename = "figures/essd/ts.pdf", plot = g, width = 8)
 # legend:

### 2023-03-13 awipev-CO2.Rmd
further figs refinement

@@
   theme(
+    plot.margin = margin(t = 0, r = 0.2, b = 0, l = 0, unit = "cm"),
     panel.grid.major.x = element_blank(),
@@
   ggplot() +
-  geom_point(aes(x = montht, y = thermal_nonthermal), col="blue", size = 2) +
-  labs(x="Month", y= latex2exp::TeX("Thermal/non-thermal control of $pCO_{2}",
-                                    bold = TRUE))  +
+  geom_point(aes(x = montht, y = thermal_nonthermal),
+             col = "blue",
+             size = 2) +
+  labs(
+    x = "Month",
+    y = latex2exp::TeX("Thermal/non-thermal control of $pCO_{2}",
+                       bold = TRUE)
+  )  +
   geom_hline(yintercept = 1, linetype = "dashed") +
   theme_bw() + Mytheme(size_labs = 14) +
-  theme(aspect.ratio = 1,
+  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
+                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))+
+  coord_fixed(ratio = 1,
+              expand = TRUE,
+              clip = "on") +
+  theme(
+    plot.margin = margin(
+      t = 0.2,
+      r = 0.2,
+      b = 0.2,
+      l = 0.2,
+      unit = "cm"
+    ),
+    aspect.ratio = 1,
     axis.title.x = element_text(size = 14, face = "bold"),
-        axis.title.y = element_text(size = 14, face = "bold")) +
-  coord_fixed(ratio = 1, expand = TRUE, clip = "on")
+    axis.title.y = element_text(size = 14, face = "bold")
+  )
 taka_month_plt
 ggsave(filename = "figures/taka_month.png", plot = taka_month_plt, width = 25, height = 25, units = "cm")
-ggsave(filename = "figures/essd/taka_month.pdf", plot = taka_month_plt, width = 25, height = 25, units = "cm")
+ggsave(filename = "figures/essd/taka_month.pdf", plot = taka_month_plt, width = 12, height = 12, units = "cm")
 
@@
   ggplot(aes(x = montht, y = f_air_sea / 1000), na.rm = TRUE) +
-  geom_col(colour="blue", fill = "blue",  alpha = alpha, stat="identity") +
+  geom_col(colour="blue", fill = "blue",  alpha = alpha) +
   lims(y = c(-3, 0)) +
@@
   Mytheme(size_labs = size_labs) +
-  theme(axis.title.x = element_text(face = "bold", size = size_labs))
+  theme(plot.margin = margin(t = 0.2, r = 0.2, b = 0.2, l = 0.2, unit = "cm"),
+        axis.title.x = element_text(face = "bold", size = 14),
+        axis.title.y = element_text(face = "bold", size = 14),
+        axis.text.x = element_text(size=14),
+        axis.text.y = element_text(size=14)
+        ) +
+  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
+                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
 ts_air_sea

### 2023-03-13 awipev-CO2.Rmd
more fine-tuning of figs

@@
 ggsave(filename = "figures/deltas_pco2.png", plot = g, width = 15, height = 20, units = "cm")
-ggsave(filename = "figures/essd/deltas_pco2.pdf", plot = g, width = 20, height = 20, units = "cm")
+ggsave(filename = "figures/essd/deltas_pco2.pdf", plot = g, width = 15, height = 20, units = "cm")
 ```
@@
   Mytheme(size_labs = size_labs) +
-  theme(plot.margin = margin(t = 0.2, r = 0.2, b = 0.2, l = 0.2, unit = "cm"),
+  theme(aspect.ratio=0.5,
+        plot.margin = margin(t = -10, r = 0.2, b = -10, l = 0.2, unit = "cm"),
         axis.title.x = element_text(face = "bold", size = 14),
@@
 ggsave(filename = "figures/ts_air_sea.png", plot = ts_air_sea, width = 20, units = "cm")
-ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea, width = 20, units = "cm")
+ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea, width = 15, height = 10, units = "cm")
 #rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
@@
   ylim(0, 3) +
-  labs(title="",x="", y=latex2exp::TeX("$\\Omega_{aragonite}$")) +
-  Mytheme(size_labs = size_labs)
+  labs(title=NULL,x="Time", y=latex2exp::TeX("\\textbf{$\\Omega_{aragonite}$}")) +
+  Mytheme(size_labs = size_labs) +
+    theme(aspect.ratio=0.5,
+        plot.margin = margin(t = 0, r = 0.2, b = 0, l = 0.2, unit = "cm"),
+        axis.title.x = element_text(face = "bold", size = 14),
+        axis.title.y = element_text(face = "bold", size = 14),
+        axis.text.x = element_text(size=14),
+        axis.text.y = element_text(size=14)
+        )
+ts_oa
 ggsave(filename = "figures/OmegaAragonite.png", plot = ts_oa, width = 15, height = 10, units = "cm")
 ggsave(filename = "figures/essd/OmegaAragonite.pdf", plot = ts_oa, width = 15, height = 10, units = "cm")
-
 ```

### 2023-05-25 awipev-CO2_presentation.qmd
prez update

--- 2022-03-31 awipev-CO2_presentation.Rmd
@@
 author: "Jean-Pierre Gattuso^1,2^, Samir Alliouane^1^ & Philipp Fisher^3^"
-date: '`r format(Sys.Date(), "%d %B %Y")`'
-output:
-  html_document:
-    # code_folding: show
-    #css: acid.css
-    fig_caption: no
-    #fig_width: 2
-    #fig_height: 2
-    highlight: default    
-    number_sections: no
-    #theme: yeti
-    theme: cerulean
-    toc: no
-    toc_float: no
-    fontsize: 32pt
-#language: Australian
-#css: acid.css
-## mainfont: PT Serif  
-## monofont: PT Mono
-#csl: frontiers.csl
-## sansfont: PT Sans
-#bibliography: ArcticKelp.bib
-## papersize: A4
+format:
+  revealjs:
+    smaller: true
+    scrollable: true
+editor: visual
 ---
-<!-- <style type="text/css"> -->
-<!-- .main-container { -->
-<!--   max-width: 100% !important; -->
-<!--   margin: auto; -->
-<!-- } -->
-<!-- </style> -->
-<style type="text/css">
-.main-container {
-  max-width: 100% !important;
-  margin: auto;
-}
-h1.title {
-  font-size: 50px;
-}
-body{
-  font-size: 24pt;
-}
-h1,h2,h3,h4,h5,h6{
-  font-size: 32pt;
-}
-h2,h3,h4,h5,h6{
-  font-size: 28pt;
-}
-.blackbox {
-  padding: 1em;
-  background: LightYellow;
-  color: black;
-  border: 0px solid orange;
-  border-radius: 10px;
-}
-.center {
-  text-align: center;
-}
-</style>
 
-^1^Laboratoire d'Océanographie de Villefranche, CNRS-Sorbonne Université\
-^2^Iddri, Sciences Po\
-^3^Alfred Wegener Institute for Polar and Marine Research\
+\^1\^Laboratoire d'Océanographie de Villefranche, CNRS-Sorbonne Université\\
+\^2\^Iddri, Sciences Po\\
+\^3\^Alfred Wegener Institute for Polar and Marine Research\\
 
-```{r set-up, echo=FALSE, warning=FALSE, message=FALSE, include=FALSE}
-  #if (Sys.getenv("LOGNAME") == "gattuso") path = "."
-```
+!\[\](images/AWIPEV-Logo.jpg){width="500px"}
 
-![](images/AWIPEV-Logo.jpg){width="500px"}
-
-<br><br><br><br><br><br><br><br><br><br><br><br><br>
-
-***
-
-:::: {.blackbox data-latex=""}
-
-# **Introduction**
+## **Introduction**
 
@@
 :::: {.blackbox data-latex=""}
-# **Instrumental set-up**
+## **Instrumental set-up**
 

### 2023-05-25 awipev-CO2_presentation.qmd
minor

@@
 
-\^1\^Laboratoire d'Océanographie de Villefranche, CNRS-Sorbonne Université\\
-\^2\^Iddri, Sciences Po\\
-\^3\^Alfred Wegener Institute for Polar and Marine Research\\
+\^1\^Laboratoire d'Océanographie de Villefranche, CNRS-Sorbonne Université\\ \^2\^Iddri, Sciences Po\\ \^3\^Alfred Wegener Institute for Polar and Marine Research\\
 
@@
 -   **Undersaturation** of surface water with respect to aragonite ﬁrst reported in 2008 in the Canada Basin; due to the decrease of salinity and degradation of organic matter
-- **No** fewer observations than elsewhere for carbonate variables: 11.6% of the SOCAT pCO<sub>2</sub> records and 9.1% of the GLODAP C<sub>T</sub> records are from the Arctic Ocean which is only about 4.3% of the global ocean surface
-<!-- - Coastal data relatively well represented in both products (25% and 10% of the SOCAT and SOCAT Arctic data, respectively) -->
+-   **No** fewer observations than elsewhere for carbonate variables: 11.6% of the SOCAT pCO<sub>2</sub> records and 9.1% of the GLODAP C<sub>T</sub> records are from the Arctic Ocean which is only about 4.3% of the global ocean surface <!-- - Coastal data relatively well represented in both products (25% and 10% of the SOCAT and SOCAT Arctic data, respectively) -->
 -   **Uneven time distribution**: 71.5% of the SOCAT pCO<sub>2</sub> data and 72% of the GLODAP C<sub>T</sub> data collected Jun-Sep. Few to very few data Dec-Mar.
-- Critical to document the changes but no high frequency multi-year time-series
-:::
+-   Critical to document the changes but no high frequency multi-year time-series :::
 
-***
+------------------------------------------------------------------------
 
@@
 
-![ ](images/map_fransner.png){width="50%"}
-![ ](images/pH_fransner.png){width="50%"}
+![](images/map_fransner.png){width="50%"} ![](images/pH_fransner.png){width="50%"}
 
-***
+------------------------------------------------------------------------
 
 # **Study location**
-![ ](images/map_platt.png)
+
+![](images/map_platt.png)
 
@@
 
-***
+------------------------------------------------------------------------
 
-:::: {.blackbox data-latex=""}
+::: {.blackbox data-latex=""}
 ## **Instrumental set-up**
@@
 
-:::: {style="display: flex;"}
-::: {class='col-md-4'}
-![ ](images/container.png)
+::: {style="display: flex;"}
+::: col-md-4
+![](images/container.png)
 :::
 
-::: {class='col-md-4'}
-![ ](images/intake.png)
+::: col-md-4
+![](images/intake.png)
 :::
 
-::: {class='col-md-4'}
-![ ](images/ferrybox.jpg)
+::: col-md-4
+![](images/ferrybox.jpg)
 :::
-::::
+:::
 
 ## **Instruments on the REMOS**
-![ ](images/seafet.png)
 
-***
+![](images/seafet.png)
+
+------------------------------------------------------------------------
 
 <!-- # No longer in real-time: https://awipev-co2.obs-vlfr.fr -->
+
 <!-- ![ ](images/web_page.png) -->
@@
 # **Availability of data**
-:::: {style="display: flex;"}
-::: {class='col-md-4'}
+
+::: {style="display: flex;"}
+::: col-md-4
 ## Many challenges:
@@
 :::
-::: {class='col-md-8'}
 
-![ ](figures/availability.png){ width=70% }
+::: col-md-8
+![](figures/availability.png){width="70%"}
 :::
-::::
+:::
 
-***
+------------------------------------------------------------------------
 
 # **Nutrients**
-:::: {style="display: flex;"}
-::: {class='col-md-4'}
 
+::: {style="display: flex;"}
+::: col-md-4
 -   90 phosphate and 133 silicate data kindly provided by van de Poll (unpubl.)
@@
 -   disregarding nutrients does not generate large differences:
-  - pCO2-AT pair, differences in pH, CT and OmegaA: < 0.001 unit, 0.7 umol/kg and <0.01
-  - CT-AT pair: differences in pH, pCO2 and OmegaA: 0.002 units, 1.5 uatm and <0.01
+    -   pCO2-AT pair, differences in pH, CT and OmegaA: \< 0.001 unit, 0.7 umol/kg and \<0.01
+    -   CT-AT pair: differences in pH, pCO2 and OmegaA: 0.002 units, 1.5 uatm and \<0.01
 :::
-::: {class='col-md-8'}
-![ ](figures/nutrients.png)
+
+::: col-md-8
+![](figures/nutrients.png)
 :::
-::::
+:::
 
-***
+------------------------------------------------------------------------
 
-:::: {.blackbox data-latex=""}
+::: {.blackbox data-latex=""}
 # **K1 and K2**
@@
 -   Big issue in the Arctic due to low temperature and salinity (Sulpis et al., 2020)
-- Lueker et al. (2000), which are recommended by the community (Jiang et al., 2022) derived in lab conditions with no temperature value < 2 °C. Overestimates K1 and K2 at temperatures below about 8 °C
-- Millero et al. (2002) and Sulpis et al. (2020) based on large (> 900) field data sets that include cold temperature values
+-   Lueker et al.
+(2000), which are recommended by the community (Jiang et al., 2022) derived in lab conditions with no temperature value \< 2 °C.
+Overestimates K1 and K2 at temperatures below about 8 °C
+-   Millero et al. (2002) and Sulpis et al. (2020) based on large (\> 900) field data sets that include cold temperature values
 -   Papadimitriou et al. (2018), obtained in the laboratory, also cover cold temperatures
@@
 
-***
+------------------------------------------------------------------------
 
 # **Total alkalinity vs salinity relationship**
+
 r2 = 0.81
 
-![ ](figures/p_at_s.png){ width=50% height=50% }
+![](figures/p_at_s.png){width="50%" height="50%"}
 
-***
+------------------------------------------------------------------------
 
 # **Time series of key variables**
-![ ](figures/time_series.png)
 
-***
+![](figures/time_series.png)
+
+------------------------------------------------------------------------
 
 # **Monthly means**
-![ ](figures/ts_boxplots.png)
 
-***
+![](figures/ts_boxplots.png)
+
+------------------------------------------------------------------------
 
@@
 <!-- ::: {style="text-align:center" markdown="1"} -->
-![ ](figures/pco2_calc_meas.png){ width=70% height=70% }
-<!-- ::: -->
 
-***
+![](figures/pco2_calc_meas.png){width="70%" height="70%"} <!-- ::: -->
+
+------------------------------------------------------------------------
 
@@
 
-:::: {style="display: flex;"}
-::: {class='col-md-5'}
-
+::: {style="display: flex;"}
+::: col-md-5
 -   Weird profiling approach
@@
 -   Density is almost always higher in the bottom than in the surface layer.
+:::
 
+::: col-md-5
+![](figures/deltas.png)
 :::
-::: {class='col-md-5'}
+:::
 
-  ![ ](figures/deltas.png)
-:::
-::::
+------------------------------------------------------------------------
 
-***
+# **Air-sea CO**<sub>2</sub> flux
 
-# **Air-sea CO<sub>2</sub> flux**
+![](figures/air-sea_CO2_flux.png)
 
-  ![ ](figures/air-sea_CO2_flux.png)
+------------------------------------------------------------------------
 
-***
-
-:::: {.blackbox data-latex=""}
+::: {.blackbox data-latex=""}
 # **Conclusion**
@@
     -   New regulation for the use HgCl<sub>2</sub> and transportation of poisoned samples
-
 :::
 
-  ***
+------------------------------------------------------------------------
 
-:::: {.blackbox data-latex=""}
+::: {.blackbox data-latex=""}
 # **Acknowledgements**

### 2023-05-29 awipev-CO2.Rmd
Kdrive path

@@
 #export latex table
-tables_path <- "~/kDrive/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/paper/tables/"
+tables_path <- "/Users/gattuso/kDrive/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised/tables"
 knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "latex") %>% 
@@
 #export latex table
-tables_path <- "~/kDrive/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/paper/tables/"
+tables_path <- "/Users/gattuso/kDrive/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised/tables"
 knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "latex") %>% 

### 2023-05-29 awipev-CO2.Rmd
refined paths

--- 2023-03-13 awipev-CO2.Rmd
@@
 #if (Sys.getenv("LOGNAME") == "gattuso") path = "../../pCloud\ Sync/Documents/experiments/exp168_awipev-CO2/"
-if (Sys.getenv("LOGNAME") == "gattuso") path = "../../kDrive/Documents/experiments/exp168_awipev-CO2/"
+#if (Sys.getenv("LOGNAME") == "gattuso") path = "../../kDrive/Documents/experiments/exp168_awipev-CO2/"
+
+# MacBook
+if (Sys.getenv("R_PLATFORM") == "aarch64-apple-darwin20") {
+  path = "../../kDrive/Documents/experiments/exp168_awipev-CO2/"
+  tables_path <- "/Users/gattuso/kDrive/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised/tables/"}
+#iMac Home
+if (Sys.getenv("R_PLATFORM") == "x86_64-apple-darwin20") {
+  path = "../../kDrive2/Documents/experiments/exp168_awipev-CO2/"
+  tables_path <- "/Users/gattuso/kDrive2/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised/tables/"}
+# Samir
 if (Sys.getenv("LOGNAME") == "samir") path = "../../pCloud\ Sync/exp168_awipev-CO2/"
@@
 #export latex table
-tables_path <- "~/kDrive/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/paper/tables/"
 knitr::kable(diff_table_pco2_at, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with pCO2 and AT using different formulations for K1 and K2.", format = "latex") %>% 
@@
 #export latex table
-tables_path <- "~/kDrive/Documents/publications/publications_inpreparation/gattuso_etal_awipev-CO2/paper/tables/"
 knitr::kable(diff_table_at_ct, digits = 3, caption = "Difference between spectrophotometric pH and pH calculated with AT and CT using different formulations for K1 and K2.", format = "latex") %>% 

### 2023-05-31 awipev-CO2.Rmd
Added chunk to calculate the time spent by REMOS at each depth group.

@@
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
+# we calculate the duration of each stop 
+depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
+tmp <- d_all %>% 
+  dplyr::select(datetime, depth_group) %>%
+  dplyr::filter(depth_group != "NA") %>% 
+  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
+```
+
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 size_labs = 14

### 2023-05-31 awipev-CO2.Rmd
refined new chunk

--- 2023-05-29 awipev-CO2.Rmd
@@
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
+# we calculate the duration of each stop
+
+# Function written by Robert Schlegel
+depth_time <- function(df){
+  # Get proto event info
+  ex1 <- rle(as.numeric(df$depth_group))
+  ind1 <- rep(seq_along(ex1$lengths), ex1$lengths)
+  s1 <- base::split(base::seq_len(nrow(df)), ind1)
+  # Extract the start and end times per depth group
+  depth_count <- do.call(rbind, lapply(s1, function(x)
+    data.frame(depth_group = tmp$depth_group[min(x)],
+               time_start = tmp$datetime[min(x)], 
+               time_end = tmp$datetime[max(x)])))
+  # Calculate the time spent there in seconds
+  depth_count$time_spent <- depth_count$time_end-depth_count$time_start+3600
+  # Convert to hours if desired
+  depth_count$hours_spent <- as.numeric(depth_count$time_spent)/3600
+  # Exit
+  return(depth_count)
+}
+
+# First create the tibble
+depth_labels <- c("0-2", "2-4", "4-6", "6-8", ">8")
+tmp <- d_all %>% 
+  dplyr::select(datetime, depth_group) %>%
+  dplyr::filter(depth_group != "NA") %>% 
+  dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
+
+count_depth <- depth_time(tmp) 
+plot_all_depths <- count_depth %>% 
+  ggplot() +
+  geom_bar(aes(x=hours_spent))
+plot_all_depths
+```
+
+```{r, echo=FALSE, message= FALSE, warning=FALSE}
 size_labs = 14

### 2023-05-31 awipev-CO2.Rmd
minor change path totables

@@
   path = "../../kDrive/Documents/experiments/exp168_awipev-CO2/"
-  tables_path <- "/Users/gattuso/kDrive/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised/tables/"}
+  tables_path <- "/Users/gattuso/kDrive/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised1/tables/"}
 #iMac Home
@@
   path = "../../kDrive2/Documents/experiments/exp168_awipev-CO2/"
-  tables_path <- "/Users/gattuso/kDrive2/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised/tables/"}
+  tables_path <- "/Users/gattuso/kDrive2/Documents/publications/publications_submitted/2023_gattuso_etal_essd/revised1/tables/"}
 # Samir

### 2023-06-02 awipev-CO2.Rmd
Time spent at each depth group Various updates in figures for ESSD

@@
 
-## Stratification
-
-### Stratification salinity
+## Stratification {.tabset .tabset-pills}
+
+### REMOS
 
@@
   dplyr::select(datetime, depth_group) %>%
-  dplyr::filter(depth_group != "NA") %>% 
+#  dplyr::filter(depth_group != "NA") %>% 
   dplyr::mutate(depth_group = factor(depth_group, levels = depth_labels))
 
-count_depth <- depth_time(tmp) 
-plot_all_depths <- count_depth %>% 
-  ggplot() +
-  geom_bar(aes(x=hours_spent))
-plot_all_depths
-```
-
+count_depth <- depth_time(tmp) %>% 
+  dplyr::filter(depth_group != "NA")
+p <- ggplot(count_depth) +
+  geom_bar(aes(x=log10(hours_spent)))
+ggsave(filename = "figures/REMOS.png", plot = p, width = 15, height = 10, units = "cm")
+
+```
+The REMOS spent a highly variable period of time in each depth group.
+![Distribution of the number of hours spent by the REMOS at depth](figures/REMOS.png)
+`r knitr::kable(summary(count_depth$hours_spent))`
+
+### Stratification salinity
 ```{r, echo=FALSE, message= FALSE, warning=FALSE}
@@
   geom_point(colour="blue", alpha = alpha, na.rm = TRUE, size = size_point) +
-  labs(title="A",x=NULL, y="Salinity") +
+  labs(title="A",x=NULL, y="Salinity (< 8 m)") +
   scale_y_continuous(limits = c(31.8, 35.5)) +
@@
         axis.ticks.y = element_line(size = 0.5)
-        ) #+
+        )
+# to change color of median line
+tmp <- ggplot_build(ts_sal_bp)$data[[1]]
+ts_sal_bp <- ts_sal_bp + geom_segment(data=tmp, aes(x=xmin, xend=xmax, 
+                               y=middle, yend=middle), colour="cyan", size=1)
+
+#+
   # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"), 
@@
   #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
-
+# to change color of median line
+tmp <- ggplot_build(ts_temp_bp)$data[[1]]
+ts_temp_bp <- ts_temp_bp + geom_segment(data=tmp, aes(x=xmin, xend=xmax, 
+                               y=middle, yend=middle), colour="cyan", size=1)
 ts_pco2_bp <- d_bp %>%
@@
   #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
+# to change color of median line
+tmp <- ggplot_build(ts_pco2_bp)$data[[1]]
+ts_pco2_bp <- ts_pco2_bp + geom_segment(data=tmp, aes(x=xmin, xend=xmax, 
+                               y=middle, yend=middle), colour="cyan", size=1)
+
 ts_pH_bp <- d_bp %>%
@@
   #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
-
+# to change color of median line
+tmp <- ggplot_build(ts_pH_bp)$data[[1]]
+ts_pH_bp <- ts_pH_bp + geom_segment(data=tmp, aes(x=xmin, xend=xmax, 
+                               y=middle, yend=middle), colour="cyan", size=1)
 ts_at_bp <- d_bp %>%
@@
                    labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
+# to change color of median line
+tmp <- ggplot_build(ts_at_bp)$data[[1]]
+ts_at_bp <- ts_at_bp + geom_segment(data=tmp, aes(x=xmin, xend=xmax, 
+                               y=middle, yend=middle), colour="cyan", size=1)
+
 # Combine plots

### 2023-06-02 awipev-CO2.Rmd
Added air-sea CO2 flux estimates with Dobashi

@@
 ggsave(filename = "figures/REMOS.png", plot = p, width = 15, height = 10, units = "cm")
-
+summary(count_depth$hours_spent)
 ```
@@
 ![Distribution of the number of hours spent by the REMOS at depth](figures/REMOS.png)
-`r knitr::kable(summary(count_depth$hours_spent))`
 
@@
     delta_pco2 = pco2_fb_ctd_temp - co2_air, # uatm
-    k600 = 0.266 * ws ^ 2, # cm/h Ho et al. (2006)
+    k600h = 0.266 * ws ^ 2, # cm/h Ho et al. (2006)
+    k600d = 0.143 * ws ^ 2, # cm/h Dobashi and Ho (2023)
     Sc = 2073.1 - (125.62 * temp_insitu_ctd) + (3.6276 * temp_insitu_ctd^2) -
       (0.043219 * temp_insitu_ctd^3),    #dimensionless
-    k = (k600 * (Sc / 600) ^ -0.5), #cm/h
-    k = k/10, #m/h
+    kh = (k600h * (Sc / 600) ^ -0.5), #cm/h
+    kd = (k600d * (Sc / 600) ^ -0.5), #cm/h
+   kh = kh/10, #m/h
+   kd = kd/10, #m/h
     alpha = seacarb::K0(
@@
     alpha = alpha * (seacarb::rho(
-      S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0
-    ) / 1000), # mol/(l atm)
+      S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0) / 1000), # mol/(l atm)
     alpha = alpha * 1000 , # mol/(m3 atm)
-    f_air_sea = k * alpha * delta_pco2, # mol/(m2 h 1e6)
-    f_air_sea = k * alpha * delta_pco2 * 1e-6 * 1000 # mmol/(m2 h)
-  )
-
-p_f_air_sea <- ggplot(data = d_all) +
-  geom_point(aes(x = datetime, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
-  labs(title = "Air-sea CO2 flux (all data)", x = "Time", y = "CO2 (mmol/(m2 h))") +
+    f_air_sea_h = kh * alpha * delta_pco2, # mol/(m2 h 1e6)
+    f_air_sea_h = kh * alpha * delta_pco2 * 1e-6 * 1000, # mmol/(m2 h)
+    f_air_sea_d = kd * alpha * delta_pco2, # mol/(m2 h 1e6)
+    f_air_sea_d = kd * alpha * delta_pco2 * 1e-6 * 1000 # mmol/(m2 h)
+  )
+
+p_f_air_sea_h <- ggplot(data = d_all) +
+  geom_point(aes(x = datetime, y = f_air_sea_h), col = "blue", size = 0.15, na.rm = TRUE) +
+  labs(title = "Air-sea CO2 flux (all data) with Ho's formulation", x = "Time", y = "CO2 (mmol/(m2 h))") +
   Mytheme(size_labs = 8)
-p_f_air_sea
-ggsave(filename = "figures/p_f_air_sea.png", plot = p_f_air_sea, width = 20, units = "cm")
-
-air_sea_day <- d_all %>%
-  dplyr::select(datetime, f_air_sea) %>%
+p_f_air_sea_h
+ggsave(filename = "figures/p_f_air_sea_h.png", plot = p_f_air_sea_h, width = 20, units = "cm")
+
+air_sea_day_h <- d_all %>%
+  dplyr::select(datetime, f_air_sea_h) %>%
   dplyr::group_by(lubridate::yday(datetime)) %>%
-  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)) %>% #mmol/(m2 d)
+  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_h, na.rm = TRUE)) %>% #mmol/(m2 d)
   ungroup() %>%
@@
 
-p_f_air_sea_d <- ggplot(data = air_sea_day) +
+p_f_air_sea_day_h <- ggplot(data = air_sea_day_h) +
   geom_point(aes(x = day, y = f_air_sea), col = "blue", size = 0.15, na.rm = TRUE) +
-  labs(title = "Air-sea CO2 flux (per day)", x = "Julian day", y = "CO2 (mmol/(m2 d))") +
+  labs(title = "Air-sea CO2 flux (per day) with Ho's formulation", x = "Julian day", y = "CO2 (mmol/(m2 d))") +
   Mytheme(size_labs = 8)
 #p_f_air_sea_d
-ggsave(filename = "figures/f_air_sea_d.png", plot = p_f_air_sea_d, width = 20, units = "cm")
-
-air_sea_month <- d_all %>%
-  dplyr::select(monthd, f_air_sea) %>%
+ggsave(filename = "figures/f_air_sea_day_h.png", plot = p_f_air_sea_day_h, width = 20, units = "cm")
+
+air_sea_month_h <- d_all %>%
+  dplyr::select(monthd, f_air_sea_h) %>%
   dplyr::group_by(monthd) %>%
-  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea, na.rm = TRUE)) %>% #mmol/(m2 d)
+  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_h, na.rm = TRUE)) %>% #mmol/(m2 d)
   ungroup() %>%
@@
 #air_sea_month
-p_f_air_sea_month <- ggplot(data = air_sea_month) +
+p_f_air_sea_month_h <- ggplot(data = air_sea_month_h) +
   geom_point(aes(x = montht, y = f_air_sea), col = "blue", size = 2, na.rm = TRUE) +
   lims(y = c(-3000, 0)) +
-  labs(title = "Air-sea CO2 flux (per month)", x = "Month", y = "CO2 (mmol/(m2 month))") +
+  labs(title = "Air-sea CO2 flux (per month) with Ho's formulation", x = "Month", y = "CO2 (mmol/(m2 month))") +
   Mytheme(size_labs = 8)
-ggsave(filename = "figures/f_air_sea_m.png", plot = p_f_air_sea_month, width = 20, units = "cm")
-
-p <- p_f_air_sea / p_f_air_sea_d / p_f_air_sea_month
-ggsave(filename = "figures/air-sea_CO2_flux.png", plot = p, width = 20, units = "cm")
-knitr::include_graphics("figures/air-sea_CO2_flux.png")
-
-# For paper
+ggsave(filename = "figures/f_air_sea_m_h.png", plot = p_f_air_sea_month_h, width = 20, units = "cm")
+
+p <- p_f_air_sea_h / p_f_air_sea_day_h / p_f_air_sea_month_h
+ggsave(filename = "figures/air-sea_CO2_flux_h.png", plot = p, width = 20, units = "cm")
+knitr::include_graphics("figures/air-sea_CO2_flux_h.png")
+
+# For paper Ho only
 size_point <- 1.5 # size of data points
@@
 # temp_insitu_11m
-ts_air_sea <- air_sea_month %>%
-  ggplot(aes(x = montht, y = f_air_sea / 1000), na.rm = TRUE) +
+tmp <- d_all %>% 
+  dplyr::select(montht, f_air_sea_h)
+ts_air_sea_h <- tmp %>%
+  ggplot(aes(x = montht, y = f_air_sea_h / 1000), na.rm = TRUE) +
   geom_col(colour="blue", fill = "blue",  alpha = alpha) +
-  lims(y = c(-3, 0)) +
+  lims(y = c(-5, 0)) +
   geom_hline(yintercept = 0) +
@@
                    labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
+ts_air_sea_h
+ggsave(filename = "figures/ts_air_sea_h.png", plot = ts_air_sea_h, width = 20, units = "cm")
+ggsave(filename = "figures/essd/ts_air_sea_h.pdf", plot = ts_air_sea_h, width = 15, height = 10, units = "cm")
+
+# For paper Dobashi & Ho 
+# Above, only Ho's formulation is dealt with
+# make tibble for Dobashi's formulation to be used in plot
+air_sea_month_d <- d_all %>%
+  dplyr::select(monthd, f_air_sea_d) %>%
+  dplyr::group_by(monthd) %>%
+  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_d, na.rm = TRUE)) %>% #mmol/(m2 d)
+  ungroup() %>%
+  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
+  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
+# air_sea_month_d <- d_all %>%
+#   dplyr::select(monthd, f_air_sea_d) %>%
+#   dplyr::group_by(monthd) %>%
+#   dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_d, na.rm = TRUE)) %>% #mmol/(m2 d)
+#   ungroup() %>%
+#   dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
+#   dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
+
+# Now we combine Ho's and Dobashi's formulations
+air_sea_month_h <- air_sea_month_h %>% 
+  dplyr::rename(f_air_sea_h = f_air_sea) %>% 
+  dplyr::select(-monthd)
+air_sea_month_d <- air_sea_month_d %>% 
+  dplyr::rename(f_air_sea_d = f_air_sea) %>% 
+  dplyr::select(-monthd)
+air_sea <- dplyr::left_join(air_sea_month_h, air_sea_month_d) 
+air_sea_long <- air_sea %>% 
+  pivot_longer(!montht, names_to = "Formulation", values_to = "f_air_sea")
+
+size_point <- 1.5 # size of data points
+alpha <- 1 #transparency
+size_labs <- 14 # font size labels
+# temp_insitu_11m
+ts_air_sea <- air_sea_long %>%
+  ggplot(aes(x = montht, y = f_air_sea / 1000, fill = Formulation), na.rm = TRUE) +
+  geom_col(alpha = alpha, position = "dodge") +
+  lims(y = c(-3, 0)) +
+  geom_hline(yintercept = 0) +
+  labs(title=NULL, 
+       x="Month", 
+       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
+  scale_fill_discrete(name = "", labels = c("Dobashi & Ho (2023)", "Ho et al. (2006)")) +
+  Mytheme(size_labs = size_labs) +
+  theme(aspect.ratio=0.5,
+        plot.margin = margin(t = -10, r = 0.2, b = -10, l = 0.2, unit = "cm"),
+        axis.title.x = element_text(face = "bold", size = 14),
+        axis.title.y = element_text(face = "bold", size = 14),
+        axis.text.x = element_text(size=14),
+        axis.text.y = element_text(size=14)
+        ) 
+  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
+  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
 ts_air_sea
@@
 ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea, width = 15, height = 10, units = "cm")
-#rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
 ```
@@
   dplyr::mutate(
-    delta_pco2_corr = (pco2_fb_ctd_temp + 17) - co2_air,
-    k600 = 0.266 * ws ^ 2, # cm/h Ho et al. (2006)
+    delta_pco2_corr = (pco2_fb_ctd_temp + 17) - co2_air, # uatm
+    k600h = 0.266 * ws ^ 2, # cm/h Ho et al. (2006)
+    k600d = 0.143 * ws ^ 2, # cm/h Dobashi and Ho (2023)
     Sc = 2073.1 - (125.62 * temp_insitu_ctd) + (3.6276 * temp_insitu_ctd^2) -
       (0.043219 * temp_insitu_ctd^3),    #dimensionless
-    k = (k600 * (Sc / 600) ^ -0.5), #cm/h
-    k = k/10, #m/h
+    kh = (k600h * (Sc / 600) ^ -0.5), #cm/h
+    kd = (k600d * (Sc / 600) ^ -0.5), #cm/h
+   kh = kh/10, #m/h
+   kd = kd/10, #m/h
     alpha = seacarb::K0(
@@
     alpha = alpha * (seacarb::rho(
-      S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0
-    ) / 1000), # mol/(l atm)
+      S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0) / 1000), # mol/(l atm)
     alpha = alpha * 1000 , # mol/(m3 atm)
-    f_air_sea_corr = k * alpha * delta_pco2_corr, # mol/(m2 h 1e6)
-    f_air_sea_corr = k * alpha * delta_pco2_corr * 1e-6 * 1000 # mmol/(m2 h)
-  )
-air_sea_corr_month <- d_all %>%
-  dplyr::select(monthd, f_air_sea_corr) %>%
+    f_air_sea_h_corr = kh * alpha * delta_pco2_corr, # mol/(m2 h 1e6)
+    f_air_sea_h_corr = kh * alpha * delta_pco2_corr * 1e-6 * 1000, # mmol/(m2 h)
+    f_air_sea_d_corr = kd * alpha * delta_pco2_corr, # mol/(m2 h 1e6)
+    f_air_sea_d_corr = kd * alpha * delta_pco2_corr * 1e-6 * 1000 # mmol/(m2 h)
+  )
+
+air_sea_month_h_corr <- d_all %>%
+  dplyr::select(monthd, f_air_sea_h_corr) %>%
   dplyr::group_by(monthd) %>%
-  dplyr::summarise(f_air_sea_corr = 24 * mean(f_air_sea_corr, na.rm = TRUE)) %>% #mol/(m2 d)
+  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_h_corr, na.rm = TRUE)) %>% #mmol/(m2 d)
   ungroup() %>%
-  dplyr::mutate(f_air_sea_corr = days_in_month(monthd) * f_air_sea_corr) %>% 
+  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
   dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
-#air_sea_month
-p_f_air_sea_corr_month <- ggplot(data = air_sea_corr_month) +
-  geom_point(aes(x = montht, y = f_air_sea_corr), col = "blue", size = 2, na.rm = TRUE) +
-  #scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
-  #lims(y = c(-3, 0)) +
-  labs(title = "Air-sea CO2 flux (per month) with corrected data", x = "Month", y = "CO2 (mmol/(m2 month))") +
-  Mytheme(size_labs = 8)
-p_f_air_sea_corr_month
-ggsave(filename = "figures/f_air_sea_corr_month.png", plot = p_f_air_sea_corr_month, width = 20, units = "cm")
-# # combine without and with correction
-# p <- p_f_air_sea_month / p_f_air_sea_corr_month
-# ggsave(filename = "figures/air-sea_CO2_flux_comp.png", plot = p, width = 20, units = "cm")
-# knitr::include_graphics("figures/air-sea_CO2_flux_comp.png")
-#rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
-# Figure with and without correction on same plot
+
+# For paper Dobashi & Ho 
+# Above, only Ho's formulation is dealt with
+# make tibble for Dobashi's formulation to be used in plot
+air_sea_month_d_corr <- d_all %>%
+  dplyr::select(monthd, f_air_sea_d_corr) %>%
+  dplyr::group_by(monthd) %>%
+  dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_d_corr, na.rm = TRUE)) %>% #mmol/(m2 d)
+  ungroup() %>%
+  dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
+  dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
+
+# air_sea_month_d <- d_all %>%
+#   dplyr::select(monthd, f_air_sea_d) %>%
+#   dplyr::group_by(monthd) %>%
+#   dplyr::summarise(f_air_sea = 24 * mean(f_air_sea_d, na.rm = TRUE)) %>% #mmol/(m2 d)
+#   ungroup() %>%
+#   dplyr::mutate(f_air_sea = days_in_month(monthd) * f_air_sea) %>% 
+#   dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
+
+# Now we combine Ho's and Dobashi's formulations
+air_sea_month_h_corr <- air_sea_month_h_corr %>% 
+  dplyr::rename(f_air_sea_h_corr = f_air_sea) %>% 
+  dplyr::select(-monthd)
+air_sea_month_d_corr <- air_sea_month_d_corr %>% 
+  dplyr::rename(f_air_sea_d_corr = f_air_sea) %>% 
+  dplyr::select(-monthd)
+air_sea <- dplyr::left_join(air_sea_month_h_corr, air_sea_month_d_corr) 
+air_sea_long <- air_sea %>% 
+  pivot_longer(!montht, names_to = "Formulation", values_to = "f_air_sea")
+
+size_point <- 1.5 # size of data points
+alpha <- 1 #transparency
+size_labs <- 14 # font size labels
+# temp_insitu_11m
+ts_air_sea_corr <- air_sea_long %>%
+  ggplot(aes(x = montht, y = f_air_sea / 1000, fill = Formulation), na.rm = TRUE) +
+  geom_col(alpha = alpha, position = "dodge") +
+  lims(y = c(-3, 0)) +
+  geom_hline(yintercept = 0, size = 0.5) +
+  labs(title=NULL, 
+       x="Month", 
+       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
+  scale_fill_discrete(name = "", labels = c("Dobashi & Ho (2023)", "Ho et al. (2006)")) +
+  Mytheme(size_labs = size_labs) +
+  theme(aspect.ratio=0.5,
+        plot.margin = margin(t = -10, r = 0.2, b = -10, l = 0.2, unit = "cm"),
+        axis.title.x = element_text(face = "bold", size = 14),
+        axis.title.y = element_text(face = "bold", size = 14),
+        axis.text.x = element_text(size=14),
+        axis.text.y = element_text(size=14)
+        ) 
+  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
+  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
+ts_air_sea_corr
+ggsave(filename = "figures/ts_air_sea_corr.png", plot = ts_air_sea_corr, width = 20, units = "cm")
+ggsave(filename = "figures/essd/ts_air_sea_corr.pdf", plot = ts_air_sea_corr, width = 15, height = 10, units = "cm")
+
+# d_all <- d_all %>%
+#   dplyr::mutate(
+#     delta_pco2_corr = (pco2_fb_ctd_temp + 17) - co2_air,
+#     k600 = 0.266 * ws ^ 2, # cm/h Ho et al. (2006)
+#     Sc = 2073.1 - (125.62 * temp_insitu_ctd) + (3.6276 * temp_insitu_ctd^2) -
+#       (0.043219 * temp_insitu_ctd^3),    #dimensionless
+#     k = (k600 * (Sc / 600) ^ -0.5), #cm/h
+#     k = k/10, #m/h
+#     alpha = seacarb::K0(
+#       S = sal_insitu_ctd,
+#       T = temp_insitu_ctd,
+#       P = 0,
+#       Patm = p_air / 1013.25 # from hPa to atm
+#     ), #mol/(kg atm)
+#     alpha = alpha * (seacarb::rho(
+#       S = sal_insitu_ctd, T = temp_insitu_ctd, P = 0
+#     ) / 1000), # mol/(l atm)
+#     alpha = alpha * 1000 , # mol/(m3 atm)
+#     f_air_sea_corr = k * alpha * delta_pco2_corr, # mol/(m2 h 1e6)
+#     f_air_sea_corr = k * alpha * delta_pco2_corr * 1e-6 * 1000 # mmol/(m2 h)
+#   )
+# air_sea_corr_month <- d_all %>%
+#   dplyr::select(monthd, f_air_sea_corr) %>%
+#   dplyr::group_by(monthd) %>%
+#   dplyr::summarise(f_air_sea_corr = 24 * mean(f_air_sea_corr, na.rm = TRUE)) %>% #mol/(m2 d)
+#   ungroup() %>%
+#   dplyr::mutate(f_air_sea_corr = days_in_month(monthd) * f_air_sea_corr) %>% 
+#   dplyr::mutate(montht = month(monthd, label = TRUE, abbr = TRUE))
+# #air_sea_month
+# p_f_air_sea_corr_month <- ggplot(data = air_sea_corr_month) +
+#   geom_point(aes(x = montht, y = f_air_sea_corr), col = "blue", size = 2, na.rm = TRUE) +
+#   #scale_x_discrete(breaks=c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", "")) +
+#   #lims(y = c(-3, 0)) +
+#   labs(title = "Air-sea CO2 flux (per month) with corrected data", x = "Month", y = "CO2 (mmol/(m2 month))") +
+#   Mytheme(size_labs = 8)
+# p_f_air_sea_corr_month
+# ggsave(filename = "figures/f_air_sea_corr_month.png", plot = p_f_air_sea_corr_month, width = 20, units = "cm")
+# # # combine without and with correction
+# # p <- p_f_air_sea_month / p_f_air_sea_corr_month
+# # ggsave(filename = "figures/air-sea_CO2_flux_comp.png", plot = p, width = 20, units = "cm")
+# # knitr::include_graphics("figures/air-sea_CO2_flux_comp.png")
+# #rm(p, p_f_air_sea, p_f_air_sea_d, p_f_air_sea_m)
+# # Figure with and without correction on same plot
 ```
@@
 ```{r monthly air-sea for paper, echo=FALSE, message= FALSE, warning=FALSE}
-air_sea_month$corr <- rep("no", length=12)
-air_sea_corr_month$corr <- rep("yes", length=12)
-
-air_sea <- dplyr::left_join(air_sea_month, air_sea_corr_month, by = "montht") %>% 
-  #dplyr::mutate(air_sea_corr_month = air_sea_corr_month/1000) %>% 
-  dplyr::select(montht, f_air_sea, f_air_sea_corr) %>% 
-  tidyr::pivot_longer(!montht, names_to = "corr", values_to = "air_sea")
-ggplot(data = air_sea) +
-  geom_point(aes(x = montht, y = air_sea, colour = factor(corr)))
-```
-
-The annual air-sea CO2 flux is
-`r round(sum(air_sea_month$f_air_sea/1000), digits = 1)` and
-`r round(sum(air_sea_corr_month$f_air_sea_corr/1000), digits = 1)` mol CO2/(m2
-year) without and with correction, respectively. Or `r round(sum(air_sea_month$f_air_sea*(12/44)/1000), digits = 1)` and
-`r round(sum(air_sea_corr_month$f_air_sea_corr*(12/44)/1000), digits = 1)` mol C/(m2
+# air_sea_month$corr <- rep("no", length=12)
+# air_sea_corr_month$corr <- rep("yes", length=12)
+# 
+# air_sea <- dplyr::left_join(air_sea_month, air_sea_corr_month, by = "montht") %>% 
+#   #dplyr::mutate(air_sea_corr_month = air_sea_corr_month/1000) %>% 
+#   dplyr::select(montht, f_air_sea, f_air_sea_corr) %>% 
+#   tidyr::pivot_longer(!montht, names_to = "corr", values_to = "air_sea")
+# ggplot(data = air_sea) +
+#   geom_point(aes(x = montht, y = air_sea, colour = factor(corr)))
+```
+
+The annual air-sea CO2 flux with the Ho et al. (2006) formulation is
+`r round(sum(air_sea_month_h$f_air_sea_h/1000), digits = 1)` and
+`r round(sum(air_sea_month_h_corr$f_air_sea_h_corr/1000), digits = 1)` mol CO2/(m2
+year) without and with correction, respectively. Or `r round(sum(air_sea_month_h$f_air_sea_h*(12/44)/1000), digits = 1)` and
+`r round(sum(air_sea_month_h_corr$f_air_sea_h_corr*(12/44)/1000), digits = 1)` mol C/(m2
+year)
+
+The annual air-sea CO2 flux with the Dobashi et al. (2023) formulation is
+`r round(sum(air_sea_month_d$f_air_sea_d/1000), digits = 1)` and
+`r round(sum(air_sea_month_d_corr$f_air_sea_d_corr/1000), digits = 1)` mol CO2/(m2
+year) without and with correction, respectively. Or `r round(sum(air_sea_month_d$f_air_sea_d*(12/44)/1000), digits = 1)` and
+`r round(sum(air_sea_month_d_corr$f_air_sea_d_corr*(12/44)/1000), digits = 1)` mol C/(m2
 year)

### 2023-06-03 awipev-CO2.Rmd
Fig. air-sea flux for paper

@@
 ggsave(filename = "figures/ts_air_sea_corr.png", plot = ts_air_sea_corr, width = 20, units = "cm")
-ggsave(filename = "figures/essd/ts_air_sea_corr.pdf", plot = ts_air_sea_corr, width = 15, height = 10, units = "cm")
+#ggsave(filename = "figures/essd/ts_air_sea_corr.pdf", plot = ts_air_sea_corr, units = "cm")
 
@@
 ```{r monthly air-sea for paper, echo=FALSE, message= FALSE, warning=FALSE}
-# air_sea_month$corr <- rep("no", length=12)
-# air_sea_corr_month$corr <- rep("yes", length=12)
-# 
-# air_sea <- dplyr::left_join(air_sea_month, air_sea_corr_month, by = "montht") %>% 
-#   #dplyr::mutate(air_sea_corr_month = air_sea_corr_month/1000) %>% 
-#   dplyr::select(montht, f_air_sea, f_air_sea_corr) %>% 
-#   tidyr::pivot_longer(!montht, names_to = "corr", values_to = "air_sea")
-# ggplot(data = air_sea) +
-#   geom_point(aes(x = montht, y = air_sea, colour = factor(corr)))
+ts_air_sea <- air_sea_long %>%
+  ggplot(aes(x = montht, y = f_air_sea / 1000, fill = Formulation), na.rm = TRUE) +
+  geom_col(alpha = alpha, position = "dodge") +
+  lims(y = c(-3, 0)) +
+  geom_hline(yintercept = 0, size = 0.5) +
+  labs(title=NULL, 
+       x="Month", 
+       y=latex2exp::TeX("Air-sea CO$_2$ flux (mol $m^{-2}$ month$^{-1}$)", bold = TRUE)) +
+  scale_fill_discrete(name = "", labels = c("Dobashi & Ho (2023)", "Ho et al. (2006)")) +
+  Mytheme(size_labs = size_labs) +
+  theme(aspect.ratio=0.5,
+        plot.margin = margin(t = -10, r = 0.2, b = -10, l = 0.2, unit = "cm"),
+        axis.title.x = element_text(face = "bold", size = 14),
+        axis.title.y = element_text(face = "bold", size = 14),
+        axis.text.x = element_text(size=14),
+        axis.text.y = element_text(size=14)
+        ) 
+  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
+  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
+ts_air_sea_corr
+ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea_corr, units = "cm")
 ```

### 2023-06-03 awipev-CO2.Rmd
New fig air-sea for manuscript

@@
 size_labs <- 14 # font size labels
-# temp_insitu_11m
 ts_air_sea_corr <- air_sea_long %>%
@@
 ```{r monthly air-sea for paper, echo=FALSE, message= FALSE, warning=FALSE}
+size_point <- 1.5 # size of data points
+alpha <- 1 #transparency
+size_labs <- 14 # font size labels
 ts_air_sea <- air_sea_long %>%
@@
     Mytheme(size_labs = size_labs) +
-  theme(aspect.ratio=0.5,
-        plot.margin = margin(t = -10, r = 0.2, b = -10, l = 0.2, unit = "cm"),
-        axis.title.x = element_text(face = "bold", size = 14),
-        axis.title.y = element_text(face = "bold", size = 14),
-        axis.text.x = element_text(size=14),
-        axis.text.y = element_text(size=14)
-        ) 
-  # scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
-  #                  labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
-ts_air_sea_corr
-ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea_corr, units = "cm")
+  theme(panel.grid.major.x = element_blank(),
+        #axis.text.x=element_blank(),
+        #axis.text.y=element_blank(),
+        axis.title.x = element_text(face = "bold", size = size_labs),
+        #axis.label.x = element_text(face = "bold", size = size_labs),
+        axis.title.y = element_text(face = "bold", size = size_labs),
+        title = element_text(colour="black", size=14, face="bold"),
+        axis.ticks.length.y = unit(.2, "cm"),
+        axis.ticks.length.x = unit(.2, "cm"),
+        axis.ticks.x = element_line(size = 0.5),
+        axis.ticks.y = element_line(size = 0.5),
+        aspect.ratio=0.5,
+        plot.margin = margin(t = 0, r = 0.2, b = 0, l = 0.2, unit = "cm"),
+        legend.position = "top",
+        legend.text = element_text(size=size_labs),
+        legend.background = element_rect("transparent")
+        ) +
+  scale_x_discrete(breaks = c("Jan", "Feb", "Mar", "Apr", "May", "Jun", "Jul", "Aug", "Sep", "Oct", "Nov", "Dec"),
+                   labels = c("Jan", "", "Mar", "", "May", "", "Jul", "", "Sep", "", "Nov", ""))
+ts_air_sea
+ggsave(filename = "figures/essd/ts_air_sea.pdf", plot = ts_air_sea, width = 15, height = 10, units = "cm")
 ```
